### 2023-03-03 paper/main.tex
Updated title/authors and started writing problem statement

\documentclass{article}

%\title{Investigatin Uncertainty Quantification in Model-based Reinforcement Learning}
\title{Model-based Reinforcement Learning with Fast Posterior Updates}
\author{%
  Aidan ~Scannell \\
  Aalto University\\
  %Finnish Center for Artificial Intelligence \\
  \texttt{aidan.scannell@aalto.fi}
  \And
  Paul ~Chang \\
  Aalto University\\
  \texttt{paul.chang@aalto.fi}
  \And
  Ella ~Tamir \\
  Aalto University\\
  \texttt{ella.tamir@aalto.fi}
  \And
  Arno ~Solin \\
  Aalto University\\
  \texttt{arno.solin@aalto.fi}
  \And
  Joni ~Pajarinen \\
  Aalto University\\
  \texttt{joni.pajarinen@aalto.fi}
  % examples of more authors
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

% NeurIPS packages
\usepackage[preprint,nonatbib]{neurips_2022}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
%\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors

% Bibliography
\usepackage[maxcitenames=1, maxbibnames=4, doi=false, isbn=false, eprint=true, backend=bibtex, hyperref=true, url=false, style=authoryear-comp]{biblatex}
\addbibresource{zotero-library.bib}
% \addbibresource{paper/zotero-library.bib}

% Our packages
\usepackage{todonotes}
\usepackage[colorlinks=true,linkcolor=blue,allcolors=blue]{hyperref}
\usepackage{amsmath}
\usepackage{bm}

\usepackage{tikz,pgfplots}
\usepackage{subcaption}
\usetikzlibrary{}

% This must be imported last!
%\usepackage{cleveref}
\usepackage[capitalise,nameinlink]{cleveref}

% Config for Arno's awesome TikZ plotting stuff
\newlength{\figurewidth}
\newlength{\figureheight}

\begin{document}

\maketitle

\begin{abstract}
  %Reinforcement learning (RL) agents typically perform learning after an episode and do not utilise the information gained during an episode.
  Reinforcement learning (RL) agents typically perform learning after an episode and do not utilise the information gained during an episode.
  We present a Bayesian model-based RL algorithm which incorporates this information by updating its dynamic model's posterior during an episode.
  We prove that for stationary dynamic model priors, our method achieves sublinear regret, i.e. it will converge to the optimal policy.
  Importantly, our dynamic model (and it's converge guarantees) scales to high dimensional problems via neural networks with stationary priors.
  We demonstrate that our fast posterior updates lead to improved sample efficiency in environments with action penalties, a notoriously difficult
  challenge for model-based RL algorithms.

  % Model-based reinforcement learning (RL) typically learns
\end{abstract}

\section{Introduction} \label{sec:intro}

\section{Problem Statement and Background} \label{sec:problem-statement}
We consider environments with states \(s \in \mathcal{S}\), actions \(a \in \mathcal{A}\) and transition dynamics \(f: \mathcal{S} \times \mathcal{A} \rightarrow \mathcal{S}\) subject to
iid noise \(\epsilon_{t}\), given by,
\begin{align}
s_{t+1} = f(s_{t}, a_{t}) + \epsilon_{t}.
\end{align}

\textbf{Reinforcement learning RL}
The goal of reinforcement learning is to find a policy \(\pi \in \Pi\) that maximises the sum of discounted
rewards in expecation under the transition noise (aleatoric uncertainty),
\begin{align} \label{eq-model-free-objective}
\pi^{*} = \arg \max_{\pi \in \Pi} J(f, \pi) = \arg \max_{\pi \in \Pi} \mathbb{E}_{\bm\epsilon_{0:\infty}} \left[ \sum_{t=0}^{\infty} \gamma^{t} r(s_{t},a_{t}) \right].
\end{align}

\textbf{Model-based RL}
In Bayesian model-based RL, we obtain the posterior over the dynamics \(p(f\mid\mathcal{D})\) after performing (approximate) Bayesian
inference given a state transition data set \(\mathcal{D} = \{\{(s_{t},a_{t}), s_{t+1}\}^{T_{i}}_{t=1}\}_{i=0}^{N}\).
In this work we are interested in how we can use \(p(f \mid \mathcal{D})\) to alleviate some of the issues in model-based RL,
for example, model bias and the exploration-exploitation trade-off.

\textbf{Greedy exploitation}
Given the posterior dynamics \(p(f \mid \mathcal{D})\),
a common approach is to simply take the expecation over both the aleatoric and epistemic uncertainty,
\begin{align} \label{eq-greedy}
\pi_{\text{greedy}} = \arg \max_{\pi} \mathbb{E}_{f \sim p(f \mid \mathcal{D})} \left[ J(f, \pi) \right],
\end{align}
This approach has been widely adopted, for example, in PILCO, PETS, GP-MPC

\cite{deisenrothPILCO2011,chuaDeepReinforcementLearning2018,kamtheDataEfficient2018}.
This approach helps to alleviate model bias as the posterior ``knows what the model does not know''.
This is because the predictive posterior \(p(f(s_{t},a_{t}) \mid (s_{t},a_{t}),  \mathcal{D} )\) will be (or should be) uncertain when making
predictions far away from the training data.
The expectation considers all possible dynamics models which prevents the policy optimisation from
exploiting innacuracies in the model.
This approach has no guarantees for exploration in the general case.
However, under specific dynamics and reward structures (e.g. PILCO) this objective can achieve sublinear regret.
\todo{need to double check sublinear regret statement. And give a reference}

\textbf{Hallucinated upper confidence RL}
A more theoretically grounded exploration strategy is UCRL \autocite{jakschNearoptimal2010}, which optimises joinly over
policies and models inside the set
\(\mathcal{M} = \{ f \mid | f(s,a) - \mu_{i}(s, a) | \leq \beta_{i} \Sigma_{i}(s, a) \quad \forall s, a \in \mathcal{S} \times \mathcal{A} \}\), representing all statistically plausible
models under the posterior \(p(f(s,a) \mid \mathcal{D}_{0:i} \cup (s,a)) = \mathcal{N}(f(s,a) \mid \mu_{i}(s,a), \Sigma_{i}(s,a))\) at episode \(i\).
This strategy is given by,
\begin{align}
\pi_{\text{UCRL}} = \arg \max_{\pi} \max_{f \in \mathcal{M}} J(f, \pi).
\end{align}
This strategy optimises an optimistic policy over the set of plausible dynamics models.
However, the joint optimisation is intractable in general.
\cite{curiEfficient2020} introduced a tractable approximation which retains some of the theoretical guarantees whilst
being applicable with deep model-based RL.
They introduce a function \(\eta: \mathcal{S} \times \mathcal{A} \rightarrow [-1, 1]^{p}\) which acts as a hallucinated control input.
The strategy is given by,
\begin{align} \label{eq-hucrl}
\pi_{\text{UCRL}} = \arg \max_{\pi} \max_{\eta(\cdot) \in [-1,1]} J(f, \pi) \quad \text{s.t.} \quad f = \mu_{i}(s_{t}, a_{t}) + \beta \Sigma_{i}(s_{t}, a_{t}) \eta(s_{t},a_{t}).
\end{align}
Intuitively, \(\eta(s,a) \in [-1,1]\) enables the optimisation to select any dynamics model
\(f\) within \(\pm \beta \Sigma_{i}(s_{t}, a_{t})\) of the posterior mean \(\mu_{i}(s_{t}, a_{t})\).

\textbf{MPC vs policy learning}
It is worth noting that the strategies in \cref{eq-hucrl,eq-greedy} can be used with both model predictive control (MPC)
techniques, such as the cross entoropy method (CEM), and model-free RL techniques, such as soft actor-critic (SAC).

\section{Model-based RL with Fast Bayesian Updates}
The strategy in \cref{eq-hucrl} does not update the dynamics model during an episode.
A better approach would be to update the posterior at every time step during an episode, for example,
\begin{align} \label{eq-objective-with-online-updates}
\pi_{\text{online}} = \arg \max_{\pi} \mathbb{E}_{\bm\epsilon_{0:\infty}} \left[ \sum_{t=0}^{K-1}
\mathbb{E}_{\underbrace{f \sim p(f \mid \mathcal{D} \cup \{(s_{j}, a_{j}), s_{j+1}\}_{j=0}^{t-1})}_{\text{updated posterior}}} \left[ \gamma^{t} r(s_{t}, a_{t}) \mid s_{0}=s \right] \right] +
\gamma^{K} Q(s_{K},a_{K})
\end{align}
We can do this with GPs becuase they are non parameteric but doing it with BNNs is harder. But Me and Paul think we can do it.

The idea is then to compare all of the ideas in the previous paper with and without updating the dynamics during an episode.

\section{Experiments}
Environments
\begin{itemize}
  \item Compare updated posterior with non updated posterior
  \begin{itemize}
  \item Compare for different strategies of making decisions under dynamic model's uncertainty:
    \begin{itemize}
      \item \textbf{Greedy exploitation} \(\pi_{\text{greedy}}\)
      \item \textbf{Hallucinated-UCRL} \(\pi_{\text{HUCRL}}\)
      \item \textbf{Thompson sampling} \(\pi_{\text{TS}}\)
    \end{itemize}
  \end{itemize}
  \item Compare impact of stationary vs non-stationary priors
  \begin{itemize}
    \item First do this with GP
    \item Then try to do with Laplace BNN
  \end{itemize}
\end{itemize}

\section{Conclusion} \label{sec:conclusion}

\section*{Broader Impact}

\section*{Acknowledgements}
Aidan Scannell is funded by the Finnish Center for Artificial Intelligence.

% \section*{References}
\small
\printbibliography
\normalsize
% TODO make bibliography small a better way

References follow the acknowledgments. Use unnumbered first-level heading for
the references. Any choice of citation style is acceptable as long as you are
consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
when listing the references.
Note that the Reference section does not count towards the page limit.
\medskip

\section{Template stuff}
\subsection{Generate TikZ Figures from Python}
We can generate figures in \texttt{.tex} format directly from Python:
\begin{verbatim}
tikzplotlib.save("fig.tex", axis_width="\\figurewidth", axis_height="\\figureheight")
\end{verbatim}
\cref{fig:example} shows that we get nicely formatted lables/titles/etc when we include them in our paper.
\begin{figure}[h]
    \centering\footnotesize

    % Set your figure size here
    \setlength{\figurewidth}{.33\textwidth}
    \setlength{\figureheight}{.75\figurewidth}

    % Customize your plot here
    % (scale only axis applies the size to the axis box and not entire figure)
    \pgfplotsset{grid style={dotted},title={Foo},scale only axis}

    % Use the subcaption package (= subfigure) for sub-plots, that is
    % plot the separate plots separately in Python
    \begin{subfigure}{.4\textwidth}
        \centering
        \input{./figs/example_fig.tex}
    \end{subfigure}
    \hfill
    \begin{subfigure}{.4\textwidth}
        \centering
        \input{./figs/example_fig.tex}
    \end{subfigure}
    \caption{Foo}
    \label{fig:example}
\end{figure}

\subsection{Generate Tables from Python}
We can also generate tables straight from python using \href{https://github.com/astanin/python-tabulate}{tabulate}:
\begin{verbatim}
table = [["Sun",696000,1989100000],["Earth",6371,5973.6],
        ["Moon",1737,73.5],["Mars",3390,641.85]]
headers = ["Planet","R (km)", "mass (x 10^29 kg)"]
table = tabulate(table, headers=headers, tablefmt="latex")
with open("table.tex", 'w') as file:
    file.write(table)
\end{verbatim}

\begin{table}[h]
    \centering
    \input{./tables/example_table.tex}
\end{table}

\subsection{Biblatex}
Rember when using biblatex to use 'parencite' for \parencite{kamtheDataEfficient2018} and when using natbib to use 'citep'.

\appendix

\section{Appendix}

Optionally include extra information (complete proofs, additional experiments and plots) in the appendix.
This section will often be part of the supplemental material.

\end{document}

### 2023-03-07 src/models/__init__.py
initial commit

@@ -1,0 +1,2 @@
+# #!/usr/bin/env python3
+from .base import DynamicModel

### 2023-03-07 src/models/base.py

@@ -1,0 +1,67 @@
+#!/usr/bin/env python3
+from typing import Callable, NamedTuple, Optional
+
+import pytorch_lightning as pl
+import torch
+import torch.distributions as td
+import torch.nn as nn
+import torch.optim as optim
+from custom_types import Action, Prediction, State
+from torchrl.data import ReplayBuffer
+
+
+class DynamicModel:
+    def __call__(self, state: State, action: Action) -> Prediction:
+        return self.predict(state=state, action=action)
+
+    def predict(
+        self, state: State, action: Action, data_new: Optional = None
+    ) -> Prediction:
+        x = torch.concat([state, action], -1)
+        return self.forward(x)
+
+    def forward(self, x, data_new: Optional = None) -> Prediction:
+        raise NotImplementedError
+
+    def train(self, replay_buffer: ReplayBuffer, delta_state: bool = True):
+        raise NotImplementedError
+
+
+# class DynamicsModel(pl.LightningModule):
+#     def __init__(
+#         self,
+#         model,
+#         trainer,
+#         batch_size: int = 64,
+#         num_workers: int = 1,
+#         shuffle: bool = True,
+#     ):
+#         self.model = model
+#         self.trainer = trainer
+#         self.batch_size = batch_size
+#         self.num_workers = num_workers
+#         self.shuffle = shuffle
+
+#     def predict(self, state: State, action: Action) -> Prediction:
+#         x = torch.concat([state, action], -1)
+#         return self.forward(x)
+
+#     def forward(self) -> Prediction:
+#         raise NotImplementedError
+
+#     def train(self, replay_buffer: ReplayBuffer, delta_state: bool = True):
+#         train_loader = ReplayBuffer_to_dynamics_DataLoader(
+#             replay_buffer=replay_buffer,
+#             batch_size=self.batch_size,
+#             shuffle=self.shuffle,
+#             delta_state=delta_state,
+#             num_workers=self.num_workers,
+#         )
+#         self.trainer.fit(self.model, train_loader)
+
+#     def training_step(self, batch, batch_idx):
+#         raise NotImplementedError
+
+#     def configure_optimizers(self):
+#         optimizer = optim.Adam(self.parameters(), lr=1e-3)
+#         return optimizer

### 2023-03-07 src/models/gp/__init__.py

@@ -1,0 +1,4 @@
+#!/usr/bin/env python3
+
+from .gp import GPDynamicModel
+from .svgp import SVGPDynamicModel

### 2023-03-07 src/models/gp/base.py

@@ -1,0 +1,104 @@
+#!/usr/bin/env python3
+from typing import Optional
+
+import gpytorch
+import pytorch_lightning as pl
+import torch
+import torch.distributions as td
+from custom_types import (
+    Action,
+    Prediction,
+    # ReplayBuffer_to_dynamics_TensorDataset,
+    State,
+)
+from torchrl.data import ReplayBuffer
+from pytorch_lightning import Trainer
+from torch.utils.data import DataLoader, TensorDataset
+
+from .models import DynamicModel
+
+
+class GPModule(pl.LightningModule):
+    def __init__(
+        self, gp: gpytorch.models.GP, likelihood: gpytorch.likelihoods.Likelihood
+    ):
+        super(GPModule, self).__init__()
+        self.gp = gp
+        self.likelihood = likelihood
+
+    def forward_(self, x) -> Prediction:
+        # self.gp.eval()
+        # self.likelihood.eval()
+        latent = self.gp(x)
+        print("latent {}".format(latent))
+        output = self.likelihood(latent)
+        print("output {}".format(output))
+        f_dist = td.Normal(loc=latent.mean, scale=torch.sqrt(latent.variance))
+        print("f_dist {}".format(f_dist))
+        y_dist = td.Normal(loc=latent.mean, scale=torch.sqrt(output.variance))
+        print("y_dist {}".format(y_dist))
+        noise_var = output.variance - latent.variance
+        print("noise_var {}".format(noise_var))
+        # pred = Prediction(latent=f_dist, output=y_dist, noise_var=noise_var)
+        pred = Prediction(latent_dist=f_dist, output_dist=y_dist, noise_var=noise_var)
+        print("pred {}".format(pred))
+        return pred
+
+    def training_step(self, batch, batch_idx):
+        raise NotImplementedError
+
+    def configure_optimizers(self):
+        raise NotImplementedError
+
+
+# class BaseGPDynamicsModel(DynamicModel):
+#     # TODO implement delta_state properly
+#     def __init__(
+#         self,
+#         gp_module: GPModule,
+#         trainer: Optional[Trainer] = None,
+#         delta_state: bool = True,
+#         num_workers: int = 1,
+#     ):
+#         super(BaseGPDynamicsModel, self).__init__()
+#         self.gp_module = gp_module
+#         if trainer is None:
+#             self.trainer = Trainer()
+#         else:
+#             self.trainer = trainer
+#         self.delta_state = delta_state
[…]

### 2023-03-07 src/models/gp/gp.py

@@ -1,0 +1,185 @@
+#!/usr/bin/env python3
+from typing import Optional
+
+import gpytorch
+import pytorch_lightning as pl
+import torch
+import torch.distributions as td
+from pytorch_lightning import Trainer
+from torch.utils.data import DataLoader, TensorDataset
+from torchrl.data import ReplayBuffer
+from custom_types import (
+    Action,
+    State,
+    Prediction,
+    # ReplayBuffer_to_dynamics_TensorDataset,
+)
+from models import DynamicModel
+
+
+class GPDynamicModel(DynamicModel):
+    # TODO implement delta_state properly
+    def __init__(
+        self,
+        # gp_module: GPModule,
+        likelihood: gpytorch.likelihoods.Likelihood = None,
+        mean_module: gpytorch.means.Mean = None,
+        covar_module: gpytorch.kernels.Kernel = None,
+        learning_rate: float = 1,
+        trainer: Optional[Trainer] = None,
+        delta_state: bool = True,
+        num_workers: int = 1,
+    ):
+        super(GPDynamicModel, self).__init__()
+        # self.gp_module = gp_module
+        self.gp_module = ExactGPModule(
+            likelihood=likelihood,
+            mean_module=mean_module,
+            covar_module=covar_module,
+            learning_rate=learning_rate,
+        )
+        if trainer is None:
+            self.trainer = Trainer()
+        else:
+            self.trainer = trainer
+        self.delta_state = delta_state
+        self.num_workers = num_workers
+
+    def forward(self, x) -> Prediction:
+        self.gp_module.eval()
+        latent = self.gp_module(x)
+        print("latent")
+        print(latent)
+        output = self.gp_module.likelihood(latent)
+        print("output")
+        print(output)
+        f_dist = td.Normal(loc=latent.mean, scale=torch.sqrt(latent.variance))
+        print("f_dist")
+        print(f_dist)
+        y_dist = td.Normal(loc=latent.mean, scale=torch.sqrt(output.variance))
+        print("y_dist")
+        print(y_dist)
+        noise_var = output.variance - latent.variance
+        print("noise_var")
+        print(noise_var)
+        # pred = Prediction(latent=f_dist, output=y_dist, noise_var=noise_var)
+        pred = Prediction(latent_dist=f_dist, output_dist=y_dist, noise_var=noise_var)
+        print("pred")
+        print(pred)
+        return pred
+
+    def train(self, replay_buffer: ReplayBuffer):
+        dataset = ReplayBuffer_to_dynamics_TensorDataset(
[…]

### 2023-03-07 src/models/gp/svgp.py

@@ -1,0 +1,226 @@
+#!/usr/bin/env python3
+from typing import Optional
+
+import gpytorch
+import pytorch_lightning as pl
+import torch
+import torch.distributions as td
+from custom_types import Prediction
+from models import DynamicModel
+from pytorch_lightning import Trainer
+from torch.utils.data import DataLoader, TensorDataset
+from torchrl.data import ReplayBuffer
+from utils import make_data_loader
+
+
+class SVGPDynamicModel(DynamicModel):
+    # TODO implement delta_state properly
+    def __init__(
+        self,
+        likelihood: gpytorch.likelihoods.Likelihood = None,
+        mean_module: gpytorch.means.Mean = None,
+        covar_module: gpytorch.kernels.Kernel = None,
+        num_inducing: int = 16,
+        learning_rate: float = 0.1,
+        batch_size: int = 16,
+        trainer: Optional[Trainer] = None,
+        delta_state: bool = True,
+        num_workers: int = 1,
+    ):
+        super(SVGPDynamicModel, self).__init__()
+        self.gp_module = SVGPModule(
+            likelihood=likelihood,
+            mean_module=mean_module,
+            covar_module=covar_module,
+            num_inducing=num_inducing,
+            learning_rate=learning_rate,
+            out_size=covar_module.batch_shape[0],
+            # TODO is this the bset way to set out_size?
+        )
+        if trainer is None:
+            self.trainer = Trainer()
+        else:
+            self.trainer = trainer
+        self.batch_size = batch_size
+        self.delta_state = delta_state
+        self.num_workers = num_workers
+
+    def forward(self, x, data_new: Optional = None) -> Prediction:
+        # TODO should I reshape x here as [N, D]?
+        self.gp_module.eval()
+        latent = self.gp_module.forward(x, data_new=data_new)
+        # print("latent {}".format(latent))
+
+        output = self.gp_module.likelihood(latent)
+        # print("output {}".format(output))
+        f_dist = td.Normal(
+            loc=latent.mean[:, 0:-1], scale=torch.sqrt(latent.variance[:, 0:-1])
+        )
+        # print("f_dist {}".format(f_dist))
+        y_dist = td.Normal(
+            loc=latent.mean[:, 0:-1], scale=torch.sqrt(output.variance[:, 0:-1])
+        )
+        # print("y_dist {}".format(y_dist))
+        noise_var = output.variance[:, 0:-1] - latent.variance[:, 0:-1]
+        reward_dist = td.Normal(
[…]

### 2023-03-07 src/custom_types.py
initial commit

@@ -1,0 +1,62 @@
+#!/usr/bin/env python3
+from collections import deque, namedtuple
+from typing import Any, Iterator, NamedTuple, Optional, Tuple, Union
+
+import numpy as np
+import torch
+import torch.distributions as td
+from torch.utils.data import DataLoader, TensorDataset
+from torch.utils.data.dataset import IterableDataset
+from torchtyping import TensorType
+
+
+Tensor = Any
+# Observation = Tensor
+State = Tensor
+Action = Tensor
+
+ActionSequence = Any
+Prediction = Any
+
+ActionTrajectory = TensorType["horizon", "action_dim"]
+
+
+class Prediction(NamedTuple):
+    latent_dist: td.Distribution  # p(f_{\theta}(s, a) \mid (s, a), \mathcal{D})
+    output_dist: td.Distribution  # p(\Delta s' \mid (s, a), \mathcal{D})
+    noise_var: Optional[
+        Union[td.Distribution, TensorType[""]]
+    ] = 0.0  # p(\Delta s' \mid f(s, a), \Sigma_n(s, a))
+    reward_dist: td.Distribution = 0.0  # p(r_t \mid (s_t, a_t), \mathcal{D})
+
+
+# def ReplayBuffer_to_dynamics_DataLoader(
+#     replay_buffer: ReplayBuffer,
+#     batch_size: int = 64,
+#     shuffle=True,
+#     delta_state: Optional[bool] = True,
+#     num_workers: Optional[int] = 1,
+# ):
+#     dataset = ReplayBuffer_to_dynamics_TensorDataset(
+#         replay_buffer=replay_buffer, delta_state=delta_state
+#     )
+#     train_loader = DataLoader(
+#         dataset, batch_size=batch_size, shuffle=shuffle, num_workers=num_workers
+#     )
+#     return train_loader
+
+
+# def ReplayBuffer_to_dynamics_TensorDataset(
+#     replay_buffer, delta_state: Optional[bool] = True
+# ) -> TensorDataset:
+#     transitions = replay_buffer.sample(len(replay_buffer))
+#     observation_action_inputs = torch.concat(
+#         [transitions.observations, transitions.actions], -1
+#     )
+#     if delta_state:
+#         delta_observations = transitions.next_observations - transitions.observations
+#         dataset = (observation_action_inputs, delta_observations)
+#     else:
+#         dataset = (observation_action_inputs, transitions.next_observations)
+#     dataset = TensorDataset(*dataset)
+#     return dataset

### 2023-03-07 paper/main.tex
updated

@@
   Reinforcement learning (RL) agents typically perform learning after an episode and do not utilise the information gained during an episode.
-  We present a Bayesian model-based RL algorithm which incorporates this information by updating its dynamic model's posterior during an episode.
-  We prove that for stationary dynamic model priors, our method achieves sublinear regret, i.e. it will converge to the optimal policy.
+  We present a Bayesian model-based RL algorithm which incorporates this information by updating a dynamic model's posterior during an episode.
   Importantly, our dynamic model (and it's converge guarantees) scales to high dimensional problems via neural networks with stationary priors.

### 2023-03-07 src/train.py

@@ -1,28 +1,183 @@
 #!/usr/bin/env python3
 import logging
+import random
+from functools import partial
+from pathlib import Path
+from typing import List, Optional
 
 
 logging.basicConfig(level=logging.INFO)
-
-import hydra
-import matplotlib.pyplot as plt
-import numpy as np
-import omegaconf
-import wandb
-
-
 logger = logging.getLogger(__name__)
 
+import gpytorch
+import hydra
+import numpy as np
+import omegaconf
+import pytorch_lightning as pl
+import torch
+import torch.nn as nn
+import torchrl
+import tqdm
+import wandb
+from dm_env import specs
+from models.gp.svgp import SVGPDynamicModel
+from omegaconf import DictConfig, OmegaConf
+from pytorch_lightning import Trainer
+from pytorch_lightning.loggers import WandbLogger
+from setuptools.dist import Optional
+from tensordict.nn import TensorDictModule
+from torch import nn, optim
+from torchrl.collectors import MultiaSyncDataCollector, SyncDataCollector
+from torchrl.data import CompositeSpec, TensorDictReplayBuffer
+from torchrl.data.postprocs import MultiStep
+from torchrl.data.replay_buffers import ReplayBuffer
+from torchrl.data.replay_buffers.samplers import (
+    PrioritizedSampler,
+    RandomSampler,
+    SamplerWithoutReplacement,
+)
+from torchrl.data.replay_buffers.storages import LazyMemmapStorage, LazyTensorStorage
+from torchrl.envs import CatTensors, DoubleToFloat
+from torchrl.envs.libs.gym import GymEnv
+from torchrl.envs.transforms import RewardScaling, TransformedEnv
+from torchrl.trainers import Recorder
+from utils import set_seed_everywhere
 
-@hydra.main(config_path="../configs", config_name="main")
-def train(cfg: omegaconf.DictConfig):
-    # Make experiment reproducible
-    # set_random_seed(cfg.random_seed) # TODO implement function to set random seed
+
+def make_replay_buffer(
+    buffer_size: int, device, buffer_scratch_dir: str = "/tmp/", prefetch: int = 3
+):
+    sampler = RandomSampler()
+    replay_buffer = TensorDictReplayBuffer(
+        storage=LazyTensorStorage(buffer_size, device=device),
+        # storage=LazyMemmapStorage(
+        #     buffer_size,
+        #     scratch_dir=buffer_scratch_dir,
+        #     device=device,
+        # ),
+        sampler=sampler,
[…]

### 2023-03-09 paper/main.tex
commit after adding some SVGO maths and algs

@@
 \usepackage{bm}
+\usepackage{algpseudocode}
+\usepackage{algorithm}
 
@@
 \newlength{\figureheight}
+
+% Variables
+\newcommand{\state}{\ensuremath{\mathbf{s}}}
+\newcommand{\action}{\ensuremath{\mathbf{a}}}
+\newcommand{\noise}{\ensuremath{\bm\epsilon}}
+\newcommand{\discount}{\ensuremath{\gamma}}
+\newcommand{\inducingVariable}{\ensuremath{\mathbf{u}}}
+\newcommand{\dataset}{\ensuremath{\mathcal{D}}}
+\newcommand{\dualParam}[1]{\ensuremath{\bm{\lambda}_{#1}}}
+\newcommand{\meanParam}[1]{\ensuremath{\bm{\mu}_{#1}}}
+
+% Indexes
+\newcommand{\horizon}{\ensuremath{h}}
+\newcommand{\Horizon}{\ensuremath{H}}
+
+% Domains
+\newcommand{\stateDomain}{\ensuremath{\mathcal{S}}}
+\newcommand{\actionDomain}{\ensuremath{\mathcal{A}}}
+\newcommand{\policyDomain}{\ensuremath{\Pi}}
+
+% Functions
+\newcommand{\rewardFn}{\ensuremath{r}}
+\newcommand{\transitionFn}{\ensuremath{f}}
+\newcommand{\latentFn}{\ensuremath{f}}
+
+\newcommand{\optimisticTransition}{\ensuremath{\hat{f}}}
+\newcommand{\optimisticTransitionMean}{\ensuremath{\mu_{\optimisticTransition}}}
+\newcommand{\optimisticTransitionCov}{\ensuremath{\mu_{\optimisticTransition}}}
+\newcommand{\optimisticTransitionSet}{\ensuremath{\mathcal{M}}}
+
+% Parameters
+\newcommand{\transitionParams}{\ensuremath{\phi}}
+\newcommand{\valueFnParams}{\ensuremath{\psi}}
+\newcommand{\policyParams}{\ensuremath{\theta}}
+
+% Networks
+\newcommand{\transition}{\ensuremath{\mathbf{d}_{\transitionParams}}}
+\newcommand{\valueFn}{\ensuremath{\mathbf{Q}}}
+\newcommand{\stateValueFn}{\ensuremath{\mathbf{V}}}
+% \newcommand{\valueFn}{\ensuremath{\mathbf{Q}_{\valueFnParams}}}
+\newcommand{\policy}{\ensuremath{\pi}}
+\newcommand{\pPolicy}{\ensuremath{\pi_{\policyParams}}}
 
@@
 \section{Problem Statement and Background} \label{sec:problem-statement}
-We consider environments with states \(s \in \mathcal{S}\), actions \(a \in \mathcal{A}\) and transition dynamics \(f: \mathcal{S} \times \mathcal{A} \rightarrow \mathcal{S}\) subject to
-iid noise \(\epsilon_{t}\), given by,
+We consider environments with states \(\state \in \stateDomain \), actions \(\action \in \actionDomain\) and transition dynamics \(\transitionFn: \stateDomain \times \actionDomain \rightarrow \stateDomain \) subject to
+iid noise \(\noise_{t}\), given by,
 \begin{align}
-s_{t+1} = f(s_{t}, a_{t}) + \epsilon_{t}.
+\state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t}.
 \end{align}
 
-\textbf{Reinforcement learning RL}
+\textbf{Reinforcement learning (RL)}
 The goal of reinforcement learning is to find a policy \(\pi \in \Pi\) that maximises the sum of discounted
@@
 \begin{align} \label{eq-model-free-objective}
-\pi^{*} = \arg \max_{\pi \in \Pi} J(f, \pi) = \arg \max_{\pi \in \Pi} \mathbb{E}_{\bm\epsilon_{0:\infty}} \left[ \sum_{t=0}^{\infty} \gamma^{t} r(s_{t},a_{t}) \right].
+\policy^{*} = \arg \max_{\policy \in \policyDomain} J(\transitionFn, \policy) = \arg \max_{\policy \in \policyDomain} \mathbb{E}_{\noise_{0:\infty}} \left[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \right].
 \end{align}
@@
 
+\begin{align} \label{eq-fast-update-mpc}
+  \policy(\state) = \arg &\max_{\action_{0}} \max_{\action_{1}, \ldots, \action_{\Horizon}}
+  \mathbb{E}_{\state_{\horizon} \sim p(\state_{\horizon+1} \mid \transitionFn(\state_{\horizon}, \action_{\horizon}))} \left[ \sum_{\horizon=0}^{\Horizon}     \discount^{\horizon} \rewardFn(\state_{\horizon},\action_{\horizon}) \mid \state_{0}=\state \right] + \discount^{\Horizon+1} \stateValueFn(\state_{\Horizon+1})
+\end{align}
+
+\begin{align} \label{eq-fast-update-mpc}
+  \stateValueFn(\state) = \mathbb{E} \left[ \sum_{t=0}^{\infty}     \discount^{t} \rewardFn(\state_{t},\action_{t}) \mid \state_{0}=\state \right]
+\end{align}
+
+\begin{align} \label{eq-fast-update-mpc}
+  \policy(\state) = \arg &\max_{\action_{0}} \max_{\action_{1}, \ldots, \action_{\Horizon}} \max_{\optimisticTransition \in \optimisticTransitionSet}
+  \sum_{\horizon=0}^{\Horizon}  \mathbb{E}_{\noise_{\horizon}} \left[  \discount^{\horizon} \rewardFn(\state_{\horizon},\action_{\horizon}) \right] + \discount^{\Horizon+1} \stateValueFn(\state_{\Horizon+1}) \\
+  \text{s.t. } \state_{\horizon+1} &= \optimisticTransition(\state_{\horizon}, \action_{\horizon}) + \noise_{\horizon} \\
+  \optimisticTransition(\state_{\horizon}, \action_{\horizon}) &=
+\optimisticTransitionMean(\state_{\horizon}, \action_{\horizon}) \pm \beta_{i}
+\optimisticTransitionCov(\state_{\horizon}, \action_{\horizon})
+\end{align}
+
+\begin{align} \label{eq-svgp-predictive-posterior}
+  q_{\inducingVariable}(\transitionFn(\state_{t}, \action_{t})) = \mathcal{N}
+  \left( \transitionFn(\state_{t}, \action_{t}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} \mathbf{A}^{T} + \mathbf{A} \mathbf{V}^{*} \mathbf{A}^{T} \right)
+\end{align}
+
+\begin{align} \label{eq-matrix-A}
+  \mathbf{A} = \mathbf{K}_{\mathbf{X}\mathbf{Z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}}
+\end{align}
+
+\begin{align} \label{eq-dual-params}
+  \mathbf{m}^{*} = \mathbf{V}^{*}\dualParam{1}^{*} \quad \mathbf{V}^{*} = [\mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} + \dualParam{2}^{*}]
+\end{align}
+
+\begin{align} \label{eq-dual-update-svgp-old-new}
+ \dualParam{1}^{\text{new}} &\leftarrow \dualParam{1}^{\text{old}} +
+  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\text{new}}, \action_{\text{new}}))}
+ \left[ \log p(\state_{\text{new}} \mid \latentFn(\state_{\text{new}}, \action_{\text{new}}) ) \right] \\
+ \dualParam{2}^{\text{new}} &\leftarrow \dualParam{2}^{\text{old}} +
+  \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\text{new}}, \action_{\text{new}}))}
+ \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\text{new}}, \action_{\text{new}}) ) \right]
+\end{align}
+
+\begin{align} \label{eq-dual-update-svgp}
+ \dualParam{1}^{\horizon+1} &\leftarrow \dualParam{1}^{\horizon} +
+  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}
+ \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right] \\
+ \dualParam{2}^{\horizon+1} &\leftarrow \dualParam{2}^{\horizon} +
+  \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}
+ \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right]
+\end{align}
+
+\begin{algorithm}[H]
+\caption{Model-based RL}\label{alg-mbrl}
+\begin{algorithmic}[1]
+    % ${p(\state_{\timeInd+1} \mid \singleInput, \dataset_{0})}$}
+\For{$i  \in \{0, 1, \ldots, \text{num episodes} \}$}
+    \State Train dynamics using $\dataset_{0:i}$
+    \For{$t  \in \{0, 1, \ldots, \text{num steps} \}$}
+      \State Execute policy $\policy(\state_{t})$ in environment
+      \State Set $\mathcal{D}_{i} = \mathcal{D}_{i} \cup (\state_{t}, \action_{t}, \state_{t+1}, r_{t+1})$
+    \EndFor
+    \State Update data $\mathcal{D}_{0:i} = \mathcal{D}_{0:i-1} \cup \mathcal{D}_{i}$
+\EndFor
+\end{algorithmic}
+\end{algorithm}
+\begin{algorithm}[H]
+\caption{Model-based RL with fast updates}\label{alg-mbrl-fast-updates}
+\begin{algorithmic}[1]
+    % ${p(\state_{\timeInd+1} \mid \singleInput, \dataset_{0})}$}
+\For{$i  \in \{0, 1, \ldots, \text{num episodes} \}$}
+    \State Train dynamics using $\dataset_{0:i}$
+    \For{$t  \in \{0, 1, \ldots, \text{num steps} \}$}
+      \State Execute policy $\policy(\state_{t})$ in environment
+      \State Set $\mathcal{D}_{i} = \mathcal{D}_{i} \cup (\state_{t}, \action_{t}, \state_{t+1}, r_{t+1})$
+      \State {\color{blue}Update dynamics posterior}
+    \EndFor
+    \State Update data $\mathcal{D}_{0:i} = \mathcal{D}_{0:i-1} \cup \mathcal{D}_{i}$
+\EndFor
+\end{algorithmic}
+\end{algorithm}
+
+\begin{minipage}{0.499\textwidth}
+\begin{algorithm}[H]
+\caption{Model-based RL}\label{alg-mbrl}
+\begin{algorithmic}[1]
+  % \Require{Start state $\state_0$, initial data set $\dataset_0$, policy $\pi_{0}$, dynamic model}
+    % ${p(\state_{\timeInd+1} \mid \singleInput, \dataset_{0})}$}
+\For{$i  \in \{0, 1, \ldots, \text{num episodes} \}$}
+    \State Train dynamics using $\dataset_{0:i}$
+    \State Train value function $\stateValueFn$ using $\dataset_{0:i}$
+    \For{$t  \in \{0, 1, \ldots, \text{num steps} \}$}
+      % \State Calculate $\action_{t}$ using \cref{eq-fast-update-mpc}
+      % \State Execute 1 step in environment using $\policy(\state_{t})$ and observe $(\state_{t}, \action_{t}, \state_{t+1}, r_{t+1})$
+      \State Execute policy $\policy(\state_{t})$ in environment
+      \State Set $\mathcal{D}_{i} = \mathcal{D}_{i} \cup (\state_{t}, \action_{t}, \state_{t+1}, r_{t+1})$
+    \EndFor
+    \State Update data $\mathcal{D}_{0:i} = \mathcal{D}_{0:i-1} \cup \mathcal{D}_{i}$
+\EndFor
+\end{algorithmic}
+\end{algorithm}
+\end{minipage}
+\hfill
+\begin{minipage}{0.499\textwidth}
+\begin{algorithm}[H]
+\caption{Model-based RL with fast updates}\label{alg-mbrl-with-fast-updates-simple}
+\begin{algorithmic}[1]
+  % \Require{Start state $\state_0$, initial data set $\dataset_0$, policy $\pi_{0}$, dynamic model}
+    % ${p(\state_{\timeInd+1} \mid \singleInput, \dataset_{0})}$}
+\For{$i  \in \{0, 1, \ldots, \text{num episodes} \}$}
+    \State Train dynamics using $\dataset_{0:i}$
+    \State Train value function $\stateValueFn$ using $\dataset_{0:i}$
+    \For{$t  \in \{0, 1, \ldots, \text{num steps} \}$}
+      \State Execute policy $\policy(\state_{t})$ in environment
+      \State Set $\mathcal{D}_{i} = \mathcal{D}_{i} \cup (\state_{t}, \action_{t}, \state_{t+1}, r_{t+1})$
+      \State {\color{blue}Update dynamics posterior}
+    \EndFor
+    \State Update data $\mathcal{D}_{0:i} = \mathcal{D}_{0:i-1} \cup \mathcal{D}_{i}$
+\EndFor
+\end{algorithmic}
+\end{algorithm}
+\end{minipage}
+
+\begin{algorithm}[!t]
+\caption{Model-based RL with fast updates}\label{alg-mbrl-with-fast-updates}
+\begin{algorithmic}[1]
+  % \Require{Start state $\state_0$, initial data set $\dataset_0$, policy $\pi_{0}$, dynamic model}
+    % ${p(\state_{\timeInd+1} \mid \singleInput, \dataset_{0})}$}
+\For{$i  \in \{0, 1, \ldots, \text{num episodes} \}$}
+    \State Train dynamics using $\dataset_{0:i}$ to get $p(\mathbf{\transitionFn} \mid \dataset_{0:i})$
+    \State Train value function $\stateValueFn$ using $\dataset_{0:i}$
+    % \While{not converged}
+    %     \State Sample $N_{b}$ state transitions $\mathcal{B} \sim \dataset_{0:i}$
+    %     \State Update dynamics using with $\mathcal{B}$
+    % \EndWhile
+    \For{$t  \in \{0, 1, \ldots, \text{num steps} \}$}
+      \State Calculate $\action_{t}$ using \cref{eq-fast-update-mpc}
+      \State Execute $\action_{t}$ in environment and observe $(\state_{t}, \action_{t}, \state_{t+1}, r_{t+1})$
+      \State Update dynamics posterior (i.e. fast update via dual parameters)
+      \begin{align}
+      \dualParam{1}^{\horizon+1} &\leftarrow \dualParam{1}^{\horizon} +  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))} \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right] \\
+      \dualParam{2}^{\horizon+1} &\leftarrow \dualParam{2}^{\horizon} +  \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}  \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right]
+      \end{align}
+    \EndFor
+    % \State Calculate $\action_{\horizon}$ using \cref{eq-fast-update-mpc}
+    % \State Execute $\action_{\horizon}$ in environment and observe $(\state_{\horizon}, \action_{\horizon}, \state_{\horizon+1}, r_{\horizon+1})$
+\EndFor
+\end{algorithmic}
+\end{algorithm}
+
 \section{Experiments}
@@
   \end{itemize}
+  \item Compare impact of function vs weight space
 \end{itemize}

### 2023-03-09 paper/main.tex
Restructured everything!

--- 2023-03-07 paper/main.tex
@@
 
+\input{aidans-utils.tex}
+
+% Short section names etc
 % This must be imported last!
@@
 \usepackage[capitalise,nameinlink]{cleveref}
+\crefname{section}{Sec.}{Secs.}
+\crefname{algorithm}{Alg.}{Algs.}
+\crefname{appendix}{App.}{Apps.}
+\crefname{definition}{Def.}{Defs.}
+\crefname{table}{Tab.}{Tabs}
 
@@
 \newlength{\figureheight}
+
+% Variables
+\newcommand{\state}{\ensuremath{\mathbf{s}}}
+\newcommand{\action}{\ensuremath{\mathbf{a}}}
+\newcommand{\noise}{\ensuremath{\bm\epsilon}}
+\newcommand{\discount}{\ensuremath{\gamma}}
+\newcommand{\inducingVariable}{\ensuremath{\mathbf{u}}}
+\newcommand{\dataset}{\ensuremath{\mathcal{D}}}
+\newcommand{\dualParam}[1]{\ensuremath{\bm{\lambda}_{#1}}}
+\newcommand{\meanParam}[1]{\ensuremath{\bm{\mu}_{#1}}}
+
+% Indexes
+\newcommand{\horizon}{\ensuremath{h}}
+\newcommand{\Horizon}{\ensuremath{H}}
+\newcommand{\numDataNew}{\ensuremath{N^{\text{new}}}}
+\newcommand{\numDataOld}{\ensuremath{N^{\text{old}}}}
+\newcommand{\numInducing}{\ensuremath{M}}
+
+% Domains
+\newcommand{\stateDomain}{\ensuremath{\mathcal{S}}}
+\newcommand{\actionDomain}{\ensuremath{\mathcal{A}}}
+\newcommand{\policyDomain}{\ensuremath{\Pi}}
+
+% Functions
+\newcommand{\rewardFn}{\ensuremath{r}}
+\newcommand{\transitionFn}{\ensuremath{f}}
+\newcommand{\latentFn}{\ensuremath{f}}
+
+\newcommand{\optimisticTransition}{\ensuremath{\hat{f}}}
+\newcommand{\optimisticTransitionMean}{\ensuremath{\mu_{\optimisticTransition}}}
+\newcommand{\optimisticTransitionCov}{\ensuremath{\mu_{\optimisticTransition}}}
+\newcommand{\optimisticTransitionSet}{\ensuremath{\mathcal{M}}}
+
+% Parameters
+\newcommand{\transitionParams}{\ensuremath{\phi}}
+\newcommand{\valueFnParams}{\ensuremath{\psi}}
+\newcommand{\policyParams}{\ensuremath{\theta}}
+
+% Networks
+\newcommand{\transition}{\ensuremath{\mathbf{d}_{\transitionParams}}}
+\newcommand{\valueFn}{\ensuremath{\mathbf{Q}}}
+\newcommand{\stateValueFn}{\ensuremath{\mathbf{V}}}
+% \newcommand{\valueFn}{\ensuremath{\mathbf{Q}_{\valueFnParams}}}
+\newcommand{\policy}{\ensuremath{\pi}}
+\newcommand{\pPolicy}{\ensuremath{\pi_{\policyParams}}}
 
@@
 \begin{abstract}
-  %Reinforcement learning (RL) agents typically perform learning after an episode and do not utilise the information gained during an episode.
-  Reinforcement learning (RL) agents typically perform learning after an episode and do not utilise the information gained during an episode.
+  % Reinforcement learning (RL) agents typically do not utilise the information previously gained during an episode.
+  % as they perform learning offline, i.e. after an episode.
+  % Reinforcement learning (RL) agents typically perform learning after an episode, ignoring the potential information gain whilst collecting data.
+  Reinforcement learning (RL) agents typically perform learning offline and do not utilise the information gained during an episode.
   We present a Bayesian model-based RL algorithm which incorporates this information by updating a dynamic model's posterior during an episode.
-  Importantly, our dynamic model (and it's converge guarantees) scales to high dimensional problems via neural networks with stationary priors.
-  We demonstrate that our fast posterior updates lead to improved sample efficiency in environments with action penalties, a notoriously difficult
+  Our method leverages the fast posterior updates available in the dual parameterisation of sparse variational Gaussian processes.
+  Importantly, our algorithm scales to 1) environment's with high dimensional state-spaces as it is built upon the connection between Bayesian neural networks (BNNs) and
+  Gaussian processes (GPs) and 2) long episodes, as the complexity of our updates is independent of episode length.
+  We demonstrate that our fast posterior updates improve sample efficiency in environments with action penalties, a notoriously difficult
   challenge for model-based RL algorithms.
-
-  % Model-based reinforcement learning (RL) typically learns
 \end{abstract}
@@
 
+Why model-based RL:
+\begin{itemize}
+  \item Better sample efficiency than model-free RL
+\end{itemize}
+
+Why Bayesian model-based RL:
+\begin{itemize}
+  \item Can be used to combat model bias
+  \item Better exploration in environment's that are hard to explore (sparse reward/control penalties)
+  \item Bayesian framwork can naturally handle stochastic environments
+\end{itemize}
+
+Issues with uncertainty in model-based RL:
+\begin{itemize}
+  \item Over exploration when using optimism in the face of uncertainty
+  \begin{itemize}
+    \item Agent drives exploration into region of high epistemic uncertainty because it thinks it could have high return.
+    \item In reality, the dynamic model is innacurate and the agent spends the majority of an episode exploiting this innacuracy.
+    \item What if the agent could update it's model during an episode and realise it's pointless to explore in this region
+    \item We show that this can reduce model exploration and in turn, improve sample efficiency.
+  \end{itemize}
+\end{itemize}
+
 \section{Problem Statement and Background} \label{sec:problem-statement}
-We consider environments with states \(s \in \mathcal{S}\), actions \(a \in \mathcal{A}\) and transition dynamics \(f: \mathcal{S} \times \mathcal{A} \rightarrow \mathcal{S}\) subject to
-iid noise \(\epsilon_{t}\), given by,
+We consider environments with states \(\state \in \stateDomain \), actions \(\action \in \actionDomain\) and transition dynamics \(\transitionFn: \stateDomain \times \actionDomain \rightarrow \stateDomain \) subject to
+iid noise \(\noise_{t}\), given by,
 \begin{align}
-s_{t+1} = f(s_{t}, a_{t}) + \epsilon_{t}.
+\state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t}.
 \end{align}
+\begin{assumption}
+  (system properties) The environment's dynamics are $L_{\transitionFn}\text{-Lipschitz}$ continuous and the transition noise $\noise_{t}$ is $\sigma\text{-sub-Gaussian}$ for all $t \geq 0$.
+\end{assumption}
 
-\textbf{Reinforcement learning RL}
+\subsection{Model-based Reinforcement Learning (RL)}
 The goal of reinforcement learning is to find a policy \(\pi \in \Pi\) that maximises the sum of discounted
@@
 \begin{align} \label{eq-model-free-objective}
-\pi^{*} = \arg \max_{\pi \in \Pi} J(f, \pi) = \arg \max_{\pi \in \Pi} \mathbb{E}_{\bm\epsilon_{0:\infty}} \left[ \sum_{t=0}^{\infty} \gamma^{t} r(s_{t},a_{t}) \right].
+\policy^{*} = \arg \max_{\policy \in \policyDomain} J(\transitionFn, \policy) = \arg \max_{\policy \in \policyDomain} \mathbb{E}_{\noise_{0:\infty}} \left[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \right],
 \end{align}
+where $\gamma \in [0, 1]$
 
-\textbf{Model-based RL}
+\textbf{Model-based}
 In Bayesian model-based RL, we obtain the posterior over the dynamics \(p(f\mid\mathcal{D})\) after performing (approximate) Bayesian
 inference given a state transition data set \(\mathcal{D} = \{\{(s_{t},a_{t}), s_{t+1}\}^{T_{i}}_{t=1}\}_{i=0}^{N}\).
-In this work we are interested in how we can use \(p(f \mid \mathcal{D})\) to alleviate some of the issues in model-based RL,
-for example, model bias and the exploration-exploitation trade-off.
+\cref{alg-mbrl} shows the typical model-based RL loop.
+Importantly, the dynamics are usually only updated after an episode.
 
+\begin{algorithm}[!t]
+\caption{Model-based RL}\label{alg-mbrl}
+\begin{algorithmic}[1]
+  \Require Start state $\state_{0}$, initial data set $\dataset_{0}$, dynamics posterior $p(\transitionFn \mid \dataset_{0})$, policy $\policy_{0}$
+\For{$i  \in \{1, 2, \ldots, \text{num episodes} \}$}
+    \State Reset the system to $\state_{0}$ and reset trajectory buffers $\bm\tau_{t} = \emptyset \ \forall t$
+    \For{$t  \in \{1, 2, \ldots, \text{num steps} \}$}
+      % \State Collect  $\tau_{0:t} = \tau_{0:t-1} \cup (\state_{j}, \action_{j}, \state_{j+1}, r_{j+1})$
+      \State Use \cref{eq-greedy}/\cref{eq-posterior-sampling}/\cref{eq-hucrl} to collect data $\bm\tau_{t} = \bm\tau_{t-1} \cup (\state_{t}, \policy_{i}(\state_{t}), \transitionFn(\state_{t}, \policy_{i}(\state_{t})), r_{t+1})$
+      % \State Execute policy $\policy_{i}(\state_{t})$ in environment and update trajectory $\tau_{i+1} = \{\state_{j}, \action_{j}, \state_{j+1}, r_{j+1}) \}_{j=0}^{t}$
+    \EndFor
+    \State Update data set $\dataset_{0:i} = \dataset_{0:i-1} \cup \tau$
+    \State Train dynamics $p(\transitionFn \mid \dataset_{0:i}) \leftarrow \text{update\_dynamics}(\dataset_{0:i}, p(\transitionFn \mid \dataset_{0:i-1}))$
+    % \State Train dynamics $p(\transitionFn \mid \dataset_{0:i+1})$ using $\dataset_{0:i+1}$
+    % \State Improve policy $\pi_{i+1}$ using $p(\transitionFn \mid \dataset_{0:i+1})$ and/or $\dataset_{0:i+1}$
+    \State Improve policy $\pi_{i+1} \leftarrow \text{update\_policy}(p\left(\transitionFn \mid \dataset_{0:i}), \dataset_{0:i} \right)$
+    %\State Improve policy $\pi_{i+1}$ using $p(\transitionFn \mid \dataset_{0:i+1})$ and/or $\dataset_{0:i+1}$
+\EndFor
+\end{algorithmic}
+\end{algorithm}
+
+% \begin{minipage}{0.499\textwidth}
+% \begin{algorithm}[H]
+% \caption{Model-based RL}\label{alg-mbrl}
+% \begin{algorithmic}[1]
+%   \Require Initial data set $\dataset_{0}$, dynamics posterior $p(\transitionFn \mid \dataset_{0})$, policy $\policy_{0}$
+% \For{$i  \in \{0, 1, \ldots, \text{num episodes} \}$}
+%     \For{$t  \in \{0, 1, \ldots, \text{num steps} \}$}
+%       \State Execute policy $\policy_{i}(\state_{t})$ in environment
+%       \State $\tau_{i+1} = \{\state_{j}, \action_{j}, \state_{j+1}, r_{j+1}) \}_{j=0}^{t}$
+%     \EndFor
+%     \State Update data set $\mathcal{D}_{0:i+1} = \mathcal{D}_{0:i} \cup \tau_{i+1}$
+%     \State Train dynamics $p(\transitionFn \mid \dataset_{0:i+1})$
+%     \State Improve policy $\pi_{i+1}$
+%     %\State Improve policy $\pi_{i+1}$ using $p(\transitionFn \mid \dataset_{0:i+1})$ and/or $\dataset_{0:i+1}$
+% \EndFor
+% \end{algorithmic}
+% \end{algorithm}
+% \end{minipage}
+% \hfill
+% \begin{minipage}{0.499\textwidth}
+% \begin{algorithm}[H]
+% \caption{Model-based RL with fast updates}\label{alg-mbrl-fast-updates}
+% \begin{algorithmic}[1]
+%   \Require Initial data set $\dataset_{0}$, dynamics posterior $p(\transitionFn \mid \dataset_{0})$, policy $\policy_{0}$
+%     % ${p(\state_{\timeInd+1} \mid \singleInput, \dataset_{0})}$}
+% \For{$i  \in \{0, 1, \ldots, \text{num episodes} \}$}
+%     \For{$t  \in \{0, 1, \ldots, \text{num steps} \}$}
+%       \State Execute policy $\policy_{i}(\state_{t})$ in environment
+%       % \State Append transition $\state_{t}, \action_{t}, \state_{t+1}, r_{t+1})$ to trajectory $\tau_{i}$
+%       \State $\tau_{i+1} = \{\state_{j}, \action_{j}, \state_{j+1}, r_{j+1}) \}_{j=0}^{t}$
+%       \State {\color{blue}Update dynamics $p(\transitionFn \mid \dataset_{0:i} \cup \tau_{i+1})$}
+%     \EndFor
+%     \State Update data set $\mathcal{D}_{0:i+1} = \mathcal{D}_{0:i} \cup \tau_{i+1}$
+%     \State Train dynamics $p(\transitionFn \mid \dataset_{0:i+1})$
+%     \State Improve policy $\pi_{i+1}$
+%     %\State Improve policy $\pi_{i+1}$ using $p(\transitionFn \mid \dataset_{0:i+1})$ and/or $\dataset_{0:i+1}$
+% \EndFor
+% \end{algorithmic}
+% \end{algorithm}
+% \end{minipage}
+
+\subsection{Exploration Strategies}
 \textbf{Greedy exploitation}
-Given the posterior dynamics \(p(f \mid \mathcal{D})\),
+Given the posterior dynamics \(p(\transitionFn \mid \mathcal{D})\),
 a common approach is to simply take the expecation over both the aleatoric and epistemic uncertainty,
 \begin{align} \label{eq-greedy}
-\pi_{\text{greedy}} = \arg \max_{\pi} \mathbb{E}_{f \sim p(f \mid \mathcal{D})} \left[ J(f, \pi) \right],
+\policy_{i+1}^{\text{greedy}} = \arg \max_{\policy \in \policyDomain} \mathbb{E}_{\transitionFn \sim p(\transitionFn \mid \dataset_{0:i})} \left[ J(\transitionFn, \policy) \right],
 \end{align}
 This approach has been widely adopted, for example, in PILCO, PETS, GP-MPC
-
 \cite{deisenrothPILCO2011,chuaDeepReinforcementLearning2018,kamtheDataEfficient2018}.
@@
 
+\textbf{Posterior sampling}
+\cite{osbandWhyPosteriorSampling2017,osbandMoreEfficientReinforcement2013}
+\begin{align} \label{eq-posterior-sampling}
+\policy_{i+1}^{\text{PS}} = \arg \max_{\policy \in \policyDomain} \left[ J(\transitionFn, \policy) \right] \quad \text{s.t. } \transitionFn \sim p(\transitionFn \mid \dataset_{0:i})
+\end{align}
+
 \textbf{Hallucinated upper confidence RL}
@@
 \begin{align}
-\pi_{\text{UCRL}} = \arg \max_{\pi} \max_{f \in \mathcal{M}} J(f, \pi).
+\policy_{i+1}^{\text{UCRL}} = \arg \max_{\policy \in \policyDomain} \max_{\transitionFn \in \mathcal{M}} J(\transitionFn, \policy).
 \end{align}
 This strategy optimises an optimistic policy over the set of plausible dynamics models.
-However, the joint optimisation is intractable in general.
-\cite{curiEfficient2020} introduced a tractable approximation which retains some of the theoretical guarantees whilst
-being applicable with deep model-based RL.
-They introduce a function \(\eta: \mathcal{S} \times \mathcal{A} \rightarrow [-1, 1]^{p}\) which acts as a hallucinated control input.
-The strategy is given by,
-\begin{align} \label{eq-hucrl}
-\pi_{\text{UCRL}} = \arg \max_{\pi} \max_{\eta(\cdot) \in [-1,1]} J(f, \pi) \quad \text{s.t.} \quad f = \mu_{i}(s_{t}, a_{t}) + \beta \Sigma_{i}(s_{t}, a_{t}) \eta(s_{t},a_{t}).
-\end{align}
-Intuitively, \(\eta(s,a) \in [-1,1]\) enables the optimisation to select any dynamics model
-\(f\) within \(\pm \beta \Sigma_{i}(s_{t}, a_{t})\) of the posterior mean \(\mu_{i}(s_{t}, a_{t})\).
+Although this joint optimisation is intractable in general,
+\cite{curiEfficient2020} proposed a practical alternative which is detailed in \cref{sec-hucrl}.
 
 \textbf{MPC vs policy learning}
-It is worth noting that the strategies in \cref{eq-hucrl,eq-greedy} can be used with both model predictive control (MPC)
+It is worth noting that the strategies in \cref{eq-greedy,eq-posterior-sampling,eq-hucrl} can be used with both model predictive control (MPC)
 techniques, such as the cross entoropy method (CEM), and model-free RL techniques, such as soft actor-critic (SAC).
 
-\section{Model-based RL with Fast Bayesian Updates}
-The strategy in \cref{eq-hucrl} does not update the dynamics model during an episode.
+In this work we are interested in how we can use \(p(f \mid \mathcal{D})\) to alleviate some of the issues in model-based RL,
+for example, model bias and the exploration-exploitation trade-off.
+
+\todo{show how to get new $\dualParam{1}$ and $\dualParam{2}$ in Train dynamics line of \cref{alg-mbrl-fast-updates}}
+\begin{algorithm}[!t]
+\caption{Model-based RL with fast updates}\label{alg-mbrl-fast-updates}
+\begin{algorithmic}[1]
+  \Require Start state $\state_{0}$, initial data set $\dataset_{0}$, dynamics posterior $p(\transitionFn \mid \dataset_{0})$ (inc.
+dual parameters $\dualParam{1}, \dualParam{2}$), policy $\policy_{0}$
+    % ${p(\state_{\timeInd+1} \mid \singleInput, \dataset_{0})}$}
+\For{$i  \in \{1, 2, \ldots, \text{num episodes} \}$}
+    \State Reset the system to $\state_{0}$ and reset trajectory buffers $\bm\tau_{t} = \emptyset \ \forall t$
+    \For{$t  \in \{1, 2, \ldots, \text{num steps} \}$}
+      % \State Execute policy $\policy_{i}(\state_{t})$ (\cref{eq-fast-update-mpc}) in environment
+      \State Use \cref{eq-fast-update-mpc} to collect data $\bm\tau_{t} = \bm\tau_{t-1} \cup (\state_{t}, \policy_{i}(\state_{t}), \transitionFn(\state_{t}, \policy^{\text{fast}}_{i}(\state_{t})), r_{t+1})$
+      % \State Append transition $\state_{t}, \action_{t}, \state_{t+1}, r_{t+1})$ to trajectory $\tau_{i}$
+      % \State $\tau_{i+1} = \{\state_{j}, \action_{j}, \state_{j+1}, r_{j+1}) \}_{j=0}^{t}$
+      %\State {\color{blue}Update dynamics $p(\transitionFn \mid \dataset_{0:i} \cup \tau_{i+1})$}
+      \State {\color{blue}Update dynamics posterior using \cref{eq-dual-update-svgp}, i.e. fast update}
+      % \begin{align}
+      % \dualParam{1}^{t+1} &\leftarrow \dualParam{1}^{t} +  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))} \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right] \\
+      % \dualParam{2}^{t+1} &\leftarrow \dualParam{2}^{t} +  \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))}  \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right]
+      % \end{align}}
+    \EndFor
+    \State Update data set $\dataset_{0:i} = \dataset_{0:i-1} \cup \tau$
+    \State Train dynamics $p(\transitionFn \mid \dataset_{0:i}) \leftarrow \text{update\_dynamics}(\dataset_{0:i}, p(\transitionFn \mid \dataset_{0:i-1}))$
+    \State Improve policy $\pi^{\text{fast}}_{i+1} \leftarrow \text{update\_policy}(p\left(\transitionFn \mid \dataset_{0:i}), \dataset_{0:i} \right)$
+\EndFor
+\end{algorithmic}
+\end{algorithm}
+
+\section{Model-based Reinforcement Learning with Fast Updates}
+The strategies in \cref{eq-greedy,eq-posterior-sampling,eq-hucrl} do not update the dynamic model during an episode.
 A better approach would be to update the posterior at every time step during an episode, for example,
-\begin{align} \label{eq-objective-with-online-updates}
-\pi_{\text{online}} = \arg \max_{\pi} \mathbb{E}_{\bm\epsilon_{0:\infty}} \left[ \sum_{t=0}^{K-1}
-\mathbb{E}_{\underbrace{f \sim p(f \mid \mathcal{D} \cup \{(s_{j}, a_{j}), s_{j+1}\}_{j=0}^{t-1})}_{\text{updated posterior}}} \left[ \gamma^{t} r(s_{t}, a_{t}) \mid s_{0}=s \right] \right] +
-\gamma^{K} Q(s_{K},a_{K})
+\begin{subequations}
+\begin{align} \label{eq-fast-update-mpc}
+  \policy_{i+1}^{\text{greedy}}(\state) &= \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
+\E_{p(\transitionFn \mid \dataset_{0:i})} \left[J^{\Horizon}(\policy, \transitionFn) \right] + \stateValueFn(\state_{\Horizon+1}) \\
+  \policy_{i+1}^{\text{PS}}(\state) &= \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
+J^{\Horizon}(\policy, \transitionFn) + \stateValueFn(\state_{\Horizon+1}) \quad \text{s.t. } \transitionFn \sim p(\transitionFn \mid \dataset_{0:i} \cup \bm\tau_{t}) \\
+  \policy_{i+1}^{\text{UCRL}}(\state) &= \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
+J^{\Horizon}(\policy, \transitionFn) + \stateValueFn(\state_{\Horizon+1}) \\
+  \stateValueFn(\state) &= \mathbb{E} \left[ \sum_{t=0}^{\infty}     \discount^{t} \rewardFn(\state_{t},\action_{t}) \mid \state_{0}=\state \right] \label{eq-value-fn}
 \end{align}
-We can do this with GPs becuase they are non parameteric but doing it with BNNs is harder. But Me and Paul think we can do it.
+\end{subequations}
+\begin{subequations}
+\begin{align} \label{eq-fast-update-mpc-old}
+  \policy^{\text{fast}}(\state) = \arg &\max_{\action_{0}} \max_{\action_{1}, \ldots, \action_{\Horizon}}
+  \mathbb{E}_{\state_{\horizon} \sim p(\state_{\horizon+1} \mid \transitionFn(\state_{\horizon}, \action_{\horizon}))} \left[ \sum_{\horizon=0}^{\Horizon}     \discount^{\horizon} \rewardFn(\state_{\horizon},\action_{\horizon}) \mid \state_{0}=\state \right] + \discount^{\Horizon+1} \stateValueFn(\state_{\Horizon+1}) \\
+  \stateValueFn(\state) &= \mathbb{E} \left[ \sum_{t=0}^{\infty}     \discount^{t} \rewardFn(\state_{t},\action_{t}) \mid \state_{0}=\state \right] \label{eq-fast-update-mpc}
+\end{align}
+\end{subequations}
 
-The idea is then to compare all of the ideas in the previous paper with and without updating the dynamics during an episode.
+\begin{align} \label{}
+  \policy(\state) = \arg &\max_{\action_{0}} \max_{\action_{1}, \ldots, \action_{\Horizon}} \max_{\optimisticTransition \in \optimisticTransitionSet}
+  \sum_{\horizon=0}^{\Horizon}  \mathbb{E}_{\noise_{\horizon}} \left[  \discount^{\horizon} \rewardFn(\state_{\horizon},\action_{\horizon}) \right] + \discount^{\Horizon+1} \stateValueFn(\state_{\Horizon+1}) \\
+  \text{s.t. } \state_{\horizon+1} &= \optimisticTransition(\state_{\horizon}, \action_{\horizon}) + \noise_{\horizon} \\
+  \optimisticTransition(\state_{\horizon}, \action_{\horizon}) &=
+\optimisticTransitionMean(\state_{\horizon}, \action_{\horizon}) \pm \beta_{i}
+\optimisticTransitionCov(\state_{\horizon}, \action_{\horizon})
+\end{align}
+
+\subsection{Dual GPs for Fast Updates}
+Sparse GP predictive posterior is given by,
+\begin{align} \label{eq-svgp-predictive-posterior}
+  q_{\inducingVariable}(\transitionFn(\state_{t}, \action_{t})) = \mathcal{N}
+  \left( \transitionFn(\state_{t}, \action_{t}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} \mathbf{A}^{T} + \mathbf{A} \mathbf{V}^{*} \mathbf{A}^{T} \right)
+\end{align}
+where $\mathbf{A} = \mathbf{K}_{\mathbf{X}\mathbf{Z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}}$.
+\cite{adamDualParameterizationSparse2021} showed that optimal variational parameters are given by,
+\begin{align} \label{eq-dual-params}
+\mathbf{m}^{*} = \mathbf{V}^{*}\dualParam{1}^{*} \quad \mathbf{V}^{*} = [\mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} + \dualParam{2}^{*}]
+\end{align}
+Importantly, \cite{changFantasizingDualGPs2022} show that in the dual space,
+conditioning on new observations reduces to suming the dual variables from the previous time
+step with an update, given by,
+\todo{pick best way to show new data (using superscript new or just time indexing?)}
+\begin{align} \label{eq-dual-update-svgp}
+\dualParam{1}^{t+1} &\leftarrow \dualParam{1}^{t} +  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))} \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right] \\
+\dualParam{2}^{t+1} &\leftarrow \dualParam{2}^{t} +  \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))}  \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right]
+\end{align}
+Importantly, for a single new observation $((\state_{t}, \action_{t}), \state_{t+1})$ this update has
+complexity $\mathcal{O}(\numInducing^{2})$.
+This is a significant improvement to naive GP conditioning, which has complexity $\mathcal{O}((\numDataNew + \numDataOld)^{3})$
+and sparse GP conditioning, which has complexity $\mathcal{O}((\numDataNew + \numDataOld)\numInducing^{2})$.
+\todo{double check these complexities are right and cite them/show equaitons}
+It is worth highlighting that the complexity of Paul et als update does not increase during an episode,
+
+% \begin{align} \label{eq-dual-update-svgp}
+%  \dualParam{1}^{\text{new}} &\leftarrow \dualParam{1}^{\text{old}} +
+%   \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}))}
+%  \left[ \log p(\state_{t+1}^{\text{new}} \mid \latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}) ) \right] \\
+%  \dualParam{2}^{\text{new}} &\leftarrow \dualParam{2}^{\text{old}} +
+%   \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}))}
+%  \left[ \log p(\state_t^{\horizon+1} \mid \latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}) ) \right] \\
+%  \dualParam{1}^{\horizon+1} &\leftarrow \dualParam{1}^{\horizon} +
+%   \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}
+%  \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right] \\
+%  \dualParam{2}^{\horizon+1} &\leftarrow \dualParam{2}^{\horizon} +
+%   \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}
+%  \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right]
+% \end{align}
+
+\subsection{BNN to SVGP}
+\begin{itemize}
+  \item Write up Laplace BNN to SVGP
+  \item Extend fast updates to SVGP
+\end{itemize}
+
+\begin{assumption} \label{assumption-ntk-linearisation}
+  Something about NTK being a linearisation around $\theta^{MAP}$ but each update moves away from $\theta^{MAP}$
+\end{assumption}
+
+\subsection{Efficiently Sampling Functions for Posterior Sampling}
+\cite{wilsonEfficiently2020}
 
@@
   \item Compare updated posterior with non updated posterior
+  \item Need to show update is fast enough for practical use?
+  \begin{itemize}
+    \item How frequently can we do the posterior update? Every time step or every $K$ steps?
+    \item Update depends on number of inducing points?
+    \item What experiments can we show for this? Wall clock time vs planning horizon with different numbers of inducing points?
+  \end{itemize}
+  \item How does number of inducing points affect performance?
+  \begin{itemize}
+    \item More inducing points means better approximation but larger computational complexity.
+  \end{itemize}
+  \item How good is the assumption that we can linearise BNN to get NTK?
+  \begin{itemize}
+    \item Does model's performance get worse during an episode because linearisation becomes more wrong?
+    \item SVGP does't have this issue so compare to SVGP in cartpole?
+  \end{itemize}
+  \item What length planning horizon to use?
+  \begin{itemize}
+    \item Too small (e.g. $\Horizon=0$) would mean no exploration?
+    \item Can $\Horizon$ be too large?
+  \end{itemize}
   \begin{itemize}
@@
 \medskip
+
+\appendix
+
+\section{Appendix}
+
+Optionally include extra information (complete proofs, additional experiments and plots) in the appendix.
+This section will often be part of the supplemental material.
+
+\section{Hallucinated Upper Confidence Reinforcement Learning (H-UCRL)} \label{sec-hucrl}
+\cite{curiEfficient2020} introduced a tractable approximation which retains some of the theoretical guarantees whilst
+being applicable with deep model-based RL.
+They introduce a function \(\eta: \mathcal{S} \times \mathcal{A} \rightarrow [-1, 1]^{p}\) which acts as a hallucinated control input.
+The strategy is given by,
+\begin{align} \label{eq-hucrl}
+\pi_i^{\text{UCRL}} = \arg \max_{\policy \in \policyDomain} \max_{\eta(\cdot) \in [-1,1]} J(\transitionFn, \policy) \quad \text{s.t.} \quad \transitionFn = \mu_{i}(\state_{t}, \action_{t}) + \beta_{i} \Sigma_{i}(\state_{t}, \action_{t}) \eta(\state_{t},\action_{t}).
+\end{align}
+Intuitively, \(\eta(\state,\action) \in [-1,1]\) enables the optimisation to select any dynamics model
+\(\transitionFn\) within \(\pm \beta \Sigma_{i}(\state_{t}, \action_{t})\) of the posterior mean \(\mu_{i}(\state_{t}, \action_{t})\).
 
@@
 
-\appendix
-
-\section{Appendix}
-
-Optionally include extra information (complete proofs, additional experiments and plots) in the appendix.
-This section will often be part of the supplemental material.
-
 \end{document}

### 2023-03-10 paper/main.tex
Started adding details of BNN/laplace/BNN2GP

@@
 \usepackage{algorithm}
+\usepackage{derivative}
 
@@
 \newcommand{\discount}{\ensuremath{\gamma}}
+\newcommand{\inducingInput}{\ensuremath{\mathbf{Z}}}
 \newcommand{\inducingVariable}{\ensuremath{\mathbf{u}}}
@@
 % Parameters
-\newcommand{\transitionParams}{\ensuremath{\phi}}
+\newcommand{\transitionParams}{\ensuremath{\bm\phi}}
 \newcommand{\valueFnParams}{\ensuremath{\psi}}
@@
 % Networks
-\newcommand{\transition}{\ensuremath{\mathbf{d}_{\transitionParams}}}
+\newcommand{\transitionFnWithParams}{\ensuremath{\transitionFn_{\transitionParams}}}
 \newcommand{\valueFn}{\ensuremath{\mathbf{Q}}}
@@
     \item What if the agent could update it's model during an episode and realise it's pointless to explore in this region
-    \item We show that this can reduce model exploration and in turn, improve sample efficiency.
+    \item We show that this can reduce model exploitation and in turn, improve sample efficiency.
   \end{itemize}
@@
 \cref{alg-mbrl} shows the typical model-based RL loop.
-Importantly, the dynamics are usually only updated after an episode.
+Importantly, the dynamics are usually only updated after an episode $i$.
 
@@
       % \State Collect  $\tau_{0:t} = \tau_{0:t-1} \cup (\state_{j}, \action_{j}, \state_{j+1}, r_{j+1})$
-      \State Use \cref{eq-greedy}/\cref{eq-posterior-sampling}/\cref{eq-hucrl} to collect data $\bm\tau_{t} = \bm\tau_{t-1} \cup (\state_{t}, \policy_{i}(\state_{t}), \transitionFn(\state_{t}, \policy_{i}(\state_{t})), r_{t+1})$
+      \State Use \cref{eq-greedy}/\cref{eq-posterior-sampling}/\cref{eq-ucrl} to collect data $\bm\tau_{t} = \bm\tau_{t-1} \cup (\state_{t}, \policy_{i}(\state_{t}), \transitionFn(\state_{t}, \policy_{i}(\state_{t})), r_{t+1})$
       % \State Execute policy $\policy_{i}(\state_{t})$ in environment and update trajectory $\tau_{i+1} = \{\state_{j}, \action_{j}, \state_{j+1}, r_{j+1}) \}_{j=0}^{t}$
@@
 This strategy is given by,
-\begin{align}
+\begin{align} \label{eq-ucrl}
 \policy_{i+1}^{\text{UCRL}} = \arg \max_{\policy \in \policyDomain} \max_{\transitionFn \in \mathcal{M}} J(\transitionFn, \policy).
@@
 \textbf{MPC vs policy learning}
-It is worth noting that the strategies in \cref{eq-greedy,eq-posterior-sampling,eq-hucrl} can be used with both model predictive control (MPC)
+It is worth noting that the strategies in \cref{eq-greedy,eq-posterior-sampling,eq-ucrl} can be used with both model predictive control (MPC)
 techniques, such as the cross entoropy method (CEM), and model-free RL techniques, such as soft actor-critic (SAC).
@@
   \policy_{i+1}^{\text{greedy}}(\state) &= \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
-\E_{p(\transitionFn \mid \dataset_{0:i})} \left[J^{\Horizon}(\policy, \transitionFn) \right] + \stateValueFn(\state_{\Horizon+1}) \\
+\E_{p(\transitionFn \mid \dataset_{0:i})} \left[J^{\Horizon}(\action_{0:\Horizon}, \transitionFn) \right] + \stateValueFn(\state_{\Horizon+1}) \\
   \policy_{i+1}^{\text{PS}}(\state) &= \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
-J^{\Horizon}(\policy, \transitionFn) + \stateValueFn(\state_{\Horizon+1}) \quad \text{s.t. } \transitionFn \sim p(\transitionFn \mid \dataset_{0:i} \cup \bm\tau_{t}) \\
-  \policy_{i+1}^{\text{UCRL}}(\state) &= \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
-J^{\Horizon}(\policy, \transitionFn) + \stateValueFn(\state_{\Horizon+1}) \\
+J^{\Horizon}(\action_{0:\Horizon}, \transitionFn) + \stateValueFn(\state_{\Horizon+1}) \quad \text{s.t. } \transitionFn \sim p(\transitionFn \mid \dataset_{0:i} \cup \bm\tau_{t}) \\
+  \policy_{i+1}^{\text{UCRL}}(\state) &= \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}} \max_{\transitionFn \in \mathcal{M}}
+J^{\Horizon}(\action_{0:\Horizon}, \transitionFn) + \stateValueFn(\state_{\Horizon+1}) \quad \text{s.t.
+} \mathcal{M} = \{\transitionFn(\state_{t},\action_{t}) - \mu_{i,t}(\state_{t},\action_{t}) \leq \beta_{i,t} \Sigma_{i,t}(\state_{t}, \action_{t})\} \\
   \stateValueFn(\state) &= \mathbb{E} \left[ \sum_{t=0}^{\infty}     \discount^{t} \rewardFn(\state_{t},\action_{t}) \mid \state_{0}=\state \right] \label{eq-value-fn}
@@
   q_{\inducingVariable}(\transitionFn(\state_{t}, \action_{t})) = \mathcal{N}
-  \left( \transitionFn(\state_{t}, \action_{t}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} \mathbf{A}^{T} + \mathbf{A} \mathbf{V}^{*} \mathbf{A}^{T} \right)
+  \left( \transitionFn(\state_{t}, \action_{t}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\inducingInput\inducingInput}^{-1} \mathbf{A}^{T} + \mathbf{A} \mathbf{V}^{*} \mathbf{A}^{T} \right)
 \end{align}
-where $\mathbf{A} = \mathbf{K}_{\mathbf{X}\mathbf{Z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}}$.
+where $\mathbf{A} = \mathbf{K}_{\mathbf{X}\inducingInput} \mathbf{K}^{-1}_{\inducingInput\inducingInput}$.
 \cite{adamDualParameterizationSparse2021} showed that optimal variational parameters are given by,
 \begin{align} \label{eq-dual-params}
-\mathbf{m}^{*} = \mathbf{V}^{*}\dualParam{1}^{*} \quad \mathbf{V}^{*} = [\mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} + \dualParam{2}^{*}]
+\mathbf{m}^{*} = \mathbf{V}^{*}\dualParam{1}^{*} \quad \mathbf{V}^{*} = [\mathbf{K}_{\inducingInput\inducingInput}^{-1} + \dualParam{2}^{*}]
 \end{align}
@@
 \todo{double check these complexities are right and cite them/show equaitons}
-It is worth highlighting that the complexity of Paul et als update does not increase during an episode,
+It is worth highlighting that the complexity of \cite{changFantasizingDualGPs2022} update does not increase during an episode.
 
@@
 \subsection{BNN to SVGP}
-\begin{itemize}
-  \item Write up Laplace BNN to SVGP
-  \item Extend fast updates to SVGP
-\end{itemize}
+In this section we extend these fast updates to environment's with high dimensional state spaces and large data sets.
+% Our method draws on the connection between BNNs and GPs and formulates a function space SVGP posterior given
+Our method uses a BNN dynamic model and draws on the connection between BNNs and GPs
+\parencite{khanApproximate2019} to formulate a function space SVGP posterior,
+where we can apply the fast updates from \cref{eq-dual-update-svgp}.
+At a high-level, we first use Laplace's approximation to obtain a weight space posterior for our BNN.
+We then linearise our BNN around the optimal parameters and interpret it as a GP.
+Finally, we formulate a lower rank approximation of this GP posterior (i.e. a SVGP posterior) using inducing variables.
+% formulates a function space SVGP posterior by drawing on the connection between BNNs and GPs.
+
+% We first show how to
+% i.e. we show these fast updates when using a BNN dynamic model
+
+\textbf{Model learning}
+We paraterise our single-step dynamic model $\transitionFnWithParams : \stateDomain \times \actionDomain \rightarrow \stateDomain$
+as an $L\text{-layer}$ NN with weights $\transitionParams$.
+Given the state transition data set $\dataset_{0:i} = \{(\state_{n}, \action_{n}), \state_{n+1}\}_{n=0}^{N_{i}}$ at episode $i$,
+we train the weights $\transitionParams$ to minimize the (regularized) empirical risk,
+\begin{align}
+  \transitionParams^{*}_{i} = \arg \min_{\transitionParams \in \R^{D}} \mathcal{L}(\dataset_{0:i};\transitionParams) = \arg \min_{\transitionParams \in \R^{D}} \left(
+  R(\transitionParams) + \sum_{n=0}^{N-1} l(\transitionFnWithParams(\state_{n}, \action_{n}), \state_{n+1}; \transitionParams) \right)
+\end{align}
+In practice, it is common to use the mean squared error (MSE) loss
+$l(\cdot,\cdot;\transitionParams) = \|\transitionFnWithParams(\state_{n}, \action_{n}) - \state_{n+1} \|^{2}_{2}$
+and to use the weight decay regularizer $R(\transitionParams)=\frac{1}{2}\gamma^{-2}\|\transitionParams\|^{2}_{2}$.
+However, the practioner is free to choose any loss and regularizer. \todo{I think?}
+
+\textbf{Laplace approximation}
+The Laplace approximation \todo{add citation of original paper} constructs a Gaussian approximation of the weight-space posterior $p(\transitionParams_{i} \mid \dataset_{0:i})$
+by using a second-order Taylor expansion of $\mathcal{L}$ around $\transitionParams^{*}_{i}$.
+The posterior approximation is given by,
+\begin{align} \label{eq-laplace-approx-weight-space}
+  p(\transitionParams_{i} \mid \dataset_{0:i}) \approx \mathcal{N} \left( \transitionParams_{i} \mid \transitionParams^{*}_{i} , \bm\Sigma_{\transitionParams^{*}_{i}} \right)
+  \quad \text{with} \quad \bm\Sigma_{\transitionParams_{i}} =
+ - \nabla_{\transitionParams \transitionParams}^{2} \mathcal{L} ( \dataset_{0:i} ; \transitionParams)|_{\transitionParams=\transitionParams^{*}_{i}}
+\end{align}
+That is, it sets the posterior precision to the hessian of the loss at the optimal parameters $\transitionParams^{*}_{i}$.
+It is worth noting that computing the hessian of the loss can be computationally intractable for large networks.
+Many approximations exist and can be used alongsied our method. We refer the reader to \cite{daxbergerLaplace2021} for more details.
+See \cref{sec-laplace-approximation} for further details on the Laplace approximation.
+% \begin{align}
+% \Sigma_{\transitionParams_{i}}^{-1} = - \nabla_{\transitionParams \transitionParams}^{2} \log p(\transitionParams \mid \dataset_{0:i})|_{\transitionParams=\transitionParams^{*}_{i}}
+%   + \frac{1}{\sigma^{2}_{0}} \mathbf{I}
+% \end{align}
+
+\textbf{Weight space to function space}
+% Note that the posterior in \cref{eq-laplace-approx-weight-space} is in weight space.
+We can represent the weight space posterior in \cref{eq-laplace-approx-weight-space} in
+function space by linearising the BNN and interpreting it as a GP.
+\begin{align} \label{eq-laplace-approx-function-space}
+  \transitionFn_{\transitionParams_{i}^{*}}(\cdot) &\sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \quad
+  \mu_{\transitionParams_{i}^{*}}(\cdot) &= \transitionFn_{\transitionParams^{*}_{i}}(\cdot) \quad
+  K_{\transitionParams_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) \bm\Sigma_{\transitionParams^{*}_{i}} \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot')^{T}
+\end{align}
+where the Jacobian is given by $\mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}$.
+
+\begin{align} \label{eq-laplace-approx-jacobian}
+\mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}
+\end{align}
 
 \begin{assumption} \label{assumption-ntk-linearisation}
-  Something about NTK being a linearisation around $\theta^{MAP}$ but each update moves away from $\theta^{MAP}$
+  Something about NTK being a linearisation around $\theta^{*}_{i}$ but each update moves away from $\theta^{*}_{i}$
 \end{assumption}
@@
   \end{itemize}
+  \item Is linearising NN mean and using fast updates during episode better than keeping non-linearised mean and not updating?
   \item How does number of inducing points affect performance?
@@
 
+\section{Laplace Approximation} \label{sec-laplace-approximation}
+
 \section{Template stuff}

### 2023-03-24 paper/proof.tex
initial commit

\section{Assumptions}\label{sec:assumptions}
This section is a draft, possibly contains mistakes
Assumptions on the model required for deriving regret bounds, in the spirit of \cite{curiCombining2021}. \cref{ass:lipschitz-f} and \cref{ass:lipschitz-gp} are copied from \cite{curiCombining2021}, whereas \cref{ass:calibrated} has been modified to accommodate the mean and variance changing during the episode.
\begin{assumption}\label{ass:lipschitz-f}
The true underlying function $f$ is $L_f$-Lipschitz and the elements of the noise vector $w_n$ are $\sigma$-sub-Gaussian.
\end{assumption}
\begin{assumption}[Well-calibrated]\label{ass:calibrated}
Assume that for any $\delta >0$ $\exists$ a set of sequences $\{\beta_{t, i}\}_{t>0, i=0}^{episode_length}$ such that the model mean and variance functions $\mu_{t, i}$, $\sigma_{t, i}$ satisfy for all $(s, a) \in \mathcal{S} \times \mathcal{A}$ the upper bound
\begin{equation}\label{eq:calibrated}
\text{Pr}(\| f(s, a) - \mu_{t, i}(s, a) \| \leq \beta_{t, i}\sigma_{t, i}) \geq 1 - \delta
\end{equation}
\end{assumption}

\begin{assumption}\label{ass:lipschitz-gp}
The mean and variance functions are lipschitz
\end{assumption}
\section{Proof of regret bounds}
This section is a draft, possibly contains mistakes
Plan for the proof:
\begin{itemize}
\item Following Appendix D in \cite{curiCombining2021}, derive a regret bound for the case where the model $\mu_t$ and $\sigma_t$ can be updated within the episode, if assumptions in \cref{sec:assumptions} are satisfied.
\item Show that sparse GPs satisfy \cref{ass:calibrated}
\end{itemize}

### 2023-03-24 paper/main.tex
added citations
added proog
updated abstract after meeting 23rd march

@@
   % Reinforcement learning (RL) agents typically perform learning after an episode, ignoring the potential information gain whilst collecting data.
+  % Reinforcement learning (RL) agents typically perform learning offline and do not utilise the information gained during an episode.
+  % We present a Bayesian model-based RL algorithm which incorporates this information by updating a dynamic model's posterior during an episode.
+  % Our method leverages the fast posterior updates available in the dual parameterisation of sparse variational Gaussian processes.
+  % Importantly, our algorithm scales to 1) environment's with high dimensional state-spaces as it is built upon the connection between Bayesian neural networks (BNNs) and
+  % Gaussian processes (GPs) and 2) long episodes, as the complexity of our updates is independent of episode length.
+  % We demonstrate that our fast posterior updates improve sample efficiency in environments with action penalties, a notoriously difficult
+  % challenge for model-based RL algorithms.
   Reinforcement learning (RL) agents typically perform learning offline and do not utilise the information gained during an episode.
   We present a Bayesian model-based RL algorithm which incorporates this information by updating a dynamic model's posterior during an episode.
-  Our method leverages the fast posterior updates available in the dual parameterisation of sparse variational Gaussian processes.
-  Importantly, our algorithm scales to 1) environment's with high dimensional state-spaces as it is built upon the connection between Bayesian neural networks (BNNs) and
-  Gaussian processes (GPs) and 2) long episodes, as the complexity of our updates is independent of episode length.
+  Typically training a neural network dynamic model is not feasible and nonparameteric methods such as Gaussian processes scale poorly with data.
+  Importantly, our algorithm scales to 1) environment's with high dimensional state-spaces, 2) large data sets and 3) long episodes,
+  as the complexity of our updates is independent of episode length.
   We demonstrate that our fast posterior updates improve sample efficiency in environments with action penalties, a notoriously difficult
@@
 
+\cite{rossellApproximateLaplaceApproximations2021}
+
 \subsection{Efficiently Sampling Functions for Posterior Sampling}
 \cite{wilsonEfficiently2020}
+\cite{wilsonPathwise2021}
 
@@
 
+\input{proof.tex}
+
 \section{Hallucinated Upper Confidence Reinforcement Learning (H-UCRL)} \label{sec-hucrl}

### 2023-03-30 paper/main.tex
merged

@@
 %\title{Investigatin Uncertainty Quantification in Model-based Reinforcement Learning}
-\title{Model-based Reinforcement Learning with Fast Posterior Updates}
+% \title{Model-based Reinforcement Learning with Fast Posterior Updates}
+\title{Sequential Decision-Making under Uncertainty with Big Data}
 \author{%
@@
 \newcommand{\actionDomain}{\ensuremath{\mathcal{A}}}
+\newcommand{\inputDomain}{\ensuremath{\mathbb{R}^{D}}}
+\newcommand{\outputDomain}{\ensuremath{\mathbb{R}^{C}}}
 \newcommand{\policyDomain}{\ensuremath{\Pi}}
@@
   % challenge for model-based RL algorithms.
-  Reinforcement learning (RL) agents typically perform learning offline and do not utilise the information gained during an episode.
-  We present a Bayesian model-based RL algorithm which incorporates this information by updating a dynamic model's posterior during an episode.
-  Typically training a neural network dynamic model is not feasible and nonparameteric methods such as Gaussian processes scale poorly with data.
-  Importantly, our algorithm scales to 1) environment's with high dimensional state-spaces, 2) large data sets and 3) long episodes,
-  as the complexity of our updates is independent of episode length.
-  We demonstrate that our fast posterior updates improve sample efficiency in environments with action penalties, a notoriously difficult
-  challenge for model-based RL algorithms.
+  %
+  % Reinforcement learning (RL) agents typically perform learning offline and do not utilise the information gained during an episode.
+  % We present a Bayesian model-based RL algorithm which incorporates this information by updating a dynamic model's posterior during an episode.
+  % Typically training a neural network dynamic model is not feasible and nonparameteric methods such as Gaussian processes scale poorly with data.
+  % Importantly, our algorithm scales to 1) environment's with high dimensional state-spaces, 2) large data sets and 3) long episodes,
+  % as the complexity of our updates is independent of episode length.
+  % We demonstrate that our fast posterior updates improve sample efficiency in environments with action penalties, a notoriously difficult
+  % challenge for model-based RL algorithms.
+  %
+  Deep neural networks
+
+  Obtain SVGP posterior on trained deep neural network (NN) without optimising any variational parameters.
+
+  Dual formulation enables fast updates for 1) model-based RL 2) pathwise, function-space conditioning.
+  % Reinforcement learning (RL) agents typically perform learning offline and do not utilise the information gained during an episode.
+  % We present a Bayesian model-based RL algorithm which incorporates this information by updating a dynamic model's posterior during an episode.
+  % Typically training a neural network dynamic model is not feasible and nonparameteric methods such as Gaussian processes scale poorly with data.
+  % Importantly, our algorithm scales to 1) environment's with high dimensional state-spaces, 2) large data sets and 3) long episodes,
+  % as the complexity of our updates is independent of episode length.
+  % We demonstrate that our fast posterior updates improve sample efficiency in environments with action penalties, a notoriously difficult
+  % challenge for model-based RL algorithms.
 \end{abstract}
@@
 
-Why model-based RL:
 \begin{itemize}
-  \item Better sample efficiency than model-free RL
-\end{itemize}
-
-Why Bayesian model-based RL:
+  \item DNNs scale to high-dimensional and large data sets but 1) no UQ and 2) cannot be updated quickly
   \begin{itemize}
-  \item Can be used to combat model bias
-  \item Better exploration in environment's that are hard to explore (sparse reward/control penalties)
-  \item Bayesian framwork can naturally handle stochastic environments
-\end{itemize}
-
-Issues with uncertainty in model-based RL:
-\begin{itemize}
-  \item Over exploration when using optimism in the face of uncertainty
-  \begin{itemize}
-    \item Agent drives exploration into region of high epistemic uncertainty because it thinks it could have high return.
-    \item In reality, the dynamic model is innacurate and the agent spends the majority of an episode exploiting this innacuracy.
-    \item What if the agent could update it's model during an episode and realise it's pointless to explore in this region
-    \item We show that this can reduce model exploitation and in turn, improve sample efficiency.
+    \item In many domains we want to make decisions under a learned model's uncertainty, e.g. in healthcare, robotics, autonomous vehicles. (safey, sample efficiency (cost/time))
+    \item In continual learning (e.g. online learning/RL) we need to update model quicker than retraining NN with SGD.
+    \item Poorly calibrated model uncertainty
   \end{itemize}
@@
 
-\section{Problem Statement and Background} \label{sec:problem-statement}
+\begin{itemize}
+  \item BNNs give UQ over high-dimensional parameter space,
+  \begin{itemize}
+    \item Exact inference intractable
+    \item Sampling in parameter space vs Sampling in function space
+  \end{itemize}
+\end{itemize}
+
+\begin{itemize}
+  \item BNN to dual SVGP
+  \begin{itemize}
+    \item Keep in spirit of Laplace approx and fit SVGP with no more optimisation
+    \item Now we can update posterior without retraining, which is fast (good for model-based RL and TS BO?)
+    \item Now we can sample in function space with pathwise conditioning (because we have SVGP).
+    \begin{itemize}
+      \item Our pathwise conditioning will be better as we can use dual update
+    \end{itemize}
+  \end{itemize}
+\end{itemize}
+
+\section{Background} \label{sec:background}
+% \section{dual SVGP}
+% In this section we extend these fast updates to environment's with high dimensional state spaces and large data sets.
+% % Our method draws on the connection between BNNs and GPs and formulates a function space SVGP posterior given
+% Our method uses a BNN dynamic model and draws on the connection between BNNs and GPs
+% \parencite{khanApproximate2019} to formulate a function space SVGP posterior,
+% where we can apply the fast updates from \cref{eq-dual-update-svgp}.
+% At a high-level, we first use Laplace's approximation to obtain a weight space posterior for our BNN.
+% We then linearise our BNN around the optimal parameters and interpret it as a GP.
+% Finally, we formulate a lower rank approximation of this GP posterior (i.e. a SVGP posterior) using inducing variables.
+% % formulates a function space SVGP posterior by drawing on the connection between BNNs and GPs.
+
+In this section, we recap how to fit a GP posterior to a trained deep neural network (DNN).
+We start by obtaining a posterior over the weights of a trained neural network via the Laplace approximation.
+We then show how we can obtain a function-space posterior, (i.e. a GP posterior)
+by linearising the neural network around the weights Maximum a Posteriori (MAP) estimate.
+% We then show that by linearising the neural network we can obtain a function-space posterior, i.e. a GP posterior.
+
+% We paraterise our single-step dynamic model $\transitionFnWithParams : \inputDomain \rightarrow \outputDomain$
+% as an $L\text{-layer}$ NN with weights $\transitionParams$.
+Given a data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
+the goal of (supervised) deep learning, is to train the weights $\transitionParams \in \R^{P}$ of an $L\text{-layer}$ NN
+$f : \inputDomain \rightarrow \outputDomain$ to minimize the (regularized) empirical risk,
+\begin{align}
+  \transitionParams^{*} = \arg \min_{\transitionParams \in \R^{D}} \mathcal{L}(\dataset;\transitionParams) = \arg \min_{\transitionParams \in \R^{D}} \left(
+  R(\transitionParams) + \sum_{n=0}^{N-1} l(f(\mathbf{x}_{n} ; \transitionParams), \mathbf{y}_{n}) \right).
+\end{align}
+In practice, it is common to use the mean squared error (MSE) loss
+$l(f(\mathbf{x}_{n} ; \transitionParams),\mathbf{y}_{n}) = \|f(\mathbf{x}_{n} ; \transitionParams) - \mathbf{y}_{n} \|^{2}_{2}$
+and to use the weight decay regularizer $R(\transitionParams)=\frac{1}{2}\gamma^{-2}\|\transitionParams\|^{2}_{2}$.
+However, the practioner is free to choose any loss and regularizer. \todo{I think?}
+
+\textbf{Laplace approximation}
+The Laplace approximation \todo{add citation of original paper} constructs a Gaussian approximation of the weight-space posterior $p(\transitionParams \mid \dataset)$
+by using a second-order Taylor expansion of $\mathcal{L}$ around $\transitionParams^{*}$.
+The posterior approximation is given by,
+\begin{align} \label{eq-laplace-approx-weight-space}
+  p(\transitionParams \mid \dataset) \approx \mathcal{N} \left( \transitionParams \mid \transitionParams^{*} , \bm\Sigma_{\transitionParams^{*}} \right)
+  \quad \text{with} \quad \bm\Sigma_{\transitionParams} =
+ - \nabla_{\transitionParams \transitionParams}^{2} \mathcal{L} ( \dataset ; \transitionParams)|_{\transitionParams=\transitionParams^{*}}
+\end{align}
+That is, it sets the posterior precision to the Hessian of the loss at the optimal parameters $\transitionParams^{*}$.
+It is worth noting that computing the Hessian of the loss can be computationally intractable for large networks.
+The prior terms are usually trivial, so we will focus on the likelihood here.
+The Jacobian and Hessian of the log likelihood can be expressed per data point,
+\begin{align} \label{eq-jac}
+  \nabla_{\transitionParams} \log p(\mathbf{y} \mid \mathbf{f}(\mathbf{x}; \transitionParams)) &= \mathbf{J}(\mathbf{x})^{T} \mathbf{r}(\mathbf{y} ; \mathbf{f}) \\
+  \nabla^{2}_{\transitionParams\transitionParams} \log p(\mathbf{y} \mid \mathbf{f}(\mathbf{x}; \transitionParams)) &= \mathbf{H}(\mathbf{x})^{T}
+  \mathbf{r}(\mathbf{y};\mathbf{f}) - \mathbf{J}(\mathbf{x})^{T} \bm\Lambda(\mathbf{y};\mathbf{f}) \mathbf{J}(\mathbf{x}),
+\label{eq-hess}
+\end{align}
+through the Jacobian $\mathbf{J} \in \R^{C \times P}$ and Hessian $\mathbf{H} \in \R^{C \times P \times P}$ of the feature extractor $\mathbf{f}(\mathbf{x}; \bm\transitionParams)$,
+\begin{align} \label{eq-jac}
+[\mathbf{J}(\cdot)]_{ci} = \odv{f_{c}(\cdot ; \transitionParams)}{\transitionParams_{i}}_{\transitionParams=\transitionParams^{*}} \qquad
+[\mathbf{H}(\cdot)]_{cij} = \odv{f_{c}(\cdot ; \transitionParams)}{\transitionParams_{i}\transitionParams_{j}}_{\transitionParams=\transitionParams^{*}}
+\end{align}
+where
+$\mathbf{r}(\mathbf{y}; \mathbf{f}) = \nabla_{\mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$ can be interpreted as a residual and
+$\bm\Lambda(\mathbf{y} ; \mathbf{f}) &= \nabla^{2}_{\mathbf{f} \mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$
+as per-input noise.
+Many approximations exist and can be used alongsied our method.
+We refer the reader to \cite{daxbergerLaplace2021} for more details.
+See \cref{sec-laplace-approximation} for further details on the Laplace approximation.
+
+% \begin{align}
+% \Sigma_{\transitionParams_{i}}^{-1} = - \nabla_{\transitionParams \transitionParams}^{2} \log p(\transitionParams \mid \dataset_{0:i})|_{\transitionParams=\transitionParams^{*}_{i}}
+%   + \frac{1}{\sigma^{2}_{0}} \mathbf{I}
+% \end{align}
+
+\textbf{Weight space to function space}
+% We can represent the log joint density in the function space,
+% \begin{align} \label{eq-laplace-approx-function-space}
+%   \sum_{n=1}^{N} \log p \left(y_{n} \mid f(\mathbf{x}_{n} ; \transitionParams_{0:i}) \right) + \log p(f(\mathbf{X}; \transitionParams_{0:i}))
+% \end{align}
+We can represent the weight space posterior from \cref{eq-laplace-approx-weight-space}, in
+function space, by linearising the BNN and interpretting it as a GP.
+The GP prior is then given by,
+\begin{align} \label{eq-laplace-approx-function-space}
+  % \transitionFn_{\transitionParams_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \qquad
+  f(\cdot ;\transitionParams) \sim \mathcal{N} \left( \mu(\cdot), k(\cdot, \cdot') \right) \qquad
+  % \mu_{\transitionParams_{i}^{*}}(\cdot)
+  \mu(\cdot)
+  = f(\cdot ;\transitionParams^{*}) \qquad
+  % K_{\transitionParams_{i}^{*}}(\cdot, \cdot')
+  k(\cdot, \cdot')
+  = \gamma^{2} \mathbf{J}(\cdot) \mathbf{J}(\cdot')^{T},
+\end{align}
+where the kernel is the neural tangent kernel (NTK) \parencite{immerImprovingPredictionsBayesian2021}.
+\todo{what mean function shoudl this use???}
+\todo{NTK times some factor??}
+% with Jacobian given by $\mathbf{J}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}$.
+% The kernel in \cref{eq-laplace-approx-function-space} is the neural tangent kernel (NTK)
+% $k(\mathbf{x}, \mathbf{x}') = \sigma_{0}^{2} J_{\transitionParams^{*}}(\mathbf{x}) J_{\transitionParams^{*}}(\mathbf{x}')^{T}$
+% \parencite{immerImprovingPredictionsBayesian2021}
+% to formulate the GP posterior $p(f(\mathbf{X} ;\transitionParams_{0:i}) \mid \dataset_{0:i})$.
+It is worth noting that the NTK linearises the network around the optimised parameters $\transitionParams_{i}^{*}$,
+so the function space prior (and thus posterior) is only a locally linear approximation.
+In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
+It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.
+Given our GP prior, we can use the properties of multivariate normals to obtain our GP posterior by conditioning on the data.
+Our GP posterior is given by,
+\todo{add mean func to GP posterior if we're using one}
+\begin{align} \label{eq-gp-predictive-posterior}
+  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
+  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
+  \left( f(\mathbf{x}_{*}) \mid \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} \mathbf{m}^{*},
+  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} + \bm\Lambda(\mathbf{y} ; \mathbf{f})^{-1} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
+\end{align}
+
+\section{Dual SVGP} \label{sec:method}
+The GP predictive posterior in \cref{eq-gp-predictive-posterior} is computationally expensive
+as it requires inverting $N\times N$ matrix.
+Sparse approximations using pseudo points ...
+\begin{align} \label{eq-svgp-predictive-posterior}
+  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
+  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
+  \left( f(\mathbf{x}_{*}) \mid \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} \mathbf{m}^{*},
+  k_{**} - \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} \mathbf{k}_{*\mathbf{x}}^{T} \right) \\
+  % &\approx \mathcal{N}
+  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} \mathbf{A}^{T} + \mathbf{A} \mathbf{V}^{*} \mathbf{A}^{T} \right) \\
+&\approx \mathcal{N} \left( f(\mathbf{x}_{*}) \mid \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{m}^{*},
+  k_{**} - \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
+  % \mathbf{k}_{*\inducingInput} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\inducingInput}^{T}
+  + \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}}  \mathbf{V}^{*}  \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
+  \right)
+\coloneqq q_{\inducingVariable}(f(\mathbf{x}_{*}))
+\end{align}
+% where $\mathbf{A} = \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}}$
+
+We follow \cite{csatoSparseOnlineGaussian2002} and express our GP posterior in the dual parameter space.
+However, we consider the variational formulation introduced by \cite{adamDualParameterizationSparse2021}, where the optimal variational parameters are given by,
+\begin{align} \label{eq-dual-params}
+\mathbf{m}^{*} = \mathbf{V}^{*}\bm\alpha^{*} \quad \mathbf{V}^{*} = [\mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} + \bm\beta^{*}]
+\end{align}
+Importantly, we can calculate the natural parameters $(\bm\alpha, \bm\beta)$ in closed form,
+\todo{paul needs to update \cref{eq-dual-svgp-params}}
+\begin{align} \label{eq-dual-svgp-params}
+\bm\alpha_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right] \\
+\bm\beta_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right].
+\end{align}
+This simplifies SVGP inference \parencite{hensmanGaussian2013} as it no longer requires the variational parameters $(\mathbf{m}, \mathbf{V})$ to be optimised.
+
+% Importantly, \cite{changFantasizingDualGPs2022} show that in the dual space,
+% conditioning on new observations reduces to suming the dual variables from the previous time
+% step with an update, given by,
+% \todo{pick best way to show new data (using superscript new or just time indexing?)}
+% \begin{align} \label{eq-dual-update-svgp}
+% \bm\alpha_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right] \\
+% \bm\beta_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right]
+% \end{align}
+
+% We follow \cite{csatoSparseOnlineGaussian2002} and express our GP posterior in the dual parameter space,
+% % to write GP posterior $p(f(\mathbf{X} ;\transitionParams_{0:i}) \mid \dataset_{0:i})$ as,
+% \begin{align} \label{eq-gp-post}
+%   \mathbb{E}_{p(f(\mathbf{x}_{*}) \mid \mathbf{y}_{n})} \left[ f(\mathbf{x}_{*}) \right] &= \mu(\mathbf{x}_{*}) + \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
+%   \mathbb{V}_{p(f(\mathbf{x}_{*}) \mid \mathbf{y}_{n})} \left[ f(\mathbf{x}_{*}) \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \text{diag}(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
+% \end{align}
+% % \begin{align} \label{eq-laplace-approx-function-space}
+% %   \mathbb{E}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
+% %   \mathbb{V}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \diag(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
+% % \end{align}
+% where the dual parameters $(\bm\alpha_n, \bm\beta_n)$ are vectors of,
+% \begin{align} \label{eq-gp-dual-params}
+%   \bm\alpha_{n} \coloneqq \left\{ \mathbb{E}_{p(f(\mathbf{x}_{i}) \mid \mathbf{y}_{n})} \left[ \nabla_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \right\}_{i=1}^{N} \qquad
+%   \bm\beta_{n} \coloneqq \left\{ \mathbb{E}_{p(f(\mathbf{x}_{i}) \mid \mathbf{y}_{n})} \left[ \nabla^{2}_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \right\}_{i=1}^{N}
+% \end{align}
+% Importantly, this parameterisation
+
+% \textbf{dual-SVGP}
+% \begin{align} \label{eq-svgp-post}
+%   \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ f(\mathbf{x}_{*}) \right] &= \mu(\mathbf{x}_{*}) + \mathbf{k}_{\mathbf{z}*}^{T} \bm\alpha_{\mathbf{u}} \\
+%   \mathbb{V}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ f(\mathbf{x}_{*}) \right] &= k_{**} - \mathbf{k}_{\mathbf{z}*}^{T} \left[ \mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} - \left( \mathbf{K}_{\mathbf{z} \mathbf{z}} + \bm\beta_{\mathbf{u}} \right)^{-1} \right] \mathbf{k}_{\mathbf{z}*}
+% \end{align}
+% % \begin{align} \label{eq-laplace-approx-function-space}
+% %   \mathbb{E}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
+% %   \mathbb{V}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \diag(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
+% % \end{align}
+% where the dual parameters $(\bm\alpha_{\mathbf{u}}, \bm\beta_{\mathbf{u}})$ are vectors of,
+% \begin{align} \label{eq-svgp-dual-params}
+%   \bm\alpha_{\mathbf{u}} \coloneqq \mathbf{k}_{\mathbf{z}i} \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ \nabla_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \qquad
+%   \bm\beta_{\mathbf{u}} \coloneqq \mathbf{k}_{\mathbf{z}i} \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ \nabla^{2}_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \mathbf{k}_{\mathbf{z}i}^{T}
+% \end{align}
+
+% weight space posterior in \cref{eq-laplace-approx-weight-space} in
+% function space by linearising the BNN and interpreting it as a GP.
+% \begin{align} \label{eq-laplace-approx-function-space}
+%   \transitionFn_{\transitionParams_{i}}(\cdot) &\sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \quad
+%   \mu_{\transitionParams_{i}^{*}}(\cdot) &= \transitionFn_{\transitionParams^{*}_{i}}(\cdot) \quad
+%   K_{\transitionParams_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) \bm\Sigma_{\transitionParams^{*}_{i}} \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot')^{T}
+% \end{align}
+% where the Jacobian is given by $\mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}$.
+
+% \begin{align} \label{eq-laplace-approx-jacobian}
+% \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}
+% \end{align}
+
+% % Note that the posterior in \cref{eq-laplace-approx-weight-space} is in weight space.
+% We can represent the weight space posterior in \cref{eq-laplace-approx-weight-space} in
+% function space by linearising the BNN and interpreting it as a GP.
+% \begin{align} \label{eq-laplace-approx-function-space}
+%   \transitionFn_{\transitionParams_{i}^{*}}(\cdot) &\sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \quad
+%   \mu_{\transitionParams_{i}^{*}}(\cdot) &= \transitionFn_{\transitionParams^{*}_{i}}(\cdot) \quad
+%   K_{\transitionParams_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) \bm\Sigma_{\transitionParams^{*}_{i}} \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot')^{T}
+% \end{align}
+% where the Jacobian is given by $\mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}$.
+
+% \begin{align} \label{eq-laplace-approx-jacobian}
+% \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}
+% \end{align}
+
+\subsection{Fast Updates}
+Importantly, \cite{changFantasizingDualGPs2022} show that in the dual space,
+conditioning on new observations reduces to suming the dual variables from the previous time
+step with an update, given by,
+\todo{pick best way to show new data (using superscript new or just time indexing?)}
+\begin{align} \label{eq-dual-update-svgp}
+\dualParam{1}^{t+1} &\leftarrow \dualParam{1}^{t} +  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))} \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right] \\
+\dualParam{2}^{t+1} &\leftarrow \dualParam{2}^{t} +  \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))}  \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right]
+\end{align}
+Importantly, for a single new observation $((\state_{t}, \action_{t}), \state_{t+1})$ this update has
+complexity $\mathcal{O}(\numInducing^{2})$.
+This is a significant improvement to naive GP conditioning, which has complexity $\mathcal{O}((\numDataNew + \numDataOld)^{3})$
+and sparse GP conditioning, which has complexity $\mathcal{O}((\numDataNew + \numDataOld)\numInducing^{2})$.
+\todo{double check these complexities are right and cite them/show equaitons}
+It is worth highlighting that the complexity of \cite{changFantasizingDualGPs2022} update does not increase during an episode.
+
+\subsubsection{Model-based RL}
+
+\subsubsection{Efficiently Sampling Functions for Posterior Sampling}
+\cite{wilsonEfficiently2020}
+\cite{wilsonPathwise2021}
+
+% \begin{align} \label{eq-dual-update-svgp}
+%  \dualParam{1}^{\text{new}} &\leftarrow \dualParam{1}^{\text{old}} +
+%   \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}))}
+%  \left[ \log p(\state_{t+1}^{\text{new}} \mid \latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}) ) \right] \\
+%  \dualParam{2}^{\text{new}} &\leftarrow \dualParam{2}^{\text{old}} +
+%   \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}))}
+%  \left[ \log p(\state_t^{\horizon+1} \mid \latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}) ) \right] \\
+%  \dualParam{1}^{\horizon+1} &\leftarrow \dualParam{1}^{\horizon} +
+%   \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}
+%  \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right] \\
+%  \dualParam{2}^{\horizon+1} &\leftarrow \dualParam{2}^{\horizon} +
+%   \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}
+%  \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right]
+% \end{align}
+
+\begin{assumption} \label{assumption-ntk-linearisation}
+  Something about NTK being a linearisation around $\theta^{*}_{i}$ but each update moves away from $\theta^{*}_{i}$
+\end{assumption}
+
+\cite{rossellApproximateLaplaceApproximations2021}
+
+\section{Experiments}
+Environments
+\begin{itemize}
+  \item Compare updated posterior with non updated posterior
+  \item Need to show update is fast enough for practical use?
+  \begin{itemize}
+    \item How frequently can we do the posterior update? Every time step or every $K$ steps?
+    \item Update depends on number of inducing points?
+    \item What experiments can we show for this? Wall clock time vs planning horizon with different numbers of inducing points?
+  \end{itemize}
+  \item Is linearising NN mean and using fast updates during episode better than keeping non-linearised mean and not updating?
+  \item How does number of inducing points affect performance?
+  \begin{itemize}
+    \item More inducing points means better approximation but larger computational complexity.
+  \end{itemize}
+  \item How good is the assumption that we can linearise BNN to get NTK?
+  \begin{itemize}
+    \item Does model's performance get worse during an episode because linearisation becomes more wrong?
+    \item SVGP does't have this issue so compare to SVGP in cartpole?
+  \end{itemize}
+  \item What length planning horizon to use?
+  \begin{itemize}
+    \item Too small (e.g. $\Horizon=0$) would mean no exploration?
+    \item Can $\Horizon$ be too large?
+  \end{itemize}
+  \begin{itemize}
+  \item Compare for different strategies of making decisions under dynamic model's uncertainty:
+    \begin{itemize}
+      \item \textbf{Greedy exploitation} \(\pi_{\text{greedy}}\)
+      \item \textbf{Hallucinated-UCRL} \(\pi_{\text{HUCRL}}\)
+      \item \textbf{Thompson sampling} \(\pi_{\text{TS}}\)
+    \end{itemize}
+  \end{itemize}
+  \item Compare impact of stationary vs non-stationary priors
+  \begin{itemize}
+    \item First do this with GP
+    \item Then try to do with Laplace BNN
+  \end{itemize}
+  \item Compare impact of function vs weight space
+\end{itemize}
+
+\section{Conclusion} \label{sec:conclusion}
+
+\section*{Broader Impact}
+
+\section*{Acknowledgements}
+Aidan Scannell is funded by the Finnish Center for Artificial Intelligence.
+
+% \section*{References}
+\small
+\printbibliography
+\normalsize
+% TODO make bibliography small a better way
+
+References follow the acknowledgments. Use unnumbered first-level heading for
+the references. Any choice of citation style is acceptable as long as you are
+consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
+when listing the references.
+Note that the Reference section does not count towards the page limit.
+\medskip
+
+\appendix
+
+\section{Appendix}
+
+Optionally include extra information (complete proofs, additional experiments and plots) in the appendix.
+This section will often be part of the supplemental material.
+
+\section{Model-based Reinforcement Learning with Fast Updates}
+
+\subsection{Problem Statement and Background} \label{sec:problem-statement}
 We consider environments with states \(\state \in \stateDomain \), actions \(\action \in \actionDomain\) and transition dynamics \(\transitionFn: \stateDomain \times \actionDomain \rightarrow \stateDomain \) subject to
@@
 
-\section{Model-based Reinforcement Learning with Fast Updates}
+\subsubsection{Fast updates}
+
+In this section we extend these fast updates to environment's with high dimensional state spaces and large data sets.
+% Our method draws on the connection between BNNs and GPs and formulates a function space SVGP posterior given
+Our method uses a BNN dynamic model and draws on the connection between BNNs and GPs
+\parencite{khanApproximate2019} to formulate a function space SVGP posterior,
+where we can apply the fast updates from \cref{eq-dual-update-svgp}.
+At a high-level, we first use Laplace's approximation to obtain a weight space posterior for our BNN.
+We then linearise our BNN around the optimal parameters and interpret it as a GP.
+Finally, we formulate a lower rank approximation of this GP posterior (i.e. a SVGP posterior) using inducing variables.
+% formulates a function space SVGP posterior by drawing on the connection between BNNs and GPs.
+
 The strategies in \cref{eq-greedy,eq-posterior-sampling,eq-hucrl} do not update the dynamic model during an episode.
@@
 \end{align}
-
-\subsection{Dual GPs for Fast Updates}
-Sparse GP predictive posterior is given by,
-\begin{align} \label{eq-svgp-predictive-posterior}
-  q_{\inducingVariable}(\transitionFn(\state_{t}, \action_{t})) = \mathcal{N}
-  \left( \transitionFn(\state_{t}, \action_{t}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\inducingInput\inducingInput}^{-1} \mathbf{A}^{T} + \mathbf{A} \mathbf{V}^{*} \mathbf{A}^{T} \right)
-\end{align}
-where $\mathbf{A} = \mathbf{K}_{\mathbf{X}\inducingInput} \mathbf{K}^{-1}_{\inducingInput\inducingInput}$.
-\cite{adamDualParameterizationSparse2021} showed that optimal variational parameters are given by,
-\begin{align} \label{eq-dual-params}
-\mathbf{m}^{*} = \mathbf{V}^{*}\dualParam{1}^{*} \quad \mathbf{V}^{*} = [\mathbf{K}_{\inducingInput\inducingInput}^{-1} + \dualParam{2}^{*}]
-\end{align}
-Importantly, \cite{changFantasizingDualGPs2022} show that in the dual space,
-conditioning on new observations reduces to suming the dual variables from the previous time
-step with an update, given by,
-\todo{pick best way to show new data (using superscript new or just time indexing?)}
-\begin{align} \label{eq-dual-update-svgp}
-\dualParam{1}^{t+1} &\leftarrow \dualParam{1}^{t} +  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))} \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right] \\
-\dualParam{2}^{t+1} &\leftarrow \dualParam{2}^{t} +  \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))}  \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right]
-\end{align}
-Importantly, for a single new observation $((\state_{t}, \action_{t}), \state_{t+1})$ this update has
-complexity $\mathcal{O}(\numInducing^{2})$.
-This is a significant improvement to naive GP conditioning, which has complexity $\mathcal{O}((\numDataNew + \numDataOld)^{3})$
-and sparse GP conditioning, which has complexity $\mathcal{O}((\numDataNew + \numDataOld)\numInducing^{2})$.
-\todo{double check these complexities are right and cite them/show equaitons}
-It is worth highlighting that the complexity of \cite{changFantasizingDualGPs2022} update does not increase during an episode.
-
-% \begin{align} \label{eq-dual-update-svgp}
-%  \dualParam{1}^{\text{new}} &\leftarrow \dualParam{1}^{\text{old}} +
-%   \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}))}
-%  \left[ \log p(\state_{t+1}^{\text{new}} \mid \latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}) ) \right] \\
-%  \dualParam{2}^{\text{new}} &\leftarrow \dualParam{2}^{\text{old}} +
-%   \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}))}
-%  \left[ \log p(\state_t^{\horizon+1} \mid \latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}) ) \right] \\
-%  \dualParam{1}^{\horizon+1} &\leftarrow \dualParam{1}^{\horizon} +
-%   \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}
-%  \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right] \\
-%  \dualParam{2}^{\horizon+1} &\leftarrow \dualParam{2}^{\horizon} +
-%   \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}
-%  \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right]
-% \end{align}
-
-\subsection{BNN to SVGP}
-In this section we extend these fast updates to environment's with high dimensional state spaces and large data sets.
-% Our method draws on the connection between BNNs and GPs and formulates a function space SVGP posterior given
-Our method uses a BNN dynamic model and draws on the connection between BNNs and GPs
-\parencite{khanApproximate2019} to formulate a function space SVGP posterior,
-where we can apply the fast updates from \cref{eq-dual-update-svgp}.
-At a high-level, we first use Laplace's approximation to obtain a weight space posterior for our BNN.
-We then linearise our BNN around the optimal parameters and interpret it as a GP.
-Finally, we formulate a lower rank approximation of this GP posterior (i.e. a SVGP posterior) using inducing variables.
-% formulates a function space SVGP posterior by drawing on the connection between BNNs and GPs.
-
-% We first show how to
-% i.e. we show these fast updates when using a BNN dynamic model
-
-\textbf{Model learning}
-We paraterise our single-step dynamic model $\transitionFnWithParams : \stateDomain \times \actionDomain \rightarrow \stateDomain$
-as an $L\text{-layer}$ NN with weights $\transitionParams$.
-Given the state transition data set $\dataset_{0:i} = \{(\state_{n}, \action_{n}), \state_{n+1}\}_{n=0}^{N_{i}}$ at episode $i$,
-we train the weights $\transitionParams$ to minimize the (regularized) empirical risk,
-\begin{align}
-  \transitionParams^{*}_{i} = \arg \min_{\transitionParams \in \R^{D}} \mathcal{L}(\dataset_{0:i};\transitionParams) = \arg \min_{\transitionParams \in \R^{D}} \left(
-  R(\transitionParams) + \sum_{n=0}^{N-1} l(\transitionFnWithParams(\state_{n}, \action_{n}), \state_{n+1}; \transitionParams) \right)
-\end{align}
-In practice, it is common to use the mean squared error (MSE) loss
-$l(\cdot,\cdot;\transitionParams) = \|\transitionFnWithParams(\state_{n}, \action_{n}) - \state_{n+1} \|^{2}_{2}$
-and to use the weight decay regularizer $R(\transitionParams)=\frac{1}{2}\gamma^{-2}\|\transitionParams\|^{2}_{2}$.
-However, the practioner is free to choose any loss and regularizer. \todo{I think?}
-
-\textbf{Laplace approximation}
-The Laplace approximation \todo{add citation of original paper} constructs a Gaussian approximation of the weight-space posterior $p(\transitionParams_{i} \mid \dataset_{0:i})$
-by using a second-order Taylor expansion of $\mathcal{L}$ around $\transitionParams^{*}_{i}$.
-The posterior approximation is given by,
-\begin{align} \label{eq-laplace-approx-weight-space}
-  p(\transitionParams_{i} \mid \dataset_{0:i}) \approx \mathcal{N} \left( \transitionParams_{i} \mid \transitionParams^{*}_{i} , \bm\Sigma_{\transitionParams^{*}_{i}} \right)
-  \quad \text{with} \quad \bm\Sigma_{\transitionParams_{i}} =
- - \nabla_{\transitionParams \transitionParams}^{2} \mathcal{L} ( \dataset_{0:i} ; \transitionParams)|_{\transitionParams=\transitionParams^{*}_{i}}
-\end{align}
-That is, it sets the posterior precision to the hessian of the loss at the optimal parameters $\transitionParams^{*}_{i}$.
-It is worth noting that computing the hessian of the loss can be computationally intractable for large networks.
-Many approximations exist and can be used alongsied our method. We refer the reader to \cite{daxbergerLaplace2021} for more details.
-See \cref{sec-laplace-approximation} for further details on the Laplace approximation.
-% \begin{align}
-% \Sigma_{\transitionParams_{i}}^{-1} = - \nabla_{\transitionParams \transitionParams}^{2} \log p(\transitionParams \mid \dataset_{0:i})|_{\transitionParams=\transitionParams^{*}_{i}}
-%   + \frac{1}{\sigma^{2}_{0}} \mathbf{I}
-% \end{align}
-
-\textbf{Weight space to function space}
-% Note that the posterior in \cref{eq-laplace-approx-weight-space} is in weight space.
-We can represent the weight space posterior in \cref{eq-laplace-approx-weight-space} in
-function space by linearising the BNN and interpreting it as a GP.
-\begin{align} \label{eq-laplace-approx-function-space}
-  \transitionFn_{\transitionParams_{i}^{*}}(\cdot) &\sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \quad
-  \mu_{\transitionParams_{i}^{*}}(\cdot) &= \transitionFn_{\transitionParams^{*}_{i}}(\cdot) \quad
-  K_{\transitionParams_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) \bm\Sigma_{\transitionParams^{*}_{i}} \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot')^{T}
-\end{align}
-where the Jacobian is given by $\mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}$.
-
-\begin{align} \label{eq-laplace-approx-jacobian}
-\mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}
-\end{align}
-
-\begin{assumption} \label{assumption-ntk-linearisation}
-  Something about NTK being a linearisation around $\theta^{*}_{i}$ but each update moves away from $\theta^{*}_{i}$
-\end{assumption}
-
-\cite{rossellApproximateLaplaceApproximations2021}
-
-\subsection{Efficiently Sampling Functions for Posterior Sampling}
-\cite{wilsonEfficiently2020}
-\cite{wilsonPathwise2021}
-
-\section{Experiments}
-Environments
-\begin{itemize}
-  \item Compare updated posterior with non updated posterior
-  \item Need to show update is fast enough for practical use?
-  \begin{itemize}
-    \item How frequently can we do the posterior update? Every time step or every $K$ steps?
-    \item Update depends on number of inducing points?
-    \item What experiments can we show for this? Wall clock time vs planning horizon with different numbers of inducing points?
-  \end{itemize}
-  \item Is linearising NN mean and using fast updates during episode better than keeping non-linearised mean and not updating?
-  \item How does number of inducing points affect performance?
-  \begin{itemize}
-    \item More inducing points means better approximation but larger computational complexity.
-  \end{itemize}
-  \item How good is the assumption that we can linearise BNN to get NTK?
-  \begin{itemize}
-    \item Does model's performance get worse during an episode because linearisation becomes more wrong?
-    \item SVGP does't have this issue so compare to SVGP in cartpole?
-  \end{itemize}
-  \item What length planning horizon to use?
-  \begin{itemize}
-    \item Too small (e.g. $\Horizon=0$) would mean no exploration?
-    \item Can $\Horizon$ be too large?
-  \end{itemize}
-  \begin{itemize}
-  \item Compare for different strategies of making decisions under dynamic model's uncertainty:
-    \begin{itemize}
-      \item \textbf{Greedy exploitation} \(\pi_{\text{greedy}}\)
-      \item \textbf{Hallucinated-UCRL} \(\pi_{\text{HUCRL}}\)
-      \item \textbf{Thompson sampling} \(\pi_{\text{TS}}\)
-    \end{itemize}
-  \end{itemize}
-  \item Compare impact of stationary vs non-stationary priors
-  \begin{itemize}
-    \item First do this with GP
-    \item Then try to do with Laplace BNN
-  \end{itemize}
-  \item Compare impact of function vs weight space
-\end{itemize}
-
-\section{Conclusion} \label{sec:conclusion}
-
-\section*{Broader Impact}
-
-\section*{Acknowledgements}
-Aidan Scannell is funded by the Finnish Center for Artificial Intelligence.
-
-% \section*{References}
-\small
-\printbibliography
-\normalsize
-% TODO make bibliography small a better way
-
-References follow the acknowledgments. Use unnumbered first-level heading for
-the references. Any choice of citation style is acceptable as long as you are
-consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
-when listing the references.
-Note that the Reference section does not count towards the page limit.
-\medskip
-
-\appendix
-
-\section{Appendix}
-
-Optionally include extra information (complete proofs, additional experiments and plots) in the appendix.
-This section will often be part of the supplemental material.
 

### 2023-03-30 src/models/base.py

@@ -1,7 +1,12 @@
 #!/usr/bin/env python3
+import logging
 from typing import Any, Callable, NamedTuple, Optional, Tuple
 
-import pytorch_lightning as pl
+
+logging.basicConfig(level=logging.INFO)
+logger = logging.getLogger(__name__)
+
+# import pytorch_lightning as pl
 import torch
 import torch.distributions as td
 import torch.nn as nn
@@ -24,7 +29,10 @@ from torchrl.modules import SafeModule, WorldModelWrapper
 from torchtyping import TensorType
 
 
-class TransitionModel:
+class TransitionModel(nn.Module):
+    def __init(self):
+        super().__init__()
+
     def __call__(
         # self, state: State, action: Action
         self,
@@ -73,8 +81,11 @@ class TransitionModel:
     def train(self, replay_buffer: ReplayBuffer):
         raise NotImplementedError
 
+    def build_loss(self, num_data: int):
+        raise NotImplementedError
 
-class RewardModel:
+
+class RewardModel(nn.Module):
     def __call__(
         self,
         state_mean: StateMean,
@@ -101,6 +112,9 @@ class RewardModel:
     def train(self, replay_buffer: ReplayBuffer):
         raise NotImplementedError
 
+    def build_loss(self, num_data: int):
+        raise NotImplementedError
+
 
 class GaussianModelBaseEnv(ModelBasedEnvBase):
     def __init__(
@@ -109,6 +123,8 @@ class GaussianModelBaseEnv(ModelBasedEnvBase):
         reward_model: RewardModel,
         state_size: int,
         action_size: int,
+        learning_rate: float = 0.01,
+        num_iterations: int = 5000,
         device: str = "cpu",
         dtype=None,
         batch_size: int = None,
@@ -145,6 +161,8 @@ class GaussianModelBaseEnv(ModelBasedEnvBase):
             action=UnboundedContinuousTensorSpec((action_size)),
         )
         self.reward_spec = UnboundedContinuousTensorSpec((1,))
+        self.learning_rate = learning_rate
+        self.num_iterations = num_iterations
 
     def _reset(self, tensordict: TensorDict) -> TensorDict:
         print("inside reset yo")
@@ -155,6 +173,39 @@ class GaussianModelBaseEnv(ModelBasedEnvBase):
         tensordict = tensordict.update({"state_vector_mean": torch.zeros(1)})
         print(tensordict)
         return tensordict
+
[…]

### 2023-03-30 src/models/gp/__init__.py

@@ -1,3 +1,0 @@
-#!/usr/bin/env python3
-from .gp import GPTransitionModel
-from .svgp import SVGPTransitionModel

### 2023-03-30 src/models/gp/svgp.py

@@ -1,448 +1,0 @@
-#!/usr/bin/env python3
-import logging
-from copy import deepcopy
-from typing import Optional
-
-
-logging.basicConfig(level=logging.INFO)
-logger = logging.getLogger(__name__)
-
-import gpytorch
-import pytorch_lightning as pl
-import torch
-import torch.distributions as td
-import torch.nn as nn
-import wandb
-from custom_types import (
-    Action,
-    DeltaStateMean,
-    DeltaStateVar,
-    NoiseVar,
-    Prediction,
-    State,
-    StateMean,
-    StateVar,
-)
-from models import TransitionModel
-from pytorch_lightning import Trainer
-from torch.utils.data import DataLoader, TensorDataset
-from torchrl.data import ReplayBuffer
-from utils import make_data_loader
-
-
-class SVGPTransitionModel(TransitionModel):
-    # TODO implement delta_state properly
-    def __init__(
-        self,
-        likelihood: gpytorch.likelihoods.Likelihood = None,
-        mean_module: gpytorch.means.Mean = None,
-        covar_module: gpytorch.kernels.Kernel = None,
-        num_inducing: int = 16,
-        learning_rate: float = 0.1,
-        batch_size: int = 16,
-        # trainer: Optional[Trainer] = None,
-        num_iterations: int = 1000,
-        delta_state: bool = True,
-        num_workers: int = 1,
-        learn_inducing_locations: bool = True,
-    ):
-        # TODO is this the bset way to set out_size?
-        in_size = 6
-        out_size = covar_module.batch_shape[0]
-
-        self.learning_rate = learning_rate
-        self.batch_size = batch_size
-        self.num_iterations = num_iterations
-        self.delta_state = delta_state
-        self.num_workers = num_workers
-
-        # Learn seperate hyperparameters for each output dim
-        if likelihood is None:
-            likelihood = gpytorch.likelihoods.MultitaskGaussianLikelihood(
-                num_tasks=out_size
-            )
-        # # TODO remove this override
-        # likelihood = gpytorch.likelihoods.MultitaskGaussianLikelihood(
-        #     num_tasks=out_size
-        # )
-
-        self.gp = IndependentMultitaskGPModel(
-            in_size=in_size,
-            out_size=out_size,
-            mean_module=mean_module,
-            covar_module=covar_module,
-            num_inducing=num_inducing,
-            learn_inducing_locations=learn_inducing_locations,
-        )
-        self.likelihood = likelihood
-
-        print("GP params:")
-        for param in self.gp.parameters():
[…]

### 2023-03-30 src/models/transition/base.py

@@ -1,80 +1,54 @@
 #!/usr/bin/env python3
-from typing import Callable, NamedTuple, Optional
+import logging
+from typing import Any, Callable, NamedTuple, Optional, Tuple
 
-import pytorch_lightning as pl
+
+logging.basicConfig(level=logging.INFO)
+logger = logging.getLogger(__name__)
+
+# import pytorch_lightning as pl
 import torch
 import torch.distributions as td
 import torch.nn as nn
 import torch.optim as optim
-from custom_types import Action, Prediction, State
-from torchrl.data import ReplayBuffer
-from torchrl.modules import WorldModelWrapper
+from custom_types import (
+    Action,
+    DeltaStateMean,
+    DeltaStateVar,
+    NoiseVar,
+    Prediction,
+    State,
+    StateMean,
+    StateVar,
+)
+from tensordict import TensorDict
+from tensordict.nn import TensorDictModule
+from torchrl.data import CompositeSpec, ReplayBuffer, UnboundedContinuousTensorSpec
+from torchrl.envs import ModelBasedEnvBase
+from torchrl.modules import SafeModule, WorldModelWrapper
+from torchtyping import TensorType
 
 
-def predict_hucrl(
-    transition_model: TransitionModel,
-    state: State,
-    action: Action,
-    beta: float = 0.01,
-    data_new: Optional = None,
-) -> Prediction:
-    real_action = action[:, 0:-2]
-    print("action: {}".format(action.shape))
-    hallucinated_action = action[:, -1]
-    print("hallucinated_action: {}".format(hallucinated_action.shape))
-    x = torch.concat([state, real_action], -1)
-    prediction = transition_model.forward(x)
-    latent = prediction.latent_dist
-    mu = latent.mean
-    sigma = latent.stddev
-    next_state_mean = mu + sigma * beta
-    next_state_dist = td.Normal(
-        loc=next_state_mean, scale=torch.sqrt(prediction.noise_var)
-    )
-    return next_state_dist
+class TransitionModel(nn.Module):
+    predict: Callable[
+        [InputData, Optional[Data]], Tuple[DeltaStateMean, DeltaStateVar, NoiseVar]
+    ]
+    train: Callable[[DataLoader], TensorType[float, ""]]
 
-
-class TransitionModel:
-    def __call__(self, state: State, action: Action) -> Prediction:
-        return self.predict(state=state, action=action)
-
-    def predict(
-        self, state: State, action: Action, data_new: Optional = None
-    ) -> Prediction:
[…]

### 2023-04-06 src/models/__init__.py
commit before trying on triton

@@ -1,2 +1,5 @@
 # #!/usr/bin/env python3
-from .base import TransitionModel, GaussianModelBaseEnv
+# from .base import TransitionModel, GaussianModelBaseEnv
+from .transition import TransitionModel
+from .reward import RewardModel
+from .world_model import GaussianModelBaseEnv

### 2023-04-06 src/models/reward.py

@@ -1,0 +1,135 @@
+#!/usr/bin/env python3
+#!/usr/bin/env python3
+import logging
+from typing import Any, Callable, NamedTuple, Optional, Tuple
+
+
+logging.basicConfig(level=logging.INFO)
+logger = logging.getLogger(__name__)
+
+import gpytorch
+import torch
+import torch.distributions as td
+import torch.optim as optim
+from custom_types import (
+    Action,
+    DeltaStateMean,
+    DeltaStateVar,
+    NoiseVar,
+    Prediction,
+    State,
+    StateMean,
+    StateVar,
+)
+from models.svgp import SVGP
+from tensordict import TensorDict
+from tensordict.nn import TensorDictModule
+from torch.utils.data import DataLoader, TensorDataset
+from torchrl.data import ReplayBuffer
+from torchrl.envs import ModelBasedEnvBase
+from torchrl.modules import SafeModule, WorldModelWrapper
+from torchtyping import TensorType
+from utils import EarlyStopper
+
+
+class RewardModel(NamedTuple):
+    # predict: Callable[[InputData, Optional[Data]], Tuple[Mean, Var, NoiseVar]]
+    predict: Callable[[TensorDict], TensorDict]
+    train: Callable[[ReplayBuffer], TensorType[float, ""]]
+
+
+def build_SVGPRewardModel(
+    svgp: SVGP,
+    likelihood: gpytorch.likelihoods.Likelihood,
+    learning_rate: float = 1e-2,
+    batch_size: int = 64,
+    num_epochs: int = 1000,
+    num_workers: int = 1,
+    wandb_loss_name: str = "Reward model loss",
+    num_samples: int = 20,
+    early_stopper: EarlyStopper = None,
+):
+    assert len(svgp.variational_strategy.inducing_points.shape) == 2
+    num_inducing, input_dim = svgp.variational_strategy.inducing_points.shape
+    from models.svgp import predict, train
+
+    predict_fn = predict(svgp=svgp, likelihood=likelihood)
+
+    def expected_reward_fn(state, state_var, noise_var, action):
+        # state_action_inputs = torch.concat([state, action], -1)
+        # # print("state_action_inputs {}".format(state_action_inputs.shape))
+        # reward_mean, reward_var, noise_var = predict_fn(state_action_inputs)
+        # return reward_mean
+
+        # print("inside expected reward")
+        # # def expected_reward_fn(td: TensorDict) -> TensorDict:
[…]

### 2023-04-06 src/models/reward/gp.py

@@ -1,210 +1,0 @@
-#!/usr/bin/env python3
-import logging
-from typing import Any, Callable, NamedTuple, Optional, Tuple
-
-
-logging.basicConfig(level=logging.INFO)
-logger = logging.getLogger(__name__)
-
-import gpytorch
-import pytorch_lightning as pl
-import torch
-import torch.distributions as td
-import torch.nn as nn
-import torch.optim as optim
-import wandb
-from custom_types import (
-    Action,
-    DeltaStateMean,
-    DeltaStateVar,
-    NoiseVar,
-    Prediction,
-    State,
-    StateMean,
-    StateVar,
-)
-from models.base import RewardModel
-from torchrl.data import ReplayBuffer
-from torchrl.modules import SafeModule, WorldModelWrapper
-from torchtyping import TensorType
-
-
-class GPRewardModel(RewardModel):
-    def __init__(
-        self,
-        likelihood: gpytorch.likelihoods.Likelihood = None,
-        mean_module: gpytorch.means.Mean = None,
-        covar_module: gpytorch.kernels.Kernel = None,
-        num_inducing: int = 16,
-        learning_rate: float = 0.1,
-        batch_size: int = 16,
-        num_iterations: int = 1000,
-        num_workers: int = 1,
-        learn_inducing_locations: bool = True,
-    ):
-        super().__init__()
-        # TODO set in_size somewhere else
-        in_size = 5
-
-        self.learning_rate = learning_rate
-        self.batch_size = batch_size
-        self.num_iterations = num_iterations
-        self.num_workers = num_workers
-
-        if likelihood is None:
-            likelihood = gpytorch.likelihoods.GaussianLikelihood()
-
-        self.gp = GPModel(
-            in_size=in_size,
-            mean_module=mean_module,
-            covar_module=covar_module,
-            num_inducing=num_inducing,
-            learn_inducing_locations=learn_inducing_locations,
-        )
-        self.likelihood = likelihood
-
-        print("Reward GP params:")
-        for param in self.gp.parameters():
-            print(param)
-        print("Reward lik params:")
-        for param in self.likelihood.parameters():
-            print(param)
-        # self.gp = torch.compile(self.gp)
-        # self.likelihood = torch.compile(self.likelihood)
-
-    def __call__(
-        self,
-        state_mean: StateMean,
-        state_var: StateVar,
-        noise_var: NoiseVar,
-        # self, state_mean: StateMean, state_var: StateVar, num_samples: int = 5
-    ) -> TensorType["one"]:
[…]

### 2023-04-06 src/models/svgp.py

@@ -1,0 +1,670 @@
+#!/usr/bin/env python3
+import logging
+from typing import Any, Callable, NamedTuple, Optional, Tuple
+
+
+logging.basicConfig(level=logging.INFO)
+logger = logging.getLogger(__name__)
+
+from utils import EarlyStopper
+import gpytorch
+import torch
+import torch.distributions as td
+import torch.nn as nn
+import torch.optim as optim
+import wandb
+from custom_types import (
+    Action,
+    DeltaStateMean,
+    DeltaStateVar,
+    NoiseVar,
+    Prediction,
+    State,
+    StateMean,
+    StateVar,
+)
+from models.base import RewardModel
+from torch.utils.data import DataLoader, TensorDataset
+from torchrl.data import ReplayBuffer
+from torchrl.modules import SafeModule, WorldModelWrapper
+from torchtyping import TensorType
+
+
+# class Model:
+#     train_fn: Callable
+#     predict: Callable
+
+
+# def build_svgp_world_model(
+#     state_size: int,
+#     action_size: int,
+#     inducing_points,
+#     mean_module: gpytorch.means.Mean,
+#     covar_module: gpytorch.kernels.Kernel,
+#     likelihood: gpytorch.likelihoods.Likelihood,
+#     learn_inducing_locations: bool = True,
+# ):
+#     return GaussianModelBaseEnv(
+#         transition_model=transition_model,
+#         reward_model=reward_model,
+#         state_size=state_size,
+#         action_size=action_size,
+#         learning_rate=learning_rate,
+#         num_iterations=num_iterations,
+#         device=device,
+#         dtype=dtype,
+#         batch_size=batch_size,
+#     )
+
+
+# def build_svgp_(
+#     out_size: int,
+#     inducing_points,
+#     mean_module: gpytorch.means.Mean,
+#     covar_module: gpytorch.kernels.Kernel,
+#     likelihood: gpytorch.likelihoods.Likelihood,
+#     learn_inducing_locations: bool = True,
+# ):
+#     svgp = SVGP(
+#         out_size=out_size,
+#         inducing_points=inducing_points,
+#         mean_module=mean_module,
+#         covar_module=covar_module,
+#         learn_inducing_locations=learn_inducing_locations,
+#     )
+#     predict_fn = predict(svgp=svgp, likelihood=likelihood)
+#     train_fn = train(
+#         svgp=svgp,
+#         likelihood=likelihood,
[…]

### 2023-04-06 src/models/transition.py

@@ -1,0 +1,197 @@
+#!/usr/bin/env python3
+import logging
+from copy import deepcopy
+from typing import Any, Callable, NamedTuple, Optional, Tuple
+
+
+logging.basicConfig(level=logging.INFO)
+logger = logging.getLogger(__name__)
+
+from utils import EarlyStopper
+import gpytorch
+import torch
+import torch.distributions as td
+import torch.optim as optim
+from custom_types import (
+    Action,
+    DeltaStateMean,
+    DeltaStateVar,
+    NoiseVar,
+    Prediction,
+    State,
+    StateMean,
+    StateVar,
+)
+from models.svgp import SVGP
+from tensordict import TensorDict
+from tensordict.nn import TensorDictModule
+from torch.utils.data import DataLoader, TensorDataset
+from torchrl.data import CompositeSpec, ReplayBuffer, UnboundedContinuousTensorSpec
+from torchrl.envs import ModelBasedEnvBase
+from torchrl.modules import SafeModule, WorldModelWrapper
+from torchtyping import TensorType
+
+
+class TransitionModel(NamedTuple):
+    # [InputData, Optional[Data]], Tuple[DeltaStateMean, DeltaStateVar, NoiseVar]
+    predict: Callable[[TensorDict], TensorDict]
+    train: Callable[[ReplayBuffer], TensorType[float, ""]]
+
+
+def build_SVGPTransitionModel(
+    svgp: SVGP,
+    likelihood: gpytorch.likelihoods.Likelihood,
+    learning_rate: float = 1e-2,
+    batch_size: int = 64,
+    num_epochs: int = 1000,
+    num_workers: int = 1,
+    wandb_loss_name: str = "Transition model loss",
+    num_samples: int = 10,
+    early_stopper: EarlyStopper = None,
+):
+    from models.svgp import predict, train
+
+    # output_dim = 5
+    # num_inducing = 500
+    # Z = torch.rand(output_dim, num_inducing, 6)
+    # svgp = SVGP(
+    #     inducing_points=Z,
+    #     mean_module=deepcopy(mean_module),
+    #     covar_module=deepcopy(covar_module),
+    #     learn_inducing_locations=learn_inducing_locations,
+    # )
+
+    assert (
+        len(svgp.variational_strategy.base_variational_strategy.inducing_points.shape)
+        == 3
+    )
+    (
+        output_dim,
+        num_inducing,
+        input_dim,
[…]

### 2023-04-06 src/models/transition/base.py

@@ -1,54 +1,0 @@
-#!/usr/bin/env python3
-import logging
-from typing import Any, Callable, NamedTuple, Optional, Tuple
-
-
-logging.basicConfig(level=logging.INFO)
-logger = logging.getLogger(__name__)
-
-# import pytorch_lightning as pl
-import torch
-import torch.distributions as td
-import torch.nn as nn
-import torch.optim as optim
-from custom_types import (
-    Action,
-    DeltaStateMean,
-    DeltaStateVar,
-    NoiseVar,
-    Prediction,
-    State,
-    StateMean,
-    StateVar,
-)
-from tensordict import TensorDict
-from tensordict.nn import TensorDictModule
-from torchrl.data import CompositeSpec, ReplayBuffer, UnboundedContinuousTensorSpec
-from torchrl.envs import ModelBasedEnvBase
-from torchrl.modules import SafeModule, WorldModelWrapper
-from torchtyping import TensorType
-
-
-class TransitionModel(nn.Module):
-    predict: Callable[
-        [InputData, Optional[Data]], Tuple[DeltaStateMean, DeltaStateVar, NoiseVar]
-    ]
-    train: Callable[[DataLoader], TensorType[float, ""]]
-
-    def __call__(
-        self,
-        state_mean: StateMean,
-        state_var: StateVar,
-        noise_var: NoiseVar,
-        action: Action,
-    ) -> Tuple[StateMean, StateVar, NoiseVar]:
-        """Returns next state mean/var and noise var"""
-
-    def forward(
-        self, x, data_new: Optional = None
-    ) -> Tuple[DeltaStateMean, DeltaStateVar, NoiseVar]:
-        """Returns change in state"""
-        raise NotImplementedError
-
-    def train(self, replay_buffer: ReplayBuffer):
-        raise NotImplementedError

### 2023-04-06 src/models/world_model.py

@@ -12,6 +12,18 @@ from torchrl.modules import (
     WorldModelWrapper,
 )
 from torchrl.objectives.value import TDLambdaEstimate
+from models import TransitionModel, RewardModel
+
+
+# def cartpole_pets(state, state_var, noise_var, action) -> TensorDict:
+#     assert len(next_obs.shape) == len(act.shape) == 2
+#     goal_pos = torch.tensor([0.0, 0.6]).to(next_obs.device)
+#     x0 = next_obs[:, :1]
+#     theta = next_obs[:, 1:2]
+#     ee_pos = torch.cat([x0 - 0.6 * theta.sin(), -0.6 * theta.cos()], dim=1)
+#     obs_cost = torch.exp(-torch.sum((ee_pos - goal_pos) ** 2, dim=1) / (0.6**2))
+#     act_cost = -0.01 * torch.sum(act**2, dim=1)
+#     return (obs_cost + act_cost).view(-1, 1)
 
 
 class GaussianModelBaseEnv(ModelBasedEnvBase):
@@ -21,25 +33,20 @@ class GaussianModelBaseEnv(ModelBasedEnvBase):
         reward_model: RewardModel,
         state_size: int,
         action_size: int,
-        learning_rate: float = 0.01,
-        num_iterations: int = 5000,
         device: str = "cpu",
         dtype=None,
         batch_size: int = None,
     ):
         world_model = WorldModelWrapper(
             transition_model=TensorDictModule(
-                transition_model,
+                transition_model.predict,
                 in_keys=["state_vector", "state_vector_var", "noise_var", "action"],
                 out_keys=["state_vector", "state_vector_var", "noise_var"],
             ),
             reward_model=TensorDictModule(
-                reward_model,
-                in_keys=["state_vector", "state_vector_var", "noise_var"],
-                # in_keys=["state_vector"],
-                # in_keys=["state_vector"],
+                reward_model.predict,
+                in_keys=["state_vector", "state_vector_var", "noise_var", "action"],
                 out_keys=["reward"],
-                # out_keys=["expected_reward"],
             ),
         )
         super(GaussianModelBaseEnv, self).__init__(
@@ -59,8 +66,6 @@ class GaussianModelBaseEnv(ModelBasedEnvBase):
             action=UnboundedContinuousTensorSpec((action_size)),
         )
         self.reward_spec = UnboundedContinuousTensorSpec((1,))
[…]

### 2023-04-06 src/train.py

@@ -1,647 +1,571 @@
 #!/usr/bin/env python3
+import logging
+import random
+from copy import deepcopy
+from functools import partial
+from pathlib import Path
+from typing import List, Optional
+
+
+logging.basicConfig(level=logging.INFO)
+logger = logging.getLogger(__name__)
+
+import gpytorch
 import hydra
+import imageio
+import models
+import numpy as np
+import omegaconf
+import torch
+import torch.nn as nn
+import torchrl
+import tqdm
+import wandb
+from dm_env import specs
+from models import GaussianModelBaseEnv
 from omegaconf import DictConfig, OmegaConf
+from pytorch_lightning import Trainer
+from pytorch_lightning.loggers import WandbLogger
+from setuptools.dist import Optional
+from tensordict.nn import TensorDictModule
+from tensordict.nn.distributions import NormalParamExtractor
+from torch import nn, optim
+from torchrl.collectors import MultiaSyncDataCollector, SyncDataCollector
+from torchrl.data import CompositeSpec, TensorDictReplayBuffer
+from torchrl.data.postprocs import MultiStep
+from torchrl.data.replay_buffers import ReplayBuffer
+from torchrl.data.replay_buffers.samplers import (
+    PrioritizedSampler,
+    RandomSampler,
+    SamplerWithoutReplacement,
+)
+from torchrl.data.replay_buffers.storages import LazyMemmapStorage, LazyTensorStorage
+from torchrl.envs import CatTensors, DoubleToFloat
+from torchrl.envs.libs.gym import GymEnv
+from torchrl.envs.transforms import ObservationNorm, RewardScaling, TransformedEnv
+from torchrl.envs.utils import step_mdp
+from torchrl.modules import (
+    Actor,
+    CEMPlanner,
+    ProbabilisticActor,
+    TanhNormal,
+    ValueOperator,
+)
+from torchrl.objectives.value import GAE
+from torchrl.record import VideoRecorder
+from torchrl.record.loggers.wandb import WandbLogger
+from torchrl.trainers import Recorder
+from utils import EarlyStopper, set_seed_everywhere
+
+
+def make_replay_buffer(
+    buffer_size: int,
+    device,
+    buffer_scratch_dir: str = "/tmp/",
+    batch_size: int = 64,
+    # prefetch: int = 3,
+):
+    sampler = RandomSampler()
+    replay_buffer = TensorDictReplayBuffer(
[…]

### 2023-04-06 src/utils.py

@@ -10,13 +10,35 @@ logging.basicConfig(level=logging.INFO)
 logger = logging.getLogger(__name__)
 
 import numpy as np
-import pytorch_lightning as pl
+
+# import pytorch_lightning as pl
 import torch
 import torch.nn as nn
 from dm_control import suite
 from setuptools.dist import Optional
 from torch.utils.data import DataLoader, TensorDataset
 from torchrl.data import ReplayBuffer
+
+
+class EarlyStopper:
+    def __init__(self, patience: int = 1, min_delta: float = 0.0):
+        self.patience = patience
+        self.min_delta = min_delta
+        self.reset()
+
+    def __call__(self, validation_loss):
+        if validation_loss < self.min_validation_loss:
+            self.min_validation_loss = validation_loss
+            self.counter = 0
+        elif validation_loss > (self.min_validation_loss + self.min_delta):
+            self.counter += 1
+            if self.counter >= self.patience:
+                return True
+        return False
+
+    def reset(self):
+        self.counter = 0
+        self.min_validation_loss = np.inf
 
 
 def set_seed_everywhere(random_seed):
@@ -30,7 +52,7 @@ def set_seed_everywhere(random_seed):
     # torch.backends.cudnn.benchmark = False
     np.random.seed(random_seed)
     random.seed(random_seed)
-    pl.seed_everything(random_seed)
+    # pl.seed_everything(random_seed)
 
 
 def make_data_loader(

### 2023-04-06 paper/main.tex

@@
 $\mathbf{r}(\mathbf{y}; \mathbf{f}) = \nabla_{\mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$ can be interpreted as a residual and
-$\bm\Lambda(\mathbf{y} ; \mathbf{f}) &= \nabla^{2}_{\mathbf{f} \mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$
+$\bm\Lambda(\mathbf{y} ; \mathbf{f}) = \nabla^{2}_{\mathbf{f} \mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$
 as per-input noise.

### 2023-04-13 paper/main.tex
commit for pual

@@
 % Parameters
-\newcommand{\transitionParams}{\ensuremath{\bm\phi}}
+% \newcommand{\transitionParams}{\ensuremath{\bm\phi}}
+\newcommand{\transitionParams}{\ensuremath{\mathbf{w}}}
 \newcommand{\valueFnParams}{\ensuremath{\psi}}
@@
 
+% \section{Background} \label{sec:background}
+% In this section, we recap how to fit a GP posterior to a trained deep neural network (DNN).
+% We start by obtaining a posterior over the weights of a trained neural network via the Laplace approximation.
+% We then show how we can obtain a function-space posterior, (i.e. a GP posterior)
+% by linearising the neural network around the weights Maximum a Posteriori (MAP) estimate.
+% % We then show that by linearising the neural network we can obtain a function-space posterior, i.e. a GP posterior.
+
 \section{Background} \label{sec:background}
@@
 
-In this section, we recap how to fit a GP posterior to a trained deep neural network (DNN).
-We start by obtaining a posterior over the weights of a trained neural network via the Laplace approximation.
-We then show how we can obtain a function-space posterior, (i.e. a GP posterior)
-by linearising the neural network around the weights Maximum a Posteriori (MAP) estimate.
+In this section, we recap how can obtain a GP posterior from a trained deep neural network (DNN).
+% We start by obtaining a posterior over the weights of a trained neural network via the Laplace approximation.
+% We then show how we can obtain a function-space posterior, (i.e. a GP posterior)
+% by linearising the neural network around the weights Maximum a Posteriori (MAP) estimate.
 % We then show that by linearising the neural network we can obtain a function-space posterior, i.e. a GP posterior.
-
 % We paraterise our single-step dynamic model $\transitionFnWithParams : \inputDomain \rightarrow \outputDomain$
 % as an $L\text{-layer}$ NN with weights $\transitionParams$.
+\textbf{Gaussian processes}
+A Gaussian process (GP) is a distribution over real-valued functions $f(\cdot): \mathcal{X} \rightarrow \R$ defined over $\mathcal{X}$.
+Formally, a GP is defined as,
+\begin{align}
+\label{eq-gp-prior}
+  f(\cdot) \sim \mathcal{N}\left( \mu(\cdot), k(\cdot,\cdot') \right) \quad
+  \mu(\cdot): \mathcal{X} \rightarrow \R \quad
+  k(\cdot,\cdot'): \mathcal{X} \times \mathcal{X} \rightarrow \R
+\end{align}
+where $\mu(\cdot)$ denotes a mean function and $k(\cdot,\cdot')$ a positive definite covariance function, also known as a kernel.
 Given a data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
+we can obtain the GP posterior via multivariate normal conditioning,
+\begin{align}
+\label{eq-gp-predictive-posterior}
+  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
+  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
+  \left( f(\mathbf{x}_{*}) \mid \mu(\mathbf{x}_{*}) + \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} (\mathbf{y} - \bm\mu_{\mathbf{X}})),
+  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
+\end{align}
+% Our GP posterior is then given by,
+\todo{add mean func to GP posterior if we're using one}
+\begin{align}
+\label{eq-gp-predictive-posterior}
+  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
+  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
+  \left( f(\mathbf{x}_{*}) \mid \mu(\mathbf{x}_{*}) + \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} \mu_{\mathbf{x}},
+  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} + \bm\Lambda(\mathbf{y} ; \mathbf{f})^{-1} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
+\end{align}
+where $\bm\Lambda(\mathbf{y} ; \mathbf{f}) = \nabla^{2}_{\mathbf{f} \mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$ can be viewed as per-input noise.
+\todo{I'm unsure about this per input noise bit.
+Check with paul.}
+\todo{what about regression/classification likelhoods}
+This GP predictive posterior is computationally expensive as it requires inverting an $N\times N$ matrix.
+
+\textbf{Sparse Gaussian processes}
+% The GP predictive posterior in \cref{eq-gp-predictive-posterior} is computationally expensive as it requires inverting an $N\times N$ matrix.
+A practical and computationally appealing alternative is to augment the joint probability space with pseudo inputs $\mathbf{Z} \in \R^{M \times D}$
+and corresponding outputs
+$\mathbf{u} = f(\mathbf{Z}; \transitionParams) \in \R^{M \times C}$, known as inducing variables, where $M \ll N$.
+\todo{cite sparse gp papers}
+Instead of collapsing the inducing variables like \cite{titsiasVariational2009}, they can be treated variationally
+$p(\mathbf{u} \mid \mathbf{y}) \approx q(\mathbf{u}) = \mathcal{N}\left( \mathbf{u} \mid \mathbf{m}, \mathbf{V} \right)$, where $\mathbf{m}$ and $\mathbf{V}$ are variational parameters
+which need to be optimised \parencite{hensmanGaussian2013}.
+The sparse variational GP (SVGP) predictive posterior is then given by,
+\begin{align}
+\label{eq-dual-svgp-predictive-posterior}
+  p(f(\mathbf{x}_{*}) \mid \mathbf{y})
+&\approx \mathcal{N} \left( f(\mathbf{x}_{*}) \mid \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{m}^{*},
+  k_{**} - \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
+  % \mathbf{k}_{*\inducingInput} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\inducingInput}^{T}
+  + \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}}  \mathbf{V}^{*}  \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
+  \right)
+\coloneqq q_{\inducingVariable}(f(\mathbf{x}_{*}))
+\end{align}
+
+\textbf{Deep learning}
+Given the data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
 the goal of (supervised) deep learning, is to train the weights $\transitionParams \in \R^{P}$ of an $L\text{-layer}$ NN
 $f : \inputDomain \rightarrow \outputDomain$ to minimize the (regularized) empirical risk,
-\begin{align}
+\begin{align} \label{eq-empirical-risk}
   \transitionParams^{*} = \arg \min_{\transitionParams \in \R^{D}} \mathcal{L}(\dataset;\transitionParams) = \arg \min_{\transitionParams \in \R^{D}} \left(
@@
 However, the practioner is free to choose any loss and regularizer. \todo{I think?}
+% \textbf{Bayesian neural networks}
+% \textbf{Weight space to function space}
+From a Bayesian perspective, we can interpret the terms in \cref{eq-empirical-risk} as the log-prior and the i.i.d. log likelihood, i.e.,
+\begin{align} \label{eq-log-prior}
+  R(\transitionParams) &= \underbrace{\log p(\transitionParams)}_{\text{log prior}} = \log \mathcal{N}(\transitionParams \mid 0, \gamma^{2} \mathbf{I}) \\
+  l(f(\mathbf{x}_{n} ; \transitionParams), \mathbf{y}_{n}) &= \underbrace{\log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \transitionParams))}_{\text{log likelihood}}
+  = \log \mathcal{N} \left( \mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \transitionParams), \mathbf{I} \right) \label{eq-log-likelihood}
+\end{align}
 
-\textbf{Laplace approximation}
-The Laplace approximation \todo{add citation of original paper} constructs a Gaussian approximation of the weight-space posterior $p(\transitionParams \mid \dataset)$
-by using a second-order Taylor expansion of $\mathcal{L}$ around $\transitionParams^{*}$.
-The posterior approximation is given by,
-\begin{align} \label{eq-laplace-approx-weight-space}
-  p(\transitionParams \mid \dataset) \approx \mathcal{N} \left( \transitionParams \mid \transitionParams^{*} , \bm\Sigma_{\transitionParams^{*}} \right)
-  \quad \text{with} \quad \bm\Sigma_{\transitionParams} =
- - \nabla_{\transitionParams \transitionParams}^{2} \mathcal{L} ( \dataset ; \transitionParams)|_{\transitionParams=\transitionParams^{*}}
-\end{align}
-That is, it sets the posterior precision to the Hessian of the loss at the optimal parameters $\transitionParams^{*}$.
-It is worth noting that computing the Hessian of the loss can be computationally intractable for large networks.
-The prior terms are usually trivial, so we will focus on the likelihood here.
-The Jacobian and Hessian of the log likelihood can be expressed per data point,
-\begin{align} \label{eq-jac}
-  \nabla_{\transitionParams} \log p(\mathbf{y} \mid \mathbf{f}(\mathbf{x}; \transitionParams)) &= \mathbf{J}(\mathbf{x})^{T} \mathbf{r}(\mathbf{y} ; \mathbf{f}) \\
-  \nabla^{2}_{\transitionParams\transitionParams} \log p(\mathbf{y} \mid \mathbf{f}(\mathbf{x}; \transitionParams)) &= \mathbf{H}(\mathbf{x})^{T}
-  \mathbf{r}(\mathbf{y};\mathbf{f}) - \mathbf{J}(\mathbf{x})^{T} \bm\Lambda(\mathbf{y};\mathbf{f}) \mathbf{J}(\mathbf{x}),
-\label{eq-hess}
-\end{align}
-through the Jacobian $\mathbf{J} \in \R^{C \times P}$ and Hessian $\mathbf{H} \in \R^{C \times P \times P}$ of the feature extractor $\mathbf{f}(\mathbf{x}; \bm\transitionParams)$,
-\begin{align} \label{eq-jac}
-[\mathbf{J}(\cdot)]_{ci} = \odv{f_{c}(\cdot ; \transitionParams)}{\transitionParams_{i}}_{\transitionParams=\transitionParams^{*}} \qquad
-[\mathbf{H}(\cdot)]_{cij} = \odv{f_{c}(\cdot ; \transitionParams)}{\transitionParams_{i}\transitionParams_{j}}_{\transitionParams=\transitionParams^{*}}
-\end{align}
-where
-$\mathbf{r}(\mathbf{y}; \mathbf{f}) = \nabla_{\mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$ can be interpreted as a residual and
-$\bm\Lambda(\mathbf{y} ; \mathbf{f}) = \nabla^{2}_{\mathbf{f} \mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$
-as per-input noise.
-Many approximations exist and can be used alongsied our method.
-We refer the reader to \cite{daxbergerLaplace2021} for more details.
-See \cref{sec-laplace-approximation} for further details on the Laplace approximation.
-
-% \begin{align}
-% \Sigma_{\transitionParams_{i}}^{-1} = - \nabla_{\transitionParams \transitionParams}^{2} \log p(\transitionParams \mid \dataset_{0:i})|_{\transitionParams=\transitionParams^{*}_{i}}
-%   + \frac{1}{\sigma^{2}_{0}} \mathbf{I}
-% \end{align}
-
-\textbf{Weight space to function space}
-% We can represent the log joint density in the function space,
-% \begin{align} \label{eq-laplace-approx-function-space}
-%   \sum_{n=1}^{N} \log p \left(y_{n} \mid f(\mathbf{x}_{n} ; \transitionParams_{0:i}) \right) + \log p(f(\mathbf{X}; \transitionParams_{0:i}))
-% \end{align}
-We can represent the weight space posterior from \cref{eq-laplace-approx-weight-space}, in
-function space, by linearising the BNN and interpretting it as a GP.
+\textbf{NN to GP}
+Given this interpretation, we can represent the weight space prior from \cref{eq-log-prior}, in
+function space, by linearising the BNN around $\transitionParams^{*}$ and interpretting it as a GP.
 The GP prior is then given by,
@@
   % \transitionFn_{\transitionParams_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \qquad
-  f(\cdot ;\transitionParams) \sim \mathcal{N} \left( \mu(\cdot), k(\cdot, \cdot') \right) \qquad
+  f(\cdot ;\transitionParams) \sim \mathcal{N} \left( \mu(\cdot), k(\cdot, \cdot') \right) \quad
   % \mu_{\transitionParams_{i}^{*}}(\cdot)
   \mu(\cdot)
-  = f(\cdot ;\transitionParams^{*}) \qquad
+  = 0 \quad
+  % = f(\cdot ;\transitionParams^{*}) \quad
   % K_{\transitionParams_{i}^{*}}(\cdot, \cdot')
   k(\cdot, \cdot')
-  = \gamma^{2} \mathbf{J}(\cdot) \mathbf{J}(\cdot')^{T},
+  = \frac{1}{\gamma^{2}} \mathbf{J}(\cdot) \mathbf{J}(\cdot')^{T},
 \end{align}
-where the kernel is the neural tangent kernel (NTK) \parencite{immerImprovingPredictionsBayesian2021}.
+where the kernel is the neural tangent kernel (NTK) \parencite{immerImprovingPredictionsBayesian2021},
 \todo{what mean function shoudl this use???}
 \todo{NTK times some factor??}
-% with Jacobian given by $\mathbf{J}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}$.
+with Jacobian given by $\mathbf{J}(\cdot) = \odv{\transitionFn(\cdot; \transitionParams)}{\transitionParams}_{\transitionParams=\transitionParams^{*}}$.
 % The kernel in \cref{eq-laplace-approx-function-space} is the neural tangent kernel (NTK)
@@
 % to formulate the GP posterior $p(f(\mathbf{X} ;\transitionParams_{0:i}) \mid \dataset_{0:i})$.
-It is worth noting that the NTK linearises the network around the optimised parameters $\transitionParams_{i}^{*}$,
+Given this GP prior, we can use \cref{eq-gp-predictive-posterior} to obtain our GP posterior by conditioning on the data.
+% Given our GP prior, we can use the properties of multivariate normals to obtain our GP posterior by conditioning on the data.
+% where $\mathbf{A} = \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}}$
+In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
+Intuitively, we can view the optimisation in \cref{eq-empirical-risk} as learning our kernel.
+As a result, our NTK may be highly non stationary as it is dependent on the NN architecture, for example, the activation functions.
+It is worth noting that the NTK linearises the network around the optimised parameters $\transitionParams^{*}$,
 so the function space prior (and thus posterior) is only a locally linear approximation.
-In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
-It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.
-Given our GP prior, we can use the properties of multivariate normals to obtain our GP posterior by conditioning on the data.
-Our GP posterior is given by,
-\todo{add mean func to GP posterior if we're using one}
-\begin{align} \label{eq-gp-predictive-posterior}
-  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
-  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
-  \left( f(\mathbf{x}_{*}) \mid \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} \mathbf{m}^{*},
-  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} + \bm\Lambda(\mathbf{y} ; \mathbf{f})^{-1} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
-\end{align}
 
-\section{Dual SVGP} \label{sec:method}
-The GP predictive posterior in \cref{eq-gp-predictive-posterior} is computationally expensive
-as it requires inverting $N\times N$ matrix.
-Sparse approximations using pseudo points ...
-\begin{align} \label{eq-svgp-predictive-posterior}
-  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
-  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
-  \left( f(\mathbf{x}_{*}) \mid \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} \mathbf{m}^{*},
-  k_{**} - \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} \mathbf{k}_{*\mathbf{x}}^{T} \right) \\
-  % &\approx \mathcal{N}
-  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} \mathbf{A}^{T} + \mathbf{A} \mathbf{V}^{*} \mathbf{A}^{T} \right) \\
-&\approx \mathcal{N} \left( f(\mathbf{x}_{*}) \mid \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{m}^{*},
-  k_{**} - \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
-  % \mathbf{k}_{*\inducingInput} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\inducingInput}^{T}
-  + \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}}  \mathbf{V}^{*}  \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
-  \right)
-\coloneqq q_{\inducingVariable}(f(\mathbf{x}_{*}))
-\end{align}
-% where $\mathbf{A} = \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}}$
+We now have a method to obtain a GP posterior from a trained DNN.
+% In contrast to other approaches, our formulation has not restricted us to using a weight-space posterior obtained from the Laplace approximation.
+In contrast to other approaches, our formulation has not restricted us to using a weight-space posterior from a BNN.
+However, in practice, the GP posterior is not very useful as it requires inverting an $N\times N$ matrix which has complexity $\mathcal{O}(N^{3})$.
+The SVGP in \cref{eq-dual-svgp-predictive-posterior} offers a solution to this problem but it is not immediately clear how to set $\mathbf{m}$ and $\mathbf{V}$.
+In the next section, we show how we can directly obtain an SVGP posterior (i.e. set $\mathbf{m}$ and $\mathbf{V}$) directly from both
+1) a trained NN and 2) a BNN weight-space posterior.
+% $\mathbf{m}$ and $\mathbf{V}$
+% However, it is not obvious how we can use a SVGP to set $\mathbf{m}$ and $\mathbf{V}$
+
+% In contrast, to previous work, this approach did not require us Laplace approximation. we will not restrict our
+% It is worth noting that the NTK linearises the network around the optimised parameters $\transitionParams^{*}$,
+% so the function space prior (and thus posterior) is only a locally linear approximation.
+% In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
+% It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.
+
+\section{Method}
+In the next section we show how we can obtain a SVGP directly from 1) a trained NN and 2) a BNN posterior.
 
@@
 \section{Experiments}
+
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=0.5\textwidth, angle=270]{figs/weight-space-to-functio-space.pdf}
+%   \caption{}
+% \end{figure}
+
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=0.5\textwidth, trim=0 100 0 10]{figs/cartpole-training-curves.pdf}
+%   \caption{}
+% \end{figure}
+
+% \begin{table}
+%   \caption{Negative test log likelihood (lower is better) on UCI classification tasks (2 hidden layers, 50 tanh). Our SVGP predictive outperforms the GLM predictive. }
+% \end{table}
+
+\begin{itemize}
+  \item Show prediction performance in classification: UCI classification results, compare to BNN predictive paper
+  \item Fast adapatation in model-based RL: results for cartpole
+  \item Is linearising NN mean and using fast updates during episode better than keeping non-linearised mean and not updating?
+  \item Possible ablations
+  \begin{itemize}
+    \item How does number of inducing points affect performance?
+  \end{itemize}
+  \item How good is the assumption that we can linearise BNN to get NTK?
+\end{itemize}
+
 Environments
@@
 
+\textbf{Laplace approximation}
+The Laplace approximation \todo{add citation of original paper} constructs a Gaussian approximation of the weight-space posterior $p(\transitionParams \mid \dataset)$
+by using a second-order Taylor expansion of $\mathcal{L}$ around $\transitionParams^{*}$.
+The posterior approximation is given by,
+\begin{align} \label{eq-laplace-approx-weight-space}
+  p(\transitionParams \mid \dataset) \approx \mathcal{N} \left( \transitionParams \mid \transitionParams^{*} , \bm\Sigma_{\transitionParams^{*}} \right)
+  \quad \text{with} \quad \bm\Sigma_{\transitionParams} =
+ - \nabla_{\transitionParams \transitionParams}^{2} \mathcal{L} ( \dataset ; \transitionParams)|_{\transitionParams=\transitionParams^{*}}
+\end{align}
+That is, it sets the posterior precision to the Hessian of the loss at the optimal parameters $\transitionParams^{*}$.
+It is worth noting that computing the Hessian of the loss can be computationally intractable for large networks.
+The prior terms are usually trivial, so we focus on the likelihood here.
+The Jacobian and Hessian of the log likelihood can be expressed per data point,
+\begin{align} \label{eq-jac}
+  \nabla_{\transitionParams} \log p(\mathbf{y} \mid \mathbf{f}(\mathbf{x}; \transitionParams)) &= \mathbf{J}(\mathbf{x})^{T} \mathbf{r}(\mathbf{y} ; \mathbf{f}) \\
+  \nabla^{2}_{\transitionParams\transitionParams} \log p(\mathbf{y} \mid \mathbf{f}(\mathbf{x}; \transitionParams)) &= \mathbf{H}(\mathbf{x})^{T}
+  \mathbf{r}(\mathbf{y};\mathbf{f}) - \mathbf{J}(\mathbf{x})^{T} \bm\Lambda(\mathbf{y};\mathbf{f}) \mathbf{J}(\mathbf{x}),
+\label{eq-hess}
+\end{align}
+through the Jacobian $\mathbf{J} \in \R^{C \times P}$ and Hessian $\mathbf{H} \in \R^{C \times P \times P}$ of the feature extractor $\mathbf{f}(\mathbf{x}; \bm\transitionParams)$,
+\begin{align} \label{eq-jac}
+[\mathbf{J}(\cdot)]_{ci} = \odv{f_{c}(\cdot ; \transitionParams)}{\transitionParams_{i}}_{\transitionParams=\transitionParams^{*}} \qquad
+[\mathbf{H}(\cdot)]_{cij} = \odv{f_{c}(\cdot ; \transitionParams)}{\transitionParams_{i}\transitionParams_{j}}_{\transitionParams=\transitionParams^{*}}
+\end{align}
+where
+$\mathbf{r}(\mathbf{y}; \mathbf{f}) = \nabla_{\mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$ can be interpreted as a residual and
+$\bm\Lambda(\mathbf{y} ; \mathbf{f}) = \nabla^{2}_{\mathbf{f} \mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$
+as per-input noise.
+Many approximations exist and can be used alongsied our method.
+We refer the reader to \cite{daxbergerLaplace2021} for more details.
+See \cref{sec-laplace-approximation} for further details on the Laplace approximation.
+
 \section{Template stuff}

### 2023-04-14 paper/main.tex
added pausl titles
added few changes data
added abstract

@@
 % \title{Model-based Reinforcement Learning with Fast Posterior Updates}
-\title{Sequential Decision-Making under Uncertainty with Big Data}
+\title{Neural Sparse Gaussian Process: For Updated Exploration}
 \author{%
@@
   %
-  Deep neural networks
+  %Models that can process new information quickly
 
-  Obtain SVGP posterior on trained deep neural network (NN) without optimising any variational parameters.
+ % Fast adaptation of 
+ Building systems that adapt to new information is essential to deploy methods in real-world applications.
+While gradient-based training is symbiotic to modern deep learning, it is rigid regarding adding further information, usually involving retraining from scratch.
+In a functional view, we can view data as the parameters of our model instead of the weights, which we call the dual parameterization of a model.
+Using the formulation we can assimilate data without gradient-based retraining in dual parameterization.
+Our proposed method allows for deployment in any sequential decision-making process.
+We show its effectiveness in model-based reinforcement learning using updated information for more efficient exploration.
 
-  Dual formulation enables fast updates for 1) model-based RL 2) pathwise, function-space conditioning.
+  %Deep neural networks
+
+%  Obtain SVGP posterior on trained deep neural network (NN) without optimising any variational parameters.
+
+  %Dual formulation enables fast updates for 1) model-based RL 2) pathwise, function-space conditioning.
   % Reinforcement learning (RL) agents typically perform learning offline and do not utilise the information gained during an episode.
@@
   \transitionParams^{*} = \arg \min_{\transitionParams \in \R^{D}} \mathcal{L}(\dataset;\transitionParams) = \arg \min_{\transitionParams \in \R^{D}} \left(
-  R(\transitionParams) + \sum_{n=0}^{N-1} l(f(\mathbf{x}_{n} ; \transitionParams), \mathbf{y}_{n}) \right).
+  \sum_{n=0}^{N-1} l(f(\mathbf{x}_{n} ; \transitionParams), \mathbf{y}_{n}) + R(\transitionParams)  \right).
 \end{align}
@@
 
+%\bibliography{biblio.bib}
 \end{document}

### 2023-04-14 paper/main.tex
added abstract
Minor

@@
 % \title{Model-based Reinforcement Learning with Fast Posterior Updates}
+%\title{Sequential Decision-Making under Uncertainty with Big Data}
 \title{Neural Sparse Gaussian Process: For Updated Exploration}
+
 \author{%
@@
 % Bibliography
-\usepackage[maxcitenames=1, maxbibnames=4, doi=false, isbn=false, eprint=true, backend=bibtex, hyperref=true, url=false, style=authoryear-comp]{biblatex}
-\addbibresource{zotero-library.bib}
+%\usepackage[maxcitenames=1, maxbibnames=4, doi=false, isbn=false, eprint=true, backend=bibtex, hyperref=true, url=false, style=authoryear-comp]{biblatex}
+%\addbibresource{zotero-library.bib}
 % \addbibresource{paper/zotero-library.bib}
@@
 \section{Background} \label{sec:background}
+
+\cite{hernandez2016scalable}
 % \section{dual SVGP}
@@
 
-\section*{Acknowledgements}
+\begin{ack}
+ASK A ABOUT THIS SECTION:
 Aidan Scannell is funded by the Finnish Center for Artificial Intelligence.
+\end{ack}
 
 % \section*{References}
-\small
-\printbibliography
-\normalsize
+%\small
+%\printbibliography
+%\normalsize
 % TODO make bibliography small a better way
 
-References follow the acknowledgments. Use unnumbered first-level heading for
-the references. Any choice of citation style is acceptable as long as you are
-consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
-when listing the references.
-Note that the Reference section does not count towards the page limit.
-\medskip
+%References follow the acknowledgments. Use unnumbered first-level heading for
+%the references. Any choice of citation style is acceptable as long as you are
+%consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
+%when listing the references.
+%Note that the Reference section does not count towards the page limit.
+%\medskip
+
+\phantomsection%
+\addcontentsline{toc}{section}{References}
+\begingroup
+\small
+\bibliographystyle{abbrvnat}
+\bibliography{main-blx,zotero-library,bibliography}
+\endgroup
+
+\clearpage
 

### 2023-04-14 paper/main.tex
Switch to use bibtex and update Makefile

@@
 
+% Pass options to natbib
+\PassOptionsToPackage{numbers, compress}{natbib}
+
 % NeurIPS packages
-\usepackage[preprint,nonatbib]{neurips_2022}
+\usepackage[preprint]{neurips_2022}
 \usepackage[utf8]{inputenc} % allow utf-8 input
@@
 % \addbibresource{paper/zotero-library.bib}
+
+% Let's use good old bibtex instead
 
@@
 % Our method uses a BNN dynamic model and draws on the connection between BNNs and GPs
-% \parencite{khanApproximate2019} to formulate a function space SVGP posterior,
+% \citep{khanApproximate2019} to formulate a function space SVGP posterior,
 % where we can apply the fast updates from \cref{eq-dual-update-svgp}.
@@
 $p(\mathbf{u} \mid \mathbf{y}) \approx q(\mathbf{u}) = \mathcal{N}\left( \mathbf{u} \mid \mathbf{m}, \mathbf{V} \right)$, where $\mathbf{m}$ and $\mathbf{V}$ are variational parameters
-which need to be optimised \parencite{hensmanGaussian2013}.
+which need to be optimised \citep{hensmanGaussian2013}.
 The sparse variational GP (SVGP) predictive posterior is then given by,
@@
 \end{align}
-where the kernel is the neural tangent kernel (NTK) \parencite{immerImprovingPredictionsBayesian2021},
+where the kernel is the neural tangent kernel (NTK) \citep{immerImprovingPredictionsBayesian2021},
 \todo{what mean function shoudl this use???}
@@
 % $k(\mathbf{x}, \mathbf{x}') = \sigma_{0}^{2} J_{\transitionParams^{*}}(\mathbf{x}) J_{\transitionParams^{*}}(\mathbf{x}')^{T}$
-% \parencite{immerImprovingPredictionsBayesian2021}
+% \citep{immerImprovingPredictionsBayesian2021}
 % to formulate the GP posterior $p(f(\mathbf{X} ;\transitionParams_{0:i}) \mid \dataset_{0:i})$.
@@
 \end{align}
-This simplifies SVGP inference \parencite{hensmanGaussian2013} as it no longer requires the variational parameters $(\mathbf{m}, \mathbf{V})$ to be optimised.
+This simplifies SVGP inference \citep{hensmanGaussian2013} as it no longer requires the variational parameters $(\mathbf{m}, \mathbf{V})$ to be optimised.
 
@@
 \textbf{Hallucinated upper confidence RL}
-A more theoretically grounded exploration strategy is UCRL \autocite{jakschNearoptimal2010}, which optimises joinly over
+A more theoretically grounded exploration strategy is UCRL \citep{jakschNearoptimal2010}, which optimises joinly over
 policies and models inside the set
@@
 Our method uses a BNN dynamic model and draws on the connection between BNNs and GPs
-\parencite{khanApproximate2019} to formulate a function space SVGP posterior,
+\citep{khanApproximate2019} to formulate a function space SVGP posterior,
 where we can apply the fast updates from \cref{eq-dual-update-svgp}.
@@
 \subsection{Biblatex}
-Rember when using biblatex to use 'parencite' for \parencite{kamtheDataEfficient2018} and when using natbib to use 'citep'.
+Rember when using biblatex to use 'parencite' for \citep{kamtheDataEfficient2018} and when using natbib to use 'citep'.
 

### 2023-04-14 paper/main.tex
Cleaning up
Change template to 2023

@@
 % NeurIPS packages
-\usepackage[preprint]{neurips_2022}
+\usepackage[]{neurips_2023}
 \usepackage[utf8]{inputenc} % allow utf-8 input
@@
 
-\section{Introduction} \label{sec:intro}
+\section{Introduction}
+\label{sec:intro}
+%
 
@@
 % % We then show that by linearising the neural network we can obtain a function-space posterior, i.e. a GP posterior.
+
+\begin{figure}[t!]
+  \setlength{\figurewidth}{.48\textwidth}
+  \setlength{\figureheight}{.5\figurewidth}
+  \begin{subfigure}{.48\textwidth}
+    \centering
+    \tikz\node[fill=black!10,minimum width=\figurewidth,minimum height=\figureheight,rounded corners=5pt]{};
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}{.48\textwidth}
+    \centering
+    \tikz\node[fill=black!10,minimum width=\figurewidth,minimum height=\figureheight,rounded corners=5pt]{};
+  \end{subfigure}
+  \caption{Teaser figure goes here.}
+  \label{fig:teaser}  
+\end{figure}
 
@@
 
-\section{Method}
+\section{Methods}
 In the next section we show how we can obtain a SVGP directly from 1) a trained NN and 2) a BNN posterior.
@@
 \bibliographystyle{abbrvnat}
-\bibliography{main-blx,zotero-library,bibliography}
+\bibliography{zotero-library,bibliography}
 \endgroup

### 2023-04-14 paper/main.tex
started intro

@@
 %\title{Sequential Decision-Making under Uncertainty with Big Data}
-\title{Neural Sparse Gaussian Process: For Updated Exploration}
+\title{Neural Sparse Gaussian Process: For Online Exploration}
 
@@
 \begin{abstract}
-  % Reinforcement learning (RL) agents typically do not utilise the information previously gained during an episode.
-  % as they perform learning offline, i.e. after an episode.
-  % Reinforcement learning (RL) agents typically perform learning after an episode, ignoring the potential information gain whilst collecting data.
-  % Reinforcement learning (RL) agents typically perform learning offline and do not utilise the information gained during an episode.
-  % We present a Bayesian model-based RL algorithm which incorporates this information by updating a dynamic model's posterior during an episode.
-  % Our method leverages the fast posterior updates available in the dual parameterisation of sparse variational Gaussian processes.
-  % Importantly, our algorithm scales to 1) environment's with high dimensional state-spaces as it is built upon the connection between Bayesian neural networks (BNNs) and
-  % Gaussian processes (GPs) and 2) long episodes, as the complexity of our updates is independent of episode length.
-  % We demonstrate that our fast posterior updates improve sample efficiency in environments with action penalties, a notoriously difficult
-  % challenge for model-based RL algorithms.
-  %
-  % Reinforcement learning (RL) agents typically perform learning offline and do not utilise the information gained during an episode.
-  % We present a Bayesian model-based RL algorithm which incorporates this information by updating a dynamic model's posterior during an episode.
-  % Typically training a neural network dynamic model is not feasible and nonparameteric methods such as Gaussian processes scale poorly with data.
-  % Importantly, our algorithm scales to 1) environment's with high dimensional state-spaces, 2) large data sets and 3) long episodes,
-  % as the complexity of our updates is independent of episode length.
-  % We demonstrate that our fast posterior updates improve sample efficiency in environments with action penalties, a notoriously difficult
-  % challenge for model-based RL algorithms.
-  %
-  %Models that can process new information quickly
 
- % Fast adaptation of 
  Building systems that adapt to new information is essential to deploy methods in real-world applications.
@@
 
-  %Deep neural networks
-
-%  Obtain SVGP posterior on trained deep neural network (NN) without optimising any variational parameters.
-
-  %Dual formulation enables fast updates for 1) model-based RL 2) pathwise, function-space conditioning.
-  % Reinforcement learning (RL) agents typically perform learning offline and do not utilise the information gained during an episode.
-  % We present a Bayesian model-based RL algorithm which incorporates this information by updating a dynamic model's posterior during an episode.
-  % Typically training a neural network dynamic model is not feasible and nonparameteric methods such as Gaussian processes scale poorly with data.
-  % Importantly, our algorithm scales to 1) environment's with high dimensional state-spaces, 2) large data sets and 3) long episodes,
-  % as the complexity of our updates is independent of episode length.
-  % We demonstrate that our fast posterior updates improve sample efficiency in environments with action penalties, a notoriously difficult
-  % challenge for model-based RL algorithms.
 \end{abstract}
 
-\section{Introduction}
-\label{sec:intro}
-%
+\section{Introduction} \label{sec:intro}
+
+%Explain uncertainty in sequential decision making but need for neural networks.
+Sequential decision making requires uncertainty estimates for effective exploration.
+For this reason Gaussian processes (GPs) are a common surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and in model-based reinforcement learning \citep{deisenroth2011pilco}.
+Yet many problems lie in high dimensional input space for example images are where GPs lack the ability to learn representations.
+However, uncertainty is still essential to ensure effective exploration for sequential algorithms \todo{cite here}.
+Many approaches
+
+%Need for adaptive learning methods + failures with current methods
+
+%Dual formulation in GPs space solves this
+
+%Talk about planning and exploration in RL.
+
+%List the contributions.
 
@@
 
-% \section{Background} \label{sec:background}
-% In this section, we recap how to fit a GP posterior to a trained deep neural network (DNN).
-% We start by obtaining a posterior over the weights of a trained neural network via the Laplace approximation.
-% We then show how we can obtain a function-space posterior, (i.e. a GP posterior)
-% by linearising the neural network around the weights Maximum a Posteriori (MAP) estimate.
-% % We then show that by linearising the neural network we can obtain a function-space posterior, i.e. a GP posterior.
-
 \begin{figure}[t!]
@@
 \section{Background} \label{sec:background}
-
-\cite{hernandez2016scalable}
-% \section{dual SVGP}
-% In this section we extend these fast updates to environment's with high dimensional state spaces and large data sets.
-% % Our method draws on the connection between BNNs and GPs and formulates a function space SVGP posterior given
-% Our method uses a BNN dynamic model and draws on the connection between BNNs and GPs
-% \citep{khanApproximate2019} to formulate a function space SVGP posterior,
-% where we can apply the fast updates from \cref{eq-dual-update-svgp}.
-% At a high-level, we first use Laplace's approximation to obtain a weight space posterior for our BNN.
-% We then linearise our BNN around the optimal parameters and interpret it as a GP.
-% Finally, we formulate a lower rank approximation of this GP posterior (i.e. a SVGP posterior) using inducing variables.
-% % formulates a function space SVGP posterior by drawing on the connection between BNNs and GPs.
+Sequential decision making requires uncertainty estimates for effective exploration.
 

### 2023-04-16 paper/main.tex
added contributions

@@
 %\title{Sequential Decision-Making under Uncertainty with Big Data}
-\title{Neural Sparse Gaussian Process: For Online Exploration}
+\title{Neural Network to Sparse Gaussian Process: For Online Exploration}
 
@@
 
- Building systems that adapt to new information is essential to deploy methods in real-world applications.
+Building systems that adapt to new information and express uncertainty is essential to deploy methods in real-world applications e.g.
+healthcare, autonomous vehicles.
 While gradient-based training is symbiotic to modern deep learning, it is rigid regarding adding further information, usually involving retraining from scratch.
 In a functional view, we can view data as the parameters of our model instead of the weights, which we call the dual parameterization of a model.
-Using the formulation we can assimilate data without gradient-based retraining in dual parameterization.
+Using the formulation we can assimilate data without gradient-based retraining.
 Our proposed method allows for deployment in any sequential decision-making process.
@@
 %Explain uncertainty in sequential decision making but need for neural networks.
-Sequential decision making requires uncertainty estimates for effective exploration.
-For this reason Gaussian processes (GPs) are a common surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and in model-based reinforcement learning \citep{deisenroth2011pilco}.
-Yet many problems lie in high dimensional input space for example images are where GPs lack the ability to learn representations.
+Sequential decision-making requires uncertainty estimates for effective exploration \citep{srinivas2009gaussian}.
+For this reason, Gaussian processes (GPs) are a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and in model-based reinforcement learning \citep{deisenroth2011pilco}.
+Yet many problems lie in high dimensional input space; for example, images are where GPs cannot learn representations.
 However, uncertainty is still essential to ensure effective exploration for sequential algorithms \todo{cite here}.
-Many approaches
+Successful approaches have attempted to blend neural networks with uncertainty estimates around predictions, allowing for sophisticated exploration strategies.
+[ensembles of NN and citations]
+
+% Intoduce the laplace GNN
 
 %Need for adaptive learning methods + failures with current methods
+Whether using a Gaussian process or a neural network it is often the case that the surrogate model obtains new information which it wants to incorporate in to its
+
+%Need uncertainty and adaptive methods
 
@@
 %List the contributions.
-
+The contributions of the paper our is as follows:
 \begin{itemize}
-  \item DNNs scale to high-dimensional and large data sets but 1) no UQ and 2) cannot be updated quickly
-  \begin{itemize}
-    \item In many domains we want to make decisions under a learned model's uncertainty, e.g. in healthcare, robotics, autonomous vehicles. (safey, sample efficiency (cost/time))
-    \item In continual learning (e.g. online learning/RL) we need to update model quicker than retraining NN with SGD.
-    \item Poorly calibrated model uncertainty
-  \end{itemize}
-\end{itemize}
-
-\begin{itemize}
-  \item BNNs give UQ over high-dimensional parameter space,
-  \begin{itemize}
-    \item Exact inference intractable
-    \item Sampling in parameter space vs Sampling in function space
-  \end{itemize}
-\end{itemize}
-
-\begin{itemize}
-  \item BNN to dual SVGP
-  \begin{itemize}
-    \item Keep in spirit of Laplace approx and fit SVGP with no more optimisation
-    \item Now we can update posterior without retraining, which is fast (good for model-based RL and TS BO?)
-    \item Now we can sample in function space with pathwise conditioning (because we have SVGP).
-    \begin{itemize}
-      \item Our pathwise conditioning will be better as we can use dual update
-    \end{itemize}
-  \end{itemize}
+\item We show how to take a trained neural network and convert it to a dual sparse GP.
+We are able to do this without retraining the GP.
+Our sparse GP uses the variational formulation, and thus gives better uncertainty estimates than other no variational sparse approaches used previously.
+\item Our sparse GP now gives us a compact representation of our parameters in the function space.
+We can therefore take advantage of the dual parameters formulation for fast conditioning of new data in to our posterior.
+Crucially this allows for fast adaptation of models that our used in sequential decision making.
+We show how this is effective in the planning stage of model-based reinforcement exploration.
 \end{itemize}

### 2023-04-16 paper/main.tex
small fix

@@
 \item We show how to take a trained neural network and convert it to a dual sparse GP.
-We are able to do this without retraining the GP.
+We are able to do this without retraining a variational objective for the Sparse GP.
 Our sparse GP uses the variational formulation, and thus gives better uncertainty estimates than other no variational sparse approaches used previously.
-\item Our sparse GP now gives us a compact representation of our parameters in the function space.
-We can therefore take advantage of the dual parameters formulation for fast conditioning of new data in to our posterior.
+\item The sparse GP now gives us a compact representation of our parameters in the function space.
+We can therefore take advantage of the dual parameters formulation for fast conditioning of new data in to our posterior avoiding retraining of the neural network.
 Crucially this allows for fast adaptation of models that our used in sequential decision making.

### 2023-04-18 paper/main.tex
put in draft intro

@@
 %\title{Sequential Decision-Making under Uncertainty with Big Data}
-\title{Neural Network to Sparse Gaussian Process: For Online Exploration}
+\title{Neural Network to Vatiational Sparse Gaussian Process: For Adaptive Exploration}
 
@@
 \begin{abstract}
-
 Building systems that adapt to new information and express uncertainty is essential to deploy methods in real-world applications e.g.
@@
 While gradient-based training is symbiotic to modern deep learning, it is rigid regarding adding further information, usually involving retraining from scratch.
-In a functional view, we can view data as the parameters of our model instead of the weights, which we call the dual parameterization of a model.
-Using the formulation we can assimilate data without gradient-based retraining.
-Our proposed method allows for deployment in any sequential decision-making process.
+Converting a trained neural network to its dual parameterization we can view the parameters of the model as data dependent terms instead of the weights.
+Furthermore, we can then build a sparse model to form a variational dual sparse Gaussian process.
+The resultant sparse GP has two obvious advantages: scalable principled uncertainty estimation and the ability adapt to new data without gradient based retraining.
+Our proposed method can be deployed in any sequential decision-making process, where new information is received and retraining from scratch is not available.
 We show its effectiveness in model-based reinforcement learning using updated information for more efficient exploration.
-
 \end{abstract}
@@
 \section{Introduction} \label{sec:intro}
+%Why we need uncertainty and adaptiveness
+How to adapt to new information is a limitation of current machine learning models.
+The problem is specifically relevant when we combine a model with a decision-making process.
+In such a sequential setting, an agent typically makes decisions in an environment and obtains new information and would ideally incorporate the information into their parameters.
+Not only do we need models that adapt to new informatoion but all express uncertainty over the models predictions.
+The reason being twofold: in many applications, e.g.
+healthcare, autonomous driving is an essential requirement, and many advanced exploration techniques require uncertainty to determine where to query next.
 
-%Explain uncertainty in sequential decision making but need for neural networks.
-Sequential decision-making requires uncertainty estimates for effective exploration \citep{srinivas2009gaussian}.
-For this reason, Gaussian processes (GPs) are a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and in model-based reinforcement learning \citep{deisenroth2011pilco}.
+%Current state of affairs 
+GPs give principled uncertainty estimates and are a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} furthermore they have theoretical guarantees on regret bounds \citep{srinivas2009gaussian}.
 Yet many problems lie in high dimensional input space; for example, images are where GPs cannot learn representations.
-However, uncertainty is still essential to ensure effective exploration for sequential algorithms \todo{cite here}.
+In such scenarios such as in many reinforcement learning environments neural networks are used as the surrogate model.
+However, uncertainty is still essential to ensure effective exploration for sequential algorithms.
 Successful approaches have attempted to blend neural networks with uncertainty estimates around predictions, allowing for sophisticated exploration strategies.
-[ensembles of NN and citations]
+However, there has been limited use of hybrid models that possess the feature representation ability of neural networks but also attractive the properties of GPs, such a hybrid method we propose in this paper.
 
-% Intoduce the laplace GNN
+% Introduce the laplace GNN + shortcomings
+One common approach for uncertainty with neural networks is a Laplace GNN approximation \citep{daxbergerLaplace2021}.
+The idea is to essentially takes a trained neural network and linearises around the optimal weights.
+The resulting linear model can be used to obtain uncertainty estimates and sometimes improved predictions \citep{immerScalable2021}.
+Given the resultant model is now linear with respect to the weights its is also now possible to convert to a Gaussian process as shown in \citep{immerScalable2021, khan2019approximate}.
+Yet to obtain uncertainty estimates there is the usual computational scaling of the GP of $O(n^3)$, so cubic in the number of data points.
+Many approaches  apply crude approximations and yet still obtain good uncertainty estimates.
 
 %Need for adaptive learning methods + failures with current methods
-Whether using a Gaussian process or a neural network it is often the case that the surrogate model obtains new information which it wants to incorporate in to its
+In this paper we show that we can take any neural network and define the dual parameters of a Gaussian process \citep{csato2002sparse, adam2021dual, chang2020fast}.
+Crucially the resultant GP now has predictions in the same space as the space as the initial trained neural network, a property not of previous approaches.
+Given the dual parameter formulation we can then easily convert a full GP to a variational sparse version.
+Using the sparse GP we can then take advantage of the property of dual parameters that allows for fast conditioning recently shown in \citep{chang2022fantasizing}.
+Thus we are able to avoid retraining and condition new data in to our model.
+The resultant DNN2SGP method can be used in any sequential decision-making scenario where retraining is not available and we show its effectiveness in a planning stage of a model based reinforcement algorithim.
 
 %Need uncertainty and adaptive methods
-
 %Dual formulation in GPs space solves this
-
 %Talk about planning and exploration in RL.

### 2023-04-18 paper/main.tex
Aidan updated abstract

@@
 \begin{abstract}
-Building systems that adapt to new information and express uncertainty is essential to deploy methods in real-world applications e.g.
+% Building systems that adapt to new information and express uncertainty is essential to deploy methods in real-world applications e.g.
 healthcare, autonomous vehicles.
@@
 We show its effectiveness in model-based reinforcement learning using updated information for more efficient exploration.
+%
+  Building learning-based systems that can adapt to new data and express uncertainty is essential for their deployment in real-world applications, e.g.
+healthcare and robotics.
+However, modern deep learning cannot adapt to new data because it relies upon gradient-based optimisation, which requires retraining with the addition of new data.
+In contrast, nonparametric approaches -- such as Gaussian processes -- can adapt to new data without further training.
+However, they are limited to low-dimensional and small data sets.
+We present a method that enables any trained neural network (NN) to be converted to a sparse variational Gaussian process (SVGP).
+Importantly, our method 1) enables fast adaptation to new data, 2) provides well-calibrated uncertainty estimates, and 3) scales to high-dimensional and large data sets.
+Essentially, our method reaps the benefits of nonparametric models without their well-known issues.
+We demonstrate the effectiveness of our model's fast adaptation by showing that it can improve sample-efficiency in model-based reinforcement learning and we demonstrate our state-of-the-art NN uncertainty quantification with experiments using UCI data sets.
+
+  % Building learning-based systems that can adapt to new data and express uncertainty is essential for their deployment
+  % in real-world applications, e.g. healthcare and robotics.
+  % % The ability to adapt to new information and express uncertainty is essential for deploying learning-based systems in real-world applications, e.g. healthcare and robotics.
+  % However, modern deep learning cannot adapt to new data because it relies upon gradient-based optimisation,
+  % which requires retraining with the addition of new data.
+  % In contrast, nonparametric approaches -- such as Gaussian processes -- can adapt to new data without further training.
+  % % Although, traditional approaches are limited to low-dimensional and small data sets, recent advances have scaled
+  % % GPs to large data sets.
+  % However, they are limited to low-dimensional and small data sets.
+  % % We present a method that enables any trained neural network to adapt to new data without further gradient-based optimisation,
+  % % whilst providing scalable and principled uncertainty quantification.
+  % We present a method that enables any trained neural network (NN) to be converted to a sparse variational Gaussian
+  % process (SVGP).
+  % % We present a method that enables any trained neural network to adapt to new data without further gradient-based optimisation,
+  % % whilst providing scalable and principled uncertainty quantification.
+  % % Our method u converts a trained neural network to a sparse variational Gaussian process (SVGP).
+  % Importantly, our method 1) enables fast adaptation to new data,
+  % 2) provides well-calibrated uncertainty estimates, and 3) scales to high-dimensional and large data sets.
+  % % Importantly, our method 1) enables fast adaptation to new data,
+  % % 2) provides well-calibrated uncertainty estimates, and 3) scales to high-dimensional and large data sets.
+  % Essentially, our method reaps the benefits of nonparametric models without their well-known issues.
+  % % 2) does not require further gradient-based optimisation,
+  % We demonstrate the effectiveness of our model's fast adaptation by showing that it can improve sample-efficiency in
+  % model-based reinforcement learning and
+  % we demonstrate our state-of-the-art NN uncertainty quantification with experiments using UCI data sets.
+
+  % obtains principled uncertainty estimates by
+  % Our experiments demonstrate that our model's adaptivity can improve the sample-efficiency of model-based reinforcement
+  % learning.
+
+  % in model-based reinforcement learning using updated information for more efficient exploration.
+
+  % Our method can be deployed in any sequential decision-making process, where new information is received and retraining from scratch is not available.
+
+  % % While gradient-based training is symbiotic to modern deep learning, it is rigid regarding adding further information, usually involving retraining from scratch.
+  % Converting a trained neural network to its dual parameterization we can view the parameters of the model as data dependent terms instead of the weights.
+  % Furthermore, we can then build a sparse model to form a variational dual sparse Gaussian process.
+  % The resultant sparse GP has two obvious advantages: scalable principled uncertainty estimation and the ability adapt to new data without gradient based retraining.
+  % Our proposed method can be deployed in any sequential decision-making process, where new information is received and retraining from scratch is not available.
+  % We show its effectiveness in model-based reinforcement learning using updated information for more efficient exploration.
 \end{abstract}

### 2023-04-18 paper/main.tex
updated title

@@
 %\title{Sequential Decision-Making under Uncertainty with Big Data}
-\title{Neural Network to Vatiational Sparse Gaussian Process: For Adaptive Exploration}
+% \title{Neural Network to Vatiational Sparse Gaussian Process: For Adaptive Exploration}
+% \title{Neural Network to Sparse Variational Gaussian Process: For Updates in Sequential Decision Making}
+% \title{Adapting Neural Networks to New Data For Updates in Sequential Decision Making via Gaussian Processes}
+\title{Converting Neural Networks to Gaussian Processes for Sequential Decision Making Under Uncertainty}
 
@@
 healthcare and robotics.
-However, modern deep learning cannot adapt to new data because it relies upon gradient-based optimisation, which requires retraining with the addition of new data.
-In contrast, nonparametric approaches -- such as Gaussian processes -- can adapt to new data without further training.
+However, modern deep learning methods cannot adapt to new data because they rely on gradient-based optimisation, which requires retraining with the addition of new data.
+In contrast, nonparametric approaches -- such as Gaussian processes -- can adapt to new data.
 However, they are limited to low-dimensional and small data sets.

### 2023-04-18 paper/main.tex
added some bullet points for how I would structure intro

@@
 % \title{Adapting Neural Networks to New Data For Updates in Sequential Decision Making via Gaussian Processes}
-\title{Converting Neural Networks to Gaussian Processes for Sequential Decision Making Under Uncertainty}
+\title{Converting Neural Networks to Gaussian Processes for Sequential Decision-Making Under Uncertainty}
+% \title{Capturing Neural Networks with Gaussian Processes for Sequential Decision-Making Under Uncertainty}
 
@@
 \section{Introduction} \label{sec:intro}
+
+\begin{itemize}
+  \item Many real-world problems require learning-based systems that can adapt to new data.
+  \begin{itemize}
+    % \item For example, in domains such as robotics and healthcare,
+    \item For example, when controlling robots in non-stationary environments it is important for the robot to adapt to the changing dynamics.
+    \item However neural networks rely upon gradient-based optimisation.
+    \item Uncertainty can be used to improve sample efficiency via targeted exploration.
+    \item Uncertainty can be used to handle risk in decision making.
+  \end{itemize}
+
+  \item Gaussian processes can easily adapt to new data and they offer well-calibrated uncertainty estimates.
+  \begin{itemize}
+    \item However, they don't scale to high-dimensional and large data sets.
+  \end{itemize}
+  \item
+  \begin{itemize}
+    \item
+  \end{itemize}
+\end{itemize}
+
 %Why we need uncertainty and adaptiveness

### 2023-04-20 src/models/__init__.py
fixed import errors

@@ -3,3 +3,4 @@ from .rewards.base import RewardModel
 from .transitions.base import TransitionModel
 from .rewards import *
 from .transitions import *
+from .svgp import *

### 2023-04-20 src/models/rewards/base.py

@@ -6,7 +6,7 @@ from typing import Any, Callable, NamedTuple, Optional, Tuple
 logging.basicConfig(level=logging.INFO)
 logger = logging.getLogger(__name__)
 
-from custom_types import Action, RewardPrediction, State, Data
+from src.custom_types import Action, RewardPrediction, State, Data
 from torch.utils.data import DataLoader
 
 

### 2023-04-20 src/models/transitions/base.py

@@ -6,7 +6,7 @@ from typing import Callable, NamedTuple
 logging.basicConfig(level=logging.INFO)
 logger = logging.getLogger(__name__)
 
-from custom_types import Action, State, StatePrediction, Data
+from src.custom_types import Action, StatePrediction, State, Data
 from torch.utils.data import DataLoader
 
 

### 2023-04-20 src/test_update.py
initial commit

@@ -1,0 +1,193 @@
+#!/usr/bin/env python3
+import logging
+import random
+import time
+from pathlib import Path
+
+
+logging.basicConfig(level=logging.INFO)
+logger = logging.getLogger(__name__)
+
+import hydra
+import numpy as np
+import omegaconf
+import torch
+
+
+torch.set_default_dtype(torch.float64)
+import torchrl
+import utils
+import wandb
+from dm_env import specs, StepType
+from omegaconf import DictConfig, OmegaConf
+from tensordict import TensorDict
+import src
+
+# from src.utils.buffer import ReplayBuffer
+from utils import EarlyStopper, set_seed_everywhere
+
+
+@hydra.main(version_base="1.3", config_path="../configs", config_name="svgp")
+def train(cfg: DictConfig):
+    set_seed_everywhere(42)
+    # try:  # Make experiment reproducible
+    #     set_seed_everywhere(cfg.random_seed)
+    # except:
+    #     random_seed = random.randint(0, 10000)
+    #     set_seed_everywhere(random_seed)
+    # set_seed_everywhere(cfg.random_seed)
+
+    # cfg.device = "cuda" if torch.cuda.is_available() else "cpu"
+
+    # Ensure that all operations are deterministic on GPU (if used) for reproducibility
+    torch.backends.cudnn.determinstic = True
+    torch.backends.cudnn.benchmark = False
+
+    svgp = hydra.utils.instantiate(cfg.svgp)
+    likelihood = hydra.utils.instantiate(cfg.likelihood)
+
+    def func(x, noise=True):
+        # x = x + 1e-6
+        f = torch.sin(x * 5) / x + torch.cos(
+            x * 10
+        )  # + x**2 +np.log(5*x + 0.00001)  + 0.5
+        if noise == True:
+            y = f + torch.randn(size=(x.shape)) * 0.2
+            return y[:, 0]
+        else:
+            return f[:, 0]
+
+    # X_train = torch.rand((50, 1)) * 2 - 1
+    # X_train = torch.rand((50, 1)) * 2
+    X_train = torch.rand((100, 1)) * 2
+    # X_train = torch.rand((15, 1)) * 2
+    # X_train = torch.linspace(-1, 1, 50, dtype=torch.float64).reshape(-1, 1)
[…]

### 2023-04-21 bnn-predictive/preds/models.py
Sketch of torch 2 version

@@ -3,8 +3,6 @@ import torch
 from torch import nn
 from torch.nn import init
 import torch.nn.functional as F
-from deepobs.pytorch.testproblems.testproblems_utils import tfconv2d, \
-    tfmaxpool2d, _truncated_normal_init
 
 
 class BayesianLinear(nn.Module):
@@ -179,63 +177,6 @@ testproblems_modules.py
 """
 
 
-class CIFAR100Net(nn.Sequential):
-    """
-    Deepobs network with optional last sigmoid activation (instead of relu)
-    called `net_cifar100_allcnnc`
-    """
-
-    def __init__(self, in_channels=3, n_out=100):
-        super(CIFAR100Net, self).__init__()
-        assert n_out in (10, 100)
-        self.output_size = n_out
-        # only supported for these
-
-        # self.add_module('dropout1', nn.Dropout(p=0.2))
-
-        self.add_module('conv1', tfconv2d(
-            in_channels=in_channels, out_channels=96, kernel_size=3, tf_padding_type='same'))
-        self.add_module('relu1', nn.ReLU())
-        self.add_module('conv2', tfconv2d(
-            in_channels=96, out_channels=96, kernel_size=3, tf_padding_type='same'))
-        self.add_module('relu2', nn.ReLU())
-        self.add_module('conv3', tfconv2d(in_channels=96, out_channels=96, kernel_size=3,
-                                          stride=(2, 2), tf_padding_type='same'))
-        self.add_module('relu3', nn.ReLU())
-
-        # self.add_module('dropout2', nn.Dropout(p=0.5))
-
-        self.add_module('conv4', tfconv2d(
-            in_channels=96, out_channels=192, kernel_size=3, tf_padding_type='same'))
-        self.add_module('relu4', nn.ReLU())
-        self.add_module('conv5', tfconv2d(
-            in_channels=192, out_channels=192, kernel_size=3, tf_padding_type='same'))
-        self.add_module('relu5', nn.ReLU())
-        self.add_module('conv6', tfconv2d(in_channels=192, out_channels=192, kernel_size=3,
-                                          stride=(2, 2), tf_padding_type='same'))
-        self.add_module('relu6', nn.ReLU())
-
-        # self.add_module('dropout3', nn.Dropout(p=0.5))
-
-        self.add_module('conv7', tfconv2d(
-            in_channels=192, out_channels=192, kernel_size=3))
-        self.add_module('relu7', nn.ReLU())
[…]

### 2023-04-21 bnn-predictive/preds/refine.py

@@ -1,5 +1,5 @@
 import torch
-from preds.gradients import Jacobians
+from preds.gradients import Jacobians_naive
 from torch.nn.utils import parameters_to_vector
 from torch.optim import Adam
 from torch.distributions import MultivariateNormal, Normal, kl_divergence
@@ -8,7 +8,7 @@ from opt_einsum import contract as einsum
 
 def laplace_refine(model, X, y, likelihood, prior_prec, n_epochs=1000, lr=1e-3):
     """Laplace in LinNN (GLM) giving posterior mean, and Sigma_chol(d)"""
-    J, f = Jacobians(model, X)
+    J, f = Jacobians_naive(model, X)
     if len(J.shape) == 3:
         J = J.transpose(1, 2)
     theta_star = parameters_to_vector(model.parameters()).detach()
@@ -42,7 +42,7 @@ def laplace_refine(model, X, y, likelihood, prior_prec, n_epochs=1000, lr=1e-3):
 def vi_refine(model, opt, X, y, likelihood, n_epochs=250, lr=1e-2):
     """VI in LinNN (GLM) giving posterior mean, and Sigma_chol(d)"""
     beta = lr
-    J, f = Jacobians(model, X)
+    J, f = Jacobians_naive(model, X)
     if len(J.shape) == 3:
         J = J.transpose(1, 2)
     theta_star = parameters_to_vector(model.parameters()).detach()
@@ -84,7 +84,7 @@ def vi_refine(model, opt, X, y, likelihood, n_epochs=250, lr=1e-2):
 def vi_diag_refine(model, opt, X, y, likelihood, n_epochs=250, lr=1e-3):
     """diag VI in LinNN (GLM) giving posterior mean, and Sigma_chol(d)"""
     beta = lr
-    J, f = Jacobians(model, X)
+    J, f = Jacobians_naive(model, X)
     if len(J.shape) == 3:
         J = J.transpose(1, 2)
     theta_star = parameters_to_vector(model.parameters()).detach()

### 2023-04-21 bnn-predictive/preds/svgp.py
UCI running without refinement

@@ -1,0 +1,40 @@
+"""SVGP class for neural networks.."""
+
+import torch
+import torch.distributions as dist
+import gpytorch
+import functorch
+
+class SVGP(torch.nn.Module):
+
+    def __init__(self, nn_model, likelihood,  data, alpha, beta,  kernel_type='ntk', device='cpu'):
+        # data
+        y, x = data
+        self.y = y  
+        self.x = x
+
+        # dual parameters
+        self.alpha = alpha
+        self.beta = beta
+
+        # trained model and kernel type
+        self.nn_model = nn_model
+        self.kernel_type = 'ntk'
+
+        self.likelihood = likelihood
+
+        self.device = device
+
+    def predict(self, x_):
+        """Evaluate the SVGP predictive."""
+
+    def sample(self, x_, n_samples):
+        """Sample the predictive distribution."""
+        pred_mu, pred_var = self.predict(x_)
+        pred_dist = dist.MultivariateNormal(pred_mu, pred_var)
+        
+        samples = pred_dist.sample((n_samples, ))
+        return samples
+
+
+

### 2023-04-21 bnn-predictive/preds/refine.py
Working refinement

@@ -32,9 +32,9 @@ def laplace_refine(model, X, y, likelihood, prior_prec, n_epochs=1000, lr=1e-3):
     else:
         Hessian = (J.T * Lams.reshape(1, -1)) @ J
     Precision = Hessian + prior_prec * torch.eye(len(Hessian), device=Hessian.device)
-    Chol = torch.cholesky(Precision)
+    Chol = torch.linalg.cholesky(Precision)
     Sigma = torch.cholesky_inverse(Chol, upper=False)
-    Sigma_chol = torch.cholesky(Sigma, upper=False)
+    Sigma_chol = torch.linalg.cholesky(Sigma, upper=False)
     Sigma_chold = torch.diag(torch.sqrt(1 / torch.diag(Precision)))
     return mu.detach(), Sigma_chol, Sigma_chold, losses
 
@@ -70,10 +70,10 @@ def vi_refine(model, opt, X, y, likelihood, n_epochs=250, lr=1e-2):
             g = J.T @ rs - prior_prec @ mu
         # Update
         prec = (1 - beta) * prec + beta * (H + prior_prec)
-        pchol = torch.cholesky(prec, upper=False)
+        pchol = torch.linalg.cholesky(prec, upper=False)
         b = torch.cholesky_solve(g.reshape(-1, 1), pchol, upper=False).squeeze()
         mu = mu + beta * b
-        Sigma_chol = torch.cholesky(torch.cholesky_inverse(pchol, upper=False), upper=False)
+        Sigma_chol = torch.linalg.cholesky(torch.cholesky_inverse(pchol, upper=False), upper=False)
         q = MultivariateNormal(loc=mu, scale_tril=Sigma_chol)
         loss = -likelihood.log_likelihood(y, f_t) + kl_divergence(q, p)
         losses.append(loss.detach().cpu().item())

### 2023-04-21 bnn-predictive/preds/svgp.py

@@ -3,13 +3,13 @@
 import torch
 import torch.distributions as dist
 import gpytorch
-import functorch
+from functorch import make_functional, vmap, vjp, jvp, jacrev
 
 class SVGP(torch.nn.Module):
 
-    def __init__(self, nn_model, likelihood,  data, alpha, beta,  kernel_type='ntk', device='cpu'):
+    def __init__(self, nn_model, likelihood,  data, alpha, beta, device='cpu'):
         # data
-        y, x = data
+        (y, x) = data
         self.y = y  
         self.x = x
 
@@ -18,23 +18,45 @@ class SVGP(torch.nn.Module):
         self.beta = beta
 
         # trained model and kernel type
-        self.nn_model = nn_model
-        self.kernel_type = 'ntk'
-
+        self.kernel = NTK(nn_model, device)
         self.likelihood = likelihood
-
         self.device = device
 
     def predict(self, x_):
         """Evaluate the SVGP predictive."""
 
+
     def sample(self, x_, n_samples):
         """Sample the predictive distribution."""
         pred_mu, pred_var = self.predict(x_)
         pred_dist = dist.MultivariateNormal(pred_mu, pred_var)
-        
-        samples = pred_dist.sample((n_samples, ))
+        samples = pred_dist.sample((n_samples, ), device=self.device)
         return samples
+
+
+class NTK(torch.nn.Module):
+
+    def __init__(self, nn_model, device='cpu'):
+        self.fnet, self.params = make_functional(nn_model().to(device))
+        self.device = device
+         
+    def fnet_single(self, params, x):
+        return self.fnet(params, x.unsqueeze(0)).squeeze(0)
+
+    def empirical_ntk_jacobian_contraction(self, params, x1, x2):
+        # Compute J(x1)
+        jac1 = vmap(jacrev(self.fnet_single), (None, 0))(params, x1)
+        jac1 = [j.flatten(2) for j in jac1]
+    
+        # Compute J(x2)
+        jac2 = vmap(jacrev(self.fnet_single), (None, 0))(params, x2)
+        jac2 = [j.flatten(2) for j in jac2]
+    
+        # Compute J(x1) @ J(x2).T
+        result = torch.stack([torch.einsum('Naf,Mbf->NMab', j1, j2) for j1, j2 in zip(jac1, jac2)])
+        result = result.sum(0)
+        return result
+
 
 
 

### 2023-04-21 paper/main.tex
added sentance to abstract
Minor
RL figure placeholder

@@
+% !TeX spellcheck = en_GB
 \documentclass{article}
@@
 
+% Redefine paragraph to be tighter
+\renewcommand{\paragraph}[1]{{\bf #1}~~}
+
+% Latin
+\usepackage{xspace}
+\newcommand{\eg}{\textit{e.g.\@}\xspace}
+\newcommand{\ie}{\textit{i.e.\@}\xspace}
+\newcommand{\cf}{\textit{cf.\@}\xspace}
+\newcommand{\etc}{\textit{etc.\@}\xspace}
+\newcommand{\etal}{\textit{et~al.\@}\xspace}
+
+% Tikz
+\usepackage{tikz}
+\usepackage{pgfplots}
+\usetikzlibrary{patterns}
+\usetikzlibrary{decorations,backgrounds,arrows.meta,calc}
+
+% Appendix/supplement title
+\newcommand{\nipstitle}[1]{{%
+    % rules for title box at top and bottom
+    \def\toptitlebar{\hrule height4pt \vskip .25in \vskip -\parskip} 
+    \def\bottomtitlebar{\vskip .29in \vskip -\parskip \hrule height1pt \vskip .09in} 
+    \phantomsection\hsize\textwidth\linewidth\hsize%
+    \vskip 0.1in%
+    \toptitlebar%
+    \begin{minipage}{\textwidth}%
+        \centering{\LARGE\bf #1\par}%
+    \end{minipage}%
+    \bottomtitlebar%
+    \addcontentsline{toc}{section}{#1}%
+}}
+
 % Bibliography
@@
 %
+The world is a dynamic environment that requires humans and animals to constantly adapt.
   Building learning-based systems that can adapt to new data and express uncertainty is essential for their deployment in real-world applications, e.g.
@@
 \section{Experiments}
+\label{sec:experiments}
+
+\todo{Overview of experiments}
+
+\subsection{Benchmarks on UCI to for supervised learning}
+
+\subsection{Supervised learning on image data sets}
+
+\subsection{Updating the representation during continual learning}
+
+\subsection{Fast updates in reinforcement learning}
+
+\begin{figure}[!t]
+  \centering
+  \begin{subfigure}{.2\textwidth}
+  \resizebox{\textwidth}{!}{%
+  \begin{tikzpicture}[inner sep=0,outer sep=0]
+
+    % Draw decorated 'ground'
+    \draw[postaction={draw, decorate, decoration={border, angle=-45,
+					amplitude=1cm, segment length=.5cm}}] (-3,-1.5) -- (12,-1.5);
+
+    % The cart
+    \draw[draw=black,fill=black!50,draw=black,line width=3pt,rounded corners=1mm] (0,0) rectangle (9cm,3cm);
+    \node[fill=black,circle,minimum size=.5cm] (dot) at (4.5cm,3cm) {};
+
+    % Wheels
+    \node[fill=white,draw=black,line width=3pt,circle,minimum size=2cm,,fill=black!50] at (2cm,-.5cm) {};
+    \node[fill=white,draw=black,line width=3pt,circle,minimum size=2cm,fill=black!50] at (7cm,-.5cm) {};
+
+    % The arm
+    \node[anchor=north,minimum width=1cm,minimum height=14cm,draw=black,rotate=20,rounded corners=5mm,yshift=7mm,xshift=-.3mm,fill=white,draw=black,line width=3pt] at (dot) {};
+    \node[fill=black,circle,minimum size=.5cm] at (dot) {};
+
+    % Markings
+    \draw[loosely dashed,line width=1pt] (4.5,6) -- (4.5,-10);
+
+    % Arrow
+    \draw[->,black,line width=3pt,-{Latex[length=7mm,width=7mm]}] (1,5) --node[above,outer sep=6pt]{\large $x$} (4.5,5);
+
+    \def\centerarc[#1](#2)(#3:#4:#5)% Syntax: [draw options] (center) (initial angle:final angle:radius)
+    { \draw[#1] ($(#2)+({#5*cos(#3)},{#5*sin(#3)})$) arc (#3:#4:#5); }
+
+    % Draw arc
+    \centerarc[black,line width=3pt](dot)(270:290:11)
+    \node at (6.5,-9) {$\theta$};
+
+    \node[white,minimum size=1cm] at (4.5,-13) {};
+
+  \end{tikzpicture}}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}{.78\textwidth}
+    \tikz\node[minimum width=\textwidth,minimum height=.35\textwidth,fill=black!10,rounded corners=2pt]{RL trjectories or something interesting?};
+  \end{subfigure}
+  \hfill
+  \caption{Add caption.}
+  \label{fig:rl}
+\end{figure}
 
@@
 
-\section{Conclusion} \label{sec:conclusion}
-
-\section*{Broader Impact}
+\section{Discussion and Conclusion}
+\label{sec:conclusion}
+
+%\section*{Broader Impact}
 
@@
 
+\nipstitle{
+    {\Large Supplementary Material:} \\
+    PAPER TITLE GOES HERE}
+\pagestyle{empty}
+
 \appendix
 
-\section{Appendix}
+\section{Method Details}
 
@@
 
-\begin{algorithm}[!t]
+\begin{algorithm}[!b]
 \caption{Model-based RL}\label{alg-mbrl}

### 2023-04-21 src/models/svgp.py
fixed dual update code I think

@@ -122,7 +122,10 @@ def predict(
 ):
     @torch.no_grad()
     def predict_fn(x, data_new: Optional = None, full_cov: bool = False) -> Prediction:
-        print("out_size=0")
+        # if svgp.is_multi_output:
+        #     print("out_size>0")
+        # else:
+        #     print("out_size=0")
         white: bool = False
         svgp.eval()
         likelihood.eval()
@@ -140,7 +143,7 @@ def predict(
             # TODO how to handle diff Z on each output_dim??
             # var_dist = svgp.variational_strategy.variational_distribution
             if svgp.is_multi_output:
-                print("is mo")
+                # print("is mo")
                 Z = svgp.variational_strategy.base_variational_strategy.inducing_points
                 # if Z.ndim == 3 and Z.shape[0] > 1:
                 #     raise NotImplementedError(
@@ -152,7 +155,7 @@ def predict(
                     svgp.variational_strategy.base_variational_strategy.variational_distribution
                 )
             else:
-                print("isn't mo")
+                # print("isn't mo")
                 Z = svgp.variational_strategy.inducing_points
                 var_dist = svgp.variational_strategy.variational_distribution
             num_inducing = Z.size(-2)
@@ -162,18 +165,25 @@ def predict(
             # GPyTorch's way of computing Kuf:
             if Z.ndim == 3:
                 X = X[None, ...].tile((Z.shape[0], 1, 1))
-            print("Z: {}".format(Z.shape))
-            print("X: {}".format(X.shape))
+            # print("Z: {}".format(Z.shape))
+            # print("X: {}".format(X.shape))
+            # X = X[0, ...]
+            # Z = Z[0, ...]
             full_inputs = torch.cat([Z, X], dim=-2)
+
             # else:
             #     full_inputs = torch.cat([Z, X], dim=-2)
             full_covar = svgp.covar_module(full_inputs)
             Kuu = full_covar[..., :num_inducing, :num_inducing].add_jitter()
             Kuf = full_covar[..., :num_inducing, num_inducing:].evaluate()
-            print("full_inputs {}".format(full_inputs.shape))
-            print("Kuu {}".format(Kuu.shape))
-            print("Kuf {}".format(Kuf.shape))
-            print("full_covar {}".format(full_covar.shape))
[…]

### 2023-04-21 src/train.py

@@ -122,10 +122,10 @@ def train(cfg: DictConfig):
             else:
                 if cfg.online_updates and t > 0:
                     # if cfg.online_updates and t > 1:
-                    # transition_data_new = (state_action_inputs, state_diff_outputs)
-                    # reward_data_new = (state_action_inputs, reward_outputs)
-                    transition_data_new = (state_action_input, state_diff_output)
-                    reward_data_new = (state_action_input, reward_output)
+                    transition_data_new = (state_action_inputs, state_diff_outputs)
+                    reward_data_new = (state_action_inputs, reward_outputs)
+                    # transition_data_new = (state_action_input, state_diff_output)
+                    # reward_data_new = (state_action_input, reward_output)
                     data_new = {
                         "transition": transition_data_new,
                         "reward": reward_data_new,
@@ -157,6 +157,7 @@ def train(cfg: DictConfig):
             time_step = env.step(action)
 
             reward_output = torch.Tensor([time_step["reward"]]).to(cfg.device)
+            # print("reward_output {}".format(reward_output.shape))
             state_action_input = torch.concatenate(
                 [state, torch.Tensor(time_step["action"]).to(cfg.device)], -1
             )[None, ...]

### 2023-04-21 paper/main.tex
updated title and abstract

--- 2023-04-18 paper/main.tex
@@
 % \title{Adapting Neural Networks to New Data For Updates in Sequential Decision Making via Gaussian Processes}
-\title{Converting Neural Networks to Gaussian Processes for Sequential Decision-Making Under Uncertainty}
+% \title{Converting Neural Networks to Gaussian Processes for Sequential Decision-Making Under Uncertainty}
+\title{Deep Neural Networks to Sparse Variational Gaussian Processes}
 % \title{Capturing Neural Networks with Gaussian Processes for Sequential Decision-Making Under Uncertainty}
@@
 %
-  Building learning-based systems that can adapt to new data and express uncertainty is essential for their deployment in real-world applications, e.g.
+  % Building learning-based systems  for their deployment in real-world applications
+
+  The world is a complex dynamic environment where humans and animals leverage high-dimensional sensory data to successfully operate and
+  adapt to changes in the environment.
+  Building learning-based systems that can handle high-dimensional data whilst adapting to new data whilst expressing uncertainty is essential for their deployment in real-world applications, e.g.
+healthcare and robotics.
+  However, modern deep learning methods cannot adapt to new data because they rely on gradient-based optimisation, which requires retraining with the addition of new data.
+In contrast, nonparametric approaches -- such as Gaussian processes -- can adapt to new data.
+However, they are limited to low-dimensional and small data sets.
+We present a method that enables any trained neural network (NN) to be converted to a sparse variational Gaussian process (SVGP).
+
+  However, modern deep learning methods cannot adapt to new data because they rely on gradient-based optimisation, which requires retraining with the addition of new data.
+In contrast, nonparametric approaches -- such as Gaussian processes -- can adapt to new data.
+However, they are limited to low-dimensional and small data sets.
+We present a method that enables any trained neural network (NN) to be converted to a sparse variational Gaussian process (SVGP).
+Importantly, our method
+1) scales to high-dimensional and large data sets,
+2) provides well-calibrated uncertainty estimates, and
+3) enables fast adaptation to new data.
+Essentially, our method reaps the benefits of nonparametric models without their well-known issues.
+We demonstrate our state-of-the-art NN uncertainty quantification with experiments using UCI data sets and
+demonstrate the effectiveness of our model's fast adaptation by showing that it can improve sample-efficiency in model-based reinforcement learning.
+%
+% The world is a dynamic environment that requires humans and animals to constantly adapt.
+%   Building learning-based systems that can adapt to new data and express uncertainty is essential for their deployment in real-world applications, e.g.
 healthcare and robotics.

### 2023-04-21 src/models/nn2gp.py
updaetdc

@@ -75,7 +75,7 @@ def predict(
     print("Kxx {}".format(Kxx.shape))
     B = Kxx + torch.eye(Kxx.shape[-1])
     U = torch.linalg.cholesky(Kxx + torch.eye(Kxx.shape[-1]))  # [num_train, num_train]
-    #print("U {}".format(U.shape))
+    # print("U {}".format(U.shape))
 
     def predict_fn(x, full_cov: bool = False) -> Prediction:
         # mean = network.forward(x)
@@ -98,7 +98,7 @@ def predict(
         print("A {}".format(A.shape))
 
         # conditional mean
-        #f_mean = A.T @ Y_train  # [N]
+        # f_mean = A.T @ Y_train  # [N]
         print("f_mean {}".format(f_mean.shape))
 
         # compute the covariance due to the conditioning
@@ -316,7 +316,7 @@ if __name__ == "__main__":
     )
     plt.legend()
     plt.savefig("nn2gp.pdf", transparent=True)
-    #plt.plot(X_train, Y_train)
+    # plt.plot(X_train, Y_train)
 
     fig = plt.subplots(1, 1)
     plt.plot(X_test[:, 0], pred.var)

### 2023-04-21 src/train.py

@@ -122,10 +122,10 @@ def train(cfg: DictConfig):
             else:
                 if cfg.online_updates and t > 0:
                     # if cfg.online_updates and t > 1:
-                    transition_data_new = (state_action_inputs, state_diff_outputs)
-                    reward_data_new = (state_action_inputs, reward_outputs)
-                    # transition_data_new = (state_action_input, state_diff_output)
-                    # reward_data_new = (state_action_input, reward_output)
+                    # transition_data_new = (state_action_inputs, state_diff_outputs)
+                    # reward_data_new = (state_action_inputs, reward_outputs)
+                    transition_data_new = (state_action_input, state_diff_output)
+                    reward_data_new = (state_action_input, reward_output)
                     data_new = {
                         "transition": transition_data_new,
                         "reward": reward_data_new,

### 2023-04-21 paper/main.tex

--- 2023-04-21 paper/main.tex
@@
 %
-The world is a dynamic environment that requires humans and animals to constantly adapt.
-  Building learning-based systems that can adapt to new data and express uncertainty is essential for their deployment in real-world applications, e.g.
+  % Building learning-based systems  for their deployment in real-world applications
+
+  The world is a complex dynamic environment where humans and animals leverage high-dimensional sensory data to successfully operate and
+  adapt to changes in the environment.
+  Building learning-based systems that can handle high-dimensional data whilst adapting to new data whilst expressing uncertainty is essential for their deployment in real-world applications, e.g.
+healthcare and robotics.
+  However, modern deep learning methods cannot adapt to new data because they rely on gradient-based optimisation, which requires retraining with the addition of new data.
+In contrast, nonparametric approaches -- such as Gaussian processes -- can adapt to new data.
+However, they are limited to low-dimensional and small data sets.
+We present a method that enables any trained neural network (NN) to be converted to a sparse variational Gaussian process (SVGP).
+
+  However, modern deep learning methods cannot adapt to new data because they rely on gradient-based optimisation, which requires retraining with the addition of new data.
+In contrast, nonparametric approaches -- such as Gaussian processes -- can adapt to new data.
+However, they are limited to low-dimensional and small data sets.
+We present a method that enables any trained neural network (NN) to be converted to a sparse variational Gaussian process (SVGP).
+Importantly, our method
+1) scales to high-dimensional and large data sets,
+2) provides well-calibrated uncertainty estimates, and
+3) enables fast adaptation to new data.
+Essentially, our method reaps the benefits of nonparametric models without their well-known issues.
+We demonstrate our state-of-the-art NN uncertainty quantification with experiments using UCI data sets and
+demonstrate the effectiveness of our model's fast adaptation by showing that it can improve sample-efficiency in model-based reinforcement learning.
+%
+% The world is a dynamic environment that requires humans and animals to constantly adapt.
+%   Building learning-based systems that can adapt to new data and express uncertainty is essential for their deployment in real-world applications, e.g.
 healthcare and robotics.

### 2023-04-24 paper/main.tex
updated abstract for new paper

@@
 
-  The world is a complex dynamic environment where humans and animals leverage high-dimensional sensory data to successfully operate and
-  adapt to changes in the environment.
-  Building learning-based systems that can handle high-dimensional data whilst adapting to new data whilst expressing uncertainty is essential for their deployment in real-world applications, e.g.
-healthcare and robotics.
-  However, modern deep learning methods cannot adapt to new data because they rely on gradient-based optimisation, which requires retraining with the addition of new data.
+  % The world is a complex dynamic environment where humans and animals leverage high-dimensional sensory data to successfully operate and
+  % adapt to changes in the environment.
+  Building learning-based systems that can handle high-dimensional and large data sets whilst expressing uncertainty is essential in many real-world applications, e.g. healthcare and robotics.
+  Although Gaussian processes can learn nonlinear functions whilst providing principled uncertainty quantification, they are limited to low-dimensional and small data sets.
+  We present a method that enables any trained neural network (NN) to be converted to a sparse variational Gaussian process (SVGP).
+Importantly, our method scales to high-dimensional and large data sets whilst providing well-calibrated uncertainty estimates.
+Further to this, our function-space posterior enables
+any neural network to be 1) adapted online without retraining and 2) used as a functional regulariser in continual learning.
+Essentially, our method reaps the benefits of function space without the well-known issues associated with nonparametric models.
+% Essentially, our method reaps the benefits of nonparametric models without their well-known issues.
+We demonstrate that our method scales to high-dimensional and large data sets such as XXXXX.
+We then show that our method obtains state-of-the-art uncertainty quantification with experiments using UCI data sets.
+Finally, we demonstrate the power of our NN's function-space posterior by showing
+that 1) it can improve sample-efficiency in model-based reinforcement learning (via our model's online adaptation)
+and 2) it can improve XXXX in continual learning.
+
+% Further to this, our method enables neural networks to be adapted online via efficient updates
+
+% Essentially, our method reaps the benefits of nonparametric models without their well-known issues.
+
+% We further show the benefits
+% 3) enables fast adaptation to new data.
+
+%   In contrast, nonparametric approaches -- such as Gaussian processes -- can adapt to new data.
+However, they are limited to low-dimensional and small data sets.
+We present a method that enables any trained neural network (NN) to be converted to a sparse variational Gaussian process (SVGP).
+
+%   However, modern deep learning methods cannot adapt to new data because they rely on gradient-based optimisation, which requires retraining with the addition of new data.
+
+%   However, modern deep learning methods cannot adapt to new data because they rely on gradient-based optimisation, which requires retraining with the addition of new data.
 In contrast, nonparametric approaches -- such as Gaussian processes -- can adapt to new data.
 However, they are limited to low-dimensional and small data sets.
-We present a method that enables any trained neural network (NN) to be converted to a sparse variational Gaussian process (SVGP).
-
-  However, modern deep learning methods cannot adapt to new data because they rely on gradient-based optimisation, which requires retraining with the addition of new data.
-In contrast, nonparametric approaches -- such as Gaussian processes -- can adapt to new data.
-However, they are limited to low-dimensional and small data sets.
-We present a method that enables any trained neural network (NN) to be converted to a sparse variational Gaussian process (SVGP).
-Importantly, our method
-1) scales to high-dimensional and large data sets,
-2) provides well-calibrated uncertainty estimates, and
-3) enables fast adaptation to new data.
-Essentially, our method reaps the benefits of nonparametric models without their well-known issues.
-We demonstrate our state-of-the-art NN uncertainty quantification with experiments using UCI data sets and
-demonstrate the effectiveness of our model's fast adaptation by showing that it can improve sample-efficiency in model-based reinforcement learning.
+%   We present a method that enables any trained neural network (NN) to be converted to a sparse variational Gaussian process (SVGP).
+% Importantly, our method
+% 1) scales to high-dimensional and large data sets,
+% 2) provides well-calibrated uncertainty estimates, and
+% 3) enables fast adaptation to new data.
+% Essentially, our method reaps the benefits of nonparametric models without their well-known issues.
+% We demonstrate our state-of-the-art NN uncertainty quantification with experiments using UCI data sets and
+% demonstrate the effectiveness of our model's fast adaptation by showing that it can improve sample-efficiency in model-based reinforcement learning.
 %

### 2023-04-25 src/train.py
remove step= from wandb logging

@@ -136,7 +136,14 @@ def train(cfg: DictConfig):
                             state_diff_outputs,
                             reward_outputs,
                         )
+                        # print(
+                        #     "state_action_inputs {}".format(state_action_inputs.shape)
+                        # )
+                        # print("state_diff_outputs {}".format(state_diff_outputs.shape))
+                        # print("reward_outputs {}".format(reward_outputs.shape))
+                        logger.info("Updating mode at t={}".format(t))
                         agent.update(data_new)
+                        logger.info("Finished updating models")
                         reset_updates = True
                     else:
                         reset_updates = False
@@ -239,7 +246,8 @@ def train(cfg: DictConfig):
             "TRAINING | Episode: {} | Reward: {}".format(episode_idx, episode_reward)
         )
         if cfg.wandb.use_wandb:
-            wandb.log({"train/": train_metrics}, step=env_step)
+            wandb.log({"train/": train_metrics})
+            # wandb.log({"train/": train_metrics}, step=env_step)
 
         # Train agent
         # for _ in range(cfg.episode_length // cfg.update_every_steps):

### 2023-04-25 paper/main.tex
Add example table for Ella
changed abstract

--- 2023-04-21 paper/main.tex
@@
 % \title{Converting Neural Networks to Gaussian Processes for Sequential Decision-Making Under Uncertainty}
-\title{Deep Neural Networks to Sparse Variational Gaussian Processes}
+\title{Sparse Function Space Representation of Neural Networks for Exploration and Representation}
 % \title{Capturing Neural Networks with Gaussian Processes for Sequential Decision-Making Under Uncertainty}
@@
 
+% Array/table packages
+\usepackage{tabularx}
+\usepackage{array,multirow}
+\usepackage{colortbl}
+\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
+\newcolumntype{C}[1]{>{\PreserveBackslash\centering}p{#1}}
+\newlength{\tblw}
+
 % Latin
@@
 \begin{abstract}
-% Building systems that adapt to new information and express uncertainty is essential to deploy methods in real-world applications e.g.
-healthcare, autonomous vehicles.
-While gradient-based training is symbiotic to modern deep learning, it is rigid regarding adding further information, usually involving retraining from scratch.
-Converting a trained neural network to its dual parameterization we can view the parameters of the model as data dependent terms instead of the weights.
-Furthermore, we can then build a sparse model to form a variational dual sparse Gaussian process.
-The resultant sparse GP has two obvious advantages: scalable principled uncertainty estimation and the ability adapt to new data without gradient based retraining.
-Our proposed method can be deployed in any sequential decision-making process, where new information is received and retraining from scratch is not available.
-We show its effectiveness in model-based reinforcement learning using updated information for more efficient exploration.
-%
-  % Building learning-based systems  for their deployment in real-world applications
-
-  The world is a complex dynamic environment where humans and animals leverage high-dimensional sensory data to successfully operate and
-  adapt to changes in the environment.
-  Building learning-based systems that can handle high-dimensional data whilst adapting to new data whilst expressing uncertainty is essential for their deployment in real-world applications, e.g.
-healthcare and robotics.
-  However, modern deep learning methods cannot adapt to new data because they rely on gradient-based optimisation, which requires retraining with the addition of new data.
-In contrast, nonparametric approaches -- such as Gaussian processes -- can adapt to new data.
-However, they are limited to low-dimensional and small data sets.
-We present a method that enables any trained neural network (NN) to be converted to a sparse variational Gaussian process (SVGP).
-
-  However, modern deep learning methods cannot adapt to new data because they rely on gradient-based optimisation, which requires retraining with the addition of new data.
-In contrast, nonparametric approaches -- such as Gaussian processes -- can adapt to new data.
-However, they are limited to low-dimensional and small data sets.
-We present a method that enables any trained neural network (NN) to be converted to a sparse variational Gaussian process (SVGP).
-Importantly, our method
-1) scales to high-dimensional and large data sets,
-2) provides well-calibrated uncertainty estimates, and
-3) enables fast adaptation to new data.
-Essentially, our method reaps the benefits of nonparametric models without their well-known issues.
-We demonstrate our state-of-the-art NN uncertainty quantification with experiments using UCI data sets and
-demonstrate the effectiveness of our model's fast adaptation by showing that it can improve sample-efficiency in model-based reinforcement learning.
-%
-% The world is a dynamic environment that requires humans and animals to constantly adapt.
-%   Building learning-based systems that can adapt to new data and express uncertainty is essential for their deployment in real-world applications, e.g.
-healthcare and robotics.
-However, modern deep learning methods cannot adapt to new data because they rely on gradient-based optimisation, which requires retraining with the addition of new data.
-In contrast, nonparametric approaches -- such as Gaussian processes -- can adapt to new data.
-However, they are limited to low-dimensional and small data sets.
-We present a method that enables any trained neural network (NN) to be converted to a sparse variational Gaussian process (SVGP).
-Importantly, our method 1) enables fast adaptation to new data, 2) provides well-calibrated uncertainty estimates, and 3) scales to high-dimensional and large data sets.
-Essentially, our method reaps the benefits of nonparametric models without their well-known issues.
-We demonstrate the effectiveness of our model's fast adaptation by showing that it can improve sample-efficiency in model-based reinforcement learning and we demonstrate our state-of-the-art NN uncertainty quantification with experiments using UCI data sets.
-
-  % Building learning-based systems that can adapt to new data and express uncertainty is essential for their deployment
-  % in real-world applications, e.g. healthcare and robotics.
-  % % The ability to adapt to new information and express uncertainty is essential for deploying learning-based systems in real-world applications, e.g. healthcare and robotics.
-  % However, modern deep learning cannot adapt to new data because it relies upon gradient-based optimisation,
-  % which requires retraining with the addition of new data.
-  % In contrast, nonparametric approaches -- such as Gaussian processes -- can adapt to new data without further training.
-  % % Although, traditional approaches are limited to low-dimensional and small data sets, recent advances have scaled
-  % % GPs to large data sets.
-  % However, they are limited to low-dimensional and small data sets.
-  % % We present a method that enables any trained neural network to adapt to new data without further gradient-based optimisation,
-  % % whilst providing scalable and principled uncertainty quantification.
-  % We present a method that enables any trained neural network (NN) to be converted to a sparse variational Gaussian
-  % process (SVGP).
-  % % We present a method that enables any trained neural network to adapt to new data without further gradient-based optimisation,
-  % % whilst providing scalable and principled uncertainty quantification.
-  % % Our method u converts a trained neural network to a sparse variational Gaussian process (SVGP).
-  % Importantly, our method 1) enables fast adaptation to new data,
-  % 2) provides well-calibrated uncertainty estimates, and 3) scales to high-dimensional and large data sets.
-  % % Importantly, our method 1) enables fast adaptation to new data,
-  % % 2) provides well-calibrated uncertainty estimates, and 3) scales to high-dimensional and large data sets.
-  % Essentially, our method reaps the benefits of nonparametric models without their well-known issues.
-  % % 2) does not require further gradient-based optimisation,
-  % We demonstrate the effectiveness of our model's fast adaptation by showing that it can improve sample-efficiency in
-  % model-based reinforcement learning and
-  % we demonstrate our state-of-the-art NN uncertainty quantification with experiments using UCI data sets.
-
-  % obtains principled uncertainty estimates by
-  % Our experiments demonstrate that our model's adaptivity can improve the sample-efficiency of model-based reinforcement
-  % learning.
-
-  % in model-based reinforcement learning using updated information for more efficient exploration.
-
-  % Our method can be deployed in any sequential decision-making process, where new information is received and retraining from scratch is not available.
-
-  % % While gradient-based training is symbiotic to modern deep learning, it is rigid regarding adding further information, usually involving retraining from scratch.
-  % Converting a trained neural network to its dual parameterization we can view the parameters of the model as data dependent terms instead of the weights.
-  % Furthermore, we can then build a sparse model to form a variational dual sparse Gaussian process.
-  % The resultant sparse GP has two obvious advantages: scalable principled uncertainty estimation and the ability adapt to new data without gradient based retraining.
-  % Our proposed method can be deployed in any sequential decision-making process, where new information is received and retraining from scratch is not available.
-  % We show its effectiveness in model-based reinforcement learning using updated information for more efficient exploration.
+Under sequential learning paradigms, such as continual learning (CL) or reinforcement learning (RL), efficient representation and exploration elude standard training techniques for deep learning  models.
+In RL it is common to receive new information from the environment but due to time and hardware constraints it is not possible to adapt by retraining.
+Similarly, CL needs  compact representations of previous tasks to avoid forgetting.
+Recently, methods for converting trained neural networks from weight space to function space show promise in providing a principled approach for probabilistic treatment of the problem.
+However, they lack ways of sparsifying the representation and methods for quick adaptation to new data.
+We introduce a sparse representation of the neural network in function space, which enables fast adpatation and compact representation to solve the limitations of the weight space formulation.
 \end{abstract}
@@
 \section{Introduction} \label{sec:intro}
+
+Neural networks have experienced unparalleled success in the large data, offline and gradient-based training regime.
 
@@
 %Talk about planning and exploration in RL.
+We introduce a sparse representation of the neural network in the function space.
+
+1) principled uncertainty quantification.
+2) A compact representation for continual learning
+3) Fast updates for adaptive exploration.
 
@@
 
-\subsection{Benchmarks on UCI to for supervised learning}
+\subsection{Capturing uncertainty in UCI tasks under supervised learning}
+%
+
+\begin{table}[t!] 
+  \centering\small
+  \caption{Negative log predictive density (NLPD) (lower better) for the proposed model TODO} 
+	\label{tbl:uci}
+	% Control table spacing
+	\renewcommand{\arraystretch}{1.}
+	\setlength{\tabcolsep}{2pt}
+	\setlength{\tblw}{0.15\textwidth}
+
+	% Custom error formatting
+	\newcommand{\val}[2]{%
+		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
+	}
+
+    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
+	\input{tables/uci_nlpd.tex}
+\end{table}
 

### 2023-04-25 paper/main.tex
Minor

--- 2023-04-24 paper/main.tex
@@
 
+% 
+Deep learning is great and in the suerpvised and unsupervised setting solve large-scale problems.
+How about sequential learning problems such as continual or reinforcement learning.
+In continual learning mainitaining a compact representation
+In
+
 \begin{itemize}

### 2023-04-25 paper/main.tex
Reordering things

--- 2023-04-25 paper/main.tex
@@
 \documentclass{article}
-
-%\title{Investigatin Uncertainty Quantification in Model-based Reinforcement Learning}
-% \title{Model-based Reinforcement Learning with Fast Posterior Updates}
-%\title{Sequential Decision-Making under Uncertainty with Big Data}
-% \title{Neural Network to Vatiational Sparse Gaussian Process: For Adaptive Exploration}
-% \title{Neural Network to Sparse Variational Gaussian Process: For Updates in Sequential Decision Making}
-% \title{Adapting Neural Networks to New Data For Updates in Sequential Decision Making via Gaussian Processes}
-% \title{Converting Neural Networks to Gaussian Processes for Sequential Decision-Making Under Uncertainty}
-\title{Sparse Function Space Representation of Neural Networks for Exploration and Representation}
-% \title{Capturing Neural Networks with Gaussian Processes for Sequential Decision-Making Under Uncertainty}
-
-\author{%
-  Aidan ~Scannell \\
-  Aalto University\\
-  %Finnish Center for Artificial Intelligence \\
-  \texttt{aidan.scannell@aalto.fi}
-  \And
-  Paul ~Chang \\
-  Aalto University\\
-  \texttt{paul.chang@aalto.fi}
-  \And
-  Ella ~Tamir \\
-  Aalto University\\
-  \texttt{ella.tamir@aalto.fi}
-  \And
-  Arno ~Solin \\
-  Aalto University\\
-  \texttt{arno.solin@aalto.fi}
-  \And
-  Joni ~Pajarinen \\
-  Aalto University\\
-  \texttt{joni.pajarinen@aalto.fi}
-  % examples of more authors
-  % \And
-  % Coauthor \\
-  % Affiliation \\
-  % Address \\
-  % \texttt{email} \\
-}
 
@@
 
+%\title{Investigatin Uncertainty Quantification in Model-based Reinforcement Learning}
+% \title{Model-based Reinforcement Learning with Fast Posterior Updates}
+%\title{Sequential Decision-Making under Uncertainty with Big Data}
+% \title{Neural Network to Vatiational Sparse Gaussian Process: For Adaptive Exploration}
+% \title{Neural Network to Sparse Variational Gaussian Process: For Updates in Sequential Decision Making}
+% \title{Adapting Neural Networks to New Data For Updates in Sequential Decision Making via Gaussian Processes}
+% \title{Converting Neural Networks to Gaussian Processes for Sequential Decision-Making Under Uncertainty}
+\title{Sparse Function Space Representation of Neural Networks for Exploration and Representation}
+
+\author{%
+  Aidan Scannell\textsuperscript{\star} \\
+  Aalto University \\
+  Finnish Center for Artificial Intelligence \\
+  \texttt{aidan.scannell@aalto.fi}
+  \And
+  Riccardo Mereu\textsuperscript{\star} \\
+  Aalto University\\
+  \texttt{riccardo.mereu@aalto.fi}
+  \And
+  Paul Chang \\
+  Aalto University\\
+  \texttt{paul.chang@aalto.fi}
+  \And
+  Ella Tamir \\
+  Aalto University\\
+  \texttt{ella.tamir@aalto.fi}
+  \And
+  Joni Pajarinen \\
+  Aalto University\\
+  \texttt{joni.pajarinen@aalto.fi}
+  \And
+  Arno Solin \\
+  Aalto University\\
+  \texttt{arno.solin@aalto.fi}
+}
+
 \begin{document}
@@
 
-\section{Introduction} \label{sec:intro}
-
+\section{Introduction}
+\label{sec:intro}
+%
 Neural networks have experienced unparalleled success in the large data, offline and gradient-based training regime. 
+Deep learning is great and in the suerpvised and unsupervised setting solve large-scale problems.
+How about sequential learning problems such as continual or reinforcement learning.
+In continual learning mainitaining a compact representation
 

### 2023-04-25 paper/main.tex
updated abstract

@@
 \begin{abstract}
-Under sequential learning paradigms, such as continual learning (CL) or reinforcement learning (RL), efficient representation and exploration elude standard training techniques for deep learning  models.
-In RL it is common to receive new information from the environment but due to time and hardware constraints it is not possible to adapt by retraining.
-Similarly, CL needs  compact representations of previous tasks to avoid forgetting.
-Recently, methods for converting trained neural networks from weight space to function space show promise in providing a principled approach for probabilistic treatment of the problem.
-However, they lack ways of sparsifying the representation and methods for quick adaptation to new data.
-We introduce a sparse representation of the neural network in function space, which enables fast adpatation and compact representation to solve the limitations of the weight space formulation.
+Under sequential learning paradigms, such as Continual Learning (CL) or Reinforcement Learning (RL), deep learning training techniques show shortcomings in retaining previously acquired knowledge and adapting to evolving environments through exploration.
+Retraining the model to incorporate new data or avoiding forgetting can be inefficient or impossible in many scenarios, setting hard constraints on time and hardware resources.
+Existing techniques for converting trained neural networks from weight to function space allow a principled approach to the problem but still have scaling issues.
+In this paper, we present a method for sparsifying the representation of the neural networks in function space, which enables fast adaptation and compact representation that solves the limitations of the weight space formulation without the well-known flaws associated with nonparametric models.
 \end{abstract}

### 2023-04-25 paper/main.tex
Minor additions

@@
 % \title{Converting Neural Networks to Gaussian Processes for Sequential Decision-Making Under Uncertainty}
-\title{Sparse Function Space Representation of Neural Networks for Exploration and Representation}
+\title{Sparse Function Space Representation of Neural Networks for Exploration and Retention}
 
@@
 \begin{abstract}
-Under sequential learning paradigms, such as Continual Learning (CL) or Reinforcement Learning (RL), deep learning training techniques show shortcomings in retaining previously acquired knowledge and adapting to evolving environments through exploration.
+Under sequential learning paradigms, such as Continual Learning or Reinforcement Learning, deep learning training techniques show shortcomings in retaining previously acquired knowledge and adapting to evolving environments through exploration.
 Retraining the model to incorporate new data or avoiding forgetting can be inefficient or impossible in many scenarios, setting hard constraints on time and hardware resources.
 Existing techniques for converting trained neural networks from weight to function space allow a principled approach to the problem but still have scaling issues.
-In this paper, we present a method for sparsifying the representation of the neural networks in function space, which enables fast adaptation and compact representation that solves the limitations of the weight space formulation without the well-known flaws associated with nonparametric models.
+In this paper, we present a method for sparsifying the representation of the neural networks in function space, which enables fast adaptation and compact representation that solves the limitations of the weight space formulation without the well-known flaws associated with nonparametric models.\looseness-1
 \end{abstract}
@@
 %
-Neural networks have experienced unparalleled success in the large data, offline and gradient-based training regime. 
+%Neural networks have experienced unparalleled success in the large data, offline and gradient-based training regime.
 Deep learning is great and in the suerpvised and unsupervised setting solve large-scale problems.
-How about sequential learning problems such as continual or reinforcement learning.
-In continual learning mainitaining a compact representation
+%How about sequential learning problems such as continual or reinforcement learning. In continual learning mainitaining a compact representation
+Deep learning has experienced unparalleled success in contemporary artificial intelligence (AI), contributing to advancements in various domains ranging from computer vision to natural language processing.
+The capacity of deep learning models to process and learn complex patterns from large-scale supervised and unsupervised learning tasks has led to impressive breakthroughs in applications in the large data, offline, and gradient-based training regime.
+Despite this remarkable success, several challenges remain when employing gradient-based learning techniques in sequential learning paradigms such as continual learning and reinforcement learning.
 

### 2023-04-26 paper/main.tex
Sketching intro

@@
 %
-%Neural networks have experienced unparalleled success in the large data, offline and gradient-based training regime.
-Deep learning is great and in the suerpvised and unsupervised setting solve large-scale problems.
-%How about sequential learning problems such as continual or reinforcement learning. In continual learning mainitaining a compact representation
-Deep learning has experienced unparalleled success in contemporary artificial intelligence (AI), contributing to advancements in various domains ranging from computer vision to natural language processing.
-The capacity of deep learning models to process and learn complex patterns from large-scale supervised and unsupervised learning tasks has led to impressive breakthroughs in applications in the large data, offline, and gradient-based training regime.
-Despite this remarkable success, several challenges remain when employing gradient-based learning techniques in sequential learning paradigms such as continual learning and reinforcement learning.
-
-\begin{itemize}
-  \item Many real-world problems require learning-based systems that can adapt to new data.
-  \begin{itemize}
-    % \item For example, in domains such as robotics and healthcare,
-    \item For example, when controlling robots in non-stationary environments it is important for the robot to adapt to the changing dynamics.
-    \item However neural networks rely upon gradient-based optimisation.
-    \item Uncertainty can be used to improve sample efficiency via targeted exploration.
-    \item Uncertainty can be used to handle risk in decision making.
-  \end{itemize}
-
-  \item Gaussian processes can easily adapt to new data and they offer well-calibrated uncertainty estimates.
-  \begin{itemize}
-    \item However, they don't scale to high-dimensional and large data sets.
-  \end{itemize}
-  \item
-  \begin{itemize}
-    \item
-  \end{itemize}
-\end{itemize}
-
-%Why we need uncertainty and adaptiveness
-How to adapt to new information is a limitation of current machine learning models.
-The problem is specifically relevant when we combine a model with a decision-making process.
-In such a sequential setting, an agent typically makes decisions in an environment and obtains new information and would ideally incorporate the information into their parameters.
-Not only do we need models that adapt to new informatoion but all express uncertainty over the models predictions.
-The reason being twofold: in many applications, e.g.
-healthcare, autonomous driving is an essential requirement, and many advanced exploration techniques require uncertainty to determine where to query next.
+Deep learning has become the cornerstone of contemporary artificial intelligence, proving remarkably effective in tackling supervised and unsupervised learning tasks in the {\em large data}, {\em offline}, and {\em gradient-based training} regime.
+Despite its success, gradient-based learning techniques exhibit limitations when applied to sequential learning paradigms, such as Continual Learning (CL, \cite{add}) and Reinforcement Learning (RL, \cite{add}).
+In CL, the challenge is retaining a compact representation of the problem and avoid forgetting over the life-long learning horizon (see, \eg, \cite{add}).
+Similarly in RL, the model would need to adapt to observations of the environment through exploration, but this can be inefficient and would require constant retraining (\eg, \cite{add}).
 
 %Current state of affairs 
-GPs give principled uncertainty estimates and are a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} furthermore they have theoretical guarantees on regret bounds \citep{srinivas2009gaussian}.
-Yet many problems lie in high dimensional input space; for example, images are where GPs cannot learn representations.
+Recent work on techniques (\eg, \cite{list}) for converting trained neural networks from weight space to function space allow a principled mathematical approach for analyzing the behaviour \cite{add}, performing probabilistic inference \cite{add}, and quantifying uncertainty in neural networks \cite{add}.
+The methods rely on linearizing the neural network and capturing the first two moments in function space in terms of a mean function and covariance function (kernel)---defining a Gaussian process (GP, \cite{rasmussen2006}).
+GPs provide a widely-used probabilistic toolkit with principled uncertainty estimates, and they are a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} with theoretical guarantees on regret bounds \citep{srinivas2009gaussian}.
+%Yet many problems lie in high dimensional input space; for example, images are where GPs cannot learn representations.
 In such scenarios such as in many reinforcement learning environments neural networks are used as the surrogate model.
@@
 
-% Introduce the laplace GNN + shortcomings
-One common approach for uncertainty with neural networks is a Laplace GNN approximation \citep{daxbergerLaplace2021}.
-The idea is to essentially takes a trained neural network and linearises around the optimal weights.
-The resulting linear model can be used to obtain uncertainty estimates and sometimes improved predictions \citep{immerScalable2021}.
-Given the resultant model is now linear with respect to the weights its is also now possible to convert to a Gaussian process as shown in \citep{immerScalable2021, khan2019approximate}.
-Yet to obtain uncertainty estimates there is the usual computational scaling of the GP of $O(n^3)$, so cubic in the number of data points.
-Many approaches  apply crude approximations and yet still obtain good uncertainty estimates.
-
 %Need for adaptive learning methods + failures with current methods
-In this paper we show that we can take any neural network and define the dual parameters of a Gaussian process \citep{csato2002sparse, adam2021dual, chang2020fast}.
-Crucially the resultant GP now has predictions in the same space as the space as the initial trained neural network, a property not of previous approaches.
-Given the dual parameter formulation we can then easily convert a full GP to a variational sparse version.
-Using the sparse GP we can then take advantage of the property of dual parameters that allows for fast conditioning recently shown in \citep{chang2022fantasizing}.
+In this paper, we show that we can take any neural network and represent the model in terms of the so-called `dual' parameters of a Gaussian process \cite{csato2002sparse, adam2021dual, chang2020fast}.
+Crucially, the resultant GP now has predictions in the same space as the initial trained neural network, a property not of previous approaches.
+Given the dual parameter formulation, we can convert a full GP to a variational sparse version.
+Using the sparse GP we can then take advantage of the property of dual parameters that allows for fast conditioning recently shown in \cite{chang2022fantasizing}.
 Thus we are able to avoid retraining and condition new data in to our model.
-The resultant DNN2SGP method can be used in any sequential decision-making scenario where retraining is not available and we show its effectiveness in a planning stage of a model based reinforcement algorithim.
+The resultant DNN2SGP method can be used in any sequential decision-making scenario where retraining is not available.%and we show its effectiveness in a planning stage of a model based reinforcement algorithim.
+
+\todo{a pragraph on how this can be used for improving CL and RL}
 
@@
 %Talk about planning and exploration in RL.
+
 We introduce a sparse representation of the neural network in the function space. 
-
-1) principled uncertainty quantification.
-2) A compact representation for continual learning
-3) Fast updates for adaptive exploration.
+%
+{\em (i)}~principled uncertainty quantification.
+{\em (ii)}~A compact representation for continual learning
+{\em (iii)}~Fast updates for adaptive exploration.
+%
+We demonstrate points {\em(i)--(iii)} in the experiments.
 
 %List the contributions.
-The contributions of the paper our is as follows:
-\begin{itemize}
-\item We show how to take a trained neural network and convert it to a dual sparse GP.
+%The contributions of the paper our is as follows:
+%\begin{itemize}
+%\item We show how to take a trained neural network and convert it to a dual sparse GP.
 We are able to do this without retraining a variational objective for the Sparse GP.
 Our sparse GP uses the variational formulation, and thus gives better uncertainty estimates than other no variational sparse approaches used previously.
-\item The sparse GP now gives us a compact representation of our parameters in the function space.
+%\item The sparse GP now gives us a compact representation of our parameters in the function space.
 We can therefore take advantage of the dual parameters formulation for fast conditioning of new data in to our posterior avoiding retraining of the neural network.
@@
 We show how this is effective in the planning stage of model-based reinforcement exploration.
-\end{itemize}
+%\end{itemize}
+
+%
+%
+%\begin{itemize}
+%  \item Many real-world problems require learning-based systems that can adapt to new data.
+%  \begin{itemize}
+%    % \item For example, in domains such as robotics and healthcare,
+%    \item For example, when controlling robots in non-stationary environments it is important for the robot to adapt to the changing dynamics.
+%    \item However neural networks rely upon gradient-based optimisation.
+%    \item Uncertainty can be used to improve sample efficiency via targeted exploration.
+%    \item Uncertainty can be used to handle risk in decision making.
+%  \end{itemize}
+%
+%  \item Gaussian processes can easily adapt to new data and they offer well-calibrated uncertainty estimates.
+%  \begin{itemize}
+%    \item However, they don't scale to high-dimensional and large data sets.
+%  \end{itemize}
+%  \item
+%  \begin{itemize}
+%    \item
+%  \end{itemize}
+%\end{itemize}
+
+%Why we need uncertainty and adaptiveness
+%How to adapt to new information is a limitation of current machine learning models.
+The problem is specifically relevant when we combine a model with a decision-making process.
+In such a sequential setting, an agent typically makes decisions in an environment and obtains new information and would ideally incorporate the information into their parameters.
+Not only do we need models that adapt to new informatoion but all express uncertainty over the models predictions.
+The reason being twofold: in many applications, \eg\ healthcare, autonomous driving is an essential requirement, and many advanced exploration techniques require uncertainty to determine where to query next.
 
@@
 \end{figure}
+
+\subsection{Related Work}
+\label{sec:related}
+%
+
+% Introduce the laplace GNN + shortcomings
+One common approach for uncertainty with neural networks is a Laplace GNN approximation \citep{daxbergerLaplace2021}.
+The idea is to essentially takes a trained neural network and linearises around the optimal weights.
+The resulting linear model can be used to obtain uncertainty estimates and sometimes improved predictions \citep{immerScalable2021}.
+Given the resultant model is now linear with respect to the weights its is also now possible to convert to a Gaussian process as shown in \citep{immerScalable2021, khan2019approximate}.
+Yet to obtain uncertainty estimates there is the usual computational scaling of the GP of $O(n^3)$, so cubic in the number of data points.
+Many approaches  apply crude approximations and yet still obtain good uncertainty estimates.
 

### 2023-04-26 paper/main.tex
rewrite abstract a bit

@@
 \begin{abstract}
-Under sequential learning paradigms, such as Continual Learning or Reinforcement Learning, deep learning training techniques show shortcomings in retaining previously acquired knowledge and adapting to evolving environments through exploration.
-Retraining the model to incorporate new data or avoiding forgetting can be inefficient or impossible in many scenarios, setting hard constraints on time and hardware resources.
-Existing techniques for converting trained neural networks from weight to function space allow a principled approach to the problem but still have scaling issues.
-In this paper, we present a method for sparsifying the representation of the neural networks in function space, which enables fast adaptation and compact representation that solves the limitations of the weight space formulation without the well-known flaws associated with nonparametric models.\looseness-1
+Under sequential learning paradigms, such as Continual Learning (CL) or Reinforcement Learning (RL), deep learning training techniques show shortcomings, given limited access to previous data.
+In many scenarios, retraining the model to incorporate new data or avoiding forgetting can be inefficient or impossible.
+Existing techniques for converting trained neural networks from weight to function space allow a principled approach for CL but resort to unprincipled subset approaches.
+Whilst adaptivity in RL is typically ignored.
+In this paper, we present a method for sparsifying the representation of the neural networks in function space, which enables fast adaptation and compact representation that solves the limitations of the weight space formulation without the well-known flaws associated with nonparametric models.
+Furthermore, we show experiments on how our method can be a general approach to help solve exploration and retention in CL and RL.
 \end{abstract}

### 2023-04-26 bnn-predictive/experiments/classification.py
Bash himmeli

@@ -211,9 +211,10 @@ def main(ds_train, ds_test, ds_valid, deltas, device, dataset, name, seed, res_d
     resdict['N_test'] = len(ds_test)
     resdict['K'] = ds_train.C
 
-    with open(os.path.join(res_dir, f'classification_{dataset}_{name}_{seed}.pkl'), 'wb') as f:
+    res_file = f'classification_{dataset}_{name}_{seed}.pkl'
+    with open(os.path.join(res_dir, res_file), 'wb') as f:
         pickle.dump(resdict, f)
-
+    print(f'Wrote results to {res_file}')
 
 if __name__ == '__main__':
     import argparse
@@ -255,7 +256,7 @@ if __name__ == '__main__':
     refine = args.refine
 
     data_dir = os.path.join(root_dir, 'data')
-    res_dir = os.path.join(root_dir, 'experiments', 'results')
+    res_dir = os.path.join(root_dir, 'experiments', 'results', 'uci')
     print(f'Writing results to {res_dir}')
     print(f'Reading data from {data_dir}')
     print(f'Dataset: {dataset}')
@@ -266,7 +267,10 @@ if __name__ == '__main__':
 
     device = 'cuda' if torch.cuda.is_available() else 'cpu'
     torch.set_default_device(device)
-
+    if device != 'cuda':
+        print('Running on CPU')
+    else:
+        print(f'Device name: {torch.cuda.get_device_name()}')
     ds_train = UCIClassificationDatasets(dataset, random_seed=seed, root=data_dir, stratify=True,
                                          train=True, double=double)
     ds_test = UCIClassificationDatasets(dataset, random_seed=seed, root=data_dir, stratify=True,

### 2023-04-26 paper/main.tex

@@
 In CL, the challenge is retaining a compact representation of the problem and avoid forgetting over the life-long learning horizon (see, \eg, \cite{add}).
-Similarly in RL, the model would need to adapt to observations of the environment through exploration, but this can be inefficient and would require constant retraining (\eg, \cite{add}).
+Similarly in RL, the model would need to adapt to observations of the environment through exploration, but this can be inefficient and would require constant retraining (\eg, \cite{add, add}).
 

### 2023-05-02 bnn-predictive/preds/predictives.py
Fixed bug with subsets

@@ -52,7 +52,7 @@ def svgp_sampling_predictive(X, X_train, y_train, model, likelihood, prior_prec,
     """Returns the sparse data used for convenience."""
     link = (lambda x: x) if no_link else likelihood.inv_link
     data = (y_train, X_train)
-    svgp = SVGPNTK(model, likelihood, data, prior_prec, n_sparse=n_sparse, sparse_data=sparse_data)
+    svgp = SVGPNTK(model, likelihood, data, prior_prec, n_sparse=n_sparse, sparse_data=sparse_data, subset=False)
     f_mu, f_var = svgp.predict(X)
     f_mu = model(X) + f_mu
     data_sparse = svgp.get_sparse_data()

### 2023-05-02 bnn-predictive/preds/svgp.py

@@ -12,22 +12,30 @@ from torch.func import vmap, jacrev, functional_call, hessian
 
 class SVGPNTK():
 
-    def __init__(self, nn_model, likelihood, data, prior_prec, n_sparse=0.25, sparse_data=None, device='cpu'):
+    def __init__(self, nn_model, likelihood, data, prior_prec, n_sparse=0.25, sparse_data=None, subset=False, device='cpu'):
         # data
         (y, x) = data
         self.n_classes = nn_model(x[0]).shape[-1]
         self.nn_model = nn_model
 
+        self.y = y
+        self.x = x
+         
         # randomly select n_sparse points
         if sparse_data is None:
             self.n_sparse = int(y.shape[0]*n_sparse)
             indices = torch.randperm(y.shape[0])[:self.n_sparse]
-            self.y = y[indices]
-            self.x = x[indices]
+            self.z = x[indices]
+            sparse_y = y[indices]
+            self.z_y = sparse_y
         else:
             (sparse_y, sparse_x) = sparse_data
+            self.z = sparse_x
+            self.z_y = sparse_y
+
+        if subset:  # makes the subset
+            self.x = self.z 
             self.y = sparse_y
-            self.x = sparse_x
 
         self.n_classes = nn_model(self.x[0]).shape[-1]
         self.delta = prior_prec
@@ -40,7 +48,7 @@ class SVGPNTK():
         self.device = device
 
         # precompute the duals
-        alpha, beta = self.estimate_duals((self.y, self.x))
+        alpha, beta = self.estimate_duals()
         self.alpha = alpha
         self.beta = beta
 
@@ -48,7 +56,7 @@ class SVGPNTK():
         return -self.likelihood.log_likelihood(y, logits)
 
     def get_sparse_data(self):
-        return (self.y, self.x)
+        return (self.z_y, self.z)
 
     def estimate_lambdas(self, lambdas_data, clip_lambda=True):
         (y, logits_train) = lambdas_data
@@ -68,26 +76,26 @@ class SVGPNTK():
             lambdas = mask*torch.diag(diag) + (1. - mask)*lambdas
         return lambdas
 
-    def estimate_duals(self, data):
+    def estimate_duals(self):
         """Estimate the duals alpha and beta."""
[…]

### 2023-05-08 paper/main.tex
Placeholder table
added cl table placeholder
updated abstract

@@
 \begin{abstract}
-Under sequential learning paradigms, such as Continual Learning (CL) or Reinforcement Learning (RL), deep learning training techniques show shortcomings, given limited access to previous data.
-In many scenarios, retraining the model to incorporate new data or avoiding forgetting can be inefficient or impossible.
-Existing techniques for converting trained neural networks from weight to function space allow a principled approach for CL but resort to unprincipled subset approaches.
-Whilst adaptivity in RL is typically ignored.
-In this paper, we present a method for sparsifying the representation of the neural networks in function space, which enables fast adaptation and compact representation that solves the limitations of the weight space formulation without the well-known flaws associated with nonparametric models.
-Furthermore, we show experiments on how our method can be a general approach to help solve exploration and retention in CL and RL.
+Sequential learning paradigms such as Continual Learning (CL) or Reinforcement Learning (RL) pose a challenge for gradient-based deep learning techniques as they struggle to incorporate new data and retain previous knowledge.
+Existing methods for converting neural networks from weight to function space allow a probabilistic treatment of the distribution over the function learned by the neural networks but are computationally expensive.
+We propose a method that converts a neural network to a low-rank functional representation as a sparse Gaussian process. 
+With this approach, we can build a compact representation of the function encoded by the neural network that can replace previous data in continual settings and be used for fast adaptation in RL, avoiding full retraining of the model.
 \end{abstract}
@@
 \begin{table}[t!] 
-  \centering\small
+  \centering\scriptsize
   \caption{Negative log predictive density (NLPD) (lower better) for the proposed model TODO} 
@@
 	\setlength{\tabcolsep}{2pt}
-	\setlength{\tblw}{0.15\textwidth}
+	\setlength{\tblw}{0.14\textwidth}
 
@@
     % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
-	\input{tables/uci_nlpd.tex}
+	\input{tables/uci.tex}
 \end{table}
@@
 \subsection{Updating the representation during continual learning}
+
+\begin{table}[t!] 
+  \centering\scriptsize
+  \caption{CL Experiments  TODO} 
+	\label{tbl:cl_table_1}
+	% Control table spacing
+	\renewcommand{\arraystretch}{1.}
+	\setlength{\tabcolsep}{2pt}
+	\setlength{\tblw}{0.14\textwidth}
+
+	% Custom error formatting
+	\newcommand{\val}[2]{%
+		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
+	}
+
+	\input{tables/cl_table_1}
+\end{table}
 

### 2023-05-09 src/nn2svgp/ntksvgp.py
return correct lambda u

@@ -418,6 +418,7 @@ def calc_sparse_dual_params_batch(
 
     ################  Compute alpha/beta batched version START ################
     alpha_u = torch.zeros((out_dim, Z.shape[0])).cpu()
+    Lambda_u = torch.zeros((out_dim, Z.shape[0])).cpu()
     beta_u = torch.zeros((out_dim, Z.shape[0], Z.shape[0])).cpu()
 
     if subset_out_dim is not None:
@@ -447,6 +448,7 @@ def calc_sparse_dual_params_batch(
             start_idx = end_idx
             del Kui_c
         torch.cuda.empty_cache()
+        Lambda_u[output_c] = alpha_u[output_c]
         Kzz_c = (
             kernel(Z, Z, output_c).cpu() + torch.eye(Z.shape[0], device="cpu") * jitter
         )
@@ -454,7 +456,7 @@ def calc_sparse_dual_params_batch(
             (Kzz_c + beta_u[output_c]), alpha_u[output_c]
         )
 
-    return alpha_u.to(device), beta_u.to(device), Lambda.to(device)
+    return alpha_u.to(device), beta_u.to(device), Lambda_u.to(device)
     ################  Compute alpha/beta batched version END ################
 
 

### 2023-05-09 src/nn2svgp/train_regression.py
use batch kernel dual params calc

@@ -156,6 +156,7 @@ if __name__ == "__main__":
         output_dim=3,
         # num_inducing=500,
         num_inducing=50,
+        dual_batch_size=32,
         # num_inducing=20,
         # jitter=1e-6,
         jitter=1e-4,
@@ -191,7 +192,7 @@ if __name__ == "__main__":
 
     plot_var = False
     plot_var = True
-    save_dir = "figs/resample"
+    save_dir = "figs"
 
     def plot_output(i):
         fig = plt.subplots(1, 1)

### 2023-05-09 bnn-predictive/experiments/scripts/classification.py
Make bbb smaller,  read n_inducing 32 results

@@ -217,8 +217,8 @@ def inference(
         epochsv,
         lr=lrv,
         n_samples_train=1,
-        n_samples_pred=n_samples,
-        n_layers=n_layers,
+        n_samples_pred=100, # was n_samples
+        n_layers=n_layers,  
         n_units=n_units,
         activation=activation,
     )
@@ -458,6 +458,7 @@ if __name__ == "__main__":
     print(f"Writing results to {res_dir}")
     print(f"Reading data from {data_dir}")
     print(f"Dataset: {dataset}")
+    print(f'Number of inducing points: {n_inducing}')
     print(f"Seed: {seed}")
     print(double)
 

### 2023-05-09 bnn-predictive/preds/mfvi.py

@@ -18,7 +18,7 @@ def preds_bbb(model, X, n_samples, likelihood):
 
 
 def run_bbb(ds_train, ds_test, ds_valid, prior_prec, device, likelihood, n_epochs, lr,
-            n_samples_train=10, n_samples_pred=1000, n_layers=2, n_units=50, activation='tanh'):
+            n_samples_train=10, n_samples_pred=100, n_layers=2, n_units=50, activation='tanh'):
     D = ds_train.data.shape[1]
     if type(likelihood) is BernoulliLh or type(likelihood) is ntksvgp.likelihoods.Gaussian:
         K = 1

### 2023-05-10 paper/main.tex
Added new table to paper
updated cl table
starting to fill out background

@@
 \newcommand{\pPolicy}{\ensuremath{\pi_{\policyParams}}}
+
+% Packages for bold math
+\usepackage{bm}
+\newcommand{\mathbold}[1]{\bm{#1}}
+\newcommand{\mbf}[1]{\mathbf{#1}}
+
+% Math Macros
+\newcommand{\MC}{\mbf{C}}
+\newcommand{\MZ}{\mbf{Z}}
+\newcommand{\MV}{\mbf{V}}
+\newcommand{\MX}{\mbf{X}}
+\newcommand{\MA}{\mbf{A}}
+\newcommand{\MK}{\mbf{K}}
+\newcommand{\MI}{\mbf{I}}
+\newcommand{\MH}{\mbf{H}}
+\newcommand{\T}{\top}
+\newcommand{\vzeros}{\mbf{0}}
+\newcommand{\vtheta}[0]{\mathbold{\theta}}
+\newcommand{\valpha}[0]{\mathbold{\alpha}}
+\newcommand{\vkappa}[0]{\mathbold{\kappa}}
+\newcommand{\vbeta}[0]{\mathbold{\beta}}
+\newcommand{\vlambda}[0]{\mathbold{\lambda}}
+
+\newcommand{\vm}{\mbf{m}}
+%\newcommand{\vz}{\mbf{z}}
+%\newcommand{\vf}{\mbf{f}}
+\newcommand{\vu}{\mbf{u}}
+\newcommand{\vx}{\mbf{x}}
+\newcommand{\vy}{\mbf{y}}
+
+\newcommand{\GP}{\mathcal{GP}}
+\newcommand{\KL}[2]{\mathrm{D}_\textrm{KL} \dbar*{#1}{#2}}
+\newcommand{\MKzz}{\mbf{K}_{\mbf{z}\mbf{z}}}
+\newcommand{\MKxx}{\mbf{K}_{\mbf{x}\mbf{x}}}
+\newcommand{\MKzx}{\mbf{K}_{\mbf{z}\mbf{x}}}
+\newcommand{\MKxz}{\mbf{K}_{\mbf{x}\mbf{z}}}
+\newcommand{\vkzi}{\mbf{k}_{\mbf{z}i}}
+\newcommand{\vkzs}{\mbf{k}_{\mbf{z}i}}
+\newcommand{\vk}{\mbf{k}}
+\newcommand{\MLambda}[0]{\mathbold{\Lambda}}
+\definecolor{matplotlib-blue}{HTML}{1f77b4}
+\newcommand{\N}{\mathrm{N}}
+\newcommand{\myexpect}{\mathbb{E}}
 
@@
 \section{Background} \label{sec:background}
-Sequential decision making requires uncertainty estimates for effective exploration.
-
-In this section, we recap how can obtain a GP posterior from a trained deep neural network (DNN).
+
+\textbf{Neural Network in weight space}
+
+\textbf{Laplace approximation}
+
+\textbf{Dual GP}
+\begin{align}
+   \myexpect_{q_{\vu}(f)}[f_i] &= \vkzs^{\T} \valpha_{\vu} , \\
+   %\textrm{Var}_{q_{\vu}(f)}[f_i]  &= \kappa_{ii} - \vkzs^\top \sqr{\MKzz^{-1} - \rnd{ \MKzz + \vbeta_{\vu} }^{-1} }   \vkzs, \nonumber
+\end{align}
+now the dual parameters consist of an $m$-length vector $\valpha_\vu$ and $m\times m$-size matrix $\vbeta_\vu$, defined as
+\begin{equation} 
+\begin{split}
+   \vlambda & = [ \MKzz + \vbeta_{\vu}]\valpha_{\vu}  = \sum_{i \in \mathcal{D}_{\textrm{old}} \cup \mathcal{D}_{\textrm{new}}}  \vkzi \, \hat{\lambda}_{i}, \\
+   \vbeta_{\vu} &= \sum_{i \in \mathcal{D}_{\textrm{old}} \cup \mathcal{D}_{\textrm{new}}} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,
+\label{eq:dual_sparse}
+\end{split}
+\end{equation}
+where $\tilde{\lambda}_i = \alpha_i - \myexpect_{q_{\vu}(f)}[f_i] \beta_i$ is a different form of the first dual parameter, the gradient with respect to the first expectation parameter of $q_{\vu}(f)$ proposed in \cite{khan2017conjugate,chang2020fast}, with $(\hat{\alpha}_i, \hat{\beta}_i)$ defined as follows,
+\begin{equation}
+\begin{aligned}
+   \hat{\alpha}_i &= \myexpect_{q_{\vu}(f_i)} [\nabla_{f_i}\log p(y_i \mid f_i)],\\
+   \hat{\beta}_i &= \myexpect_{q_{\vu}(f_i)} [ -\nabla^2_{f_i}\log p(y_i \mid f_i)],
+\end{aligned} \label{eq:svgp_dual}
+\end{equation}
+
 % We start by obtaining a posterior over the weights of a trained neural network via the Laplace approximation.
@@
 % as an $L\text{-layer}$ NN with weights $\transitionParams$.
-\textbf{Gaussian processes}
-A Gaussian process (GP) is a distribution over real-valued functions $f(\cdot): \mathcal{X} \rightarrow \R$ defined over $\mathcal{X}$.
-Formally, a GP is defined as,
-\begin{align}
-\label{eq-gp-prior}
-  f(\cdot) \sim \mathcal{N}\left( \mu(\cdot), k(\cdot,\cdot') \right) \quad
-  \mu(\cdot): \mathcal{X} \rightarrow \R \quad
-  k(\cdot,\cdot'): \mathcal{X} \times \mathcal{X} \rightarrow \R
-\end{align}
-where $\mu(\cdot)$ denotes a mean function and $k(\cdot,\cdot')$ a positive definite covariance function, also known as a kernel.
-Given a data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
-we can obtain the GP posterior via multivariate normal conditioning,
-\begin{align}
-\label{eq-gp-predictive-posterior}
-  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
-  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
-  \left( f(\mathbf{x}_{*}) \mid \mu(\mathbf{x}_{*}) + \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} (\mathbf{y} - \bm\mu_{\mathbf{X}})),
-  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
-\end{align}
-% Our GP posterior is then given by,
-\todo{add mean func to GP posterior if we're using one}
-\begin{align}
-\label{eq-gp-predictive-posterior}
-  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
-  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
-  \left( f(\mathbf{x}_{*}) \mid \mu(\mathbf{x}_{*}) + \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} \mu_{\mathbf{x}},
-  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} + \bm\Lambda(\mathbf{y} ; \mathbf{f})^{-1} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
-\end{align}
-where $\bm\Lambda(\mathbf{y} ; \mathbf{f}) = \nabla^{2}_{\mathbf{f} \mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$ can be viewed as per-input noise.
+
+%A Gaussian process (GP) is a distribution over real-valued functions $f(\cdot): \mathcal{X} \rightarrow \R$ defined over $\mathcal{X}$.
+%Formally, a GP is defined as,
+%\begin{align}
+%\label{eq-gp-prior}
+%  f(\cdot) \sim \mathcal{N}\left( \mu(\cdot), k(\cdot,\cdot') \right) \quad
+%  \mu(\cdot): \mathcal{X} \rightarrow \R \quad
+%  k(\cdot,\cdot'): \mathcal{X} \times \mathcal{X} \rightarrow \R
+%\end{align}
+%where $\mu(\cdot)$ denotes a mean function and $k(\cdot,\cdot')$ a positive definite covariance function, also known as a kernel.
+%Given a data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
+%we can obtain the GP posterior via multivariate normal conditioning,
+%\begin{align}
+%\label{eq-gp-predictive-posterior}
+%  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
+%  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
+%  \left( f(\mathbf{x}_{*}) \mid \mu(\mathbf{x}_{*}) + \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} (\mathbf{y} - \bm\mu_{\mathbf{X}})),
+%  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
+%\end{align}
+%% Our GP posterior is then given by,
+%\todo{add mean func to GP posterior if we're using one}
+%\begin{align}
+%\label{eq-gp-predictive-posterior}
+%  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
+%  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
+%  \left( f(\mathbf{x}_{*}) \mid \mu(\mathbf{x}_{*}) + \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} \mu_{\mathbf{x}},
+%  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} + \bm\Lambda(\mathbf{y} ; \mathbf{f})^{-1} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
+%\end{align}
+%where $\bm\Lambda(\mathbf{y} ; \mathbf{f}) = \nabla^{2}_{\mathbf{f} \mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$ can be viewed as per-input noise.
 \todo{I'm unsure about this per input noise bit.
 Check with paul.}
-\todo{what about regression/classification likelhoods}
-This GP predictive posterior is computationally expensive as it requires inverting an $N\times N$ matrix.
-
-\textbf{Sparse Gaussian processes}
-% The GP predictive posterior in \cref{eq-gp-predictive-posterior} is computationally expensive as it requires inverting an $N\times N$ matrix.
-A practical and computationally appealing alternative is to augment the joint probability space with pseudo inputs $\mathbf{Z} \in \R^{M \times D}$
-and corresponding outputs
-$\mathbf{u} = f(\mathbf{Z}; \transitionParams) \in \R^{M \times C}$, known as inducing variables, where $M \ll N$.
-\todo{cite sparse gp papers}
-Instead of collapsing the inducing variables like \cite{titsiasVariational2009}, they can be treated variationally
-$p(\mathbf{u} \mid \mathbf{y}) \approx q(\mathbf{u}) = \mathcal{N}\left( \mathbf{u} \mid \mathbf{m}, \mathbf{V} \right)$, where $\mathbf{m}$ and $\mathbf{V}$ are variational parameters
-which need to be optimised \citep{hensmanGaussian2013}.
-The sparse variational GP (SVGP) predictive posterior is then given by,
-\begin{align}
-\label{eq-dual-svgp-predictive-posterior}
-  p(f(\mathbf{x}_{*}) \mid \mathbf{y})
-&\approx \mathcal{N} \left( f(\mathbf{x}_{*}) \mid \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{m}^{*},
-  k_{**} - \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
-  % \mathbf{k}_{*\inducingInput} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\inducingInput}^{T}
-  + \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}}  \mathbf{V}^{*}  \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
-  \right)
-\coloneqq q_{\inducingVariable}(f(\mathbf{x}_{*}))
-\end{align}
-
-\textbf{Deep learning}
-Given the data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
-the goal of (supervised) deep learning, is to train the weights $\transitionParams \in \R^{P}$ of an $L\text{-layer}$ NN
-$f : \inputDomain \rightarrow \outputDomain$ to minimize the (regularized) empirical risk,
-\begin{align} \label{eq-empirical-risk}
-  \transitionParams^{*} = \arg \min_{\transitionParams \in \R^{D}} \mathcal{L}(\dataset;\transitionParams) = \arg \min_{\transitionParams \in \R^{D}} \left(
-  \sum_{n=0}^{N-1} l(f(\mathbf{x}_{n} ; \transitionParams), \mathbf{y}_{n}) + R(\transitionParams)  \right).
-\end{align}
-In practice, it is common to use the mean squared error (MSE) loss
-$l(f(\mathbf{x}_{n} ; \transitionParams),\mathbf{y}_{n}) = \|f(\mathbf{x}_{n} ; \transitionParams) - \mathbf{y}_{n} \|^{2}_{2}$
-and to use the weight decay regularizer $R(\transitionParams)=\frac{1}{2}\gamma^{-2}\|\transitionParams\|^{2}_{2}$.
-However, the practioner is free to choose any loss and regularizer. \todo{I think?}
-% \textbf{Bayesian neural networks}
-% \textbf{Weight space to function space}
-From a Bayesian perspective, we can interpret the terms in \cref{eq-empirical-risk} as the log-prior and the i.i.d. log likelihood, i.e.,
-\begin{align} \label{eq-log-prior}
-  R(\transitionParams) &= \underbrace{\log p(\transitionParams)}_{\text{log prior}} = \log \mathcal{N}(\transitionParams \mid 0, \gamma^{2} \mathbf{I}) \\
-  l(f(\mathbf{x}_{n} ; \transitionParams), \mathbf{y}_{n}) &= \underbrace{\log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \transitionParams))}_{\text{log likelihood}}
-  = \log \mathcal{N} \left( \mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \transitionParams), \mathbf{I} \right) \label{eq-log-likelihood}
-\end{align}
-
-\textbf{NN to GP}
-Given this interpretation, we can represent the weight space prior from \cref{eq-log-prior}, in
-function space, by linearising the BNN around $\transitionParams^{*}$ and interpretting it as a GP.
-The GP prior is then given by,
-\begin{align} \label{eq-laplace-approx-function-space}
-  % \transitionFn_{\transitionParams_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \qquad
-  f(\cdot ;\transitionParams) \sim \mathcal{N} \left( \mu(\cdot), k(\cdot, \cdot') \right) \quad
-  % \mu_{\transitionParams_{i}^{*}}(\cdot)
-  \mu(\cdot)
-  = 0 \quad
-  % = f(\cdot ;\transitionParams^{*}) \quad
-  % K_{\transitionParams_{i}^{*}}(\cdot, \cdot')
-  k(\cdot, \cdot')
-  = \frac{1}{\gamma^{2}} \mathbf{J}(\cdot) \mathbf{J}(\cdot')^{T},
-\end{align}
-where the kernel is the neural tangent kernel (NTK) \citep{immerImprovingPredictionsBayesian2021},
-\todo{what mean function shoudl this use???}
-\todo{NTK times some factor??}
-with Jacobian given by $\mathbf{J}(\cdot) = \odv{\transitionFn(\cdot; \transitionParams)}{\transitionParams}_{\transitionParams=\transitionParams^{*}}$.
-% The kernel in \cref{eq-laplace-approx-function-space} is the neural tangent kernel (NTK)
-% $k(\mathbf{x}, \mathbf{x}') = \sigma_{0}^{2} J_{\transitionParams^{*}}(\mathbf{x}) J_{\transitionParams^{*}}(\mathbf{x}')^{T}$
-% \citep{immerImprovingPredictionsBayesian2021}
-% to formulate the GP posterior $p(f(\mathbf{X} ;\transitionParams_{0:i}) \mid \dataset_{0:i})$.
-Given this GP prior, we can use \cref{eq-gp-predictive-posterior} to obtain our GP posterior by conditioning on the data.
-% Given our GP prior, we can use the properties of multivariate normals to obtain our GP posterior by conditioning on the data.
-% where $\mathbf{A} = \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}}$
-In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
-Intuitively, we can view the optimisation in \cref{eq-empirical-risk} as learning our kernel.
-As a result, our NTK may be highly non stationary as it is dependent on the NN architecture, for example, the activation functions.
-It is worth noting that the NTK linearises the network around the optimised parameters $\transitionParams^{*}$,
-so the function space prior (and thus posterior) is only a locally linear approximation.
-
-We now have a method to obtain a GP posterior from a trained DNN.
-% In contrast to other approaches, our formulation has not restricted us to using a weight-space posterior obtained from the Laplace approximation.
-In contrast to other approaches, our formulation has not restricted us to using a weight-space posterior from a BNN.
-However, in practice, the GP posterior is not very useful as it requires inverting an $N\times N$ matrix which has complexity $\mathcal{O}(N^{3})$.
-The SVGP in \cref{eq-dual-svgp-predictive-posterior} offers a solution to this problem but it is not immediately clear how to set $\mathbf{m}$ and $\mathbf{V}$.
-In the next section, we show how we can directly obtain an SVGP posterior (i.e. set $\mathbf{m}$ and $\mathbf{V}$) directly from both
-1) a trained NN and 2) a BNN weight-space posterior.
-% $\mathbf{m}$ and $\mathbf{V}$
-% However, it is not obvious how we can use a SVGP to set $\mathbf{m}$ and $\mathbf{V}$
-
-% In contrast, to previous work, this approach did not require us Laplace approximation. we will not restrict our
-% It is worth noting that the NTK linearises the network around the optimised parameters $\transitionParams^{*}$,
-% so the function space prior (and thus posterior) is only a locally linear approximation.
-% In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
-% It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.
-
-\section{Methods}
-In the next section we show how we can obtain a SVGP directly from 1) a trained NN and 2) a BNN posterior.
-
-We follow \cite{csatoSparseOnlineGaussian2002} and express our GP posterior in the dual parameter space.
-However, we consider the variational formulation introduced by \cite{adamDualParameterizationSparse2021}, where the optimal variational parameters are given by,
-\begin{align} \label{eq-dual-params}
-\mathbf{m}^{*} = \mathbf{V}^{*}\bm\alpha^{*} \quad \mathbf{V}^{*} = [\mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} + \bm\beta^{*}]
-\end{align}
-Importantly, we can calculate the natural parameters $(\bm\alpha, \bm\beta)$ in closed form,
-\todo{paul needs to update \cref{eq-dual-svgp-params}}
-\begin{align} \label{eq-dual-svgp-params}
-\bm\alpha_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right] \\
-\bm\beta_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right].
-\end{align}
-This simplifies SVGP inference \citep{hensmanGaussian2013} as it no longer requires the variational parameters $(\mathbf{m}, \mathbf{V})$ to be optimised.
-
-% Importantly, \cite{changFantasizingDualGPs2022} show that in the dual space,
-% conditioning on new observations reduces to suming the dual variables from the previous time
-% step with an update, given by,
-% \todo{pick best way to show new data (using superscript new or just time indexing?)}
-% \begin{align} \label{eq-dual-update-svgp}
-% \bm\alpha_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right] \\
-% \bm\beta_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right]
-% \end{align}
-
-% We follow \cite{csatoSparseOnlineGaussian2002} and express our GP posterior in the dual parameter space,
-% % to write GP posterior $p(f(\mathbf{X} ;\transitionParams_{0:i}) \mid \dataset_{0:i})$ as,
-% \begin{align} \label{eq-gp-post}
-%   \mathbb{E}_{p(f(\mathbf{x}_{*}) \mid \mathbf{y}_{n})} \left[ f(\mathbf{x}_{*}) \right] &= \mu(\mathbf{x}_{*}) + \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
-%   \mathbb{V}_{p(f(\mathbf{x}_{*}) \mid \mathbf{y}_{n})} \left[ f(\mathbf{x}_{*}) \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \text{diag}(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
-% \end{align}
-% % \begin{align} \label{eq-laplace-approx-function-space}
-% %   \mathbb{E}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
-% %   \mathbb{V}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \diag(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
-% % \end{align}
-% where the dual parameters $(\bm\alpha_n, \bm\beta_n)$ are vectors of,
-% \begin{align} \label{eq-gp-dual-params}
-%   \bm\alpha_{n} \coloneqq \left\{ \mathbb{E}_{p(f(\mathbf{x}_{i}) \mid \mathbf{y}_{n})} \left[ \nabla_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \right\}_{i=1}^{N} \qquad
-%   \bm\beta_{n} \coloneqq \left\{ \mathbb{E}_{p(f(\mathbf{x}_{i}) \mid \mathbf{y}_{n})} \left[ \nabla^{2}_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \right\}_{i=1}^{N}
-% \end{align}
-% Importantly, this parameterisation
-
-% \textbf{dual-SVGP}
-% \begin{align} \label{eq-svgp-post}
-%   \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ f(\mathbf{x}_{*}) \right] &= \mu(\mathbf{x}_{*}) + \mathbf{k}_{\mathbf{z}*}^{T} \bm\alpha_{\mathbf{u}} \\
-%   \mathbb{V}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ f(\mathbf{x}_{*}) \right] &= k_{**} - \mathbf{k}_{\mathbf{z}*}^{T} \left[ \mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} - \left( \mathbf{K}_{\mathbf{z} \mathbf{z}} + \bm\beta_{\mathbf{u}} \right)^{-1} \right] \mathbf{k}_{\mathbf{z}*}
-% \end{align}
-% % \begin{align} \label{eq-laplace-approx-function-space}
-% %   \mathbb{E}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
-% %   \mathbb{V}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \diag(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
-% % \end{align}
-% where the dual parameters $(\bm\alpha_{\mathbf{u}}, \bm\beta_{\mathbf{u}})$ are vectors of,
-% \begin{align} \label{eq-svgp-dual-params}
-%   \bm\alpha_{\mathbf{u}} \coloneqq \mathbf{k}_{\mathbf{z}i} \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ \nabla_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \qquad
-%   \bm\beta_{\mathbf{u}} \coloneqq \mathbf{k}_{\mathbf{z}i} \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ \nabla^{2}_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \mathbf{k}_{\mathbf{z}i}^{T}
-% \end{align}
-
-% weight space posterior in \cref{eq-laplace-approx-weight-space} in
-% function space by linearising the BNN and interpreting it as a GP.
-% \begin{align} \label{eq-laplace-approx-function-space}
-%   \transitionFn_{\transitionParams_{i}}(\cdot) &\sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \quad
-%   \mu_{\transitionParams_{i}^{*}}(\cdot) &= \transitionFn_{\transitionParams^{*}_{i}}(\cdot) \quad
-%   K_{\transitionParams_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) \bm\Sigma_{\transitionParams^{*}_{i}} \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot')^{T}
-% \end{align}
-% where the Jacobian is given by $\mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}$.
-
-% \begin{align} \label{eq-laplace-approx-jacobian}
-% \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}
-% \end{align}
-
-% % Note that the posterior in \cref{eq-laplace-approx-weight-space} is in weight space.
-% We can represent the weight space posterior in \cref{eq-laplace-approx-weight-space} in
-% function space by linearising the BNN and interpreting it as a GP.
-% \begin{align} \label{eq-laplace-approx-function-space}
-%   \transitionFn_{\transitionParams_{i}^{*}}(\cdot) &\sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \quad
-%   \mu_{\transitionParams_{i}^{*}}(\cdot) &= \transitionFn_{\transitionParams^{*}_{i}}(\cdot) \quad
-%   K_{\transitionParams_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) \bm\Sigma_{\transitionParams^{*}_{i}} \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot')^{T}
-% \end{align}
-% where the Jacobian is given by $\mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}$.
-
-% \begin{align} \label{eq-laplace-approx-jacobian}
-% \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}
-% \end{align}
-
-\subsection{Fast Updates}
-Importantly, \cite{changFantasizingDualGPs2022} show that in the dual space,
-conditioning on new observations reduces to suming the dual variables from the previous time
-step with an update, given by,
-\todo{pick best way to show new data (using superscript new or just time indexing?)}
-\begin{align} \label{eq-dual-update-svgp}
-\dualParam{1}^{t+1} &\leftarrow \dualParam{1}^{t} +  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))} \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right] \\
-\dualParam{2}^{t+1} &\leftarrow \dualParam{2}^{t} +  \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))}  \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right]
-\end{align}
-Importantly, for a single new observation $((\state_{t}, \action_{t}), \state_{t+1})$ this update has
-complexity $\mathcal{O}(\numInducing^{2})$.
-This is a significant improvement to naive GP conditioning, which has complexity $\mathcal{O}((\numDataNew + \numDataOld)^{3})$
-and sparse GP conditioning, which has complexity $\mathcal{O}((\numDataNew + \numDataOld)\numInducing^{2})$.
-\todo{double check these complexities are right and cite them/show equaitons}
-It is worth highlighting that the complexity of \cite{changFantasizingDualGPs2022} update does not increase during an episode.
-
-\subsubsection{Model-based RL}
-
-\subsubsection{Efficiently Sampling Functions for Posterior Sampling}
-\cite{wilsonEfficiently2020}
-\cite{wilsonPathwise2021}
-
-% \begin{align} \label{eq-dual-update-svgp}
-%  \dualParam{1}^{\text{new}} &\leftarrow \dualParam{1}^{\text{old}} +
-%   \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}))}
-%  \left[ \log p(\state_{t+1}^{\text{new}} \mid \latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}) ) \right] \\
-%  \dualParam{2}^{\text{new}} &\leftarrow \dualParam{2}^{\text{old}} +
-%   \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}))}
-%  \left[ \log p(\state_t^{\horizon+1} \mid \latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}) ) \right] \\
-%  \dualParam{1}^{\horizon+1} &\leftarrow \dualParam{1}^{\horizon} +
-%   \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}
-%  \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right] \\
-%  \dualParam{2}^{\horizon+1} &\leftarrow \dualParam{2}^{\horizon} +
-%   \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}
-%  \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right]
-% \end{align}
-
-\begin{assumption} \label{assumption-ntk-linearisation}
-  Something about NTK being a linearisation around $\theta^{*}_{i}$ but each update moves away from $\theta^{*}_{i}$
-\end{assumption}
-
-\cite{rossellApproximateLaplaceApproximations2021}
+%\todo{what about regression/classification likelhoods}
+%This GP predictive posterior is computationally expensive as it requires inverting an $N\times N$ matrix.
+%
+%\textbf{Sparse Gaussian processes}
+%% The GP predictive posterior in \cref{eq-gp-predictive-posterior} is computationally expensive as it requires inverting an $N\times N$ matrix.
+%A practical and computationally appealing alternative is to augment the joint probability space with pseudo inputs $\mathbf{Z} \in \R^{M \times D}$
+%and corresponding outputs
+%$\mathbf{u} = f(\mathbf{Z}; \transitionParams) \in \R^{M \times C}$, known as inducing variables, where $M \ll N$.
+%\todo{cite sparse gp papers}
+%Instead of collapsing the inducing variables like \cite{titsiasVariational2009}, they can be treated variationally
+%$p(\mathbf{u} \mid \mathbf{y}) \approx q(\mathbf{u}) = \mathcal{N}\left( \mathbf{u} \mid \mathbf{m}, \mathbf{V} \right)$, where $\mathbf{m}$ and $\mathbf{V}$ are variational parameters
+%which need to be optimised \citep{hensmanGaussian2013}.
+%The sparse variational GP (SVGP) predictive posterior is then given by,
+%\begin{align}
+%\label{eq-dual-svgp-predictive-posterior}
+%  p(f(\mathbf{x}_{*}) \mid \mathbf{y})
+%&\approx \mathcal{N} \left( f(\mathbf{x}_{*}) \mid \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{m}^{*},
+%  k_{**} - \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
+%  % \mathbf{k}_{*\inducingInput} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\inducingInput}^{T}
+%  + \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}}  \mathbf{V}^{*}  \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
+%  \right)
+%\coloneqq q_{\inducingVariable}(f(\mathbf{x}_{*}))
+%\end{align}
+%
+%
+%\textbf{Deep learning}
+%Given the data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
+%the goal of (supervised) deep learning, is to train the weights $\transitionParams \in \R^{P}$ of an $L\text{-layer}$ NN
+%$f : \inputDomain \rightarrow \outputDomain$ to minimize the (regularized) empirical risk,
+%\begin{align} \label{eq-empirical-risk}
+%  \transitionParams^{*} = \arg \min_{\transitionParams \in \R^{D}} \mathcal{L}(\dataset;\transitionParams) = \arg \min_{\transitionParams \in \R^{D}} \left(
+%  \sum_{n=0}^{N-1} l(f(\mathbf{x}_{n} ; \transitionParams), \mathbf{y}_{n}) + R(\transitionParams)  \right).
+%\end{align}
+%In practice, it is common to use the mean squared error (MSE) loss
+%$l(f(\mathbf{x}_{n} ; \transitionParams),\mathbf{y}_{n}) = \|f(\mathbf{x}_{n} ; \transitionParams) - \mathbf{y}_{n} \|^{2}_{2}$
+%and to use the weight decay regularizer $R(\transitionParams)=\frac{1}{2}\gamma^{-2}\|\transitionParams\|^{2}_{2}$.
+%However, the practioner is free to choose any loss and regularizer. \todo{I think?}
+%% \textbf{Bayesian neural networks}
+%% \textbf{Weight space to function space}
+%From a Bayesian perspective, we can interpret the terms in \cref{eq-empirical-risk} as the log-prior and the i.i.d. log likelihood, i.e.,
+%\begin{align} \label{eq-log-prior}
+%  R(\transitionParams) &= \underbrace{\log p(\transitionParams)}_{\text{log prior}} = \log \mathcal{N}(\transitionParams \mid 0, \gamma^{2} \mathbf{I}) \\
+%  l(f(\mathbf{x}_{n} ; \transitionParams), \mathbf{y}_{n}) &= \underbrace{\log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \transitionParams))}_{\text{log likelihood}}
+%  = \log \mathcal{N} \left( \mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \transitionParams), \mathbf{I} \right) \label{eq-log-likelihood}
+%\end{align}
+%
+%\textbf{NN to GP}
+%Given this interpretation, we can represent the weight space prior from \cref{eq-log-prior}, in
+%function space, by linearising the BNN around $\transitionParams^{*}$ and interpretting it as a GP.
+%The GP prior is then given by,
+%\begin{align} \label{eq-laplace-approx-function-space}
+%  % \transitionFn_{\transitionParams_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \qquad
+%  f(\cdot ;\transitionParams) \sim \mathcal{N} \left( \mu(\cdot), k(\cdot, \cdot') \right) \quad
+%  % \mu_{\transitionParams_{i}^{*}}(\cdot)
+%  \mu(\cdot)
+%  = 0 \quad
+%  % = f(\cdot ;\transitionParams^{*}) \quad
+%  % K_{\transitionParams_{i}^{*}}(\cdot, \cdot')
+%  k(\cdot, \cdot')
+%  = \frac{1}{\gamma^{2}} \mathbf{J}(\cdot) \mathbf{J}(\cdot')^{T},
+%\end{align}
+%where the kernel is the neural tangent kernel (NTK) \citep{immerImprovingPredictionsBayesian2021},
+%\todo{what mean function shoudl this use???}
+%\todo{NTK times some factor??}
+%with Jacobian given by $\mathbf{J}(\cdot) = \odv{\transitionFn(\cdot; \transitionParams)}{\transitionParams}_{\transitionParams=\transitionParams^{*}}$.
+%% The kernel in \cref{eq-laplace-approx-function-space} is the neural tangent kernel (NTK)
+%% $k(\mathbf{x}, \mathbf{x}') = \sigma_{0}^{2} J_{\transitionParams^{*}}(\mathbf{x}) J_{\transitionParams^{*}}(\mathbf{x}')^{T}$
+%% \citep{immerImprovingPredictionsBayesian2021}
+%% to formulate the GP posterior $p(f(\mathbf{X} ;\transitionParams_{0:i}) \mid \dataset_{0:i})$.
+%Given this GP prior, we can use \cref{eq-gp-predictive-posterior} to obtain our GP posterior by conditioning on the data.
+%% Given our GP prior, we can use the properties of multivariate normals to obtain our GP posterior by conditioning on the data.
+%% where $\mathbf{A} = \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}}$
+%In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
+%Intuitively, we can view the optimisation in \cref{eq-empirical-risk} as learning our kernel.
+%As a result, our NTK may be highly non stationary as it is dependent on the NN architecture, for example, the activation functions.
+%It is worth noting that the NTK linearises the network around the optimised parameters $\transitionParams^{*}$,
+%so the function space prior (and thus posterior) is only a locally linear approximation.
+%
+%We now have a method to obtain a GP posterior from a trained DNN.
+%% In contrast to other approaches, our formulation has not restricted us to using a weight-space posterior obtained from the Laplace approximation.
+%In contrast to other approaches, our formulation has not restricted us to using a weight-space posterior from a BNN.
+%However, in practice, the GP posterior is not very useful as it requires inverting an $N\times N$ matrix which has complexity $\mathcal{O}(N^{3})$.
+%The SVGP in \cref{eq-dual-svgp-predictive-posterior} offers a solution to this problem but it is not immediately clear how to set $\mathbf{m}$ and $\mathbf{V}$.
+%In the next section, we show how we can directly obtain an SVGP posterior (i.e. set $\mathbf{m}$ and $\mathbf{V}$) directly from both
+%1) a trained NN and 2) a BNN weight-space posterior.
+%% $\mathbf{m}$ and $\mathbf{V}$
+%% However, it is not obvious how we can use a SVGP to set $\mathbf{m}$ and $\mathbf{V}$
+%
+%
+%
+%% In contrast, to previous work, this approach did not require us Laplace approximation. we will not restrict our
+%% It is worth noting that the NTK linearises the network around the optimised parameters $\transitionParams^{*}$,
+%% so the function space prior (and thus posterior) is only a locally linear approximation.
+%% In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
+%% It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.
+%
+%
+%\section{Methods}
+%In the next section we show how we can obtain a SVGP directly from 1) a trained NN and 2) a BNN posterior.
+%
+%We follow \cite{csatoSparseOnlineGaussian2002} and express our GP posterior in the dual parameter space.
+%However, we consider the variational formulation introduced by \cite{adamDualParameterizationSparse2021}, where the optimal variational parameters are given by,
+%\begin{align} \label{eq-dual-params}
+%\mathbf{m}^{*} = \mathbf{V}^{*}\bm\alpha^{*} \quad \mathbf{V}^{*} = [\mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} + \bm\beta^{*}]
+%\end{align}
+%Importantly, we can calculate the natural parameters $(\bm\alpha, \bm\beta)$ in closed form,
+%\todo{paul needs to update \cref{eq-dual-svgp-params}}
+%\begin{align} \label{eq-dual-svgp-params}
+%\bm\alpha_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right] \\
+%\bm\beta_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right].
+%\end{align}
+%This simplifies SVGP inference \citep{hensmanGaussian2013} as it no longer requires the variational parameters $(\mathbf{m}, \mathbf{V})$ to be optimised.
+%
+%% Importantly, \cite{changFantasizingDualGPs2022} show that in the dual space,
+%% conditioning on new observations reduces to suming the dual variables from the previous time
+%% step with an update, given by,
+%% \todo{pick best way to show new data (using superscript new or just time indexing?)}
+%% \begin{align} \label{eq-dual-update-svgp}
+%% \bm\alpha_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right] \\
+%% \bm\beta_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right]
+%% \end{align}
+%
+%% We follow \cite{csatoSparseOnlineGaussian2002} and express our GP posterior in the dual parameter space,
+%% % to write GP posterior $p(f(\mathbf{X} ;\transitionParams_{0:i}) \mid \dataset_{0:i})$ as,
+%% \begin{align} \label{eq-gp-post}
+%%   \mathbb{E}_{p(f(\mathbf{x}_{*}) \mid \mathbf{y}_{n})} \left[ f(\mathbf{x}_{*}) \right] &= \mu(\mathbf{x}_{*}) + \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
+%%   \mathbb{V}_{p(f(\mathbf{x}_{*}) \mid \mathbf{y}_{n})} \left[ f(\mathbf{x}_{*}) \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \text{diag}(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
+%% \end{align}
+%% % \begin{align} \label{eq-laplace-approx-function-space}
+%% %   \mathbb{E}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
+%% %   \mathbb{V}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \diag(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
+%% % \end{align}
+%% where the dual parameters $(\bm\alpha_n, \bm\beta_n)$ are vectors of,
+%% \begin{align} \label{eq-gp-dual-params}
+%%   \bm\alpha_{n} \coloneqq \left\{ \mathbb{E}_{p(f(\mathbf{x}_{i}) \mid \mathbf{y}_{n})} \left[ \nabla_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \right\}_{i=1}^{N} \qquad
+%%   \bm\beta_{n} \coloneqq \left\{ \mathbb{E}_{p(f(\mathbf{x}_{i}) \mid \mathbf{y}_{n})} \left[ \nabla^{2}_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \right\}_{i=1}^{N}
+%% \end{align}
+%% Importantly, this parameterisation
+%
+%% \textbf{dual-SVGP}
+%% \begin{align} \label{eq-svgp-post}
+%%   \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ f(\mathbf{x}_{*}) \right] &= \mu(\mathbf{x}_{*}) + \mathbf{k}_{\mathbf{z}*}^{T} \bm\alpha_{\mathbf{u}} \\
+%%   \mathbb{V}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ f(\mathbf{x}_{*}) \right] &= k_{**} - \mathbf{k}_{\mathbf{z}*}^{T} \left[ \mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} - \left( \mathbf{K}_{\mathbf{z} \mathbf{z}} + \bm\beta_{\mathbf{u}} \right)^{-1} \right] \mathbf{k}_{\mathbf{z}*}
+%% \end{align}
+%% % \begin{align} \label{eq-laplace-approx-function-space}
+%% %   \mathbb{E}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
+%% %   \mathbb{V}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \diag(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
+%% % \end{align}
+%% where the dual parameters $(\bm\alpha_{\mathbf{u}}, \bm\beta_{\mathbf{u}})$ are vectors of,
+%% \begin{align} \label{eq-svgp-dual-params}
+%%   \bm\alpha_{\mathbf{u}} \coloneqq \mathbf{k}_{\mathbf{z}i} \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ \nabla_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \qquad
+%%   \bm\beta_{\mathbf{u}} \coloneqq \mathbf{k}_{\mathbf{z}i} \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ \nabla^{2}_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \mathbf{k}_{\mathbf{z}i}^{T}
+%% \end{align}
+%
+%% weight space posterior in \cref{eq-laplace-approx-weight-space} in
+%% function space by linearising the BNN and interpreting it as a GP.
+%% \begin{align} \label{eq-laplace-approx-function-space}
+%%   \transitionFn_{\transitionParams_{i}}(\cdot) &\sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \quad
+%%   \mu_{\transitionParams_{i}^{*}}(\cdot) &= \transitionFn_{\transitionParams^{*}_{i}}(\cdot) \quad
+%%   K_{\transitionParams_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) \bm\Sigma_{\transitionParams^{*}_{i}} \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot')^{T}
+%% \end{align}
+%% where the Jacobian is given by $\mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}$.
+%
+%% \begin{align} \label{eq-laplace-approx-jacobian}
+%% \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}
+%% \end{align}
+%
+%
+%% % Note that the posterior in \cref{eq-laplace-approx-weight-space} is in weight space.
+%% We can represent the weight space posterior in \cref{eq-laplace-approx-weight-space} in
+%% function space by linearising the BNN and interpreting it as a GP.
+%% \begin{align} \label{eq-laplace-approx-function-space}
+%%   \transitionFn_{\transitionParams_{i}^{*}}(\cdot) &\sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \quad
+%%   \mu_{\transitionParams_{i}^{*}}(\cdot) &= \transitionFn_{\transitionParams^{*}_{i}}(\cdot) \quad
+%%   K_{\transitionParams_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) \bm\Sigma_{\transitionParams^{*}_{i}} \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot')^{T}
+%% \end{align}
+%% where the Jacobian is given by $\mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}$.
+%
+%% \begin{align} \label{eq-laplace-approx-jacobian}
+%% \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}
+%% \end{align}
+%
+%
+%\subsection{Fast Updates}
+%Importantly, \cite{changFantasizingDualGPs2022} show that in the dual space,
+%conditioning on new observations reduces to suming the dual variables from the previous time
+%step with an update, given by,
+%\todo{pick best way to show new data (using superscript new or just time indexing?)}
+%\begin{align} \label{eq-dual-update-svgp}
+%\dualParam{1}^{t+1} &\leftarrow \dualParam{1}^{t} +  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))} \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right] \\
+%\dualParam{2}^{t+1} &\leftarrow \dualParam{2}^{t} +  \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))}  \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right]
+%\end{align}
+%Importantly, for a single new observation $((\state_{t}, \action_{t}), \state_{t+1})$ this update has
+%complexity $\mathcal{O}(\numInducing^{2})$.
+%This is a significant improvement to naive GP conditioning, which has complexity $\mathcal{O}((\numDataNew + \numDataOld)^{3})$
+%and sparse GP conditioning, which has complexity $\mathcal{O}((\numDataNew + \numDataOld)\numInducing^{2})$.
+%\todo{double check these complexities are right and cite them/show equaitons}
+%It is worth highlighting that the complexity of \cite{changFantasizingDualGPs2022} update does not increase during an episode.
+%
+%\subsubsection{Model-based RL}
+%
+%\subsubsection{Efficiently Sampling Functions for Posterior Sampling}
+%\cite{wilsonEfficiently2020}
+%\cite{wilsonPathwise2021}
+%
+%% \begin{align} \label{eq-dual-update-svgp}
+%%  \dualParam{1}^{\text{new}} &\leftarrow \dualParam{1}^{\text{old}} +
+%%   \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}))}
+%%  \left[ \log p(\state_{t+1}^{\text{new}} \mid \latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}) ) \right] \\
+%%  \dualParam{2}^{\text{new}} &\leftarrow \dualParam{2}^{\text{old}} +
+%%   \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}))}
+%%  \left[ \log p(\state_t^{\horizon+1} \mid \latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}) ) \right] \\
+%%  \dualParam{1}^{\horizon+1} &\leftarrow \dualParam{1}^{\horizon} +
+%%   \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}
+%%  \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right] \\
+%%  \dualParam{2}^{\horizon+1} &\leftarrow \dualParam{2}^{\horizon} +
+%%   \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}
+%%  \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right]
+%% \end{align}
+%
+%
+%\begin{assumption} \label{assumption-ntk-linearisation}
+%  Something about NTK being a linearisation around $\theta^{*}_{i}$ but each update moves away from $\theta^{*}_{i}$
+%\end{assumption}
+%
+%\cite{rossellApproximateLaplaceApproximations2021}
 
@@
 
-\subsection{Updating the representation during continual learning}
-
 \begin{table}[t!] 
   \centering\scriptsize
-  \caption{CL Experiments  TODO} 
+  \caption{Metrics for supervised learning with image data} 
+	\label{tbl:imagesuper}
+	% Control table spacing
+	\renewcommand{\arraystretch}{1.}
+	\setlength{\tabcolsep}{2pt}
+	\setlength{\tblw}{0.14\textwidth}
+
+	% Custom error formatting
+	\newcommand{\val}[2]{%
+		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
+	}
+
+    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
+	\input{tables/img_super.tex}
+\end{table}
+\subsection{Updating the representation during continual learning}
+
+\begin{table}[t!] 
+  \centering\scriptsize
+  \caption{TODO: CL Experiments.
+$^*$ Methods relying only on weight regularization.
+\color{blue}{Results from \cite{rudner2022continual}.} \color{red}{Preliminary results need more runs or hyperparam tuning}}
 	\label{tbl:cl_table_1}

### 2023-05-10 paper/main.tex
starting to fill out background

@@
 
-\section{Background} \label{sec:background}
+\section{Methods} \label{sec:methods}
 
@@
 
-\begin{itemize}
-  \item Show prediction performance in classification: UCI classification results, compare to BNN predictive paper
-  \item Fast adapatation in model-based RL: results for cartpole
-  \item Is linearising NN mean and using fast updates during episode better than keeping non-linearised mean and not updating?
-  \item Possible ablations
-  \begin{itemize}
-    \item How does number of inducing points affect performance?
-  \end{itemize}
-  \item How good is the assumption that we can linearise BNN to get NTK?
-\end{itemize}
-
-Environments
-\begin{itemize}
-  \item Compare updated posterior with non updated posterior
-  \item Need to show update is fast enough for practical use?
-  \begin{itemize}
-    \item How frequently can we do the posterior update? Every time step or every $K$ steps?
-    \item Update depends on number of inducing points?
-    \item What experiments can we show for this? Wall clock time vs planning horizon with different numbers of inducing points?
-  \end{itemize}
-  \item Is linearising NN mean and using fast updates during episode better than keeping non-linearised mean and not updating?
-  \item How does number of inducing points affect performance?
-  \begin{itemize}
-    \item More inducing points means better approximation but larger computational complexity.
-  \end{itemize}
-  \item How good is the assumption that we can linearise BNN to get NTK?
-  \begin{itemize}
-    \item Does model's performance get worse during an episode because linearisation becomes more wrong?
-    \item SVGP does't have this issue so compare to SVGP in cartpole?
-  \end{itemize}
-  \item What length planning horizon to use?
-  \begin{itemize}
-    \item Too small (e.g. $\Horizon=0$) would mean no exploration?
-    \item Can $\Horizon$ be too large?
-  \end{itemize}
-  \begin{itemize}
-  \item Compare for different strategies of making decisions under dynamic model's uncertainty:
-    \begin{itemize}
-      \item \textbf{Greedy exploitation} \(\pi_{\text{greedy}}\)
-      \item \textbf{Hallucinated-UCRL} \(\pi_{\text{HUCRL}}\)
-      \item \textbf{Thompson sampling} \(\pi_{\text{TS}}\)
-    \end{itemize}
-  \end{itemize}
-  \item Compare impact of stationary vs non-stationary priors
-  \begin{itemize}
-    \item First do this with GP
-    \item Then try to do with Laplace BNN
-  \end{itemize}
-  \item Compare impact of function vs weight space
-\end{itemize}
-
 \section{Discussion and Conclusion}
@@
 %\section*{Broader Impact}
-
-\begin{ack}
-ASK A ABOUT THIS SECTION:
-Aidan Scannell is funded by the Finnish Center for Artificial Intelligence.
-\end{ack}
 

### 2023-05-10 paper/main.tex
starting to fill out background

@@
 \textbf{Dual GP}
+
+The dual parameterization states that we can decompose the optimal sparse Gaussian process posterior as follows:
 \begin{align}
    \myexpect_{q_{\vu}(f)}[f_i] &= \vkzs^{\T} \valpha_{\vu} , \\
-   %\textrm{Var}_{q_{\vu}(f)}[f_i]  &= \kappa_{ii} - \vkzs^\top \sqr{\MKzz^{-1} - \rnd{ \MKzz + \vbeta_{\vu} }^{-1} }   \vkzs, \nonumber
-\end{align}
-now the dual parameters consist of an $m$-length vector $\valpha_\vu$ and $m\times m$-size matrix $\vbeta_\vu$, defined as
+   \textrm{Var}_{q_{\vu}(f)}[f_i]  &= \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - \MKzz + \vbeta_{\vu} ]^{-1} \vkzs.
+\end{align}
+The dual parameters consist of an $m$-length vector $\valpha_\vu$ and $m\times m$-size matrix $\vbeta_\vu$, defined as
 \begin{equation} 
@@
 \end{equation}
-where $\tilde{\lambda}_i = \alpha_i - \myexpect_{q_{\vu}(f)}[f_i] \beta_i$ is a different form of the first dual parameter, the gradient with respect to the first expectation parameter of $q_{\vu}(f)$ proposed in \cite{khan2017conjugate,chang2020fast}, with $(\hat{\alpha}_i, \hat{\beta}_i)$ defined as follows,
+where $\tilde{\lambda}_i = \alpha_i - \myexpect_{q_{\vu}(f)}[f_i] \beta_i$ with $(\hat{\alpha}_i, \hat{\beta}_i)$ defined as follows,
 \begin{equation}

### 2023-05-10 paper/main.tex
starting to fill out background

@@
 
-\textbf{Dual GP}
-
-The dual parameterization states that we can decompose the optimal sparse Gaussian process posterior as follows:
+\textbf{Dual GP} Sparse Gaussian processes \citep{hensman2013gaussian} are a principled way to scale Gaussian processes to large datasets by changing the complexity from $O(n^3)$ where n is number of data points to $O(m^3)$ where $m \ll n$.
+The key to the complexity saving is to use a sparse distribution
+
+dual parameterization states that we can decompose the optimal sparse Gaussian process posterior as follows:
 \begin{align}
    \myexpect_{q_{\vu}(f)}[f_i] &= \vkzs^{\T} \valpha_{\vu} , \\
-   \textrm{Var}_{q_{\vu}(f)}[f_i]  &= \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - \MKzz + \vbeta_{\vu} ]^{-1} \vkzs.
+   \textrm{Var}_{q_{\vu}(f)}[f_i]  &= \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \vbeta_{\vu})^{-1} ]\vkzs.
 \end{align}
@@
 \begin{split}
-   \vlambda & = [ \MKzz + \vbeta_{\vu}]\valpha_{\vu}  = \sum_{i \in \mathcal{D}_{\textrm{old}} \cup \mathcal{D}_{\textrm{new}}}  \vkzi \, \hat{\lambda}_{i}, \\
+   \vlambda & = [ \MKzz + \vbeta_{\vu}]\valpha_{\vu}  = \sum_{i \in \mathcal{D}_{\textrm{old}} \cup \mathcal{D}_{\textrm{new}}}  \vkzi \, \tilde{\lambda}_{i}, \\
    \vbeta_{\vu} &= \sum_{i \in \mathcal{D}_{\textrm{old}} \cup \mathcal{D}_{\textrm{new}}} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,
@@
 \begin{aligned}
-   \hat{\alpha}_i &= \myexpect_{q_{\vu}(f_i)} [\nabla_{f_i}\log p(y_i \mid f_i)],\\
-   \hat{\beta}_i &= \myexpect_{q_{\vu}(f_i)} [ -\nabla^2_{f_i}\log p(y_i \mid f_i)],
+   \alpha_i &= \myexpect_{q_{\vu}(f_i)} [\nabla_{f_i}\log p(y_i \mid f_i)],\\
+   \beta_i &= \myexpect_{q_{\vu}(f_i)} [ -\nabla^2_{f_i}\log p(y_i \mid f_i)],
 \end{aligned} \label{eq:svgp_dual}
 \end{equation}
+
+The key quantities we need to build our sparse GP are $(\alpha_i, \beta_i)$ and a kernel function $\kappa$
+
+\textbf{Neural network to sparse GP}
+
+\textbf{Continual learning}
+
+\textbf{Reinforcement learning}
 

### 2023-05-10 paper/main.tex
minor

--- 2023-05-10 paper/main.tex
@@
 \newcommand{\pPolicy}{\ensuremath{\pi_{\policyParams}}}
-
-% Packages for bold math
-\usepackage{bm}
-\newcommand{\mathbold}[1]{\bm{#1}}
-\newcommand{\mbf}[1]{\mathbf{#1}}
-
-% Math Macros
-\newcommand{\MC}{\mbf{C}}
-\newcommand{\MZ}{\mbf{Z}}
-\newcommand{\MV}{\mbf{V}}
-\newcommand{\MX}{\mbf{X}}
-\newcommand{\MA}{\mbf{A}}
-\newcommand{\MK}{\mbf{K}}
-\newcommand{\MI}{\mbf{I}}
-\newcommand{\MH}{\mbf{H}}
-\newcommand{\T}{\top}
-\newcommand{\vzeros}{\mbf{0}}
-\newcommand{\vtheta}[0]{\mathbold{\theta}}
-\newcommand{\valpha}[0]{\mathbold{\alpha}}
-\newcommand{\vkappa}[0]{\mathbold{\kappa}}
-\newcommand{\vbeta}[0]{\mathbold{\beta}}
-\newcommand{\vlambda}[0]{\mathbold{\lambda}}
-
-\newcommand{\vm}{\mbf{m}}
-%\newcommand{\vz}{\mbf{z}}
-%\newcommand{\vf}{\mbf{f}}
-\newcommand{\vu}{\mbf{u}}
-\newcommand{\vx}{\mbf{x}}
-\newcommand{\vy}{\mbf{y}}
-
-\newcommand{\GP}{\mathcal{GP}}
-\newcommand{\KL}[2]{\mathrm{D}_\textrm{KL} \dbar*{#1}{#2}}
-\newcommand{\MKzz}{\mbf{K}_{\mbf{z}\mbf{z}}}
-\newcommand{\MKxx}{\mbf{K}_{\mbf{x}\mbf{x}}}
-\newcommand{\MKzx}{\mbf{K}_{\mbf{z}\mbf{x}}}
-\newcommand{\MKxz}{\mbf{K}_{\mbf{x}\mbf{z}}}
-\newcommand{\vkzi}{\mbf{k}_{\mbf{z}i}}
-\newcommand{\vkzs}{\mbf{k}_{\mbf{z}i}}
-\newcommand{\vk}{\mbf{k}}
-\newcommand{\MLambda}[0]{\mathbold{\Lambda}}
-\definecolor{matplotlib-blue}{HTML}{1f77b4}
-\newcommand{\N}{\mathrm{N}}
-\newcommand{\myexpect}{\mathbb{E}}
 
@@
 
-\section{Methods} \label{sec:methods}
-
-\textbf{Neural Network in weight space}
-
-\textbf{Laplace approximation}
-
-\textbf{Dual GP}
-
-The dual parameterization states that we can decompose the optimal sparse Gaussian process posterior as follows:
-\begin{align}
-   \myexpect_{q_{\vu}(f)}[f_i] &= \vkzs^{\T} \valpha_{\vu} , \\
-   \textrm{Var}_{q_{\vu}(f)}[f_i]  &= \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - \MKzz + \vbeta_{\vu} ]^{-1} \vkzs.
-\end{align}
-The dual parameters consist of an $m$-length vector $\valpha_\vu$ and $m\times m$-size matrix $\vbeta_\vu$, defined as
-\begin{equation} 
-\begin{split}
-   \vlambda & = [ \MKzz + \vbeta_{\vu}]\valpha_{\vu}  = \sum_{i \in \mathcal{D}_{\textrm{old}} \cup \mathcal{D}_{\textrm{new}}}  \vkzi \, \hat{\lambda}_{i}, \\
-   \vbeta_{\vu} &= \sum_{i \in \mathcal{D}_{\textrm{old}} \cup \mathcal{D}_{\textrm{new}}} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,
-\label{eq:dual_sparse}
-\end{split}
-\end{equation}
-where $\tilde{\lambda}_i = \alpha_i - \myexpect_{q_{\vu}(f)}[f_i] \beta_i$ with $(\hat{\alpha}_i, \hat{\beta}_i)$ defined as follows,
-\begin{equation}
-\begin{aligned}
-   \hat{\alpha}_i &= \myexpect_{q_{\vu}(f_i)} [\nabla_{f_i}\log p(y_i \mid f_i)],\\
-   \hat{\beta}_i &= \myexpect_{q_{\vu}(f_i)} [ -\nabla^2_{f_i}\log p(y_i \mid f_i)],
-\end{aligned} \label{eq:svgp_dual}
-\end{equation}
-
+\section{Background} \label{sec:background}
+Sequential decision making requires uncertainty estimates for effective exploration.
+
+In this section, we recap how can obtain a GP posterior from a trained deep neural network (DNN).
 % We start by obtaining a posterior over the weights of a trained neural network via the Laplace approximation.
@@
 % as an $L\text{-layer}$ NN with weights $\transitionParams$.
-
-%A Gaussian process (GP) is a distribution over real-valued functions $f(\cdot): \mathcal{X} \rightarrow \R$ defined over $\mathcal{X}$.
-%Formally, a GP is defined as,
-%\begin{align}
-%\label{eq-gp-prior}
-%  f(\cdot) \sim \mathcal{N}\left( \mu(\cdot), k(\cdot,\cdot') \right) \quad
-%  \mu(\cdot): \mathcal{X} \rightarrow \R \quad
-%  k(\cdot,\cdot'): \mathcal{X} \times \mathcal{X} \rightarrow \R
-%\end{align}
-%where $\mu(\cdot)$ denotes a mean function and $k(\cdot,\cdot')$ a positive definite covariance function, also known as a kernel.
-%Given a data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
-%we can obtain the GP posterior via multivariate normal conditioning,
-%\begin{align}
-%\label{eq-gp-predictive-posterior}
-%  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
-%  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
-%  \left( f(\mathbf{x}_{*}) \mid \mu(\mathbf{x}_{*}) + \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} (\mathbf{y} - \bm\mu_{\mathbf{X}})),
-%  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
-%\end{align}
-%% Our GP posterior is then given by,
-%\todo{add mean func to GP posterior if we're using one}
-%\begin{align}
-%\label{eq-gp-predictive-posterior}
-%  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
-%  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
-%  \left( f(\mathbf{x}_{*}) \mid \mu(\mathbf{x}_{*}) + \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} \mu_{\mathbf{x}},
-%  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} + \bm\Lambda(\mathbf{y} ; \mathbf{f})^{-1} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
-%\end{align}
-%where $\bm\Lambda(\mathbf{y} ; \mathbf{f}) = \nabla^{2}_{\mathbf{f} \mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$ can be viewed as per-input noise.
+\textbf{Gaussian processes}
+A Gaussian process (GP) is a distribution over real-valued functions $f(\cdot): \mathcal{X} \rightarrow \R$ defined over $\mathcal{X}$.
+Formally, a GP is defined as,
+\begin{align}
+\label{eq-gp-prior}
+  f(\cdot) \sim \mathcal{N}\left( \mu(\cdot), k(\cdot,\cdot') \right) \quad
+  \mu(\cdot): \mathcal{X} \rightarrow \R \quad
+  k(\cdot,\cdot'): \mathcal{X} \times \mathcal{X} \rightarrow \R
+\end{align}
+where $\mu(\cdot)$ denotes a mean function and $k(\cdot,\cdot')$ a positive definite covariance function, also known as a kernel.
+Given a data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
+we can obtain the GP posterior via multivariate normal conditioning,
+\begin{align}
+\label{eq-gp-predictive-posterior}
+  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
+  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
+  \left( f(\mathbf{x}_{*}) \mid \mu(\mathbf{x}_{*}) + \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} (\mathbf{y} - \bm\mu_{\mathbf{X}})),
+  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
+\end{align}
+% Our GP posterior is then given by,
+\todo{add mean func to GP posterior if we're using one}
+\begin{align}
+\label{eq-gp-predictive-posterior}
+  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
+  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
+  \left( f(\mathbf{x}_{*}) \mid \mu(\mathbf{x}_{*}) + \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} \mu_{\mathbf{x}},
+  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} + \bm\Lambda(\mathbf{y} ; \mathbf{f})^{-1} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
+\end{align}
+where $\bm\Lambda(\mathbf{y} ; \mathbf{f}) = \nabla^{2}_{\mathbf{f} \mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$ can be viewed as per-input noise.
 \todo{I'm unsure about this per input noise bit.
 Check with paul.}
-%\todo{what about regression/classification likelhoods}
-%This GP predictive posterior is computationally expensive as it requires inverting an $N\times N$ matrix.
-%
-%\textbf{Sparse Gaussian processes}
-%% The GP predictive posterior in \cref{eq-gp-predictive-posterior} is computationally expensive as it requires inverting an $N\times N$ matrix.
-%A practical and computationally appealing alternative is to augment the joint probability space with pseudo inputs $\mathbf{Z} \in \R^{M \times D}$
-%and corresponding outputs
-%$\mathbf{u} = f(\mathbf{Z}; \transitionParams) \in \R^{M \times C}$, known as inducing variables, where $M \ll N$.
-%\todo{cite sparse gp papers}
-%Instead of collapsing the inducing variables like \cite{titsiasVariational2009}, they can be treated variationally
-%$p(\mathbf{u} \mid \mathbf{y}) \approx q(\mathbf{u}) = \mathcal{N}\left( \mathbf{u} \mid \mathbf{m}, \mathbf{V} \right)$, where $\mathbf{m}$ and $\mathbf{V}$ are variational parameters
-%which need to be optimised \citep{hensmanGaussian2013}.
-%The sparse variational GP (SVGP) predictive posterior is then given by,
-%\begin{align}
-%\label{eq-dual-svgp-predictive-posterior}
-%  p(f(\mathbf{x}_{*}) \mid \mathbf{y})
-%&\approx \mathcal{N} \left( f(\mathbf{x}_{*}) \mid \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{m}^{*},
-%  k_{**} - \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
-%  % \mathbf{k}_{*\inducingInput} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\inducingInput}^{T}
-%  + \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}}  \mathbf{V}^{*}  \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
-%  \right)
-%\coloneqq q_{\inducingVariable}(f(\mathbf{x}_{*}))
-%\end{align}
-%
-%
-%\textbf{Deep learning}
-%Given the data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
-%the goal of (supervised) deep learning, is to train the weights $\transitionParams \in \R^{P}$ of an $L\text{-layer}$ NN
-%$f : \inputDomain \rightarrow \outputDomain$ to minimize the (regularized) empirical risk,
-%\begin{align} \label{eq-empirical-risk}
-%  \transitionParams^{*} = \arg \min_{\transitionParams \in \R^{D}} \mathcal{L}(\dataset;\transitionParams) = \arg \min_{\transitionParams \in \R^{D}} \left(
-%  \sum_{n=0}^{N-1} l(f(\mathbf{x}_{n} ; \transitionParams), \mathbf{y}_{n}) + R(\transitionParams)  \right).
-%\end{align}
-%In practice, it is common to use the mean squared error (MSE) loss
-%$l(f(\mathbf{x}_{n} ; \transitionParams),\mathbf{y}_{n}) = \|f(\mathbf{x}_{n} ; \transitionParams) - \mathbf{y}_{n} \|^{2}_{2}$
-%and to use the weight decay regularizer $R(\transitionParams)=\frac{1}{2}\gamma^{-2}\|\transitionParams\|^{2}_{2}$.
-%However, the practioner is free to choose any loss and regularizer. \todo{I think?}
-%% \textbf{Bayesian neural networks}
-%% \textbf{Weight space to function space}
-%From a Bayesian perspective, we can interpret the terms in \cref{eq-empirical-risk} as the log-prior and the i.i.d. log likelihood, i.e.,
-%\begin{align} \label{eq-log-prior}
-%  R(\transitionParams) &= \underbrace{\log p(\transitionParams)}_{\text{log prior}} = \log \mathcal{N}(\transitionParams \mid 0, \gamma^{2} \mathbf{I}) \\
-%  l(f(\mathbf{x}_{n} ; \transitionParams), \mathbf{y}_{n}) &= \underbrace{\log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \transitionParams))}_{\text{log likelihood}}
-%  = \log \mathcal{N} \left( \mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \transitionParams), \mathbf{I} \right) \label{eq-log-likelihood}
-%\end{align}
-%
-%\textbf{NN to GP}
-%Given this interpretation, we can represent the weight space prior from \cref{eq-log-prior}, in
-%function space, by linearising the BNN around $\transitionParams^{*}$ and interpretting it as a GP.
-%The GP prior is then given by,
-%\begin{align} \label{eq-laplace-approx-function-space}
-%  % \transitionFn_{\transitionParams_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \qquad
-%  f(\cdot ;\transitionParams) \sim \mathcal{N} \left( \mu(\cdot), k(\cdot, \cdot') \right) \quad
-%  % \mu_{\transitionParams_{i}^{*}}(\cdot)
-%  \mu(\cdot)
-%  = 0 \quad
-%  % = f(\cdot ;\transitionParams^{*}) \quad
-%  % K_{\transitionParams_{i}^{*}}(\cdot, \cdot')
-%  k(\cdot, \cdot')
-%  = \frac{1}{\gamma^{2}} \mathbf{J}(\cdot) \mathbf{J}(\cdot')^{T},
-%\end{align}
-%where the kernel is the neural tangent kernel (NTK) \citep{immerImprovingPredictionsBayesian2021},
-%\todo{what mean function shoudl this use???}
-%\todo{NTK times some factor??}
-%with Jacobian given by $\mathbf{J}(\cdot) = \odv{\transitionFn(\cdot; \transitionParams)}{\transitionParams}_{\transitionParams=\transitionParams^{*}}$.
-%% The kernel in \cref{eq-laplace-approx-function-space} is the neural tangent kernel (NTK)
-%% $k(\mathbf{x}, \mathbf{x}') = \sigma_{0}^{2} J_{\transitionParams^{*}}(\mathbf{x}) J_{\transitionParams^{*}}(\mathbf{x}')^{T}$
-%% \citep{immerImprovingPredictionsBayesian2021}
-%% to formulate the GP posterior $p(f(\mathbf{X} ;\transitionParams_{0:i}) \mid \dataset_{0:i})$.
-%Given this GP prior, we can use \cref{eq-gp-predictive-posterior} to obtain our GP posterior by conditioning on the data.
-%% Given our GP prior, we can use the properties of multivariate normals to obtain our GP posterior by conditioning on the data.
-%% where $\mathbf{A} = \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}}$
-%In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
-%Intuitively, we can view the optimisation in \cref{eq-empirical-risk} as learning our kernel.
-%As a result, our NTK may be highly non stationary as it is dependent on the NN architecture, for example, the activation functions.
-%It is worth noting that the NTK linearises the network around the optimised parameters $\transitionParams^{*}$,
-%so the function space prior (and thus posterior) is only a locally linear approximation.
-%
-%We now have a method to obtain a GP posterior from a trained DNN.
-%% In contrast to other approaches, our formulation has not restricted us to using a weight-space posterior obtained from the Laplace approximation.
-%In contrast to other approaches, our formulation has not restricted us to using a weight-space posterior from a BNN.
-%However, in practice, the GP posterior is not very useful as it requires inverting an $N\times N$ matrix which has complexity $\mathcal{O}(N^{3})$.
-%The SVGP in \cref{eq-dual-svgp-predictive-posterior} offers a solution to this problem but it is not immediately clear how to set $\mathbf{m}$ and $\mathbf{V}$.
-%In the next section, we show how we can directly obtain an SVGP posterior (i.e. set $\mathbf{m}$ and $\mathbf{V}$) directly from both
-%1) a trained NN and 2) a BNN weight-space posterior.
-%% $\mathbf{m}$ and $\mathbf{V}$
-%% However, it is not obvious how we can use a SVGP to set $\mathbf{m}$ and $\mathbf{V}$
-%
-%
-%
-%% In contrast, to previous work, this approach did not require us Laplace approximation. we will not restrict our
-%% It is worth noting that the NTK linearises the network around the optimised parameters $\transitionParams^{*}$,
-%% so the function space prior (and thus posterior) is only a locally linear approximation.
-%% In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
-%% It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.
-%
-%
-%\section{Methods}
-%In the next section we show how we can obtain a SVGP directly from 1) a trained NN and 2) a BNN posterior.
-%
-%We follow \cite{csatoSparseOnlineGaussian2002} and express our GP posterior in the dual parameter space.
-%However, we consider the variational formulation introduced by \cite{adamDualParameterizationSparse2021}, where the optimal variational parameters are given by,
-%\begin{align} \label{eq-dual-params}
-%\mathbf{m}^{*} = \mathbf{V}^{*}\bm\alpha^{*} \quad \mathbf{V}^{*} = [\mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} + \bm\beta^{*}]
-%\end{align}
-%Importantly, we can calculate the natural parameters $(\bm\alpha, \bm\beta)$ in closed form,
-%\todo{paul needs to update \cref{eq-dual-svgp-params}}
-%\begin{align} \label{eq-dual-svgp-params}
-%\bm\alpha_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right] \\
-%\bm\beta_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right].
-%\end{align}
-%This simplifies SVGP inference \citep{hensmanGaussian2013} as it no longer requires the variational parameters $(\mathbf{m}, \mathbf{V})$ to be optimised.
-%
-%% Importantly, \cite{changFantasizingDualGPs2022} show that in the dual space,
-%% conditioning on new observations reduces to suming the dual variables from the previous time
-%% step with an update, given by,
-%% \todo{pick best way to show new data (using superscript new or just time indexing?)}
-%% \begin{align} \label{eq-dual-update-svgp}
-%% \bm\alpha_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right] \\
-%% \bm\beta_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right]
-%% \end{align}
-%
-%% We follow \cite{csatoSparseOnlineGaussian2002} and express our GP posterior in the dual parameter space,
-%% % to write GP posterior $p(f(\mathbf{X} ;\transitionParams_{0:i}) \mid \dataset_{0:i})$ as,
-%% \begin{align} \label{eq-gp-post}
-%%   \mathbb{E}_{p(f(\mathbf{x}_{*}) \mid \mathbf{y}_{n})} \left[ f(\mathbf{x}_{*}) \right] &= \mu(\mathbf{x}_{*}) + \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
-%%   \mathbb{V}_{p(f(\mathbf{x}_{*}) \mid \mathbf{y}_{n})} \left[ f(\mathbf{x}_{*}) \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \text{diag}(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
-%% \end{align}
-%% % \begin{align} \label{eq-laplace-approx-function-space}
-%% %   \mathbb{E}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
-%% %   \mathbb{V}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \diag(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
-%% % \end{align}
-%% where the dual parameters $(\bm\alpha_n, \bm\beta_n)$ are vectors of,
-%% \begin{align} \label{eq-gp-dual-params}
-%%   \bm\alpha_{n} \coloneqq \left\{ \mathbb{E}_{p(f(\mathbf{x}_{i}) \mid \mathbf{y}_{n})} \left[ \nabla_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \right\}_{i=1}^{N} \qquad
-%%   \bm\beta_{n} \coloneqq \left\{ \mathbb{E}_{p(f(\mathbf{x}_{i}) \mid \mathbf{y}_{n})} \left[ \nabla^{2}_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \right\}_{i=1}^{N}
-%% \end{align}
-%% Importantly, this parameterisation
-%
-%% \textbf{dual-SVGP}
-%% \begin{align} \label{eq-svgp-post}
-%%   \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ f(\mathbf{x}_{*}) \right] &= \mu(\mathbf{x}_{*}) + \mathbf{k}_{\mathbf{z}*}^{T} \bm\alpha_{\mathbf{u}} \\
-%%   \mathbb{V}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ f(\mathbf{x}_{*}) \right] &= k_{**} - \mathbf{k}_{\mathbf{z}*}^{T} \left[ \mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} - \left( \mathbf{K}_{\mathbf{z} \mathbf{z}} + \bm\beta_{\mathbf{u}} \right)^{-1} \right] \mathbf{k}_{\mathbf{z}*}
-%% \end{align}
-%% % \begin{align} \label{eq-laplace-approx-function-space}
-%% %   \mathbb{E}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
-%% %   \mathbb{V}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \diag(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
-%% % \end{align}
-%% where the dual parameters $(\bm\alpha_{\mathbf{u}}, \bm\beta_{\mathbf{u}})$ are vectors of,
-%% \begin{align} \label{eq-svgp-dual-params}
-%%   \bm\alpha_{\mathbf{u}} \coloneqq \mathbf{k}_{\mathbf{z}i} \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ \nabla_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \qquad
-%%   \bm\beta_{\mathbf{u}} \coloneqq \mathbf{k}_{\mathbf{z}i} \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ \nabla^{2}_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \mathbf{k}_{\mathbf{z}i}^{T}
-%% \end{align}
-%
-%% weight space posterior in \cref{eq-laplace-approx-weight-space} in
-%% function space by linearising the BNN and interpreting it as a GP.
-%% \begin{align} \label{eq-laplace-approx-function-space}
-%%   \transitionFn_{\transitionParams_{i}}(\cdot) &\sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \quad
-%%   \mu_{\transitionParams_{i}^{*}}(\cdot) &= \transitionFn_{\transitionParams^{*}_{i}}(\cdot) \quad
-%%   K_{\transitionParams_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) \bm\Sigma_{\transitionParams^{*}_{i}} \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot')^{T}
-%% \end{align}
-%% where the Jacobian is given by $\mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}$.
-%
-%% \begin{align} \label{eq-laplace-approx-jacobian}
-%% \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}
-%% \end{align}
-%
-%
-%% % Note that the posterior in \cref{eq-laplace-approx-weight-space} is in weight space.
-%% We can represent the weight space posterior in \cref{eq-laplace-approx-weight-space} in
-%% function space by linearising the BNN and interpreting it as a GP.
-%% \begin{align} \label{eq-laplace-approx-function-space}
-%%   \transitionFn_{\transitionParams_{i}^{*}}(\cdot) &\sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \quad
-%%   \mu_{\transitionParams_{i}^{*}}(\cdot) &= \transitionFn_{\transitionParams^{*}_{i}}(\cdot) \quad
-%%   K_{\transitionParams_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) \bm\Sigma_{\transitionParams^{*}_{i}} \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot')^{T}
-%% \end{align}
-%% where the Jacobian is given by $\mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}$.
-%
-%% \begin{align} \label{eq-laplace-approx-jacobian}
-%% \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}
-%% \end{align}
-%
-%
-%\subsection{Fast Updates}
-%Importantly, \cite{changFantasizingDualGPs2022} show that in the dual space,
-%conditioning on new observations reduces to suming the dual variables from the previous time
-%step with an update, given by,
-%\todo{pick best way to show new data (using superscript new or just time indexing?)}
-%\begin{align} \label{eq-dual-update-svgp}
-%\dualParam{1}^{t+1} &\leftarrow \dualParam{1}^{t} +  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))} \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right] \\
-%\dualParam{2}^{t+1} &\leftarrow \dualParam{2}^{t} +  \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))}  \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right]
-%\end{align}
-%Importantly, for a single new observation $((\state_{t}, \action_{t}), \state_{t+1})$ this update has
-%complexity $\mathcal{O}(\numInducing^{2})$.
-%This is a significant improvement to naive GP conditioning, which has complexity $\mathcal{O}((\numDataNew + \numDataOld)^{3})$
-%and sparse GP conditioning, which has complexity $\mathcal{O}((\numDataNew + \numDataOld)\numInducing^{2})$.
-%\todo{double check these complexities are right and cite them/show equaitons}
-%It is worth highlighting that the complexity of \cite{changFantasizingDualGPs2022} update does not increase during an episode.
-%
-%\subsubsection{Model-based RL}
-%
-%\subsubsection{Efficiently Sampling Functions for Posterior Sampling}
-%\cite{wilsonEfficiently2020}
-%\cite{wilsonPathwise2021}
-%
-%% \begin{align} \label{eq-dual-update-svgp}
-%%  \dualParam{1}^{\text{new}} &\leftarrow \dualParam{1}^{\text{old}} +
-%%   \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}))}
-%%  \left[ \log p(\state_{t+1}^{\text{new}} \mid \latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}) ) \right] \\
-%%  \dualParam{2}^{\text{new}} &\leftarrow \dualParam{2}^{\text{old}} +
-%%   \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}))}
-%%  \left[ \log p(\state_t^{\horizon+1} \mid \latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}) ) \right] \\
-%%  \dualParam{1}^{\horizon+1} &\leftarrow \dualParam{1}^{\horizon} +
-%%   \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}
-%%  \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right] \\
-%%  \dualParam{2}^{\horizon+1} &\leftarrow \dualParam{2}^{\horizon} +
-%%   \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}
-%%  \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right]
-%% \end{align}
-%
-%
-%\begin{assumption} \label{assumption-ntk-linearisation}
-%  Something about NTK being a linearisation around $\theta^{*}_{i}$ but each update moves away from $\theta^{*}_{i}$
-%\end{assumption}
-%
-%\cite{rossellApproximateLaplaceApproximations2021}
+\todo{what about regression/classification likelhoods}
+This GP predictive posterior is computationally expensive as it requires inverting an $N\times N$ matrix.
+
+\textbf{Sparse Gaussian processes}
+% The GP predictive posterior in \cref{eq-gp-predictive-posterior} is computationally expensive as it requires inverting an $N\times N$ matrix.
+A practical and computationally appealing alternative is to augment the joint probability space with pseudo inputs $\mathbf{Z} \in \R^{M \times D}$
+and corresponding outputs
+$\mathbf{u} = f(\mathbf{Z}; \transitionParams) \in \R^{M \times C}$, known as inducing variables, where $M \ll N$.
+\todo{cite sparse gp papers}
+Instead of collapsing the inducing variables like \cite{titsiasVariational2009}, they can be treated variationally
+$p(\mathbf{u} \mid \mathbf{y}) \approx q(\mathbf{u}) = \mathcal{N}\left( \mathbf{u} \mid \mathbf{m}, \mathbf{V} \right)$, where $\mathbf{m}$ and $\mathbf{V}$ are variational parameters
+which need to be optimised \citep{hensmanGaussian2013}.
+The sparse variational GP (SVGP) predictive posterior is then given by,
+\begin{align}
+\label{eq-dual-svgp-predictive-posterior}
+  p(f(\mathbf{x}_{*}) \mid \mathbf{y})
+&\approx \mathcal{N} \left( f(\mathbf{x}_{*}) \mid \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{m}^{*},
+  k_{**} - \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
+  % \mathbf{k}_{*\inducingInput} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\inducingInput}^{T}
+  + \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}}  \mathbf{V}^{*}  \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
+  \right)
+\coloneqq q_{\inducingVariable}(f(\mathbf{x}_{*}))
+\end{align}
+
+\textbf{Deep learning}
+Given the data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
+the goal of (supervised) deep learning, is to train the weights $\transitionParams \in \R^{P}$ of an $L\text{-layer}$ NN
+$f : \inputDomain \rightarrow \outputDomain$ to minimize the (regularized) empirical risk,
+\begin{align} \label{eq-empirical-risk}
+  \transitionParams^{*} = \arg \min_{\transitionParams \in \R^{D}} \mathcal{L}(\dataset;\transitionParams) = \arg \min_{\transitionParams \in \R^{D}} \left(
+  \sum_{n=0}^{N-1} l(f(\mathbf{x}_{n} ; \transitionParams), \mathbf{y}_{n}) + R(\transitionParams)  \right).
+\end{align}
+In practice, it is common to use the mean squared error (MSE) loss
+$l(f(\mathbf{x}_{n} ; \transitionParams),\mathbf{y}_{n}) = \|f(\mathbf{x}_{n} ; \transitionParams) - \mathbf{y}_{n} \|^{2}_{2}$
+and to use the weight decay regularizer $R(\transitionParams)=\frac{1}{2}\gamma^{-2}\|\transitionParams\|^{2}_{2}$.
+However, the practioner is free to choose any loss and regularizer. \todo{I think?}
+% \textbf{Bayesian neural networks}
+% \textbf{Weight space to function space}
+From a Bayesian perspective, we can interpret the terms in \cref{eq-empirical-risk} as the log-prior and the i.i.d. log likelihood, i.e.,
+\begin{align} \label{eq-log-prior}
+  R(\transitionParams) &= \underbrace{\log p(\transitionParams)}_{\text{log prior}} = \log \mathcal{N}(\transitionParams \mid 0, \gamma^{2} \mathbf{I}) \\
+  l(f(\mathbf{x}_{n} ; \transitionParams), \mathbf{y}_{n}) &= \underbrace{\log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \transitionParams))}_{\text{log likelihood}}
+  = \log \mathcal{N} \left( \mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \transitionParams), \mathbf{I} \right) \label{eq-log-likelihood}
+\end{align}
+
+\textbf{NN to GP}
+Given this interpretation, we can represent the weight space prior from \cref{eq-log-prior}, in
+function space, by linearising the BNN around $\transitionParams^{*}$ and interpretting it as a GP.
+The GP prior is then given by,
+\begin{align} \label{eq-laplace-approx-function-space}
+  % \transitionFn_{\transitionParams_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \qquad
+  f(\cdot ;\transitionParams) \sim \mathcal{N} \left( \mu(\cdot), k(\cdot, \cdot') \right) \quad
+  % \mu_{\transitionParams_{i}^{*}}(\cdot)
+  \mu(\cdot)
+  = 0 \quad
+  % = f(\cdot ;\transitionParams^{*}) \quad
+  % K_{\transitionParams_{i}^{*}}(\cdot, \cdot')
+  k(\cdot, \cdot')
+  = \frac{1}{\gamma^{2}} \mathbf{J}(\cdot) \mathbf{J}(\cdot')^{T},
+\end{align}
+where the kernel is the neural tangent kernel (NTK) \citep{immerImprovingPredictionsBayesian2021},
+\todo{what mean function shoudl this use???}
+\todo{NTK times some factor??}
+with Jacobian given by $\mathbf{J}(\cdot) = \odv{\transitionFn(\cdot; \transitionParams)}{\transitionParams}_{\transitionParams=\transitionParams^{*}}$.
+% The kernel in \cref{eq-laplace-approx-function-space} is the neural tangent kernel (NTK)
+% $k(\mathbf{x}, \mathbf{x}') = \sigma_{0}^{2} J_{\transitionParams^{*}}(\mathbf{x}) J_{\transitionParams^{*}}(\mathbf{x}')^{T}$
+% \citep{immerImprovingPredictionsBayesian2021}
+% to formulate the GP posterior $p(f(\mathbf{X} ;\transitionParams_{0:i}) \mid \dataset_{0:i})$.
+Given this GP prior, we can use \cref{eq-gp-predictive-posterior} to obtain our GP posterior by conditioning on the data.
+% Given our GP prior, we can use the properties of multivariate normals to obtain our GP posterior by conditioning on the data.
+% where $\mathbf{A} = \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}}$
+In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
+Intuitively, we can view the optimisation in \cref{eq-empirical-risk} as learning our kernel.
+As a result, our NTK may be highly non stationary as it is dependent on the NN architecture, for example, the activation functions.
+It is worth noting that the NTK linearises the network around the optimised parameters $\transitionParams^{*}$,
+so the function space prior (and thus posterior) is only a locally linear approximation.
+
+We now have a method to obtain a GP posterior from a trained DNN.
+% In contrast to other approaches, our formulation has not restricted us to using a weight-space posterior obtained from the Laplace approximation.
+In contrast to other approaches, our formulation has not restricted us to using a weight-space posterior from a BNN.
+However, in practice, the GP posterior is not very useful as it requires inverting an $N\times N$ matrix which has complexity $\mathcal{O}(N^{3})$.
+The SVGP in \cref{eq-dual-svgp-predictive-posterior} offers a solution to this problem but it is not immediately clear how to set $\mathbf{m}$ and $\mathbf{V}$.
+In the next section, we show how we can directly obtain an SVGP posterior (i.e. set $\mathbf{m}$ and $\mathbf{V}$) directly from both
+1) a trained NN and 2) a BNN weight-space posterior.
+% $\mathbf{m}$ and $\mathbf{V}$
+% However, it is not obvious how we can use a SVGP to set $\mathbf{m}$ and $\mathbf{V}$
+
+% In contrast, to previous work, this approach did not require us Laplace approximation. we will not restrict our
+% It is worth noting that the NTK linearises the network around the optimised parameters $\transitionParams^{*}$,
+% so the function space prior (and thus posterior) is only a locally linear approximation.
+% In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
+% It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.
+
+\section{Methods}
+In the next section we show how we can obtain a SVGP directly from 1) a trained NN and 2) a BNN posterior.
+
+We follow \cite{csatoSparseOnlineGaussian2002} and express our GP posterior in the dual parameter space.
+However, we consider the variational formulation introduced by \cite{adamDualParameterizationSparse2021}, where the optimal variational parameters are given by,
+\begin{align} \label{eq-dual-params}
+\mathbf{m}^{*} = \mathbf{V}^{*}\bm\alpha^{*} \quad \mathbf{V}^{*} = [\mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} + \bm\beta^{*}]
+\end{align}
+Importantly, we can calculate the natural parameters $(\bm\alpha, \bm\beta)$ in closed form,
+\todo{paul needs to update \cref{eq-dual-svgp-params}}
+\begin{align} \label{eq-dual-svgp-params}
+\bm\alpha_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right] \\
+\bm\beta_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right].
+\end{align}
+This simplifies SVGP inference \citep{hensmanGaussian2013} as it no longer requires the variational parameters $(\mathbf{m}, \mathbf{V})$ to be optimised.
+
+% Importantly, \cite{changFantasizingDualGPs2022} show that in the dual space,
+% conditioning on new observations reduces to suming the dual variables from the previous time
+% step with an update, given by,
+% \todo{pick best way to show new data (using superscript new or just time indexing?)}
+% \begin{align} \label{eq-dual-update-svgp}
+% \bm\alpha_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right] \\
+% \bm\beta_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right]
+% \end{align}
+
+% We follow \cite{csatoSparseOnlineGaussian2002} and express our GP posterior in the dual parameter space,
+% % to write GP posterior $p(f(\mathbf{X} ;\transitionParams_{0:i}) \mid \dataset_{0:i})$ as,
+% \begin{align} \label{eq-gp-post}
+%   \mathbb{E}_{p(f(\mathbf{x}_{*}) \mid \mathbf{y}_{n})} \left[ f(\mathbf{x}_{*}) \right] &= \mu(\mathbf{x}_{*}) + \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
+%   \mathbb{V}_{p(f(\mathbf{x}_{*}) \mid \mathbf{y}_{n})} \left[ f(\mathbf{x}_{*}) \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \text{diag}(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
+% \end{align}
+% % \begin{align} \label{eq-laplace-approx-function-space}
+% %   \mathbb{E}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
+% %   \mathbb{V}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \diag(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
+% % \end{align}
+% where the dual parameters $(\bm\alpha_n, \bm\beta_n)$ are vectors of,
+% \begin{align} \label{eq-gp-dual-params}
+%   \bm\alpha_{n} \coloneqq \left\{ \mathbb{E}_{p(f(\mathbf{x}_{i}) \mid \mathbf{y}_{n})} \left[ \nabla_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \right\}_{i=1}^{N} \qquad
+%   \bm\beta_{n} \coloneqq \left\{ \mathbb{E}_{p(f(\mathbf{x}_{i}) \mid \mathbf{y}_{n})} \left[ \nabla^{2}_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \right\}_{i=1}^{N}
+% \end{align}
+% Importantly, this parameterisation
+
+% \textbf{dual-SVGP}
+% \begin{align} \label{eq-svgp-post}
+%   \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ f(\mathbf{x}_{*}) \right] &= \mu(\mathbf{x}_{*}) + \mathbf{k}_{\mathbf{z}*}^{T} \bm\alpha_{\mathbf{u}} \\
+%   \mathbb{V}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ f(\mathbf{x}_{*}) \right] &= k_{**} - \mathbf{k}_{\mathbf{z}*}^{T} \left[ \mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} - \left( \mathbf{K}_{\mathbf{z} \mathbf{z}} + \bm\beta_{\mathbf{u}} \right)^{-1} \right] \mathbf{k}_{\mathbf{z}*}
+% \end{align}
+% % \begin{align} \label{eq-laplace-approx-function-space}
+% %   \mathbb{E}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
+% %   \mathbb{V}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \diag(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
+% % \end{align}
+% where the dual parameters $(\bm\alpha_{\mathbf{u}}, \bm\beta_{\mathbf{u}})$ are vectors of,
+% \begin{align} \label{eq-svgp-dual-params}
+%   \bm\alpha_{\mathbf{u}} \coloneqq \mathbf{k}_{\mathbf{z}i} \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ \nabla_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \qquad
+%   \bm\beta_{\mathbf{u}} \coloneqq \mathbf{k}_{\mathbf{z}i} \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ \nabla^{2}_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \mathbf{k}_{\mathbf{z}i}^{T}
+% \end{align}
+
+% weight space posterior in \cref{eq-laplace-approx-weight-space} in
+% function space by linearising the BNN and interpreting it as a GP.
+% \begin{align} \label{eq-laplace-approx-function-space}
+%   \transitionFn_{\transitionParams_{i}}(\cdot) &\sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \quad
+%   \mu_{\transitionParams_{i}^{*}}(\cdot) &= \transitionFn_{\transitionParams^{*}_{i}}(\cdot) \quad
+%   K_{\transitionParams_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) \bm\Sigma_{\transitionParams^{*}_{i}} \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot')^{T}
+% \end{align}
+% where the Jacobian is given by $\mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}$.
+
+% \begin{align} \label{eq-laplace-approx-jacobian}
+% \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}
+% \end{align}
+
+% % Note that the posterior in \cref{eq-laplace-approx-weight-space} is in weight space.
+% We can represent the weight space posterior in \cref{eq-laplace-approx-weight-space} in
+% function space by linearising the BNN and interpreting it as a GP.
+% \begin{align} \label{eq-laplace-approx-function-space}
+%   \transitionFn_{\transitionParams_{i}^{*}}(\cdot) &\sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \quad
+%   \mu_{\transitionParams_{i}^{*}}(\cdot) &= \transitionFn_{\transitionParams^{*}_{i}}(\cdot) \quad
+%   K_{\transitionParams_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) \bm\Sigma_{\transitionParams^{*}_{i}} \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot')^{T}
+% \end{align}
+% where the Jacobian is given by $\mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}$.
+
+% \begin{align} \label{eq-laplace-approx-jacobian}
+% \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}
+% \end{align}
+
+\subsection{Fast Updates}
+Importantly, \cite{changFantasizingDualGPs2022} show that in the dual space,
+conditioning on new observations reduces to suming the dual variables from the previous time
+step with an update, given by,
+\todo{pick best way to show new data (using superscript new or just time indexing?)}
+\begin{align} \label{eq-dual-update-svgp}
+\dualParam{1}^{t+1} &\leftarrow \dualParam{1}^{t} +  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))} \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right] \\
+\dualParam{2}^{t+1} &\leftarrow \dualParam{2}^{t} +  \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))}  \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right]
+\end{align}
+Importantly, for a single new observation $((\state_{t}, \action_{t}), \state_{t+1})$ this update has
+complexity $\mathcal{O}(\numInducing^{2})$.
+This is a significant improvement to naive GP conditioning, which has complexity $\mathcal{O}((\numDataNew + \numDataOld)^{3})$
+and sparse GP conditioning, which has complexity $\mathcal{O}((\numDataNew + \numDataOld)\numInducing^{2})$.
+\todo{double check these complexities are right and cite them/show equaitons}
+It is worth highlighting that the complexity of \cite{changFantasizingDualGPs2022} update does not increase during an episode.
+
+\subsubsection{Model-based RL}
+
+\subsubsection{Efficiently Sampling Functions for Posterior Sampling}
+\cite{wilsonEfficiently2020}
+\cite{wilsonPathwise2021}
+
+% \begin{align} \label{eq-dual-update-svgp}
+%  \dualParam{1}^{\text{new}} &\leftarrow \dualParam{1}^{\text{old}} +
+%   \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}))}
+%  \left[ \log p(\state_{t+1}^{\text{new}} \mid \latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}) ) \right] \\
+%  \dualParam{2}^{\text{new}} &\leftarrow \dualParam{2}^{\text{old}} +
+%   \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}))}
+%  \left[ \log p(\state_t^{\horizon+1} \mid \latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}) ) \right] \\
+%  \dualParam{1}^{\horizon+1} &\leftarrow \dualParam{1}^{\horizon} +
+%   \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}
+%  \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right] \\
+%  \dualParam{2}^{\horizon+1} &\leftarrow \dualParam{2}^{\horizon} +
+%   \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}
+%  \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right]
+% \end{align}
+
+\begin{assumption} \label{assumption-ntk-linearisation}
+  Something about NTK being a linearisation around $\theta^{*}_{i}$ but each update moves away from $\theta^{*}_{i}$
+\end{assumption}
+
+\cite{rossellApproximateLaplaceApproximations2021}
 
@@
 	\renewcommand{\arraystretch}{1.}
-	\setlength{\tabcolsep}{2pt}
-	\setlength{\tblw}{0.14\textwidth}
+	\setlength{\tabcolsep}{6pt}
+	\setlength{\tblw}{0.2\textwidth}
 
@@
 
+\begin{itemize}
+  \item Show prediction performance in classification: UCI classification results, compare to BNN predictive paper
+  \item Fast adapatation in model-based RL: results for cartpole
+  \item Is linearising NN mean and using fast updates during episode better than keeping non-linearised mean and not updating?
+  \item Possible ablations
+  \begin{itemize}
+    \item How does number of inducing points affect performance?
+  \end{itemize}
+  \item How good is the assumption that we can linearise BNN to get NTK?
+\end{itemize}
+
+Environments
+\begin{itemize}
+  \item Compare updated posterior with non updated posterior
+  \item Need to show update is fast enough for practical use?
+  \begin{itemize}
+    \item How frequently can we do the posterior update? Every time step or every $K$ steps?
+    \item Update depends on number of inducing points?
+    \item What experiments can we show for this? Wall clock time vs planning horizon with different numbers of inducing points?
+  \end{itemize}
+  \item Is linearising NN mean and using fast updates during episode better than keeping non-linearised mean and not updating?
+  \item How does number of inducing points affect performance?
+  \begin{itemize}
+    \item More inducing points means better approximation but larger computational complexity.
+  \end{itemize}
+  \item How good is the assumption that we can linearise BNN to get NTK?
+  \begin{itemize}
+    \item Does model's performance get worse during an episode because linearisation becomes more wrong?
+    \item SVGP does't have this issue so compare to SVGP in cartpole?
+  \end{itemize}
+  \item What length planning horizon to use?
+  \begin{itemize}
+    \item Too small (e.g. $\Horizon=0$) would mean no exploration?
+    \item Can $\Horizon$ be too large?
+  \end{itemize}
+  \begin{itemize}
+  \item Compare for different strategies of making decisions under dynamic model's uncertainty:
+    \begin{itemize}
+      \item \textbf{Greedy exploitation} \(\pi_{\text{greedy}}\)
+      \item \textbf{Hallucinated-UCRL} \(\pi_{\text{HUCRL}}\)
+      \item \textbf{Thompson sampling} \(\pi_{\text{TS}}\)
+    \end{itemize}
+  \end{itemize}
+  \item Compare impact of stationary vs non-stationary priors
+  \begin{itemize}
+    \item First do this with GP
+    \item Then try to do with Laplace BNN
+  \end{itemize}
+  \item Compare impact of function vs weight space
+\end{itemize}
+
 \section{Discussion and Conclusion}
@@
 %\section*{Broader Impact}
+
+\begin{ack}
+ASK A ABOUT THIS SECTION:
+Aidan Scannell is funded by the Finnish Center for Artificial Intelligence.
+\end{ack}
 

### 2023-05-10 paper/main.tex
Rename figs folder to fig
starting to fill out background

--- 2023-05-10 paper/main.tex
@@
 \newcommand{\N}{\mathrm{N}}
+%\newcommand{\R}{\mathrm{R}}
 \newcommand{\myexpect}{\mathbb{E}}
@@
 
-\textbf{Dual GP} Sparse Gaussian processes \citep{hensman2013gaussian} are a principled way to scale Gaussian processes to large datasets by changing the complexity from $O(n^3)$ where n is number of data points to $O(m^3)$ where $m \ll n$.
-The key to the complexity saving is to use a sparse distribution
+\textbf{Dual GP} A Gaussian process is a prior over functions $f \sim \GP(0, \kappa)$.
+The prior is characterized by a covariance kernel function $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors.
+Once combined with a data set ${\mathcal{D}_n = \{(\vx_i, y_i)\}_{i=1}^n}$ with $n$ examples, each modeled by the likelihood $p(y_i \mid f_i)$ at function $f_i = f(\vx_i)$, we can form a posterior using multivariate conditioning.
+
+Sparse Gaussian processes \citep{hensman2013gaussian} are a principled way to scale Gaussian processes to large datasets by changing the complexity from $O(n^3)$ where n is number of data points to $O(m^3)$ with $m$ the number of inducing points, where typically $m \ll n$.
+The key to the complexity saving is to use a sparse distribution $q(\vu; \vm, \MV)$, where $\vm \in \R^{m}$ and $\MV \in \R^{m \times m}$.
+The distribution at all over points is then defined as $q_{\vu}(f) = \int p(f \mid \vu) q(\vu) d\vu$.
 
@@
 %   \centering
-%   \includegraphics[width=0.5\textwidth, angle=270]{figs/weight-space-to-functio-space.pdf}
+%   \includegraphics[width=0.5\textwidth, angle=270]{fig/weight-space-to-functio-space.pdf}
 %   \caption{}
@@
 %   \centering
-%   \includegraphics[width=0.5\textwidth, trim=0 100 0 10]{figs/cartpole-training-curves.pdf}
+%   \includegraphics[width=0.5\textwidth, trim=0 100 0 10]{fig/cartpole-training-curves.pdf}
 %   \caption{}
@@
         \centering
-        \input{./figs/example_fig.tex}
+        \input{./fig/example_fig.tex}
     \end{subfigure}

### 2023-05-10 paper/main.tex
starting to fill out background

@@
 
-\textbf{Dual GP} A Gaussian process is a prior over functions $f \sim \GP(0, \kappa)$.
-The prior is characterized by a covariance kernel function $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors.
-Once combined with a data set ${\mathcal{D}_n = \{(\vx_i, y_i)\}_{i=1}^n}$ with $n$ examples, each modeled by the likelihood $p(y_i \mid f_i)$ at function $f_i = f(\vx_i)$, we can form a posterior using multivariate conditioning.
-
-Sparse Gaussian processes \citep{hensman2013gaussian} are a principled way to scale Gaussian processes to large datasets by changing the complexity from $O(n^3)$ where n is number of data points to $O(m^3)$ with $m$ the number of inducing points, where typically $m \ll n$.
-The key to the complexity saving is to use a sparse distribution $q(\vu; \vm, \MV)$, where $\vm \in \R^{m}$ and $\MV \in \R^{m \times m}$.
+\textbf{Dual Gaussian Process} A Gaussian process (GP) is a prior over functions $f \sim \GP(0, \kappa)$.
+The prior is characterized by a covariance kernel function $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors typically in $\R^{\mathrm{D}}$.
+Once combined with a data set ${\mathcal{D}_n = \{(\vx_i, y_i)\}_{i=1}^n}$ with $n$ examples, each modeled by the likelihood $p(y_i \mid f_i)$ at function $f_i = f(\vx_i)$, we can form a posterior proccess using multivariate conditioning.
+The drawbacks to GPs are their lack of scaling to large datasets and non-tractability with non-Gaussian likelihoods.
+
+Sparse Gaussian processes \citep{hensman2013gaussian} are a principled way to scale Gaussian processes to large datasets by changing the complexity from $O(n^3)$ to $O(m^3)$ with $m$ the number of inducing points, and typically $m \ll n$.
+The key insight is to use a sparse approximating distribution $q(\vu; \vm, \MV)$, where $\vm \in \R^{m}$ and $\MV \in \R^{m \times m}$, and find its parameters through maximizing the evidence lower bound (ELBO).
 The distribution at all over points is then defined as $q_{\vu}(f) = \int p(f \mid \vu) q(\vu) d\vu$.
-
-dual parameterization states that we can decompose the optimal sparse Gaussian process posterior as follows:
-\begin{align}
-   \myexpect_{q_{\vu}(f)}[f_i] &= \vkzs^{\T} \valpha_{\vu} , \\
-   \textrm{Var}_{q_{\vu}(f)}[f_i]  &= \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \vbeta_{\vu})^{-1} ]\vkzs.
-\end{align}
-The dual parameters consist of an $m$-length vector $\valpha_\vu$ and $m\times m$-size matrix $\vbeta_\vu$, defined as
+The dual parameterization \citet{adam2021dual} states that we can decompose the optimal sparse Gaussian process posterior as follows:
 \begin{equation}
-\begin{split}
-   \vlambda & = [ \MKzz + \vbeta_{\vu}]\valpha_{\vu}  = \sum_{i \in \mathcal{D}_{\textrm{old}} \cup \mathcal{D}_{\textrm{new}}}  \vkzi \, \tilde{\lambda}_{i}, \\
-   \vbeta_{\vu} &= \sum_{i \in \mathcal{D}_{\textrm{old}} \cup \mathcal{D}_{\textrm{new}}} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,
+   \myexpect_{q_{\vu}(f)}[f_i] = \vkzs^{\T} \valpha , \quad 
+   \textrm{Var}_{q_{\vu}(f)}[f_i]  = \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \vbeta)^{-1} ]\vkzs.
+\end{equation}
+The dual parameters consist of an $m$-length vector $\valpha$ and $m\times m$-size matrix $\vbeta$, defined as
+\begin{equation} 
+   \vlambda = [ \MKzz + \vbeta]\valpha  = \sum_{i \in \mathcal{D}_{n}}  \vkzi \, \tilde{\lambda}_{i}, \quad
+   \vbeta = \sum_{i \in \mathcal{D}_{n}} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,
 \label{eq:dual_sparse}
-\end{split}
 \end{equation}
+
 where $\tilde{\lambda}_i = \alpha_i - \myexpect_{q_{\vu}(f)}[f_i] \beta_i$ with $(\hat{\alpha}_i, \hat{\beta}_i)$ defined as follows,
 \begin{equation}
-\begin{aligned}
-   \alpha_i &= \myexpect_{q_{\vu}(f_i)} [\nabla_{f_i}\log p(y_i \mid f_i)],\\
-   \beta_i &= \myexpect_{q_{\vu}(f_i)} [ -\nabla^2_{f_i}\log p(y_i \mid f_i)],
-\end{aligned} \label{eq:svgp_dual}
+ \alpha_i = \myexpect_{q_{\vu}(f_i)} [\nabla_{f_i}\log p(y_i \mid f_i)], \quad
+   \beta_i = \myexpect_{q_{\vu}(f_i)} [ -\nabla^{2}_{f_i}\log p(y_i \mid f_i)],
+\label{eq:svgp_dual}
 \end{equation}

### 2023-05-10 bnn-predictive/experiments/scripts/classification.py
Updating results, preparing to run FMNIST

@@ -130,12 +130,17 @@ def inference(
     res = dict()
     torch.manual_seed(seed)
     if ds_train.C == 2:
-        likelihood = BernoulliLh(EPS=0.000001)
+        likelihood = BernoulliLh(EPS=0.000000001)
         K = 1
     else:
         eps = 0.0000000001
         likelihood = CategoricalLh(EPS=eps)
         K = ds_train.C
+
+    print(f'X_train shape: {X_train.shape[0]}')
+    if X_train.shape[0] <= n_inducing:
+        print('WARNING: Using all training data as inducing points')
+        n_inducing = X_train.shape[0]
 
     prior_prec_n = prior_prec / y_train.shape[0]
     print(f"prior precision: {prior_prec_n}")

### 2023-05-10 paper/main.tex
Added new table to paper, updated results
starting to fill out background

@@
 The distribution at all over points is then defined as $q_{\vu}(f) = \int p(f \mid \vu) q(\vu) d\vu$.
-The dual parameterization \citet{adam2021dual} states that we can decompose the optimal sparse Gaussian process posterior as follows:
+The dual parameterization \cite{adam2021dual} states that we can decompose the optimal sparse Gaussian process posterior as follows:
 \begin{equation}
@@
 \end{equation}
+
+Here, we omit the dependency of the kernel on $n$, and simply use $\MKxx$ to denote the $n \times n$ matrix with $\kappa(\vx_i,\vx_j)$ as the $ij$\textsuperscript{th} entry, computed for all $\vx_i \in\vX$ where $\vX = (\vx_1,\ldots,\vx_n)$.
+Similarly, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
+
 The dual parameters consist of an $m$-length vector $\valpha$ and $m\times m$-size matrix $\vbeta$, defined as
@@
 
-where $\tilde{\lambda}_i = \alpha_i - \myexpect_{q_{\vu}(f)}[f_i] \beta_i$ with $(\hat{\alpha}_i, \hat{\beta}_i)$ defined as follows,
+where $\tilde{\lambda}_i = \alpha_i - \myexpect_{q_{\vu}(f)}[f_i] \hat{\beta}_i$ with $(\hat{\alpha}_i, \hat{\beta}_i)$ defined as,
 \begin{equation}
@@
 
+\section{Experiment details}
+
+\subsection{UCI}
+
+\begin{table}[t!] 
+  \centering\scriptsize
+  \caption{Negative log predictive density (NLPD) (lower better) for the proposed model TODO} 
+	\label{tbl:uci_all}
+	% Control table spacing
+	\renewcommand{\arraystretch}{1.}
+	\setlength{\tabcolsep}{2pt}
+	\setlength{\tblw}{0.14\textwidth}
+
+	% Custom error formatting
+	\newcommand{\val}[2]{%
+		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
+	}
+
+    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
+	\input{tables/uci_all.tex}
+\end{table}
+
 \section{Template stuff}

### 2023-05-10 paper/main.tex
Sketch banana

--- 2023-05-10 paper/main.tex
@@
 \usetikzlibrary{decorations,backgrounds,arrows.meta,calc}
+\usetikzlibrary{shapes,arrows,positioning}
 
@@
 \newcommand{\N}{\mathrm{N}}
-%\newcommand{\R}{\mathrm{R}}
 \newcommand{\myexpect}{\mathbb{E}}
@@
 
+\begin{figure}[t!]
+  \centering
+  % Set figure size
+  \setlength{\figurewidth}{.31\textwidth}
+  \setlength{\figureheight}{\figurewidth}
+  %
+  \begin{tikzpicture}[outer sep=0,inner sep=0]
+
+    \newcommand{\addfig}[2]{
+    \begin{scope}
+      \clip[rounded corners=3pt] ($(#1)+(-.5\figurewidth,-.5\figureheight)$) rectangle ++(\figurewidth,\figureheight);
+      \node (#2) at (#1) {\includegraphics[width=1.05\figurewidth]{./fig/#2}};
+    \end{scope}
+    %\draw[rounded corners=3pt,line width=1.2pt,black!60] ($(#1)+(-.5\figurewidth,-.5\figureheight)$) rectangle ++(\figurewidth,\figureheight);
+    }
+
+    % The neural network
+    \addfig{0,0}{banana-nn}
+
+    % The nn2svgp
+    \addfig{1.1\figurewidth,0}{banana-nn2svgp}
+
+    % The update
+    \addfig{2.2\figurewidth,0}{banana-update}
+
+     % The arrow
+     \tikzstyle{myarrow} = [draw=black!80, single arrow, minimum height=12mm, minimum width=2pt, single arrow head extend=4pt, fill=black!80, anchor=center, rotate=0, inner sep=5pt, rounded corners=1pt]
+     \node[myarrow] (first-arr) at ($(banana-nn)!0.5!(banana-nn2svgp)$) {};
+     \node[myarrow] (second-arr) at ($(banana-nn2svgp)!0.5!(banana-update)$) {};
+
+     % Arrow labels
+     \node[font=\scriptsize,color=white] at (first-arr) {nn2svgp};
+     \node[font=\scriptsize,color=white] at (second-arr) {new data};
+
+     % Labels
+     \node[anchor=north, font=\small] at ($(banana-nn) + (0,-.55\figureheight)$) {Neural network prediction};
+     \node[anchor=north, font=\small] at ($(banana-nn2svgp) + (0,-.55\figureheight)$) {Sparse GP representation};
+     \node[anchor=north, font=\small] at ($(banana-update) + (0,-.55\figureheight)$) {Update without re-training};
+
+  \end{tikzpicture}
+  \caption{Teaser figure goes here.}
+  \label{fig:banana}  
+\end{figure}
+
 \subsection{Related Work}
@@
 
-\textbf{Dual GP} A Gaussian process is a prior over functions $f \sim \GP(0, \kappa)$.
-The prior is characterized by a covariance kernel function $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors.
-Once combined with a data set ${\mathcal{D}_n = \{(\vx_i, y_i)\}_{i=1}^n}$ with $n$ examples, each modeled by the likelihood $p(y_i \mid f_i)$ at function $f_i = f(\vx_i)$, we can form a posterior using multivariate conditioning.
-
-Sparse Gaussian processes \citep{hensman2013gaussian} are a principled way to scale Gaussian processes to large datasets by changing the complexity from $O(n^3)$ where n is number of data points to $O(m^3)$ with $m$ the number of inducing points, where typically $m \ll n$.
-The key to the complexity saving is to use a sparse distribution $q(\vu; \vm, \MV)$, where $\vm \in \R^{m}$ and $\MV \in \R^{m \times m}$.
-The distribution at all over points is then defined as $q_{\vu}(f) = \int p(f \mid \vu) q(\vu) d\vu$.
+\textbf{Dual GP} Sparse Gaussian processes \citep{hensman2013gaussian} are a principled way to scale Gaussian processes to large datasets by changing the complexity from $O(n^3)$ where n is number of data points to $O(m^3)$ where $m \ll n$.
+The key to the complexity saving is to use a sparse distribution
 

### 2023-05-10 paper/main.tex

--- 2023-05-10 paper/main.tex
@@
   \label{fig:teaser}  
+\end{figure}
+
+\begin{figure}[t!]
+  \centering
+  % Set figure size
+  \setlength{\figurewidth}{.31\textwidth}
+  \setlength{\figureheight}{\figurewidth}
+  %
+  \begin{tikzpicture}[outer sep=0,inner sep=0]
+
+    \newcommand{\addfig}[2]{
+    \begin{scope}
+      \clip[rounded corners=3pt] ($(#1)+(-.5\figurewidth,-.5\figureheight)$) rectangle ++(\figurewidth,\figureheight);
+      \node (#2) at (#1) {\includegraphics[width=1.05\figurewidth]{./fig/#2}};
+    \end{scope}
+    %\draw[rounded corners=3pt,line width=1.2pt,black!60] ($(#1)+(-.5\figurewidth,-.5\figureheight)$) rectangle ++(\figurewidth,\figureheight);
+    }
+
+    % The neural network
+    \addfig{0,0}{banana-nn}
+
+    % The nn2svgp
+    \addfig{1.1\figurewidth,0}{banana-nn2svgp}
+
+    % The update
+    \addfig{2.2\figurewidth,0}{banana-update}
+
+     % The arrow
+     \tikzstyle{myarrow} = [draw=black!80, single arrow, minimum height=12mm, minimum width=2pt, single arrow head extend=4pt, fill=black!80, anchor=center, rotate=0, inner sep=5pt, rounded corners=1pt]
+     \node[myarrow] (first-arr) at ($(banana-nn)!0.5!(banana-nn2svgp)$) {};
+     \node[myarrow] (second-arr) at ($(banana-nn2svgp)!0.5!(banana-update)$) {};
+
+     % Arrow labels
+     \node[font=\scriptsize,color=white] at (first-arr) {nn2svgp};
+     \node[font=\scriptsize,color=white] at (second-arr) {new data};
+
+     % Labels
+     \node[anchor=north, font=\small] at ($(banana-nn) + (0,-.55\figureheight)$) {Neural network prediction};
+     \node[anchor=north, font=\small] at ($(banana-nn2svgp) + (0,-.55\figureheight)$) {Sparse GP representation};
+     \node[anchor=north, font=\small] at ($(banana-update) + (0,-.55\figureheight)$) {Update without re-training};
+
+  \end{tikzpicture}
+  \caption{Teaser figure goes here.}
+  \label{fig:banana}  
 \end{figure}

### 2023-05-10 paper/main.tex
update cl results table

--- 2023-05-10 paper/main.tex
@@
 The distribution at all over points is then defined as $q_{\vu}(f) = \int p(f \mid \vu) q(\vu) d\vu$.
-The dual parameterization \cite{adam2021dual} states that we can decompose the optimal sparse Gaussian process posterior as follows:
+The dual parameterization \citet{adam2021dual} states that we can decompose the optimal sparse Gaussian process posterior as follows:
 \begin{equation}
@@
 \end{equation}
-
-Here, we omit the dependency of the kernel on $n$, and simply use $\MKxx$ to denote the $n \times n$ matrix with $\kappa(\vx_i,\vx_j)$ as the $ij$\textsuperscript{th} entry, computed for all $\vx_i \in\vX$ where $\vX = (\vx_1,\ldots,\vx_n)$.
-Similarly, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
-
 The dual parameters consist of an $m$-length vector $\valpha$ and $m\times m$-size matrix $\vbeta$, defined as
@@
 
-where $\tilde{\lambda}_i = \alpha_i - \myexpect_{q_{\vu}(f)}[f_i] \hat{\beta}_i$ with $(\hat{\alpha}_i, \hat{\beta}_i)$ defined as,
+where $\tilde{\lambda}_i = \alpha_i - \myexpect_{q_{\vu}(f)}[f_i] \beta_i$ with $(\hat{\alpha}_i, \hat{\beta}_i)$ defined as follows,
 \begin{equation}
@@
   \centering\scriptsize
-  \caption{TODO: CL Experiments.
-$^*$ Methods relying only on weight regularization.
-\color{blue}{Results from \cite{rudner2022continual}.} \color{red}{Preliminary results need more runs or hyperparam tuning}}
+  \caption{
+  TODO: CL Experiments. $^*$ Methods relying only on weight regularization. 
+  \color{blue}{Results from \cite{rudner2022continual}.} 
+  %\color{red}{Preliminary results need more runs or hyperparam tuning}
+  }
 	\label{tbl:cl_table_1}
@@
 
-\section{Experiment details}
-
-\subsection{UCI}
-
-\begin{table}[t!] 
-  \centering\scriptsize
-  \caption{Negative log predictive density (NLPD) (lower better) for the proposed model TODO} 
-	\label{tbl:uci_all}
-	% Control table spacing
-	\renewcommand{\arraystretch}{1.}
-	\setlength{\tabcolsep}{2pt}
-	\setlength{\tblw}{0.14\textwidth}
-
-	% Custom error formatting
-	\newcommand{\val}[2]{%
-		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
-	}
-
-    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
-	\input{tables/uci_all.tex}
-\end{table}
-
 \section{Template stuff}

### 2023-05-10 paper/main.tex
starting to fill out background

--- 2023-05-10 paper/main.tex
@@
 
-Here, we omit the dependency of the kernel on $n$, and simply use $\MKxx$ to denote the $n \times n$ matrix with $\kappa(\vx_i,\vx_j)$ as the $ij$\textsuperscript{th} entry, computed for all $\vx_i \in\vX$ where $\vX = (\vx_1,\ldots,\vx_n)$.
+%Here, we omit the dependency of the kernel on $n$, and simply use $\MKxx$ to denote the $n \times n$ matrix with $\kappa(\vx_i,\vx_j)$ as the $ij$\textsuperscript{th} entry, computed for all $\vx_i \in\vX$ where $\vX = (\vx_1,\ldots,\vx_n)$.
 Similarly, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.

### 2023-05-10 bnn-predictive/experiments/scripts/classification.py
Added option for batches to UCI scripts

@@ -58,8 +58,8 @@ def preds_glm(X, model, likelihood, mu, Sigma_chol, samples):
     return gs.mean(dim=0)
 
 
-def preds_svgp(X, svgp, likelihood, samples=1000):
-    gs = svgp_sampling_predictive(X, svgp, likelihood, mc_samples=samples)
+def preds_svgp(X, svgp, likelihood, samples=1000, batch_size=100, device='cpu'):
+    gs = svgp_sampling_predictive(X, svgp, likelihood, mc_samples=samples, batch_size=batch_size, device=device)
     return gs.mean(dim=0)
 
 
@@ -83,7 +83,7 @@ def evaluate(p, y, likelihood, name, data):
 
 
 def create_ntksvgp(
-    X_train, y_train, model, likelihood, prior_prec, n_inducing=64, device="cpu"
+    X_train, y_train, model, likelihood, prior_prec, n_inducing=64, batch_size=1000, device="cpu"
 ):
     data = (X_train, y_train)
     n_classes = model(X_train).shape[-1]
@@ -96,6 +96,7 @@ def create_ntksvgp(
         output_dim=n_classes,
         likelihood=likelihood,
         num_inducing=n_inducing,
+        dual_batch_size=batch_size,
         device=device,
     )
     svgp.set_data(data)
@@ -113,6 +114,7 @@ def inference(
     seed,
     n_layers=2,
     n_units=50,
+    batch_size=1000,
     activation="tanh",
     n_inducing=64,
     n_samples=1000,
@@ -179,11 +181,12 @@ def inference(
         likelihood_svgp,
         prior_prec_n,
         n_inducing=n_inducing,
+        batch_size=batch_size,
         device=device,
     )
-    fs_train = preds_svgp(X_train, svgp, likelihood_svgp, samples=n_samples)
-    fs_test = preds_svgp(X_test, svgp, likelihood_svgp, samples=n_samples)
-    fs_valid = preds_svgp(X_valid, svgp, likelihood_svgp, samples=n_samples)
+    fs_train = preds_svgp(X_train, svgp, likelihood_svgp, samples=n_samples, batch_size=batch_size, device=device)
+    fs_test = preds_svgp(X_test, svgp, likelihood_svgp, samples=n_samples, batch_size=batch_size, device=device)
+    fs_valid = preds_svgp(X_valid, svgp, likelihood_svgp, samples=n_samples, batch_size=batch_size, device=device)
     res.update(evaluate(fs_train, y_train, lh, "svgp_ntk", "train"))
[…]

### 2023-05-10 bnn-predictive/preds/predictives.py

@@ -1,6 +1,7 @@
 import torch
 from torch.distributions import MultivariateNormal, LowRankMultivariateNormal, Normal
 from torch.nn.utils import parameters_to_vector, vector_to_parameters
+from torch.utils.data import DataLoader, TensorDataset
 import logging
 
 from preds.gradients import Jacobians_naive
@@ -60,18 +61,36 @@ def linear_sampling_predictive(
     return torch.stack(predictions)
 
 
-def svgp_sampling_predictive(X, svgp, likelihood, mc_samples=100, no_link=False):
+def svgp_sampling_predictive(X, svgp, likelihood, mc_samples=100, no_link=False, batch_size=None, device='cpu'):
     """Returns the sparse data used for convenience."""
     link = (lambda x: x) if no_link else likelihood.inv_link
-    f_mu, f_var = svgp.predict_f(X)
-    # print('Inside SVGP predictive')
-    # print(svgp.network(X).mean())
-    # print(f_mu.mean())
-    # print(f_var.mean())
-    # print(f_var.shape)
-    fs = Normal(f_mu, torch.sqrt(f_var.clamp(1e-5)))
-    return link(fs.sample((mc_samples,)))
+    if batch_size is None:
+        f_mu, f_var = svgp.predict_f(X)
+        fs = Normal(f_mu, torch.sqrt(f_var.clamp(1e-5)))
+        return link(fs.sample((mc_samples,)))
+    else:
+        dataset = TensorDataset(X)
+        data_loader = DataLoader(dataset, batch_size=batch_size)
+        ps = []
+        for X in iter(data_loader):    
+            X = X[0]  
+            X = X.to(device)
+            ps.append(
+                sample_svgp(X, likelihood, svgp,  n_samples=mc_samples))
+        ps = torch.cat(ps, axis=1)
+        return ps
 
+
+def sample_svgp(X, likelihood, svgp,  n_samples: int):
+    """Sample the SVGP, assumes a batched input."""
+    n_data = X.shape[0]
+    gp_means, gp_vars = svgp.predict_f(X)
+    dist = Normal(gp_means, torch.sqrt(gp_vars.clamp(10 ** (-8))))
+    logit_samples = dist.sample((n_samples,))
+    out_dim = logit_samples.shape[-1]
+    samples = likelihood.inv_link(logit_samples)
+    samples = samples.reshape(n_samples, n_data, out_dim)
+    return samples
 
 def functional_sampling_predictive(
[…]

### 2023-05-10 paper/main.tex
Minor
updated title and abstract

@@
 % \title{Converting Neural Networks to Gaussian Processes for Sequential Decision-Making Under Uncertainty}
-\title{Sparse Function Space Representation of Neural Networks for Exploration and Retention}
-
+%\title{Sparse Function Space Representation of Neural Networks for Exploration and Retention}
+\title{Sparse Function-space Neural Networks}
 \author{%
@@
 \begin{abstract}
-Sequential learning paradigms such as Continual Learning (CL) or Reinforcement Learning (RL) pose a challenge for gradient-based deep learning techniques as they struggle to incorporate new data and retain previous knowledge.
-Existing methods for converting neural networks from weight to function space allow a probabilistic treatment of the distribution over the function learned by the neural networks but are computationally expensive.
-We propose a method that converts a neural network to a low-rank functional representation as a sparse Gaussian process. 
-With this approach, we can build a compact representation of the function encoded by the neural network that can replace previous data in continual settings and be used for fast adaptation in RL, avoiding full retraining of the model.
+Deep neural networks lack uncertainty estimates, struggle to incorporate new data, and fail to retain previous knowledge.
+We present a method that overcomes these limitations by converting a weight-space neural network to a low-rank function-space representation, through a dual parameterisation.
+In contrast to previous work, we model the joint distribution over the full data set and not just a subset.
+Our method provides uncertainty estimates and enables us to incorporate new data without retraining, whilst retaining predictive performance.
+We also show that our function-space representation can be used as a low-rank summary of previous data in continual learning problems.
 \end{abstract}

### 2023-05-10 paper/main.tex
Minot

--- 2023-05-10 paper/main.tex
@@
   %
+  % Colours
+  \definecolor{C0}{HTML}{DF6679}
+  \definecolor{C1}{HTML}{69A9CE}
+  %
   \begin{tikzpicture}[outer sep=0,inner sep=0]
@@
      % The arrow
-     \tikzstyle{myarrow} = [draw=black!80, single arrow, minimum height=12mm, minimum width=2pt, single arrow head extend=4pt, fill=black!80, anchor=center, rotate=0, inner sep=5pt, rounded corners=1pt]
+     \tikzstyle{myarrow} = [draw=black!80, single arrow, minimum height=14mm, minimum width=2pt, single arrow head extend=4pt, fill=black!80, anchor=center, rotate=0, inner sep=5pt, rounded corners=1pt]
      \node[myarrow] (first-arr) at ($(banana-nn)!0.5!(banana-nn2svgp)$) {};
@@
      % Arrow labels
-     \node[font=\scriptsize,color=white] at (first-arr) {nn2svgp};
-     \node[font=\scriptsize,color=white] at (second-arr) {new data};
+     \node[font=\scriptsize\sc,color=white] at (first-arr) {nn2svgp};
+     \node[font=\scriptsize\sc,color=white] at (second-arr) {new data};
 
@@
   \end{tikzpicture}
-  \caption{Teaser figure goes here.}
+  \newcommand{\mycircle}{\protect\tikz[baseline=-.5ex]\protect\node[circle,inner sep=2pt,draw=black,fill=C0,opacity=.5]{};}
+  \newcommand{\mysquare}{\protect\tikz[baseline=-.5ex]\protect\node[inner sep=2.5pt,draw=black,fill=C1,opacity=.5]{};}
+  %
+  \caption{Binary classification (\mysquare~vs.~\mycircle)}
   \label{fig:banana}  
@@
 \label{sec:conclusion}
+
+A reference implementation of the methods presented in this paper is currently available as supplementary material and will be made available under the MIT License on GitHub upon acceptance.
 

### 2023-05-10 paper/main.tex
Arno proposing abstract

@@
 %\title{Sparse Function Space Representation of Neural Networks for Exploration and Retention}
-\title{Sparse Function-space Neural Networks}
+%\title{Sparse Function-space Neural Networks}
+\title{Sparse Function Space Representation of Neural Networks for Adaption and Retention}
 \author{%
@@
 \begin{abstract}
-Deep neural networks lack uncertainty estimates, struggle to incorporate new data, and fail to retain previous knowledge.
-We present a method that overcomes these limitations by converting a weight-space neural network to a low-rank function-space representation, through a dual parameterisation.
-In contrast to previous work, we model the joint distribution over the full data set and not just a subset.
-Our method provides uncertainty estimates and enables us to incorporate new data without retraining, whilst retaining predictive performance.
-We also show that our function-space representation can be used as a low-rank summary of previous data in continual learning problems.
+% OLDER VERSION
+%Sequential learning paradigms such as Continual Learning (CL) or Reinforcement Learning (RL) pose a challenge for gradient-based deep learning techniques as they struggle to incorporate new data and retain previous knowledge.
+Existing methods for converting neural networks from weight to function space allow a probabilistic treatment of the distribution over the function learned by the neural networks but are computationally expensive.
+We propose a method that converts a neural network to a low-rank functional representation as a sparse Gaussian process.
+With this approach, we can build a compact representation of the function encoded by the neural network that can replace previous data in continual settings and be used for fast adaptation in RL, avoiding full retraining of the model.
+%
+% Rewrite on 2023-05-10
+Deep neural networks are known to lack uncertainty estimates, struggle to incorporate new data, and fail to retain previous knowledge.
+We present a method that mitigates these issues by transforming a weight-space neural network to a low-rank function-space representation, via the so-called dual parameters.
+In contrast to previous work, we model the joint distribution across the entire data set rather than a subset.
+This offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst retaining predictive performance.
+We demonstrate the efficiency of the proposed approach in quantifying uncertainty in supervised learning, maintaining a summary representation in continual learning, and rapid updates in active learning.
 \end{abstract}

### 2023-05-10 paper/main.tex
started the NN section

@@
 
-\textbf{Neural Network in weight space}
+\textbf{Neural Network} A neural network takes ${\mathcal{D}_n = \{(\vx_i, y_i)\}_{i=1}^n}$ and fits a function $f(\mathbf{x}_{i};\transitionParams)$ through the following optimization:
+\begin{align} \label{eq-empirical-risk}
+  \transitionParams^{*} = \arg \min_{\transitionParams \in \R^{P}} \mathcal{L}(\dataset;\transitionParams) = \arg \min_{\transitionParams \in \R^{P}} \left(
+  \sum_{i=1}^{N} l(f(\mathbf{x}_{i} ; \transitionParams), y_i) + \frac{1}{\delta}R(\transitionParams)  \right).
+\end{align}
+If $l(f(\mathbf{x}_{i} ; \transitionParams), y_i) = -\log(p(y \mid f(\mathbf{x}_{i}))$
 
@@
 
-%Here, we omit the dependency of the kernel on $n$, and simply use $\MKxx$ to denote the $n \times n$ matrix with $\kappa(\vx_i,\vx_j)$ as the $ij$\textsuperscript{th} entry, computed for all $\vx_i \in\vX$ where $\vX = (\vx_1,\ldots,\vx_n)$.
-Similarly, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
-
+Here, $\MKzz$ to denote the $m \times m$ matrix with $\kappa(\vx_i,\vx_j)$ as the $ij$\textsuperscript{th} entry, Similarly, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
 The dual parameters consist of an $m$-length vector $\valpha$ and $m\times m$-size matrix $\vbeta$, defined as
@@
 
-The key quantities we need to build our sparse GP are $(\alpha_i, \beta_i)$ and a kernel function $\kappa$
+The key quantities we need to build our sparse GP are $(\alpha_i, \beta_i)$ and a kernel function $\kappa$  and from that we are able to make predictions and variance estimates.
+Crucially in the dual formulation our posterior contains all the training data given the sum in \cref{eq:dual_sparse}.
 

### 2023-05-10 paper/main.tex
Fig sketch

--- 2023-05-10 paper/main.tex
@@
 %\title{Sparse Function-space Neural Networks}
-\title{Sparse Function Space Representation of Neural Networks for Adaption and Retention}
+\title{Sparse Function-space Representation \\ of Neural Networks}% for Adaptation and Retention}
 \author{%
@@
 This offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst retaining predictive performance.
-We demonstrate the efficiency of the proposed approach in quantifying uncertainty in supervised learning, maintaining a summary representation in continual learning, and rapid updates in active learning.
+We demonstrate the proposed approach in quantifying uncertainty in supervised learning, maintaining a summary representation in continual learning, and in active learning.
 \end{abstract}
@@
 %
+
+\subsection{Related Work}
+\label{sec:related}
+%
+
+% Introduce the laplace GNN + shortcomings
+One common approach for uncertainty with neural networks is a Laplace GNN approximation \citep{daxbergerLaplace2021}.
+The idea is to essentially takes a trained neural network and linearises around the optimal weights.
+The resulting linear model can be used to obtain uncertainty estimates and sometimes improved predictions \citep{immerScalable2021}.
+Given the resultant model is now linear with respect to the weights its is also now possible to convert to a Gaussian process as shown in \citep{immerScalable2021, khan2019approximate}.
+Yet to obtain uncertainty estimates there is the usual computational scaling of the GP of $O(n^3)$, so cubic in the number of data points.
+Many approaches  apply crude approximations and yet still obtain good uncertainty estimates.
+
 Deep learning has become the cornerstone of contemporary artificial intelligence, proving remarkably effective in tackling supervised and unsupervised learning tasks in the {\em large data}, {\em offline}, and {\em gradient-based training} regime.
@@
 \begin{figure}[t!]
-  \setlength{\figurewidth}{.48\textwidth}
-  \setlength{\figureheight}{.5\figurewidth}
-  \begin{subfigure}{.48\textwidth}
-    \centering
-    \tikz\node[fill=black!10,minimum width=\figurewidth,minimum height=\figureheight,rounded corners=5pt]{};
+%  \begin{subfigure}{.48\textwidth}
+%    \centering
+%    \tikz\node[fill=black!10,minimum width=\figurewidth,minimum height=\figureheight,rounded corners=5pt]{};
+%  \end{subfigure}
+%  \hfill
+%  \begin{subfigure}{.48\textwidth}
+%    \centering
+%    \tikz\node[fill=black!10,minimum width=\figurewidth,minimum height=\figureheight,rounded corners=5pt]{};
+%  \end{subfigure}
+
+  \centering\scriptsize
+  % Figure options
+  \pgfplotsset{axis on top,scale only axis,width=\figurewidth,height=\figureheight, ylabel near ticks,ylabel style={yshift=-2pt},y tick label style={rotate=90},legend style={nodes={scale=1., transform shape}},tick label style={font=\tiny,scale=1}}
+  \pgfplotsset{xlabel={Input, $x$},axis line style={rounded corners=3pt}}
+  % Set figure 
+  \setlength{\figurewidth}{.28\textwidth}
+  \setlength{\figureheight}{\figurewidth}
+  %
+  \def\inducing{\normalsize Sparse inducing points}
+  %
+  \begin{subfigure}[c]{.34\textwidth}
+    \raggedleft
+    \pgfplotsset{ylabel={Output, $y$}}
+    \input{./fig/regression-nn.tex}%
   \end{subfigure}
   \hfill  
-  \begin{subfigure}{.48\textwidth}
+  \begin{subfigure}[c]{.01\textwidth}
     \centering
-    \tikz\node[fill=black!10,minimum width=\figurewidth,minimum height=\figureheight,rounded corners=5pt]{};
+    \tikz[overlay,remember picture]\node(p0){.};
   \end{subfigure}  
-  \caption{Teaser figure goes here.}
+  \hfill
+  \begin{subfigure}[c]{.28\textwidth}
+    \raggedleft
+    \pgfplotsset{yticklabels={,,},ytick={\empty}}
+    \input{./fig/regression-nn2svgp.tex}%
+  \end{subfigure}
+  \hfill  
+  \begin{subfigure}[c]{.01\textwidth}
+    \centering
+    \tikz[overlay,remember picture]\node(p1){.};
+  \end{subfigure}  
+  \hfill
+  \begin{subfigure}[c]{.28\textwidth}
+    \raggedleft
+    \pgfplotsset{yticklabels={,,},ytick={\empty}}        
+    \input{./fig/regression-update.tex}%
+  \end{subfigure}
+  \caption{\textbf{Regression example on an MLP with two hidden layers.} Left:~Predictions from the trained neural network. Center:~Our approach summarizes the...}
   \label{fig:teaser} 
+  % 
+  \begin{tikzpicture}[remember picture,overlay]
+    % Arrow style
+    \tikzstyle{myarrow} = [draw=black!80, single arrow, minimum height=14mm, minimum width=2pt, single arrow head extend=4pt, fill=black!80, anchor=center, rotate=0, inner sep=5pt, rounded corners=1pt]
+    % Arrows
+    \node[myarrow] (p0-arr) at ($(p0) + (0em,1.5em)$) {};
+    \node[myarrow] (p1-arr) at ($(p1) + (0em,1.5em)$) {};
+    % Arrow labels
+    \node[font=\scriptsize\sc,color=white] at (p0-arr) {nn2svgp};
+    \node[font=\scriptsize\sc,color=white] at (p1-arr) {new data};   
+  \end{tikzpicture}
 \end{figure}
@@
 \end{figure}
-
-\subsection{Related Work}
-\label{sec:related}
-%
-
-% Introduce the laplace GNN + shortcomings
-One common approach for uncertainty with neural networks is a Laplace GNN approximation \citep{daxbergerLaplace2021}.
-The idea is to essentially takes a trained neural network and linearises around the optimal weights.
-The resulting linear model can be used to obtain uncertainty estimates and sometimes improved predictions \citep{immerScalable2021}.
-Given the resultant model is now linear with respect to the weights its is also now possible to convert to a Gaussian process as shown in \citep{immerScalable2021, khan2019approximate}.
-Yet to obtain uncertainty estimates there is the usual computational scaling of the GP of $O(n^3)$, so cubic in the number of data points.
-Many approaches  apply crude approximations and yet still obtain good uncertainty estimates.
 

### 2023-05-10 paper/main.tex
started laplace section

@@
 \newcommand{\vy}{\mbf{y}}
+\newcommand{\vw}{\mbf{w}}
 
@@
 
-\textbf{Neural Network} A neural network takes ${\mathcal{D}_n = \{(\vx_i, y_i)\}_{i=1}^n}$ and fits a function $f(\mathbf{x}_{i};\transitionParams)$ through the following optimization:
+\textbf{Neural Network} Given the data set $\dataset_n = \{\mathbf{x}_{i} \in \inputDomain, y_{i} \in \outputDomain\}_{i=1}^{N}$,
+the goal of (supervised) deep learning, is to train the weights $\transitionParams \in \R^{P}$ of an $L\text{-layer}$ NN
+$f : \inputDomain \rightarrow \outputDomain$ to minimize the (regularized) empirical risk,
 \begin{align} \label{eq-empirical-risk}
@@
 \end{align}
-If $l(f(\mathbf{x}_{i} ; \transitionParams), y_i) = -\log(p(y \mid f(\mathbf{x}_{i}))$
-
-\textbf{Laplace approximation}
+If $l(f(\mathbf{x}_{i} ; \transitionParams), y_i) = -\log(p(y \mid f(\mathbf{x}_{i}))$ and $R(\transitionParams) = \|\transitionParams\|^{2}$ then we can view \cref{eq-empirical-risk} as the MAP solution to a Bayesian objective, where $p(\vw) = \N(\vzeros,\delta\MI)$.
+
+\textbf{Laplace approximation} The Laplace approximation allows us to build a posterior approximation $q(\vw)$ from the optimized objective \cref{eq-empirical-risk}.
 

### 2023-05-10 src/rl/train.py
LOTS og chnages to add hard coded reward fn

@@ -2,6 +2,7 @@
 import logging
 import random
 import time
+from collections import deque, namedtuple
 from pathlib import Path
 
 
@@ -17,6 +18,7 @@ import torch
 
 torch.set_default_dtype(torch.float64)
 
+from src.rl.custom_types import State, Action
 import src
 import torchrl
 import wandb
@@ -24,6 +26,54 @@ from dm_env import specs, StepType
 from omegaconf import DictConfig, OmegaConf
 from src.rl.utils import EarlyStopper, set_seed_everywhere
 from tensordict import TensorDict
+
+
+reward_fn = src.rl.models.rewards.CartpoleRewardModel().predict
+# def reward_fn(state, action):
+#     return torch.vmap(src.rl.models.rewards.cartpole_swingup_reward)(state, action)
+Transition = namedtuple("Transition", ("state", "action", "next_state", "reward"))
+
+
+class ReplayMemory(object):
+    def __init__(self, capacity: int, batch_size: int):
+        self.memory = deque([], maxlen=capacity)
+        self.batch_size = batch_size
+
+    def push(self, state: State, action: Action, next_state: State, reward):
+        """Save a transition"""
+        self.memory.append(
+            Transition(state=state, action=action, next_state=next_state, reward=reward)
+        )
+        # self.memory.append(Transition(*args))
+
+    def sample(self, batch_size=None):
+        if batch_size is None:
+            batch_size = self.batch_size
+        samples = random.sample(self.memory, batch_size)
+        states = []
+        actions = []
+        rewards = []
+        next_states = []
+        for sample in samples:
+            # print("sample {}".format(sample))
+            states.append(torch.Tensor(sample.state))
+            actions.append(torch.Tensor(sample.action))
+            rewards.append(torch.Tensor(sample.reward))
+            next_states.append(torch.Tensor(sample.next_state))
+        states = torch.stack(states, 0)
+        actions = torch.stack(actions, 0)
+        rewards = torch.stack(rewards, 0)
+        next_states = torch.stack(next_states, 0)
+        return {
+            "state": states,
+            "action": actions,
+            "reward": rewards,
+            "next_state": next_states,
+        }
+        # return random.sample(self.memory, batch_size)
+
+    def __len__(self):
+        return len(self.memory)
 
 
 @hydra.main(version_base="1.3", config_path="./configs", config_name="main")
@@ -46,6 +96,9 @@ def train(cfg: DictConfig):
     num_train_steps = cfg.num_train_episodes * cfg.episode_length
 
[…]

### 2023-05-10 src/nn2svgp/ntksvgp.py
clone data

@@ -64,6 +64,8 @@ class NTKSVGP(nn.Module):
     def set_data(self, train_data: Data):
         """Sets training data, samples inducing points, calcs dual parameters, builds predict fn"""
         X_train, Y_train = train_data
+        X_train = torch.clone(X_train)
+        Y_train = torch.clone(Y_train)
         # if X_train.ndim > 2:
         #     # TODO flatten dims for images
         #     logger.info("X_train.ndim>2 so flattening {}".format(X_train.shape))

### 2023-05-11 bnn-predictive/experiments/scripts/imginference.py
Added plotting for UCI results, working on CIFAR10 classification

@@ -94,7 +94,7 @@ def sample_svgp(X, likelihood, svgp, use_nn_out: bool, n_samples: int):
     logit_samples = dist.sample((n_samples,))
     out_dim = logit_samples.shape[-1]
     samples = likelihood.inv_link(logit_samples)
-    samples = samples.reshape(n_samples, n_data, out_dim)
+   # samples = samples.reshape(n_samples, n_data, out_dim)
     return samples
 
 
@@ -151,12 +151,12 @@ def main(
     n_sparse,
     name,
     n_inducing,
-    delta_min=1e-7,
-    delta_max=1e7,
+    delta_min=1e-5,
+    delta_max=1e8,
     res_dir="experiments/results",
     device="cuda",
 ):
-    lh = CategoricalLh(EPS=0.0000000001)
+    lh = CategoricalLh(EPS=0.00000000000001)
 
     eligible_files = list()
     deltas = list()
@@ -222,6 +222,7 @@ def main(
         gstar_te, yte = get_map_predictive(test_loader, model)
         gstar_va, yva = get_map_predictive(val_loader, model)
         state["map"] = evaluate(lh, yte, gstar_te, yva, gstar_va)
+        logging.info(state['map'])
 
         # SVGP
         logging.info("SVGP performance")
@@ -256,6 +257,32 @@ def main(
         )
         state[f"svgp_ntk_nn_{name}"] = evaluate(lh, yte, gstar_te, yva, gstar_va)
         logging.info(state[f"svgp_ntk_nn_{name}"])
+
+        # GP subset
+        logging.info("GP subset")
+        sparse_idx = torch.randperm(X_train.shape[0])[:n_inducing]
+        sparse_x = X_train[sparse_idx]
+        sparse_y = y_train[sparse_idx]
+        data_sparse = (sparse_x, sparse_y)
+        prior = ntksvgp.priors.Gaussian(params=model.parameters, delta=delta)
+        svgp_subset = NTKSVGP(
+            network=model,
+            prior=prior,
+            output_dim=output_dim,
+            likelihood=lh,
+            num_inducing=n_inducing,
+            dual_batch_size=batch_size,
+            device=device,
+        )
+        svgp_subset.set_data(data_sparse)
+        gstar_te, yte = get_svgp_predictive(
+            test_loader, svgp_subset, use_nn_out=False, likelihood=lh
+        )
+        gstar_va, yva = get_svgp_predictive(
+            val_loader, svgp_subset, use_nn_out=False, likelihood=lh
+        )
[…]

### 2023-05-11 paper/main.tex
Update fig
rewritten some equations in the method

--- 2023-05-10 paper/main.tex
@@
 % Let's use good old bibtex instead
+
+% Figure customization: Tight legend box
+\pgfplotsset{every axis/.append style={
+		legend style={inner xsep=1pt, inner ysep=0.5pt, nodes={inner sep=1pt, text depth=0.1em},draw=none,fill=none}
+}}
 
@@
 %\newcommand{\vz}{\mbf{z}}
-%\newcommand{\vf}{\mbf{f}}
+\newcommand{\vf}{\mbf{f}}
 \newcommand{\vu}{\mbf{u}}
@@
 \newcommand{\myexpect}{\mathbb{E}}
+
+\DeclareMathOperator*{\argmax}{argmax}
+\DeclareMathOperator*{\argmin}{argmin}
+\newcommand{\Norm}{\mathcal{N}}
 
@@
 %
-
-\subsection{Related Work}
-\label{sec:related}
-%
-
-% Introduce the laplace GNN + shortcomings
-One common approach for uncertainty with neural networks is a Laplace GNN approximation \citep{daxbergerLaplace2021}.
-The idea is to essentially takes a trained neural network and linearises around the optimal weights.
-The resulting linear model can be used to obtain uncertainty estimates and sometimes improved predictions \citep{immerScalable2021}.
-Given the resultant model is now linear with respect to the weights its is also now possible to convert to a Gaussian process as shown in \citep{immerScalable2021, khan2019approximate}.
-Yet to obtain uncertainty estimates there is the usual computational scaling of the GP of $O(n^3)$, so cubic in the number of data points.
-Many approaches  apply crude approximations and yet still obtain good uncertainty estimates.
-
 Deep learning has become the cornerstone of contemporary artificial intelligence, proving remarkably effective in tackling supervised and unsupervised learning tasks in the {\em large data}, {\em offline}, and {\em gradient-based training} regime.
@@
 
+\subsection{Related Work}
+\label{sec:related}
+%
+% Introduce the laplace GNN + shortcomings
+One common approach for uncertainty with neural networks is a Laplace GNN approximation \citep{daxbergerLaplace2021}.
+The idea is to essentially takes a trained neural network and linearises around the optimal weights.
+The resulting linear model can be used to obtain uncertainty estimates and sometimes improved predictions \citep{immerScalable2021}.
+Given the resultant model is now linear with respect to the weights its is also now possible to convert to a Gaussian process as shown in \citep{immerScalable2021, khan2019approximate}.
+Yet to obtain uncertainty estimates there is the usual computational scaling of the GP of $O(n^3)$, so cubic in the number of data points.
+Many approaches  apply crude approximations and yet still obtain good uncertainty estimates.
+
 %Why we need uncertainty and adaptiveness
@@
 \begin{figure}[t!]
-%  \begin{subfigure}{.48\textwidth}
-%    \centering
-%    \tikz\node[fill=black!10,minimum width=\figurewidth,minimum height=\figureheight,rounded corners=5pt]{};
-%  \end{subfigure}
-%  \hfill
-%  \begin{subfigure}{.48\textwidth}
-%    \centering
-%    \tikz\node[fill=black!10,minimum width=\figurewidth,minimum height=\figureheight,rounded corners=5pt]{};
-%  \end{subfigure}
-
   \centering\scriptsize
@@
     \centering
-    \tikz[overlay,remember picture]\node(p0){.};
+    \tikz[overlay,remember picture]\node(p0){};
   \end{subfigure}  
@@
     \centering
-    \tikz[overlay,remember picture]\node(p1){.};
+    \tikz[overlay,remember picture]\node(p1){};
   \end{subfigure}  
@@
     % Arrows
-    \node[myarrow] (p0-arr) at ($(p0) + (0em,1.5em)$) {};
-    \node[myarrow] (p1-arr) at ($(p1) + (0em,1.5em)$) {};
+    \node[myarrow] (p0-arr) at ($(p0) + (1em,1.5em)$) {};
+    \node[myarrow] (p1-arr) at ($(p1) + (1em,1.5em)$) {};
     % Arrow labels
@@
 
-\textbf{Neural Network} A neural network takes ${\mathcal{D}_n = \{(\vx_i, y_i)\}_{i=1}^n}$ and fits a function $f(\mathbf{x}_{i};\transitionParams)$ through the following optimization:
+\textbf{Neural Network} In supervised learning, given a data set $\dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{N}$, with $\mathbf{x}_i \in \inputDomain$ and $\mathbf{y}_i \in \outputDomain$, the weights $\transitionParams \in \R^{P}$ of a neural network
+, $f_\mathbf{w} : \inputDomain \mapsto \outputDomain$, 
+are usually trained to minimize the (regularized) empirical risk,
 \begin{align} \label{eq-empirical-risk}
-  \transitionParams^{*} = \arg \min_{\transitionParams \in \R^{P}} \mathcal{L}(\dataset;\transitionParams) = \arg \min_{\transitionParams \in \R^{P}} \left(
-  \sum_{i=1}^{N} l(f(\mathbf{x}_{i} ; \transitionParams), y_i) + \frac{1}{\delta}R(\transitionParams)  \right).
+  \transitionParams^{*} = 
+  \argmin_{\transitionParams} \mathcal{L}(\dataset,\transitionParams) =
+  \argmin_{\transitionParams} \sum_{i=1}^{N} \ell(f_\transitionParams(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\transitionParams).
 \end{align}
-If $l(f(\mathbf{x}_{i} ; \transitionParams), y_i) = -\log(p(y \mid f(\mathbf{x}_{i}))$
-
-\textbf{Laplace approximation}
-
-\textbf{Dual Gaussian Process} A Gaussian process (GP) is a prior over functions $f \sim \GP(0, \kappa)$.
-The prior is characterized by a covariance kernel function $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors typically in $\R^{\mathrm{D}}$.
-Once combined with a data set ${\mathcal{D}_n = \{(\vx_i, y_i)\}_{i=1}^n}$ with $n$ examples, each modeled by the likelihood $p(y_i \mid f_i)$ at function $f_i = f(\vx_i)$, we can form a posterior proccess using multivariate conditioning.
+If $\ell(f_\transitionParams(\mathbf{x}_{i}), \mathbf{y}_i) = -\log(p(\mathbf{y} \mid f_\transitionParams(\mathbf{x}_{i}))$ and $\mathcal{R}(\transitionParams) = \|\transitionParams\|^{2}_2$ then we can view \cref{eq-empirical-risk} as the MAP solution to a Bayesian objective, where $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.
+
+\textbf{Laplace approximation} The Laplace approximation allows us to build a posterior approximation $q(\vw)$ from the optimized objective \cref{eq-empirical-risk}.
+
+\textbf{Dual Gaussian Process} A Gaussian process (GP) is a prior over functions $f \sim \GP(\mathbf{0}, \kappa(\cdot, \cdot))$.
+The prior is characterized by a covariance kernel function $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors in $\R^{\mathrm{D}}$.
+Once combined with a data set ${\mathcal{D} = \{(\vx_i, y_i)\}_{i=1}^N}$ with $N$ examples, each modelled by the likelihood $p(\vy_i \mid \vf_i)$ at function $\vf_i = f(\vx_i)$\, we can form a posterior proccess using multivariate conditioning.
 The drawbacks to GPs are their lack of scaling to large datasets and non-tractability with non-Gaussian likelihoods.
 
-Sparse Gaussian processes \citep{hensman2013gaussian} are a principled way to scale Gaussian processes to large datasets by changing the complexity from $O(n^3)$ to $O(m^3)$ with $m$ the number of inducing points, and typically $m \ll n$.
-The key insight is to use a sparse approximating distribution $q(\vu; \vm, \MV)$, where $\vm \in \R^{m}$ and $\MV \in \R^{m \times m}$, and find its parameters through maximizing the evidence lower bound (ELBO).
-The distribution at all over points is then defined as $q_{\vu}(f) = \int p(f \mid \vu) q(\vu) d\vu$.
-The dual parameterization \cite{adam2021dual} states that we can decompose the optimal sparse Gaussian process posterior as follows:
+Sparse Gaussian processes \citep{hensman2013gaussian} are a principled way to scale Gaussian processes to large datasets by using a subset of $M$ inducing points, with $M \ll N$,  lowering the complexity from $\mathcal{O}(N^3)$ to $\mathcal{O}(M^3)$.
+The key insight is to use a sparse approximating distribution $q(\vu; \vm, \MV)$, where $\vm \in \R^{M}$ and $\MV \in \R^{M \times M}$, and find its parameters through maximizing the evidence lower bound (ELBO).
+Then, the distribution over all points is defined as $q_{\vu}(\vf) = \int p(\vf \mid \vu) q(\vu) \mathrm{d}\vu$.
+As shown in \cite{adam2021dual}, we can decompose the optimal sparse GP  with a dual parameterization \cite{adam2021dual} as follows:
 \begin{equation}
-   \myexpect_{q_{\vu}(f)}[f_i] = \vkzs^{\T} \valpha , \quad 
-   \textrm{Var}_{q_{\vu}(f)}[f_i]  = \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \vbeta)^{-1} ]\vkzs.
+   \myexpect_{q_{\vu}(\vf)}[\vf_i] = \vkzs^{\T} \valpha , \quad 
+   \textrm{Var}_{q_{\vu}(\vf)}[\vf_i]  = \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \vbeta)^{-1} ]\vkzs
 \end{equation}
 
-Here, $\MKzz$ to denote the $m \times m$ matrix with $\kappa(\vx_i,\vx_j)$ as the $ij$\textsuperscript{th} entry, Similarly, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
-The dual parameters consist of an $m$-length vector $\valpha$ and $m\times m$-size matrix $\vbeta$, defined as
+where the $ij$th entry of the matrix $\MKzz \in \R^{M \times M}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$\todo{the equation above uses $\vkzs$ not $\vk_{\vx i}$} denotes a vector where each $j$th element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
+The dual parameters consist of the vector $\valpha \in \R^{M}$ and the matrix $\vbeta \in \R^{M\times M}$, defined as
 \begin{equation} 
-   \vlambda = [ \MKzz + \vbeta]\valpha  = \sum_{i \in \mathcal{D}_{n}}  \vkzi \, \tilde{\lambda}_{i}, \quad
-   \vbeta = \sum_{i \in \mathcal{D}_{n}} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,
+	\valpha  = \sum_{i \in \mathcal{D}_{n}}  \vkzi \, \tilde{\lambda}_{i}, \quad
+	\vbeta = \sum_{i \in \mathcal{D}_{n}} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    \vlambda = [ \MKzz + \vbeta]
 \label{eq:dual_sparse}
@@
 
-where $\tilde{\lambda}_i = \alpha_i - \myexpect_{q_{\vu}(f)}[f_i] \hat{\beta}_i$ with $(\hat{\alpha}_i, \hat{\beta}_i)$ defined as,
+where $\tilde{\lambda}_i = \alpha_i - \myexpect_{q_{\vu}(\vf)}[\vf_i] \hat{\beta}_i$ with $(\hat{\alpha}_i, \hat{\beta}_i)$ defined as,
 \begin{equation}
- \alpha_i = \myexpect_{q_{\vu}(f_i)} [\nabla_{f_i}\log p(y_i \mid f_i)], \quad
-   \beta_i = \myexpect_{q_{\vu}(f_i)} [ -\nabla^{2}_{f_i}\log p(y_i \mid f_i)],
+ \alpha_i = \myexpect_{q_{\vu}(\vf_i)} [\nabla_{\vf_i}\log p(\vy_i \mid \vf_i)], \quad
+   \beta_i = \myexpect_{q_{\vu}(\vf_i)} [ -\nabla^{2}_{\vf_i}\log p(\vy_i \mid \vf_i)],
 \label{eq:svgp_dual}

### 2023-05-11 paper/main.tex
small fixes to the paper

@@
 % Introduce the laplace GNN + shortcomings
-One common approach for uncertainty with neural networks is a Laplace GNN approximation \citep{daxbergerLaplace2021}.
-The idea is to essentially takes a trained neural network and linearises around the optimal weights.
-The resulting linear model can be used to obtain uncertainty estimates and sometimes improved predictions \citep{immerScalable2021}.
-Given the resultant model is now linear with respect to the weights its is also now possible to convert to a Gaussian process as shown in \citep{immerScalable2021, khan2019approximate}.
-Yet to obtain uncertainty estimates there is the usual computational scaling of the GP of $O(n^3)$, so cubic in the number of data points.
+One common approach for uncertainty with neural networks is a Laplace GNN approximation \citep{daxbergerLaplace2021}, that takes a trained neural network and linearises it around the optimal weights.
+The resulting linear model can be used to obtain uncertainty estimates and refine the neural network predictions \citep{immerScalable2021}.
+The resultant model is linear with respect to the weights, therefor it is possible to convert it to a Gaussian process (GP) as shown in \citep{immerScalable2021, khan2019approximate}.
+Yet to obtain uncertainty estimates there is the usual computational scaling  cubic in the number of data points of GPs ($\mathcal{O}(n^3)$).
 Many approaches  apply crude approximations and yet still obtain good uncertainty estimates.
@@
 
-\textbf{Neural Network} In supervised learning, given a data set $\dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{N}$, with $\mathbf{x}_i \in \inputDomain$ and $\mathbf{y}_i \in \outputDomain$, the weights $\transitionParams \in \R^{P}$ of a neural network
+\textbf{Neural Network} In supervised learning, given a data set $\dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with $\mathbf{x}_i \in \inputDomain$ and $\mathbf{y}_i \in \outputDomain$, the weights $\transitionParams \in \R^{P}$ of a neural network
 , $f_\mathbf{w} : \inputDomain \mapsto \outputDomain$, 
@@
   \argmin_{\transitionParams} \mathcal{L}(\dataset,\transitionParams) =
-  \argmin_{\transitionParams} \sum_{i=1}^{N} \ell(f_\transitionParams(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\transitionParams).
+  \argmin_{\transitionParams} \sum_{i=1}^{n} \ell(f_\transitionParams(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\transitionParams).
 \end{align}
@@
 The prior is characterized by a covariance kernel function $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors in $\R^{\mathrm{D}}$.
-Once combined with a data set ${\mathcal{D} = \{(\vx_i, y_i)\}_{i=1}^N}$ with $N$ examples, each modelled by the likelihood $p(\vy_i \mid \vf_i)$ at function $\vf_i = f(\vx_i)$\, we can form a posterior proccess using multivariate conditioning.
-The drawbacks to GPs are their lack of scaling to large datasets and non-tractability with non-Gaussian likelihoods.
-
-Sparse Gaussian processes \citep{hensman2013gaussian} are a principled way to scale Gaussian processes to large datasets by using a subset of $M$ inducing points, with $M \ll N$,  lowering the complexity from $\mathcal{O}(N^3)$ to $\mathcal{O}(M^3)$.
-The key insight is to use a sparse approximating distribution $q(\vu; \vm, \MV)$, where $\vm \in \R^{M}$ and $\MV \in \R^{M \times M}$, and find its parameters through maximizing the evidence lower bound (ELBO).
+Once combined with a data set ${\mathcal{D} = \{(\vx_i, y_i)\}_{i=1}^n}$ with $n$ examples, each modelled by the likelihood $p(\vy_i \mid \vf_i)$ at function $\vf_i = f(\vx_i)$\, we can form a posterior proccess using multivariate conditioning.
+The drawbacks of GPs reside in their lack of scaling to large datasets and non-tractability with non-Gaussian likelihoods.
+
+Sparse Gaussian processes \citep{hensman2013gaussian} are a principled way to scale Gaussian processes to large datasets by using a subset of $m$ inducing points, with $m \ll n$,  lowering the complexity from $\mathcal{O}(n^3)$ to $\mathcal{O}(m^3)$.
+The key insight is to use a sparse approximating distribution $q(\vu; \vm, \MV)$, where $\vm \in \R^{m}$ and $\MV \in \R^{m \times m}$, and find its parameters through maximizing the evidence lower bound (ELBO).
 Then, the distribution over all points is defined as $q_{\vu}(\vf) = \int p(\vf \mid \vu) q(\vu) \mathrm{d}\vu$.
@@
 
-where the $ij$th entry of the matrix $\MKzz \in \R^{M \times M}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$\todo{the equation above uses $\vkzs$ not $\vk_{\vx i}$} denotes a vector where each $j$th element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
-The dual parameters consist of the vector $\valpha \in \R^{M}$ and the matrix $\vbeta \in \R^{M\times M}$, defined as
+where the $ij$th entry of the matrix $\MKzz \in \R^{m \times m}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$\todo{the equation above uses $\vkzs$ not $\vk_{\vx i}$} denotes a vector where each $j$th element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
+The dual parameters consist of the vector $\valpha \in \R^{m}$ and the matrix $\vbeta \in \R^{m \times m}$, defined as
 \begin{equation} 

### 2023-05-11 paper/main.tex
started laplace section

@@
 \newcommand{\MLambda}[0]{\mathbold{\Lambda}}
+\newcommand{\MSigma}[0]{\mathbold{\Sigma}}
 \definecolor{matplotlib-blue}{HTML}{1f77b4}
@@
 
-\textbf{Laplace approximation} The Laplace approximation allows us to build a posterior approximation $q(\vw)$ from the optimized objective \cref{eq-empirical-risk}.
+\textbf{Neural network to GP} Our goal is to find a kernel from which to build a sparse Gaussian process model.
+If we had the following function paramaterizatoin $f_i = \phi^\T(\vx)$ we would could simply convert from weight space to function space the prior
+
+% The Laplace approximation allows us to build a posterior approximation $q(\vw)$ from the optimized objective \cref{eq-empirical-risk}.
+Central to the approximation is how to form the hessian of \cref{eq-empirical-risk} a common approach is to use the the GGN approximation which would result in the following posterior $q(\vw;\vw^*, \MSigma_{\textrm{GGN}})$ where
+
+As was pointed out in \citep{immerScalable2021} we can view the approximation in two steps.
+
+Given this interpretation, we can represent the weight space prior from \cref{eq-log-prior}, in
+function space, by linearising the BNN around $\transitionParams^{*}$ and interpretting it as a GP.  
+The GP prior is then given by,
+\begin{align} \label{eq-laplace-approx-function-space}
+  % \transitionFn_{\transitionParams_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \qquad
+  f(\cdot ;\transitionParams) \sim \mathcal{N} \left( \mu(\cdot), k(\cdot, \cdot') \right) \quad
+  % \mu_{\transitionParams_{i}^{*}}(\cdot)
+  \mu(\cdot)
+  = 0 \quad
+  % = f(\cdot ;\transitionParams^{*}) \quad
+  % K_{\transitionParams_{i}^{*}}(\cdot, \cdot')
+  k(\cdot, \cdot')
+  = \frac{1}{\gamma^{2}} \mathbf{J}(\cdot) \mathbf{J}(\cdot')^{T},
+\end{align}
+where the kernel is the neural tangent kernel (NTK) \citep{immerImprovingPredictionsBayesian2021},
+\todo{what mean function shoudl this use???}
+\todo{NTK times some factor??}
+with Jacobian given by $\mathbf{J}(\cdot) = \odv{\transitionFn(\cdot; \transitionParams)}{\transitionParams}_{\transitionParams=\transitionParams^{*}}$.
+% The kernel in \cref{eq-laplace-approx-function-space} is the neural tangent kernel (NTK)
+% $k(\mathbf{x}, \mathbf{x}') = \sigma_{0}^{2} J_{\transitionParams^{*}}(\mathbf{x}) J_{\transitionParams^{*}}(\mathbf{x}')^{T}$
+% \citep{immerImprovingPredictionsBayesian2021}
+% to formulate the GP posterior $p(f(\mathbf{X} ;\transitionParams_{0:i}) \mid \dataset_{0:i})$.
+Given this GP prior, we can use \cref{eq-gp-predictive-posterior} to obtain our GP posterior by conditioning on the data.
+% Given our GP prior, we can use the properties of multivariate normals to obtain our GP posterior by conditioning on the data.
+% where $\mathbf{A} = \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}}$
+In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
+Intuitively, we can view the optimisation in \cref{eq-empirical-risk} as learning our kernel.
+As a result, our NTK may be highly non stationary as it is dependent on the NN architecture, for example, the activation functions.
+It is worth noting that the NTK linearises the network around the optimised parameters $\transitionParams^{*}$,
+so the function space prior (and thus posterior) is only a locally linear approximation.
 

### 2023-05-11 paper/main.tex
paper updates
started laplace section

@@
 \newcommand{\vw}{\mbf{w}}
+
+\newcommand{\Jac}[2]{\mathcal{J}_{#1}(#2)}
 
@@
 \textbf{Neural network to GP} Our goal is to find a kernel from which to build a sparse Gaussian process model.
-If we had the following function paramaterizatoin $f_i = \phi^\T(\vx)$ we would could simply convert from weight space to function space the prior
+If we had the following function parameterization $g_i(\vx) = \phi^\T(\vx)$ we would could simply convert from weight space to function space the prior under the prior distribution meaning $\kappa(\vx, \vx) = \delta^{-1} \phi(\vx) \phi(\vx)^\T$.
+Our
 
@@
   % \transitionFn_{\transitionParams_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \qquad
-  f(\cdot ;\transitionParams) \sim \mathcal{N} \left( \mu(\cdot), k(\cdot, \cdot') \right) \quad
+  g(\vx_i) \sim \mathcal{N} \left( \mu(\vx_i), k(\vx_i, \vx_i) \right) 
   % \mu_{\transitionParams_{i}^{*}}(\cdot)
@@
   % K_{\transitionParams_{i}^{*}}(\cdot, \cdot')
-  k(\cdot, \cdot')
-  = \frac{1}{\gamma^{2}} \mathbf{J}(\cdot) \mathbf{J}(\cdot')^{T},
+  k(\mathbf{x}, \mathbf{x}')
+  = \frac{1}{\gamma^{2}} \Jac{\transitionParams^*}{\mathbf{x}}\Jac{\transitionParams^*}{\mathbf{x}'}^\top,
 \end{align}
@@
 \todo{NTK times some factor??}
-with Jacobian given by $\mathbf{J}(\cdot) = \odv{\transitionFn(\cdot; \transitionParams)}{\transitionParams}_{\transitionParams=\transitionParams^{*}}$.
+with Jacobian given by $\Jac{\transitionParams}{\mathbf{x}} := \nabla_\transitionParams f(\mathbf{x})^\top \in \R^{C \times P}$
+%$\mathbf{J}(\cdot) = \odv{\transitionFn(\cdot; \transitionParams)}{\transitionParams}_{\transitionParams=\transitionParams^{*}}$.
 % The kernel in \cref{eq-laplace-approx-function-space} is the neural tangent kernel (NTK)
@@
 \begin{equation} 
-	\valpha  = \sum_{i \in \mathcal{D}_{n}}  \vkzi \, \tilde{\lambda}_{i}, \quad
-	\vbeta = \sum_{i \in \mathcal{D}_{n}} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    \vlambda = [ \MKzz + \vbeta]
+	\vlambda = [ \MKzz + \vbeta] \valpha  = \sum_{i \in \mathcal{D}_{n}}  \vkzi \, \tilde{\lambda}_{i}, \quad
+	\vbeta = \sum_{i \in \mathcal{D}_{n}} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
 \label{eq:dual_sparse}

### 2023-05-11 paper/main.tex
added Jacobian macro

@@
 \textbf{Neural network to GP} Our goal is to find a kernel from which to build a sparse Gaussian process model.
-If we had the following function parameterization $g_i(\vx) = \phi^\T(\vx)$ we would could simply convert from weight space to function space the prior under the prior distribution meaning $\kappa(\vx, \vx) = \delta^{-1} \phi(\vx) \phi(\vx)^\T$.
-Our
+If we had the following function paramaterizatoin $f_i = \phi^\T(\vx)$ we would could simply convert from weight space to function space the prior
 
@@
   % \transitionFn_{\transitionParams_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \qquad
-  g(\vx_i) \sim \mathcal{N} \left( \mu(\vx_i), k(\vx_i, \vx_i) \right) 
+  f(\cdot ;\transitionParams) \sim \mathcal{N} \left( \mu(\cdot), k(\cdot, \cdot') \right) \quad
   % \mu_{\transitionParams_{i}^{*}}(\cdot)

### 2023-05-11 paper/main.tex
starting to fill out background

--- 2023-05-11 paper/main.tex
@@
 \textbf{Neural network to GP} Our goal is to find a kernel from which to build a sparse Gaussian process model.
-If we had the following function parameterization $g_i(\vx) = \phi^\T(\vx)$ we would could simply convert from weight space to function space the prior under the prior distribution meaning $\kappa(\vx, \vx) = \delta^{-1} \phi(\vx) \phi(\vx)^\T$.
-Our
+If we had the following function parameterization $g_i(\vx) = \phi^\T(\vx)$ we would could simply convert from weight space to function space the prior under the prior distribution meaning $\kappa(\vx, \vx) = \delta^{-1} \phi(\vx) \phi(\vx)^\T$ see \citet{rasmussen2006gaussian} for details.
+We linearise the neural network function
 

### 2023-05-11 paper/main.tex
changed weights macro name

@@
 % Parameters
-% \newcommand{\transitionParams}{\ensuremath{\bm\phi}}
-\newcommand{\transitionParams}{\ensuremath{\mathbf{w}}}
+% \newcommand{\weights}{\ensuremath{\bm\phi}}
+\newcommand{\weights}{\ensuremath{\mathbf{w}}}
 \newcommand{\valueFnParams}{\ensuremath{\psi}}
@@
 % Networks
-\newcommand{\transitionFnWithParams}{\ensuremath{\transitionFn_{\transitionParams}}}
+\newcommand{\transitionFnWithParams}{\ensuremath{\transitionFn_{\weights}}}
 \newcommand{\valueFn}{\ensuremath{\mathbf{Q}}}
@@
 
-\textbf{Neural Network} In supervised learning, given a data set $\dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with $\mathbf{x}_i \in \inputDomain$ and $\mathbf{y}_i \in \outputDomain$, the weights $\transitionParams \in \R^{P}$ of a neural network
+\textbf{Neural Network} In supervised learning, given a data set $\dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with $\mathbf{x}_i \in \inputDomain$ and $\mathbf{y}_i \in \outputDomain$, the weights $\weights \in \R^{P}$ of a neural network
 , $f_\mathbf{w} : \inputDomain \mapsto \outputDomain$, 
@@
 \begin{align} \label{eq-empirical-risk}
-  \transitionParams^{*} = 
-  \argmin_{\transitionParams} \mathcal{L}(\dataset,\transitionParams) =
-  \argmin_{\transitionParams} \sum_{i=1}^{n} \ell(f_\transitionParams(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\transitionParams).
+  \weights^{*} = 
+  \argmin_{\weights} \mathcal{L}(\dataset,\weights) =
+  \argmin_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
 \end{align}
-If $\ell(f_\transitionParams(\mathbf{x}_{i}), \mathbf{y}_i) = -\log(p(\mathbf{y} \mid f_\transitionParams(\mathbf{x}_{i}))$ and $\mathcal{R}(\transitionParams) = \|\transitionParams\|^{2}_2$ then we can view \cref{eq-empirical-risk} as the MAP solution to a Bayesian objective, where $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.
+If $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) = -\log(p(\mathbf{y} \mid f_\weights(\mathbf{x}_{i}))$ and $\mathcal{R}(\weights) = \|\weights\|^{2}_2$ then we can view \cref{eq-empirical-risk} as the MAP solution to a Bayesian objective, where $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.
 
@@
 Given this interpretation, we can represent the weight space prior from \cref{eq-log-prior}, in
-function space, by linearising the BNN around $\transitionParams^{*}$ and interpretting it as a GP.
+function space, by linearising the BNN around $\weights^{*}$ and interpretting it as a GP.
 The GP prior is then given by,
 \begin{align} \label{eq-laplace-approx-function-space}
-  % \transitionFn_{\transitionParams_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \qquad
+  % \transitionFn_{\weights_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \qquad
   g(\vx_i) \sim \mathcal{N} \left( \mu(\vx_i), k(\vx_i, \vx_i) \right) 
-  % \mu_{\transitionParams_{i}^{*}}(\cdot)
+  % \mu_{\weights_{i}^{*}}(\cdot)
   \mu(\cdot)
   = 0 \quad
-  % = f(\cdot ;\transitionParams^{*}) \quad
-  % K_{\transitionParams_{i}^{*}}(\cdot, \cdot')
+  % = f(\cdot ;\weights^{*}) \quad
+  % K_{\weights_{i}^{*}}(\cdot, \cdot')
   k(\mathbf{x}, \mathbf{x}')
-  = \frac{1}{\gamma^{2}} \Jac{\transitionParams^*}{\mathbf{x}}\Jac{\transitionParams^*}{\mathbf{x}'}^\top,
+  = \frac{1}{\gamma^{2}} \Jac{\weights^*}{\mathbf{x}}\Jac{\weights^*}{\mathbf{x}'}^\top,
 \end{align}
@@
 \todo{NTK times some factor??}
-with Jacobian given by $\Jac{\transitionParams}{\mathbf{x}} := \nabla_\transitionParams f(\mathbf{x})^\top \in \R^{C \times P}$
-%$\mathbf{J}(\cdot) = \odv{\transitionFn(\cdot; \transitionParams)}{\transitionParams}_{\transitionParams=\transitionParams^{*}}$.
+with Jacobian given by $\Jac{\weights}{\mathbf{x}} := \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$
+%$\mathbf{J}(\cdot) = \odv{\transitionFn(\cdot; \weights)}{\weights}_{\weights=\weights^{*}}$.
 % The kernel in \cref{eq-laplace-approx-function-space} is the neural tangent kernel (NTK)
-% $k(\mathbf{x}, \mathbf{x}') = \sigma_{0}^{2} J_{\transitionParams^{*}}(\mathbf{x}) J_{\transitionParams^{*}}(\mathbf{x}')^{T}$
+% $k(\mathbf{x}, \mathbf{x}') = \sigma_{0}^{2} J_{\weights^{*}}(\mathbf{x}) J_{\weights^{*}}(\mathbf{x}')^{T}$
 % \citep{immerImprovingPredictionsBayesian2021}
-% to formulate the GP posterior $p(f(\mathbf{X} ;\transitionParams_{0:i}) \mid \dataset_{0:i})$.
+% to formulate the GP posterior $p(f(\mathbf{X} ;\weights_{0:i}) \mid \dataset_{0:i})$.
 Given this GP prior, we can use \cref{eq-gp-predictive-posterior} to obtain our GP posterior by conditioning on the data.
@@
 As a result, our NTK may be highly non stationary as it is dependent on the NN architecture, for example, the activation functions.
-It is worth noting that the NTK linearises the network around the optimised parameters $\transitionParams^{*}$,
+It is worth noting that the NTK linearises the network around the optimised parameters $\weights^{*}$,
 so the function space prior (and thus posterior) is only a locally linear approximation.
@@
 % We paraterise our single-step dynamic model $\transitionFnWithParams : \inputDomain \rightarrow \outputDomain$
-% as an $L\text{-layer}$ NN with weights $\transitionParams$.
+% as an $L\text{-layer}$ NN with weights $\weights$.
 
@@
 %and corresponding outputs
-%$\mathbf{u} = f(\mathbf{Z}; \transitionParams) \in \R^{M \times C}$, known as inducing variables, where $M \ll N$.
+%$\mathbf{u} = f(\mathbf{Z}; \weights) \in \R^{M \times C}$, known as inducing variables, where $M \ll N$.
 %\todo{cite sparse gp papers}
@@
 %Given the data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
-%the goal of (supervised) deep learning, is to train the weights $\transitionParams \in \R^{P}$ of an $L\text{-layer}$ NN
+%the goal of (supervised) deep learning, is to train the weights $\weights \in \R^{P}$ of an $L\text{-layer}$ NN
 %$f : \inputDomain \rightarrow \outputDomain$ to minimize the (regularized) empirical risk,
 %\begin{align} \label{eq-empirical-risk}
-%  \transitionParams^{*} = \arg \min_{\transitionParams \in \R^{D}} \mathcal{L}(\dataset;\transitionParams) = \arg \min_{\transitionParams \in \R^{D}} \left(
-%  \sum_{n=0}^{N-1} l(f(\mathbf{x}_{n} ; \transitionParams), \mathbf{y}_{n}) + R(\transitionParams)  \right).
+%  \weights^{*} = \arg \min_{\weights \in \R^{D}} \mathcal{L}(\dataset;\weights) = \arg \min_{\weights \in \R^{D}} \left(
+%  \sum_{n=0}^{N-1} l(f(\mathbf{x}_{n} ; \weights), \mathbf{y}_{n}) + R(\weights)  \right).
 %\end{align}
 %In practice, it is common to use the mean squared error (MSE) loss
-%$l(f(\mathbf{x}_{n} ; \transitionParams),\mathbf{y}_{n}) = \|f(\mathbf{x}_{n} ; \transitionParams) - \mathbf{y}_{n} \|^{2}_{2}$
-%and to use the weight decay regularizer $R(\transitionParams)=\frac{1}{2}\gamma^{-2}\|\transitionParams\|^{2}_{2}$.
+%$l(f(\mathbf{x}_{n} ; \weights),\mathbf{y}_{n}) = \|f(\mathbf{x}_{n} ; \weights) - \mathbf{y}_{n} \|^{2}_{2}$
+%and to use the weight decay regularizer $R(\weights)=\frac{1}{2}\gamma^{-2}\|\weights\|^{2}_{2}$.
 %However, the practioner is free to choose any loss and regularizer. \todo{I think?}
@@
 %\begin{align} \label{eq-log-prior}
-%  R(\transitionParams) &= \underbrace{\log p(\transitionParams)}_{\text{log prior}} = \log \mathcal{N}(\transitionParams \mid 0, \gamma^{2} \mathbf{I}) \\
-%  l(f(\mathbf{x}_{n} ; \transitionParams), \mathbf{y}_{n}) &= \underbrace{\log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \transitionParams))}_{\text{log likelihood}}
-%  = \log \mathcal{N} \left( \mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \transitionParams), \mathbf{I} \right) \label{eq-log-likelihood}
+%  R(\weights) &= \underbrace{\log p(\weights)}_{\text{log prior}} = \log \mathcal{N}(\weights \mid 0, \gamma^{2} \mathbf{I}) \\
+%  l(f(\mathbf{x}_{n} ; \weights), \mathbf{y}_{n}) &= \underbrace{\log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \weights))}_{\text{log likelihood}}
+%  = \log \mathcal{N} \left( \mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \weights), \mathbf{I} \right) \label{eq-log-likelihood}
 %\end{align}
@@
 %Given this interpretation, we can represent the weight space prior from \cref{eq-log-prior}, in
-%function space, by linearising the BNN around $\transitionParams^{*}$ and interpretting it as a GP.
+%function space, by linearising the BNN around $\weights^{*}$ and interpretting it as a GP.
 %The GP prior is then given by,
 %\begin{align} \label{eq-laplace-approx-function-space}
-%  % \transitionFn_{\transitionParams_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \qquad
-%  f(\cdot ;\transitionParams) \sim \mathcal{N} \left( \mu(\cdot), k(\cdot, \cdot') \right) \quad
-%  % \mu_{\transitionParams_{i}^{*}}(\cdot)
+%  % \transitionFn_{\weights_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \qquad
+%  f(\cdot ;\weights) \sim \mathcal{N} \left( \mu(\cdot), k(\cdot, \cdot') \right) \quad
+%  % \mu_{\weights_{i}^{*}}(\cdot)
 %  \mu(\cdot)
 %  = 0 \quad
-%  % = f(\cdot ;\transitionParams^{*}) \quad
-%  % K_{\transitionParams_{i}^{*}}(\cdot, \cdot')
+%  % = f(\cdot ;\weights^{*}) \quad
+%  % K_{\weights_{i}^{*}}(\cdot, \cdot')
 %  k(\cdot, \cdot')
@@
 %\todo{NTK times some factor??}
-%with Jacobian given by $\mathbf{J}(\cdot) = \odv{\transitionFn(\cdot; \transitionParams)}{\transitionParams}_{\transitionParams=\transitionParams^{*}}$.
+%with Jacobian given by $\mathbf{J}(\cdot) = \odv{\transitionFn(\cdot; \weights)}{\weights}_{\weights=\weights^{*}}$.
 %% The kernel in \cref{eq-laplace-approx-function-space} is the neural tangent kernel (NTK)
-%% $k(\mathbf{x}, \mathbf{x}') = \sigma_{0}^{2} J_{\transitionParams^{*}}(\mathbf{x}) J_{\transitionParams^{*}}(\mathbf{x}')^{T}$
+%% $k(\mathbf{x}, \mathbf{x}') = \sigma_{0}^{2} J_{\weights^{*}}(\mathbf{x}) J_{\weights^{*}}(\mathbf{x}')^{T}$
 %% \citep{immerImprovingPredictionsBayesian2021}
-%% to formulate the GP posterior $p(f(\mathbf{X} ;\transitionParams_{0:i}) \mid \dataset_{0:i})$.
+%% to formulate the GP posterior $p(f(\mathbf{X} ;\weights_{0:i}) \mid \dataset_{0:i})$.
 %Given this GP prior, we can use \cref{eq-gp-predictive-posterior} to obtain our GP posterior by conditioning on the data.
@@
 %As a result, our NTK may be highly non stationary as it is dependent on the NN architecture, for example, the activation functions.
-%It is worth noting that the NTK linearises the network around the optimised parameters $\transitionParams^{*}$,
+%It is worth noting that the NTK linearises the network around the optimised parameters $\weights^{*}$,
 %so the function space prior (and thus posterior) is only a locally linear approximation.
@@
 %% In contrast, to previous work, this approach did not require us Laplace approximation. we will not restrict our
-%% It is worth noting that the NTK linearises the network around the optimised parameters $\transitionParams^{*}$,
+%% It is worth noting that the NTK linearises the network around the optimised parameters $\weights^{*}$,
 %% so the function space prior (and thus posterior) is only a locally linear approximation.
@@
 %% We follow \cite{csatoSparseOnlineGaussian2002} and express our GP posterior in the dual parameter space,
-%% % to write GP posterior $p(f(\mathbf{X} ;\transitionParams_{0:i}) \mid \dataset_{0:i})$ as,
+%% % to write GP posterior $p(f(\mathbf{X} ;\weights_{0:i}) \mid \dataset_{0:i})$ as,
 %% \begin{align} \label{eq-gp-post}
@@
 %% \begin{align} \label{eq-laplace-approx-function-space}
-%%   \transitionFn_{\transitionParams_{i}}(\cdot) &\sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \quad
-%%   \mu_{\transitionParams_{i}^{*}}(\cdot) &= \transitionFn_{\transitionParams^{*}_{i}}(\cdot) \quad
-%%   K_{\transitionParams_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) \bm\Sigma_{\transitionParams^{*}_{i}} \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot')^{T}
+%%   \transitionFn_{\weights_{i}}(\cdot) &\sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \quad
+%%   \mu_{\weights_{i}^{*}}(\cdot) &= \transitionFn_{\weights^{*}_{i}}(\cdot) \quad
+%%   K_{\weights_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\weights^{*}_{i}}(\cdot) \bm\Sigma_{\weights^{*}_{i}} \mathbf{J}_{\weights^{*}_{i}}(\cdot')^{T}
 %% \end{align}
-%% where the Jacobian is given by $\mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}$.
+%% where the Jacobian is given by $\mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}$.
 %
 %% \begin{align} \label{eq-laplace-approx-jacobian}
-%% \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}
+%% \mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}
 %% \end{align}
@@
 %% \begin{align} \label{eq-laplace-approx-function-space}
-%%   \transitionFn_{\transitionParams_{i}^{*}}(\cdot) &\sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \quad
-%%   \mu_{\transitionParams_{i}^{*}}(\cdot) &= \transitionFn_{\transitionParams^{*}_{i}}(\cdot) \quad
-%%   K_{\transitionParams_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) \bm\Sigma_{\transitionParams^{*}_{i}} \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot')^{T}
+%%   \transitionFn_{\weights_{i}^{*}}(\cdot) &\sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \quad
+%%   \mu_{\weights_{i}^{*}}(\cdot) &= \transitionFn_{\weights^{*}_{i}}(\cdot) \quad
+%%   K_{\weights_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\weights^{*}_{i}}(\cdot) \bm\Sigma_{\weights^{*}_{i}} \mathbf{J}_{\weights^{*}_{i}}(\cdot')^{T}
 %% \end{align}
-%% where the Jacobian is given by $\mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}$.
+%% where the Jacobian is given by $\mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}$.
 %
 %% \begin{align} \label{eq-laplace-approx-jacobian}
-%% \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}
+%% \mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}
 %% \end{align}
@@
 \textbf{Laplace approximation}
-The Laplace approximation \todo{add citation of original paper} constructs a Gaussian approximation of the weight-space posterior $p(\transitionParams \mid \dataset)$
-by using a second-order Taylor expansion of $\mathcal{L}$ around $\transitionParams^{*}$.
+The Laplace approximation \todo{add citation of original paper} constructs a Gaussian approximation of the weight-space posterior $p(\weights \mid \dataset)$
+by using a second-order Taylor expansion of $\mathcal{L}$ around $\weights^{*}$.
 The posterior approximation is given by,
 \begin{align} \label{eq-laplace-approx-weight-space}
-  p(\transitionParams \mid \dataset) \approx \mathcal{N} \left( \transitionParams \mid \transitionParams^{*} , \bm\Sigma_{\transitionParams^{*}} \right)
-  \quad \text{with} \quad \bm\Sigma_{\transitionParams} =
- - \nabla_{\transitionParams \transitionParams}^{2} \mathcal{L} ( \dataset ; \transitionParams)|_{\transitionParams=\transitionParams^{*}}
+  p(\weights \mid \dataset) \approx \mathcal{N} \left( \weights \mid \weights^{*} , \bm\Sigma_{\weights^{*}} \right)
+  \quad \text{with} \quad \bm\Sigma_{\weights} =
+ - \nabla_{\weights \weights}^{2} \mathcal{L} ( \dataset ; \weights)|_{\weights=\weights^{*}}
 \end{align}
-That is, it sets the posterior precision to the Hessian of the loss at the optimal parameters $\transitionParams^{*}$.
+That is, it sets the posterior precision to the Hessian of the loss at the optimal parameters $\weights^{*}$.
 It is worth noting that computing the Hessian of the loss can be computationally intractable for large networks.
@@
 \begin{align} \label{eq-jac}
-  \nabla_{\transitionParams} \log p(\mathbf{y} \mid \mathbf{f}(\mathbf{x}; \transitionParams)) &= \mathbf{J}(\mathbf{x})^{T} \mathbf{r}(\mathbf{y} ; \mathbf{f}) \\
-  \nabla^{2}_{\transitionParams\transitionParams} \log p(\mathbf{y} \mid \mathbf{f}(\mathbf{x}; \transitionParams)) &= \mathbf{H}(\mathbf{x})^{T}
+  \nabla_{\weights} \log p(\mathbf{y} \mid \mathbf{f}(\mathbf{x}; \weights)) &= \mathbf{J}(\mathbf{x})^{T} \mathbf{r}(\mathbf{y} ; \mathbf{f}) \\
+  \nabla^{2}_{\weights\weights} \log p(\mathbf{y} \mid \mathbf{f}(\mathbf{x}; \weights)) &= \mathbf{H}(\mathbf{x})^{T}
   \mathbf{r}(\mathbf{y};\mathbf{f}) - \mathbf{J}(\mathbf{x})^{T} \bm\Lambda(\mathbf{y};\mathbf{f}) \mathbf{J}(\mathbf{x}),
@@
 \end{align}
-through the Jacobian $\mathbf{J} \in \R^{C \times P}$ and Hessian $\mathbf{H} \in \R^{C \times P \times P}$ of the feature extractor $\mathbf{f}(\mathbf{x}; \bm\transitionParams)$,
+through the Jacobian $\mathbf{J} \in \R^{C \times P}$ and Hessian $\mathbf{H} \in \R^{C \times P \times P}$ of the feature extractor $\mathbf{f}(\mathbf{x}; \bm\weights)$,
 \begin{align} \label{eq-jac}
-[\mathbf{J}(\cdot)]_{ci} = \odv{f_{c}(\cdot ; \transitionParams)}{\transitionParams_{i}}_{\transitionParams=\transitionParams^{*}} \qquad
-[\mathbf{H}(\cdot)]_{cij} = \odv{f_{c}(\cdot ; \transitionParams)}{\transitionParams_{i}\transitionParams_{j}}_{\transitionParams=\transitionParams^{*}}
+[\mathbf{J}(\cdot)]_{ci} = \odv{f_{c}(\cdot ; \weights)}{\weights_{i}}_{\weights=\weights^{*}} \qquad
+[\mathbf{H}(\cdot)]_{cij} = \odv{f_{c}(\cdot ; \weights)}{\weights_{i}\weights_{j}}_{\weights=\weights^{*}}
 \end{align}

### 2023-05-11 paper/main.tex
started new related work section

@@
 \textbf{Neural network to GP} Our goal is to find a kernel from which to build a sparse Gaussian process model.
-If we had the following function parameterization $g_i(\vx) = \phi^\T(\vx)$ we would could simply convert from weight space to function space the prior under the prior distribution meaning $\kappa(\vx, \vx) = \delta^{-1} \phi(\vx) \phi(\vx)^\T$ see \citet{rasmussen2006gaussian} for details.
-We linearise the neural network function
+If we had the following function parameterization $g_i(\vx) = \phi^\T(\vx)$ we would could simply convert from weight space to function space the prior under the prior distribution meaning $\kappa(\vx, \vx) = \delta^{-1} \phi(\vx) \phi(\vx)^\T$ see \citep{rasmussen2006gaussian} for details.
+We use the jacobian of the function $f_\transitionParams(\mathbf{x}_{i})$ and set that to be $\phi(\vx)$.
 

### 2023-05-11 src/rl/train.py
use cpu

@@ -92,6 +92,7 @@ def train(cfg: DictConfig):
     torch.backends.cudnn.benchmark = False
 
     cfg.device = "cuda" if torch.cuda.is_available() else "cpu"
+    cfg.device = "cpu"
     print("Using device: {}".format(cfg.device))
     cfg.episode_length = cfg.episode_length // cfg.env.action_repeat
     num_train_steps = cfg.num_train_episodes * cfg.episode_length

### 2023-05-11 paper/main.tex
started new related work section

--- 2023-05-11 paper/main.tex
@@
 \textbf{Neural network to GP} Our goal is to find a kernel from which to build a sparse Gaussian process model.
-If we had the following function parameterization $g_i(\vx) = \phi^\T(\vx)$ we would could simply convert from weight space to function space the prior under the prior distribution meaning $\kappa(\vx, \vx) = \delta^{-1} \phi(\vx) \phi(\vx)^\T$ see \citet{rasmussen2006gaussian} for details.
-We linearise the neural network function
-
-% The Laplace approximation allows us to build a posterior approximation $q(\vw)$ from the optimized objective \cref{eq-empirical-risk}.
-Central to the approximation is how to form the hessian of \cref{eq-empirical-risk} a common approach is to use the the GGN approximation which would result in the following posterior $q(\vw;\vw^*, \MSigma_{\textrm{GGN}})$ where
-
-As was pointed out in \citep{immerScalable2021} we can view the approximation in two steps.
-
-Given this interpretation, we can represent the weight space prior from \cref{eq-log-prior}, in
-function space, by linearising the BNN around $\weights^{*}$ and interpretting it as a GP.
-The GP prior is then given by,
+If we had the following function parameterization $g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx) = \delta^{-1} \phi(\vx) \phi(\vx)^\T$ see \citep{rasmussen2006gaussian} for details.
+We can approximate the feature map of the neural network  $f_\weights(\mathbf{x}_{i})$  by using the Jacobian at $\weights^*$ giving thus our GP prior becomes:
 \begin{align} \label{eq-laplace-approx-function-space}
@@
 \end{align}
-where the kernel is the neural tangent kernel (NTK) \citep{immerImprovingPredictionsBayesian2021},
-\todo{what mean function shoudl this use???}
-\todo{NTK times some factor??}
-with Jacobian given by $\Jac{\weights}{\mathbf{x}} := \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$
-%$\mathbf{J}(\cdot) = \odv{\transitionFn(\cdot; \weights)}{\weights}_{\weights=\weights^{*}}$.
-% The kernel in \cref{eq-laplace-approx-function-space} is the neural tangent kernel (NTK)
-% $k(\mathbf{x}, \mathbf{x}') = \sigma_{0}^{2} J_{\weights^{*}}(\mathbf{x}) J_{\weights^{*}}(\mathbf{x}')^{T}$
-% \citep{immerImprovingPredictionsBayesian2021}
-% to formulate the GP posterior $p(f(\mathbf{X} ;\weights_{0:i}) \mid \dataset_{0:i})$.
-Given this GP prior, we can use \cref{eq-gp-predictive-posterior} to obtain our GP posterior by conditioning on the data.
-% Given our GP prior, we can use the properties of multivariate normals to obtain our GP posterior by conditioning on the data.
-% where $\mathbf{A} = \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}}$
-In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
-Intuitively, we can view the optimisation in \cref{eq-empirical-risk} as learning our kernel.
-As a result, our NTK may be highly non stationary as it is dependent on the NN architecture, for example, the activation functions.
-It is worth noting that the NTK linearises the network around the optimised parameters $\weights^{*}$,
-so the function space prior (and thus posterior) is only a locally linear approximation.
+where the kernel is the neural tangent kernel (NTK) ,with Jacobian given by $\Jac{\weights}{\mathbf{x}} := \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$.
+Alternatively we could have followed the derivation in \citet{immerImprovingPredictionsBayesian2021} where we perform a local linearization of the neural network prediction function $f^{\textrm{lin}}$
 

### 2023-05-11 bnn-predictive/experiments/scripts/imginference.py
Testing fmnist

@@ -156,7 +156,7 @@ def main(
     res_dir="experiments/results",
     device="cuda",
 ):
-    lh = CategoricalLh(EPS=0.00000000000001)
+    lh = CategoricalLh(EPS=0.000000000000000001)
 
     eligible_files = list()
     deltas = list()

### 2023-05-11 paper/main.tex

@@
 
-\textbf{Neural network to GP} Our goal is to find a kernel from which to build a sparse Gaussian process model.
+\textbf{Neural network to GP prior} Our goal is to find a kernel from which to build a sparse Gaussian process model.
 If we had the following function parameterization $g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx) = \delta^{-1} \phi(\vx) \phi(\vx)^\T$ see \citep{rasmussen2006gaussian} for details.
-We can approximate the feature map of the neural network  $f_\weights(\mathbf{x}_{i})$  by using the Jacobian at $\weights^*$ giving thus our GP prior becomes:
+We can approximate the feature map of the neural network  $f_\weights(\mathbf{x}_{i})$  by using the Jacobian at $\weights^*$ thus our GP prior becomes:
 \begin{align} \label{eq-laplace-approx-function-space}
-  % \transitionFn_{\weights_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \qquad
  g(\vx_i) \sim \mathcal{N} \left( \mu(\vx_i), k(\vx_i, \vx_i) \right) 
-  % \mu_{\weights_{i}^{*}}(\cdot)
   \mu(\cdot)
   = 0 \quad
-  % = f(\cdot ;\weights^{*}) \quad
-  % K_{\weights_{i}^{*}}(\cdot, \cdot')
   k(\mathbf{x}, \mathbf{x}')
-  = \frac{1}{\gamma^{2}} \Jac{\weights^*}{\mathbf{x}}\Jac{\weights^*}{\mathbf{x}'}^\top,
+  = \frac{1}{\delta} \Jac{\weights^*}{\mathbf{x}}\Jac{\weights^*}{\mathbf{x}'}^\top,
 \end{align}
 where the kernel is the neural tangent kernel (NTK) ,with Jacobian given by $\Jac{\weights}{\mathbf{x}} := \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$.
-Alternatively we could have followed the derivation in \citet{immerImprovingPredictionsBayesian2021} where we perform a local linearization of the neural network prediction function $f^{\textrm{lin}}$
-
-\textbf{Dual Gaussian Process} A Gaussian process (GP) is a prior over functions $f \sim \GP(\mathbf{0}, \kappa(\cdot, \cdot))$.
+Alternatively we could have followed the derivation in \citet{immerImprovingPredictionsBayesian2021} where we perform a local linearization of the neural network prediction function $f^{\textrm{lin}}_{\vw^*}(\vx) = f_{\vw^*}(\vx) + \Jac{\weights^*}{\mathbf{x}} (\vw - \vw^*)$.
+The difference with our GP prior in \cref{eq-laplace-approx-function-space} would be a slightly different linear
+
+\textbf{Dual Gaussian Process} A Gaussian process characterizes a distribution over functions in terms of the first two moment. Seminal work by \citet{}
+
+A Gaussian process (GP) is a prior over functions $f \sim \GP(\mathbf{0}, \kappa(\cdot, \cdot))$.
 The prior is characterized by a covariance kernel function $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors in $\R^{\mathrm{D}}$.

### 2023-05-11 paper/main.tex
Abstratct

@@
 % Rewrite on 2023-05-10
-Deep neural networks are known to lack uncertainty estimates, struggle to incorporate new data, and fail to retain previous knowledge.
+%Deep neural networks are known to lack uncertainty estimates, struggle to incorporate new data, and fail to retain previous knowledge.
 We present a method that mitigates these issues by transforming a weight-space neural network to a low-rank function-space representation, via the so-called dual parameters.
@@
 This offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst retaining predictive performance.
-We demonstrate the proposed approach in quantifying uncertainty in supervised learning, maintaining a summary representation in continual learning, and in active learning.
+We demonstrate the proposed approach for quantifying uncertainty in supervised learning and maintaining a compact representation in sequential learning.\looseness-1
+
+Deep neural networks are known to lack uncertainty estimates, struggle to incorporate new data, and suffer from catastrophic forgetting.
+We present a method that mitigates these issues by converting the neural network from weight-space to a low-rank function-space representation, via the so-called dual parameters.
+In contrast to previous work, we model the joint distribution across the entire data set rather than a subset.
+Our approach offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst retaining predictive performance.
+We demonstrate the proposed approach for quantifying uncertainty in supervised learning and maintaining an expressive functional representation for sequential learning.
+
 \end{abstract}
+
+%, maintaining a summary representation in continual learning,
 

### 2023-05-12 bnn-predictive/experiments/scripts/imginference.py
Running with EPS 0 and smaller jitter

@@ -156,7 +156,7 @@ def main(
     res_dir="experiments/results",
     device="cuda",
 ):
-    lh = CategoricalLh(EPS=0.000000000000000001)
+    lh = CategoricalLh(EPS=0)  #0.000000000000000001)
 
     eligible_files = list()
     deltas = list()
@@ -237,6 +237,7 @@ def main(
             likelihood=lh,
             num_inducing=n_inducing,
             dual_batch_size=batch_size,
+            jitter=10**(-9),
             device=device,
         )
         svgp.set_data(data)
@@ -613,6 +614,9 @@ if __name__ == "__main__":
     print(f"Reading data from {data_dir}")
     print(f"Dataset: {dataset}")
     print(f"Seed: {args.seed}")
+
+
+    torch.set_default_dtype(torch.double)
 
     device = "cuda" if torch.cuda.is_available() else "cpu"
     torch.set_default_device(device)

### 2023-05-12 paper/main.tex

@@
 Deep neural networks are known to lack uncertainty estimates, struggle to incorporate new data, and suffer from catastrophic forgetting.
-We present a method that mitigates these issues by converting the neural network from weight-space to a low-rank function-space representation, via the so-called dual parameters.
-In contrast to previous work, we model the joint distribution across the entire data set rather than a subset.
-Our approach offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst retaining predictive performance.
-We demonstrate the proposed approach for quantifying uncertainty in supervised learning and maintaining an expressive functional representation for sequential learning.
+We present a method that mitigates these issues by converting neural networks from weight-space to a low-rank function-space representation, via the so-called dual parameters.
+In contrast to previous work, our sparse representation captures the joint distribution over the entire data set, rather than only over a subset.
+This offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst retaining predictive performance.
+We demonstrate the proposed approach for quantifying uncertainty in supervised learning and maintaining an expressive functional representation for sequential learning.\looseness-1
 

### 2023-05-12 paper/main.tex
written some dual variable stuff

@@
 \newcommand{\vlambda}[0]{\mathbold{\lambda}}
+\newcommand{\diag}{\text{{diag}}}
 
@@
 
-\textbf{Neural network to GP prior} Our goal is to find a kernel from which to build a sparse Gaussian process model.
+\textbf{Neural network to GP prior} Our goal is to find a kernel from which to build a sparse Gaussian process model, central to this is a kernel function  $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors in $\R^{\mathrm{D}}$.
 If we had the following function parameterization $g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx) = \delta^{-1} \phi(\vx) \phi(\vx)^\T$ see \citep{rasmussen2006gaussian} for details.
@@
 \begin{align} \label{eq-laplace-approx-function-space}
- g(\vx_i) \sim \mathcal{N} \left( \mu(\vx_i), k(\vx_i, \vx_i) \right) 
-  \mu(\cdot)
-  = 0 \quad
+ g(\vx_i) \sim \mathcal{N} \left( \mu(\vx_i), k(\vx_i, \vx_i) \right) \quad
+  \mu(\vx)
+  = \vzeros \quad
   k(\mathbf{x}, \mathbf{x}')
@@
 where the kernel is the neural tangent kernel (NTK) ,with Jacobian given by $\Jac{\weights}{\mathbf{x}} := \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$.
-Alternatively we could have followed the derivation in \citet{immerImprovingPredictionsBayesian2021} where we perform a local linearization of the neural network prediction function $f^{\textrm{lin}}_{\vw^*}(\vx) = f_{\vw^*}(\vx) + \Jac{\weights^*}{\mathbf{x}} (\vw - \vw^*)$.
-The difference with our GP prior in \cref{eq-laplace-approx-function-space} would be a slightly different linear
-
-\textbf{Dual Gaussian Process} A Gaussian process characterizes a distribution over functions in terms of the first two moment. Seminal work by \citet{}
+Alternatively we could have followed the derivation in \citet{immerImprovingPredictionsBayesian2021} where we perform a local linearization of the neural network prediction function $f^{\textrm{lin}}_{\vw^*}(\vx; \vw) = f_{\vw^*}(\vx) + \Jac{\weights^*}{\mathbf{x}} (\vw - \vw^*)$.
+The difference with our GP prior mean function and \cref{eq-laplace-approx-function-space} is a different mean prior function which comes from $f^{\textrm{lin}}_{\vw^*}(\vx; \vzeros) = f_{\vw^*}(\vx) - \Jac{\weights^*}{\mathbf{x}} \vw^*$, essentially they use the difference from the linear model approximation and the neural network function, which does not seem useful as a prior mean function, so instead we use $ \mu(\vx_i) = \vzeros$ as is common in GP literature and derived from a feature map conversion.
+
+As stated in \citet[Lemma~1]{csato2002sparse} the posterior process mean and covariance function of a GP prior combined with a likelihood function and $\dataset$ can be stated as:
+\begin{equation}  \label{eq:gp_pred}
+ \myexpect_{p(f\mid\vy)}[f_i] = \vk_{\vx i}^\top \valpha , \quad
+\textrm{Var}_{p(f\mid\vy)}[f_i] = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
+\end{equation}
+where $(\valpha,\vbeta)$ are vectors of
+\begin{equation}
+\label{eq:dual_param}
+\alpha_i \coloneqq\myexpect_{p(f_i \mid \vy)}[\nabla_{f_i}\log p(y_i \mid f_i)],  \quad
+\beta_i \coloneqq - \myexpect_{p(f_i \mid \vy)}[\nabla^2_{f_i}\log p(y_i \mid f_i)] ,
+\end{equation}
+The parameters $(\alpha_i, \beta_i)$ are the dual parameters that arise in the dual formulations used in, for example, support vector machines \citep{cortes1995support}, whose origins are found in work by \citet{kimeldorf1971some}.
+The above relations holds for generic likelihoods, and no approximations are involved as the expectation is under the exact posterior.
+The question is how do we form the dual variables without access to the exact posterior and different approximate inference techniques solve the question in different ways.
+Bound techniques such as \citet{jaakkola1997variational} attempt to bound the integral thus making the integral tractable, while Expecation Propogation (EP) as used in \citet{csato2002sparse} iteratively finds dual variables but sets them to log of the expectation of the approximate posterior.
+Meanwhile variational inference  \cite{khan2017conjugate, adam2021dual} find them using the variational approximation of the posterior to solve the integral.
+
+As we are using the MAP solution of the neural network loss we will use the Laplace approximation for the dual variables but other techniques could be used.
+As was detailed in \cite{wilkinson2023bayes, rasmussen2006gaussian} the dual variables of the Laplace approximation is the same as removing the posterior averaging from \cref{eq:dual_param} meaning:
+\begin{equation}
+\label{eq:dual_param_laplace}
+\hat{\alpha}_i \coloneqq \nabla_{f_i}\log p(y_i \mid f_i),  \quad
+\hat{\beta}_i \coloneqq - \nabla^2_{f_i}\log p(y_i \mid f_i),
+\end{equation}
+
+Replacing \cref{eq:dual_param_laplace} in to \cref{eq-laplace-approx-function-space} and we arrive at our GP model based on the converged neural network.
+
+\textbf{Dual Gaussian Process} A Gaussian process characterizes a distribution over functions in terms of the first two moment.
 

### 2023-05-12 src/rl/agents/objectives.py
added no_grad around predict

@@ -75,6 +75,7 @@ def greedy(
                 )
             return state_trajectory
 
+    @torch.no_grad()
     def greedy_fn(start_state: State, actions: ActionTrajectory) -> TensorType[""]:
         """Estimate value of a trajectory starting at state and executing given actions."""
         # state = start_state

### 2023-05-12 src/rl/models/rewards/cartpole_swingup.py

@@ -19,6 +19,7 @@ class CartpoleRewardModel(RewardModel):
         self._reward_fn = torch.vmap(reward_fn)
         # self._reward_fn = torch.vmap(cartpole_swingup_reward)
 
+    @torch.no_grad()
     def predict(self, state: State, action: Action) -> RewardPrediction:
         # print("state {}".format(state.shape))
         # print("aciton {}".format(action.shape))

### 2023-05-12 src/rl/models/transitions/nn2svgp.py

@@ -74,6 +74,7 @@ class NTKSVGPTransitionModel(TransitionModel):
             self.ntksvgp.cuda()
             print("put transition ntksvgp on cuda")
 
+    @torch.no_grad()
     def predict(self, state: State, action: Action) -> StatePrediction:
         state_action_input = torch.concat([state, action], -1)
         if "NN" in self.prediction_type:

### 2023-05-12 src/rl/models/rewards/cartpole_swingup.py
use copy of dm_control reward fn

@@ -12,12 +12,13 @@ _DEFAULT_VALUE_AT_MARGIN = torch.Tensor([0.1])
 
 
 class CartpoleRewardModel(RewardModel):
-    def __init__(self, action_penalty: float = 0.0, sparse_threshold: float = 0.0):
+    def __init__(self, action_penalty: float = 0.0, sparse_threshold: float = 0.3):
         reward_fn = tensor_reward
         self.action_penalty = action_penalty
         self.sparse_threshold = sparse_threshold
-        self._reward_fn = torch.vmap(reward_fn)
-        # self._reward_fn = torch.vmap(cartpole_swingup_reward)
+        # self._reward_fn = torch.vmap(reward_fn)
+        self._reward_fn = torch.vmap(cartpole_swingup_reward)
+        # self._reward_fn = torch.vmap(pets_cartpole_swingup_reward)
 
     @torch.no_grad()
     def predict(self, state: State, action: Action) -> RewardPrediction:
@@ -33,12 +34,20 @@ class CartpoleRewardModel(RewardModel):
             partial(action_penalty_reward, action_penalty=self.action_penalty)
         )(action)
         # print("penalty {}".format(penalty.shape))
-        if (reward > self.sparse_threshold).any():
-            print("using reward")
+        # print("reward {}".format(reward.max()))
+        # if (reward > self.sparse_threshold).any():
+        #     print("using reward")
         # else:
         # logger.info("only using using reward")
-        # print("reward {}".format(reward.max()))
-        reward = torch.where(reward > self.sparse_threshold, reward + penalty, penalty)
+        print("reward BEFORE {}".format(reward.max()))
+        # print("reward BEFORE {}".format(reward))
+        reward = torch.where(
+            reward > self.sparse_threshold, reward, torch.zeros_like(reward)
+        )
+        # reward = torch.where(reward > self.sparse_threshold, reward + penalty, penalty)
+
+        # print("reward {}".format(reward))
+        print("reward MAX {}".format(reward.max()))
         return RewardPrediction(reward_mean=reward, reward_var=None, noise_var=None)
 
     def update(self, data_new):
@@ -59,6 +68,7 @@ def tensor_reward(state: State, action: Action):
     dist_penalty = 0.01 * x**2 + (y - 1) ** 2
     vel_penalty = 1e-3 * v**2
     reward = -dist_penalty - vel_penalty
[…]

### 2023-05-12 paper/main.tex

@@
 \end{align}
-If $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) = -\log(p(\mathbf{y} \mid f_\weights(\mathbf{x}_{i}))$ and $\mathcal{R}(\weights) = \|\weights\|^{2}_2$ then we can view \cref{eq-empirical-risk} as the MAP solution to a Bayesian objective, where $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.
-
-\textbf{Neural network to GP prior} Our goal is to find a kernel from which to build a sparse Gaussian process model, central to this is a kernel function  $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors in $\R^{\mathrm{D}}$.
+If $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) = -\log(p(\mathbf{y} \mid f_\weights(\mathbf{x}_{i}))$ and $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$ then we can view \cref{eq-empirical-risk} as the MAP solution to a Bayesian objective, where $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.
+
+\textbf{Neural network to GP prior} A Gaussian process characterizes a distribution over functions in terms of the first two moment.
+The key quantity of a Gaussian process is the prior covariance function $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors in $\R^{\mathrm{D}}$.
+Our goal is to find a kernel based on the neural network from which to build Gaussian process posterior.
 If we had the following function parameterization $g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx) = \delta^{-1} \phi(\vx) \phi(\vx)^\T$ see \citep{rasmussen2006gaussian} for details.
@@
 Replacing \cref{eq:dual_param_laplace} in to \cref{eq-laplace-approx-function-space} and we arrive at our GP model based on the converged neural network.
-
-\textbf{Dual Gaussian Process} A Gaussian process characterizes a distribution over functions in terms of the first two moment.
-
-A Gaussian process (GP) is a prior over functions $f \sim \GP(\mathbf{0}, \kappa(\cdot, \cdot))$.
-The prior is characterized by a covariance kernel function $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors in $\R^{\mathrm{D}}$.
-Once combined with a data set ${\mathcal{D} = \{(\vx_i, y_i)\}_{i=1}^n}$ with $n$ examples, each modelled by the likelihood $p(\vy_i \mid \vf_i)$ at function $\vf_i = f(\vx_i)$\, we can form a posterior proccess using multivariate conditioning.
-The drawbacks of GPs reside in their lack of scaling to large datasets and non-tractability with non-Gaussian likelihoods.
+Again this is similar to what was arrived at for \citet{immerImprovingPredictionsBayesian2021} for the posterior variance function, but they instead use the $f_{\vw^*}(\vx)$ for the posterior mean and fail to spot the significance of the dual variables.
+The problem with \cref{eq:gp_pred} is that to make predictions and compute variances we must incur a cost of $O(n^3)$ which limits the use of the GP on large datasets.
+
+\textbf{Sparse Dual Gaussian Process} Sparse Gaussian processes are a way to reduce the computational complexity of a full GP using a low rank approximation many approaches have been devised see \citet{quinonero2005unifying} for an overview.
+Given we have our dual variables derived from our neural network predictions and kernel function we could make use any approximation.
+We decide to follow the the \citep{titsias2009variational}, which is to say that our marginal distribution $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) q(\vu)  d\vu$
 

### 2023-05-12 paper/main.tex
started doing rl stuff

@@
 
-\textbf{Reinforcement learning}
+\textbf{Model-based reinforcement learning}
+We now detail how our method can be used in model-based RL.
+Folling the Markov decision process formulation \cite{bellmanDynamic1956}, we
+denote states \(\state \in \stateDomain \subseteq \R^{D_{\state}} \), actions \(\action \in \actionDomain \subseteq \R^{D_{\action}}\) and
+transition dynamics \(\transitionFn: \stateDomain \times \actionDomain \rightarrow \stateDomain \) subject to  i.i.d. transition noise \(\noise_{t}\).
+The goal of RL is to find the policy \(\pi \in \Pi \) that maximises the sum of rewards
+in expecation over the transition noise,
+\begin{align} \label{eq-model-free-objective}
+\policy^{*} = \arg \max_{\policy \in \policyDomain} J(\transitionFn, \policy) = \arg \max_{\policy \in \policyDomain} \mathbb{E}_{\noise_{0:\infty}} \left[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \right]
+\quad \text{s.t. } \state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t}.
+\end{align}
+where $\gamma \in [0, 1]$ is a discount factor to account for the infinte sum.
+
+In model-based RL, the state transition data set \(\mathcal{D} = \{\{(s_{t},a_{t}), s_{t+1}\}^{T_{i}}_{t=1}\}_{i=0}^{N}\) is first used to
+learn a dynamic model \(f_{\mathbf{w}})\) using supervised learning.
+\cref{alg-mbrl} shows the typical model-based RL loop.
+
+\begin{subequations}
+\begin{align} \label{eq-fast-update-mpc}
+  \policy_{i+1}^{\text{PS}}(\state) &= \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
+J^{\Horizon}(\action_{0:\Horizon}, \transitionFn) + \stateValueFn(\state_{\Horizon+1})
+\end{align}
+\end{subequations}
+\begin{subequations}
+\begin{align} \label{eq-fast-update-mpc-old}
+  \stateValueFn(\state) &= \mathbb{E} \left[ \sum_{t=0}^{\infty}     \discount^{t} \rewardFn(\state_{t},\action_{t}) \mid \state_{0}=\state \right] \label{eq-fast-update-mpc}
+\end{align}
+\end{subequations}
+
+In model-based RL, we obtain the posterior over the dynamics \(p(f\mid\mathcal{D})\) after performing (approximate) Bayesian
+inference given a state transition data set \(\mathcal{D} = \{\{(s_{t},a_{t}), s_{t+1}\}^{T_{i}}_{t=1}\}_{i=0}^{N}\).
+\cref{alg-mbrl} shows the typical model-based RL loop.
+Importantly, the dynamics are usually only updated after an episode $i$.
+
+\textbf{Posterior sampling}
+Given the posterior dynamics \(p(\transitionFn \mid \mathcal{D})\),
+an effective and  common approach is to simply take the expecation over both the aleatoric and epistemic uncertainty,
+
+\cite{osbandWhyPosteriorSampling2017,osbandMoreEfficientReinforcement2013}
+\begin{align} \label{eq-posterior-sampling}
+\policy_{i+1}^{\text{PS}} = \arg \max_{\policy \in \policyDomain} \left[ J(\transitionFn, \policy) \right] \quad \text{s.t. } \transitionFn \sim p(\transitionFn \mid \dataset_{0:i})
+\end{align}
 

### 2023-05-12 bnn-predictive/experiments/scripts/imginference.py
Getting results for FMNIST

@@ -237,7 +237,7 @@ def main(
             likelihood=lh,
             num_inducing=n_inducing,
             dual_batch_size=batch_size,
-            jitter=10**(-9),
+            jitter=0,#10**(-9),
             device=device,
         )
         svgp.set_data(data)
@@ -273,6 +273,7 @@ def main(
             likelihood=lh,
             num_inducing=n_inducing,
             dual_batch_size=batch_size,
+            jitter=0,
             device=device,
         )
         svgp_subset.set_data(data_sparse)
@@ -315,9 +316,11 @@ def ood(
             and float(delta) > 0
             and seed == int(s)
         ):
-            eligible_files.append(os.path.join(res_dir, "models/" + file))
-            state = torch.load(os.path.join(res_dir, "models/" + file))
 
+            state = torch.load(os.path.join(res_dir, "models/" + file))
+            if 'map' not in state:
+                continue
+            eligible_files.append(os.path.join(res_dir, "models/" + file))
             perfs.append({k: state[k]["nll_va"] for k in perf_keys})
 
     train_loader = DataLoader(ds_train, batch_size=256)
@@ -453,7 +456,7 @@ def ood(
     # mstar_od, _ = get_nn_predictive(tqdm(ood_loader), lap)
     # pred_ents['lap_diag_nn'] = predictive_entropies(mstar_te, mstar_od)
 
-    fname = f"results/{dataset_name}_{model_name}_{seed}_ood.pkl"
+    fname = f"{res_dir}/{dataset_name}_{model_name}_{seed}_{name}_ood.pkl"
     logging.info(f"save {fname}")
     with open(fname, "wb") as f:
         pickle.dump(pred_ents, f)
@@ -559,7 +562,7 @@ def gp(dataset_name, ds_train, ds_test, ds_ood, model_name, batch_size, seed):
                     "perf": evaluate(lh, yte, pred_test, yva, pred_val),
                 }
 
-    fname = f"results/{dataset_name}_{model_name}_{seed}_GP.pkl"
+    fname = f"results/{dataset_name}_{model_name}_{seed}_{name}_GP.pkl"
     logging.info(f"save {fname}")
     with open(fname, "wb") as f:
         pickle.dump(gp_perf, f)
@@ -616,7 +619,7 @@ if __name__ == "__main__":
     print(f"Seed: {args.seed}")
 
 
-    torch.set_default_dtype(torch.double)
+    #torch.set_default_dtype(torch.double)
 
[…]

### 2023-05-13 bnn-predictive/experiments/scripts/imginference.py
Reading CIFAR10 results

@@ -619,7 +619,7 @@ if __name__ == "__main__":
     print(f"Seed: {args.seed}")
 
 
-    #torch.set_default_dtype(torch.double)
+    torch.set_default_dtype(torch.double)
 
     device = "cuda" if torch.cuda.is_available() else "cpu"
     torch.set_default_device(device)

### 2023-05-13 paper/main.tex

@@
 Deep learning has become the cornerstone of contemporary artificial intelligence, proving remarkably effective in tackling supervised and unsupervised learning tasks in the {\em large data}, {\em offline}, and {\em gradient-based training} regime.
-Despite its success, gradient-based learning techniques exhibit limitations when applied to sequential learning paradigms, such as Continual Learning (CL, \cite{add}) and Reinforcement Learning (RL, \cite{add}).
+Despite its success, gradient-based learning techniques exhibit limitations when applied to sequential learning paradigms, such as Continual Learning (CL, \cite{add}) and Reinforcement Learning (RL, \cite{sutton2018reinforcement}).
 In CL, the challenge is retaining a compact representation of the problem and avoid forgetting over the life-long learning horizon (see, \eg, \cite{add}).

### 2023-05-13 paper/main.tex
fixed formulas

@@
 
-\textbf{Neural network to GP prior} A Gaussian process characterizes a distribution over functions in terms of the first two moment.
+\textbf{Neural network to GP prior} A Gaussian process characterizes a distribution over functions in terms of the first two moments.
 The key quantity of a Gaussian process is the prior covariance function $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors in $\R^{\mathrm{D}}$.
-Our goal is to find a kernel based on the neural network from which to build Gaussian process posterior.
-If we had the following function parameterization $g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx) = \delta^{-1} \phi(\vx) \phi(\vx)^\T$ see \citep{rasmussen2006gaussian} for details.
-We can approximate the feature map of the neural network  $f_\weights(\mathbf{x}_{i})$  by using the Jacobian at $\weights^*$ thus our GP prior becomes:
+We aim to find a kernel based on the neural network to build the Gaussian process posterior.
+If we had the following function parameterization $g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx') = \delta^{-1} \phi(\vx) \phi(\vx')^\T$ see \citep{rasmussen2006gaussian} for details.
+We can approximate the feature map of the neural network  $f_\weights(\mathbf{x})$  by using the Jacobian at $\weights^*$ thus our GP prior becomes:
 \begin{align} \label{eq-laplace-approx-function-space}
- g(\vx_i) \sim \mathcal{N} \left( \mu(\vx_i), k(\vx_i, \vx_i) \right) \quad
+ g(\vx) \sim \Norm \left( \mu(\vx), k(\vx, \vx') \right) \quad
   \mu(\vx)
@@
 \end{align}
-where the kernel is the neural tangent kernel (NTK) ,with Jacobian given by $\Jac{\weights}{\mathbf{x}} := \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$.
-Alternatively we could have followed the derivation in \citet{immerImprovingPredictionsBayesian2021} where we perform a local linearization of the neural network prediction function $f^{\textrm{lin}}_{\vw^*}(\vx; \vw) = f_{\vw^*}(\vx) + \Jac{\weights^*}{\mathbf{x}} (\vw - \vw^*)$.
-The difference with our GP prior mean function and \cref{eq-laplace-approx-function-space} is a different mean prior function which comes from $f^{\textrm{lin}}_{\vw^*}(\vx; \vzeros) = f_{\vw^*}(\vx) - \Jac{\weights^*}{\mathbf{x}} \vw^*$, essentially they use the difference from the linear model approximation and the neural network function, which does not seem useful as a prior mean function, so instead we use $ \mu(\vx_i) = \vzeros$ as is common in GP literature and derived from a feature map conversion.
+where the kernel is the neural tangent kernel (NTK) with Jacobian given by $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$.
+Alternatively, we could have followed the derivation in \citet{immerImprovingPredictionsBayesian2021} where we perform a local linearization of the neural network prediction function $f^{\textrm{lin}}_{\vw^*}(\vx; \vw) = f_{\vw^*}(\vx) + \Jac{\weights^*}{\mathbf{x}} (\vw - \vw^*)$.
+The difference between our GP prior mean function and \cref{eq-laplace-approx-function-space} is that we use a different mean prior function coming from $f^{\textrm{lin}}_{\vw^*}(\vx; \vzeros) = f_{\vw^*}(\vx) - \Jac{\weights^*}{\mathbf{x}} \vw^*$, essentially they use the difference from the linear model approximation and the neural network function, which does not seem useful as a prior mean function, so instead we use $ \mu(\vx_i) = \vzeros$ as is common in GP literature and derived from a feature map conversion.
 
@@
 \begin{align} \label{eq-fast-update-mpc-old}
-  \stateValueFn(\state) &= \mathbb{E} \left[ \sum_{t=0}^{\infty}     \discount^{t} \rewardFn(\state_{t},\action_{t}) \mid \state_{0}=\state \right] \label{eq-fast-update-mpc}
+  \stateValueFn(\state) &= \mathbb{E} \left[ \sum_{t=0}^{\infty}     \discount^{t} \rewardFn(\state_{t},\action_{t}) \mid \state_{0}=\state \right]
 \end{align}

### 2023-05-13 paper/main.tex
written some dual variable stuff

@@
 
-\textbf{Sparse Dual Gaussian Process} Sparse Gaussian processes are a way to reduce the computational complexity of a full GP using a low rank approximation many approaches have been devised see \citet{quinonero2005unifying} for an overview.
-Given we have our dual variables derived from our neural network predictions and kernel function we could make use any approximation.
-We decide to follow the the \citep{titsias2009variational}, which is to say that our marginal distribution $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) q(\vu)  d\vu$
+\textbf{Sparse Dual Gaussian Process} Sparse Gaussian processes are a way to reduce the computational complexity of a full GP using a low-rank approximation.
+Many sparsifying approaches exist (see \citet{quinonero2005unifying}) for an overview.
+Given that we have our dual variables derived from our neural network predictions and kernel function, we could use any approximation.
+We decide to follow the sparsifying approach of \citep{titsias2009variational}, which is to define the marginal distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) q(\vu)  d\vu$.
+Given that we have $p(f_i  \mid \vu)$ determined by our GP prior, the goal is to find a $q(\vu)$.
+As was shown in \cite{adam2021dual}, the posterior under this model has a particular structure similar to \cref{eq:gp_pred}.
+In that paper, they spot the dual variables' importance for approximate inference but write them in the natural parameter form as this form is more suitable for optimization through natural gradients.
+In order to make the link
 

### 2023-05-13 paper/main.tex
written some dual variable stuff

@@
 \end{equation}
-where $(\valpha,\vbeta)$ are vectors of
+where the $ij$th entry of the matrix $\MKxx \in \R^{m \times m}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$th element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
+The dual parameters consist of the vector $\valpha \in \R^{m}$ and vector $\vbeta \in \R^{m}$, defined as:
 \begin{equation}
@@
 Given that we have our dual variables derived from our neural network predictions and kernel function, we could use any approximation.
-We decide to follow the sparsifying approach of \citep{titsias2009variational}, which is to define the marginal distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) q(\vu)  d\vu$.
+We decide to follow the sparsifying approach of \citep{titsias2009variational}, which is to define the marginal distribution as $q_{\vu}(\vf)  = \int p(\vf  \mid \vu) q(\vu)  d\vu$.
 Given that we have $p(f_i  \mid \vu)$ determined by our GP prior, the goal is to find a $q(\vu)$.
@@
 In that paper, they spot the dual variables' importance for approximate inference but write them in the natural parameter form as this form is more suitable for optimization through natural gradients.
-In order to make the link
+In order to make the link to the dual variables defined in \cref{eq:dual_param} we write them in the sparse GP in the dual variable form.
+
+\begin{equation} 
+	\valpha_{\vu}  = \sum_{i \in \mathcal{D}_{n}}  \vkzi \, \hat{\alpha}_{i}, \quad
+	\vbeta_{\vu} = \sum_{i \in \mathcal{D}_{n}} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
+\label{eq:dual_sparse}
+\end{equation}
 
@@
 \begin{equation}
-   \myexpect_{q_{\vu}(\vf)}[\vf_i] = \vkzs^{\T} \valpha , \quad 
-   \textrm{Var}_{q_{\vu}(\vf)}[\vf_i]  = \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \vbeta)^{-1} ]\vkzs
+   \myexpect_{q_{\vu}(\vf)}[\vf_i] = \vkzs^{\T} \MKzz^{-1}  \valpha_{\vu} , \quad 
+   \textrm{Var}_{q_{\vu}(\vf)}[\vf_i]  = \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \vbeta_{\vu})^{-1} ]\vkzs
 \end{equation}
@@
 \label{eq:dual_sparse}
-\end{equation}
-
-where $\tilde{\lambda}_i = \alpha_i - \myexpect_{q_{\vu}(\vf)}[\vf_i] \hat{\beta}_i$ with $(\hat{\alpha}_i, \hat{\beta}_i)$ defined as,
-\begin{equation}
- \alpha_i = \myexpect_{q_{\vu}(\vf_i)} [\nabla_{\vf_i}\log p(\vy_i \mid \vf_i)], \quad
-   \beta_i = \myexpect_{q_{\vu}(\vf_i)} [ -\nabla^{2}_{\vf_i}\log p(\vy_i \mid \vf_i)],
-\label{eq:svgp_dual}
 \end{equation}

### 2023-05-13 paper/main.tex
updated paper

--- 2023-05-13 paper/main.tex
@@
 \newcommand{\vm}{\mbf{m}}
-%\newcommand{\vz}{\mbf{z}}
+\newcommand{\vz}{\mbf{z}}
 \newcommand{\vf}{\mbf{f}}
@@
 
+%% CL section 
+%%
+%% EWC, SI, VCL -> weight regularization 
+EWC \cite{kirkpatrick2017overcoming}
+SI \cite{zenke17a}, 
+VCL \cite{nguyen-tuongModel2009},
+
+%% DER, FROMP, S-FSVI
+DER \cite{buzzega2020dark}
+FROMP \cite{pan2020continual}
+S-FSVI \cite{rudner2022continual}
+
 %Why we need uncertainty and adaptiveness
@@
 \label{eq:dual_param}
-\alpha_i \coloneqq\myexpect_{p(f_i \mid \vy)}[\nabla_{f_i}\log p(y_i \mid f_i)],  \quad
-\beta_i \coloneqq - \myexpect_{p(f_i \mid \vy)}[\nabla^2_{f_i}\log p(y_i \mid f_i)] ,
+\alpha_i \coloneqq \myexpect_{p(f_i \mid \vy)}[\nabla_{f_i}\log p(y_i \mid f_i)],  \quad
+\beta_i \coloneqq - \myexpect_{p(f_i \mid \vy)}[\nabla^2_{f_i f_i}\log p(y_i \mid f_i)] ,
 \end{equation}
@@
 \hat{\alpha}_i \coloneqq \nabla_{f_i}\log p(y_i \mid f_i),  \quad
-\hat{\beta}_i \coloneqq - \nabla^2_{f_i}\log p(y_i \mid f_i),
+\hat{\beta}_i \coloneqq - \nabla^2_{f_i f_i}\log p(y_i \mid f_i),
 \end{equation}
@@
 
-where the $ij$th entry of the matrix $\MKzz \in \R^{m \times m}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$\todo{the equation above uses $\vkzs$ not $\vk_{\vx i}$} denotes a vector where each $j$th element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
+where the $ij$th entry of the matrix $\MKzz \in \R^{m \times m}$ is $\kappa(\vz_i,\vz_j)$, $\vk_{\vz i}$\todo{the equation above uses $\vkzs$ not $\vk_{\vx i}$} denotes a vector where each $j$th element is $\kappa(\vz_j, \vx_i)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
 The dual parameters consist of the vector $\valpha \in \R^{m}$ and the matrix $\vbeta \in \R^{m \times m}$, defined as

### 2023-05-13 paper/main.tex
written some dual variable stuff

@@
 In order to make the link to the dual variables defined in \cref{eq:dual_param} we write them in the sparse GP in the dual variable form.
-
 \begin{equation} 
@@
 \end{equation}
+Using the sparse definition of the dual variables our sparse GP posterior takes the following form:
+\begin{equation}
+   \myexpect_{q_{\vu}(\vf)}[\vf_i] = \vkzs^{\T} \MKzz^{-1}  \valpha_{\vu} , \quad 
+   \textrm{Var}_{q_{\vu}(\vf)}[\vf_i]  = \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \vbeta_{\vu})^{-1} ]\vkzs
+\end{equation}
+
+where $\MKzz$ and $\vkzs$ are define similarly to $\MKxx$ and $\vk_{\vx i}$ but now over the $\MZ \in \R^{M \times D} $ inducing points instead of the full dataset.
 
@@
 As shown in \cite{adam2021dual}, we can decompose the optimal sparse GP  with a dual parameterization \cite{adam2021dual} as follows:
-\begin{equation}
-   \myexpect_{q_{\vu}(\vf)}[\vf_i] = \vkzs^{\T} \MKzz^{-1}  \valpha_{\vu} , \quad 
-   \textrm{Var}_{q_{\vu}(\vf)}[\vf_i]  = \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \vbeta_{\vu})^{-1} ]\vkzs
-\end{equation}
-
-where the $ij$th entry of the matrix $\MKzz \in \R^{m \times m}$ is $\kappa(\vz_i,\vz_j)$, $\vk_{\vz i}$\todo{the equation above uses $\vkzs$ not $\vk_{\vx i}$} denotes a vector where each $j$th element is $\kappa(\vz_j, \vx_i)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
+
+denotes a vector where each $j$th element is $\kappa(\vz_j, \vx_i)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
 The dual parameters consist of the vector $\valpha \in \R^{m}$ and the matrix $\vbeta \in \R^{m \times m}$, defined as

### 2023-05-13 paper/main.tex
written some dual variable stuff

@@
 Using the sparse definition of the dual variables our sparse GP posterior takes the following form:
-\begin{equation}
+\begin{equation}\label{eq:dual_sparse_post}
    \myexpect_{q_{\vu}(\vf)}[\vf_i] = \vkzs^{\T} \MKzz^{-1}  \valpha_{\vu} , \quad 
@@
 \end{equation}
-
-where $\MKzz$ and $\vkzs$ are define similarly to $\MKxx$ and $\vk_{\vx i}$ but now over the $\MZ \in \R^{M \times D} $ inducing points instead of the full dataset.
-
-Sparse Gaussian processes \citep{hensman2013gaussian} are a principled way to scale Gaussian processes to large datasets by using a subset of $m$ inducing points, with $m \ll n$,  lowering the complexity from $\mathcal{O}(n^3)$ to $\mathcal{O}(m^3)$.
-The key insight is to use a sparse approximating distribution $q(\vu; \vm, \MV)$, where $\vm \in \R^{m}$ and $\MV \in \R^{m \times m}$, and find its parameters through maximizing the evidence lower bound (ELBO).
-Then, the distribution over all points is defined as $q_{\vu}(\vf) = \int p(\vf \mid \vu) q(\vu) \mathrm{d}\vu$.
-As shown in \cite{adam2021dual}, we can decompose the optimal sparse GP  with a dual parameterization \cite{adam2021dual} as follows:
-
-denotes a vector where each $j$th element is $\kappa(\vz_j, \vx_i)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
-The dual parameters consist of the vector $\valpha \in \R^{m}$ and the matrix $\vbeta \in \R^{m \times m}$, defined as
-\begin{equation} 
-	\vlambda = [ \MKzz + \vbeta] \valpha  = \sum_{i \in \mathcal{D}_{n}}  \vkzi \, \tilde{\lambda}_{i}, \quad
-	\vbeta = \sum_{i \in \mathcal{D}_{n}} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
-\label{eq:dual_sparse}
-\end{equation}
-
-The key quantities we need to build our sparse GP are $(\alpha_i, \beta_i)$ and a kernel function $\kappa$  and from that we are able to make predictions and variance estimates.
+where $\MKzz$ and $\vkzs$ are define similarly to $\MKxx$ and $\vk_{\vx i}$ but now over the $\MZ \in \R^{M \times D} $ inducing points instead of the full dataset $\MX$.
+The key quantities we need to make predictions from out sparse GP from the converged neural network are $(\hat{\alpha}_i, \hat{\beta}_i)$ and a kernel function $\kappa$ which are then combined in \cref{eq:dual_sparse_post}/ Contrasting \cref{eq:dual_sparse_post} and \cref{eq:gp_pred} we can see that the computational complexity is now $\mathcal{O}(m^3)$ to $\mathcal{O}(n^3)$ where $m \ll n$.
+
 Crucially in the dual formulation our posterior contains all the training data given the sum in \cref{eq:dual_sparse}.
+
+mention DITC and consfusion
+
+principled way to contain information
+
+write it out for Gaussian
 

### 2023-05-13 src/nn2svgp/plot_banana.py
Scripts for Figs. 1-2

@@ -1,0 +1,226 @@
+## BANANA DATA EXAMPLE FOR THE PAPER
+
+import logging
+
+
+logging.basicConfig(level=logging.INFO)
+logger = logging.getLogger(__name__)
+
+import src
+import torch
+import torch.nn as nn
+from src.nn2svgp import NTKSVGP
+from src.nn2svgp.custom_types import Data
+import numpy as np
+
+# Download the Banana data
+X = np.loadtxt('https://raw.githubusercontent.com/AaltoML/BayesNewton/main/data/banana_X_train', delimiter=',')
+Y = np.loadtxt('https://raw.githubusercontent.com/AaltoML/BayesNewton/main/data/banana_Y_train')[:, None]
+
+X_train = torch.from_numpy(X)
+Y_train = torch.from_numpy(Y)
+
+def train(
+    ntksvgp: NTKSVGP,
+    data: Data,
+    num_epochs: int = 1000,
+    batch_size: int = 16,
+    learning_rate: float = 1e-3,
+):
+    data_loader = torch.utils.data.DataLoader(
+        torch.utils.data.TensorDataset(*data),
+        batch_size=batch_size,
+    )
+
+    ntksvgp.train()
+    optimizer = torch.optim.Adam([{"params": ntksvgp.parameters()}], lr=learning_rate)
+    loss_history = []
+    for epoch_idx in range(num_epochs):
+        for batch_idx, batch in enumerate(data_loader):
+            x, y = batch
+            loss = ntksvgp.loss(x, y)
+
+            optimizer.zero_grad()
+            loss.backward()
+            optimizer.step()
+            loss_history.append(loss.detach().numpy())
+
+            if epoch_idx % 500 == 0:
+                logger.info(
+                    "Epoch: {} | Batch: {} | Loss: {}".format(epoch_idx, batch_idx, loss)
+                )
+
+    ntksvgp.build_dual_svgp()
+    return {"loss": loss_history}
+
+
+if __name__ == "__main__":
+    import os
+    import numpy as np
+    import matplotlib.pyplot as plt
+
+    torch.manual_seed(45)
+    torch.set_default_dtype(torch.float64)
+
+    save_dir = "./figs/"
+
+    torch.set_default_dtype(torch.float64)
+
+    delta = 0.0002
+    #delta = 0.00001
+
+    class Sin(nn.Module):
+        def forward(self, x):
[…]

### 2023-05-13 src/nn2svgp/plot_banana_hmc.py

@@ -1,0 +1,245 @@
+import random
+#from pandas import read_csv
+import numpy as np
+import torch
+from tqdm import tqdm, trange
+from torch.utils.data import Dataset, DataLoader
+import torch.nn as nn
+import matplotlib.pyplot as plt
+from PIL import Image
+import torch.nn.functional as F
+import hamiltorch
+import numpy as np
+
+seed = 42
+
+class banana_dataset(Dataset):
+    def __init__(self, x, y, labels):
+        super(banana_dataset).__init__()
+        self.x = x
+        self.y = y
+        self.labels = labels
+    def __getitem__(self, index):
+        point = torch.FloatTensor((self.x[index],self.y[index]))
+        label = int(self.labels[index])
+        return point, label
+    def __len__(self):
+        return len(self.labels)
+        
+torch.manual_seed(seed)
+np.random.seed(seed)
+random.seed(seed)
+hamiltorch.set_random_seed(seed)
+
+# Training data
+#data = read_csv(datapath+"banana_datapoints_subset.csv", header = None, prefix = 'col') 
+#classes = read_csv(datapath+"banana_classes_subset.csv", header = None, prefix = 'col')
+
+# Banana data
+X = np.loadtxt('https://raw.githubusercontent.com/AaltoML/BayesNewton/main/data/banana_X_train', delimiter=',')
+Y = np.loadtxt('https://raw.githubusercontent.com/AaltoML/BayesNewton/main/data/banana_Y_train')[:, None]
+
+Y = Y.astype('float')
+
+n = X.shape[0]
+train_set = banana_dataset([X[i,0] for i in range(n)], [X[i,1] for i in range(n)], [Y[i] for i in range(n)])
+
+print('data set')
+
+# Test data
+gridwidth = 100
+gridlength = 2.8
+x_vals = np.linspace(-gridlength,gridlength,gridwidth)
+y_vals = np.linspace(-gridlength,gridlength,gridwidth)
+grid_samples = np.zeros((gridwidth*gridwidth,2))
+for i in range(gridwidth):
+    for j in range(gridwidth):
+        grid_samples[i*gridwidth + j, 0] = x_vals[i]
+        grid_samples[i*gridwidth + j, 1] = y_vals[j]
+
+grid_set = torch.from_numpy(grid_samples).float()
+big_n = grid_set.shape[0]
+
[…]

### 2023-05-13 paper/main.tex
Add figs to paper

@@
   \pgfplotsset{axis on top,scale only axis,width=\figurewidth,height=\figureheight, ylabel near ticks,ylabel style={yshift=-2pt},y tick label style={rotate=90},legend style={nodes={scale=1., transform shape}},tick label style={font=\tiny,scale=1}}
-  \pgfplotsset{xlabel={Input, $x$},axis line style={rounded corners=3pt}}
+  \pgfplotsset{xlabel={Input, $x$},axis line style={rounded corners=2pt}}
   % Set figure 
@@
     \pgfplotsset{ylabel={Output, $y$}}
-    \input{./fig/regression-nn.tex}%
+    \input{../src/nn2svgp/figs/regression-nn.tex}%
   \end{subfigure}
@@
     \pgfplotsset{yticklabels={,,},ytick={\empty}}
-    \input{./fig/regression-nn2svgp.tex}%
+    \input{../src/nn2svgp/figs/regression-nn2svgp.tex}%
   \end{subfigure}
@@
     \pgfplotsset{yticklabels={,,},ytick={\empty}}        
-    \input{./fig/regression-update.tex}%
+    \input{../src/nn2svgp/figs/regression-update.tex}%
   \end{subfigure}
@@
     % The update
-    \addfig{2.2\figurewidth,0}{banana-update}
+    \addfig{2.2\figurewidth,0}{banana-hmc}
 
@@
     \tikzstyle{myarrow} = [draw=black!80, single arrow, minimum height=14mm, minimum width=2pt, single arrow head extend=4pt, fill=black!80, anchor=center, rotate=0, inner sep=5pt, rounded corners=1pt]
+    \tikzstyle{myblock} = [draw=black!80, minimum height=4mm, minimum width=7mm, fill=black!80, anchor=center, rotate=0, inner sep=5pt, rounded corners=1pt]
     \node[myarrow] (first-arr) at ($(banana-nn)!0.5!(banana-nn2svgp)$) {};
-    \node[myarrow] (second-arr) at ($(banana-nn2svgp)!0.5!(banana-update)$) {};
+    \node[myblock] (second-arr) at ($(banana-nn2svgp)!0.5!(banana-hmc)$) {};
 
@@
     \node[font=\scriptsize\sc,color=white] at (first-arr) {nn2svgp};
-    \node[font=\scriptsize\sc,color=white] at (second-arr) {new data};
+    \node[font=\scriptsize\sc,color=white] at (second-arr) {\normalsize$\bm\approx$};
 
@@
     \node[anchor=north, font=\small] at ($(banana-nn2svgp) + (0,-.55\figureheight)$) {Sparse GP representation};
-    \node[anchor=north, font=\small] at ($(banana-update) + (0,-.55\figureheight)$) {Update without re-training};
+    \node[anchor=north, font=\small] at ($(banana-hmc) + (0,-.55\figureheight)$) {HMC result as baseline};
 

### 2023-05-13 paper/main.tex
Sections

@@
 
-\subsection{Related Work}
-\label{sec:related}
-%
-% Introduce the laplace GNN + shortcomings
-One common approach for uncertainty with neural networks is a Laplace GNN approximation \citep{daxbergerLaplace2021}, that takes a trained neural network and linearises it around the optimal weights.
-The resulting linear model can be used to obtain uncertainty estimates and refine the neural network predictions \citep{immerScalable2021}.
-The resultant model is linear with respect to the weights, therefor it is possible to convert it to a Gaussian process (GP) as shown in \citep{immerScalable2021, khan2019approximate}.
-Yet to obtain uncertainty estimates there is the usual computational scaling  cubic in the number of data points of GPs ($\mathcal{O}(n^3)$).
-Many approaches  apply crude approximations and yet still obtain good uncertainty estimates.
-
-%% CL section 
-%%
-%% EWC, SI, VCL -> weight regularization 
-EWC \cite{kirkpatrick2017overcoming}
-SI \cite{zenke17a}, 
-VCL \cite{nguyen-tuongModel2009},
-
-%% DER, FROMP, S-FSVI
-DER \cite{buzzega2020dark}
-FROMP \cite{pan2020continual}
-S-FSVI \cite{rudner2022continual}
-
-%Why we need uncertainty and adaptiveness
-%How to adapt to new information is a limitation of current machine learning models.
-The problem is specifically relevant when we combine a model with a decision-making process.
-In such a sequential setting, an agent typically makes decisions in an environment and obtains new information and would ideally incorporate the information into their parameters.
-Not only do we need models that adapt to new informatoion but all express uncertainty over the models predictions.
-The reason being twofold: in many applications, \eg\ healthcare, autonomous driving is an essential requirement, and many advanced exploration techniques require uncertainty to determine where to query next.
-
 \begin{figure}[t!]
@@
 
+\subsection{Related work}
+\label{sec:related}
+%
+% Introduce the laplace GNN + shortcomings
+One common approach for uncertainty with neural networks is a Laplace GNN approximation \citep{daxbergerLaplace2021}, that takes a trained neural network and linearises it around the optimal weights.
+The resulting linear model can be used to obtain uncertainty estimates and refine the neural network predictions \citep{immerScalable2021}.
+The resultant model is linear with respect to the weights, therefor it is possible to convert it to a Gaussian process (GP) as shown in \citep{immerScalable2021, khan2019approximate}.
+Yet to obtain uncertainty estimates there is the usual computational scaling  cubic in the number of data points of GPs ($\mathcal{O}(n^3)$).
+Many approaches  apply crude approximations and yet still obtain good uncertainty estimates.
+
+%% CL section 
+%%
+%% EWC, SI, VCL -> weight regularization 
+EWC \cite{kirkpatrick2017overcoming}
+SI \cite{zenke17a}, 
+VCL \cite{nguyen-tuongModel2009},
+
+%% DER, FROMP, S-FSVI
+DER \cite{buzzega2020dark}
+FROMP \cite{pan2020continual}
+S-FSVI \cite{rudner2022continual}
+
+%Why we need uncertainty and adaptiveness
+%How to adapt to new information is a limitation of current machine learning models.
+The problem is specifically relevant when we combine a model with a decision-making process.
+In such a sequential setting, an agent typically makes decisions in an environment and obtains new information and would ideally incorporate the information into their parameters.
+Not only do we need models that adapt to new informatoion but all express uncertainty over the models predictions.
+The reason being twofold: in many applications, \eg\ healthcare, autonomous driving is an essential requirement, and many advanced exploration techniques require uncertainty to determine where to query next.
+
 \begin{figure}[t!]
@@
 
-\section{Methods} \label{sec:methods}
-
-\textbf{Neural Network} In supervised learning, given a data set $\dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with $\mathbf{x}_i \in \inputDomain$ and $\mathbf{y}_i \in \outputDomain$, the weights $\weights \in \R^{P}$ of a neural network
+\section{Methods}
+\label{sec:methods}
+%
+In supervised learning, given a data set $\dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with $\mathbf{x}_i \in \inputDomain$ and $\mathbf{y}_i \in \outputDomain$, the weights $\weights \in \R^{P}$ of a neural network
 , $f_\mathbf{w} : \inputDomain \mapsto \outputDomain$, 
@@
 
-\textbf{Neural network to GP prior} A Gaussian process characterizes a distribution over functions in terms of the first two moments.
+\subsection{Neural network to GP prior} 
+\label{sec:nn2gp}
+%
+A Gaussian process characterizes a distribution over functions in terms of the first two moments.
 The key quantity of a Gaussian process is the prior covariance function $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors in $\R^{\mathrm{D}}$.
@@
 
-\textbf{Sparse Dual Gaussian Process} Sparse Gaussian processes are a way to reduce the computational complexity of a full GP using a low-rank approximation.
-Many sparsifying approaches exist (see \citet{quinonero2005unifying}) for an overview.
+\subsection{Sparse dual Gaussian process} 
+\label{sec:sparse-dual-gp}
+%
+Sparse Gaussian processes are a way to reduce the computational complexity of a full GP using a low-rank approximation.
+Many sparsifying approaches exist (see \cite{quinonero2005unifying}) for an overview.
 Given that we have our dual variables derived from our neural network predictions and kernel function, we could use any approximation.
-We decide to follow the sparsifying approach of \citep{titsias2009variational}, which is to define the marginal distribution as $q_{\vu}(\vf)  = \int p(\vf  \mid \vu) q(\vu)  d\vu$.
+We decide to follow the sparsifying approach of \citet{titsias2009variational}, which is to define the marginal distribution as $q_{\vu}(\vf)  = \int p(\vf  \mid \vu) q(\vu)  d\vu$.
 Given that we have $p(f_i  \mid \vu)$ determined by our GP prior, the goal is to find a $q(\vu)$.
@@
 
-\textbf{Neural network to sparse GP}
+\subsection{Forming the sparse function-space representation of a neural network}
+
+\section{Sparse function-space sequential learning}
 

### 2023-05-13 paper/main.tex
written some dual variable stuff

@@
 
-As we are using the MAP solution of the neural network loss we will use the Laplace approximation for the dual variables but other techniques could be used.
+\textbf{Neural network dual variables} As we are using the MAP solution of the neural network loss we will use the Laplace approximation for the dual variables but other techniques could be used.
 As was detailed in \cite{wilkinson2023bayes, rasmussen2006gaussian} the dual variables of the Laplace approximation is the same as removing the posterior averaging from \cref{eq:dual_param} meaning:
@@
 In order to make the link to the dual variables defined in \cref{eq:dual_param} we write them in the sparse GP in the dual variable form.
+
 \begin{equation} 
-	\valpha_{\vu}  = \sum_{i \in \mathcal{D}_{n}}  \vkzi \, \hat{\alpha}_{i}, \quad
+	\valpha_{\vu}  = \MKzz^{-1}  \sum_{i \in \mathcal{D}_{n}}  \vkzi \, \hat{\alpha}_{i}, \quad
 	\vbeta_{\vu} = \sum_{i \in \mathcal{D}_{n}} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
@@
 \begin{equation}\label{eq:dual_sparse_post}
-   \myexpect_{q_{\vu}(\vf)}[\vf_i] = \vkzs^{\T} \MKzz^{-1}  \valpha_{\vu} , \quad 
+   \myexpect_{q_{\vu}(\vf)}[\vf_i] = \vkzs^{\T}  \valpha_{\vu} , \quad 
    \textrm{Var}_{q_{\vu}(\vf)}[\vf_i]  = \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \vbeta_{\vu})^{-1} ]\vkzs
@@
 where $\MKzz$ and $\vkzs$ are define similarly to $\MKxx$ and $\vk_{\vx i}$ but now over the $\MZ \in \R^{M \times D} $ inducing points instead of the full dataset $\MX$.
-The key quantities we need to make predictions from out sparse GP from the converged neural network are $(\hat{\alpha}_i, \hat{\beta}_i)$ and a kernel function $\kappa$ which are then combined in \cref{eq:dual_sparse_post}/ Contrasting \cref{eq:dual_sparse_post} and \cref{eq:gp_pred} we can see that the computational complexity is now $\mathcal{O}(m^3)$ to $\mathcal{O}(n^3)$ where $m \ll n$.
-
-Crucially in the dual formulation our posterior contains all the training data given the sum in \cref{eq:dual_sparse}.
+The key quantities we need to make predictions from out sparse GP from the converged neural network are $(\hat{\alpha}_i, \hat{\beta}_i)$ and a kernel function $\kappa$ which are then combined in \cref{eq:dual_sparse_post}.
+Contrasting \cref{eq:dual_sparse_post} and \cref{eq:gp_pred} we can see that the computational complexity is now $\mathcal{O}(m^3)$ to $\mathcal{O}(n^3)$ where $m \ll n$.
+Crucially given the structure of our probabilistic model our sparse dual variables \cref{eq:dual_sparse} are a compact form of the full model projected using kernel computations.
+Our approach is in contrast to \citet{immerImprovingPredictionsBayesian2021} which simply use a subset of the full model, which is a less principled approach to build a sparse model given it ignores information in the dataset.
+
+It is important to highlight that the sparsifying approach is independent of the approximate inference technique. An example would be to use a Gaussian likelihood for $p(y_i \mid f_i)$ then
 

### 2023-05-13 paper/main.tex
merge
Fix fig paths

@@
     \pgfplotsset{ylabel={Output, $y$}}
-    \input{../src/nn2svgp/figs/regression-nn.tex}%
+    \input{./fig/regression-nn.tex}%
   \end{subfigure}
@@
     \pgfplotsset{yticklabels={,,},ytick={\empty}}
-    \input{../src/nn2svgp/figs/regression-nn2svgp.tex}%
+    \input{./fig/regression-nn2svgp.tex}%
   \end{subfigure}
@@
     \pgfplotsset{yticklabels={,,},ytick={\empty}}        
-    \input{../src/nn2svgp/figs/regression-update.tex}%
+    \input{./fig/regression-update.tex}%
   \end{subfigure}
@@
 Given that we have our dual variables derived from our neural network predictions and kernel function, we could use any approximation.
-We decide to follow the sparsifying approach of \citet{titsias2009variational}, which is to define the marginal distribution as $q_{\vu}(\vf)  = \int p(\vf  \mid \vu) q(\vu)  d\vu$.
+We decide to follow the sparsifying approach of \citet{titsias2009variational} and also used in the DITC approximaton \cite{quinonero2005unifying}, which is to define the marginal distribution as $q_{\vu}(\vf)  = \int p(\vf  \mid \vu) q(\vu)  d\vu$.
 Given that we have $p(f_i  \mid \vu)$ determined by our GP prior, the goal is to find a $q(\vu)$.
 As was shown in \cite{adam2021dual}, the posterior under this model has a particular structure similar to \cref{eq:gp_pred}.
-In that paper, they spot the dual variables' importance for approximate inference but write them in the natural parameter form as this form is more suitable for optimization through natural gradients.
+In the paper, they spot the dual variables' importance for approximate inference but write them in the natural parameter form as this form is more suitable for optimization through natural gradients.
 In order to make the link to the dual variables defined in \cref{eq:dual_param} we write them in the sparse GP in the dual variable form.
@@
 \begin{equation} 
-	\valpha_{\vu}  = \MKzz^{-1}  \sum_{i \in \mathcal{D}_{n}}  \vkzi \, \hat{\alpha}_{i}, \quad
+	\valpha_{\vu}  =  \sum_{i \in \mathcal{D}_{n}}  \vkzi \, \hat{\alpha}_{i}, \quad
 	\vbeta_{\vu} =  \sum_{i \in \mathcal{D}_{n}} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
@@
 \begin{equation}\label{eq:dual_sparse_post}
-   \myexpect_{q_{\vu}(\vf)}[\vf_i] = \vkzs^{\T}  \valpha_{\vu} , \quad 
+   \myexpect_{q_{\vu}(\vf)}[\vf_i] = \vkzs^{\T} \MKzz^{-1}   \valpha_{\vu} , \quad 
    \textrm{Var}_{q_{\vu}(\vf)}[\vf_i]  = \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \vbeta_{\vu})^{-1} ]\vkzs
@@
 Our approach is in contrast to \citet{immerImprovingPredictionsBayesian2021} which simply use a subset of the full model, which is a less principled approach to build a sparse model given it ignores information in the dataset.
-
-It is important to highlight that the sparsifying approach is independent of the approximate inference technique. An example would be to use a Gaussian likelihood for $p(y_i \mid f_i)$ then
-
-mention DITC and consfusion
-
-principled way to contain information
-
-write it out for Gaussian
-
-\subsection{Forming the sparse function-space representation of a neural network}
+It is important to highlight that the sparsifying approach is independent of the approximate inference technique which is determined from the neural network, which determines \cref{eq:dual_param}.
+More complicated inference techniques such as variational inference could be used but given its simplicity, all we need is trained neural network, we use a Laplace approximation in our experiments.
 

### 2023-05-13 paper/main.tex
modifying reference and cl table

--- 2023-05-13 paper/main.tex
@@
 %
-% Introduce the laplace GNN + shortcomings
-One common approach for uncertainty with neural networks is a Laplace GNN approximation \citep{daxbergerLaplace2021}, that takes a trained neural network and linearises it around the optimal weights.
-The resulting linear model can be used to obtain uncertainty estimates and refine the neural network predictions \citep{immerScalable2021}.
-The resultant model is linear with respect to the weights, therefor it is possible to convert it to a Gaussian process (GP) as shown in \citep{immerScalable2021, khan2019approximate}.
-Yet to obtain uncertainty estimates there is the usual computational scaling  cubic in the number of data points of GPs ($\mathcal{O}(n^3)$).
-Many approaches  apply crude approximations and yet still obtain good uncertainty estimates.
+% Introduce the laplace GGN + shortcomings
+One common approach for uncertainty with neural networks is a Laplace-GGN approximation \citep{daxbergerLaplace2021}, which takes a trained neural network and linearises it around the optimal weights.
+The resulting linear model can be used to obtain uncertainty estimates and refine the neural network predictions \citep{immerScalable2021}, and is linear with respect to the weights.
+Therefore, as shown in \citep{immerScalable2021, khan2019approximate}, the linear model can be converted to a Gaussian process (GP), which is then used to obtain the uncertainty estimates.
+However, the GP introduces a computational scaling that is cubic in the number of data points ($\mathcal{O}(n^3)$).
+Many approaches apply crude approximations to alleviate the computational costs, \eg, considering only a subset of the training datas, but are still obtain good uncertainty estimates \citep{immerScalable2021}\todo{other methods?}.
 
@@
 %% EWC, SI, VCL -> weight regularization
+
 EWC \cite{kirkpatrick2017overcoming}

### 2023-05-13 paper/main.tex
commit for ricardo

@@
 Deep learning has become the cornerstone of contemporary artificial intelligence, proving remarkably effective in tackling supervised and unsupervised learning tasks in the {\em large data}, {\em offline}, and {\em gradient-based training} regime.
-Despite its success, gradient-based learning techniques exhibit limitations when applied to sequential learning paradigms, such as Continual Learning (CL, \cite{add}) and Reinforcement Learning (RL, \cite{sutton2018reinforcement}).
+Despite its success, gradient-based learning techniques exhibit limitations two specific examples specifically how to incorporate uncertainty quantification over predictions which is needed in many applications and how to retain the
+
+when applied to sequential learning paradigms, such as Continual Learning (CL, \cite{add}) and Reinforcement Learning (RL, \cite{sutton2018reinforcement}).
+Recently there has been some success in tackling uncertainty quantification
+
 In CL, the challenge is retaining a compact representation of the problem and avoid forgetting over the life-long learning horizon (see, \eg, \cite{add}).

### 2023-05-13 paper/main.tex
commit for ricardo

@@
 Deep learning has become the cornerstone of contemporary artificial intelligence, proving remarkably effective in tackling supervised and unsupervised learning tasks in the {\em large data}, {\em offline}, and {\em gradient-based training} regime.
-Despite its success, gradient-based learning techniques exhibit limitations two specific examples specifically how to incorporate uncertainty quantification over predictions which is needed in many applications and how to retain the
+Despite its success, gradient-based learning techniques exhibit limitations.
+Firstly how to incorporate uncertainty quantification over predictions which is needed in many applications.
+Secondly, how to retain information from previous tasks whilst learning new tasks such as Continual Learning (CL, \cite{add})
 
@@
 where $\MKzz$ and $\vkzs$ are define similarly to $\MKxx$ and $\vk_{\vx i}$ but now over the $\MZ \in \R^{M \times D} $ inducing points instead of the full dataset $\MX$.
-The key quantities we need to make predictions from out sparse GP from the converged neural network are $(\hat{\alpha}_i, \hat{\beta}_i)$ and a kernel function $\kappa$ which are then combined in \cref{eq:dual_sparse_post}.
+The key quantities we need to make predictions from our sparse GP from the converged neural network are $(\hat{\alpha}_i, \hat{\beta}_i)$ and a kernel function $\kappa$.
 Contrasting \cref{eq:dual_sparse_post} and \cref{eq:gp_pred} we can see that the computational complexity is now $\mathcal{O}(m^3)$ to $\mathcal{O}(n^3)$ where $m \ll n$.
-Crucially given the structure of our probabilistic model our sparse dual variables \cref{eq:dual_sparse} are a compact form of the full model projected using kernel computations.
-Our approach is in contrast to \citet{immerImprovingPredictionsBayesian2021} which simply use a subset of the full model, which is a less principled approach to build a sparse model given it ignores information in the dataset.
-It is important to highlight that the sparsifying approach is independent of the approximate inference technique which is determined from the neural network, which determines \cref{eq:dual_param}.
-More complicated inference techniques such as variational inference could be used but given its simplicity, all we need is trained neural network, we use a Laplace approximation in our experiments.
+Crucially given the structure of our probabilistic model, our sparse dual variables \cref{eq:dual_sparse} are a compact form of the full model projected using the kernel.
+Our approach contrasts to \citet{immerImprovingPredictionsBayesian2021}, which uses a subset of the full model, a less principled approach to build a sparse model given it ignores the information in the dataset.
+It is important to highlight that the sparsifying approach is independent of the approximate inference technique.
+The \cref{eq:dual_param} are determined from the neural network.
+More complicated inference techniques, such as variational inference, could be used, but given its simplicity, we only need a trained neural network; we use a Laplace approximation in our experiments.
 

### 2023-05-13 paper/main.tex
add catasrophic forgetting ref

--- 2023-05-13 paper/main.tex
@@
 Deep learning has become the cornerstone of contemporary artificial intelligence, proving remarkably effective in tackling supervised and unsupervised learning tasks in the {\em large data}, {\em offline}, and {\em gradient-based training} regime.
-Despite its success, gradient-based learning techniques exhibit limitations when applied to sequential learning paradigms, such as Continual Learning (CL, \cite{add}) and Reinforcement Learning (RL, \cite{sutton2018reinforcement}).
+Despite its success, gradient-based learning techniques exhibit limitations when applied to sequential learning paradigms, such as Continual Learning (CL, \cite{mccloskey1989catastrophic}) and Reinforcement Learning (RL, \cite{sutton2018reinforcement}).
 In CL, the challenge is retaining a compact representation of the problem and avoid forgetting over the life-long learning horizon (see, \eg, \cite{add}).
@@
 \end{align}
-where the kernel is the neural tangent kernel (NTK) with Jacobian given by $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$.
+where the kernel is the Neural Tangent Kernel (NTK) with Jacobian given by $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$.
 Alternatively, we could have followed the derivation in \citet{immerImprovingPredictionsBayesian2021} where we perform a local linearization of the neural network prediction function $f^{\textrm{lin}}_{\vw^*}(\vx; \vw) = f_{\vw^*}(\vx) + \Jac{\weights^*}{\mathbf{x}} (\vw - \vw^*)$.

### 2023-05-13 paper/main.tex

--- 2023-05-13 paper/main.tex
@@
 
-when applied to sequential learning paradigms, such as Continual Learning (CL, \cite{add}) and Reinforcement Learning (RL, \cite{sutton2018reinforcement}).
+when applied to sequential learning paradigms, such as Continual Learning (CL, \cite{mccloskey1989catastrophic}) and Reinforcement Learning (RL, \cite{sutton2018reinforcement}).
 Recently there has been some success in tackling uncertainty quantification

### 2023-05-13 paper/main.tex
commit for ricardo

@@
 Firstly how to incorporate uncertainty quantification over predictions which is needed in many applications.
-Secondly, how to retain information from previous tasks whilst learning new tasks such as Continual Learning (CL, \cite{add})
+Secondly, if the data is from the same distribution
+
+Secondly, how to retain information from previous tasks whilst learning new tasks where the tasks aresuch as Continual Learning (CL, \cite{add})
+
+Thirdly and differently from the CL problem is that given some data from the same distribution
 

### 2023-05-13 paper/main.tex
update methods

@@
 A Gaussian process characterizes a distribution over functions in terms of the first two moments.
-The key quantity of a Gaussian process is the prior covariance function $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors in $\R^{\mathrm{D}}$.
+The key quantity of a Gaussian process is the prior covariance function (or kernel function) $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors in $\R^{\mathrm{D}}$.
 We aim to find a kernel based on the neural network to build the Gaussian process posterior.
-If we had the following function parameterization $g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx') = \delta^{-1} \phi(\vx) \phi(\vx')^\T$ see \citep{rasmussen2006gaussian} for details.
+If we had the following function parameterization $g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx') = \delta^{-1} \phi(\vx) \phi(\vx')^\T$ see \citep{rasmussen2006gaussian} for details.\todo{this part needs to be rewritten, starts talking about a general function parameterisation and then jumps directly to the neural network}
 We can approximate the feature map of the neural network  $f_\weights(\mathbf{x})$  by using the Jacobian at $\weights^*$ thus our GP prior becomes:
 \begin{align} \label{eq-laplace-approx-function-space}
- g(\vx) \sim \Norm \left( \mu(\vx), k(\vx, \vx') \right) \quad
+ g(\vx) \sim \Norm \left( \mu(\vx), \kappa(\vx, \vx') \right) \quad
   \mu(\vx)
   = \vzeros \quad
-  k(\mathbf{x}, \mathbf{x}')
+  \kappa(\mathbf{x}, \mathbf{x}')
   = \frac{1}{\delta} \Jac{\weights^*}{\mathbf{x}}\Jac{\weights^*}{\mathbf{x}'}^\top,
 \end{align}
-where the kernel is the Neural Tangent Kernel (NTK) with Jacobian given by $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$.
-Alternatively, we could have followed the derivation in \citet{immerImprovingPredictionsBayesian2021} where we perform a local linearization of the neural network prediction function $f^{\textrm{lin}}_{\vw^*}(\vx; \vw) = f_{\vw^*}(\vx) + \Jac{\weights^*}{\mathbf{x}} (\vw - \vw^*)$.
-The difference between our GP prior mean function and \cref{eq-laplace-approx-function-space} is that we use a different mean prior function coming from $f^{\textrm{lin}}_{\vw^*}(\vx; \vzeros) = f_{\vw^*}(\vx) - \Jac{\weights^*}{\mathbf{x}} \vw^*$, essentially they use the difference from the linear model approximation and the neural network function, which does not seem useful as a prior mean function, so instead we use $ \mu(\vx_i) = \vzeros$ as is common in GP literature and derived from a feature map conversion.
-
-As stated in \citet[Lemma~1]{csato2002sparse} the posterior process mean and covariance function of a GP prior combined with a likelihood function and $\dataset$ can be stated as:
+where the kernel is the Neural Tangent Kernel (NTK) \citep{jacot2018neural} with Jacobian $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$.
+Alternatively, we could have followed the derivation in \citet{immerImprovingPredictionsBayesian2021} where they perform a local linearization of the neural network  $f^{\textrm{lin}}_{\vw^*}(\vx; \vw) = f_{\vw^*}(\vx) + \Jac{\weights^*}{\mathbf{x}} \, (\vw - \vw^*)$.
+Their mean prior function differ from ours, \cref{eq-laplace-approx-function-space}, as theirs comes from setting  $  \mu(\vx) = f^{\textrm{lin}}_{\vw_*}(\vx; \vw = \vzeros) = f_{\vw^*}(\vx) - \Jac{\weights^*}{\mathbf{x}} \vw^*$, \ie the difference between the linear model approximation and the neural network function at $\vx$.
+%which does not seem useful as a prior mean function,
+On the other hand, we set $\mu(\vx) = \vzeros$, as common in GP literature and derived from a feature map conversion. \todo{derived what?}
+
+As stated in \citet[Lemma~1]{csato2002sparse}, the posterior process mean and covariance functions of a GP prior, combined with a likelihood function and $\dataset$ can be stated as:
 \begin{equation}  \label{eq:gp_pred}
- \myexpect_{p(f\mid\vy)}[f_i] = \vk_{\vx i}^\top \valpha , \quad
+ \myexpect_{p(f_i \mid\vy)}[f_i] = \vk_{\vx i}^\top \valpha , \quad
 \textrm{Var}_{p(f\mid\vy)}[f_i] = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
 \end{equation}
-where the $ij$th entry of the matrix $\MKxx \in \R^{m \times m}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$th element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
+where $f_i = f_\weights(\vx_i)$, the $ij$th entry of the matrix $\MKxx \in \R^{m \times m}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$th element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
 The dual parameters consist of the vector $\valpha \in \R^{m}$ and vector $\vbeta \in \R^{m}$, defined as:

### 2023-05-13 paper/main.tex
commit for ricardo

@@
 Firstly how to incorporate uncertainty quantification over predictions which is needed in many applications.
-Secondly, if the data is from the same distribution
-
-Secondly, how to retain information from previous tasks whilst learning new tasks where the tasks aresuch as Continual Learning (CL, \cite{add})
+Secondly, in the sequential data regime.
+
+Secondly, how to retain information from previous tasks whilst learning new tasks where the tasks aresuch as Continual Learning (CL, \cite{de2021continual})
 

### 2023-05-13 paper/main.tex
bibs to related work

--- 2023-05-13 paper/main.tex
@@
 Recent work on techniques (\eg, \cite{list}) for converting trained neural networks from weight space to function space allow a principled mathematical approach for analyzing the behaviour \cite{add}, performing probabilistic inference \cite{add}, and quantifying uncertainty in neural networks \cite{add}.
-The methods rely on linearizing the neural network and capturing the first two moments in function space in terms of a mean function and covariance function (kernel)---defining a Gaussian process (GP, \cite{rasmussen2006}).
+The methods rely on linearizing the neural network and capturing the first two moments in function space in terms of a mean function and covariance function (kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}).
 GPs provide a widely-used probabilistic toolkit with principled uncertainty estimates, and they are a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} with theoretical guarantees on regret bounds \citep{srinivas2009gaussian}.
@@
 %
+% General Bayesian deep learning
+Bayesian deep learning~\cite{Wilson:ensembles,neal1995bayesian} has recently gained increasing attention in the machine learning community as a means for uncertainty quantification (\eg, \cite{kendall2017what,wilson2020bayes}) and model selection (\eg,~\cite{immer2021marginal,antoran2022marginal}) with advancements in prior specification (\eg, \cite{meronen2020stationary,meronen2021periodic,fortuin2021bayesian,nalisnick2018do}) and efficient approximate inference under the specified model.
+Calculating the posterior distribution of a Bayesian neural network is usually intractable, and approximate inference techniques need to be used, such as variational inference \cite{blei2017variational}, deep ensembles \cite{lakshminarayanan2017simple}, MC dropout \cite{gal2016dropout}, or Laplace approximation \cite{ritter2018kfac,kristiadi2020being,immer2021improving}---each having strengths and weaknesses.
+% point out strngths and weaknesses for each
+
 % Introduce the laplace GGN + shortcomings
-One common approach for uncertainty with neural networks is a Laplace-GGN approximation \citep{daxbergerLaplace2021}, which takes a trained neural network and linearises it around the optimal weights.
+One common approach for uncertainty with neural networks is a Laplace-GGN approximation \citep{daxberger2021laplace}, which takes a trained neural network and linearises it around the optimal weights.
 The resulting linear model can be used to obtain uncertainty estimates and refine the neural network predictions \citep{immerScalable2021}, and is linear with respect to the weights.
@@
 Many approaches apply crude approximations to alleviate the computational costs, \eg, considering only a subset of the training datas, but are still obtain good uncertainty estimates \citep{immerScalable2021}\todo{other methods?}.
+
+The Hessian can be efficiently approximated using the generalised Gauss-Newton algorithm \cite{botev2017practical} or by Kronecker factorisation \cite{martens2015optimizing,ritter2018kfac}.
 

### 2023-05-13 paper/main.tex
Sec. 2

@@
 %
-In supervised learning, given a data set $\dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with $\mathbf{x}_i \in \inputDomain$ and $\mathbf{y}_i \in \outputDomain$, the weights $\weights \in \R^{P}$ of a neural network
-, $f_\mathbf{w} : \inputDomain \mapsto \outputDomain$, 
-are usually trained to minimize the (regularized) empirical risk,
-\begin{align} \label{eq-empirical-risk}
+In supervised learning, given a data set $\dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with input $\mathbf{x}_i \in \inputDomain$ and output $\mathbf{y}_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w} : \inputDomain \mapsto \outputDomain$, are usually trained to minimize the (regularized) empirical risk,
+%
+\begin{equation} \label{eq-empirical-risk}
   \weights^{*} = 
-  \argmin_{\weights} \mathcal{L}(\dataset,\weights) =
-  \argmin_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
-\end{align}
-If $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) = -\log(p(\mathbf{y} \mid f_\weights(\mathbf{x}_{i}))$ and $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$ then we can view \cref{eq-empirical-risk} as the MAP solution to a Bayesian objective, where $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.
+  \arg \min_{\weights} \mathcal{L}(\dataset,\weights) =
+  \arg \min_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
+\end{equation}
+%
+If $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) = -\log(p(\mathbf{y} \mid f_\weights(\mathbf{x}_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.
 
@@
 We can approximate the feature map of the neural network  $f_\weights(\mathbf{x})$  by using the Jacobian at $\weights^*$ thus our GP prior becomes:
-\begin{align} \label{eq-laplace-approx-function-space}
- g(\vx) \sim \Norm \left( \mu(\vx), \kappa(\vx, \vx') \right) \quad
-  \mu(\vx)
-  = \vzeros \quad
+\begin{equation} \label{eq-laplace-approx-function-space}
+ g(\vx) \sim \Norm \left( \mu(\vx), \kappa(\vx, \vx') \right) \quad \text{with} \quad
+  \mu(\vx) = \vzeros \quad \text{and} \quad
   \kappa(\mathbf{x}, \mathbf{x}')
   = \frac{1}{\delta} \Jac{\weights^*}{\mathbf{x}}\Jac{\weights^*}{\mathbf{x}'}^\top,
-\end{align}
+\end{equation}
 where the kernel is the Neural Tangent Kernel (NTK) \citep{jacot2018neural} with Jacobian $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$.

### 2023-05-13 paper/main.tex
Sec. 2

@@
 %
-In supervised learning, given a data set $\dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with input $\mathbf{x}_i \in \inputDomain$ and output $\mathbf{y}_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w} : \inputDomain \mapsto \outputDomain$, are usually trained to minimize the (regularized) empirical risk,
+In supervised learning, given a data set $\dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with input $\mathbf{x}_i \in \inputDomain$ and output $\mathbf{y}_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w} : \inputDomain \to \outputDomain$, are usually trained to minimize the (regularized) empirical risk,
 %

### 2023-05-13 paper/main.tex
commit start of rewrite

@@
 
-\subsection{Neural network to GP prior} 
+\subsection{Neural Network to GP Prior} 
 \label{sec:nn2gp}
@@
 We aim to find a kernel based on the neural network to build the Gaussian process posterior.
-If we had the following function parameterization $g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx') = \delta^{-1} \phi(\vx) \phi(\vx')^\T$ see \citep{rasmussen2006gaussian} for details.\todo{this part needs to be rewritten, starts talking about a general function parameterisation and then jumps directly to the neural network}
+A common approach to find a $q(\vw)$ is to perform a Laplace-GGN approximation.
+The approximation can be seen as taking the map solution of \cref{eq-empirical-risk}
+
+A linear function in terms of parameters can easily be converted from the weight space to the function space as follows
+
+\begin{equation}
+\hat{f}_\weights(\mathbf{x}_{i})) = \phi(\vx)^\top \vw
+\end{equation}
+
+$g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx') = \delta^{-1} \phi(\vx) \phi(\vx')^\T$ see \citep{rasmussen2006gaussian} for details.\todo{this part needs to be rewritten, starts talking about a general function parameterisation and then jumps directly to the neural network}
 We can approximate the feature map of the neural network  $f_\weights(\mathbf{x})$  by using the Jacobian at $\weights^*$ thus our GP prior becomes:

### 2023-05-13 paper/main.tex
tried to update rl fig

--- 2023-05-13 paper/main.tex
@@
 %
-In supervised learning, given a data set $\dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with input $\mathbf{x}_i \in \inputDomain$ and output $\mathbf{y}_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w} : \inputDomain \to \outputDomain$, are usually trained to minimize the (regularized) empirical risk,
-%
-\begin{equation} \label{eq-empirical-risk}
+In supervised learning, given a data set $\dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with $\mathbf{x}_i \in \inputDomain$ and $\mathbf{y}_i \in \outputDomain$, the weights $\weights \in \R^{P}$ of a neural network
+, $f_\mathbf{w} : \inputDomain \mapsto \outputDomain$, 
+are usually trained to minimize the (regularized) empirical risk,
+\begin{align} \label{eq-empirical-risk}
   \weights^{*} = 
-  \arg \min_{\weights} \mathcal{L}(\dataset,\weights) =
-  \arg \min_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
-\end{equation}
-%
-If $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) = -\log(p(\mathbf{y} \mid f_\weights(\mathbf{x}_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.
+  \argmin_{\weights} \mathcal{L}(\dataset,\weights) =
+  \argmin_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
+\end{align}
+If $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) = -\log(p(\mathbf{y} \mid f_\weights(\mathbf{x}_{i}))$ and $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$ then we can view \cref{eq-empirical-risk} as the MAP solution to a Bayesian objective, where $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.
 
@@
 We can approximate the feature map of the neural network  $f_\weights(\mathbf{x})$  by using the Jacobian at $\weights^*$ thus our GP prior becomes:
-\begin{equation} \label{eq-laplace-approx-function-space}
- g(\vx) \sim \Norm \left( \mu(\vx), \kappa(\vx, \vx') \right) \quad \text{with} \quad
-  \mu(\vx) = \vzeros \quad \text{and} \quad
+\begin{align} \label{eq-laplace-approx-function-space}
+ g(\vx) \sim \Norm \left( \mu(\vx), \kappa(\vx, \vx') \right) \quad
+  \mu(\vx)
+  = \vzeros \quad
   \kappa(\mathbf{x}, \mathbf{x}')
   = \frac{1}{\delta} \Jac{\weights^*}{\mathbf{x}}\Jac{\weights^*}{\mathbf{x}'}^\top,
-\end{equation}
+\end{align}
 where the kernel is the Neural Tangent Kernel (NTK) \citep{jacot2018neural} with Jacobian $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$.
@@
   \begin{subfigure}{.78\textwidth}
-    \tikz\node[minimum width=\textwidth,minimum height=.35\textwidth,fill=black!10,rounded corners=2pt]{RL trjectories or something interesting?};
+    % \tikz\node[minimum width=\textwidth,minimum height=.35\textwidth,fill=black!10,rounded corners=2pt]{RL trjectories or something interesting?};
+
+    % \includegraphics[width=0.5\textwidth]{./fig/rl.pdf}
+    \input{./fig/rl}
+
   \end{subfigure}

### 2023-05-13 paper/main.tex
updating rl stuff

@@
 denote states \(\state \in \stateDomain \subseteq \R^{D_{\state}} \), actions \(\action \in \actionDomain \subseteq \R^{D_{\action}}\) and
-transition dynamics \(\transitionFn: \stateDomain \times \actionDomain \rightarrow \stateDomain \) subject to  i.i.d. transition noise \(\noise_{t}\).
-The goal of RL is to find the policy \(\pi \in \Pi \) that maximises the sum of rewards
-in expecation over the transition noise,
+transition dynamics \(\transitionFn: \stateDomain \times \actionDomain \rightarrow \stateDomain \).
+The goal of RL is to find the policy \(\pi : \stateDomain \rightarrow \actionDomain \), that maximises the sum of rewards
 \begin{align} \label{eq-model-free-objective}
@@
 \end{align}
+in expecation over the transition noise,
+ subject to  i.i.d. transition noise \(\noise_{t}\).
 where $\gamma \in [0, 1]$ is a discount factor to account for the infinte sum.

### 2023-05-13 paper/main.tex
Sec. 2

--- 2023-05-13 paper/main.tex
@@
 \newcommand{\Jac}[2]{\mathcal{J}_{#1}(#2)}
+\newcommand{\JacT}[2]{\mathcal{J}_{#1}^\top(#2)}
 
@@
 %
-In supervised learning, given a data set $\dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with $\mathbf{x}_i \in \inputDomain$ and $\mathbf{y}_i \in \outputDomain$, the weights $\weights \in \R^{P}$ of a neural network
-, $f_\mathbf{w} : \inputDomain \mapsto \outputDomain$, 
-are usually trained to minimize the (regularized) empirical risk,
-\begin{align} \label{eq-empirical-risk}
+In supervised learning, given a data set $\dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with input $\mathbf{x}_i \in \inputDomain$ and output $\mathbf{y}_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w} : \inputDomain \to \outputDomain$, are usually trained to minimize the (regularized) empirical risk,
+%
+\begin{equation} \label{eq-empirical-risk}
   \weights^{*} = 
-  \argmin_{\weights} \mathcal{L}(\dataset,\weights) =
-  \argmin_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
-\end{align}
-If $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) = -\log(p(\mathbf{y} \mid f_\weights(\mathbf{x}_{i}))$ and $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$ then we can view \cref{eq-empirical-risk} as the MAP solution to a Bayesian objective, where $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.
-
-\subsection{Neural network to GP prior} 
+  \arg \min_{\weights} \mathcal{L}(\dataset,\weights) =
+  \arg \min_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
+\end{equation}
+%
+If $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) = -\log(p(\mathbf{y} \mid f_\weights(\mathbf{x}_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$, where the regularization weight takes the role of a prior precision parameter.
+
+\subsection{Linearization gives rise to a Gaussian process posterior} 
 \label{sec:nn2gp}
 %
-A Gaussian process characterizes a distribution over functions in terms of the first two moments.
-The key quantity of a Gaussian process is the prior covariance function (or kernel function) $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors in $\R^{\mathrm{D}}$.
+The structure of the posterior given by the loss-landscape around the MAP weights $\vw^*$  induces a correlation structure on learned model functions of the neural network.
+These can be seen as possible perturbed versions of $f_{\vw^*}$ that can be used for characterizing ambiguity and uncertainty in the learned model (see \cref{fig:banana} for an example of sampling in weight-space).
+This gives rise to a probability {\em distribution} over the possible functions.
+If we limit the interest to the first two moments, we can characterize the resulting posterior over these functions as a Gaussian process (GP).
+
+%A Gaussian procss characterizes a distribution over functions in terms of the first two moments. The key quantity of 
+%A Gaussian process is the prior covariance function (or kernel function) $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors in $\R^{\mathrm{D}}$.
 We aim to find a kernel based on the neural network to build the Gaussian process posterior.
-If we had the following function parameterization $g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx') = \delta^{-1} \phi(\vx) \phi(\vx')^\T$ see \citep{rasmussen2006gaussian} for details.\todo{this part needs to be rewritten, starts talking about a general function parameterisation and then jumps directly to the neural network}
+A GP is fully characterized by a mean $\mu(\cdot)$ and covariance function $\kappa(\cdot,\cdot)$ (kernel).
+If we had the following function parameterization $g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx') = \delta^{-1} \phi(\vx) \phi^\T(\vx')$ (see Ch.~XXX in \cite{rasmussen2006gaussian} for details).\todo{this part needs to be rewritten, starts talking about a general function parameterisation and then jumps directly to the neural network}
 We can approximate the feature map of the neural network  $f_\weights(\mathbf{x})$  by using the Jacobian at $\weights^*$ thus our GP prior becomes:
-\begin{align} \label{eq-laplace-approx-function-space}
- g(\vx) \sim \Norm \left( \mu(\vx), \kappa(\vx, \vx') \right) \quad
-  \mu(\vx)
-  = \vzeros \quad
+\begin{equation} \label{eq-laplace-approx-function-space}
+ g(\vx) \sim \GP \left( \mu(\vx), \kappa(\vx, \vx') \right) \quad \text{with} \quad
+  \mu(\vx) = 0 \quad \text{and} \quad
   \kappa(\mathbf{x}, \mathbf{x}')
-  = \frac{1}{\delta} \Jac{\weights^*}{\mathbf{x}}\Jac{\weights^*}{\mathbf{x}'}^\top,
-\end{align}
-where the kernel is the Neural Tangent Kernel (NTK) \citep{jacot2018neural} with Jacobian $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$.
-Alternatively, we could have followed the derivation in \citet{immerImprovingPredictionsBayesian2021} where they perform a local linearization of the neural network  $f^{\textrm{lin}}_{\vw^*}(\vx; \vw) = f_{\vw^*}(\vx) + \Jac{\weights^*}{\mathbf{x}} \, (\vw - \vw^*)$.
-Their mean prior function differ from ours, \cref{eq-laplace-approx-function-space}, as theirs comes from setting  $  \mu(\vx) = f^{\textrm{lin}}_{\vw_*}(\vx; \vw = \vzeros) = f_{\vw^*}(\vx) - \Jac{\weights^*}{\mathbf{x}} \vw^*$, \ie the difference between the linear model approximation and the neural network function at $\vx$.
+  = \frac{1}{\delta} \Jac{\weights^*}{\mathbf{x}}\JacT{\weights^*}{\mathbf{x}'},
+\end{equation}
+%
+where the kernel is the so-called Neural Tangent Kernel (NTK, \cite{jacot2018neural}) with Jacobian $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$.
+Alternatively, we could have followed the derivation by \citet{immerImprovingPredictionsBayesian2021}, where they perform a local linearization of the neural network  $f^{\textrm{lin.}}_{\vw^*}(\vx; \vw) = f_{\vw^*}(\vx) + \Jac{\weights^*}{\mathbf{x}} \, (\vw - \vw^*)$.
+Their mean function differ from ours, \cref{eq-laplace-approx-function-space}, as theirs comes from setting  $\mu(\vx) = f^{\textrm{lin.}}_{\vw_*}(\vx; \vw = \vzeros) = f_{\vw^*}(\vx) - \Jac{\weights^*}{\mathbf{x}} \vw^*$, \ie the difference between the linear model approximation and the neural network function at $\vx$.
 %which does not seem useful as a prior mean function,
@@
 
+\paragraph{Linearization in the dual parameters}
 As stated in \citet[Lemma~1]{csato2002sparse}, the posterior process mean and covariance functions of a GP prior, combined with a likelihood function and $\dataset$ can be stated as:
 \begin{equation}  \label{eq:gp_pred}
- \myexpect_{p(f_i \mid\vy)}[f_i] = \vk_{\vx i}^\top \valpha , \quad
-\textrm{Var}_{p(f\mid\vy)}[f_i] = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
+ \myexpect_{p(f_i \mid\vy)}[f_i] = \vk_{\vx i}^\top \valpha \quad \text{and} \quad
+\mathrm{Var}_{p(f\mid\vy)}[f_i] = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
 \end{equation}
-where $f_i = f_\weights(\vx_i)$, the $ij$th entry of the matrix $\MKxx \in \R^{m \times m}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$th element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
+where $f_i = f_\weights(\vx_i)$, the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{m \times m}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
 The dual parameters consist of the vector $\valpha \in \R^{m}$ and vector $\vbeta \in \R^{m}$, defined as:
@@
 \end{equation}
+%
 The parameters $(\alpha_i, \beta_i)$ are the dual parameters that arise in the dual formulations used in, for example, support vector machines \citep{cortes1995support}, whose origins are found in work by \citet{kimeldorf1971some}.
@@
 
-\textbf{Neural network dual variables} As we are using the MAP solution of the neural network loss we will use the Laplace approximation for the dual variables but other techniques could be used.
-As was detailed in \cite{wilkinson2023bayes, rasmussen2006gaussian} the dual variables of the Laplace approximation is the same as removing the posterior averaging from \cref{eq:dual_param} meaning:
+\paragraph{Neural network dual variables}
+As we are using the MAP solution of the neural network loss we will use the Laplace approximation for the dual variables but other techniques could be used.
+As was detailed in \cite{wilkinson2023bayes, rasmussen2006gaussian}, the dual variables of the Laplace approximation is the same as removing the posterior averaging from \cref{eq:dual_param} meaning:
 \begin{equation}
 \label{eq:dual_param_laplace}
-\hat{\alpha}_i \coloneqq \nabla_{f_i}\log p(y_i \mid f_i),  \quad
-\hat{\beta}_i \coloneqq - \nabla^2_{f_i f_i}\log p(y_i \mid f_i),
+\hat{\alpha}_i \coloneqq \nabla_{f_i}\log p(y_i \mid f_i),  \quad \text{and} \quad
+\hat{\beta}_i \coloneqq - \nabla^2_{f_i f_i}\log p(y_i \mid f_i).
 \end{equation}
@@
 Again this is similar to what was arrived at for \citet{immerImprovingPredictionsBayesian2021} for the posterior variance function, but they instead use the $f_{\vw^*}(\vx)$ for the posterior mean and fail to spot the significance of the dual variables.
-The problem with \cref{eq:gp_pred} is that to make predictions and compute variances we must incur a cost of $O(n^3)$ which limits the use of the GP on large datasets.
+The problem with \cref{eq:gp_pred} is that to make predictions and compute variances we must incur a cost of $O(n^3)$ which limits the use of the GP on large data sets.
 
@@
   \begin{subfigure}{.78\textwidth}
-    % \tikz\node[minimum width=\textwidth,minimum height=.35\textwidth,fill=black!10,rounded corners=2pt]{RL trjectories or something interesting?};
-
-    % \includegraphics[width=0.5\textwidth]{./fig/rl.pdf}
-    \input{./fig/rl}
-
+    \tikz\node[minimum width=\textwidth,minimum height=.35\textwidth,fill=black!10,rounded corners=2pt]{RL trjectories or something interesting?};
   \end{subfigure}

### 2023-05-13 paper/main.tex

@@
 If we had the following function parameterization $g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx') = \delta^{-1} \phi(\vx) \phi^\T(\vx')$ (see Ch.~XXX in \cite{rasmussen2006gaussian} for details).\todo{this part needs to be rewritten, starts talking about a general function parameterisation and then jumps directly to the neural network}
+%=======
+%\subsection{Neural Network to GP Prior} 
+%\label{sec:nn2gp}
+%%
+%A Gaussian process characterizes a distribution over functions in terms of the first two moments.
+The key quantity of a Gaussian process is the prior covariance function (or kernel function) $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors in $\R^{\mathrm{D}}$.
+We aim to find a kernel based on the neural network to build the Gaussian process posterior.
+A common approach to find a $q(\vw)$ is to perform a Laplace-GGN approximation.
+The approximation can be seen as taking the map solution of \cref{eq-empirical-risk}
+%
+%A linear function in terms of parameters can easily be converted from the weight space to the function space as follows
+%
+%\begin{equation}
+%\hat{f}_\weights(\mathbf{x}_{i})) = \phi(\vx)^\top \vw
+%\end{equation}
+%
+%$g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx') = \delta^{-1} \phi(\vx) \phi(\vx')^\T$ see \citep{rasmussen2006gaussian} for details.\todo{this part needs to be rewritten, starts talking about a general function parameterisation and then jumps directly to the neural network}
 We can approximate the feature map of the neural network  $f_\weights(\mathbf{x})$  by using the Jacobian at $\weights^*$ thus our GP prior becomes:

### 2023-05-13 paper/main.tex
commit start of rewrite 2
Minor

@@
   %
-  \caption{Binary classification (\mysquare~vs.~\mycircle)}
+  \caption{Binary classification (\mysquare~vs.~\mycircle) on the {\sc banana} toy data data set. We convert the left-hand neural network  }
   \label{fig:banana}  
@@
 %
+
 The structure of the posterior given by the loss-landscape around the MAP weights $\vw^*$  induces a correlation structure on learned model functions of the neural network.
@@
 If we limit the interest to the first two moments, we can characterize the resulting posterior over these functions as a Gaussian process (GP).
+
+%A Gaussian process characterizes a distribution over functions in terms of the first two moments.
+The key quantity of a Gaussian process is the prior covariance function (or kernel function) $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors in $\R^{\mathrm{D}}$.
+We aim to find a kernel based on the neural network to build the Gaussian process posterior.
+A linear function in terms of parameters can easily be converted from the weight space to the function space as follows:
+%\begin{equation}
+%g_\weights(\mathbf{x}_{i})) = \phi(\vx)^\top \vw \implies \mu(\vx) = \vzeros \quad \kappa(\mathbf{x}, \mathbf{x}') = \frac{1}{\delta} \phi(\vx)^\top \phi(\vx)
+%\end{equation}
+%
+%
+%
+% The approximation can be seen as taking the map solution of \cref{eq-empirical-risk} as the mean of $q(\vw)$ but then substituting the following functional approximation for $\hat{f}_\weights(\mathbf{x}_{i}) = \Jac{\weights^*}{\mathbf{x}} $
 
@@
 %=======
-%\subsection{Neural Network to GP Prior} 
-%\label{sec:nn2gp}
-%%
-%A Gaussian process characterizes a distribution over functions in terms of the first two moments.
+\subsection{Neural Network to GP Prior} 
+\label{sec:nn2gp}
+%
+A common approach to find a distribution over $q(\vw)$ is to perform a Laplace-GGN approximation.
+The approximation can be seen as taking the Laplace approximation of \cref{eq-empirical-risk} and approximating the   Hessian of $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i)$ with the Generalized Gauss Newton(GGN) approximation.
+\citet{immerImprovingPredictionsBayesian2021} proposed to make the following linear approximation
+$f^{\textrm{lin.}}_{\vw^*}(\vx; \vw) = f_{\vw^*}(\vx) + \Jac{\weights^*}{\mathbf{x}} \, (\vw - \vw^*)$ of the neural network, with Jacobian $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$.
+The idea
+
+ at the map estimate it was possible to improve predictions from a Laplace-GGN Bayesian neural network.
+with Jacobian $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$
+
+A Gaussian process characterizes a distribution over functions in terms of the first two moments.
 The key quantity of a Gaussian process is the prior covariance function (or kernel function) $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors in $\R^{\mathrm{D}}$.
 We aim to find a kernel based on the neural network to build the Gaussian process posterior.
-A common approach to find a $q(\vw)$ is to perform a Laplace-GGN approximation.
-The approximation can be seen as taking the map solution of \cref{eq-empirical-risk}
-%
-%A linear function in terms of parameters can easily be converted from the weight space to the function space as follows
-%
-%\begin{equation}
-%\hat{f}_\weights(\mathbf{x}_{i})) = \phi(\vx)^\top \vw
-%\end{equation}
-%
-%$g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx') = \delta^{-1} \phi(\vx) \phi(\vx')^\T$ see \citep{rasmussen2006gaussian} for details.\todo{this part needs to be rewritten, starts talking about a general function parameterisation and then jumps directly to the neural network}
+
+A linear function in terms of parameters can easily be converted from the weight space to the function space as follows
+
+\begin{equation}
+\hat{f}_\weights(\mathbf{x}_{i})) = \phi(\vx)^\top \vw
+\end{equation}
+
+$g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx') = \delta^{-1} \phi(\vx) \phi(\vx')^\T$ see \citep{rasmussen2006gaussian} for details.\todo{this part needs to be rewritten, starts talking about a general function parameterisation and then jumps directly to the neural network}
 We can approximate the feature map of the neural network  $f_\weights(\mathbf{x})$  by using the Jacobian at $\weights^*$ thus our GP prior becomes:

### 2023-05-13 paper/main.tex
commit start of rewrite 2

@@
 %
-A common approach to find a distribution over $q(\vw)$ is to perform a Laplace-GGN approximation.
-The approximation can be seen as taking the Laplace approximation of \cref{eq-empirical-risk} and approximating the   Hessian of $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i)$ with the Generalized Gauss Newton(GGN) approximation.
-\citet{immerImprovingPredictionsBayesian2021} proposed to make the following linear approximation
+Given an approximate posterior $q(\vw)$  \citet{immerImprovingPredictionsBayesian2021} proposed to make the following linear approximation
 $f^{\textrm{lin.}}_{\vw^*}(\vx; \vw) = f_{\vw^*}(\vx) + \Jac{\weights^*}{\mathbf{x}} \, (\vw - \vw^*)$ of the neural network, with Jacobian $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$.
-The idea
+The approximation can be used with any approximate inference technique but in the paper they focus on the Laplace-GNN.
+They find that the linear approximation helps to improve predictions by correcting the approximate posterior when sampled through a non-Gaussian likelihoods.
 

### 2023-05-13 paper/main.tex
making it work

@@
 \end{table}
-
-\subsection{Fast updates in reinforcement learning}
-
-\begin{figure}[!t]
-  \centering
-  \begin{subfigure}{.2\textwidth}
-  \resizebox{\textwidth}{!}{%
-  \begin{tikzpicture}[inner sep=0,outer sep=0]
-
-    % Draw decorated 'ground'
-    \draw[postaction={draw, decorate, decoration={border, angle=-45,
-					amplitude=1cm, segment length=.5cm}}] (-3,-1.5) -- (12,-1.5);
-
-    % The cart
-    \draw[draw=black,fill=black!50,draw=black,line width=3pt,rounded corners=1mm] (0,0) rectangle (9cm,3cm);
-    \node[fill=black,circle,minimum size=.5cm] (dot) at (4.5cm,3cm) {};
-
-    % Wheels
-    \node[fill=white,draw=black,line width=3pt,circle,minimum size=2cm,,fill=black!50] at (2cm,-.5cm) {};
-    \node[fill=white,draw=black,line width=3pt,circle,minimum size=2cm,fill=black!50] at (7cm,-.5cm) {};
-
-    % The arm
-    \node[anchor=north,minimum width=1cm,minimum height=14cm,draw=black,rotate=20,rounded corners=5mm,yshift=7mm,xshift=-.3mm,fill=white,draw=black,line width=3pt] at (dot) {};
-    \node[fill=black,circle,minimum size=.5cm] at (dot) {};
-
-    % Markings
-    \draw[loosely dashed,line width=1pt] (4.5,6) -- (4.5,-10);
-
-    % Arrow
-    \draw[->,black,line width=3pt,-{Latex[length=7mm,width=7mm]}] (1,5) --node[above,outer sep=6pt]{\large $x$} (4.5,5);
-
-    \def\centerarc[#1](#2)(#3:#4:#5)% Syntax: [draw options] (center) (initial angle:final angle:radius)
-    { \draw[#1] ($(#2)+({#5*cos(#3)},{#5*sin(#3)})$) arc (#3:#4:#5); }
-
-    % Draw arc
-    \centerarc[black,line width=3pt](dot)(270:290:11)
-    \node at (6.5,-9) {$\theta$};
-
-    \node[white,minimum size=1cm] at (4.5,-13) {};
-
-  \end{tikzpicture}}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}{.78\textwidth}
-    % \tikz\node[minimum width=\textwidth,minimum height=.35\textwidth,fill=black!10,rounded corners=2pt]{RL trjectories or something interesting?};
-
-    % \includegraphics[width=0.5\textwidth]{./fig/rl.pdf}
-    \input{./fig/rl}
-
-  \end{subfigure}
-  \hfill
-  \caption{Add caption.}
-  \label{fig:rl}
-\end{figure}
+%
+%
+%\subsection{Fast updates in reinforcement learning}
+%
+%\begin{figure}[!t]
+%  \centering
+%  \begin{subfigure}{.2\textwidth}
+%  \resizebox{\textwidth}{!}{%
+%  \begin{tikzpicture}[inner sep=0,outer sep=0]
+%  
+%    % Draw decorated 'ground'
+%    \draw[postaction={draw, decorate, decoration={border, angle=-45,
+%					amplitude=1cm, segment length=.5cm}}] (-3,-1.5) -- (12,-1.5);
+%  
+%    % The cart
+%    \draw[draw=black,fill=black!50,draw=black,line width=3pt,rounded corners=1mm] (0,0) rectangle (9cm,3cm);
+%    \node[fill=black,circle,minimum size=.5cm] (dot) at (4.5cm,3cm) {};
+%    
+%    % Wheels
+%    \node[fill=white,draw=black,line width=3pt,circle,minimum size=2cm,,fill=black!50] at (2cm,-.5cm) {};
+%    \node[fill=white,draw=black,line width=3pt,circle,minimum size=2cm,fill=black!50] at (7cm,-.5cm) {};  
+%    
+%    % The arm
+%    \node[anchor=north,minimum width=1cm,minimum height=14cm,draw=black,rotate=20,rounded corners=5mm,yshift=7mm,xshift=-.3mm,fill=white,draw=black,line width=3pt] at (dot) {};
+%    \node[fill=black,circle,minimum size=.5cm] at (dot) {};
+%    
+%    % Markings
+%    \draw[loosely dashed,line width=1pt] (4.5,6) -- (4.5,-10);
+%    
+%    % Arrow
+%    \draw[->,black,line width=3pt,-{Latex[length=7mm,width=7mm]}] (1,5) --node[above,outer sep=6pt]{\large $x$} (4.5,5);
+%    
+%    \def\centerarc[#1](#2)(#3:#4:#5)% Syntax: [draw options] (center) (initial angle:final angle:radius)
+%    { \draw[#1] ($(#2)+({#5*cos(#3)},{#5*sin(#3)})$) arc (#3:#4:#5); }
+%    
+%    % Draw arc
+%    \centerarc[black,line width=3pt](dot)(270:290:11)
+%    \node at (6.5,-9) {$\theta$};
+%    
+%    \node[white,minimum size=1cm] at (4.5,-13) {};
+%    
+%  \end{tikzpicture}}
+%  \end{subfigure}
+%  \hfill
+%  \begin{subfigure}{.78\textwidth}
+%    % \tikz\node[minimum width=\textwidth,minimum height=.35\textwidth,fill=black!10,rounded corners=2pt]{RL trjectories or something interesting?};
+%
+%    % \includegraphics[width=0.5\textwidth]{./fig/rl.pdf}
+%    \input{./fig/rl}
+%
+%
+%  \end{subfigure}
+%  \hfill
+%  \caption{Add caption.}
+%  \label{fig:rl}
+%\end{figure}
+%
+%
 
@@
 \end{assumption}
-
-\subsection{Model-based Reinforcement Learning (RL)}
-The goal of reinforcement learning is to find a policy \(\pi \in \Pi\) that maximises the sum of discounted
-rewards in expecation under the transition noise (aleatoric uncertainty),
-\begin{align} \label{eq-model-free-objective}
-\policy^{*} = \arg \max_{\policy \in \policyDomain} J(\transitionFn, \policy) = \arg \max_{\policy \in \policyDomain} \mathbb{E}_{\noise_{0:\infty}} \left[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \right],
-\end{align}
-where $\gamma \in [0, 1]$
-
-\textbf{Model-based}
-In Bayesian model-based RL, we obtain the posterior over the dynamics \(p(f\mid\mathcal{D})\) after performing (approximate) Bayesian
-inference given a state transition data set \(\mathcal{D} = \{\{(s_{t},a_{t}), s_{t+1}\}^{T_{i}}_{t=1}\}_{i=0}^{N}\).
-\cref{alg-mbrl} shows the typical model-based RL loop.
-Importantly, the dynamics are usually only updated after an episode $i$.
-
-\begin{algorithm}[!b]
-\caption{Model-based RL}\label{alg-mbrl}
-\begin{algorithmic}[1]
-  \Require Start state $\state_{0}$, initial data set $\dataset_{0}$, dynamics posterior $p(\transitionFn \mid \dataset_{0})$, policy $\policy_{0}$
-\For{$i  \in \{1, 2, \ldots, \text{num episodes} \}$}
-    \State Reset the system to $\state_{0}$ and reset trajectory buffers $\bm\tau_{t} = \emptyset \ \forall t$
-    \For{$t  \in \{1, 2, \ldots, \text{num steps} \}$}
-      % \State Collect  $\tau_{0:t} = \tau_{0:t-1} \cup (\state_{j}, \action_{j}, \state_{j+1}, r_{j+1})$
-      \State Use \cref{eq-greedy}/\cref{eq-posterior-sampling}/\cref{eq-ucrl} to collect data $\bm\tau_{t} = \bm\tau_{t-1} \cup (\state_{t}, \policy_{i}(\state_{t}), \transitionFn(\state_{t}, \policy_{i}(\state_{t})), r_{t+1})$
-      % \State Execute policy $\policy_{i}(\state_{t})$ in environment and update trajectory $\tau_{i+1} = \{\state_{j}, \action_{j}, \state_{j+1}, r_{j+1}) \}_{j=0}^{t}$
-    \EndFor
-    \State Update data set $\dataset_{0:i} = \dataset_{0:i-1} \cup \tau$
-    \State Train dynamics $p(\transitionFn \mid \dataset_{0:i}) \leftarrow \text{update\_dynamics}(\dataset_{0:i}, p(\transitionFn \mid \dataset_{0:i-1}))$
-    % \State Train dynamics $p(\transitionFn \mid \dataset_{0:i+1})$ using $\dataset_{0:i+1}$
-    % \State Improve policy $\pi_{i+1}$ using $p(\transitionFn \mid \dataset_{0:i+1})$ and/or $\dataset_{0:i+1}$
-    \State Improve policy $\pi_{i+1} \leftarrow \text{update\_policy}(p\left(\transitionFn \mid \dataset_{0:i}), \dataset_{0:i} \right)$
-    %\State Improve policy $\pi_{i+1}$ using $p(\transitionFn \mid \dataset_{0:i+1})$ and/or $\dataset_{0:i+1}$
-\EndFor
-\end{algorithmic}
-\end{algorithm}
-
-% \begin{minipage}{0.499\textwidth}
-% \begin{algorithm}[H]
-% \caption{Model-based RL}\label{alg-mbrl}
-% \begin{algorithmic}[1]
-%   \Require Initial data set $\dataset_{0}$, dynamics posterior $p(\transitionFn \mid \dataset_{0})$, policy $\policy_{0}$
-% \For{$i  \in \{0, 1, \ldots, \text{num episodes} \}$}
-%     \For{$t  \in \{0, 1, \ldots, \text{num steps} \}$}
-%       \State Execute policy $\policy_{i}(\state_{t})$ in environment
-%       \State $\tau_{i+1} = \{\state_{j}, \action_{j}, \state_{j+1}, r_{j+1}) \}_{j=0}^{t}$
+%
+%\subsection{Model-based Reinforcement Learning (RL)}
+%The goal of reinforcement learning is to find a policy \(\pi \in \Pi\) that maximises the sum of discounted
+%rewards in expecation under the transition noise (aleatoric uncertainty),
+%\begin{align} \label{eq-model-free-objective}
+%\policy^{*} = \arg \max_{\policy \in \policyDomain} J(\transitionFn, \policy) = \arg \max_{\policy \in \policyDomain} \mathbb{E}_{\noise_{0:\infty}} \left[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \right],
+%\end{align}
+%where $\gamma \in [0, 1]$
+%
+%\textbf{Model-based}
+%In Bayesian model-based RL, we obtain the posterior over the dynamics \(p(f\mid\mathcal{D})\) after performing (approximate) Bayesian
+%inference given a state transition data set \(\mathcal{D} = \{\{(s_{t},a_{t}), s_{t+1}\}^{T_{i}}_{t=1}\}_{i=0}^{N}\).
+%\cref{alg-mbrl} shows the typical model-based RL loop.
+%Importantly, the dynamics are usually only updated after an episode $i$.
+%
+%\begin{algorithm}[!b]
+%\caption{Model-based RL}\label{alg-mbrl}
+%\begin{algorithmic}[1]
+%  \Require Start state $\state_{0}$, initial data set $\dataset_{0}$, dynamics posterior $p(\transitionFn \mid \dataset_{0})$, policy $\policy_{0}$
+%\For{$i  \in \{1, 2, \ldots, \text{num episodes} \}$}
+%    \State Reset the system to $\state_{0}$ and reset trajectory buffers $\bm\tau_{t} = \emptyset \ \forall t$
+%    \For{$t  \in \{1, 2, \ldots, \text{num steps} \}$}
+%      % \State Collect  $\tau_{0:t} = \tau_{0:t-1} \cup (\state_{j}, \action_{j}, \state_{j+1}, r_{j+1})$
+%      \State Use \cref{eq-greedy}/\cref{eq-posterior-sampling}/\cref{eq-ucrl} to collect data $\bm\tau_{t} = \bm\tau_{t-1} \cup (\state_{t}, \policy_{i}(\state_{t}), \transitionFn(\state_{t}, \policy_{i}(\state_{t})), r_{t+1})$
+%      % \State Execute policy $\policy_{i}(\state_{t})$ in environment and update trajectory $\tau_{i+1} = \{\state_{j}, \action_{j}, \state_{j+1}, r_{j+1}) \}_{j=0}^{t}$
 %    \EndFor
-%     \State Update data set $\mathcal{D}_{0:i+1} = \mathcal{D}_{0:i} \cup \tau_{i+1}$
-%     \State Train dynamics $p(\transitionFn \mid \dataset_{0:i+1})$
-%     \State Improve policy $\pi_{i+1}$
+%    \State Update data set $\dataset_{0:i} = \dataset_{0:i-1} \cup \tau$
+%    \State Train dynamics $p(\transitionFn \mid \dataset_{0:i}) \leftarrow \text{update\_dynamics}(\dataset_{0:i}, p(\transitionFn \mid \dataset_{0:i-1}))$
+%    % \State Train dynamics $p(\transitionFn \mid \dataset_{0:i+1})$ using $\dataset_{0:i+1}$
+%    % \State Improve policy $\pi_{i+1}$ using $p(\transitionFn \mid \dataset_{0:i+1})$ and/or $\dataset_{0:i+1}$
+%    \State Improve policy $\pi_{i+1} \leftarrow \text{update\_policy}(p\left(\transitionFn \mid \dataset_{0:i}), \dataset_{0:i} \right)$
 %    %\State Improve policy $\pi_{i+1}$ using $p(\transitionFn \mid \dataset_{0:i+1})$ and/or $\dataset_{0:i+1}$
+%\EndFor
+%\end{algorithmic}
+%\end{algorithm}
+%
+%% \begin{minipage}{0.499\textwidth}
+%% \begin{algorithm}[H]
+%% \caption{Model-based RL}\label{alg-mbrl}
+%% \begin{algorithmic}[1]
+%%   \Require Initial data set $\dataset_{0}$, dynamics posterior $p(\transitionFn \mid \dataset_{0})$, policy $\policy_{0}$
+%% \For{$i  \in \{0, 1, \ldots, \text{num episodes} \}$}
+%%     \For{$t  \in \{0, 1, \ldots, \text{num steps} \}$}
+%%       \State Execute policy $\policy_{i}(\state_{t})$ in environment
+%%       \State $\tau_{i+1} = \{\state_{j}, \action_{j}, \state_{j+1}, r_{j+1}) \}_{j=0}^{t}$
+%%     \EndFor
+%%     \State Update data set $\mathcal{D}_{0:i+1} = \mathcal{D}_{0:i} \cup \tau_{i+1}$
+%%     \State Train dynamics $p(\transitionFn \mid \dataset_{0:i+1})$
+%%     \State Improve policy $\pi_{i+1}$
+%%     %\State Improve policy $\pi_{i+1}$ using $p(\transitionFn \mid \dataset_{0:i+1})$ and/or $\dataset_{0:i+1}$
+%% \EndFor
+%% \end{algorithmic}
+%% \end{algorithm}
+%% \end{minipage}
+%% \hfill
+%% \begin{minipage}{0.499\textwidth}
+%% \begin{algorithm}[H]
+%% \caption{Model-based RL with fast updates}\label{alg-mbrl-fast-updates}
+%% \begin{algorithmic}[1]
+%%   \Require Initial data set $\dataset_{0}$, dynamics posterior $p(\transitionFn \mid \dataset_{0})$, policy $\policy_{0}$
+%%     % ${p(\state_{\timeInd+1} \mid \singleInput, \dataset_{0})}$}
+%% \For{$i  \in \{0, 1, \ldots, \text{num episodes} \}$}
+%%     \For{$t  \in \{0, 1, \ldots, \text{num steps} \}$}
+%%       \State Execute policy $\policy_{i}(\state_{t})$ in environment
+%%       % \State Append transition $\state_{t}, \action_{t}, \state_{t+1}, r_{t+1})$ to trajectory $\tau_{i}$
+%%       \State $\tau_{i+1} = \{\state_{j}, \action_{j}, \state_{j+1}, r_{j+1}) \}_{j=0}^{t}$
+%%       \State {\color{blue}Update dynamics $p(\transitionFn \mid \dataset_{0:i} \cup \tau_{i+1})$}
+%%     \EndFor
+%%     \State Update data set $\mathcal{D}_{0:i+1} = \mathcal{D}_{0:i} \cup \tau_{i+1}$
+%%     \State Train dynamics $p(\transitionFn \mid \dataset_{0:i+1})$
+%%     \State Improve policy $\pi_{i+1}$
+%%     %\State Improve policy $\pi_{i+1}$ using $p(\transitionFn \mid \dataset_{0:i+1})$ and/or $\dataset_{0:i+1}$
+%% \EndFor
+%% \end{algorithmic}
+%% \end{algorithm}
+%% \end{minipage}
+%
+%
+%
+%\subsection{Exploration Strategies}
+%\textbf{Greedy exploitation}
+%Given the posterior dynamics \(p(\transitionFn \mid \mathcal{D})\),
+%a common approach is to simply take the expecation over both the aleatoric and epistemic uncertainty,
+%\begin{align} \label{eq-greedy}
+%\policy_{i+1}^{\text{greedy}} = \arg \max_{\policy \in \policyDomain} \mathbb{E}_{\transitionFn \sim p(\transitionFn \mid \dataset_{0:i})} \left[ J(\transitionFn, \policy) \right],
+%\end{align}
+%This approach has been widely adopted, for example, in PILCO, PETS, GP-MPC
+%\cite{deisenrothPILCO2011,chuaDeepReinforcementLearning2018,kamtheDataEfficient2018}.
+%This approach helps to alleviate model bias as the posterior ``knows what the model does not know''.
+%This is because the predictive posterior \(p(f(s_{t},a_{t}) \mid (s_{t},a_{t}),  \mathcal{D} )\) will be (or should be) uncertain when making
+%predictions far away from the training data.
+%The expectation considers all possible dynamics models which prevents the policy optimisation from
+%exploiting innacuracies in the model.
+%This approach has no guarantees for exploration in the general case.
+%However, under specific dynamics and reward structures (e.g. PILCO) this objective can achieve sublinear regret.
+%\todo{need to double check sublinear regret statement. And give a reference}
+%
+%
+%\textbf{Posterior sampling}
+%\cite{osbandWhyPosteriorSampling2017,osbandMoreEfficientReinforcement2013}
+%\begin{align} \label{eq-posterior-sampling}
+%\policy_{i+1}^{\text{PS}} = \arg \max_{\policy \in \policyDomain} \left[ J(\transitionFn, \policy) \right] \quad \text{s.t. } \transitionFn \sim p(\transitionFn \mid \dataset_{0:i})
+%\end{align}
+%
+%\textbf{Hallucinated upper confidence RL}
+%A more theoretically grounded exploration strategy is UCRL \citep{jakschNearoptimal2010}, which optimises joinly over
+%policies and models inside the set
+%\(\mathcal{M} = \{ f \mid | f(s,a) - \mu_{i}(s, a) | \leq \beta_{i} \Sigma_{i}(s, a) \quad \forall s, a \in \mathcal{S} \times \mathcal{A} \}\), representing all statistically plausible
+%models under the posterior \(p(f(s,a) \mid \mathcal{D}_{0:i} \cup (s,a)) = \mathcal{N}(f(s,a) \mid \mu_{i}(s,a), \Sigma_{i}(s,a))\) at episode \(i\).
+%This strategy is given by,
+%\begin{align} \label{eq-ucrl}
+%\policy_{i+1}^{\text{UCRL}} = \arg \max_{\policy \in \policyDomain} \max_{\transitionFn \in \mathcal{M}} J(\transitionFn, \policy).
+%\end{align}
+%This strategy optimises an optimistic policy over the set of plausible dynamics models.
+%Although this joint optimisation is intractable in general,
+%\cite{curiEfficient2020} proposed a practical alternative which is detailed in \cref{sec-hucrl}.
+%
+%\textbf{MPC vs policy learning}
+%It is worth noting that the strategies in \cref{eq-greedy,eq-posterior-sampling,eq-ucrl} can be used with both model predictive control (MPC)
+%techniques, such as the cross entoropy method (CEM), and model-free RL techniques, such as soft actor-critic (SAC).
+%
+%
+%In this work we are interested in how we can use \(p(f \mid \mathcal{D})\) to alleviate some of the issues in model-based RL,
+%for example, model bias and the exploration-exploitation trade-off.
+%
+%
+%
+%\todo{show how to get new $\dualParam{1}$ and $\dualParam{2}$ in Train dynamics line of \cref{alg-mbrl-fast-updates}}
+%\begin{algorithm}[!t]
+%\caption{Model-based RL with fast updates}\label{alg-mbrl-fast-updates}
+%\begin{algorithmic}[1]
+%  \Require Start state $\state_{0}$, initial data set $\dataset_{0}$, dynamics posterior $p(\transitionFn \mid \dataset_{0})$ (inc.
+dual parameters $\dualParam{1}, \dualParam{2}$), policy $\policy_{0}$
+%    % ${p(\state_{\timeInd+1} \mid \singleInput, \dataset_{0})}$}
+%\For{$i  \in \{1, 2, \ldots, \text{num episodes} \}$}
+%    \State Reset the system to $\state_{0}$ and reset trajectory buffers $\bm\tau_{t} = \emptyset \ \forall t$
+%    \For{$t  \in \{1, 2, \ldots, \text{num steps} \}$}
+%      % \State Execute policy $\policy_{i}(\state_{t})$ (\cref{eq-fast-update-mpc}) in environment
+%      \State Use \cref{eq-fast-update-mpc} to collect data $\bm\tau_{t} = \bm\tau_{t-1} \cup (\state_{t}, \policy_{i}(\state_{t}), \transitionFn(\state_{t}, \policy^{\text{fast}}_{i}(\state_{t})), r_{t+1})$
+%      % \State Append transition $\state_{t}, \action_{t}, \state_{t+1}, r_{t+1})$ to trajectory $\tau_{i}$
+%      % \State $\tau_{i+1} = \{\state_{j}, \action_{j}, \state_{j+1}, r_{j+1}) \}_{j=0}^{t}$
+%      %\State {\color{blue}Update dynamics $p(\transitionFn \mid \dataset_{0:i} \cup \tau_{i+1})$}
+%      \State {\color{blue}Update dynamics posterior using \cref{eq-dual-update-svgp}, i.e. fast update}
+%      % \begin{align}
+%      % \dualParam{1}^{t+1} &\leftarrow \dualParam{1}^{t} +  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))} \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right] \\
+%      % \dualParam{2}^{t+1} &\leftarrow \dualParam{2}^{t} +  \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))}  \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right]
+%      % \end{align}}
 %    \EndFor
-% \end{algorithmic}
-% \end{algorithm}
-% \end{minipage}
+%    \State Update data set $\dataset_{0:i} = \dataset_{0:i-1} \cup \tau$
+%    \State Train dynamics $p(\transitionFn \mid \dataset_{0:i}) \leftarrow \text{update\_dynamics}(\dataset_{0:i}, p(\transitionFn \mid \dataset_{0:i-1}))$
+%    \State Improve policy $\pi^{\text{fast}}_{i+1} \leftarrow \text{update\_policy}(p\left(\transitionFn \mid \dataset_{0:i}), \dataset_{0:i} \right)$
+%\EndFor
+%\end{algorithmic}
+%\end{algorithm}
+%
+%
+%\subsubsection{Fast updates}
+%
+%
+%In this section we extend these fast updates to environment's with high dimensional state spaces and large data sets.
+%% Our method draws on the connection between BNNs and GPs and formulates a function space SVGP posterior given
+%Our method uses a BNN dynamic model and draws on the connection between BNNs and GPs
+%\citep{khanApproximate2019} to formulate a function space SVGP posterior,
+%where we can apply the fast updates from \cref{eq-dual-update-svgp}.
+%At a high-level, we first use Laplace's approximation to obtain a weight space posterior for our BNN.
+%We then linearise our BNN around the optimal parameters and interpret it as a GP.
+%Finally, we formulate a lower rank approximation of this GP posterior (i.e. a SVGP posterior) using inducing variables.
+%% formulates a function space SVGP posterior by drawing on the connection between BNNs and GPs.
+%
+%
+%The strategies in \cref{eq-greedy,eq-posterior-sampling,eq-hucrl} do not update the dynamic model during an episode.
+%A better approach would be to update the posterior at every time step during an episode, for example,
+%\begin{subequations}
+%\begin{align} \label{eq-fast-update-mpc}
+%  \policy_{i+1}^{\text{greedy}}(\state) &= \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
+%\E_{p(\transitionFn \mid \dataset_{0:i})} \left[J^{\Horizon}(\action_{0:\Horizon}, \transitionFn) \right] + \stateValueFn(\state_{\Horizon+1}) \\
+%  \policy_{i+1}^{\text{PS}}(\state) &= \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
+%J^{\Horizon}(\action_{0:\Horizon}, \transitionFn) + \stateValueFn(\state_{\Horizon+1}) \quad \text{s.t. } \transitionFn \sim p(\transitionFn \mid \dataset_{0:i} \cup \bm\tau_{t}) \\
+%  \policy_{i+1}^{\text{UCRL}}(\state) &= \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}} \max_{\transitionFn \in \mathcal{M}}
+%J^{\Horizon}(\action_{0:\Horizon}, \transitionFn) + \stateValueFn(\state_{\Horizon+1}) \quad \text{s.t.
+} \mathcal{M} = \{\transitionFn(\state_{t},\action_{t}) - \mu_{i,t}(\state_{t},\action_{t}) \leq \beta_{i,t} \Sigma_{i,t}(\state_{t}, \action_{t})\} \\
+%  \stateValueFn(\state) &= \mathbb{E} \left[ \sum_{t=0}^{\infty}     \discount^{t} \rewardFn(\state_{t},\action_{t}) \mid \state_{0}=\state \right] \label{eq-value-fn}
+%\end{align}
+%\end{subequations}
+%\begin{subequations}
+%\begin{align} \label{eq-fast-update-mpc-old}
+%  \policy^{\text{fast}}(\state) = \arg &\max_{\action_{0}} \max_{\action_{1}, \ldots, \action_{\Horizon}}
+%  \mathbb{E}_{\state_{\horizon} \sim p(\state_{\horizon+1} \mid \transitionFn(\state_{\horizon}, \action_{\horizon}))} \left[ \sum_{\horizon=0}^{\Horizon}     \discount^{\horizon} \rewardFn(\state_{\horizon},\action_{\horizon}) \mid \state_{0}=\state \right] + \discount^{\Horizon+1} \stateValueFn(\state_{\Horizon+1}) \\
+%  \stateValueFn(\state) &= \mathbb{E} \left[ \sum_{t=0}^{\infty}     \discount^{t} \rewardFn(\state_{t},\action_{t}) \mid \state_{0}=\state \right] \label{eq-fast-update-mpc}
+%\end{align}
+%\end{subequations}
+%
+%\begin{align} \label{}
+%  \policy(\state) = \arg &\max_{\action_{0}} \max_{\action_{1}, \ldots, \action_{\Horizon}} \max_{\optimisticTransition \in \optimisticTransitionSet}
+%  \sum_{\horizon=0}^{\Horizon}  \mathbb{E}_{\noise_{\horizon}} \left[  \discount^{\horizon} \rewardFn(\state_{\horizon},\action_{\horizon}) \right] + \discount^{\Horizon+1} \stateValueFn(\state_{\Horizon+1}) \\
+%  \text{s.t. } \state_{\horizon+1} &= \optimisticTransition(\state_{\horizon}, \action_{\horizon}) + \noise_{\horizon} \\
+%  \optimisticTransition(\state_{\horizon}, \action_{\horizon}) &=
+%\optimisticTransitionMean(\state_{\horizon}, \action_{\horizon}) \pm \beta_{i}
+%\optimisticTransitionCov(\state_{\horizon}, \action_{\horizon})
+%\end{align}
+%
+%\input{proof.tex}
+%
+%
+%\section{Hallucinated Upper Confidence Reinforcement Learning (H-UCRL)} \label{sec-hucrl}
+%\cite{curiEfficient2020} introduced a tractable approximation which retains some of the theoretical guarantees whilst
+%being applicable with deep model-based RL.
+%They introduce a function \(\eta: \mathcal{S} \times \mathcal{A} \rightarrow [-1, 1]^{p}\) which acts as a hallucinated control input.
+%The strategy is given by,
+%\begin{align} \label{eq-hucrl}
+%\pi_i^{\text{UCRL}} = \arg \max_{\policy \in \policyDomain} \max_{\eta(\cdot) \in [-1,1]} J(\transitionFn, \policy) \quad \text{s.t.} \quad \transitionFn = \mu_{i}(\state_{t}, \action_{t}) + \beta_{i} \Sigma_{i}(\state_{t}, \action_{t}) \eta(\state_{t},\action_{t}).
+%\end{align}
+%Intuitively, \(\eta(\state,\action) \in [-1,1]\) enables the optimisation to select any dynamics model
+%\(\transitionFn\) within \(\pm \beta \Sigma_{i}(\state_{t}, \action_{t})\) of the posterior mean \(\mu_{i}(\state_{t}, \action_{t})\).
+%
+%\section{Laplace Approximation} \label{sec-laplace-approximation}
+%
+%\textbf{Laplace approximation}
+%The Laplace approximation \todo{add citation of original paper} constructs a Gaussian approximation of the weight-space posterior $p(\weights \mid \dataset)$
+%by using a second-order Taylor expansion of $\mathcal{L}$ around $\weights^{*}$.
+%The posterior approximation is given by,
+%\begin{align} \label{eq-laplace-approx-weight-space}
+%  p(\weights \mid \dataset) \approx \mathcal{N} \left( \weights \mid \weights^{*} , \bm\Sigma_{\weights^{*}} \right)
+%  \quad \text{with} \quad \bm\Sigma_{\weights} =
+% - \nabla_{\weights \weights}^{2} \mathcal{L} ( \dataset ; \weights)|_{\weights=\weights^{*}}
+%\end{align}
+%That is, it sets the posterior precision to the Hessian of the loss at the optimal parameters $\weights^{*}$.
+%It is worth noting that computing the Hessian of the loss can be computationally intractable for large networks.
+%The prior terms are usually trivial, so we focus on the likelihood here.
+%The Jacobian and Hessian of the log likelihood can be expressed per data point,
+%\begin{align} \label{eq-jac}
+%  \nabla_{\weights} \log p(\mathbf{y} \mid \mathbf{f}(\mathbf{x}; \weights)) &= \mathbf{J}(\mathbf{x})^{T} \mathbf{r}(\mathbf{y} ; \mathbf{f}) \\
+%  \nabla^{2}_{\weights\weights} \log p(\mathbf{y} \mid \mathbf{f}(\mathbf{x}; \weights)) &= \mathbf{H}(\mathbf{x})^{T}
+%  \mathbf{r}(\mathbf{y};\mathbf{f}) - \mathbf{J}(\mathbf{x})^{T} \bm\Lambda(\mathbf{y};\mathbf{f}) \mathbf{J}(\mathbf{x}),
+%\label{eq-hess}
+%\end{align}
+%through the Jacobian $\mathbf{J} \in \R^{C \times P}$ and Hessian $\mathbf{H} \in \R^{C \times P \times P}$ of the feature extractor $\mathbf{f}(\mathbf{x}; \bm\weights)$,
+%\begin{align} \label{eq-jac}
+%[\mathbf{J}(\cdot)]_{ci} = \odv{f_{c}(\cdot ; \weights)}{\weights_{i}}_{\weights=\weights^{*}} \qquad
+%[\mathbf{H}(\cdot)]_{cij} = \odv{f_{c}(\cdot ; \weights)}{\weights_{i}\weights_{j}}_{\weights=\weights^{*}}
+%\end{align}
+%where
+%$\mathbf{r}(\mathbf{y}; \mathbf{f}) = \nabla_{\mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$ can be interpreted as a residual and
+%$\bm\Lambda(\mathbf{y} ; \mathbf{f}) = \nabla^{2}_{\mathbf{f} \mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$
+%as per-input noise.
+%Many approximations exist and can be used alongsied our method.
+%We refer the reader to \cite{daxbergerLaplace2021} for more details.
+%See \cref{sec-laplace-approximation} for further details on the Laplace approximation.
+%
+%
+%\section{Experiment details}
+%
+%\subsection{UCI}
+%
+%\begin{table}[t!] 
+%  \centering\scriptsize
+%  \caption{Negative log predictive density (NLPD) (lower better) for the proposed model TODO} 
+%	\label{tbl:uci_all}
+%	% Control table spacing
+%	\renewcommand{\arraystretch}{1.}
+%	\setlength{\tabcolsep}{2pt}
+%	\setlength{\tblw}{0.14\textwidth}  
+%	
+%	% Custom error formatting
+%	\newcommand{\val}[2]{%
+%		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
+%	} 
+%
+%    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
+%	\input{tables/uci_all.tex}
+%\end{table}
+%
+%\section{Template stuff}
+%\subsection{Generate TikZ Figures from Python}
+%We can generate figures in \texttt{.tex} format directly from Python:
+%\begin{verbatim}
+%tikzplotlib.save("fig.tex", axis_width="\\figurewidth", axis_height="\\figureheight")
+%\end{verbatim}
+%\cref{fig:example} shows that we get nicely formatted lables/titles/etc when we include them in our paper.
+%\begin{figure}[h]
+%    \centering\footnotesize
+%
+%    % Set your figure size here
+%    \setlength{\figurewidth}{.33\textwidth}
+%    \setlength{\figureheight}{.75\figurewidth}
+%
+%    % Customize your plot here
+%    % (scale only axis applies the size to the axis box and not entire figure)
+%    \pgfplotsset{grid style={dotted},title={Foo},scale only axis}
+%
+%    % Use the subcaption package (= subfigure) for sub-plots, that is
+%    % plot the separate plots separately in Python
+%    \begin{subfigure}{.4\textwidth}
+%        \centering
+%        \input{./fig/example_fig.tex}
+%    \end{subfigure}
 %    \hfill
-% \begin{minipage}{0.499\textwidth}
-% \begin{algorithm}[H]
-% \caption{Model-based RL with fast updates}\label{alg-mbrl-fast-updates}
-% \begin{algorithmic}[1]
-%   \Require Initial data set $\dataset_{0}$, dynamics posterior $p(\transitionFn \mid \dataset_{0})$, policy $\policy_{0}$
-%     % ${p(\state_{\timeInd+1} \mid \singleInput, \dataset_{0})}$}
-% \For{$i  \in \{0, 1, \ldots, \text{num episodes} \}$}
-%     \For{$t  \in \{0, 1, \ldots, \text{num steps} \}$}
-%       \State Execute policy $\policy_{i}(\state_{t})$ in environment
-%       % \State Append transition $\state_{t}, \action_{t}, \state_{t+1}, r_{t+1})$ to trajectory $\tau_{i}$
-%       \State $\tau_{i+1} = \{\state_{j}, \action_{j}, \state_{j+1}, r_{j+1}) \}_{j=0}^{t}$
-%       \State {\color{blue}Update dynamics $p(\transitionFn \mid \dataset_{0:i} \cup \tau_{i+1})$}
-%     \EndFor
-%     \State Update data set $\mathcal{D}_{0:i+1} = \mathcal{D}_{0:i} \cup \tau_{i+1}$
-%     \State Train dynamics $p(\transitionFn \mid \dataset_{0:i+1})$
-%     \State Improve policy $\pi_{i+1}$
-%     %\State Improve policy $\pi_{i+1}$ using $p(\transitionFn \mid \dataset_{0:i+1})$ and/or $\dataset_{0:i+1}$
-% \EndFor
-% \end{algorithmic}
-% \end{algorithm}
-% \end{minipage}
-
-\subsection{Exploration Strategies}
-\textbf{Greedy exploitation}
-Given the posterior dynamics \(p(\transitionFn \mid \mathcal{D})\),
-a common approach is to simply take the expecation over both the aleatoric and epistemic uncertainty,
-\begin{align} \label{eq-greedy}
-\policy_{i+1}^{\text{greedy}} = \arg \max_{\policy \in \policyDomain} \mathbb{E}_{\transitionFn \sim p(\transitionFn \mid \dataset_{0:i})} \left[ J(\transitionFn, \policy) \right],
-\end{align}
-This approach has been widely adopted, for example, in PILCO, PETS, GP-MPC
-\cite{deisenrothPILCO2011,chuaDeepReinforcementLearning2018,kamtheDataEfficient2018}.
-This approach helps to alleviate model bias as the posterior ``knows what the model does not know''.
-This is because the predictive posterior \(p(f(s_{t},a_{t}) \mid (s_{t},a_{t}),  \mathcal{D} )\) will be (or should be) uncertain when making
-predictions far away from the training data.
-The expectation considers all possible dynamics models which prevents the policy optimisation from
-exploiting innacuracies in the model.
-This approach has no guarantees for exploration in the general case.
-However, under specific dynamics and reward structures (e.g. PILCO) this objective can achieve sublinear regret.
-\todo{need to double check sublinear regret statement. And give a reference}
-
-\textbf{Posterior sampling}
-\cite{osbandWhyPosteriorSampling2017,osbandMoreEfficientReinforcement2013}
-\begin{align} \label{eq-posterior-sampling}
-\policy_{i+1}^{\text{PS}} = \arg \max_{\policy \in \policyDomain} \left[ J(\transitionFn, \policy) \right] \quad \text{s.t. } \transitionFn \sim p(\transitionFn \mid \dataset_{0:i})
-\end{align}
-
-\textbf{Hallucinated upper confidence RL}
-A more theoretically grounded exploration strategy is UCRL \citep{jakschNearoptimal2010}, which optimises joinly over
-policies and models inside the set
-\(\mathcal{M} = \{ f \mid | f(s,a) - \mu_{i}(s, a) | \leq \beta_{i} \Sigma_{i}(s, a) \quad \forall s, a \in \mathcal{S} \times \mathcal{A} \}\), representing all statistically plausible
-models under the posterior \(p(f(s,a) \mid \mathcal{D}_{0:i} \cup (s,a)) = \mathcal{N}(f(s,a) \mid \mu_{i}(s,a), \Sigma_{i}(s,a))\) at episode \(i\).
-This strategy is given by,
-\begin{align} \label{eq-ucrl}
-\policy_{i+1}^{\text{UCRL}} = \arg \max_{\policy \in \policyDomain} \max_{\transitionFn \in \mathcal{M}} J(\transitionFn, \policy).
-\end{align}
-This strategy optimises an optimistic policy over the set of plausible dynamics models.
-Although this joint optimisation is intractable in general,
-\cite{curiEfficient2020} proposed a practical alternative which is detailed in \cref{sec-hucrl}.
-
-\textbf{MPC vs policy learning}
-It is worth noting that the strategies in \cref{eq-greedy,eq-posterior-sampling,eq-ucrl} can be used with both model predictive control (MPC)
-techniques, such as the cross entoropy method (CEM), and model-free RL techniques, such as soft actor-critic (SAC).
-
-In this work we are interested in how we can use \(p(f \mid \mathcal{D})\) to alleviate some of the issues in model-based RL,
-for example, model bias and the exploration-exploitation trade-off.
-
-\todo{show how to get new $\dualParam{1}$ and $\dualParam{2}$ in Train dynamics line of \cref{alg-mbrl-fast-updates}}
-\begin{algorithm}[!t]
-\caption{Model-based RL with fast updates}\label{alg-mbrl-fast-updates}
-\begin{algorithmic}[1]
-  \Require Start state $\state_{0}$, initial data set $\dataset_{0}$, dynamics posterior $p(\transitionFn \mid \dataset_{0})$ (inc.
-dual parameters $\dualParam{1}, \dualParam{2}$), policy $\policy_{0}$
-    % ${p(\state_{\timeInd+1} \mid \singleInput, \dataset_{0})}$}
-\For{$i  \in \{1, 2, \ldots, \text{num episodes} \}$}
-    \State Reset the system to $\state_{0}$ and reset trajectory buffers $\bm\tau_{t} = \emptyset \ \forall t$
-    \For{$t  \in \{1, 2, \ldots, \text{num steps} \}$}
-      % \State Execute policy $\policy_{i}(\state_{t})$ (\cref{eq-fast-update-mpc}) in environment
-      \State Use \cref{eq-fast-update-mpc} to collect data $\bm\tau_{t} = \bm\tau_{t-1} \cup (\state_{t}, \policy_{i}(\state_{t}), \transitionFn(\state_{t}, \policy^{\text{fast}}_{i}(\state_{t})), r_{t+1})$
-      % \State Append transition $\state_{t}, \action_{t}, \state_{t+1}, r_{t+1})$ to trajectory $\tau_{i}$
-      % \State $\tau_{i+1} = \{\state_{j}, \action_{j}, \state_{j+1}, r_{j+1}) \}_{j=0}^{t}$
-      %\State {\color{blue}Update dynamics $p(\transitionFn \mid \dataset_{0:i} \cup \tau_{i+1})$}
-      \State {\color{blue}Update dynamics posterior using \cref{eq-dual-update-svgp}, i.e. fast update}
-      % \begin{align}
-      % \dualParam{1}^{t+1} &\leftarrow \dualParam{1}^{t} +  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))} \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right] \\
-      % \dualParam{2}^{t+1} &\leftarrow \dualParam{2}^{t} +  \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))}  \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right]
-      % \end{align}}
-    \EndFor
-    \State Update data set $\dataset_{0:i} = \dataset_{0:i-1} \cup \tau$
-    \State Train dynamics $p(\transitionFn \mid \dataset_{0:i}) \leftarrow \text{update\_dynamics}(\dataset_{0:i}, p(\transitionFn \mid \dataset_{0:i-1}))$
-    \State Improve policy $\pi^{\text{fast}}_{i+1} \leftarrow \text{update\_policy}(p\left(\transitionFn \mid \dataset_{0:i}), \dataset_{0:i} \right)$
-\EndFor
-\end{algorithmic}
-\end{algorithm}
-
-\subsubsection{Fast updates}
-
-In this section we extend these fast updates to environment's with high dimensional state spaces and large data sets.
-% Our method draws on the connection between BNNs and GPs and formulates a function space SVGP posterior given
-Our method uses a BNN dynamic model and draws on the connection between BNNs and GPs
-\citep{khanApproximate2019} to formulate a function space SVGP posterior,
-where we can apply the fast updates from \cref{eq-dual-update-svgp}.
-At a high-level, we first use Laplace's approximation to obtain a weight space posterior for our BNN.
-We then linearise our BNN around the optimal parameters and interpret it as a GP.
-Finally, we formulate a lower rank approximation of this GP posterior (i.e. a SVGP posterior) using inducing variables.
-% formulates a function space SVGP posterior by drawing on the connection between BNNs and GPs.
-
-The strategies in \cref{eq-greedy,eq-posterior-sampling,eq-hucrl} do not update the dynamic model during an episode.
-A better approach would be to update the posterior at every time step during an episode, for example,
-\begin{subequations}
-\begin{align} \label{eq-fast-update-mpc}
-  \policy_{i+1}^{\text{greedy}}(\state) &= \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
-\E_{p(\transitionFn \mid \dataset_{0:i})} \left[J^{\Horizon}(\action_{0:\Horizon}, \transitionFn) \right] + \stateValueFn(\state_{\Horizon+1}) \\
-  \policy_{i+1}^{\text{PS}}(\state) &= \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
-J^{\Horizon}(\action_{0:\Horizon}, \transitionFn) + \stateValueFn(\state_{\Horizon+1}) \quad \text{s.t. } \transitionFn \sim p(\transitionFn \mid \dataset_{0:i} \cup \bm\tau_{t}) \\
-  \policy_{i+1}^{\text{UCRL}}(\state) &= \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}} \max_{\transitionFn \in \mathcal{M}}
-J^{\Horizon}(\action_{0:\Horizon}, \transitionFn) + \stateValueFn(\state_{\Horizon+1}) \quad \text{s.t.
-} \mathcal{M} = \{\transitionFn(\state_{t},\action_{t}) - \mu_{i,t}(\state_{t},\action_{t}) \leq \beta_{i,t} \Sigma_{i,t}(\state_{t}, \action_{t})\} \\
-  \stateValueFn(\state) &= \mathbb{E} \left[ \sum_{t=0}^{\infty}     \discount^{t} \rewardFn(\state_{t},\action_{t}) \mid \state_{0}=\state \right] \label{eq-value-fn}
-\end{align}
-\end{subequations}
-\begin{subequations}
-\begin{align} \label{eq-fast-update-mpc-old}
-  \policy^{\text{fast}}(\state) = \arg &\max_{\action_{0}} \max_{\action_{1}, \ldots, \action_{\Horizon}}
-  \mathbb{E}_{\state_{\horizon} \sim p(\state_{\horizon+1} \mid \transitionFn(\state_{\horizon}, \action_{\horizon}))} \left[ \sum_{\horizon=0}^{\Horizon}     \discount^{\horizon} \rewardFn(\state_{\horizon},\action_{\horizon}) \mid \state_{0}=\state \right] + \discount^{\Horizon+1} \stateValueFn(\state_{\Horizon+1}) \\
-  \stateValueFn(\state) &= \mathbb{E} \left[ \sum_{t=0}^{\infty}     \discount^{t} \rewardFn(\state_{t},\action_{t}) \mid \state_{0}=\state \right] \label{eq-fast-update-mpc}
-\end{align}
-\end{subequations}
-
-\begin{align} \label{}
-  \policy(\state) = \arg &\max_{\action_{0}} \max_{\action_{1}, \ldots, \action_{\Horizon}} \max_{\optimisticTransition \in \optimisticTransitionSet}
-  \sum_{\horizon=0}^{\Horizon}  \mathbb{E}_{\noise_{\horizon}} \left[  \discount^{\horizon} \rewardFn(\state_{\horizon},\action_{\horizon}) \right] + \discount^{\Horizon+1} \stateValueFn(\state_{\Horizon+1}) \\
-  \text{s.t. } \state_{\horizon+1} &= \optimisticTransition(\state_{\horizon}, \action_{\horizon}) + \noise_{\horizon} \\
-  \optimisticTransition(\state_{\horizon}, \action_{\horizon}) &=
-\optimisticTransitionMean(\state_{\horizon}, \action_{\horizon}) \pm \beta_{i}
-\optimisticTransitionCov(\state_{\horizon}, \action_{\horizon})
-\end{align}
-
-\input{proof.tex}
-
-\section{Hallucinated Upper Confidence Reinforcement Learning (H-UCRL)} \label{sec-hucrl}
-\cite{curiEfficient2020} introduced a tractable approximation which retains some of the theoretical guarantees whilst
-being applicable with deep model-based RL.
-They introduce a function \(\eta: \mathcal{S} \times \mathcal{A} \rightarrow [-1, 1]^{p}\) which acts as a hallucinated control input.
-The strategy is given by,
-\begin{align} \label{eq-hucrl}
-\pi_i^{\text{UCRL}} = \arg \max_{\policy \in \policyDomain} \max_{\eta(\cdot) \in [-1,1]} J(\transitionFn, \policy) \quad \text{s.t.} \quad \transitionFn = \mu_{i}(\state_{t}, \action_{t}) + \beta_{i} \Sigma_{i}(\state_{t}, \action_{t}) \eta(\state_{t},\action_{t}).
-\end{align}
-Intuitively, \(\eta(\state,\action) \in [-1,1]\) enables the optimisation to select any dynamics model
-\(\transitionFn\) within \(\pm \beta \Sigma_{i}(\state_{t}, \action_{t})\) of the posterior mean \(\mu_{i}(\state_{t}, \action_{t})\).
-
-\section{Laplace Approximation} \label{sec-laplace-approximation}
-
-\textbf{Laplace approximation}
-The Laplace approximation \todo{add citation of original paper} constructs a Gaussian approximation of the weight-space posterior $p(\weights \mid \dataset)$
-by using a second-order Taylor expansion of $\mathcal{L}$ around $\weights^{*}$.
-The posterior approximation is given by,
-\begin{align} \label{eq-laplace-approx-weight-space}
-  p(\weights \mid \dataset) \approx \mathcal{N} \left( \weights \mid \weights^{*} , \bm\Sigma_{\weights^{*}} \right)
-  \quad \text{with} \quad \bm\Sigma_{\weights} =
- - \nabla_{\weights \weights}^{2} \mathcal{L} ( \dataset ; \weights)|_{\weights=\weights^{*}}
-\end{align}
-That is, it sets the posterior precision to the Hessian of the loss at the optimal parameters $\weights^{*}$.
-It is worth noting that computing the Hessian of the loss can be computationally intractable for large networks.
-The prior terms are usually trivial, so we focus on the likelihood here.
-The Jacobian and Hessian of the log likelihood can be expressed per data point,
-\begin{align} \label{eq-jac}
-  \nabla_{\weights} \log p(\mathbf{y} \mid \mathbf{f}(\mathbf{x}; \weights)) &= \mathbf{J}(\mathbf{x})^{T} \mathbf{r}(\mathbf{y} ; \mathbf{f}) \\
-  \nabla^{2}_{\weights\weights} \log p(\mathbf{y} \mid \mathbf{f}(\mathbf{x}; \weights)) &= \mathbf{H}(\mathbf{x})^{T}
-  \mathbf{r}(\mathbf{y};\mathbf{f}) - \mathbf{J}(\mathbf{x})^{T} \bm\Lambda(\mathbf{y};\mathbf{f}) \mathbf{J}(\mathbf{x}),
-\label{eq-hess}
-\end{align}
-through the Jacobian $\mathbf{J} \in \R^{C \times P}$ and Hessian $\mathbf{H} \in \R^{C \times P \times P}$ of the feature extractor $\mathbf{f}(\mathbf{x}; \bm\weights)$,
-\begin{align} \label{eq-jac}
-[\mathbf{J}(\cdot)]_{ci} = \odv{f_{c}(\cdot ; \weights)}{\weights_{i}}_{\weights=\weights^{*}} \qquad
-[\mathbf{H}(\cdot)]_{cij} = \odv{f_{c}(\cdot ; \weights)}{\weights_{i}\weights_{j}}_{\weights=\weights^{*}}
-\end{align}
-where
-$\mathbf{r}(\mathbf{y}; \mathbf{f}) = \nabla_{\mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$ can be interpreted as a residual and
-$\bm\Lambda(\mathbf{y} ; \mathbf{f}) = \nabla^{2}_{\mathbf{f} \mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$
-as per-input noise.
-Many approximations exist and can be used alongsied our method.
-We refer the reader to \cite{daxbergerLaplace2021} for more details.
-See \cref{sec-laplace-approximation} for further details on the Laplace approximation.
-
-\section{Experiment details}
-
-\subsection{UCI}
-
-\begin{table}[t!] 
-  \centering\scriptsize
-  \caption{Negative log predictive density (NLPD) (lower better) for the proposed model TODO} 
-	\label{tbl:uci_all}
-	% Control table spacing
-	\renewcommand{\arraystretch}{1.}
-	\setlength{\tabcolsep}{2pt}
-	\setlength{\tblw}{0.14\textwidth}
-
-	% Custom error formatting
-	\newcommand{\val}[2]{%
-		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
-	}
-
-    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
-	\input{tables/uci_all.tex}
-\end{table}
-
-\section{Template stuff}
-\subsection{Generate TikZ Figures from Python}
-We can generate figures in \texttt{.tex} format directly from Python:
-\begin{verbatim}
-tikzplotlib.save("fig.tex", axis_width="\\figurewidth", axis_height="\\figureheight")
-\end{verbatim}
-\cref{fig:example} shows that we get nicely formatted lables/titles/etc when we include them in our paper.
-\begin{figure}[h]
-    \centering\footnotesize
-
-    % Set your figure size here
-    \setlength{\figurewidth}{.33\textwidth}
-    \setlength{\figureheight}{.75\figurewidth}
-
-    % Customize your plot here
-    % (scale only axis applies the size to the axis box and not entire figure)
-    \pgfplotsset{grid style={dotted},title={Foo},scale only axis}
-
-    % Use the subcaption package (= subfigure) for sub-plots, that is
-    % plot the separate plots separately in Python
-    \begin{subfigure}{.4\textwidth}
-        \centering
-        \input{./fig/example_fig.tex}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{.4\textwidth}
-        \centering
-        \input{./fig/example_fig.tex}
-    \end{subfigure}
-    \caption{Foo}
-    \label{fig:example}
-\end{figure}
-
-\subsection{Generate Tables from Python}
-We can also generate tables straight from python using \href{https://github.com/astanin/python-tabulate}{tabulate}:
-\begin{verbatim}
-table = [["Sun",696000,1989100000],["Earth",6371,5973.6],
-        ["Moon",1737,73.5],["Mars",3390,641.85]]
-headers = ["Planet","R (km)", "mass (x 10^29 kg)"]
-table = tabulate(table, headers=headers, tablefmt="latex")
-with open("table.tex", 'w') as file:
-    file.write(table)
-\end{verbatim}
-
-\begin{table}[h]
-    \centering
-    \input{./tables/example_table.tex}
-\end{table}
+%    \begin{subfigure}{.4\textwidth}
+%        \centering
+%        \input{./fig/example_fig.tex}
+%    \end{subfigure}
+%    \caption{Foo}
+%    \label{fig:example}
+%\end{figure}
+%
+%\subsection{Generate Tables from Python}
+%We can also generate tables straight from python using \href{https://github.com/astanin/python-tabulate}{tabulate}:
+%\begin{verbatim}
+%table = [["Sun",696000,1989100000],["Earth",6371,5973.6],
+%        ["Moon",1737,73.5],["Mars",3390,641.85]]
+%headers = ["Planet","R (km)", "mass (x 10^29 kg)"]
+%table = tabulate(table, headers=headers, tablefmt="latex")
+%with open("table.tex", 'w') as file:
+%    file.write(table)
+%\end{verbatim}
+%
+%\begin{table}[h]
+%    \centering
+%    \input{./tables/example_table.tex}
+%\end{table}
 

### 2023-05-13 paper/main.tex
making it work

@@
 
-\subsection{Linearization gives rise to a Gaussian process posterior} 
-\label{sec:nn2gp}
-%
-
-The structure of the posterior given by the loss-landscape around the MAP weights $\vw^*$  induces a correlation structure on learned model functions of the neural network.
+%
+%\subsection{Linearization gives rise to a Gaussian process posterior} 
+%\label{sec:nn2gp}
+%
+%
+%The structure of the posterior given by the loss-landscape around the MAP weights $\vw^*$  induces a correlation structure on learned model functions of the neural network.
 These can be seen as possible perturbed versions of $f_{\vw^*}$ that can be used for characterizing ambiguity and uncertainty in the learned model (see \cref{fig:banana} for an example of sampling in weight-space).
@@
 We aim to find a kernel based on the neural network to build the Gaussian process posterior.
-A GP is fully characterized by a mean $\mu(\cdot)$ and covariance function $\kappa(\cdot,\cdot)$ (kernel).
-If we had the following function parameterization $g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx') = \delta^{-1} \phi(\vx) \phi^\T(\vx')$ (see Ch.~XXX in \cite{rasmussen2006gaussian} for details).\todo{this part needs to be rewritten, starts talking about a general function parameterisation and then jumps directly to the neural network}
+%A GP is fully characterized by a mean $\mu(\cdot)$ and covariance function $\kappa(\cdot,\cdot)$ (kernel).
+%If we had the following function parameterization $g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx') = \delta^{-1} \phi(\vx) \phi^\T(\vx')$ (see Ch.~XXX in \cite{rasmussen2006gaussian} for details).\todo{this part needs to be rewritten, starts talking about a general function parameterisation and then jumps directly to the neural network}
 %=======
@@
 %
-Given an approximate posterior $q(\vw)$  \citet{immerImprovingPredictionsBayesian2021} proposed to make the following linear approximation
-$f^{\textrm{lin.}}_{\vw^*}(\vx; \vw) = f_{\vw^*}(\vx) + \Jac{\weights^*}{\mathbf{x}} \, (\vw - \vw^*)$ of the neural network, with Jacobian $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$.
+A Gaussian process characterizes a distribution over functions in terms of the first two moments,  a mean $\mu(\cdot)$ and covariance function $\kappa(\cdot,\cdot)$ (kernel).
+We aim to find a kernel and mean function based on the neural network to build the Gaussian process posterior.
+A linear function in terms of parameters can be converted from the weight space to the function space (see Ch.~XXX in \cite{rasmussen2006gaussian} as follows:
+\begin{equation} \label{eq:weight_func}
+g_\weights(\mathbf{x}_{i}) = \phi(\vx)^\top \vw \implies \mu(\vx) = \vzeros \quad \kappa(\mathbf{x}, \mathbf{x}') = \frac{1}{\delta} \phi(\vx)^\top \phi(\vx)
+\end{equation}
+Given an approximate posterior $q(\vw)$, \citet{immerImprovingPredictionsBayesian2021} proposed to make the following linear approximation
+$f^{\textrm{lin.}}_{\vw^*}(\vx; \vw) = f_{\vw^*}(\vx) + \Jac{\weights^*}{\mathbf{x}} \, (\vw - \vw^*)$ of the neural network, where $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$ is the Jacobian.
 The approximation can be used with any approximate inference technique but in the paper they focus on the Laplace-GNN.
@@
 
- at the map estimate it was possible to improve predictions from a Laplace-GGN Bayesian neural network.
-with Jacobian $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$
-
-A Gaussian process characterizes a distribution over functions in terms of the first two moments.
-The key quantity of a Gaussian process is the prior covariance function (or kernel function) $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors in $\R^{\mathrm{D}}$.
-We aim to find a kernel based on the neural network to build the Gaussian process posterior.
-
-A linear function in terms of parameters can easily be converted from the weight space to the function space as follows
-
-\begin{equation}
-\hat{f}_\weights(\mathbf{x}_{i})) = \phi(\vx)^\top \vw
-\end{equation}
-
-$g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx') = \delta^{-1} \phi(\vx) \phi(\vx')^\T$ see \citep{rasmussen2006gaussian} for details.\todo{this part needs to be rewritten, starts talking about a general function parameterisation and then jumps directly to the neural network}
-We can approximate the feature map of the neural network  $f_\weights(\mathbf{x})$  by using the Jacobian at $\weights^*$ thus our GP prior becomes:
+Furthermore, under the linear approximation they showed you can now convert your weight space prior to the function space by combining with \cref{eq:weight_func} meaning the converged neural network GP prior is:
 \begin{equation} \label{eq-laplace-approx-function-space}
- g(\vx) \sim \GP \left( \mu(\vx), \kappa(\vx, \vx') \right) \quad \text{with} \quad
-  \mu(\vx) = 0 \quad \text{and} \quad
+% g(\vx) \sim \GP \left( \mu(\vx), \kappa(\vx, \vx') \right) \quad \text{with} \quad
+  \mu(\vx) =  f^{\textrm{lin.}}_{\vw_*}(\vx; \vw = \vzeros) = f_{\vw^*}(\vx) - \Jac{\weights^*}{\mathbf{x}} \vw^* \quad \text{and} \quad
   \kappa(\mathbf{x}, \mathbf{x}')
@@
 %
-where the kernel is the so-called Neural Tangent Kernel (NTK, \cite{jacot2018neural}) with Jacobian $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$.
+%where the kernel is the so-called Neural Tangent Kernel (NTK, \cite{jacot2018neural}) with Jacobian $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$.
 Alternatively, we could have followed the derivation by \citet{immerImprovingPredictionsBayesian2021}, where they perform a local linearization of the neural network  $f^{\textrm{lin.}}_{\vw^*}(\vx; \vw) = f_{\vw^*}(\vx) + \Jac{\weights^*}{\mathbf{x}} \, (\vw - \vw^*)$.
@@
 %which does not seem useful as a prior mean function,
-On the other hand, we set $\mu(\vx) = \vzeros$, as common in GP literature and derived from a feature map conversion. \todo{derived what?}
+%On the other hand, we set $\mu(\vx) = \vzeros$, as common in GP literature and derived from a feature map conversion. \todo{derived what?}
 

### 2023-05-13 paper/main.tex
added some rl stuff

--- 2023-05-13 paper/main.tex
@@
 %
-Given an approximate posterior $q(\vw)$  \citet{immerImprovingPredictionsBayesian2021} proposed to make the following linear approximation
+A common approach to find a distribution over $q(\vw)$ is to perform a Laplace-GGN approximation.
+The approximation can be seen as taking the Laplace approximation of \cref{eq-empirical-risk} and approximating the   Hessian of $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i)$ with the Generalized Gauss Newton(GGN) approximation.
+\citet{immerImprovingPredictionsBayesian2021} proposed to make the following linear approximation
 $f^{\textrm{lin.}}_{\vw^*}(\vx; \vw) = f_{\vw^*}(\vx) + \Jac{\weights^*}{\mathbf{x}} \, (\vw - \vw^*)$ of the neural network, with Jacobian $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$.
-The approximation can be used with any approximate inference technique but in the paper they focus on the Laplace-GNN.
-They find that the linear approximation helps to improve predictions by correcting the approximate posterior when sampled through a non-Gaussian likelihoods.
+The idea
 
@@
 
-\textbf{Model-based reinforcement learning}
+\subsection{Reinforcement learning}
 We now detail how our method can be used in model-based RL.
-Folling the Markov decision process formulation \cite{bellmanDynamic1956}, we
-denote states \(\state \in \stateDomain \subseteq \R^{D_{\state}} \), actions \(\action \in \actionDomain \subseteq \R^{D_{\action}}\) and
-transition dynamics \(\transitionFn: \stateDomain \times \actionDomain \rightarrow \stateDomain \).
-The goal of RL is to find the policy \(\pi : \stateDomain \rightarrow \actionDomain \), that maximises the sum of rewards
+We consider stochastic environments with states \(\state \in \stateDomain \subseteq \R^{D_{\state}} \),
+actions \(\action \in \actionDomain \subseteq \R^{D_{\action}}\) and transition dynamics
+\(\transitionFn: \stateDomain \times \actionDomain \rightarrow \stateDomain \), such that
+$\state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t}$, where  $\noise_{t}$
+is i.i.d. transition noise.
+We consider the episodic setting where the system is reset to an initial state $\state_{0}$ at each episode and we
+assume that there is a known reward function $r : \stateDomain \times \actionDomain \rightarrow \R$.
+% Following the Markov decision process formulation \cite{bellmanMarkovianDecisionProcess1957a}, we
+% denote the states \(\state \in \stateDomain \subseteq \R^{D_{\state}} \) and actions \(\action \in \actionDomain \subseteq \R^{D_{\action}}\)
+% of the sytem, the reward function $r : \stateDomain \times \actionDomain \rightarrow \R$, and transition dynamics
+% \(\transitionFn: \stateDomain \times \actionDomain \rightarrow \stateDomain \), such that
+% $\state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t}$ where  $\noise_{t}$
+% is i.i.d. transition noise.
+The goal of RL is to find the policy \(\pi : \stateDomain \rightarrow \actionDomain\) that maximises the sum of discounted rewards
+in expecation over the transition noise,
 \begin{align} \label{eq-model-free-objective}
 \policy^{*} = \arg \max_{\policy \in \policyDomain} J(\transitionFn, \policy) = \arg \max_{\policy \in \policyDomain} \mathbb{E}_{\noise_{0:\infty}} \left[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \right]
-\quad \text{s.t. } \state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t}.
+\quad \text{s.t. } \state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t},
 \end{align}
-in expecation over the transition noise,
- subject to  i.i.d. transition noise \(\noise_{t}\).
-where $\gamma \in [0, 1]$ is a discount factor to account for the infinte sum.
-
+where $\gamma \in [0, 1]$ is a discount factor and $\Pi$ is a set of policies.
+
+\textbf{Model-learning}
 In model-based RL, the state transition data set \(\mathcal{D} = \{\{(s_{t},a_{t}), s_{t+1}\}^{T_{i}}_{t=1}\}_{i=0}^{N}\) is first used to
@@
 J^{\Horizon}(\action_{0:\Horizon}, \transitionFn) + \stateValueFn(\state_{\Horizon+1})
-\end{align}
-\end{subequations}
-\begin{subequations}
-\begin{align} \label{eq-fast-update-mpc-old}
-  \stateValueFn(\state) &= \mathbb{E} \left[ \sum_{t=0}^{\infty}     \discount^{t} \rewardFn(\state_{t},\action_{t}) \mid \state_{0}=\state \right]
+\quad
+  \stateValueFn(\state) &= \mathbb{E} \left[ \sum_{t=0}^{\infty}     \discount^{t} \rewardFn(\state_{t},\action_{t}) \mid \state_{0}=\state \right] \label{eq-fast-update-mpc-old}
 \end{align}

### 2023-05-14 paper/main.tex
Was not compiling

@@
 %
-%\subsection{Linearization gives rise to a Gaussian process posterior} 
-%\label{sec:nn2gp}
-%
-%
-%The structure of the posterior given by the loss-landscape around the MAP weights $\vw^*$  induces a correlation structure on learned model functions of the neural network.
+\subsection{Linearization gives rise to a Gaussian process} 
+\label{sec:nn2gp}
+%
+\todo{You need something like this to bridge from the previous, GPs cannot come from nowhere!}
+The structure of the posterior given by the loss-landscape around the MAP weights $\vw^*$  induces a correlation structure on learned model functions of the neural network.
 These can be seen as possible perturbed versions of $f_{\vw^*}$ that can be used for characterizing ambiguity and uncertainty in the learned model (see \cref{fig:banana} for an example of sampling in weight-space).
@@
 %If we had the following function parameterization $g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx') = \delta^{-1} \phi(\vx) \phi^\T(\vx')$ (see Ch.~XXX in \cite{rasmussen2006gaussian} for details).\todo{this part needs to be rewritten, starts talking about a general function parameterisation and then jumps directly to the neural network}
-%=======
-\subsection{Neural Network to GP Prior} 
-\label{sec:nn2gp}
+%\subsection{Neural Network to GP Prior} 
+%\label{sec:nn2gp}
 %
@@
 \begin{equation} \label{eq:weight_func}
-g_\weights(\mathbf{x}_{i}) = \phi(\vx)^\top \vw \implies \mu(\vx) = \vzeros \quad \kappa(\mathbf{x}, \mathbf{x}') = \frac{1}{\delta} \phi(\vx)^\top \phi(\vx)
+g_\weights(\mathbf{x}_{i}) = \phi^\top\!(\vx) \, \vw \implies \mu(\vx) = \vzeros \quad \kappa(\mathbf{x}, \mathbf{x}') = \frac{1}{\delta} \phi(\vx)^\top \phi(\vx)
 \end{equation}
@@
 
-\begin{subequations}
 \begin{align} \label{eq-fast-update-mpc}
@@
 \quad
-  \stateValueFn(\state) &= \mathbb{E} \left[ \sum_{t=0}^{\infty}     \discount^{t} \rewardFn(\state_{t},\action_{t}) \mid \state_{0}=\state \right] \label{eq-fast-update-mpc-old}
+  \stateValueFn(\state) &= \mathbb{E} \left[ \sum_{t=0}^{\infty}     \discount^{t} \rewardFn(\state_{t},\action_{t}) \mid \state_{0}=\state \right] %\label{eq-fast-update-mpc-old}
 \end{align}
-\end{subequations}
 

### 2023-05-14 paper/main.tex
making it work

@@
 Firstly how to incorporate uncertainty quantification over predictions which is needed in many applications.
-Secondly, in the sequential data regime.
+Secondly, in the sequential data regime data arrives not in batches
 
@@
 %% EWC, SI, VCL -> weight regularization 
-
+% 1) what is the central problem of CL? 
+% 		Training from a non-stationary distribution the models overwrites the previously learnt parameters and then forgets the previous learnt function.
+% 2) What others have done?
+% 		starting with EWC and SI, that are the most known methods in term of weight regularization. And others took a different approach again in the weight regularization real with VCL (to check)
+% 3) People started to try experimenting with the functional regularization -> 
+% In order of complexity -> DER, FROMP, S-FSVI
+% In order of pubblication -> DER/FROMP, K-Priors (?), S-FSVI
 EWC \cite{kirkpatrick2017overcoming}
@@
 %
-If $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) = -\log(p(\mathbf{y} \mid f_\weights(\mathbf{x}_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$, where the regularization weight takes the role of a prior precision parameter.
+If $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) = -\log(p(\mathbf{y} \mid f_\weights(\mathbf{x}_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where the regularization weight takes the role of a prior precision parameter, \ie, $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.
 
@@
 If we limit the interest to the first two moments, we can characterize the resulting posterior over these functions as a Gaussian process (GP).
+
+- distribution over w given to you by the non-linear function.
+One could sample over weights pass it over the function and you have distribution over functions.
+HMC is heavy, structure of the problem around the map estimate.
+characteruze this as the first two moments of the distributions over the functions restrict to the first two moments.
+
+Replace with a taylor series at the MAP first order taylor expansion in w. degenerate cov function.
+
+- more citations there.
+
+- GP induced by the trained neural network. not GP prior.
+
+- Add the NTK bit back in.
+
+- assume that when you are at the map estimate when you have converged this should be small.
+
+- Write out that w beomces zero under the expectation.
+
+-  transition from background to methods.
+
+- More explination of the dual equation 5 the loss landscape link. Perbutation point linked directly to that here.
+
+-
 
@@
   \centering\scriptsize
-  \caption{Metrics for supervised learning with image data} 
+  \caption{Metrics for supervised learning with image data.
+SVGP is our method, and the number inside parentheses is the number of inducing points.
+SVGP NN is a modification of our method, where the mean is from the NN directly and the variance is from the GP model}
 	\label{tbl:imagesuper}
@@
 \end{table}
-%
-%
-%\subsection{Fast updates in reinforcement learning}
-%
-%\begin{figure}[!t]
-%  \centering
-%  \begin{subfigure}{.2\textwidth}
-%  \resizebox{\textwidth}{!}{%
-%  \begin{tikzpicture}[inner sep=0,outer sep=0]
-%  
-%    % Draw decorated 'ground'
-%    \draw[postaction={draw, decorate, decoration={border, angle=-45,
-%					amplitude=1cm, segment length=.5cm}}] (-3,-1.5) -- (12,-1.5);
-%  
-%    % The cart
-%    \draw[draw=black,fill=black!50,draw=black,line width=3pt,rounded corners=1mm] (0,0) rectangle (9cm,3cm);
-%    \node[fill=black,circle,minimum size=.5cm] (dot) at (4.5cm,3cm) {};
-%    
-%    % Wheels
-%    \node[fill=white,draw=black,line width=3pt,circle,minimum size=2cm,,fill=black!50] at (2cm,-.5cm) {};
-%    \node[fill=white,draw=black,line width=3pt,circle,minimum size=2cm,fill=black!50] at (7cm,-.5cm) {};  
-%    
-%    % The arm
-%    \node[anchor=north,minimum width=1cm,minimum height=14cm,draw=black,rotate=20,rounded corners=5mm,yshift=7mm,xshift=-.3mm,fill=white,draw=black,line width=3pt] at (dot) {};
-%    \node[fill=black,circle,minimum size=.5cm] at (dot) {};
-%    
-%    % Markings
-%    \draw[loosely dashed,line width=1pt] (4.5,6) -- (4.5,-10);
-%    
-%    % Arrow
-%    \draw[->,black,line width=3pt,-{Latex[length=7mm,width=7mm]}] (1,5) --node[above,outer sep=6pt]{\large $x$} (4.5,5);
-%    
-%    \def\centerarc[#1](#2)(#3:#4:#5)% Syntax: [draw options] (center) (initial angle:final angle:radius)
-%    { \draw[#1] ($(#2)+({#5*cos(#3)},{#5*sin(#3)})$) arc (#3:#4:#5); }
-%    
-%    % Draw arc
-%    \centerarc[black,line width=3pt](dot)(270:290:11)
-%    \node at (6.5,-9) {$\theta$};
-%    
-%    \node[white,minimum size=1cm] at (4.5,-13) {};
-%    
-%  \end{tikzpicture}}
-%  \end{subfigure}
-%  \hfill
-%  \begin{subfigure}{.78\textwidth}
-%    % \tikz\node[minimum width=\textwidth,minimum height=.35\textwidth,fill=black!10,rounded corners=2pt]{RL trjectories or something interesting?};
-%
-%    % \includegraphics[width=0.5\textwidth]{./fig/rl.pdf}
-%    \input{./fig/rl}
-%
-%
-%  \end{subfigure}
-%  \hfill
-%  \caption{Add caption.}
-%  \label{fig:rl}
-%\end{figure}
-%
+
+\subsection{Fast updates in reinforcement learning}
+
+\begin{figure}[!t]
+ \centering
+ \begin{subfigure}{.2\textwidth}
+ \resizebox{\textwidth}{!}{%
+ \begin{tikzpicture}[inner sep=0,outer sep=0]
+
+   % Draw decorated 'ground'
+   \draw[postaction={draw, decorate, decoration={border, angle=-45,
+					amplitude=1cm, segment length=.5cm}}] (-3,-1.5) -- (12,-1.5);
+
+   % The cart
+   \draw[draw=black,fill=black!50,draw=black,line width=3pt,rounded corners=1mm] (0,0) rectangle (9cm,3cm);
+   \node[fill=black,circle,minimum size=.5cm] (dot) at (4.5cm,3cm) {};
+
+   % Wheels
+   \node[fill=white,draw=black,line width=3pt,circle,minimum size=2cm,,fill=black!50] at (2cm,-.5cm) {};
+   \node[fill=white,draw=black,line width=3pt,circle,minimum size=2cm,fill=black!50] at (7cm,-.5cm) {};
+
+   % The arm
+   \node[anchor=north,minimum width=1cm,minimum height=14cm,draw=black,rotate=20,rounded corners=5mm,yshift=7mm,xshift=-.3mm,fill=white,draw=black,line width=3pt] at (dot) {};
+   \node[fill=black,circle,minimum size=.5cm] at (dot) {};
+
+   % Markings
+   \draw[loosely dashed,line width=1pt] (4.5,6) -- (4.5,-10);
+
+   % Arrow
+   \draw[->,black,line width=3pt,-{Latex[length=7mm,width=7mm]}] (1,5) --node[above,outer sep=6pt]{\large $x$} (4.5,5);
+
+   \def\centerarc[#1](#2)(#3:#4:#5)% Syntax: [draw options] (center) (initial angle:final angle:radius)
+   { \draw[#1] ($(#2)+({#5*cos(#3)},{#5*sin(#3)})$) arc (#3:#4:#5); }
+
+   % Draw arc
+   \centerarc[black,line width=3pt](dot)(270:290:11)
+   \node at (6.5,-9) {$\theta$};
+
+   \node[white,minimum size=1cm] at (4.5,-13) {};
+
+ \end{tikzpicture}}
+ \end{subfigure}
+ \hfill
+  \setlength{\figurewidth}{.28\textwidth}
+  \setlength{\figureheight}{\figurewidth}
+ \begin{subfigure}{.78\textwidth}
+   % \tikz\node[minimum width=\textwidth,minimum height=.35\textwidth,fill=black!10,rounded corners=2pt]{RL trjectories or something interesting?};
+   % \includegraphics[width=0.5\textwidth]{./fig/rl.pdf}
+   \input{./fig/rl.tex}
+ \end{subfigure}
+ \hfill
+ \caption{Add caption.}
+ \label{fig:rl}
+\end{figure}
+
 %

### 2023-05-14 paper/main.tex

@@
 Firstly how to incorporate uncertainty quantification over predictions which is needed in many applications.
-Secondly, in the sequential data regime data arrives not in batches
+Secondly, in the sequential data regime.
 
@@
 %% EWC, SI, VCL -> weight regularization
-% 1) what is the central problem of CL? 
-% 		Training from a non-stationary distribution the models overwrites the previously learnt parameters and then forgets the previous learnt function.
-% 2) What others have done?
-% 		starting with EWC and SI, that are the most known methods in term of weight regularization. And others took a different approach again in the weight regularization real with VCL (to check)
-% 3) People started to try experimenting with the functional regularization -> 
-% In order of complexity -> DER, FROMP, S-FSVI
-% In order of pubblication -> DER/FROMP, K-Priors (?), S-FSVI
+
 EWC \cite{kirkpatrick2017overcoming}
@@
 %
-If $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) = -\log(p(\mathbf{y} \mid f_\weights(\mathbf{x}_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where the regularization weight takes the role of a prior precision parameter, \ie, $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.
+If $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) = -\log(p(\mathbf{y} \mid f_\weights(\mathbf{x}_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$, where the regularization weight takes the role of a prior precision parameter.
 
@@
 If we limit the interest to the first two moments, we can characterize the resulting posterior over these functions as a Gaussian process (GP).
-
-- distribution over w given to you by the non-linear function.
-One could sample over weights pass it over the function and you have distribution over functions.
-HMC is heavy, structure of the problem around the map estimate.
-characteruze this as the first two moments of the distributions over the functions restrict to the first two moments.
-
-Replace with a taylor series at the MAP first order taylor expansion in w. degenerate cov function.
-
-- more citations there.
-
-- GP induced by the trained neural network. not GP prior.
-
-- Add the NTK bit back in.
-
-- assume that when you are at the map estimate when you have converged this should be small.
-
-- Write out that w beomces zero under the expectation.
-
--  transition from background to methods.
-
-- More explination of the dual equation 5 the loss landscape link. Perbutation point linked directly to that here.
-
--
 
@@
   \centering\scriptsize
-  \caption{Metrics for supervised learning with image data.
-SVGP is our method, and the number inside parentheses is the number of inducing points.
-SVGP NN is a modification of our method, where the mean is from the NN directly and the variance is from the GP model}
+  \caption{Metrics for supervised learning with image data} 
 	\label{tbl:imagesuper}

### 2023-05-14 bnn-predictive/experiments/scripts/classification.py
Preparing to run UCI again

@@ -7,7 +7,7 @@ from torch.nn.utils import parameters_to_vector
 
 from preds.optimizers import LaplaceGGN, get_diagonal_ggn
 from preds.models import SiMLP
-from src import BernoulliLh, CategoricalLh, NTKSVGP
+from src import BernoulliLh, CategoricalLh, NTKSVGP, NN2GPSubset
 import src as ntksvgp
 
 # from preds.likelihoods import BernoulliLh, CategoricalLh
@@ -83,23 +83,32 @@ def evaluate(p, y, likelihood, name, data):
 
 
 def create_ntksvgp(
-    X_train, y_train, model, likelihood, prior_prec, n_inducing=64, batch_size=1000, device="cpu"
+    X_train, y_train, model, likelihood, prior_prec, n_inducing=64, batch_size=1000, device="cpu", subset=False
 ):
     data = (X_train, y_train)
     n_classes = model(X_train).shape[-1]
     print(f"N classes: {n_classes}")
     print(f"Prior prec: {prior_prec}")
     prior = ntksvgp.priors.Gaussian(params=model.parameters, delta=prior_prec)
-    svgp = NTKSVGP(
-        network=model,
-        prior=prior,
-        output_dim=n_classes,
-        likelihood=likelihood,
-        num_inducing=n_inducing,
-        dual_batch_size=batch_size,
-        jitter=0,
-        device=device,
-    )
+    if not subset:
+        svgp = NTKSVGP(
+            network=model,
+            prior=prior,
+            output_dim=n_classes,
+            likelihood=likelihood,
+            num_inducing=n_inducing,
+            dual_batch_size=batch_size,
+            jitter=0,
+            device=device,
+        )
+    else:
+       svgp = NN2GPSubset(network=model,
+                          prior=prior,
+                          likelihood=likelihood,
+                          output_dim=n_classes,
+                          subset_size=n_inducing,
+                          jitter=0,
+                          device=device)
     svgp.set_data(data)
     return svgp
 
@@ -133,7 +142,9 @@ def inference(
     res = dict()
     torch.manual_seed(seed)
     if ds_train.C == 2:
-        likelihood = BernoulliLh(EPS=0.000000001)
+        eps = 0.000000001
+        eps = 0
+        likelihood = BernoulliLh(EPS=eps)
         K = 1
     else:
         eps = 0.0000000001
@@ -195,22 +206,17 @@ def inference(
 
[…]

### 2023-05-14 bnn-predictive/experiments/scripts/imginference.py

@@ -615,6 +615,7 @@ if __name__ == "__main__":
 
     print(f"Writing results to {res_dir}")
     print(f"Reading data from {data_dir}")
+    print(f'Experiment name: {name}')
     print(f"Dataset: {dataset}")
     print(f"Seed: {args.seed}")
 

### 2023-05-14 paper/main.tex
added caption to rl

--- 2023-05-14 paper/main.tex
@@
  \hfill
- \caption{Add caption.}
+ \caption{\textbf{Reinforcement learning experiments} Training curves showing that our model's uncertainty estimates improve sample efficiency in RL.
+   Our method (blue/green) converges to the optimal solution in fewer environment steps than the baseline model-based RL method (magenta) and (DDPG) the model-free baseline  (yellow).}
  \label{fig:rl}

### 2023-05-14 paper/main.tex
made rl fig bigger
updated rl section

@@
 \subsection{Reinforcement learning}
-We now detail how our method can be used in model-based RL.
+A key challenge in RL is to balance the trade-off between exploration and exploitation.
+That is, should the agent select an action that it knows will lead to a high reward (exploitation), or should it select an action that it has
+not selected before, which could lead to either a higher or lower reward (exploration).
+In this section, we detail how our method's principled uncertainty estimates can be used to balance this trade-off using a model-based RL algorithim.
+
 We consider stochastic environments with states \(\state \in \stateDomain \subseteq \R^{D_{\state}} \),
@@
 % is i.i.d. transition noise.
-The goal of RL is to find the policy \(\pi : \stateDomain \rightarrow \actionDomain\) that maximises the sum of discounted rewards
+% $\mathbb{E}_{\noise_{0:\infty}} \big[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \big]$
+% \begin{align} \label{eq-model-free-objective}
+% \policy^{*} = \arg \max_{\policy \in \policyDomain} J(\transitionFn, \policy) = \arg \max_{\policy \in \policyDomain} \mathbb{E}_{\noise_{0:\infty}} \bigg[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \bigg]
+% \quad \text{s.t. } \state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t},
+% \end{align}
+The goal of RL is to find the policy \(\pi : \stateDomain \rightarrow \actionDomain\)
+(from a set of policies $\Pi$) that maximises the sum of discounted rewards
 in expecation over the transition noise,
 \begin{align} \label{eq-model-free-objective}
-\policy^{*} = \arg \max_{\policy \in \policyDomain} J(\transitionFn, \policy) = \arg \max_{\policy \in \policyDomain} \mathbb{E}_{\noise_{0:\infty}} \left[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \right]
-\quad \text{s.t. } \state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t},
+J(\transitionFn, \policy) = \mathbb{E}_{\noise_{0:\infty}} \bigg[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \bigg]
+\quad \text{s.t. } \state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t}
 \end{align}
-where $\gamma \in [0, 1]$ is a discount factor and $\Pi$ is a set of policies.
-
-\textbf{Model-learning}
-In model-based RL, the state transition data set \(\mathcal{D} = \{\{(s_{t},a_{t}), s_{t+1}\}^{T_{i}}_{t=1}\}_{i=0}^{N}\) is first used to
-learn a dynamic model \(f_{\mathbf{w}})\) using supervised learning.
-\cref{alg-mbrl} shows the typical model-based RL loop.
-
+where $\gamma \in [0, 1]$ is a discount factor.
+In this work, we consider model-based RL where a model of the transition dynamics \(f_{\mathbf{w}} \approx \transitionFn\) is learned and then used by a planning algorithm.
 \begin{align} \label{eq-fast-update-mpc}
-  \policy_{i+1}^{\text{PS}}(\state) &= \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
-J^{\Horizon}(\action_{0:\Horizon}, \transitionFn) + \stateValueFn(\state_{\Horizon+1})
-\quad
-  \stateValueFn(\state) &= \mathbb{E} \left[ \sum_{t=0}^{\infty}     \discount^{t} \rewardFn(\state_{t},\action_{t}) \mid \state_{0}=\state \right] %\label{eq-fast-update-mpc-old}
+  \policy^{\text{Greedy}}(\state) &= \arg \max_{\pi \in \Pi} J(f_{\mathbf{w}^{*}}, \pi) \quad   \\
+  \policy^{\text{PS}}(\state) &= \arg \max_{\pi \in \Pi} J(\hat{f}, \pi)
+\quad \text{s.t. } \hat{\transitionFn} \sim p(\transitionFn_{\mathbf{w}} \mid \dataset),
 \end{align}
-
-In model-based RL, we obtain the posterior over the dynamics \(p(f\mid\mathcal{D})\) after performing (approximate) Bayesian
-inference given a state transition data set \(\mathcal{D} = \{\{(s_{t},a_{t}), s_{t+1}\}^{T_{i}}_{t=1}\}_{i=0}^{N}\).
-\cref{alg-mbrl} shows the typical model-based RL loop.
-Importantly, the dynamics are usually only updated after an episode $i$.
-
-\textbf{Posterior sampling}
-Given the posterior dynamics \(p(\transitionFn \mid \mathcal{D})\),
-an effective and  common approach is to simply take the expecation over both the aleatoric and epistemic uncertainty,
-
+Our exact set up uses
+Model Predictive Path Integral (MPPI) control
+\cite{panSample2015}
+\cite{williamsModel2017}
+A principled approach
+% Given the posterior dynamics \(p(\transitionFn \mid \mathcal{D})\),
+% an effective and  common approach is to simply take the expecation over both the aleatoric and epistemic uncertainty,
 \cite{osbandWhyPosteriorSampling2017,osbandMoreEfficientReinforcement2013}
-\begin{align} \label{eq-posterior-sampling}
-\policy_{i+1}^{\text{PS}} = \arg \max_{\policy \in \policyDomain} \left[ J(\transitionFn, \policy) \right] \quad \text{s.t. } \transitionFn \sim p(\transitionFn \mid \dataset_{0:i})
+
+\textbf{Appendix}
+
+% \cref{alg-mbrl} shows the typical model-based RL loop.
+\begin{align} \label{eq-fast-update-mpc}
+  \policy_{i+1}^{\text{PS}}(\state) = \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
+\E \bigg[ \sum_{t=0}^{H-1} \gamma^{t} r(\state_{t},\action_{t}) \mid \state_{0}=\state  \bigg] + Q_{\theta}(\state_{\Horizon}, \action_{H})
+\quad \text{s.t. } \state_{t+1} &= \hat{\transitionFn}(\state_{t}, \action_{t}) + \noise_{t} \\
+\hat{\transitionFn} &\sim p(\transitionFn \mid \dataset),
 \end{align}
+with $\hat{\transitionFn} \sim p(\transitionFn \mid \dataset)$
+
+We use deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016} to learn an action value function $Q_{\theta}$.
+Note that we also learn a policy but its sole purpose is for learning the value function.
 
@@
  \hfill
-  \setlength{\figurewidth}{.28\textwidth}
+  \setlength{\figurewidth}{.4\textwidth}
   \setlength{\figureheight}{\figurewidth}

### 2023-05-14 paper/main.tex
started experiments section
added intro for sequential leqrnaing

@@
 \section{Sparse function-space sequential learning}
+
+We have presented a method for converting any trained neural network into a sparse function-space representation.
+In this section, we demonstrate how sequential learning methods can benefit from our function-space representation.
 
@@
 
+Our experiments seek to answer the following questions:
+\begin{itemize}
+  \item Does NN2SFR caputure good uncertainty estimates
+\end{itemize}
+
 \subsection{Capturing uncertainty in UCI tasks under supervised learning}

### 2023-05-14 paper/main.tex
made continual learning a sub section
rewrite 2.1

--- 2023-05-14 paper/main.tex
@@
 %
-\todo{You need something like this to bridge from the previous, GPs cannot come from nowhere!}
-The structure of the posterior given by the loss-landscape around the MAP weights $\vw^*$  induces a correlation structure on learned model functions of the neural network.
-These can be seen as possible perturbed versions of $f_{\vw^*}$ that can be used for characterizing ambiguity and uncertainty in the learned model (see \cref{fig:banana} for an example of sampling in weight-space).
-This gives rise to a probability {\em distribution} over the possible functions.
-If we limit the interest to the first two moments, we can characterize the resulting posterior over these functions as a Gaussian process (GP).
+Quantifying uncertainty in a Bayesian framework boils down to finding a posterior of $p(\vw \mid \dataset)$ from, which represents the uncertainty over our parameters based on the prior and data.
+The posterior structure is related to the loss-landscape around the MAP weights $\vw^*$, which induces a correlation structure on functions produced from the neural network's deterministic mapping.
+Samples from the weight posterior are perturbed versions of $f_{\vw^*}$ characterizing uncertainty in the learned model in the function space.
+Although the true posterior is intractable given the non-linearities of the neural network sampling techniques available such as Hamiltonian Monte-Carlo (HMC), The uncertainty plotted \cref{fig:banana} shows the induced function space posterior by sampling through the model.
+However, in most cases, sampling techniques like HMC are not available given the computational burden.
+
+A common approach is to approximate the correlation structure of a distribution centred at the MAP estimate such as the Laplace-GNN \citep{khan2019approximate, daxberger2021laplace, maddox2021fast}.
+The Laplace GNN takes the MAP solution and approximates the Hessian of our loss function  $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i)$ with the GGN approximation.
+Another way of viewing the
+
+In this paper we are concerned with learning posterior directly in the function space.
+
+- distribution over w given to you by the non-linear function.
+One could sample over weights pass it over the function and you have distribution over functions.
+HMC is heavy, structure of the problem around the map estimate.
+characteruze this as the first two moments of the distributions over the functions restrict to the first two moments.
+
+Replace with a taylor series at the MAP first order taylor expansion in w. degenerate cov function.
+
+- more citations there.
+
+- GP induced by the trained neural network. not GP prior.
+
+- Add the NTK bit back in.
+
+- assume that when you are at the map estimate when you have converged this should be small.
+
+- Write out that w beomces zero under the expectation.
+
+-  transition from background to methods.
+
+- More explination of the dual equation 5 the loss landscape link. Perbutation point linked directly to that here.
+
+-
 
@@
 \label{eq:dual_param}
-\alpha_i \coloneqq \myexpect_{p(f_i \mid \vy)}[\nabla_{f_i}\log p(y_i \mid f_i)],  \quad
-\beta_i \coloneqq - \myexpect_{p(f_i \mid \vy)}[\nabla^2_{f_i f_i}\log p(y_i \mid f_i)] ,
+\alpha_i \coloneqq \myexpect_{p(\vw \mid \vy)}[\nabla_{f_i}\log p(y_i \mid f_i)],  \quad
+\beta_i \coloneqq - \myexpect_{p(\vw \mid \vy)}[\nabla^2_{f_i f_i}\log p(y_i \mid f_i)] ,
 \end{equation}
@@
  \hfill
- \caption{\textbf{Reinforcement learning experiments} Training curves showing that our model's uncertainty estimates improve sample efficiency in RL.
-   Our method (blue/green) converges to the optimal solution in fewer environment steps than the baseline model-based RL method (magenta) and (DDPG) the model-free baseline  (yellow).}
+ \caption{Add caption.}
  \label{fig:rl}

### 2023-05-14 paper/main.tex

--- 2023-05-14 paper/main.tex
@@
 
-\textbf{Continual learning}
+\subsection{Continual learning}
 

### 2023-05-14 src/nn2svgp/train_regression_subset.py
updated sequential ledarning intro

@@ -57,7 +57,7 @@ if __name__ == "__main__":
     updates = False
     plot_var = False
     plot_var = True
-    save_dir = "figs"
+    save_dir = "figs/nn2gp"
 
     def func(x, noise=True):
         # x = x + 1e-6

### 2023-05-14 paper/main.tex
updated sequential ledarning intro
updated rl

@@
 We have presented a method for converting any trained neural network into a sparse function-space representation.
-In this section, we demonstrate how sequential learning methods can benefit from our function-space representation.
+In this section, we demonstrate how sequential learning methods can benefit from our function-space representation and it's associated uncertainty estimates.
 
@@
 In this work, we consider model-based RL where a model of the transition dynamics \(f_{\mathbf{w}} \approx \transitionFn\) is learned and then used by a planning algorithm.
+A simple approach is to use the learned dynamic $f_{\mathbf{w}^{*}}$,
 \begin{align} \label{eq-fast-update-mpc}
-  \policy^{\text{Greedy}}(\state) &= \arg \max_{\pi \in \Pi} J(f_{\mathbf{w}^{*}}, \pi) \quad   \\
+  \policy^{\text{Greedy}}(\state) &= \arg \max_{\pi \in \Pi} J(f_{\mathbf{w}^{*}}, \pi)
+\end{align}
+However, we can leverage our method to
+$p(\transitionFn_{\mathbf{w}^{*}} \mid \dataset) = \mathcal{N}$
+\cite{osbandWhyPosteriorSampling2017,osbandMoreEfficientReinforcement2013}
+\begin{align} \label{eq-fast-update-mpc}
   \policy^{\text{PS}}(\state) &= \arg \max_{\pi \in \Pi} J(\hat{f}, \pi)
-\quad \text{s.t. } \hat{\transitionFn} \sim p(\transitionFn_{\mathbf{w}} \mid \dataset),
+\quad \text{s.t. } \tilde{\transitionFn} \sim q_{\mathbf{u}}(\hat{\transitionFn} \mid \dataset),
 \end{align}
+
 Our exact set up uses
@@
 \cite{williamsModel2017}
+\todo{what is correct citation for MPPI?}
 A principled approach
@@
 % an effective and  common approach is to simply take the expecation over both the aleatoric and epistemic uncertainty,
-\cite{osbandWhyPosteriorSampling2017,osbandMoreEfficientReinforcement2013}
 

### 2023-05-14 paper/main.tex
rewrite 2.1

@@
 The Laplace GNN takes the MAP solution and approximates the Hessian of our loss function  $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i)$ with the GGN approximation.
-Another way of viewing the
+Another way of viewing the approximation is that we build the following approximate model $\hat{f}_\weights(\mathbf{x}_{i}) = \Jac{\weights}{\mathbf{x}_i} \vw $  where $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$ is the Jacobian.
+Using such an approximation we arrive at the Laplace-GGN posterior $q(\vw;  f_{\vw^*}(\vx_i) )$
 
@@
 \begin{equation}\label{eq:dual_sparse_post}
-   \myexpect_{q_{\vu}(\vf)}[\vf_i] = \vkzs^{\T} \MKzz^{-1}   \valpha_{\vu} , \quad 
-   \textrm{Var}_{q_{\vu}(\vf)}[\vf_i]  = \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \vbeta_{\vu})^{-1} ]\vkzs
+   \myexpect_{q_{\vu}(\vf)}[f_i] = \vkzs^{\T} \MKzz^{-1}   \valpha_{\vu} , \quad 
+   \textrm{Var}_{q_{\vu}(\vf)}[f_i]  = \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \vbeta_{\vu})^{-1} ]\vkzs
 \end{equation}
@@
  \hfill
-  \setlength{\figurewidth}{.4\textwidth}
-  \setlength{\figureheight}{\figurewidth}
  \begin{subfigure}{.78\textwidth}
-   % \tikz\node[minimum width=\textwidth,minimum height=.35\textwidth,fill=black!10,rounded corners=2pt]{RL trjectories or something interesting?};
-   % \includegraphics[width=0.5\textwidth]{./fig/rl.pdf}
+   \centering\scriptsize
+   \setlength{\figurewidth}{\textwidth}
+   \setlength{\figureheight}{.5\figurewidth}
+   \pgfplotsset{axis on top}
    \input{./fig/rl.tex}

### 2023-05-14 paper/main.tex
Fig.
rewrite 2.1

@@
 
-\section{Methods}
+\section{Background}
 \label{sec:methods}
@@
 
-A common approach is to approximate the correlation structure of a distribution centred at the MAP estimate such as the Laplace-GNN \citep{khan2019approximate, daxberger2021laplace, maddox2021fast}.
-The Laplace GNN takes the MAP solution and approximates the Hessian of our loss function  $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i)$ with the GGN approximation.
-Another way of viewing the approximation is that we build the following approximate model $\hat{f}_\weights(\mathbf{x}_{i}) = \Jac{\weights}{\mathbf{x}_i} \vw $  where $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$ is the Jacobian.
-Using such an approximation we arrive at the Laplace-GGN posterior $q(\vw;  f_{\vw^*}(\vx_i) )$
-
-In this paper we are concerned with learning posterior directly in the function space.
+A common approach is to approximate the correlation structure of a distribution centred at the MAP estimate as done in the Laplace-GGN \citep{khan2019approximate, daxberger2021laplace, maddox2021fast}.
+The Laplace GGN takes the MAP solution and approximates the Hessian of our loss function  $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i)$ with the GGN approximation.
+Another way of viewing the approximation is that we build the following approximate model $\hat{f}_\weights(\mathbf{x}_{i}) = \Jac{\weights}{\mathbf{x}_i} \vw $  where $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$ is the Jacobian as was pointed out in \citep{khan2019approximate}.
+Using the Hessian of the approximate model, we arrive at the Laplace-GGN posterior for $q(\vw)$.
+
+In this paper we are concerned with learning posterior directly in the function space that is having a $q(\vf)$ instead of a $q(\vw)$.
+A common choice is to use a Gaussian process characterizes a distribution over functions in terms of the first two moments, a mean $\mu(\cdot)$ and covariance function $\kappa(\cdot,\cdot)$ (kernel).
+We aim to find a kernel and mean function based on the neural network to build the Gaussian process posterior.
+A linear function in terms of parameters can be converted from the weight space to the function space (see Ch.~XXX in \cite{rasmussen2006gaussian} as follows:
+\begin{equation} \label{eq:weight_func}
+g_\weights(\mathbf{x}_{i}) = \phi^\top\!(\vx) \, \vw \implies \mu(\vx) = \vzeros \quad \kappa(\mathbf{x}, \mathbf{x}') = \frac{1}{\delta} \phi(\vx)^\top \phi(\vx)
+\end{equation}
 
@@
 
+\section{Methods}
 \paragraph{Linearization in the dual parameters}

### 2023-05-14 paper/main.tex
merge

@@
 Despite its success, gradient-based learning techniques exhibit limitations.
-Firstly how to incorporate uncertainty quantification over predictions which is needed in many applications.
+Firstly, how to incorporate uncertainty quantification over predictions which is needed in many applications.
 Secondly, in the sequential data regime data arrives not in batches
@@
 Recent work on techniques (\eg, \cite{list}) for converting trained neural networks from weight space to function space allow a principled mathematical approach for analyzing the behaviour \cite{add}, performing probabilistic inference \cite{add}, and quantifying uncertainty in neural networks \cite{add}.
-The methods rely on linearizing the neural network and capturing the first two moments in function space in terms of a mean function and covariance function (kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}).
+The methods rely on linearizing the neural network and capturing the first two moments in function space in terms of a mean function and covariance function (or kernel) --- defining a Gaussian process (GP, \cite{rasmussen2006gaussian}).
 GPs provide a widely-used probabilistic toolkit with principled uncertainty estimates, and they are a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} with theoretical guarantees on regret bounds \citep{srinivas2009gaussian}.
@@
 %
-Quantifying uncertainty in a Bayesian framework boils down to finding a posterior of $p(\vw \mid \dataset)$ from, which represents the uncertainty over our parameters based on the prior and data.
+Quantifying uncertainty in a Bayesian framework boils down to finding a posterior of $p(\vw \mid \dataset)$, which represents the uncertainty over our parameters based on the prior and the data.
 The posterior structure is related to the loss-landscape around the MAP weights $\vw^*$, which induces a correlation structure on functions produced from the neural network's deterministic mapping.
 Samples from the weight posterior are perturbed versions of $f_{\vw^*}$ characterizing uncertainty in the learned model in the function space.
-Although the true posterior is intractable given the non-linearities of the neural network sampling techniques available such as Hamiltonian Monte-Carlo (HMC), The uncertainty plotted \cref{fig:banana} shows the induced function space posterior by sampling through the model.
-However, in most cases, sampling techniques like HMC are not available given the computational burden.
+Although the true posterior is intractable given the non-linearities of the neural network, sampling techniques available, such as Hamiltonian Monte-Carlo (HMC), in most cases, are not available given the computational burden.
+ The uncertainty plotted \cref{fig:banana} shows the induced function space posterior by sampling through the model.
 
@@
 \begin{equation} \label{eq:weight_func}
-g_\weights(\mathbf{x}_{i}) = \phi^\top\!(\vx) \, \vw \implies \mu(\vx) = \vzeros \quad \kappa(\mathbf{x}, \mathbf{x}') = \frac{1}{\delta} \phi(\vx)^\top \phi(\vx)
+g_\weights(\mathbf{x}) = \phi^\top\!(\vx) \, \vw \implies \mu(\vx) = \vzeros \quad \kappa(\mathbf{x}, \mathbf{x}') = \frac{1}{\delta} \phi(\vx)^\top \phi(\vx)
 \end{equation}
@@
 $f^{\textrm{lin.}}_{\vw^*}(\vx; \vw) = f_{\vw^*}(\vx) + \Jac{\weights^*}{\mathbf{x}} \, (\vw - \vw^*)$ of the neural network, where $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$ is the Jacobian.
-The approximation can be used with any approximate inference technique but in the paper they focus on the Laplace-GNN.
+The approximation can be used with any approximate inference technique but in the paper they focus on the Laplace-GGN.
 They find that the linear approximation helps to improve predictions by correcting the approximate posterior when sampled through a non-Gaussian likelihoods.
 
-Furthermore, under the linear approximation they showed you can now convert your weight space prior to the function space by combining with \cref{eq:weight_func} meaning the converged neural network GP prior is:
+Furthermore, under the linear approximation they showed one can convert the weight space prior to the function space by combining with \cref{eq:weight_func} meaning the converged neural network GP prior is:
 \begin{equation} \label{eq-laplace-approx-function-space}
@@
 \paragraph{Neural network dual variables}
-As we are using the MAP solution of the neural network loss we will use the Laplace approximation for the dual variables but other techniques could be used.
-As was detailed in \cite{wilkinson2023bayes, rasmussen2006gaussian}, the dual variables of the Laplace approximation is the same as removing the posterior averaging from \cref{eq:dual_param} meaning:
+As we are using the MAP solution of the neural network loss, we will use the Laplace approximation for the dual variables but other techniques could be used.
+As detailed in \cite{wilkinson2023bayes, rasmussen2006gaussian}, the dual variables of the Laplace approximation are the same as removing the posterior averaging from \cref{eq:dual_param}, meaning:
 \begin{equation}
@@
 Sparse Gaussian processes are a way to reduce the computational complexity of a full GP using a low-rank approximation.
-Many sparsifying approaches exist (see \cite{quinonero2005unifying}) for an overview.
+Many sparsifying approaches exist, we refer the reader to \cite{quinonero2005unifying} for an overview.
 Given that we have our dual variables derived from our neural network predictions and kernel function, we could use any approximation.

### 2023-05-14 paper/main.tex
added to rl appendix

--- 2023-05-14 paper/main.tex
@@
 The Laplace GNN takes the MAP solution and approximates the Hessian of our loss function  $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i)$ with the GGN approximation.
-Another way of viewing the approximation is that we build the following approximate model $\hat{f}_\weights(\mathbf{x}_{i}) = \Jac{\weights}{\mathbf{x}_i} \vw $  where $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$ is the Jacobian.
-Using such an approximation we arrive at the Laplace-GGN posterior $q(\vw;  f_{\vw^*}(\vx_i) )$
+Another way of viewing the
 
@@
 \begin{equation}\label{eq:dual_sparse_post}
-   \myexpect_{q_{\vu}(\vf)}[f_i] = \vkzs^{\T} \MKzz^{-1}   \valpha_{\vu} , \quad 
-   \textrm{Var}_{q_{\vu}(\vf)}[f_i]  = \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \vbeta_{\vu})^{-1} ]\vkzs
+   \myexpect_{q_{\vu}(\vf)}[\vf_i] = \vkzs^{\T} \MKzz^{-1}   \valpha_{\vu} , \quad 
+   \textrm{Var}_{q_{\vu}(\vf)}[\vf_i]  = \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \vbeta_{\vu})^{-1} ]\vkzs
 \end{equation}
@@
  \hfill
+  \setlength{\figurewidth}{.4\textwidth}
+  \setlength{\figureheight}{\figurewidth}
  \begin{subfigure}{.78\textwidth}
-   \centering\scriptsize
-   \setlength{\figurewidth}{\textwidth}
-   \setlength{\figureheight}{.5\figurewidth}
-   \pgfplotsset{axis on top}
+   % \tikz\node[minimum width=\textwidth,minimum height=.35\textwidth,fill=black!10,rounded corners=2pt]{RL trjectories or something interesting?};
+   % \includegraphics[width=0.5\textwidth]{./fig/rl.pdf}
    \input{./fig/rl.tex}
@@
 
-\section{Model-based Reinforcement Learning with Fast Updates}
-
-\subsection{Problem Statement and Background} \label{sec:problem-statement}
-We consider environments with states \(\state \in \stateDomain \), actions \(\action \in \actionDomain\) and transition dynamics \(\transitionFn: \stateDomain \times \actionDomain \rightarrow \stateDomain \) subject to
-iid noise \(\noise_{t}\), given by,
-\begin{align}
-\state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t}.
+\section{Model-based Reinforcement Learning}
+\label{sec-rl-appendix}
+
+Model Predictive Path Integral (MPPI) control
+\cite{panSample2015}
+\cite{williamsModel2017}
+\todo{what is correct citation for MPPI?}
+
+% \cref{alg-mbrl} shows the typical model-based RL loop.
+\begin{align} \label{eq-fast-update-mpc}
+  \policy_{i+1}^{\text{PS}}(\state) = \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
+\E \bigg[ \sum_{t=0}^{H-1} \gamma^{t} r(\state_{t},\action_{t}) \mid \state_{0}=\state  \bigg] + Q_{\theta}(\state_{\Horizon}, \action_{H})
+\quad \text{s.t. } \state_{t+1} &= \hat{\transitionFn}(\state_{t}, \action_{t}) + \noise_{t}
 \end{align}
-\begin{assumption}
-  (system properties) The environment's dynamics are $L_{\transitionFn}\text{-Lipschitz}$ continuous and the transition noise $\noise_{t}$ is $\sigma\text{-sub-Gaussian}$ for all $t \geq 0$.
-\end{assumption}
+with $\hat{\transitionFn} \sim p(\transitionFn \mid \dataset)$
+
+We use deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016} to learn an action value function $Q_{\theta}$.
+Note that we also learn a policy but its sole purpose is for learning the value function.
+
+\subsection{Experiment Configuration}
+This section details how we configured and ran our reinforcement learning experiments.
+
+\textbf{Dynamic model}
+In all experiments we used an MLP dynamic model with a single hidden layer of width 64 and TanH activation functions.
+At each episode we used Adam \cite{adam} to optimise the NN parameters for $5000$ iterations with a learning rate of $0.001$.
+We reset the optimizer after each episode.
+As we are performing regression we instantiate the loss function in \cref{eq-empirical-risk} as the well-known mean squared error.
+This corresponds to a Gaussian likelihood with unit variance.
+We then set the prior precision as $\delta=0.0001$.
+% It is worth noting that $\delta$ effects both the neur
+In all experiments our sparse function-space representation uses $m=128$ inducing points and this seemed to be sufficient.
+
+\textbf{Model predictive path integral (MPPI)}
+MPPI is an online planning algorithim which iteratively improves the action trajectory $\action_{t:t+H}$ using samples.
+At each iteration $j$, $N=256$ trajectories are sampled according to the currect action trajectory $\action^{j}_{t:t+H}$.
+The $K=32$ top trajectories with highest returns $\sum_{h=0}^{H} = r(\state^{j}_{t+h}, \action^{j}_{t+h})$ are selected.
+The next action trajectory $\action^{j+1}_{t:t+H}$ is then computed by taking the weighted average of the top $K=32$ trajectories
+with weights from the softmax over returns from top $K=32$ trajectories.
+
+$\gamma 0.9$
+$\tau=0.005$
+horizon $H=5$
+temperature $0.5$
+momentum $0.1$
+
+\textbf{Initial data set}
+We collect an initial data set using a random policy for one episode.
+
+\textbf{DDPG}
+action value function is an MLP with a single hidden layer of width $128$ with ELU activation functions.
+We train the DDPG agent using Adam for $500$ iterations at each episode, using a learning rate $0.0001$.
+
 %

### 2023-05-14 paper/main.tex
added to rl experiments sectin
added to rl section

@@
 A key challenge in RL is to balance the trade-off between exploration and exploitation.
-That is, should the agent select an action that it knows will lead to a high reward (exploitation), or should it select an action that it has
-not selected before, which could lead to either a higher or lower reward (exploration).
-In this section, we detail how our method's principled uncertainty estimates can be used to balance this trade-off using a model-based RL algorithim.
+That is, should the agent select an action that it knows will lead to a high reward (exploitation), or should it
+hope to discover new actions which lead to high reward (exploration) by selecting actions that it has not selected before.
+In this section, we detail how our method's principled uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim.
 
@@
 (from a set of policies $\Pi$) that maximises the sum of discounted rewards
-in expecation over the transition noise,
+in expectation over the transition noise,
 \begin{align} \label{eq-model-free-objective}
 J(\transitionFn, \policy) = \mathbb{E}_{\noise_{0:\infty}} \bigg[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \bigg]
-\quad \text{s.t. } \state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t}
+\quad \text{s.t. } \state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t},
 \end{align}
-where $\gamma \in [0, 1]$ is a discount factor.
-In this work, we consider model-based RL where a model of the transition dynamics \(f_{\mathbf{w}} \approx \transitionFn\) is learned and then used by a planning algorithm.
-A simple approach is to use the learned dynamic $f_{\mathbf{w}^{*}}$,
-\begin{align} \label{eq-fast-update-mpc}
-  \policy^{\text{Greedy}}(\state) &= \arg \max_{\pi \in \Pi} J(f_{\mathbf{w}^{*}}, \pi)
+where $\gamma \in [0, 1)$ is a discount factor.
+In this work, we consider model-based RL where a model of the transition dynamics is learned \(f_{\mathbf{w}} \approx \transitionFn\) and then used by a planning algorithm.
+A simple approach is to use the learned dynamic model $f_{\mathbf{w}^{*}}$ and maximise the objective in \cref{eq-model-free-objective},
+\begin{align} \label{eq-greedy}
+  \policy^{\text{Greedy}}(\state) &= \arg \max_{\pi \in \Pi} J(f_{\mathbf{w}^{*}}, \pi).
 \end{align}
-However, we can leverage our method to
-$p(\transitionFn_{\mathbf{w}^{*}} \mid \dataset) = \mathcal{N}$
-\cite{osbandWhyPosteriorSampling2017,osbandMoreEfficientReinforcement2013}
-\begin{align} \label{eq-fast-update-mpc}
+However, we can leverage the method in \cref{sec:methods} to obtain a function-space posterior over the learned dynamics $q_{\mathbf{u}}(\hat{\transitionFn} \mid \dataset)$,
+where $\mathcal{D}$ represents the state transition data set \(\mathcal{D} = \{(s_{i},a_{i}), s_{i+1}\}_{i=0}^{N}\).
+Importantly, the uncertainty represented by this posterior distribution can be used to balance the exploration-exploitation trade-off,
+using approaches such as posterior sampling \cite{osbandWhyPosteriorSampling2017,osbandMoreEfficientReinforcement2013},
+\begin{align} \label{eq-posterior-sampling}
   \policy^{\text{PS}}(\state) &= \arg \max_{\pi \in \Pi} J(\hat{f}, \pi)
@@
 \end{align}
-
-Our exact set up uses
-Model Predictive Path Integral (MPPI) control
-\cite{panSample2015}
-\cite{williamsModel2017}
-\todo{what is correct citation for MPPI?}
-A principled approach
-% Given the posterior dynamics \(p(\transitionFn \mid \mathcal{D})\),
-% an effective and  common approach is to simply take the expecation over both the aleatoric and epistemic uncertainty,
-
-\textbf{Appendix}
-
-% \cref{alg-mbrl} shows the typical model-based RL loop.
-\begin{align} \label{eq-fast-update-mpc}
-  \policy_{i+1}^{\text{PS}}(\state) = \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
-\E \bigg[ \sum_{t=0}^{H-1} \gamma^{t} r(\state_{t},\action_{t}) \mid \state_{0}=\state  \bigg] + Q_{\theta}(\state_{\Horizon}, \action_{H})
-\quad \text{s.t. } \state_{t+1} &= \hat{\transitionFn}(\state_{t}, \action_{t}) + \noise_{t} \\
-\hat{\transitionFn} &\sim p(\transitionFn \mid \dataset),
-\end{align}
-with $\hat{\transitionFn} \sim p(\transitionFn \mid \dataset)$
-
-We use deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016} to learn an action value function $Q_{\theta}$.
-Note that we also learn a policy but its sole purpose is for learning the value function.
+where a function $\tilde{\transitionFn}$ is sampled from the (approximate) posterior $q_{\mathbf{u}}(\hat{\transitionFn} \mid \dataset)$ and used to find a policy as
+in \cref{eq-greedy}.
+Intuitively, this strategy will explore where the model has high uncertainty, which in turn will reduce the model's uncertainty as data is collected and used to
+train the model.
+See \cref{sec-rl-appendix} for more details of how we use
+
+\textbf{Pathwise conditioning in function-space??}
+\todo{could try to implement this}
 
@@
 
-\subsection{Fast updates in reinforcement learning}
+\subsection{Reinforcement Learning}
+
+In section \label{sec-rl} we detailed how our method can be used to
+
+See \label{sec-rl-experiments-appendix} for more details of our experiments.
+
+We compare a model-based RL agent using a simple MLP dynamic model with
+\begin{itemize}
+  \item uncertainty is good for exploration
+\end{itemize}
+
+\cref{fig:rl} shows training curves
 

### 2023-05-14 paper/main.tex

@@
 %
-Quantifying uncertainty in a Bayesian framework boils down to finding a posterior of $p(\vw \mid \dataset)$ from, which represents the uncertainty over our parameters based on the prior and data.
+Quantifying uncertainty in a Bayesian framework boils down to finding a posterior of $p(\vw \mid \dataset)$, which represents the uncertainty over our parameters based on the prior and the data.
 The posterior structure is related to the loss-landscape around the MAP weights $\vw^*$, which induces a correlation structure on functions produced from the neural network's deterministic mapping.
 Samples from the weight posterior are perturbed versions of $f_{\vw^*}$ characterizing uncertainty in the learned model in the function space.
-Although the true posterior is intractable given the non-linearities of the neural network sampling techniques available such as Hamiltonian Monte-Carlo (HMC), The uncertainty plotted \cref{fig:banana} shows the induced function space posterior by sampling through the model.
-However, in most cases, sampling techniques like HMC are not available given the computational burden.
-
-A common approach is to approximate the correlation structure of a distribution centred at the MAP estimate such as the Laplace-GNN \citep{khan2019approximate, daxberger2021laplace, maddox2021fast}.
-The Laplace GNN takes the MAP solution and approximates the Hessian of our loss function  $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i)$ with the GGN approximation.
-Another way of viewing the
-
-In this paper we are concerned with learning posterior directly in the function space.
+Although the true posterior is intractable given the non-linearities of the neural network, sampling techniques available, such as Hamiltonian Monte-Carlo (HMC), in most cases, are not available given the computational burden.
+ The uncertainty plotted \cref{fig:banana} shows the induced function space posterior by sampling through the model.
+
+A common approach is to approximate the correlation structure of a distribution centred at the MAP estimate as done in the Laplace-GGN \citep{khan2019approximate, daxberger2021laplace, maddox2021fast}.
+The Laplace GGN takes the MAP solution and approximates the Hessian of our loss function  $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i)$ with the GGN approximation.
+Another way of viewing the approximation is that we build the following approximate model $\hat{f}_\weights(\mathbf{x}_{i}) = \Jac{\weights}{\mathbf{x}_i} \vw $  where $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$ is the Jacobian as was pointed out in \citep{khan2019approximate}.
+Using the Hessian of the approximate model, we arrive at the Laplace-GGN posterior for $q(\vw)$.
+
+In this paper we are concerned with learning posterior directly in the function space that is having a $q(\vf)$ instead of a $q(\vw)$.
+A common choice is to use a Gaussian process characterizes a distribution over functions in terms of the first two moments, a mean $\mu(\cdot)$ and covariance function $\kappa(\cdot,\cdot)$ (kernel).
+We aim to find a kernel and mean function based on the neural network to build the Gaussian process posterior.
+A linear function in terms of parameters can be converted from the weight space to the function space (see Ch.~XXX in \cite{rasmussen2006gaussian} as follows:
+\begin{equation} \label{eq:weight_func}
+g_\weights(\mathbf{x}_{i}) = \phi^\top\!(\vx) \, \vw \implies \mu(\vx) = \vzeros \quad \kappa(\mathbf{x}, \mathbf{x}') = \frac{1}{\delta} \phi(\vx)^\top \phi(\vx)
+\end{equation}
 

### 2023-05-14 paper/main.tex
updated CL part

@@
 % Math Macros
+\newcommand{\MB}{\mbf{B}}
 \newcommand{\MC}{\mbf{C}}
@@
 %
+
 A Gaussian process characterizes a distribution over functions in terms of the first two moments, a mean $\mu(\cdot)$ and covariance function $\kappa(\cdot,\cdot)$ (kernel).
@@
 
-\section{Sparse function-space sequential learning}
+\section{Sparse Function-space Sequential Learning}
 
@@
 
-\subsection{Continual learning}
+\subsection{Continual Learning}
+
+\begin{equation}
+ 	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{m \times m}
+ \end{equation}
+
+\begin{equation}
+	\mathcal{R_\textit{SFR}}(\mathbf{w}) = \sum_{s=1}^{t-1}\left[\left(f_{\vw}(\MZ_{s}) - f_{\vw_{s}}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\vw}(\MZ_{s}) - f_{\vw_{s}}(\MZ_s) \right) \right] \in \R
+\end{equation}
 
@@
 A key challenge in RL is to balance the trade-off between exploration and exploitation.
-That is, should the agent select an action that it knows will lead to a high reward (exploitation), or should it
-hope to discover new actions which lead to high reward (exploration) by selecting actions that it has not selected before.
-In this section, we detail how our method's principled uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim.
+That is, should the agent select an action that it knows will lead to a high reward (exploitation), or should it select an action that it has
+not selected before, which could lead to either a higher or lower reward (exploration).
+In this section, we detail how our method's principled uncertainty estimates can be used to balance this trade-off using a model-based RL algorithim.
 
@@
 (from a set of policies $\Pi$) that maximises the sum of discounted rewards
-in expectation over the transition noise,
+in expecation over the transition noise,
 \begin{align} \label{eq-model-free-objective}
 J(\transitionFn, \policy) = \mathbb{E}_{\noise_{0:\infty}} \bigg[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \bigg]
-\quad \text{s.t. } \state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t},
+\quad \text{s.t. } \state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t}
 \end{align}
-where $\gamma \in [0, 1)$ is a discount factor.
-In this work, we consider model-based RL where a model of the transition dynamics is learned \(f_{\mathbf{w}} \approx \transitionFn\) and then used by a planning algorithm.
-A simple approach is to use the learned dynamic model $f_{\mathbf{w}^{*}}$ and maximise the objective in \cref{eq-model-free-objective},
-\begin{align} \label{eq-greedy}
-  \policy^{\text{Greedy}}(\state) &= \arg \max_{\pi \in \Pi} J(f_{\mathbf{w}^{*}}, \pi).
+where $\gamma \in [0, 1]$ is a discount factor.
+In this work, we consider model-based RL where a model of the transition dynamics \(f_{\mathbf{w}} \approx \transitionFn\) is learned and then used by a planning algorithm.
+A simple approach is to use the learned dynamic $f_{\mathbf{w}^{*}}$,
+\begin{align} \label{eq-fast-update-mpc}
+  \policy^{\text{Greedy}}(\state) &= \arg \max_{\pi \in \Pi} J(f_{\mathbf{w}^{*}}, \pi)
 \end{align}
-However, we can leverage the method in \cref{sec:methods} to obtain a function-space posterior over the learned dynamics $q_{\mathbf{u}}(\hat{\transitionFn} \mid \dataset)$,
-where $\mathcal{D}$ represents the state transition data set \(\mathcal{D} = \{(s_{i},a_{i}), s_{i+1}\}_{i=0}^{N}\).
-Importantly, the uncertainty represented by this posterior distribution can be used to balance the exploration-exploitation trade-off,
-using approaches such as posterior sampling \cite{osbandWhyPosteriorSampling2017,osbandMoreEfficientReinforcement2013},
-\begin{align} \label{eq-posterior-sampling}
+However, we can leverage our method to
+$p(\transitionFn_{\mathbf{w}^{*}} \mid \dataset) = \mathcal{N}$
+\cite{osbandWhyPosteriorSampling2017,osbandMoreEfficientReinforcement2013}
+\begin{align} \label{eq-fast-update-mpc}
   \policy^{\text{PS}}(\state) &= \arg \max_{\pi \in \Pi} J(\hat{f}, \pi)
@@
 \end{align}
-where a function $\tilde{\transitionFn}$ is sampled from the (approximate) posterior $q_{\mathbf{u}}(\hat{\transitionFn} \mid \dataset)$ and used to find a policy as
-in \cref{eq-greedy}.
-Intuitively, this strategy will explore where the model has high uncertainty, which in turn will reduce the model's uncertainty as data is collected and used to
-train the model.
-See \cref{sec-rl-appendix} for more details of how we use
-
-\textbf{Pathwise conditioning in function-space??}
-\todo{could try to implement this}
+
+Our exact set up uses
+Model Predictive Path Integral (MPPI) control
+\cite{panSample2015}
+\cite{williamsModel2017}
+\todo{what is correct citation for MPPI?}
+A principled approach
+% Given the posterior dynamics \(p(\transitionFn \mid \mathcal{D})\),
+% an effective and  common approach is to simply take the expecation over both the aleatoric and epistemic uncertainty,
+
+\textbf{Appendix}
+
+% \cref{alg-mbrl} shows the typical model-based RL loop.
+\begin{align} \label{eq-fast-update-mpc}
+  \policy_{i+1}^{\text{PS}}(\state) = \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
+\E \bigg[ \sum_{t=0}^{H-1} \gamma^{t} r(\state_{t},\action_{t}) \mid \state_{0}=\state  \bigg] + Q_{\theta}(\state_{\Horizon}, \action_{H})
+\quad \text{s.t. } \state_{t+1} &= \hat{\transitionFn}(\state_{t}, \action_{t}) + \noise_{t} \\
+\hat{\transitionFn} &\sim p(\transitionFn \mid \dataset),
+\end{align}
+with $\hat{\transitionFn} \sim p(\transitionFn \mid \dataset)$
+
+We use deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016} to learn an action value function $Q_{\theta}$.
+Note that we also learn a policy but its sole purpose is for learning the value function.
 
@@
   \item Does NN2SFR caputure good uncertainty estimates
+  \item Can NN2SFR be used to build a summary of the current neural network to mitigate catastrophic forgetting over previous tasks?
 \end{itemize}
@@
 
-\subsection{Reinforcement Learning}
-
-In section \label{sec-rl} we detailed how our method can be used to
-
-See \label{sec-rl-experiments-appendix} for more details of our experiments.
-
-We compare a model-based RL agent using a simple MLP dynamic model with
-\begin{itemize}
-  \item uncertainty is good for exploration
-\end{itemize}
-
-\cref{fig:rl} shows training curves
+\subsection{Fast updates in reinforcement learning}
 
@@
 
-\section{Model-based Reinforcement Learning}
-\label{sec-rl-appendix}
-
-Model Predictive Path Integral (MPPI) control
-\cite{panSample2015}
-\cite{williamsModel2017}
-\todo{what is correct citation for MPPI?}
-
-% \cref{alg-mbrl} shows the typical model-based RL loop.
-\begin{align} \label{eq-fast-update-mpc}
-  \policy_{i+1}^{\text{PS}}(\state) = \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
-\E \bigg[ \sum_{t=0}^{H-1} \gamma^{t} r(\state_{t},\action_{t}) \mid \state_{0}=\state  \bigg] + Q_{\theta}(\state_{\Horizon}, \action_{H})
-\quad \text{s.t. } \state_{t+1} &= \hat{\transitionFn}(\state_{t}, \action_{t}) + \noise_{t}
+\section{Model-based Reinforcement Learning with Fast Updates}
+
+\subsection{Problem Statement and Background} \label{sec:problem-statement}
+We consider environments with states \(\state \in \stateDomain \), actions \(\action \in \actionDomain\) and transition dynamics \(\transitionFn: \stateDomain \times \actionDomain \rightarrow \stateDomain \) subject to
+iid noise \(\noise_{t}\), given by,
+\begin{align}
+\state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t}.
 \end{align}
-with $\hat{\transitionFn} \sim p(\transitionFn \mid \dataset)$
-
-We use deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016} to learn an action value function $Q_{\theta}$.
-Note that we also learn a policy but its sole purpose is for learning the value function.
-
-\subsection{Experiment Configuration}
-This section details how we configured and ran our reinforcement learning experiments.
-
-\textbf{Dynamic model}
-In all experiments we used an MLP dynamic model with a single hidden layer of width 64 and TanH activation functions.
-At each episode we used Adam \cite{adam} to optimise the NN parameters for $5000$ iterations with a learning rate of $0.001$.
-We reset the optimizer after each episode.
-As we are performing regression we instantiate the loss function in \cref{eq-empirical-risk} as the well-known mean squared error.
-This corresponds to a Gaussian likelihood with unit variance.
-We then set the prior precision as $\delta=0.0001$.
-% It is worth noting that $\delta$ effects both the neur
-In all experiments our sparse function-space representation uses $m=128$ inducing points and this seemed to be sufficient.
-
-\textbf{Model predictive path integral (MPPI)}
-MPPI is an online planning algorithim which iteratively improves the action trajectory $\action_{t:t+H}$ using samples.
-At each iteration $j$, $N=256$ trajectories are sampled according to the currect action trajectory $\action^{j}_{t:t+H}$.
-The $K=32$ top trajectories with highest returns $\sum_{h=0}^{H} = r(\state^{j}_{t+h}, \action^{j}_{t+h})$ are selected.
-The next action trajectory $\action^{j+1}_{t:t+H}$ is then computed by taking the weighted average of the top $K=32$ trajectories
-with weights from the softmax over returns from top $K=32$ trajectories.
-
-$\gamma 0.9$
-$\tau=0.005$
-horizon $H=5$
-temperature $0.5$
-momentum $0.1$
-
-\textbf{Initial data set}
-We collect an initial data set using a random policy for one episode.
-
-\textbf{DDPG}
-action value function is an MLP with a single hidden layer of width $128$ with ELU activation functions.
-We train the DDPG agent using Adam for $500$ iterations at each episode, using a learning rate $0.0001$.
+\begin{assumption}
+  (system properties) The environment's dynamics are $L_{\transitionFn}\text{-Lipschitz}$ continuous and the transition noise $\noise_{t}$ is $\sigma\text{-sub-Gaussian}$ for all $t \geq 0$.
+\end{assumption}
+
+\section{Extending the CL regularizer to multi-class settings}
+
+\begin{align}
+ 	\bar{\MB}^{-1}_s &= \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{C \times m \times m}\\
+ 	& \Kzz \in \R^{C \times m \times m} 
+ \end{align}
+
+\begin{equation}
+	\mathcal{R_\textit{SFR}}(\mathbf{w}) = \sum_{s=1}^{t-1}\left[\left(f_{\vw}(\MZ_{s}) - f_{\vw_{s}}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\vw}(\MZ_{s}) - f_{\vw_{s}}(\MZ_s) \right) \right] \in \R
+\end{equation}
 

### 2023-05-14 paper/main.tex
updated intro to experiments

--- 2023-05-14 paper/main.tex
@@
 Our experiments seek to answer the following questions:
-\begin{itemize}
-  \item Does NN2SFR caputure good uncertainty estimates
-\end{itemize}
+\begin{enumerate}
+  \item \textbf{Predictions} How do predictions with our sparse function-space approximation compare to weight-space approximations?
+Does our method's ability to consider the full data set offer benefits over subset function-space methods?
+  % \item Does our method's ability to consider the full data set offer benefits over subset function-space methods?
+  \item \textbf{Function-space updates} How faster are our function-space updates relative to retraining from scratch?
+Do they improve predictive performance?
+Are they as good as retraining from scratch?
+  \item \textbf{Uncertainty} How good are our uncertainty estimates? Can they be used in downstream settings like RL?
+  \item \textbf{Representation} Is our sparse function-space representation useful for continual learning?
+\end{enumerate}
 

### 2023-05-14 paper/main.tex
rewrite 2.1 first draft done

@@
 %
-Quantifying uncertainty in a Bayesian framework boils down to finding a posterior of $p(\vw \mid \dataset)$, which represents the uncertainty over our parameters based on the prior and the data.
-The posterior structure is related to the loss-landscape around the MAP weights $\vw^*$, which induces a correlation structure on functions produced from the neural network's deterministic mapping.
-Samples from the weight posterior are perturbed versions of $f_{\vw^*}$ characterizing uncertainty in the learned model in the function space.
-Although the true posterior is intractable given the non-linearities of the neural network, sampling techniques available, such as Hamiltonian Monte-Carlo (HMC), in most cases, are not available given the computational burden.
- The uncertainty plotted \cref{fig:banana} shows the induced function space posterior by sampling through the model.
+
+Quantifying uncertainty in a Bayesian framework means finding a posterior of $p(\vw \mid \dataset)$.
+The posterior represents the uncertainty over our parameters based on the prior and the data.
+The posterior structure directly relates to the optimization loss around the MAP weights $\vw^*$.
+Furthermore, the landscape in the weight space induces functions produced by the neural network's deterministic mapping.
+If one was to sample from the weight posterior, the corresponding functions created can be viewed as perturbed versions of the $f_{\vw^*}$.
+In most applications, we care about predictions from the neural network, so the distribution in the function space not in the weight space.
+
+Although the true posterior is intractable given the non-linearities of the neural network sampling techniques are available such as Hamiltonian Monte-Carlo (HMC), The uncertainty plotted \cref{fig:banana} shows the induced function space posterior by sampling through the model.
+However, in most cases, sampling techniques like HMC are not available, given the computational burden.
 
 A common approach is to approximate the correlation structure of a distribution centred at the MAP estimate as done in the Laplace-GGN \citep{khan2019approximate, daxberger2021laplace, maddox2021fast}.
-The Laplace GGN takes the MAP solution and approximates the Hessian of our loss function  $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i)$ with the GGN approximation.
-Another way of viewing the approximation is that we build the following approximate model $\hat{f}_\weights(\mathbf{x}_{i}) = \Jac{\weights}{\mathbf{x}_i} \vw $  where $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$ is the Jacobian as was pointed out in \citep{khan2019approximate}.
+The Laplace GGN takes the MAP solution and approximates the Hessian of the loss function  $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i)$ with the GGN approximation.
+Another way of viewing the approximation is that we build the following approximate model $\hat{f}_\weights(\mathbf{x}_{i}) = \Jac{\weights_*}{\mathbf{x}_i} \vw_i $  where $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$ is the Jacobian as was pointed out in \citep{khan2019approximate}.
 Using the Hessian of the approximate model, we arrive at the Laplace-GGN posterior for $q(\vw)$.
+As pointed out in \citet{khan2019approximate}, a Gaussian posterior covariance approximation in the weight space implies a covariance structure in the function space.
 
 In this paper we are concerned with learning posterior directly in the function space that is having a $q(\vf)$ instead of a $q(\vw)$.
-A common choice is to use a Gaussian process characterizes a distribution over functions in terms of the first two moments, a mean $\mu(\cdot)$ and covariance function $\kappa(\cdot,\cdot)$ (kernel).
+We choose is to use a Gaussian process an extension of the multivariate normal that characterizes a distribution over functions in terms of the first two moments, a mean $\mu(\cdot)$ and covariance function $\kappa(\cdot,\cdot)$ (kernel).
 We aim to find a kernel and mean function based on the neural network to build the Gaussian process posterior.
@@
 \begin{equation} \label{eq:weight_func}
-g_\weights(\mathbf{x}_{i}) = \phi^\top\!(\vx) \, \vw \implies \mu(\vx) = \vzeros \quad \kappa(\mathbf{x}, \mathbf{x}') = \frac{1}{\delta} \phi(\vx)^\top \phi(\vx)
+g_\weights(\mathbf{x}_{i}) = \phi^\top\!(\vx) \, \vw \implies \mu(\vx) = 0 \quad \kappa(\mathbf{x}, \mathbf{x}') = \frac{1}{\delta} \phi(\vx)^\top \phi(\vx)
 \end{equation}
 
-- distribution over w given to you by the non-linear function.
-One could sample over weights pass it over the function and you have distribution over functions.
-HMC is heavy, structure of the problem around the map estimate.
-characteruze this as the first two moments of the distributions over the functions restrict to the first two moments.
-
-Replace with a taylor series at the MAP first order taylor expansion in w. degenerate cov function.
-
-- more citations there.
-
-- GP induced by the trained neural network. not GP prior.
-
-- Add the NTK bit back in.
-
-- assume that when you are at the map estimate when you have converged this should be small.
-
-- Write out that w beomces zero under the expectation.
-
--  transition from background to methods.
-
-- More explination of the dual equation 5 the loss landscape link. Perbutation point linked directly to that here.
-
--
-
-%A Gaussian process characterizes a distribution over functions in terms of the first two moments.
-The key quantity of a Gaussian process is the prior covariance function (or kernel function) $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors in $\R^{\mathrm{D}}$.
-We aim to find a kernel based on the neural network to build the Gaussian process posterior.
-A linear function in terms of parameters can easily be converted from the weight space to the function space as follows:
-%\begin{equation}
-%g_\weights(\mathbf{x}_{i})) = \phi(\vx)^\top \vw \implies \mu(\vx) = \vzeros \quad \kappa(\mathbf{x}, \mathbf{x}') = \frac{1}{\delta} \phi(\vx)^\top \phi(\vx)
-%\end{equation}
-%
-%
-%
-% The approximation can be seen as taking the map solution of \cref{eq-empirical-risk} as the mean of $q(\vw)$ but then substituting the following functional approximation for $\hat{f}_\weights(\mathbf{x}_{i}) = \Jac{\weights^*}{\mathbf{x}} $
-
-%A Gaussian procss characterizes a distribution over functions in terms of the first two moments. The key quantity of 
-%A Gaussian process is the prior covariance function (or kernel function) $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors in $\R^{\mathrm{D}}$.
-We aim to find a kernel based on the neural network to build the Gaussian process posterior.
-%A GP is fully characterized by a mean $\mu(\cdot)$ and covariance function $\kappa(\cdot,\cdot)$ (kernel).
-%If we had the following function parameterization $g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx') = \delta^{-1} \phi(\vx) \phi^\T(\vx')$ (see Ch.~XXX in \cite{rasmussen2006gaussian} for details).\todo{this part needs to be rewritten, starts talking about a general function parameterisation and then jumps directly to the neural network}
-%\subsection{Neural Network to GP Prior} 
-%\label{sec:nn2gp}
-%
-A Gaussian process characterizes a distribution over functions in terms of the first two moments, a mean $\mu(\cdot)$ and covariance function $\kappa(\cdot,\cdot)$ (kernel).
-We aim to find a kernel and mean function based on the neural network to build the Gaussian process posterior.
-A linear function in terms of parameters can be converted from the weight space to the function space (see Ch.~XXX in \cite{rasmussen2006gaussian} as follows:
-\begin{equation} \label{eq:weight_func}
-g_\weights(\mathbf{x}) = \phi^\top\!(\vx) \, \vw \implies \mu(\vx) = \vzeros \quad \kappa(\mathbf{x}, \mathbf{x}') = \frac{1}{\delta} \phi(\vx)^\top \phi(\vx)
-\end{equation}
-Given an approximate posterior $q(\vw)$, \citet{immerImprovingPredictionsBayesian2021} proposed to make the following linear approximation
-$f^{\textrm{lin.}}_{\vw^*}(\vx; \vw) = f_{\vw^*}(\vx) + \Jac{\weights^*}{\mathbf{x}} \, (\vw - \vw^*)$ of the neural network, where $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$ is the Jacobian.
-The approximation can be used with any approximate inference technique but in the paper they focus on the Laplace-GGN.
-They find that the linear approximation helps to improve predictions by correcting the approximate posterior when sampled through a non-Gaussian likelihoods.
-
-Furthermore, under the linear approximation they showed one can convert the weight space prior to the function space by combining with \cref{eq:weight_func} meaning the converged neural network GP prior is:
+We can therefore use the approximate linear model defined by the GGN approximation to define our GP derived from the trained neural network,
 \begin{equation} \label{eq-laplace-approx-function-space}
 % g(\vx) \sim \GP \left( \mu(\vx), \kappa(\vx, \vx') \right) \quad \text{with} \quad
-  \mu(\vx) =  f^{\textrm{lin.}}_{\vw_*}(\vx; \vw = \vzeros) = f_{\vw^*}(\vx) - \Jac{\weights^*}{\mathbf{x}} \vw^* \quad \text{and} \quad
+  \mu(\vx) =  0 \quad \text{and} \quad
   \kappa(\mathbf{x}, \mathbf{x}')
@@
 \end{equation}
-%
-%where the kernel is the so-called Neural Tangent Kernel (NTK, \cite{jacot2018neural}) with Jacobian $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$.
-Alternatively, we could have followed the derivation by \citet{immerImprovingPredictionsBayesian2021}, where they perform a local linearization of the neural network  $f^{\textrm{lin.}}_{\vw^*}(\vx; \vw) = f_{\vw^*}(\vx) + \Jac{\weights^*}{\mathbf{x}} \, (\vw - \vw^*)$.
-Their mean function differ from ours, \cref{eq-laplace-approx-function-space}, as theirs comes from setting  $\mu(\vx) = f^{\textrm{lin.}}_{\vw_*}(\vx; \vw = \vzeros) = f_{\vw^*}(\vx) - \Jac{\weights^*}{\mathbf{x}} \vw^*$, \ie the difference between the linear model approximation and the neural network function at $\vx$.
-%which does not seem useful as a prior mean function,
-%On the other hand, we set $\mu(\vx) = \vzeros$, as common in GP literature and derived from a feature map conversion. \todo{derived what?}
+where the kernel is the so-called Neural Tangent Kernel (NTK, \cite{jacot2018neural}), given we have a kernel function, we can then combine it with the $\dataset$ to form the posterior.
+In \citep{khan2019approximate} they took a similar approach but instead of fitting the GP posterior to the actual data they adjusted the data to be pseudo data.
+Similarly, using a first order approximation of the neural network function to form a GLM model \citet{immerImprovingPredictionsBayesian2021} also arrives at the same NTK function for the GP derived from the neural network, however a different mean function.
+Both previous approaches have attempted to adjust the GP posterior mean function to ensure the predictions are from the neural network $f_{\vw^*}(\vx)$.
+In our method, we wish to make predictions from the derived GP and thus do not make such adjustments.
+We now present the general formulation of the functional representation of our trained neural network
 
@@
 \beta_i \coloneqq - \myexpect_{p(\vw \mid \vy)}[\nabla^2_{f_i f_i}\log p(y_i \mid f_i)] ,
-\end{equation}
+\end{equation}\todo{ More explination of the dual equation 6 the loss landscape link. Perbutation point linked directly to that here. }
 %

### 2023-05-14 paper/main.tex

--- 2023-05-14 paper/main.tex
@@
 
-\subsection{Continual learning}
+\subsection{Continual Learning}
+In Continal Learning,
+
+\begin{equation}
+ 	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{m \times m}, \quad \forall s \in [1, t-1]
+ \end{equation}
+
+\begin{equation}
+	\mathcal{R_\textit{SFR}}(\mathbf{w}) = \sum_{s=1}^{t-1}\left[\left(f_{\vw}(\MZ_{s}) - f_{\vw_{s}}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\vw}(\MZ_{s}) - f_{\vw_{s}}(\MZ_s) \right) \right]
+\end{equation} 
+with $f_\vw(\MZ_{s}), f_{\vw_s}(\MZ_s) \in \R^m$ are vectors of the outputs of the neural
 
@@
 Our experiments seek to answer the following questions:
-\begin{enumerate}
-  \item \textbf{Predictions} How do predictions with our sparse function-space approximation compare to weight-space approximations?
-Does our method's ability to consider the full data set offer benefits over subset function-space methods?
-  % \item Does our method's ability to consider the full data set offer benefits over subset function-space methods?
-  \item \textbf{Function-space updates} How faster are our function-space updates relative to retraining from scratch?
-Do they improve predictive performance?
-Are they as good as retraining from scratch?
-  \item \textbf{Uncertainty} How good are our uncertainty estimates? Can they be used in downstream settings like RL?
-  \item \textbf{Representation} Is our sparse function-space representation useful for continual learning?
-\end{enumerate}
+\begin{itemize}
+  \item Does NN2SFR caputure good uncertainty estimates
+  \item Can NN2SFR be used to build a summary of the current neural network to mitigate catastrophic forgetting over previous tasks?
+\end{itemize}
 
@@
 \end{align}
+
 with $\hat{\transitionFn} \sim p(\transitionFn \mid \dataset)$
@@
 We train the DDPG agent using Adam for $500$ iterations at each episode, using a learning rate $0.0001$.
+
+\section{Extending the CL regularizer to multi-class settings}
+\begin{equation}
+	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{C \times m \times m} \quad \MKzz \in \R^{C \times m \times m} 
+\end{equation}
+
+\begin{equation}
+	\mathcal{R_\textit{SFR}}(\mathbf{w}) = \sum_{s=1}^{t-1}	\sum_{k \in 	C}\left[\left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s}, k}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s, k}}(\MZ_s) \right) \right]
+\end{equation}
 

### 2023-05-14 paper/main.tex
update paper

--- 2023-05-14 paper/main.tex
@@
 
-The Hessian can be efficiently approximated using the generalised Gauss-Newton algorithm \cite{botev2017practical} or by Kronecker factorisation \cite{martens2015optimizing,ritter2018kfac}.
+The Hessian can be efficiently approximated using the generalised Gauss-Newton approximation \cite{botev2017practical} or by Kronecker factorisation \cite{martens2015optimizing,ritter2018kfac}.
 
@@
   \weights^{*} = 
-  \arg \min_{\weights} \mathcal{L}(\dataset,\weights) =
-  \arg \min_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
+  \argmin_{\weights} \mathcal{L}(\dataset,\weights) =
+  \argmin_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
 \end{equation}
@@
 If one was to sample from the weight posterior, the corresponding functions created can be viewed as perturbed versions of the $f_{\vw^*}$.
-In most applications, we care about predictions from the neural network, so the distribution in the function space not in the weight space.
-
-Although the true posterior is intractable given the non-linearities of the neural network sampling techniques are available such as Hamiltonian Monte-Carlo (HMC), The uncertainty plotted \cref{fig:banana} shows the induced function space posterior by sampling through the model.
-However, in most cases, sampling techniques like HMC are not available, given the computational burden.
+In most applications, we care about predictions from the neural network, so the distribution is in the function space and not in the weight space.
+
+Although the true posterior is intractable given the non-linearities of the neural network, one can restore to sampling techniques such as Hamiltonian Monte-Carlo (HMC).
+However, even in this case, the high computational costs make them impractical.
+In \cref{fig:banana}, we show a qualitative example of the induced function space posterior obtained with our method compared to the posterior obtained through HMC sampling on the Banana toy dataset.
+\todo{make it more straightforward that we are computationally cheaper?}
 
 A common approach is to approximate the correlation structure of a distribution centred at the MAP estimate as done in the Laplace-GGN \citep{khan2019approximate, daxberger2021laplace, maddox2021fast}.
-The Laplace GGN takes the MAP solution and approximates the Hessian of the loss function  $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i)$ with the GGN approximation.
-Another way of viewing the approximation is that we build the following approximate model $\hat{f}_\weights(\mathbf{x}_{i}) = \Jac{\weights_*}{\mathbf{x}_i} \vw_i $  where $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$ is the Jacobian as was pointed out in \citep{khan2019approximate}.
+The Laplace-GGN takes the MAP solution and approximates the Hessian of the loss function
+% $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i)$ 
+with the Generalized Gaussian-Newton approximation (GGN). 
+Following the work of \citep{khan2019approximate}, we can view this approximation as building an approximate linear model of the neural network as $\hat{f}_\weights(\mathbf{x}) = \Jac{\weights_*}{\mathbf{x}} \, \weights$, where $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$ is the Jacobian at the MAP.
 Using the Hessian of the approximate model, we arrive at the Laplace-GGN posterior for $q(\vw)$.
 As pointed out in \citet{khan2019approximate}, a Gaussian posterior covariance approximation in the weight space implies a covariance structure in the function space.
-
-In this paper we are concerned with learning posterior directly in the function space that is having a $q(\vf)$ instead of a $q(\vw)$.
-We choose is to use a Gaussian process an extension of the multivariate normal that characterizes a distribution over functions in terms of the first two moments, a mean $\mu(\cdot)$ and covariance function $\kappa(\cdot,\cdot)$ (kernel).
-We aim to find a kernel and mean function based on the neural network to build the Gaussian process posterior.
-A linear function in terms of parameters can be converted from the weight space to the function space (see Ch.~XXX in \cite{rasmussen2006gaussian} as follows:
+\todo{the last two sentences are not linked to the previous ones}
+
+In this paper, we are concerned with learning the posterior $q(\vf)$ directly in the function space, instead of $q(\vw)$.
+We choose to use a Gaussian process, an extension of the multivariate normal that characterizes a distribution over functions in terms of the first two moments, a mean $\mu(\cdot)$ and covariance  (or kernel) function $\kappa(\cdot,\cdot)$.
+We aim to these two functions based on the neural network to then build the Gaussian process posterior.
+A function linear with respect to its parameters can be converted from the weight space to the function space (see Ch.~XXX in \cite{rasmussen2006gaussian} as follows: \todo{this part needs to be improved the linear function pops out of nowhere}
 \begin{equation} \label{eq:weight_func}
@@
 
-We can therefore use the approximate linear model defined by the GGN approximation to define our GP derived from the trained neural network,
-\begin{equation} \label{eq-laplace-approx-function-space}
+Therefore, we can use the approximate linear model defined by the Laplace-GGN approximation to define our GP derived from the trained neural network,
+\begin{equation} 
+\label{eq-laplace-approx-function-space}
 % g(\vx) \sim \GP \left( \mu(\vx), \kappa(\vx, \vx') \right) \quad \text{with} \quad
@@
 \end{equation}
-where the kernel is the so-called Neural Tangent Kernel (NTK, \cite{jacot2018neural}), given we have a kernel function, we can then combine it with the $\dataset$ to form the posterior.
-In \citep{khan2019approximate} they took a similar approach but instead of fitting the GP posterior to the actual data they adjusted the data to be pseudo data.
-Similarly, using a first order approximation of the neural network function to form a GLM model \citet{immerImprovingPredictionsBayesian2021} also arrives at the same NTK function for the GP derived from the neural network, however a different mean function.
-Both previous approaches have attempted to adjust the GP posterior mean function to ensure the predictions are from the neural network $f_{\vw^*}(\vx)$.
-In our method, we wish to make predictions from the derived GP and thus do not make such adjustments.
-We now present the general formulation of the functional representation of our trained neural network
+where the kernel is the so-called Neural Tangent Kernel (NTK, \cite{jacot2018neural}).
+With this kernel function, we can then combine it with the dataset $\dataset$ to form the posterior $q(\vf)$.
+\citet{khan2019approximate} took a similar approach, but instead of fitting the GP posterior to the actual data, they adjusted the data to be pseudo-data.\todo{The reader may wonder what is pseudo-data then} Similarly, \citet{immerImprovingPredictionsBayesian2021} obtain the same covariance function but a different mean because they rely on a first order approximation of the neural network to form a Bayesian GLM model.
+Both approaches attempted to adjust the GP posterior mean function to ensure the predictions are from the neural network $f_{\vw^*}(\vx)$.
+In our method, we wish to make predictions from the derived GP and thus we avoid such adjustments.
+We now present the general formulation of the functional representation of our trained neural network.
+\todo{this sentence can be avoided probably}
 
@@
 
-\subsection{Continual learning}
+\subsection{Continual Learning}
+% Definition of CL -> a sequence of tasks
+
+\begin{equation}
+ 	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{m \times m}, \quad \forall s \in [1, t-1]
+ \end{equation}
+
+\begin{equation}
+	\mathcal{R}_\textit{SFR}(\weights) = \sum_{s=1}^{t-1} \frac{1}{m} \left[\left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right) \right]
+\end{equation} 
+with $f_\vw(\MZ_{s}), f_{\vw_s}(\MZ_s) \in \R^m$ are vectors of the outputs of the neural networks with the current weights $\vw$ and stored function outputs of the neural network at the MAP optimum for task $s$.
+
+%\begin{equation}
+%	\argmin_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights) + \tau \mathcal{R}_\textit{SFR}(\weights)
+%\end{equation}
+
+\begin{equation}
+	\weights_t^* = \argmin_{\weights} \mathcal{L}(\mathcal{D}_t, \weights) + \tau \mathcal{R}_\textit{SFR}(\weights)
+\end{equation}
 

### 2023-05-14 paper/main.tex
rewrite 2.1 first draft done

@@
 
-Although the true posterior is intractable given the non-linearities of the neural network, one can restore to sampling techniques such as Hamiltonian Monte-Carlo (HMC).
-However, even in this case, the high computational costs make them impractical.
+Although the true posterior is intractable given the non-linearities of the neural network, one can resort to sampling techniques such as Hamiltonian Monte-Carlo (HMC).
+However, even in this case, the high computational costs make them impractical meaning for most applications we need approximate inference techniques.
 In \cref{fig:banana}, we show a qualitative example of the induced function space posterior obtained with our method compared to the posterior obtained through HMC sampling on the Banana toy dataset.
@@
 Using the Hessian of the approximate model, we arrive at the Laplace-GGN posterior for $q(\vw)$.
-As pointed out in \citet{khan2019approximate}, a Gaussian posterior covariance approximation in the weight space implies a covariance structure in the function space.
-\todo{the last two sentences are not linked to the previous ones}
 
@@
 We choose to use a Gaussian process, an extension of the multivariate normal that characterizes a distribution over functions in terms of the first two moments, a mean $\mu(\cdot)$ and covariance  (or kernel) function $\kappa(\cdot,\cdot)$.
-We aim to these two functions based on the neural network to then build the Gaussian process posterior.
-A function linear with respect to its parameters can be converted from the weight space to the function space (see Ch.~XXX in \cite{rasmussen2006gaussian} as follows: \todo{this part needs to be improved the linear function pops out of nowhere}
+We aim to derive these two functions based on the neural network to then build the Gaussian process posterior.
+Gaussian distributions remain tractable under learn transformations.
+Therefore, a linear function with respect to its parameters can be converted from the weight space to the function space (see Ch.~XXX in \cite{rasmussen2006gaussian} as follows: \todo{this part needs to be improved the linear function pops out of nowhere}
 \begin{equation} \label{eq:weight_func}
@@
 
-Therefore, we can use the approximate linear model defined by the Laplace-GGN approximation to define our GP derived from the trained neural network,
+Therefore, the GGN approximate linear model can be used to convert our weight space model to the function space by,
 \begin{equation} 

### 2023-05-14 paper/main.tex
rewrite 2.1 first draft done

@@
 with the Generalized Gaussian-Newton approximation (GGN). 
-Following the work of \citep{khan2019approximate}, we can view this approximation as building an approximate linear model of the neural network as $\hat{f}_\weights(\mathbf{x}) = \Jac{\weights_*}{\mathbf{x}} \, \weights$, where $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$ is the Jacobian at the MAP.
+Following the work of \citep{khan2019approximate}, we can view this approximation as building an approximate linear model of the neural network as $\hat{f}_\weights(\mathbf{x}_i) = \Jac{\weights_*}{\mathbf{x}_i} \, \weights$, where $\Jac{\weights}{\mathbf{x}_i} \coloneqq \nabla_\weights f(\mathbf{x}_i)^\top \in \R^{C \times P}$ is the Jacobian at the MAP.
 Using the Hessian of the approximate model, we arrive at the Laplace-GGN posterior for $q(\vw)$.
 
-In this paper, we are concerned with learning the posterior $q(\vf)$ directly in the function space, instead of $q(\vw)$.
-We choose to use a Gaussian process, an extension of the multivariate normal that characterizes a distribution over functions in terms of the first two moments, a mean $\mu(\cdot)$ and covariance  (or kernel) function $\kappa(\cdot,\cdot)$.
-We aim to derive these two functions based on the neural network to then build the Gaussian process posterior.
-Gaussian distributions remain tractable under learn transformations.
-Therefore, a linear function with respect to its parameters can be converted from the weight space to the function space (see Ch.~XXX in \cite{rasmussen2006gaussian} as follows: \todo{this part needs to be improved the linear function pops out of nowhere}
-\begin{equation} \label{eq:weight_func}
-g_\weights(\mathbf{x}_{i}) = \phi^\top\!(\vx) \, \vw \implies \mu(\vx) = 0 \quad \kappa(\mathbf{x}, \mathbf{x}') = \frac{1}{\delta} \phi(\vx)^\top \phi(\vx)
+Recent work \citep{khan2019approximate,maddox2021fast} shows that linearizing approximations in the weight space lead to function space equivalent approximations.
+As our goal is to build a sparse functional representation of a neural network, a starting point is the non-sparse  $q(\vf)$ function space posterior approximation.
+We choose to use a Gaussian process, as is typical, an extension of the multivariate normal that characterizes a distribution over functions in terms of the first two moments, a mean $\mu(\cdot)$ and covariance  (or kernel) function $\kappa(\cdot,\cdot)$.
+Thus, we need these two functions based on the neural network to build the Gaussian process posterior.
+Gaussian distributions remain tractable under linear transformations.
+Therefore, a linear function in terms of parameters can be converted from the weight space to the function space (see Ch.~2.1 in \cite{rasmussen2006gaussian}) as follows:\begin{equation} \label{eq:weight_func}
+g_\weights(\mathbf{x}_{i}) = \phi^\top\!(\vx_i) \, \vw \implies \mu(\vx_i) = 0 \quad \kappa(\mathbf{x}_i, \mathbf{x}_i') = \frac{1}{\delta} \phi(\vx_i)^\top \phi(\vx_i)
 \end{equation}

### 2023-05-14 paper/main.tex
rewrite 2.1 first draft done

@@
 
-Although the true posterior is intractable given the non-linearities of the neural network, one can resort to sampling techniques such as Hamiltonian Monte-Carlo (HMC).
+Although the true posterior $p(\vw \mid \dataset)$ is intractable given the non-linearities of the neural network, one can resort to sampling techniques such as Hamiltonian Monte-Carlo (HMC).
 However, even in this case, the high computational costs make them impractical meaning for most applications we need approximate inference techniques.
 In \cref{fig:banana}, we show a qualitative example of the induced function space posterior obtained with our method compared to the posterior obtained through HMC sampling on the Banana toy dataset.
-\todo{make it more straightforward that we are computationally cheaper?}
+\todo{make it more straightforward that we are computationally cheaper?
+A: Not sure we are reallying trying to sell our method here}
 
@@
 With this kernel function, we can then combine it with the dataset $\dataset$ to form the posterior $q(\vf)$.
-\citet{khan2019approximate} took a similar approach, but instead of fitting the GP posterior to the actual data, they adjusted the data to be pseudo-data.\todo{The reader may wonder what is pseudo-data then} Similarly, \citet{immerImprovingPredictionsBayesian2021} obtain the same covariance function but a different mean because they rely on a first order approximation of the neural network to form a Bayesian GLM model.
+\citet{khan2019approximate} took a similar approach, but instead of fitting the GP posterior to the actual $\vy$, but a transformation of $\vy$ which they refer to as pseudo-data.\todo{The reader may wonder what is pseudo-data then A: Is this better?} Similarly, \citet{immerImprovingPredictionsBayesian2021} obtain the same covariance function but a different mean because they rely on a first order approximation of the neural network to form a Bayesian GLM model.
 Both approaches attempted to adjust the GP posterior mean function to ensure the predictions are from the neural network $f_{\vw^*}(\vx)$.
 In our method, we wish to make predictions from the derived GP and thus we avoid such adjustments.
-We now present the general formulation of the functional representation of our trained neural network.
-\todo{this sentence can be avoided probably}
+We now present the general formulation of the sparse functional representation of our trained neural network based on the non-sparse approximation.
+\todo{this sentence can be avoided probably, A: its what Aidan calls setting the scene}
 

### 2023-05-14 paper/main.tex
added ntk stuff to discussion

--- 2023-05-14 paper/main.tex
@@
 
+It is worth noting that the NTK linearises the network around the MAP solution $\weights^{*}$,
+so the function space prior (and thus posterior) is only a locally linear approximation.
+In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
+It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.
+
 A reference implementation of the methods presented in this paper is currently available as supplementary material and will be made available under the MIT License on GitHub upon acceptance.

### 2023-05-14 paper/main.tex
typo
removed state from policy
add missing i
remove un needed i
added rasmussen chap

@@
 with the Generalized Gaussian-Newton approximation (GGN). 
-Following the work of \citep{khan2019approximate}, we can view this approximation as building an approximate linear model of the neural network as $\hat{f}_\weights(\mathbf{x}) = \Jac{\weights_*}{\mathbf{x}} \, \weights$, where $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$ is the Jacobian at the MAP.
+Following the work of \citep{khan2019approximate}, we can view this approximation as building an approximate linear model of the neural network as $\hat{f}_\weights(\mathbf{x}) = \Jac{\weights_*}{\mathbf{x}} \, \weights$, where $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f_{\weights}(\mathbf{x})^\top \in \R^{C \times P}$ is the Jacobian at the MAP.
 Using the Hessian of the approximate model, we arrive at the Laplace-GGN posterior for $q(\vw)$.
@@
 Gaussian distributions remain tractable under learn transformations.
-Therefore, a linear function with respect to its parameters can be converted from the weight space to the function space (see Ch.~XXX in \cite{rasmussen2006gaussian} as follows: \todo{this part needs to be improved the linear function pops out of nowhere}
+Therefore, a linear function with respect to its parameters can be converted from the weight space to the function space (see Ch.~2.1 in \cite{rasmussen2006gaussian}) as follows: \todo{this part needs to be improved the linear function pops out of nowhere}
 \begin{equation} \label{eq:weight_func}
-g_\weights(\mathbf{x}_{i}) = \phi^\top\!(\vx) \, \vw \implies \mu(\vx) = 0 \quad \kappa(\mathbf{x}, \mathbf{x}') = \frac{1}{\delta} \phi(\vx)^\top \phi(\vx)
+g_\weights(\mathbf{x}) = \phi^\top\!(\vx) \, \vw \implies \mu(\vx) = 0 \quad \kappa(\mathbf{x}, \mathbf{x}') = \frac{1}{\delta} \phi(\vx)^\top \phi(\vx)
 \end{equation}
@@
  \myexpect_{p(f_i \mid\vy)}[f_i] = \vk_{\vx i}^\top \valpha \quad \text{and} \quad
-\mathrm{Var}_{p(f\mid\vy)}[f_i] = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
+\mathrm{Var}_{p(f_{i}\mid\vy)}[f_i] = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
 \end{equation}
@@
 \begin{align} \label{eq-greedy}
-  \policy^{\text{Greedy}}(\state) &= \arg \max_{\pi \in \Pi} J(f_{\mathbf{w}^{*}}, \pi).
+  \policy^{\text{Greedy}} &= \arg \max_{\pi \in \Pi} J(f_{\mathbf{w}^{*}}, \pi).
 \end{align}
@@
 \begin{align} \label{eq-posterior-sampling}
-  \policy^{\text{PS}}(\state) &= \arg \max_{\pi \in \Pi} J(\hat{f}, \pi)
+  \policy^{\text{PS}} &= \arg \max_{\pi \in \Pi} J(\hat{f}, \pi)
 \quad \text{s.t. } \tilde{\transitionFn} \sim q_{\mathbf{u}}(\hat{\transitionFn} \mid \dataset),
@@
   % \item Does our method's ability to consider the full data set offer benefits over subset function-space methods?
-  \item \textbf{Function-space updates} How faster are our function-space updates relative to retraining from scratch?
+  \item \textbf{Function-space updates} How fast are our function-space updates relative to retraining from scratch?
 Do they improve predictive performance?

### 2023-05-14 paper/main.tex
added intro to section 2

--- 2023-05-14 paper/main.tex
@@
 \label{sec:methods}
-%
+
+In this section, we recap how a function-space posterior -- a GP posterior -- can be obtained
+by linearising a neural network around the Maximum a Posteriori (MAP) weights.
+
 In supervised learning, given a data set $\dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with input $\mathbf{x}_i \in \inputDomain$ and output $\mathbf{y}_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w} : \inputDomain \to \outputDomain$, are usually trained to minimize the (regularized) empirical risk,
@@
 \label{sec:conclusion}
+
+It is worth noting that the NTK linearises the network around the MAP solution $\weights^{*}$,
+so the function space prior (and thus posterior) is only a locally linear approximation.
+In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
+It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.
 

### 2023-05-14 paper/main.tex
updatedd
update section intro

@@
 
-In this section, we recap how a function-space posterior -- a GP posterior -- can be obtained
-by linearising a neural network around the Maximum a Posteriori (MAP) weights.
+In this section, we recap how a trained neural network (NN) can be converted to a Gaussian process by locally linearising
+its weights.
+% a GP posterior -- can be obtained
+% around the Maximum a Posteriori (MAP) weights.
+
+% by linearising a neural network around the Maximum a Posteriori (MAP) weights.
+% a GP posterior -- can be obtained
 

### 2023-05-14 paper/main.tex
re ordered a few things and reworded a few things

@@
 %
-\subsection{Linearization gives rise to a Gaussian process} 
-\label{sec:nn2gp}
-%
-
-Quantifying uncertainty in a Bayesian framework means finding a posterior of $p(\vw \mid \dataset)$.
-The posterior represents the uncertainty over our parameters based on the prior and the data.
-The posterior structure directly relates to the optimization loss around the MAP weights $\vw^*$.
-Furthermore, the landscape in the weight space induces functions produced by the neural network's deterministic mapping.
-If one was to sample from the weight posterior, the corresponding functions created can be viewed as perturbed versions of the $f_{\vw^*}$.
-In most applications, we care about predictions from the neural network, so the distribution is in the function space and not in the weight space.
-
+% \subsection{Linearization gives rise to a Gaussian process}
+% \label{sec:nn2gp}
+%
+
+\textbf{Uncertainty quantification}
+Bayesian inference offers a principled approach to quantifying uncertainty in neural networks.
+The goal is to find the posterior over the weights ${p(\vw \mid \vy) \propto p(\vy \mid f_{\weights}(\vx)) p(\weights)}$ as
+it represents our belief in the parameters after combining data $\dataset$ with our prior $p(\vw)$.
 Although the true posterior $p(\vw \mid \dataset)$ is intractable given the non-linearities of the neural network, one can resort to sampling techniques such as Hamiltonian Monte-Carlo (HMC).
-However, even in this case, the high computational costs make them impractical meaning for most applications we need approximate inference techniques.
-In \cref{fig:banana}, we show a qualitative example of the induced function space posterior obtained with our method compared to the posterior obtained through HMC sampling on the Banana toy dataset.
+However, for most applications their high computational costs make them impractical so we need approximate inference techniques.
+In \cref{fig:banana}, we show a qualitative example of the induced function-space posterior obtained with our method compared to the posterior obtained through HMC sampling on the Banana toy dataset.
 \todo{make it more straightforward that we are computationally cheaper?
@@
 
+\textbf{Function space}
+As a neural network is a deterministic mapping, the weight-space posterior induces a distribution over the function values.
+Intuitively, if one was to sample from the weight posterior, the corresponding functions created can
+be viewed as perturbed versions of the function at the MAP estimate $f_{\vw^*}$.
+% \todo{not super sure about the perturbed part here. I know what \textrm{you}'re trying to say but a little confused}
+In most applications, we care about predictions from the neural network and not the weights themselves.
+As such, it is the distribution over function values that we are actually interested in.
+
+\textbf{Linearization gives rise to a Gaussian process}
+Our goal is to build a sparse function-space representation of a neural network.
+Gaussian processes are an extension of the multivariate normal that characterizes a distribution over
+functions in terms of the first two moments.
+They are defined by a mean function $\mu(\cdot)$ and a covariance (aka kernel) function $\kappa(\cdot,\cdot)$.
+Thus, we need these two functions based on the neural network to build the Gaussian process posterior.
+Recent work \citep{khan2019approximate,maddox2021fast} has shown that linearizing approximations in the weight space
+lead to function space equivalent approximations.
+As Gaussian distributions remain tractable under linear transformations, a linear function in
+terms of parameters can be converted from the weight space to the function space (see Ch.~2.1 in \cite{rasmussen2006gaussian}) as follows:\begin{equation} \label{eq:weight_func}
+g_\weights(\mathbf{x}_{i}) = \phi^\top\!(\vx_i) \, \vw \implies \mu(\vx_i) = 0 \quad \kappa(\mathbf{x}_i, \mathbf{x}_i') = \frac{1}{\delta} \phi(\vx_i)^\top \phi(\vx_i).
+\end{equation}
+% The posterior structure directly relates to the optimization loss around the MAP weights $\vw^*$.
 A common approach is to approximate the correlation structure of a distribution centred at the MAP estimate as done in the Laplace-GGN \citep{khan2019approximate, daxberger2021laplace, maddox2021fast}.
@@
 Using the Hessian of the approximate model, we arrive at the Laplace-GGN posterior for $q(\vw)$.
-
-Recent work \citep{khan2019approximate,maddox2021fast} shows that linearizing approximations in the weight space lead to function space equivalent approximations.
-As our goal is to build a sparse functional representation of a neural network, a starting point is the non-sparse  $q(\vf)$ function space posterior approximation.
-We choose to use a Gaussian process, as is typical, an extension of the multivariate normal that characterizes a distribution over functions in terms of the first two moments, a mean $\mu(\cdot)$ and covariance  (or kernel) function $\kappa(\cdot,\cdot)$.
-Thus, we need these two functions based on the neural network to build the Gaussian process posterior.
-Gaussian distributions remain tractable under linear transformations.
-Therefore, a linear function in terms of parameters can be converted from the weight space to the function space (see Ch.~2.1 in \cite{rasmussen2006gaussian}) as follows:\begin{equation} \label{eq:weight_func}
-g_\weights(\mathbf{x}_{i}) = \phi^\top\!(\vx_i) \, \vw \implies \mu(\vx_i) = 0 \quad \kappa(\mathbf{x}_i, \mathbf{x}_i') = \frac{1}{\delta} \phi(\vx_i)^\top \phi(\vx_i)
-\end{equation}
-
+\todo{do we need this sentence about the Hessian to get Laplace-GGN??}
 Therefore, the GGN approximate linear model can be used to convert our weight space model to the function space by,

### 2023-05-15 paper/main.tex
Sec. 1

@@
 \newcommand{\etal}{\textit{et~al.\@}\xspace}
+
+% Our method
+\newcommand{\our}{DNN2SGP}
 
@@
 
-\DeclareMathOperator*{\argmax}{argmax}
-\DeclareMathOperator*{\argmin}{argmin}
+\DeclareMathOperator*{\argmax}{arg\,max}
+\DeclareMathOperator*{\argmin}{arg\,min}
 \newcommand{\Norm}{\mathcal{N}}
@@
 %
-Deep learning has become the cornerstone of contemporary artificial intelligence, proving remarkably effective in tackling supervised and unsupervised learning tasks in the {\em large data}, {\em offline}, and {\em gradient-based training} regime.
+Deep learning \cite{goodfellow2016deep} has become the cornerstone of contemporary artificial intelligence, proving remarkably effective in tackling supervised and unsupervised learning tasks in the {\em large data}, {\em offline}, and {\em gradient-based training} regime.
 Despite its success, gradient-based learning techniques exhibit limitations.
-Firstly, how to incorporate uncertainty quantification over predictions which is needed in many applications.
-Secondly, in the sequential data regime data arrives not in batches
-
-Secondly, how to retain information from previous tasks whilst learning new tasks where the tasks aresuch as Continual Learning (CL, \cite{de2021continual})
-
-Thirdly and differently from the CL problem is that given some data from the same distribution
-
-when applied to sequential learning paradigms, such as Continual Learning (CL, \cite{mccloskey1989catastrophic}) and Reinforcement Learning (RL, \cite{sutton2018reinforcement}).
-Recently there has been some success in tackling uncertainty quantification
-
-In CL, the challenge is retaining a compact representation of the problem and avoid forgetting over the life-long learning horizon (see, \eg, \cite{add}).
-Similarly in RL, the model would need to adapt to observations of the environment through exploration, but this can be inefficient and would require constant retraining (\eg, \cite{add, add}).
+Firstly, how can we efficiently quantify uncertainty without resorting to expensive and hard-to-interpret sampling in the model's weight-space?
+Secondly, how to update the wights of an already trained model with new batches of data without compromising the performance on past data?
+These questions become central when applied to sequential learning paradigms, such as continual learning (CL, \cite{de2021continual}) and reinforcement learning (RL, \cite{sutton2018reinforcement}).
+In CL, access to the previous data is lost and the challenge is retaining a compact representation of the problem and avoiding forgetting over the life-long learning horizon~\cite{mccloskey1989catastrophic}.
+Similarly, in RL, the model must adapt to environmental observations through exploration, while leveraging prediction uncertainties to assess potential future paths.
+
+%Secondly, how to retain information from previous tasks whilst learning new tasks where the tasks are such as Continual Learning (CL, \cite{de2021continual})
+%Thirdly and differently from the CL problem is that given some data from the same distribution
 
 %Current state of affairs 
-Recent work on techniques (\eg, \cite{list}) for converting trained neural networks from weight space to function space allow a principled mathematical approach for analyzing the behaviour \cite{add}, performing probabilistic inference \cite{add}, and quantifying uncertainty in neural networks \cite{add}.
-The methods rely on linearizing the neural network and capturing the first two moments in function space in terms of a mean function and covariance function (or kernel) --- defining a Gaussian process (GP, \cite{rasmussen2006gaussian}).
+Recent work on techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) for converting trained neural networks from weight-space to function-space allow a principled mathematical approach for analyzing the behaviour \cite{add}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{add}.
+The methods rely on linearizing \cite{jacot2018neural} the neural network and capturing the first two moments in function space in terms of a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}).
 GPs provide a widely-used probabilistic toolkit with principled uncertainty estimates, and they are a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} with theoretical guarantees on regret bounds \citep{srinivas2009gaussian}.
@@
 Thus we are able to avoid retraining and condition new data in to our model.
-The resultant DNN2SGP method can be used in any sequential decision-making scenario where retraining is not available.%and we show its effectiveness in a planning stage of a model based reinforcement algorithim.
+The resultant \our method can be used in any sequential decision-making scenario where retraining is not available.%and we show its effectiveness in a planning stage of a model based reinforcement algorithim.
 
@@
 % General Bayesian deep learning
-Bayesian deep learning~\cite{Wilson:ensembles,neal1995bayesian} has recently gained increasing attention in the machine learning community as a means for uncertainty quantification (\eg, \cite{kendall2017what,wilson2020bayes}) and model selection (\eg,~\cite{immer2021marginal,antoran2022marginal}) with advancements in prior specification (\eg, \cite{meronen2020stationary,meronen2021periodic,fortuin2021bayesian,nalisnick2018do}) and efficient approximate inference under the specified model.
+Bayesian deep learning~\cite{Wilson:ensembles,neal1995bayesian} has recently gained increasing attention in the machine learning community as a means for uncertainty quantification (\eg, \cite{kendall2017what,wilson2020bayes}) and model selection (\eg,~\cite{immer2021scalable,antoran2022marginal}) with advancements in prior specification (\eg, \cite{meronen2020stationary,meronen2021periodic,fortuin2021bayesian,nalisnick2018do}) and efficient approximate inference under the specified model.
 Calculating the posterior distribution of a Bayesian neural network is usually intractable, and approximate inference techniques need to be used, such as variational inference \cite{blei2017variational}, deep ensembles \cite{lakshminarayanan2017simple}, MC dropout \cite{gal2016dropout}, or Laplace approximation \cite{ritter2018kfac,kristiadi2020being,immer2021improving}---each having strengths and weaknesses.
@@
 One common approach for uncertainty with neural networks is a Laplace-GGN approximation \citep{daxberger2021laplace}, which takes a trained neural network and linearises it around the optimal weights.
-The resulting linear model can be used to obtain uncertainty estimates and refine the neural network predictions \citep{immerScalable2021}, and is linear with respect to the weights.
-Therefore, as shown in \citep{immerScalable2021, khan2019approximate}, the linear model can be converted to a Gaussian process (GP), which is then used to obtain the uncertainty estimates.
+The resulting linear model can be used to obtain uncertainty estimates and refine the neural network predictions \citep{immer2021scalable}, and is linear with respect to the weights.
+Therefore, as shown in \citep{immer2021scalable, khan2019approximate}, the linear model can be converted to a Gaussian process (GP), which is then used to obtain the uncertainty estimates.
 However, the GP introduces a computational scaling that is cubic in the number of data points ($\mathcal{O}(n^3)$).
@@
 
+\clearpage
+
 \phantomsection%

### 2023-05-15 paper/main.tex
Sec. 1'

@@
 % Our method
-\newcommand{\our}{DNN2SGP}
+\newcommand{\our}{DNN2SGP\xspace}
 
@@
 Firstly, how can we efficiently quantify uncertainty without resorting to expensive and hard-to-interpret sampling in the model's weight-space?
-Secondly, how to update the wights of an already trained model with new batches of data without compromising the performance on past data?
+Secondly, how to update the weights of an already trained model with new batches of data without compromising the performance on past data?
 These questions become central when applied to sequential learning paradigms, such as continual learning (CL, \cite{de2021continual}) and reinforcement learning (RL, \cite{sutton2018reinforcement}).
@@
 %Current state of affairs 
-Recent work on techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) for converting trained neural networks from weight-space to function-space allow a principled mathematical approach for analyzing the behaviour \cite{add}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{add}.
+Recent work on techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) for converting trained neural networks from weight-space to function-space allow a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{add}.
 The methods rely on linearizing \cite{jacot2018neural} the neural network and capturing the first two moments in function space in terms of a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}).
@@
 % General Bayesian deep learning
-Bayesian deep learning~\cite{Wilson:ensembles,neal1995bayesian} has recently gained increasing attention in the machine learning community as a means for uncertainty quantification (\eg, \cite{kendall2017what,wilson2020bayes}) and model selection (\eg,~\cite{immer2021scalable,antoran2022marginal}) with advancements in prior specification (\eg, \cite{meronen2020stationary,meronen2021periodic,fortuin2021bayesian,nalisnick2018do}) and efficient approximate inference under the specified model.
+\textbf{Bayesian deep learning}
+Probabilistic method in deep learning~\cite{Wilson:ensembles,neal1995bayesian} have recently gained increasing attention in the machine learning community as a means for uncertainty quantification (\eg, \cite{kendall2017what,wilson2020bayes}) and model selection (\eg,~\cite{immer2021scalable,antoran2022marginal}) with advancements in prior specification (\eg, \cite{cho2009kernel,meronen2020stationary,meronen2021periodic,fortuin2021bayesian,nalisnick2018do}) and efficient approximate inference under the specified model.
 Calculating the posterior distribution of a Bayesian neural network is usually intractable, and approximate inference techniques need to be used, such as variational inference \cite{blei2017variational}, deep ensembles \cite{lakshminarayanan2017simple}, MC dropout \cite{gal2016dropout}, or Laplace approximation \cite{ritter2018kfac,kristiadi2020being,immer2021improving}---each having strengths and weaknesses.
@@
 % Introduce the laplace GGN + shortcomings
+\textbf{Function-space methods}
 One common approach for uncertainty with neural networks is a Laplace-GGN approximation \citep{daxberger2021laplace}, which takes a trained neural network and linearises it around the optimal weights.
+The Hessian can be efficiently approximated using the generalised Gauss--Newton approximation \cite{botev2017practical} or by Kronecker factorisation \cite{martens2015optimizing,ritter2018kfac}.
 The resulting linear model can be used to obtain uncertainty estimates and refine the neural network predictions \citep{immer2021scalable}, and is linear with respect to the weights.
-Therefore, as shown in \citep{immer2021scalable, khan2019approximate}, the linear model can be converted to a Gaussian process (GP), which is then used to obtain the uncertainty estimates.
+Therefore, as shown in \cite{immer2021scalable, khan2019approximate}, the linear model can be converted to a GP, which is then used to obtain the uncertainty estimates.
+
 However, the GP introduces a computational scaling that is cubic in the number of data points ($\mathcal{O}(n^3)$).
-Many approaches apply crude approximations to alleviate the computational costs, \eg, considering only a subset of the training datas, but are still obtain good uncertainty estimates \citep{immerScalable2021}\todo{other methods?}.
-
-The Hessian can be efficiently approximated using the generalised Gauss-Newton approximation \cite{botev2017practical} or by Kronecker factorisation \cite{martens2015optimizing,ritter2018kfac}.
+Previous approaches apply crude approximations to alleviate the computational costs, \eg, by considering only a subset of the training data \cite{immer2021scalable}.
+In the GP community, the scaling problem is not seen as an issue any more due to efficient and stochastic methods for sparse approximations (\eg, \cite{hensman2013gaussian,wang2019exact}).
+However, it is not entirely clear how to combine the linearization of the neural network with sparse methods \cite{titsias2009variational} without falling back to crude subset methods as in \cite{immer2021scalable}.
+We tackle this problem, by framing the problem in the dual parameters \cite{csato2002sparse} of the GP that has previously been used for non-conjugate likelihood models in GPs \cite{adam2021dual}.
+
+\textbf{Function-space methods for sequential learning} The central problem in continual learning is the non-stationary nature of the training distribution which causes the training to overwrite the previously learnt parameters---leading to the model forgetting the previous learnt functions.
+This problem is typically tackled in weight-space with regularisation methods such as EWC, \cite{kirkpatrick2017overcoming}, SI~\cite{zenke17a}), or VCL~\cite{nguyen-tuongModel2009} that induce retention of previously learned information in the weights.
+However, encoding functional knowledge in the weights directly is challening, and thus recent methods such as DER~\cite{buzzega2020dark}, FROMP~\cite{pan2020continual}, and S-FSVI~\cite{rudner2022continual} have focused on function-space regularization.
 
@@
 % In order of pubblication -> DER/FROMP, K-Priors (?), S-FSVI
-EWC \cite{kirkpatrick2017overcoming}
-SI \cite{zenke17a}, 
-VCL \cite{nguyen-tuongModel2009},
+%EWC \cite{kirkpatrick2017overcoming}
+%SI \cite{zenke17a}, 
+%VCL \cite{nguyen-tuongModel2009},
 
 %% DER, FROMP, S-FSVI
-DER \cite{buzzega2020dark}
-FROMP \cite{pan2020continual}
-S-FSVI \cite{rudner2022continual}
+%DER \cite{buzzega2020dark}
+%FROMP \cite{pan2020continual}
+%S-FSVI \cite{rudner2022continual}
 

### 2023-05-15 paper/main.tex
Sec. 1

@@
 In CL, access to the previous data is lost and the challenge is retaining a compact representation of the problem and avoiding forgetting over the life-long learning horizon~\cite{mccloskey1989catastrophic}.
-Similarly, in RL, the model must adapt to environmental observations through exploration, while leveraging prediction uncertainties to assess potential future paths.
+Similarly, in RL, the model must adapt to environmental observations through exploration, while leveraging prediction uncertainties to assess potential future paths.\looseness-1
 
@@
 %Current state of affairs 
-Recent work on techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) for converting trained neural networks from weight-space to function-space allow a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{add}.
-The methods rely on linearizing \cite{jacot2018neural} the neural network and capturing the first two moments in function space in terms of a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}).
-GPs provide a widely-used probabilistic toolkit with principled uncertainty estimates, and they are a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} with theoretical guarantees on regret bounds \citep{srinivas2009gaussian}.
+Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) for converting trained neural networks from weight-space to function-space allow a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{add}.
+These methods rely on the linearization of neural networks\cite{jacot2018neural} the neural network and capturing the first two moments in function space in terms of a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}).
+GPs provide a widely-used probabilistic toolkit with principled uncertainty estimates, and they serve as a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} with theoretical guarantees on regret bounds \citep{srinivas2009gaussian}.
 %Yet many problems lie in high dimensional input space; for example, images are where GPs cannot learn representations.
@@
 %Need for adaptive learning methods + failures with current methods
-In this paper, we show that we can take any neural network and represent the model in terms of the so-called `dual' parameters of a Gaussian process \cite{csato2002sparse, adam2021dual, chang2020fast}.
-Crucially, the resultant GP now has predictions in the same space as the initial trained neural network, a property not of previous approaches.
+In this paper, we demonstrate that any neural network can be represented in terms of the so-called `dual' parameters of a GP~\cite{csato2002sparse, adam2021dual, chang2020fast}.
+Contrasting to previous work that use subsets \cite{immer2021scalable}, this parameterization allows squashing the contributions of {\em all} training data into a sparse representation.
+Crucially, the resulting GP now predicts in the same space as the originally trained neural network, a feature not present in previous approaches, while still avoiding the notorious cubic complexity of vanilla GPs.
 Given the dual parameter formulation, we can convert a full GP to a variational sparse version.
@@
 Therefore, as shown in \cite{immer2021scalable, khan2019approximate}, the linear model can be converted to a GP, which is then used to obtain the uncertainty estimates.
-
-However, the GP introduces a computational scaling that is cubic in the number of data points ($\mathcal{O}(n^3)$).
+%
+However, the GP introduces a cubic scaling $\mathcal{O}(N^3)$ in the number of data points $N$.
 Previous approaches apply crude approximations to alleviate the computational costs, \eg, by considering only a subset of the training data \cite{immer2021scalable}.
 In the GP community, the scaling problem is not seen as an issue any more due to efficient and stochastic methods for sparse approximations (\eg, \cite{hensman2013gaussian,wang2019exact}).
-However, it is not entirely clear how to combine the linearization of the neural network with sparse methods \cite{titsias2009variational} without falling back to crude subset methods as in \cite{immer2021scalable}.
-We tackle this problem, by framing the problem in the dual parameters \cite{csato2002sparse} of the GP that has previously been used for non-conjugate likelihood models in GPs \cite{adam2021dual}.
+However, it is not entirely clear how to combine the linearization of the neural network with sparse methods \cite{titsias2009variational} without falling back to crude subset methods.
+We tackle this problem by framing the problem in the dual parameters \cite{csato2002sparse} of the GP that has previously been used for non-conjugate likelihood models in GPs \cite{adam2021dual}.
 

### 2023-05-15 paper/main.tex
Sec. 1 WIP

@@
 Crucially, the resulting GP now predicts in the same space as the originally trained neural network, a feature not present in previous approaches, while still avoiding the notorious cubic complexity of vanilla GPs.
-Given the dual parameter formulation, we can convert a full GP to a variational sparse version.
+Given the dual parameter formulation, we establish a link between the neural network, the resulting full GP, and a sparse approximation of it akin to variational sparse GPs~\cite{titsias2009variational}.
 Using the sparse GP we can then take advantage of the property of dual parameters that allows for fast conditioning recently shown in \cite{chang2022fantasizing}.
 Thus we are able to avoid retraining and condition new data in to our model.
-The resultant \our method can be used in any sequential decision-making scenario where retraining is not available.%and we show its effectiveness in a planning stage of a model based reinforcement algorithim.
-
-\todo{a pragraph on how this can be used for improving CL and RL}
+The resultant \our method can be used in any sequential decision-making scenario where retraining is not available.
+%\todo{a pragraph on how this can be used for improving CL and RL}
 
@@
 
-We introduce a sparse representation of the neural network in the function space. 
-%
-{\em (i)}~principled uncertainty quantification.
-{\em (ii)}~A compact representation for continual learning
+The contributions of this paper are as follows.
+%
+{\em (i)}~We introduce \our, a new approah for sparse representation of the neural network in the function space.
+{\em (ii)}~We show that, despite being sparse, the method gives a good   
+A compact representation for continual learning
 {\em (iii)}~Fast updates for adaptive exploration.
 %
-We demonstrate points {\em(i)--(iii)} in the experiments.
+We provide extenive experiments for showcasing our approach and demonstrate importance and applicability across supervised, continual, and reinforcement learning to stimulate future use of the approach.
 

### 2023-05-15 paper/main.tex
rewrite intro

@@
 % Introduce the laplace GGN + shortcomings
-\textbf{Function-space methods}
+%\textbf{Function-space methods}
 One common approach for uncertainty with neural networks is a Laplace-GGN approximation \citep{daxberger2021laplace}, which takes a trained neural network and linearises it around the optimal weights.
-The Hessian can be efficiently approximated using the generalised Gauss--Newton approximation \cite{botev2017practical} or by Kronecker factorisation \cite{martens2015optimizing,ritter2018kfac}.
+The Hessian can be efficiently approximated using the generalised Gauss--Newton approximation \cite{botev2017practical} but typically involves a cubic scaling in the number of parameters, in practice a further approximation such as the Kronecker factorisation \cite{martens2015optimizing,ritter2018kfac} is needed.
 The resulting linear model can be used to obtain uncertainty estimates and refine the neural network predictions \citep{immer2021scalable}, and is linear with respect to the weights.

### 2023-05-15 paper/main.tex
rewrite intro

@@
 %Current state of affairs 
-Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) for converting trained neural networks from weight-space to function-space allow a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{add}.
+Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) for converting trained neural networks from weight-space to function-space allow a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{foong2019between}.
 These methods rely on the linearization of neural networks\cite{jacot2018neural} the neural network and capturing the first two moments in function space in terms of a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}).
@@
 Crucially, the resulting GP now predicts in the same space as the originally trained neural network, a feature not present in previous approaches, while still avoiding the notorious cubic complexity of vanilla GPs.
-Given the dual parameter formulation, we establish a link between the neural network, the resulting full GP, and a sparse approximation of it akin to variational sparse GPs~\cite{titsias2009variational}.
+Given the dual parameter formulation, we establish a link between the neural network, the resulting full GP, and a sparse approximation of it akin to sparse GPs~\cite{titsias2009variational}.
 Using the sparse GP we can then take advantage of the property of dual parameters that allows for fast conditioning recently shown in \cite{chang2022fantasizing}.

### 2023-05-15 paper/main.tex
Sec. 1

--- 2023-05-15 paper/main.tex
@@
 In this paper, we demonstrate that any neural network can be represented in terms of the so-called `dual' parameters of a GP~\cite{csato2002sparse, adam2021dual, chang2020fast}.
-Contrasting to previous work that use subsets \cite{immer2021scalable}, this parameterization allows squashing the contributions of {\em all} training data into a sparse representation.
+In contrast to previous work that utilizes subsets \cite{immer2021scalable}, this parameterization allows for the consolidation of contributions from {\em all} training data into a sparse representation.
 Crucially, the resulting GP now predicts in the same space as the originally trained neural network, a feature not present in previous approaches, while still avoiding the notorious cubic complexity of vanilla GPs.
-Given the dual parameter formulation, we establish a link between the neural network, the resulting full GP, and a sparse approximation of it akin to variational sparse GPs~\cite{titsias2009variational}.
+Through the dual parameter formulation, we establish a connection between the neural network, the resulting full GP, and a sparse approximation similar to variational sparse GPs~\cite{titsias2009variational}.
 Using the sparse GP we can then take advantage of the property of dual parameters that allows for fast conditioning recently shown in \cite{chang2022fantasizing}.
 Thus we are able to avoid retraining and condition new data in to our model.
-The resultant \our method can be used in any sequential decision-making scenario where retraining is not available.
+The resulting \our method can be applied in any sequential decision-making scenario where retraining is not feasible.
 %\todo{a pragraph on how this can be used for improving CL and RL}
@@
 
-The contributions of this paper are as follows.
-%
-{\em (i)}~We introduce \our, a new approah for sparse representation of the neural network in the function space.
-{\em (ii)}~We show that, despite being sparse, the method gives a good   
-A compact representation for continual learning
-{\em (iii)}~Fast updates for adaptive exploration.
-%
-We provide extenive experiments for showcasing our approach and demonstrate importance and applicability across supervised, continual, and reinforcement learning to stimulate future use of the approach.
+The contributions of this paper are:
+%
+{\em (i)}~We introduce \our, a new approach for sparse representation of the neural network in the function space.
+{\em (ii)}~We demonstrate that, despite its sparsity, our method effectively captures predictive uncertainty, provides means of updating the model post-training, and gives a a compact representation suitable for continual learning.
+{\em (iii)}~We provide extensive experiments for showcasing our approach and demonstrate significance and applicability across supervised, continual, and reinforcement learning, aiming to stimulate future use of the approach.
 

### 2023-05-15 paper/main.tex
rewrite intro

@@
 % Our method
-\newcommand{\our}{DNN2SGP\xspace}
+\newcommand{\our}{\textsc{dnn2sgp}\xspace}
 
@@
 The resulting \our method can be applied in any sequential decision-making scenario where retraining is not feasible.
-%\todo{a pragraph on how this can be used for improving CL and RL}
 
@@
   %
-  \def\inducing{\normalsize Sparse inducing points}
+  \def\inducing{\large Sparse inducing points}
   %
@@
   \end{subfigure}
-  \caption{\textbf{Regression example on an MLP with two hidden layers.} Left:~Predictions from the trained neural network. Center:~Our approach summarizes the...}
+  \caption{\textbf{Regression example on an MLP with two hidden layers.} Left:~Predictions from the trained neural network.
+Middle:~Our approach summarizes all the training data with the help of an iducing set of points.
+The model captures the predictive mean and uncertainty, and (right) makes it possible to update the model with new data without degrading previous performance.}
   \label{fig:teaser} 
@@
     % Arrow labels
-    \node[font=\scriptsize\sc,color=white] at (p0-arr) {nn2svgp};
+    \node[font=\scriptsize\sc,color=white] at (p0-arr) {\our};
     \node[font=\scriptsize\sc,color=white] at (p1-arr) {new data};   
@@
     % Arrow labels
-    \node[font=\scriptsize\sc,color=white] at (first-arr) {nn2svgp};
+    \node[font=\scriptsize\sc,color=white] at (first-arr) {\our};
     \node[font=\scriptsize\sc,color=white] at (second-arr) {\normalsize$\bm\approx$};
@@
   \end{tikzpicture}
-  \newcommand{\mycircle}{\protect\tikz[baseline=-.5ex]\protect\node[circle,inner sep=2pt,draw=black,fill=C0,opacity=.5]{};}
-  \newcommand{\mysquare}{\protect\tikz[baseline=-.5ex]\protect\node[inner sep=2.5pt,draw=black,fill=C1,opacity=.5]{};}
-  %
-  \caption{Binary classification (\mysquare~vs.~\mycircle) on the {\sc banana} toy data data set. We convert the left-hand neural network  }
+  \newcommand{\mycircle}{\protect\tikz[baseline=-.6ex]\protect\node[circle,inner sep=2pt,draw=black,fill=C0,opacity=.5]{};}
+  \newcommand{\mysquare}{\protect\tikz[baseline=-.6ex]\protect\node[inner sep=2.5pt,draw=black,fill=C1,opacity=.5]{};}
+  \newcommand{\myinducing}{\protect\tikz[baseline=-.7ex]\protect\node[circle,inner sep=1.5pt,draw=black,fill=black]{};}
+  %
+  \caption{\textbf{Uncertainty quantification} for binary classification (\mysquare~vs.~\mycircle).
+We convert the trained neural network (left) to a sparse GP model that summarizes all data onto a sparse set of inducing points~\myinducing\ (middle).
+This gives similar behaviour as would running full Hamiltonian Monte Carlo (HMC) on the original neural network model weights (right).
+Marginal uncertainty depicted by colour intensity.\looseness-1}
   \label{fig:banana}  
@@
 
-\section{Background}
+\section{Background: Function-space representation of neural networks}
 \label{sec:methods}
-
-In this section, we recap how a trained neural network (NN) can be converted to a Gaussian process by locally linearising
-its weights.
+%
+%In this section, we recap how a trained neural network (NN) can be converted to a Gaussian process by locally linearising its weights.
 % a GP posterior -- can be obtained
@@
   \weights^{*} = 
-  \argmin_{\weights} \mathcal{L}(\dataset,\weights) =
-  \argmin_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
+  \arg \min_{\weights} \mathcal{L}(\dataset,\weights) =
+  \arg \min_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
 \end{equation}
@@
 % g(\vx) \sim \GP \left( \mu(\vx), \kappa(\vx, \vx') \right) \quad \text{with} \quad
-  \mu(\vx) =  0 \quad \text{and} \quad
-  \kappa(\mathbf{x}, \mathbf{x}')
-  = \frac{1}{\delta} \Jac{\weights^*}{\mathbf{x}}\JacT{\weights^*}{\mathbf{x}'},
+  \mu(\vx_i) =  0 \quad \text{and} \quad
+  \kappa(\mathbf{x}_i, \mathbf{x}_i')
+  = \frac{1}{\delta} \Jac{\weights^*}{\mathbf{x}_i}\JacT{\weights^*}{\mathbf{x}_i'},
 \end{equation}
@@
 
-\section{Methods}
+\section{\our: Sparse function-space represenation of neural networks}
 \paragraph{Linearization in the dual parameters}
-As stated in \citet[Lemma~1]{csato2002sparse}, the posterior process mean and covariance functions of a GP prior, combined with a likelihood function and $\dataset$ can be stated as:
+As stated in \citet[Lemma~1]{csato2002sparse}, the posterior process $f$ mean and covariance functions of a GP prior, combined with a likelihood function and $\dataset$ can be parameterized:
 \begin{equation}  \label{eq:gp_pred}
- \myexpect_{p(f_i \mid\vy)}[f_i] = \vk_{\vx i}^\top \valpha \quad \text{and} \quad
-\mathrm{Var}_{p(f_{i}\mid\vy)}[f_i] = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
+ \mu(\vx_i)_\textrm{post} = \vk_{\vx i}^\top \valpha \quad \text{and} \quad
+  \kappa(\mathbf{x}_i, \mathbf{x}_i')_\textrm{post} = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
 \end{equation}
-where $f_i = f_\weights(\vx_i)$, the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{m \times m}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
+, the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{m \times m}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
 The dual parameters consist of the vector $\valpha \in \R^{m}$ and vector $\vbeta \in \R^{m}$, defined as:
@@
 
-\subsection{Continual Learning}
+\subsection{Sparse functional regularization (SFR) in continual learning}
 % Definition of CL -> a sequence of tasks
@@
 \end{table}
+We trained a two-layer MLP for each of the $8$ classification tasks in UCI, see \cref{tbl:uci} for a list of the datasets.
+The neural network training was done using MAP, with a prior $\mathcal{N}(0,\delta^{-1} \MI)$ with prior precision $\delta$.
+After training, we constructed the SVGP dual and used the resulting SVGP model for uncertainty quantification.
+Depending on task dimension and complexity, our model can match the NN MAP in NLPD performance even with a low number of inducing points, see \cref{tbl:uci}.
+We performed hyperparameter search over the prior precision, and ran the experiment over $10$ seeds.
+During the initial NN training, we used a learning rate of $1e-3$.
 
@@
 \end{table}
+
+Similarly to the UCI experiments, we trained neural networks (CNN, architexture matches \citet{immerImprovingPredictionsBayesian2021}) for the FMNIST and CIFAR10 classification tasks.
+After training, we computed the duals for NN2SVGP and used the resulting SVGP for uncertainty estimates, see \cref{tbl:imagesuper}.
+We performed hyperparameter optimization over the prior precision, and found the optimal value to be [insert].
+We ran the experiment over $5$ seeds.
+During the NN training, we used a batch size of $512$ and an Adam optimizer with learning rate $1e-3$.
+
+In addition to uncertainty estimates, our method can update the posterior when given new data.
+We gave the SVGP model 10 \% of the test dataset used for evaluation, and compare the performance of the SVGP model and the retrained NN in [INSERT TABLE].
 \subsection{Updating the representation during continual learning}

### 2023-05-15 bnn-predictive/experiments/scripts/imgclassification.py
Plot training losses, parallelize vision training

@@ -218,7 +218,7 @@ if __name__ == '__main__':
     # naming convention: dataset_model_seed_delta
     fname = 'models/' + '_'.join([dataset, model_name, str(seed)]) + '_{delta:.1e}.pt'
     deltas = np.logspace(logd_min, logd_max, n_deltas)
-    deltas = np.insert(deltas, 0, 0)  # add unregularized network
+ #   deltas = np.insert(deltas, 0, 0)  # add unregularized network
     print(f'Train set size: {len(ds_train)}')
     deltas = deltas / len(ds_train)
 

### 2023-05-15 bnn-predictive/experiments/scripts/imginference.py

@@ -11,7 +11,7 @@ from itertools import chain
 
 # from preds.laplace import Laplace, FunctionaLaplace
 from preds.laplace import FunctionaLaplace
-from src import CategoricalLh, NTKSVGP
+from src import CategoricalLh, NTKSVGP, NN2GPSubset
 import src as ntksvgp
 from preds.utils import nll_cls, macc, ece
 from preds.datasets import MNIST, FMNIST, SVHN
@@ -139,6 +139,27 @@ def get_perf_dict():
 def get_quick_loader(loader, device="cuda"):
     return [(X.to(device), y.to(device)) for X, y in loader]
 
+def update_with_ood(svgp, likelihood,  ds_ood, update_size=100, batch_size=512):
+
+    perm_ixs = torch.randperm(len(ds_ood))
+    update_ixs, test_ixs = perm_ixs[:update_size], perm_ixs[int(M / 2) :]
+    ds_ood_update = Subset(ds_ood, val_ixs)
+    ds_ood_test = Subset(ds_ood, test_ixs)
+
+    test_ood_loader = get_quick_loader(DataLoader(ds_ood_test, batch_size=batch_size))
+
+    update_X, update_y = ds_ood
+    svgp.update(update_X, update_y)
+    gstar_ood, yte = get_svgp_predictive(
+            test_ood_loader, svgp, use_nn_out=False, likelihood=likelihood
+        )
+    state[f"svgp_ntk_{name}_ood"] = evaluate_one(lh, yte, gstar_ood)
+
+def retrain_and_update_(svgp, likelihood, ds_test, update_size=100):
+
+
+
+
 
 def main(
     dataset_name,
@@ -151,8 +172,8 @@ def main(
     n_sparse,
     name,
     n_inducing,
-    delta_min=1e-5,
-    delta_max=1e8,
+    logdelta_min=-5,
+    logdelta_max=8,
     res_dir="experiments/results",
     device="cuda",
 ):
@@ -168,8 +189,8 @@ def main(
             ds == dataset_name
             and m == model_name
             and seed == int(s)
-            and (float(delta) >= delta_min)
-            and (float(delta) <= delta_max)
+            and (np.log10(float(delta)) >= delta_min)
+            and (np.log10(float(delta)) <= delta_max)
         ):
             eligible_files.append(os.path.join(res_dir, "models/" + file))
             deltas.append(float(delta))
[…]

### 2023-05-15 paper/main.tex
Captions

@@
 % Our method
-\newcommand{\our}{DNN2SGP\xspace}
+\newcommand{\our}{{\sc dnn2sgp}\xspace}
 

### 2023-05-15 paper/main.tex
Section titles
rewrite intro

--- 2023-05-15 paper/main.tex
@@
 Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) for converting trained neural networks from weight-space to function-space allow a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{foong2019between}.
-These methods rely on the linearization of neural networks\cite{jacot2018neural} the neural network and capturing the first two moments in function space in terms of a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}).
+These methods rely on the linearization of neural networks.
+\cite{jacot2018neural} the neural network and capturing the first two moments in function space in terms of a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}).
 GPs provide a widely-used probabilistic toolkit with principled uncertainty estimates, and they serve as a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} with theoretical guarantees on regret bounds \citep{srinivas2009gaussian}.

### 2023-05-15 paper/main.tex

--- 2023-05-15 paper/main.tex
@@
 
-\section{Methods}
+\section{DNN2SGP: Sparse Function-space represenation of neural networks}
 \paragraph{Linearization in the dual parameters}

### 2023-05-15 paper/main.tex
Section titles

@@
 % Our method
-\newcommand{\our}{{\sc dnn2sgp}\xspace}
+\newcommand{\our}{\textsc{dnn2sgp}\xspace}
 
@@
 
-\section{DNN2SGP: Sparse Function-space represenation of neural networks}
+\section{\our: Sparse function-space represenation of neural networks}
 \paragraph{Linearization in the dual parameters}
@@
 \end{table}
-We trained a two-layer MLP for each of the $8$ classification tasks in UCI, see \cref{tbl:uci} for a list of the datasets.
-The neural network training was done using MAP, with a prior $\mathcal{N}(0,\delta^{-1} \MI)$ with prior precision $\delta$.
-After training, we constructed the SVGP dual and used the resulting SVGP model for uncertainty quantification.
-Depending on task dimension and complexity, our model can match the NN MAP in NLPD performance even with a low number of inducing points, see \cref{tbl:uci}.
-We performed hyperparameter search over the prior precision, and ran the experiment over $10$ seeds.
-During the initial NN training, we used a learning rate of $1e-3$.
 
@@
 \end{table}
-
-Similarly to the UCI experiments, we trained neural networks (CNN, architexture matches \citet{immerImprovingPredictionsBayesian2021}) for the FMNIST and CIFAR10 classification tasks.
-After training, we computed the duals for NN2SVGP and used the resulting SVGP for uncertainty estimates, see \cref{tbl:imagesuper}.
-We performed hyperparameter optimization over the prior precision, and found the optimal value to be [insert].
-We ran the experiment over $5$ seeds.
-During the NN training, we used a batch size of $512$ and an Adam optimizer with learning rate $1e-3$.
-
-In addition to uncertainty estimates, our method can update the posterior when given new data.
-We gave the SVGP model 10 \% of the test dataset used for evaluation, and compare the performance of the SVGP model and the retrained NN in [INSERT TABLE].
 \subsection{Updating the representation during continual learning}

### 2023-05-15 paper/main.tex
Section titles
updates cl part

--- 2023-05-15 paper/main.tex
@@
 Secondly, how to update the weights of an already trained model with new batches of data without compromising the performance on past data?
-These questions become central when applied to sequential learning paradigms, such as continual learning (CL, \cite{de2021continual}) and reinforcement learning (RL, \cite{sutton2018reinforcement}).
+These questions become central when applied to sequential learning paradigms, such as continual learning (CL, \citep{parisi2019continual, de2021continual}) and reinforcement learning (RL, \cite{sutton2018reinforcement}).
 In CL, access to the previous data is lost and the challenge is retaining a compact representation of the problem and avoiding forgetting over the life-long learning horizon~\cite{mccloskey1989catastrophic}.
@@
 %Current state of affairs 
-Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) for converting trained neural networks from weight-space to function-space allow a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{foong2019between}.
+Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) for converting trained neural networks from weight-space to function-space allow a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{add}.
 These methods rely on the linearization of neural networks\cite{jacot2018neural} the neural network and capturing the first two moments in function space in terms of a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}).
@@
 In this paper, we demonstrate that any neural network can be represented in terms of the so-called `dual' parameters of a GP~\cite{csato2002sparse, adam2021dual, chang2020fast}.
-In contrast to previous work that utilizes subsets \cite{immer2021scalable}, this parameterization allows for the consolidation of contributions from {\em all} training data into a sparse representation.
+Contrasting to previous work that use subsets \cite{immer2021scalable}, this parameterization allows squashing the contributions of {\em all} training data into a sparse representation.
 Crucially, the resulting GP now predicts in the same space as the originally trained neural network, a feature not present in previous approaches, while still avoiding the notorious cubic complexity of vanilla GPs.
-Through the dual parameter formulation, we establish a connection between the neural network, the resulting full GP, and a sparse approximation similar to variational sparse GPs~\cite{titsias2009variational}.
+Given the dual parameter formulation, we establish a link between the neural network, the resulting full GP, and a sparse approximation of it akin to variational sparse GPs~\cite{titsias2009variational}.
 Using the sparse GP we can then take advantage of the property of dual parameters that allows for fast conditioning recently shown in \cite{chang2022fantasizing}.
 Thus we are able to avoid retraining and condition new data in to our model.
-The resulting \our method can be applied in any sequential decision-making scenario where retraining is not feasible.
+The resultant \our method can be used in any sequential decision-making scenario where retraining is not available.
+%\todo{a pragraph on how this can be used for improving CL and RL}
 
@@
 
-The contributions of this paper are:
-%
-{\em (i)}~We introduce \our, a new approach for sparse representation of the neural network in the function space.
-{\em (ii)}~We demonstrate that, despite its sparsity, our method effectively captures predictive uncertainty, provides means of updating the model post-training, and gives a a compact representation suitable for continual learning.
-{\em (iii)}~We provide extensive experiments for showcasing our approach and demonstrate significance and applicability across supervised, continual, and reinforcement learning, aiming to stimulate future use of the approach.
+The contributions of this paper are as follows.
+%
+{\em (i)}~We introduce \our, a new approah for sparse representation of the neural network in the function space.
+{\em (ii)}~We show that, despite being sparse, the method gives a good   
+A compact representation for continual learning
+{\em (iii)}~Fast updates for adaptive exploration.
+%
+We provide extenive experiments for showcasing our approach and demonstrate importance and applicability across supervised, continual, and reinforcement learning to stimulate future use of the approach.
 
@@
 
-\textbf{Function-space methods for sequential learning} The central problem in continual learning is the non-stationary nature of the training distribution which causes the training to overwrite the previously learnt parameters---leading to the model forgetting the previous learnt functions.
-This problem is typically tackled in weight-space with regularisation methods such as EWC, \cite{kirkpatrick2017overcoming}, SI~\cite{zenke17a}), or VCL~\cite{nguyen-tuongModel2009} that induce retention of previously learned information in the weights.
-However, encoding functional knowledge in the weights directly is challening, and thus recent methods such as DER~\cite{buzzega2020dark}, FROMP~\cite{pan2020continual}, and S-FSVI~\cite{rudner2022continual} have focused on function-space regularization.
-
-%% CL section 
-%%
-%% EWC, SI, VCL -> weight regularization 
-% 1) what is the central problem of CL? 
-% 		Training from a non-stationary distribution the models overwrites the previously learnt parameters and then forgets the previous learnt function.
-% 2) What others have done?
-% 		starting with EWC and SI, that are the most known methods in term of weight regularization. And others took a different approach again in the weight regularization real with VCL (to check)
-% 3) People started to try experimenting with the functional regularization -> 
-% In order of complexity -> DER, FROMP, S-FSVI
-% In order of pubblication -> DER/FROMP, K-Priors (?), S-FSVI
-%EWC \cite{kirkpatrick2017overcoming}
-%SI \cite{zenke17a}, 
-%VCL \cite{nguyen-tuongModel2009},
-
-%% DER, FROMP, S-FSVI
-%DER \cite{buzzega2020dark}
-%FROMP \cite{pan2020continual}
-%S-FSVI \cite{rudner2022continual}
+% CL section
+\textbf{Function-space methods for sequential learning} The central problem in continual learning is how to deal with the non-stationary nature of the training distribution which causes the training process to overwrite the previously learnt parameters---leading to the model forgetting the previous learnt functions.
+The approaches proposed in the CL literature can be categorized into inference-based, reharsal-based, and model-based methods, we refer the reader to \citep{parisi2019continual, de2021continual} for complete reviews.
+Many methods in the first category tackled this problem with weight-space regularization, such as EWC~\cite{kirkpatrick2017overcoming}, SI~\cite{zenke17a}), or VCL~\cite{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone.
+However, encoding functional knowledge in the weights does not guarantees a good quality of the predictions, and thus recent methods such as DER~\cite{buzzega2020dark}, FROMP~\cite{pan2020continual}, and S-FSVI~\cite{rudner2022continual} have focused on function-space regularization.
+% It should be written clearly that our method actually is doing a "functional" reharsal, because we store a set of inducing points that are replayed in order to check if the logits change.
+
+% Other methods that could be worth citing are 
+% Learning without forgetting \citep{li2018lwf} :  first paper proposing to use functional regularization computes a smoothed version of the current logits for the new examples at the beginning of each task, minimizing their drift during training.
+It doesn't have any set of inducing points
+% \citep{benjamin2018measuring} this is not a proper CL paper, but it's usually referred in the functional regularization papers, because shows how to improve Adam with measuring the network difference in function space.
+They also have some easy CL examples there.
 
@@
 In \cref{fig:banana}, we show a qualitative example of the induced function-space posterior obtained with our method compared to the posterior obtained through HMC sampling on the Banana toy dataset.
-\todo{make it more straightforward that we are computationally cheaper?
-A: Not sure we are reallying trying to sell our method here}
 
@@
 % Definition of CL -> a sequence of tasks 
+In this paper we consider the Continual learning setting were a sequence of disjoint sets
 
@@
 \end{table}
-
-Similarly to the UCI experiments, we trained neural networks (CNN, architexture matches \citet{immerImprovingPredictionsBayesian2021}) for the FMNIST and CIFAR10 classification tasks.
-After training, we computed the duals for NN2SVGP and used the resulting SVGP for uncertainty estimates, see \cref{tbl:imagesuper}.
-We performed hyperparameter optimization over the prior precision, and found the optimal value to be [insert].
-We ran the experiment over $5$ seeds.
-During the NN training, we used a batch size of $512$ and an Adam optimizer with learning rate $1e-3$.
-
-In addition to uncertainty estimates, our method can update the posterior when given new data.
-We gave the SVGP model 10 \% of the test dataset used for evaluation, and compare the performance of the SVGP model and the retrained NN in [INSERT TABLE].
-\subsection{Updating the representation during continual learning}
-
+\subsection{Updating the  network representation for Continual learning}
+The Continual learning setting is a challenging and the training and
 \begin{table}[t!] 

### 2023-05-15 paper/main.tex
rewrite intro

--- 2023-05-15 paper/main.tex
@@
 %Current state of affairs 
-Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) for converting trained neural networks from weight-space to function-space allow a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{foong2019between}.
-These methods rely on the linearization of neural networks\cite{jacot2018neural} the neural network and capturing the first two moments in function space in terms of a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}).
+Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) show that converting trained neural networks to a Bayesian neural network through the Laplace-GGN can provide uncertainty without sacrificing additional training cost \cite{foong2019between}.
+Furthermore, the resultant weight space posterior can be converted to the function space as shown \cite{khan2019approximate, immer2021improving}.
+The function space allows for a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{foong2019between}.
+These methods rely on the linearization of the neural network and the resultant NTK \cite{jacot2018neural}.
+The result function space neural network is characterized by its first two moment functions, a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}).
 GPs provide a widely-used probabilistic toolkit with principled uncertainty estimates, and they serve as a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} with theoretical guarantees on regret bounds \citep{srinivas2009gaussian}.
@@
 The resulting linear model can be used to obtain uncertainty estimates and refine the neural network predictions \citep{immer2021scalable}, and is linear with respect to the weights.
-Therefore, as shown in \cite{immer2021scalable, khan2019approximate}, the linear model can be converted to a GP, which is then used to obtain the uncertainty estimates.
+Therefore, as shown in \cite{immer2021scalable, khan2019approximate,maddox2021fast}, the linear model can be converted to a GP, which is then used to obtain the uncertainty estimates.
 %
@@
 Our goal is to build a sparse function-space representation of a neural network.
-Gaussian processes are an extension of the multivariate normal that characterizes a distribution over
+Gaussian processes $f$ are an extension of the multivariate normal that characterizes a distribution over
 functions in terms of the first two moments.
@@
 We now present the general formulation of the sparse functional representation of our trained neural network based on the non-sparse approximation.
-\todo{this sentence can be avoided probably, A: its what Aidan calls setting the scene}
-
-\section{DNN2SGP: Sparse Function-space represenation of neural networks}
+
+\section{\our: Sparse function-space represenation of neural networks}
 \paragraph{Linearization in the dual parameters}
-As stated in \citet[Lemma~1]{csato2002sparse}, the posterior process mean and covariance functions of a GP prior, combined with a likelihood function and $\dataset$ can be stated as:
+As stated in \citet[Lemma~1]{csato2002sparse}, the posterior process $f_{\textrm{post}}$ mean and covariance functions of a GP prior, combined with a likelihood function and $\dataset$ can be parameterized:
 \begin{equation}  \label{eq:gp_pred}
- \myexpect_{p(f_i \mid\vy)}[f_i] = \vk_{\vx i}^\top \valpha \quad \text{and} \quad
-\mathrm{Var}_{p(f_{i}\mid\vy)}[f_i] = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
+ \mu(\vx_i)_\textrm{post} = \vk_{\vx i}^\top \valpha \quad \text{and} \quad
+  \kappa(\mathbf{x}_i, \mathbf{x}_i')_\textrm{post} = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
 \end{equation}
-where $f_i = f_\weights(\vx_i)$, the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{m \times m}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
+, the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{m \times m}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
 The dual parameters consist of the vector $\valpha \in \R^{m}$ and vector $\vbeta \in \R^{m}$, defined as:

### 2023-05-15 paper/main.tex

--- 2023-05-15 paper/main.tex
@@
 
-\subsection{Continual Learning}
+\subsection{Sparse functional regularization (SFR) in Continual learning}
 % Definition of CL -> a sequence of tasks 
+In this paper we consider the Continual learning setting were a sequence of disjoint sets
 
@@
 \end{table}
-\subsection{Updating the representation during continual learning}
+
+Similarly to the UCI experiments, we trained neural networks (CNN, architexture matches \citet{immerImprovingPredictionsBayesian2021}) for the FMNIST and CIFAR10 classification tasks.
+After training, we computed the duals for NN2SVGP and used the resulting SVGP for uncertainty estimates, see \cref{tbl:imagesuper}.
+We performed hyperparameter optimization over the prior precision, and found the optimal value to be [insert].
+We ran the experiment over $5$ seeds.
+During the NN training, we used a batch size of $512$ and an Adam optimizer with learning rate $1e-3$.
+
+In addition to uncertainty estimates, our method can update the posterior when given new data.
+We gave the SVGP model 10 \% of the test dataset used for evaluation, and compare the performance of the SVGP model and the retrained NN in [INSERT TABLE].
+
+\subsection{Updating the  network representation for Continual learning}
+The Continual learning setting is a challenging and the training and
 

### 2023-05-15 bnn-predictive/experiments/scripts/imginference.py
Sketching update vs retrain code

@@ -155,9 +155,45 @@ def update_with_ood(svgp, likelihood,  ds_ood, update_size=100, batch_size=512):
         )
     state[f"svgp_ntk_{name}_ood"] = evaluate_one(lh, yte, gstar_ood)
 
-def retrain_and_update_(svgp, likelihood, ds_test, update_size=100):
+def retrain_and_update(state, svgp, likelihood, ds_test, ds_train, name='sparse_500',
+    update_size=100, batch_size=500, device='cpu'):
+    # get update dataset
+    perm_ixs = torch.randperm(len(test))
+    update_ixs, test_ixs = perm_ixs[:update_size], perm_ixs[update_size:]
+    ds_update = Subset(ds_test, update_ixs)
+    ds_update_test = Subset(ds_test, test_ixs)
+
+    # update SVGP
+    all_update = DataLoader(ds_update, batch_size=len(ds_update))
+    batched_update = DataLoader(ds_update, batch_size=batch_size)
+    (X_update, y_update) = next(iter(all_update))
+    svgp.update(update_X, update_y)
+
+    gstar_update, yte = get_svgp_predictive(
+            batched_update, svgp, use_nn_out=False, likelihood=likelihood
+        )
+    state[f"svgp_ntk_{name}_updated"] = evaluate_one(likelihood, yte, gstar_update)
+
+    # Retrain network
+    train_update_loader = ds_train + ds_update
+
+    model = retrain_nn(svgp, train_update_loader, delta=svgp.prior.delta)
+    gstar_update, yte = get_map_predictive(model=model, loader=batched_update)
+    state[f'nn_retrain_map'] = evaluate_one(likelihood, yte, gstar_update)
 
 
+def retrain_nn(svgp, train_loader, delta, lr=1e-3, device='cpu', n_epochs=500):
+    optim = Adam(svgp.network.parameters(), lr=lr, weight_decay=delta)
+    scheduler = LambdaLR(optim, lr_lambda=lambda epoch: 1/(epoch // 10 + 1))
+    for epoch in tqdm(list(range(n_epochs))):
+        for X, y in train_loader:
+            X, y = X.to(device), y.to(device)
+            loss = svgp.loss(X, y)
+            optimizer.zero_grad()
+            loss.backward()
+            optimizer.step()
+        scheduler.step()
+    return svgp.network
 
 
 
@@ -175,6 +211,7 @@ def main(
     logdelta_min=-5,
     logdelta_max=8,
[…]

### 2023-05-15 paper/main.tex

@@
 We now present the general formulation of the sparse functional representation of our trained neural network based on the non-sparse approximation.
-\todo{this sentence can be avoided probably, A: its what Aidan calls setting the scene}
 
@@
 \paragraph{Linearization in the dual parameters}
-As stated in \citet[Lemma~1]{csato2002sparse}, the posterior process mean and covariance functions of a GP prior, combined with a likelihood function and $\dataset$ can be stated as:
+As stated in \citet[Lemma~1]{csato2002sparse}, the posterior process $f_{\textrm{post}}$ mean and covariance functions of a GP prior, combined with a likelihood function and $\dataset$ can be parameterized:
 \begin{equation}  \label{eq:gp_pred}
- \myexpect_{p(f_i \mid\vy)}[f_i] = \vk_{\vx i}^\top \valpha \quad \text{and} \quad
-\mathrm{Var}_{p(f_{i}\mid\vy)}[f_i] = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
+ \mu(\vx_i)_\textrm{post} = \vk_{\vx i}^\top \valpha \quad \text{and} \quad
+  \kappa(\mathbf{x}_i, \mathbf{x}_i')_\textrm{post} = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
 \end{equation}
-where $f_i = f_\weights(\vx_i)$, the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{m \times m}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
+, the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{m \times m}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
 The dual parameters consist of the vector $\valpha \in \R^{m}$ and vector $\vbeta \in \R^{m}$, defined as:

### 2023-05-15 paper/main.tex
Table sketch

--- 2023-05-15 paper/main.tex
@@
 %Current state of affairs 
-Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) show that converting trained neural networks to a Bayesian neural network through the Laplace-GGN can provide uncertainty without sacrificing additional training cost \cite{foong2019between}.
-Furthermore, the resultant weight space posterior can be converted to the function space as shown \cite{khan2019approximate, immer2021improving}.
-The function space allows for a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{foong2019between}.
-These methods rely on the linearization of the neural network and the resultant NTK \cite{jacot2018neural}.
-The result function space neural network is characterized by its first two moment functions, a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}).
+Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) for converting trained neural networks from weight-space to function-space allow a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{foong2019between}.
+These methods rely on the linearization of neural networks\cite{jacot2018neural} the neural network and capturing the first two moments in function space in terms of a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}).
 GPs provide a widely-used probabilistic toolkit with principled uncertainty estimates, and they serve as a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} with theoretical guarantees on regret bounds \citep{srinivas2009gaussian}.
@@
 The resulting linear model can be used to obtain uncertainty estimates and refine the neural network predictions \citep{immer2021scalable}, and is linear with respect to the weights.
-Therefore, as shown in \cite{immer2021scalable, khan2019approximate,maddox2021fast}, the linear model can be converted to a GP, which is then used to obtain the uncertainty estimates.
+Therefore, as shown in \cite{immer2021scalable, khan2019approximate}, the linear model can be converted to a GP, which is then used to obtain the uncertainty estimates.
 %
@@
 Our goal is to build a sparse function-space representation of a neural network.
-Gaussian processes $f$ are an extension of the multivariate normal that characterizes a distribution over
+Gaussian processes are an extension of the multivariate normal that characterizes a distribution over
 functions in terms of the first two moments.
@@
 % g(\vx) \sim \GP \left( \mu(\vx), \kappa(\vx, \vx') \right) \quad \text{with} \quad
-  \mu(\vx_i) =  0 \quad \text{and} \quad
-  \kappa(\mathbf{x}_i, \mathbf{x}_i')
-  = \frac{1}{\delta} \Jac{\weights^*}{\mathbf{x}_i}\JacT{\weights^*}{\mathbf{x}_i'},
+  \mu(\vx) =  0 \quad \text{and} \quad
+  \kappa(\mathbf{x}, \mathbf{x}')
+  = \frac{1}{\delta} \Jac{\weights^*}{\mathbf{x}}\JacT{\weights^*}{\mathbf{x}'},
 \end{equation}
@@
 We now present the general formulation of the sparse functional representation of our trained neural network based on the non-sparse approximation.
+\todo{this sentence can be avoided probably, A: its what Aidan calls setting the scene}
 
@@
 \paragraph{Linearization in the dual parameters}
-As stated in \citet[Lemma~1]{csato2002sparse}, the posterior process $f_{\textrm{post}}$ mean and covariance functions of a GP prior, combined with a likelihood function and $\dataset$ can be parameterized:
+As stated in \citet[Lemma~1]{csato2002sparse}, the posterior process mean and covariance functions of a GP prior, combined with a likelihood function and $\dataset$ can be stated as:
 \begin{equation}  \label{eq:gp_pred}
- \mu(\vx_i)_\textrm{post} = \vk_{\vx i}^\top \valpha \quad \text{and} \quad
-  \kappa(\mathbf{x}_i, \mathbf{x}_i')_\textrm{post} = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
+ \myexpect_{p(f_i \mid\vy)}[f_i] = \vk_{\vx i}^\top \valpha \quad \text{and} \quad
+\mathrm{Var}_{p(f_{i}\mid\vy)}[f_i] = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
 \end{equation}
-, the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{m \times m}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
+where $f_i = f_\weights(\vx_i)$, the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{m \times m}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
 The dual parameters consist of the vector $\valpha \in \R^{m}$ and vector $\vbeta \in \R^{m}$, defined as:
@@
 	\setlength{\tabcolsep}{6pt}
-	\setlength{\tblw}{0.2\textwidth}
+	\setlength{\tblw}{0.15\textwidth}
 
@@
 	}
+
+    % THE TABLE CAN BE FORMATTED MORE LIKE THIS
+    \begin{tabular}{l l C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
+    \toprule
+    & Method & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ & OOD-AUC~$\uparrow$  \\
+    \midrule
+    \multirow{2}{*}{FMNIST} 
+    & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\    
+    \midrule
+    \multirow{2}{*}{CIFAR-10} 
+    & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\    
+    \bottomrule
+    \end{tabular}
 

### 2023-05-15 bnn-predictive/experiments/scripts/imginference.py
Continue with update sketch

@@ -2,7 +2,7 @@ import os
 import numpy as np
 import pickle
 import torch
-from torch.utils.data import DataLoader
+from torch.utils.data import DataLoader, ConcatDataset
 from torch.utils.data.dataset import Subset
 from torch.distributions import Categorical, Normal
 from tqdm import tqdm
@@ -175,9 +175,10 @@ def retrain_and_update(state, svgp, likelihood, ds_test, ds_train, name='sparse_
     state[f"svgp_ntk_{name}_updated"] = evaluate_one(likelihood, yte, gstar_update)
 
     # Retrain network
-    train_update_loader = ds_train + ds_update
+    ds_train_update = ConcatDataset(ds_train, ds_update)
+    train_update_loader = DataLoader(ds_train_update, batch_size=batch_size)
 
-    model = retrain_nn(svgp, train_update_loader, delta=svgp.prior.delta)
+    model = retrain_nn(svgp, train_update_loader, delta=svgp.prior.delta, device=device)
     gstar_update, yte = get_map_predictive(model=model, loader=batched_update)
     state[f'nn_retrain_map'] = evaluate_one(likelihood, yte, gstar_update)
 
@@ -194,7 +195,6 @@ def retrain_nn(svgp, train_loader, delta, lr=1e-3, device='cpu', n_epochs=500):
             optimizer.step()
         scheduler.step()
     return svgp.network
-
 
 
 def main(

### 2023-05-15 paper/main.tex
updated cl related works

--- 2023-05-15 paper/main.tex
@@
 The approaches proposed in the CL literature can be categorized into inference-based, reharsal-based, and model-based methods, we refer the reader to \citep{parisi2019continual, de2021continual} for complete reviews.
-Many methods in the first category tackled this problem with weight-space regularization, such as EWC~\cite{kirkpatrick2017overcoming}, SI~\cite{zenke17a}), or VCL~\cite{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone.
-However, encoding functional knowledge in the weights does not guarantees a good quality of the predictions, and thus recent methods such as DER~\cite{buzzega2020dark}, FROMP~\cite{pan2020continual}, and S-FSVI~\cite{rudner2022continual} have focused on function-space regularization.
+The methods in the first category usually tackle this problem with weight-space regularization, such as EWC~\cite{kirkpatrick2017overcoming}, SI~\cite{zenke17a}), or VCL~\cite{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone.
+However, encoding functional knowledge in the weights does not guarantees a good quality of the predictions, thus a better to introduce a function-space regularization \citep{li2018lwf, benjamin2018measuring, titsias2019functional, buzzega2020dark, pan2020continual, rudner2022continual}.
+These methods bridge the gap between objective and reharsal-based methods, since they rely on a subset of the training data for each task to compute the regularization term.
+Recent methods, such as DER~\cite{buzzega2020dark}, FROMP~\cite{pan2020continual}, and S-FSVI~\cite{rudner2022continual} achieve state-of-the-art performances among the objective-based techniques in several CL benchmarks.
 % It should be written clearly that our method actually is doing a "functional" reharsal, because we store a set of inducing points that are replayed in order to check if the logits change.
@@
 With this kernel function, we can then combine it with the dataset $\dataset$ to form the posterior $q(\vf)$.
-\citet{khan2019approximate} took a similar approach, but instead of fitting the GP posterior to the actual $\vy$, but a transformation of $\vy$ which they refer to as pseudo-data.\todo{The reader may wonder what is pseudo-data then A: Is this better?} Similarly, \citet{immerImprovingPredictionsBayesian2021} obtain the same covariance function but a different mean because they rely on a first order approximation of the neural network to form a Bayesian GLM model.
+\citet{khan2019approximate} took a similar approach, but instead of fitting the GP posterior to the actual $\vy$, but a transformation of $\vy$ which they refer to as pseudo-data.
+Similarly, \citet{immerImprovingPredictionsBayesian2021} obtain the same covariance function but a different mean because they rely on a first order approximation of the neural network to form a Bayesian GLM model.
 Both approaches attempted to adjust the GP posterior mean function to ensure the predictions are from the neural network $f_{\vw^*}(\vx)$.

### 2023-05-15 paper/main.tex
fixed typos

@@
 One common approach for uncertainty with neural networks is a Laplace-GGN approximation \citep{daxberger2021laplace}, which takes a trained neural network and linearises it around the optimal weights.
-The Hessian can be efficiently approximated using the generalised Gauss--Newton approximation \cite{botev2017practical} but typically involves a cubic scaling in the number of parameters, in practice a further approximation such as the Kronecker factorisation \cite{martens2015optimizing,ritter2018kfac} is needed.
+The Hessian can be efficiently approximated using the generalized Gauss--Newton approximation (GGN)~\cite{botev2017practical} but typically involves a cubic scaling in the number of parameters, in practice a further approximation such as the Kronecker factorisation \cite{martens2015optimizing,ritter2018kfac} is needed.
 The resulting linear model can be used to obtain uncertainty estimates and refine the neural network predictions \citep{immer2021scalable}, and is linear with respect to the weights.
@@
 % $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i)$
-with the Generalized Gaussian-Newton approximation (GGN).
+with the GGN.
 Following the work of \citep{khan2019approximate}, we can view this approximation as building an approximate linear model of the neural network as $\hat{f}_\weights(\mathbf{x}_i) = \Jac{\weights_*}{\mathbf{x}_i} \, \weights$, where $\Jac{\weights}{\mathbf{x}_i} \coloneqq \nabla_\weights f(\mathbf{x}_i)^\top \in \R^{C \times P}$ is the Jacobian at the MAP.

### 2023-05-15 src/rl/train.py
deleted torch replay buffer

@@ -25,54 +25,10 @@ import wandb
 from dm_env import specs, StepType
 from omegaconf import DictConfig, OmegaConf
 from src.rl.custom_types import Action, State
-from src.rl.utils import EarlyStopper, set_seed_everywhere
+from src.rl.utils import EarlyStopper, set_seed_everywhere, ReplayBuffer
 from tensordict import TensorDict
 
-
-Transition = namedtuple("Transition", ("state", "action", "next_state", "reward"))
-
-
-class ReplayMemory(object):
-    def __init__(self, capacity: int, batch_size: int, device):
-        self.memory = deque([], maxlen=capacity)
-        self.batch_size = batch_size
-        self.device = device
-
-    def push(self, state: State, action: Action, next_state: State, reward):
-        """Save a transition"""
-        self.memory.append(
-            Transition(state=state, action=action, next_state=next_state, reward=reward)
-        )
-        # self.memory.append(Transition(*args))
-
-    def sample(self, batch_size=None):
-        if batch_size is None:
-            batch_size = self.batch_size
-        samples = random.sample(self.memory, batch_size)
-        states = []
-        actions = []
-        rewards = []
-        next_states = []
-        for sample in samples:
-            # print("sample {}".format(sample))
-            states.append(torch.Tensor(sample.state).to(self.device))
-            actions.append(torch.Tensor(sample.action).to(self.device))
-            rewards.append(torch.Tensor(sample.reward).to(self.device))
-            next_states.append(torch.Tensor(sample.next_state))
-        states = torch.stack(states, 0).to(self.device)
-        actions = torch.stack(actions, 0).to(self.device)
-        rewards = torch.stack(rewards, 0).to(self.device)
-        next_states = torch.stack(next_states, 0).to(self.device)
-        return {
-            "state": states,
-            "action": actions,
-            "reward": rewards,
-            "next_state": next_states,
-        }
-        # return random.sample(self.memory, batch_size)
-
-    def __len__(self):
-        return len(self.memory)
+# Transition = namedtuple("Transition", ("state", "action", "next_state", "reward"))
 
 
 @hydra.main(version_base="1.3", config_path="./configs", config_name="main")
@@ -152,14 +108,14 @@ def train(cfg: DictConfig):
     #     pin_memory=False,
     #     # prefetch=prefetch,
     # )
[…]

### 2023-05-15 src/rl/train.py
rename replay memory replay_buffer

@@ -117,7 +117,7 @@ def train(cfg: DictConfig):
     #     pin_memory=False,
     # )
     print("num_train_steps {}".format(num_train_steps))
-    replay_memory = ReplayMemory(
+    replay_memory = ReplayBuffer(
         capacity=num_train_steps, batch_size=cfg.batch_size, device=cfg.device
     )
     # replay_buffer = ReplayMemory(capacity=num_train_steps, batch_size=cfg.batch_size)

### 2023-05-15 src/rl/train.py
change MSE/NLPD logging to work with laplace

@@ -481,6 +481,15 @@ def train(cfg: DictConfig):
                 )
                 if isinstance(
                     agent.transition_model,
+                    src.rl.models.transitions.SVGPTransitionModel,
+                ):
+                    (
+                        state_diff_mean,
+                        state_diff_var,
+                        _,
+                    ) = agent.transition_model.svgp.predict(state_action_inputs)
+                elif isinstance(
+                    agent.transition_model,
                     src.rl.models.transitions.NTKSVGPTransitionModel,
                 ):
                     (
@@ -492,12 +501,19 @@ def train(cfg: DictConfig):
                         (state_diff_nn - state_diff_output) ** 2
                     )
                     wandb.log({"mse_transition_model_nn": mse_transition_model_nn})
-                else:
-                    (
-                        state_diff_mean,
-                        state_diff_var,
-                        _,
-                    ) = agent.transition_model.svgp.predict(state_action_inputs)
+                elif isinstance(
+                    agent.transition_model,
+                    src.rl.models.transitions.LaplaceTransitionModel,
+                ):
+                    state_diff_mean, state_diff_var = agent.transition_model.la(
+                        state_action_inputs
+                    )
+                    state_diff_var = torch.diagonal(state_diff_var, dim1=-1, dim2=-2)
+                    state_diff_nn = agent.transition_model.network(state_action_inputs)
+                    mse_transition_model_nn = torch.mean(
+                        (state_diff_nn - state_diff_output) ** 2
+                    )
+                    wandb.log({"mse_transition_model_nn": mse_transition_model_nn})
 
                 # Log transition model stuff
                 mse_transition_model = torch.mean(

### 2023-05-15 paper/main.tex

@@
 terms of parameters can be converted from the weight space to the function space (see Ch.~2.1 in \cite{rasmussen2006gaussian}) as follows:\begin{equation} \label{eq:weight_func}
-g_\weights(\mathbf{x}_{i}) = \phi^\top\!(\vx_i) \, \vw \implies \mu(\vx_i) = 0 \quad \kappa(\mathbf{x}_i, \mathbf{x}_i') = \frac{1}{\delta} \phi(\vx_i)^\top \phi(\vx_i).
+f_\weights(\vx) \approx 
+%g_\weights(\mathbf{x}) = 
+\phi^\top\!(\vx) \, \vw \implies \mu(\vx) = 0 \quad \kappa(\vx, \vx') = \frac{1}{\delta} \phi^\T\!(\vx) \, \phi(\vx')
 \end{equation}
@@
 with the GGN.
-Following the work of \citep{khan2019approximate}, we can view this approximation as building an approximate linear model of the neural network as $\hat{f}_\weights(\mathbf{x}_i) = \Jac{\weights_*}{\mathbf{x}_i} \, \weights$, where $\Jac{\weights}{\mathbf{x}_i} \coloneqq \nabla_\weights f(\mathbf{x}_i)^\top \in \R^{C \times P}$ is the Jacobian at the MAP.
-Using the Hessian of the approximate model, we arrive at the Laplace-GGN posterior for $q(\vw)$.
+Following the work of \citep{khan2019approximate}, we can view this approximation as building an approximate linear model of the neural network as $f_{\weights^*}(\vx) \approx 
+%g_{\weights}(\vx) = 
+\Jac{\weights_*}{\vx} \, \weights$, where $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{C \times P}$ is the Jacobian at the MAP.
+Using the Hessian of the approximate model, we arrive at the Laplace-GGN approximate posterior for $q(\vw)$.
 \todo{do we need this sentence about the Hessian to get Laplace-GGN??}
-Therefore, the GGN approximate linear model can be used to convert our weight space model to the function space by,
+Therefore, the Laplace-GGN linear model can be used to convert our weight space model to the function space by,
 \begin{equation} 
@@
 % g(\vx) \sim \GP \left( \mu(\vx), \kappa(\vx, \vx') \right) \quad \text{with} \quad
-  \mu(\vx_i) =  0 \quad \text{and} \quad
-  \kappa(\mathbf{x}_i, \mathbf{x}_i')
-  = \frac{1}{\delta} \Jac{\weights^*}{\mathbf{x}_i}\JacT{\weights^*}{\mathbf{x}_i'},
+  \mu(\vx) =  0 \quad \text{and} \quad
+  \kappa(\vx, \vx')
+  = \frac{1}{\delta} \Jac{\weights^*}{\vx} \, \JacT{\weights^*}{\vx'}, 
 \end{equation}
 where the kernel is the so-called Neural Tangent Kernel (NTK, \cite{jacot2018neural}).
+In \cref{eq-laplace-approx-function-space}, for notational convenience, we restricted the function output to single dimension, but this could be easily extend for the multi-dimensional case.
 With this kernel function, we can then combine it with the dataset $\dataset$ to form the posterior $q(\vf)$.
@@
 % Definition of CL -> a sequence of tasks 
+% Possible storyline:
+after each task we use the model
+
 In this paper we consider the Continual learning setting were a sequence of disjoint sets

### 2023-05-15 paper/main.tex
Placeholders

@@
 \newcommand{\mbf}[1]{\mathbf{#1}}
+\renewcommand{\mid}{\,|\,}
 
@@
 
-\section{Sparse Function-space Sequential Learning}
+\section{Sparse function-space sequential learning}
 
@@
 
-\subsection{Sparse functional regularization (SFR) in Continual learning}
+\subsection{Sparse functional regularization (SFR) in continual learning}
 % Definition of CL -> a sequence of tasks 
@@
     % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
-	\input{tables/img_super.tex}
+	%\input{tables/img_super.tex}
 \end{table}
@@
 
-\section{Discussion and Conclusion}
+\section{Discussion and conclusion}
 \label{sec:conclusion}
+%
 
@@
 
-\section{Method Details}
-
+This supplementary document is organized as follows. 
+%
+\cref{app:method} provides a more extensive overview of the techncical details of \our.
+%
+\cref{app:cl} covers the sparse-functional regularisation (SFR) setup for continual learning.
+%
+\cref{app:rl} provides a more extensive writeup of the reinforcement learning setup used in the experiments.
+%
+\cref{app:experiments} provides the full details of each individual experiments in the main paper.
+
+\section{Method details}
+\label{app:method}
+%
 Optionally include extra information (complete proofs, additional experiments and plots) in the appendix.
@@
 
-\section{Model-based Reinforcement Learning}
-\label{sec-rl-appendix}
+\section{Sparse functional regularisation in continual learning}
+\label{app:cl}
+
+\subsection{Extending the CL regularizer to multi-class settings}
+\begin{equation}
+	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{C \times m \times m} \quad \MKzz \in \R^{C \times m \times m} 
+\end{equation}
+
+\begin{equation}
+	\mathcal{R_\textit{SFR}}(\mathbf{w}) = \sum_{s=1}^{t-1}	\sum_{k \in 	C}\left[\left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s}, k}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s, k}}(\MZ_s) \right) \right]
+\end{equation}
+
+\section{Sparse functional model-based reinforcement learning}
+\label{app:rl}
 
@@
 
-\section{Extending the CL regularizer to multi-class settings}
-\begin{equation}
-	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{C \times m \times m} \quad \MKzz \in \R^{C \times m \times m} 
-\end{equation}
-
-\begin{equation}
-	\mathcal{R_\textit{SFR}}(\mathbf{w}) = \sum_{s=1}^{t-1}	\sum_{k \in 	C}\left[\left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s}, k}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s, k}}(\MZ_s) \right) \right]
-\end{equation}
+\section{Experiment details}
+\label{app:experiments}
+
+\subsection{Uncertainty quantification on UCI data sets}
+\label{app:uci}
+
+\subsection{Uncertainty benchmarks for image data}
+\label{app:image}
+
+\subsection{Sparse functional regularisation in continual learning}
+\label{app:cl-experiment}
+
+\subsection{Reinforcement learning experiment}
+\label{app:rl-experiment}
 

### 2023-05-15 paper/main.tex
Merge bib files

@@
 \citet{khan2019approximate} took a similar approach, but instead of fitting the GP posterior to the actual $\vy$, but a transformation of $\vy$ which they refer to as pseudo-data.
-Similarly, \citet{immerImprovingPredictionsBayesian2021} obtain the same covariance function but a different mean because they rely on a first order approximation of the neural network to form a Bayesian GLM model.
+Similarly, \citet{immer2021improving} obtain the same covariance function but a different mean because they rely on a first order approximation of the neural network to form a Bayesian GLM model.
 Both approaches attempted to adjust the GP posterior mean function to ensure the predictions are from the neural network $f_{\vw^*}(\vx)$.
@@
 Replacing \cref{eq:dual_param_laplace} in to \cref{eq-laplace-approx-function-space} and we arrive at our GP model based on the converged neural network.
-Again this is similar to what was arrived at for \citet{immerImprovingPredictionsBayesian2021} for the posterior variance function, but they instead use the $f_{\vw^*}(\vx)$ for the posterior mean and fail to spot the significance of the dual variables.
+Again this is similar to what was arrived at for \citet{immer2021improving} for the posterior variance function, but they instead use the $f_{\vw^*}(\vx)$ for the posterior mean and fail to spot the significance of the dual variables.
 The problem with \cref{eq:gp_pred} is that to make predictions and compute variances we must incur a cost of $O(n^3)$ which limits the use of the GP on large data sets.
@@
 Crucially given the structure of our probabilistic model, our sparse dual variables \cref{eq:dual_sparse} are a compact form of the full model projected using the kernel.
-Our approach contrasts to \citet{immerImprovingPredictionsBayesian2021}, which uses a subset of the full model, a less principled approach to build a sparse model given it ignores the information in the dataset.
+Our approach contrasts to \citet{immer2021improving}, which uses a subset of the full model, a less principled approach to build a sparse model given it ignores the information in the dataset.
 It is important to highlight that the sparsifying approach is independent of the approximate inference technique.
@@
 
-Similarly to the UCI experiments, we trained neural networks (CNN, architexture matches \citet{immerImprovingPredictionsBayesian2021}) for the FMNIST and CIFAR10 classification tasks.
+Similarly to the UCI experiments, we trained neural networks (CNN, architexture matches \citet{immer2021improving}) for the FMNIST and CIFAR10 classification tasks.
 After training, we computed the duals for NN2SVGP and used the resulting SVGP for uncertainty estimates, see \cref{tbl:imagesuper}.
@@
 \bibliographystyle{abbrvnat}
-\bibliography{zotero-library,bibliography}
+\bibliography{bibliography}%zotero-library
 \endgroup

### 2023-05-15 paper/main.tex
rewrite section 3

@@
 
-\textbf{Uncertainty quantification}
+\textbf{Uncertainty quantification} \todo{Move this section to the related work}
 Bayesian inference offers a principled approach to quantifying uncertainty in neural networks.
@@
 \section{\our: Sparse function-space represenation of neural networks}
-\paragraph{Linearization in the dual parameters}
-As stated in \citet[Lemma~1]{csato2002sparse}, the posterior process $f_{\textrm{post}}$ mean and covariance functions of a GP prior, combined with a likelihood function and $\dataset$ can be parameterized:
+\paragraph{GP in the dual parameters}
+As stated in \citet[Parameterization Lemma~1]{csato2002sparse}, the posterior process $f_{\textrm{post}}$ found through the Bayesian update equation using  GP prior and likelihood function can be parameterized by $\valpha$ and $\vbeta$:
 \begin{equation}  \label{eq:gp_pred}
@@
 \end{equation}
-, the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{m \times m}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
-The dual parameters consist of the vector $\valpha \in \R^{m}$ and vector $\vbeta \in \R^{m}$, defined as:
+the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{m \times m}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
+The dual parameters are the vector $\valpha \in \R^{m}$ and vector $\vbeta \in \R^{m}$, defined as:
 \begin{equation}
@@
 \alpha_i \coloneqq \myexpect_{p(\vw \mid \vy)}[\nabla_{f_i}\log p(y_i \mid f_i)],  \quad
-\beta_i \coloneqq - \myexpect_{p(\vw \mid \vy)}[\nabla^2_{f_i f_i}\log p(y_i \mid f_i)] ,
-\end{equation}\todo{ More explination of the dual equation 6 the loss landscape link. Perbutation point linked directly to that here. }
-%
-The parameters $(\alpha_i, \beta_i)$ are the dual parameters that arise in the dual formulations used in, for example, support vector machines \citep{cortes1995support}, whose origins are found in work by \citet{kimeldorf1971some}.
-The above relations holds for generic likelihoods, and no approximations are involved as the expectation is under the exact posterior.
-The question is how do we form the dual variables without access to the exact posterior and different approximate inference techniques solve the question in different ways.
-Bound techniques such as \citet{jaakkola1997variational} attempt to bound the integral thus making the integral tractable, while Expecation Propogation (EP) as used in \citet{csato2002sparse} iteratively finds dual variables but sets them to log of the expectation of the approximate posterior.
-Meanwhile variational inference  \cite{khan2017conjugate, adam2021dual} find them using the variational approximation of the posterior to solve the integral.
-
-\paragraph{Neural network dual variables}
-As we are using the MAP solution of the neural network loss, we will use the Laplace approximation for the dual variables but other techniques could be used.
-As detailed in \cite{wilkinson2023bayes, rasmussen2006gaussian}, the dual variables of the Laplace approximation are the same as removing the posterior averaging from \cref{eq:dual_param}, meaning:
+\beta_i \coloneqq - \myexpect_{p(\vw \mid \vy)}[\nabla^2_{f_i f_i}\log p(y_i \mid f_i)] .
+\end{equation}
+%
+The above relations hold for generic likelihoods, and no approximations are involved as the expectation is under the exact posterior.
+It also highlights that our approximate inference technique, while usually considered a posterior approximation, can instead be seen as approximating the expectation of gradients of loss/likelihoods.
+In \citet{csato2002sparse}, they iteratively find dual variables setting them to log the expectation of the approximate posterior.
+At the same time, in \cite{adam2021dual, chang2020fast}, they showed this relationship for variational Gaussian processes where the above expectation is with respect to the approximate posterior from the variational approximation.
+The parameter $\alpha$ relates to non-Bayesian approaches, for example, support vector machines \citep{cortes1995support}, whose origins are found in work by \citet{kimeldorf1971some}.
+The above relations hold for generic likelihoods, and no approximations are involved as the expectation is under the exact posterior.
+For more detail, see \citet{wilkinson2023bayes}, which shows the links between approximate inference methods and how they solve the \cref{eq:dual_param}.
+
+\paragraph{Dual parameters from NN}
+Given we are making a Laplace approximation of the neural network we can remove the expectation over the posterior to find the following approximate dual variables (see Ch.~3.4.1 in \cite{rasmussen2006gaussian} for derivation).
+Meaning we arrive at the following dual variables.
 \begin{equation}
@@
 Replacing \cref{eq:dual_param_laplace} in to \cref{eq-laplace-approx-function-space} and we arrive at our GP model based on the converged neural network.
-Again this is similar to what was arrived at for \citet{immer2021improving} for the posterior variance function, but they instead use the $f_{\vw^*}(\vx)$ for the posterior mean and fail to spot the significance of the dual variables.
+Again this is similar to what was arrived at for \citet{immerImprovingPredictionsBayesian2021} for the posterior variance function, but they instead use the $f_{\vw^*}(\vx)$ for the posterior mean and fail to spot the significance of the dual variables.
 The problem with \cref{eq:gp_pred} is that to make predictions and compute variances we must incur a cost of $O(n^3)$ which limits the use of the GP on large data sets.
 
-\subsection{Sparse dual Gaussian process} 
+\paragraph{Sparsifying the NNGP}
 \label{sec:sparse-dual-gp}
@@
 Given that we have our dual variables derived from our neural network predictions and kernel function, we could use any approximation.
-We decide to follow the sparsifying approach of \citet{titsias2009variational} and also used in the DITC approximaton \cite{quinonero2005unifying}, which is to define the marginal distribution as $q_{\vu}(\vf)  = \int p(\vf  \mid \vu) q(\vu)  d\vu$.
+We decide to follow the sparsifying approach of \citet{titsias2009variational} and also used in the DTC approximaton \cite{quinonero2005unifying}, which is to define the marginal predictive distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) q(\vu)  d\vu$.
 Given that we have $p(f_i  \mid \vu)$ determined by our GP prior, the goal is to find a $q(\vu)$.
+
 As was shown in \cite{adam2021dual}, the posterior under this model has a particular structure similar to \cref{eq:gp_pred}.
@@
 In order to make the link to the dual variables defined in \cref{eq:dual_param} we write them in the sparse GP in the dual variable form.
-
+%
 \begin{equation} 
@@
 \end{equation}
+the sparse dual variables are now a sum over all data points, with $\valpha_{\vu} \in \R^{M}$ and $\vbeta_{\vu} \in \R^{M  \times M}$.
 Using the sparse definition of the dual variables our sparse GP posterior takes the following form:

### 2023-05-15 paper/main.tex
rewrite section 3

@@
 \paragraph{Dual parameters from NN}
-Given we are making a Laplace approximation of the neural network we can remove the expectation over the posterior to find the following approximate dual variables (see Ch.~3.4.1 in \cite{rasmussen2006gaussian} for derivation).
+Given we are making a Laplace approximation of the neural network we can remove the expectation over the posterior (see Ch.~3.4.1 in \cite{rasmussen2006gaussian} for derivation).
 Meaning we arrive at the following dual variables.
@@
 
-Replacing \cref{eq:dual_param_laplace} in to \cref{eq-laplace-approx-function-space} and we arrive at our GP model based on the converged neural network.
-Again this is similar to what was arrived at for \citet{immerImprovingPredictionsBayesian2021} for the posterior variance function, but they instead use the $f_{\vw^*}(\vx)$ for the posterior mean and fail to spot the significance of the dual variables.
+Substiuting \cref{eq:dual_param_laplace} in to \cref{eq:gp_pred} and we arrive at our GP model based on the converged neural network.
+Again this is similar to what was derived in \citet{immerImprovingPredictionsBayesian2021} for the posterior variance function, but they instead use the $f_{\vw^*}$ for the posterior mean and fail to spot the significance of the dual variables.
 The problem with \cref{eq:gp_pred} is that to make predictions and compute variances we must incur a cost of $O(n^3)$ which limits the use of the GP on large data sets.
@@
 Many sparsifying approaches exist, we refer the reader to \cite{quinonero2005unifying} for an overview.
-Given that we have our dual variables derived from our neural network predictions and kernel function, we could use any approximation.
-We decide to follow the sparsifying approach of \citet{titsias2009variational} and also used in the DTC approximaton \cite{quinonero2005unifying}, which is to define the marginal predictive distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) q(\vu)  d\vu$.
+Given that we have our dual variables derived from our neural network predictions and a kernel function, we could essentially use any approximation.
+We decide to follow the sparsifying approach of \citet{titsias2009variational} and also used in the DTC appeoximation \cite{quinonero2005unifying}, which is to define the marginal predictive distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) q(\vu)  d\vu$.
 Given that we have $p(f_i  \mid \vu)$ determined by our GP prior, the goal is to find a $q(\vu)$.
@@
 Crucially given the structure of our probabilistic model, our sparse dual variables \cref{eq:dual_sparse} are a compact form of the full model projected using the kernel.
-Our approach contrasts to \citet{immer2021improving}, which uses a subset of the full model, a less principled approach to build a sparse model given it ignores the information in the dataset.
-It is important to highlight that the sparsifying approach is independent of the approximate inference technique.
-The \cref{eq:dual_param} are determined from the neural network.
+
+Our approach contrasts to \citet{immer2021improving}, which uses a subset of the full model to try to reduce complexity, a less principled approach to build a sparse model given it ignores the information in the dataset.
+It is important to highlight that the sparsifying process is independent of the approximate inference technique.
+The \cref{eq:dual_param} are from the neural network definition \cref{eq-empirical-risk}.
 More complicated inference techniques, such as variational inference, could be used, but given its simplicity, we only need a trained neural network; we use a Laplace approximation in our experiments.

### 2023-05-15 bnn-predictive/experiments/scripts/imginference.py
Sketching delta optimization loop

@@ -210,6 +210,7 @@ def main(
     logdelta_min=-5,
     logdelta_max=8,
     res_dir="experiments/results",
+    run_with_best=False,
     run_update=False,
     device="cuda",
 ):
@@ -217,6 +218,7 @@ def main(
 
     eligible_files = list()
     deltas = list()
+    perfs = list()
     for file in os.listdir(os.path.join(res_dir, "models")):
         # strip off filename ending using indexing
         print(file)
@@ -230,24 +232,19 @@ def main(
         ):
             eligible_files.append(os.path.join(res_dir, "models/" + file))
             deltas.append(float(delta))
+            state = torch.load("models/" + file)
+            if "map" not in state:
+                continue
+            perfs.append(state["map"]["nll_va"])
     logging.info(f"Deltas: {deltas}")
-    # start with smallest delta and continue
-    ixlist = np.argsort(deltas)
-    deltas = np.array(deltas)[ixlist]
-    eligible_files = list(np.array(eligible_files)[ixlist])
+    best_file = eligible_files[np.argmin(perfs)]
 
-    train_loader = DataLoader(ds_train, batch_size=256)
-    all_train = DataLoader(ds_train, batch_size=len(ds_train))
-    (X_train, y_train) = next(iter(all_train))
-    X_train = X_train.to(device)
-    y_train = y_train.to(device)
-
+    # Create train, test and val
     torch.manual_seed(seed)
     M = len(ds_test)
     n_inducing = n_inducing_points  # int(len(ds_train)*n_sparse)
     logging.info(f"Train set size: {len(ds_train)}")
     logging.info(f"Num inducing points: {n_inducing}")
-    print(X_train.shape)
     perm_ixs = torch.randperm(M)
     val_ixs, test_ixs = perm_ixs[: int(M / 2)], perm_ixs[int(M / 2) :]
     ds_val = Subset(ds_test, val_ixs)
@@ -258,95 +255,120 @@ def main(
     test_loader = get_quick_loader(
         DataLoader(ds_test, batch_size=batch_size), device=device
     )
+    train_loader = DataLoader(ds_train, batch_size=256)
+    all_train = DataLoader(ds_train, batch_size=len(ds_train))
+    (X_train, y_train) = next(iter(all_train))
+    X_train = X_train.to(device)
+    y_train = y_train.to(device)
 
-    for f, delta in tqdm(list(zip(eligible_files, deltas))):
-        logging.info(f"inference for delta={delta}")
-        state = torch.load(f)
[…]

### 2023-05-15 src/rl/train.py
don't fail when logging mse/nlpd just ignore

@@ -515,18 +515,26 @@ def train(cfg: DictConfig):
                     )
                     wandb.log({"mse_transition_model_nn": mse_transition_model_nn})
 
-                # Log transition model stuff
-                mse_transition_model = torch.mean(
-                    (state_diff_mean - state_diff_output) ** 2
-                )
-                wandb.log({"mse_transition_model_svgp": mse_transition_model})
+                try:
+                    # Log transition model stuff
+                    mse_transition_model = torch.mean(
+                        (state_diff_mean - state_diff_output) ** 2
+                    )
+                    wandb.log({"mse_transition_model_svgp": mse_transition_model})
+                except:
+                    pass
 
-                nlpd_transition_model = -torch.mean(
-                    torch.distributions.Normal(
-                        state_diff_mean, torch.sqrt(state_diff_var)
-                    ).log_prob(state_diff_output)
-                )
-                wandb.log({"nlpd_transition_model": torch.mean(nlpd_transition_model)})
+                try:
+                    nlpd_transition_model = -torch.mean(
+                        torch.distributions.Normal(
+                            state_diff_mean, torch.sqrt(state_diff_var)
+                        ).log_prob(state_diff_output)
+                    )
+                    wandb.log(
+                        {"nlpd_transition_model": torch.mean(nlpd_transition_model)}
+                    )
+                except:
+                    pass
 
                 # print("dataset['reward'] {}".format(dataset["reward"].shape))
                 reward_output = dataset["reward"][:, 0]

### 2023-05-15 paper/main.tex
rewrite section 3

@@
 \begin{equation}  \label{eq:gp_pred}
- \mu(\vx_i)_\textrm{post} = \vk_{\vx i}^\top \valpha \quad \text{and} \quad
-  \kappa(\mathbf{x}_i, \mathbf{x}_i')_\textrm{post} = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
+  \myexpect_{p(f_i \mid\vy)}[f_i]= \vk_{\vx i}^\top \valpha \quad \text{and} \quad
+  \mathrm{Var}_{p(f\mid\vy)}[f_i] = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
 \end{equation}
@@
 The parameter $\alpha$ relates to non-Bayesian approaches, for example, support vector machines \citep{cortes1995support}, whose origins are found in work by \citet{kimeldorf1971some}.
-The above relations hold for generic likelihoods, and no approximations are involved as the expectation is under the exact posterior.
-For more detail, see \citet{wilkinson2023bayes}, which shows the links between approximate inference methods and how they solve the \cref{eq:dual_param}.
+While in \citet{wilkinson2023bayes}, they show links between linearization methods and how they solve the \cref{eq:dual_param}.
 
@@
 More complicated inference techniques, such as variational inference, could be used, but given its simplicity, we only need a trained neural network; we use a Laplace approximation in our experiments.
+Furthermore, our dual variable view of approximate inference means we do not need to resort to retraining a separate sparse GP model.
 

### 2023-05-15 paper/main.tex
update on the CL part

--- 2023-05-15 paper/main.tex
@@
 \newcommand{\mbf}[1]{\mathbf{#1}}
-\renewcommand{\mid}{\,|\,}
 
@@
 % CL section
-\textbf{Function-space methods for sequential learning} The central problem in continual learning is how to deal with the non-stationary nature of the training distribution which causes the training process to overwrite the previously learnt parameters---leading to the model forgetting the previous learnt functions.
-The approaches proposed in the CL literature can be categorized into inference-based, reharsal-based, and model-based methods, we refer the reader to \citep{parisi2019continual, de2021continual} for complete reviews.
-The methods in the first category usually tackle this problem with weight-space regularization, such as EWC~\cite{kirkpatrick2017overcoming}, SI~\cite{zenke17a}), or VCL~\cite{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone.
-However, encoding functional knowledge in the weights does not guarantees a good quality of the predictions, thus a better to introduce a function-space regularization \citep{li2018lwf, benjamin2018measuring, titsias2019functional, buzzega2020dark, pan2020continual, rudner2022continual}.
-These methods bridge the gap between objective and reharsal-based methods, since they rely on a subset of the training data for each task to compute the regularization term.
-Recent methods, such as DER~\cite{buzzega2020dark}, FROMP~\cite{pan2020continual}, and S-FSVI~\cite{rudner2022continual} achieve state-of-the-art performances among the objective-based techniques in several CL benchmarks.
+\textbf{Function-space methods for sequential learning} The central problem in continual learning is how to deal with the non-stationary nature of the training distribution, which causes the training process to overwrite the previously learnt parameters---leading to the model forgetting the previously learnt functions.
+The approaches proposed in the CL literature can be categorized into inference-based, rehearsal-based, and model-based methods; we refer the reader to \citep{parisi2019continual, de2021continual} for complete reviews.
+The methods in the first category usually tackle this problem with weight-space regularization, such as EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke17a}), or VCL~\citep{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone.
+However, encoding functional knowledge in the weights does not guarantee a good quality of the predictions, thus a better to introduce a function-space regularization \citep{li2018lwf, benjamin2018measuring, titsias2019functional, buzzega2020dark, pan2020continual, rudner2022continual}.
+These methods bridge the gap between objective and rehearsal-based methods since they rely on a subset of the training data for each task to compute the regularization term.
+Recently proposed methods, such as DER~\citep{buzzega2020dark}, FROMP~\citep{pan2020continual}, and S-FSVI~\citep{rudner2022continual} achieve state-of-the-art performances among the objective-based techniques in several CL benchmarks.
+
 % It should be written clearly that our method actually is doing a "functional" reharsal, because we store a set of inducing points that are replayed in order to check if the logits change.
@@
 
-In supervised learning, given a data set $\dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with input $\mathbf{x}_i \in \inputDomain$ and output $\mathbf{y}_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w} : \inputDomain \to \outputDomain$, are usually trained to minimize the (regularized) empirical risk,
+In supervised learning, given a data set $\dataset = \dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with input $\mathbf{x}_i \in \inputDomain$ and output $\mathbf{y}_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w} : \inputDomain \to \outputDomain$, are usually trained to minimize the (regularized) empirical risk,
 %
@@
 
-\textbf{Uncertainty quantification} \todo{Move this section to the related work}
+\textbf{Uncertainty quantification}
 Bayesian inference offers a principled approach to quantifying uncertainty in neural networks.
@@
 where the kernel is the so-called Neural Tangent Kernel (NTK, \cite{jacot2018neural}).
-In \cref{eq-laplace-approx-function-space}, for notational convenience, we restricted the function output to single dimension, but this could be easily extend for the multi-dimensional case.
+In \cref{eq-laplace-approx-function-space} and \cref{eq:weight_func}, for notational convenience, we restricted the function output to single dimension, but this could be easily extend for the multi-dimensional case.
 With this kernel function, we can then combine it with the dataset $\dataset$ to form the posterior $q(\vf)$.
 \citet{khan2019approximate} took a similar approach, but instead of fitting the GP posterior to the actual $\vy$, but a transformation of $\vy$ which they refer to as pseudo-data.
-Similarly, \citet{immer2021improving} obtain the same covariance function but a different mean because they rely on a first order approximation of the neural network to form a Bayesian GLM model.
+Similarly, \citet{immerImprovingPredictionsBayesian2021} obtain the same covariance function but a different mean because they rely on a first order approximation of the neural network to form a Bayesian GLM model.
 Both approaches attempted to adjust the GP posterior mean function to ensure the predictions are from the neural network $f_{\vw^*}(\vx)$.
@@
 \section{\our: Sparse function-space represenation of neural networks}
-\paragraph{GP in the dual parameters}
-As stated in \citet[Parameterization Lemma~1]{csato2002sparse}, the posterior process $f_{\textrm{post}}$ found through the Bayesian update equation using  GP prior and likelihood function can be parameterized by $\valpha$ and $\vbeta$:
+\paragraph{Linearization in the dual parameters}
+As stated in \citet[Lemma~1]{csato2002sparse}, the posterior process $f_{\textrm{post}}$ mean and covariance functions of a GP prior, combined with a likelihood function and $\dataset$ can be parameterized:
 \begin{equation}  \label{eq:gp_pred}
@@
 \end{equation}
-the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{m \times m}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
-The dual parameters are the vector $\valpha \in \R^{m}$ and vector $\vbeta \in \R^{m}$, defined as:
+, the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{m \times m}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
+The dual parameters consist of the vector $\valpha \in \R^{m}$ and vector $\vbeta \in \R^{m}$, defined as:
 \begin{equation}
@@
 \alpha_i \coloneqq \myexpect_{p(\vw \mid \vy)}[\nabla_{f_i}\log p(y_i \mid f_i)],  \quad
-\beta_i \coloneqq - \myexpect_{p(\vw \mid \vy)}[\nabla^2_{f_i f_i}\log p(y_i \mid f_i)] .
-\end{equation}
-%
-The above relations hold for generic likelihoods, and no approximations are involved as the expectation is under the exact posterior.
-It also highlights that our approximate inference technique, while usually considered a posterior approximation, can instead be seen as approximating the expectation of gradients of loss/likelihoods.
-In \citet{csato2002sparse}, they iteratively find dual variables setting them to log the expectation of the approximate posterior.
-At the same time, in \cite{adam2021dual, chang2020fast}, they showed this relationship for variational Gaussian processes where the above expectation is with respect to the approximate posterior from the variational approximation.
-The parameter $\alpha$ relates to non-Bayesian approaches, for example, support vector machines \citep{cortes1995support}, whose origins are found in work by \citet{kimeldorf1971some}.
-The above relations hold for generic likelihoods, and no approximations are involved as the expectation is under the exact posterior.
-For more detail, see \citet{wilkinson2023bayes}, which shows the links between approximate inference methods and how they solve the \cref{eq:dual_param}.
-
-\paragraph{Dual parameters from NN}
-Given we are making a Laplace approximation of the neural network we can remove the expectation over the posterior to find the following approximate dual variables (see Ch.~3.4.1 in \cite{rasmussen2006gaussian} for derivation).
-Meaning we arrive at the following dual variables.
+\beta_i \coloneqq - \myexpect_{p(\vw \mid \vy)}[\nabla^2_{f_i f_i}\log p(y_i \mid f_i)] ,
+\end{equation}\todo{ More explination of the dual equation 6 the loss landscape link. Perbutation point linked directly to that here. }
+%
+The parameters $(\alpha_i, \beta_i)$ are the dual parameters that arise in the dual formulations used in, for example, support vector machines \citep{cortes1995support}, whose origins are found in work by \citet{kimeldorf1971some}.
+The above relations holds for generic likelihoods, and no approximations are involved as the expectation is under the exact posterior.
+The question is how do we form the dual variables without access to the exact posterior and different approximate inference techniques solve the question in different ways.
+Bound techniques such as \citet{jaakkola1997variational} attempt to bound the integral thus making the integral tractable, while Expecation Propogation (EP) as used in \citet{csato2002sparse} iteratively finds dual variables but sets them to log of the expectation of the approximate posterior.
+Meanwhile variational inference  \cite{khan2017conjugate, adam2021dual} find them using the variational approximation of the posterior to solve the integral.
+
+\paragraph{Neural network dual variables}
+As we are using the MAP solution of the neural network loss, we will use the Laplace approximation for the dual variables but other techniques could be used.
+As detailed in \cite{wilkinson2023bayes, rasmussen2006gaussian}, the dual variables of the Laplace approximation are the same as removing the posterior averaging from \cref{eq:dual_param}, meaning:
 \begin{equation}
@@
 
-\paragraph{Sparsifying the NNGP}
+\subsection{Sparse dual Gaussian process} 
 \label{sec:sparse-dual-gp}
@@
 Given that we have our dual variables derived from our neural network predictions and kernel function, we could use any approximation.
-We decide to follow the sparsifying approach of \citet{titsias2009variational} and also used in the DTC approximaton \cite{quinonero2005unifying}, which is to define the marginal predictive distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) q(\vu)  d\vu$.
+We decide to follow the sparsifying approach of \citet{titsias2009variational} and also used in the DITC approximaton \cite{quinonero2005unifying}, which is to define the marginal distribution as $q_{\vu}(\vf)  = \int p(\vf  \mid \vu) q(\vu)  d\vu$.
 Given that we have $p(f_i  \mid \vu)$ determined by our GP prior, the goal is to find a $q(\vu)$.
-
 As was shown in \cite{adam2021dual}, the posterior under this model has a particular structure similar to \cref{eq:gp_pred}.
@@
 In order to make the link to the dual variables defined in \cref{eq:dual_param} we write them in the sparse GP in the dual variable form.
-%
+
 \begin{equation} 
@@
 \end{equation}
-the sparse dual variables are now a sum over all data points, with $\valpha_{\vu} \in \R^{M}$ and $\vbeta_{\vu} \in \R^{M  \times M}$.
 Using the sparse definition of the dual variables our sparse GP posterior takes the following form:
@@
 Crucially given the structure of our probabilistic model, our sparse dual variables \cref{eq:dual_sparse} are a compact form of the full model projected using the kernel.
-Our approach contrasts to \citet{immer2021improving}, which uses a subset of the full model, a less principled approach to build a sparse model given it ignores the information in the dataset.
+Our approach contrasts to \citet{immerImprovingPredictionsBayesian2021}, which uses a subset of the full model, a less principled approach to build a sparse model given it ignores the information in the dataset.
 It is important to highlight that the sparsifying approach is independent of the approximate inference technique.
@@
 
-\subsection{Sparse functional regularization (SFR) in continual learning}
+\subsection{\our for Continual learning}
 % Definition of CL -> a sequence of tasks 
-% Possible storyline:
-after each task we use the model
-
-In this paper we consider the Continual learning setting were a sequence of disjoint sets
-
+In the Continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{n_t}$, which after the task is discarded and cannot be accessed in the later stages of the training.
+However, rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting.
+After each task, we can use our \our to build a compact representation of the neural network and then use that as an additional term to the training loss to regularize the model.
+\todo{this term is replacing the missing data}
+
+% Where the regularizer comes from
+At the end of the training for each task $t$, we compute the Laplace-GGN approximated kernel function for the current model and randomly select $m$ inducing points.
+Given the issues described in the previous sections, related to computing the full covariance posterior $\MKxx$,\todo{this should be $\kappa(\MX_t, \MX_t)$}, we can exploit the dual parameterization to efficiently encode the information from the $\dataset_t$ using the dual parameterization, as follows,
 \begin{equation}
- 	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{m \times m}, \quad \forall s \in [1, t-1]
+ 	\bar{\MB}^{-1}_t = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{m \times m}, 
+ 	\quad 
+ 	\vbeta_{\vu} =  \sum_{i \in \dataset_t} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
+ 	% \quad \forall t \in [1, T]
  \end{equation}
-
+ where $\MKzz$ and $\vkzi$ are the kernel function computed on the inducing points $\MZ_t \in \R^{m \times D}$ for task $t$.
+
+We can then keep a memory buffer $\mathcal{M} = \{(\MZ_t, \vu_t, \bar{\MB}^{-1}_t)\}_{t=1}^T$, where $\MZ_t$ are the inducing points selected from $\dataset_t$ and  $\vu_t = f_{\vw_t^*}(\MZ_t)\in \R^{m}$ are the neural network outputs over them computed with the MAP estimate after task $t$, $\vw_t^*$.
+Note that, for notational convenience, we are extending our neural network notation to be compatible with multiple inputs points, \ie, each $i$th entry is $f_{\vw_t^*}(\vz_i)\in \R$.
+Moreover, we restrict ourselves to single-output neural networks and refer the reader to further details on the multi-output setting to \cref{sec:cl_multioutput}.
+
+After each task, we update $\mathcal{M}$, and we can construct a regularizer term, which aims to reduce the drift of the current model from diverging on the inducing points $\MZ_s$ for all previous tasks $ s \in \left[ 1, t-1 \right]$.
+The resulting regularizer can be computed as follows
 \begin{equation}
-	\mathcal{R}_\textit{SFR}(\weights) = \sum_{s=1}^{t-1} \frac{1}{m} \left[\left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right) \right]
+	\mathcal{R}_\textit{SFR}(\weights, \mathcal{M}) = \sum_{s=1}^{t-1} \frac{1}{m} \left[\left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right) \right].
 \end{equation}
-with $f_\vw(\MZ_{s}), f_{\vw_s}(\MZ_s) \in \R^m$ are vectors of the outputs of the neural networks with the current weights $\vw$ and stored function outputs of the neural network at the MAP optimum for task $s$.
+
+\begin{equation}
+	\mathcal{R}_\textit{SFR}(\weights, \mathcal{M}) = \sum_{s=1}^{t-1} \frac{1}{m} 
+	\left\lVert 
+	f_{\weights}(\MZ_{s}) - \vu_t % f_{\weights_{s}}(\MZ_s)
+	\right\rVert_{\bar{\MB}^{-1}_{s}}.
+\end{equation}
+\todo{choose one option}
+% where $f_\vw(\MZ_{s}) \in \R^m$ are the outputs of neural networks with the current weights $\vw$ and stored function outputs of the neural network at the MAP optimum for task $s$, i.e., each $i$th entry is $f_\cdot(\vz_i) \in \R$.
 
@@
 %\end{equation}
-
+Then, when the training on the successive task, the new objective to minimize takes the following form
 \begin{equation}
-	\weights_t^* = \argmin_{\weights} \mathcal{L}(\mathcal{D}_t, \weights) + \tau \mathcal{R}_\textit{SFR}(\weights)
+	\weights_t^* = \argmin_{\weights} \mathcal{L}(\mathcal{D}_t, \weights) + \tau \mathcal{R}_\textit{SFR}(\weights, \mathcal{M})
 \end{equation}
@@
     % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
-	%\input{tables/img_super.tex}
+	\input{tables/img_super.tex}
 \end{table}
 
-Similarly to the UCI experiments, we trained neural networks (CNN, architexture matches \citet{immer2021improving}) for the FMNIST and CIFAR10 classification tasks.
+Similarly to the UCI experiments, we trained neural networks (CNN, architexture matches \citet{immerImprovingPredictionsBayesian2021}) for the FMNIST and CIFAR10 classification tasks.
 After training, we computed the duals for NN2SVGP and used the resulting SVGP for uncertainty estimates, see \cref{tbl:imagesuper}.
@@
 
-\section{Discussion and conclusion}
+\section{Discussion and Conclusion}
 \label{sec:conclusion}
-%
 
@@
 \bibliographystyle{abbrvnat}
-\bibliography{bibliography}%zotero-library
+\bibliography{zotero-library,bibliography}
 \endgroup
@@
 
-This supplementary document is organized as follows. 
-%
-\cref{app:method} provides a more extensive overview of the techncical details of \our.
-%
-\cref{app:cl} covers the sparse-functional regularisation (SFR) setup for continual learning.
-%
-\cref{app:rl} provides a more extensive writeup of the reinforcement learning setup used in the experiments.
-%
-\cref{app:experiments} provides the full details of each individual experiments in the main paper.
-
-\section{Method details}
-\label{app:method}
-%
+\section{Method Details}
+
 Optionally include extra information (complete proofs, additional experiments and plots) in the appendix.
@@
 
-\section{Sparse functional regularisation in continual learning}
-\label{app:cl}
-
-\subsection{Extending the CL regularizer to multi-class settings}
-\begin{equation}
-	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{C \times m \times m} \quad \MKzz \in \R^{C \times m \times m} 
-\end{equation}
-
-\begin{equation}
-	\mathcal{R_\textit{SFR}}(\mathbf{w}) = \sum_{s=1}^{t-1}	\sum_{k \in 	C}\left[\left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s}, k}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s, k}}(\MZ_s) \right) \right]
-\end{equation}
-
-\section{Sparse functional model-based reinforcement learning}
-\label{app:rl}
+\section{Model-based Reinforcement Learning}
+\label{sec-rl-appendix}
 
@@
 
-\section{Experiment details}
-\label{app:experiments}
-
-\subsection{Uncertainty quantification on UCI data sets}
-\label{app:uci}
-
-\subsection{Uncertainty benchmarks for image data}
-\label{app:image}
-
-\subsection{Sparse functional regularisation in continual learning}
-\label{app:cl-experiment}
-
-\subsection{Reinforcement learning experiment}
-\label{app:rl-experiment}
+\section{Extending the CL regularizer to multi-class settings}
+\label{sec:cl_multioutput}
+\begin{equation}
+	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{C \times m \times m} \quad \MKzz \in \R^{C \times m \times m} 
+\end{equation}
+
+\begin{equation}
+	\mathcal{R_\textit{SFR}}(\mathbf{w}) = \sum_{s=1}^{t-1}	\sum_{k \in 	C}\left[\left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s}, k}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s, k}}(\MZ_s) \right) \right]
+\end{equation}
 

### 2023-05-15 paper/main.tex

--- 2023-05-15 paper/main.tex
@@
 % Our method
-\newcommand{\our}{\textsc{dnn2sgp}\xspace}
+\newcommand{\our}{\textsc{sfr}\xspace}
 
@@
 where the kernel is the so-called Neural Tangent Kernel (NTK, \cite{jacot2018neural}).
-In \cref{eq-laplace-approx-function-space}, for notational convenience, we restricted the function output to single dimension, but this could be easily extend for the multi-dimensional case.
+In \cref{eq-laplace-approx-function-space}, for notational convenience, we restricted the function output to single dimension, but this could be easily extended for the multi-dimensional case.
 With this kernel function, we can then combine it with the dataset $\dataset$ to form the posterior $q(\vf)$.
-\citet{khan2019approximate} took a similar approach, but instead of fitting the GP posterior to the actual $\vy$, but a transformation of $\vy$ which they refer to as pseudo-data.
+\citet{khan2019approximate} took a similar approach, but instead of fitting the GP posterior to the actual $\vy$, they rely on a transformation of $\vy$ referred as pseudo-data.
 Similarly, \citet{immer2021improving} obtain the same covariance function but a different mean because they rely on a first order approximation of the neural network to form a Bayesian GLM model.
@@
 
-\section{\our: Sparse function-space represenation of neural networks}
+\section{\our: Sparse Function-space Represenation of neural networks}
 \paragraph{GP in the dual parameters}
@@
 
-\subsection{Sparse functional regularization (SFR) in continual learning}
+\subsection{\our for Continual Learning}
 % Definition of CL -> a sequence of tasks 
-% Possible storyline:
-after each task we use the model
-
-In this paper we consider the Continual learning setting were a sequence of disjoint sets
-
+In the Continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{n_t}$, which after the task is discarded and cannot be accessed in the later stages of the training.
+However, rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting.
+After each task, we can use our \our to build a compact representation of the neural network and then use that as an additional term to the training loss to regularize the model.
+\todo{this term is replacing the missing data}
+
+% Where the regularizer comes from
+At the end of the training for each task $t$, we compute the Laplace-GGN approximated kernel function for the current model and randomly select $m$ inducing points.
+Given the issues described in the previous sections, related to computing the full covariance posterior $\MKxx$,\todo{this should be $\kappa(\MX_t, \MX_t)$}, we can exploit the dual parameterization to efficiently encode the information from the $\dataset_t$ using the dual parameterization, as follows,
 \begin{equation}
- 	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{m \times m}, \quad \forall s \in [1, t-1]
+ 	\bar{\MB}^{-1}_t = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{m \times m}, 
+ 	\quad 
+ 	\vbeta_{\vu} =  \sum_{i \in \dataset_t} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
+ 	% \quad \forall t \in [1, T]
  \end{equation}
-
+ where $\MKzz$ and $\vkzi$ are the kernel function computed on the inducing points $\MZ_t \in \R^{m \times D}$ for task $t$.
+
+We can then keep a memory buffer $\mathcal{M} = \{(\MZ_t, \vu_t, \bar{\MB}^{-1}_t)\}_{t=1}^T$, where $\MZ_t$ are the inducing points selected from $\dataset_t$ and  $\vu_t = f_{\vw_t^*}(\MZ_t)\in \R^{m}$ are the neural network outputs over them computed with the MAP estimate after task $t$, $\vw_t^*$.
+Note that, for notational convenience, we are extending our neural network notation to be compatible with multiple inputs points, \ie, each $i$th entry is $f_{\vw_t^*}(\vz_i)\in \R$.
+Moreover, we restrict ourselves to single-output neural networks and refer the reader to further details on the multi-output setting to \cref{sec:cl_multioutput}.
+
+After each task, we update $\mathcal{M}$, and we can construct a regularizer term, which aims to reduce the drift of the current model from diverging on the inducing points $\MZ_s$ for all previous tasks $ s \in \left[ 1, t-1 \right]$.
+The resulting regularizer can be computed as follows
 \begin{equation}
-	\mathcal{R}_\textit{SFR}(\weights) = \sum_{s=1}^{t-1} \frac{1}{m} \left[\left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right) \right]
+	\mathcal{R}_\textit{SFR}(\weights, \mathcal{M}) = \sum_{s=1}^{t-1} \frac{1}{m} \left[\left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right) \right].
 \end{equation}
-with $f_\vw(\MZ_{s}), f_{\vw_s}(\MZ_s) \in \R^m$ are vectors of the outputs of the neural networks with the current weights $\vw$ and stored function outputs of the neural network at the MAP optimum for task $s$.
+
+\begin{equation}
+	\mathcal{R}_\textit{SFR}(\weights, \mathcal{M}) = \sum_{s=1}^{t-1} \frac{1}{m} 
+	\left\lVert 
+	f_{\weights}(\MZ_{s}) - \vu_t % f_{\weights_{s}}(\MZ_s)
+	\right\rVert_{\bar{\MB}^{-1}_{s}}.
+\end{equation}
+\todo{choose one option}
+% where $f_\vw(\MZ_{s}) \in \R^m$ are the outputs of neural networks with the current weights $\vw$ and stored function outputs of the neural network at the MAP optimum for task $s$, i.e., each $i$th entry is $f_\cdot(\vz_i) \in \R$.
 
@@
 
-\subsection{Sparse functional regularisation in continual learning}
+\subsection{\our for continual learning}
 \label{app:cl-experiment}
+\section{Extending the CL regularizer to multi-class settings}
+\label{sec:cl_multioutput}
+\begin{equation}
+	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{C \times m \times m} \quad \MKzz \in \R^{C \times m \times m} 
+\end{equation}
+
+\begin{equation}
+	\mathcal{R_\textit{SFR}}(\mathbf{w}) = \sum_{s=1}^{t-1}	\sum_{k \in 	C}\left[\left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s}, k}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s, k}}(\MZ_s) \right) \right]
+\end{equation}
 

### 2023-05-15 paper/main.tex
rewrite section 3

@@
 \newcommand{\vw}{\mbf{w}}
+\newcommand{\va}{\mbf{a}}
 
@@
 \todo{this term is replacing the missing data}
+
+An alternative view of the dual variables is that they parameterize approximate likelihoods as was shown in \citep{adam2021dual} we can rewrite the GP posterior in terms of the following approximate normal distributions:
+\begin{equation}
+ q(\vu) \propto \N(0, \MKzz) \prod_{i=1}^n e^{-\frac{\hat{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 } = \N(0, \MKzz) \, e^{(\tilde{\vy} - \vu)^\top\tilde{\MSigma}^{-1}(\tilde{\vy} - \vu)}  
+\end{equation}
+The first normals are the marginal likelihoods were $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}$,  replacing $\va_i^\top \vu$  wtih $\vx_i^{\top}\vw$ and we can see the similarity between the sparse GP and a linear model where the prior is determined by the kernel matrix.
+To arrive at the MVN Gaussian we need to rearrange the quadratic terms to match the prior sufficient statistics we present a derivation in [appendix].
+Performing conjugate summation of prior and likelihood we would arrive at the sparse GP posterior at the inducing points $\MZ$.
+The correlated covariance structure $\MSigma$ and the corresponding $\tilde{\vy}$ are simply a different form of the sparse dual variables
 

### 2023-05-15 paper/main.tex
Plot

--- 2023-05-15 paper/main.tex
@@
 \todo{this term is replacing the missing data}
+
+An alternative view of the dual variables is that they parameterize approximate likelihoods as was shown in \citep{adam2021dual} we can rewrite the GP posterior in terms of the following approximate normals:
+\begin{equation}
+ q(\vu) \propto \N(0, \MKzz) \prod_{i=1}^n e^{-\frac{\beta}{2}(y_i - \va_i^\top \vu)^2 } = \N(0, \MKzz) \, e^{(\tilde{\vy} - \vu)^\top\tilde{\MSigma}^{-1}(\tilde{\vy} - \vu)}  
+\end{equation}
 
@@
    \setlength{\figureheight}{.5\figurewidth}
-   \pgfplotsset{axis on top}
+   \pgfplotsset{axis on top,ymajorgrids,axis line style={draw=none} }
+   \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
    \input{./fig/rl.tex}

### 2023-05-15 paper/main.tex
Cartpole

--- 2023-05-15 paper/main.tex
@@
  \centering
- \begin{subfigure}{.2\textwidth}
+ \begin{subfigure}[c]{.24\textwidth}
  \resizebox{\textwidth}{!}{%
@@
    % The arm
-   \node[anchor=north,minimum width=1cm,minimum height=14cm,draw=black,rotate=20,rounded corners=5mm,yshift=7mm,xshift=-.3mm,fill=white,draw=black,line width=3pt] at (dot) {};
+   \node[anchor=north,minimum width=1cm,minimum height=14cm,draw=black,rotate=-20,rounded corners=5mm,yshift=7mm,xshift=-.3mm,fill=white,draw=black,line width=3pt] at (dot) {};
    \node[fill=black,circle,minimum size=.5cm] at (dot) {};
@@
    % Arrow
-   \draw[->,black,line width=3pt,-{Latex[length=7mm,width=7mm]}] (1,5) --node[above,outer sep=6pt]{\large $x$} (4.5,5);
+   \draw[->,black,line width=3pt,-{Latex[length=7mm,width=7mm]}] (1,5) --node[above,outer sep=8pt]{\scalebox{4}{$x$}} (4.5,5);
 
@@
    % Draw arc
-   \centerarc[black,line width=3pt](dot)(270:290:11)
-   \node at (6.5,-9) {$\theta$};
-
-   \node[white,minimum size=1cm] at (4.5,-13) {};
+   \centerarc[black,line width=3pt](dot)(250:270:11)
+   \node at (2.5,-9) {\scalebox{4}{$\theta$}};
+
+   %\node[white,minimum size=1cm] at (4.5,-13) {};
 
@@
  \hfill
- \begin{subfigure}{.78\textwidth}
+ \begin{subfigure}[c]{.74\textwidth}
    \centering\scriptsize
@@
    \setlength{\figureheight}{.5\figurewidth}
-   \pgfplotsset{axis on top}
+   \pgfplotsset{axis on top,ymajorgrids,axis line style={draw=none},legend style={at={(1,1)},anchor=north west}}
+   \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed},legend style={fill=white}}
    \input{./fig/rl.tex}

### 2023-05-15 paper/main.tex
rewrite CL

@@
 After each task, we can use our \our to build a compact representation of the neural network and then use that as an additional term to the training loss to regularize the model.
+Recent success has shown GP-based regularizers perform better than weight space equivalents getting state-of-the-art on typical CL benchmarks \cite{ pan2020continual, rudner2022continual}.
+The limitation of such approaches is that they must use subset approximations of the posterior, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer.
+A more principled approach would be to sparsify the data into a low-rank approximation to ensure information wasn't lost, essentially what the sparse dual variables do.
 \todo{this term is replacing the missing data}
 
-An alternative view of the dual variables is that they parameterize approximate likelihoods as was shown in \citep{adam2021dual} we can rewrite the GP posterior in terms of the following approximate normal distributions:
+An alternative view of the dual variables is that they parameterize approximate likelihoods, as shown in \citep{adam2021dual, khan2017conjugate}.
+We can rewrite the GP posterior in terms of the following approximate normal distributions:
 \begin{equation}
- q(\vu) \propto \N(0, \MKzz) \prod_{i=1}^n e^{-\frac{\hat{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 } = \N(0, \MKzz) \, e^{(\tilde{\vy} - \vu)^\top\tilde{\MSigma}^{-1}(\tilde{\vy} - \vu)}  
+ q(\vu) \propto \N(0, \MKzz) \prod_{i=1}^n e^{-\frac{\tilde{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 } = \N(0, \MKzz) \, e^{(\bar{\vy} - \vu)^\top \bar{\MSigma}^{-1}(\bar{\vy} - \vu)}  
 \end{equation}
-The first normals are the marginal likelihoods were $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}$,  replacing $\va_i^\top \vu$  wtih $\vx_i^{\top}\vw$ and we can see the similarity between the sparse GP and a linear model where the prior is determined by the kernel matrix.
-To arrive at the MVN Gaussian we need to rearrange the quadratic terms to match the prior sufficient statistics we present a derivation in [appendix].
-Performing conjugate summation of prior and likelihood we would arrive at the sparse GP posterior at the inducing points $\MZ$.
-The correlated covariance structure $\MSigma$ and the corresponding $\tilde{\vy}$ are simply a different form of the sparse dual variables
+The first normals are the marginal likelihoods where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}$,  replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$ and we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior.
+To arrive at the MVN Gaussian, we need to rearrange the quadratic terms to match the prior sufficient statistics we present a derivation in [appendix].
+Performing conjugate summation of prior and likelihood, we would arrive at the sparse GP posterior at the inducing points.
+The correlated covariance structure $\MSigma$ and the corresponding $\tilde{\vy}$ are simply a different form of the sparse dual variables,
+\begin{equation}
+\quad \bar{\MSigma} =  \MKzz \vbeta_\vu^{-1} \MKzz \quad \bar{\vy} = \MKzz \vbeta_{\vu}\valpha_{\vu}.
+\end{equation}
+Written as above, we can see that the spare dual variables can be interpreted as a sparse representation.
+We now show how we use this for a regularizer in continual learning with more details in [appendix].
 

### 2023-05-15 paper/main.tex
rewrite CL

@@
 It is important to highlight that the sparsifying process is independent of the approximate inference technique.
-The \cref{eq:dual_param} are from the neural network definition \cref{eq-empirical-risk}.
+The \cref{eq:dual_param} is a result of using \cref{eq-empirical-risk} and a Laplace approximation.
 More complicated inference techniques, such as variational inference, could be used, but given its simplicity, we only need a trained neural network; we use a Laplace approximation in our experiments.
@@
 An alternative view of the dual variables is that they parameterize approximate likelihoods, as shown in \citep{adam2021dual, khan2017conjugate}.
-We can rewrite the GP posterior in terms of the following approximate normal distributions:
+We can rewrite the GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
 \begin{equation}
@@
 \end{equation}
-The first normals are the marginal likelihoods where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}$,  replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$ and we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior.
+The first normals are the approximate likelihoods where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}$,  replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$ and we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior.
 To arrive at the MVN Gaussian, we need to rearrange the quadratic terms to match the prior sufficient statistics we present a derivation in [appendix].
@@
 \end{equation}
-Written as above, we can see that the spare dual variables can be interpreted as a sparse representation.
+Written as above, we can see that the spare dual variables can be interpreted as a sparse MVN representation.
 We now show how we use this for a regularizer in continual learning with more details in [appendix].

### 2023-05-15 paper/main.tex
moved rl stuff

--- 2023-05-15 paper/main.tex
@@
 
+% We start by obtaining a posterior over the weights of a trained neural network via the Laplace approximation.
+% We then show how we can obtain a function-space posterior, (i.e. a GP posterior)
+% by linearising the neural network around the weights Maximum a Posteriori (MAP) estimate.
+% We then show that by linearising the neural network we can obtain a function-space posterior, i.e. a GP posterior.
+% We paraterise our single-step dynamic model $\transitionFnWithParams : \inputDomain \rightarrow \outputDomain$
+% as an $L\text{-layer}$ NN with weights $\weights$.
+
+%A Gaussian process (GP) is a distribution over real-valued functions $f(\cdot): \mathcal{X} \rightarrow \R$ defined over $\mathcal{X}$.
+%Formally, a GP is defined as,
+%\begin{align}
+%\label{eq-gp-prior}
+%  f(\cdot) \sim \mathcal{N}\left( \mu(\cdot), k(\cdot,\cdot') \right) \quad
+%  \mu(\cdot): \mathcal{X} \rightarrow \R \quad
+%  k(\cdot,\cdot'): \mathcal{X} \times \mathcal{X} \rightarrow \R
+%\end{align}
+%where $\mu(\cdot)$ denotes a mean function and $k(\cdot,\cdot')$ a positive definite covariance function, also known as a kernel.
+%Given a data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
+%we can obtain the GP posterior via multivariate normal conditioning,
+%\begin{align}
+%\label{eq-gp-predictive-posterior}
+%  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
+%  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
+%  \left( f(\mathbf{x}_{*}) \mid \mu(\mathbf{x}_{*}) + \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} (\mathbf{y} - \bm\mu_{\mathbf{X}})),
+%  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
+%\end{align}
+%% Our GP posterior is then given by,
+%\todo{add mean func to GP posterior if we're using one}
+%\begin{align}
+%\label{eq-gp-predictive-posterior}
+%  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
+%  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
+%  \left( f(\mathbf{x}_{*}) \mid \mu(\mathbf{x}_{*}) + \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} \mu_{\mathbf{x}},
+%  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} + \bm\Lambda(\mathbf{y} ; \mathbf{f})^{-1} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
+%\end{align}
+%where $\bm\Lambda(\mathbf{y} ; \mathbf{f}) = \nabla^{2}_{\mathbf{f} \mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$ can be viewed as per-input noise.
+\todo{I'm unsure about this per input noise bit.
+Check with paul.}
+%\todo{what about regression/classification likelhoods}
+%This GP predictive posterior is computationally expensive as it requires inverting an $N\times N$ matrix.
+%
+%\textbf{Sparse Gaussian processes}
+%% The GP predictive posterior in \cref{eq-gp-predictive-posterior} is computationally expensive as it requires inverting an $N\times N$ matrix.
+%A practical and computationally appealing alternative is to augment the joint probability space with pseudo inputs $\mathbf{Z} \in \R^{M \times D}$
+%and corresponding outputs
+%$\mathbf{u} = f(\mathbf{Z}; \weights) \in \R^{M \times C}$, known as inducing variables, where $M \ll N$.
+%\todo{cite sparse gp papers}
+%Instead of collapsing the inducing variables like \cite{titsiasVariational2009}, they can be treated variationally
+%$p(\mathbf{u} \mid \mathbf{y}) \approx q(\mathbf{u}) = \mathcal{N}\left( \mathbf{u} \mid \mathbf{m}, \mathbf{V} \right)$, where $\mathbf{m}$ and $\mathbf{V}$ are variational parameters
+%which need to be optimised \citep{hensmanGaussian2013}.
+%The sparse variational GP (SVGP) predictive posterior is then given by,
+%\begin{align}
+%\label{eq-dual-svgp-predictive-posterior}
+%  p(f(\mathbf{x}_{*}) \mid \mathbf{y})
+%&\approx \mathcal{N} \left( f(\mathbf{x}_{*}) \mid \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{m}^{*},
+%  k_{**} - \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
+%  % \mathbf{k}_{*\inducingInput} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\inducingInput}^{T}
+%  + \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}}  \mathbf{V}^{*}  \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
+%  \right)
+%\coloneqq q_{\inducingVariable}(f(\mathbf{x}_{*}))
+%\end{align}
+%
+%
+%\textbf{Deep learning}
+%Given the data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
+%the goal of (supervised) deep learning, is to train the weights $\weights \in \R^{P}$ of an $L\text{-layer}$ NN
+%$f : \inputDomain \rightarrow \outputDomain$ to minimize the (regularized) empirical risk,
+%\begin{align} \label{eq-empirical-risk}
+%  \weights^{*} = \arg \min_{\weights \in \R^{D}} \mathcal{L}(\dataset;\weights) = \arg \min_{\weights \in \R^{D}} \left(
+%  \sum_{n=0}^{N-1} l(f(\mathbf{x}_{n} ; \weights), \mathbf{y}_{n}) + R(\weights)  \right).
+%\end{align}
+%In practice, it is common to use the mean squared error (MSE) loss
+%$l(f(\mathbf{x}_{n} ; \weights),\mathbf{y}_{n}) = \|f(\mathbf{x}_{n} ; \weights) - \mathbf{y}_{n} \|^{2}_{2}$
+%and to use the weight decay regularizer $R(\weights)=\frac{1}{2}\gamma^{-2}\|\weights\|^{2}_{2}$.
+%However, the practioner is free to choose any loss and regularizer. \todo{I think?}
+%% \textbf{Bayesian neural networks}
+%% \textbf{Weight space to function space}
+%From a Bayesian perspective, we can interpret the terms in \cref{eq-empirical-risk} as the log-prior and the i.i.d. log likelihood, i.e.,
+%\begin{align} \label{eq-log-prior}
+%  R(\weights) &= \underbrace{\log p(\weights)}_{\text{log prior}} = \log \mathcal{N}(\weights \mid 0, \gamma^{2} \mathbf{I}) \\
+%  l(f(\mathbf{x}_{n} ; \weights), \mathbf{y}_{n}) &= \underbrace{\log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \weights))}_{\text{log likelihood}}
+%  = \log \mathcal{N} \left( \mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \weights), \mathbf{I} \right) \label{eq-log-likelihood}
+%\end{align}
+%
+%\textbf{NN to GP}
+%Given this interpretation, we can represent the weight space prior from \cref{eq-log-prior}, in
+%function space, by linearising the BNN around $\weights^{*}$ and interpretting it as a GP.
+%The GP prior is then given by,
+%\begin{align} \label{eq-laplace-approx-function-space}
+%  % \transitionFn_{\weights_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \qquad
+%  f(\cdot ;\weights) \sim \mathcal{N} \left( \mu(\cdot), k(\cdot, \cdot') \right) \quad
+%  % \mu_{\weights_{i}^{*}}(\cdot)
+%  \mu(\cdot)
+%  = 0 \quad
+%  % = f(\cdot ;\weights^{*}) \quad
+%  % K_{\weights_{i}^{*}}(\cdot, \cdot')
+%  k(\cdot, \cdot')
+%  = \frac{1}{\gamma^{2}} \mathbf{J}(\cdot) \mathbf{J}(\cdot')^{T},
+%\end{align}
+%where the kernel is the neural tangent kernel (NTK) \citep{immerImprovingPredictionsBayesian2021},
+%\todo{what mean function shoudl this use???}
+%\todo{NTK times some factor??}
+%with Jacobian given by $\mathbf{J}(\cdot) = \odv{\transitionFn(\cdot; \weights)}{\weights}_{\weights=\weights^{*}}$.
+%% The kernel in \cref{eq-laplace-approx-function-space} is the neural tangent kernel (NTK)
+%% $k(\mathbf{x}, \mathbf{x}') = \sigma_{0}^{2} J_{\weights^{*}}(\mathbf{x}) J_{\weights^{*}}(\mathbf{x}')^{T}$
+%% \citep{immerImprovingPredictionsBayesian2021}
+%% to formulate the GP posterior $p(f(\mathbf{X} ;\weights_{0:i}) \mid \dataset_{0:i})$.
+%Given this GP prior, we can use \cref{eq-gp-predictive-posterior} to obtain our GP posterior by conditioning on the data.
+%% Given our GP prior, we can use the properties of multivariate normals to obtain our GP posterior by conditioning on the data.
+%% where $\mathbf{A} = \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}}$
+%In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
+%Intuitively, we can view the optimisation in \cref{eq-empirical-risk} as learning our kernel.
+%As a result, our NTK may be highly non stationary as it is dependent on the NN architecture, for example, the activation functions.
+%It is worth noting that the NTK linearises the network around the optimised parameters $\weights^{*}$,
+%so the function space prior (and thus posterior) is only a locally linear approximation.
+%
+%We now have a method to obtain a GP posterior from a trained DNN.
+%% In contrast to other approaches, our formulation has not restricted us to using a weight-space posterior obtained from the Laplace approximation.
+%In contrast to other approaches, our formulation has not restricted us to using a weight-space posterior from a BNN.
+%However, in practice, the GP posterior is not very useful as it requires inverting an $N\times N$ matrix which has complexity $\mathcal{O}(N^{3})$.
+%The SVGP in \cref{eq-dual-svgp-predictive-posterior} offers a solution to this problem but it is not immediately clear how to set $\mathbf{m}$ and $\mathbf{V}$.
+%In the next section, we show how we can directly obtain an SVGP posterior (i.e. set $\mathbf{m}$ and $\mathbf{V}$) directly from both
+%1) a trained NN and 2) a BNN weight-space posterior.
+%% $\mathbf{m}$ and $\mathbf{V}$
+%% However, it is not obvious how we can use a SVGP to set $\mathbf{m}$ and $\mathbf{V}$
+%
+%
+%
+%% In contrast, to previous work, this approach did not require us Laplace approximation. we will not restrict our
+%% It is worth noting that the NTK linearises the network around the optimised parameters $\weights^{*}$,
+%% so the function space prior (and thus posterior) is only a locally linear approximation.
+%% In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
+%% It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.
+%
+%
+%\section{Methods}
+%In the next section we show how we can obtain a SVGP directly from 1) a trained NN and 2) a BNN posterior.
+%
+%We follow \cite{csatoSparseOnlineGaussian2002} and express our GP posterior in the dual parameter space.
+%However, we consider the variational formulation introduced by \cite{adamDualParameterizationSparse2021}, where the optimal variational parameters are given by,
+%\begin{align} \label{eq-dual-params}
+%\mathbf{m}^{*} = \mathbf{V}^{*}\bm\alpha^{*} \quad \mathbf{V}^{*} = [\mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} + \bm\beta^{*}]
+%\end{align}
+%Importantly, we can calculate the natural parameters $(\bm\alpha, \bm\beta)$ in closed form,
+%\todo{paul needs to update \cref{eq-dual-svgp-params}}
+%\begin{align} \label{eq-dual-svgp-params}
+%\bm\alpha_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right] \\
+%\bm\beta_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right].
+%\end{align}
+%This simplifies SVGP inference \citep{hensmanGaussian2013} as it no longer requires the variational parameters $(\mathbf{m}, \mathbf{V})$ to be optimised.
+%
+%% Importantly, \cite{changFantasizingDualGPs2022} show that in the dual space,
+%% conditioning on new observations reduces to suming the dual variables from the previous time
+%% step with an update, given by,
+%% \todo{pick best way to show new data (using superscript new or just time indexing?)}
+%% \begin{align} \label{eq-dual-update-svgp}
+%% \bm\alpha_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right] \\
+%% \bm\beta_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right]
+%% \end{align}
+%
+%% We follow \cite{csatoSparseOnlineGaussian2002} and express our GP posterior in the dual parameter space,
+%% % to write GP posterior $p(f(\mathbf{X} ;\weights_{0:i}) \mid \dataset_{0:i})$ as,
+%% \begin{align} \label{eq-gp-post}
+%%   \mathbb{E}_{p(f(\mathbf{x}_{*}) \mid \mathbf{y}_{n})} \left[ f(\mathbf{x}_{*}) \right] &= \mu(\mathbf{x}_{*}) + \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
+%%   \mathbb{V}_{p(f(\mathbf{x}_{*}) \mid \mathbf{y}_{n})} \left[ f(\mathbf{x}_{*}) \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \text{diag}(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
+%% \end{align}
+%% % \begin{align} \label{eq-laplace-approx-function-space}
+%% %   \mathbb{E}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
+%% %   \mathbb{V}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \diag(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
+%% % \end{align}
+%% where the dual parameters $(\bm\alpha_n, \bm\beta_n)$ are vectors of,
+%% \begin{align} \label{eq-gp-dual-params}
+%%   \bm\alpha_{n} \coloneqq \left\{ \mathbb{E}_{p(f(\mathbf{x}_{i}) \mid \mathbf{y}_{n})} \left[ \nabla_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \right\}_{i=1}^{N} \qquad
+%%   \bm\beta_{n} \coloneqq \left\{ \mathbb{E}_{p(f(\mathbf{x}_{i}) \mid \mathbf{y}_{n})} \left[ \nabla^{2}_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \right\}_{i=1}^{N}
+%% \end{align}
+%% Importantly, this parameterisation
+%
+%% \textbf{dual-SVGP}
+%% \begin{align} \label{eq-svgp-post}
+%%   \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ f(\mathbf{x}_{*}) \right] &= \mu(\mathbf{x}_{*}) + \mathbf{k}_{\mathbf{z}*}^{T} \bm\alpha_{\mathbf{u}} \\
+%%   \mathbb{V}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ f(\mathbf{x}_{*}) \right] &= k_{**} - \mathbf{k}_{\mathbf{z}*}^{T} \left[ \mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} - \left( \mathbf{K}_{\mathbf{z} \mathbf{z}} + \bm\beta_{\mathbf{u}} \right)^{-1} \right] \mathbf{k}_{\mathbf{z}*}
+%% \end{align}
+%% % \begin{align} \label{eq-laplace-approx-function-space}
+%% %   \mathbb{E}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
+%% %   \mathbb{V}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \diag(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
+%% % \end{align}
+%% where the dual parameters $(\bm\alpha_{\mathbf{u}}, \bm\beta_{\mathbf{u}})$ are vectors of,
+%% \begin{align} \label{eq-svgp-dual-params}
+%%   \bm\alpha_{\mathbf{u}} \coloneqq \mathbf{k}_{\mathbf{z}i} \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ \nabla_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \qquad
+%%   \bm\beta_{\mathbf{u}} \coloneqq \mathbf{k}_{\mathbf{z}i} \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ \nabla^{2}_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \mathbf{k}_{\mathbf{z}i}^{T}
+%% \end{align}
+%
+%% weight space posterior in \cref{eq-laplace-approx-weight-space} in
+%% function space by linearising the BNN and interpreting it as a GP.
+%% \begin{align} \label{eq-laplace-approx-function-space}
+%%   \transitionFn_{\weights_{i}}(\cdot) &\sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \quad
+%%   \mu_{\weights_{i}^{*}}(\cdot) &= \transitionFn_{\weights^{*}_{i}}(\cdot) \quad
+%%   K_{\weights_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\weights^{*}_{i}}(\cdot) \bm\Sigma_{\weights^{*}_{i}} \mathbf{J}_{\weights^{*}_{i}}(\cdot')^{T}
+%% \end{align}
+%% where the Jacobian is given by $\mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}$.
+%
+%% \begin{align} \label{eq-laplace-approx-jacobian}
+%% \mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}
+%% \end{align}
+%
+%
+%% % Note that the posterior in \cref{eq-laplace-approx-weight-space} is in weight space.
+%% We can represent the weight space posterior in \cref{eq-laplace-approx-weight-space} in
+%% function space by linearising the BNN and interpreting it as a GP.
+%% \begin{align} \label{eq-laplace-approx-function-space}
+%%   \transitionFn_{\weights_{i}^{*}}(\cdot) &\sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \quad
+%%   \mu_{\weights_{i}^{*}}(\cdot) &= \transitionFn_{\weights^{*}_{i}}(\cdot) \quad
+%%   K_{\weights_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\weights^{*}_{i}}(\cdot) \bm\Sigma_{\weights^{*}_{i}} \mathbf{J}_{\weights^{*}_{i}}(\cdot')^{T}
+%% \end{align}
+%% where the Jacobian is given by $\mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}$.
+%
+%% \begin{align} \label{eq-laplace-approx-jacobian}
+%% \mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}
+%% \end{align}
+%
+%
+%\subsection{Fast Updates}
+%Importantly, \cite{changFantasizingDualGPs2022} show that in the dual space,
+%conditioning on new observations reduces to suming the dual variables from the previous time
+%step with an update, given by,
+%\todo{pick best way to show new data (using superscript new or just time indexing?)}
+%\begin{align} \label{eq-dual-update-svgp}
+%\dualParam{1}^{t+1} &\leftarrow \dualParam{1}^{t} +  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))} \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right] \\
+%\dualParam{2}^{t+1} &\leftarrow \dualParam{2}^{t} +  \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))}  \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right]
+%\end{align}
+%Importantly, for a single new observation $((\state_{t}, \action_{t}), \state_{t+1})$ this update has
+%complexity $\mathcal{O}(\numInducing^{2})$.
+%This is a significant improvement to naive GP conditioning, which has complexity $\mathcal{O}((\numDataNew + \numDataOld)^{3})$
+%and sparse GP conditioning, which has complexity $\mathcal{O}((\numDataNew + \numDataOld)\numInducing^{2})$.
+%\todo{double check these complexities are right and cite them/show equaitons}
+%It is worth highlighting that the complexity of \cite{changFantasizingDualGPs2022} update does not increase during an episode.
+%
+%\subsubsection{Model-based RL}
+%
+%\subsubsection{Efficiently Sampling Functions for Posterior Sampling}
+%\cite{wilsonEfficiently2020}
+%\cite{wilsonPathwise2021}
+%
+%% \begin{align} \label{eq-dual-update-svgp}
+%%  \dualParam{1}^{\text{new}} &\leftarrow \dualParam{1}^{\text{old}} +
+%%   \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}))}
+%%  \left[ \log p(\state_{t+1}^{\text{new}} \mid \latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}) ) \right] \\
+%%  \dualParam{2}^{\text{new}} &\leftarrow \dualParam{2}^{\text{old}} +
+%%   \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}))}
+%%  \left[ \log p(\state_t^{\horizon+1} \mid \latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}) ) \right] \\
+%%  \dualParam{1}^{\horizon+1} &\leftarrow \dualParam{1}^{\horizon} +
+%%   \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}
+%%  \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right] \\
+%%  \dualParam{2}^{\horizon+1} &\leftarrow \dualParam{2}^{\horizon} +
+%%   \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}
+%%  \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right]
+%% \end{align}
+%
+%
+%\begin{assumption} \label{assumption-ntk-linearisation}
+%  Something about NTK being a linearisation around $\theta^{*}_{i}$ but each update moves away from $\theta^{*}_{i}$
+%\end{assumption}
+%
+%\cite{rossellApproximateLaplaceApproximations2021}
+
+\section{Experiments}
+\label{sec:experiments}
+
+\todo{Overview of experiments}
+
+Our experiments seek to answer the following questions:
+\begin{enumerate}
+  \item \textbf{Predictions} How do predictions with our sparse function-space approximation compare to weight-space approximations?
+Does our method's ability to consider the full data set offer benefits over subset function-space methods?
+  % \item Does our method's ability to consider the full data set offer benefits over subset function-space methods?
+  \item \textbf{Function-space updates} How fast are our function-space updates relative to retraining from scratch?
+Do they improve predictive performance?
+Are they as good as retraining from scratch?
+  \item \textbf{Uncertainty} How good are our uncertainty estimates? Can they be used in downstream settings like RL?
+  \item \textbf{Representation} Is our sparse function-space representation useful for continual learning?
+\end{enumerate}
+
+\subsection{Capturing uncertainty in UCI tasks under supervised learning}
+%
+
+\begin{table}[t!] 
+  \centering\scriptsize
+  \caption{Negative log predictive density (NLPD) (lower better) for the proposed model TODO} 
+	\label{tbl:uci}
+	% Control table spacing
+	\renewcommand{\arraystretch}{1.}
+	\setlength{\tabcolsep}{2pt}
+	\setlength{\tblw}{0.14\textwidth}
+
+	% Custom error formatting
+	\newcommand{\val}[2]{%
+		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
+	}
+
+    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
+	\input{tables/uci.tex}
+\end{table}
+We trained a two-layer MLP for each of the $8$ classification tasks in UCI, see \cref{tbl:uci} for a list of the datasets.
+The neural network training was done using MAP, with a prior $\mathcal{N}(0,\delta^{-1} \MI)$ with prior precision $\delta$.
+After training, we constructed the SVGP dual and used the resulting SVGP model for uncertainty quantification.
+Depending on task dimension and complexity, our model can match the NN MAP in NLPD performance even with a low number of inducing points, see \cref{tbl:uci}.
+We performed hyperparameter search over the prior precision, and ran the experiment over $10$ seeds.
+During the initial NN training, we used a learning rate of $1e-3$.
+
+\subsection{Supervised learning on image data sets}
+
+\begin{table}[t!] 
+  \centering\scriptsize
+  \caption{Metrics for supervised learning with image data.
+SVGP is our method, and the number inside parentheses is the number of inducing points.
+SVGP NN is a modification of our method, where the mean is from the NN directly and the variance is from the GP model}
+	\label{tbl:imagesuper}
+	% Control table spacing
+	\renewcommand{\arraystretch}{1.}
+	\setlength{\tabcolsep}{6pt}
+	\setlength{\tblw}{0.15\textwidth}
+
+	% Custom error formatting
+	\newcommand{\val}[2]{%
+		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
+	}
+
+    % THE TABLE CAN BE FORMATTED MORE LIKE THIS
+    \begin{tabular}{l l C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
+    \toprule
+    & Method & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ & OOD-AUC~$\uparrow$  \\
+    \midrule
+    \multirow{2}{*}{FMNIST} 
+    & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\    
+    \midrule
+    \multirow{2}{*}{CIFAR-10} 
+    & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\    
+    \bottomrule
+    \end{tabular}
+
+    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
+	%\input{tables/img_super.tex}
+\end{table}
+
+Similarly to the UCI experiments, we trained neural networks (CNN, architexture matches \citet{immer2021improving}) for the FMNIST and CIFAR10 classification tasks.
+After training, we computed the duals for NN2SVGP and used the resulting SVGP for uncertainty estimates, see \cref{tbl:imagesuper}.
+We performed hyperparameter optimization over the prior precision, and found the optimal value to be [insert].
+We ran the experiment over $5$ seeds.
+During the NN training, we used a batch size of $512$ and an Adam optimizer with learning rate $1e-3$.
+
+In addition to uncertainty estimates, our method can update the posterior when given new data.
+We gave the SVGP model 10 \% of the test dataset used for evaluation, and compare the performance of the SVGP model and the retrained NN in [INSERT TABLE].
+
+\subsection{Updating the  network representation for Continual learning}
+The Continual learning setting is a challenging and the training and
+
+\begin{table}[t!] 
+  \centering\scriptsize
+  \caption{
+  TODO: CL Experiments. $^*$ Methods relying only on weight regularization. 
+  \color{blue}{Results from \cite{rudner2022continual}.} 
+  %\color{red}{Preliminary results need more runs or hyperparam tuning}
+  }
+	\label{tbl:cl_table_1}
+	% Control table spacing
+	\renewcommand{\arraystretch}{1.}
+	\setlength{\tabcolsep}{2pt}
+	\setlength{\tblw}{0.14\textwidth}
+
+	% Custom error formatting
+	\newcommand{\val}[2]{%
+		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
+	}
+
+	\input{tables/cl_table_1}
+\end{table}
+
 \subsection{Reinforcement learning}
-A key challenge in RL is to balance the trade-off between exploration and exploitation.
+A key challenge in RL is balancing the trade-off between exploration and exploitation.
 That is, should the agent select an action that it knows will lead to a high reward (exploitation), or should it
 hope to discover new actions which lead to high reward (exploration) by selecting actions that it has not selected before.
-In this section, we detail how our method's principled uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim.
-
-We consider stochastic environments with states \(\state \in \stateDomain \subseteq \R^{D_{\state}} \),
+In this section, we demonstrate  that our method's principled uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim.
+
+We consider environments with states \(\state \in \stateDomain \subseteq \R^{D_{\state}} \),
 actions \(\action \in \actionDomain \subseteq \R^{D_{\action}}\) and transition dynamics
@@
 In this work, we consider model-based RL where a model of the transition dynamics is learned \(f_{\mathbf{w}} \approx \transitionFn\) and then used by a planning algorithm.
-A simple approach is to use the learned dynamic model $f_{\mathbf{w}^{*}}$ and maximise the objective in \cref{eq-model-free-objective},
-\begin{align} \label{eq-greedy}
-  \policy^{\text{Greedy}} &= \arg \max_{\pi \in \Pi} J(f_{\mathbf{w}^{*}}, \pi).
-\end{align}
+A simple approach is to use the learned dynamic model $f_{\mathbf{w}^{*}}$ and maximise the objective in \cref{eq-model-free-objective}.
+% \begin{align} \label{eq-greedy}
+%   \policy^{\text{Greedy}} &= \arg \max_{\pi \in \Pi} J(f_{\mathbf{w}^{*}}, \pi).
+% \end{align}
 However, we can leverage the method in \cref{sec:methods} to obtain a function-space posterior over the learned dynamics $q_{\mathbf{u}}(\hat{\transitionFn} \mid \dataset)$,
@@
 
-\textbf{Pathwise conditioning in function-space??}
-\todo{could try to implement this}
-
-% We start by obtaining a posterior over the weights of a trained neural network via the Laplace approximation.
-% We then show how we can obtain a function-space posterior, (i.e. a GP posterior)
-% by linearising the neural network around the weights Maximum a Posteriori (MAP) estimate.
-% We then show that by linearising the neural network we can obtain a function-space posterior, i.e. a GP posterior.
-% We paraterise our single-step dynamic model $\transitionFnWithParams : \inputDomain \rightarrow \outputDomain$
-% as an $L\text{-layer}$ NN with weights $\weights$.
-
-%A Gaussian process (GP) is a distribution over real-valued functions $f(\cdot): \mathcal{X} \rightarrow \R$ defined over $\mathcal{X}$.
-%Formally, a GP is defined as,
-%\begin{align}
-%\label{eq-gp-prior}
-%  f(\cdot) \sim \mathcal{N}\left( \mu(\cdot), k(\cdot,\cdot') \right) \quad
-%  \mu(\cdot): \mathcal{X} \rightarrow \R \quad
-%  k(\cdot,\cdot'): \mathcal{X} \times \mathcal{X} \rightarrow \R
-%\end{align}
-%where $\mu(\cdot)$ denotes a mean function and $k(\cdot,\cdot')$ a positive definite covariance function, also known as a kernel.
-%Given a data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
-%we can obtain the GP posterior via multivariate normal conditioning,
-%\begin{align}
-%\label{eq-gp-predictive-posterior}
-%  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
-%  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
-%  \left( f(\mathbf{x}_{*}) \mid \mu(\mathbf{x}_{*}) + \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} (\mathbf{y} - \bm\mu_{\mathbf{X}})),
-%  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
-%\end{align}
-%% Our GP posterior is then given by,
-%\todo{add mean func to GP posterior if we're using one}
-%\begin{align}
-%\label{eq-gp-predictive-posterior}
-%  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
-%  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
-%  \left( f(\mathbf{x}_{*}) \mid \mu(\mathbf{x}_{*}) + \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} \mu_{\mathbf{x}},
-%  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} + \bm\Lambda(\mathbf{y} ; \mathbf{f})^{-1} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
-%\end{align}
-%where $\bm\Lambda(\mathbf{y} ; \mathbf{f}) = \nabla^{2}_{\mathbf{f} \mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$ can be viewed as per-input noise.
-\todo{I'm unsure about this per input noise bit.
-Check with paul.}
-%\todo{what about regression/classification likelhoods}
-%This GP predictive posterior is computationally expensive as it requires inverting an $N\times N$ matrix.
-%
-%\textbf{Sparse Gaussian processes}
-%% The GP predictive posterior in \cref{eq-gp-predictive-posterior} is computationally expensive as it requires inverting an $N\times N$ matrix.
-%A practical and computationally appealing alternative is to augment the joint probability space with pseudo inputs $\mathbf{Z} \in \R^{M \times D}$
-%and corresponding outputs
-%$\mathbf{u} = f(\mathbf{Z}; \weights) \in \R^{M \times C}$, known as inducing variables, where $M \ll N$.
-%\todo{cite sparse gp papers}
-%Instead of collapsing the inducing variables like \cite{titsiasVariational2009}, they can be treated variationally
-%$p(\mathbf{u} \mid \mathbf{y}) \approx q(\mathbf{u}) = \mathcal{N}\left( \mathbf{u} \mid \mathbf{m}, \mathbf{V} \right)$, where $\mathbf{m}$ and $\mathbf{V}$ are variational parameters
-%which need to be optimised \citep{hensmanGaussian2013}.
-%The sparse variational GP (SVGP) predictive posterior is then given by,
-%\begin{align}
-%\label{eq-dual-svgp-predictive-posterior}
-%  p(f(\mathbf{x}_{*}) \mid \mathbf{y})
-%&\approx \mathcal{N} \left( f(\mathbf{x}_{*}) \mid \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{m}^{*},
-%  k_{**} - \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
-%  % \mathbf{k}_{*\inducingInput} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\inducingInput}^{T}
-%  + \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}}  \mathbf{V}^{*}  \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
-%  \right)
-%\coloneqq q_{\inducingVariable}(f(\mathbf{x}_{*}))
-%\end{align}
-%
-%
-%\textbf{Deep learning}
-%Given the data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
-%the goal of (supervised) deep learning, is to train the weights $\weights \in \R^{P}$ of an $L\text{-layer}$ NN
-%$f : \inputDomain \rightarrow \outputDomain$ to minimize the (regularized) empirical risk,
-%\begin{align} \label{eq-empirical-risk}
-%  \weights^{*} = \arg \min_{\weights \in \R^{D}} \mathcal{L}(\dataset;\weights) = \arg \min_{\weights \in \R^{D}} \left(
-%  \sum_{n=0}^{N-1} l(f(\mathbf{x}_{n} ; \weights), \mathbf{y}_{n}) + R(\weights)  \right).
-%\end{align}
-%In practice, it is common to use the mean squared error (MSE) loss
-%$l(f(\mathbf{x}_{n} ; \weights),\mathbf{y}_{n}) = \|f(\mathbf{x}_{n} ; \weights) - \mathbf{y}_{n} \|^{2}_{2}$
-%and to use the weight decay regularizer $R(\weights)=\frac{1}{2}\gamma^{-2}\|\weights\|^{2}_{2}$.
-%However, the practioner is free to choose any loss and regularizer. \todo{I think?}
-%% \textbf{Bayesian neural networks}
-%% \textbf{Weight space to function space}
-%From a Bayesian perspective, we can interpret the terms in \cref{eq-empirical-risk} as the log-prior and the i.i.d. log likelihood, i.e.,
-%\begin{align} \label{eq-log-prior}
-%  R(\weights) &= \underbrace{\log p(\weights)}_{\text{log prior}} = \log \mathcal{N}(\weights \mid 0, \gamma^{2} \mathbf{I}) \\
-%  l(f(\mathbf{x}_{n} ; \weights), \mathbf{y}_{n}) &= \underbrace{\log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \weights))}_{\text{log likelihood}}
-%  = \log \mathcal{N} \left( \mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \weights), \mathbf{I} \right) \label{eq-log-likelihood}
-%\end{align}
-%
-%\textbf{NN to GP}
-%Given this interpretation, we can represent the weight space prior from \cref{eq-log-prior}, in
-%function space, by linearising the BNN around $\weights^{*}$ and interpretting it as a GP.
-%The GP prior is then given by,
-%\begin{align} \label{eq-laplace-approx-function-space}
-%  % \transitionFn_{\weights_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \qquad
-%  f(\cdot ;\weights) \sim \mathcal{N} \left( \mu(\cdot), k(\cdot, \cdot') \right) \quad
-%  % \mu_{\weights_{i}^{*}}(\cdot)
-%  \mu(\cdot)
-%  = 0 \quad
-%  % = f(\cdot ;\weights^{*}) \quad
-%  % K_{\weights_{i}^{*}}(\cdot, \cdot')
-%  k(\cdot, \cdot')
-%  = \frac{1}{\gamma^{2}} \mathbf{J}(\cdot) \mathbf{J}(\cdot')^{T},
-%\end{align}
-%where the kernel is the neural tangent kernel (NTK) \citep{immerImprovingPredictionsBayesian2021},
-%\todo{what mean function shoudl this use???}
-%\todo{NTK times some factor??}
-%with Jacobian given by $\mathbf{J}(\cdot) = \odv{\transitionFn(\cdot; \weights)}{\weights}_{\weights=\weights^{*}}$.
-%% The kernel in \cref{eq-laplace-approx-function-space} is the neural tangent kernel (NTK)
-%% $k(\mathbf{x}, \mathbf{x}') = \sigma_{0}^{2} J_{\weights^{*}}(\mathbf{x}) J_{\weights^{*}}(\mathbf{x}')^{T}$
-%% \citep{immerImprovingPredictionsBayesian2021}
-%% to formulate the GP posterior $p(f(\mathbf{X} ;\weights_{0:i}) \mid \dataset_{0:i})$.
-%Given this GP prior, we can use \cref{eq-gp-predictive-posterior} to obtain our GP posterior by conditioning on the data.
-%% Given our GP prior, we can use the properties of multivariate normals to obtain our GP posterior by conditioning on the data.
-%% where $\mathbf{A} = \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}}$
-%In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
-%Intuitively, we can view the optimisation in \cref{eq-empirical-risk} as learning our kernel.
-%As a result, our NTK may be highly non stationary as it is dependent on the NN architecture, for example, the activation functions.
-%It is worth noting that the NTK linearises the network around the optimised parameters $\weights^{*}$,
-%so the function space prior (and thus posterior) is only a locally linear approximation.
-%
-%We now have a method to obtain a GP posterior from a trained DNN.
-%% In contrast to other approaches, our formulation has not restricted us to using a weight-space posterior obtained from the Laplace approximation.
-%In contrast to other approaches, our formulation has not restricted us to using a weight-space posterior from a BNN.
-%However, in practice, the GP posterior is not very useful as it requires inverting an $N\times N$ matrix which has complexity $\mathcal{O}(N^{3})$.
-%The SVGP in \cref{eq-dual-svgp-predictive-posterior} offers a solution to this problem but it is not immediately clear how to set $\mathbf{m}$ and $\mathbf{V}$.
-%In the next section, we show how we can directly obtain an SVGP posterior (i.e. set $\mathbf{m}$ and $\mathbf{V}$) directly from both
-%1) a trained NN and 2) a BNN weight-space posterior.
-%% $\mathbf{m}$ and $\mathbf{V}$
-%% However, it is not obvious how we can use a SVGP to set $\mathbf{m}$ and $\mathbf{V}$
-%
-%
-%
-%% In contrast, to previous work, this approach did not require us Laplace approximation. we will not restrict our
-%% It is worth noting that the NTK linearises the network around the optimised parameters $\weights^{*}$,
-%% so the function space prior (and thus posterior) is only a locally linear approximation.
-%% In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
-%% It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.
-%
-%
-%\section{Methods}
-%In the next section we show how we can obtain a SVGP directly from 1) a trained NN and 2) a BNN posterior.
-%
-%We follow \cite{csatoSparseOnlineGaussian2002} and express our GP posterior in the dual parameter space.
-%However, we consider the variational formulation introduced by \cite{adamDualParameterizationSparse2021}, where the optimal variational parameters are given by,
-%\begin{align} \label{eq-dual-params}
-%\mathbf{m}^{*} = \mathbf{V}^{*}\bm\alpha^{*} \quad \mathbf{V}^{*} = [\mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} + \bm\beta^{*}]
-%\end{align}
-%Importantly, we can calculate the natural parameters $(\bm\alpha, \bm\beta)$ in closed form,
-%\todo{paul needs to update \cref{eq-dual-svgp-params}}
-%\begin{align} \label{eq-dual-svgp-params}
-%\bm\alpha_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right] \\
-%\bm\beta_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right].
-%\end{align}
-%This simplifies SVGP inference \citep{hensmanGaussian2013} as it no longer requires the variational parameters $(\mathbf{m}, \mathbf{V})$ to be optimised.
-%
-%% Importantly, \cite{changFantasizingDualGPs2022} show that in the dual space,
-%% conditioning on new observations reduces to suming the dual variables from the previous time
-%% step with an update, given by,
-%% \todo{pick best way to show new data (using superscript new or just time indexing?)}
-%% \begin{align} \label{eq-dual-update-svgp}
-%% \bm\alpha_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right] \\
-%% \bm\beta_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right]
-%% \end{align}
-%
-%% We follow \cite{csatoSparseOnlineGaussian2002} and express our GP posterior in the dual parameter space,
-%% % to write GP posterior $p(f(\mathbf{X} ;\weights_{0:i}) \mid \dataset_{0:i})$ as,
-%% \begin{align} \label{eq-gp-post}
-%%   \mathbb{E}_{p(f(\mathbf{x}_{*}) \mid \mathbf{y}_{n})} \left[ f(\mathbf{x}_{*}) \right] &= \mu(\mathbf{x}_{*}) + \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
-%%   \mathbb{V}_{p(f(\mathbf{x}_{*}) \mid \mathbf{y}_{n})} \left[ f(\mathbf{x}_{*}) \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \text{diag}(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
-%% \end{align}
-%% % \begin{align} \label{eq-laplace-approx-function-space}
-%% %   \mathbb{E}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
-%% %   \mathbb{V}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \diag(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
-%% % \end{align}
-%% where the dual parameters $(\bm\alpha_n, \bm\beta_n)$ are vectors of,
-%% \begin{align} \label{eq-gp-dual-params}
-%%   \bm\alpha_{n} \coloneqq \left\{ \mathbb{E}_{p(f(\mathbf{x}_{i}) \mid \mathbf{y}_{n})} \left[ \nabla_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \right\}_{i=1}^{N} \qquad
-%%   \bm\beta_{n} \coloneqq \left\{ \mathbb{E}_{p(f(\mathbf{x}_{i}) \mid \mathbf{y}_{n})} \left[ \nabla^{2}_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \right\}_{i=1}^{N}
-%% \end{align}
-%% Importantly, this parameterisation
-%
-%% \textbf{dual-SVGP}
-%% \begin{align} \label{eq-svgp-post}
-%%   \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ f(\mathbf{x}_{*}) \right] &= \mu(\mathbf{x}_{*}) + \mathbf{k}_{\mathbf{z}*}^{T} \bm\alpha_{\mathbf{u}} \\
-%%   \mathbb{V}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ f(\mathbf{x}_{*}) \right] &= k_{**} - \mathbf{k}_{\mathbf{z}*}^{T} \left[ \mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} - \left( \mathbf{K}_{\mathbf{z} \mathbf{z}} + \bm\beta_{\mathbf{u}} \right)^{-1} \right] \mathbf{k}_{\mathbf{z}*}
-%% \end{align}
-%% % \begin{align} \label{eq-laplace-approx-function-space}
-%% %   \mathbb{E}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
-%% %   \mathbb{V}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \diag(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
-%% % \end{align}
-%% where the dual parameters $(\bm\alpha_{\mathbf{u}}, \bm\beta_{\mathbf{u}})$ are vectors of,
-%% \begin{align} \label{eq-svgp-dual-params}
-%%   \bm\alpha_{\mathbf{u}} \coloneqq \mathbf{k}_{\mathbf{z}i} \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ \nabla_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \qquad
-%%   \bm\beta_{\mathbf{u}} \coloneqq \mathbf{k}_{\mathbf{z}i} \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ \nabla^{2}_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \mathbf{k}_{\mathbf{z}i}^{T}
-%% \end{align}
-%
-%% weight space posterior in \cref{eq-laplace-approx-weight-space} in
-%% function space by linearising the BNN and interpreting it as a GP.
-%% \begin{align} \label{eq-laplace-approx-function-space}
-%%   \transitionFn_{\weights_{i}}(\cdot) &\sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \quad
-%%   \mu_{\weights_{i}^{*}}(\cdot) &= \transitionFn_{\weights^{*}_{i}}(\cdot) \quad
-%%   K_{\weights_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\weights^{*}_{i}}(\cdot) \bm\Sigma_{\weights^{*}_{i}} \mathbf{J}_{\weights^{*}_{i}}(\cdot')^{T}
-%% \end{align}
-%% where the Jacobian is given by $\mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}$.
-%
-%% \begin{align} \label{eq-laplace-approx-jacobian}
-%% \mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}
-%% \end{align}
-%
-%
-%% % Note that the posterior in \cref{eq-laplace-approx-weight-space} is in weight space.
-%% We can represent the weight space posterior in \cref{eq-laplace-approx-weight-space} in
-%% function space by linearising the BNN and interpreting it as a GP.
-%% \begin{align} \label{eq-laplace-approx-function-space}
-%%   \transitionFn_{\weights_{i}^{*}}(\cdot) &\sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \quad
-%%   \mu_{\weights_{i}^{*}}(\cdot) &= \transitionFn_{\weights^{*}_{i}}(\cdot) \quad
-%%   K_{\weights_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\weights^{*}_{i}}(\cdot) \bm\Sigma_{\weights^{*}_{i}} \mathbf{J}_{\weights^{*}_{i}}(\cdot')^{T}
-%% \end{align}
-%% where the Jacobian is given by $\mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}$.
-%
-%% \begin{align} \label{eq-laplace-approx-jacobian}
-%% \mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}
-%% \end{align}
-%
-%
-%\subsection{Fast Updates}
-%Importantly, \cite{changFantasizingDualGPs2022} show that in the dual space,
-%conditioning on new observations reduces to suming the dual variables from the previous time
-%step with an update, given by,
-%\todo{pick best way to show new data (using superscript new or just time indexing?)}
-%\begin{align} \label{eq-dual-update-svgp}
-%\dualParam{1}^{t+1} &\leftarrow \dualParam{1}^{t} +  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))} \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right] \\
-%\dualParam{2}^{t+1} &\leftarrow \dualParam{2}^{t} +  \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))}  \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right]
-%\end{align}
-%Importantly, for a single new observation $((\state_{t}, \action_{t}), \state_{t+1})$ this update has
-%complexity $\mathcal{O}(\numInducing^{2})$.
-%This is a significant improvement to naive GP conditioning, which has complexity $\mathcal{O}((\numDataNew + \numDataOld)^{3})$
-%and sparse GP conditioning, which has complexity $\mathcal{O}((\numDataNew + \numDataOld)\numInducing^{2})$.
-%\todo{double check these complexities are right and cite them/show equaitons}
-%It is worth highlighting that the complexity of \cite{changFantasizingDualGPs2022} update does not increase during an episode.
-%
-%\subsubsection{Model-based RL}
-%
-%\subsubsection{Efficiently Sampling Functions for Posterior Sampling}
-%\cite{wilsonEfficiently2020}
-%\cite{wilsonPathwise2021}
-%
-%% \begin{align} \label{eq-dual-update-svgp}
-%%  \dualParam{1}^{\text{new}} &\leftarrow \dualParam{1}^{\text{old}} +
-%%   \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}))}
-%%  \left[ \log p(\state_{t+1}^{\text{new}} \mid \latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}) ) \right] \\
-%%  \dualParam{2}^{\text{new}} &\leftarrow \dualParam{2}^{\text{old}} +
-%%   \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}))}
-%%  \left[ \log p(\state_t^{\horizon+1} \mid \latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}) ) \right] \\
-%%  \dualParam{1}^{\horizon+1} &\leftarrow \dualParam{1}^{\horizon} +
-%%   \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}
-%%  \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right] \\
-%%  \dualParam{2}^{\horizon+1} &\leftarrow \dualParam{2}^{\horizon} +
-%%   \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}
-%%  \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right]
-%% \end{align}
-%
-%
-%\begin{assumption} \label{assumption-ntk-linearisation}
-%  Something about NTK being a linearisation around $\theta^{*}_{i}$ but each update moves away from $\theta^{*}_{i}$
-%\end{assumption}
-%
-%\cite{rossellApproximateLaplaceApproximations2021}
-
-\section{Experiments}
-\label{sec:experiments}
-
-\todo{Overview of experiments}
-
-Our experiments seek to answer the following questions:
-\begin{enumerate}
-  \item \textbf{Predictions} How do predictions with our sparse function-space approximation compare to weight-space approximations?
-Does our method's ability to consider the full data set offer benefits over subset function-space methods?
-  % \item Does our method's ability to consider the full data set offer benefits over subset function-space methods?
-  \item \textbf{Function-space updates} How fast are our function-space updates relative to retraining from scratch?
-Do they improve predictive performance?
-Are they as good as retraining from scratch?
-  \item \textbf{Uncertainty} How good are our uncertainty estimates? Can they be used in downstream settings like RL?
-  \item \textbf{Representation} Is our sparse function-space representation useful for continual learning?
-\end{enumerate}
-
-\subsection{Capturing uncertainty in UCI tasks under supervised learning}
-%
-
-\begin{table}[t!] 
-  \centering\scriptsize
-  \caption{Negative log predictive density (NLPD) (lower better) for the proposed model TODO} 
-	\label{tbl:uci}
-	% Control table spacing
-	\renewcommand{\arraystretch}{1.}
-	\setlength{\tabcolsep}{2pt}
-	\setlength{\tblw}{0.14\textwidth}
-
-	% Custom error formatting
-	\newcommand{\val}[2]{%
-		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
-	}
-
-    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
-	\input{tables/uci.tex}
-\end{table}
-We trained a two-layer MLP for each of the $8$ classification tasks in UCI, see \cref{tbl:uci} for a list of the datasets.
-The neural network training was done using MAP, with a prior $\mathcal{N}(0,\delta^{-1} \MI)$ with prior precision $\delta$.
-After training, we constructed the SVGP dual and used the resulting SVGP model for uncertainty quantification.
-Depending on task dimension and complexity, our model can match the NN MAP in NLPD performance even with a low number of inducing points, see \cref{tbl:uci}.
-We performed hyperparameter search over the prior precision, and ran the experiment over $10$ seeds.
-During the initial NN training, we used a learning rate of $1e-3$.
-
-\subsection{Supervised learning on image data sets}
-
-\begin{table}[t!] 
-  \centering\scriptsize
-  \caption{Metrics for supervised learning with image data.
-SVGP is our method, and the number inside parentheses is the number of inducing points.
-SVGP NN is a modification of our method, where the mean is from the NN directly and the variance is from the GP model}
-	\label{tbl:imagesuper}
-	% Control table spacing
-	\renewcommand{\arraystretch}{1.}
-	\setlength{\tabcolsep}{6pt}
-	\setlength{\tblw}{0.15\textwidth}
-
-	% Custom error formatting
-	\newcommand{\val}[2]{%
-		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
-	}
-
-    % THE TABLE CAN BE FORMATTED MORE LIKE THIS
-    \begin{tabular}{l l C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
-    \toprule
-    & Method & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ & OOD-AUC~$\uparrow$  \\
-    \midrule
-    \multirow{2}{*}{FMNIST} 
-    & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\    
-    \midrule
-    \multirow{2}{*}{CIFAR-10} 
-    & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\    
-    \bottomrule
-    \end{tabular}
-
-    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
-	%\input{tables/img_super.tex}
-\end{table}
-
-Similarly to the UCI experiments, we trained neural networks (CNN, architexture matches \citet{immer2021improving}) for the FMNIST and CIFAR10 classification tasks.
-After training, we computed the duals for NN2SVGP and used the resulting SVGP for uncertainty estimates, see \cref{tbl:imagesuper}.
-We performed hyperparameter optimization over the prior precision, and found the optimal value to be [insert].
-We ran the experiment over $5$ seeds.
-During the NN training, we used a batch size of $512$ and an Adam optimizer with learning rate $1e-3$.
-
-In addition to uncertainty estimates, our method can update the posterior when given new data.
-We gave the SVGP model 10 \% of the test dataset used for evaluation, and compare the performance of the SVGP model and the retrained NN in [INSERT TABLE].
-
-\subsection{Updating the  network representation for Continual learning}
-The Continual learning setting is a challenging and the training and
-
-\begin{table}[t!] 
-  \centering\scriptsize
-  \caption{
-  TODO: CL Experiments. $^*$ Methods relying only on weight regularization. 
-  \color{blue}{Results from \cite{rudner2022continual}.} 
-  %\color{red}{Preliminary results need more runs or hyperparam tuning}
-  }
-	\label{tbl:cl_table_1}
-	% Control table spacing
-	\renewcommand{\arraystretch}{1.}
-	\setlength{\tabcolsep}{2pt}
-	\setlength{\tblw}{0.14\textwidth}
-
-	% Custom error formatting
-	\newcommand{\val}[2]{%
-		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
-	}
-
-	\input{tables/cl_table_1}
-\end{table}
-
-\subsection{Reinforcement Learning}
-
-In section \label{sec-rl} we detailed how our method can be used to
-
-See \label{sec-rl-experiments-appendix} for more details of our experiments.
+\todo{could try to implement Pathwise conditioning in function-space}
+
+See \cref{app:rl} for more details of our experiments.
 
@@
  \centering
- \begin{subfigure}[c]{.24\textwidth}
+ \begin{subfigure}{.2\textwidth}
  \resizebox{\textwidth}{!}{%
@@
    % The arm
-   \node[anchor=north,minimum width=1cm,minimum height=14cm,draw=black,rotate=-20,rounded corners=5mm,yshift=7mm,xshift=-.3mm,fill=white,draw=black,line width=3pt] at (dot) {};
+   \node[anchor=north,minimum width=1cm,minimum height=14cm,draw=black,rotate=20,rounded corners=5mm,yshift=7mm,xshift=-.3mm,fill=white,draw=black,line width=3pt] at (dot) {};
    \node[fill=black,circle,minimum size=.5cm] at (dot) {};
@@
    % Arrow
-   \draw[->,black,line width=3pt,-{Latex[length=7mm,width=7mm]}] (1,5) --node[above,outer sep=8pt]{\scalebox{4}{$x$}} (4.5,5);
+   \draw[->,black,line width=3pt,-{Latex[length=7mm,width=7mm]}] (1,5) --node[above,outer sep=6pt]{\large $x$} (4.5,5);
 
@@
    % Draw arc
-   \centerarc[black,line width=3pt](dot)(250:270:11)
-   \node at (2.5,-9) {\scalebox{4}{$\theta$}};
-
-   %\node[white,minimum size=1cm] at (4.5,-13) {};
+   \centerarc[black,line width=3pt](dot)(270:290:11)
+   \node at (6.5,-9) {$\theta$};
+
+   \node[white,minimum size=1cm] at (4.5,-13) {};
 
@@
  \hfill
- \begin{subfigure}[c]{.74\textwidth}
+ \begin{subfigure}{.78\textwidth}
    \centering\scriptsize
@@
    \setlength{\figureheight}{.5\figurewidth}
-   \pgfplotsset{axis on top,ymajorgrids,axis line style={draw=none},legend style={at={(1,1)},anchor=north west}}
-   \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed},legend style={fill=white}}
+   \pgfplotsset{axis on top,ymajorgrids,axis line style={draw=none} }
+   \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
    \input{./fig/rl.tex}

### 2023-05-15 paper/main.tex
update Sec. 3

--- 2023-05-15 paper/main.tex
@@
 \newcommand{\vw}{\mbf{w}}
-\newcommand{\va}{\mbf{a}}
 
@@
 \paragraph{GP in the dual parameters}
-As stated in \citet[Parameterization Lemma~1]{csato2002sparse}, the posterior process $f_{\textrm{post}}$ found through the Bayesian update equation using  GP prior and likelihood function can be parameterized by $\valpha$ and $\vbeta$:
+As stated in \citet[Parameterization Lemma~1]{csato2002sparse}, the mean and covariance functions of the posterior process $f_{\textrm{post}}$, found through the Bayesian update using the GP prior and the likelihood function, can be parameterized by the dual parameters, $\valpha$ and $\vbeta$,
 \begin{equation}  \label{eq:gp_pred}
   \myexpect_{p(f_i \mid\vy)}[f_i]= \vk_{\vx i}^\top \valpha \quad \text{and} \quad
-  \mathrm{Var}_{p(f\mid\vy)}[f_i] = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
+  \mathrm{Var}_{p(f_i \mid \vy)}[f_i] = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
 \end{equation}
-the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{m \times m}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
+where the $ij$th entry of the matrix $\MKxx \in \R^{n \times n}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$th element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
 The dual parameters are the vector $\valpha \in \R^{m}$ and vector $\vbeta \in \R^{m}$, defined as:
@@
 It also highlights that our approximate inference technique, while usually considered a posterior approximation, can instead be seen as approximating the expectation of gradients of loss/likelihoods.
-In \citet{csato2002sparse}, they iteratively find dual variables setting them to log the expectation of the approximate posterior.
-At the same time, in \cite{adam2021dual, chang2020fast}, they showed this relationship for variational Gaussian processes where the above expectation is with respect to the approximate posterior from the variational approximation.
-The parameter $\alpha$ relates to non-Bayesian approaches, for example, support vector machines \citep{cortes1995support}, whose origins are found in work by \citet{kimeldorf1971some}.
-While in \citet{wilkinson2023bayes}, they show links between linearization methods and how they solve the \cref{eq:dual_param}.
+\todo{our approximation is late \cref{eq:dual_param_laplace}, saying this here is misleading}\\
+In \citet{csato2002sparse}, they iteratively find dual variables setting them to log the expectation of the approximate posterior.\todo{what does it mean?} 
+At the same time, in \cite{adam2021dual, chang2020fast}, they show this relationship for variational Gaussian processes where the above expectation is with respect to the approximate variational posterior.
+The dual parameter $\valpha$ appears also in non-Bayesian approaches, \eg, support vector machines \citep{cortes1995support}, whose origins are found in work by \citet{kimeldorf1971some}.
+While in \citet{wilkinson2023bayes}, they show links between linearization methods and how they solve the \cref{eq:dual_param}.\todo{is this last part used/referred somewhere else?}
 
 \paragraph{Dual parameters from NN}
-Given we are making a Laplace approximation of the neural network we can remove the expectation over the posterior (see Ch.~3.4.1 in \cite{rasmussen2006gaussian} for derivation).
-Meaning we arrive at the following dual variables.
+Given that we use a Laplace approximation of the neural network, we can remove the expectation over the posterior (see Ch.~3.4.1 in \cite{rasmussen2006gaussian} for derivation) and we get the the following formulation of the dual variables,
 \begin{equation}
@@
 
-Substiuting \cref{eq:dual_param_laplace} in to \cref{eq:gp_pred} and we arrive at our GP model based on the converged neural network.
-Again this is similar to what was derived in \citet{immerImprovingPredictionsBayesian2021} for the posterior variance function, but they instead use the $f_{\vw^*}$ for the posterior mean and fail to spot the significance of the dual variables.
+Substiuting \cref{eq:dual_param_laplace} into \cref{eq:gp_pred}, we obtain our GP model based on the converged neural network.
+Again, this is similar to what was derived in \citet{immer2021improving} for the posterior variance function.
+However, they use the $f_{\vw^*}$ for the posterior mean and do not spot the significance of the dual variables.
 The problem with \cref{eq:gp_pred} is that to make predictions and compute variances we must incur a cost of $O(n^3)$ which limits the use of the GP on large data sets.
@@
 Sparse Gaussian processes are a way to reduce the computational complexity of a full GP using a low-rank approximation.
-Many sparsifying approaches exist, we refer the reader to \cite{quinonero2005unifying} for an overview.
-Given that we have our dual variables derived from our neural network predictions and a kernel function, we could essentially use any approximation.
-We decide to follow the sparsifying approach of \citet{titsias2009variational} and also used in the DTC appeoximation \cite{quinonero2005unifying}, which is to define the marginal predictive distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) q(\vu)  d\vu$.
+Many sparsifying approaches exist and we refer the reader to \cite{quinonero2005unifying} for an overview.
+Given that we computed the dual variables derived from our neural network predictions and a kernel function, we could essentially use any approximation.\todo{approximation to get what?
+kernel and dual variables} We decide to follow the sparsifying approach of \citet{titsias2009variational} and also used in the DTC approximation \citep{quinonero2005unifying}, which defines the marginal predictive distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) q(\vu)  d\vu$.
 Given that we have $p(f_i  \mid \vu)$ determined by our GP prior, the goal is to find a $q(\vu)$.
@@
 As was shown in \cite{adam2021dual}, the posterior under this model has a particular structure similar to \cref{eq:gp_pred}.
-In the paper, they spot the dual variables' importance for approximate inference but write them in the natural parameter form as this form is more suitable for optimization through natural gradients.
-In order to make the link to the dual variables defined in \cref{eq:dual_param} we write them in the sparse GP in the dual variable form.
-%
+In the paper, the authors spot the dual variables' importance for approximate inference, but write them with the natural parameterization as this form is more suitable for optimization through natural gradients.
+In order to link the dual variables defined in \cref{eq:dual_param}, we write them in the sparse GP using the dual variables
 \begin{equation} 
@@
 \end{equation}
-the sparse dual variables are now a sum over all data points, with $\valpha_{\vu} \in \R^{M}$ and $\vbeta_{\vu} \in \R^{M  \times M}$.
-Using the sparse definition of the dual variables our sparse GP posterior takes the following form:
+where the sparse dual variables are now a sum over all data points, with $\valpha_{\vu} \in \R^{M}$ and $\vbeta_{\vu} \in \R^{M  \times M}$.
+Using these sparse definition of the dual variables, our sparse GP posterior takes the following form:
 \begin{equation}\label{eq:dual_sparse_post}
@@
 \end{equation}
-where $\MKzz$ and $\vkzs$ are define similarly to $\MKxx$ and $\vk_{\vx i}$ but now over the $\MZ \in \R^{M \times D} $ inducing points instead of the full dataset $\MX$.
-The key quantities we need to make predictions from our sparse GP from the converged neural network are $(\hat{\alpha}_i, \hat{\beta}_i)$ and a kernel function $\kappa$.
-Contrasting \cref{eq:dual_sparse_post} and \cref{eq:gp_pred} we can see that the computational complexity is now $\mathcal{O}(m^3)$ to $\mathcal{O}(n^3)$ where $m \ll n$.
-Crucially given the structure of our probabilistic model, our sparse dual variables \cref{eq:dual_sparse} are a compact form of the full model projected using the kernel.
-
-Our approach contrasts to \citet{immer2021improving}, which uses a subset of the full model to try to reduce complexity, a less principled approach to build a sparse model given it ignores the information in the dataset.
-It is important to highlight that the sparsifying process is independent of the approximate inference technique.
-The \cref{eq:dual_param} is a result of using \cref{eq-empirical-risk} and a Laplace approximation.
-More complicated inference techniques, such as variational inference, could be used, but given its simplicity, we only need a trained neural network; we use a Laplace approximation in our experiments.
-Furthermore, our dual variable view of approximate inference means we do not need to resort to retraining a separate sparse GP model.
+where $\MKzz$ and $\vkzs$ are defined similarly to $\MKxx$ and $\vk_{\vx i}$ but over the inducing points $\MZ \in \R^{M \times D} $  instead of the full dataset $\dataset$.
+The key quantities we need to make predictions from our sparse GP from the converged neural network are $(\hat{\alpha}_i, \hat{\beta}_i)$\todo{these variables need another subscript for differentiate that from the values computed at the data points} and a kernel function $\kappa$.
+Contrasting \cref{eq:dual_sparse_post} and \cref{eq:gp_pred}, we can see that the computational complexity went from $\mathcal{O}(n^3)$  $\mathcal{O}(m^3)$, with $m \ll n$.
+Crucially, given the structure of our probabilistic model, our sparse dual variables \cref{eq:dual_sparse} are a compact form \todo{use representation instead of form here ?} of the full model projected using the kernel.
+
+In contrast to our approach, \citet{immer2021improving} use a subset of the full GP model \todo{isn't the subset on the data points?} to reduce the computational complexity.
+As a result, this is a less principled approach for building a sparse model since it ignores the dataset's information.
+It is important to highlight that the sparsifying process is independent of the approximate inference technique because the dual variables of \cref{eq:dual_param} are computed using the neural network definition \cref{eq-empirical-risk}.
+More complicated inference techniques, such as variational inference, could be used, but given its simplicity, in our experiments we used the Laplace-GGN approximation with the trained neural network.
+Furthermore, our dual variable view of approximate inference means we do not need to retrain a separate sparse GP model.
+\todo{shouldn't this sentence be clear from the context?
+we derive the mean/kernel function that define the process, then we have a sparse GP already}
 
@@
 After each task, we can use our \our to build a compact representation of the neural network and then use that as an additional term to the training loss to regularize the model.
-Recent success has shown GP-based regularizers perform better than weight space equivalents getting state-of-the-art on typical CL benchmarks \cite{ pan2020continual, rudner2022continual}.
-The limitation of such approaches is that they must use subset approximations of the posterior, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer.
-A more principled approach would be to sparsify the data into a low-rank approximation to ensure information wasn't lost, essentially what the sparse dual variables do.
 \todo{this term is replacing the missing data}
-
-An alternative view of the dual variables is that they parameterize approximate likelihoods, as shown in \citep{adam2021dual, khan2017conjugate}.
-We can rewrite the GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
-\begin{equation}
- q(\vu) \propto \N(0, \MKzz) \prod_{i=1}^n e^{-\frac{\tilde{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 } = \N(0, \MKzz) \, e^{(\bar{\vy} - \vu)^\top \bar{\MSigma}^{-1}(\bar{\vy} - \vu)}  
-\end{equation}
-The first normals are the approximate likelihoods where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}$,  replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$ and we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior.
-To arrive at the MVN Gaussian, we need to rearrange the quadratic terms to match the prior sufficient statistics we present a derivation in [appendix].
-Performing conjugate summation of prior and likelihood, we would arrive at the sparse GP posterior at the inducing points.
-The correlated covariance structure $\MSigma$ and the corresponding $\tilde{\vy}$ are simply a different form of the sparse dual variables,
-\begin{equation}
-\quad \bar{\MSigma} =  \MKzz \vbeta_\vu^{-1} \MKzz \quad \bar{\vy} = \MKzz \vbeta_{\vu}\valpha_{\vu}.
-\end{equation}
-Written as above, we can see that the spare dual variables can be interpreted as a sparse MVN representation.
-We now show how we use this for a regularizer in continual learning with more details in [appendix].
 
@@
    \setlength{\figureheight}{.5\figurewidth}
-   \pgfplotsset{axis on top,ymajorgrids,axis line style={draw=none},legend style={at={(1,1)},anchor=north west}}
-   \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed},legend style={fill=white}}
+   \pgfplotsset{axis on top}
    \input{./fig/rl.tex}

### 2023-05-15 paper/main.tex

@@
 As a result, this is a less principled approach for building a sparse model since it ignores the dataset's information.
-It is important to highlight that the sparsifying process is independent of the approximate inference technique because the dual variables of \cref{eq:dual_param} are computed using the neural network definition \cref{eq-empirical-risk}.
+It is important to highlight that the sparsifying process is independent of the approximate inference technique because the dual variables of \cref{eq:dual_param} are computed using \cref{eq-empirical-risk} and a Laplace approximation.
 More complicated inference techniques, such as variational inference, could be used, but given its simplicity, in our experiments we used the Laplace-GGN approximation with the trained neural network.
@@
 we derive the mean/kernel function that define the process, then we have a sparse GP already}
-
 \section{Sparse Function-space Sequential Learning}
@@
 After each task, we can use our \our to build a compact representation of the neural network and then use that as an additional term to the training loss to regularize the model.
+Recent success has shown GP-based regularizers perform better than weight space equivalents getting state-of-the-art on typical CL benchmarks \cite{ pan2020continual, rudner2022continual}.
+The limitation of such approaches is that they must use subset approximations of the posterior, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer.
+A more principled approach would be to sparsify the data into a low-rank approximation to ensure information wasn't lost, essentially what the sparse dual variables do.
 \todo{this term is replacing the missing data}
+
+An alternative view of the dual variables is that they parameterize approximate likelihoods, as shown in \citep{adam2021dual, khan2017conjugate}.
+We can rewrite the GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
+\begin{equation}
+ q(\vu) \propto \N(0, \MKzz) \prod_{i=1}^n e^{-\frac{\tilde{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 } = \N(0, \MKzz) \, e^{(\bar{\vy} - \vu)^\top \bar{\MSigma}^{-1}(\bar{\vy} - \vu)}  
+\end{equation}
+The first normals are the approximate likelihoods where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}$,  replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$ and we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior.
+To arrive at the MVN Gaussian, we need to rearrange the quadratic terms to match the prior sufficient statistics we present a derivation in [appendix].
+Performing conjugate summation of prior and likelihood, we would arrive at the sparse GP posterior at the inducing points.
+The correlated covariance structure $\MSigma$ and the corresponding $\tilde{\vy}$ are simply a different form of the sparse dual variables,
+\begin{equation}
+\quad \bar{\MSigma} =  \MKzz \vbeta_\vu^{-1} \MKzz \quad \bar{\vy} = \MKzz \vbeta_{\vu}\valpha_{\vu}.
+\end{equation}
+Written as above, we can see that the spare dual variables can be interpreted as a sparse MVN representation.
+We now show how we use this for a regularizer in continual learning with more details in [appendix].
 

### 2023-05-15 paper/main.tex
mINor

--- 2023-05-15 paper/main.tex
@@
 It is important to highlight that the sparsifying process is independent of the approximate inference technique.
-The \cref{eq:dual_param} is a result of using \cref{eq-empirical-risk} and a Laplace approximation.
+The \cref{eq:dual_param} are from the neural network definition \cref{eq-empirical-risk}.
 More complicated inference techniques, such as variational inference, could be used, but given its simplicity, we only need a trained neural network; we use a Laplace approximation in our experiments.
@@
 After each task, we can use our \our to build a compact representation of the neural network and then use that as an additional term to the training loss to regularize the model.
-Recent success has shown GP-based regularizers perform better than weight space equivalents getting state-of-the-art on typical CL benchmarks \cite{ pan2020continual, rudner2022continual}.
-The limitation of such approaches is that they must use subset approximations of the posterior, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer.
-A more principled approach would be to sparsify the data into a low-rank approximation to ensure information wasn't lost, essentially what the sparse dual variables do.
 \todo{this term is replacing the missing data}
 
-An alternative view of the dual variables is that they parameterize approximate likelihoods, as shown in \citep{adam2021dual, khan2017conjugate}.
-We can rewrite the GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
+An alternative view of the dual variables is that they parameterize approximate likelihoods as was shown in \citep{adam2021dual} we can rewrite the GP posterior in terms of the following approximate normal distributions:
 \begin{equation}
- q(\vu) \propto \N(0, \MKzz) \prod_{i=1}^n e^{-\frac{\tilde{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 } = \N(0, \MKzz) \, e^{(\bar{\vy} - \vu)^\top \bar{\MSigma}^{-1}(\bar{\vy} - \vu)}  
+ q(\vu) \propto \N(0, \MKzz) \prod_{i=1}^n e^{-\frac{\hat{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 } = \N(0, \MKzz) \, e^{(\tilde{\vy} - \vu)^\top\tilde{\MSigma}^{-1}(\tilde{\vy} - \vu)}  
 \end{equation}
-The first normals are the approximate likelihoods where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}$,  replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$ and we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior.
-To arrive at the MVN Gaussian, we need to rearrange the quadratic terms to match the prior sufficient statistics we present a derivation in [appendix].
-Performing conjugate summation of prior and likelihood, we would arrive at the sparse GP posterior at the inducing points.
-The correlated covariance structure $\MSigma$ and the corresponding $\tilde{\vy}$ are simply a different form of the sparse dual variables,
-\begin{equation}
-\quad \bar{\MSigma} =  \MKzz \vbeta_\vu^{-1} \MKzz \quad \bar{\vy} = \MKzz \vbeta_{\vu}\valpha_{\vu}.
-\end{equation}
-Written as above, we can see that the spare dual variables can be interpreted as a sparse MVN representation.
-We now show how we use this for a regularizer in continual learning with more details in [appendix].
+The first normals are the marginal likelihoods were $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}$,  replacing $\va_i^\top \vu$  wtih $\vx_i^{\top}\vw$ and we can see the similarity between the sparse GP and a linear model where the prior is determined by the kernel matrix.
+To arrive at the MVN Gaussian we need to rearrange the quadratic terms to match the prior sufficient statistics we present a derivation in [appendix].
+Performing conjugate summation of prior and likelihood we would arrive at the sparse GP posterior at the inducing points $\MZ$.
+The correlated covariance structure $\MSigma$ and the corresponding $\tilde{\vy}$ are simply a different form of the sparse dual variables
 
@@
 
-% We start by obtaining a posterior over the weights of a trained neural network via the Laplace approximation.
-% We then show how we can obtain a function-space posterior, (i.e. a GP posterior)
-% by linearising the neural network around the weights Maximum a Posteriori (MAP) estimate.
-% We then show that by linearising the neural network we can obtain a function-space posterior, i.e. a GP posterior.
-% We paraterise our single-step dynamic model $\transitionFnWithParams : \inputDomain \rightarrow \outputDomain$
-% as an $L\text{-layer}$ NN with weights $\weights$.
-
-%A Gaussian process (GP) is a distribution over real-valued functions $f(\cdot): \mathcal{X} \rightarrow \R$ defined over $\mathcal{X}$.
-%Formally, a GP is defined as,
-%\begin{align}
-%\label{eq-gp-prior}
-%  f(\cdot) \sim \mathcal{N}\left( \mu(\cdot), k(\cdot,\cdot') \right) \quad
-%  \mu(\cdot): \mathcal{X} \rightarrow \R \quad
-%  k(\cdot,\cdot'): \mathcal{X} \times \mathcal{X} \rightarrow \R
-%\end{align}
-%where $\mu(\cdot)$ denotes a mean function and $k(\cdot,\cdot')$ a positive definite covariance function, also known as a kernel.
-%Given a data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
-%we can obtain the GP posterior via multivariate normal conditioning,
-%\begin{align}
-%\label{eq-gp-predictive-posterior}
-%  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
-%  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
-%  \left( f(\mathbf{x}_{*}) \mid \mu(\mathbf{x}_{*}) + \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} (\mathbf{y} - \bm\mu_{\mathbf{X}})),
-%  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
-%\end{align}
-%% Our GP posterior is then given by,
-%\todo{add mean func to GP posterior if we're using one}
-%\begin{align}
-%\label{eq-gp-predictive-posterior}
-%  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
-%  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
-%  \left( f(\mathbf{x}_{*}) \mid \mu(\mathbf{x}_{*}) + \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} \mu_{\mathbf{x}},
-%  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} + \bm\Lambda(\mathbf{y} ; \mathbf{f})^{-1} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
-%\end{align}
-%where $\bm\Lambda(\mathbf{y} ; \mathbf{f}) = \nabla^{2}_{\mathbf{f} \mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$ can be viewed as per-input noise.
-\todo{I'm unsure about this per input noise bit.
-Check with paul.}
-%\todo{what about regression/classification likelhoods}
-%This GP predictive posterior is computationally expensive as it requires inverting an $N\times N$ matrix.
-%
-%\textbf{Sparse Gaussian processes}
-%% The GP predictive posterior in \cref{eq-gp-predictive-posterior} is computationally expensive as it requires inverting an $N\times N$ matrix.
-%A practical and computationally appealing alternative is to augment the joint probability space with pseudo inputs $\mathbf{Z} \in \R^{M \times D}$
-%and corresponding outputs
-%$\mathbf{u} = f(\mathbf{Z}; \weights) \in \R^{M \times C}$, known as inducing variables, where $M \ll N$.
-%\todo{cite sparse gp papers}
-%Instead of collapsing the inducing variables like \cite{titsiasVariational2009}, they can be treated variationally
-%$p(\mathbf{u} \mid \mathbf{y}) \approx q(\mathbf{u}) = \mathcal{N}\left( \mathbf{u} \mid \mathbf{m}, \mathbf{V} \right)$, where $\mathbf{m}$ and $\mathbf{V}$ are variational parameters
-%which need to be optimised \citep{hensmanGaussian2013}.
-%The sparse variational GP (SVGP) predictive posterior is then given by,
-%\begin{align}
-%\label{eq-dual-svgp-predictive-posterior}
-%  p(f(\mathbf{x}_{*}) \mid \mathbf{y})
-%&\approx \mathcal{N} \left( f(\mathbf{x}_{*}) \mid \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{m}^{*},
-%  k_{**} - \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
-%  % \mathbf{k}_{*\inducingInput} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\inducingInput}^{T}
-%  + \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}}  \mathbf{V}^{*}  \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
-%  \right)
-%\coloneqq q_{\inducingVariable}(f(\mathbf{x}_{*}))
-%\end{align}
-%
-%
-%\textbf{Deep learning}
-%Given the data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
-%the goal of (supervised) deep learning, is to train the weights $\weights \in \R^{P}$ of an $L\text{-layer}$ NN
-%$f : \inputDomain \rightarrow \outputDomain$ to minimize the (regularized) empirical risk,
-%\begin{align} \label{eq-empirical-risk}
-%  \weights^{*} = \arg \min_{\weights \in \R^{D}} \mathcal{L}(\dataset;\weights) = \arg \min_{\weights \in \R^{D}} \left(
-%  \sum_{n=0}^{N-1} l(f(\mathbf{x}_{n} ; \weights), \mathbf{y}_{n}) + R(\weights)  \right).
-%\end{align}
-%In practice, it is common to use the mean squared error (MSE) loss
-%$l(f(\mathbf{x}_{n} ; \weights),\mathbf{y}_{n}) = \|f(\mathbf{x}_{n} ; \weights) - \mathbf{y}_{n} \|^{2}_{2}$
-%and to use the weight decay regularizer $R(\weights)=\frac{1}{2}\gamma^{-2}\|\weights\|^{2}_{2}$.
-%However, the practioner is free to choose any loss and regularizer. \todo{I think?}
-%% \textbf{Bayesian neural networks}
-%% \textbf{Weight space to function space}
-%From a Bayesian perspective, we can interpret the terms in \cref{eq-empirical-risk} as the log-prior and the i.i.d. log likelihood, i.e.,
-%\begin{align} \label{eq-log-prior}
-%  R(\weights) &= \underbrace{\log p(\weights)}_{\text{log prior}} = \log \mathcal{N}(\weights \mid 0, \gamma^{2} \mathbf{I}) \\
-%  l(f(\mathbf{x}_{n} ; \weights), \mathbf{y}_{n}) &= \underbrace{\log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \weights))}_{\text{log likelihood}}
-%  = \log \mathcal{N} \left( \mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \weights), \mathbf{I} \right) \label{eq-log-likelihood}
-%\end{align}
-%
-%\textbf{NN to GP}
-%Given this interpretation, we can represent the weight space prior from \cref{eq-log-prior}, in
-%function space, by linearising the BNN around $\weights^{*}$ and interpretting it as a GP.
-%The GP prior is then given by,
-%\begin{align} \label{eq-laplace-approx-function-space}
-%  % \transitionFn_{\weights_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \qquad
-%  f(\cdot ;\weights) \sim \mathcal{N} \left( \mu(\cdot), k(\cdot, \cdot') \right) \quad
-%  % \mu_{\weights_{i}^{*}}(\cdot)
-%  \mu(\cdot)
-%  = 0 \quad
-%  % = f(\cdot ;\weights^{*}) \quad
-%  % K_{\weights_{i}^{*}}(\cdot, \cdot')
-%  k(\cdot, \cdot')
-%  = \frac{1}{\gamma^{2}} \mathbf{J}(\cdot) \mathbf{J}(\cdot')^{T},
-%\end{align}
-%where the kernel is the neural tangent kernel (NTK) \citep{immerImprovingPredictionsBayesian2021},
-%\todo{what mean function shoudl this use???}
-%\todo{NTK times some factor??}
-%with Jacobian given by $\mathbf{J}(\cdot) = \odv{\transitionFn(\cdot; \weights)}{\weights}_{\weights=\weights^{*}}$.
-%% The kernel in \cref{eq-laplace-approx-function-space} is the neural tangent kernel (NTK)
-%% $k(\mathbf{x}, \mathbf{x}') = \sigma_{0}^{2} J_{\weights^{*}}(\mathbf{x}) J_{\weights^{*}}(\mathbf{x}')^{T}$
-%% \citep{immerImprovingPredictionsBayesian2021}
-%% to formulate the GP posterior $p(f(\mathbf{X} ;\weights_{0:i}) \mid \dataset_{0:i})$.
-%Given this GP prior, we can use \cref{eq-gp-predictive-posterior} to obtain our GP posterior by conditioning on the data.
-%% Given our GP prior, we can use the properties of multivariate normals to obtain our GP posterior by conditioning on the data.
-%% where $\mathbf{A} = \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}}$
-%In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
-%Intuitively, we can view the optimisation in \cref{eq-empirical-risk} as learning our kernel.
-%As a result, our NTK may be highly non stationary as it is dependent on the NN architecture, for example, the activation functions.
-%It is worth noting that the NTK linearises the network around the optimised parameters $\weights^{*}$,
-%so the function space prior (and thus posterior) is only a locally linear approximation.
-%
-%We now have a method to obtain a GP posterior from a trained DNN.
-%% In contrast to other approaches, our formulation has not restricted us to using a weight-space posterior obtained from the Laplace approximation.
-%In contrast to other approaches, our formulation has not restricted us to using a weight-space posterior from a BNN.
-%However, in practice, the GP posterior is not very useful as it requires inverting an $N\times N$ matrix which has complexity $\mathcal{O}(N^{3})$.
-%The SVGP in \cref{eq-dual-svgp-predictive-posterior} offers a solution to this problem but it is not immediately clear how to set $\mathbf{m}$ and $\mathbf{V}$.
-%In the next section, we show how we can directly obtain an SVGP posterior (i.e. set $\mathbf{m}$ and $\mathbf{V}$) directly from both
-%1) a trained NN and 2) a BNN weight-space posterior.
-%% $\mathbf{m}$ and $\mathbf{V}$
-%% However, it is not obvious how we can use a SVGP to set $\mathbf{m}$ and $\mathbf{V}$
-%
-%
-%
-%% In contrast, to previous work, this approach did not require us Laplace approximation. we will not restrict our
-%% It is worth noting that the NTK linearises the network around the optimised parameters $\weights^{*}$,
-%% so the function space prior (and thus posterior) is only a locally linear approximation.
-%% In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
-%% It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.
-%
-%
-%\section{Methods}
-%In the next section we show how we can obtain a SVGP directly from 1) a trained NN and 2) a BNN posterior.
-%
-%We follow \cite{csatoSparseOnlineGaussian2002} and express our GP posterior in the dual parameter space.
-%However, we consider the variational formulation introduced by \cite{adamDualParameterizationSparse2021}, where the optimal variational parameters are given by,
-%\begin{align} \label{eq-dual-params}
-%\mathbf{m}^{*} = \mathbf{V}^{*}\bm\alpha^{*} \quad \mathbf{V}^{*} = [\mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} + \bm\beta^{*}]
-%\end{align}
-%Importantly, we can calculate the natural parameters $(\bm\alpha, \bm\beta)$ in closed form,
-%\todo{paul needs to update \cref{eq-dual-svgp-params}}
-%\begin{align} \label{eq-dual-svgp-params}
-%\bm\alpha_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right] \\
-%\bm\beta_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right].
-%\end{align}
-%This simplifies SVGP inference \citep{hensmanGaussian2013} as it no longer requires the variational parameters $(\mathbf{m}, \mathbf{V})$ to be optimised.
-%
-%% Importantly, \cite{changFantasizingDualGPs2022} show that in the dual space,
-%% conditioning on new observations reduces to suming the dual variables from the previous time
-%% step with an update, given by,
-%% \todo{pick best way to show new data (using superscript new or just time indexing?)}
-%% \begin{align} \label{eq-dual-update-svgp}
-%% \bm\alpha_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right] \\
-%% \bm\beta_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right]
-%% \end{align}
-%
-%% We follow \cite{csatoSparseOnlineGaussian2002} and express our GP posterior in the dual parameter space,
-%% % to write GP posterior $p(f(\mathbf{X} ;\weights_{0:i}) \mid \dataset_{0:i})$ as,
-%% \begin{align} \label{eq-gp-post}
-%%   \mathbb{E}_{p(f(\mathbf{x}_{*}) \mid \mathbf{y}_{n})} \left[ f(\mathbf{x}_{*}) \right] &= \mu(\mathbf{x}_{*}) + \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
-%%   \mathbb{V}_{p(f(\mathbf{x}_{*}) \mid \mathbf{y}_{n})} \left[ f(\mathbf{x}_{*}) \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \text{diag}(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
-%% \end{align}
-%% % \begin{align} \label{eq-laplace-approx-function-space}
-%% %   \mathbb{E}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
-%% %   \mathbb{V}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \diag(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
-%% % \end{align}
-%% where the dual parameters $(\bm\alpha_n, \bm\beta_n)$ are vectors of,
-%% \begin{align} \label{eq-gp-dual-params}
-%%   \bm\alpha_{n} \coloneqq \left\{ \mathbb{E}_{p(f(\mathbf{x}_{i}) \mid \mathbf{y}_{n})} \left[ \nabla_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \right\}_{i=1}^{N} \qquad
-%%   \bm\beta_{n} \coloneqq \left\{ \mathbb{E}_{p(f(\mathbf{x}_{i}) \mid \mathbf{y}_{n})} \left[ \nabla^{2}_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \right\}_{i=1}^{N}
-%% \end{align}
-%% Importantly, this parameterisation
-%
-%% \textbf{dual-SVGP}
-%% \begin{align} \label{eq-svgp-post}
-%%   \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ f(\mathbf{x}_{*}) \right] &= \mu(\mathbf{x}_{*}) + \mathbf{k}_{\mathbf{z}*}^{T} \bm\alpha_{\mathbf{u}} \\
-%%   \mathbb{V}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ f(\mathbf{x}_{*}) \right] &= k_{**} - \mathbf{k}_{\mathbf{z}*}^{T} \left[ \mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} - \left( \mathbf{K}_{\mathbf{z} \mathbf{z}} + \bm\beta_{\mathbf{u}} \right)^{-1} \right] \mathbf{k}_{\mathbf{z}*}
-%% \end{align}
-%% % \begin{align} \label{eq-laplace-approx-function-space}
-%% %   \mathbb{E}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
-%% %   \mathbb{V}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \diag(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
-%% % \end{align}
-%% where the dual parameters $(\bm\alpha_{\mathbf{u}}, \bm\beta_{\mathbf{u}})$ are vectors of,
-%% \begin{align} \label{eq-svgp-dual-params}
-%%   \bm\alpha_{\mathbf{u}} \coloneqq \mathbf{k}_{\mathbf{z}i} \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ \nabla_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \qquad
-%%   \bm\beta_{\mathbf{u}} \coloneqq \mathbf{k}_{\mathbf{z}i} \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ \nabla^{2}_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \mathbf{k}_{\mathbf{z}i}^{T}
-%% \end{align}
-%
-%% weight space posterior in \cref{eq-laplace-approx-weight-space} in
-%% function space by linearising the BNN and interpreting it as a GP.
-%% \begin{align} \label{eq-laplace-approx-function-space}
-%%   \transitionFn_{\weights_{i}}(\cdot) &\sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \quad
-%%   \mu_{\weights_{i}^{*}}(\cdot) &= \transitionFn_{\weights^{*}_{i}}(\cdot) \quad
-%%   K_{\weights_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\weights^{*}_{i}}(\cdot) \bm\Sigma_{\weights^{*}_{i}} \mathbf{J}_{\weights^{*}_{i}}(\cdot')^{T}
-%% \end{align}
-%% where the Jacobian is given by $\mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}$.
-%
-%% \begin{align} \label{eq-laplace-approx-jacobian}
-%% \mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}
-%% \end{align}
-%
-%
-%% % Note that the posterior in \cref{eq-laplace-approx-weight-space} is in weight space.
-%% We can represent the weight space posterior in \cref{eq-laplace-approx-weight-space} in
-%% function space by linearising the BNN and interpreting it as a GP.
-%% \begin{align} \label{eq-laplace-approx-function-space}
-%%   \transitionFn_{\weights_{i}^{*}}(\cdot) &\sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \quad
-%%   \mu_{\weights_{i}^{*}}(\cdot) &= \transitionFn_{\weights^{*}_{i}}(\cdot) \quad
-%%   K_{\weights_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\weights^{*}_{i}}(\cdot) \bm\Sigma_{\weights^{*}_{i}} \mathbf{J}_{\weights^{*}_{i}}(\cdot')^{T}
-%% \end{align}
-%% where the Jacobian is given by $\mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}$.
-%
-%% \begin{align} \label{eq-laplace-approx-jacobian}
-%% \mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}
-%% \end{align}
-%
-%
-%\subsection{Fast Updates}
-%Importantly, \cite{changFantasizingDualGPs2022} show that in the dual space,
-%conditioning on new observations reduces to suming the dual variables from the previous time
-%step with an update, given by,
-%\todo{pick best way to show new data (using superscript new or just time indexing?)}
-%\begin{align} \label{eq-dual-update-svgp}
-%\dualParam{1}^{t+1} &\leftarrow \dualParam{1}^{t} +  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))} \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right] \\
-%\dualParam{2}^{t+1} &\leftarrow \dualParam{2}^{t} +  \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))}  \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right]
-%\end{align}
-%Importantly, for a single new observation $((\state_{t}, \action_{t}), \state_{t+1})$ this update has
-%complexity $\mathcal{O}(\numInducing^{2})$.
-%This is a significant improvement to naive GP conditioning, which has complexity $\mathcal{O}((\numDataNew + \numDataOld)^{3})$
-%and sparse GP conditioning, which has complexity $\mathcal{O}((\numDataNew + \numDataOld)\numInducing^{2})$.
-%\todo{double check these complexities are right and cite them/show equaitons}
-%It is worth highlighting that the complexity of \cite{changFantasizingDualGPs2022} update does not increase during an episode.
-%
-%\subsubsection{Model-based RL}
-%
-%\subsubsection{Efficiently Sampling Functions for Posterior Sampling}
-%\cite{wilsonEfficiently2020}
-%\cite{wilsonPathwise2021}
-%
-%% \begin{align} \label{eq-dual-update-svgp}
-%%  \dualParam{1}^{\text{new}} &\leftarrow \dualParam{1}^{\text{old}} +
-%%   \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}))}
-%%  \left[ \log p(\state_{t+1}^{\text{new}} \mid \latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}) ) \right] \\
-%%  \dualParam{2}^{\text{new}} &\leftarrow \dualParam{2}^{\text{old}} +
-%%   \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}))}
-%%  \left[ \log p(\state_t^{\horizon+1} \mid \latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}) ) \right] \\
-%%  \dualParam{1}^{\horizon+1} &\leftarrow \dualParam{1}^{\horizon} +
-%%   \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}
-%%  \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right] \\
-%%  \dualParam{2}^{\horizon+1} &\leftarrow \dualParam{2}^{\horizon} +
-%%   \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}
-%%  \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right]
-%% \end{align}
-%
-%
-%\begin{assumption} \label{assumption-ntk-linearisation}
-%  Something about NTK being a linearisation around $\theta^{*}_{i}$ but each update moves away from $\theta^{*}_{i}$
-%\end{assumption}
-%
-%\cite{rossellApproximateLaplaceApproximations2021}
-
-\section{Experiments}
-\label{sec:experiments}
-
-\todo{Overview of experiments}
-
-Our experiments seek to answer the following questions:
-\begin{enumerate}
-  \item \textbf{Predictions} How do predictions with our sparse function-space approximation compare to weight-space approximations?
-Does our method's ability to consider the full data set offer benefits over subset function-space methods?
-  % \item Does our method's ability to consider the full data set offer benefits over subset function-space methods?
-  \item \textbf{Function-space updates} How fast are our function-space updates relative to retraining from scratch?
-Do they improve predictive performance?
-Are they as good as retraining from scratch?
-  \item \textbf{Uncertainty} How good are our uncertainty estimates? Can they be used in downstream settings like RL?
-  \item \textbf{Representation} Is our sparse function-space representation useful for continual learning?
-\end{enumerate}
-
-\subsection{Capturing uncertainty in UCI tasks under supervised learning}
-%
-
-\begin{table}[t!] 
-  \centering\scriptsize
-  \caption{Negative log predictive density (NLPD) (lower better) for the proposed model TODO} 
-	\label{tbl:uci}
-	% Control table spacing
-	\renewcommand{\arraystretch}{1.}
-	\setlength{\tabcolsep}{2pt}
-	\setlength{\tblw}{0.14\textwidth}
-
-	% Custom error formatting
-	\newcommand{\val}[2]{%
-		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
-	}
-
-    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
-	\input{tables/uci.tex}
-\end{table}
-We trained a two-layer MLP for each of the $8$ classification tasks in UCI, see \cref{tbl:uci} for a list of the datasets.
-The neural network training was done using MAP, with a prior $\mathcal{N}(0,\delta^{-1} \MI)$ with prior precision $\delta$.
-After training, we constructed the SVGP dual and used the resulting SVGP model for uncertainty quantification.
-Depending on task dimension and complexity, our model can match the NN MAP in NLPD performance even with a low number of inducing points, see \cref{tbl:uci}.
-We performed hyperparameter search over the prior precision, and ran the experiment over $10$ seeds.
-During the initial NN training, we used a learning rate of $1e-3$.
-
-\subsection{Supervised learning on image data sets}
-
-\begin{table}[t!] 
-  \centering\scriptsize
-  \caption{Metrics for supervised learning with image data.
-SVGP is our method, and the number inside parentheses is the number of inducing points.
-SVGP NN is a modification of our method, where the mean is from the NN directly and the variance is from the GP model}
-	\label{tbl:imagesuper}
-	% Control table spacing
-	\renewcommand{\arraystretch}{1.}
-	\setlength{\tabcolsep}{6pt}
-	\setlength{\tblw}{0.15\textwidth}
-
-	% Custom error formatting
-	\newcommand{\val}[2]{%
-		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
-	}
-
-    % THE TABLE CAN BE FORMATTED MORE LIKE THIS
-    \begin{tabular}{l l C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
-    \toprule
-    & Method & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ & OOD-AUC~$\uparrow$  \\
-    \midrule
-    \multirow{2}{*}{FMNIST} 
-    & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\    
-    \midrule
-    \multirow{2}{*}{CIFAR-10} 
-    & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\    
-    \bottomrule
-    \end{tabular}
-
-    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
-	%\input{tables/img_super.tex}
-\end{table}
-
-Similarly to the UCI experiments, we trained neural networks (CNN, architexture matches \citet{immer2021improving}) for the FMNIST and CIFAR10 classification tasks.
-After training, we computed the duals for NN2SVGP and used the resulting SVGP for uncertainty estimates, see \cref{tbl:imagesuper}.
-We performed hyperparameter optimization over the prior precision, and found the optimal value to be [insert].
-We ran the experiment over $5$ seeds.
-During the NN training, we used a batch size of $512$ and an Adam optimizer with learning rate $1e-3$.
-
-In addition to uncertainty estimates, our method can update the posterior when given new data.
-We gave the SVGP model 10 \% of the test dataset used for evaluation, and compare the performance of the SVGP model and the retrained NN in [INSERT TABLE].
-
-\subsection{Updating the  network representation for Continual learning}
-The Continual learning setting is a challenging and the training and
-
-\begin{table}[t!] 
-  \centering\scriptsize
-  \caption{
-  TODO: CL Experiments. $^*$ Methods relying only on weight regularization. 
-  \color{blue}{Results from \cite{rudner2022continual}.} 
-  %\color{red}{Preliminary results need more runs or hyperparam tuning}
-  }
-	\label{tbl:cl_table_1}
-	% Control table spacing
-	\renewcommand{\arraystretch}{1.}
-	\setlength{\tabcolsep}{2pt}
-	\setlength{\tblw}{0.14\textwidth}
-
-	% Custom error formatting
-	\newcommand{\val}[2]{%
-		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
-	}
-
-	\input{tables/cl_table_1}
-\end{table}
-
 \subsection{Reinforcement learning}
-A key challenge in RL is balancing the trade-off between exploration and exploitation.
+A key challenge in RL is to balance the trade-off between exploration and exploitation.
 That is, should the agent select an action that it knows will lead to a high reward (exploitation), or should it
 hope to discover new actions which lead to high reward (exploration) by selecting actions that it has not selected before.
-In this section, we demonstrate  that our method's principled uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim.
-
-We consider environments with states \(\state \in \stateDomain \subseteq \R^{D_{\state}} \),
+In this section, we detail how our method's principled uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim.
+
+We consider stochastic environments with states \(\state \in \stateDomain \subseteq \R^{D_{\state}} \),
 actions \(\action \in \actionDomain \subseteq \R^{D_{\action}}\) and transition dynamics
@@
 In this work, we consider model-based RL where a model of the transition dynamics is learned \(f_{\mathbf{w}} \approx \transitionFn\) and then used by a planning algorithm.
-A simple approach is to use the learned dynamic model $f_{\mathbf{w}^{*}}$ and maximise the objective in \cref{eq-model-free-objective}.
-% \begin{align} \label{eq-greedy}
-%   \policy^{\text{Greedy}} &= \arg \max_{\pi \in \Pi} J(f_{\mathbf{w}^{*}}, \pi).
-% \end{align}
+A simple approach is to use the learned dynamic model $f_{\mathbf{w}^{*}}$ and maximise the objective in \cref{eq-model-free-objective},
+\begin{align} \label{eq-greedy}
+  \policy^{\text{Greedy}} &= \arg \max_{\pi \in \Pi} J(f_{\mathbf{w}^{*}}, \pi).
+\end{align}
 However, we can leverage the method in \cref{sec:methods} to obtain a function-space posterior over the learned dynamics $q_{\mathbf{u}}(\hat{\transitionFn} \mid \dataset)$,
@@
 
-\todo{could try to implement Pathwise conditioning in function-space}
-
-See \cref{app:rl} for more details of our experiments.
+\textbf{Pathwise conditioning in function-space??}
+\todo{could try to implement this}
+
+% We start by obtaining a posterior over the weights of a trained neural network via the Laplace approximation.
+% We then show how we can obtain a function-space posterior, (i.e. a GP posterior)
+% by linearising the neural network around the weights Maximum a Posteriori (MAP) estimate.
+% We then show that by linearising the neural network we can obtain a function-space posterior, i.e. a GP posterior.
+% We paraterise our single-step dynamic model $\transitionFnWithParams : \inputDomain \rightarrow \outputDomain$
+% as an $L\text{-layer}$ NN with weights $\weights$.
+
+%A Gaussian process (GP) is a distribution over real-valued functions $f(\cdot): \mathcal{X} \rightarrow \R$ defined over $\mathcal{X}$.
+%Formally, a GP is defined as,
+%\begin{align}
+%\label{eq-gp-prior}
+%  f(\cdot) \sim \mathcal{N}\left( \mu(\cdot), k(\cdot,\cdot') \right) \quad
+%  \mu(\cdot): \mathcal{X} \rightarrow \R \quad
+%  k(\cdot,\cdot'): \mathcal{X} \times \mathcal{X} \rightarrow \R
+%\end{align}
+%where $\mu(\cdot)$ denotes a mean function and $k(\cdot,\cdot')$ a positive definite covariance function, also known as a kernel.
+%Given a data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
+%we can obtain the GP posterior via multivariate normal conditioning,
+%\begin{align}
+%\label{eq-gp-predictive-posterior}
+%  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
+%  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
+%  \left( f(\mathbf{x}_{*}) \mid \mu(\mathbf{x}_{*}) + \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} (\mathbf{y} - \bm\mu_{\mathbf{X}})),
+%  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
+%\end{align}
+%% Our GP posterior is then given by,
+%\todo{add mean func to GP posterior if we're using one}
+%\begin{align}
+%\label{eq-gp-predictive-posterior}
+%  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
+%  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
+%  \left( f(\mathbf{x}_{*}) \mid \mu(\mathbf{x}_{*}) + \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} \mu_{\mathbf{x}},
+%  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} + \bm\Lambda(\mathbf{y} ; \mathbf{f})^{-1} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
+%\end{align}
+%where $\bm\Lambda(\mathbf{y} ; \mathbf{f}) = \nabla^{2}_{\mathbf{f} \mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$ can be viewed as per-input noise.
+\todo{I'm unsure about this per input noise bit.
+Check with paul.}
+%\todo{what about regression/classification likelhoods}
+%This GP predictive posterior is computationally expensive as it requires inverting an $N\times N$ matrix.
+%
+%\textbf{Sparse Gaussian processes}
+%% The GP predictive posterior in \cref{eq-gp-predictive-posterior} is computationally expensive as it requires inverting an $N\times N$ matrix.
+%A practical and computationally appealing alternative is to augment the joint probability space with pseudo inputs $\mathbf{Z} \in \R^{M \times D}$
+%and corresponding outputs
+%$\mathbf{u} = f(\mathbf{Z}; \weights) \in \R^{M \times C}$, known as inducing variables, where $M \ll N$.
+%\todo{cite sparse gp papers}
+%Instead of collapsing the inducing variables like \cite{titsiasVariational2009}, they can be treated variationally
+%$p(\mathbf{u} \mid \mathbf{y}) \approx q(\mathbf{u}) = \mathcal{N}\left( \mathbf{u} \mid \mathbf{m}, \mathbf{V} \right)$, where $\mathbf{m}$ and $\mathbf{V}$ are variational parameters
+%which need to be optimised \citep{hensmanGaussian2013}.
+%The sparse variational GP (SVGP) predictive posterior is then given by,
+%\begin{align}
+%\label{eq-dual-svgp-predictive-posterior}
+%  p(f(\mathbf{x}_{*}) \mid \mathbf{y})
+%&\approx \mathcal{N} \left( f(\mathbf{x}_{*}) \mid \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{m}^{*},
+%  k_{**} - \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
+%  % \mathbf{k}_{*\inducingInput} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\inducingInput}^{T}
+%  + \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}}  \mathbf{V}^{*}  \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
+%  \right)
+%\coloneqq q_{\inducingVariable}(f(\mathbf{x}_{*}))
+%\end{align}
+%
+%
+%\textbf{Deep learning}
+%Given the data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
+%the goal of (supervised) deep learning, is to train the weights $\weights \in \R^{P}$ of an $L\text{-layer}$ NN
+%$f : \inputDomain \rightarrow \outputDomain$ to minimize the (regularized) empirical risk,
+%\begin{align} \label{eq-empirical-risk}
+%  \weights^{*} = \arg \min_{\weights \in \R^{D}} \mathcal{L}(\dataset;\weights) = \arg \min_{\weights \in \R^{D}} \left(
+%  \sum_{n=0}^{N-1} l(f(\mathbf{x}_{n} ; \weights), \mathbf{y}_{n}) + R(\weights)  \right).
+%\end{align}
+%In practice, it is common to use the mean squared error (MSE) loss
+%$l(f(\mathbf{x}_{n} ; \weights),\mathbf{y}_{n}) = \|f(\mathbf{x}_{n} ; \weights) - \mathbf{y}_{n} \|^{2}_{2}$
+%and to use the weight decay regularizer $R(\weights)=\frac{1}{2}\gamma^{-2}\|\weights\|^{2}_{2}$.
+%However, the practioner is free to choose any loss and regularizer. \todo{I think?}
+%% \textbf{Bayesian neural networks}
+%% \textbf{Weight space to function space}
+%From a Bayesian perspective, we can interpret the terms in \cref{eq-empirical-risk} as the log-prior and the i.i.d. log likelihood, i.e.,
+%\begin{align} \label{eq-log-prior}
+%  R(\weights) &= \underbrace{\log p(\weights)}_{\text{log prior}} = \log \mathcal{N}(\weights \mid 0, \gamma^{2} \mathbf{I}) \\
+%  l(f(\mathbf{x}_{n} ; \weights), \mathbf{y}_{n}) &= \underbrace{\log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \weights))}_{\text{log likelihood}}
+%  = \log \mathcal{N} \left( \mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \weights), \mathbf{I} \right) \label{eq-log-likelihood}
+%\end{align}
+%
+%\textbf{NN to GP}
+%Given this interpretation, we can represent the weight space prior from \cref{eq-log-prior}, in
+%function space, by linearising the BNN around $\weights^{*}$ and interpretting it as a GP.
+%The GP prior is then given by,
+%\begin{align} \label{eq-laplace-approx-function-space}
+%  % \transitionFn_{\weights_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \qquad
+%  f(\cdot ;\weights) \sim \mathcal{N} \left( \mu(\cdot), k(\cdot, \cdot') \right) \quad
+%  % \mu_{\weights_{i}^{*}}(\cdot)
+%  \mu(\cdot)
+%  = 0 \quad
+%  % = f(\cdot ;\weights^{*}) \quad
+%  % K_{\weights_{i}^{*}}(\cdot, \cdot')
+%  k(\cdot, \cdot')
+%  = \frac{1}{\gamma^{2}} \mathbf{J}(\cdot) \mathbf{J}(\cdot')^{T},
+%\end{align}
+%where the kernel is the neural tangent kernel (NTK) \citep{immerImprovingPredictionsBayesian2021},
+%\todo{what mean function shoudl this use???}
+%\todo{NTK times some factor??}
+%with Jacobian given by $\mathbf{J}(\cdot) = \odv{\transitionFn(\cdot; \weights)}{\weights}_{\weights=\weights^{*}}$.
+%% The kernel in \cref{eq-laplace-approx-function-space} is the neural tangent kernel (NTK)
+%% $k(\mathbf{x}, \mathbf{x}') = \sigma_{0}^{2} J_{\weights^{*}}(\mathbf{x}) J_{\weights^{*}}(\mathbf{x}')^{T}$
+%% \citep{immerImprovingPredictionsBayesian2021}
+%% to formulate the GP posterior $p(f(\mathbf{X} ;\weights_{0:i}) \mid \dataset_{0:i})$.
+%Given this GP prior, we can use \cref{eq-gp-predictive-posterior} to obtain our GP posterior by conditioning on the data.
+%% Given our GP prior, we can use the properties of multivariate normals to obtain our GP posterior by conditioning on the data.
+%% where $\mathbf{A} = \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}}$
+%In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
+%Intuitively, we can view the optimisation in \cref{eq-empirical-risk} as learning our kernel.
+%As a result, our NTK may be highly non stationary as it is dependent on the NN architecture, for example, the activation functions.
+%It is worth noting that the NTK linearises the network around the optimised parameters $\weights^{*}$,
+%so the function space prior (and thus posterior) is only a locally linear approximation.
+%
+%We now have a method to obtain a GP posterior from a trained DNN.
+%% In contrast to other approaches, our formulation has not restricted us to using a weight-space posterior obtained from the Laplace approximation.
+%In contrast to other approaches, our formulation has not restricted us to using a weight-space posterior from a BNN.
+%However, in practice, the GP posterior is not very useful as it requires inverting an $N\times N$ matrix which has complexity $\mathcal{O}(N^{3})$.
+%The SVGP in \cref{eq-dual-svgp-predictive-posterior} offers a solution to this problem but it is not immediately clear how to set $\mathbf{m}$ and $\mathbf{V}$.
+%In the next section, we show how we can directly obtain an SVGP posterior (i.e. set $\mathbf{m}$ and $\mathbf{V}$) directly from both
+%1) a trained NN and 2) a BNN weight-space posterior.
+%% $\mathbf{m}$ and $\mathbf{V}$
+%% However, it is not obvious how we can use a SVGP to set $\mathbf{m}$ and $\mathbf{V}$
+%
+%
+%
+%% In contrast, to previous work, this approach did not require us Laplace approximation. we will not restrict our
+%% It is worth noting that the NTK linearises the network around the optimised parameters $\weights^{*}$,
+%% so the function space prior (and thus posterior) is only a locally linear approximation.
+%% In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
+%% It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.
+%
+%
+%\section{Methods}
+%In the next section we show how we can obtain a SVGP directly from 1) a trained NN and 2) a BNN posterior.
+%
+%We follow \cite{csatoSparseOnlineGaussian2002} and express our GP posterior in the dual parameter space.
+%However, we consider the variational formulation introduced by \cite{adamDualParameterizationSparse2021}, where the optimal variational parameters are given by,
+%\begin{align} \label{eq-dual-params}
+%\mathbf{m}^{*} = \mathbf{V}^{*}\bm\alpha^{*} \quad \mathbf{V}^{*} = [\mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} + \bm\beta^{*}]
+%\end{align}
+%Importantly, we can calculate the natural parameters $(\bm\alpha, \bm\beta)$ in closed form,
+%\todo{paul needs to update \cref{eq-dual-svgp-params}}
+%\begin{align} \label{eq-dual-svgp-params}
+%\bm\alpha_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right] \\
+%\bm\beta_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right].
+%\end{align}
+%This simplifies SVGP inference \citep{hensmanGaussian2013} as it no longer requires the variational parameters $(\mathbf{m}, \mathbf{V})$ to be optimised.
+%
+%% Importantly, \cite{changFantasizingDualGPs2022} show that in the dual space,
+%% conditioning on new observations reduces to suming the dual variables from the previous time
+%% step with an update, given by,
+%% \todo{pick best way to show new data (using superscript new or just time indexing?)}
+%% \begin{align} \label{eq-dual-update-svgp}
+%% \bm\alpha_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right] \\
+%% \bm\beta_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right]
+%% \end{align}
+%
+%% We follow \cite{csatoSparseOnlineGaussian2002} and express our GP posterior in the dual parameter space,
+%% % to write GP posterior $p(f(\mathbf{X} ;\weights_{0:i}) \mid \dataset_{0:i})$ as,
+%% \begin{align} \label{eq-gp-post}
+%%   \mathbb{E}_{p(f(\mathbf{x}_{*}) \mid \mathbf{y}_{n})} \left[ f(\mathbf{x}_{*}) \right] &= \mu(\mathbf{x}_{*}) + \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
+%%   \mathbb{V}_{p(f(\mathbf{x}_{*}) \mid \mathbf{y}_{n})} \left[ f(\mathbf{x}_{*}) \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \text{diag}(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
+%% \end{align}
+%% % \begin{align} \label{eq-laplace-approx-function-space}
+%% %   \mathbb{E}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
+%% %   \mathbb{V}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \diag(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
+%% % \end{align}
+%% where the dual parameters $(\bm\alpha_n, \bm\beta_n)$ are vectors of,
+%% \begin{align} \label{eq-gp-dual-params}
+%%   \bm\alpha_{n} \coloneqq \left\{ \mathbb{E}_{p(f(\mathbf{x}_{i}) \mid \mathbf{y}_{n})} \left[ \nabla_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \right\}_{i=1}^{N} \qquad
+%%   \bm\beta_{n} \coloneqq \left\{ \mathbb{E}_{p(f(\mathbf{x}_{i}) \mid \mathbf{y}_{n})} \left[ \nabla^{2}_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \right\}_{i=1}^{N}
+%% \end{align}
+%% Importantly, this parameterisation
+%
+%% \textbf{dual-SVGP}
+%% \begin{align} \label{eq-svgp-post}
+%%   \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ f(\mathbf{x}_{*}) \right] &= \mu(\mathbf{x}_{*}) + \mathbf{k}_{\mathbf{z}*}^{T} \bm\alpha_{\mathbf{u}} \\
+%%   \mathbb{V}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ f(\mathbf{x}_{*}) \right] &= k_{**} - \mathbf{k}_{\mathbf{z}*}^{T} \left[ \mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} - \left( \mathbf{K}_{\mathbf{z} \mathbf{z}} + \bm\beta_{\mathbf{u}} \right)^{-1} \right] \mathbf{k}_{\mathbf{z}*}
+%% \end{align}
+%% % \begin{align} \label{eq-laplace-approx-function-space}
+%% %   \mathbb{E}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
+%% %   \mathbb{V}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \diag(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
+%% % \end{align}
+%% where the dual parameters $(\bm\alpha_{\mathbf{u}}, \bm\beta_{\mathbf{u}})$ are vectors of,
+%% \begin{align} \label{eq-svgp-dual-params}
+%%   \bm\alpha_{\mathbf{u}} \coloneqq \mathbf{k}_{\mathbf{z}i} \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ \nabla_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \qquad
+%%   \bm\beta_{\mathbf{u}} \coloneqq \mathbf{k}_{\mathbf{z}i} \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ \nabla^{2}_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \mathbf{k}_{\mathbf{z}i}^{T}
+%% \end{align}
+%
+%% weight space posterior in \cref{eq-laplace-approx-weight-space} in
+%% function space by linearising the BNN and interpreting it as a GP.
+%% \begin{align} \label{eq-laplace-approx-function-space}
+%%   \transitionFn_{\weights_{i}}(\cdot) &\sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \quad
+%%   \mu_{\weights_{i}^{*}}(\cdot) &= \transitionFn_{\weights^{*}_{i}}(\cdot) \quad
+%%   K_{\weights_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\weights^{*}_{i}}(\cdot) \bm\Sigma_{\weights^{*}_{i}} \mathbf{J}_{\weights^{*}_{i}}(\cdot')^{T}
+%% \end{align}
+%% where the Jacobian is given by $\mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}$.
+%
+%% \begin{align} \label{eq-laplace-approx-jacobian}
+%% \mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}
+%% \end{align}
+%
+%
+%% % Note that the posterior in \cref{eq-laplace-approx-weight-space} is in weight space.
+%% We can represent the weight space posterior in \cref{eq-laplace-approx-weight-space} in
+%% function space by linearising the BNN and interpreting it as a GP.
+%% \begin{align} \label{eq-laplace-approx-function-space}
+%%   \transitionFn_{\weights_{i}^{*}}(\cdot) &\sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \quad
+%%   \mu_{\weights_{i}^{*}}(\cdot) &= \transitionFn_{\weights^{*}_{i}}(\cdot) \quad
+%%   K_{\weights_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\weights^{*}_{i}}(\cdot) \bm\Sigma_{\weights^{*}_{i}} \mathbf{J}_{\weights^{*}_{i}}(\cdot')^{T}
+%% \end{align}
+%% where the Jacobian is given by $\mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}$.
+%
+%% \begin{align} \label{eq-laplace-approx-jacobian}
+%% \mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}
+%% \end{align}
+%
+%
+%\subsection{Fast Updates}
+%Importantly, \cite{changFantasizingDualGPs2022} show that in the dual space,
+%conditioning on new observations reduces to suming the dual variables from the previous time
+%step with an update, given by,
+%\todo{pick best way to show new data (using superscript new or just time indexing?)}
+%\begin{align} \label{eq-dual-update-svgp}
+%\dualParam{1}^{t+1} &\leftarrow \dualParam{1}^{t} +  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))} \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right] \\
+%\dualParam{2}^{t+1} &\leftarrow \dualParam{2}^{t} +  \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))}  \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right]
+%\end{align}
+%Importantly, for a single new observation $((\state_{t}, \action_{t}), \state_{t+1})$ this update has
+%complexity $\mathcal{O}(\numInducing^{2})$.
+%This is a significant improvement to naive GP conditioning, which has complexity $\mathcal{O}((\numDataNew + \numDataOld)^{3})$
+%and sparse GP conditioning, which has complexity $\mathcal{O}((\numDataNew + \numDataOld)\numInducing^{2})$.
+%\todo{double check these complexities are right and cite them/show equaitons}
+%It is worth highlighting that the complexity of \cite{changFantasizingDualGPs2022} update does not increase during an episode.
+%
+%\subsubsection{Model-based RL}
+%
+%\subsubsection{Efficiently Sampling Functions for Posterior Sampling}
+%\cite{wilsonEfficiently2020}
+%\cite{wilsonPathwise2021}
+%
+%% \begin{align} \label{eq-dual-update-svgp}
+%%  \dualParam{1}^{\text{new}} &\leftarrow \dualParam{1}^{\text{old}} +
+%%   \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}))}
+%%  \left[ \log p(\state_{t+1}^{\text{new}} \mid \latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}) ) \right] \\
+%%  \dualParam{2}^{\text{new}} &\leftarrow \dualParam{2}^{\text{old}} +
+%%   \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}))}
+%%  \left[ \log p(\state_t^{\horizon+1} \mid \latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}) ) \right] \\
+%%  \dualParam{1}^{\horizon+1} &\leftarrow \dualParam{1}^{\horizon} +
+%%   \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}
+%%  \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right] \\
+%%  \dualParam{2}^{\horizon+1} &\leftarrow \dualParam{2}^{\horizon} +
+%%   \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}
+%%  \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right]
+%% \end{align}
+%
+%
+%\begin{assumption} \label{assumption-ntk-linearisation}
+%  Something about NTK being a linearisation around $\theta^{*}_{i}$ but each update moves away from $\theta^{*}_{i}$
+%\end{assumption}
+%
+%\cite{rossellApproximateLaplaceApproximations2021}
+
+\section{Experiments}
+\label{sec:experiments}
+
+\todo{Overview of experiments}
+
+Our experiments seek to answer the following questions:
+\begin{enumerate}
+  \item \textbf{Predictions} How do predictions with our sparse function-space approximation compare to weight-space approximations?
+Does our method's ability to consider the full data set offer benefits over subset function-space methods?
+  % \item Does our method's ability to consider the full data set offer benefits over subset function-space methods?
+  \item \textbf{Function-space updates} How fast are our function-space updates relative to retraining from scratch?
+Do they improve predictive performance?
+Are they as good as retraining from scratch?
+  \item \textbf{Uncertainty} How good are our uncertainty estimates? Can they be used in downstream settings like RL?
+  \item \textbf{Representation} Is our sparse function-space representation useful for continual learning?
+\end{enumerate}
+
+\subsection{Capturing uncertainty in UCI tasks under supervised learning}
+%
+
+\begin{table}[t!] 
+  \centering\scriptsize
+  \caption{Negative log predictive density (NLPD) (lower better) for the proposed model TODO} 
+	\label{tbl:uci}
+	% Control table spacing
+	\renewcommand{\arraystretch}{1.}
+	\setlength{\tabcolsep}{2pt}
+	\setlength{\tblw}{0.14\textwidth}
+
+	% Custom error formatting
+	\newcommand{\val}[2]{%
+		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
+	}
+
+    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
+	\input{tables/uci.tex}
+\end{table}
+We trained a two-layer MLP for each of the $8$ classification tasks in UCI, see \cref{tbl:uci} for a list of the datasets.
+The neural network training was done using MAP, with a prior $\mathcal{N}(0,\delta^{-1} \MI)$ with prior precision $\delta$.
+After training, we constructed the SVGP dual and used the resulting SVGP model for uncertainty quantification.
+Depending on task dimension and complexity, our model can match the NN MAP in NLPD performance even with a low number of inducing points, see \cref{tbl:uci}.
+We performed hyperparameter search over the prior precision, and ran the experiment over $10$ seeds.
+During the initial NN training, we used a learning rate of $1e-3$.
+
+\subsection{Supervised learning on image data sets}
+
+\begin{table}[t!] 
+  \centering\scriptsize
+  \caption{Metrics for supervised learning with image data.
+SVGP is our method, and the number inside parentheses is the number of inducing points.
+SVGP NN is a modification of our method, where the mean is from the NN directly and the variance is from the GP model}
+	\label{tbl:imagesuper}
+	% Control table spacing
+	\renewcommand{\arraystretch}{1.}
+	\setlength{\tabcolsep}{6pt}
+	\setlength{\tblw}{0.15\textwidth}
+
+	% Custom error formatting
+	\newcommand{\val}[2]{%
+		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
+	}
+
+    % THE TABLE CAN BE FORMATTED MORE LIKE THIS
+    \begin{tabular}{l l C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
+    \toprule
+    & Method & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ & OOD-AUC~$\uparrow$  \\
+    \midrule
+    \multirow{2}{*}{FMNIST} 
+    & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\    
+    \midrule
+    \multirow{2}{*}{CIFAR-10} 
+    & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\    
+    \bottomrule
+    \end{tabular}
+
+    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
+	%\input{tables/img_super.tex}
+\end{table}
+
+Similarly to the UCI experiments, we trained neural networks (CNN, architexture matches \citet{immer2021improving}) for the FMNIST and CIFAR10 classification tasks.
+After training, we computed the duals for NN2SVGP and used the resulting SVGP for uncertainty estimates, see \cref{tbl:imagesuper}.
+We performed hyperparameter optimization over the prior precision, and found the optimal value to be [insert].
+We ran the experiment over $5$ seeds.
+During the NN training, we used a batch size of $512$ and an Adam optimizer with learning rate $1e-3$.
+
+In addition to uncertainty estimates, our method can update the posterior when given new data.
+We gave the SVGP model 10 \% of the test dataset used for evaluation, and compare the performance of the SVGP model and the retrained NN in [INSERT TABLE].
+
+\subsection{Updating the  network representation for Continual learning}
+The Continual learning setting is a challenging and the training and
+
+\begin{table}[t!] 
+  \centering\scriptsize
+  \caption{
+  TODO: CL Experiments. $^*$ Methods relying only on weight regularization. 
+  \color{blue}{Results from \cite{rudner2022continual}.} 
+  %\color{red}{Preliminary results need more runs or hyperparam tuning}
+  }
+	\label{tbl:cl_table_1}
+	% Control table spacing
+	\renewcommand{\arraystretch}{1.}
+	\setlength{\tabcolsep}{2pt}
+	\setlength{\tblw}{0.14\textwidth}
+
+	% Custom error formatting
+	\newcommand{\val}[2]{%
+		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
+	}
+
+	\input{tables/cl_table_1}
+\end{table}
+
+\subsection{Reinforcement Learning}
+
+In section \label{sec-rl} we detailed how our method can be used to
+
+See \label{sec-rl-experiments-appendix} for more details of our experiments.
 
@@
     {\Large Supplementary Material:} \\
-    PAPER TITLE GOES HERE}
+    Sparse Function-space Representation \\ of Neural Networks}
 \pagestyle{empty}

### 2023-05-15 paper/main.tex
rewrite 3 points

--- 2023-05-15 paper/main.tex
@@
 \todo{our approximation is late \cref{eq:dual_param_laplace}, saying this here is misleading}\\
-In \citet{csato2002sparse}, they iteratively find dual variables setting them to log the expectation of the approximate posterior.\todo{what does it mean?} 
+In \citet{csato2002sparse}, they iteratively find dual variables using an Expectation Propogation (EP) method.  
 At the same time, in \cite{adam2021dual, chang2020fast}, they show this relationship for variational Gaussian processes where the above expectation is with respect to the approximate variational posterior.
@@
 \paragraph{Dual parameters from NN}
-Given that we use a Laplace approximation of the neural network, we can remove the expectation over the posterior (see Ch.~3.4.1 in \cite{rasmussen2006gaussian} for derivation) and we get the the following formulation of the dual variables,
+Given that we use a Laplace approximation of the neural network, we remove the expectation over the posterior (see Ch.~3.4.1 in \cite{rasmussen2006gaussian} for derivation) and we get the the following formulation of the dual variables,
 \begin{equation}
@@
 where $\MKzz$ and $\vkzs$ are defined similarly to $\MKxx$ and $\vk_{\vx i}$ but over the inducing points $\MZ \in \R^{M \times D} $  instead of the full dataset $\dataset$.
-The key quantities we need to make predictions from our sparse GP from the converged neural network are $(\hat{\alpha}_i, \hat{\beta}_i)$\todo{these variables need another subscript for differentiate that from the values computed at the data points} and a kernel function $\kappa$.
-Contrasting \cref{eq:dual_sparse_post} and \cref{eq:gp_pred}, we can see that the computational complexity went from $\mathcal{O}(n^3)$  $\mathcal{O}(m^3)$, with $m \ll n$.
-Crucially, given the structure of our probabilistic model, our sparse dual variables \cref{eq:dual_sparse} are a compact form \todo{use representation instead of form here ?} of the full model projected using the kernel.
-
-In contrast to our approach, \citet{immer2021improving} use a subset of the full GP model \todo{isn't the subset on the data points?} to reduce the computational complexity.
+The key quantities we need to make predictions from our sparse GP from the converged neural network are $(\hat{\alpha}_i, \hat{\beta}_i)$ \cref{eq:dual_param_laplac}\todo{these variables need another subscript for differentiate that from the values computed at the data points} and a kernel function $\kappa$ .
+Contrasting \cref{eq:dual_sparse_post} and \cref{eq:gp_pred}, we can see that the computational complexity went from $\mathcal{O}(n^3)$ to $\mathcal{O}(m^3)$, with $m \ll n$.
+Crucially, given the structure of our probabilistic model, our sparse dual variables \cref{eq:dual_sparse} are a compact representation of the full model projected using the kernel.
+
+In contrast to our approach, \citet{immer2021improving} use a subset of the data points to make a sparse GP model to reduce the computational complexity.
 As a result, this is a less principled approach for building a sparse model since it ignores the dataset's information.

### 2023-05-15 paper/main.tex
updated appendix title

--- 2023-05-15 paper/main.tex
@@
 After each task, we can use our \our to build a compact representation of the neural network and then use that as an additional term to the training loss to regularize the model.
+Recent success has shown GP-based regularizers perform better than weight space equivalents getting state-of-the-art on typical CL benchmarks \cite{ pan2020continual, rudner2022continual}.
+The limitation of such approaches is that they must use subset approximations of the posterior, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer.
+A more principled approach would be to sparsify the data into a low-rank approximation to ensure information wasn't lost, essentially what the sparse dual variables do.
 \todo{this term is replacing the missing data}
 
-An alternative view of the dual variables is that they parameterize approximate likelihoods as was shown in \citep{adam2021dual} we can rewrite the GP posterior in terms of the following approximate normal distributions:
+An alternative view of the dual variables is that they parameterize approximate likelihoods, as shown in \citep{adam2021dual, khan2017conjugate}.
+We can rewrite the GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
 \begin{equation}
- q(\vu) \propto \N(0, \MKzz) \prod_{i=1}^n e^{-\frac{\hat{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 } = \N(0, \MKzz) \, e^{(\tilde{\vy} - \vu)^\top\tilde{\MSigma}^{-1}(\tilde{\vy} - \vu)}  
+ q(\vu) \propto \N(0, \MKzz) \prod_{i=1}^n e^{-\frac{\tilde{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 } = \N(0, \MKzz) \, e^{(\bar{\vy} - \vu)^\top \bar{\MSigma}^{-1}(\bar{\vy} - \vu)}  
 \end{equation}
-The first normals are the marginal likelihoods were $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}$,  replacing $\va_i^\top \vu$  wtih $\vx_i^{\top}\vw$ and we can see the similarity between the sparse GP and a linear model where the prior is determined by the kernel matrix.
-To arrive at the MVN Gaussian we need to rearrange the quadratic terms to match the prior sufficient statistics we present a derivation in [appendix].
-Performing conjugate summation of prior and likelihood we would arrive at the sparse GP posterior at the inducing points $\MZ$.
-The correlated covariance structure $\MSigma$ and the corresponding $\tilde{\vy}$ are simply a different form of the sparse dual variables
+The first normals are the approximate likelihoods where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}$,  replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$ and we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior.
+To arrive at the MVN Gaussian, we need to rearrange the quadratic terms to match the prior sufficient statistics we present a derivation in [appendix].
+Performing conjugate summation of prior and likelihood, we would arrive at the sparse GP posterior at the inducing points.
+The correlated covariance structure $\MSigma$ and the corresponding $\tilde{\vy}$ are simply a different form of the sparse dual variables,
+\begin{equation}
+\quad \bar{\MSigma} =  \MKzz \vbeta_\vu^{-1} \MKzz \quad \bar{\vy} = \MKzz \vbeta_{\vu}\valpha_{\vu}.
+\end{equation}
+Written as above, we can see that the spare dual variables can be interpreted as a sparse MVN representation.
+We now show how we use this for a regularizer in continual learning with more details in [appendix].
 

### 2023-05-15 paper/main.tex
moved rl stuff to appendix
added to rl section in exeriments

@@
 A key challenge in RL is balancing the trade-off between exploration and exploitation.
-That is, should the agent select an action that it knows will lead to a high reward (exploitation), or should it
-hope to discover new actions which lead to high reward (exploration) by selecting actions that it has not selected before.
-In this section, we demonstrate  that our method's principled uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim.
+That is, should an agent select actions that it knows will lead to a high reward (exploitation), or should it
+hope to discover new actions which lead to high reward (exploration)?
+In this section, we show that \our's uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim,
+demonstrating the quality of our uncertainty estimates.
+% In this section, we demonstrate  that our method's principled uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim.
+We refer the reader to \cref{app:rl} for an overview of the problem and details of our experiments.
+
+Cart pole swing up task in MuJoCo \cite{todorov2012mujoco}
+We compare our method with deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016} -- a model-free RL baseline --
+which is sample inefficient.
+We test our model's uncertainty estimates by comparing it to using Laplace-GGN with GLM predictions, using an ensemble of neural networks
+(with different initialisations),
+To ensure a fair comparison, we use the same MLP architecture/training scheme and we keep the same model-based RL algorithm.
+See \cref{app:rl} for more details of our experiments.
+
+We also compare to deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016} -- a model-free RL baseline --
+which we expect to be much more sample inefficient.
+
+\cref{fig:rl} shows training curves
+
+\begin{figure}[!t]
+ \centering
+ \begin{subfigure}[c]{.24\textwidth}
+ \resizebox{\textwidth}{!}{%
+ \begin{tikzpicture}[inner sep=0,outer sep=0]
+
+   % Draw decorated 'ground'
+   \draw[postaction={draw, decorate, decoration={border, angle=-45,
+					amplitude=1cm, segment length=.5cm}}] (-3,-1.5) -- (12,-1.5);
+
+   % The cart
+   \draw[draw=black,fill=black!50,draw=black,line width=3pt,rounded corners=1mm] (0,0) rectangle (9cm,3cm);
+   \node[fill=black,circle,minimum size=.5cm] (dot) at (4.5cm,3cm) {};
+
+   % Wheels
+   \node[fill=white,draw=black,line width=3pt,circle,minimum size=2cm,,fill=black!50] at (2cm,-.5cm) {};
+   \node[fill=white,draw=black,line width=3pt,circle,minimum size=2cm,fill=black!50] at (7cm,-.5cm) {};
+
+   % The arm
+   \node[anchor=north,minimum width=1cm,minimum height=14cm,draw=black,rotate=-20,rounded corners=5mm,yshift=7mm,xshift=-.3mm,fill=white,draw=black,line width=3pt] at (dot) {};
+   \node[fill=black,circle,minimum size=.5cm] at (dot) {};
+
+   % Markings
+   \draw[loosely dashed,line width=1pt] (4.5,6) -- (4.5,-10);
+
+   % Arrow
+   \draw[->,black,line width=3pt,-{Latex[length=7mm,width=7mm]}] (1,5) --node[above,outer sep=8pt]{\scalebox{4}{$x$}} (4.5,5);
+
+   \def\centerarc[#1](#2)(#3:#4:#5)% Syntax: [draw options] (center) (initial angle:final angle:radius)
+   { \draw[#1] ($(#2)+({#5*cos(#3)},{#5*sin(#3)})$) arc (#3:#4:#5); }
+
+   % Draw arc
+   \centerarc[black,line width=3pt](dot)(250:270:11)
+   \node at (2.5,-9) {\scalebox{4}{$\theta$}};
+
+   %\node[white,minimum size=1cm] at (4.5,-13) {};
+
+ \end{tikzpicture}}
+ \end{subfigure}
+ \hfill
+ \begin{subfigure}[c]{.74\textwidth}
+   \centering\scriptsize
+   \setlength{\figurewidth}{\textwidth}
+   \setlength{\figureheight}{.5\figurewidth}
+   \pgfplotsset{axis on top,ymajorgrids,axis line style={draw=none},legend style={at={(1,1)},anchor=north west}}
+   \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed},legend style={fill=white}}
+   \input{./fig/rl.tex}
+ \end{subfigure}
+ \hfill
+ \caption{\textbf{Reinforcement learning experiments} Training curves showing that our model's uncertainty estimates improve sample efficiency in RL.
+   Our method (blue/green) converges to the optimal solution in fewer environment steps than the baseline model-based RL method (magenta) and (DDPG) the model-free baseline  (yellow).}
+ \label{fig:rl}
+\end{figure}
+
+%
+
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=0.5\textwidth, angle=270]{fig/weight-space-to-functio-space.pdf}
+%   \caption{}
+% \end{figure}
+
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=0.5\textwidth, trim=0 100 0 10]{fig/cartpole-training-curves.pdf}
+%   \caption{}
+% \end{figure}
+
+% \begin{table}
+%   \caption{Negative test log likelihood (lower is better) on UCI classification tasks (2 hidden layers, 50 tanh). Our SVGP predictive outperforms the GLM predictive. }
+% \end{table}
+
+\section{Discussion and conclusion}
+\label{sec:conclusion}
+%
+
+It is worth noting that the NTK linearises the network around the MAP solution $\weights^{*}$,
+so the function space prior (and thus posterior) is only a locally linear approximation.
+In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
+It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.
+
+A reference implementation of the methods presented in this paper is currently available as supplementary material and will be made available under the MIT License on GitHub upon acceptance.
+
+%\section*{Broader Impact}
+
+% \section*{References}
+%\small
+%\printbibliography
+%\normalsize
+% TODO make bibliography small a better way
+
+%References follow the acknowledgments. Use unnumbered first-level heading for
+%the references. Any choice of citation style is acceptable as long as you are
+%consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
+%when listing the references.
+%Note that the Reference section does not count towards the page limit.
+%\medskip
+
+\clearpage
+
+\phantomsection%
+\addcontentsline{toc}{section}{References}
+\begingroup
+\small
+\bibliographystyle{abbrvnat}
+\bibliography{bibliography}%zotero-library
+\endgroup
+
+\clearpage
+
+\nipstitle{
+    {\Large Supplementary Material:} \\
+    Sparse Function-space Representation \\ of Neural Networks}
+\pagestyle{empty}
+
+\appendix
+
+This supplementary document is organized as follows. 
+%
+\cref{app:method} provides a more extensive overview of the techncical details of \our.
+%
+\cref{app:cl} covers the sparse-functional regularisation (SFR) setup for continual learning.
+%
+\cref{app:rl} provides a more extensive writeup of the reinforcement learning setup used in the experiments.
+%
+\cref{app:experiments} provides the full details of each individual experiments in the main paper.
+
+\section{Method details}
+\label{app:method}
+%
+Optionally include extra information (complete proofs, additional experiments and plots) in the appendix.
+This section will often be part of the supplemental material.
+
+\section{Sparse functional regularisation in continual learning}
+\label{app:cl}
+
+\subsection{Extending the CL regularizer to multi-class settings}
+\begin{equation}
+	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{C \times m \times m} \quad \MKzz \in \R^{C \times m \times m} 
+\end{equation}
+
+\begin{equation}
+	\mathcal{R_\textit{SFR}}(\mathbf{w}) = \sum_{s=1}^{t-1}	\sum_{k \in 	C}\left[\left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s}, k}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s, k}}(\MZ_s) \right) \right]
+\end{equation}
+
+\section{Sparse functional model-based reinforcement learning}
+\label{app:rl}
 
@@
 
-See \cref{app:rl} for more details of our experiments.
-
-We compare a model-based RL agent using a simple MLP dynamic model with
-\begin{itemize}
-  \item uncertainty is good for exploration
-\end{itemize}
-
-\cref{fig:rl} shows training curves
-
-\begin{figure}[!t]
- \centering
- \begin{subfigure}[c]{.24\textwidth}
- \resizebox{\textwidth}{!}{%
- \begin{tikzpicture}[inner sep=0,outer sep=0]
-
-   % Draw decorated 'ground'
-   \draw[postaction={draw, decorate, decoration={border, angle=-45,
-					amplitude=1cm, segment length=.5cm}}] (-3,-1.5) -- (12,-1.5);
-
-   % The cart
-   \draw[draw=black,fill=black!50,draw=black,line width=3pt,rounded corners=1mm] (0,0) rectangle (9cm,3cm);
-   \node[fill=black,circle,minimum size=.5cm] (dot) at (4.5cm,3cm) {};
-
-   % Wheels
-   \node[fill=white,draw=black,line width=3pt,circle,minimum size=2cm,,fill=black!50] at (2cm,-.5cm) {};
-   \node[fill=white,draw=black,line width=3pt,circle,minimum size=2cm,fill=black!50] at (7cm,-.5cm) {};
-
-   % The arm
-   \node[anchor=north,minimum width=1cm,minimum height=14cm,draw=black,rotate=-20,rounded corners=5mm,yshift=7mm,xshift=-.3mm,fill=white,draw=black,line width=3pt] at (dot) {};
-   \node[fill=black,circle,minimum size=.5cm] at (dot) {};
-
-   % Markings
-   \draw[loosely dashed,line width=1pt] (4.5,6) -- (4.5,-10);
-
-   % Arrow
-   \draw[->,black,line width=3pt,-{Latex[length=7mm,width=7mm]}] (1,5) --node[above,outer sep=8pt]{\scalebox{4}{$x$}} (4.5,5);
-
-   \def\centerarc[#1](#2)(#3:#4:#5)% Syntax: [draw options] (center) (initial angle:final angle:radius)
-   { \draw[#1] ($(#2)+({#5*cos(#3)},{#5*sin(#3)})$) arc (#3:#4:#5); }
-
-   % Draw arc
-   \centerarc[black,line width=3pt](dot)(250:270:11)
-   \node at (2.5,-9) {\scalebox{4}{$\theta$}};
-
-   %\node[white,minimum size=1cm] at (4.5,-13) {};
-
- \end{tikzpicture}}
- \end{subfigure}
- \hfill
- \begin{subfigure}[c]{.74\textwidth}
-   \centering\scriptsize
-   \setlength{\figurewidth}{\textwidth}
-   \setlength{\figureheight}{.5\figurewidth}
-   \pgfplotsset{axis on top,ymajorgrids,axis line style={draw=none},legend style={at={(1,1)},anchor=north west}}
-   \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed},legend style={fill=white}}
-   \input{./fig/rl.tex}
- \end{subfigure}
- \hfill
- \caption{\textbf{Reinforcement learning experiments} Training curves showing that our model's uncertainty estimates improve sample efficiency in RL.
-   Our method (blue/green) converges to the optimal solution in fewer environment steps than the baseline model-based RL method (magenta) and (DDPG) the model-free baseline  (yellow).}
- \label{fig:rl}
-\end{figure}
-
-%
-
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.5\textwidth, angle=270]{fig/weight-space-to-functio-space.pdf}
-%   \caption{}
-% \end{figure}
-
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.5\textwidth, trim=0 100 0 10]{fig/cartpole-training-curves.pdf}
-%   \caption{}
-% \end{figure}
-
-% \begin{table}
-%   \caption{Negative test log likelihood (lower is better) on UCI classification tasks (2 hidden layers, 50 tanh). Our SVGP predictive outperforms the GLM predictive. }
-% \end{table}
-
-\section{Discussion and conclusion}
-\label{sec:conclusion}
-%
-
-It is worth noting that the NTK linearises the network around the MAP solution $\weights^{*}$,
-so the function space prior (and thus posterior) is only a locally linear approximation.
-In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
-It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.
-
-A reference implementation of the methods presented in this paper is currently available as supplementary material and will be made available under the MIT License on GitHub upon acceptance.
-
-%\section*{Broader Impact}
-
-% \section*{References}
-%\small
-%\printbibliography
-%\normalsize
-% TODO make bibliography small a better way
-
-%References follow the acknowledgments. Use unnumbered first-level heading for
-%the references. Any choice of citation style is acceptable as long as you are
-%consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
-%when listing the references.
-%Note that the Reference section does not count towards the page limit.
-%\medskip
-
-\clearpage
-
-\phantomsection%
-\addcontentsline{toc}{section}{References}
-\begingroup
-\small
-\bibliographystyle{abbrvnat}
-\bibliography{bibliography}%zotero-library
-\endgroup
-
-\clearpage
-
-\nipstitle{
-    {\Large Supplementary Material:} \\
-    Sparse Function-space Representation \\ of Neural Networks}
-\pagestyle{empty}
-
-\appendix
-
-This supplementary document is organized as follows. 
-%
-\cref{app:method} provides a more extensive overview of the techncical details of \our.
-%
-\cref{app:cl} covers the sparse-functional regularisation (SFR) setup for continual learning.
-%
-\cref{app:rl} provides a more extensive writeup of the reinforcement learning setup used in the experiments.
-%
-\cref{app:experiments} provides the full details of each individual experiments in the main paper.
-
-\section{Method details}
-\label{app:method}
-%
-Optionally include extra information (complete proofs, additional experiments and plots) in the appendix.
-This section will often be part of the supplemental material.
-
-\section{Sparse functional regularisation in continual learning}
-\label{app:cl}
-
-\subsection{Extending the CL regularizer to multi-class settings}
-\begin{equation}
-	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{C \times m \times m} \quad \MKzz \in \R^{C \times m \times m} 
-\end{equation}
-
-\begin{equation}
-	\mathcal{R_\textit{SFR}}(\mathbf{w}) = \sum_{s=1}^{t-1}	\sum_{k \in 	C}\left[\left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s}, k}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s, k}}(\MZ_s) \right) \right]
-\end{equation}
-
-\section{Sparse functional model-based reinforcement learning}
-\label{app:rl}
-
 Model Predictive Path Integral (MPPI) control

### 2023-05-15 paper/main.tex
updates to CL part

@@
 \todo{our approximation is late \cref{eq:dual_param_laplace}, saying this here is misleading}\\
-In \citet{csato2002sparse}, they iteratively find dual variables using an Expectation Propogation (EP) method.  
+In \citet{csato2002sparse}, they iteratively find dual variables setting them to log the expectation of the approximate posterior.\todo{what does it mean?} 
 At the same time, in \cite{adam2021dual, chang2020fast}, they show this relationship for variational Gaussian processes where the above expectation is with respect to the approximate variational posterior.
@@
 \paragraph{Dual parameters from NN}
-Given that we use a Laplace approximation of the neural network, we remove the expectation over the posterior (see Ch.~3.4.1 in \cite{rasmussen2006gaussian} for derivation) and we get the the following formulation of the dual variables,
+Given that we use a Laplace approximation of the neural network, we can remove the expectation over the posterior (see Ch.~3.4.1 in \cite{rasmussen2006gaussian} for derivation) and we get the the following formulation of the dual variables,
 \begin{equation}
@@
 where $\MKzz$ and $\vkzs$ are defined similarly to $\MKxx$ and $\vk_{\vx i}$ but over the inducing points $\MZ \in \R^{M \times D} $  instead of the full dataset $\dataset$.
-The key quantities we need to make predictions from our sparse GP from the converged neural network are $(\hat{\alpha}_i, \hat{\beta}_i)$ \cref{eq:dual_param_laplac}\todo{these variables need another subscript for differentiate that from the values computed at the data points} and a kernel function $\kappa$ .
-Contrasting \cref{eq:dual_sparse_post} and \cref{eq:gp_pred}, we can see that the computational complexity went from $\mathcal{O}(n^3)$ to $\mathcal{O}(m^3)$, with $m \ll n$.
-Crucially, given the structure of our probabilistic model, our sparse dual variables \cref{eq:dual_sparse} are a compact representation of the full model projected using the kernel.
-
-In contrast to our approach, \citet{immer2021improving} use a subset of the data points to make a sparse GP model to reduce the computational complexity.
+The key quantities we need to make predictions from our sparse GP from the converged neural network are $(\hat{\alpha}_i, \hat{\beta}_i)$\todo{these variables need another subscript for differentiate that from the values computed at the data points} and a kernel function $\kappa$.
+Contrasting \cref{eq:dual_sparse_post} and \cref{eq:gp_pred}, we can see that the computational complexity went from $\mathcal{O}(n^3)$  $\mathcal{O}(m^3)$, with $m \ll n$.
+Crucially, given the structure of our probabilistic model, our sparse dual variables \cref{eq:dual_sparse} are a compact form \todo{use representation instead of form here ?} of the full model projected using the kernel.
+
+In contrast to our approach, \citet{immer2021improving} use a subset of the full GP model \todo{isn't the subset on the data points?} to reduce the computational complexity.
 As a result, this is a less principled approach for building a sparse model since it ignores the dataset's information.
@@
 % Definition of CL -> a sequence of tasks 
-In the Continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{n_t}$, which after the task is discarded and cannot be accessed in the later stages of the training.
-However, rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting.
-After each task, we can use our \our to build a compact representation of the neural network and then use that as an additional term to the training loss to regularize the model.
-Recent success has shown GP-based regularizers perform better than weight space equivalents getting state-of-the-art on typical CL benchmarks \cite{ pan2020continual, rudner2022continual}.
-The limitation of such approaches is that they must use subset approximations of the posterior, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer.
-A more principled approach would be to sparsify the data into a low-rank approximation to ensure information wasn't lost, essentially what the sparse dual variables do.
+In the Continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{n_t}$, which after the task is discarded and cannot be accessed in the following stages of the training.
+Rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting.
+In the same way, after each task, we can use our \our to build a compact representation of the neural network and then exploit this representation to build a functional regularizer to add to the training loss for the subsequent tasks.
+Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art on CL benchmarks.
+However, they are limited to use subset approximations of the posterior.
+%, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer. 
+A more principled approach would be to sparsify the resultant GP into a low-rank approximation to ensure information coming from the entire task dataset is not lost.%, essentially what the sparse dual variables do.
 \todo{this term is replacing the missing data}
-
-An alternative view of the dual variables is that they parameterize approximate likelihoods, as shown in \citep{adam2021dual, khan2017conjugate}.
-We can rewrite the GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
-\begin{equation}
- q(\vu) \propto \N(0, \MKzz) \prod_{i=1}^n e^{-\frac{\tilde{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 } = \N(0, \MKzz) \, e^{(\bar{\vy} - \vu)^\top \bar{\MSigma}^{-1}(\bar{\vy} - \vu)}  
-\end{equation}
-The first normals are the approximate likelihoods where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}$,  replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$ and we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior.
-To arrive at the MVN Gaussian, we need to rearrange the quadratic terms to match the prior sufficient statistics we present a derivation in [appendix].
-Performing conjugate summation of prior and likelihood, we would arrive at the sparse GP posterior at the inducing points.
-The correlated covariance structure $\MSigma$ and the corresponding $\tilde{\vy}$ are simply a different form of the sparse dual variables,
-\begin{equation}
-\quad \bar{\MSigma} =  \MKzz \vbeta_\vu^{-1} \MKzz \quad \bar{\vy} = \MKzz \vbeta_{\vu}\valpha_{\vu}.
-\end{equation}
-Written as above, we can see that the spare dual variables can be interpreted as a sparse MVN representation.
-We now show how we use this for a regularizer in continual learning with more details in [appendix].
-
 % Where the regularizer comes from
@@
 The resulting regularizer can be computed as follows
-\begin{equation}
-	\mathcal{R}_\textit{SFR}(\weights, \mathcal{M}) = \sum_{s=1}^{t-1} \frac{1}{m} \left[\left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right) \right].
-\end{equation}
+%\begin{equation}
+%	\mathcal{R}_\textit{SFR}(\weights, \mathcal{M}) = \sum_{s=1}^{t-1} \frac{1}{m} \left[\left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right) \right].
+%\end{equation}
 
@@
 \end{equation}
-\todo{choose one option}
+%\todo{choose one option}
 % where $f_\vw(\MZ_{s}) \in \R^m$ are the outputs of neural networks with the current weights $\vw$ and stored function outputs of the neural network at the MAP optimum for task $s$, i.e., each $i$th entry is $f_\cdot(\vz_i) \in \R$.
-
 %\begin{equation}
@@
 A key challenge in RL is balancing the trade-off between exploration and exploitation.
-That is, should an agent select actions that it knows will lead to a high reward (exploitation), or should it
-hope to discover new actions which lead to high reward (exploration)?
-In this section, we show that \our's uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim,
-demonstrating the quality of our uncertainty estimates.
-% In this section, we demonstrate  that our method's principled uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim.
-We refer the reader to \cref{app:rl} for an overview of the problem and details of our experiments.
-
-Cart pole swing up task in MuJoCo \cite{todorov2012mujoco}
-We compare our method with deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016} -- a model-free RL baseline --
-which is sample inefficient.
-We test our model's uncertainty estimates by comparing it to using Laplace-GGN with GLM predictions, using an ensemble of neural networks
-(with different initialisations),
-To ensure a fair comparison, we use the same MLP architecture/training scheme and we keep the same model-based RL algorithm.
-See \cref{app:rl} for more details of our experiments.
-
-We also compare to deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016} -- a model-free RL baseline --
-which we expect to be much more sample inefficient.
-
-\cref{fig:rl} shows training curves
-
-\begin{figure}[!t]
- \centering
- \begin{subfigure}[c]{.24\textwidth}
- \resizebox{\textwidth}{!}{%
- \begin{tikzpicture}[inner sep=0,outer sep=0]
-
-   % Draw decorated 'ground'
-   \draw[postaction={draw, decorate, decoration={border, angle=-45,
-					amplitude=1cm, segment length=.5cm}}] (-3,-1.5) -- (12,-1.5);
-
-   % The cart
-   \draw[draw=black,fill=black!50,draw=black,line width=3pt,rounded corners=1mm] (0,0) rectangle (9cm,3cm);
-   \node[fill=black,circle,minimum size=.5cm] (dot) at (4.5cm,3cm) {};
-
-   % Wheels
-   \node[fill=white,draw=black,line width=3pt,circle,minimum size=2cm,,fill=black!50] at (2cm,-.5cm) {};
-   \node[fill=white,draw=black,line width=3pt,circle,minimum size=2cm,fill=black!50] at (7cm,-.5cm) {};
-
-   % The arm
-   \node[anchor=north,minimum width=1cm,minimum height=14cm,draw=black,rotate=-20,rounded corners=5mm,yshift=7mm,xshift=-.3mm,fill=white,draw=black,line width=3pt] at (dot) {};
-   \node[fill=black,circle,minimum size=.5cm] at (dot) {};
-
-   % Markings
-   \draw[loosely dashed,line width=1pt] (4.5,6) -- (4.5,-10);
-
-   % Arrow
-   \draw[->,black,line width=3pt,-{Latex[length=7mm,width=7mm]}] (1,5) --node[above,outer sep=8pt]{\scalebox{4}{$x$}} (4.5,5);
-
-   \def\centerarc[#1](#2)(#3:#4:#5)% Syntax: [draw options] (center) (initial angle:final angle:radius)
-   { \draw[#1] ($(#2)+({#5*cos(#3)},{#5*sin(#3)})$) arc (#3:#4:#5); }
-
-   % Draw arc
-   \centerarc[black,line width=3pt](dot)(250:270:11)
-   \node at (2.5,-9) {\scalebox{4}{$\theta$}};
-
-   %\node[white,minimum size=1cm] at (4.5,-13) {};
-
- \end{tikzpicture}}
- \end{subfigure}
- \hfill
- \begin{subfigure}[c]{.74\textwidth}
-   \centering\scriptsize
-   \setlength{\figurewidth}{\textwidth}
-   \setlength{\figureheight}{.5\figurewidth}
-   \pgfplotsset{axis on top,ymajorgrids,axis line style={draw=none},legend style={at={(1,1)},anchor=north west}}
-   \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed},legend style={fill=white}}
-   \input{./fig/rl.tex}
- \end{subfigure}
- \hfill
- \caption{\textbf{Reinforcement learning experiments} Training curves showing that our model's uncertainty estimates improve sample efficiency in RL.
-   Our method (blue/green) converges to the optimal solution in fewer environment steps than the baseline model-based RL method (magenta) and (DDPG) the model-free baseline  (yellow).}
- \label{fig:rl}
-\end{figure}
-
-%
-
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.5\textwidth, angle=270]{fig/weight-space-to-functio-space.pdf}
-%   \caption{}
-% \end{figure}
-
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.5\textwidth, trim=0 100 0 10]{fig/cartpole-training-curves.pdf}
-%   \caption{}
-% \end{figure}
-
-% \begin{table}
-%   \caption{Negative test log likelihood (lower is better) on UCI classification tasks (2 hidden layers, 50 tanh). Our SVGP predictive outperforms the GLM predictive. }
-% \end{table}
-
-\section{Discussion and conclusion}
-\label{sec:conclusion}
-%
-
-It is worth noting that the NTK linearises the network around the MAP solution $\weights^{*}$,
-so the function space prior (and thus posterior) is only a locally linear approximation.
-In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
-It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.
-
-A reference implementation of the methods presented in this paper is currently available as supplementary material and will be made available under the MIT License on GitHub upon acceptance.
-
-%\section*{Broader Impact}
-
-% \section*{References}
-%\small
-%\printbibliography
-%\normalsize
-% TODO make bibliography small a better way
-
-%References follow the acknowledgments. Use unnumbered first-level heading for
-%the references. Any choice of citation style is acceptable as long as you are
-%consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
-%when listing the references.
-%Note that the Reference section does not count towards the page limit.
-%\medskip
-
-\clearpage
-
-\phantomsection%
-\addcontentsline{toc}{section}{References}
-\begingroup
-\small
-\bibliographystyle{abbrvnat}
-\bibliography{bibliography}%zotero-library
-\endgroup
-
-\clearpage
-
-\nipstitle{
-    {\Large Supplementary Material:} \\
-    Sparse Function-space Representation \\ of Neural Networks}
-\pagestyle{empty}
-
-\appendix
-
-This supplementary document is organized as follows. 
-%
-\cref{app:method} provides a more extensive overview of the techncical details of \our.
-%
-\cref{app:cl} covers the sparse-functional regularisation (SFR) setup for continual learning.
-%
-\cref{app:rl} provides a more extensive writeup of the reinforcement learning setup used in the experiments.
-%
-\cref{app:experiments} provides the full details of each individual experiments in the main paper.
-
-\section{Method details}
-\label{app:method}
-%
-Optionally include extra information (complete proofs, additional experiments and plots) in the appendix.
-This section will often be part of the supplemental material.
-
-\section{Sparse functional regularisation in continual learning}
-\label{app:cl}
-
-\subsection{Extending the CL regularizer to multi-class settings}
-\begin{equation}
-	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{C \times m \times m} \quad \MKzz \in \R^{C \times m \times m} 
-\end{equation}
-
-\begin{equation}
-	\mathcal{R_\textit{SFR}}(\mathbf{w}) = \sum_{s=1}^{t-1}	\sum_{k \in 	C}\left[\left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s}, k}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s, k}}(\MZ_s) \right) \right]
-\end{equation}
-
-\section{Sparse functional model-based reinforcement learning}
-\label{app:rl}
+That is, should the agent select an action that it knows will lead to a high reward (exploitation), or should it
+hope to discover new actions which lead to high reward (exploration) by selecting actions that it has not selected before.
+In this section, we demonstrate  that our method's principled uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim.
 
@@
 
+See \cref{app:rl} for more details of our experiments.
+
+We compare a model-based RL agent using a simple MLP dynamic model with
+\begin{itemize}
+  \item uncertainty is good for exploration
+\end{itemize}
+
+\cref{fig:rl} shows training curves
+
+\begin{figure}[!t]
+ \centering
+ \begin{subfigure}[c]{.24\textwidth}
+ \resizebox{\textwidth}{!}{%
+ \begin{tikzpicture}[inner sep=0,outer sep=0]
+
+   % Draw decorated 'ground'
+   \draw[postaction={draw, decorate, decoration={border, angle=-45,
+					amplitude=1cm, segment length=.5cm}}] (-3,-1.5) -- (12,-1.5);
+
+   % The cart
+   \draw[draw=black,fill=black!50,draw=black,line width=3pt,rounded corners=1mm] (0,0) rectangle (9cm,3cm);
+   \node[fill=black,circle,minimum size=.5cm] (dot) at (4.5cm,3cm) {};
+
+   % Wheels
+   \node[fill=white,draw=black,line width=3pt,circle,minimum size=2cm,,fill=black!50] at (2cm,-.5cm) {};
+   \node[fill=white,draw=black,line width=3pt,circle,minimum size=2cm,fill=black!50] at (7cm,-.5cm) {};
+
+   % The arm
+   \node[anchor=north,minimum width=1cm,minimum height=14cm,draw=black,rotate=-20,rounded corners=5mm,yshift=7mm,xshift=-.3mm,fill=white,draw=black,line width=3pt] at (dot) {};
+   \node[fill=black,circle,minimum size=.5cm] at (dot) {};
+
+   % Markings
+   \draw[loosely dashed,line width=1pt] (4.5,6) -- (4.5,-10);
+
+   % Arrow
+   \draw[->,black,line width=3pt,-{Latex[length=7mm,width=7mm]}] (1,5) --node[above,outer sep=8pt]{\scalebox{4}{$x$}} (4.5,5);
+
+   \def\centerarc[#1](#2)(#3:#4:#5)% Syntax: [draw options] (center) (initial angle:final angle:radius)
+   { \draw[#1] ($(#2)+({#5*cos(#3)},{#5*sin(#3)})$) arc (#3:#4:#5); }
+
+   % Draw arc
+   \centerarc[black,line width=3pt](dot)(250:270:11)
+   \node at (2.5,-9) {\scalebox{4}{$\theta$}};
+
+   %\node[white,minimum size=1cm] at (4.5,-13) {};
+
+ \end{tikzpicture}}
+ \end{subfigure}
+ \hfill
+ \begin{subfigure}[c]{.74\textwidth}
+   \centering\scriptsize
+   \setlength{\figurewidth}{\textwidth}
+   \setlength{\figureheight}{.5\figurewidth}
+   \pgfplotsset{axis on top,ymajorgrids,axis line style={draw=none},legend style={at={(1,1)},anchor=north west}}
+   \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed},legend style={fill=white}}
+   \input{./fig/rl.tex}
+ \end{subfigure}
+ \hfill
+ \caption{\textbf{Reinforcement learning experiments} Training curves showing that our model's uncertainty estimates improve sample efficiency in RL.
+   Our method (blue/green) converges to the optimal solution in fewer environment steps than the baseline model-based RL method (magenta) and (DDPG) the model-free baseline  (yellow).}
+ \label{fig:rl}
+\end{figure}
+
+%
+
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=0.5\textwidth, angle=270]{fig/weight-space-to-functio-space.pdf}
+%   \caption{}
+% \end{figure}
+
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=0.5\textwidth, trim=0 100 0 10]{fig/cartpole-training-curves.pdf}
+%   \caption{}
+% \end{figure}
+
+% \begin{table}
+%   \caption{Negative test log likelihood (lower is better) on UCI classification tasks (2 hidden layers, 50 tanh). Our SVGP predictive outperforms the GLM predictive. }
+% \end{table}
+
+\section{Discussion and conclusion}
+\label{sec:conclusion}
+%
+
+It is worth noting that the NTK linearises the network around the MAP solution $\weights^{*}$,
+so the function space prior (and thus posterior) is only a locally linear approximation.
+In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
+It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.
+
+A reference implementation of the methods presented in this paper is currently available as supplementary material and will be made available under the MIT License on GitHub upon acceptance.
+
+%\section*{Broader Impact}
+
+% \section*{References}
+%\small
+%\printbibliography
+%\normalsize
+% TODO make bibliography small a better way
+
+%References follow the acknowledgments. Use unnumbered first-level heading for
+%the references. Any choice of citation style is acceptable as long as you are
+%consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
+%when listing the references.
+%Note that the Reference section does not count towards the page limit.
+%\medskip
+
+\clearpage
+
+\phantomsection%
+\addcontentsline{toc}{section}{References}
+\begingroup
+\small
+\bibliographystyle{abbrvnat}
+\bibliography{bibliography}%zotero-library
+\endgroup
+
+\clearpage
+
+\nipstitle{
+    {\Large Supplementary Material:} \\
+    PAPER TITLE GOES HERE}
+\pagestyle{empty}
+
+\appendix
+
+This supplementary document is organized as follows. 
+%
+\cref{app:method} provides a more extensive overview of the techncical details of \our.
+%
+\cref{app:cl} covers the sparse-functional regularisation (SFR) setup for continual learning.
+%
+\cref{app:rl} provides a more extensive writeup of the reinforcement learning setup used in the experiments.
+%
+\cref{app:experiments} provides the full details of each individual experiments in the main paper.
+
+\section{Method details}
+\label{app:method}
+%
+Optionally include extra information (complete proofs, additional experiments and plots) in the appendix.
+This section will often be part of the supplemental material.
+
+\section{\our for continual learning}
+\label{app:cl}
+\subsection{Derivation of the regularizer term}
+An alternative view of the dual variables is that they parameterize approximate likelihoods, as shown in \citep{adam2021dual, khan2017conjugate}.
+We can rewrite the GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
+\begin{equation}
+ q(\vu) \propto \Norm(0, \MKzz) \prod_{i=1}^n \exp \!
+\left(-\frac{\tilde{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 \right) = \Norm(0, \MKzz) \, \exp\left((\bar{\vy} - \vu)^\top \bar{\MSigma}^{-1}(\bar{\vy} - \vu)\right)
+\end{equation}
+The first normals are the approximate likelihoods where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}$,  replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$ and we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior.
+To arrive at the MVN Gaussian, we need to rearrange the quadratic terms to match the prior sufficient statistics we present a derivation in [appendix].
+Performing conjugate summation of prior and likelihood, we would arrive at the sparse GP posterior at the inducing points.
+The correlated covariance structure $\MSigma$ and the corresponding $\tilde{\vy}$ are simply a different form of the sparse dual variables,
+\begin{equation}
+\quad \bar{\MSigma} =  \MKzz \vbeta_\vu^{-1} \MKzz \quad \bar{\vy} = \MKzz \vbeta_{\vu}\valpha_{\vu}.
+\end{equation}
+Written as above, we can see that the spare dual variables can be interpreted as a sparse MVN representation.
+We now show how we use this for a regularizer in continual learning with more details in [appendix].
+
+\subsection{Extending the CL regularizer to multi-class settings}
+\begin{equation}
+	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{C \times m \times m} \quad \MKzz \in \R^{C \times m \times m} 
+\end{equation}
+
+\begin{equation}
+	\mathcal{R_\textit{SFR}}(\mathbf{w}) = \sum_{s=1}^{t-1}	\sum_{k \in 	C}\left[\left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s}, k}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s, k}}(\MZ_s) \right) \right]
+\end{equation}
+
+\section{Sparse functional model-based reinforcement learning}
+\label{app:rl}
+
 Model Predictive Path Integral (MPPI) control

### 2023-05-15 paper/main.tex

--- 2023-05-15 paper/main.tex
@@
 
-\section{Sparse functional regularisation in continual learning}
+\section{\our for continual learning}
 \label{app:cl}
+\subsection{Derivation of the regularizer term}
+An alternative view of the dual variables is that they parameterize approximate likelihoods, as shown in \citep{adam2021dual, khan2017conjugate}.
+We can rewrite the GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
+\begin{equation}
+ q(\vu) \propto \Norm(0, \MKzz) \prod_{i=1}^n \exp \!
+\left(-\frac{\tilde{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 \right) = \Norm(0, \MKzz) \, \exp\left((\bar{\vy} - \vu)^\top \bar{\MSigma}^{-1}(\bar{\vy} - \vu)\right)
+\end{equation}
+The first normals are the approximate likelihoods where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}$,  replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$ and we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior.
+To arrive at the MVN Gaussian, we need to rearrange the quadratic terms to match the prior sufficient statistics we present a derivation in [appendix].
+Performing conjugate summation of prior and likelihood, we would arrive at the sparse GP posterior at the inducing points.
+The correlated covariance structure $\MSigma$ and the corresponding $\tilde{\vy}$ are simply a different form of the sparse dual variables,
+\begin{equation}
+\quad \bar{\MSigma} =  \MKzz \vbeta_\vu^{-1} \MKzz \quad \bar{\vy} = \MKzz \vbeta_{\vu}\valpha_{\vu}.
+\end{equation}
+Written as above, we can see that the spare dual variables can be interpreted as a sparse MVN representation.
+We now show how we use this for a regularizer in continual learning with more details in [appendix].
 

### 2023-05-15 paper/main.tex
Sec. 2

--- 2023-05-15 paper/main.tex
@@
 % a GP posterior -- can be obtained
-
-In supervised learning, given a data set $\dataset = \dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with input $\mathbf{x}_i \in \inputDomain$ and output $\mathbf{y}_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w} : \inputDomain \to \outputDomain$, are usually trained to minimize the (regularized) empirical risk,
+%
+In supervised learning, given a data set $\dataset = \{(\vx_{i} , \vy_{i})\}_{i=1}^{n}$, with input $\vx_i \in \inputDomain$ and output $\vy_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w} : \inputDomain \to \outputDomain$, are usually trained to minimize the (regularized) empirical risk,
 %
@@
 %
-If $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) = -\log(p(\mathbf{y} \mid f_\weights(\mathbf{x}_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where the regularization weight takes the role of a prior precision parameter, \ie, $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.
-
-%
-% \subsection{Linearization gives rise to a Gaussian process}
-% \label{sec:nn2gp}
-%
-
-\textbf{Uncertainty quantification} \todo{Move this section to the related work}
-Bayesian inference offers a principled approach to quantifying uncertainty in neural networks.
-The goal is to find the posterior over the weights ${p(\vw \mid \vy) \propto p(\vy \mid f_{\weights}(\vx)) p(\weights)}$ as
-it represents our belief in the parameters after combining data $\dataset$ with our prior $p(\vw)$.
-Although the true posterior $p(\vw \mid \dataset)$ is intractable given the non-linearities of the neural network, one can resort to sampling techniques such as Hamiltonian Monte-Carlo (HMC).
-However, for most applications their high computational costs make them impractical so we need approximate inference techniques.
-In \cref{fig:banana}, we show a qualitative example of the induced function-space posterior obtained with our method compared to the posterior obtained through HMC sampling on the Banana toy dataset.
+If $\ell(f_\weights(\vx_{i}), \vy_i) = -\log(p(\vy \mid f_\weights(\vx_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where the regularization weight takes the role of a prior precision parameter, \ie, $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.
+%Bayesian inference offers a principled approach to quantifying uncertainty in neural networks.
+%The goal is to find the posterior over the weights ${p(\vw \mid \vy) \propto p(\vy \mid f_{\weights}(\vx)) \, p(\weights)}$ as it represents our belief in the parameters after combining data $\dataset$ with our prior $p(\vw)$.
+%Although the true posterior $p(\vw \mid \dataset)$ is intractable given the non-linearities of the neural network, one can resort to sampling techniques such as Hamiltonian Monte-Carlo (HMC).
+%However, for most applications their high computational costs make them impractical so we need approximate inference techniques.
+%In \cref{fig:banana}, we show a qualitative example of the induced function-space posterior obtained with our method compared to the posterior obtained through HMC sampling on the Banana toy dataset.
+The posterior over the weights ${p(\vw \mid \dataset) \propto p(\vy \mid f_{\weights}(\vx)) \, p(\weights)}$ is generally not available in closed form.
+Sampling methods---such as the Hamiltonian Monte Carlo (HMC) baseline used in \cref{fig:banana} (right)---are general-prupose, but comutationally heavy and impractical for downstream applications.
 
@@
 
+See \cref{app:rl} for more details of our experiments.
+
+We compare a model-based RL agent using a simple MLP dynamic model with
+\begin{itemize}
+  \item uncertainty is good for exploration
+\end{itemize}
+
+\cref{fig:rl} shows training curves
+
+\begin{figure}[!t]
+ \centering
+ \begin{subfigure}[c]{.24\textwidth}
+ \resizebox{\textwidth}{!}{%
+ \begin{tikzpicture}[inner sep=0,outer sep=0]
+
+   % Draw decorated 'ground'
+   \draw[postaction={draw, decorate, decoration={border, angle=-45,
+					amplitude=1cm, segment length=.5cm}}] (-3,-1.5) -- (12,-1.5);
+
+   % The cart
+   \draw[draw=black,fill=black!50,draw=black,line width=3pt,rounded corners=1mm] (0,0) rectangle (9cm,3cm);
+   \node[fill=black,circle,minimum size=.5cm] (dot) at (4.5cm,3cm) {};
+
+   % Wheels
+   \node[fill=white,draw=black,line width=3pt,circle,minimum size=2cm,,fill=black!50] at (2cm,-.5cm) {};
+   \node[fill=white,draw=black,line width=3pt,circle,minimum size=2cm,fill=black!50] at (7cm,-.5cm) {};
+
+   % The arm
+   \node[anchor=north,minimum width=1cm,minimum height=14cm,draw=black,rotate=-20,rounded corners=5mm,yshift=7mm,xshift=-.3mm,fill=white,draw=black,line width=3pt] at (dot) {};
+   \node[fill=black,circle,minimum size=.5cm] at (dot) {};
+
+   % Markings
+   \draw[loosely dashed,line width=1pt] (4.5,6) -- (4.5,-10);
+
+   % Arrow
+   \draw[->,black,line width=3pt,-{Latex[length=7mm,width=7mm]}] (1,5) --node[above,outer sep=8pt]{\scalebox{4}{$x$}} (4.5,5);
+
+   \def\centerarc[#1](#2)(#3:#4:#5)% Syntax: [draw options] (center) (initial angle:final angle:radius)
+   { \draw[#1] ($(#2)+({#5*cos(#3)},{#5*sin(#3)})$) arc (#3:#4:#5); }
+
+   % Draw arc
+   \centerarc[black,line width=3pt](dot)(250:270:11)
+   \node at (2.5,-9) {\scalebox{4}{$\theta$}};
+
+   %\node[white,minimum size=1cm] at (4.5,-13) {};
+
+ \end{tikzpicture}}
+ \end{subfigure}
+ \hfill
+ \begin{subfigure}[c]{.74\textwidth}
+   \centering\scriptsize
+   \setlength{\figurewidth}{\textwidth}
+   \setlength{\figureheight}{.5\figurewidth}
+   \pgfplotsset{axis on top,ymajorgrids,axis line style={draw=none},legend style={at={(1,1)},anchor=north west}}
+   \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed},legend style={fill=white}}
+   \input{./fig/rl.tex}
+ \end{subfigure}
+ \hfill
+ \caption{\textbf{Reinforcement learning experiments} Training curves showing that our model's uncertainty estimates improve sample efficiency in RL.
+   Our method (blue/green) converges to the optimal solution in fewer environment steps than the baseline model-based RL method (magenta) and (DDPG) the model-free baseline  (yellow).}
+ \label{fig:rl}
+\end{figure}
+
+%
+
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=0.5\textwidth, angle=270]{fig/weight-space-to-functio-space.pdf}
+%   \caption{}
+% \end{figure}
+
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=0.5\textwidth, trim=0 100 0 10]{fig/cartpole-training-curves.pdf}
+%   \caption{}
+% \end{figure}
+
+% \begin{table}
+%   \caption{Negative test log likelihood (lower is better) on UCI classification tasks (2 hidden layers, 50 tanh). Our SVGP predictive outperforms the GLM predictive. }
+% \end{table}
+
+\section{Discussion and conclusion}
+\label{sec:conclusion}
+%
+
+It is worth noting that the NTK linearises the network around the MAP solution $\weights^{*}$,
+so the function space prior (and thus posterior) is only a locally linear approximation.
+In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
+It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.
+
+A reference implementation of the methods presented in this paper is currently available as supplementary material and will be made available under the MIT License on GitHub upon acceptance.
+
+%\section*{Broader Impact}
+
+% \section*{References}
+%\small
+%\printbibliography
+%\normalsize
+% TODO make bibliography small a better way
+
+%References follow the acknowledgments. Use unnumbered first-level heading for
+%the references. Any choice of citation style is acceptable as long as you are
+%consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
+%when listing the references.
+%Note that the Reference section does not count towards the page limit.
+%\medskip
+
+\clearpage
+
+\phantomsection%
+\addcontentsline{toc}{section}{References}
+\begingroup
+\small
+\bibliographystyle{abbrvnat}
+\bibliography{bibliography}%zotero-library
+\endgroup
+
+\clearpage
+
+\nipstitle{
+    {\Large Supplementary Material:} \\
+    Sparse Function-space Representation \\ of Neural Networks}
+\pagestyle{empty}
+
+\appendix
+
+This supplementary document is organized as follows. 
+%
+\cref{app:method} provides a more extensive overview of the techncical details of \our.
+%
+\cref{app:cl} covers the sparse-functional regularisation (SFR) setup for continual learning.
+%
+\cref{app:rl} provides a more extensive writeup of the reinforcement learning setup used in the experiments.
+%
+\cref{app:experiments} provides the full details of each individual experiments in the main paper.
+
+\section{Method details}
+\label{app:method}
+%
+Optionally include extra information (complete proofs, additional experiments and plots) in the appendix.
+This section will often be part of the supplemental material.
+
+\section{Sparse functional regularisation in continual learning}
+\label{app:cl}
+
+\subsection{Extending the CL regularizer to multi-class settings}
+\begin{equation}
+	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{C \times m \times m} \quad \MKzz \in \R^{C \times m \times m} 
+\end{equation}
+
+\begin{equation}
+	\mathcal{R_\textit{SFR}}(\mathbf{w}) = \sum_{s=1}^{t-1}	\sum_{k \in 	C}\left[\left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s}, k}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s, k}}(\MZ_s) \right) \right]
+\end{equation}
+
+\section{Sparse functional model-based reinforcement learning}
+\label{app:rl}
+
 Model Predictive Path Integral (MPPI) control

### 2023-05-15 paper/main.tex
Sec. 2

@@
   \arg \min_{\weights} \mathcal{L}(\dataset,\weights) =
-  \arg \min_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
+  \arg \min_{\weights} \textstyle\sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
 \end{equation}
@@
 The posterior over the weights ${p(\vw \mid \dataset) \propto p(\vy \mid f_{\weights}(\vx)) \, p(\weights)}$ is generally not available in closed form.
-Sampling methods---such as the Hamiltonian Monte Carlo (HMC) baseline used in \cref{fig:banana} (right)---are general-prupose, but comutationally heavy and impractical for downstream applications.
+Sampling methods that characterize the posterior with a finite set of samples in weight-space---such as the Hamiltonian Monte Carlo (HMC) baseline used in \cref{fig:banana} (right)---are general-purpose, but comuptationally heavy and impractical for downstream applications.
 

### 2023-05-15 bnn-predictive/experiments/scripts/imginference.py
Added batch size option for subset GP, debugging delta factor loop

@@ -212,6 +212,8 @@ def main(
     res_dir="experiments/results",
     run_with_best=False,
     run_update=False,
+    only_map=False,
+    delta_factor=None,
     device="cuda",
 ):
     lh = CategoricalLh(EPS=0)  #0.000000000000000001)
@@ -223,21 +225,21 @@ def main(
         # strip off filename ending using indexing
         print(file)
         ds, m, s, delta = file[:-3].split("_")
+        if float(delta) == 0:
+            continue
         if (
             ds == dataset_name
             and m == model_name
             and seed == int(s)
-            and (np.log10(float(delta)) >= delta_min)
-            and (np.log10(float(delta)) <= delta_max)
+            and (np.log10(float(delta)) >= logdelta_min)
+            and (np.log10(float(delta)) <= logdelta_max)
         ):
             eligible_files.append(os.path.join(res_dir, "models/" + file))
             deltas.append(float(delta))
-            state = torch.load("models/" + file)
+            state = torch.load(os.path.join(res_dir, "models/" + file))
             if "map" not in state:
                 continue
             perfs.append(state["map"]["nll_va"])
-    logging.info(f"Deltas: {deltas}")
-    best_file = eligible_files[np.argmin(perfs)]
 
     # Create train, test and val
     torch.manual_seed(seed)
@@ -263,6 +265,8 @@ def main(
 
     # start with smallest delta and continue
     if not run_with_best:
+        print('Run with various deltas')
+        logging.info(f"Deltas: {deltas}")
         ixlist = np.argsort(deltas)
         deltas = np.array(deltas)[ixlist]
         eligible_files = list(np.array(eligible_files)[ixlist])
@@ -270,26 +274,32 @@ def main(
         for f, delta in tqdm(list(zip(eligible_files, deltas))):
             logging.info(f"inference for delta={delta}")
             state = torch.load(f)
-            state = run_inference(state,model, likelihood, test_loader, val_loader, ds_train, X_train, y_train,
-                    num_inducing, delta, batch_size=batch_size, model_name=model_name, name=name, device=device)
+            state = run_inference(state,model, lh, test_loader, val_loader, ds_train, X_train, y_train,
+                    n_inducing, delta, batch_size=batch_size, model_name=model_name, name=name, only_map=only_map, device=device)
             torch.save(state, f)
     else:
-        delta_factors = np.logspace(-1, 3, 13)
[…]

### 2023-05-15 paper/main.tex
Sec. 1.1

@@
 \textbf{Bayesian deep learning}
-Probabilistic method in deep learning~\cite{Wilson:ensembles,neal1995bayesian} have recently gained increasing attention in the machine learning community as a means for uncertainty quantification (\eg, \cite{kendall2017what,wilson2020bayes}) and model selection (\eg,~\cite{immer2021scalable,antoran2022marginal}) with advancements in prior specification (\eg, \cite{cho2009kernel,meronen2020stationary,meronen2021periodic,fortuin2021bayesian,nalisnick2018do}) and efficient approximate inference under the specified model.
-Calculating the posterior distribution of a Bayesian neural network is usually intractable, and approximate inference techniques need to be used, such as variational inference \cite{blei2017variational}, deep ensembles \cite{lakshminarayanan2017simple}, MC dropout \cite{gal2016dropout}, or Laplace approximation \cite{ritter2018kfac,kristiadi2020being,immer2021improving}---each having strengths and weaknesses.
-% point out strngths and weaknesses for each
-
-% Introduce the laplace GGN + shortcomings
+Probabilistic methods in deep learning~\cite{Wilson:ensembles,neal1995bayesian} have recently gained increasing attention in the machine learning community as a means for uncertainty quantification (\eg, \cite{kendall2017what,wilson2020bayes}) and model selection (\eg,~\cite{immer2021scalable,antoran2022marginal}) with advancements in prior specification (\eg, \cite{cho2009kernel,meronen2020stationary,meronen2021periodic,fortuin2021bayesian,nalisnick2018do}) and efficient approximate inference under the specified model.
+Calculating the posterior distribution of a Bayesian neural network is usually intractable, and approximate inference techniques need to be used, such as variational inference \cite{blei2017variational}, deep ensembles \cite{lakshminarayanan2017simple}, MC dropout \cite{gal2016dropout}, or Laplace approximation \cite{ritter2018kfac,kristiadi2020being,immer2021improving}---each with its own set of strengths and weaknesses.
+
 %\textbf{Function-space methods}
-One common approach for uncertainty with neural networks is a Laplace-GGN approximation \citep{daxberger2021laplace}, which takes a trained neural network and linearises it around the optimal weights.
+%One common approach for uncertainty with neural networks is a Laplace-GGN approximation \citep{daxberger2021laplace}, which takes a trained neural network and linearises it around the optimal weights.
 The Hessian can be efficiently approximated using the generalized Gauss--Newton approximation (GGN)~\cite{botev2017practical} but typically involves a cubic scaling in the number of parameters, in practice a further approximation such as the Kronecker factorisation \cite{martens2015optimizing,ritter2018kfac} is needed.
@@
 Therefore, as shown in \cite{immer2021scalable, khan2019approximate,maddox2021fast}, the linear model can be converted to a GP, which is then used to obtain the uncertainty estimates.
-%
-However, the GP introduces a cubic scaling $\mathcal{O}(N^3)$ in the number of data points $N$.
+
+% Introduce the laplace GGN + shortcomings
+\textbf{Function-space methods}
+Function-space perspectives on uncertainty in neural networks often use a Laplace-GGN approximation \citep{daxberger2021laplace}, linearizing a trained neural network around optimal weights.
+The Hessian can be efficiently approximated using the generalized Gauss--Newton approximation (GGN)~\cite{botev2017practical}.
+While efficient, it suffers from cubic scaling in parameter count, necessitating approximations like Kronecker factorisation \cite{martens2015optimizing, ritter2018kfac}.
+This linear model, linear in the weights, refines predictions and provides uncertainty estimates \citep{immer2021scalable}.
+This model has a convenient interpretation as a GP \cite{immer2021scalable, khan2019approximate, maddox2021fast}.
+%
+However, the GP's cubic $\mathcal{O}(N^3)$ scaling with data points $N$ requires costly approximations, often resorting to using data subsets \cite{immer2021scalable}.
+In the GP community, sparse approximations have mitigated this scaling issue (\eg, \cite{titsias2009variational,hensman2013gaussian}), but combining neural network linearization with sparse methods remains unclear without resorting to subset methods.
+Our work addresses this by utilizing the GP's dual parameters \cite{csato2002sparse}, previously applied to non-conjugate likelihood models \cite{adam2021dual}.
+
+%wang2019exact
+%
+%However, the GP introduces a cubic $\mathcal{O}(N^3)$ scaling in the number of data points $N$.
 Previous approaches apply crude approximations to alleviate the computational costs, \eg, by considering only a subset of the training data \cite{immer2021scalable}.
@@
 % CL section
-\textbf{Function-space methods for sequential learning} The central problem in continual learning is how to deal with the non-stationary nature of the training distribution, which causes the training process to overwrite the previously learnt parameters---leading to the model forgetting the previously learnt functions.
-The approaches proposed in the CL literature can be categorized into inference-based, rehearsal-based, and model-based methods; we refer the reader to \citep{parisi2019continual, de2021continual} for complete reviews.
+%\textbf{Function-space methods for sequential learning} The central problem in continual learning is how to deal with the non-stationary nature of the training distribution, which causes the training process to overwrite the previously learnt parameters---leading to the model forgetting the previously learnt functions.
+%The approaches proposed in the CL literature can be categorized into inference-based, rehearsal-based, and model-based methods; we refer the reader to \citep{parisi2019continual, de2021continual} for complete reviews.
 The methods in the first category usually tackle this problem with weight-space regularization, such as EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke17a}), or VCL~\citep{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone.
-However, encoding functional knowledge in the weights does not guarantee a good quality of the predictions, thus a better to introduce a function-space regularization \citep{li2018lwf, benjamin2018measuring, titsias2019functional, buzzega2020dark, pan2020continual, rudner2022continual}.
+%However, encoding functional knowledge in the weights does not guarantee a good quality of the predictions, thus a better to introduce a function-space regularization \citep{li2018lwf, benjamin2018measuring, titsias2019functional, buzzega2020dark, pan2020continual, rudner2022continual}.
 These methods bridge the gap between objective and rehearsal-based methods since they rely on a subset of the training data for each task to compute the regularization term.
 Recently proposed methods, such as DER~\citep{buzzega2020dark}, FROMP~\citep{pan2020continual}, and S-FSVI~\citep{rudner2022continual} achieve state-of-the-art performances among the objective-based techniques in several CL benchmarks.
+
+\textbf{Function-space methods for sequential learning} 
+Continual learning (CL) hinges on how to deal with the non-stationary training distribution, wherein the training process may overwrite previously learned parameters, causing catastrophic forgetting.
+CL approaches fall into inference-based, rehearsal-based, and model-based methods (see \cite{parisi2019continual, de2021continual} for an overview).
+The methods in the first category usually tackle this problem with weight-space regularization, such as EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke17a}), or VCL~\citep{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone.
+However, encoding functional knowledge in the weights does not guarantee good quality of the predictions.
+Function-space regularization techniques~\cite{li2018lwf, benjamin2018measuring, titsias2019functional, buzzega2020dark, pan2020continual, rudner2022continual} address this by relying on training data subsets for each task to compute the regularization term.
+These methods bridge the gap between objective and rehearsal-based methods since they use a subset of the training data for each task to compute the regularization term.
+Recently proposed methods, \eg DER~\citep{buzzega2020dark}, FROMP~\citep{pan2020continual}, and S-FSVI~\citep{rudner2022continual} achieve state-of-the-art performance among the objective-based techniques in several CL benchmarks.
+
+%%
 
@@
 %
-In supervised learning, given a data set $\dataset = \{(\vx_{i} , \vy_{i})\}_{i=1}^{n}$, with input $\vx_i \in \inputDomain$ and output $\vy_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w} : \inputDomain \to \outputDomain$, are usually trained to minimize the (regularized) empirical risk,
+In supervised learning, given a data set $\dataset = \{(\vx_{i} , \vy_{i})\}_{i=1}^{N}$, with input $\vx_i \in \inputDomain$ and output $\vy_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w} : \inputDomain \to \outputDomain$, are usually trained to minimize the (regularized) empirical risk,
 %
@@
   \arg \min_{\weights} \mathcal{L}(\dataset,\weights) =
-  \arg \min_{\weights} \textstyle\sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
+  \arg \min_{\weights} \textstyle\sum_{i=1}^{N} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
 \end{equation}

### 2023-05-15 paper/main.tex
Sec. 2

@@
 \textbf{Function space}
-As a neural network is a deterministic mapping, the weight-space posterior induces a distribution over the function values.
-Intuitively, if one was to sample from the weight posterior, the corresponding functions created can
-be viewed as perturbed versions of the function at the MAP estimate $f_{\vw^*}$.
-% \todo{not super sure about the perturbed part here. I know what \textrm{you}'re trying to say but a little confused}
-In most applications, we care about predictions from the neural network and not the weights themselves.
-As such, it is the distribution over function values that we are actually interested in.
+%As a neural network is a deterministic mapping, the weight-space posterior induces a distribution over the function values.
+%Intuitively, if one was to sample from the weight posterior, the corresponding functions created can
+%be viewed as perturbed versions of the function at the MAP estimate $f_{\vw^*}$.
+%In most applications, we care about predictions from the neural network and not the weights themselves.
+%As such, it is the distribution over function values that we are actually interested in.
+While neural networks are deterministic mappings defined by their weights, the ultimate goal of training a neural network is to optimize the function it represents, not the weights themselves.
+Consequently, the weight-space posterior corresponds to a distribution over function values.
+Imagine sampling from the weight posterior; the resulting functions could be viewed as perturbations of the function at the MAP estimate $f_{\vw^*}$.
+This perspective aligns better with the main objective in most applications: making representative predictions given the observations we have.
 
 \textbf{Linearization gives rise to a Gaussian process}
-Our goal is to build a sparse function-space representation of a neural network.
-Gaussian processes $f$ are an extension of the multivariate normal that characterizes a distribution over
-functions in terms of the first two moments.
-They are defined by a mean function $\mu(\cdot)$ and a covariance (aka kernel) function $\kappa(\cdot,\cdot)$.
-Thus, we need these two functions based on the neural network to build the Gaussian process posterior.
-Recent work \citep{khan2019approximate,maddox2021fast} has shown that linearizing approximations in the weight space
-lead to function space equivalent approximations.
-As Gaussian distributions remain tractable under linear transformations, a linear function in
-terms of parameters can be converted from the weight space to the function space (see Ch.~2.1 in \cite{rasmussen2006gaussian}) as follows:\begin{equation} \label{eq:weight_func}
+We are concerned with capturing the distribution over the neural network model functions, in terms of the first two moments of the distribution.
+A Gaussian process is fully characterized by these moments: a mean function $\mu(\cdot)$ and a covariance (kernel) function $\kappa(\cdot,\cdot)$.
+Recent work \cite{khan2019approximate,maddox2021fast} has shown that linearizing approximations in the weight space lead to function-space equivalent approximations.
+As Gaussian distributions remain tractable under linear transformations, a linear function in terms of parameters can be converted from the weight space to the function space (see Ch.~2.1 in \cite{rasmussen2006gaussian}) as follows:\begin{equation} \label{eq:weight_func}
 f_\weights(\vx) \approx 

### 2023-05-15 paper/main.tex
updated rl section

--- 2023-05-15 paper/main.tex
@@
 % a GP posterior -- can be obtained
-%
-In supervised learning, given a data set $\dataset = \{(\vx_{i} , \vy_{i})\}_{i=1}^{n}$, with input $\vx_i \in \inputDomain$ and output $\vy_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w} : \inputDomain \to \outputDomain$, are usually trained to minimize the (regularized) empirical risk,
+
+In supervised learning, given a data set $\dataset = \dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with input $\mathbf{x}_i \in \inputDomain$ and output $\mathbf{y}_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w} : \inputDomain \to \outputDomain$, are usually trained to minimize the (regularized) empirical risk,
 %
@@
   \arg \min_{\weights} \mathcal{L}(\dataset,\weights) =
-  \arg \min_{\weights} \textstyle\sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
+  \arg \min_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
 \end{equation}
 %
-If $\ell(f_\weights(\vx_{i}), \vy_i) = -\log(p(\vy \mid f_\weights(\vx_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where the regularization weight takes the role of a prior precision parameter, \ie, $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.
-%Bayesian inference offers a principled approach to quantifying uncertainty in neural networks.
-%The goal is to find the posterior over the weights ${p(\vw \mid \vy) \propto p(\vy \mid f_{\weights}(\vx)) \, p(\weights)}$ as it represents our belief in the parameters after combining data $\dataset$ with our prior $p(\vw)$.
-%Although the true posterior $p(\vw \mid \dataset)$ is intractable given the non-linearities of the neural network, one can resort to sampling techniques such as Hamiltonian Monte-Carlo (HMC).
-%However, for most applications their high computational costs make them impractical so we need approximate inference techniques.
-%In \cref{fig:banana}, we show a qualitative example of the induced function-space posterior obtained with our method compared to the posterior obtained through HMC sampling on the Banana toy dataset.
-The posterior over the weights ${p(\vw \mid \dataset) \propto p(\vy \mid f_{\weights}(\vx)) \, p(\weights)}$ is generally not available in closed form.
-Sampling methods that characterize the posterior with a finite set of samples in weight-space---such as the Hamiltonian Monte Carlo (HMC) baseline used in \cref{fig:banana} (right)---are general-purpose, but comuptationally heavy and impractical for downstream applications.
+If $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) = -\log(p(\mathbf{y} \mid f_\weights(\mathbf{x}_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where the regularization weight takes the role of a prior precision parameter, \ie, $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.
+
+%
+% \subsection{Linearization gives rise to a Gaussian process}
+% \label{sec:nn2gp}
+%
+
+\textbf{Uncertainty quantification} \todo{Move this section to the related work}
+Bayesian inference offers a principled approach to quantifying uncertainty in neural networks.
+The goal is to find the posterior over the weights ${p(\vw \mid \vy) \propto p(\vy \mid f_{\weights}(\vx)) p(\weights)}$ as
+it represents our belief in the parameters after combining data $\dataset$ with our prior $p(\vw)$.
+Although the true posterior $p(\vw \mid \dataset)$ is intractable given the non-linearities of the neural network, one can resort to sampling techniques such as Hamiltonian Monte-Carlo (HMC).
+However, for most applications their high computational costs make them impractical so we need approximate inference techniques.
+In \cref{fig:banana}, we show a qualitative example of the induced function-space posterior obtained with our method compared to the posterior obtained through HMC sampling on the Banana toy dataset.
 
@@
 % Definition of CL -> a sequence of tasks 
-In the Continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{n_t}$, which after the task is discarded and cannot be accessed in the following stages of the training.
-Rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting.
-In the same way, after each task, we can use our \our to build a compact representation of the neural network and then exploit this representation to build a functional regularizer to add to the training loss for the subsequent tasks.
-Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art on CL benchmarks.
-However, they are limited to use subset approximations of the posterior.
-%, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer. 
-A more principled approach would be to sparsify the resultant GP into a low-rank approximation to ensure information coming from the entire task dataset is not lost.%, essentially what the sparse dual variables do.
+In the Continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{n_t}$, which after the task is discarded and cannot be accessed in the later stages of the training.
+However, rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting.
+After each task, we can use our \our to build a compact representation of the neural network and then use that as an additional term to the training loss to regularize the model.
+Recent success has shown GP-based regularizers perform better than weight space equivalents getting state-of-the-art on typical CL benchmarks \cite{ pan2020continual, rudner2022continual}.
+The limitation of such approaches is that they must use subset approximations of the posterior, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer.
+A more principled approach would be to sparsify the data into a low-rank approximation to ensure information wasn't lost, essentially what the sparse dual variables do.
 \todo{this term is replacing the missing data}
+
+An alternative view of the dual variables is that they parameterize approximate likelihoods, as shown in \citep{adam2021dual, khan2017conjugate}.
+We can rewrite the GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
+\begin{equation}
+ q(\vu) \propto \N(0, \MKzz) \prod_{i=1}^n e^{-\frac{\tilde{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 } = \N(0, \MKzz) \, e^{(\bar{\vy} - \vu)^\top \bar{\MSigma}^{-1}(\bar{\vy} - \vu)}  
+\end{equation}
+The first normals are the approximate likelihoods where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}$,  replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$ and we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior.
+To arrive at the MVN Gaussian, we need to rearrange the quadratic terms to match the prior sufficient statistics we present a derivation in [appendix].
+Performing conjugate summation of prior and likelihood, we would arrive at the sparse GP posterior at the inducing points.
+The correlated covariance structure $\MSigma$ and the corresponding $\tilde{\vy}$ are simply a different form of the sparse dual variables,
+\begin{equation}
+\quad \bar{\MSigma} =  \MKzz \vbeta_\vu^{-1} \MKzz \quad \bar{\vy} = \MKzz \vbeta_{\vu}\valpha_{\vu}.
+\end{equation}
+Written as above, we can see that the spare dual variables can be interpreted as a sparse MVN representation.
+We now show how we use this for a regularizer in continual learning with more details in [appendix].
+
 % Where the regularizer comes from
@@
 The resulting regularizer can be computed as follows
-%\begin{equation}
-%	\mathcal{R}_\textit{SFR}(\weights, \mathcal{M}) = \sum_{s=1}^{t-1} \frac{1}{m} \left[\left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right) \right].
-%\end{equation}
+\begin{equation}
+	\mathcal{R}_\textit{SFR}(\weights, \mathcal{M}) = \sum_{s=1}^{t-1} \frac{1}{m} \left[\left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right) \right].
+\end{equation}
 
@@
 \end{equation}
-%\todo{choose one option}
+\todo{choose one option}
 % where $f_\vw(\MZ_{s}) \in \R^m$ are the outputs of neural networks with the current weights $\vw$ and stored function outputs of the neural network at the MAP optimum for task $s$, i.e., each $i$th entry is $f_\cdot(\vz_i) \in \R$.
+
 %\begin{equation}
@@
 \subsection{Reinforcement learning}
-A key challenge in RL is balancing the trade-off between exploration and exploitation.
-That is, should an agent select actions that it knows will lead to a high reward (exploitation), or should it
-hope to discover new actions which lead to high reward (exploration)?
-In this section, we show that \our's uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim,
-demonstrating the quality of our uncertainty estimates.
+We now demonstrate the quaility of \our's uncertainty estimates by showing that it can improve sample efficiency in RL when used in conjuction with an
+uncertainty-guided exploration strategy.
+Balancing the trade-off between exploration and exploitation is a key challenge in RL \cite{sutton2018reinforcement}.
+Should an agent select actions that it knows will lead to high reward (exploitation), or actions which it has not select before in the
+hope to discover new high reward actions (exploration)?
+
+Prior work has used GP dynamic models \cite{deisenrothPILCO2011,kamtheDataEfficient2018}, ensembles of neural
+networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
+variational inference \cite{galImproving2016,houthooftVIME2017}
+
+% In this section, we show that \our's uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim,
+% demonstrating the quality of our uncertainty estimates.
+
+% A key challenge in RL is balancing the trade-off between exploration and exploitation.
+% That is, should an agent select actions that it knows will lead to a high reward (exploitation), or should it
+% hope to discover new actions which lead to high reward (exploration)?
+% In this section, we show that \our's uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim,
+% demonstrating the quality of our uncertainty estimates.
 % In this section, we demonstrate  that our method's principled uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim.
-We refer the reader to \cref{app:rl} for an overview of the problem and details of our experiments.
-
-Cart pole swing up task in MuJoCo \cite{todorov2012mujoco}
-We compare our method with deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016} -- a model-free RL baseline --
-which is sample inefficient.
-We test our model's uncertainty estimates by comparing it to using Laplace-GGN with GLM predictions, using an ensemble of neural networks
-(with different initialisations),
-To ensure a fair comparison, we use the same MLP architecture/training scheme and we keep the same model-based RL algorithm.
-See \cref{app:rl} for more details of our experiments.
-
-We also compare to deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016} -- a model-free RL baseline --
-which we expect to be much more sample inefficient.
-
-\cref{fig:rl} shows training curves
+We refer the reader to \cref{app:rl} for an overview of the reinforcement learning problem and more details of our experiments.
+
+% It is an inherently unstable and underactuated mechanical system.
+
+by using it to learn a dynamics model and
+evaluate the
+We test \our by using it to learn a dynamics model
+our method on the cart pole swing up task in MuJoCo \cite{todorov2012mujoco}, a classic benchmark for nonlinear control, see \cref{fig:rl}.
+The goal is to swing the pole up and balance it around the upward position.
+We increase the  difficulty of exploration in this environment by using a sparse reward function.
+
+We compare our method to a Laplace-GGN with GLM predictions (red), an ensemble of neural networks (green) and a basic MLP wih no uncertainty (magenta).
+To ensure a fair comparison, we use the same MLP architecture/training scheme and use them in the same model-based RL algorithm, detailed in \cref{app:rl}.
+% See \cref{app:rl} for more details of our experiments.
+We also compare to deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016}, a model-free RL algorithim (yellow).
+% As expected DDPG is the least sample inefficient
+The training curves in \cref{fig:rl} show that \our's uncertainty estimates are good for exploration as it converges in fewer episodes.
+
+% We compare our method with deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016} -- a model-free RL baseline --
+% which is sample inefficient.
 
@@
 
-\section{\our for continual learning}
+\section{Sparse functional regularisation in continual learning}
 \label{app:cl}
-\subsection{Derivation of the regularizer term}
-An alternative view of the dual variables is that they parameterize approximate likelihoods, as shown in \citep{adam2021dual, khan2017conjugate}.
-We can rewrite the GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
-\begin{equation}
- q(\vu) \propto \Norm(0, \MKzz) \prod_{i=1}^n \exp \!
-\left(-\frac{\tilde{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 \right) = \Norm(0, \MKzz) \, \exp\left((\bar{\vy} - \vu)^\top \bar{\MSigma}^{-1}(\bar{\vy} - \vu)\right)
-\end{equation}
-The first normals are the approximate likelihoods where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}$,  replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$ and we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior.
-To arrive at the MVN Gaussian, we need to rearrange the quadratic terms to match the prior sufficient statistics we present a derivation in [appendix].
-Performing conjugate summation of prior and likelihood, we would arrive at the sparse GP posterior at the inducing points.
-The correlated covariance structure $\MSigma$ and the corresponding $\tilde{\vy}$ are simply a different form of the sparse dual variables,
-\begin{equation}
-\quad \bar{\MSigma} =  \MKzz \vbeta_\vu^{-1} \MKzz \quad \bar{\vy} = \MKzz \vbeta_{\vu}\valpha_{\vu}.
-\end{equation}
-Written as above, we can see that the spare dual variables can be interpreted as a sparse MVN representation.
-We now show how we use this for a regularizer in continual learning with more details in [appendix].
 

### 2023-05-15 paper/main.tex
deelte dline
updated rl fig caption

@@
  \hfill
- \caption{\textbf{Reinforcement learning experiments} Training curves showing that our model's uncertainty estimates improve sample efficiency in RL.
-   Our method (blue/green) converges to the optimal solution in fewer environment steps than the baseline model-based RL method (magenta) and (DDPG) the model-free baseline  (yellow).}
+ \caption{\textbf{Reinforcement learning experiments} Training curves showing that \our's uncertainty estimates improve sample efficiency in RL.
+   Our method (blue/green) converges in fewer environment steps than the baseline model-based RL method (magenta) and (DDPG) the model-free baseline  (yellow).}
  \label{fig:rl}
@@
 train the model.
-See \cref{sec-rl-appendix} for more details of how we use
 

### 2023-05-15 paper/main.tex

@@
 % a GP posterior -- can be obtained
-
-In supervised learning, given a data set $\dataset = \dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with input $\mathbf{x}_i \in \inputDomain$ and output $\mathbf{y}_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w} : \inputDomain \to \outputDomain$, are usually trained to minimize the (regularized) empirical risk,
+%
+In supervised learning, given a data set $\dataset = \{(\vx_{i} , \vy_{i})\}_{i=1}^{N}$, with input $\vx_i \in \inputDomain$ and output $\vy_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w} : \inputDomain \to \outputDomain$, are usually trained to minimize the (regularized) empirical risk,
 %
@@
   \arg \min_{\weights} \mathcal{L}(\dataset,\weights) =
-  \arg \min_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
+  \arg \min_{\weights} \textstyle\sum_{i=1}^{N} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
 \end{equation}
 %
-If $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) = -\log(p(\mathbf{y} \mid f_\weights(\mathbf{x}_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where the regularization weight takes the role of a prior precision parameter, \ie, $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.
-
-%
-% \subsection{Linearization gives rise to a Gaussian process}
-% \label{sec:nn2gp}
-%
-
-\textbf{Uncertainty quantification} \todo{Move this section to the related work}
-Bayesian inference offers a principled approach to quantifying uncertainty in neural networks.
-The goal is to find the posterior over the weights ${p(\vw \mid \vy) \propto p(\vy \mid f_{\weights}(\vx)) p(\weights)}$ as
-it represents our belief in the parameters after combining data $\dataset$ with our prior $p(\vw)$.
-Although the true posterior $p(\vw \mid \dataset)$ is intractable given the non-linearities of the neural network, one can resort to sampling techniques such as Hamiltonian Monte-Carlo (HMC).
-However, for most applications their high computational costs make them impractical so we need approximate inference techniques.
-In \cref{fig:banana}, we show a qualitative example of the induced function-space posterior obtained with our method compared to the posterior obtained through HMC sampling on the Banana toy dataset.
+If $\ell(f_\weights(\vx_{i}), \vy_i) = -\log(p(\vy \mid f_\weights(\vx_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where the regularization weight takes the role of a prior precision parameter, \ie, $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.
+%Bayesian inference offers a principled approach to quantifying uncertainty in neural networks.
+%The goal is to find the posterior over the weights ${p(\vw \mid \vy) \propto p(\vy \mid f_{\weights}(\vx)) \, p(\weights)}$ as it represents our belief in the parameters after combining data $\dataset$ with our prior $p(\vw)$.
+%Although the true posterior $p(\vw \mid \dataset)$ is intractable given the non-linearities of the neural network, one can resort to sampling techniques such as Hamiltonian Monte-Carlo (HMC).
+%However, for most applications their high computational costs make them impractical so we need approximate inference techniques.
+%In \cref{fig:banana}, we show a qualitative example of the induced function-space posterior obtained with our method compared to the posterior obtained through HMC sampling on the Banana toy dataset.
+The posterior over the weights ${p(\vw \mid \dataset) \propto p(\vy \mid f_{\weights}(\vx)) \, p(\weights)}$ is generally not available in closed form.
+Sampling methods that characterize the posterior with a finite set of samples in weight-space---such as the Hamiltonian Monte Carlo (HMC) baseline used in \cref{fig:banana} (right)---are general-purpose, but comuptationally heavy and impractical for downstream applications.
 
 \textbf{Function space}
-As a neural network is a deterministic mapping, the weight-space posterior induces a distribution over the function values.
-Intuitively, if one was to sample from the weight posterior, the corresponding functions created can
-be viewed as perturbed versions of the function at the MAP estimate $f_{\vw^*}$.
-% \todo{not super sure about the perturbed part here. I know what \textrm{you}'re trying to say but a little confused}
-In most applications, we care about predictions from the neural network and not the weights themselves.
-As such, it is the distribution over function values that we are actually interested in.
+%As a neural network is a deterministic mapping, the weight-space posterior induces a distribution over the function values.
+%Intuitively, if one was to sample from the weight posterior, the corresponding functions created can
+%be viewed as perturbed versions of the function at the MAP estimate $f_{\vw^*}$.
+%In most applications, we care about predictions from the neural network and not the weights themselves.
+%As such, it is the distribution over function values that we are actually interested in.
+While neural networks are deterministic mappings defined by their weights, the ultimate goal of training a neural network is to optimize the function it represents, not the weights themselves.
+Consequently, the weight-space posterior corresponds to a distribution over function values.
+Imagine sampling from the weight posterior; the resulting functions could be viewed as perturbations of the function at the MAP estimate $f_{\vw^*}$.
+This perspective aligns better with the main objective in most applications: making representative predictions given the observations we have.
 
 \textbf{Linearization gives rise to a Gaussian process}
-Our goal is to build a sparse function-space representation of a neural network.
-Gaussian processes $f$ are an extension of the multivariate normal that characterizes a distribution over
-functions in terms of the first two moments.
-They are defined by a mean function $\mu(\cdot)$ and a covariance (aka kernel) function $\kappa(\cdot,\cdot)$.
-Thus, we need these two functions based on the neural network to build the Gaussian process posterior.
-Recent work \citep{khan2019approximate,maddox2021fast} has shown that linearizing approximations in the weight space
-lead to function space equivalent approximations.
-As Gaussian distributions remain tractable under linear transformations, a linear function in
-terms of parameters can be converted from the weight space to the function space (see Ch.~2.1 in \cite{rasmussen2006gaussian}) as follows:\begin{equation} \label{eq:weight_func}
+We are concerned with capturing the distribution over the neural network model functions, in terms of the first two moments of the distribution.
+A Gaussian process is fully characterized by these moments: a mean function $\mu(\cdot)$ and a covariance (kernel) function $\kappa(\cdot,\cdot)$.
+Recent work \cite{khan2019approximate,maddox2021fast} has shown that linearizing approximations in the weight space lead to function-space equivalent approximations.
+As Gaussian distributions remain tractable under linear transformations, a linear function in terms of parameters can be converted from the weight space to the function space (see Ch.~2.1 in \cite{rasmussen2006gaussian}) as follows:\begin{equation} \label{eq:weight_func}
 f_\weights(\vx) \approx 

### 2023-05-15 paper/main.tex
update cl part

--- 2023-05-15 paper/main.tex
@@
 % Definition of CL -> a sequence of tasks 
-In the Continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{n_t}$, which after the task is discarded and cannot be accessed in the later stages of the training.
-However, rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting.
-After each task, we can use our \our to build a compact representation of the neural network and then use that as an additional term to the training loss to regularize the model.
-Recent success has shown GP-based regularizers perform better than weight space equivalents getting state-of-the-art on typical CL benchmarks \cite{ pan2020continual, rudner2022continual}.
-The limitation of such approaches is that they must use subset approximations of the posterior, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer.
-A more principled approach would be to sparsify the data into a low-rank approximation to ensure information wasn't lost, essentially what the sparse dual variables do.
+In the Continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{n_t}$, which after the task is discarded and cannot be accessed in the following stages of the training.
+Rehearsal and function regularization-based models keep a subset of the trai ning data for each task to help the model alleviate forgetting.
+In the same way, after each task, we can use our \our to build a compact representation of the neural network and then exploit this representation to build a functional regularizer to add to the training loss for the subsequent tasks.
+Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art on CL benchmarks.
+However, they are limited to use subset approximations of the posterior.
+%, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer. 
+A more principled approach would be to sparsify the resultant GP into a low-rank approximation to ensure information coming from the entire task dataset is not lost.
+%, essentially what the sparse dual variables do.
 \todo{this term is replacing the missing data}
-
-An alternative view of the dual variables is that they parameterize approximate likelihoods, as shown in \citep{adam2021dual, khan2017conjugate}.
-We can rewrite the GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
-\begin{equation}
- q(\vu) \propto \N(0, \MKzz) \prod_{i=1}^n e^{-\frac{\tilde{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 } = \N(0, \MKzz) \, e^{(\bar{\vy} - \vu)^\top \bar{\MSigma}^{-1}(\bar{\vy} - \vu)}  
-\end{equation}
-The first normals are the approximate likelihoods where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}$,  replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$ and we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior.
-To arrive at the MVN Gaussian, we need to rearrange the quadratic terms to match the prior sufficient statistics we present a derivation in [appendix].
-Performing conjugate summation of prior and likelihood, we would arrive at the sparse GP posterior at the inducing points.
-The correlated covariance structure $\MSigma$ and the corresponding $\tilde{\vy}$ are simply a different form of the sparse dual variables,
-\begin{equation}
-\quad \bar{\MSigma} =  \MKzz \vbeta_\vu^{-1} \MKzz \quad \bar{\vy} = \MKzz \vbeta_{\vu}\valpha_{\vu}.
-\end{equation}
-Written as above, we can see that the spare dual variables can be interpreted as a sparse MVN representation.
-We now show how we use this for a regularizer in continual learning with more details in [appendix].
-
 % Where the regularizer comes from
@@
 \subsection{Updating the  network representation for Continual learning}
-The Continual learning setting is a challenging and the training and
+% the problem is hard many hyperparams and also a lot of things can make huge differences
+% we restrict ourselves to the SH setting, then some values
 
@@
 \subsection{Reinforcement learning}
-We now demonstrate the quaility of \our's uncertainty estimates by showing that it can improve sample efficiency in RL when used in conjuction with an
-uncertainty-guided exploration strategy.
-Balancing the trade-off between exploration and exploitation is a key challenge in RL \cite{sutton2018reinforcement}.
-Should an agent select actions that it knows will lead to high reward (exploitation), or actions which it has not select before in the
-hope to discover new high reward actions (exploration)?
-
-Prior work has used GP dynamic models \cite{deisenrothPILCO2011,kamtheDataEfficient2018}, ensembles of neural
-networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
-variational inference \cite{galImproving2016,houthooftVIME2017}
-
-% In this section, we show that \our's uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim,
-% demonstrating the quality of our uncertainty estimates.
-
-% A key challenge in RL is balancing the trade-off between exploration and exploitation.
-% That is, should an agent select actions that it knows will lead to a high reward (exploitation), or should it
-% hope to discover new actions which lead to high reward (exploration)?
-% In this section, we show that \our's uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim,
-% demonstrating the quality of our uncertainty estimates.
+A key challenge in RL is balancing the trade-off between exploration and exploitation.
+That is, should an agent select actions that it knows will lead to a high reward (exploitation), or should it
+hope to discover new actions which lead to high reward (exploration)?
+In this section, we show that \our's uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim,
+demonstrating the quality of our uncertainty estimates.
 % In this section, we demonstrate  that our method's principled uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim.
-We refer the reader to \cref{app:rl} for an overview of the reinforcement learning problem and more details of our experiments.
-
-% It is an inherently unstable and underactuated mechanical system.
-
-by using it to learn a dynamics model and
-evaluate the
-We test \our by using it to learn a dynamics model
-our method on the cart pole swing up task in MuJoCo \cite{todorov2012mujoco}, a classic benchmark for nonlinear control, see \cref{fig:rl}.
-The goal is to swing the pole up and balance it around the upward position.
-We increase the  difficulty of exploration in this environment by using a sparse reward function.
-
-We compare our method to a Laplace-GGN with GLM predictions (red), an ensemble of neural networks (green) and a basic MLP wih no uncertainty (magenta).
-To ensure a fair comparison, we use the same MLP architecture/training scheme and use them in the same model-based RL algorithm, detailed in \cref{app:rl}.
-% See \cref{app:rl} for more details of our experiments.
-We also compare to deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016}, a model-free RL algorithim (yellow).
-% As expected DDPG is the least sample inefficient
-The training curves in \cref{fig:rl} show that \our's uncertainty estimates are good for exploration as it converges in fewer episodes.
-
-% We compare our method with deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016} -- a model-free RL baseline --
-% which is sample inefficient.
+We refer the reader to \cref{app:rl} for an overview of the problem and details of our experiments.
+
+Cart pole swing up task in MuJoCo \cite{todorov2012mujoco}
+We compare our method with deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016} -- a model-free RL baseline --
+which is sample inefficient.
+We test our model's uncertainty estimates by comparing it to using Laplace-GGN with GLM predictions, using an ensemble of neural networks
+(with different initialisations),
+To ensure a fair comparison, we use the same MLP architecture/training scheme and we keep the same model-based RL algorithm.
+See \cref{app:rl} for more details of our experiments.
+
+We also compare to deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016} -- a model-free RL baseline --
+which we expect to be much more sample inefficient.
+
+\cref{fig:rl} shows training curves
 

### 2023-05-15 paper/main.tex

--- 2023-05-15 paper/main.tex
@@
 In the Continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{n_t}$, which after the task is discarded and cannot be accessed in the following stages of the training.
-Rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting.
+Rehearsal and function regularization-based models keep a subset of the trai ning data for each task to help the model alleviate forgetting.
 In the same way, after each task, we can use our \our to build a compact representation of the neural network and then exploit this representation to build a functional regularizer to add to the training loss for the subsequent tasks.
@@
 %, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer. 
-A more principled approach would be to sparsify the resultant GP into a low-rank approximation to ensure information coming from the entire task dataset is not lost.%, essentially what the sparse dual variables do.
+A more principled approach would be to sparsify the resultant GP into a low-rank approximation to ensure information coming from the entire task dataset is not lost.
+%, essentially what the sparse dual variables do.
 \todo{this term is replacing the missing data}

### 2023-05-15 paper/main.tex
Sec. 2 end

--- 2023-05-15 paper/main.tex
@@
 \textbf{Linearization gives rise to a Gaussian process}
-We are concerned with capturing the distribution over the neural network model functions, in terms of the first two moments of the distribution.
-A Gaussian process is fully characterized by these moments: a mean function $\mu(\cdot)$ and a covariance (kernel) function $\kappa(\cdot,\cdot)$.
+Our goal is to capture the distribution over the neural network model functions through their first two moments.
+The first moments characterize a Gaussian process with a mean function $\mu(\cdot)$ and a covariance function (kernel) $\kappa(\cdot,\cdot)$.
 Recent work \cite{khan2019approximate,maddox2021fast} has shown that linearizing approximations in the weight space lead to function-space equivalent approximations.
-As Gaussian distributions remain tractable under linear transformations, a linear function in terms of parameters can be converted from the weight space to the function space (see Ch.~2.1 in \cite{rasmussen2006gaussian}) as follows:\begin{equation} \label{eq:weight_func}
+As Gaussian distributions remain tractable under linear transformations, a linear function in terms of parameters can be converted from the weight space to the function space (see Ch.~2.1 in \cite{rasmussen2006gaussian}) as follows:
+%
+\begin{equation} \label{eq:weight_func}
 f_\weights(\vx) \approx 
 %g_\weights(\mathbf{x}) = 
-\phi^\top\!(\vx) \, \vw \implies \mu(\vx) = 0 \quad \kappa(\vx, \vx') = \frac{1}{\delta} \phi^\T\!(\vx) \, \phi(\vx')
+\phi^\top\!(\vx) \, \vw \quad\implies\quad \mu(\vx) = 0 \quad \text{and} \quad \kappa(\vx, \vx') = \frac{1}{\delta} \phi^\T\!(\vx) \, \phi(\vx').
 \end{equation}
 % The posterior structure directly relates to the optimization loss around the MAP weights $\vw^*$.
-A common approach is to approximate the correlation structure of a distribution centred at the MAP estimate as done in the Laplace-GGN \citep{khan2019approximate, daxberger2021laplace, maddox2021fast}.
+A common approach is to approximate the correlation structure of a distribution centred at the MAP estimate as done in the Laplace-GGN~\cite{khan2019approximate, daxberger2021laplace, maddox2021fast}.
 The Laplace-GGN takes the MAP solution and approximates the Hessian of the loss function
-% $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i)$
 with the GGN.
-Following the work of \citep{khan2019approximate}, we can view this approximation as building an approximate linear model of the neural network as $f_{\weights^*}(\vx) \approx 
+Following the work of \citet{khan2019approximate}, we can view this approximation as building an approximate linear model of the neural network as $f_{\weights^*}(\vx) \approx 
 %g_{\weights}(\vx) = 
@@
 Using the Hessian of the approximate model, we arrive at the Laplace-GGN approximate posterior for $q(\vw)$. 
-\todo{do we need this sentence about the Hessian to get Laplace-GGN??}
 Therefore, the Laplace-GGN linear model can be used to convert our weight space model to the function space by,
@@
 where the kernel is the so-called Neural Tangent Kernel (NTK, \cite{jacot2018neural}).
-In \cref{eq-laplace-approx-function-space}, for notational convenience, we restricted the function output to single dimension, but this could be easily extended for the multi-dimensional case.
-With this kernel function, we can then combine it with the dataset $\dataset$ to form the posterior $q(\vf)$.
-\citet{khan2019approximate} took a similar approach, but instead of fitting the GP posterior to the actual $\vy$, they rely on a transformation of $\vy$ referred as pseudo-data.
-Similarly, \citet{immer2021improving} obtain the same covariance function but a different mean because they rely on a first order approximation of the neural network to form a Bayesian GLM model.
+In \cref{eq-laplace-approx-function-space}, we restrict the function output to a single dimension for notational simplicity, yet this formulation can be readily extended to the multi-output scenario.
+With this kernel function, we can combine it with the data set $\dataset$ to construct the posterior $q(\vf)$.
+%
+\citet{khan2019approximate} took a similar approach, but instead of fitting the GP posterior to the actual $\vy$, they rely on a transformation of $\vy$ referred as {\em pseudo}-data.
+Similarly, \citet{immer2021improving} obtain the same covariance function but use a different mean because they rely on a first-order approximation of the neural network to form a Bayesian GLM model.
 Both approaches attempted to adjust the GP posterior mean function to ensure the predictions are from the neural network $f_{\vw^*}(\vx)$.
-In our method, we wish to make predictions from the derived GP and thus we avoid such adjustments.
-We now present the general formulation of the sparse functional representation of our trained neural network based on the non-sparse approximation.
+Contrarily, our methodology intends to make predictions directly from the derived GP, thus evading such adjustments.
+Next, we will present the general formulation of the sparse functional representation of our trained neural network based on the non-sparse approximation.
 
@@
 \end{equation}
-where $\MKzz$ and $\vkzs$ are defined similarly to $\MKxx$ and $\vk_{\vx i}$ but over the inducing points $\MZ \in \R^{M \times D} $  instead of the full dataset $\dataset$.
+where $\MKzz$ and $\vkzs$ are defined similarly to $\MKxx$ and $\vk_{\vx i}$ but over the inducing points $\MZ \in \R^{M \times D} $  instead of the full data set $\dataset$.
 The key quantities we need to make predictions from our sparse GP from the converged neural network are $(\hat{\alpha}_i, \hat{\beta}_i)$ \cref{eq:dual_param_laplac}\todo{these variables need another subscript for differentiate that from the values computed at the data points} and a kernel function $\kappa$ .
@@
  \hfill
- \caption{\textbf{Reinforcement learning experiments} Training curves showing that \our's uncertainty estimates improve sample efficiency in RL.
-   Our method (blue/green) converges in fewer environment steps than the baseline model-based RL method (magenta) and (DDPG) the model-free baseline  (yellow).}
+ \caption{\textbf{Reinforcement learning experiments} Training curves showing that our model's uncertainty estimates improve sample efficiency in RL.
+   Our method (blue/green) converges to the optimal solution in fewer environment steps than the baseline model-based RL method (magenta) and (DDPG) the model-free baseline  (yellow).}
  \label{fig:rl}
@@
 train the model.
+See \cref{sec-rl-appendix} for more details of how we use
 

### 2023-05-15 paper/main.tex
Minor
Sec. 3

@@
 %
-{\em (i)}~We introduce \our, a new approach for sparse representation of the neural network in the function space.
+{\em (i)}~We introduce \our, a new approach for sparse functional representation of the neural network.
 {\em (ii)}~We demonstrate that, despite its sparsity, our method effectively captures predictive uncertainty, provides means of updating the model post-training, and gives a a compact representation suitable for continual learning.
@@
 
-\section{\our: Sparse Function-space Represenation of neural networks}
-\paragraph{GP in the dual parameters}
-As stated in \citet[Parameterization Lemma~1]{csato2002sparse}, the mean and covariance functions of the posterior process $f_{\textrm{post}}$, found through the Bayesian update using the GP prior and the likelihood function, can be parameterized by the dual parameters, $\valpha$ and $\vbeta$,
+\section{\our: Sparse function-space represenation of neural networks}
+%\paragraph{GP in the dual parameters}
+The early work by \citet{csato2002sparse} (Parameterization Lemma~1) states that the mean and covariance functions of the posterior process $f_{\textrm{post}}$, found through the Bayesian update using the GP prior and the likelihood function, can be parameterized by `dual' parameters, $\valpha$ and $\vbeta$,
+%
 \begin{equation}  \label{eq:gp_pred}
   \myexpect_{p(f_i \mid\vy)}[f_i]= \vk_{\vx i}^\top \valpha \quad \text{and} \quad
-  \mathrm{Var}_{p(f_i \mid \vy)}[f_i] = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
+  \mathrm{Var}_{p(f_i \mid \vy)}[f_i] = k_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
 \end{equation}
-where the $ij$th entry of the matrix $\MKxx \in \R^{n \times n}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$th element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
+%
+where the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{n \times n}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $k_{ii} = \kappa(\vx_i, \vx_i)$.
 The dual parameters are the vector $\valpha \in \R^{m}$ and vector $\vbeta \in \R^{m}$, defined as:

### 2023-05-15 paper/main.tex
updated cl

--- 2023-05-15 paper/main.tex
@@
 At the end of the training for each task $t$, we compute the Laplace-GGN approximated kernel function for the current model and randomly select $m$ inducing points.
-Given the issues described in the previous sections, related to computing the full covariance posterior $\MKxx$,\todo{this should be $\kappa(\MX_t, \MX_t)$}, we can exploit the dual parameterization to efficiently encode the information from the $\dataset_t$ using the dual parameterization, as follows,
+Given the issues described in the previous sections, related to computing the full covariance posterior $\MKxx$ for $\dataset_t$,\todo{this should be $\kappa(\MX_t, \MX_t)$} we can exploit the dual parameterization to efficiently encode the information from  $\dataset_t$ using the dual parameterization, as follows,
 \begin{equation}
@@
  \end{equation}
- where $\MKzz$ and $\vkzi$ are the kernel function computed on the inducing points $\MZ_t \in \R^{m \times D}$ for task $t$.
-
-We can then keep a memory buffer $\mathcal{M} = \{(\MZ_t, \vu_t, \bar{\MB}^{-1}_t)\}_{t=1}^T$, where $\MZ_t$ are the inducing points selected from $\dataset_t$ and  $\vu_t = f_{\vw_t^*}(\MZ_t)\in \R^{m}$ are the neural network outputs over them computed with the MAP estimate after task $t$, $\vw_t^*$.
-Note that, for notational convenience, we are extending our neural network notation to be compatible with multiple inputs points, \ie, each $i$th entry is $f_{\vw_t^*}(\vz_i)\in \R$.
+ where $\MKzz$ and $\vkzi$ are the kernel function computed on the inducing points $\MZ_t \in \R^{m \times D}$ for task $t$ .
+
+We keep a memory buffer $\mathcal{M} = \{(\MZ_t, \vu_t, \bar{\MB}^{-1}_t)\}_{t=1}^T$, where $\MZ_t$ are the inducing points selected from $\dataset_t$ and  $\vu_t = f_{\vw_t^*}(\MZ_t)\in \R^{m}$ are the neural network outputs associated to them, computed with the MAP estimate after task $t$ $\weights_t^*$.
+Note that, for notational convenience, we are extending our neural network notation to be compatible with multiple inputs points, \ie, each $i$th entry is $f_{\weights_t^*}(\vz_i)\in \R$.
 Moreover, we restrict ourselves to single-output neural networks and refer the reader to further details on the multi-output setting to \cref{sec:cl_multioutput}.
@@
 \begin{equation}
-	\mathcal{R}_\textit{SFR}(\weights, \mathcal{M}) = \sum_{s=1}^{t-1} \frac{1}{m} 
+	\mathcal{R}_\textit{SFR}(\weights, \mathcal{M}) = \frac{1}{2} \sum_{s=1}^{t-1} \frac{1}{m} 
 	\left\lVert 

### 2023-05-15 paper/main.tex
fixed typos

@@
 %
-However, the GP's cubic $\mathcal{O}(N^3)$ scaling with data points $N$ requires costly approximations, often resorting to using data subsets \cite{immer2021scalable}.
+However, the GP's cubic $\mathcal{O}(n^3)$ scaling with data points $n$ requires costly approximations, often resorting to using data subsets \cite{immer2021scalable}.
 In the GP community, sparse approximations have mitigated this scaling issue (\eg, \cite{titsias2009variational,hensman2013gaussian}), but combining neural network linearization with sparse methods remains unclear without resorting to subset methods.
@@
 \textbf{Function-space methods for sequential learning} 
-Continual learning (CL) hinges on how to deal with the non-stationary training distribution, wherein the training process may overwrite previously learned parameters, causing catastrophic forgetting.
+Continual learning (CL) hinges on how to deal with the non-stationary training distribution, wherein the training process may overwrite previously learned parameters, causing catastrophic forgetting \citep{mccloskey1989catastrophic}.
 CL approaches fall into inference-based, rehearsal-based, and model-based methods (see \cite{parisi2019continual, de2021continual} for an overview).
@@
 These methods bridge the gap between objective and rehearsal-based methods since they use a subset of the training data for each task to compute the regularization term.
-Recently proposed methods, \eg DER~\citep{buzzega2020dark}, FROMP~\citep{pan2020continual}, and S-FSVI~\citep{rudner2022continual} achieve state-of-the-art performance among the objective-based techniques in several CL benchmarks.
+Recently proposed methods, \eg, DER~\citep{buzzega2020dark}, FROMP~\citep{pan2020continual}, and S-FSVI~\citep{rudner2022continual} achieve state-of-the-art performance among the objective-based techniques in several CL benchmarks.
 
@@
 \subsection{Updating the  network representation for Continual learning}
+%% Very rough draft
+
 % the problem is hard many hyperparams and also a lot of things can make huge differences

### 2023-05-15 paper/main.tex
added rl to related work

--- 2023-05-15 paper/main.tex
@@
 %
-{\em (i)}~We introduce \our, a new approach for sparse functional representation of the neural network.
+{\em (i)}~We introduce \our, a new approach for sparse representation of the neural network in the function space.
 {\em (ii)}~We demonstrate that, despite its sparsity, our method effectively captures predictive uncertainty, provides means of updating the model post-training, and gives a a compact representation suitable for continual learning.
@@
 
+\textbf{Uncertainty quantification in RL}
+A key challenge in RL is balancing the trade-off between exploration and exploitation \cite{sutton2018reinforcement}.
+That is, should an agent select actions that it knows will lead to high reward (exploitation), or should it
+select new ones in hope to discover actions leading to higher reward (exploration).
+One promising direction to balancing this trade-off is to model the uncertainty associated with a learned transition dynamics model and use it to guide exploration.
+Prior work has taken an expectation over the dynamic model's posterior \cite{deisenrothPILCO2011,kamtheDataEfficient2018,chuaDeepReinforcementLearning2018},
+sampled from it (akin to Thompson sampling but referred to as posterior sampling RL)
+\todo{cite thopmson sampling paper dearden et al 1999}
+\cite{osbandMoreEfficientReinforcement2013},
+and used it to implement optimism in the face of uncertainty using upper confidence bounds \cite{curiEfficient2020}.
+\todo{cite UCRL paper}
+No single strategy has emerged as a go to method and we highlight that these strategies are only as good as their uncertainty estimates.
+% Central to these decision-making strategies are the methods for quantifying uncertainty.
+Previous approaches have used GPs \cite{deisenrothPILCO2011,kamtheDataEfficient2018},
+ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
+and variational inference \cite{galImproving2016,houthooftVIME2017}.
+However, there has been little leveraging
+
+% Another classical and provable exploration theory in RL is based on optimism
+% \todo{cite UCRL paper}
+% Recent work has even extended these ideas to deep RL \cite{curiEfficient2020}.
+
+% An alternative approach is to sample from the dynamic model's posterior, akin to Thompson sampling but referred to as posterior sampling RL
+% Another classical and provable exploration theory in RL is based on optimism in the face of uncertainty.
+% \todo{cite UCRL paper}
+% Recent work has even extended these ideas to deep RL \cite{curiEfficient2020}.
+% These strategies are only as good as their uncertainty estimates.
+% Prior work has learned dynamics models using GPs \cite{deisenrothPILCO2011,kamtheDataEfficient2018},
+% ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
+% and variational inference \cite{galImproving2016,houthooftVIME2017}.
+
 %%
@@
 \textbf{Linearization gives rise to a Gaussian process}
-Our goal is to capture the distribution over the neural network model functions through their first two moments.
-The first moments characterize a Gaussian process with a mean function $\mu(\cdot)$ and a covariance function (kernel) $\kappa(\cdot,\cdot)$.
+We are concerned with capturing the distribution over the neural network model functions, in terms of the first two moments of the distribution.
+A Gaussian process is fully characterized by these moments: a mean function $\mu(\cdot)$ and a covariance (kernel) function $\kappa(\cdot,\cdot)$.
 Recent work \cite{khan2019approximate,maddox2021fast} has shown that linearizing approximations in the weight space lead to function-space equivalent approximations.
-As Gaussian distributions remain tractable under linear transformations, a linear function in terms of parameters can be converted from the weight space to the function space (see Ch.~2.1 in \cite{rasmussen2006gaussian}) as follows:
-%
-\begin{equation} \label{eq:weight_func}
+As Gaussian distributions remain tractable under linear transformations, a linear function in terms of parameters can be converted from the weight space to the function space (see Ch.~2.1 in \cite{rasmussen2006gaussian}) as follows:\begin{equation} \label{eq:weight_func}
 f_\weights(\vx) \approx 
 %g_\weights(\mathbf{x}) = 
-\phi^\top\!(\vx) \, \vw \quad\implies\quad \mu(\vx) = 0 \quad \text{and} \quad \kappa(\vx, \vx') = \frac{1}{\delta} \phi^\T\!(\vx) \, \phi(\vx').
+\phi^\top\!(\vx) \, \vw \implies \mu(\vx) = 0 \quad \kappa(\vx, \vx') = \frac{1}{\delta} \phi^\T\!(\vx) \, \phi(\vx')
 \end{equation}
 % The posterior structure directly relates to the optimization loss around the MAP weights $\vw^*$.
-A common approach is to approximate the correlation structure of a distribution centred at the MAP estimate as done in the Laplace-GGN~\cite{khan2019approximate, daxberger2021laplace, maddox2021fast}.
+A common approach is to approximate the correlation structure of a distribution centred at the MAP estimate as done in the Laplace-GGN \citep{khan2019approximate, daxberger2021laplace, maddox2021fast}.
 The Laplace-GGN takes the MAP solution and approximates the Hessian of the loss function
+% $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i)$
 with the GGN.
-Following the work of \citet{khan2019approximate}, we can view this approximation as building an approximate linear model of the neural network as $f_{\weights^*}(\vx) \approx 
+Following the work of \citep{khan2019approximate}, we can view this approximation as building an approximate linear model of the neural network as $f_{\weights^*}(\vx) \approx 
 %g_{\weights}(\vx) = 
@@
 Using the Hessian of the approximate model, we arrive at the Laplace-GGN approximate posterior for $q(\vw)$.
+\todo{do we need this sentence about the Hessian to get Laplace-GGN??}
 Therefore, the Laplace-GGN linear model can be used to convert our weight space model to the function space by,
@@
 where the kernel is the so-called Neural Tangent Kernel (NTK, \cite{jacot2018neural}).
-In \cref{eq-laplace-approx-function-space}, we restrict the function output to a single dimension for notational simplicity, yet this formulation can be readily extended to the multi-output scenario.
-With this kernel function, we can combine it with the data set $\dataset$ to construct the posterior $q(\vf)$.
-%
-\citet{khan2019approximate} took a similar approach, but instead of fitting the GP posterior to the actual $\vy$, they rely on a transformation of $\vy$ referred as {\em pseudo}-data.
-Similarly, \citet{immer2021improving} obtain the same covariance function but use a different mean because they rely on a first-order approximation of the neural network to form a Bayesian GLM model.
+In \cref{eq-laplace-approx-function-space}, for notational convenience, we restricted the function output to single dimension, but this could be easily extended for the multi-dimensional case.
+With this kernel function, we can then combine it with the dataset $\dataset$ to form the posterior $q(\vf)$.
+\citet{khan2019approximate} took a similar approach, but instead of fitting the GP posterior to the actual $\vy$, they rely on a transformation of $\vy$ referred as pseudo-data.
+Similarly, \citet{immer2021improving} obtain the same covariance function but a different mean because they rely on a first order approximation of the neural network to form a Bayesian GLM model.
 Both approaches attempted to adjust the GP posterior mean function to ensure the predictions are from the neural network $f_{\vw^*}(\vx)$.
-Contrarily, our methodology intends to make predictions directly from the derived GP, thus evading such adjustments.
-Next, we will present the general formulation of the sparse functional representation of our trained neural network based on the non-sparse approximation.
+In our method, we wish to make predictions from the derived GP and thus we avoid such adjustments.
+We now present the general formulation of the sparse functional representation of our trained neural network based on the non-sparse approximation.
 
@@
 \end{equation}
-where $\MKzz$ and $\vkzs$ are defined similarly to $\MKxx$ and $\vk_{\vx i}$ but over the inducing points $\MZ \in \R^{M \times D} $  instead of the full data set $\dataset$.
+where $\MKzz$ and $\vkzs$ are defined similarly to $\MKxx$ and $\vk_{\vx i}$ but over the inducing points $\MZ \in \R^{M \times D} $  instead of the full dataset $\dataset$.
 The key quantities we need to make predictions from our sparse GP from the converged neural network are $(\hat{\alpha}_i, \hat{\beta}_i)$ \cref{eq:dual_param_laplac}\todo{these variables need another subscript for differentiate that from the values computed at the data points} and a kernel function $\kappa$ .
@@
 In the Continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{n_t}$, which after the task is discarded and cannot be accessed in the following stages of the training.
-Rehearsal and function regularization-based models keep a subset of the trai ning data for each task to help the model alleviate forgetting.
+Rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting.
 In the same way, after each task, we can use our \our to build a compact representation of the neural network and then exploit this representation to build a functional regularizer to add to the training loss for the subsequent tasks.
@@
 %, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer. 
-A more principled approach would be to sparsify the resultant GP into a low-rank approximation to ensure information coming from the entire task dataset is not lost.
-%, essentially what the sparse dual variables do.
+A more principled approach would be to sparsify the resultant GP into a low-rank approximation to ensure information coming from the entire task dataset is not lost.%, essentially what the sparse dual variables do.
 \todo{this term is replacing the missing data}
@@
 At the end of the training for each task $t$, we compute the Laplace-GGN approximated kernel function for the current model and randomly select $m$ inducing points.
-Given the issues described in the previous sections, related to computing the full covariance posterior $\MKxx$ for $\dataset_t$,\todo{this should be $\kappa(\MX_t, \MX_t)$} we can exploit the dual parameterization to efficiently encode the information from  $\dataset_t$ using the dual parameterization, as follows,
+Given the issues described in the previous sections, related to computing the full covariance posterior $\MKxx$,\todo{this should be $\kappa(\MX_t, \MX_t)$}, we can exploit the dual parameterization to efficiently encode the information from the $\dataset_t$ using the dual parameterization, as follows,
 \begin{equation}
@@
  \end{equation}
- where $\MKzz$ and $\vkzi$ are the kernel function computed on the inducing points $\MZ_t \in \R^{m \times D}$ for task $t$ .
-
-We keep a memory buffer $\mathcal{M} = \{(\MZ_t, \vu_t, \bar{\MB}^{-1}_t)\}_{t=1}^T$, where $\MZ_t$ are the inducing points selected from $\dataset_t$ and  $\vu_t = f_{\vw_t^*}(\MZ_t)\in \R^{m}$ are the neural network outputs associated to them, computed with the MAP estimate after task $t$ $\weights_t^*$.
-Note that, for notational convenience, we are extending our neural network notation to be compatible with multiple inputs points, \ie, each $i$th entry is $f_{\weights_t^*}(\vz_i)\in \R$.
+ where $\MKzz$ and $\vkzi$ are the kernel function computed on the inducing points $\MZ_t \in \R^{m \times D}$ for task $t$.
+
+We can then keep a memory buffer $\mathcal{M} = \{(\MZ_t, \vu_t, \bar{\MB}^{-1}_t)\}_{t=1}^T$, where $\MZ_t$ are the inducing points selected from $\dataset_t$ and  $\vu_t = f_{\vw_t^*}(\MZ_t)\in \R^{m}$ are the neural network outputs over them computed with the MAP estimate after task $t$, $\vw_t^*$.
+Note that, for notational convenience, we are extending our neural network notation to be compatible with multiple inputs points, \ie, each $i$th entry is $f_{\vw_t^*}(\vz_i)\in \R$.
 Moreover, we restrict ourselves to single-output neural networks and refer the reader to further details on the multi-output setting to \cref{sec:cl_multioutput}.
@@
 \begin{equation}
-	\mathcal{R}_\textit{SFR}(\weights, \mathcal{M}) = \frac{1}{2} \sum_{s=1}^{t-1} \frac{1}{m} 
+	\mathcal{R}_\textit{SFR}(\weights, \mathcal{M}) = \sum_{s=1}^{t-1} \frac{1}{m} 
 	\left\lVert 
@@
 \subsection{Updating the  network representation for Continual learning}
-% the problem is hard many hyperparams and also a lot of things can make huge differences
-% we restrict ourselves to the SH setting, then some values
+The Continual learning setting is a challenging and the training and
 

### 2023-05-15 paper/main.tex
updated rl section

@@
 \subsection{Reinforcement learning}
-We now demonstrate the quaility of \our's uncertainty estimates by showing that it can improve sample efficiency in RL when used in conjuction with an
-uncertainty-guided exploration strategy.
-Balancing the trade-off between exploration and exploitation is a key challenge in RL \cite{sutton2018reinforcement}.
-Should an agent select actions that it knows will lead to high reward (exploitation), or actions which it has not select before in the
-hope to discover new high reward actions (exploration)?
-
-Prior work has used GP dynamic models \cite{deisenrothPILCO2011,kamtheDataEfficient2018}, ensembles of neural
-networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
-variational inference \cite{galImproving2016,houthooftVIME2017}
+% We now demonstrate the quaility of \our's uncertainty estimates by showing that it can improve sample efficiency in RL.
+% Balancing the trade-off between exploration and exploitation is a key challenge in RL \cite{sutton2018reinforcement}.
+% Should an agent select actions that it knows will lead to high reward (exploitation), or actions which it has not select before in the
+% hope to discover new high reward actions (exploration)?
+
+% when used in conjuction with an
+% uncertainty-guided exploration strategy.
 
@@
 
-% A key challenge in RL is balancing the trade-off between exploration and exploitation.
-% That is, should an agent select actions that it knows will lead to a high reward (exploitation), or should it
-% hope to discover new actions which lead to high reward (exploration)?
-% In this section, we show that \our's uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim,
-% demonstrating the quality of our uncertainty estimates.
-% In this section, we demonstrate  that our method's principled uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim.
+A key challenge in RL is balancing the trade-off between exploration and exploitation.
+That is, should an agent select actions that it knows will lead to high reward (exploitation), or should it
+select new ones in hope to discover actions leading to higher reward (exploration).
+One promising direction is to model the uncertainty associated with a learned transition dynamics and use it to guide exploration.
+Prior work has learned dynamics models using GPs \cite{deisenrothPILCO2011,kamtheDataEfficient2018},
+ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
+and variational inference \cite{galImproving2016,houthooftVIME2017}.
+There are then many ways to leverage uncertainty in model-based RL, for example,
+taking an expectation over epistemic uncertainty  \cite{deisenrothPILCO2011,kamtheDataEfficient2018,chuaDeepReinforcementLearning2018},
+sampling from the posterior, akin to Thompson sampling but referred to as posterior sampling RL
+\cite{osbandMoreEfficientReinforcement2013},
+and methods based on upper confidence bounds (UCB) \cite{curiEfficient2020}.
+
+% Uncertainty-guided decision making strategies
 We refer the reader to \cref{app:rl} for an overview of the reinforcement learning problem and more details of our experiments.
 
-% It is an inherently unstable and underactuated mechanical system.
-
-by using it to learn a dynamics model and
-evaluate the
 We test \our by using it to learn a dynamics model
@@
 
-We compare our method to a Laplace-GGN with GLM predictions (red), an ensemble of neural networks (green) and a basic MLP wih no uncertainty (magenta).
+We compare \our (cyan) to a Laplace-GGN with GLM predictions (red), an ensemble of neural networks (green) and a basic MLP wih no uncertainty (magenta).
 To ensure a fair comparison, we use the same MLP architecture/training scheme and use them in the same model-based RL algorithm, detailed in \cref{app:rl}.
@@
 % As expected DDPG is the least sample inefficient
-The training curves in \cref{fig:rl} show that \our's uncertainty estimates are good for exploration as it converges in fewer episodes.
+The training curves in \cref{fig:rl} show that \our's uncertainty estimates are useful for guiding exploration as it converges in fewer episodes.
+
+% \cite{deisenrothPILCO2011},
+% Posterior sampling
+
+% based on
+
+% Model-based RL algorithims are more sample efficient than their model-free counterparts as they learn a model of the transition dynamics and
+% use it to augment the RL loop.
+
+% Prior work has used show that modelling uncertainty in the transition dynamics can further improve exploration and thus sample efficiency.
+% For example, with GPs \cite{deisenrothPILCO2011,kamtheDataEfficient2018},
+% ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
+% and variational inference \cite{galImproving2016,houthooftVIME2017}
+
+% We now demonstrate the quaility of \our's uncertainty estimates by showing that it can improve sample efficiency in RL.
+
+% In this section, we show that \our's uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim,
+% demonstrating the quality of our uncertainty estimates.
+% In this section, we demonstrate  that our method's principled uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim.
+
+% It is an inherently unstable and underactuated mechanical system.
+
+% by using it to learn a dynamics model and
+% evaluate the
+% We test \our by using it to learn a dynamics model
+% our method on the cart pole swing up task in MuJoCo \cite{todorov2012mujoco}, a classic benchmark for nonlinear control, see \cref{fig:rl}.
+% The goal is to swing the pole up and balance it around the upward position.
+% We increase the  difficulty of exploration in this environment by using a sparse reward function.
+
+% We compare our method to a Laplace-GGN with GLM predictions (red), an ensemble of neural networks (green) and a basic MLP wih no uncertainty (magenta).
+% To ensure a fair comparison, we use the same MLP architecture/training scheme and use them in the same model-based RL algorithm, detailed in \cref{app:rl}.
+% % See \cref{app:rl} for more details of our experiments.
+% We also compare to deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016}, a model-free RL algorithim (yellow).
+% % As expected DDPG is the least sample inefficient
+% The training curves in \cref{fig:rl} show that \our's uncertainty estimates are good for exploration as it converges in fewer episodes.
 

### 2023-05-15 paper/main.tex
updated rl fig caption

@@
  \hfill
- \caption{\textbf{Reinforcement learning experiments} Training curves showing that \our's uncertainty estimates improve sample efficiency in RL.
-   Our method (blue/green) converges in fewer environment steps than the baseline model-based RL method (magenta) and (DDPG) the model-free baseline  (yellow).}
+ \caption{\textbf{Cartpole swingup with sparse reward} Training curves showing that \our's uncertainty estimates improve sample efficiency in RL.
+   Our method (blue/green) converges in fewer environment steps than the baseline model-based RL method (magenta) and DDPG, the model-free baseline (yellow).}
  \label{fig:rl}

### 2023-05-15 paper/main.tex

@@
 where the kernel is the so-called Neural Tangent Kernel (NTK, \cite{jacot2018neural}).
-In \cref{eq-laplace-approx-function-space}, for notational convenience, we restricted the function output to single dimension, but this could be easily extended for the multi-dimensional case.
-With this kernel function, we can then combine it with the dataset $\dataset$ to form the posterior $q(\vf)$.
-\citet{khan2019approximate} took a similar approach, but instead of fitting the GP posterior to the actual $\vy$, they rely on a transformation of $\vy$ referred as pseudo-data.
-Similarly, \citet{immer2021improving} obtain the same covariance function but a different mean because they rely on a first order approximation of the neural network to form a Bayesian GLM model.
+In \cref{eq-laplace-approx-function-space}, we restrict the function output to a single dimension for notational simplicity, yet this formulation can be readily extended to the multi-output scenario.
+With this kernel function, we can combine it with the data set $\dataset$ to construct the posterior $q(\vf)$.
+%
+\citet{khan2019approximate} took a similar approach, but instead of fitting the GP posterior to the actual $\vy$, they rely on a transformation of $\vy$ referred as {\em pseudo}-data.
+Similarly, \citet{immer2021improving} obtain the same covariance function but use a different mean because they rely on a first-order approximation of the neural network to form a Bayesian GLM model.
 Both approaches attempted to adjust the GP posterior mean function to ensure the predictions are from the neural network $f_{\vw^*}(\vx)$.
-In our method, we wish to make predictions from the derived GP and thus we avoid such adjustments.
-We now present the general formulation of the sparse functional representation of our trained neural network based on the non-sparse approximation.
-
-\section{\our: Sparse Function-space Represenation of neural networks}
-\paragraph{GP in the dual parameters}
-As stated in \citet[Parameterization Lemma~1]{csato2002sparse}, the mean and covariance functions of the posterior process $f_{\textrm{post}}$, found through the Bayesian update using the GP prior and the likelihood function, can be parameterized by the dual parameters, $\valpha$ and $\vbeta$,
+Contrarily, our methodology intends to make predictions directly from the derived GP, thus evading such adjustments.
+Next, we will present the general formulation of the sparse functional representation of our trained neural network based on the non-sparse approximation.
+
+\section{\our: Sparse function-space represenation of neural networks}
+%\paragraph{GP in the dual parameters}
+The early work by \citet{csato2002sparse} (Parameterization Lemma~1) states that the mean and covariance functions of the posterior process $f_{\textrm{post}}$, found through the Bayesian update using the GP prior and the likelihood function, can be parameterized by `dual' parameters, $\valpha$ and $\vbeta$,
+%
 \begin{equation}  \label{eq:gp_pred}
   \myexpect_{p(f_i \mid\vy)}[f_i]= \vk_{\vx i}^\top \valpha \quad \text{and} \quad
-  \mathrm{Var}_{p(f_i \mid \vy)}[f_i] = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
+  \mathrm{Var}_{p(f_i \mid \vy)}[f_i] = k_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
 \end{equation}
-where the $ij$th entry of the matrix $\MKxx \in \R^{n \times n}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$th element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
+%
+where the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{n \times n}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $k_{ii} = \kappa(\vx_i, \vx_i)$.
 The dual parameters are the vector $\valpha \in \R^{m}$ and vector $\vbeta \in \R^{m}$, defined as:
@@
 \subsection{Updating the  network representation for Continual learning}
-The Continual learning setting is a challenging and the training and
+%% Very rough draft
+
+% the problem is hard many hyperparams and also a lot of things can make huge differences
+% we restrict ourselves to the SH setting, then some values
 

### 2023-05-15 paper/main.tex
Sec. 3

@@
 %
-However, the GP's cubic $\mathcal{O}(n^3)$ scaling with data points $n$ requires costly approximations, often resorting to using data subsets \cite{immer2021scalable}.
+However, the GP's cubic $\mathcal{O}(N^3)$ scaling with data points $N$ requires costly approximations, often resorting to using data subsets \cite{immer2021scalable}.
 In the GP community, sparse approximations have mitigated this scaling issue (\eg, \cite{titsias2009variational,hensman2013gaussian}), but combining neural network linearization with sparse methods remains unclear without resorting to subset methods.
@@
 \textbf{Function-space methods for sequential learning} 
-Continual learning (CL) hinges on how to deal with the non-stationary training distribution, wherein the training process may overwrite previously learned parameters, causing catastrophic forgetting \citep{mccloskey1989catastrophic}.
+Continual learning (CL) hinges on how to deal with the non-stationary training distribution, wherein the training process may overwrite previously learned parameters, causing catastrophic forgetting.
 CL approaches fall into inference-based, rehearsal-based, and model-based methods (see \cite{parisi2019continual, de2021continual} for an overview).
@@
 These methods bridge the gap between objective and rehearsal-based methods since they use a subset of the training data for each task to compute the regularization term.
-Recently proposed methods, \eg, DER~\citep{buzzega2020dark}, FROMP~\citep{pan2020continual}, and S-FSVI~\citep{rudner2022continual} achieve state-of-the-art performance among the objective-based techniques in several CL benchmarks.
-
-\textbf{Uncertainty quantification in RL}
-A key challenge in RL is balancing the trade-off between exploration and exploitation \cite{sutton2018reinforcement}.
-That is, should an agent select actions that it knows will lead to high reward (exploitation), or should it
-select new ones in hope to discover actions leading to higher reward (exploration).
-One promising direction to balancing this trade-off is to model the uncertainty associated with a learned transition dynamics model and use it to guide exploration.
-Prior work has taken an expectation over the dynamic model's posterior \cite{deisenrothPILCO2011,kamtheDataEfficient2018,chuaDeepReinforcementLearning2018},
-sampled from it (akin to Thompson sampling but referred to as posterior sampling RL)
-\todo{cite thopmson sampling paper dearden et al 1999}
-\cite{osbandMoreEfficientReinforcement2013},
-and used it to implement optimism in the face of uncertainty using upper confidence bounds \cite{curiEfficient2020}.
-\todo{cite UCRL paper}
-No single strategy has emerged as a go to method and we highlight that these strategies are only as good as their uncertainty estimates.
-% Central to these decision-making strategies are the methods for quantifying uncertainty.
-Previous approaches have used GPs \cite{deisenrothPILCO2011,kamtheDataEfficient2018},
-ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
-and variational inference \cite{galImproving2016,houthooftVIME2017}.
-However, there has been little leveraging
-
-% Another classical and provable exploration theory in RL is based on optimism
-% \todo{cite UCRL paper}
-% Recent work has even extended these ideas to deep RL \cite{curiEfficient2020}.
-
-% An alternative approach is to sample from the dynamic model's posterior, akin to Thompson sampling but referred to as posterior sampling RL
-% Another classical and provable exploration theory in RL is based on optimism in the face of uncertainty.
-% \todo{cite UCRL paper}
-% Recent work has even extended these ideas to deep RL \cite{curiEfficient2020}.
-% These strategies are only as good as their uncertainty estimates.
-% Prior work has learned dynamics models using GPs \cite{deisenrothPILCO2011,kamtheDataEfficient2018},
-% ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
-% and variational inference \cite{galImproving2016,houthooftVIME2017}.
+Recently proposed methods, \eg DER~\citep{buzzega2020dark}, FROMP~\citep{pan2020continual}, and S-FSVI~\citep{rudner2022continual} achieve state-of-the-art performance among the objective-based techniques in several CL benchmarks.
 
@@
     \node[anchor=north, font=\small] at ($(banana-nn) + (0,-.55\figureheight)$) {Neural network prediction};
-    \node[anchor=north, font=\small] at ($(banana-nn2svgp) + (0,-.55\figureheight)$) {Sparse GP representation};
+    \node[anchor=north, font=\small] at ($(banana-nn2svgp) + (0,-.55\figureheight)$) {Sparse function-space representation};
     \node[anchor=north, font=\small] at ($(banana-hmc) + (0,-.55\figureheight)$) {HMC result as baseline};
@@
 %\paragraph{GP in the dual parameters}
-The early work by \citet{csato2002sparse} (Parameterization Lemma~1) states that the mean and covariance functions of the posterior process $f_{\textrm{post}}$, found through the Bayesian update using the GP prior and the likelihood function, can be parameterized by `dual' parameters, $\valpha$ and $\vbeta$,
+The seminal work by \citet{csato2002sparse} (parameterization Lemma~1) gives a parameterization for the posterior process $f_{\textrm{post}}$ that can be found through the Bayesian update using the GP prior and the likelihood function.
+This gives a `dual' parameterization, $\valpha$ and $\vbeta$,
 %
@@
 %
-where the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{n \times n}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $k_{ii} = \kappa(\vx_i, \vx_i)$.
+where the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{N \times N}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $k_{ii} = \kappa(\vx_i, \vx_i)$.
 The dual parameters are the vector $\valpha \in \R^{m}$ and vector $\vbeta \in \R^{m}$, defined as:
+%
 \begin{equation}
   \label{eq:dual_param}
-\alpha_i \coloneqq \myexpect_{p(\vw \mid \vy)}[\nabla_{f_i}\log p(y_i \mid f_i)],  \quad
+  \alpha_i \coloneqq \myexpect_{p(\vw \mid \vy)}[\nabla_{f_i}\log p(y_i \mid f_i)]
+  \quad \text{and} \quad
   \beta_i \coloneqq - \myexpect_{p(\vw \mid \vy)}[\nabla^2_{f_i f_i}\log p(y_i \mid f_i)] .
@@
 %
-The above relations hold for generic likelihoods, and no approximations are involved as the expectation is under the exact posterior. 
-It also highlights that our approximate inference technique, while usually considered a posterior approximation, can instead be seen as approximating the expectation of gradients of loss/likelihoods.
-\todo{our approximation is late \cref{eq:dual_param_laplace}, saying this here is misleading}\\
-In \citet{csato2002sparse}, they iteratively find dual variables using an Expectation Propogation (EP) method.  
-At the same time, in \cite{adam2021dual, chang2020fast}, they show this relationship for variational Gaussian processes where the above expectation is with respect to the approximate variational posterior.
+The relationships specified above are valid for generic likelihoods, and involve no approximations since the expectation is under the exact posterior.
+This higlights the fact that our approximate inference technique that will follow, while usually viewed as a posterior approximation, can be alternatively interpreted as an approximation of the expectation of gradients of loss/likelihoods.
+
+Originally \citet{csato2002sparse} iteratively find dual variables using an expectation propogation (EP, \cite{minka2001expectation}) method.
+More recently \cite{khan2017conjugate,adam2021dual}, has shown this relationship for variational Gaussian processes where the above expectation is with respect to the approximate variational posterior.
 The dual parameter $\valpha$ appears also in non-Bayesian approaches, \eg, support vector machines \citep{cortes1995support}, whose origins are found in work by \citet{kimeldorf1971some}.
-While in \citet{wilkinson2023bayes}, they show links between linearization methods and how they solve the \cref{eq:dual_param}.\todo{is this last part used/referred somewhere else?}
+While in \citet{wilkinson2023bayes}, they show links between linearization methods and how they solve the \cref{eq:dual_param}.
 
@@
 Given that we use a Laplace approximation of the neural network, we remove the expectation over the posterior (see Ch.~3.4.1 in \cite{rasmussen2006gaussian} for derivation) and we get the the following formulation of the dual variables,
+%
 \begin{equation}
   \label{eq:dual_param_laplace}
-\hat{\alpha}_i \coloneqq \nabla_{f_i}\log p(y_i \mid f_i),  \quad \text{and} \quad
-\hat{\beta}_i \coloneqq - \nabla^2_{f_i f_i}\log p(y_i \mid f_i).
+  \hat{\alpha}_i \coloneqq \nabla_{f}\log p(y_i \mid f) |_{f=f_i}
+  \quad \text{and} \quad
+  \hat{\beta}_i \coloneqq - \nabla^2_{f,f}\log p(y_i \mid f) |_{f=f_i}.
 \end{equation}
-
+%
 Substiuting \cref{eq:dual_param_laplace} into \cref{eq:gp_pred}, we obtain our GP model based on the converged neural network.
 Again, this is similar to what was derived in \citet{immer2021improving} for the posterior variance function.
-However, they use the $f_{\vw^*}$ for the posterior mean and do not spot the significance of the dual variables.
-The problem with \cref{eq:gp_pred} is that to make predictions and compute variances we must incur a cost of $O(n^3)$ which limits the use of the GP on large data sets.
+However, they use the $f_{\vw^*}$ for the posterior mean and do not emphasize the significance of the dual variables.
+The problem with \cref{eq:gp_pred} is that to make predictions and compute variances we must incur a cost of $O(N^3)$ which limits the use of the GP on large data sets.
 
@@
 \subsection{Updating the  network representation for Continual learning}
-%% Very rough draft
-
+%
 % the problem is hard many hyperparams and also a lot of things can make huge differences
@@
 \subsection{Reinforcement learning}
-% We now demonstrate the quaility of \our's uncertainty estimates by showing that it can improve sample efficiency in RL.
-% Balancing the trade-off between exploration and exploitation is a key challenge in RL \cite{sutton2018reinforcement}.
-% Should an agent select actions that it knows will lead to high reward (exploitation), or actions which it has not select before in the
-% hope to discover new high reward actions (exploration)?
-
-% when used in conjuction with an
-% uncertainty-guided exploration strategy.
+We now demonstrate the quaility of \our's uncertainty estimates by showing that it can improve sample efficiency in RL when used in conjuction with an
+uncertainty-guided exploration strategy.
+Balancing the trade-off between exploration and exploitation is a key challenge in RL \cite{sutton2018reinforcement}.
+Should an agent select actions that it knows will lead to high reward (exploitation), or actions which it has not select before in the
+hope to discover new high reward actions (exploration)?
+
+Prior work has used GP dynamic models \cite{deisenrothPILCO2011,kamtheDataEfficient2018}, ensembles of neural
+networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
+variational inference \cite{galImproving2016,houthooftVIME2017}
 
@@
 
-A key challenge in RL is balancing the trade-off between exploration and exploitation.
-That is, should an agent select actions that it knows will lead to high reward (exploitation), or should it
-select new ones in hope to discover actions leading to higher reward (exploration).
-One promising direction is to model the uncertainty associated with a learned transition dynamics and use it to guide exploration.
-Prior work has learned dynamics models using GPs \cite{deisenrothPILCO2011,kamtheDataEfficient2018},
-ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
-and variational inference \cite{galImproving2016,houthooftVIME2017}.
-There are then many ways to leverage uncertainty in model-based RL, for example,
-taking an expectation over epistemic uncertainty  \cite{deisenrothPILCO2011,kamtheDataEfficient2018,chuaDeepReinforcementLearning2018},
-sampling from the posterior, akin to Thompson sampling but referred to as posterior sampling RL
-\cite{osbandMoreEfficientReinforcement2013},
-and methods based on upper confidence bounds (UCB) \cite{curiEfficient2020}.
-
-% Uncertainty-guided decision making strategies
+% A key challenge in RL is balancing the trade-off between exploration and exploitation.
+% That is, should an agent select actions that it knows will lead to a high reward (exploitation), or should it
+% hope to discover new actions which lead to high reward (exploration)?
+% In this section, we show that \our's uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim,
+% demonstrating the quality of our uncertainty estimates.
+% In this section, we demonstrate  that our method's principled uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim.
 We refer the reader to \cref{app:rl} for an overview of the reinforcement learning problem and more details of our experiments.
 
+% It is an inherently unstable and underactuated mechanical system.
+
+by using it to learn a dynamics model and
+evaluate the
 We test \our by using it to learn a dynamics model
@@
 
-We compare \our (cyan) to a Laplace-GGN with GLM predictions (red), an ensemble of neural networks (green) and a basic MLP wih no uncertainty (magenta).
+We compare our method to a Laplace-GGN with GLM predictions (red), an ensemble of neural networks (green) and a basic MLP wih no uncertainty (magenta).
 To ensure a fair comparison, we use the same MLP architecture/training scheme and use them in the same model-based RL algorithm, detailed in \cref{app:rl}.
@@
 % As expected DDPG is the least sample inefficient
-The training curves in \cref{fig:rl} show that \our's uncertainty estimates are useful for guiding exploration as it converges in fewer episodes.
-
-% \cite{deisenrothPILCO2011},
-% Posterior sampling
-
-% based on
-
-% Model-based RL algorithims are more sample efficient than their model-free counterparts as they learn a model of the transition dynamics and
-% use it to augment the RL loop.
-
-% Prior work has used show that modelling uncertainty in the transition dynamics can further improve exploration and thus sample efficiency.
-% For example, with GPs \cite{deisenrothPILCO2011,kamtheDataEfficient2018},
-% ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
-% and variational inference \cite{galImproving2016,houthooftVIME2017}
-
-% We now demonstrate the quaility of \our's uncertainty estimates by showing that it can improve sample efficiency in RL.
-
-% In this section, we show that \our's uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim,
-% demonstrating the quality of our uncertainty estimates.
-% In this section, we demonstrate  that our method's principled uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim.
-
-% It is an inherently unstable and underactuated mechanical system.
-
-% by using it to learn a dynamics model and
-% evaluate the
-% We test \our by using it to learn a dynamics model
-% our method on the cart pole swing up task in MuJoCo \cite{todorov2012mujoco}, a classic benchmark for nonlinear control, see \cref{fig:rl}.
-% The goal is to swing the pole up and balance it around the upward position.
-% We increase the  difficulty of exploration in this environment by using a sparse reward function.
-
-% We compare our method to a Laplace-GGN with GLM predictions (red), an ensemble of neural networks (green) and a basic MLP wih no uncertainty (magenta).
-% To ensure a fair comparison, we use the same MLP architecture/training scheme and use them in the same model-based RL algorithm, detailed in \cref{app:rl}.
-% % See \cref{app:rl} for more details of our experiments.
-% We also compare to deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016}, a model-free RL algorithim (yellow).
-% % As expected DDPG is the least sample inefficient
-% The training curves in \cref{fig:rl} show that \our's uncertainty estimates are good for exploration as it converges in fewer episodes.
+The training curves in \cref{fig:rl} show that \our's uncertainty estimates are good for exploration as it converges in fewer episodes.
 
@@
  \hfill
- \caption{\textbf{Cartpole swingup with sparse reward} Training curves showing that \our's uncertainty estimates improve sample efficiency in RL.
-   Our method (blue/green) converges in fewer environment steps than the baseline model-based RL method (magenta) and DDPG, the model-free baseline (yellow).}
+ \caption{\textbf{Reinforcement learning experiments} Training curves showing that \our's uncertainty estimates improve sample efficiency in RL.
+   Our method (blue/green) converges in fewer environment steps than the baseline model-based RL method (magenta) and (DDPG) the model-free baseline  (yellow).}
  \label{fig:rl}

### 2023-05-15 src/rl/figures.py
added asymptotes and put laplace/ensemble before mlp

@@ -22,13 +22,27 @@ WANDB_RUNS = OmegaConf.create(
             "aalto-ml/nn2svgp/mspoc1tp",  # 666
             "aalto-ml/nn2svgp/m20zxspk",  # 54
         ],
-        "nn2svgp-sample-with-updates": [  # id for multiple seeds
-            # "id": "aalto-ml/nn2svgp/13w22sjr",  # 42
-            "aalto-ml/nn2svgp/2nfhcyfw",  # 666
-            "aalto-ml/nn2svgp/19g1fzaa",  # 50
-            "aalto-ml/nn2svgp/igchyb8j",  # 100
-            "aalto-ml/nn2svgp/1ep2s2ne",  # 69
-            "aalto-ml/nn2svgp/to5ptnuu",  # 54
+        # "nn2svgp-sample-with-updates": [  # id for multiple seeds
+        #     # "id": "aalto-ml/nn2svgp/13w22sjr",  # 42
+        #     "aalto-ml/nn2svgp/2nfhcyfw",  # 666
+        #     "aalto-ml/nn2svgp/19g1fzaa",  # 50
+        #     "aalto-ml/nn2svgp/igchyb8j",  # 100
+        #     "aalto-ml/nn2svgp/1ep2s2ne",  # 69
+        #     "aalto-ml/nn2svgp/to5ptnuu",  # 54
+        # ],
+        "laplace": [
+            "aalto-ml/nn2svgp/ovi8ooil",  # 100
+            "aalto-ml/nn2svgp/ttgleyig",  # 666
+            "aalto-ml/nn2svgp/r6j12038",  # 50
+            "aalto-ml/nn2svgp/zc55qobv",  # 69
+            "aalto-ml/nn2svgp/p92x5hkv",  # 54
+        ],
+        "ensemble": [
+            "aalto-ml/nn2svgp/zzcv9ew2",  # 100
+            "aalto-ml/nn2svgp/bg3cgoze",  # 666
+            "aalto-ml/nn2svgp/4jtgz6l5",  # 50
+            "aalto-ml/nn2svgp/afpm5hc2",  # 69
+            "aalto-ml/nn2svgp/jlumgtyu",  # 54
         ],
         "mlp": [
             "aalto-ml/nn2svgp/1ags2von",  # 666
@@ -45,20 +59,6 @@ WANDB_RUNS = OmegaConf.create(
             "aalto-ml/nn2svgp/rbq90bf5",  # 69
[…]

### 2023-05-15 paper/main.tex
add rl todo
added rough draft in main paper  of the CL experiments

--- 2023-05-15 paper/main.tex
@@
     \node[anchor=north, font=\small] at ($(banana-nn) + (0,-.55\figureheight)$) {Neural network prediction};
-    \node[anchor=north, font=\small] at ($(banana-nn2svgp) + (0,-.55\figureheight)$) {Sparse function-space representation};
+    \node[anchor=north, font=\small] at ($(banana-nn2svgp) + (0,-.55\figureheight)$) {Sparse GP representation};
     \node[anchor=north, font=\small] at ($(banana-hmc) + (0,-.55\figureheight)$) {HMC result as baseline};
@@
 %\paragraph{GP in the dual parameters}
-The seminal work by \citet{csato2002sparse} (parameterization Lemma~1) gives a parameterization for the posterior process $f_{\textrm{post}}$ that can be found through the Bayesian update using the GP prior and the likelihood function.
-This gives a `dual' parameterization, $\valpha$ and $\vbeta$,
+The early work by \citet{csato2002sparse} (Parameterization Lemma~1) states that the mean and covariance functions of the posterior process $f_{\textrm{post}}$, found through the Bayesian update using the GP prior and the likelihood function, can be parameterized by `dual' parameters, $\valpha$ and $\vbeta$,
 %
@@
 %
-where the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{N \times N}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $k_{ii} = \kappa(\vx_i, \vx_i)$.
+where the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{n \times n}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $k_{ii} = \kappa(\vx_i, \vx_i)$.
 The dual parameters are the vector $\valpha \in \R^{m}$ and vector $\vbeta \in \R^{m}$, defined as:
-%
 \begin{equation}
 \label{eq:dual_param}
-  \alpha_i \coloneqq \myexpect_{p(\vw \mid \vy)}[\nabla_{f_i}\log p(y_i \mid f_i)]
-  \quad \text{and} \quad
+\alpha_i \coloneqq \myexpect_{p(\vw \mid \vy)}[\nabla_{f_i}\log p(y_i \mid f_i)],  \quad
 \beta_i \coloneqq - \myexpect_{p(\vw \mid \vy)}[\nabla^2_{f_i f_i}\log p(y_i \mid f_i)] .
@@
 %
-The relationships specified above are valid for generic likelihoods, and involve no approximations since the expectation is under the exact posterior.
-This higlights the fact that our approximate inference technique that will follow, while usually viewed as a posterior approximation, can be alternatively interpreted as an approximation of the expectation of gradients of loss/likelihoods.
-
-Originally \citet{csato2002sparse} iteratively find dual variables using an expectation propogation (EP, \cite{minka2001expectation}) method.
-More recently \cite{khan2017conjugate,adam2021dual}, has shown this relationship for variational Gaussian processes where the above expectation is with respect to the approximate variational posterior.
+The above relations hold for generic likelihoods, and no approximations are involved as the expectation is under the exact posterior. 
+It also highlights that our approximate inference technique, while usually considered a posterior approximation, can instead be seen as approximating the expectation of gradients of loss/likelihoods.
+\todo{our approximation is late \cref{eq:dual_param_laplace}, saying this here is misleading}\\
+In \citet{csato2002sparse}, they iteratively find dual variables using an Expectation Propogation (EP) method.  
+At the same time, in \cite{adam2021dual, chang2020fast}, they show this relationship for variational Gaussian processes where the above expectation is with respect to the approximate variational posterior.
 The dual parameter $\valpha$ appears also in non-Bayesian approaches, \eg, support vector machines \citep{cortes1995support}, whose origins are found in work by \citet{kimeldorf1971some}.
-While in \citet{wilkinson2023bayes}, they show links between linearization methods and how they solve the \cref{eq:dual_param}.
+While in \citet{wilkinson2023bayes}, they show links between linearization methods and how they solve the \cref{eq:dual_param}.\todo{is this last part used/referred somewhere else?}
 
@@
 Given that we use a Laplace approximation of the neural network, we remove the expectation over the posterior (see Ch.~3.4.1 in \cite{rasmussen2006gaussian} for derivation) and we get the the following formulation of the dual variables,
-%
 \begin{equation}
 \label{eq:dual_param_laplace}
-  \hat{\alpha}_i \coloneqq \nabla_{f}\log p(y_i \mid f) |_{f=f_i}
-  \quad \text{and} \quad
-  \hat{\beta}_i \coloneqq - \nabla^2_{f,f}\log p(y_i \mid f) |_{f=f_i}.
+\hat{\alpha}_i \coloneqq \nabla_{f_i}\log p(y_i \mid f_i),  \quad \text{and} \quad
+\hat{\beta}_i \coloneqq - \nabla^2_{f_i f_i}\log p(y_i \mid f_i).
 \end{equation}
-%
+
 Substiuting \cref{eq:dual_param_laplace} into \cref{eq:gp_pred}, we obtain our GP model based on the converged neural network.
 Again, this is similar to what was derived in \citet{immer2021improving} for the posterior variance function.
-However, they use the $f_{\vw^*}$ for the posterior mean and do not emphasize the significance of the dual variables.
-The problem with \cref{eq:gp_pred} is that to make predictions and compute variances we must incur a cost of $O(N^3)$ which limits the use of the GP on large data sets.
+However, they use the $f_{\vw^*}$ for the posterior mean and do not spot the significance of the dual variables.
+The problem with \cref{eq:gp_pred} is that to make predictions and compute variances we must incur a cost of $O(n^3)$ which limits the use of the GP on large data sets.
 
@@
 \subsection{Updating the  network representation for Continual learning}
-%
-% the problem is hard many hyperparams and also a lot of things can make huge differences
-% we restrict ourselves to the SH setting, then some values
+%% Very rough draft
+This experiment's section is meant to demonstrate the quality of our sparse representation to retain previous knowledge in the Continual learning setting.
+Unfortunately the CL literature is based on methods that require very diverse set of hyperparameters
+% Idea: it is very difficult to have everything under control, because model changes, settings change, optimizer change, and so on.
+Then what we did was trying to replicate as close as possible the results for the competing methods by using their codebases where available and choosing the hyperpameters accordingly to their choices.
+
+% Why SH?
+% TODO: there are at least two papers that clearly say MH is unrealistic and too simple as a consequence is not a good way to assess the quality of the method
+
+% Architectures
+We conduct the experiments on a set of three CL benchmarks Sequential-MNIST (S-MNIST), Sequential-FashionMNIST (S-FMNIST), and Permuted-MNIST (P-MNIST).
+Following \cite{rudner2022continual, pan2020continual}, we used a two-layer MLP with 256 hidden units with ReLU activation for S-MNIST and S-FMNIST, and a two-layer with 100 hidden units for P-MNIST.
+
+% Methods
+We compared our method to 1) weight-regularization based methods EWC, SI and VCL (which also has the addition of coresets); 2) function-based regularization based methods DER, FROMP, S-FSVI, SFR; 3) an ablation for which we replace $\bar{\MB}^{-1}$ with an identity matrix $\MI_m$, \ie which is equivalent to assuming a GP with iid realization \todo{Not sure this is 100$\%$ correct}.
+% Inducing points
+Following \citep{rudner2022continual}, we use 200 inducing points per tasks % this one can be difficult to justify since S-FSVI samples 200 context points and then iteratively samples 40 coresets points (or at least that's what I got)
+on all the inducing points, and a lower number of inducing point for S-MNIST, to investigate if our method was still capable of capture more information due to its sparse formulation, as explained in \cref{todo}.
+
+%% Questions: Should we also mention the Identity outside when not trained on those classes or just leave that for the appendix?
+
+%% Comments on the results:
+We get the best results on S-MNIST both 40 and 200 pts. per task
+
+On S-FMNIST we are on par with DER, which is however exploiting a reservoir buffer technique, that iteratively samples new "inducing points"
+
+On P-MNIST we are lower than S-FSVI, however % I'm still running experiments, so we can hope that it is not the best overall in the end
 

### 2023-05-15 paper/main.tex

--- 2023-05-15 paper/main.tex
@@
 
+ \todo{I'm thinking we should take out the SFR with updates result}
 \begin{figure}[!t]

### 2023-05-15 paper/main.tex
Sec. 3

--- 2023-05-15 paper/main.tex
@@
 %
-Sparse Gaussian processes are a way to reduce the computational complexity of a full GP using a low-rank approximation.
-Many sparsifying approaches exist and we refer the reader to \cite{quinonero2005unifying} for an overview.
-Given that we computed the dual variables derived from our neural network predictions and a kernel function, we could essentially use any approximation.\todo{approximation to get what?
-kernel and dual variables} We decide to follow the sparsifying approach of \citet{titsias2009variational} and also used in the DTC approximation \citep{quinonero2005unifying}, which defines the marginal predictive distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) q(\vu)  d\vu$.
+Sparse Gaussian processes reduce the computational complexity by representing the GP as a low-rank approximation induced by a sparse set of inputs points (see \cite{quinonero2005unifying} for an early overview).
+Given that we have computed the dual variables derived from our neural network predictions and a kernel function, we could essentially employ any of these sparsification methods.
+In this work, we opt for the approach suggested by \citet{titsias2009variational} (also used in the DTC approximation, see \cite{quinonero2005unifying}), which defines the marginal predictive distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) \, q(\vu) \, \mathrm{d}\vu$.
 Given that we have $p(f_i \mid \vu)$ determined by our GP prior, the goal is to find a $q(\vu)$.
 
-As was shown in \cite{adam2021dual}, the posterior under this model has a particular structure similar to \cref{eq:gp_pred}.
-In the paper, the authors spot the dual variables' importance for approximate inference, but write them with the natural parameterization as this form is more suitable for optimization through natural gradients.
+As demonstrated in \cite{adam2021dual}, the posterior under this model bears a structure akin to \cref{eq:gp_pred}.
+The authors of that paper see the significance of the dual variables for approximate inference, but write them using the natural parameterization, primarily because this form is more suitable for optimization through natural gradients.
 In order to link the dual variables defined in \cref{eq:dual_param}, we write them in the sparse GP using the dual variables
+%
 \begin{equation} 
-	\valpha_{\vu}  =  \sum_{i \in \mathcal{D}_{n}}  \vkzi \, \hat{\alpha}_{i}, \quad
+  \valpha_{\vu}  =  \sum_{i \in \mathcal{D}_{n}}  \vkzi \, \hat{\alpha}_{i}
+  \quad \text{and} \quad
   \vbeta_{\vu} =  \sum_{i \in \mathcal{D}_{n}} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
@@
 \end{equation}
+%
 where the sparse dual variables are now a sum over all data points, with $\valpha_{\vu} \in \R^{M}$ and $\vbeta_{\vu} \in \R^{M  \times M}$.

### 2023-05-15 paper/main.tex
Sec. 3
updated rl experiemetn

--- 2023-05-15 paper/main.tex
@@
 %
-Sparse Gaussian processes reduce the computational complexity by representing the GP as a low-rank approximation induced by a sparse set of inputs points (see \cite{quinonero2005unifying} for an early overview).
-Given that we have computed the dual variables derived from our neural network predictions and a kernel function, we could essentially employ any of these sparsification methods.
-In this work, we opt for the approach suggested by \citet{titsias2009variational} (also used in the DTC approximation, see \cite{quinonero2005unifying}), which defines the marginal predictive distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) \, q(\vu) \, \mathrm{d}\vu$.
+Sparse Gaussian processes are a way to reduce the computational complexity of a full GP using a low-rank approximation.
+Many sparsifying approaches exist and we refer the reader to \cite{quinonero2005unifying} for an overview.
+Given that we computed the dual variables derived from our neural network predictions and a kernel function, we could essentially use any approximation.\todo{approximation to get what?
+kernel and dual variables} We decide to follow the sparsifying approach of \citet{titsias2009variational} and also used in the DTC approximation \citep{quinonero2005unifying}, which defines the marginal predictive distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) q(\vu)  d\vu$.
 Given that we have $p(f_i  \mid \vu)$ determined by our GP prior, the goal is to find a $q(\vu)$.
 
-As demonstrated in \cite{adam2021dual}, the posterior under this model bears a structure akin to \cref{eq:gp_pred}.
-The authors of that paper see the significance of the dual variables for approximate inference, but write them using the natural parameterization, primarily because this form is more suitable for optimization through natural gradients.
+As was shown in \cite{adam2021dual}, the posterior under this model has a particular structure similar to \cref{eq:gp_pred}.
+In the paper, the authors spot the dual variables' importance for approximate inference, but write them with the natural parameterization as this form is more suitable for optimization through natural gradients.
 In order to link the dual variables defined in \cref{eq:dual_param}, we write them in the sparse GP using the dual variables
-%
 \begin{equation} 
-  \valpha_{\vu}  =  \sum_{i \in \mathcal{D}_{n}}  \vkzi \, \hat{\alpha}_{i}
-  \quad \text{and} \quad
+	\valpha_{\vu}  =  \sum_{i \in \mathcal{D}_{n}}  \vkzi \, \hat{\alpha}_{i}, \quad
 	\vbeta_{\vu} =  \sum_{i \in \mathcal{D}_{n}} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
@@
 \end{equation}
-%
 where the sparse dual variables are now a sum over all data points, with $\valpha_{\vu} \in \R^{M}$ and $\vbeta_{\vu} \in \R^{M  \times M}$.
@@
 
-A key challenge in RL is balancing the trade-off between exploration and exploitation.
-That is, should an agent select actions that it knows will lead to high reward (exploitation), or should it
-select new ones in hope to discover actions leading to higher reward (exploration).
-One promising direction is to model the uncertainty associated with a learned transition dynamics and use it to guide exploration.
-Prior work has learned dynamics models using GPs \cite{deisenrothPILCO2011,kamtheDataEfficient2018},
-ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
-and variational inference \cite{galImproving2016,houthooftVIME2017}.
-There are then many ways to leverage uncertainty in model-based RL, for example,
-taking an expectation over epistemic uncertainty  \cite{deisenrothPILCO2011,kamtheDataEfficient2018,chuaDeepReinforcementLearning2018},
-sampling from the posterior, akin to Thompson sampling but referred to as posterior sampling RL
-\cite{osbandMoreEfficientReinforcement2013},
-and methods based on upper confidence bounds (UCB) \cite{curiEfficient2020}.
-
+% A key challenge in RL is balancing the trade-off between exploration and exploitation.
+% That is, should an agent select actions that it knows will lead to high reward (exploitation), or should it
+% select new ones in hope to discover actions leading to higher reward (exploration).
+% One promising direction is to model the uncertainty associated with a learned transition dynamics and use it to guide exploration.
+% Prior work has learned dynamics models using GPs \cite{deisenrothPILCO2011,kamtheDataEfficient2018},
+% ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
+% and variational inference \cite{galImproving2016,houthooftVIME2017}.
+% There are then many ways to leverage uncertainty in model-based RL, for example,
+% taking an expectation over epistemic uncertainty  \cite{deisenrothPILCO2011,kamtheDataEfficient2018,chuaDeepReinforcementLearning2018},
+% sampling from the posterior, akin to Thompson sampling but referred to as posterior sampling RL
+% \cite{osbandMoreEfficientReinforcement2013},
+% and methods based on upper confidence bounds (UCB) \cite{curiEfficient2020}.
+
+In this section, we show that \our's uncertainty estimates can be used to guide exploration in model-based RL;
+demonstrating the quality of our uncertainty estimates.
 % Uncertainty-guided decision making strategies
-We refer the reader to \cref{app:rl} for an overview of the reinforcement learning problem and more details of our experiments.
-
-We test \our by using it to learn a dynamics model
-our method on the cart pole swing up task in MuJoCo \cite{todorov2012mujoco}, a classic benchmark for nonlinear control, see \cref{fig:rl}.
+We test \our by using it to learn a dynamics model within a model-based RL strategy which uses posterior sampling to guide exploration
+\cite{osbandMoreEfficientReinforcement2013,osbandWhyPosteriorSampling2017}.
+We use the cart pole swing up task in MuJoCo \cite{todorov2012mujoco}, a classic benchmark for nonlinear control, see \cref{fig:rl}.
 The goal is to swing the pole up and balance it around the upward position.
-We increase the  difficulty of exploration in this environment by using a sparse reward function.
-
-We compare \our (cyan) to a Laplace-GGN with GLM predictions (red), an ensemble of neural networks (green) and a basic MLP wih no uncertainty (magenta).
+We increase the difficulty of exploration by using a sparse reward function.
+We refer the reader to \cref{app:rl} for an overview of the reinforcement learning problem, details of the algorithim we implement and our experiment's configuration.
+
+\cref{fig:rl} shows training curves using \our as the dynamic model (cyan) as well as a Laplace-GGN with GLM predictions (red), an ensemble of neural
+networks (green) and a basic MLP wih no uncertainty (magenta).
 To ensure a fair comparison, we use the same MLP architecture/training scheme and use them in the same model-based RL algorithm, detailed in \cref{app:rl}.
+% that \our's uncertainty estimates are useful for guiding exploration as it converges in fewer episodes.
+We also compare to deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016}, a model-free RL algorithim (yellow).
+The training curves show that \our's uncertainty estimates are useful for guiding exploration as it converges in fewer episodes, i.e.
+it is more sample efficient.
+As expected, the MLP strategy (without uncertainty) was not able to successfuly explore the environment.
+
+% We compare \our (cyan) to a Laplace-GGN with GLM predictions (red), an ensemble of neural networks (green) and a basic MLP wih no uncertainty (magenta).
+% To ensure a fair comparison, we use the same MLP architecture/training scheme and use them in the same model-based RL algorithm, detailed in \cref{app:rl}.
 % See \cref{app:rl} for more details of our experiments.
-We also compare to deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016}, a model-free RL algorithim (yellow).
 % As expected DDPG is the least sample inefficient
-The training curves in \cref{fig:rl} show that \our's uncertainty estimates are useful for guiding exploration as it converges in fewer episodes.
+% The training curves in \cref{fig:rl} show that \our's uncertainty estimates are useful for guiding exploration as it converges in fewer episodes.
 

### 2023-05-15 paper/main.tex

--- 2023-05-15 paper/main.tex
@@
 %
-\begin{equation} 
+\begin{equation} \textstyle
   \valpha_{\vu}  =  \sum_{i \in \mathcal{D}_{n}}  \vkzi \, \hat{\alpha}_{i}

### 2023-05-15 paper/main.tex
Sec. 3

@@
 \newcommand{\vbeta}[0]{\mathbold{\beta}}
+\newcommand{\MBeta}[0]{\mathbold{B}}
 \newcommand{\vlambda}[0]{\mathbold{\lambda}}
@@
 Function-space perspectives on uncertainty in neural networks often use a Laplace-GGN approximation \citep{daxberger2021laplace}, linearizing a trained neural network around optimal weights.
-The Hessian can be efficiently approximated using the generalized Gauss--Newton approximation (GGN)~\cite{botev2017practical}.
+The Hessian can be efficiently approximated using the generalized Gauss--Newton approximation (GGN, \cite{botev2017practical}).
 While efficient, it suffers from cubic scaling in parameter count, necessitating approximations like Kronecker factorisation \cite{martens2015optimizing, ritter2018kfac}.
@@
 Recently proposed methods, \eg, DER~\citep{buzzega2020dark}, FROMP~\citep{pan2020continual}, and S-FSVI~\citep{rudner2022continual} achieve state-of-the-art performance among the objective-based techniques in several CL benchmarks.
+\looseness-2
 
@@
 No single strategy has emerged as a go to method and we highlight that these strategies are only as good as their uncertainty estimates.
-% Central to these decision-making strategies are the methods for quantifying uncertainty.
 Previous approaches have used GPs \cite{deisenrothPILCO2011,kamtheDataEfficient2018},
@@
 and variational inference \cite{galImproving2016,houthooftVIME2017}.
-However, there has been little leveraging
+%However, there has been little leveraging
 
@@
 where the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{N \times N}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $k_{ii} = \kappa(\vx_i, \vx_i)$.
-The dual parameters are the vector $\valpha \in \R^{m}$ and vector $\vbeta \in \R^{m}$, defined as:
+The dual parameters are the vectors $\valpha, \vbeta \in \R^{N}$, defined as:\looseness-1
 %
@@
 \begin{equation} \textstyle
-  \valpha_{\vu}  =  \sum_{i \in \mathcal{D}_{n}}  \vkzi \, \hat{\alpha}_{i}
+  \valpha_{\vu}  =  \sum_{i=1}^N  \vkzi \, \hat{\alpha}_{i}
   \quad \text{and} \quad
-  \vbeta_{\vu} =  \sum_{i \in \mathcal{D}_{n}} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
+  \MBeta_{\vu} =  \sum_{i=1}^N \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
 \label{eq:dual_sparse}
@@
 %
-where the sparse dual variables are now a sum over all data points, with $\valpha_{\vu} \in \R^{M}$ and $\vbeta_{\vu} \in \R^{M  \times M}$.
+where the sparse dual variables are now a sum over all data points, with $\valpha_{\vu} \in \R^{M}$ and $\MBeta_{\vu} \in \R^{M  \times M}$.
 Using these sparse definition of the dual variables, our sparse GP posterior takes the following form:
 \begin{equation}\label{eq:dual_sparse_post}
-   \myexpect_{q_{\vu}(\vf)}[f_i] = \vkzs^{\T} \MKzz^{-1}   \valpha_{\vu} , \quad 
-   \textrm{Var}_{q_{\vu}(\vf)}[f_i]  = \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \vbeta_{\vu})^{-1} ]\vkzs
+   \myexpect_{q_{\vu}(\vf)}[f_i] = \vkzs^{\T} \MKzz^{-1} \valpha_{\vu}
+   \quad \text{and} \quad 
+   \textrm{Var}_{q_{\vu}(\vf)}[f_i]  = k_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \MBeta_{\vu})^{-1} ]\vkzs
 \end{equation}
-where $\MKzz$ and $\vkzs$ are defined similarly to $\MKxx$ and $\vk_{\vx i}$ but over the inducing points $\MZ \in \R^{M \times D} $  instead of the full data set $\dataset$.
-The key quantities we need to make predictions from our sparse GP from the converged neural network are $(\hat{\alpha}_i, \hat{\beta}_i)$ \cref{eq:dual_param_laplac}\todo{these variables need another subscript for differentiate that from the values computed at the data points} and a kernel function $\kappa$ .
-Contrasting \cref{eq:dual_sparse_post} and \cref{eq:gp_pred}, we can see that the computational complexity went from $\mathcal{O}(n^3)$ to $\mathcal{O}(m^3)$, with $m \ll n$.
+where $\MKzz$ and $\vkzs$ are defined similarly to $\MKxx$ and $\vk_{\vx i}$ but over the inducing points $\{\vz_j\}_{i=1}^M$, $\vz \in \R^{D}$, instead of the full data set $\dataset$.
+The key quantities we need to make predictions from our sparse GP from the converged neural network are $(\hat{\alpha}_i, \hat{\beta}_i)$ \cref{eq:dual_param_laplace} and a kernel function $\kappa$ .
+Contrasting \cref{eq:dual_sparse_post} and \cref{eq:gp_pred}, we can see that the computational complexity went from $\mathcal{O}(N^3)$ to $\mathcal{O}(M^3)$, with $M \ll N$.
 Crucially, given the structure of our probabilistic model, our sparse dual variables \cref{eq:dual_sparse} are a compact representation of the full model projected using the kernel.
 
-In contrast to our approach, \citet{immer2021improving} use a subset of the data points to make a sparse GP model to reduce the computational complexity.
-As a result, this is a less principled approach for building a sparse model since it ignores the dataset's information.
-It is important to highlight that the sparsifying process is independent of the approximate inference technique because the dual variables of \cref{eq:dual_param} are computed using \cref{eq-empirical-risk} and a Laplace approximation.
+Unlike our approach, \citet{immer2021improving} employ a subset of the data points to construct a sparse GP model, reducing computational complexity.
+However, this method could be considered less principled for building a sparse model, as it ignores contribution from data.
+It is important to note that the sparsifying process is independent of the approximate inference technique because the dual variables of \cref{eq:dual_param} are computed using \cref{eq-empirical-risk} and a Laplace approximation.
 More complicated inference techniques, such as variational inference, could be used, but given its simplicity, in our experiments we used the Laplace-GGN approximation with the trained neural network.
-Furthermore, our dual variable view of approximate inference means we do not need to retrain a separate sparse GP model.
-\todo{shouldn't this sentence be clear from the context?
+Furthermore, our dual variable view of approximate inference means we do not need to retrain a separate sparse GP model.%\todo{shouldn't this sentence be clear from the context?
 we derive the mean/kernel function that define the process, then we have a sparse GP already}
+
 \section{Sparse Function-space Sequential Learning}

### 2023-05-15 paper/main.tex
Sec. 4

@@
 Using the sparse GP we can then take advantage of the property of dual parameters that allows for fast conditioning recently shown in \cite{chang2022fantasizing}.
-Thus we are able to avoid retraining and condition new data in to our model.
+Thus we are able to avoid retraining and condition new data in to our model (see \cref{fig:teaser}).
 The resulting \our method can be applied in any sequential decision-making scenario where retraining is not feasible.
@@
 %
-where the sparse dual variables are now a sum over all data points, with $\valpha_{\vu} \in \R^{M}$ and $\MBeta_{\vu} \in \R^{M  \times M}$.
-Using these sparse definition of the dual variables, our sparse GP posterior takes the following form:
+where the sparse dual variables are now a sum over \emph{all data points}, with $\valpha_{\vu} \in \R^{M}$ and $\MBeta_{\vu} \in \R^{M  \times M}$.
+Using this sparse definition of the dual variables, our sparse GP posterior takes the following form:
 \begin{equation}\label{eq:dual_sparse_post}
@@
 
-\section{Sparse Function-space Sequential Learning}
-
+\section{Sparse function-space sequential learning}
+\label{sec:sequential}
+%
 We have presented a method for converting any trained neural network into a sparse function-space representation.
@@
 
-\subsection{\our for Continual Learning}
+\paragraph{\our for continual learning}
 % Definition of CL -> a sequence of tasks 
-In the Continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{n_t}$, which after the task is discarded and cannot be accessed in the following stages of the training.
-Rehearsal and function regularization-based models keep a subset of the trai ning data for each task to help the model alleviate forgetting.
-In the same way, after each task, we can use our \our to build a compact representation of the neural network and then exploit this representation to build a functional regularizer to add to the training loss for the subsequent tasks.
+In the Continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{N_t}$, which after the task is discarded and cannot be accessed in the following stages of the training.
+Rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting.
+In the same way, after each task, we can use our \our method to build a compact representation of the neural network and then exploit this representation to build a functional regularizer to add to the training loss for the subsequent tasks.
 Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art on CL benchmarks.
@@
 % Where the regularizer comes from
-At the end of the training for each task $t$, we compute the Laplace-GGN approximated kernel function for the current model and randomly select $m$ inducing points.
+At the end of the training for each task $t$, we compute the Laplace-GGN approximated kernel function for the current model and randomly select $M$ inducing points.
 Given the issues described in the previous sections, related to computing the full covariance posterior $\MKxx$ for $\dataset_t$,\todo{this should be $\kappa(\MX_t, \MX_t)$} we can exploit the dual parameterization to efficiently encode the information from  $\dataset_t$ using the dual parameterization, as follows,
-\begin{equation}
- 	\bar{\MB}^{-1}_t = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{m \times m}, 
- 	\quad 
- 	\vbeta_{\vu} =  \sum_{i \in \dataset_t} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
+%
+\begin{equation}\textstyle
+ 	\bar{\MB}^{-1}_t = \MKzz^{-1} \MBeta_\vu \MKzz^{-1} \in \R^{M \times M}, 
+ 	\quad \text{s.t.} \quad
+ 	\MBeta_{\vu} =  \sum_{i \in \dataset_t} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
  	% \quad \forall t \in [1, T]
 \end{equation}
- where $\MKzz$ and $\vkzi$ are the kernel function computed on the inducing points $\MZ_t \in \R^{m \times D}$ for task $t$ .
-
-We keep a memory buffer $\mathcal{M} = \{(\MZ_t, \vu_t, \bar{\MB}^{-1}_t)\}_{t=1}^T$, where $\MZ_t$ are the inducing points selected from $\dataset_t$ and  $\vu_t = f_{\vw_t^*}(\MZ_t)\in \R^{m}$ are the neural network outputs associated to them, computed with the MAP estimate after task $t$ $\weights_t^*$.
-Note that, for notational convenience, we are extending our neural network notation to be compatible with multiple inputs points, \ie, each $i$th entry is $f_{\weights_t^*}(\vz_i)\in \R$.
+%
+where $\MKzz$ and $\vkzi$ are the gram matrix and vector computed on the inducing points $\MZ_t = \{\vz_i\}_{i=1}^M$ for task $t$ .
+%
+We keep a memory buffer $\mathcal{M} = \{(\MZ_t, \vu_t, \bar{\MB}^{-1}_t)\}_{t=1}^T$, where $\MZ_t$ are the inducing points selected from $\dataset_t$ and  $\vu_t = f_{\vw_t^*}(\MZ_t)\in \R^{M}$ are the neural network outputs associated to them, computed with the MAP estimate $\weights_t^*$ after task $t$.
+Note that, for notational convenience, we are extending our neural network notation to be compatible with multiple inputs points, \ie, each $i$\textsuperscript{th} entry is $f_{\weights_t^*}(\vz_i)\in \R$.
 Moreover, we restrict ourselves to single-output neural networks and refer the reader to further details on the multi-output setting to \cref{sec:cl_multioutput}.
 
-After each task, we update $\mathcal{M}$, and we can construct a regularizer term, which aims to reduce the drift of the current model from diverging on the inducing points $\MZ_s$ for all previous tasks $ s \in \left[ 1, t-1 \right]$.
-The resulting regularizer can be computed as follows
-%\begin{equation}
-%	\mathcal{R}_\textit{SFR}(\weights, \mathcal{M}) = \sum_{s=1}^{t-1} \frac{1}{m} \left[\left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right) \right].
-%\end{equation}
-
-\begin{equation}
-	\mathcal{R}_\textit{SFR}(\weights, \mathcal{M}) = \frac{1}{2} \sum_{s=1}^{t-1} \frac{1}{m} 
+After each task, we update $\mathcal{M}$, and we can construct a regularizer term, which aims to reduce the drift of the current model from diverging on the inducing points $\MZ_s$ for all previous tasks $ s \in \{1, \ldots, t-1 \}$.
+This means that for training  the successive task, the new objective to minimize becomes $\weights_t^* = \arg\min_{\weights} \mathcal{L}(\mathcal{D}_t, \weights) + \tau \, \mathcal{R}_\textrm{\our}(\weights, \mathcal{M})$, with the regularizer
+%
+\begin{equation}\label{eq-cl-regularizer}
+  \mathcal{R}_\mathrm{\our}(\weights, \mathcal{M}) = \frac{1}{2} \sum_{s=1}^{t-1} \frac{1}{M} 
 	\left\lVert 
@@
 \end{equation}
-%\todo{choose one option}
-% where $f_\vw(\MZ_{s}) \in \R^m$ are the outputs of neural networks with the current weights $\vw$ and stored function outputs of the neural network at the MAP optimum for task $s$, i.e., each $i$th entry is $f_\cdot(\vz_i) \in \R$.
+
+%%The resulting regularizer can be computed as follows
+%%\begin{equation}
+%%	\mathcal{R}_\textit{SFR}(\weights, \mathcal{M}) = \sum_{s=1}^{t-1} \frac{1}{m} \left[\left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right) \right].
+%%\end{equation}
+%%
 %\begin{equation}
-%	\argmin_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights) + \tau \mathcal{R}_\textit{SFR}(\weights)
+%	\mathcal{R}_\mathrm{\our}(\weights, \mathcal{M}) = \frac{1}{2} \sum_{s=1}^{t-1} \frac{1}{M} 
+%	\left\lVert 
+%	f_{\weights}(\MZ_{s}) - \vu_t % f_{\weights_{s}}(\MZ_s)
+%	\right\rVert_{\bar{\MB}^{-1}_{s}}.
 %\end{equation}
-Then, when the training on the successive task, the new objective to minimize takes the following form
-\begin{equation}
-	\weights_t^* = \argmin_{\weights} \mathcal{L}(\mathcal{D}_t, \weights) + \tau \mathcal{R}_\textit{SFR}(\weights, \mathcal{M})
-\end{equation}
+%%\todo{choose one option}
+%% where $f_\vw(\MZ_{s}) \in \R^m$ are the outputs of neural networks with the current weights $\vw$ and stored function outputs of the neural network at the MAP optimum for task $s$, i.e., each $i$th entry is $f_\cdot(\vz_i) \in \R$.
+%%\begin{equation}
+%%	\argmin_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights) + \tau \mathcal{R}_\textit{SFR}(\weights)
+%%\end{equation}
+%Then, when the training on the successive task, the new objective to minimize takes the following form
+%\begin{equation}
+%	\weights_t^* = \argmin_{\weights} \mathcal{L}(\mathcal{D}_t, \weights) + \tau \mathcal{R}_\textit{SFR}(\weights, \mathcal{M})
+%\end{equation}
 

### 2023-05-15 paper/main.tex
Sec. 4

@@
 
-After each task, we update $\mathcal{M}$, and we can construct a regularizer term, which aims to reduce the drift of the current model from diverging on the inducing points $\MZ_s$ for all previous tasks $ s \in \{1, \ldots, t-1 \}$.
+After each task, we update $\mathcal{M}$, and we can construct a regularizer term, which aims to reduce the drift of the current model from diverging on the inducing points $\MZ_s$ for all previous tasks $ s = 1, \ldots, t-1$.
 This means that for training  the successive task, the new objective to minimize becomes $\weights_t^* = \arg\min_{\weights} \mathcal{L}(\mathcal{D}_t, \weights) + \tau \, \mathcal{R}_\textrm{\our}(\weights, \mathcal{M})$, with the regularizer

### 2023-05-16 paper/main.tex
rewrite 3 points
Sec. 4 and 5

@@
 \crefname{definition}{Def.}{Defs.}
-\crefname{table}{Tab.}{Tabs}
+\crefname{table}{Table}{Tables}
 
@@
 
-\section{Sparse function-space sequential learning}
+\section{Maintaining a sparse function-space representation in sequential learning}
 \label{sec:sequential}
@@
 We have presented a method for converting any trained neural network into a sparse function-space representation.
-In this section, we demonstrate how sequential learning methods can benefit from our function-space representation and it's associated uncertainty estimates.
+The sparse representation opens an avenue for maintaining (and updating) a representation of the neural network, an important feature for sequential learning, such as continual learning.\looseness-1
+%In this section, we demonstrate how sequential learning methods can benefit from our function-space representation and it's associated uncertainty estimates.
 
@@
 % Definition of CL -> a sequence of tasks 
-In the Continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{N_t}$, which after the task is discarded and cannot be accessed in the following stages of the training.
+In the continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{N_t}$, which after the task is discarded and cannot be accessed in the following stages of the training.
 Rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting.
@@
 \label{sec:experiments}
-
-\todo{Overview of experiments}
-
-Our experiments seek to answer the following questions:
-\begin{enumerate}
-  \item \textbf{Predictions} How do predictions with our sparse function-space approximation compare to weight-space approximations?
-Does our method's ability to consider the full data set offer benefits over subset function-space methods?
-  % \item Does our method's ability to consider the full data set offer benefits over subset function-space methods?
-  \item \textbf{Function-space updates} How fast are our function-space updates relative to retraining from scratch?
+%
+We present a series of experiments designed to demonstrate the versatility and efficacy of our proposed \our framework. We seek to find answers to the following questions: 
+\textbf{Predictions:}~Does our method's ability to consider the full data set offer benefits over subset function-space methods?
+(\cref{sec:uci}) How do predictions with our sparse function-space approximation compare to weight-space approximations?
+\textbf{Function-space updates:} How fast are our function-space updates relative to retraining from scratch?
 Do they improve predictive performance?
 Are they as good as retraining from scratch?
-  \item \textbf{Uncertainty} How good are our uncertainty estimates? Can they be used in downstream settings like RL?
-  \item \textbf{Representation} Is our sparse function-space representation useful for continual learning?
-\end{enumerate}
+\todo{what do we have on this?}
+\textbf{Representation:} Can a sparse function-space representation help retain knowlegde from previous tasks in CL? (\cref{sec:cl-exp})
+\textbf{Uncertainty:} Can our uncertainty estimates help exploration in RL under sparse rewards? (\cref{sec:rl-exp})
+
+%Initially, we explore the capability of our method to capture predictive uncertainty through supervised learning tasks using UCI datasets.
+Subsequently, we extend our supervised learning experiment to image datasets, demonstrating our method's robustness and adaptability to more complex, high-dimensional data.
+Next, we investigate the potential of our method in a continual learning context, where we update the neural network representation in response to incoming data without necessitating retraining.
+Lastly, we delve into the realm of reinforcement learning to ascertain the applicability of our approach in an environment that requires sequential decision-making.
+Each experiment is designed to illuminate a different facet of our method, thereby exemplifying its broad range of applicability and potential for future utilization.
+
+%
+%Our experiments seek to answer the following questions:
+%\begin{enumerate}
+%  \item \textbf{Predictions:} How do predictions with our sparse function-space approximation compare to weight-space approximations?
+Does our method's ability to consider the full data set offer benefits over subset function-space methods?
+%  % \item Does our method's ability to consider the full data set offer benefits over subset function-space methods?
+%  \item \textbf{Function-space updates:} How fast are our function-space updates relative to retraining from scratch?
+Do they improve predictive performance?
+Are they as good as retraining from scratch?
+%  \item \textbf{Uncertainty:} How good are our uncertainty estimates? Can they be used in downstream settings like RL?
+%  \item \textbf{Representation:} Is our sparse function-space representation useful for continual learning?
+%\end{enumerate}
 
 \subsection{Capturing uncertainty in UCI tasks under supervised learning}
+\label{sec:uci}
 %
@@
 
-\subsection{Updating the  network representation for Continual learning}
+\subsection{Updating the  network representation in continual learning}
 %% Very rough draft
@@
 
-\subsection{Reinforcement learning}
+\subsection{Reinforcement learning under sparse rewards}
+\label{sec:rl-exp}
 % We now demonstrate the quaility of \our's uncertainty estimates by showing that it can improve sample efficiency in RL.

### 2023-05-16 paper/main.tex
Minor
Sec. 6

@@
 %
-where $\MKzz$ and $\vkzi$ are the gram matrix and vector computed on the inducing points $\MZ_t = \{\vz_i\}_{i=1}^M$ for task $t$ .
+where $\MKzz$ and $\vkzi$ are the gram matrix and vector computed on the inducing points $\MZ_t = \{\vz_i\}_{i=1}^M$ for task $t$ .\
 %
@@
 %
-\begin{equation}\label{eq-cl-regularizer}
+\begin{equation}\label{eq-cl-regularizer}\textstyle
   \mathcal{R}_\mathrm{\our}(\weights, \mathcal{M}) = \frac{1}{2} \sum_{s=1}^{t-1} \frac{1}{M} 
@@
 %
-
+In this paper, we have introduced \our, a novel approach for representing neural networks in sparse function-space, exploiting the dual parameters for an efficient low-rank approximation that accommodates information from the entire data distribution.
+Our method offers a powerful mechanism for capturing predictive uncertainty, updating the model with new data without retraining, and providing a compact representation suitable for continual learning.
+These aspects were demonstrated in a wide range of problems, datasets, and learning contexts.
+We showcased our method's ability to capture uncertainty in UCI and image tasks under supervised learning (\cref{sec:uci}), demonstrated robustness on image data sets (\cref{,sec:image}), established its potential for continual learning (\cref{sec:cl-exp}), and finally, verified its applicability in reinforcement learning scenarios (\cref{sec:rl-exp}).
+
+% Discussion points
 It is worth noting that the NTK linearises the network around the MAP solution $\weights^{*}$,
@@
 It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.
+
+The broader impact of this work lies in its potential to provide tooling for how neural networks are utilized, offering more efficient and principled ways of handling uncertainty and continual learning.
+This contribution, we believe, has significant implications for future applications of machine learning in dynamic, real-world settings where data is unevenly distributed, uncertain, and continuously evolves.
 

### 2023-05-16 paper/main.tex
rewrite 3 points

@@
 \end{equation}
-where $\MKzz$ and $\vkzs$ are defined similarly to $\MKxx$ and $\vk_{\vx i}$ but over the inducing points $\{\vz_j\}_{i=1}^M$, $\vz \in \R^{D}$, instead of the full data set $\dataset$.
+where $\MKzz$ and $\vkzs$ are defined similarly to $\MKxx$ and $\vk_{\vx i}$ but over the inducing points $\{\vz_j\}_{i=1}^M$, $\vz \in \R^{D}$ \todo{These are already defined}, instead of the full data set $\dataset$.
 The key quantities we need to make predictions from our sparse GP from the converged neural network are $(\hat{\alpha}_i, \hat{\beta}_i)$ \cref{eq:dual_param_laplace} and a kernel function $\kappa$ .
@@
 Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art on CL benchmarks.
-However, they are limited to use subset approximations of the posterior.
+However, they are limited to use subset approximations of the posterior \cref{app:cl-experiment}..
 %, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer. 
@@
 %\end{equation}
-
-% We start by obtaining a posterior over the weights of a trained neural network via the Laplace approximation.
-% We then show how we can obtain a function-space posterior, (i.e. a GP posterior)
-% by linearising the neural network around the weights Maximum a Posteriori (MAP) estimate.
-% We then show that by linearising the neural network we can obtain a function-space posterior, i.e. a GP posterior.
-% We paraterise our single-step dynamic model $\transitionFnWithParams : \inputDomain \rightarrow \outputDomain$
-% as an $L\text{-layer}$ NN with weights $\weights$.
-
-%A Gaussian process (GP) is a distribution over real-valued functions $f(\cdot): \mathcal{X} \rightarrow \R$ defined over $\mathcal{X}$.
-%Formally, a GP is defined as,
-%\begin{align}
-%\label{eq-gp-prior}
-%  f(\cdot) \sim \mathcal{N}\left( \mu(\cdot), k(\cdot,\cdot') \right) \quad
-%  \mu(\cdot): \mathcal{X} \rightarrow \R \quad
-%  k(\cdot,\cdot'): \mathcal{X} \times \mathcal{X} \rightarrow \R
-%\end{align}
-%where $\mu(\cdot)$ denotes a mean function and $k(\cdot,\cdot')$ a positive definite covariance function, also known as a kernel.
-%Given a data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
-%we can obtain the GP posterior via multivariate normal conditioning,
-%\begin{align}
-%\label{eq-gp-predictive-posterior}
-%  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
-%  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
-%  \left( f(\mathbf{x}_{*}) \mid \mu(\mathbf{x}_{*}) + \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} (\mathbf{y} - \bm\mu_{\mathbf{X}})),
-%  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
-%\end{align}
-%% Our GP posterior is then given by,
-%\todo{add mean func to GP posterior if we're using one}
-%\begin{align}
-%\label{eq-gp-predictive-posterior}
-%  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
-%  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
-%  \left( f(\mathbf{x}_{*}) \mid \mu(\mathbf{x}_{*}) + \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} \mu_{\mathbf{x}},
-%  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} + \bm\Lambda(\mathbf{y} ; \mathbf{f})^{-1} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
-%\end{align}
-%where $\bm\Lambda(\mathbf{y} ; \mathbf{f}) = \nabla^{2}_{\mathbf{f} \mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$ can be viewed as per-input noise.
-\todo{I'm unsure about this per input noise bit.
-Check with paul.}
-%\todo{what about regression/classification likelhoods}
-%This GP predictive posterior is computationally expensive as it requires inverting an $N\times N$ matrix.
-%
-%\textbf{Sparse Gaussian processes}
-%% The GP predictive posterior in \cref{eq-gp-predictive-posterior} is computationally expensive as it requires inverting an $N\times N$ matrix.
-%A practical and computationally appealing alternative is to augment the joint probability space with pseudo inputs $\mathbf{Z} \in \R^{M \times D}$
-%and corresponding outputs
-%$\mathbf{u} = f(\mathbf{Z}; \weights) \in \R^{M \times C}$, known as inducing variables, where $M \ll N$.
-%\todo{cite sparse gp papers}
-%Instead of collapsing the inducing variables like \cite{titsiasVariational2009}, they can be treated variationally
-%$p(\mathbf{u} \mid \mathbf{y}) \approx q(\mathbf{u}) = \mathcal{N}\left( \mathbf{u} \mid \mathbf{m}, \mathbf{V} \right)$, where $\mathbf{m}$ and $\mathbf{V}$ are variational parameters
-%which need to be optimised \citep{hensmanGaussian2013}.
-%The sparse variational GP (SVGP) predictive posterior is then given by,
-%\begin{align}
-%\label{eq-dual-svgp-predictive-posterior}
-%  p(f(\mathbf{x}_{*}) \mid \mathbf{y})
-%&\approx \mathcal{N} \left( f(\mathbf{x}_{*}) \mid \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{m}^{*},
-%  k_{**} - \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
-%  % \mathbf{k}_{*\inducingInput} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\inducingInput}^{T}
-%  + \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}}  \mathbf{V}^{*}  \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
-%  \right)
-%\coloneqq q_{\inducingVariable}(f(\mathbf{x}_{*}))
-%\end{align}
-%
-%
-%\textbf{Deep learning}
-%Given the data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
-%the goal of (supervised) deep learning, is to train the weights $\weights \in \R^{P}$ of an $L\text{-layer}$ NN
-%$f : \inputDomain \rightarrow \outputDomain$ to minimize the (regularized) empirical risk,
-%\begin{align} \label{eq-empirical-risk}
-%  \weights^{*} = \arg \min_{\weights \in \R^{D}} \mathcal{L}(\dataset;\weights) = \arg \min_{\weights \in \R^{D}} \left(
-%  \sum_{n=0}^{N-1} l(f(\mathbf{x}_{n} ; \weights), \mathbf{y}_{n}) + R(\weights)  \right).
-%\end{align}
-%In practice, it is common to use the mean squared error (MSE) loss
-%$l(f(\mathbf{x}_{n} ; \weights),\mathbf{y}_{n}) = \|f(\mathbf{x}_{n} ; \weights) - \mathbf{y}_{n} \|^{2}_{2}$
-%and to use the weight decay regularizer $R(\weights)=\frac{1}{2}\gamma^{-2}\|\weights\|^{2}_{2}$.
-%However, the practioner is free to choose any loss and regularizer. \todo{I think?}
-%% \textbf{Bayesian neural networks}
-%% \textbf{Weight space to function space}
-%From a Bayesian perspective, we can interpret the terms in \cref{eq-empirical-risk} as the log-prior and the i.i.d. log likelihood, i.e.,
-%\begin{align} \label{eq-log-prior}
-%  R(\weights) &= \underbrace{\log p(\weights)}_{\text{log prior}} = \log \mathcal{N}(\weights \mid 0, \gamma^{2} \mathbf{I}) \\
-%  l(f(\mathbf{x}_{n} ; \weights), \mathbf{y}_{n}) &= \underbrace{\log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \weights))}_{\text{log likelihood}}
-%  = \log \mathcal{N} \left( \mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \weights), \mathbf{I} \right) \label{eq-log-likelihood}
-%\end{align}
-%
-%\textbf{NN to GP}
-%Given this interpretation, we can represent the weight space prior from \cref{eq-log-prior}, in
-%function space, by linearising the BNN around $\weights^{*}$ and interpretting it as a GP.
-%The GP prior is then given by,
-%\begin{align} \label{eq-laplace-approx-function-space}
-%  % \transitionFn_{\weights_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \qquad
-%  f(\cdot ;\weights) \sim \mathcal{N} \left( \mu(\cdot), k(\cdot, \cdot') \right) \quad
-%  % \mu_{\weights_{i}^{*}}(\cdot)
-%  \mu(\cdot)
-%  = 0 \quad
-%  % = f(\cdot ;\weights^{*}) \quad
-%  % K_{\weights_{i}^{*}}(\cdot, \cdot')
-%  k(\cdot, \cdot')
-%  = \frac{1}{\gamma^{2}} \mathbf{J}(\cdot) \mathbf{J}(\cdot')^{T},
-%\end{align}
-%where the kernel is the neural tangent kernel (NTK) \citep{immerImprovingPredictionsBayesian2021},
-%\todo{what mean function shoudl this use???}
-%\todo{NTK times some factor??}
-%with Jacobian given by $\mathbf{J}(\cdot) = \odv{\transitionFn(\cdot; \weights)}{\weights}_{\weights=\weights^{*}}$.
-%% The kernel in \cref{eq-laplace-approx-function-space} is the neural tangent kernel (NTK)
-%% $k(\mathbf{x}, \mathbf{x}') = \sigma_{0}^{2} J_{\weights^{*}}(\mathbf{x}) J_{\weights^{*}}(\mathbf{x}')^{T}$
-%% \citep{immerImprovingPredictionsBayesian2021}
-%% to formulate the GP posterior $p(f(\mathbf{X} ;\weights_{0:i}) \mid \dataset_{0:i})$.
-%Given this GP prior, we can use \cref{eq-gp-predictive-posterior} to obtain our GP posterior by conditioning on the data.
-%% Given our GP prior, we can use the properties of multivariate normals to obtain our GP posterior by conditioning on the data.
-%% where $\mathbf{A} = \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}}$
-%In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
-%Intuitively, we can view the optimisation in \cref{eq-empirical-risk} as learning our kernel.
-%As a result, our NTK may be highly non stationary as it is dependent on the NN architecture, for example, the activation functions.
-%It is worth noting that the NTK linearises the network around the optimised parameters $\weights^{*}$,
-%so the function space prior (and thus posterior) is only a locally linear approximation.
-%
-%We now have a method to obtain a GP posterior from a trained DNN.
-%% In contrast to other approaches, our formulation has not restricted us to using a weight-space posterior obtained from the Laplace approximation.
-%In contrast to other approaches, our formulation has not restricted us to using a weight-space posterior from a BNN.
-%However, in practice, the GP posterior is not very useful as it requires inverting an $N\times N$ matrix which has complexity $\mathcal{O}(N^{3})$.
-%The SVGP in \cref{eq-dual-svgp-predictive-posterior} offers a solution to this problem but it is not immediately clear how to set $\mathbf{m}$ and $\mathbf{V}$.
-%In the next section, we show how we can directly obtain an SVGP posterior (i.e. set $\mathbf{m}$ and $\mathbf{V}$) directly from both
-%1) a trained NN and 2) a BNN weight-space posterior.
-%% $\mathbf{m}$ and $\mathbf{V}$
-%% However, it is not obvious how we can use a SVGP to set $\mathbf{m}$ and $\mathbf{V}$
-%
-%
-%
-%% In contrast, to previous work, this approach did not require us Laplace approximation. we will not restrict our
-%% It is worth noting that the NTK linearises the network around the optimised parameters $\weights^{*}$,
-%% so the function space prior (and thus posterior) is only a locally linear approximation.
-%% In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
-%% It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.
-%
-%
-%\section{Methods}
-%In the next section we show how we can obtain a SVGP directly from 1) a trained NN and 2) a BNN posterior.
-%
-%We follow \cite{csatoSparseOnlineGaussian2002} and express our GP posterior in the dual parameter space.
-%However, we consider the variational formulation introduced by \cite{adamDualParameterizationSparse2021}, where the optimal variational parameters are given by,
-%\begin{align} \label{eq-dual-params}
-%\mathbf{m}^{*} = \mathbf{V}^{*}\bm\alpha^{*} \quad \mathbf{V}^{*} = [\mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} + \bm\beta^{*}]
-%\end{align}
-%Importantly, we can calculate the natural parameters $(\bm\alpha, \bm\beta)$ in closed form,
-%\todo{paul needs to update \cref{eq-dual-svgp-params}}
-%\begin{align} \label{eq-dual-svgp-params}
-%\bm\alpha_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right] \\
-%\bm\beta_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right].
-%\end{align}
-%This simplifies SVGP inference \citep{hensmanGaussian2013} as it no longer requires the variational parameters $(\mathbf{m}, \mathbf{V})$ to be optimised.
-%
-%% Importantly, \cite{changFantasizingDualGPs2022} show that in the dual space,
-%% conditioning on new observations reduces to suming the dual variables from the previous time
-%% step with an update, given by,
-%% \todo{pick best way to show new data (using superscript new or just time indexing?)}
-%% \begin{align} \label{eq-dual-update-svgp}
-%% \bm\alpha_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right] \\
-%% \bm\beta_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right]
-%% \end{align}
-%
-%% We follow \cite{csatoSparseOnlineGaussian2002} and express our GP posterior in the dual parameter space,
-%% % to write GP posterior $p(f(\mathbf{X} ;\weights_{0:i}) \mid \dataset_{0:i})$ as,
-%% \begin{align} \label{eq-gp-post}
-%%   \mathbb{E}_{p(f(\mathbf{x}_{*}) \mid \mathbf{y}_{n})} \left[ f(\mathbf{x}_{*}) \right] &= \mu(\mathbf{x}_{*}) + \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
-%%   \mathbb{V}_{p(f(\mathbf{x}_{*}) \mid \mathbf{y}_{n})} \left[ f(\mathbf{x}_{*}) \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \text{diag}(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
-%% \end{align}
-%% % \begin{align} \label{eq-laplace-approx-function-space}
-%% %   \mathbb{E}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
-%% %   \mathbb{V}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \diag(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
-%% % \end{align}
-%% where the dual parameters $(\bm\alpha_n, \bm\beta_n)$ are vectors of,
-%% \begin{align} \label{eq-gp-dual-params}
-%%   \bm\alpha_{n} \coloneqq \left\{ \mathbb{E}_{p(f(\mathbf{x}_{i}) \mid \mathbf{y}_{n})} \left[ \nabla_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \right\}_{i=1}^{N} \qquad
-%%   \bm\beta_{n} \coloneqq \left\{ \mathbb{E}_{p(f(\mathbf{x}_{i}) \mid \mathbf{y}_{n})} \left[ \nabla^{2}_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \right\}_{i=1}^{N}
-%% \end{align}
-%% Importantly, this parameterisation
-%
-%% \textbf{dual-SVGP}
-%% \begin{align} \label{eq-svgp-post}
-%%   \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ f(\mathbf{x}_{*}) \right] &= \mu(\mathbf{x}_{*}) + \mathbf{k}_{\mathbf{z}*}^{T} \bm\alpha_{\mathbf{u}} \\
-%%   \mathbb{V}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ f(\mathbf{x}_{*}) \right] &= k_{**} - \mathbf{k}_{\mathbf{z}*}^{T} \left[ \mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} - \left( \mathbf{K}_{\mathbf{z} \mathbf{z}} + \bm\beta_{\mathbf{u}} \right)^{-1} \right] \mathbf{k}_{\mathbf{z}*}
-%% \end{align}
-%% % \begin{align} \label{eq-laplace-approx-function-space}
-%% %   \mathbb{E}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
-%% %   \mathbb{V}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \diag(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
-%% % \end{align}
-%% where the dual parameters $(\bm\alpha_{\mathbf{u}}, \bm\beta_{\mathbf{u}})$ are vectors of,
-%% \begin{align} \label{eq-svgp-dual-params}
-%%   \bm\alpha_{\mathbf{u}} \coloneqq \mathbf{k}_{\mathbf{z}i} \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ \nabla_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \qquad
-%%   \bm\beta_{\mathbf{u}} \coloneqq \mathbf{k}_{\mathbf{z}i} \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ \nabla^{2}_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \mathbf{k}_{\mathbf{z}i}^{T}
-%% \end{align}
-%
-%% weight space posterior in \cref{eq-laplace-approx-weight-space} in
-%% function space by linearising the BNN and interpreting it as a GP.
-%% \begin{align} \label{eq-laplace-approx-function-space}
-%%   \transitionFn_{\weights_{i}}(\cdot) &\sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \quad
-%%   \mu_{\weights_{i}^{*}}(\cdot) &= \transitionFn_{\weights^{*}_{i}}(\cdot) \quad
-%%   K_{\weights_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\weights^{*}_{i}}(\cdot) \bm\Sigma_{\weights^{*}_{i}} \mathbf{J}_{\weights^{*}_{i}}(\cdot')^{T}
-%% \end{align}
-%% where the Jacobian is given by $\mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}$.
-%
-%% \begin{align} \label{eq-laplace-approx-jacobian}
-%% \mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}
-%% \end{align}
-%
-%
-%% % Note that the posterior in \cref{eq-laplace-approx-weight-space} is in weight space.
-%% We can represent the weight space posterior in \cref{eq-laplace-approx-weight-space} in
-%% function space by linearising the BNN and interpreting it as a GP.
-%% \begin{align} \label{eq-laplace-approx-function-space}
-%%   \transitionFn_{\weights_{i}^{*}}(\cdot) &\sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \quad
-%%   \mu_{\weights_{i}^{*}}(\cdot) &= \transitionFn_{\weights^{*}_{i}}(\cdot) \quad
-%%   K_{\weights_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\weights^{*}_{i}}(\cdot) \bm\Sigma_{\weights^{*}_{i}} \mathbf{J}_{\weights^{*}_{i}}(\cdot')^{T}
-%% \end{align}
-%% where the Jacobian is given by $\mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}$.
-%
-%% \begin{align} \label{eq-laplace-approx-jacobian}
-%% \mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}
-%% \end{align}
-%
-%
-%\subsection{Fast Updates}
-%Importantly, \cite{changFantasizingDualGPs2022} show that in the dual space,
-%conditioning on new observations reduces to suming the dual variables from the previous time
-%step with an update, given by,
-%\todo{pick best way to show new data (using superscript new or just time indexing?)}
-%\begin{align} \label{eq-dual-update-svgp}
-%\dualParam{1}^{t+1} &\leftarrow \dualParam{1}^{t} +  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))} \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right] \\
-%\dualParam{2}^{t+1} &\leftarrow \dualParam{2}^{t} +  \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))}  \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right]
-%\end{align}
-%Importantly, for a single new observation $((\state_{t}, \action_{t}), \state_{t+1})$ this update has
-%complexity $\mathcal{O}(\numInducing^{2})$.
-%This is a significant improvement to naive GP conditioning, which has complexity $\mathcal{O}((\numDataNew + \numDataOld)^{3})$
-%and sparse GP conditioning, which has complexity $\mathcal{O}((\numDataNew + \numDataOld)\numInducing^{2})$.
-%\todo{double check these complexities are right and cite them/show equaitons}
-%It is worth highlighting that the complexity of \cite{changFantasizingDualGPs2022} update does not increase during an episode.
-%
-%\subsubsection{Model-based RL}
-%
-%\subsubsection{Efficiently Sampling Functions for Posterior Sampling}
-%\cite{wilsonEfficiently2020}
-%\cite{wilsonPathwise2021}
-%
-%% \begin{align} \label{eq-dual-update-svgp}
-%%  \dualParam{1}^{\text{new}} &\leftarrow \dualParam{1}^{\text{old}} +
-%%   \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}))}
-%%  \left[ \log p(\state_{t+1}^{\text{new}} \mid \latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}) ) \right] \\
-%%  \dualParam{2}^{\text{new}} &\leftarrow \dualParam{2}^{\text{old}} +
-%%   \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}))}
-%%  \left[ \log p(\state_t^{\horizon+1} \mid \latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}) ) \right] \\
-%%  \dualParam{1}^{\horizon+1} &\leftarrow \dualParam{1}^{\horizon} +
-%%   \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}
-%%  \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right] \\
-%%  \dualParam{2}^{\horizon+1} &\leftarrow \dualParam{2}^{\horizon} +
-%%   \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}
-%%  \left[ \log p(\state_{\horizon+1} \mid \latentFn(\state_{\horizon}, \action_{\horizon}) ) \right]
-%% \end{align}
-%
-%
-%\begin{assumption} \label{assumption-ntk-linearisation}
-%  Something about NTK being a linearisation around $\theta^{*}_{i}$ but each update moves away from $\theta^{*}_{i}$
-%\end{assumption}
-%
-%\cite{rossellApproximateLaplaceApproximations2021}
 
@@
 
-%
-%\subsection{Model-based Reinforcement Learning (RL)}
-%The goal of reinforcement learning is to find a policy \(\pi \in \Pi\) that maximises the sum of discounted
-%rewards in expecation under the transition noise (aleatoric uncertainty),
-%\begin{align} \label{eq-model-free-objective}
-%\policy^{*} = \arg \max_{\policy \in \policyDomain} J(\transitionFn, \policy) = \arg \max_{\policy \in \policyDomain} \mathbb{E}_{\noise_{0:\infty}} \left[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \right],
-%\end{align}
-%where $\gamma \in [0, 1]$
-%
-%\textbf{Model-based}
-%In Bayesian model-based RL, we obtain the posterior over the dynamics \(p(f\mid\mathcal{D})\) after performing (approximate) Bayesian
-%inference given a state transition data set \(\mathcal{D} = \{\{(s_{t},a_{t}), s_{t+1}\}^{T_{i}}_{t=1}\}_{i=0}^{N}\).
-%\cref{alg-mbrl} shows the typical model-based RL loop.
-%Importantly, the dynamics are usually only updated after an episode $i$.
-%
-%\begin{algorithm}[!b]
-%\caption{Model-based RL}\label{alg-mbrl}
-%\begin{algorithmic}[1]
-%  \Require Start state $\state_{0}$, initial data set $\dataset_{0}$, dynamics posterior $p(\transitionFn \mid \dataset_{0})$, policy $\policy_{0}$
-%\For{$i  \in \{1, 2, \ldots, \text{num episodes} \}$}
-%    \State Reset the system to $\state_{0}$ and reset trajectory buffers $\bm\tau_{t} = \emptyset \ \forall t$
-%    \For{$t  \in \{1, 2, \ldots, \text{num steps} \}$}
-%      % \State Collect  $\tau_{0:t} = \tau_{0:t-1} \cup (\state_{j}, \action_{j}, \state_{j+1}, r_{j+1})$
-%      \State Use \cref{eq-greedy}/\cref{eq-posterior-sampling}/\cref{eq-ucrl} to collect data $\bm\tau_{t} = \bm\tau_{t-1} \cup (\state_{t}, \policy_{i}(\state_{t}), \transitionFn(\state_{t}, \policy_{i}(\state_{t})), r_{t+1})$
-%      % \State Execute policy $\policy_{i}(\state_{t})$ in environment and update trajectory $\tau_{i+1} = \{\state_{j}, \action_{j}, \state_{j+1}, r_{j+1}) \}_{j=0}^{t}$
-%    \EndFor
-%    \State Update data set $\dataset_{0:i} = \dataset_{0:i-1} \cup \tau$
-%    \State Train dynamics $p(\transitionFn \mid \dataset_{0:i}) \leftarrow \text{update\_dynamics}(\dataset_{0:i}, p(\transitionFn \mid \dataset_{0:i-1}))$
-%    % \State Train dynamics $p(\transitionFn \mid \dataset_{0:i+1})$ using $\dataset_{0:i+1}$
-%    % \State Improve policy $\pi_{i+1}$ using $p(\transitionFn \mid \dataset_{0:i+1})$ and/or $\dataset_{0:i+1}$
-%    \State Improve policy $\pi_{i+1} \leftarrow \text{update\_policy}(p\left(\transitionFn \mid \dataset_{0:i}), \dataset_{0:i} \right)$
-%    %\State Improve policy $\pi_{i+1}$ using $p(\transitionFn \mid \dataset_{0:i+1})$ and/or $\dataset_{0:i+1}$
-%\EndFor
-%\end{algorithmic}
-%\end{algorithm}
-%
-%% \begin{minipage}{0.499\textwidth}
-%% \begin{algorithm}[H]
-%% \caption{Model-based RL}\label{alg-mbrl}
-%% \begin{algorithmic}[1]
-%%   \Require Initial data set $\dataset_{0}$, dynamics posterior $p(\transitionFn \mid \dataset_{0})$, policy $\policy_{0}$
-%% \For{$i  \in \{0, 1, \ldots, \text{num episodes} \}$}
-%%     \For{$t  \in \{0, 1, \ldots, \text{num steps} \}$}
-%%       \State Execute policy $\policy_{i}(\state_{t})$ in environment
-%%       \State $\tau_{i+1} = \{\state_{j}, \action_{j}, \state_{j+1}, r_{j+1}) \}_{j=0}^{t}$
-%%     \EndFor
-%%     \State Update data set $\mathcal{D}_{0:i+1} = \mathcal{D}_{0:i} \cup \tau_{i+1}$
-%%     \State Train dynamics $p(\transitionFn \mid \dataset_{0:i+1})$
-%%     \State Improve policy $\pi_{i+1}$
-%%     %\State Improve policy $\pi_{i+1}$ using $p(\transitionFn \mid \dataset_{0:i+1})$ and/or $\dataset_{0:i+1}$
-%% \EndFor
-%% \end{algorithmic}
-%% \end{algorithm}
-%% \end{minipage}
-%% \hfill
-%% \begin{minipage}{0.499\textwidth}
-%% \begin{algorithm}[H]
-%% \caption{Model-based RL with fast updates}\label{alg-mbrl-fast-updates}
-%% \begin{algorithmic}[1]
-%%   \Require Initial data set $\dataset_{0}$, dynamics posterior $p(\transitionFn \mid \dataset_{0})$, policy $\policy_{0}$
-%%     % ${p(\state_{\timeInd+1} \mid \singleInput, \dataset_{0})}$}
-%% \For{$i  \in \{0, 1, \ldots, \text{num episodes} \}$}
-%%     \For{$t  \in \{0, 1, \ldots, \text{num steps} \}$}
-%%       \State Execute policy $\policy_{i}(\state_{t})$ in environment
-%%       % \State Append transition $\state_{t}, \action_{t}, \state_{t+1}, r_{t+1})$ to trajectory $\tau_{i}$
-%%       \State $\tau_{i+1} = \{\state_{j}, \action_{j}, \state_{j+1}, r_{j+1}) \}_{j=0}^{t}$
-%%       \State {\color{blue}Update dynamics $p(\transitionFn \mid \dataset_{0:i} \cup \tau_{i+1})$}
-%%     \EndFor
-%%     \State Update data set $\mathcal{D}_{0:i+1} = \mathcal{D}_{0:i} \cup \tau_{i+1}$
-%%     \State Train dynamics $p(\transitionFn \mid \dataset_{0:i+1})$
-%%     \State Improve policy $\pi_{i+1}$
-%%     %\State Improve policy $\pi_{i+1}$ using $p(\transitionFn \mid \dataset_{0:i+1})$ and/or $\dataset_{0:i+1}$
-%% \EndFor
-%% \end{algorithmic}
-%% \end{algorithm}
-%% \end{minipage}
-%
-%
-%
-%\subsection{Exploration Strategies}
-%\textbf{Greedy exploitation}
-%Given the posterior dynamics \(p(\transitionFn \mid \mathcal{D})\),
-%a common approach is to simply take the expecation over both the aleatoric and epistemic uncertainty,
-%\begin{align} \label{eq-greedy}
-%\policy_{i+1}^{\text{greedy}} = \arg \max_{\policy \in \policyDomain} \mathbb{E}_{\transitionFn \sim p(\transitionFn \mid \dataset_{0:i})} \left[ J(\transitionFn, \policy) \right],
-%\end{align}
-%This approach has been widely adopted, for example, in PILCO, PETS, GP-MPC
-%\cite{deisenrothPILCO2011,chuaDeepReinforcementLearning2018,kamtheDataEfficient2018}.
-%This approach helps to alleviate model bias as the posterior ``knows what the model does not know''.
-%This is because the predictive posterior \(p(f(s_{t},a_{t}) \mid (s_{t},a_{t}),  \mathcal{D} )\) will be (or should be) uncertain when making
-%predictions far away from the training data.
-%The expectation considers all possible dynamics models which prevents the policy optimisation from
-%exploiting innacuracies in the model.
-%This approach has no guarantees for exploration in the general case.
-%However, under specific dynamics and reward structures (e.g. PILCO) this objective can achieve sublinear regret.
-%\todo{need to double check sublinear regret statement. And give a reference}
-%
-%
-%\textbf{Posterior sampling}
-%\cite{osbandWhyPosteriorSampling2017,osbandMoreEfficientReinforcement2013}
-%\begin{align} \label{eq-posterior-sampling}
-%\policy_{i+1}^{\text{PS}} = \arg \max_{\policy \in \policyDomain} \left[ J(\transitionFn, \policy) \right] \quad \text{s.t. } \transitionFn \sim p(\transitionFn \mid \dataset_{0:i})
-%\end{align}
-%
-%\textbf{Hallucinated upper confidence RL}
-%A more theoretically grounded exploration strategy is UCRL \citep{jakschNearoptimal2010}, which optimises joinly over
-%policies and models inside the set
-%\(\mathcal{M} = \{ f \mid | f(s,a) - \mu_{i}(s, a) | \leq \beta_{i} \Sigma_{i}(s, a) \quad \forall s, a \in \mathcal{S} \times \mathcal{A} \}\), representing all statistically plausible
-%models under the posterior \(p(f(s,a) \mid \mathcal{D}_{0:i} \cup (s,a)) = \mathcal{N}(f(s,a) \mid \mu_{i}(s,a), \Sigma_{i}(s,a))\) at episode \(i\).
-%This strategy is given by,
-%\begin{align} \label{eq-ucrl}
-%\policy_{i+1}^{\text{UCRL}} = \arg \max_{\policy \in \policyDomain} \max_{\transitionFn \in \mathcal{M}} J(\transitionFn, \policy).
-%\end{align}
-%This strategy optimises an optimistic policy over the set of plausible dynamics models.
-%Although this joint optimisation is intractable in general,
-%\cite{curiEfficient2020} proposed a practical alternative which is detailed in \cref{sec-hucrl}.
-%
-%\textbf{MPC vs policy learning}
-%It is worth noting that the strategies in \cref{eq-greedy,eq-posterior-sampling,eq-ucrl} can be used with both model predictive control (MPC)
-%techniques, such as the cross entoropy method (CEM), and model-free RL techniques, such as soft actor-critic (SAC).
-%
-%
-%In this work we are interested in how we can use \(p(f \mid \mathcal{D})\) to alleviate some of the issues in model-based RL,
-%for example, model bias and the exploration-exploitation trade-off.
-%
-%
-%
-%\todo{show how to get new $\dualParam{1}$ and $\dualParam{2}$ in Train dynamics line of \cref{alg-mbrl-fast-updates}}
-%\begin{algorithm}[!t]
-%\caption{Model-based RL with fast updates}\label{alg-mbrl-fast-updates}
-%\begin{algorithmic}[1]
-%  \Require Start state $\state_{0}$, initial data set $\dataset_{0}$, dynamics posterior $p(\transitionFn \mid \dataset_{0})$ (inc.
-dual parameters $\dualParam{1}, \dualParam{2}$), policy $\policy_{0}$
-%    % ${p(\state_{\timeInd+1} \mid \singleInput, \dataset_{0})}$}
-%\For{$i  \in \{1, 2, \ldots, \text{num episodes} \}$}
-%    \State Reset the system to $\state_{0}$ and reset trajectory buffers $\bm\tau_{t} = \emptyset \ \forall t$
-%    \For{$t  \in \{1, 2, \ldots, \text{num steps} \}$}
-%      % \State Execute policy $\policy_{i}(\state_{t})$ (\cref{eq-fast-update-mpc}) in environment
-%      \State Use \cref{eq-fast-update-mpc} to collect data $\bm\tau_{t} = \bm\tau_{t-1} \cup (\state_{t}, \policy_{i}(\state_{t}), \transitionFn(\state_{t}, \policy^{\text{fast}}_{i}(\state_{t})), r_{t+1})$
-%      % \State Append transition $\state_{t}, \action_{t}, \state_{t+1}, r_{t+1})$ to trajectory $\tau_{i}$
-%      % \State $\tau_{i+1} = \{\state_{j}, \action_{j}, \state_{j+1}, r_{j+1}) \}_{j=0}^{t}$
-%      %\State {\color{blue}Update dynamics $p(\transitionFn \mid \dataset_{0:i} \cup \tau_{i+1})$}
-%      \State {\color{blue}Update dynamics posterior using \cref{eq-dual-update-svgp}, i.e. fast update}
-%      % \begin{align}
-%      % \dualParam{1}^{t+1} &\leftarrow \dualParam{1}^{t} +  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))} \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right] \\
-%      % \dualParam{2}^{t+1} &\leftarrow \dualParam{2}^{t} +  \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))}  \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right]
-%      % \end{align}}
-%    \EndFor
-%    \State Update data set $\dataset_{0:i} = \dataset_{0:i-1} \cup \tau$
-%    \State Train dynamics $p(\transitionFn \mid \dataset_{0:i}) \leftarrow \text{update\_dynamics}(\dataset_{0:i}, p(\transitionFn \mid \dataset_{0:i-1}))$
-%    \State Improve policy $\pi^{\text{fast}}_{i+1} \leftarrow \text{update\_policy}(p\left(\transitionFn \mid \dataset_{0:i}), \dataset_{0:i} \right)$
-%\EndFor
-%\end{algorithmic}
-%\end{algorithm}
-%
-%
-%\subsubsection{Fast updates}
-%
-%
-%In this section we extend these fast updates to environment's with high dimensional state spaces and large data sets.
-%% Our method draws on the connection between BNNs and GPs and formulates a function space SVGP posterior given
-%Our method uses a BNN dynamic model and draws on the connection between BNNs and GPs
-%\citep{khanApproximate2019} to formulate a function space SVGP posterior,
-%where we can apply the fast updates from \cref{eq-dual-update-svgp}.
-%At a high-level, we first use Laplace's approximation to obtain a weight space posterior for our BNN.
-%We then linearise our BNN around the optimal parameters and interpret it as a GP.
-%Finally, we formulate a lower rank approximation of this GP posterior (i.e. a SVGP posterior) using inducing variables.
-%% formulates a function space SVGP posterior by drawing on the connection between BNNs and GPs.
-%
-%
-%The strategies in \cref{eq-greedy,eq-posterior-sampling,eq-hucrl} do not update the dynamic model during an episode.
-%A better approach would be to update the posterior at every time step during an episode, for example,
-%\begin{subequations}
-%\begin{align} \label{eq-fast-update-mpc}
-%  \policy_{i+1}^{\text{greedy}}(\state) &= \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
-%\E_{p(\transitionFn \mid \dataset_{0:i})} \left[J^{\Horizon}(\action_{0:\Horizon}, \transitionFn) \right] + \stateValueFn(\state_{\Horizon+1}) \\
-%  \policy_{i+1}^{\text{PS}}(\state) &= \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
-%J^{\Horizon}(\action_{0:\Horizon}, \transitionFn) + \stateValueFn(\state_{\Horizon+1}) \quad \text{s.t. } \transitionFn \sim p(\transitionFn \mid \dataset_{0:i} \cup \bm\tau_{t}) \\
-%  \policy_{i+1}^{\text{UCRL}}(\state) &= \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}} \max_{\transitionFn \in \mathcal{M}}
-%J^{\Horizon}(\action_{0:\Horizon}, \transitionFn) + \stateValueFn(\state_{\Horizon+1}) \quad \text{s.t.
-} \mathcal{M} = \{\transitionFn(\state_{t},\action_{t}) - \mu_{i,t}(\state_{t},\action_{t}) \leq \beta_{i,t} \Sigma_{i,t}(\state_{t}, \action_{t})\} \\
-%  \stateValueFn(\state) &= \mathbb{E} \left[ \sum_{t=0}^{\infty}     \discount^{t} \rewardFn(\state_{t},\action_{t}) \mid \state_{0}=\state \right] \label{eq-value-fn}
-%\end{align}
-%\end{subequations}
-%\begin{subequations}
-%\begin{align} \label{eq-fast-update-mpc-old}
-%  \policy^{\text{fast}}(\state) = \arg &\max_{\action_{0}} \max_{\action_{1}, \ldots, \action_{\Horizon}}
-%  \mathbb{E}_{\state_{\horizon} \sim p(\state_{\horizon+1} \mid \transitionFn(\state_{\horizon}, \action_{\horizon}))} \left[ \sum_{\horizon=0}^{\Horizon}     \discount^{\horizon} \rewardFn(\state_{\horizon},\action_{\horizon}) \mid \state_{0}=\state \right] + \discount^{\Horizon+1} \stateValueFn(\state_{\Horizon+1}) \\
-%  \stateValueFn(\state) &= \mathbb{E} \left[ \sum_{t=0}^{\infty}     \discount^{t} \rewardFn(\state_{t},\action_{t}) \mid \state_{0}=\state \right] \label{eq-fast-update-mpc}
-%\end{align}
-%\end{subequations}
-%
-%\begin{align} \label{}
-%  \policy(\state) = \arg &\max_{\action_{0}} \max_{\action_{1}, \ldots, \action_{\Horizon}} \max_{\optimisticTransition \in \optimisticTransitionSet}
-%  \sum_{\horizon=0}^{\Horizon}  \mathbb{E}_{\noise_{\horizon}} \left[  \discount^{\horizon} \rewardFn(\state_{\horizon},\action_{\horizon}) \right] + \discount^{\Horizon+1} \stateValueFn(\state_{\Horizon+1}) \\
-%  \text{s.t. } \state_{\horizon+1} &= \optimisticTransition(\state_{\horizon}, \action_{\horizon}) + \noise_{\horizon} \\
-%  \optimisticTransition(\state_{\horizon}, \action_{\horizon}) &=
-%\optimisticTransitionMean(\state_{\horizon}, \action_{\horizon}) \pm \beta_{i}
-%\optimisticTransitionCov(\state_{\horizon}, \action_{\horizon})
-%\end{align}
-%
-%\input{proof.tex}
-%
-%
-%\section{Hallucinated Upper Confidence Reinforcement Learning (H-UCRL)} \label{sec-hucrl}
-%\cite{curiEfficient2020} introduced a tractable approximation which retains some of the theoretical guarantees whilst
-%being applicable with deep model-based RL.
-%They introduce a function \(\eta: \mathcal{S} \times \mathcal{A} \rightarrow [-1, 1]^{p}\) which acts as a hallucinated control input.
-%The strategy is given by,
-%\begin{align} \label{eq-hucrl}
-%\pi_i^{\text{UCRL}} = \arg \max_{\policy \in \policyDomain} \max_{\eta(\cdot) \in [-1,1]} J(\transitionFn, \policy) \quad \text{s.t.} \quad \transitionFn = \mu_{i}(\state_{t}, \action_{t}) + \beta_{i} \Sigma_{i}(\state_{t}, \action_{t}) \eta(\state_{t},\action_{t}).
-%\end{align}
-%Intuitively, \(\eta(\state,\action) \in [-1,1]\) enables the optimisation to select any dynamics model
-%\(\transitionFn\) within \(\pm \beta \Sigma_{i}(\state_{t}, \action_{t})\) of the posterior mean \(\mu_{i}(\state_{t}, \action_{t})\).
-%
-%\section{Laplace Approximation} \label{sec-laplace-approximation}
-%
-%\textbf{Laplace approximation}
-%The Laplace approximation \todo{add citation of original paper} constructs a Gaussian approximation of the weight-space posterior $p(\weights \mid \dataset)$
-%by using a second-order Taylor expansion of $\mathcal{L}$ around $\weights^{*}$.
-%The posterior approximation is given by,
-%\begin{align} \label{eq-laplace-approx-weight-space}
-%  p(\weights \mid \dataset) \approx \mathcal{N} \left( \weights \mid \weights^{*} , \bm\Sigma_{\weights^{*}} \right)
-%  \quad \text{with} \quad \bm\Sigma_{\weights} =
-% - \nabla_{\weights \weights}^{2} \mathcal{L} ( \dataset ; \weights)|_{\weights=\weights^{*}}
-%\end{align}
-%That is, it sets the posterior precision to the Hessian of the loss at the optimal parameters $\weights^{*}$.
-%It is worth noting that computing the Hessian of the loss can be computationally intractable for large networks.
-%The prior terms are usually trivial, so we focus on the likelihood here.
-%The Jacobian and Hessian of the log likelihood can be expressed per data point,
-%\begin{align} \label{eq-jac}
-%  \nabla_{\weights} \log p(\mathbf{y} \mid \mathbf{f}(\mathbf{x}; \weights)) &= \mathbf{J}(\mathbf{x})^{T} \mathbf{r}(\mathbf{y} ; \mathbf{f}) \\
-%  \nabla^{2}_{\weights\weights} \log p(\mathbf{y} \mid \mathbf{f}(\mathbf{x}; \weights)) &= \mathbf{H}(\mathbf{x})^{T}
-%  \mathbf{r}(\mathbf{y};\mathbf{f}) - \mathbf{J}(\mathbf{x})^{T} \bm\Lambda(\mathbf{y};\mathbf{f}) \mathbf{J}(\mathbf{x}),
-%\label{eq-hess}
-%\end{align}
-%through the Jacobian $\mathbf{J} \in \R^{C \times P}$ and Hessian $\mathbf{H} \in \R^{C \times P \times P}$ of the feature extractor $\mathbf{f}(\mathbf{x}; \bm\weights)$,
-%\begin{align} \label{eq-jac}
-%[\mathbf{J}(\cdot)]_{ci} = \odv{f_{c}(\cdot ; \weights)}{\weights_{i}}_{\weights=\weights^{*}} \qquad
-%[\mathbf{H}(\cdot)]_{cij} = \odv{f_{c}(\cdot ; \weights)}{\weights_{i}\weights_{j}}_{\weights=\weights^{*}}
-%\end{align}
-%where
-%$\mathbf{r}(\mathbf{y}; \mathbf{f}) = \nabla_{\mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$ can be interpreted as a residual and
-%$\bm\Lambda(\mathbf{y} ; \mathbf{f}) = \nabla^{2}_{\mathbf{f} \mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$
-%as per-input noise.
-%Many approximations exist and can be used alongsied our method.
-%We refer the reader to \cite{daxbergerLaplace2021} for more details.
-%See \cref{sec-laplace-approximation} for further details on the Laplace approximation.
-%
-%
-%\section{Experiment details}
-%
-%\subsection{UCI}
-%
-%\begin{table}[t!] 
-%  \centering\scriptsize
-%  \caption{Negative log predictive density (NLPD) (lower better) for the proposed model TODO} 
-%	\label{tbl:uci_all}
-%	% Control table spacing
-%	\renewcommand{\arraystretch}{1.}
-%	\setlength{\tabcolsep}{2pt}
-%	\setlength{\tblw}{0.14\textwidth}  
-%	
-%	% Custom error formatting
-%	\newcommand{\val}[2]{%
-%		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
-%	} 
-%
-%    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
-%	\input{tables/uci_all.tex}
-%\end{table}
-%
-%\section{Template stuff}
-%\subsection{Generate TikZ Figures from Python}
-%We can generate figures in \texttt{.tex} format directly from Python:
-%\begin{verbatim}
-%tikzplotlib.save("fig.tex", axis_width="\\figurewidth", axis_height="\\figureheight")
-%\end{verbatim}
-%\cref{fig:example} shows that we get nicely formatted lables/titles/etc when we include them in our paper.
-%\begin{figure}[h]
-%    \centering\footnotesize
-%
-%    % Set your figure size here
-%    \setlength{\figurewidth}{.33\textwidth}
-%    \setlength{\figureheight}{.75\figurewidth}
-%
-%    % Customize your plot here
-%    % (scale only axis applies the size to the axis box and not entire figure)
-%    \pgfplotsset{grid style={dotted},title={Foo},scale only axis}
-%
-%    % Use the subcaption package (= subfigure) for sub-plots, that is
-%    % plot the separate plots separately in Python
-%    \begin{subfigure}{.4\textwidth}
-%        \centering
-%        \input{./fig/example_fig.tex}
-%    \end{subfigure}
-%    \hfill
-%    \begin{subfigure}{.4\textwidth}
-%        \centering
-%        \input{./fig/example_fig.tex}
-%    \end{subfigure}
-%    \caption{Foo}
-%    \label{fig:example}
-%\end{figure}
-%
-%\subsection{Generate Tables from Python}
-%We can also generate tables straight from python using \href{https://github.com/astanin/python-tabulate}{tabulate}:
-%\begin{verbatim}
-%table = [["Sun",696000,1989100000],["Earth",6371,5973.6],
-%        ["Moon",1737,73.5],["Mars",3390,641.85]]
-%headers = ["Planet","R (km)", "mass (x 10^29 kg)"]
-%table = tabulate(table, headers=headers, tablefmt="latex")
-%with open("table.tex", 'w') as file:
-%    file.write(table)
-%\end{verbatim}
-%
 %\begin{table}[h]

### 2023-05-16 paper/main.tex
Minor
added dual conditionign paragraph

@@
 While efficient, it suffers from cubic scaling in parameter count, necessitating approximations like Kronecker factorisation \cite{martens2015optimizing, ritter2018kfac}.
-This linear model, linear in the weights, refines predictions and provides uncertainty estimates \citep{immer2021scalable}.
+This linear model (linear in the weights) refines predictions and provides uncertainty estimates \citep{immer2021scalable}.
 This model has a convenient interpretation as a GP \cite{immer2021scalable, khan2019approximate, maddox2021fast}.
@@
 More recently \cite{khan2017conjugate,adam2021dual}, has shown this relationship for variational Gaussian processes where the above expectation is with respect to the approximate variational posterior.
-The dual parameter $\valpha$ appears also in non-Bayesian approaches, \eg, support vector machines \citep{cortes1995support}, whose origins are found in work by \citet{kimeldorf1971some}.
-While in \citet{wilkinson2023bayes}, they show links between linearization methods and how they solve the \cref{eq:dual_param}.
+Meanwhile in \citet{wilkinson2023bayes}, they show links between linearization methods and how they solve the \cref{eq:dual_param}.
 
@@
 Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art on CL benchmarks.
-However, they are limited to use subset approximations of the posterior \cref{app:cl-experiment}..
+However, they are limited to use subset approximations of the posterior \cref{app:cl-experiment}.
 %, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer. 
@@
 
+\paragraph{\our for Dual Conditioning} Adding new data to a trained neural network without retraining from scratch is not obvious.
+Some approaches exist \citep{kirsch2022marginal, spiegelhalter1990sequential} but are in the weight space formulation, which makes conditioning harder to formulate.
+As pointed out in \citet{chang2022fantasizing}, dual parameter conditioning updates are straightforward and were the original motivation of \citep{csato2002sparse}.
+It involves integrating data into the sum in \cref{eq:dual_sparse}.
+We thus need to find the data dual variables $\hat{\alpha}$ and $\hat{\beta}$ for the new data subset $\mathcal{D}_\textrm{new} = \{\vx_i,\vy_i\}_{i=1}^{n_{\textrm{new}}}$ and compute the corresponding kernel terms.
+As pointed out in \citet{chang2022fantasizing}, for GPs, these updates are exact if we have a Gaussian likelihood and the kernel remains constant.
+For non-Gaussian likelihoods, the results are almost the same as retraining with all the data.
+Clearly, in practice, given our NN-derived kernel's dependency on the Jacobian of the trained neural network $\Jac{\weights_*}{\vx}$ as we add more data, the Jacobians become outdated.
+But we find we can still improve predictions by conditioning data without retraining.
+[SEE EXPERIMENT ???].
 %%The resulting regularizer can be computed as follows

### 2023-05-16 paper/main.tex
Rewriting CL exp

--- 2023-05-16 paper/main.tex
@@
 \subsection{Updating the  network representation in continual learning}
-%% Very rough draft
-This experiment's section is meant to demonstrate the quality of our sparse representation to retain previous knowledge in the Continual learning setting.
+\label{sec:cl-exp}
+%
+%%% Very rough draft
+%This experiment's section is meant to demonstrate the quality of our sparse representation to retain previous knowledge in the Continual learning setting.
 Unfortunately the CL literature is based on methods that require very diverse set of hyperparameters
-% Idea: it is very difficult to have everything under control, because model changes, settings change, optimizer change, and so on.
+%% Idea: it is very difficult to have everything under control, because model changes, settings change, optimizer change, and so on.
 Then what we did was trying to replicate as close as possible the results for the competing methods by using their codebases where available and choosing the hyperpameters accordingly to their choices.
-
-% Why SH?
-% TODO: there are at least two papers that clearly say MH is unrealistic and too simple as a consequence is not a good way to assess the quality of the method
-
-% Architectures
-We conduct the experiments on a set of three CL benchmarks Sequential-MNIST (S-MNIST), Sequential-FashionMNIST (S-FMNIST), and Permuted-MNIST (P-MNIST).
+%
+%% Why SH?
+%% TODO: there are at least two papers that clearly say MH is unrealistic and too simple as a consequence is not a good way to assess the quality of the method
+%
+%% Architectures
+%We conduct the experiments on a set of three CL benchmarks Sequential-MNIST (S-MNIST), Sequential-FashionMNIST (S-FMNIST), and Permuted-MNIST (P-MNIST).
 Following \cite{rudner2022continual, pan2020continual}, we used a two-layer MLP with 256 hidden units with ReLU activation for S-MNIST and S-FMNIST, and a two-layer with 100 hidden units for P-MNIST.
+%
+%% Methods
+%We compared our method to 1) weight-regularization based methods EWC, SI and VCL (which also has the addition of coresets); 2) function-based regularization based methods DER, FROMP, S-FSVI, SFR; 3) an ablation for which we replace $\bar{\MB}^{-1}$ with an identity matrix $\MI_m$, \ie which is equivalent to assuming a GP with iid realization \todo{Not sure this is 100$\%$ correct}.
+%% Inducing points
+%Following \citep{rudner2022continual}, we use 200 inducing points per tasks % this one can be difficult to justify since S-FSVI samples 200 context points and then iteratively samples 40 coresets points (or at least that's what I got)
+%on all the inducing points, and a lower number of inducing point for S-MNIST, to investigate if our method was still capable of capture more information due to its sparse formulation, as explained in \cref{todo}.
+%
+%%% Questions: Should we also mention the Identity outside when not trained on those classes or just leave that for the appendix?
+
+% Overview
+We aim to highlight our sparse representation's ability to retain prior knowledge within a continual learning (CL) setting (as in \cref{sec:sequential}).
+Notably, CL methods require tuning hyperparameters, making direct comparisons difficult.
+We consider the setup with single-head (SH) setting that is typically hard and more competitive.
+%
+% Benchmarks/architectures
+We consider the CL benchmarks: Sequential-MNIST (S-MNIST), Sequential-FashionMNIST (S-FMNIST), and Permuted-MNIST (P-MNIST).
+We follow the setups described in \cite{rudner2022continual, pan2020continual}, using a two-layer MLP with 256 hidden units and ReLU activation for S-MNIST and S-FMNIST, and a two-layer MLP with 100 hidden units for P-MNIST (full details in \cref{app:cl-exp}).
 
 % Methods
-We compared our method to 1) weight-regularization based methods EWC, SI and VCL (which also has the addition of coresets); 2) function-based regularization based methods DER, FROMP, S-FSVI, SFR; 3) an ablation for which we replace $\bar{\MB}^{-1}$ with an identity matrix $\MI_m$, \ie which is equivalent to assuming a GP with iid realization \todo{Not sure this is 100$\%$ correct}.
-% Inducing points
-Following \citep{rudner2022continual}, we use 200 inducing points per tasks % this one can be difficult to justify since S-FSVI samples 200 context points and then iteratively samples 40 coresets points (or at least that's what I got)
-on all the inducing points, and a lower number of inducing point for S-MNIST, to investigate if our method was still capable of capture more information due to its sparse formulation, as explained in \cref{todo}.
-
-%% Questions: Should we also mention the Identity outside when not trained on those classes or just leave that for the appendix?
+We compare our method against two categories of methods: {\em (i)}~weight-regularization methods: EWC, SI, and VCL (which additionally incorporates coresets), and {\em(ii)}~function-based regularization methods: DER, FROMP, S-FSVI, SFR.
+We also introduce an ablation study where we replace $\bar{\MB}^{-1}$ with an identity matrix $\MI_M$, equivalent to assuming a GP with i.i.d.\ prior.
+Following \cite{rudner2022continual}, we use 200 inducing points per tasks.
+Additionally,  we consider only 40 inducing points for S-MNIST, to investigate if our method was still capable of capture more information due to its sparse formulation.
 
@@
 \subsection{\our for continual learning}
-\label{app:cl-experiment}
+\label{app:cl-exp}
+
 \section{Extending the CL regularizer to multi-class settings}

### 2023-05-16 src/sl/cluster_train.py
initial commit of supervised learning stuff

@@ -1,0 +1,14 @@
+#!/usr/bin/env python3
+import hydra
+from omegaconf import DictConfig
+
+
+@hydra.main(version_base="1.3", config_path="./configs", config_name="main")
+def train(cfg: DictConfig):
+    from src.sl.train import train as train_fn
+
+    train_fn(cfg)
+
+
+if __name__ == "__main__":
+    train()  # pyright: ignore

### 2023-05-16 src/sl/datasets.py

@@ -1,0 +1,360 @@
+#!/usr/bin/env python3
+import os
+import pickle
+import numpy as np
+from sklearn.datasets import make_moons
+import sklearn.model_selection as modsel
+from sklearn.preprocessing import StandardScaler
+import torch
+import torch.utils.data as data
+import torchvision.datasets as dset
+import torchvision.transforms as transforms
+
+# from preds import DATA_DIR
+
+import os
+
+PACKAGE_DIR = os.path.dirname(os.path.realpath(__file__))
+ROOT = "/".join(PACKAGE_DIR.split("/")[:-1])
+print("ROOT {}".format(ROOT))
+DATA_DIR = ROOT + "/data"
+
+CIFAR10_transform = transforms.Compose(
+    [
+        transforms.ToTensor(),
+        transforms.Normalize(
+            (0.49139968, 0.48215841, 0.44653091), (0.24703223, 0.24348513, 0.26158784)
+        ),
+    ]
+)
+
+MNIST_transform = transforms.ToTensor()
+
+
+class SnelsonGen(data.Dataset):
+    def __init__(
+        self,
+        train=True,
+        n_samples=150,
+        s_noise=0.3,
+        random_seed=6,
+        filter_left=True,
+        filter_right=False,
+        root=DATA_DIR,
+        double=False,
+    ):
+        self.train = train
+        self.seed = random_seed if train else random_seed - 1
+        self.n_samples = n_samples
+        self.s_noise = s_noise
+        self.filter_left = filter_left
+        self.filter_right = filter_right
+        with open(root + "/fsnelson.spy", "rb") as file:
+            self.fsnelson = pickle.load(file)
+        X, y = self.generate()
+        if double:
+            self.data = torch.from_numpy(X).double()
+            self.targets = torch.from_numpy(y).double()
+        else:
+            self.data = torch.from_numpy(X).float()
+            self.targets = torch.from_numpy(y).float()
+
+    def generate(self):
+        samples = self.n_samples * 10
+        np.random.seed(self.seed)
+        x_min, x_max = self.x_bounds
+        xs = (x_max - x_min) * np.random.rand(samples) + x_min
+        fs = self.fsnelson(xs)
+        ys = fs + np.random.randn(samples) * self.s_noise
+        if self.filter_left:
+            xfilter = (xs <= 1.5) | (xs >= 2.4)
+            xs, ys = xs[xfilter], ys[xfilter]
[…]

### 2023-05-16 src/sl/train.py

@@ -1,0 +1,273 @@
+#!/usr/bin/env python3
+import logging
+import random
+import time
+from collections import deque, namedtuple
+from pathlib import Path
+
+
+logging.basicConfig(level=logging.INFO)
+logger = logging.getLogger(__name__)
+
+import os
+
+import hydra
+import matplotlib.pyplot as plt
+import numpy as np
+import omegaconf
+import src
+import torch
+from tqdm import tqdm
+import wandb
+from omegaconf import DictConfig, OmegaConf
+from src.rl.utils import set_seed_everywhere
+from src.sl.datasets import CIFAR10, FMNIST, MNIST
+from src.sl.networks import CIFAR10Net, CIFAR100Net, MLPS
+from torch.utils.data import DataLoader
+from torchvision.datasets import VisionDataset
+
+
+torch.set_default_dtype(torch.float64)
+
+PACKAGE_DIR = os.path.dirname(os.path.realpath(__file__))
+ROOT = "/".join(PACKAGE_DIR.split("/")[:-2])
+DATA_DIR = os.path.join(ROOT, "bnn-predictive/data")
+
+
+class QuickDS(VisionDataset):
+    def __init__(self, ds, device):
+        self.D = [
+            (ds[i][0].to(device), torch.tensor(ds[i][1]).to(device))
+            for i in range(len(ds))
+        ]
+        self.K = ds.K
+        self.channels = ds.channels
+        self.pixels = ds.pixels
+
+    def __getitem__(self, index):
+        return self.D[index]
+
+    def __len__(self):
+        return len(self.D)
+
+
+def get_dataset(dataset, double, dir, device=None):
+    if dataset == "MNIST":
+        # Download training data from open datasets.
+        ds_train = MNIST(train=True, double=double, root=dir)
+        ds_test = MNIST(train=False, double=double, root=dir)
+    elif dataset == "FMNIST":
+        ds_train = FMNIST(train=True, double=double, root=dir)
+        ds_test = FMNIST(train=False, double=double, root=dir)
+    elif dataset == "CIFAR10":
+        ds_train = CIFAR10(train=True, double=double, root=dir)
+        ds_test = CIFAR10(train=False, double=double, root=dir)
+    else:
+        raise ValueError("Invalid dataset argument")
+    if device is not None:
+        return QuickDS(ds_train, device), QuickDS(ds_test, device)
+    else:
[…]

### 2023-05-16 paper/main.tex
Modify UCI caption

@@
   \centering\scriptsize
-  \caption{Negative log predictive density (NLPD) (lower better) for the proposed model TODO} 
+  \caption{Negative log predictive density (NLPD) (lower better) for SVGP (sparse GP mean and variance), SVGP NN (NN mean and sparse GP variance), GP subset (subset GP mean and variance) and GP NN subset (NN mean and GP subset variance).
+}
 	\label{tbl:uci}
@@
 SVGP is our method, and the number inside parentheses is the number of inducing points.
-SVGP NN is a modification of our method, where the mean is from the NN directly and the variance is from the GP model}
+SVGP NN is a modification of our method, where the mean is from the NN directly and the variance is from the GP model.}
 	\label{tbl:imagesuper}

### 2023-05-16 paper/main.tex
Wraptable
Table tuning

--- 2023-05-16 paper/main.tex
@@
 \usepackage{derivative}
+\usepackage{wrapfig}
 
@@
 
-% Overview
-We aim to highlight our sparse representation's ability to retain prior knowledge within a continual learning (CL) setting (as in \cref{sec:sequential}).
-Notably, CL methods require tuning hyperparameters, making direct comparisons difficult.
-We consider the setup with single-head (SH) setting that is typically hard and more competitive.
-%
-% Benchmarks/architectures
-We consider the CL benchmarks: Sequential-MNIST (S-MNIST), Sequential-FashionMNIST (S-FMNIST), and Permuted-MNIST (P-MNIST).
-We follow the setups described in \cite{rudner2022continual, pan2020continual}, using a two-layer MLP with 256 hidden units and ReLU activation for S-MNIST and S-FMNIST, and a two-layer MLP with 100 hidden units for P-MNIST (full details in \cref{app:cl-exp}).
-
-% Methods
-We compare our method against two categories of methods: {\em (i)}~weight-regularization methods: EWC, SI, and VCL (which additionally incorporates coresets), and {\em(ii)}~function-based regularization methods: DER, FROMP, S-FSVI, SFR.
-We also introduce an ablation study where we replace $\bar{\MB}^{-1}$ with an identity matrix $\MI_M$, equivalent to assuming a GP with i.i.d.\ prior.
-Following \cite{rudner2022continual}, we use 200 inducing points per tasks.
-Additionally,  we consider only 40 inducing points for S-MNIST, to investigate if our method was still capable of capture more information due to its sparse formulation.
-
-%% Comments on the results:
-We get the best results on S-MNIST both 40 and 200 pts. per task
-
-On S-FMNIST we are on par with DER, which is however exploiting a reservoir buffer technique, that iteratively samples new "inducing points"
-
-On P-MNIST we are lower than S-FSVI, however % I'm still running experiments, so we can hope that it is not the best overall in the end
-
-\begin{table}[t!] 
+\setlength{\columnsep}{8pt}
+\setlength{\intextsep}{0pt}
+\begin{wraptable}{R}{.65\textwidth}
   \centering\scriptsize
-  \caption{
-  TODO: CL Experiments. $^*$ Methods relying only on weight regularization. 
-  \color{blue}{Results from \cite{rudner2022continual}.} 
+  \caption{Continual learning experiments. We report accuracy${\pm}$std and bold based on a $t$-test. $^*$Methods rely on weight regularization.}
+  %\textcolor{blue}{Results from \cite{rudner2022continual}
   %\color{red}{Preliminary results need more runs or hyperparam tuning}
-  }
 	\label{tbl:cl_table_1}
+
 	% Control table spacing
 	\renewcommand{\arraystretch}{1.}
-	\setlength{\tabcolsep}{2pt}
+	\setlength{\tabcolsep}{1pt}
 	\setlength{\tblw}{0.14\textwidth}
@@
 
+	\vspace*{-4pt}
+
+	% Import table content
 	\input{tables/cl_table_1}
-\end{table}
+\end{wraptable}
+%
+% Overview
+We aim to highlight our sparse representation's ability to retain prior knowledge within a continual learning (CL) setting (as in \cref{sec:sequential}).
+Notably, CL methods require tuning making direct comparisons difficult.
+We consider the setup with single-head (SH) setting that is typically hard and more competitive.
+%
+% Benchmarks/architectures
+We consider the CL benchmarks: Sequential-MNIST (S-MNIST), Sequential-FashionMNIST (S-FMNIST), and Permuted-MNIST (P-MNIST).
+We follow the setups described in \cite{rudner2022continual, pan2020continual}, using a two-layer MLP with 256 hidden units and ReLU activation for S-MNIST and S-FMNIST, and a two-layer MLP with 100 hidden units for P-MNIST (full details in \cref{app:cl-exp}).
+
+% Methods
+We compare our method against two categories of methods: {\em (i)}~weight-regularization methods: EWC, SI, and VCL (which additionally incorporates coresets), and {\em(ii)}~function-based regularization methods: DER, FROMP, S-FSVI, SFR.
+We also introduce an ablation study where we replace $\bar{\MB}^{-1}$ with an identity matrix $\MI_M$, equivalent to assuming a GP with i.i.d.\ prior (giving an L2 regularizer).
+Following \cite{rudner2022continual}, we use 200 inducing points per tasks.
+Additionally,  we consider only 40 inducing points for S-MNIST, to investigate if our method was still capable of capture more information due to its sparse formulation.
+
+%% Comments on the results:
+\cref{tbl:cl_table_1} shows results
+We get the best results on S-MNIST both 40 and 200 pts. per task
+
+On S-FMNIST we are on par with DER, which is however exploiting a reservoir buffer technique, that iteratively samples new "inducing points"
+
+On P-MNIST we are lower than S-FSVI, however % I'm still running experiments, so we can hope that it is not the best overall in the end
 

### 2023-05-16 paper/main.tex
RL

@@
 \subsection{Supervised learning on image data sets}
+\label{sec:image}
 
@@
 
-In this section, we show that \our's uncertainty estimates can be used to guide exploration in model-based RL;
-demonstrating the quality of our uncertainty estimates.
-% Uncertainty-guided decision making strategies
-We test \our by using it to learn a dynamics model within a model-based RL strategy which uses posterior sampling to guide exploration
-\cite{osbandMoreEfficientReinforcement2013,osbandWhyPosteriorSampling2017}.
-We use the cart pole swing up task in MuJoCo \cite{todorov2012mujoco}, a classic benchmark for nonlinear control, see \cref{fig:rl}.
+% Make custom TikZ command (argument: colour)
+\newcommand{\lab}[1]{\tikz[baseline=-.8ex]{\node[minimum width=2em,minimum height=.8em,fill=#1,opacity=.1](a){};\draw[#1,thick](a.west)--(a.east);}}
+
+% The methods
+\definecolor{darkgray176}{RGB}{176,176,176} % darkgray176
+\definecolor{color-our}{RGB}{0,191,191} %darkturquoise0191191
+\definecolor{color-mlp}{RGB}{191,0,191} % darkviolet1910191
+\definecolor{color-ddpg}{RGB}{191,191,0} % goldenrod1911910
+\definecolor{green01270}{RGB}{0,127,0} % green01270
+\definecolor{lightgray204}{RGB}{204,204,204} % lightgray204
+
+As a final experiment, we demonstrate the capability of \our to use its uncertainty estimates as guidance for exploration in model-based reinforcement learning (RL); this serves as a practical test to the quality of our uncertainty estimates.
+We use \our to help learn a dynamics model within a model-based RL strategy that employs posterior sampling to guide exploration \cite{osbandMoreEfficientReinforcement2013,osbandWhyPosteriorSampling2017}.
+%
+We use the cartpole swingup task in MuJoCo \cite{todorov2012mujoco}, a classic benchmark for nonlinear control (see \cref{fig:rl}).
 The goal is to swing the pole up and balance it around the upward position.
 We increase the difficulty of exploration by using a sparse reward function.
-We refer the reader to \cref{app:rl} for an overview of the reinforcement learning problem, details of the algorithim we implement and our experiment's configuration.
+See \cref{app:rl} for an overview of the reinforcement learning problem, details of the algorithm, and the experiment setup.
 
@@
 To ensure a fair comparison, we use the same MLP architecture/training scheme and use them in the same model-based RL algorithm, detailed in \cref{app:rl}.
-% that \our's uncertainty estimates are useful for guiding exploration as it converges in fewer episodes.
 We also compare to deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016}, a model-free RL algorithim (yellow).
@@
 it is more sample efficient.
-As expected, the MLP strategy (without uncertainty) was not able to successfuly explore the environment.
+As expected, the MLP strategy (without uncertainty) was not able to successfuly explore the environment.(\lab{color-our}), (\lab{color-mlp}),
 
@@
 
- \todo{I'm thinking we should take out the SFR with updates result}
 \begin{figure}[!t]
+ \centering\scriptsize
+ \begin{subfigure}[c]{.24\textwidth}
  \centering
- \begin{subfigure}[c]{.24\textwidth}
+ \textbf{Cartpole swingup setup}\\[1em]
  \resizebox{\textwidth}{!}{%
@@
  \begin{subfigure}[c]{.74\textwidth}
-   \centering\scriptsize
+   \raggedleft\scriptsize
    \setlength{\figurewidth}{\textwidth}

### 2023-05-16 src/sl/train.py
train script running

@@ -91,7 +91,7 @@ def evaluate(model, data_loader, device):
     loss, loss_mean, acc = 0, 0, 0
     with torch.no_grad():
         for X, y in data_loader:
-            X, y = X.to(device), y.to(device)
+            # X, y = X.to(device), y.to(device)
             fs = model(X)
             acc += (torch.argmax(fs, dim=-1) == y).sum().cpu().float().item()
             loss += criterion(fs, y).item()
@@ -177,7 +177,7 @@ def train(cfg: DictConfig):
     # print("DATA_DIR {}".format(DATA_DIR))
     # logger.info("cfg {}".format(cfg))
     ds_train, ds_test = src.sl.train.get_dataset(
-        dataset=cfg.dataset, double=True, dir="./", device="cpu"
+        dataset=cfg.dataset, double=True, dir="./", device=cfg.device
     )
     # print("ds_train {}".format(ds_train.D[0].shape))
     # print("ds_train {}".format(ds_train.D[1].shape))
@@ -215,10 +215,10 @@ def train(cfg: DictConfig):
     # print("ntksvgp {}".format(ntksvgp))
 
     train_loader = DataLoader(
-        ds_train, batch_size=cfg.batch_size, shuffle=True, num_workers=cfg.num_workers
+        ds_train, batch_size=cfg.batch_size, shuffle=True
     )
     test_loader = DataLoader(
-        ds_test, batch_size=cfg.batch_size, shuffle=False, num_workers=cfg.num_workers
+        ds_test, batch_size=cfg.batch_size, shuffle=False
     )
 
     optimizer = torch.optim.Adam([{"params": sfr.parameters()}], lr=cfg.lr)

### 2023-05-16 src/sl/train.py
add set seed everywhere

@@ -20,7 +20,8 @@ import torch
 from tqdm import tqdm
 import wandb
 from omegaconf import DictConfig, OmegaConf
-from src.rl.utils import set_seed_everywhere
+
+# from src.rl.utils import set_seed_everywhere
 from src.sl.datasets import CIFAR10, FMNIST, MNIST
 from src.sl.networks import CIFAR10Net, CIFAR100Net, MLPS
 from torch.utils.data import DataLoader
@@ -32,6 +33,20 @@ torch.set_default_dtype(torch.float64)
 PACKAGE_DIR = os.path.dirname(os.path.realpath(__file__))
 ROOT = "/".join(PACKAGE_DIR.split("/")[:-2])
 DATA_DIR = os.path.join(ROOT, "bnn-predictive/data")
+
+
+def set_seed_everywhere(random_seed):
+    random.seed(random_seed)
+    np.random.seed(random_seed)
+    torch.manual_seed(random_seed)
+    torch.cuda.manual_seed(random_seed)
+    torch.manual_seed(random_seed)
+    # torch.cuda.manual_seed(cfg.random_seed)
+    # torch.backends.cudnn.deterministic = True
+    # torch.backends.cudnn.benchmark = False
+    np.random.seed(random_seed)
+    random.seed(random_seed)
+    # pl.seed_everything(random_seed)
 
 
 class QuickDS(VisionDataset):
@@ -214,12 +229,8 @@ def train(cfg: DictConfig):
     # ntksvgp = hydra.utils.instantiate(cfg.ntksvgp)
     # print("ntksvgp {}".format(ntksvgp))
 
-    train_loader = DataLoader(
-        ds_train, batch_size=cfg.batch_size, shuffle=True
-    )
-    test_loader = DataLoader(
-        ds_test, batch_size=cfg.batch_size, shuffle=False
-    )
+    train_loader = DataLoader(ds_train, batch_size=cfg.batch_size, shuffle=True)
+    test_loader = DataLoader(ds_test, batch_size=cfg.batch_size, shuffle=False)
 
     optimizer = torch.optim.Adam([{"params": sfr.parameters()}], lr=cfg.lr)
 
@@ -244,6 +255,7 @@ def train(cfg: DictConfig):
             wandb.log({"test/loss_mean": te_loss_mean})
             wandb.log({"training/acc": tr_acc})
             wandb.log({"test/acc": te_acc})
+        wandb.log({"epoch": epoch})
 
     logger.info("Finished training")
     # # evaluation

### 2023-05-16 paper/main.tex

@@
 
-\paragraph{\our for Dual Conditioning} Adding new data to a trained neural network without retraining from scratch is not obvious.
+\paragraph{\our for dual conditioning} Adding new data to a trained neural network without retraining from scratch is a non-trivial problem.
 Some approaches exist \citep{kirsch2022marginal, spiegelhalter1990sequential} but are in the weight space formulation, which makes conditioning harder to formulate.
-As pointed out in \citet{chang2022fantasizing}, dual parameter conditioning updates are straightforward and were the original motivation of \citep{csato2002sparse}.
-It involves integrating data into the sum in \cref{eq:dual_sparse}.
-We thus need to find the data dual variables $\hat{\alpha}$ and $\hat{\beta}$ for the new data subset $\mathcal{D}_\textrm{new} = \{\vx_i,\vy_i\}_{i=1}^{n_{\textrm{new}}}$ and compute the corresponding kernel terms.
-As pointed out in \citet{chang2022fantasizing}, for GPs, these updates are exact if we have a Gaussian likelihood and the kernel remains constant.
+As pointed out in \cite{chang2022fantasizing}, dual parameter conditioning updates are straightforward and were the original motivation of \cite{csato2002sparse}.
+This involves integrating data into the sum in \cref{eq:dual_sparse}.
+Thus, we need to find the data dual variables $\hat{\alpha}$ and $\hat{\beta}$ for the new data subset $\mathcal{D}_\textrm{new} = \{\vx_i,\vy_i\}_{i=1}^{n_{\textrm{new}}}$ and compute the corresponding kernel terms.
+As pointed out in \cite{chang2022fantasizing}, for GPs, these updates are exact under a Gaussian likelihood and the kernel remains constant.
 For non-Gaussian likelihoods, the results are almost the same as retraining with all the data.
@@
 But we find we can still improve predictions by conditioning data without retraining.
-[SEE EXPERIMENT ???].
+%[SEE EXPERIMENT ???].
 %%The resulting regularizer can be computed as follows

### 2023-05-16 paper/main.tex
added dual conditionign paragraph
updated cl notation

@@
   \label{eq:dual_param}
-  \alpha_i \coloneqq \myexpect_{p(\vw \mid \vy)}[\nabla_{f_i}\log p(y_i \mid f_i)]
+  \alpha_i \coloneqq \myexpect_{p(\vw \mid \vy)}[\nabla_{f}\log p(y_i \mid f) |_{f=f_i}]
   \quad \text{and} \quad
-  \beta_i \coloneqq - \myexpect_{p(\vw \mid \vy)}[\nabla^2_{f_i f_i}\log p(y_i \mid f_i)] .
-\end{equation}
-%
+  \beta_i \coloneqq - \myexpect_{p(\vw \mid \vy)}[\nabla^2_{f f}\log p(y_i \mid f_i) |_{f=f_i}],
+\end{equation}
+%
+where $f_\vw(\vx_i) = f_i$ above.
 The relationships specified above are valid for generic likelihoods, and involve no approximations since the expectation is under the exact posterior.
@@
 %
-where $\MKzz$ and $\vkzi$ are the gram matrix and vector computed on the inducing points $\MZ_t = \{\vz_i\}_{i=1}^M$ for task $t$ .\
-%
-We keep a memory buffer $\mathcal{M} = \{(\MZ_t, \vu_t, \bar{\MB}^{-1}_t)\}_{t=1}^T$, where $\MZ_t$ are the inducing points selected from $\dataset_t$ and  $\vu_t = f_{\vw_t^*}(\MZ_t)\in \R^{M}$ are the neural network outputs associated to them, computed with the MAP estimate $\weights_t^*$ after task $t$.
-Note that, for notational convenience, we are extending our neural network notation to be compatible with multiple inputs points, \ie, each $i$\textsuperscript{th} entry is $f_{\weights_t^*}(\vz_i)\in \R$.
-Moreover, we restrict ourselves to single-output neural networks and refer the reader to further details on the multi-output setting to \cref{sec:cl_multioutput}.
+where $\MKzz$ and $\vkzi$ are the gram matrix and vector computed on the inducing points $\mathcal{Z}_t = \{\vz_i\}_{i=1}^M$ selected from $\dataset_t$.\
+%
+We keep a memory buffer $\mathcal{M} = \{(\mathcal{Z}_t, \vu_t, \bar{\MB}^{-1}_t)\}_{t=1}^T$, where $\vu_t \in \R^{M}$ is a vector with entries $u_{t, i} = f_{\vw_t^*}(\vz_i), \forall \vz_i \in \mathcal{Z}_t$ are the neural network outputs computed on the inducing points with the MAP estimate $\weights_t^*$ after task $t$.
+For notational convenience, we restrict here to single-output neural networks and refer the reader to further details on the multi-output setting to \cref{sec:cl_multioutput}.
 
 After each task, we update $\mathcal{M}$, and we can construct a regularizer term, which aims to reduce the drift of the current model from diverging on the inducing points $\MZ_s$ for all previous tasks $ s = 1, \ldots, t-1$.
-This means that for training  the successive task, the new objective to minimize becomes $\weights_t^* = \arg\min_{\weights} \mathcal{L}(\mathcal{D}_t, \weights) + \tau \, \mathcal{R}_\textrm{\our}(\weights, \mathcal{M})$, with the regularizer
+This means that for training  the successive task, the new objective to minimize becomes $\weights_t^* = \arg\min_{\weights} \mathcal{L}(\mathcal{D}_t, \weights) + \tau \, \mathcal{R}_\textrm{\our}(\weights, \mathcal{M})$, with weight $\tau$ and regularizer
 %
@@
 	\left\lVert 
-	f_{\weights}(\MZ_{s}) - \vu_t % f_{\weights_{s}}(\MZ_s)
-	\right\rVert_{\bar{\MB}^{-1}_{s}}.
+	\vu_t - \vu_s % f_{\weights_{s}}(\MZ_s)
+	\right\rVert_{\bar{\MB}^{-1}_{s}}, \quad \vu_t \in \R^M, \text{with } u_{s,i} = f_{\weights}(\vz_{i}) \forall {\vz_i} \in \mathcal{Z}_s .
 \end{equation}

### 2023-05-16 paper/main.tex
Minor

--- 2023-05-16 paper/main.tex
@@
 This involves integrating data into the sum in \cref{eq:dual_sparse}.
-Thus, we need to find the data dual variables $\hat{\alpha}$ and $\hat{\beta}$ for the new data subset $\mathcal{D}_\textrm{new} = \{\vx_i,\vy_i\}_{i=1}^{n_{\textrm{new}}}$ and compute the corresponding kernel terms.
+Thus, we need to find the data dual variables $\hat{\alpha}$ and $\hat{\beta}$ for the new data subset $\mathcal{D}_\textrm{new} = \{\vx_i,\vy_i\}_{i=1}^{N_{\textrm{new}}}$ and compute the corresponding kernel terms.
 As pointed out in \cite{chang2022fantasizing}, for GPs, these updates are exact under a Gaussian likelihood and the kernel remains constant.

### 2023-05-16 paper/main.tex
WIP

@@
 On P-MNIST we are lower than S-FSVI, however % I'm still running experiments, so we can hope that it is not the best overall in the end
+
+\cref{fig:rl} shows training curves for using \our as the dynamic model (cyan), along with a Laplace-GGN with GLM predictions (red), an ensemble of neural networks (green), and a basic MLP without uncertainty (magenta).
+To ensure an equitable comparison, we maintain the same MLP architecture/training scheme across all these methods and incorporate them into the same model-based RL algorithm, as detailed in \cref{app:rl}.
+We also compare our results with Deep Deterministic Policy Gradient (DDPG) \cite{lillicrapContinuousControlDeep2016}, a model-free RL algorithm (yellow).
+
+The training curves clearly show that \our's uncertainty estimates are instrumental in guiding exploration as it converges in fewer episodes, which demonstrates higher sample efficiency.
+As anticipated, the MLP strategy, devoid of uncertainty, was unable to successfully explore the environment."
 

### 2023-05-16 paper/main.tex
Minor fixes in CL

@@
 %
-We keep a memory buffer $\mathcal{M} = \{(\mathcal{Z}_t, \vu_t, \bar{\MB}^{-1}_t)\}_{t=1}^T$, where $\vu_t \in \R^{M}$ is a vector with entries $u_{t, i} = f_{\vw_t^*}(\vz_i), \forall \vz_i \in \mathcal{Z}_t$ are the neural network outputs computed on the inducing points with the MAP estimate $\weights_t^*$ after task $t$.
-For notational convenience, we restrict here to single-output neural networks and refer the reader to further details on the multi-output setting to \cref{sec:cl_multioutput}.
+We keep a memory buffer $\mathcal{M} = \{(\mathcal{Z}_t, \vu_t, \bar{\MB}^{-1}_t)\}_{t=1}^T$, where $\vu_t \in \R^{M}$ is a vector with entries $u_{t, i} = f_{\vw_t^*}(\vz_i), \forall \vz_i \in \mathcal{Z}_t$, are the neural network outputs computed on the inducing points with the MAP estimate $\weights_t^*$ after task $t$.
+For notational convenience, we restrict ourselves here to single-output neural networks and refer the reader to \cref{sec:cl_multioutput} for details on the multi-output setting.
 
@@
 	\vu_t - \vu_s % f_{\weights_{s}}(\MZ_s)
-	\right\rVert_{\bar{\MB}^{-1}_{s}}, \quad \vu_t \in \R^M, \text{with } u_{s,i} = f_{\weights}(\vz_{i}) \forall {\vz_i} \in \mathcal{Z}_s .
+	\right\rVert_{\bar{\MB}^{-1}_{s}}, \quad \vu_t \in \R^M \text{~with~} u_{s,i} = f_{\weights}(\vz_{i}),~\forall {\vz_i} \in \mathcal{Z}_s .
 \end{equation}

### 2023-05-16 paper/main.tex
WIP

@@
 
-\cref{fig:rl} shows training curves for using \our as the dynamic model (cyan), along with a Laplace-GGN with GLM predictions (red), an ensemble of neural networks (green), and a basic MLP without uncertainty (magenta).
-To ensure an equitable comparison, we maintain the same MLP architecture/training scheme across all these methods and incorporate them into the same model-based RL algorithm, as detailed in \cref{app:rl}.
-We also compare our results with Deep Deterministic Policy Gradient (DDPG) \cite{lillicrapContinuousControlDeep2016}, a model-free RL algorithm (yellow).
-
-The training curves clearly show that \our's uncertainty estimates are instrumental in guiding exploration as it converges in fewer episodes, which demonstrates higher sample efficiency.
-As anticipated, the MLP strategy, devoid of uncertainty, was unable to successfully explore the environment."
-
 \subsection{Reinforcement learning under sparse rewards}
@@
 As expected, the MLP strategy (without uncertainty) was not able to successfuly explore the environment.(\lab{color-our}), (\lab{color-mlp}),
+
+%\cref{fig:rl} shows training curves for using \our as the dynamic model (cyan), along with a Laplace-GGN with GLM predictions (red), an ensemble of neural networks (green), and a basic MLP without uncertainty (magenta).
+To ensure an equitable comparison, we maintain the same MLP architecture/training scheme across all these methods and incorporate them into the same model-based RL algorithm, as detailed in \cref{app:rl}.
+We also compare our results with Deep Deterministic Policy Gradient (DDPG) \cite{lillicrapContinuousControlDeep2016}, a model-free RL algorithm (yellow).
+%
+%The training curves clearly show that \our's uncertainty estimates are instrumental in guiding exploration as it converges in fewer episodes, which demonstrates higher sample efficiency.
+As anticipated, the MLP strategy, devoid of uncertainty, was unable to successfully explore the environment.
 

### 2023-05-16 paper/main.tex
RL exp

--- 2023-05-16 paper/main.tex
@@
 % Make custom TikZ command (argument: colour)
-\newcommand{\lab}[1]{\tikz[baseline=-.8ex]{\node[minimum width=2em,minimum height=.8em,fill=#1,opacity=.1](a){};\draw[#1,thick](a.west)--(a.east);}}
+\newcommand{\lab}[1]{\tikz[baseline=-.5ex]{\node[minimum width=1.5em,minimum height=.8em,fill=#1,opacity=.1](a){};\draw[#1,thick](a.west)--(a.east);}}
 
@@
 
-\cref{fig:rl} shows training curves using \our as the dynamic model (cyan) as well as a Laplace-GGN with GLM predictions (red), an ensemble of neural
-networks (green) and a basic MLP wih no uncertainty (magenta).
+%\cref{fig:rl} shows training curves using \our as the dynamic model (cyan) as well as a Laplace-GGN with GLM predictions (red), an ensemble of neuralnetworks (green) and a basic MLP wih no uncertainty (magenta).
 To ensure a fair comparison, we use the same MLP architecture/training scheme and use them in the same model-based RL algorithm, detailed in \cref{app:rl}.
@@
 it is more sample efficient.
-As expected, the MLP strategy (without uncertainty) was not able to successfuly explore the environment.(\lab{color-our}), (\lab{color-mlp}),
+As expected, the MLP strategy (without uncertainty) was not able to successfuly explore the environment.(), (\lab{color-mlp}),
+
+\cref{fig:rl} shows training curves for using \our as the dynamic model (\lab{color-our}), along with a Laplace-GGN~\cite{ADD} with GLM predictions (\lab{black})\todo{Arno cannot see these colour, someone help}, an ensemble of neural networks (\lab{black}), and a basic MLP without uncertainty (\lab{color-mlp}).
+To ensure a fair comparison, we maintain the same MLP architecture/training scheme across all these methods and incorporate them into the same model-based RL algorithm (see \cref{app:rl}).
+We also compare our results with Deep Deterministic Policy Gradient (DDPG, \cite{lillicrapContinuousControlDeep2016}), a model-free RL algorithm (\lab{color-ddpg}).
+%
+The training curves clearly show that \our's uncertainty estimates help exploration as it converges in fewer episodes, demonstrating higher sample efficiency.
+As expected, the MLP strategy (without uncertainty) was not able to successfuly explore the environment.
 

### 2023-05-16 paper/main.tex
RL exp

@@
 % Make custom TikZ command (argument: colour)
-\newcommand{\lab}[1]{\tikz[baseline=-.5ex]{\node[minimum width=1.5em,minimum height=.8em,fill=#1,opacity=.1](a){};\draw[#1,thick](a.west)--(a.east);}}
+\newcommand{\lab}[1]{\protect\tikz[baseline=-.5ex]{\protect\node[minimum width=1.5em,minimum height=.8em,fill=#1,opacity=.1](a){};\protect\draw[#1,thick](a.west)--(a.east);}}
 
@@
  \hfill
- \caption{\textbf{Cartpole swingup with sparse reward} Training curves showing that \our's uncertainty estimates improve sample efficiency in RL.
-   Our method (blue/green) converges in fewer environment steps than the baseline model-based RL method (magenta) and DDPG, the model-free baseline (yellow).}
+ \caption{\textbf{Cartpole swingup with sparse reward.} Training curves showing that \our's uncertainty estimates improve sample efficiency in RL.
+   Our method (\lab{color-our}) converges in fewer environment steps than the baseline model-based RL method (\lab{black}) and DDPG, the model-free baseline (\lab{black}).}
  \label{fig:rl}

### 2023-05-16 paper/main.tex
intro

@@
 These methods rely on the linearization of the neural network and the resultant NTK \cite{jacot2018neural}.
-The result function space neural network is characterized by its first two moment functions, a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}).
+The function space neural network is characterized by its first two moment functions, a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}).
 GPs provide a widely-used probabilistic toolkit with principled uncertainty estimates, and they serve as a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} with theoretical guarantees on regret bounds \citep{srinivas2009gaussian}.
@@
 %Need for adaptive learning methods + failures with current methods
-In this paper, we demonstrate that any neural network can be represented in terms of the so-called `dual' parameters of a GP~\cite{csato2002sparse, adam2021dual, chang2020fast}.
-In contrast to previous work that utilizes subsets \cite{immer2021scalable}, this parameterization allows for the consolidation of contributions from {\em all} training data into a sparse representation.
-Crucially, the resulting GP now predicts in the same space as the originally trained neural network, a feature not present in previous approaches, while still avoiding the notorious cubic complexity of vanilla GPs.
-Through the dual parameter formulation, we establish a connection between the neural network, the resulting full GP, and a sparse approximation similar to variational sparse GPs~\cite{titsias2009variational}.
-Using the sparse GP we can then take advantage of the property of dual parameters that allows for fast conditioning recently shown in \cite{chang2022fantasizing}.
-Thus we are able to avoid retraining and condition new data in to our model (see \cref{fig:teaser}).
-The resulting \our method can be applied in any sequential decision-making scenario where retraining is not feasible.
-
+Given an approximate inference technique, we demonstrate that the neural network emits`dual' parameters which are the building blocks of a GP~\cite{csato2002sparse, adam2021dual, chang2020fast}.
+In contrast to previous work that utilizes subsets \cite{immer2021scalable}, this parameterization allows consolidating contributions from {\em all} training data into a sparse representation, essential for predictive uncertainty.
+Crucially, the resulting GP now predicts in the same space as the original trained neural network, a feature not present in previous approaches, while avoiding the notorious cubic complexity of vanilla GPs.
+Through the dual parameter formulation, we establish a connection between the neural network, full GPs, and a sparse approximation similar to sparse variational GPs~\cite{titsias2009variational}.
+We call our method \our.
+A sparse GP derived from a trained neural network.
+As \our is in the dual parameters, we can perform dual conditioning recently shown effective in \cite{chang2022fantasizing}, that is, avoid retraining and condition new data into our model (see \cref{fig:teaser}).
 %Need uncertainty and adaptive methods
@@
 %
-{\em (i)}~We introduce \our, a new approach for sparse functional representation of the neural network.
-{\em (ii)}~We demonstrate that, despite its sparsity, our method effectively captures predictive uncertainty, provides means of updating the model post-training, and gives a a compact representation suitable for continual learning.
+{\em (i)}~We introduce \our, a new approach for building a sparse functional representation of a neural network.
+{\em (ii)}~We demonstrate that, despite its sparsity, our method effectively captures predictive uncertainty, provides means of updating the model post-training, and gives a a compact regularizer suitable for continual learning.
 {\em (iii)}~We provide extensive experiments for showcasing our approach and demonstrate significance and applicability across supervised, continual, and reinforcement learning, aiming to stimulate future use of the approach.

### 2023-05-16 paper/main.tex
experiments

@@
 In \cref{eq-laplace-approx-function-space}, we restrict the function output to a single dimension for notational simplicity, yet this formulation can be readily extended to the multi-output scenario.
-With this kernel function, we can combine it with the data set $\dataset$ to construct the posterior $q(\vf)$.
-%
-\citet{khan2019approximate} took a similar approach, but instead of fitting the GP posterior to the actual $\vy$, they rely on a transformation of $\vy$ referred as {\em pseudo}-data.
+With this kernel function, we can combine it with the data set $\dataset$ to construct the posterior.
+%
+\citet{khan2019approximate} took a similar approach, but instead of fitting the GP posterior to the actual $\vy$, they rely on a transformation of $\vy$.
 Similarly, \citet{immer2021improving} obtain the same covariance function but use a different mean because they rely on a first-order approximation of the neural network to form a Bayesian GLM model.
@@
 
-\section{\our: Sparse function-space represenation of neural networks}
+\section{\our: Sparse function-space representation of neural networks}
 %\paragraph{GP in the dual parameters}
@@
 %
-where $f_\vw(\vx_i) = f_i$ above.
-The relationships specified above are valid for generic likelihoods, and involve no approximations since the expectation is under the exact posterior.
-This higlights the fact that our approximate inference technique that will follow, while usually viewed as a posterior approximation, can be alternatively interpreted as an approximation of the expectation of gradients of loss/likelihoods.
+where $f_\vw(\vx_i) = f_i$ is the function output at input $\vx_i$.
+The relationships specified are valid for generic likelihoods, and involve no approximations since the expectation is under the exact posterior.
+\cref{eq:gp_pred} and \cref{eq:dual_param} highlight that the approximate inference technique, usually viewed as a posterior approximation, can be alternatively interpreted as an approximation of the expectation of gradients of loss/likelihoods.
 
@@
 \end{equation}
-where $\MKzz$ and $\vkzs$ are defined similarly to $\MKxx$ and $\vk_{\vx i}$ but over the inducing points $\{\vz_j\}_{i=1}^M$, $\vz \in \R^{D}$ \todo{These are already defined}, instead of the full data set $\dataset$.
-The key quantities we need to make predictions from our sparse GP from the converged neural network are $(\hat{\alpha}_i, \hat{\beta}_i)$ \cref{eq:dual_param_laplace} and a kernel function $\kappa$ .
+where $\MKzz$ and $\vkzs$ are defined similarly to $\MKxx$ and $\vk_{\vx i}$ but over the inducing points $\{\vz_j\}_{i=1}^M$, $\vz \in \R^{D}$, instead of the full data set $\dataset$.
+The key quantities we need to make predictions from our sparse GP from the converged neural network are $(\hat{\alpha}_i, \hat{\beta}_i)$ (\cref{eq:dual_param_laplace}) and a kernel function $\kappa$ (\cref{eq-laplace-approx-function-space}).
 Contrasting \cref{eq:dual_sparse_post} and \cref{eq:gp_pred}, we can see that the computational complexity went from $\mathcal{O}(N^3)$ to $\mathcal{O}(M^3)$, with $M \ll N$.
@@
 Unlike our approach, \citet{immer2021improving} employ a subset of the data points to construct a sparse GP model, reducing computational complexity.
-However, this method could be considered less principled for building a sparse model, as it ignores contribution from data.
+However, the method could be considered less principled for building a sparse model, as it ignores contribution from the complete dataset.
 It is important to note that the sparsifying process is independent of the approximate inference technique because the dual variables of \cref{eq:dual_param} are computed using \cref{eq-empirical-risk} and a Laplace approximation.
@@
 Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art on CL benchmarks.
-However, they are limited to use subset approximations of the posterior \cref{app:cl-experiment}.
+However, they are limited to use subset approximations of the posterior \cref{app:cl}.
 %, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer. 
-A more principled approach would be to sparsify the resultant GP into a low-rank approximation to ensure information coming from the entire task dataset is not lost.
+\our is a more principled approach since it sparsifies the resultant GP into a low-rank approximation to ensure information coming from the entire task dataset is not lost.
 %, essentially what the sparse dual variables do.
@@
 % Where the regularizer comes from
-At the end of the training for each task $t$, we compute the Laplace-GGN approximated kernel function for the current model and randomly select $M$ inducing points.
+
+In practice this means,  at the end of the training for each task $t$, we compute the Laplace-GGN approximated kernel function for the current model and randomly select $M$ inducing points.
 Given the issues described in the previous sections, related to computing the full covariance posterior $\MKxx$ for $\dataset_t$,\todo{this should be $\kappa(\MX_t, \MX_t)$} we can exploit the dual parameterization to efficiently encode the information from  $\dataset_t$ using the dual parameterization, as follows,

### 2023-05-16 paper/main.tex
experiments

@@
 
-In practice this means,  at the end of the training for each task $t$, we compute the Laplace-GGN approximated kernel function for the current model and randomly select $M$ inducing points.
+In practice this means,  at the end of the training for each task $t$, we compute the approximated kernel function for the current model and randomly select $M$ inducing points.
 Given the issues described in the previous sections, related to computing the full covariance posterior $\MKxx$ for $\dataset_t$,\todo{this should be $\kappa(\MX_t, \MX_t)$} we can exploit the dual parameterization to efficiently encode the information from  $\dataset_t$ using the dual parameterization, as follows,
@@
 
-After each task, we update $\mathcal{M}$, and we can construct a regularizer term, which aims to reduce the drift of the current model from diverging on the inducing points $\MZ_s$ for all previous tasks $ s = 1, \ldots, t-1$.
+After each task, we update $\mathcal{M}$, and can construct a regularizer term, which aims to reduce the drift of the current model from diverging on the inducing points $\MZ_s$ for all previous tasks $ s = 1, \ldots, t-1$.
 This means that for training  the successive task, the new objective to minimize becomes $\weights_t^* = \arg\min_{\weights} \mathcal{L}(\mathcal{D}_t, \weights) + \tau \, \mathcal{R}_\textrm{\our}(\weights, \mathcal{M})$, with weight $\tau$ and regularizer
@@
 For non-Gaussian likelihoods, the results are almost the same as retraining with all the data.
-Clearly, in practice, given our NN-derived kernel's dependency on the Jacobian of the trained neural network $\Jac{\weights_*}{\vx}$ as we add more data, the Jacobians become outdated.
-But we find we can still improve predictions by conditioning data without retraining.
+In practice, given our NN-derived kernel's dependency on the Jacobian of the trained neural network $\Jac{\weights_*}{\vx}$, the Jacobians become outdated as we add more data.
+However, we can still improve predictions by conditioning data without retraining.
 %[SEE EXPERIMENT ???].

### 2023-05-16 paper/main.tex
RL fig

--- 2023-05-16 paper/main.tex
@@
 %Need for adaptive learning methods + failures with current methods
-Given an approximate inference technique, we demonstrate that the neural network emits`dual' parameters which are the building blocks of a GP~\cite{csato2002sparse, adam2021dual, chang2020fast}.
+Given an approximate inference technique, we demonstrate that the neural network emits `dual' parameters which are the building blocks of a GP~\cite{csato2002sparse, adam2021dual, chang2020fast}.
 In contrast to previous work that utilizes subsets \cite{immer2021scalable}, this parameterization allows consolidating contributions from {\em all} training data into a sparse representation, essential for predictive uncertainty.
@@
 Through the dual parameter formulation, we establish a connection between the neural network, full GPs, and a sparse approximation similar to sparse variational GPs~\cite{titsias2009variational}.
-We call our method \our.
-A sparse GP derived from a trained neural network.
-As \our is in the dual parameters, we can perform dual conditioning recently shown effective in \cite{chang2022fantasizing}, that is, avoid retraining and condition new data into our model (see \cref{fig:teaser}).
+We refer to our method as \our---a sparse GP derived from a trained neural network.
+As \our is in the dual parameters, we can perform dual conditioning recently shown effective in \cite{chang2022fantasizing}, that is, avoid retraining and condition new data into our model (see \cref{fig:teaser}).\looseness-2
 %Need uncertainty and adaptive methods
@@
 A key challenge in RL is balancing the trade-off between exploration and exploitation \cite{sutton2018reinforcement}.
-That is, should an agent select actions that it knows will lead to high reward (exploitation), or should it
-select new ones in hope to discover actions leading to higher reward (exploration).
+%That is, should an agent select actions that it knows will lead to high reward %(exploitation), or should it
+%select new ones in hope to discover actions leading to higher reward (exploration).
 One promising direction to balancing this trade-off is to model the uncertainty associated with a learned transition dynamics model and use it to guide exploration.
@@
 % Make custom TikZ command (argument: colour)
-\newcommand{\lab}[1]{\protect\tikz[baseline=-.5ex]{\protect\node[minimum width=1.5em,minimum height=.8em,fill=#1,opacity=.1](a){};\protect\draw[#1,thick](a.west)--(a.east);}}
+\newcommand{\lab}[1]{\protect\tikz[baseline=-.5ex]{\protect\node[minimum width=1.5em,minimum height=.8em,fill=#1,opacity=.1](a){};\protect\draw[#1,semithick](a.west)--(a.east);}}
 
@@
 
- \end{tikzpicture}}
+ \end{tikzpicture}}\\[2em]~
  \end{subfigure}
  \hfill
- \begin{subfigure}[c]{.74\textwidth}
+ \begin{subfigure}[c]{.7\textwidth}
    \raggedleft\scriptsize
    \setlength{\figurewidth}{\textwidth}
-   \setlength{\figureheight}{.5\figurewidth}
-   \pgfplotsset{axis on top,ymajorgrids,axis line style={draw=none},legend style={at={(1,1)},anchor=north west}}
-   \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed},legend style={fill=white}}
+   \setlength{\figureheight}{.55\figurewidth}
+   \pgfplotsset{axis on top,ymajorgrids,axis line style={draw=none},legend style={at={(-.1,-.1)},anchor=north east}}
+   \pgfplotsset{grid style={line width=.1pt, draw=gray!10,densely dotted}}
+   \hspace*{-1.7cm}%
+   \def\our{{\sc sfr} (ours)}
    \input{./fig/rl.tex}
- \end{subfigure}
- \hfill
+ \end{subfigure}\\[-1em]
  \caption{\textbf{Cartpole swingup with sparse reward.} Training curves showing that \our's uncertainty estimates improve sample efficiency in RL.
-   Our method (\lab{color-our}) converges in fewer environment steps than the baseline model-based RL method (\lab{black}) and DDPG, the model-free baseline (\lab{black}).}
+   Our method (\lab{color-our}) converges in fewer environment steps than the baseline model-based RL method and DDPG, the model-free baseline.
+The dashed lines mark the asymptotic return for the methods not coverged in the plot.}
  \label{fig:rl}

### 2023-05-16 paper/main.tex
Colours

@@
 
+\paragraph{Implementation} We implement all methods in PyTorch~\ref{todo}
+
+\paragraph{Toy examples} \cref{fig:teaser} and \cref{fig:banana}
+
 %Initially, we explore the capability of our method to capture predictive uncertainty through supervised learning tasks using UCI datasets.
@@
 \definecolor{color-ddpg}{RGB}{191,191,0} % goldenrod1911910
-\definecolor{green01270}{RGB}{0,127,0} % green01270
+\definecolor{color-ensemble}{RGB}{0,127,0} % green01270
 \definecolor{lightgray204}{RGB}{204,204,204} % lightgray204
@@
 
-\cref{fig:rl} shows training curves for using \our as the dynamic model (\lab{color-our}), along with a Laplace-GGN~\cite{ADD} with GLM predictions (\lab{black})\todo{Arno cannot see these colour, someone help}, an ensemble of neural networks (\lab{black}), and a basic MLP without uncertainty (\lab{color-mlp}).
+\cref{fig:rl} shows training curves for using \our as the dynamic model (\lab{color-our}), along with a Laplace-GGN~\cite{ADD} with GLM predictions (\lab{red}), an ensemble of neural networks (\lab{color-ensemble}), and a basic MLP without uncertainty (\lab{color-mlp}).
 To ensure a fair comparison, we maintain the same MLP architecture/training scheme across all these methods and incorporate them into the same model-based RL algorithm (see \cref{app:rl}).

### 2023-05-16 src/sl/inference.py
first version new inference script

@@ -1,0 +1,248 @@
+#!/usr/bin/env python3
+
+import logging
+import random
+import time
+from collections import deque, namedtuple
+from pathlib import Path
+import wandb
+from omegaconf import DictConfig, OmegaConf
+import os
+import hydra
+import numpy as np
+import pickle
+import torch
+from torch.utils.data import DataLoader, ConcatDataset
+from torch.utils.data.dataset import Subset
+from torch.distributions import Categorical, Normal
+from tqdm import tqdm
+import logging
+from itertools import chain
+# from preds.laplace import Laplace, FunctionaLaplace
+from preds.laplace import FunctionaLaplace
+from src import CategoricalLh, NTKSVGP, NN2GPSubset
+import src as ntksvgp
+from preds.utils import nll_cls, macc, ece
+from preds.datasets import MNIST, FMNIST, SVHN
+from train import  get_dataset, get_model, set_seed_everywhere
+
+from tqdm import tqdm
+logging.basicConfig(level=logging.INFO)
+logger = logging.getLogger(__name__)
+
+
+def get_quick_loader(loader, device="cuda"):
+    return [(X.to(device), y.to(device)) for X, y in loader]
+
+
+def get_map_predictive(loader, model):
+    ys, pstar = list(), list()
+    for X, y in loader:
+        X, y = X, y
+        ys.append(y)
+        pstar.append(torch.softmax(model(X), dim=-1).detach())
+    ys = torch.cat(ys)
+    pstar = torch.cat(pstar)
+    return pstar, ys
+
+
+def get_svgp_predictive(
+    loader, svgp, likelihood, use_nn_out: bool = True, seeding: bool = False
+):
+    ys, ps = list(), list()
+    output_dim = svgp.output_dim
+    for X, y in tqdm(loader):
+        X, y = X.cuda(), y.cuda()
+        if seeding:
+            torch.manual_seed(711)
+        ps.append(
+            sample_svgp(X, likelihood, svgp, use_nn_out, n_samples=100).mean(dim=0)
+        )
+        ys.append(y)
+    ps = torch.cat(ps)
+    ys = torch.cat(ys)
+    return ps, ys
+
+
+def sample_svgp(X, likelihood, svgp, use_nn_out: bool, n_samples: int):
+    """Sample the SVGP, assumes a batched input."""
+    n_data = X.shape[0]
[…]

### 2023-05-16 src/sl/train.py

@@ -64,7 +64,7 @@ class QuickDS(VisionDataset):
         return len(self.D)
 
 
-def get_dataset(dataset, double, dir, device=None):
+def get_dataset(dataset, double, dir, cfg, device=None):
     if dataset == "MNIST":
         # Download training data from open datasets.
         ds_train = MNIST(train=True, double=double, root=dir)
@@ -78,6 +78,11 @@ def get_dataset(dataset, double, dir, device=None):
     else:
         raise ValueError("Invalid dataset argument")
     if device is not None:
+        if cfg.debug:
+            ds_train.data = ds_train.data[:500]
+            ds_train.targets = ds_train.targets[:500]
+            ds_test.data = ds_test.data[:500]
+            ds_test.targets = ds_test.targets[:500]
         return QuickDS(ds_train, device), QuickDS(ds_test, device)
     else:
         return ds_train, ds_test
@@ -188,7 +193,7 @@ def train(cfg: DictConfig):
     # print("DATA_DIR {}".format(DATA_DIR))
     # logger.info("cfg {}".format(cfg))
     ds_train, ds_test = src.sl.train.get_dataset(
-        dataset=cfg.dataset, double=cfg.double, dir="./", device=cfg.device
+        dataset=cfg.dataset, double=cfg.double, dir="./", device=cfg.device, cfg=cfg
     )
     # print("ds_train {}".format(ds_train.D[0].shape))
     # print("ds_train {}".format(ds_train.D[1].shape))

### 2023-05-16 paper/main.tex
Minor

@@
 This involves integrating data into the sum in \cref{eq:dual_sparse}.
-Thus, we need to find the data dual variables $\hat{\alpha}$ and $\hat{\beta}$ for the new data subset $\mathcal{D}_\textrm{new} = \{\vx_i,\vy_i\}_{i=1}^{N_{\textrm{new}}}$ and compute the corresponding kernel terms.
+Thus, we need to find the data dual variables $\hat{\alpha}$ and $\hat{\beta}$ for the new data subset $\mathcal{D}_\textrm{new} = \{(\vx_i,\vy_i)\}_{i=1}^{N_{\textrm{new}}}$ and compute the corresponding kernel terms.
 As pointed out in \cite{chang2022fantasizing}, for GPs, these updates are exact under a Gaussian likelihood and the kernel remains constant.

### 2023-05-16 paper/main.tex
Fix first 18 bib items

@@
 One promising direction to balancing this trade-off is to model the uncertainty associated with a learned transition dynamics model and use it to guide exploration.
-Prior work has taken an expectation over the dynamic model's posterior \cite{deisenrothPILCO2011,kamtheDataEfficient2018,chuaDeepReinforcementLearning2018},
+Prior work has taken an expectation over the dynamic model's posterior \cite{deisenroth2011pilco,kamtheDataEfficient2018,chuaDeepReinforcementLearning2018},
 sampled from it (akin to Thompson sampling but referred to as posterior sampling RL)
@@
 No single strategy has emerged as a go to method and we highlight that these strategies are only as good as their uncertainty estimates.
-Previous approaches have used GPs \cite{deisenrothPILCO2011,kamtheDataEfficient2018},
+Previous approaches have used GPs \cite{deisenroth2011pilco,kamtheDataEfficient2018},
 ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}

### 2023-05-17 paper/main.tex
Add UCI table to appendix (to be polished)
Minor

@@
 \textbf{Predictions:}~Does our method's ability to consider the full data set offer benefits over subset function-space methods?
-(\cref{sec:uci}) How do predictions with our sparse function-space approximation compare to weight-space approximations?
-\textbf{Function-space updates:} How fast are our function-space updates relative to retraining from scratch?
+(\cref{sec:uci,sec:image}) How do predictions with our sparse function-space approximation compare to weight-space approximations?
+%\textbf{Function-space updates:} How fast are our function-space updates relative to retraining from scratch?
 Do they improve predictive performance?
@@
 
-\paragraph{Toy examples} \cref{fig:teaser} and \cref{fig:banana}
+\paragraph{Toy examples} For illustrative purposes, we smoke-test our approach on a 1D regression problem (\cref{fig:teaser}) and on the 2D Banana classification task (\cref{fig:banana}).
+In \cref{fig:teaser}, we train an MLP neural network with two hidden layers (64 hidden units each, tanh activation).
+The middle panel shows the \our result on a sparse set of data examples, while the rightmost panel demonstrates fast dual conditioning on new data (from \cref{sec:sequential}).
+In \cref{fig:banana}, we use an MLP with two hidden layers (64 units, sigmoid) and compare to the HMC result obtained by hamiltorch \cite{cobb:} (10~chains, 10,000 samples).
 

### 2023-05-17 paper/main.tex
toy examples

@@
 The middle panel shows the \our result on a sparse set of data examples, while the rightmost panel demonstrates fast dual conditioning on new data (from \cref{sec:sequential}).
-In \cref{fig:banana}, we use an MLP with two hidden layers (64 units, sigmoid) and compare to the HMC result obtained by hamiltorch \cite{cobb:} (10~chains, 10,000 samples).
+In \cref{fig:banana}, we use an MLP with two hidden layers (64 units, sigmoid) and compare to the HMC result obtained by hamiltorch \cite{cobb2020scaling} that shows capture similar behaviour as HMC.
 
@@
 
+\begin{table}[t!] 
+  \centering\scriptsize
+  \caption{Negative log predictive density (NLPD) (lower better) for SVGP (sparse GP mean and variance), SVGP NN (NN mean and sparse GP variance), GP subset (subset GP mean and variance) and GP NN subset (NN mean and GP subset variance) for inducing points in $[16, 32, 64, 128, 256]$.
+}
+	\label{tbl:uci}
+	% Control table spacing
+	\renewcommand{\arraystretch}{1.}
+	\setlength{\tabcolsep}{2pt}
+	\setlength{\tblw}{0.14\textwidth}
+
+	% Custom error formatting
+	\newcommand{\val}[2]{%
+		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
+	}
+
+    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
+	\input{tables/uci_all.tex}
+\end{table}
+
 \subsection{Uncertainty benchmarks for image data}

### 2023-05-17 paper/main.tex
More details
New version of UCI table

--- 2023-05-16 paper/main.tex
@@
   \caption{Negative log predictive density (NLPD) (lower better) for SVGP (sparse GP mean and variance), SVGP NN (NN mean and sparse GP variance), GP subset (subset GP mean and variance) and GP NN subset (NN mean and GP subset variance).
-}
+The \our on the left side of the table used 256 inducing points }
 	\label{tbl:uci}
@@
 	\renewcommand{\arraystretch}{1.}
-	\setlength{\tabcolsep}{2pt}
-	\setlength{\tblw}{0.14\textwidth}
+	\setlength{\tabcolsep}{1pt}
+	\setlength{\tblw}{0.08\textwidth}
 

### 2023-05-17 paper/main.tex
UCI

--- 2023-05-17 paper/main.tex
@@
 
-\paragraph{Implementation} We implement all methods in PyTorch~\ref{todo}
+\paragraph{Implementation} We implement all methods in PyTorch~\cite{paszke2019pytorch} and leverange the XXXX libraries.. \todo{add brief details}. Experiments were run on clusters
 
@@
 
-\subsection{Capturing uncertainty in UCI tasks under supervised learning}
-\label{sec:uci}
-%
-
 \begin{table}[t!] 
@@
 \end{table}
-We trained a two-layer MLP for each of the $8$ classification tasks in UCI, see \cref{tbl:uci} for a list of the datasets.
+
+\subsection{Capturing uncertainty in UCI tasks under supervised learning}
+\label{sec:uci}
+%
+We consider the same 8 UCI~\cite{uci} classification benchamrks tasks and setup as were considered in \cite{add}.
+We use a two-layer MLP for all tasks and follow the setup in \cref{sec:methods} for \our.
+After training, we construct the \our dual and use the resulting model for uncertainty quantification.
+We performed hyperparameter search over the prior precision $\delta$, and ran the experiment over $10$ seeds.
+%Depending on task dimension and complexity, our model can match the neural network MAP in negative log-predictive density (NLPD) even with a low number of inducing points (see \cref{tbl:uci} left).
+In \cref{tbl:uci} (left), we compare our model to the NN MAP estimate, mean-field VI, a Baysian NN, and a GLM model (see \cite{add} for the baselines) in negative log-predictive density (NLPD).
+We match the predictive performance despite being sparse (here, $M=$).
+Results for $M=16,32,64,128,256$ included in \cref{app:uci} with full experiment details.
+
+In \cref{tbl:uci} (right), we also include an ablation and comparison (to \cite{add}) study with a fixed low number of inducing points ($M=$).
+The comparison shows that our sparse method is able to summarize the information of the full data set more efficiently than sparse subset methods.
+
+% see \cref{tbl:uci} for a list of the datasets.
 The neural network training was done using MAP, with a prior $\mathcal{N}(0,\delta^{-1} \MI)$ with prior precision $\delta$.

### 2023-05-17 paper/main.tex
update the cl notation
experiments

@@
   \caption{\textbf{Regression example on an MLP with two hidden layers.} Left:~Predictions from the trained neural network.
-Middle:~Our approach summarizes all the training data with the help of an iducing set of points.
+Middle:~Our approach summarizes all the training data with the help of an inducing set of points.
 The model captures the predictive mean and uncertainty, and (right) makes it possible to update the model with new data without degrading previous performance.}
@@
 \textbf{Function-space methods for sequential learning} 
-Continual learning (CL) hinges on how to deal with the non-stationary training distribution, wherein the training process may overwrite previously learned parameters, causing catastrophic forgetting \citep{mccloskey1989catastrophic}.
+Continual learning (CL) hinges on how to deal with a non-stationary training distribution, wherein the training process may overwrite previously learned parameters, causing catastrophic forgetting \citep{mccloskey1989catastrophic}.
 CL approaches fall into inference-based, rehearsal-based, and model-based methods (see \cite{parisi2019continual, de2021continual} for an overview).
@@
 The posterior over the weights ${p(\vw \mid \dataset) \propto p(\vy \mid f_{\weights}(\vx)) \, p(\weights)}$ is generally not available in closed form.
-Sampling methods that characterize the posterior with a finite set of samples in weight-space---such as the Hamiltonian Monte Carlo (HMC) baseline used in \cref{fig:banana} (right)---are general-purpose, but comuptationally heavy and impractical for downstream applications.
+Sampling methods that characterize the posterior with a finite set of samples in weight-space---such as the Hamiltonian Monte Carlo (HMC) baseline used in \cref{fig:banana} (right)---are general-purpose, but computationally heavy and impractical for downstream applications.
 
@@
 where $f_\vw(\vx_i) = f_i$ is the function output at input $\vx_i$.
-The relationships specified are valid for generic likelihoods, and involve no approximations since the expectation is under the exact posterior.
+The relationships specified are valid for generic likelihoods, and involve no approximations since the expectation is under the exact posterior, but given that your model can be expressed in kernel formulation.
 \cref{eq:gp_pred} and \cref{eq:dual_param} highlight that the approximate inference technique, usually viewed as a posterior approximation, can be alternatively interpreted as an approximation of the expectation of gradients of loss/likelihoods.
 
-Originally \citet{csato2002sparse} iteratively find dual variables using an expectation propogation (EP, \cite{minka2001expectation}) method.
+Originally \citet{csato2002sparse} iteratively find dual variables using an expectation propagation (EP, \cite{minka2001expectation}) method.
 More recently \cite{khan2017conjugate,adam2021dual}, has shown this relationship for variational Gaussian processes where the above expectation is with respect to the approximate variational posterior.
@@
 
-\paragraph{Sparsifying the NNGP}
+\paragraph{Sparsifying the NN GP}
 \label{sec:sparse-dual-gp}
@@
 Rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting.
-In the same way, after each task, we can use our \our method to build a compact representation of the neural network and then exploit this representation to build a functional regularizer to add to the training loss for the subsequent tasks.
+In the same way, after each task, we can use \our method to build a compact representation of the neural network and then exploit this representation to construct a functional regularizer to add to the training loss for the subsequent tasks.
 Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art on CL benchmarks.
-However, they are limited to use subset approximations of the posterior \cref{app:cl}.
+However, they are limited to using subset approximations of the posterior.
+Instead, we use the sparse data term posterior see \cref{app:cl} for details.
 %, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer. 
-\our is a more principled approach since it sparsifies the resultant GP into a low-rank approximation to ensure information coming from the entire task dataset is not lost.
+\our is a more principled approach since the resultant GP is a low-rank approximation of the full data which ensures information is not lost.
 %, essentially what the sparse dual variables do.
@@
 	\left\lVert 
-	\vu_t - \vu_s % f_{\weights_{s}}(\MZ_s)
-	\right\rVert_{\bar{\MB}^{-1}_{s}}, \quad \vu_t \in \R^M \text{~with~} u_{s,i} = f_{\weights}(\vz_{i}),~\forall {\vz_i} \in \mathcal{Z}_s .
+	\vu - \vu_s % f_{\weights_{s}}(\MZ_s)
+	\right\rVert_{\bar{\MB}^{-1}_{s}}, \quad \vu \in \R^M \text{~with~} u_{i} = f_{\weights}(\vz_{i}),~\forall {\vz_i} \in \mathcal{Z}_s .
 \end{equation}
@@
 %
-We present a series of experiments designed to demonstrate the versatility and efficacy of our proposed \our framework. We seek to find answers to the following questions: 
+
+We present a series of experiments designed to demonstrate the versatility and efficacy of \our. We seek to find answers to the following questions: 
 \textbf{Predictions:}~Does our method's ability to consider the full data set offer benefits over subset function-space methods?
-(\cref{sec:uci,sec:image}) How do predictions with our sparse function-space approximation compare to weight-space approximations?
-%\textbf{Function-space updates:} How fast are our function-space updates relative to retraining from scratch?
-Do they improve predictive performance?
-Are they as good as retraining from scratch?
-\todo{what do we have on this?}
-\textbf{Representation:} Can a sparse function-space representation help retain knowlegde from previous tasks in CL? (\cref{sec:cl-exp})
-\textbf{Uncertainty:} Can our uncertainty estimates help exploration in RL under sparse rewards? (\cref{sec:rl-exp})
+(\cref{sec:uci}) How do predictions with our sparse function-space approximation compare to weight-space approximations?
+\textbf{Function-space updates:} How fast are our function-space updates relative to retraining from scratch? Do they improve predictive performance? \todo{what do we have on this?}
+\textbf{Representation:} Can a sparse function-space representation help retain knowledge from previous tasks in CL? (\cref{sec:cl-exp})
+\textbf{Uncertainty:} Can our uncertainty estimates help exploration in RL? (\cref{sec:rl-exp})
 
@@
 
-Similarly to the UCI experiments, we trained neural networks (CNN, architexture matches \citet{immer2021improving}) for the FMNIST and CIFAR10 classification tasks.
+Similarly to the UCI experiments, we trained neural networks (CNN, architecture matches \citet{immer2021improving}) for the FMNIST and CIFAR10 classification tasks.
 After training, we computed the duals for NN2SVGP and used the resulting SVGP for uncertainty estimates, see \cref{tbl:imagesuper}.

### 2023-05-17 paper/main.tex
Minor

--- 2023-05-17 paper/main.tex
@@
   \centering\scriptsize
-  \caption{Negative log predictive density (NLPD) (lower better) for SVGP (sparse GP mean and variance), SVGP NN (NN mean and sparse GP variance), GP subset (subset GP mean and variance) and GP NN subset (NN mean and GP subset variance).
-}
+  \caption{Comparisons and ablations on UCI data with negative log predictive density (NLPD, lower better).
+Our sparse \our ($M=256$) is on par with or better than full models (left) and outperforms the GP subset approach of \cite{todo}.
+See \cref{app:uci} for additional tables with comparisons.}
 	\label{tbl:uci}
@@
 %
-We consider the same 8 UCI~\cite{uci} classification benchamrks tasks and setup as were considered in \cite{add}.
+We consider the same 8 UCI~\cite{UCI} classification benchamrks tasks and setup as were considered in \cite{todo}.
 We use a two-layer MLP for all tasks and follow the setup in \cref{sec:methods} for \our.
@@
 
-In \cref{tbl:uci} (right), we also include an ablation and comparison (to \cite{add}) study with a fixed low number of inducing points ($M=$).
+In \cref{tbl:uci} (right), we also include an ablation and comparison (to \cite{todo}) study with a fixed low number of inducing points ($M=$).
 The comparison shows that our sparse method is able to summarize the information of the full data set more efficiently than sparse subset methods.
@@
 
-\cref{fig:rl} shows training curves for using \our as the dynamic model (\lab{color-our}), along with a Laplace-GGN~\cite{ADD} with GLM predictions (\lab{red}), an ensemble of neural networks (\lab{color-ensemble}), and a basic MLP without uncertainty (\lab{color-mlp}).
+\cref{fig:rl} shows training curves for using \our as the dynamic model (\lab{color-our}), along with a Laplace-GGN~\cite{todo} with GLM predictions (\lab{red}), an ensemble of neural networks (\lab{color-ensemble}), and a basic MLP without uncertainty (\lab{color-mlp}).
 To ensure a fair comparison, we maintain the same MLP architecture/training scheme across all these methods and incorporate them into the same model-based RL algorithm (see \cref{app:rl}).

### 2023-05-17 paper/main.tex

--- 2023-05-17 paper/main.tex
@@
   \centering\scriptsize
-  \caption{Negative log predictive density (NLPD) (lower better) for SVGP (sparse GP mean and variance), SVGP NN (NN mean and sparse GP variance), GP subset (subset GP mean and variance) and GP NN subset (NN mean and GP subset variance).
-The \our on the left side of the table used 256 inducing points }
+  \caption{Comparisons and ablations on UCI data with negative log predictive density (NLPD, lower better).
+Our sparse \our ($M=256$) is on par with or better than full models (left) and outperforms the GP subset approach of \cite{todo}.
+See \cref{app:uci} for additional tables with comparisons.}
 	\label{tbl:uci}

### 2023-05-17 paper/main.tex
Minor

@@
   \centering\scriptsize
-  \caption{Comparisons and ablations on UCI data with negative log predictive density (NLPD, lower better).
+  \caption{Comparisons and ablations on UCI data with negative log predictive density (NLPD\textcolor{gray}{\footnotesize$\pm$std}, lower better).
 Our sparse \our ($M=256$) is on par with or better than full models (left) and outperforms the GP subset approach of \cite{todo}.
@@
 After training, we construct the \our dual and use the resulting model for uncertainty quantification.
-We performed hyperparameter search over the prior precision $\delta$, and ran the experiment over $10$ seeds.
+We performed hyperparameter search over the prior precision $\delta$, and ran the experiment over 10 random splits.
 %Depending on task dimension and complexity, our model can match the neural network MAP in negative log-predictive density (NLPD) even with a low number of inducing points (see \cref{tbl:uci} left).
-In \cref{tbl:uci} (left), we compare our model to the NN MAP estimate, mean-field VI, a Baysian NN, and a GLM model (see \cite{add} for the baselines) in negative log-predictive density (NLPD).
+In \cref{tbl:uci} (left), we compare our model to the NN MAP estimate, mean-field VI, a Bayesian NN, and a GLM model (see \cite{add} for the baselines) in negative log-predictive density (NLPD).
 We match the predictive performance despite being sparse (here, $M=$).

### 2023-05-17 paper/main.tex
Finalizing UCI table
experiments

@@
 The function space allows for a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{foong2019between}.
-These methods rely on the linearization of the neural network and the resultant NTK \cite{jacot2018neural}.
+These methods rely on the linearization of the neural network and the resultant neural tangent kernel (NTK, \cite{jacot2018neural}).
 The function space neural network is characterized by its first two moment functions, a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}).
@@
 where $f_\vw(\vx_i) = f_i$ is the function output at input $\vx_i$.
-The relationships specified are valid for generic likelihoods, and involve no approximations since the expectation is under the exact posterior, but given that your model can be expressed in kernel formulation.
+The relationships specified are valid for generic likelihoods, and involve no approximations since the expectation is under the exact posterior, but given that the model can be expressed in a kernel formulation.
 \cref{eq:gp_pred} and \cref{eq:dual_param} highlight that the approximate inference technique, usually viewed as a posterior approximation, can be alternatively interpreted as an approximation of the expectation of gradients of loss/likelihoods.
@@
   \quad \text{and} \quad
-  \hat{\beta}_i \coloneqq - \nabla^2_{f,f}\log p(y_i \mid f) |_{f=f_i}.
+  \hat{\beta}_i \coloneqq - \nabla^2_{ff}\log p(y_i \mid f) |_{f=f_i}.
 \end{equation}
@@
 	\renewcommand{\arraystretch}{1.}
-	\setlength{\tabcolsep}{1pt}
-	\setlength{\tblw}{0.08\textwidth}
+	\setlength{\tabcolsep}{1.2pt}
+	\setlength{\tblw}{0.083\textwidth}
 

### 2023-05-17 paper/main.tex
Figure

--- 2023-05-17 paper/main.tex
@@
 \end{table}
+
+\begin{figure}[t]
+  \centering\scriptsize
+  \setlength{\figurewidth}{.26\textwidth}
+  \setlength{\figureheight}{\figurewidth}
+  \pgfplotsset{axis on top,scale only axis,y tick label style={rotate=90}, x tick label style={font=\footnotesize},y tick label style={font=\footnotesize},title style={yshift=-4pt,font=\large}, y label style={font=\large},x label style={font=\large},grid=major, width=\figurewidth, height=\figureheight}
+  \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
+  \pgfplotsset{xlabel={$M$},ylabel style={yshift=-12pt}}  
+  %
+  \begin{minipage}[t]{.17\textwidth}
+    \raggedleft
+    \pgfplotsset{ylabel=NLPD}
+    \input{./fig/australian.tex}
+  \end{minipage}
+  \hfill
+%  \begin{minipage}[t]{.16\textwidth}
+%    \raggedleft
+%    \input{./fig/breast_cancer.tex}
+%  \end{minipage}
+%  \hfill
+%  \begin{minipage}[t]{.16\textwidth}
+%    \raggedleft
+%    \input{./fig/ionosphere.tex}
+%  \end{minipage}
+%  \hfill
+  \begin{minipage}[t]{.16\textwidth}
+    \raggedleft
+    \input{./fig/glass.tex}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[t]{.16\textwidth}
+    \raggedleft
+    \input{./fig/vehicle.tex}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[t]{.16\textwidth}
+    \raggedleft
+    \input{./fig/waveform.tex}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[t]{.16\textwidth}
+    \raggedleft
+    \input{./fig/digits.tex}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[t]{.16\textwidth}
+    \raggedleft
+    \input{./fig/satellite.tex}
+  \end{minipage}\\%[1em]
+  %
+  % Show the legend separately
+  %\pgfplotsset{hide axis,legend columns=-1,legend style={draw=none,column sep=1ex,font=\Large}}
+  %\input{./fig/uci-legend.tex}\\[-2.5em]
+  \caption{Comparison of convergence in terms of  negative log-predictive density (NLPD) as averages over 10-fold cross-validation runs, on UCI classification tasks.}
+  \label{fig:uci}
+  %\vspace*{-6pt}
+\end{figure}
 
@@
 During the initial NN training, we used a learning rate of $1e-3$.
+
+\begin{figure}
+  \raggedleft\scriptsize
+  \setlength{\figurewidth}{\textwidth}
+  \setlength{\figureheight}{.55\figurewidth}
+  %\pgfplotsset{axis on top,ymajorgrids,axis line style={draw=none},legend style={at={(-.1,-.1)},anchor=north east}}
+  %\pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
+  %\def\our{{\sc sfr} (ours)}
+  \input{./fig/MNIST_acc.tex}
+  \caption{Foo}
+  \label{fig:mnist}
+\end{figure}
 

### 2023-05-17 paper/main.tex

@@
 %\paragraph{GP in the dual parameters}
-The seminal work by \citet{csato2002sparse} (parameterization Lemma~1) gives a parameterization for the posterior process $f_{\textrm{post}}$ that can be found through the Bayesian update using the GP prior and the likelihood function.
+The seminal work by \citet{csato2002sparse} (parameterization Lemma~1) gives a parameterization for the posterior process $f_{\textrm{post}}$ that can be found through using Bayes formula the GP prior and the likelihood function.
 This gives a `dual' parameterization, $\valpha$ and $\vbeta$,
@@
 where the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{N \times N}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $k_{ii} = \kappa(\vx_i, \vx_i)$.
+\cref{eq:gp_pred} gives the first two moments of the posterior processes.
+The actual posterior may or may not be a Gaussian process but we can still approximate it with its first two moments.
 The dual parameters are the vectors $\valpha, \vbeta \in \R^{N}$, defined as:\looseness-1
@@
 
-\paragraph{Sparsifying the NN GP}
+\paragraph{Sparsifying the Neural Network GP}
 \label{sec:sparse-dual-gp}
@@
 The authors of that paper see the significance of the dual variables for approximate inference, but write them using the natural parameterization, primarily because this form is more suitable for optimization through natural gradients.
-In order to link the dual variables defined in \cref{eq:dual_param}, we write them in the sparse GP using the dual variables
+In order to link the dual variables defined in \cref{eq:dual_param}, we write them in the sparse GP formulation mean the dual variables become
 %

### 2023-05-17 paper/main.tex
update cl experiments

--- 2023-05-17 paper/main.tex
@@
 The function space allows for a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{foong2019between}.
-These methods rely on the linearization of the neural network and the resultant neural tangent kernel (NTK, \cite{jacot2018neural}).
+These methods rely on the linearization of the neural network and the resultant NTK \cite{jacot2018neural}.
 The function space neural network is characterized by its first two moment functions, a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}).
@@
   \caption{\textbf{Regression example on an MLP with two hidden layers.} Left:~Predictions from the trained neural network.
-Middle:~Our approach summarizes all the training data with the help of an inducing set of points.
+Middle:~Our approach summarizes all the training data with the help of an iducing set of points.
 The model captures the predictive mean and uncertainty, and (right) makes it possible to update the model with new data without degrading previous performance.}
@@
 \textbf{Function-space methods for sequential learning} 
-Continual learning (CL) hinges on how to deal with a non-stationary training distribution, wherein the training process may overwrite previously learned parameters, causing catastrophic forgetting \citep{mccloskey1989catastrophic}.
+Continual learning (CL) hinges on how to deal with the non-stationary training distribution, wherein the training process may overwrite previously learned parameters, causing catastrophic forgetting \citep{mccloskey1989catastrophic}.
 CL approaches fall into inference-based, rehearsal-based, and model-based methods (see \cite{parisi2019continual, de2021continual} for an overview).
@@
 The posterior over the weights ${p(\vw \mid \dataset) \propto p(\vy \mid f_{\weights}(\vx)) \, p(\weights)}$ is generally not available in closed form.
-Sampling methods that characterize the posterior with a finite set of samples in weight-space---such as the Hamiltonian Monte Carlo (HMC) baseline used in \cref{fig:banana} (right)---are general-purpose, but computationally heavy and impractical for downstream applications.
+Sampling methods that characterize the posterior with a finite set of samples in weight-space---such as the Hamiltonian Monte Carlo (HMC) baseline used in \cref{fig:banana} (right)---are general-purpose, but comuptationally heavy and impractical for downstream applications.
 
@@
 where $f_\vw(\vx_i) = f_i$ is the function output at input $\vx_i$.
-The relationships specified are valid for generic likelihoods, and involve no approximations since the expectation is under the exact posterior, but given that the model can be expressed in a kernel formulation.
+The relationships specified are valid for generic likelihoods, and involve no approximations since the expectation is under the exact posterior.
 \cref{eq:gp_pred} and \cref{eq:dual_param} highlight that the approximate inference technique, usually viewed as a posterior approximation, can be alternatively interpreted as an approximation of the expectation of gradients of loss/likelihoods.
 
-Originally \citet{csato2002sparse} iteratively find dual variables using an expectation propagation (EP, \cite{minka2001expectation}) method.
+Originally \citet{csato2002sparse} iteratively find dual variables using an expectation propogation (EP, \cite{minka2001expectation}) method.
 More recently \cite{khan2017conjugate,adam2021dual}, has shown this relationship for variational Gaussian processes where the above expectation is with respect to the approximate variational posterior.
@@
   \quad \text{and} \quad
-  \hat{\beta}_i \coloneqq - \nabla^2_{ff}\log p(y_i \mid f) |_{f=f_i}.
+  \hat{\beta}_i \coloneqq - \nabla^2_{f,f}\log p(y_i \mid f) |_{f=f_i}.
 \end{equation}
@@
 
-\paragraph{Sparsifying the NN GP}
+\paragraph{Sparsifying the NNGP}
 \label{sec:sparse-dual-gp}
@@
 Rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting.
-In the same way, after each task, we can use \our method to build a compact representation of the neural network and then exploit this representation to construct a functional regularizer to add to the training loss for the subsequent tasks.
+In the same way, after each task, we can use our \our method to build a compact representation of the neural network and then exploit this representation to build a functional regularizer to add to the training loss for the subsequent tasks.
 Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art on CL benchmarks.
-However, they are limited to using subset approximations of the posterior.
-Instead, we use the sparse data term posterior see \cref{app:cl} for details.
+However, they are limited to use subset approximations of the posterior \cref{app:cl}.
 %, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer. 
-\our is a more principled approach since the resultant GP is a low-rank approximation of the full data which ensures information is not lost.
+\our is a more principled approach since it sparsifies the resultant GP into a low-rank approximation to ensure information coming from the entire task dataset is not lost.
 %, essentially what the sparse dual variables do.
@@
 %
-
-We present a series of experiments designed to demonstrate the versatility and efficacy of \our. We seek to find answers to the following questions: 
+We present a series of experiments designed to demonstrate the versatility and efficacy of our proposed \our framework. We seek to find answers to the following questions: 
 \textbf{Predictions:}~Does our method's ability to consider the full data set offer benefits over subset function-space methods?
-(\cref{sec:uci}) How do predictions with our sparse function-space approximation compare to weight-space approximations?
-\textbf{Function-space updates:} How fast are our function-space updates relative to retraining from scratch? Do they improve predictive performance? \todo{what do we have on this?}
-\textbf{Representation:} Can a sparse function-space representation help retain knowledge from previous tasks in CL? (\cref{sec:cl-exp})
-\textbf{Uncertainty:} Can our uncertainty estimates help exploration in RL? (\cref{sec:rl-exp})
+(\cref{sec:uci,sec:image}) How do predictions with our sparse function-space approximation compare to weight-space approximations?
+%\textbf{Function-space updates:} How fast are our function-space updates relative to retraining from scratch?
+Do they improve predictive performance?
+Are they as good as retraining from scratch?
+\todo{what do we have on this?}
+\textbf{Representation:} Can a sparse function-space representation help retain knowlegde from previous tasks in CL? (\cref{sec:cl-exp})
+\textbf{Uncertainty:} Can our uncertainty estimates help exploration in RL under sparse rewards? (\cref{sec:rl-exp})
 
@@
   \centering\scriptsize
-  \caption{Comparisons and ablations on UCI data with negative log predictive density (NLPD\textcolor{gray}{\footnotesize$\pm$std}, lower better).
-Our sparse \our ($M=256$) is on par with or better than full models (left) and outperforms the GP subset approach of \cite{todo}.
-See \cref{app:uci} for additional tables with comparisons.}
+  \caption{Negative log predictive density (NLPD) (lower better) for SVGP (sparse GP mean and variance), SVGP NN (NN mean and sparse GP variance), GP subset (subset GP mean and variance) and GP NN subset (NN mean and GP subset variance).
+The \our on the left side of the table used 256 inducing points }
 	\label{tbl:uci}
@@
 	\renewcommand{\arraystretch}{1.}
-	\setlength{\tabcolsep}{1.2pt}
-	\setlength{\tblw}{0.083\textwidth}
+	\setlength{\tabcolsep}{1pt}
+	\setlength{\tblw}{0.08\textwidth}
 
@@
 %
-We consider the same 8 UCI~\cite{UCI} classification benchamrks tasks and setup as were considered in \cite{todo}.
+We consider the same 8 UCI~\cite{uci} classification benchamrks tasks and setup as were considered in \cite{add}.
 We use a two-layer MLP for all tasks and follow the setup in \cref{sec:methods} for \our.
 After training, we construct the \our dual and use the resulting model for uncertainty quantification.
-We performed hyperparameter search over the prior precision $\delta$, and ran the experiment over 10 random splits.
+We performed hyperparameter search over the prior precision $\delta$, and ran the experiment over $10$ seeds.
 %Depending on task dimension and complexity, our model can match the neural network MAP in negative log-predictive density (NLPD) even with a low number of inducing points (see \cref{tbl:uci} left).
-In \cref{tbl:uci} (left), we compare our model to the NN MAP estimate, mean-field VI, a Bayesian NN, and a GLM model (see \cite{add} for the baselines) in negative log-predictive density (NLPD).
+In \cref{tbl:uci} (left), we compare our model to the NN MAP estimate, mean-field VI, a Baysian NN, and a GLM model (see \cite{add} for the baselines) in negative log-predictive density (NLPD).
 We match the predictive performance despite being sparse (here, $M=$).
@@
 
-In \cref{tbl:uci} (right), we also include an ablation and comparison (to \cite{todo}) study with a fixed low number of inducing points ($M=$).
+In \cref{tbl:uci} (right), we also include an ablation and comparison (to \cite{add}) study with a fixed low number of inducing points ($M=$).
 The comparison shows that our sparse method is able to summarize the information of the full data set more efficiently than sparse subset methods.
@@
 
-Similarly to the UCI experiments, we trained neural networks (CNN, architecture matches \citet{immer2021improving}) for the FMNIST and CIFAR10 classification tasks.
+Similarly to the UCI experiments, we trained neural networks (CNN, architexture matches \citet{immer2021improving}) for the FMNIST and CIFAR10 classification tasks.
 After training, we computed the duals for NN2SVGP and used the resulting SVGP for uncertainty estimates, see \cref{tbl:imagesuper}.
@@
   \centering\scriptsize
-  \caption{Continual learning experiments. We report accuracy${\pm}$std and bold based on a $t$-test. $^*$Methods rely on weight regularization.}
+  \caption{Continual learning experiments. We report mean accuracy${\pm}$std over five runs, and bold based on a $t$-test.\\ $^*$Methods relying on weight regularization.}
   %\textcolor{blue}{Results from \cite{rudner2022continual}
@@
 Notably, CL methods require tuning making direct comparisons difficult.
-We consider the setup with single-head (SH) setting that is typically hard and more competitive.
+We consider the setup with single-head (SH) setting that is a harder and more realistic CL setting \citep{van2019three}.	 \todo{can't find the bibtex for their NIPS workshop paper} % typically hard and more competitive \cite{}
 %
 % Benchmarks/architectures
-We consider the CL benchmarks: Sequential-MNIST (S-MNIST), Sequential-FashionMNIST (S-FMNIST), and Permuted-MNIST (P-MNIST).
+We consider the CL benchmarks: Split-MNIST (S-MNIST), Split-FashionMNIST (S-FMNIST), and the 10-tasks Permuted-MNIST (P-MNIST).
 We follow the setups described in \cite{rudner2022continual, pan2020continual}, using a two-layer MLP with 256 hidden units and ReLU activation for S-MNIST and S-FMNIST, and a two-layer MLP with 100 hidden units for P-MNIST (full details in \cref{app:cl-exp}).
@@
 %% Comments on the results:
-\cref{tbl:cl_table_1} shows results
-We get the best results on S-MNIST both 40 and 200 pts. per task
-
-On S-FMNIST we are on par with DER, which is however exploiting a reservoir buffer technique, that iteratively samples new "inducing points"
-
-On P-MNIST we are lower than S-FSVI, however % I'm still running experiments, so we can hope that it is not the best overall in the end
+From \cref{tbl:cl_table_1}, it is clear that the objective methods completely fail compared to the function-space methods on S-MNIST and S-FMNIST, where the tasks are composed of disjoint set of classes, but they are still able to retain previous performance on P-MNIST where the challenge is to contrast the domain shift over the tasks.
+%, commonly referred as Domain Incremental Learning.
+(opposed to the Class-Incremental Learning for S-MNIST and S-FMNIST)
+Considering the function-space methods, we can see that \our achieves the best results on both settings on S-MNIST, where the condensing the information coming from the entire task datasets $\dataset_t$ is particularly effective, when using fewer points per task.
+On S-FMNIST, our method obtains close results to DER, which regularizes the model by taking the mean squared error between current and old function outputs without accounting the covariance structure of the loss but assumes an i.i.d.
+prior similar to our L2 ablation.
+Moreover, their method exploits reservoir sampling \citep{vitter1985random} to obtain a continuously updated set inducing points.
+S-FSVI obtains the best on P-MNIST, but with the downside of requiring high computational costs, compared to \our.
+\todo{on PMNIST our method is not really super-fast, so that could be not the best thing to say here} % we could also say that P-MNIST is known to be a bad/ill-posed dataset for CL
+Finally, it is worth noticing as our ablation already provides a very solid baseline consistently over all datasets.
 
@@
 
-\cref{fig:rl} shows training curves for using \our as the dynamic model (\lab{color-our}), along with a Laplace-GGN~\cite{todo} with GLM predictions (\lab{red}), an ensemble of neural networks (\lab{color-ensemble}), and a basic MLP without uncertainty (\lab{color-mlp}).
+\cref{fig:rl} shows training curves for using \our as the dynamic model (\lab{color-our}), along with a Laplace-GGN~\cite{ADD} with GLM predictions (\lab{red}), an ensemble of neural networks (\lab{color-ensemble}), and a basic MLP without uncertainty (\lab{color-mlp}).
 To ensure a fair comparison, we maintain the same MLP architecture/training scheme across all these methods and incorporate them into the same model-based RL algorithm (see \cref{app:rl}).

### 2023-05-17 paper/main.tex
Sketching UCI text

--- 2023-05-17 paper/main.tex
@@
 %\paragraph{GP in the dual parameters}
-The seminal work by \citet{csato2002sparse} (parameterization Lemma~1) gives a parameterization for the posterior process $f_{\textrm{post}}$ that can be found through using Bayes formula the GP prior and the likelihood function.
+The seminal work by \citet{csato2002sparse} (parameterization Lemma~1) gives a parameterization for the posterior process $f_{\textrm{post}}$ that can be found through the Bayesian update using the GP prior and the likelihood function.
 This gives a `dual' parameterization, $\valpha$ and $\vbeta$,
@@
 where the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{N \times N}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $k_{ii} = \kappa(\vx_i, \vx_i)$.
-\cref{eq:gp_pred} gives the first two moments of the posterior processes.
-The actual posterior may or may not be a Gaussian process but we can still approximate it with its first two moments.
 The dual parameters are the vectors $\valpha, \vbeta \in \R^{N}$, defined as:\looseness-1
@@
 
-\paragraph{Sparsifying the Neural Network GP}
+\paragraph{Sparsifying the NN GP}
 \label{sec:sparse-dual-gp}
@@
 The authors of that paper see the significance of the dual variables for approximate inference, but write them using the natural parameterization, primarily because this form is more suitable for optimization through natural gradients.
-In order to link the dual variables defined in \cref{eq:dual_param}, we write them in the sparse GP formulation mean the dual variables become
+In order to link the dual variables defined in \cref{eq:dual_param}, we write them in the sparse GP using the dual variables
 %
@@
 
-\paragraph{Implementation} We implement all methods in PyTorch~\cite{paszke2019pytorch} and leverange the XXXX libraries.. \todo{add brief details}. Experiments were run on clusters
+\paragraph{Implementation} We implement all methods in PyTorch~\cite{paszke2019pytorch} and leverage the XXXX libraries.. \todo{add brief details}. Experiments were run on clusters
 
@@
 
-\begin{figure}[t]
-  \centering\scriptsize
-  \setlength{\figurewidth}{.26\textwidth}
-  \setlength{\figureheight}{\figurewidth}
-  \pgfplotsset{axis on top,scale only axis,y tick label style={rotate=90}, x tick label style={font=\footnotesize},y tick label style={font=\footnotesize},title style={yshift=-4pt,font=\large}, y label style={font=\large},x label style={font=\large},grid=major, width=\figurewidth, height=\figureheight}
-  \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
-  \pgfplotsset{xlabel={$M$},ylabel style={yshift=-12pt}}  
-  %
-  \begin{minipage}[t]{.17\textwidth}
-    \raggedleft
-    \pgfplotsset{ylabel=NLPD}
-    \input{./fig/australian.tex}
-  \end{minipage}
-  \hfill
-%  \begin{minipage}[t]{.16\textwidth}
-%    \raggedleft
-%    \input{./fig/breast_cancer.tex}
-%  \end{minipage}
-%  \hfill
-%  \begin{minipage}[t]{.16\textwidth}
-%    \raggedleft
-%    \input{./fig/ionosphere.tex}
-%  \end{minipage}
-%  \hfill
-  \begin{minipage}[t]{.16\textwidth}
-    \raggedleft
-    \input{./fig/glass.tex}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[t]{.16\textwidth}
-    \raggedleft
-    \input{./fig/vehicle.tex}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[t]{.16\textwidth}
-    \raggedleft
-    \input{./fig/waveform.tex}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[t]{.16\textwidth}
-    \raggedleft
-    \input{./fig/digits.tex}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[t]{.16\textwidth}
-    \raggedleft
-    \input{./fig/satellite.tex}
-  \end{minipage}\\%[1em]
-  %
-  % Show the legend separately
-  %\pgfplotsset{hide axis,legend columns=-1,legend style={draw=none,column sep=1ex,font=\Large}}
-  %\input{./fig/uci-legend.tex}\\[-2.5em]
-  \caption{Comparison of convergence in terms of  negative log-predictive density (NLPD) as averages over 10-fold cross-validation runs, on UCI classification tasks.}
-  \label{fig:uci}
-  %\vspace*{-6pt}
-\end{figure}
-
 \subsection{Capturing uncertainty in UCI tasks under supervised learning}
@@
 %
-We consider the same 8 UCI~\cite{UCI} classification benchamrks tasks and setup as were considered in \cite{todo}.
-We use a two-layer MLP for all tasks and follow the setup in \cref{sec:methods} for \our.
+We consider $8$ of the UCI~\cite{UCI} classification benchmarks as in \cite{immer2021improving}, consisting of a range of binary and multi-class classification with varying dataset sizes.
+We first train two-layer MLPs for each of the classification tasks and follow the setup in \cref{sec:methods} for \our.
 After training, we construct the \our dual and use the resulting model for uncertainty quantification.
-We performed hyperparameter search over the prior precision $\delta$, and ran the experiment over 10 random splits.
+For comparison, we used the same hyperparameters for neural network training as in the UCI experiments of \cite{immer2021improving}, and similarly performed hyperparameter search over the prior precision $\delta$, and ran the experiment over 10 random splits.
 %Depending on task dimension and complexity, our model can match the neural network MAP in negative log-predictive density (NLPD) even with a low number of inducing points (see \cref{tbl:uci} left).
 In \cref{tbl:uci} (left), we compare our model to the NN MAP estimate, mean-field VI, a Bayesian NN, and a GLM model (see \cite{add} for the baselines) in negative log-predictive density (NLPD).
-We match the predictive performance despite being sparse (here, $M=$).
+We match the predictive performance despite being sparse (here, $M=256$).
 Results for $M=16,32,64,128,256$ included in \cref{app:uci} with full experiment details.
 
-In \cref{tbl:uci} (right), we also include an ablation and comparison (to \cite{todo}) study with a fixed low number of inducing points ($M=$).
-The comparison shows that our sparse method is able to summarize the information of the full data set more efficiently than sparse subset methods.
+In \cref{tbl:uci} (right), we also include an ablation and comparison study with a fixed low number of inducing points ($M=32$).
+The comparison shows that our sparse method is able to summarize the information of the full data set more efficiently than sparse subset methods, and can match the performance of the full GP even with a low number of inducing points.
 
@@
 During the initial NN training, we used a learning rate of $1e-3$.
-
-\begin{figure}
-  \raggedleft\scriptsize
-  \setlength{\figurewidth}{\textwidth}
-  \setlength{\figureheight}{.55\figurewidth}
-  %\pgfplotsset{axis on top,ymajorgrids,axis line style={draw=none},legend style={at={(-.1,-.1)},anchor=north east}}
-  %\pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
-  %\def\our{{\sc sfr} (ours)}
-  \input{./fig/MNIST_acc.tex}
-  \caption{Foo}
-  \label{fig:mnist}
-\end{figure}
 

### 2023-05-17 paper/main.tex
Revert back to an older version that is ok.

--- 2023-05-17 paper/main.tex
@@
 
-\paragraph{Implementation} We implement all methods in PyTorch~\cite{paszke2019pytorch} and leverage the XXXX libraries.. \todo{add brief details}. Experiments were run on clusters
+\paragraph{Implementation} We implement all methods in PyTorch~\cite{paszke2019pytorch} and leverange the XXXX libraries.. \todo{add brief details}. Experiments were run on clusters
 
@@
 
+\begin{figure}[t]
+  \centering\scriptsize
+  \setlength{\figurewidth}{.26\textwidth}
+  \setlength{\figureheight}{\figurewidth}
+  \pgfplotsset{axis on top,scale only axis,y tick label style={rotate=90}, x tick label style={font=\footnotesize},y tick label style={font=\footnotesize},title style={yshift=-4pt,font=\large}, y label style={font=\large},x label style={font=\large},grid=major, width=\figurewidth, height=\figureheight}
+  \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
+  \pgfplotsset{xlabel={$M$},ylabel style={yshift=-12pt}}  
+  %
+  \begin{minipage}[t]{.17\textwidth}
+    \raggedleft
+    \pgfplotsset{ylabel=NLPD}
+    \input{./fig/australian.tex}
+  \end{minipage}
+  \hfill
+%  \begin{minipage}[t]{.16\textwidth}
+%    \raggedleft
+%    \input{./fig/breast_cancer.tex}
+%  \end{minipage}
+%  \hfill
+%  \begin{minipage}[t]{.16\textwidth}
+%    \raggedleft
+%    \input{./fig/ionosphere.tex}
+%  \end{minipage}
+%  \hfill
+  \begin{minipage}[t]{.16\textwidth}
+    \raggedleft
+    \input{./fig/glass.tex}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[t]{.16\textwidth}
+    \raggedleft
+    \input{./fig/vehicle.tex}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[t]{.16\textwidth}
+    \raggedleft
+    \input{./fig/waveform.tex}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[t]{.16\textwidth}
+    \raggedleft
+    \input{./fig/digits.tex}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[t]{.16\textwidth}
+    \raggedleft
+    \input{./fig/satellite.tex}
+  \end{minipage}\\%[1em]
+  %
+  % Show the legend separately
+  %\pgfplotsset{hide axis,legend columns=-1,legend style={draw=none,column sep=1ex,font=\Large}}
+  %\input{./fig/uci-legend.tex}\\[-2.5em]
+  \caption{Comparison of convergence in terms of  negative log-predictive density (NLPD) as averages over 10-fold cross-validation runs, on UCI classification tasks.}
+  \label{fig:uci}
+  %\vspace*{-6pt}
+\end{figure}
+
 \subsection{Capturing uncertainty in UCI tasks under supervised learning}
@@
 %
-We consider $8$ of the UCI~\cite{UCI} classification benchmarks as in \cite{immer2021improving}, consisting of a range of binary and multi-class classification with varying dataset sizes.
-We first train two-layer MLPs for each of the classification tasks and follow the setup in \cref{sec:methods} for \our.
+We consider the same 8 UCI~\cite{UCI} classification benchamrks tasks and setup as were considered in \cite{todo}.
+We use a two-layer MLP for all tasks and follow the setup in \cref{sec:methods} for \our.
 After training, we construct the \our dual and use the resulting model for uncertainty quantification.
-For comparison, we used the same hyperparameters for neural network training as in the UCI experiments of \cite{immer2021improving}, and similarly performed hyperparameter search over the prior precision $\delta$, and ran the experiment over 10 random splits.
+We performed hyperparameter search over the prior precision $\delta$, and ran the experiment over 10 random splits.
 %Depending on task dimension and complexity, our model can match the neural network MAP in negative log-predictive density (NLPD) even with a low number of inducing points (see \cref{tbl:uci} left).
 In \cref{tbl:uci} (left), we compare our model to the NN MAP estimate, mean-field VI, a Bayesian NN, and a GLM model (see \cite{add} for the baselines) in negative log-predictive density (NLPD).
-We match the predictive performance despite being sparse (here, $M=256$).
+We match the predictive performance despite being sparse (here, $M=$).
 Results for $M=16,32,64,128,256$ included in \cref{app:uci} with full experiment details.
 
-In \cref{tbl:uci} (right), we also include an ablation and comparison study with a fixed low number of inducing points ($M=32$).
-The comparison shows that our sparse method is able to summarize the information of the full data set more efficiently than sparse subset methods, and can match the performance of the full GP even with a low number of inducing points.
+In \cref{tbl:uci} (right), we also include an ablation and comparison (to \cite{todo}) study with a fixed low number of inducing points ($M=$).
+The comparison shows that our sparse method is able to summarize the information of the full data set more efficiently than sparse subset methods.
 

### 2023-05-17 src/sl/train.py
put inference in try/except

@@ -349,29 +349,35 @@ def train(cfg: DictConfig):
         cfg.gp_subset, prior=prior, network=network
     )
 
-    cfg.predictive_model = "glm"
-    compute_metrics(
-        sfr=sfr,
-        gp_subset=gp_subset_not_used,
-        ds_train=ds_train,
-        ds_test=ds_test,
-        cfg=cfg,
-        checkpoint={},
-    )
+    try:
+        cfg.predictive_model = "glm"
+        compute_metrics(
+            sfr=sfr,
+            gp_subset=gp_subset_not_used,
+            ds_train=ds_train,
+            ds_test=ds_test,
+            cfg=cfg,
+            checkpoint={},
+        )
+    except:
+        logger.info("GLM failed predict")
 
-    cfg.predictive_model = "bnn"
-    compute_metrics(
-        sfr=sfr,
-        gp_subset=gp_subset_not_used,
-        ds_train=ds_train,
-        ds_test=ds_test,
-        cfg=cfg,
-        checkpoint={},
-    )
+    try:
+        cfg.predictive_model = "bnn"
+        compute_metrics(
+            sfr=sfr,
+            gp_subset=gp_subset_not_used,
+            ds_train=ds_train,
+            ds_test=ds_test,
+            cfg=cfg,
+            checkpoint={},
+        )
+    except:
+        logger.info("BNN failed predict")
 
     num_data = len(ds_train)
     # for m in [16, 32, 64, 128, 256, 512, 1024, 2048, 3200]:
-    for m in [256, 512, 1024, 2048, 3200]:
+    for m in [128, 256, 512, 1024, 2048, 3200]:
         if m >= num_data:
             break
         sfr.num_inducing = m
@@ -390,26 +396,32 @@ def train(cfg: DictConfig):
             cfg.gp_subset, subset_size=m, prior=prior, network=network
         )
 
-        cfg.predictive_model = "sfr"
-        compute_metrics(
-            sfr=sfr_double,
-            gp_subset=gp_subset,
-            ds_train=ds_train,
-            ds_test=ds_test,
-            cfg=cfg,
-            checkpoint={},
-        )
+        try:
+            cfg.predictive_model = "sfr"
+            compute_metrics(
+                sfr=sfr_double,
+                gp_subset=gp_subset,
+                ds_train=ds_train,
+                ds_test=ds_test,
+                cfg=cfg,
+                checkpoint={},
+            )
+        except:
+            logger.info("SFR failed predict")
 
[…]

### 2023-05-17 paper/main.tex
CL bit

@@
-% !TeX spellcheck = en_GB
+% !TeX spellcheck = en_US
 \documentclass{article}
@@
 % Overview
-We aim to highlight our sparse representation's ability to retain prior knowledge within a continual learning (CL) setting (as in \cref{sec:sequential}).
-Notably, CL methods require tuning making direct comparisons difficult.
-We consider the setup with single-head (SH) setting that is typically hard and more competitive.
+
+We aim to highlight our sparse representation's ability to retain prior knowledge for continual learning (CL) (as in \cref{sec:sequential}).
+We consider the single-head (SH) setting that is harder and more realistic than multi-head (MH)~\citep{van2019three}.	 \todo{can't find the bibtex for their NIPS workshop paper} % typically hard and more competitive \cite{}
 %
 % Benchmarks/architectures
-We consider the CL benchmarks: Sequential-MNIST (S-MNIST), Sequential-FashionMNIST (S-FMNIST), and Permuted-MNIST (P-MNIST).
-We follow the setups described in \cite{rudner2022continual, pan2020continual}, using a two-layer MLP with 256 hidden units and ReLU activation for S-MNIST and S-FMNIST, and a two-layer MLP with 100 hidden units for P-MNIST (full details in \cref{app:cl-exp}).
+ Our \our-based regularizer is evaluated on three CL benchmarks, specifically Split-MNIST (S-MNIST), Split-FashionMNIST (S-FMNIST), and the 10-tasks Permuted-MNIST (P-MNIST).
+We adhere to the same setups as outlined in \cite{rudner2022continual, pan2020continual}, which involve utilizing a two-layer MLP with 256 hidden units and ReLU activation for S-MNIST and S-FMNIST, and a two-layer MLP with 100 hidden units for P-MNIST, to ensure consistency.
+Please refer to \cref{app:cl-exp} for full details.
 
@@
 We compare our method against two categories of methods: {\em (i)}~weight-regularization methods: EWC, SI, and VCL (which additionally incorporates coresets), and {\em(ii)}~function-based regularization methods: DER, FROMP, S-FSVI, SFR.
-We also introduce an ablation study where we replace $\bar{\MB}^{-1}$ with an identity matrix $\MI_M$, equivalent to assuming a GP with i.i.d.\ prior (giving an L2 regularizer).
-Following \cite{rudner2022continual}, we use 200 inducing points per tasks.
-Additionally,  we consider only 40 inducing points for S-MNIST, to investigate if our method was still capable of capture more information due to its sparse formulation.
+We also introduce an ablation study where we replace $\bar{\MB_t}^{-1}$ with an identity matrix $\MI_M$, equivalent to assuming a GP with i.i.d.\ prior with a unit variance (giving an L2 regularizer).
+Following \cite{rudner2022continual}, we use 200 points per tasks.
+Additionally,  we consider only 40 points for S-MNIST, to investigate if our method was still capable of capture more information due to its sparse formulation.
 

### 2023-05-17 paper/main.tex
CL bit

@@
 % Overview
-
-We aim to highlight our sparse representation's ability to retain prior knowledge for continual learning (CL) (as in \cref{sec:sequential}).
+We aim to highlight our sparse representation's ability to retain previous knowledge for continual learning (CL) (as in \cref{sec:sequential}).
 We consider the single-head (SH) setting that is harder and more realistic than multi-head (MH)~\citep{van2019three}.	 \todo{can't find the bibtex for their NIPS workshop paper} % typically hard and more competitive \cite{}
@@
 We compare our method against two categories of methods: {\em (i)}~weight-regularization methods: EWC, SI, and VCL (which additionally incorporates coresets), and {\em(ii)}~function-based regularization methods: DER, FROMP, S-FSVI, SFR.
-We also introduce an ablation study where we replace $\bar{\MB_t}^{-1}$ with an identity matrix $\MI_M$, equivalent to assuming a GP with i.i.d.\ prior with a unit variance (giving an L2 regularizer).
-Following \cite{rudner2022continual}, we use 200 points per tasks.
-Additionally,  we consider only 40 points for S-MNIST, to investigate if our method was still capable of capture more information due to its sparse formulation.
+We also introduce an ablation study where we replace $\bar{\MB}_t^{-1}$ with an identity matrix $\MI_M$, equivalent to using an L2 regularizer.
+In \cref{tbl:cl_table_1}, we use 200 points for each task, and we further demonstrate our method's ability to compress information to a low number of points in S-MNIST.
 
 %% Comments on the results:
-\cref{tbl:cl_table_1} shows results
-We get the best results on S-MNIST both 40 and 200 pts. per task
-
-On S-FMNIST we are on par with DER, which is however exploiting a reservoir buffer technique, that iteratively samples new "inducing points"
-
-On P-MNIST we are lower than S-FSVI, however % I'm still running experiments, so we can hope that it is not the best overall in the end
+From \cref{tbl:cl_table_1}, it is clear that the weight-space regularization methods completely fail compared to the function-space methods on S-MNIST and S-FMNIST, but are comparable on P-MNIST.
+%, commonly referred as Domain Incremental Learning.
+(opposed to the Class-Incremental Learning for S-MNIST and S-FMNIST)
+Considering only function-space methods, we can see that \our achieves the best results on most datasets, and is particularly effective, when using fewer points per task.
+On S-FMNIST, our method obtains close results to DER, which regularizes the model by taking the mean squared error between current and old function outputs without accounting the covariance structure of the loss similar to our L2 ablation.
+Moreover, their method exploits reservoir sampling \citep{vitter1985random} to obtain a continuously updated set inducing points.
+S-FSVI obtains the best on P-MNIST, but with the downside of requiring high computational costs based on performing variational inference, compared to \our.
+\todo{on PMNIST our method is not really super-fast, so that could be not the best thing to say here} % we could also say that P-MNIST is known to be a bad/ill-posed dataset for CL
+Finally, it is worth noticing as our ablation already provides a very solid baseline consistently over all datasets.
 

### 2023-05-17 paper/main.tex
Polishing UCI text

--- 2023-05-17 paper/main.tex
@@
   \caption{Comparisons and ablations on UCI data with negative log predictive density (NLPD\textcolor{gray}{\footnotesize$\pm$std}, lower better).
-Our sparse \our ($M=256$) is on par with or better than full models (left) and outperforms the GP subset approach of \cite{todo}.
+Our sparse \our ($M=256$) is on par with or better than full models (left) and outperforms the GP subset approach of \cite{immer2021improving} (right).
+Results for methods marked with * are from their original implementation in \cite{immer2021improving}.
 See \cref{app:uci} for additional tables with comparisons.}
@@
   %\input{./fig/uci-legend.tex}\\[-2.5em]
-  \caption{Comparison of convergence in terms of  negative log-predictive density (NLPD) as averages over 10-fold cross-validation runs, on UCI classification tasks.}
+  \caption{Comparison of convergence in terms of negative log-predictive density (NLPD) as averages over $10$-fold cross-validation runs, on UCI classification tasks.}
   \label{fig:uci}
@@
 %
-We consider the same 8 UCI~\cite{UCI} classification benchamrks tasks and setup as were considered in \cite{todo}.
-We use a two-layer MLP for all tasks and follow the setup in \cref{sec:methods} for \our.
-After training, we construct the \our dual and use the resulting model for uncertainty quantification.
-We performed hyperparameter search over the prior precision $\delta$, and ran the experiment over 10 random splits.
+We consider $8$ of the UCI~\cite{UCI} benchmarks, consisting of a range of binary and multi-class classification with varying dataset sizes.
+We first train two-layer MLPs for each of the classification tasks and follow the setup in \cref{sec:methods} for \our.
+That is, after training we construct the \our dual and use the resulting model for uncertainty quantification.
+For comparison, we used the same hyperparameters for neural network training as in the UCI experiments of \cite{immer2021improving}, and similarly performed hyperparameter search over the prior precision $\delta$, and ran the experiment over $10$ random splits.
  %Depending on task dimension and complexity, our model can match the neural network MAP in negative log-predictive density (NLPD) even with a low number of inducing points (see \cref{tbl:uci} left).
-In \cref{tbl:uci} (left), we compare our model to the NN MAP estimate, mean-field VI, a Bayesian NN, and a GLM model (see \cite{add} for the baselines) in negative log-predictive density (NLPD).
-We match the predictive performance despite being sparse (here, $M=$).
-Results for $M=16,32,64,128,256$ included in \cref{app:uci} with full experiment details.
-
-In \cref{tbl:uci} (right), we also include an ablation and comparison (to \cite{todo}) study with a fixed low number of inducing points ($M=$).
-The comparison shows that our sparse method is able to summarize the information of the full data set more efficiently than sparse subset methods.
+In \cref{tbl:uci} (left), we compare our model to the NN MAP estimate, mean-field VI, a Bayesian NN, and a GLM model (see \cite{immer2021improving} for the baselines) in negative log-predictive density (NLPD).
+We match the predictive performance despite being sparse (here, $M=256$).
+Results for $M=16,32,64,128,256$ are included in \cref{app:uci} with full experiment details.
+
+In \cref{tbl:uci} (right), we also include an ablation and comparison (to \cite{immer2021improving}) study with a fixed low number of inducing points ($M=32$).
+The comparison shows that our sparse method is able to summarize the information of the full data set more efficiently than sparse subset methods, and can match the performance of the full GP even with a low number of inducing points.
 

### 2023-05-17 paper/main.tex
Comments to intro 1.0

@@
 %Current state of affairs 
-Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) show that converting trained neural networks to a Bayesian neural network through the Laplace-GGN can provide uncertainty without sacrificing additional training cost \cite{foong2019between}.
-Furthermore, the resultant weight space posterior can be converted to the function space as shown \cite{khan2019approximate, immer2021improving}.
-The function space allows for a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{foong2019between}.
+Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) show that converting trained neural networks to a Bayesian neural network through the Laplace-GGN \todo{Is Laplace-GGN a well-known acronym?} can provide uncertainty without sacrificing additional resources to training \cite{foong2019between}.
+Furthermore, the resultant weight space posterior can be converted to the function space as shown in \cite{khan2019approximate, immer2021improving}.
+The function space representation allows for a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{foong2019between}.
 These methods rely on the linearization of the neural network and the resultant neural tangent kernel (NTK, \cite{jacot2018neural}).
@@
 %Need for adaptive learning methods + failures with current methods
-Given an approximate inference technique, we demonstrate that the neural network emits `dual' parameters which are the building blocks of a GP~\cite{csato2002sparse, adam2021dual, chang2020fast}.
-In contrast to previous work that utilizes subsets \cite{immer2021scalable}, this parameterization allows consolidating contributions from {\em all} training data into a sparse representation, essential for predictive uncertainty.
-Crucially, the resulting GP now predicts in the same space as the original trained neural network, a feature not present in previous approaches, while avoiding the notorious cubic complexity of vanilla GPs.
+Given an approximate inference technique, we demonstrate that the neural network emits \todo{is 'emits' a clear enough expression here?}`dual' parameters which are the building blocks of a GP~\cite{csato2002sparse, adam2021dual, chang2020fast} .
+In contrast to previous work that utilizes subsets \todo{What kind of subsets?
+Probably should specify NTK + GP subset to be clear} \cite{immer2021scalable}, this parameterization allows consolidating contributions from {\em all} training data into a sparse representation, essential for predictive uncertainty.
+Crucially, the resulting GP now predicts in the same space as the original trained neural network \todo{Could make it clearer that the GP predicts in the output space while avoiding the NN parameter space}, a feature not present in previous approaches, while avoiding the notorious cubic complexity of vanilla GPs.
 Through the dual parameter formulation, we establish a connection between the neural network, full GPs, and a sparse approximation similar to sparse variational GPs~\cite{titsias2009variational}.
-We refer to our method as \our---a sparse GP derived from a trained neural network.
-As \our is in the dual parameters, we can perform dual conditioning recently shown effective in \cite{chang2022fantasizing}, that is, avoid retraining and condition new data into our model (see \cref{fig:teaser}).\looseness-2
+We refer to our method as \our---a sparse GP derived from a trained neural network \todo{I assume FR is for functional representation?
+Could be written here for extra clarity}.
+As \our is in the dual parameters, we can perform dual conditioning recently shown effective in \cite{chang2022fantasizing}, that is, avoid retraining and condition new data into our model (see \cref{fig:teaser}) \todo{Effective compared to what?}.\looseness-2
 %Need uncertainty and adaptive methods

### 2023-05-17 paper/main.tex
Caption

--- 2023-05-17 paper/main.tex
@@
 %
-
 We present a series of experiments designed to demonstrate the versatility and efficacy of \our. We seek to find answers to the following questions: 
@@
 (\cref{sec:uci}) How do predictions with our sparse function-space approximation compare to weight-space approximations?
-\textbf{Function-space updates:} How fast are our function-space updates relative to retraining from scratch? Do they improve predictive performance? \todo{what do we have on this?}
+\textbf{Function-space updates:} How fast are our function-space updates relative to retraining from scratch? Do they improve predictive performance? 
 \textbf{Representation:} Can a sparse function-space representation help retain knowledge from previous tasks in CL? (\cref{sec:cl-exp})
@@
   \caption{Comparisons and ablations on UCI data with negative log predictive density (NLPD\textcolor{gray}{\footnotesize$\pm$std}, lower better).
-Our sparse \our ($M=256$) is on par with or better than full models (left) and outperforms the GP subset approach of \cite{immer2021improving} (right).
-Results for methods marked with * are from their original implementation in \cite{immer2021improving}.
+Our sparse \our ($M=256$) is on par with or better than full models (left) and outperforms the GP subset approach of \cite{todo}.
 See \cref{app:uci} for additional tables with comparisons.}
@@
     \input{./fig/satellite.tex}
-  \end{minipage}\\%[1em]
-  %
-  % Show the legend separately
-  %\pgfplotsset{hide axis,legend columns=-1,legend style={draw=none,column sep=1ex,font=\Large}}
-  %\input{./fig/uci-legend.tex}\\[-2.5em]
-  \caption{Comparison of convergence in terms of negative log-predictive density (NLPD) as averages over $10$-fold cross-validation runs, on UCI classification tasks.}
+  \end{minipage}\\[-1em]
+  %
+  % Legend  
+  \definecolor{steelblue31119180}{RGB}{31,119,180}
+  \newcommand{\myline}[1]{\protect\tikz[baseline=-.5ex,line width=1.6pt]\protect\draw[draw=#1](0,0)--(1.2em,0);}
+  \caption{Comparison of convergence in terms of number of inducing data points $M$ in NLPD (mean over 10 random splits) on UCI classification tasks: \our (thick) vs.\ subsets (thin).
+The blue lines (\myline{steelblue31119180}) use the NN mean, whereas the orange lines (\myline{steelblue31119180}) use the GP mean.
+Our \our's converges fast for all cases.}
   \label{fig:uci}
@@
 %
-We consider $8$ of the UCI~\cite{UCI} benchmarks, consisting of a range of binary and multi-class classification with varying dataset sizes.
-We first train two-layer MLPs for each of the classification tasks and follow the setup in \cref{sec:methods} for \our.
-That is, after training we construct the \our dual and use the resulting model for uncertainty quantification.
-For comparison, we used the same hyperparameters for neural network training as in the UCI experiments of \cite{immer2021improving}, and similarly performed hyperparameter search over the prior precision $\delta$, and ran the experiment over $10$ random splits.
+We consider the same 8 UCI~\cite{UCI} classification benchamrks tasks and setup as were considered in \cite{todo}.
+We use a two-layer MLP for all tasks and follow the setup in \cref{sec:methods} for \our.
+After training, we construct the \our dual and use the resulting model for uncertainty quantification.
+We performed hyperparameter search over the prior precision $\delta$, and ran the experiment over 10 random splits.
 %Depending on task dimension and complexity, our model can match the neural network MAP in negative log-predictive density (NLPD) even with a low number of inducing points (see \cref{tbl:uci} left).
-In \cref{tbl:uci} (left), we compare our model to the NN MAP estimate, mean-field VI, a Bayesian NN, and a GLM model (see \cite{immer2021improving} for the baselines) in negative log-predictive density (NLPD).
-We match the predictive performance despite being sparse (here, $M=256$).
-Results for $M=16,32,64,128,256$ are included in \cref{app:uci} with full experiment details.
-
-In \cref{tbl:uci} (right), we also include an ablation and comparison (to \cite{immer2021improving}) study with a fixed low number of inducing points ($M=32$).
-The comparison shows that our sparse method is able to summarize the information of the full data set more efficiently than sparse subset methods, and can match the performance of the full GP even with a low number of inducing points.
+In \cref{tbl:uci} (left), we compare our model to the NN MAP estimate, mean-field VI, a Bayesian NN, and a GLM model (see \cite{add} for the baselines) in negative log-predictive density (NLPD).
+We match the predictive performance despite being sparse (here, $M=$).
+Results for $M=16,32,64,128,256$ included in \cref{app:uci} with full experiment details.
+
+In \cref{tbl:uci} (right), we also include an ablation and comparison (to \cite{todo}) study with a fixed low number of inducing points ($M=$).
+The comparison shows that our sparse method is able to summarize the information of the full data set more efficiently than sparse subset methods.
 
@@
 
-\begin{figure}
-  \raggedleft\scriptsize
-  \setlength{\figurewidth}{\textwidth}
-  \setlength{\figureheight}{.55\figurewidth}
-  %\pgfplotsset{axis on top,ymajorgrids,axis line style={draw=none},legend style={at={(-.1,-.1)},anchor=north east}}
-  %\pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
-  %\def\our{{\sc sfr} (ours)}
-  \input{./fig/MNIST_acc.tex}
-  \caption{Foo}
-  \label{fig:mnist}
-\end{figure}
+%\begin{figure}
+%  \raggedleft\scriptsize
+%  \setlength{\figurewidth}{\textwidth}
+%  \setlength{\figureheight}{.55\figurewidth}
+%  %\pgfplotsset{axis on top,ymajorgrids,axis line style={draw=none},legend style={at={(-.1,-.1)},anchor=north east}}
+%  %\pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
+%  %\def\our{{\sc sfr} (ours)}
+%  \input{./fig/MNIST_acc.tex}
+%  \caption{Foo}
+%  \label{fig:mnist}
+%\end{figure}
+%
 

### 2023-05-17 paper/main.tex
Caption
Comments on related work

--- 2023-05-17 paper/main.tex
@@
 Function-space perspectives on uncertainty in neural networks often use a Laplace-GGN approximation \citep{daxberger2021laplace}, linearizing a trained neural network around optimal weights.
-The Hessian can be efficiently approximated using the generalized Gauss--Newton approximation (GGN, \cite{botev2017practical}).
+\todo{Could modify the sentence a bit, maybe "The Laplace-GGN approximates the Hessian by using..."}The Hessian can be efficiently approximated using the generalized Gauss--Newton approximation (GGN, \cite{botev2017practical}).
 While efficient, it suffers from cubic scaling in parameter count, necessitating approximations like Kronecker factorisation \cite{martens2015optimizing, ritter2018kfac}.
-This linear model (linear in the weights) refines predictions and provides uncertainty estimates \citep{immer2021scalable}.
+\todo{Reads a bit repetitive to start two sentences in a row by This, could maybe be combined in one.} This linear model (linear in the weights) refines predictions and provides uncertainty estimates \citep{immer2021scalable}.
 This model has a convenient interpretation as a GP \cite{immer2021scalable, khan2019approximate, maddox2021fast}.
@@
 However, the GP's cubic $\mathcal{O}(n^3)$ scaling with data points $n$ requires costly approximations, often resorting to using data subsets \cite{immer2021scalable}.
-In the GP community, sparse approximations have mitigated this scaling issue (\eg, \cite{titsias2009variational,hensman2013gaussian}), but combining neural network linearization with sparse methods remains unclear without resorting to subset methods.
+In the GP community, sparse approximations have mitigated this scaling issue (\eg, \cite{titsias2009variational,hensman2013gaussian}), but combining neural network linearization with sparse methods remains \todo{Maybe unexplored instead of unclear?} unclear without resorting to subset methods \todo{Could add something on subset methods here, for example 'which do not retain information from the full dataset' or something like that}.
 Our work addresses this by utilizing the GP's dual parameters \cite{csato2002sparse}, previously applied to non-conjugate likelihood models \cite{adam2021dual}.
@@
 However, encoding functional knowledge in the weights does not guarantee good quality of the predictions.
-Function-space regularization techniques~\cite{li2018lwf, benjamin2018measuring, titsias2019functional, buzzega2020dark, pan2020continual, rudner2022continual} address this by relying on training data subsets for each task to compute the regularization term.
-These methods bridge the gap between objective and rehearsal-based methods since they use a subset of the training data for each task to compute the regularization term.
+Function-space regularization techniques~\cite{li2018lwf, benjamin2018measuring, titsias2019functional, buzzega2020dark, pan2020continual, rudner2022continual} address this by relying on training data subsets for each task to compute a regularization term.
+These methods bridge the gap between objective and rehearsal-based methods \todo{I'm not familiar with the differences between objective vs rehearsal based methods, and it isn't explained here} since they use a subset of the training data for each task to compute the regularization term.
 Recently proposed methods, \eg, DER~\citep{buzzega2020dark}, FROMP~\citep{pan2020continual}, and S-FSVI~\citep{rudner2022continual} achieve state-of-the-art performance among the objective-based techniques in several CL benchmarks.
-\looseness-2
+\todo{Are DER, FROMP and FSVI function-space regularization methods?
+I assume so but the text makes it a bit vague.}\looseness-2
 
@@
 \todo{cite UCRL paper}
-No single strategy has emerged as a go to method and we highlight that these strategies are only as good as their uncertainty estimates.
+No single strategy has emerged as a go-to method and we highlight that these strategies are only as good as their uncertainty estimates.
 Previous approaches have used GPs \cite{deisenroth2011pilco,kamtheDataEfficient2018},
 ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
-and variational inference \cite{galImproving2016,houthooftVIME2017}.
+and variational inference \cite{galImproving2016,houthooftVIME2017}. \todo{Could specify here how the previous methods have used these models}
 %However, there has been little leveraging

### 2023-05-17 paper/main.tex

@@
     \input{./fig/satellite.tex}
-  \end{minipage}\\%[1em]
-  %
-  % Show the legend separately
-  %\pgfplotsset{hide axis,legend columns=-1,legend style={draw=none,column sep=1ex,font=\Large}}
-  %\input{./fig/uci-legend.tex}\\[-2.5em]
-  \caption{Comparison of convergence in terms of negative log-predictive density (NLPD) as averages over $10$-fold cross-validation runs, on UCI classification tasks.}
+  \end{minipage}\\[-1em]
+  %
+  % Legend  
+  \definecolor{steelblue31119180}{RGB}{31,119,180}
+  \definecolor{darkorange25512714}{RGB}{255,127,14}  
+  \newcommand{\myline}[1]{\protect\tikz[baseline=-.5ex,line width=1.6pt]\protect\draw[draw=#1](0,0)--(1.2em,0);}
+  \caption{Comparison of convergence in terms of number of inducing data points $M$ in NLPD (mean over 10 random splits) on UCI classification tasks: \our (thick) vs.\ subsets (thin).
+The orange lines (\myline{darkorange25512714}) use the GP mean, whereas the blue lines (\myline{steelblue31119180}) the NN MAP estimate as the mean.
+Our \our's converges fast for all cases.}
   \label{fig:uci}

### 2023-05-17 paper/main.tex
Minor

--- 2023-05-17 paper/main.tex
@@
   \definecolor{steelblue31119180}{RGB}{31,119,180}
+  \definecolor{darkorange25512714}{RGB}{255,127,14}  
   \newcommand{\myline}[1]{\protect\tikz[baseline=-.5ex,line width=1.6pt]\protect\draw[draw=#1](0,0)--(1.2em,0);}
-  \caption{Comparison of convergence in terms of number of inducing data points $M$ in NLPD (mean over 10 random splits) on UCI classification tasks: \our (thick) vs.\ subsets (thin).
-The blue lines (\myline{steelblue31119180}) use the NN mean, whereas the orange lines (\myline{steelblue31119180}) use the GP mean.
+  \caption{Comparison of convergence in terms of number of inducing data points $M$ in NLPD (mean over 10 seeds) on UCI classification tasks: \our (thick) vs.\ subsets (thin).
+The orange lines (\myline{darkorange25512714}) use the GP mean, whereas the blue lines (\myline{steelblue31119180}) the NN MAP estimate as the mean.
 Our \our's converges fast for all cases.}

### 2023-05-17 paper/main.tex

--- 2023-05-17 paper/main.tex
@@
   \newcommand{\myline}[1]{\protect\tikz[baseline=-.5ex,line width=1.6pt]\protect\draw[draw=#1](0,0)--(1.2em,0);}
-  \caption{Comparison of convergence in terms of number of inducing data points $M$ in NLPD (mean over 10 random splits) on UCI classification tasks: \our (thick) vs.\ subsets (thin).
+  \caption{Comparison of convergence in terms of number of inducing data points $M$ in NLPD (mean over 10 seeds) on UCI classification tasks: \our (thick) vs.\ subsets (thin).
 The orange lines (\myline{darkorange25512714}) use the GP mean, whereas the blue lines (\myline{steelblue31119180}) the NN MAP estimate as the mean.

### 2023-05-17 paper/main.tex
Commenting Background section

--- 2023-05-17 paper/main.tex
@@
 
-\textbf{Function space}
+\textbf{Function space} \todo{Could be titled some other way, like Function-space representation}
 %As a neural network is a deterministic mapping, the weight-space posterior induces a distribution over the function values.
@@
 It is worth noting that the NTK linearises the network around the MAP solution $\weights^{*}$,
-so the function space prior (and thus posterior) is only a locally linear approximation.
+so the function-space prior (and thus posterior) is only a locally linear approximation.
 In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.

### 2023-05-17 paper/main.tex
Comments on Section 3

--- 2023-05-17 paper/main.tex
@@
 \Jac{\weights_*}{\vx} \, \weights$, where $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{C \times P}$ is the Jacobian at the MAP.
-Using the Hessian of the approximate model, we arrive at the Laplace-GGN approximate posterior for $q(\vw)$. 
-Therefore, the Laplace-GGN linear model can be used to convert our weight space model to the function space by,
+Using the Hessian of the approximate model, we arrive at the Laplace-GGN approximate posterior for $q(\vw)$ \todo{This is the first time q(w) is used, should define it}. 
+Therefore, the Laplace-GGN linear model can be used to convert our weight space model to the function space by \todo{To be super clear even when reading this part out of context: could specify that using a GP with this mean and covariance},
 \begin{equation} 
@@
 With this kernel function, we can combine it with the data set $\dataset$ to construct the posterior.
+\todo{what is "it" here?}
 %
@@
 %\paragraph{GP in the dual parameters}
-The seminal work by \citet{csato2002sparse} (parameterization Lemma~1) gives a parameterization for the posterior process $f_{\textrm{post}}$ that can be found through the Bayesian update using the GP prior and the likelihood function.
+The seminal work by \citet{csato2002sparse} (parameterization Lemma~1) gives a parameterization for the posterior process $f_{\textrm{post}}$ \todo{The f post doesn't match the notation in Background?} that can be found through the Bayesian update using the GP prior and the likelihood function.
 This gives a `dual' parameterization, $\valpha$ and $\vbeta$,
@@
 Originally \citet{csato2002sparse} iteratively find dual variables using an expectation propagation (EP, \cite{minka2001expectation}) method.
-More recently \cite{khan2017conjugate,adam2021dual}, has shown this relationship for variational Gaussian processes where the above expectation is with respect to the approximate variational posterior.
-Meanwhile in \citet{wilkinson2023bayes}, they show links between linearization methods and how they solve the \cref{eq:dual_param}.
+More recently \cite{khan2017conjugate,adam2021dual}, has \todo{Should it be have or has?}shown this relationship for variational Gaussian processes where the above expectation is with respect to the approximate variational posterior.
+Meanwhile in \citet{wilkinson2023bayes}, they show links between linearization methods and how they solve the \todo{Could make passive / active voice more consistent in this paragraph} \cref{eq:dual_param}.
 
@@
 %
-Substiuting \cref{eq:dual_param_laplace} into \cref{eq:gp_pred}, we obtain our GP model based on the converged neural network.
+Substituting \cref{eq:dual_param_laplace} into \cref{eq:gp_pred}, we obtain our GP model based on the converged neural network.
 Again, this is similar to what was derived in \citet{immer2021improving} for the posterior variance function.
@@
 %
-Sparse Gaussian processes reduce the computational complexity by representing the GP as a low-rank approximation induced by a sparse set of inputs points (see \cite{quinonero2005unifying} for an early overview).
+Sparse Gaussian processes reduce the computational complexity by representing the GP as a low-rank approximation induced by a sparse set of input points (see \cite{quinonero2005unifying} for an early overview).
 Given that we have computed the dual variables derived from our neural network predictions and a kernel function, we could essentially employ any of these sparsification methods.
@@
 As demonstrated in \cite{adam2021dual}, the posterior under this model bears a structure akin to \cref{eq:gp_pred}.
-The authors of that paper see the significance of the dual variables for approximate inference, but write them using the natural parameterization, primarily because this form is more suitable for optimization through natural gradients.
+The authors of that paper \todo{Even though it's us, should we speculate about how authors see things?
+Maybe nicer to write about how the paper uses the dual} see the significance of the dual variables for approximate inference, but write them using the natural parameterization, primarily because this form is more suitable for optimization through natural gradients.
 In order to link the dual variables defined in \cref{eq:dual_param}, we write them in the sparse GP using the dual variables

### 2023-05-17 paper/main.tex
UCI

--- 2023-05-17 paper/main.tex
@@
   \caption{Comparisons and ablations on UCI data with negative log predictive density (NLPD\textcolor{gray}{\footnotesize$\pm$std}, lower better).
-Our sparse \our ($M=256$) is on par with or better than full models (left) and outperforms the GP subset approach of \cite{immer2021improving} (right).
-Results for methods marked with * are from their original implementation in \cite{immer2021improving}.
+Our sparse \our ($M=256$) is on par with full models (left) and outperforms the GP subset approach of \cite{immer2021improving} (right).
+Results for methods marked with * as reported in teh original benchmark~\cite{immer2021improving}.
 See \cref{app:uci} for additional tables with comparisons.}
 	\label{tbl:uci}
+	\vspace*{-4pt}
+
 	% Control table spacing
@@
   \newcommand{\myline}[1]{\protect\tikz[baseline=-.5ex,line width=1.6pt]\protect\draw[draw=#1](0,0)--(1.2em,0);}
-  \caption{Comparison of convergence in terms of number of inducing data points $M$ in NLPD (mean over 10 seeds) on UCI classification tasks: \our (thick) vs.\ subsets (thin).
-The orange lines (\myline{darkorange25512714}) use the GP mean, whereas the blue lines (\myline{steelblue31119180}) the NN MAP estimate as the mean.
-Our \our's converges fast for all cases.}
+  \caption{Comparison of convergence in terms of number of inducing points $M$ in NLPD (mean over 10 seeds) on UCI classification tasks: \our (thick) vs.\ subsets (\cite{immer2021improving}, thin).
+Orange lines (\myline{darkorange25512714}) use the GP mean, whereas blue lines (\myline{steelblue31119180}) the NN MAP estimate as mean.
+Our \our converges fast for all cases.\looseness-1}
   \label{fig:uci}
@@
 %
-We consider $8$ of the UCI~\cite{UCI} benchmarks, consisting of a range of binary and multi-class classification with varying dataset sizes.
+We consider 8 UCI~\cite{UCI} benchmarks, consisting of a range of binary and multi-class classification tasks with varying data set sizes.
 We first train two-layer MLPs for each of the classification tasks and follow the setup in \cref{sec:methods} for \our.
 That is, after training we construct the \our dual and use the resulting model for uncertainty quantification.
-For comparison, we used the same hyperparameters for neural network training as in the UCI experiments of \cite{immer2021improving}, and similarly performed hyperparameter search over the prior precision $\delta$, and ran the experiment over $10$ random splits.
+For comparison, we used the same hyperparameters for the neural network training as in the UCI experiments of \cite{immer2021improving}, and similarly perform hyperparameter search over the prior precision $\delta$, and run the experiment over $10$ random splits.
  %Depending on task dimension and complexity, our model can match the neural network MAP in negative log-predictive density (NLPD) even with a low number of inducing points (see \cref{tbl:uci} left).
@@
 The comparison shows that our sparse method is able to summarize the information of the full data set more efficiently than sparse subset methods, and can match the performance of the full GP even with a low number of inducing points.
+This is even more apparent from \cref{fig:uci} which shows the benefits of \our in summarizing the full data distribution onto a small set of inducing points over just picking a random subset.
 

### 2023-05-17 paper/main.tex
Commenting Section 4

--- 2023-05-17 paper/main.tex
@@
 %
-We have presented a method for converting any trained neural network into a sparse function-space representation.
+We have presented a method for converting \todo{Is it really for any, no regularity at all required?
+Would remove that word if we're not sure} any trained neural network into a sparse function-space representation.
 The sparse representation opens an avenue for maintaining (and updating) a representation of the neural network, an important feature for sequential learning, such as continual learning.\looseness-1
@@
 In the same way, after each task, we can use \our method to build a compact representation of the neural network and then exploit this representation to construct a functional regularizer to add to the training loss for the subsequent tasks.
-Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art on CL benchmarks.
+Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art \todo{Could add a noun after state-of-the-art} on CL benchmarks.
 However, they are limited to using subset approximations of the posterior.
-Instead, we use the sparse data term posterior see \cref{app:cl} for details.
+Instead, we use the sparse data term posterior, see \cref{app:cl} for details.
 %, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer. 
@@
 
-In practice this means,  at the end of the training for each task $t$, we compute the approximated kernel function for the current model and randomly select $M$ inducing points.
+In practice this means, that at the end of the training for each task $t$, we compute the approximated kernel function for the current model and randomly select $M$ inducing points.
 Given the issues described in the previous sections, related to computing the full covariance posterior $\MKxx$ for $\dataset_t$,\todo{this should be $\kappa(\MX_t, \MX_t)$} we can exploit the dual parameterization to efficiently encode the information from  $\dataset_t$ using the dual parameterization, as follows,

### 2023-05-17 paper/main.tex
Experiments

@@
 %
-We present a series of experiments designed to demonstrate the versatility and efficacy of \our. We seek to find answers to the following questions: 
+We present a series of experiments specifically designed to showcase the robustness and effectiveness of \our. The experiments are aimed at answering the following key questions:
 \textbf{Predictions:}~Does our method's ability to consider the full data set offer benefits over subset function-space methods?
@@
 \textbf{Representation:} Can a sparse function-space representation help retain knowledge from previous tasks in CL? (\cref{sec:cl-exp})
-\textbf{Uncertainty:} Can our uncertainty estimates help exploration in RL? (\cref{sec:rl-exp})
-
-\paragraph{Implementation} We implement all methods in PyTorch~\cite{paszke2019pytorch} and leverange the XXXX libraries.. \todo{add brief details}. Experiments were run on clusters
-
-\paragraph{Toy examples} For illustrative purposes, we smoke-test our approach on a 1D regression problem (\cref{fig:teaser}) and on the 2D Banana classification task (\cref{fig:banana}).
-In \cref{fig:teaser}, we train an MLP neural network with two hidden layers (64 hidden units each, tanh activation).
+\textbf{Uncertainty:} Can our uncertainty estimates help exploration in RL?
+(\cref{sec:rl-exp}) We implement all methods in PyTorch~\cite{paszke2019pytorch} and run the benchmarks using a GPU cluster.
+We provide full experiment details in \cref{app:experiments}.
+
+\paragraph{Toy examples} For illustrative purposes, we show our approach on a 1D regression problem (\cref{fig:teaser}) and on the 2D {\sc Banana} classification task (\cref{fig:banana}).
+In \cref{fig:teaser}, we train an MLP neural network with two hidden layers (64 hidden units each, tanh activation) and pass it through \our.
 The middle panel shows the \our result on a sparse set of data examples, while the rightmost panel demonstrates fast dual conditioning on new data (from \cref{sec:sequential}).
-In \cref{fig:banana}, we use an MLP with two hidden layers (64 units, sigmoid) and compare to the HMC result obtained by hamiltorch \cite{cobb2020scaling} that shows capture similar behaviour as HMC.
+In \cref{fig:banana}, we use an MLP with two hidden layers (64 units, sigmoid) and compare to a HMC sampling result obtained by hamiltorch~\cite{cobb2020scaling}.
+The HMC result is more expressive, but the results are still similar in terms of quantifying the uncertainty in low-data regions.
 

### 2023-05-17 paper/main.tex
added mnist results

--- 2023-05-17 paper/main.tex
@@
 %
-We have presented a method for converting \todo{Is it really for any, no regularity at all required?
-Would remove that word if we're not sure} any trained neural network into a sparse function-space representation.
+We have presented a method for converting any trained neural network into a sparse function-space representation.
 The sparse representation opens an avenue for maintaining (and updating) a representation of the neural network, an important feature for sequential learning, such as continual learning.\looseness-1
@@
 In the same way, after each task, we can use \our method to build a compact representation of the neural network and then exploit this representation to construct a functional regularizer to add to the training loss for the subsequent tasks.
-Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art \todo{Could add a noun after state-of-the-art} on CL benchmarks.
+Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art on CL benchmarks.
 However, they are limited to using subset approximations of the posterior.
-Instead, we use the sparse data term posterior, see \cref{app:cl} for details.
+Instead, we use the sparse data term posterior see \cref{app:cl} for details.
 %, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer. 
@@
 
-In practice this means, that at the end of the training for each task $t$, we compute the approximated kernel function for the current model and randomly select $M$ inducing points.
+In practice this means,  at the end of the training for each task $t$, we compute the approximated kernel function for the current model and randomly select $M$ inducing points.
 Given the issues described in the previous sections, related to computing the full covariance posterior $\MKxx$ for $\dataset_t$,\todo{this should be $\kappa(\MX_t, \MX_t)$} we can exploit the dual parameterization to efficiently encode the information from  $\dataset_t$ using the dual parameterization, as follows,
@@
     % THE TABLE CAN BE FORMATTED MORE LIKE THIS
+    % \begin{tabular}{l l C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
+    % \toprule
+    % & Method & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ & OOD-AUC~$\uparrow$  \\
+    % \midrule
+    % \multirow{2}{*}{FMNIST}
+    % & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    % & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    % & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    % & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    % & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    % & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    % & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    % \midrule
+    % \multirow{2}{*}{CIFAR-10}
+    % & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    % & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    % & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    % & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    % & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    % & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    % & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    % \bottomrule
+    % \end{tabular}
   \begin{tabular}{l l C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
     \toprule
-    & Method & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ & OOD-AUC~$\uparrow$  \\
+    & Method & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$   \\
+    \midrule
+    \multirow{2}{*}{MNIST}
+    & MAP & \val{98.22}{0.13} & \val{0.061}{0.004} & \val{0.006}{0.001} \\
+    & BNN predictive \cite{todo} & \val{93.03}{0.13} & \val{0.369}{0.003} & \val{0.168}{0.001} \\
+    & GLM predictive & \val{98.40}{0.05} & \val{0.054}{0.002} & \val{0.007}{0.001} \\
+    & GP predictive $m=3200$ & \val{98.22}{0.13} & \val{0.058}{0.001} & \val{0.003}{0.000} \\
+    & GP predictive NN $m=1024$ &  \val{97.70}{0.07} & \val{0.080}{0.002} & \val{0.011}{0.001} \\
+    & GP predictive $m=1024$  &  \val{76.28}{1.85} & \val{0.702}{0.029} & \val{0.070}{0.022} \\
+    & \our NN $m=1024$ &  \val{98.02}{0.12} & \val{0.066}{0.003} & \val{0.007}{0.001} \\
+    & \our $m=1024$ &  \val{98.07}{0.06} & \val{0.063}{0.003} & \val{0.005}{0.001} \\
     \midrule
     \multirow{2}{*}{FMNIST}
-    & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\    
-    \midrule
-    \multirow{2}{*}{CIFAR-10} 
-    & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\    
+    & MAP & \val{91.39}{0.11} & \val{0.258}{0.004} & \val{0.017}{0.001} \\
+    & BNN predictive & \val{84.42}{0.12} & \val{0.942}{0.016} & \val{0.411}{0.008} \\
+    & BNN predictive (Ritter et al.) & \val{91.20}{0.07} & \val{0.265}{0.004} & \val{0.024}{0.002} \\
+    & GLM predictive & \val{92.25}{0.10} & \val{0.244}{0.003} & \val{0.012}{0.003} \\
+    & GP predictive $m=3200$ & \val{91.36}{0.11} & \val{0.25}{0.004} & \val{0.007}{0.001} \\
+    & GP predictive NN $m=1024$ &  \val{0}{0.07} & \val{0}{0.002} & \val{0}{0.001} \\
+    & GP predictive $m=1024$  &  \val{0}{1.85} & \val{0}{0.029} & \val{0}{0.022} \\
+    & \our NN $m=1024$ &  \val{0}{0.0} & \val{0}{0.003} & \val{0}{0.001} \\
+    & \our $m=1024$ &  \val{0}{0.06} & \val{0}{0.003} & \val{0}{0.001} \\
     \bottomrule
   \end{tabular}
+
+% & \sc \sc gp predictive  &  \val{76.28333}{1.849} & \val{0.70168}{0.02883} & \val{0.07049}{0.02154} \\
+% & \sc \sc gp predictive NN \cite{immer2021improving} &  \val{97.70333}{0.074} & \val{0.08027}{0.00248} & \val{0.01052}{0.00097} \\
+% & \sc \our &  \val{98.06667}{0.060} & \val{0.06312}{0.00284} & \val{0.00493}{0.00086} \\
+% & \sc \our NN &  \val{98.02000}{0.122} & \val{0.06583}{0.00294} & \val{0.00714}{0.00096} \\
+% M=512
+% & \sc \our &  \val{96.05}{0.00} & \val{0.85}{0.01} & \val{0.50}{0.00} \\
+% & \sc \sc gp predictive  &  \val{14.79}{0.01} & \val{2.30}{0.02} & \val{0.02}{0.01} \\
+% & \sc \sc gp predictive NN \cite{immer2021improving} &  \val{91.49}{0.01} & \val{1.25}{0.01} & \val{0.61}{0.00} \\
+% & \sc \our NN &  \val{96.96}{0.00} & \val{0.63}{0.00} & \val{0.40}{0.00} \\
+
+% M=1024
 

### 2023-05-17 paper/main.tex
added citatios to table

@@
     & MAP & \val{98.22}{0.13} & \val{0.061}{0.004} & \val{0.006}{0.001} \\
-    & BNN predictive \cite{todo} & \val{93.03}{0.13} & \val{0.369}{0.003} & \val{0.168}{0.001} \\
-    & GLM predictive & \val{98.40}{0.05} & \val{0.054}{0.002} & \val{0.007}{0.001} \\
-    & GP predictive $m=3200$ & \val{98.22}{0.13} & \val{0.058}{0.001} & \val{0.003}{0.000} \\
+    & BNN predictive \cite{immer2021improving} & \val{93.14}{0.05} & \val{0.304}{0.002} & \val{0.111}{0.003} \\
+    & BNN predictive \cite{ritter2018kfac} & \val{93.03}{0.13} & \val{0.369}{0.003} & \val{0.168}{0.001} \\
+    & GLM predictive \cite{immer2021improving} & \val{98.40}{0.05} & \val{0.054}{0.002} & \val{0.007}{0.001} \\
+    & GP predictive \cite{immer2021improving} $m=3200$ & \val{98.22}{0.13} & \val{0.058}{0.001} & \val{0.003}{0.000} \\
     & GP predictive NN $m=1024$ &  \val{97.70}{0.07} & \val{0.080}{0.002} & \val{0.011}{0.001} \\
@@
     & MAP & \val{91.39}{0.11} & \val{0.258}{0.004} & \val{0.017}{0.001} \\
-    & BNN predictive & \val{84.42}{0.12} & \val{0.942}{0.016} & \val{0.411}{0.008} \\
-    & BNN predictive (Ritter et al.) & \val{91.20}{0.07} & \val{0.265}{0.004} & \val{0.024}{0.002} \\
-    & GLM predictive & \val{92.25}{0.10} & \val{0.244}{0.003} & \val{0.012}{0.003} \\
-    & GP predictive $m=3200$ & \val{91.36}{0.11} & \val{0.25}{0.004} & \val{0.007}{0.001} \\
+    & BNN predictive \cite{immer2021improving} & \val{84.42}{0.12} & \val{0.942}{0.016} & \val{0.411}{0.008} \\
+    & BNN predictive \cite{ritter2018kfac} & \val{91.20}{0.07} & \val{0.265}{0.004} & \val{0.024}{0.002} \\
+    & GLM predictive \cite{immer2021improving} & \val{92.25}{0.10} & \val{0.244}{0.003} & \val{0.012}{0.003} \\
+    & GP predictive \cite{immer2021improving} $m=3200$ & \val{91.36}{0.11} & \val{0.25}{0.004} & \val{0.007}{0.001} \\
     & GP predictive NN $m=1024$ &  \val{0}{0.07} & \val{0}{0.002} & \val{0}{0.001} \\

### 2023-05-17 paper/main.tex
Experiments

--- 2023-05-17 paper/main.tex
@@
 %
-We consider 8 UCI~\cite{UCI} benchmarks, consisting of a range of binary and multi-class classification tasks with varying data set sizes.
-We first train two-layer MLPs for each of the classification tasks and follow the setup in \cref{sec:methods} for \our.
+We consider eight UCI benchmarks~\cite{UCI}, covering of a variety of binary and multi-class classification tasks with different data set sizes.
+We initially train a two-layer MLP for each of the classification tasks and follow the setup in \cref{sec:methods} for \our.
 That is, after training we construct the \our dual and use the resulting model for uncertainty quantification.
 For comparison, we used the same hyperparameters for the neural network training as in the UCI experiments of \cite{immer2021improving}, and similarly perform hyperparameter search over the prior precision $\delta$, and run the experiment over $10$ random splits.
- %Depending on task dimension and complexity, our model can match the neural network MAP in negative log-predictive density (NLPD) even with a low number of inducing points (see \cref{tbl:uci} left).
 In \cref{tbl:uci} (left), we compare our model to the NN MAP estimate, mean-field VI, a Bayesian NN, and a GLM model (see \cite{immer2021improving} for the baselines) in negative log-predictive density (NLPD).
@@
 
-In \cref{tbl:uci} (right), we also include an ablation and comparison (to \cite{immer2021improving}) study with a fixed low number of inducing points ($M=32$).
+In \cref{tbl:uci} (right), we also include an ablation and comparison study (to \cite{immer2021improving}) with a fixed low number of inducing points ($M=32$).
 The comparison shows that our sparse method is able to summarize the information of the full data set more efficiently than sparse subset methods, and can match the performance of the full GP even with a low number of inducing points.
@@
     % THE TABLE CAN BE FORMATTED MORE LIKE THIS
-    % \begin{tabular}{l l C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
-    % \toprule
-    % & Method & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ & OOD-AUC~$\uparrow$  \\
-    % \midrule
-    % \multirow{2}{*}{FMNIST}
-    % & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % \midrule
-    % \multirow{2}{*}{CIFAR-10}
-    % & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % \bottomrule
-    % \end{tabular}
     \begin{tabular}{l l C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
     \toprule
-    & Method & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$   \\
-    \midrule
-    \multirow{2}{*}{MNIST}
-    & MAP & \val{98.22}{0.13} & \val{0.061}{0.004} & \val{0.006}{0.001} \\
-    & BNN predictive \cite{todo} & \val{93.03}{0.13} & \val{0.369}{0.003} & \val{0.168}{0.001} \\
-    & GLM predictive & \val{98.40}{0.05} & \val{0.054}{0.002} & \val{0.007}{0.001} \\
-    & GP predictive $m=3200$ & \val{98.22}{0.13} & \val{0.058}{0.001} & \val{0.003}{0.000} \\
-    & GP predictive NN $m=1024$ &  \val{97.70}{0.07} & \val{0.080}{0.002} & \val{0.011}{0.001} \\
-    & GP predictive $m=1024$  &  \val{76.28}{1.85} & \val{0.702}{0.029} & \val{0.070}{0.022} \\
-    & \our NN $m=1024$ &  \val{98.02}{0.12} & \val{0.066}{0.003} & \val{0.007}{0.001} \\
-    & \our $m=1024$ &  \val{98.07}{0.06} & \val{0.063}{0.003} & \val{0.005}{0.001} \\
+    & Method & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ & OOD-AUC~$\uparrow$  \\
     \midrule
     \multirow{2}{*}{FMNIST} 
-    & MAP & \val{91.39}{0.11} & \val{0.258}{0.004} & \val{0.017}{0.001} \\
-    & BNN predictive & \val{84.42}{0.12} & \val{0.942}{0.016} & \val{0.411}{0.008} \\
-    & BNN predictive (Ritter et al.) & \val{91.20}{0.07} & \val{0.265}{0.004} & \val{0.024}{0.002} \\
-    & GLM predictive & \val{92.25}{0.10} & \val{0.244}{0.003} & \val{0.012}{0.003} \\
-    & GP predictive $m=3200$ & \val{91.36}{0.11} & \val{0.25}{0.004} & \val{0.007}{0.001} \\
-    & GP predictive NN $m=1024$ &  \val{0}{0.07} & \val{0}{0.002} & \val{0}{0.001} \\
-    & GP predictive $m=1024$  &  \val{0}{1.85} & \val{0}{0.029} & \val{0}{0.022} \\
-    & \our NN $m=1024$ &  \val{0}{0.0} & \val{0}{0.003} & \val{0}{0.001} \\
-    & \our $m=1024$ &  \val{0}{0.06} & \val{0}{0.003} & \val{0}{0.001} \\
+    & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\    
+    \midrule
+    \multirow{2}{*}{CIFAR-10} 
+    & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
+    & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\    
     \bottomrule
     \end{tabular}
-
-% & \sc \sc gp predictive  &  \val{76.28333}{1.849} & \val{0.70168}{0.02883} & \val{0.07049}{0.02154} \\
-% & \sc \sc gp predictive NN \cite{immer2021improving} &  \val{97.70333}{0.074} & \val{0.08027}{0.00248} & \val{0.01052}{0.00097} \\
-% & \sc \our &  \val{98.06667}{0.060} & \val{0.06312}{0.00284} & \val{0.00493}{0.00086} \\
-% & \sc \our NN &  \val{98.02000}{0.122} & \val{0.06583}{0.00294} & \val{0.00714}{0.00096} \\
-% M=512
-% & \sc \our &  \val{96.05}{0.00} & \val{0.85}{0.01} & \val{0.50}{0.00} \\
-% & \sc \sc gp predictive  &  \val{14.79}{0.01} & \val{2.30}{0.02} & \val{0.02}{0.01} \\
-% & \sc \sc gp predictive NN \cite{immer2021improving} &  \val{91.49}{0.01} & \val{1.25}{0.01} & \val{0.61}{0.00} \\
-% & \sc \our NN &  \val{96.96}{0.00} & \val{0.63}{0.00} & \val{0.40}{0.00} \\
-
-% M=1024
 

### 2023-05-17 paper/main.tex
changes in sec. 1

--- 2023-05-17 paper/main.tex
@@
 These questions become central when applied to sequential learning paradigms, such as continual learning (CL, \citep{parisi2019continual, de2021continual}) and reinforcement learning (RL, \cite{sutton2018reinforcement}).
-In CL, access to the previous data is lost and the challenge is retaining a compact representation of the problem and avoiding forgetting over the life-long learning horizon~\cite{mccloskey1989catastrophic}.
+In CL, access to the previous data is lost, and then the challenge is retaining a compact representation of the problem to alleviate forgetting over the life-long learning horizon~\cite{mccloskey1989catastrophic}.
 Similarly, in RL, the model must adapt to environmental observations through exploration, while leveraging prediction uncertainties to assess potential future paths.\looseness-1
@@
 %Current state of affairs 
-Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) show that converting trained neural networks to a Bayesian neural network through the Laplace-GGN \todo{Is Laplace-GGN a well-known acronym?} can provide uncertainty without sacrificing additional resources to training \cite{foong2019between}.
-Furthermore, the resultant weight space posterior can be converted to the function space as shown in \cite{khan2019approximate, immer2021improving}.
-The function space representation allows for a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{foong2019between}.
+Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) apply the Laplace-GGN approximation\todo{Is Laplace-GGN a well-known acronym?} to convert a trained neural networks into a Bayesian neural network, that can provide uncertainty without sacrificing additional resources to training \cite{foong2019between}.
+Furthermore, the resultant weight-space posterior can be converted to the function-space as shown in \cite{khan2019approximate, immer2021improving}.
+The function-space representation allows for a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{foong2019between}.
 These methods rely on the linearization of the neural network and the resultant neural tangent kernel (NTK, \cite{jacot2018neural}).
-The function space neural network is characterized by its first two moment functions, a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}).
-GPs provide a widely-used probabilistic toolkit with principled uncertainty estimates, and they serve as a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} with theoretical guarantees on regret bounds \citep{srinivas2009gaussian}.
+The neural network is characterized in function-space by its first two moment functions, a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}).
+GPs provide a widely-used probabilistic toolkit with principled uncertainty estimates.
+They serve as a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} with theoretical guarantees on regret bounds \citep{srinivas2009gaussian}.
 %Yet many problems lie in high dimensional input space; for example, images are where GPs cannot learn representations.
@@
 %
-We present a series of experiments specifically designed to showcase the robustness and effectiveness of \our. The experiments are aimed at answering the following key questions:
+We present a series of experiments designed to demonstrate the versatility and efficacy of \our. We seek to find answers to the following questions: 
 \textbf{Predictions:}~Does our method's ability to consider the full data set offer benefits over subset function-space methods?
@@
 \textbf{Representation:} Can a sparse function-space representation help retain knowledge from previous tasks in CL? (\cref{sec:cl-exp})
-\textbf{Uncertainty:} Can our uncertainty estimates help exploration in RL?
-(\cref{sec:rl-exp}) We implement all methods in PyTorch~\cite{paszke2019pytorch} and run the benchmarks using a GPU cluster.
-We provide full experiment details in \cref{app:experiments}.
-
-\paragraph{Toy examples} For illustrative purposes, we show our approach on a 1D regression problem (\cref{fig:teaser}) and on the 2D {\sc Banana} classification task (\cref{fig:banana}).
-In \cref{fig:teaser}, we train an MLP neural network with two hidden layers (64 hidden units each, tanh activation) and pass it through \our.
+\textbf{Uncertainty:} Can our uncertainty estimates help exploration in RL? (\cref{sec:rl-exp})
+
+\paragraph{Implementation} We implement all methods in PyTorch~\cite{paszke2019pytorch} and leverange the XXXX libraries.. \todo{add brief details}. Experiments were run on clusters
+
+\paragraph{Toy examples} For illustrative purposes, we smoke-test our approach on a 1D regression problem (\cref{fig:teaser}) and on the 2D Banana classification task (\cref{fig:banana}).
+In \cref{fig:teaser}, we train an MLP neural network with two hidden layers (64 hidden units each, tanh activation).
 The middle panel shows the \our result on a sparse set of data examples, while the rightmost panel demonstrates fast dual conditioning on new data (from \cref{sec:sequential}).
-In \cref{fig:banana}, we use an MLP with two hidden layers (64 units, sigmoid) and compare to a HMC sampling result obtained by hamiltorch~\cite{cobb2020scaling}.
-The HMC result is more expressive, but the results are still similar in terms of quantifying the uncertainty in low-data regions.
+In \cref{fig:banana}, we use an MLP with two hidden layers (64 units, sigmoid) and compare to the HMC result obtained by hamiltorch \cite{cobb2020scaling} that shows capture similar behaviour as HMC.
 
@@
 %
-We consider eight UCI benchmarks~\cite{UCI}, covering of a variety of binary and multi-class classification tasks with different data set sizes.
-We initially train a two-layer MLP for each of the classification tasks and follow the setup in \cref{sec:methods} for \our.
+We consider 8 UCI~\cite{UCI} benchmarks, consisting of a range of binary and multi-class classification tasks with varying data set sizes.
+We first train two-layer MLPs for each of the classification tasks and follow the setup in \cref{sec:methods} for \our.
 That is, after training we construct the \our dual and use the resulting model for uncertainty quantification.
 For comparison, we used the same hyperparameters for the neural network training as in the UCI experiments of \cite{immer2021improving}, and similarly perform hyperparameter search over the prior precision $\delta$, and run the experiment over $10$ random splits.
+ %Depending on task dimension and complexity, our model can match the neural network MAP in negative log-predictive density (NLPD) even with a low number of inducing points (see \cref{tbl:uci} left).
 In \cref{tbl:uci} (left), we compare our model to the NN MAP estimate, mean-field VI, a Bayesian NN, and a GLM model (see \cite{immer2021improving} for the baselines) in negative log-predictive density (NLPD).
@@
 
-In \cref{tbl:uci} (right), we also include an ablation and comparison study (to \cite{immer2021improving}) with a fixed low number of inducing points ($M=32$).
+In \cref{tbl:uci} (right), we also include an ablation and comparison (to \cite{immer2021improving}) study with a fixed low number of inducing points ($M=32$).
 The comparison shows that our sparse method is able to summarize the information of the full data set more efficiently than sparse subset methods, and can match the performance of the full GP even with a low number of inducing points.

### 2023-05-17 paper/main.tex
formatted table 2

--- 2023-05-17 paper/main.tex
@@
     % \end{tabular}
-  \begin{tabular}{l l C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
+  \begin{tabular}{l c C{\tblw} C{\tblw} C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
     \toprule
-    & Method & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$   \\
+     Method & M &  & MNIST &  &  & FMNIST &  \\
+            &   & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ \\
     \midrule
-    \multirow{2}{*}{MNIST}
-    & MAP & \val{98.22}{0.13} & \val{0.061}{0.004} & \val{0.006}{0.001} \\
-    & BNN predictive \cite{immer2021improving} & \val{93.14}{0.05} & \val{0.304}{0.002} & \val{0.111}{0.003} \\
-    & BNN predictive \cite{ritter2018kfac} & \val{93.03}{0.13} & \val{0.369}{0.003} & \val{0.168}{0.001} \\
-    & GLM predictive \cite{immer2021improving} & \val{98.40}{0.05} & \val{0.054}{0.002} & \val{0.007}{0.001} \\
-    & GP predictive \cite{immer2021improving} $m=3200$ & \val{98.22}{0.13} & \val{0.058}{0.001} & \val{0.003}{0.000} \\
-    & GP predictive NN $m=1024$ &  \val{97.70}{0.07} & \val{0.080}{0.002} & \val{0.011}{0.001} \\
-    & GP predictive $m=1024$  &  \val{76.28}{1.85} & \val{0.702}{0.029} & \val{0.070}{0.022} \\
-    & \our NN $m=1024$ &  \val{98.02}{0.12} & \val{0.066}{0.003} & \val{0.007}{0.001} \\
-    & \our $m=1024$ &  \val{98.07}{0.06} & \val{0.063}{0.003} & \val{0.005}{0.001} \\
+    %\multirow{2}{*}{MNIST}
+    MAP & & \val{98.22}{0.13} & \val{0.061}{0.004} & \val{0.006}{0.001}
+          & \val{91.39}{0.11} & \val{0.258}{0.004} & \val{0.017}{0.001} \\
+    BNN predictive \cite{immer2021improving} & & \val{93.14}{0.05} & \val{0.304}{0.002} & \val{0.111}{0.003}
+                                               & \val{84.42}{0.12} & \val{0.942}{0.016} & \val{0.411}{0.008} \\
+    BNN predictive \cite{ritter2018kfac} & & \val{93.03}{0.13} & \val{0.369}{0.003} & \val{0.168}{0.001}
+                                           & \val{91.20}{0.07} & \val{0.265}{0.004} & \val{0.024}{0.002} \\
+    GLM predictive \cite{immer2021improving} & & \val{98.40}{0.05} & \val{0.054}{0.002} & \val{0.007}{0.001}
+                                               & \val{92.25}{0.10} & \val{0.244}{0.003} & \val{0.012}{0.003} \\
+    GP predictive \cite{immer2021improving} & $3200$ & \val{98.22}{0.13} & \val{0.058}{0.001} & \val{0.003}{0.000}
+                                                     & \val{91.36}{0.11} & \val{0.25}{0.004} & \val{0.007}{0.001} \\
+
+    GP predictive NN & $1024$ &  \val{97.70}{0.07} & \val{0.080}{0.002} & \val{0.011}{0.001}
+                              &  \val{0}{0.07} & \val{0}{0.002} & \val{0}{0.001} \\
+
+    GP predictive & $1024$  & \val{76.28}{1.85} & \val{0.702}{0.029} & \val{0.070}{0.022}
+                            & \val{0}{1.85} & \val{0}{0.029} & \val{0}{0.022} \\
+    \our NN & $1024$ &  \val{98.02}{0.12} & \val{0.066}{0.003} & \val{0.007}{0.001}
+                     &  \val{0}{0.0} & \val{0}{0.003} & \val{0}{0.001} \\
+    \our & $1024$ & \val{98.07}{0.06} & \val{0.063}{0.003} & \val{0.005}{0.001}
+                  & \val{0}{0.06} & \val{0}{0.003} & \val{0}{0.001} \\
     \midrule
-    \multirow{2}{*}{FMNIST}
-    & MAP & \val{91.39}{0.11} & \val{0.258}{0.004} & \val{0.017}{0.001} \\
-    & BNN predictive \cite{immer2021improving} & \val{84.42}{0.12} & \val{0.942}{0.016} & \val{0.411}{0.008} \\
-    & BNN predictive \cite{ritter2018kfac} & \val{91.20}{0.07} & \val{0.265}{0.004} & \val{0.024}{0.002} \\
-    & GLM predictive \cite{immer2021improving} & \val{92.25}{0.10} & \val{0.244}{0.003} & \val{0.012}{0.003} \\
-    & GP predictive \cite{immer2021improving} $m=3200$ & \val{91.36}{0.11} & \val{0.25}{0.004} & \val{0.007}{0.001} \\
-    & GP predictive NN $m=1024$ &  \val{0}{0.07} & \val{0}{0.002} & \val{0}{0.001} \\
-    & GP predictive $m=1024$  &  \val{0}{1.85} & \val{0}{0.029} & \val{0}{0.022} \\
-    & \our NN $m=1024$ &  \val{0}{0.0} & \val{0}{0.003} & \val{0}{0.001} \\
-    & \our $m=1024$ &  \val{0}{0.06} & \val{0}{0.003} & \val{0}{0.001} \\
+%    \multirow{2}{*}{FMNIST}
+%    & MAP & \val{91.39}{0.11} & \val{0.258}{0.004} & \val{0.017}{0.001} \\
+    %& BNN predictive \cite{immer2021improving} & \val{84.42}{0.12} & \val{0.942}{0.016} & \val{0.411}{0.008} \\
+    % & BNN predictive \cite{ritter2018kfac} & \val{91.20}{0.07} & \val{0.265}{0.004} & \val{0.024}{0.002} \\
+    % & GLM predictive \cite{immer2021improving} & \val{92.25}{0.10} & \val{0.244}{0.003} & \val{0.012}{0.003} \\
+    %& GP predictive \cite{immer2021improving} $m=3200$ & \val{91.36}{0.11} & \val{0.25}{0.004} & \val{0.007}{0.001} \\
+    % & GP predictive NN $m=1024$ &  \val{0}{0.07} & \val{0}{0.002} & \val{0}{0.001} \\
+    % & GP predictive $m=1024$  &  \val{0}{1.85} & \val{0}{0.029} & \val{0}{0.022} \\
+    % & \our NN $m=1024$ &  \val{0}{0.0} & \val{0}{0.003} & \val{0}{0.001} \\
+    % & \our $m=1024$ &  \val{0}{0.06} & \val{0}{0.003} & \val{0}{0.001} \\
     \bottomrule

### 2023-05-17 paper/main.tex
WIP

--- 2023-05-17 paper/main.tex
@@
 These questions become central when applied to sequential learning paradigms, such as continual learning (CL, \citep{parisi2019continual, de2021continual}) and reinforcement learning (RL, \cite{sutton2018reinforcement}).
-In CL, access to the previous data is lost, and then the challenge is retaining a compact representation of the problem to alleviate forgetting over the life-long learning horizon~\cite{mccloskey1989catastrophic}.
+In CL, access to the previous data is lost and the challenge is retaining a compact representation of the problem and avoiding forgetting over the life-long learning horizon~\cite{mccloskey1989catastrophic}.
 Similarly, in RL, the model must adapt to environmental observations through exploration, while leveraging prediction uncertainties to assess potential future paths.\looseness-1
@@
 %Current state of affairs 
-Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) apply the Laplace-GGN approximation\todo{Is Laplace-GGN a well-known acronym?} to convert a trained neural networks into a Bayesian neural network, that can provide uncertainty without sacrificing additional resources to training \cite{foong2019between}.
-Furthermore, the resultant weight-space posterior can be converted to the function-space as shown in \cite{khan2019approximate, immer2021improving}.
-The function-space representation allows for a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{foong2019between}.
+Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) show that converting trained neural networks to a Bayesian neural network through the Laplace-GGN \todo{Is Laplace-GGN a well-known acronym?} can provide uncertainty without sacrificing additional resources to training \cite{foong2019between}.
+Furthermore, the resultant weight space posterior can be converted to the function space as shown in \cite{khan2019approximate, immer2021improving}.
+The function space representation allows for a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{foong2019between}.
 These methods rely on the linearization of the neural network and the resultant neural tangent kernel (NTK, \cite{jacot2018neural}).
-The neural network is characterized in function-space by its first two moment functions, a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}).
-GPs provide a widely-used probabilistic toolkit with principled uncertainty estimates.
-They serve as a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} with theoretical guarantees on regret bounds \citep{srinivas2009gaussian}.
+The function space neural network is characterized by its first two moment functions, a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}).
+GPs provide a widely-used probabilistic toolkit with principled uncertainty estimates, and they serve as a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} with theoretical guarantees on regret bounds \citep{srinivas2009gaussian}.
 %Yet many problems lie in high dimensional input space; for example, images are where GPs cannot learn representations.
@@
 
-Similarly to the UCI experiments, we trained neural networks (CNN, architecture matches \citet{immer2021improving}) for the FMNIST and CIFAR10 classification tasks.
+Similarly to the UCI experiments, we seek to demonstrate \our on image data.
+We consider MNIST and Fashion-MNIST (FMNIST), and neural networks (CNN, architecture matches \cite{immer2021improving}) for the FMNIST and CIFAR10 classification tasks.
 After training, we computed the duals for NN2SVGP and used the resulting SVGP for uncertainty estimates, see \cref{tbl:imagesuper}.

### 2023-05-17 paper/main.tex
Table

@@
 	\setlength{\tabcolsep}{6pt}
-	\setlength{\tblw}{0.15\textwidth}
+	\setlength{\tblw}{0.095\textwidth}
 
@@
     % \end{tabular}
+  \newcommand{\myline}{\protect\tikz[baseline=-.5ex,line width=1pt]\protect\draw[draw=black!50](0,0)--(7em,0);}
   \begin{tabular}{l c C{\tblw} C{\tblw} C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
     \toprule
-     Method & M &  & MNIST &  &  & FMNIST &  \\
-            &   & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ \\
+            &     &  \multicolumn{3}{c}{\myline~MNIST~\myline} & \multicolumn{3}{c}{\myline~FMNIST~\myline} \\
+     Method & $M$ & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ \\
     \midrule
@@
                   & \val{0}{0.06} & \val{0}{0.003} & \val{0}{0.001} \\
-    \midrule
 %    \multirow{2}{*}{FMNIST}

### 2023-05-17 paper/main.tex
updates introduction

--- 2023-05-17 paper/main.tex
@@
 Given an approximate inference technique, we demonstrate that the neural network emits \todo{is 'emits' a clear enough expression here?}`dual' parameters which are the building blocks of a GP~\cite{csato2002sparse, adam2021dual, chang2020fast} .
-In contrast to previous work that utilizes subsets \todo{What kind of subsets?
+In contrast to previous work that utilizes subsets of training data to avoid the computational complexity of constructing the GP over the full data set\todo{What kind of subsets?
 Probably should specify NTK + GP subset to be clear} \cite{immer2021scalable}, this parameterization allows consolidating contributions from {\em all} training data into a sparse representation, essential for predictive uncertainty.
@@
 Through the dual parameter formulation, we establish a connection between the neural network, full GPs, and a sparse approximation similar to sparse variational GPs~\cite{titsias2009variational}.
-We refer to our method as \our---a sparse GP derived from a trained neural network \todo{I assume FR is for functional representation?
-Could be written here for extra clarity}.
-As \our is in the dual parameters, we can perform dual conditioning recently shown effective in \cite{chang2022fantasizing}, that is, avoid retraining and condition new data into our model (see \cref{fig:teaser}) \todo{Effective compared to what?}.\looseness-2
+We refer to our method as Sparse Function-space Representation (\our)---a sparse GP derived from a trained neural network.
+Moreover, this dual parameterization can be exploited to perform dual conditioning \citep{chang2022fantasizing}, \ie, an effective approach to condition on new incoming data into our model crucially without need of retraning it(see \cref{fig:teaser}).
+%As \our is in the dual parameters, we can perform dual conditioning recently shown effective in \cite{chang2022fantasizing}, that is, avoid retraining and condition new data into our model (see \cref{fig:teaser}) \todo{Effective compared to what?}.
+\looseness-2
+
 %Need uncertainty and adaptive methods
@@
 
-Similarly to the UCI experiments, we seek to demonstrate \our on image data.
-We consider MNIST and Fashion-MNIST (FMNIST), and neural networks (CNN, architecture matches \cite{immer2021improving}) for the FMNIST and CIFAR10 classification tasks.
+Similarly to the UCI experiments, we trained neural networks (CNN, architecture matches \citet{immer2021improving}) for the FMNIST and CIFAR10 classification tasks.
 After training, we computed the duals for NN2SVGP and used the resulting SVGP for uncertainty estimates, see \cref{tbl:imagesuper}.

### 2023-05-17 paper/main.tex
Table
Experiments

@@
   \centering\scriptsize
-  \caption{Metrics for supervised learning with image data.
-SVGP is our method, and the number inside parentheses is the number of inducing points.
-SVGP NN is a modification of our method, where the mean is from the NN directly and the variance is from the GP model.}
+  \caption{Metrics for supervised learning on image data with a CNN.
+We report accuracy, NLPD, and expected calibration error (mean$\pm$std) over 10 seeds.
+Our \our method is able to match the full methods using only a sparse set.
+For the GP predictive sparse subset method and \our we report results both using the NN MAP as mean (NN) and GP  mean.}
 	\label{tbl:imagesuper}
@@
     % \end{tabular}
-  \newcommand{\myline}{\protect\tikz[baseline=-.5ex,line width=1pt]\protect\draw[draw=black!50](0,0)--(7em,0);}
+  \newcommand{\myline}{\protect\tikz[baseline=-.5ex,line width=.7pt]\protect\draw[draw=gray](0,0)--(7em,0);}
   \begin{tabular}{l c C{\tblw} C{\tblw} C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
@@
 
-Similarly to the UCI experiments, we seek to demonstrate \our on image data.
-We consider MNIST and Fashion-MNIST (FMNIST), and neural networks (CNN, architecture matches \cite{immer2021improving}) for the FMNIST and CIFAR10 classification tasks.
-After training, we computed the duals for NN2SVGP and used the resulting SVGP for uncertainty estimates, see \cref{tbl:imagesuper}.
-We performed hyperparameter optimization over the prior precision, and found the optimal value to be [insert].
+Similarly to the UCI experiments, we seek to demonstrate \our on image data that features more complicated data manifolds and model structures.
+We consider the MNIST and Fashion-MNIST (FMNIST) classification tasks, and use a CNN architecture (matching the setup in \cite{immer2021improving}).
+After training, we computed the duals for \our and use the model for prediction (full experiment details in \cref{app:image}).
+In \cref{tbl:imagesuper}, we compare to baselines also used in \cite{immer2021improving}.
+For \our and the GP predictive subset method by \cite{immer2021improving} we fix the number of points $M=1024$.
+For the baseline we additionally include a higher $M$ for comparison.
+We report accuracy (ACC), NLPD, and expected calibration error (ECE).
+The results in \cref{tbl:imagesuper} agree with the conclusions drawn from the UCI experiments showing that \our is able to more efficiently capture the posterior using a sparse set of points.
+These results on image data motivates, the experiments that follow that consider learning beyond the supervised learning setting.
+%We performed hyperparameter optimization over the prior precision, and found the optimal value to be [insert].
 We ran the experiment over $5$ seeds.
@@
 
-In addition to uncertainty estimates, our method can update the posterior when given new data.
+%In addition to uncertainty estimates, our method can update the posterior when given new data.
 We gave the SVGP model 10 \% of the test dataset used for evaluation, and compare the performance of the SVGP model and the retrained NN in [INSERT TABLE].

### 2023-05-17 paper/main.tex
updates in sec. 1.1

--- 2023-05-17 paper/main.tex
@@
 %Current state of affairs 
-Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) apply the Laplace-GGN approximation\todo{Is Laplace-GGN a well-known acronym?} to convert a trained neural networks into a Bayesian neural network, that can provide uncertainty without sacrificing additional resources to training \cite{foong2019between}.
+Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) apply a Laplace-GGN approximation\todo{Is Laplace-GGN a well-known acronym?} to convert trained neural networks into Bayesian neural networks, that can provide uncertainty without sacrificing additional resources to training \cite{foong2019between}.
 Furthermore, the resultant weight-space posterior can be converted to the function-space as shown in \cite{khan2019approximate, immer2021improving}.
@@
 \textbf{Function-space methods}
-Function-space perspectives on uncertainty in neural networks often use a Laplace-GGN approximation \citep{daxberger2021laplace}, linearizing a trained neural network around optimal weights.
-\todo{Could modify the sentence a bit, maybe "The Laplace-GGN approximates the Hessian by using..."}The Hessian can be efficiently approximated using the generalized Gauss--Newton approximation (GGN, \cite{botev2017practical}).
+Function-space perspectives on uncertainty in neural networks often use a Laplace-GGN approximation \citep{daxberger2021laplace}, that linearize a trained neural network around MAP weights and approximates the neural network's Hessian using the generalized Gauss--Newton approximation (GGN, \cite{botev2017practical}).
+%\todo{Could modify the sentence a bit, maybe "The Laplace-GGN approximates the Hessian by using..."}
+%The Hessian can be efficiently approximated using the generalized Gauss--Newton approximation . 
 While efficient, it suffers from cubic scaling in parameter count, necessitating approximations like Kronecker factorisation \cite{martens2015optimizing, ritter2018kfac}.

### 2023-05-17 paper/main.tex
updaetd rows of table

--- 2023-05-17 paper/main.tex
@@
 %Current state of affairs 
-Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) apply a Laplace-GGN approximation\todo{Is Laplace-GGN a well-known acronym?} to convert trained neural networks into Bayesian neural networks, that can provide uncertainty without sacrificing additional resources to training \cite{foong2019between}.
+Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) apply the Laplace-GGN approximation\todo{Is Laplace-GGN a well-known acronym?} to convert a trained neural networks into a Bayesian neural network, that can provide uncertainty without sacrificing additional resources to training \cite{foong2019between}.
 Furthermore, the resultant weight-space posterior can be converted to the function-space as shown in \cite{khan2019approximate, immer2021improving}.
@@
 Given an approximate inference technique, we demonstrate that the neural network emits \todo{is 'emits' a clear enough expression here?}`dual' parameters which are the building blocks of a GP~\cite{csato2002sparse, adam2021dual, chang2020fast} .
-In contrast to previous work that utilizes subsets of training data to avoid the computational complexity of constructing the GP over the full data set\todo{What kind of subsets?
+In contrast to previous work that utilizes subsets \todo{What kind of subsets?
 Probably should specify NTK + GP subset to be clear} \cite{immer2021scalable}, this parameterization allows consolidating contributions from {\em all} training data into a sparse representation, essential for predictive uncertainty.
@@
 Through the dual parameter formulation, we establish a connection between the neural network, full GPs, and a sparse approximation similar to sparse variational GPs~\cite{titsias2009variational}.
-We refer to our method as Sparse Function-space Representation (\our)---a sparse GP derived from a trained neural network.
-Moreover, this dual parameterization can be exploited to perform dual conditioning \citep{chang2022fantasizing}, \ie, an effective approach to condition on new incoming data into our model crucially without need of retraning it(see \cref{fig:teaser}).
-%As \our is in the dual parameters, we can perform dual conditioning recently shown effective in \cite{chang2022fantasizing}, that is, avoid retraining and condition new data into our model (see \cref{fig:teaser}) \todo{Effective compared to what?}.
-\looseness-2
-
+We refer to our method as \our---a sparse GP derived from a trained neural network \todo{I assume FR is for functional representation?
+Could be written here for extra clarity}.
+As \our is in the dual parameters, we can perform dual conditioning recently shown effective in \cite{chang2022fantasizing}, that is, avoid retraining and condition new data into our model (see \cref{fig:teaser}) \todo{Effective compared to what?}.\looseness-2
 %Need uncertainty and adaptive methods
@@
 \textbf{Function-space methods}
-Function-space perspectives on uncertainty in neural networks often use a Laplace-GGN approximation \citep{daxberger2021laplace}, that linearize a trained neural network around MAP weights and approximates the neural network's Hessian using the generalized Gauss--Newton approximation (GGN, \cite{botev2017practical}).
-%\todo{Could modify the sentence a bit, maybe "The Laplace-GGN approximates the Hessian by using..."}
-%The Hessian can be efficiently approximated using the generalized Gauss--Newton approximation . 
+Function-space perspectives on uncertainty in neural networks often use a Laplace-GGN approximation \citep{daxberger2021laplace}, linearizing a trained neural network around optimal weights.
+\todo{Could modify the sentence a bit, maybe "The Laplace-GGN approximates the Hessian by using..."}The Hessian can be efficiently approximated using the generalized Gauss--Newton approximation (GGN, \cite{botev2017practical}).
 While efficient, it suffers from cubic scaling in parameter count, necessitating approximations like Kronecker factorisation \cite{martens2015optimizing, ritter2018kfac}.
@@
 	\setlength{\tabcolsep}{6pt}
-	\setlength{\tblw}{0.095\textwidth}
+	\setlength{\tblw}{0.15\textwidth}
 
@@
     % \end{tabular}
-  \newcommand{\myline}{\protect\tikz[baseline=-.5ex,line width=1pt]\protect\draw[draw=black!50](0,0)--(7em,0);}
   \begin{tabular}{l c C{\tblw} C{\tblw} C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
     \toprule
-            &     &  \multicolumn{3}{c}{\myline~MNIST~\myline} & \multicolumn{3}{c}{\myline~FMNIST~\myline} \\
-     Method & $M$ & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ \\
+     Method & M &  & MNIST &  &  & FMNIST &  \\
+            &   & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ \\
     \midrule
@@
     GP predictive NN & $1024$ & \val{97.70}{0.07} & \val{0.080}{0.002} & \val{0.011}{0.001}
-                              &  \val{0}{0.07} & \val{0}{0.002} & \val{0}{0.001} \\
+                              & \val{91.47}{0.41} & \val{0.289}{0.009} & \val{0.033}{0.003} \\
 
     GP predictive & $1024$  & \val{76.28}{1.85} & \val{0.702}{0.029} & \val{0.070}{0.022}
-                            & \val{0}{1.85} & \val{0}{0.029} & \val{0}{0.022} \\
+                            & \val{83.98}{0.35} & \val{0.503}{0.012} & \val{0.052}{0.006} \\
     \our NN & $1024$ &  \val{98.02}{0.12} & \val{0.066}{0.003} & \val{0.007}{0.001}
-                     &  \val{0}{0.0} & \val{0}{0.003} & \val{0}{0.001} \\
+                     & \val{91.93}{0.45} & \val{0.267}{0.011} & \val{0.028}{0.003} \\
     \our & $1024$ & \val{98.07}{0.06} & \val{0.063}{0.003} & \val{0.005}{0.001}
-                  & \val{0}{0.06} & \val{0}{0.003} & \val{0}{0.001} \\
+                  & \val{91.56}{0.35} & \val{0.253}{0.006} & \val{0.012}{0.001} \\
+    \midrule
 %    \multirow{2}{*}{FMNIST}

### 2023-05-17 paper/main.tex
Conclusions typo fixes

--- 2023-05-17 paper/main.tex
@@
     % \end{tabular}
-  \newcommand{\myline}{\protect\tikz[baseline=-.5ex,line width=1pt]\protect\draw[draw=black!50](0,0)--(7em,0);}
+  \newcommand{\myline}{\protect\tikz[baseline=-.5ex,line width=1pt]\protect\draw[draw=gray](0,0)--(7em,0);}
   \begin{tabular}{l c C{\tblw} C{\tblw} C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
@@
 %
-In this paper, we have introduced \our, a novel approach for representing neural networks in sparse function-space, exploiting the dual parameters for an efficient low-rank approximation that accommodates information from the entire data distribution.
+In this paper, we have introduced \our, a novel approach for representing neural networks in sparse function space, exploiting the dual parameters for an efficient low-rank approximation that accommodates information from the entire data distribution.
 Our method offers a powerful mechanism for capturing predictive uncertainty, updating the model with new data without retraining, and providing a compact representation suitable for continual learning.
 These aspects were demonstrated in a wide range of problems, datasets, and learning contexts.
-We showcased our method's ability to capture uncertainty in UCI and image tasks under supervised learning (\cref{sec:uci}), demonstrated robustness on image data sets (\cref{,sec:image}), established its potential for continual learning (\cref{sec:cl-exp}), and finally, verified its applicability in reinforcement learning scenarios (\cref{sec:rl-exp}).
+We showcased our method's ability to capture uncertainty in UCI classification tasks (\cref{sec:uci}), demonstrated robustness on image data sets (\cref{,sec:image}), established its potential for continual learning (\cref{sec:cl-exp}), and finally, verified its applicability in reinforcement learning scenarios (\cref{sec:rl-exp}).
 
@@
 In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
-It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.
+On the other hand, the NTK may be highly non-stationary and is dependent on the NN architecture, for example, the activation functions.
 

### 2023-05-17 paper/main.tex
intro

@@
 The methods in the first category usually tackle this problem with weight-space regularization, such as EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke17a}), or VCL~\citep{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone.
-However, encoding functional knowledge in the weights does not guarantee good quality of the predictions.
+However, regularizing the weights does not guarantee good quality predictions.
 Function-space regularization techniques~\cite{li2018lwf, benjamin2018measuring, titsias2019functional, buzzega2020dark, pan2020continual, rudner2022continual} address this by relying on training data subsets for each task to compute a regularization term.
@@
 Prior work has taken an expectation over the dynamic model's posterior \cite{deisenroth2011pilco,kamtheDataEfficient2018,chuaDeepReinforcementLearning2018},
-sampled from it (akin to Thompson sampling but referred to as posterior sampling RL)
+sampled from it (akin to Thompson sampling but referred to as posterior sampling in RL)
 \todo{cite thopmson sampling paper dearden et al 1999}

### 2023-05-17 paper/main.tex
Scalar output

--- 2023-05-17 paper/main.tex
@@
 %
-In supervised learning, given a data set $\dataset = \{(\vx_{i} , \vy_{i})\}_{i=1}^{N}$, with input $\vx_i \in \inputDomain$ and output $\vy_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w} : \inputDomain \to \outputDomain$, are usually trained to minimize the (regularized) empirical risk,
+In supervised learning, given a data set $\dataset = \{(\vx_{i} , \vy_{i})\}_{i=1}^{N}$, with input $\vx_i \in \inputDomain$ and output $\vy_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w}: \inputDomain \to \outputDomain$ (yet, to simplify the notation we restrict presentation to scalar output), are usually trained to minimize the (regularized) empirical risk,\looseness-1
 %
@@
 %g_{\weights}(\vx) = 
-\Jac{\weights_*}{\vx} \, \weights$, where $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{C \times P}$ is the Jacobian at the MAP.
+\Jac{\weights_*}{\vx} \, \weights$, where $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{1 \times P}$ is the Jacobian at the MAP.
 Using the Hessian of the approximate model, we arrive at the Laplace-GGN approximate posterior for $q(\vw)$ \todo{This is the first time q(w) is used, should define it}. 
@@
 %
-In this paper, we have introduced \our, a novel approach for representing neural networks in sparse function space, exploiting the dual parameters for an efficient low-rank approximation that accommodates information from the entire data distribution.
+In this paper, we have introduced \our, a novel approach for representing neural networks in sparse function-space, exploiting the dual parameters for an efficient low-rank approximation that accommodates information from the entire data distribution.
 Our method offers a powerful mechanism for capturing predictive uncertainty, updating the model with new data without retraining, and providing a compact representation suitable for continual learning.
 These aspects were demonstrated in a wide range of problems, datasets, and learning contexts.
-We showcased our method's ability to capture uncertainty in UCI classification tasks (\cref{sec:uci}), demonstrated robustness on image data sets (\cref{,sec:image}), established its potential for continual learning (\cref{sec:cl-exp}), and finally, verified its applicability in reinforcement learning scenarios (\cref{sec:rl-exp}).
+We showcased our method's ability to capture uncertainty in UCI and image tasks under supervised learning (\cref{sec:uci}), demonstrated robustness on image data sets (\cref{,sec:image}), established its potential for continual learning (\cref{sec:cl-exp}), and finally, verified its applicability in reinforcement learning scenarios (\cref{sec:rl-exp}).
 
@@
 In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
-On the other hand, the NTK may be highly non-stationary and is dependent on the NN architecture, for example, the activation functions.
+It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.
 

### 2023-05-17 paper/main.tex
updated notation

--- 2023-05-17 paper/main.tex
@@
 %
-In supervised learning, given a data set $\dataset = \{(\vx_{i} , \vy_{i})\}_{i=1}^{N}$, with input $\vx_i \in \inputDomain$ and output $\vy_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w}: \inputDomain \to \outputDomain$ (yet, to simplify the notation we restrict presentation to scalar output), are usually trained to minimize the (regularized) empirical risk,\looseness-1
+In supervised learning, given a data set $\dataset = \{(\vx_{i} , y_{i})\}_{i=1}^{N}$, with input $\vx_i \in \inputDomain$ and output $y_i \in \R$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w} : \inputDomain \to \R$, are usually trained to minimize the (regularized) empirical risk,
 %
@@
   \arg \min_{\weights} \mathcal{L}(\dataset,\weights) =
-  \arg \min_{\weights} \textstyle\sum_{i=1}^{N} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
+  \arg \min_{\weights} \textstyle\sum_{i=1}^{N} \ell(f_\weights(\mathbf{x}_{i}), y_i) + \delta \mathcal{R}(\weights).
 \end{equation}
 %
-If $\ell(f_\weights(\vx_{i}), \vy_i) = -\log(p(\vy \mid f_\weights(\vx_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where the regularization weight takes the role of a prior precision parameter, \ie, $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.
+If $\ell(f_\weights(\vx_{i}), y_i) = -\log(p(y \mid f_\weights(\vx_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where the regularization weight takes the role of a prior precision parameter, \ie, $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.
 %Bayesian inference offers a principled approach to quantifying uncertainty in neural networks.
@@
 %In \cref{fig:banana}, we show a qualitative example of the induced function-space posterior obtained with our method compared to the posterior obtained through HMC sampling on the Banana toy dataset.
-The posterior over the weights ${p(\vw \mid \dataset) \propto p(\vy \mid f_{\weights}(\vx)) \, p(\weights)}$ is generally not available in closed form.
+The posterior over the weights ${p(\vw \mid \dataset) \propto p(y \mid f_{\weights}(\vx)) \, p(\weights)}$ is generally not available in closed form.
 Sampling methods that characterize the posterior with a finite set of samples in weight-space---such as the Hamiltonian Monte Carlo (HMC) baseline used in \cref{fig:banana} (right)---are general-purpose, but computationally heavy and impractical for downstream applications.
@@
 %g_{\weights}(\vx) = 
-\Jac{\weights_*}{\vx} \, \weights$, where $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{1 \times P}$ is the Jacobian at the MAP.
+\Jac{\weights_*}{\vx} \, \weights$, where $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{P}$ is the Jacobian at the MAP.
 Using the Hessian of the approximate model, we arrive at the Laplace-GGN approximate posterior for $q(\vw)$ \todo{This is the first time q(w) is used, should define it}. 

### 2023-05-17 paper/main.tex
Minor

--- 2023-05-17 paper/main.tex
@@
 \Jac{\weights_*}{\vx} \, \weights$, where $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{1 \times P}$ is the Jacobian at the MAP.
+
 Using the Hessian of the approximate model, we arrive at the Laplace-GGN approximate posterior for $q(\vw)$ \todo{This is the first time q(w) is used, should define it}. 

### 2023-05-17 paper/main.tex
updated sentance

--- 2023-05-17 paper/main.tex
@@
 The methods in the first category usually tackle this problem with weight-space regularization, such as EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke17a}), or VCL~\citep{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone.
-However, regularizing the weights does not guarantee good quality predictions.
+However, encoding functional knowledge in the weights does not guarantee good quality of the predictions.
 Function-space regularization techniques~\cite{li2018lwf, benjamin2018measuring, titsias2019functional, buzzega2020dark, pan2020continual, rudner2022continual} address this by relying on training data subsets for each task to compute a regularization term.
@@
 Prior work has taken an expectation over the dynamic model's posterior \cite{deisenroth2011pilco,kamtheDataEfficient2018,chuaDeepReinforcementLearning2018},
-sampled from it (akin to Thompson sampling but referred to as posterior sampling in RL)
+sampled from it (akin to Thompson sampling but referred to as posterior sampling RL)
 \todo{cite thopmson sampling paper dearden et al 1999}
@@
 %
-In supervised learning, given a data set $\dataset = \{(\vx_{i} , \vy_{i})\}_{i=1}^{N}$, with input $\vx_i \in \inputDomain$ and output $\vy_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w}: \inputDomain \to \outputDomain$ (yet, to simplify the notation we restrict presentation to scalar output), are usually trained to minimize the (regularized) empirical risk,\looseness-1
+In supervised learning, given a data set $\dataset = \{(\vx_{i} , \vy_{i})\}_{i=1}^{N}$, with input $\vx_i \in \inputDomain$ and output $\vy_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w} : \inputDomain \to \outputDomain$, are usually trained to minimize the (regularized) empirical risk,
 %
@@
 %g_{\weights}(\vx) = 
-\Jac{\weights_*}{\vx} \, \weights$, where $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{1 \times P}$ is the Jacobian at the MAP.
+\Jac{\weights_*}{\vx} \, \weights$, where $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{C \times P}$ is the Jacobian at the MAP.
 Using the Hessian of the approximate model, we arrive at the Laplace-GGN approximate posterior for $q(\vw)$ \todo{This is the first time q(w) is used, should define it}. 
@@
 For non-Gaussian likelihoods, the results are almost the same as retraining with all the data.
-In practice, given our NN-derived kernel's dependency on the Jacobian of the trained neural network $\Jac{\weights_*}{\vx}$, the Jacobians become outdated as we add more data.
-However, we can still improve predictions by conditioning data without retraining.
+However, it is worth noting that our kernel's dependency on the trained neural network $\Jac{\weights_*}{\vx}$ (via the Jacobian) becomes outdated as we add more data.
+Nevertheless, we can still improve predictions by conditioning on new data without retraining.
 %[SEE EXPERIMENT ???].

### 2023-05-17 paper/main.tex
commetned out because we don't show this

--- 2023-05-17 paper/main.tex
@@
 (\cref{sec:uci}) How do predictions with our sparse function-space approximation compare to weight-space approximations?
-\textbf{Function-space updates:} How fast are our function-space updates relative to retraining from scratch? Do they improve predictive performance? 
+% \textbf{Function-space updates:} How fast are our function-space updates relative to retraining from scratch? Do they improve predictive performance?
 \textbf{Representation:} Can a sparse function-space representation help retain knowledge from previous tasks in CL? (\cref{sec:cl-exp})
@@
 Our \our method is able to match the full methods using only a sparse set.
-For the GP predictive sparse subset method and \our we report results both using the NN MAP as mean (NN) and GP  mean.}
+For the GP predictive sparse subset method and \our we report results both using the NN MAP as mean (NN) and using the GP mean.}
 	\label{tbl:imagesuper}
@@
 
-    GP predictive NN & $1024$ & \val{97.70}{0.07} & \val{0.080}{0.002} & \val{0.011}{0.001}
+    GP predictive (NN) & $1024$ & \val{97.70}{0.07} & \val{0.080}{0.002} & \val{0.011}{0.001}
                               & \val{91.47}{0.41} & \val{0.289}{0.009} & \val{0.033}{0.003} \\
@@
                             & \val{83.98}{0.35} & \val{0.503}{0.012} & \val{0.052}{0.006} \\
-    \our NN & $1024$ &  \val{98.02}{0.12} & \val{0.066}{0.003} & \val{0.007}{0.001}
+    \our (NN) & $1024$ &  \val{98.02}{0.12} & \val{0.066}{0.003} & \val{0.007}{0.001}
                      & \val{91.93}{0.45} & \val{0.267}{0.011} & \val{0.028}{0.003} \\
@@
                   & \val{91.56}{0.35} & \val{0.253}{0.006} & \val{0.012}{0.001} \\
-    \midrule
 %    \multirow{2}{*}{FMNIST}

### 2023-05-17 paper/main.tex
updfatedd
fixed typo

@@
 However, it is worth noting that our kernel's dependency on the trained neural network $\Jac{\weights_*}{\vx}$ (via the Jacobian) becomes outdated as we add more data.
-Nevertheless, we can still improve predictions by conditioning on new data without retraining.
+Nevertheless, we can still improve predictions without retraining by conditioning on new data.
 %[SEE EXPERIMENT ???].
@@
 Our sparse \our ($M=256$) is on par with full models (left) and outperforms the GP subset approach of \cite{immer2021improving} (right).
-Results for methods marked with * as reported in teh original benchmark~\cite{immer2021improving}.
+Results for methods marked with * as reported in the original benchmark~\cite{immer2021improving}.
 See \cref{app:uci} for additional tables with comparisons.}

### 2023-05-17 paper/main.tex
update sec. 1

--- 2023-05-17 paper/main.tex
@@
 %Current state of affairs 
-Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) apply a Laplace-GGN approximation\todo{Is Laplace-GGN a well-known acronym?} to convert trained neural networks into Bayesian neural networks, that can provide uncertainty without sacrificing additional resources to training \cite{foong2019between}.
+Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) apply a Laplace-GGN approximation to convert trained neural networks into Bayesian neural networks, that can provide uncertainty without sacrificing additional resources to training \cite{foong2019between}.
 Furthermore, the resultant weight-space posterior can be converted to the function-space as shown in \cite{khan2019approximate, immer2021improving}.
@@
 Given an approximate inference technique, we demonstrate that the neural network emits \todo{is 'emits' a clear enough expression here?}`dual' parameters which are the building blocks of a GP~\cite{csato2002sparse, adam2021dual, chang2020fast} .
-In contrast to previous work that utilizes subsets of training data to avoid the computational complexity of constructing the GP over the full data set\todo{What kind of subsets?
-Probably should specify NTK + GP subset to be clear} \cite{immer2021scalable}, this parameterization allows consolidating contributions from {\em all} training data into a sparse representation, essential for predictive uncertainty.
+In contrast to previous work that utilizes subsets of training data \cite{immer2021scalable},
+this parameterization allows capturing the contributions from {\em all} data points into a sparse representation, essential for predictive uncertainty.
 Crucially, the resulting GP now predicts in the same space as the original trained neural network \todo{Could make it clearer that the GP predicts in the output space while avoiding the NN parameter space}, a feature not present in previous approaches, while avoiding the notorious cubic complexity of vanilla GPs.
@@
 CL approaches fall into inference-based, rehearsal-based, and model-based methods (see \cite{parisi2019continual, de2021continual} for an overview).
-The methods in the first category usually tackle this problem with weight-space regularization, such as EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke17a}), or VCL~\citep{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone.
+The methods in the first category usually tackle this problem with weight-space regularization methods, such as EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke17a}), or VCL~\citep{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone.
 However, regularizing the weights does not guarantee good quality predictions.
@@
 For non-Gaussian likelihoods, the results are almost the same as retraining with all the data.
-However, it is worth noting that our kernel's dependency on the trained neural network $\Jac{\weights_*}{\vx}$ (via the Jacobian) becomes outdated as we add more data.
-Nevertheless, we can still improve predictions by conditioning on new data without retraining.
+In practice, given our NN-derived kernel's dependency on the Jacobian of the trained neural network $\Jac{\weights_*}{\vx}$, the Jacobians become outdated as we add more data.
+However, we can still improve predictions by conditioning data without retraining.
 %[SEE EXPERIMENT ???].
@@
 (\cref{sec:uci}) How do predictions with our sparse function-space approximation compare to weight-space approximations?
-% \textbf{Function-space updates:} How fast are our function-space updates relative to retraining from scratch? Do they improve predictive performance?
+\textbf{Function-space updates:} How fast are our function-space updates relative to retraining from scratch? Do they improve predictive performance? 
 \textbf{Representation:} Can a sparse function-space representation help retain knowledge from previous tasks in CL? (\cref{sec:cl-exp})

### 2023-05-17 paper/main.tex

@@
 For non-Gaussian likelihoods, the results are almost the same as retraining with all the data.
-In practice, given our NN-derived kernel's dependency on the Jacobian of the trained neural network $\Jac{\weights_*}{\vx}$, the Jacobians become outdated as we add more data.
-However, we can still improve predictions by conditioning data without retraining.
+However, it is worth noting that our kernel's dependency on the trained neural network $\Jac{\weights_*}{\vx}$ (via the Jacobian) becomes outdated as we add more data.
+Nevertheless, we can still improve predictions without retraining by conditioning on new data.
 %[SEE EXPERIMENT ???].

### 2023-05-17 paper/main.tex
small thing

@@
 where the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{N \times N}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $k_{ii} = \kappa(\vx_i, \vx_i)$.
-The dual parameters are the vectors $\valpha, \vbeta \in \R^{N}$, defined as:\looseness-1
+\cref{eq:gp_pred} states that the resultant posterior process, which may not be a GP, first two moments can be parameterized via the dual parameters, which are the vectors $\valpha, \vbeta \in \R^{N}$, defined as:\looseness-1
 %

### 2023-05-17 paper/main.tex
small thing

@@
 %\paragraph{GP in the dual parameters}
-The seminal work by \citet{csato2002sparse} (parameterization Lemma~1) gives a parameterization for the posterior process $f_{\textrm{post}}$ \todo{The f post doesn't match the notation in Background?} that can be found through the Bayesian update using the GP prior and the likelihood function.
+The seminal work by \citet{csato2002sparse} (parameterization Lemma~1) gives a parameterization for the posterior process that can be found through the Bayesian update using the GP prior and the likelihood function.
 This gives a `dual' parameterization, $\valpha$ and $\vbeta$,

### 2023-05-17 paper/main.tex
Fix bib

--- 2023-05-17 paper/main.tex
@@
 %Current state of affairs 
-Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) apply a Laplace-GGN approximation to convert trained neural networks into Bayesian neural networks, that can provide uncertainty without sacrificing additional resources to training \cite{foong2019between}.
+Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) apply a Laplace-GGN approximation\todo{Is Laplace-GGN a well-known acronym?} to convert trained neural networks into Bayesian neural networks, that can provide uncertainty without sacrificing additional resources to training \cite{foong2019between}.
 Furthermore, the resultant weight-space posterior can be converted to the function-space as shown in \cite{khan2019approximate, immer2021improving}.
@@
 Given an approximate inference technique, we demonstrate that the neural network emits \todo{is 'emits' a clear enough expression here?}`dual' parameters which are the building blocks of a GP~\cite{csato2002sparse, adam2021dual, chang2020fast} .
-In contrast to previous work that utilizes subsets of training data \cite{immer2021scalable},
-this parameterization allows capturing the contributions from {\em all} data points into a sparse representation, essential for predictive uncertainty.
+In contrast to previous work that utilizes subsets of training data to avoid the computational complexity of constructing the GP over the full data set\todo{What kind of subsets?
+Probably should specify NTK + GP subset to be clear} \cite{immer2021scalable}, this parameterization allows consolidating contributions from {\em all} training data into a sparse representation, essential for predictive uncertainty.
 Crucially, the resulting GP now predicts in the same space as the original trained neural network \todo{Could make it clearer that the GP predicts in the output space while avoiding the NN parameter space}, a feature not present in previous approaches, while avoiding the notorious cubic complexity of vanilla GPs.
@@
 %The approaches proposed in the CL literature can be categorized into inference-based, rehearsal-based, and model-based methods; we refer the reader to \citep{parisi2019continual, de2021continual} for complete reviews.
-The methods in the first category usually tackle this problem with weight-space regularization, such as EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke17a}), or VCL~\citep{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone.
+The methods in the first category usually tackle this problem with weight-space regularization, such as EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke2017continual}), or VCL~\citep{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone.
 %However, encoding functional knowledge in the weights does not guarantee a good quality of the predictions, thus a better to introduce a function-space regularization \citep{li2018lwf, benjamin2018measuring, titsias2019functional, buzzega2020dark, pan2020continual, rudner2022continual}.
@@
 CL approaches fall into inference-based, rehearsal-based, and model-based methods (see \cite{parisi2019continual, de2021continual} for an overview).
-The methods in the first category usually tackle this problem with weight-space regularization methods, such as EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke17a}), or VCL~\citep{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone.
+The methods in the first category usually tackle this problem with weight-space regularization, such as EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke2017continual}), or VCL~\citep{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone.
 However, regularizing the weights does not guarantee good quality predictions.
@@
 For non-Gaussian likelihoods, the results are almost the same as retraining with all the data.
-However, it is worth noting that our kernel's dependency on the trained neural network $\Jac{\weights_*}{\vx}$ (via the Jacobian) becomes outdated as we add more data.
-Nevertheless, we can still improve predictions without retraining by conditioning on new data.
+In practice, given our NN-derived kernel's dependency on the Jacobian of the trained neural network $\Jac{\weights_*}{\vx}$, the Jacobians become outdated as we add more data.
+However, we can still improve predictions by conditioning data without retraining.
 %[SEE EXPERIMENT ???].
@@
 Our sparse \our ($M=256$) is on par with full models (left) and outperforms the GP subset approach of \cite{immer2021improving} (right).
-Results for methods marked with * as reported in the original benchmark~\cite{immer2021improving}.
+Results for methods marked with * as reported in teh original benchmark~\cite{immer2021improving}.
 See \cref{app:uci} for additional tables with comparisons.}

### 2023-05-17 paper/main.tex
small thing

--- 2023-05-17 paper/main.tex
@@
 However, the GP's cubic $\mathcal{O}(n^3)$ scaling with data points $n$ requires costly approximations, often resorting to using data subsets \cite{immer2021scalable}.
-In the GP community, sparse approximations have mitigated this scaling issue (\eg, \cite{titsias2009variational,hensman2013gaussian}), but combining neural network linearization with sparse methods remains \todo{Maybe unexplored instead of unclear?} unclear without resorting to subset methods \todo{Could add something on subset methods here, for example 'which do not retain information from the full dataset' or something like that}.
+In the GP community, sparse approximations have mitigated this scaling issue (\eg, \cite{titsias2009variational,hensman2013gaussian}), but combining neural network linearization with sparse methods remains \todo{Maybe unexplored instead of unclear?} unclear without resorting to subset methods or separately retraining a GP model \cite{ortega2023variational} \todo{Could add something on subset methods here, for example 'which do not retain information from the full dataset' or something like that}.
 Our work addresses this by utilizing the GP's dual parameters \cite{csato2002sparse}, previously applied to non-conjugate likelihood models \cite{adam2021dual}.

### 2023-05-17 paper/main.tex

--- 2023-05-17 paper/main.tex
@@
 CL approaches fall into inference-based, rehearsal-based, and model-based methods (see \cite{parisi2019continual, de2021continual} for an overview).
-The methods in the first category usually tackle this problem with weight-space regularization methods, such as EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke17a}), or VCL~\citep{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone.
+The methods in the first category usually tackle this problem with weight-space regularization methods, such as EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke2017continual}), or VCL~\citep{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone.
 However, regularizing the weights does not guarantee good quality predictions.

### 2023-05-17 paper/main.tex
update intro

--- 2023-05-17 paper/main.tex
@@
 this parameterization allows capturing the contributions from {\em all} data points into a sparse representation, essential for predictive uncertainty.
-Crucially, the resulting GP now predicts in the same space as the original trained neural network \todo{Could make it clearer that the GP predicts in the output space while avoiding the NN parameter space}, a feature not present in previous approaches, while avoiding the notorious cubic complexity of vanilla GPs.
+Crucially, the resulting GP directly predicts in the same space as the original trained neural network, with the benefit of avoiding the complexity introduced by working in weight-space and the notorious cubic complexity of vanilla GPs.
+%\todo{Could make it clearer that the GP predicts in the output space while avoiding the NN parameter space}
+%, a feature not present in previous approaches, while avoiding the notorious cubic complexity of vanilla GPs. 
 Through the dual parameter formulation, we establish a connection between the neural network, full GPs, and a sparse approximation similar to sparse variational GPs~\cite{titsias2009variational}.
@@
 
-The contributions of this paper are:
+The contributions of this paper are that:
 %
@@
 However, the GP's cubic $\mathcal{O}(n^3)$ scaling with data points $n$ requires costly approximations, often resorting to using data subsets \cite{immer2021scalable}.
-In the GP community, sparse approximations have mitigated this scaling issue (\eg, \cite{titsias2009variational,hensman2013gaussian}), but combining neural network linearization with sparse methods remains \todo{Maybe unexplored instead of unclear?} unclear without resorting to subset methods or separately retraining a GP model \cite{ortega2023variational} \todo{Could add something on subset methods here, for example 'which do not retain information from the full dataset' or something like that}.
+In the GP community, sparse approximations have mitigated this scaling issue (\eg, \cite{titsias2009variational,hensman2013gaussian}), but combining neural network linearization with sparse methods remains \todo{Maybe unexplored instead of unclear?} unclear without resorting to subset methods \todo{Could add something on subset methods here, for example 'which do not retain information from the full dataset' or something like that}.
 Our work addresses this by utilizing the GP's dual parameters \cite{csato2002sparse}, previously applied to non-conjugate likelihood models \cite{adam2021dual}.
@@
 %\paragraph{GP in the dual parameters}
-The seminal work by \citet{csato2002sparse} (parameterization Lemma~1) gives a parameterization for the posterior process that can be found through the Bayesian update using the GP prior and the likelihood function.
+The seminal work by \citet{csato2002sparse} (parameterization Lemma~1) gives a parameterization for the posterior process $f_{\textrm{post}}$ \todo{The f post doesn't match the notation in Background?} that can be found through the Bayesian update using the GP prior and the likelihood function.
 This gives a `dual' parameterization, $\valpha$ and $\vbeta$,
@@
 where the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{N \times N}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $k_{ii} = \kappa(\vx_i, \vx_i)$.
-\cref{eq:gp_pred} states that the resultant posterior process, which may not be a GP, first two moments can be parameterized via the dual parameters, which are the vectors $\valpha, \vbeta \in \R^{N}$, defined as:\looseness-1
+The dual parameters are the vectors $\valpha, \vbeta \in \R^{N}$, defined as:\looseness-1
 %

### 2023-05-17 paper/main.tex
update intro

@@
 We refer to our method as Sparse Function-space Representation (\our)---a sparse GP derived from a trained neural network.
-Moreover, this dual parameterization can be exploited to perform dual conditioning \citep{chang2022fantasizing}, \ie, an effective approach to condition on new incoming data into our model crucially without need of retraning it(see \cref{fig:teaser}).
+Moreover, this dual parameterization can be exploited to perform dual conditioning \citep{chang2022fantasizing}, \ie, an effective approach to condition on new incoming data into our model without need of retraning the model (see \cref{fig:teaser}).
 %As \our is in the dual parameters, we can perform dual conditioning recently shown effective in \cite{chang2022fantasizing}, that is, avoid retraining and condition new data into our model (see \cref{fig:teaser}) \todo{Effective compared to what?}.

### 2023-05-17 paper/main.tex
update intro

@@
 CL approaches fall into inference-based, rehearsal-based, and model-based methods (see \cite{parisi2019continual, de2021continual} for an overview).
-The methods in the first category usually tackle this problem with weight-space regularization methods, such as EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke2017continual}), or VCL~\citep{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone.
+The methods in the first category usually tackle this problem with weight-space regularization, such as EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke2017continual}), or VCL~\citep{nguyen-tuongModel2009}, that induce retention of previously learned information in the weights alone.
 However, regularizing the weights does not guarantee good quality predictions.
 Function-space regularization techniques~\cite{li2018lwf, benjamin2018measuring, titsias2019functional, buzzega2020dark, pan2020continual, rudner2022continual} address this by relying on training data subsets for each task to compute a regularization term.
-These methods bridge the gap between objective and rehearsal-based methods \todo{I'm not familiar with the differences between objective vs rehearsal based methods, and it isn't explained here} since they use a subset of the training data for each task to compute the regularization term.
-Recently proposed methods, \eg, DER~\citep{buzzega2020dark}, FROMP~\citep{pan2020continual}, and S-FSVI~\citep{rudner2022continual} achieve state-of-the-art performance among the objective-based techniques in several CL benchmarks.
-\todo{Are DER, FROMP and FSVI function-space regularization methods?
-I assume so but the text makes it a bit vague.}\looseness-2
+These methods can be seen as a hybrid between objective and rehearsal-based methods, since they also store a subset of training data for each task to construct the regularization term.
+Recent function-based methods, \eg, DER~\citep{buzzega2020dark}, FROMP~\citep{pan2020continual}, and S-FSVI~\citep{rudner2022continual}, achieve state-of-the-art performance among the objective-based techniques in several CL benchmarks.
+\looseness-2
 

### 2023-05-17 paper/main.tex
Discussion

--- 2023-05-17 paper/main.tex
@@
 this parameterization allows capturing the contributions from {\em all} data points into a sparse representation, essential for predictive uncertainty.
-Crucially, the resulting GP directly predicts in the same space as the original trained neural network, with the benefit of avoiding the complexity introduced by working in weight-space and the notorious cubic complexity of vanilla GPs.
-%\todo{Could make it clearer that the GP predicts in the output space while avoiding the NN parameter space}
-%, a feature not present in previous approaches, while avoiding the notorious cubic complexity of vanilla GPs. 
+Crucially, the resulting GP now predicts in the same space as the original trained neural network \todo{Could make it clearer that the GP predicts in the output space while avoiding the NN parameter space}, a feature not present in previous approaches, while avoiding the notorious cubic complexity of vanilla GPs.
 Through the dual parameter formulation, we establish a connection between the neural network, full GPs, and a sparse approximation similar to sparse variational GPs~\cite{titsias2009variational}.
@@
 
-The contributions of this paper are that:
+The contributions of this paper are:
 %
@@
 % Discussion points
-It is worth noting that the NTK linearises the network around the MAP solution $\weights^{*}$,
-so the function-space prior (and thus posterior) is only a locally linear approximation.
-In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
-On the other hand, the NTK may be highly non-stationary and is dependent on the NN architecture, for example, the activation functions.
+In practical terms, our model serves a role similar to a sparse GP.
+However, unlike a conventional GP, it does not provide a straightforward method for specifying or tuning the prior covariance function.
+This limitation can be addressed indirectly: the architecture of the neural network and the choice of activation functions can be used to implicitly specify and tune the prior assumptions, thereby incorporating a broad range of inductive biases into the model.
+It is important to note that the NTK linearizes the network around the MAP solution $\weights^{*}$, resulting in the function-space prior (and consequently the posterior) being only a locally linear approximation of the neural network model.
+
+%In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
+%On the other hand, the NTK may be highly non-stationary and is dependent on the NN architecture, for example, the activation functions.
 
 The broader impact of this work lies in its potential to provide tooling for how neural networks are utilized, offering more efficient and principled ways of handling uncertainty and continual learning.
-This contribution, we believe, has significant implications for future applications of machine learning in dynamic, real-world settings where data is unevenly distributed, uncertain, and continuously evolves.
+This contribution, we believe, has significant implications for future applications of machine learning in dynamic, real-world settings where data is unevenly distributed, uncertain, and continuously evolves.\looseness-1
 

### 2023-05-17 paper/main.tex
Link colours
reworked uci

--- 2023-05-17 paper/main.tex
@@
 %The approaches proposed in the CL literature can be categorized into inference-based, rehearsal-based, and model-based methods; we refer the reader to \citep{parisi2019continual, de2021continual} for complete reviews.
-The methods in the first category usually tackle this problem with weight-space regularization, such as EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke2017continual}), or VCL~\citep{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone.
+The methods in the first category usually tackle this problem with weight-space regularization, such as EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke17a}), or VCL~\citep{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone.
 %However, encoding functional knowledge in the weights does not guarantee a good quality of the predictions, thus a better to introduce a function-space regularization \citep{li2018lwf, benjamin2018measuring, titsias2019functional, buzzega2020dark, pan2020continual, rudner2022continual}.
@@
 CL approaches fall into inference-based, rehearsal-based, and model-based methods (see \cite{parisi2019continual, de2021continual} for an overview).
-The methods in the first category usually tackle this problem with weight-space regularization methods, such as EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke2017continual}), or VCL~\citep{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone.
+The methods in the first category usually tackle this problem with weight-space regularization, such as EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke17a}), or VCL~\citep{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone.
 However, regularizing the weights does not guarantee good quality predictions.
@@
 %
-We consider eight UCI benchmarks~\cite{UCI}, covering of a variety of binary and multi-class classification tasks with different data set sizes.
-We initially train a two-layer MLP for each of the classification tasks and follow the setup in \cref{sec:methods} for \our.
-That is, after training we construct the \our dual and use the resulting model for uncertainty quantification.
-For comparison, we used the same hyperparameters for the neural network training as in the UCI experiments of \cite{immer2021improving}, and similarly perform hyperparameter search over the prior precision $\delta$, and run the experiment over $10$ random splits.
-In \cref{tbl:uci} (left), we compare our model to the NN MAP estimate, mean-field VI, a Bayesian NN, and a GLM model (see \cite{immer2021improving} for the baselines) in negative log-predictive density (NLPD).
-We match the predictive performance despite being sparse (here, $M=256$).
-Results for $M=16,32,64,128,256$ are included in \cref{app:uci} with full experiment details.
-
-In \cref{tbl:uci} (right), we also include an ablation and comparison study (to \cite{immer2021improving}) with a fixed low number of inducing points ($M=32$).
-The comparison shows that our sparse method is able to summarize the information of the full data set more efficiently than sparse subset methods, and can match the performance of the full GP even with a low number of inducing points.
+We first evaluate \our on eight UCI benchmarks~\cite{UCI}, a variety of binary and multi-class classification tasks with different data set sizes.
+We train a two-layer MLP for each of the classification tasks and follow the experiment set up in \cite{immer2021improving}.
+%by using the same hyperparameters, performing a hyperparameter search over the prior precision $\delta$,
+% We follow \cite{immer2021improving} by using the same hyperparameters, performing a hyperparameter search over the prior precision $\delta$,
+% and run the experiment over $10$ random splits.
+% That is, after training we construct the \our dual and use the resulting model for uncertainty quantification.
+% for the neural network training as in the UCI experiments of
+\cref{tbl:uci} (left) shows that \our with $M=256$ either matches or outperforms the predictive performance of the NN MAP, mean-field VI, Bayesian NN, and GLM
+predictions %in terms of negative log-predictive density (NLPD).
+(baselines from \cite{immer2021improving}).
+That is, we match predictive performance despite being sparse.
+
+In \cref{tbl:uci} (right) we compare to the subset GP method from \cite{immer2021improving} whilst using only $M=32$ inducing points.
+It shows that \our is able to summarize the full data set more effectively than the GP subset method as it maintains predictive performance
+whilst using fewer inducing points.
+\cref{fig:uci} further shows that as the number of inducing points is lowered $M=512\rigtharrow 16$, \our is able to maintain a much better NLPD than the GP subset.
+These results demonstrate \our's sparse representation captures information from the entire data set and as a result provides good uncertainty estimates.
+We provide full details of our experiments and further results using $M=16,32,64,128,256$ in \cref{app:uci}.
+% benefits of \our in summarizing the full data distribution onto a small set of inducing
+% points over just picking a random subset.
+
+% We match the predictive performance despite being sparse (here, $M=256$).
+
+% This is
+% However, our method used
+
+% despite being sparse (here, $M=256$).
+
+% (left), we compare our model to the NN MAP estimate, mean-field VI, a Bayesian NN, and a GLM model (see \cite{immer2021improving} for the baselines) in negative log-predictive density (NLPD).
+% In \cref{tbl:uci} (left), we compare our model to the NN MAP estimate, mean-field VI, a Bayesian NN, and a GLM model (see \cite{immer2021improving} for the baselines) in negative log-predictive density (NLPD).
+% We match the predictive performance despite being sparse (here, $M=256$).
+% Results for $M=16,32,64,128,256$ are included in \cref{app:uci} with full experiment details.
+
+% \cref{tbl:uci} (right) shows that \our is able to summarize the information of the full data set more efficiently than the sparse GP subset method.
+% As a result, it maintains predictive performance whilst using fewer inducing points.
+% This is even more apparent from \cref{fig:uci} which shows the benefits of \our in summarizing the full data distribution onto a small set of inducing points over just picking a random subset.
+
+% In \cref{tbl:uci} (right), we also include an ablation and comparison study (to \cite{immer2021improving}) with a fixed low number of inducing points ($M=32$).
+% The comparison shows that our sparse method is able to summarize the information of the full data set more efficiently than sparse subset methods, and can match the performance of the full GP even with a low number of inducing points.
 This is even more apparent from \cref{fig:uci} which shows the benefits of \our in summarizing the full data distribution onto a small set of inducing points over just picking a random subset.
@@
 % Discussion points
-In practical terms, our model serves a role similar to a sparse GP.
-However, unlike a conventional GP, it does not provide a straightforward method for specifying or tuning the prior covariance function.
-This limitation can be addressed indirectly: the architecture of the neural network and the choice of activation functions can be used to implicitly specify and tune the prior assumptions, thereby incorporating a broad range of inductive biases into the model.
-It is important to note that the NTK linearizes the network around the MAP solution $\weights^{*}$, resulting in the function-space prior (and consequently the posterior) being only a locally linear approximation of the neural network model.
-
-%In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
-%On the other hand, the NTK may be highly non-stationary and is dependent on the NN architecture, for example, the activation functions.
+It is worth noting that the NTK linearises the network around the MAP solution $\weights^{*}$,
+so the function-space prior (and thus posterior) is only a locally linear approximation.
+In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
+On the other hand, the NTK may be highly non-stationary and is dependent on the NN architecture, for example, the activation functions.
 
 The broader impact of this work lies in its potential to provide tooling for how neural networks are utilized, offering more efficient and principled ways of handling uncertainty and continual learning.
-This contribution, we believe, has significant implications for future applications of machine learning in dynamic, real-world settings where data is unevenly distributed, uncertain, and continuously evolves.\looseness-1
+This contribution, we believe, has significant implications for future applications of machine learning in dynamic, real-world settings where data is unevenly distributed, uncertain, and continuously evolves.
 

### 2023-05-17 paper/main.tex
fixed uci appendix table label

--- 2023-05-17 paper/main.tex
@@
 \usepackage{todonotes}
-\usepackage[colorlinks=true,linkcolor=blue,allcolors=blue]{hyperref}
+\usepackage[colorlinks=true,linkcolor=black,allcolors=black,urlcolor=black,citecolor=black]{hyperref}
 \usepackage{amsmath}
@@
 }
-	\label{tbl:uci}
+	\label{tbl:uci-appendix}
 	% Control table spacing

### 2023-05-17 paper/main.tex
update sec. 2

--- 2023-05-17 paper/main.tex
@@
 
-\textbf{Function space} \todo{Could be titled some other way, like Function-space representation}
+\textbf{Neural Network Function-space} %\todo{Could be titled some other way, like Function-space representation}
 %As a neural network is a deterministic mapping, the weight-space posterior induces a distribution over the function values.
@@
 %As such, it is the distribution over function values that we are actually interested in.
-While neural networks are deterministic mappings defined by their weights, the ultimate goal of training a neural network is to optimize the function it represents, not the weights themselves.
+Neural networks are deterministic parametric functions, but even if the training is typically an optimization in the weight-space, in most applications, we are interested in the parametrized function and not in the weights themselves.
+%While neural networks are deterministic mappings defined by their weights, the ultimate goal of training a neural network is to optimize the function it represents, not the weights themselves. 
 Consequently, the weight-space posterior corresponds to a distribution over function values. 
-Imagine sampling from the weight posterior; the resulting functions could be viewed as perturbations of the function at the MAP estimate $f_{\vw^*}$.
-This perspective aligns better with the main objective in most applications: making representative predictions given the observations we have.
+Intuitively, if one was to sample from the weight posterior, the corresponding functions created can be viewed as perturbed versions of the function at the MAP estimate $f_{\vw^*}$.
+This perspective aligns better with the main objective of making representative predictions given the observations.
 

### 2023-05-17 paper/main.tex
typo

--- 2023-05-17 paper/main.tex
@@
 whilst using fewer inducing points.
-\cref{fig:uci} further shows that as the number of inducing points is lowered $M=512\rigtharrow 16$, \our is able to maintain a much better NLPD than the GP subset.
+\cref{fig:uci} further shows that as the number of inducing points is lowered $M=512,\ldots, 16$, \our is able to maintain a much better NLPD than the GP subset.
 These results demonstrate \our's sparse representation captures information from the entire data set and as a result provides good uncertainty estimates.

### 2023-05-17 paper/main.tex
fixed soem todos

@@
 In the same way, after each task, we can use \our method to build a compact representation of the neural network and then exploit this representation to construct a functional regularizer to add to the training loss for the subsequent tasks.
-Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art \todo{Could add a noun after state-of-the-art} on CL benchmarks.
+Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art results \todo{Could add a noun after state-of-the-art} on CL benchmarks.
 However, they are limited to using subset approximations of the posterior.
@@
 whilst using fewer inducing points.
-\cref{fig:uci} further shows that as the number of inducing points is lowered $M=512,\ldots, 16$, \our is able to maintain a much better NLPD than the GP subset.
+\cref{fig:uci} further shows that as the number of inducing points is lowered $M=512 \rightarrow 16$, \our is able to maintain a much better NLPD than the GP subset.
 These results demonstrate \our's sparse representation captures information from the entire data set and as a result provides good uncertainty estimates.
@@
 We aim to highlight our sparse representation's ability to retain previous knowledge for continual learning (CL) (as in \cref{sec:sequential}).
-We consider the single-head (SH) setting that is harder and more realistic than multi-head (MH)~\citep{van2019three}.	 \todo{can't find the bibtex for their NIPS workshop paper} % typically hard and more competitive \cite{}
-%
+We consider the single-head (SH) setting that is harder and more realistic than multi-head (MH)~\citep{van2019three}.
 % Benchmarks/architectures

### 2023-05-17 paper/main.tex

@@
 whilst using fewer inducing points.
-\cref{fig:uci} further shows that as the number of inducing points is lowered $M=512 \rightarrow 16$, \our is able to maintain a much better NLPD than the GP subset.
+\cref{fig:uci} further shows that as the number of inducing points is lowered $M=512,\ldots, 16$, \our is able to maintain a much better NLPD than the GP subset.
 These results demonstrate \our's sparse representation captures information from the entire data set and as a result provides good uncertainty estimates.

### 2023-05-17 paper/main.tex
updated image reseutls

--- 2023-05-17 paper/main.tex
@@
 Similarly to the UCI experiments, we seek to demonstrate \our on image data that features more complicated data manifolds and model structures.
-We consider the MNIST and Fashion-MNIST (FMNIST) classification tasks, and use a CNN architecture (matching the setup in \cite{immer2021improving}).
+We consider the MNIST and Fashion-MNIST (FMNIST) classification tasks, and use an MLP and a CNN architecture respectively (matching the setup in \cite{immer2021improving}).
 After training, we computed the duals for \our and use the model for prediction (full experiment details in \cref{app:image}).
@@
 For \our and the GP predictive subset method by \cite{immer2021improving} we fix the number of points $M=1024$.
-For the baseline we additionally include a higher $M$ for comparison.
+For completeness, we include the GP predictive result from \cite{immer2021improving} which used more inducing points $M=3200$.
 We report accuracy (ACC), NLPD, and expected calibration error (ECE).
 The results in \cref{tbl:imagesuper} agree with the conclusions drawn from the UCI experiments showing that \our is able to more efficiently capture the posterior using a sparse set of points.
-These results on image data motivates, the experiments that follow that consider learning beyond the supervised learning setting.
+These results on image data sets motivate experiments beyond the supervised learning setting, which we now detail.
 %We performed hyperparameter optimization over the prior precision, and found the optimal value to be [insert].

### 2023-05-17 paper/main.tex
Minor

--- 2023-05-17 paper/main.tex
@@
 In the same way, after each task, we can use \our method to build a compact representation of the neural network and then exploit this representation to construct a functional regularizer to add to the training loss for the subsequent tasks.
-Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art results \todo{Could add a noun after state-of-the-art} on CL benchmarks.
+Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art \todo{Could add a noun after state-of-the-art} on CL benchmarks.
 However, they are limited to using subset approximations of the posterior.
@@
 We aim to highlight our sparse representation's ability to retain previous knowledge for continual learning (CL) (as in \cref{sec:sequential}).
-We consider the single-head (SH) setting that is harder and more realistic than multi-head (MH)~\citep{van2019three}.
+We consider the single-head (SH) setting that is harder and more realistic than multi-head (MH)~\citep{van2019three}.	 \todo{can't find the bibtex for their NIPS workshop paper} % typically hard and more competitive \cite{}
+%
 % Benchmarks/architectures
@@
 This limitation can be addressed indirectly: the architecture of the neural network and the choice of activation functions can be used to implicitly specify and tune the prior assumptions, thereby incorporating a broad range of inductive biases into the model.
-It is important to note that the NTK linearizes the network around the MAP solution $\weights^{*}$, resulting in the function-space prior (and consequently the posterior) being only a locally linear approximation of the neural network model.
+It is important to note that the Laplace-GGN approach linearizes the network around the MAP solution $\weights^{*}$, resulting in the function-space prior (and consequently the posterior) being only a locally linear approximation of the neural network model.\looseness-1
 

### 2023-05-17 paper/main.tex
Tweak fig
fixed some todos

--- 2023-05-17 paper/main.tex
@@
 Originally \citet{csato2002sparse} iteratively find dual variables using an expectation propagation (EP, \cite{minka2001expectation}) method.
-More recently \cite{khan2017conjugate,adam2021dual}, has \todo{Should it be have or has?}shown this relationship for variational Gaussian processes where the above expectation is with respect to the approximate variational posterior.
-Meanwhile in \citet{wilkinson2023bayes}, they show links between linearization methods and how they solve the \todo{Could make passive / active voice more consistent in this paragraph} \cref{eq:dual_param}.
+More recently, \cite{khan2017conjugate,adam2021dual} have shown this relationship for variational Gaussian processes where the above expectation is with respect to the approximate variational posterior.
+Meanwhile in \citet{wilkinson2023bayes}, they show links between linearization methods and how they solve the \cref{eq:dual_param}.
 
@@
 As demonstrated in \cite{adam2021dual}, the posterior under this model bears a structure akin to \cref{eq:gp_pred}.
-The authors of that paper \todo{Even though it's us, should we speculate about how authors see things?
-Maybe nicer to write about how the paper uses the dual} see the significance of the dual variables for approximate inference, but write them using the natural parameterization, primarily because this form is more suitable for optimization through natural gradients.
+The authors of that paper exploit the dual variables for approximate inference, but write them using the natural parameterization, primarily because this form is more suitable for optimization through natural gradients.
 In order to link the dual variables defined in \cref{eq:dual_param}, we write them in the sparse GP using the dual variables
@@
 %
-We have presented a method for converting \todo{Is it really for any, no regularity at all required?
-Would remove that word if we're not sure} any trained neural network into a sparse function-space representation.
+We have presented a method for converting trained neural networks into a sparse function-space representations.
 The sparse representation opens an avenue for maintaining (and updating) a representation of the neural network, an important feature for sequential learning, such as continual learning.\looseness-1
@@
 In the same way, after each task, we can use \our method to build a compact representation of the neural network and then exploit this representation to construct a functional regularizer to add to the training loss for the subsequent tasks.
-Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art results \todo{Could add a noun after state-of-the-art} on CL benchmarks.
+Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art results on CL benchmarks.
 However, they are limited to using subset approximations of the posterior.
@@
 In practice this means, that at the end of the training for each task $t$, we compute the approximated kernel function for the current model and randomly select $M$ inducing points.
-Given the issues described in the previous sections, related to computing the full covariance posterior $\MKxx$ for $\dataset_t$,\todo{this should be $\kappa(\MX_t, \MX_t)$} we can exploit the dual parameterization to efficiently encode the information from  $\dataset_t$ using the dual parameterization, as follows,
+Given the issues described in the previous sections, related to computing the full covariance posterior $\MKxx$ for $\dataset_t$, we can exploit the dual parameterization to efficiently encode the information from  $\dataset_t$ using the dual parameterization, as follows,
 %
@@
 This limitation can be addressed indirectly: the architecture of the neural network and the choice of activation functions can be used to implicitly specify and tune the prior assumptions, thereby incorporating a broad range of inductive biases into the model.
-It is important to note that the Laplace-GGN approach linearizes the network around the MAP solution $\weights^{*}$, resulting in the function-space prior (and consequently the posterior) being only a locally linear approximation of the neural network model.\looseness-1
+It is important to note that the NTK linearizes the network around the MAP solution $\weights^{*}$, resulting in the function-space prior (and consequently the posterior) being only a locally linear approximation of the neural network model.
 

### 2023-05-17 paper/main.tex

@@
    \setlength{\figureheight}{.55\figurewidth}
-   \pgfplotsset{axis on top,ymajorgrids,axis line style={draw=none},legend style={at={(-.1,-.1)},anchor=north east}}
+   \pgfplotsset{axis on top,ymajorgrids,axis line style={draw=none},legend style={at={(-.1,-.1)},anchor=south east}}
    \pgfplotsset{grid style={line width=.1pt, draw=gray!10,densely dotted}}
@@
    \input{./fig/rl.tex}
- \end{subfigure}\\[-1em]
+ \end{subfigure}\\[-1.5em]
  \caption{\textbf{Cartpole swingup with sparse reward.} Training curves showing that \our's uncertainty estimates improve sample efficiency in RL.

### 2023-05-17 paper/main.tex
typoe

--- 2023-05-17 paper/main.tex
@@
 Our method offers a powerful mechanism for capturing predictive uncertainty, updating the model with new data without retraining, and providing a compact representation suitable for continual learning.
-These aspects were demonstrated in a wide range of problems, datasets, and learning contexts.
+These aspects were demonstrated in a wide range of problems, data sets, and learning contexts.
 We showcased our method's ability to capture uncertainty in UCI classification tasks (\cref{sec:uci}), demonstrated robustness on image data sets (\cref{,sec:image}), established its potential for continual learning (\cref{sec:cl-exp}), and finally, verified its applicability in reinforcement learning scenarios (\cref{sec:rl-exp}).

### 2023-05-17 paper/main.tex
typo

@@
 (opposed to the Class-Incremental Learning for S-MNIST and S-FMNIST)
-Considering only function-space methods, we can see that \our achieves the best results on most datasets, and is particularly effective, when using fewer points per task.
+Considering only function-space methods, we can see that \our achieves the best results on most data sets, and is particularly effective, when using fewer points per task.
 On S-FMNIST, our method obtains close results to DER, which regularizes the model by taking the mean squared error between current and old function outputs without accounting the covariance structure of the loss similar to our L2 ablation.
@@
 \todo{on PMNIST our method is not really super-fast, so that could be not the best thing to say here} % we could also say that P-MNIST is known to be a bad/ill-posed dataset for CL
-Finally, it is worth noticing as our ablation already provides a very solid baseline consistently over all datasets.
+Finally, it is worth noticing as our ablation already provides a very solid baseline consistently over all data sets.
 

### 2023-05-17 paper/main.tex
updated iimage results

@@
 In \cref{tbl:imagesuper}, we compare to baselines also used in \cite{immer2021improving}.
-For \our and the GP predictive subset method by \cite{immer2021improving} we fix the number of points $M=1024$.
-For completeness, we include the GP predictive result from \cite{immer2021improving} which used more inducing points $M=3200$.
 We report accuracy (ACC), NLPD, and expected calibration error (ECE).
+For \our and the GP predictive subset method by \cite{immer2021improving}, we provide results when predicting with GP mean and when using the neural network (NN) and
+fix the number of inducing points $M=1024$.
+For completeness, we also include the GP predictive result from \cite{immer2021improving} which used more inducing points $M=3200$.
 The results in \cref{tbl:imagesuper} agree with the conclusions drawn from the UCI experiments showing that \our is able to more efficiently capture the posterior using a sparse set of points.
+They further demonstrate that \our's predictive mean (GP) significantly outperforms the GP predictive subset.
+This is an interesting result as we cannot rely on the NN's prediction if we wish to condition on new data, using the dual conditioning from \label{sec:sequential}.
+In this setting, we must rely on our GP's predictive mean.
+% Other approaches, \cite{immer2021improving} never inten
+% The resutls demonstrate that \our's predictive GP mean significantly outperforms the
 These results on image data sets motivate experiments beyond the supervised learning setting, which we now detail.
+
+% For \our and the GP predictive subset method by \cite{immer2021improving} we fix the number of points $M=1024$.
+
 %We performed hyperparameter optimization over the prior precision, and found the optimal value to be [insert].

### 2023-05-17 paper/main.tex
added dashes in table SL

@@
     %\multirow{2}{*}{MNIST}
-    MAP & & \val{98.22}{0.13} & \val{0.061}{0.004} & \val{0.006}{0.001}
+    MAP & -- & \val{98.22}{0.13} & \val{0.061}{0.004} & \val{0.006}{0.001}
           & \val{91.39}{0.11} & \val{0.258}{0.004} & \val{0.017}{0.001} \\
-    BNN predictive \cite{immer2021improving} & & \val{93.14}{0.05} & \val{0.304}{0.002} & \val{0.111}{0.003}
+    BNN predictive \cite{immer2021improving} & -- & \val{93.14}{0.05} & \val{0.304}{0.002} & \val{0.111}{0.003}
                                                & \val{84.42}{0.12} & \val{0.942}{0.016} & \val{0.411}{0.008} \\
-    BNN predictive \cite{ritter2018kfac} & & \val{93.03}{0.13} & \val{0.369}{0.003} & \val{0.168}{0.001}
+    BNN predictive \cite{ritter2018kfac} & -- & \val{93.03}{0.13} & \val{0.369}{0.003} & \val{0.168}{0.001}
                                            & \val{91.20}{0.07} & \val{0.265}{0.004} & \val{0.024}{0.002} \\
-    GLM predictive \cite{immer2021improving} & & \val{98.40}{0.05} & \val{0.054}{0.002} & \val{0.007}{0.001}
+    GLM predictive \cite{immer2021improving} & -- & \val{98.40}{0.05} & \val{0.054}{0.002} & \val{0.007}{0.001}
                                                & \val{92.25}{0.10} & \val{0.244}{0.003} & \val{0.012}{0.003} \\

### 2023-05-17 paper/main.tex
updated rl
tyos

--- 2023-05-17 paper/main.tex
@@
 \textbf{Function-space methods}
-Function-space perspectives on uncertainty in neural networks often use a Laplace-GGN approximation \citep{daxberger2021laplace}, that linearize a trained neural network around MAP weights and approximates the neural network's Hessian using the generalized Gauss--Newton approximation (GGN, \cite{botev2017practical}).
+Function-space perspectives on uncertainty in neural networks often use a Laplace-GGN approximation \citep{daxberger2021laplace}, which linearizes a trained neural network around MAP weights and approximates the neural network's Hessian using the generalized Gauss--Newton approximation (GGN, \cite{botev2017practical}).
 %\todo{Could modify the sentence a bit, maybe "The Laplace-GGN approximates the Hessian by using..."}
@@
 While efficient, it suffers from cubic scaling in parameter count, necessitating approximations like Kronecker factorisation \cite{martens2015optimizing, ritter2018kfac}.
-\todo{Reads a bit repetitive to start two sentences in a row by This, could maybe be combined in one.} This linear model (linear in the weights) refines predictions and provides uncertainty estimates \citep{immer2021scalable}.
-This model has a convenient interpretation as a GP \cite{immer2021scalable, khan2019approximate, maddox2021fast}.
-%
-However, the GP's cubic $\mathcal{O}(n^3)$ scaling with data points $n$ requires costly approximations, often resorting to using data subsets \cite{immer2021scalable}.
-In the GP community, sparse approximations have mitigated this scaling issue (\eg, \cite{titsias2009variational,hensman2013gaussian}), but combining neural network linearization with sparse methods remains \todo{Maybe unexplored instead of unclear?} unclear without resorting to subset methods or separately retraining a GP model \cite{ortega2023variational} \todo{Could add something on subset methods here, for example 'which do not retain information from the full dataset' or something like that}.
+This linear model (linear in the weights) refines predictions and provides uncertainty estimates \citep{immer2021scalable}.
+It has a convenient interpretation as a GP \cite{immer2021scalable, khan2019approximate, maddox2021fast}.
+%
+However, the GP's cubic $\mathcal{O}(N^3)$ scaling with data points $N$ requires costly approximations, often resorting to using data subsets \cite{immer2021scalable}.
+In the GP community, sparse approximations have mitigated this scaling issue (\eg, \cite{titsias2009variational,hensman2013gaussian}), but combining neural network linearization with sparse methods remains unclear without resorting to subset methods or separately retraining a GP model \cite{ortega2023variational}.
 Our work addresses this by utilizing the GP's dual parameters \cite{csato2002sparse}, previously applied to non-conjugate likelihood models \cite{adam2021dual}.
 
+% \todo{Could add something on subset methods here, for example 'which do not retain information from the full dataset' or something like that}.
 %wang2019exact
@@
 and variational inference \cite{galImproving2016,houthooftVIME2017}. \todo{Could specify here how the previous methods have used these models}
+However, each method has its pros and cons.
+In this paper we present a method which combines some of the pros from NNs with the benefits of GPs.
+
 %However, there has been little leveraging

### 2023-05-17 paper/main.tex
removed todo

@@
 %Need for adaptive learning methods + failures with current methods
-Given an approximate inference technique, we demonstrate that the neural network emits \todo{is 'emits' a clear enough expression here?}`dual' parameters which are the building blocks of a GP~\cite{csato2002sparse, adam2021dual, chang2020fast} .
+Given an approximate inference technique, we demonstrate that the neural network emits `dual' parameters which are the building blocks of a GP~\cite{csato2002sparse, adam2021dual, chang2020fast} .
 In contrast to previous work that utilizes subsets of training data \cite{immer2021scalable},

### 2023-05-17 paper/main.tex
small change

@@
 %Need for adaptive learning methods + failures with current methods
-Given an approximate inference technique, we demonstrate that the neural network emits `dual' parameters which are the building blocks of a GP~\cite{csato2002sparse, adam2021dual, chang2020fast} .
+Given an approximate inference technique, we demonstrate that the neural network emits \todo{is 'emits' a clear enough expression here?}`dual' parameters which are the building blocks of a GP~\cite{csato2002sparse, adam2021dual, chang2020fast} .
 In contrast to previous work that utilizes subsets of training data \cite{immer2021scalable},
@@
 \textbf{Function-space methods}
-Function-space perspectives on uncertainty in neural networks often use a Laplace-GGN approximation \citep{daxberger2021laplace}, which linearizes a trained neural network around MAP weights and approximates the neural network's Hessian using the generalized Gauss--Newton approximation (GGN, \cite{botev2017practical}).
+Function-space perspectives on uncertainty in neural networks often use a Laplace-GGN approximation \citep{daxberger2021laplace}, that linearize a trained neural network around MAP weights and approximates the neural network's Hessian using the generalized Gauss--Newton approximation (GGN, \cite{botev2017practical}).
 %\todo{Could modify the sentence a bit, maybe "The Laplace-GGN approximates the Hessian by using..."}
@@
 While efficient, it suffers from cubic scaling in parameter count, necessitating approximations like Kronecker factorisation \cite{martens2015optimizing, ritter2018kfac}.
-This linear model (linear in the weights) refines predictions and provides uncertainty estimates \citep{immer2021scalable}.
-It has a convenient interpretation as a GP \cite{immer2021scalable, khan2019approximate, maddox2021fast}.
-%
-However, the GP's cubic $\mathcal{O}(N^3)$ scaling with data points $N$ requires costly approximations, often resorting to using data subsets \cite{immer2021scalable}.
-In the GP community, sparse approximations have mitigated this scaling issue (\eg, \cite{titsias2009variational,hensman2013gaussian}), but combining neural network linearization with sparse methods remains unclear without resorting to subset methods or separately retraining a GP model \cite{ortega2023variational}.
+\todo{Reads a bit repetitive to start two sentences in a row by This, could maybe be combined in one.} This linear model (linear in the weights) refines predictions and provides uncertainty estimates \citep{immer2021scalable}.
+This model has a convenient interpretation as a GP \cite{immer2021scalable, khan2019approximate, maddox2021fast}.
+%
+However, the GP's cubic $\mathcal{O}(n^3)$ scaling with data points $n$ requires costly approximations, often resorting to using data subsets \cite{immer2021scalable}.
+In the GP community, sparse approximations have mitigated this scaling issue (\eg, \cite{titsias2009variational,hensman2013gaussian}), but combining neural network linearization with sparse methods remains \todo{Maybe unexplored instead of unclear?} unclear without resorting to subset methods or separately retraining a GP model \cite{ortega2023variational} \todo{Could add something on subset methods here, for example 'which do not retain information from the full dataset' or something like that}.
 Our work addresses this by utilizing the GP's dual parameters \cite{csato2002sparse}, previously applied to non-conjugate likelihood models \cite{adam2021dual}.
 
-% \todo{Could add something on subset methods here, for example 'which do not retain information from the full dataset' or something like that}.
 %wang2019exact
@@
 and variational inference \cite{galImproving2016,houthooftVIME2017}. \todo{Could specify here how the previous methods have used these models}
-However, each method has its pros and cons.
-In this paper we present a method which combines some of the pros from NNs with the benefits of GPs.
-
 %However, there has been little leveraging
@@
 
-Using the Hessian of the approximate model, we arrive at the Laplace-GGN approximate posterior for $q(\vw)$ \todo{This is the first time q(w) is used, should define it}. 
+Using the Hessian of the approximate model, we arrive at the Laplace-GGN approximate posterior for the weight space, $q(\vw)$. \todo{This is the first time q(w) is used, should define it}. 
 Therefore, the Laplace-GGN linear model can be used to convert our weight space model to the function space by \todo{To be super clear even when reading this part out of context: could specify that using a GP with this mean and covariance},

### 2023-05-17 paper/main.tex
reworded

--- 2023-05-17 paper/main.tex
@@
 
-Using the Hessian of the approximate model, we arrive at the Laplace-GGN approximate posterior for $q(\vw)$ \todo{This is the first time q(w) is used, should define it}. 
-Therefore, the Laplace-GGN linear model can be used to convert our weight space model to the function space by \todo{To be super clear even when reading this part out of context: could specify that using a GP with this mean and covariance},
+Using the Hessian of the approximate model, we arrive at the Laplace-GGN approximate posterior over $\vw$.
+Therefore, the Laplace-GGN linear model can be used to convert our weight space model to the function space by
 \begin{equation}
@@
 where the kernel is the so-called Neural Tangent Kernel (NTK, \cite{jacot2018neural}).
-In \cref{eq-laplace-approx-function-space}, we restrict the function output to a single dimension for notational simplicity, yet this formulation can be readily extended to the multi-output scenario.
-With this kernel function, we can combine it with the data set $\dataset$ to construct the posterior.
-\todo{what is "it" here?}
+For notational conciseness, we % \cref{eq-laplace-approx-function-space},
+restrict our notatin to a single function output dimension. The extension to multiple outputs is straightforward.
+We can combine this kernel function with the data set $\dataset$ to construct the posterior.
 %

### 2023-05-17 paper/main.tex
Bold for within-GP test

--- 2023-05-17 paper/main.tex
@@
 
-Using the Hessian of the approximate model, we arrive at the Laplace-GGN approximate posterior for the weight space, $q(\vw)$. \todo{This is the first time q(w) is used, should define it}. 
+Using the Hessian of the approximate model, we arrive at the Laplace-GGN approximate posterior for $q(\vw)$ \todo{This is the first time q(w) is used, should define it}. 
 Therefore, the Laplace-GGN linear model can be used to convert our weight space model to the function space by \todo{To be super clear even when reading this part out of context: could specify that using a GP with this mean and covariance},
@@
     %\multirow{2}{*}{MNIST}
-    MAP & -- & \val{98.22}{0.13} & \val{0.061}{0.004} & \val{0.006}{0.001}
+    MAP & & \val{98.22}{0.13} & \val{0.061}{0.004} & \val{0.006}{0.001}
           & \val{91.39}{0.11} & \val{0.258}{0.004} & \val{0.017}{0.001} \\
-    BNN predictive \cite{immer2021improving} & -- & \val{93.14}{0.05} & \val{0.304}{0.002} & \val{0.111}{0.003}
+    BNN predictive \cite{immer2021improving} & & \val{93.14}{0.05} & \val{0.304}{0.002} & \val{0.111}{0.003}
                                                & \val{84.42}{0.12} & \val{0.942}{0.016} & \val{0.411}{0.008} \\
-    BNN predictive \cite{ritter2018kfac} & -- & \val{93.03}{0.13} & \val{0.369}{0.003} & \val{0.168}{0.001}
+    BNN predictive \cite{ritter2018kfac} & & \val{93.03}{0.13} & \val{0.369}{0.003} & \val{0.168}{0.001}
                                            & \val{91.20}{0.07} & \val{0.265}{0.004} & \val{0.024}{0.002} \\
-    GLM predictive \cite{immer2021improving} & -- & \val{98.40}{0.05} & \val{0.054}{0.002} & \val{0.007}{0.001}
+    GLM predictive \cite{immer2021improving} & & \val{98.40}{0.05} & \val{0.054}{0.002} & \val{0.007}{0.001}
                                                & \val{92.25}{0.10} & \val{0.244}{0.003} & \val{0.012}{0.003} \\
-    GP predictive \cite{immer2021improving} & $3200$ & \val{98.22}{0.13} & \val{0.058}{0.001} & \val{0.003}{0.000}
-                                                     & \val{91.36}{0.11} & \val{0.25}{0.004} & \val{0.007}{0.001} \\
+    GP predictive \cite{immer2021improving} & $3200$ & \val{\textbf{98.22}}{0.13} & \val{\textbf{0.058}}{0.001} & \val{\textbf{0.003}}{0.000}
+                                                     & \val{91.36}{0.11} & \val{\textbf{0.25}}{0.004} & \val{\textbf{0.007}}{0.001} \\
 
     GP predictive (NN) & $1024$ & \val{97.70}{0.07} & \val{0.080}{0.002} & \val{0.011}{0.001}
-                              & \val{91.47}{0.41} & \val{0.289}{0.009} & \val{0.033}{0.003} \\
+                              & \val{\textbf{91.47}}{0.41} & \val{0.289}{0.009} & \val{0.033}{0.003} \\
 
@@
     \our (NN) & $1024$ &  \val{98.02}{0.12} & \val{0.066}{0.003} & \val{0.007}{0.001}
-                     & \val{91.93}{0.45} & \val{0.267}{0.011} & \val{0.028}{0.003} \\
-    \our & $1024$ & \val{98.07}{0.06} & \val{0.063}{0.003} & \val{0.005}{0.001}
-                  & \val{91.56}{0.35} & \val{0.253}{0.006} & \val{0.012}{0.001} \\
+                     & \val{\textbf{91.93}}{0.45} & \val{0.267}{0.011} & \val{0.028}{0.003} \\
+    \our & $1024$ & \val{\textbf{98.07}}{0.06} & \val{0.063}{0.003} & \val{0.005}{0.001}
+                  & \val{\textbf{91.56}}{0.35} & \val{\textbf{0.253}}{0.006} & \val{0.012}{0.001} \\
 %    \multirow{2}{*}{FMNIST}
@@
 In \cref{tbl:imagesuper}, we compare to baselines also used in \cite{immer2021improving}.
+For \our and the GP predictive subset method by \cite{immer2021improving} we fix the number of points $M=1024$.
+For completeness, we include the GP predictive result from \cite{immer2021improving} which used more inducing points $M=3200$.
 We report accuracy (ACC), NLPD, and expected calibration error (ECE).
-For \our and the GP predictive subset method by \cite{immer2021improving}, we provide results when predicting with GP mean and when using the neural network (NN) and
-fix the number of inducing points $M=1024$.
-For completeness, we also include the GP predictive result from \cite{immer2021improving} which used more inducing points $M=3200$.
 The results in \cref{tbl:imagesuper} agree with the conclusions drawn from the UCI experiments showing that \our is able to more efficiently capture the posterior using a sparse set of points.
-They further demonstrate that \our's predictive mean (GP) significantly outperforms the GP predictive subset.
-This is an interesting result as we cannot rely on the NN's prediction if we wish to condition on new data, using the dual conditioning from \label{sec:sequential}.
-In this setting, we must rely on our GP's predictive mean.
-% Other approaches, \cite{immer2021improving} never inten
-% The resutls demonstrate that \our's predictive GP mean significantly outperforms the
 These results on image data sets motivate experiments beyond the supervised learning setting, which we now detail.
-
-% For \our and the GP predictive subset method by \cite{immer2021improving} we fix the number of points $M=1024$.
-
 %We performed hyperparameter optimization over the prior precision, and found the optimal value to be [insert].
@@
 (opposed to the Class-Incremental Learning for S-MNIST and S-FMNIST)
-Considering only function-space methods, we can see that \our achieves the best results on most data sets, and is particularly effective, when using fewer points per task.
+Considering only function-space methods, we can see that \our achieves the best results on most datasets, and is particularly effective, when using fewer points per task.
 On S-FMNIST, our method obtains close results to DER, which regularizes the model by taking the mean squared error between current and old function outputs without accounting the covariance structure of the loss similar to our L2 ablation.
@@
 \todo{on PMNIST our method is not really super-fast, so that could be not the best thing to say here} % we could also say that P-MNIST is known to be a bad/ill-posed dataset for CL
-Finally, it is worth noticing as our ablation already provides a very solid baseline consistently over all data sets.
+Finally, it is worth noticing as our ablation already provides a very solid baseline consistently over all datasets.
 
@@
 Our method offers a powerful mechanism for capturing predictive uncertainty, updating the model with new data without retraining, and providing a compact representation suitable for continual learning.
-These aspects were demonstrated in a wide range of problems, data sets, and learning contexts.
+These aspects were demonstrated in a wide range of problems, datasets, and learning contexts.
 We showcased our method's ability to capture uncertainty in UCI classification tasks (\cref{sec:uci}), demonstrated robustness on image data sets (\cref{,sec:image}), established its potential for continual learning (\cref{sec:cl-exp}), and finally, verified its applicability in reinforcement learning scenarios (\cref{sec:rl-exp}).

### 2023-05-17 paper/main.tex

--- 2023-05-17 paper/main.tex
@@
                                                & \val{92.25}{0.10} & \val{0.244}{0.003} & \val{0.012}{0.003} \\
-    GP predictive \cite{immer2021improving} & $3200$ & \val{98.22}{0.13} & \val{0.058}{0.001} & \val{0.003}{0.000}
-                                                     & \val{91.36}{0.11} & \val{0.25}{0.004} & \val{0.007}{0.001} \\
+    GP predictive \cite{immer2021improving} & $3200$ & \val{\textbf{98.22}}{0.13} & \val{\textbf{0.058}}{0.001} & \val{\textbf{0.003}}{0.000}
+                                                     & \val{91.36}{0.11} & \val{\textbf{0.25}}{0.004} & \val{\textbf{0.007}}{0.001} \\
 
     GP predictive (NN) & $1024$ & \val{97.70}{0.07} & \val{0.080}{0.002} & \val{0.011}{0.001}
-                              & \val{91.47}{0.41} & \val{0.289}{0.009} & \val{0.033}{0.003} \\
+                              & \val{\textbf{91.47}}{0.41} & \val{0.289}{0.009} & \val{0.033}{0.003} \\
 

### 2023-05-17 paper/main.tex

--- 2023-05-17 paper/main.tex
@@
 Prior work has taken an expectation over the dynamic model's posterior \cite{deisenroth2011pilco,kamtheDataEfficient2018,chuaDeepReinforcementLearning2018},
-sampled from it (akin to Thompson sampling but referred to as posterior sampling in RL)
-\todo{cite thopmson sampling paper dearden et al 1999}
-\cite{osbandMoreEfficientReinforcement2013},
-and used it to implement optimism in the face of uncertainty using upper confidence bounds \cite{curiEfficient2020}.
-\todo{cite UCRL paper}
+sampled from it (akin to Thompson sampling but referred to as posterior sampling in RL) \cite{dearden1999model,osbandMoreEfficientReinforcement2013},
+and used it to implement optimism in the face of uncertainty using upper confidence bounds \cite{curiEfficient2020,jaksch2010near}.
 No single strategy has emerged as a go-to method and we highlight that these strategies are only as good as their uncertainty estimates.
@@
 ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
-and variational inference \cite{galImproving2016,houthooftVIME2017}. \todo{Could specify here how the previous methods have used these models}
+and variational inference \cite{galImproving2016,houthooftVIME2017}.
 However, each method has its pros and cons.
-In this paper we present a method which combines some of the pros from NNs with the benefits of GPs.
+In this paper, we present a method which combines some of the pros from NNs with the benefits of GPs.
 
@@
 Using the Hessian of the approximate model, we arrive at the Laplace-GGN approximate posterior over $\vw$.
-Therefore, the Laplace-GGN linear model can be used to convert our weight space model to the function space by
+Therefore, the Laplace-GGN linear model can be used to convert our weight space model to the function space,
 \begin{equation}

### 2023-05-17 paper/main.tex
new cl experiments

--- 2023-05-17 paper/main.tex
@@
                                                & \val{92.25}{0.10} & \val{0.244}{0.003} & \val{0.012}{0.003} \\
-    GP predictive \cite{immer2021improving} & $3200$ & \val{\textbf{98.22}}{0.13} & \val{\textbf{0.058}}{0.001} & \val{\textbf{0.003}}{0.000}
-                                                     & \val{91.36}{0.11} & \val{\textbf{0.25}}{0.004} & \val{\textbf{0.007}}{0.001} \\
+    GP predictive \cite{immer2021improving} & $3200$ & \val{98.22}{0.13} & \val{0.058}{0.001} & \val{0.003}{0.000}
+                                                     & \val{91.36}{0.11} & \val{0.25}{0.004} & \val{0.007}{0.001} \\
 
     GP predictive (NN) & $1024$ & \val{97.70}{0.07} & \val{0.080}{0.002} & \val{0.011}{0.001}
-                              & \val{\textbf{91.47}}{0.41} & \val{0.289}{0.009} & \val{0.033}{0.003} \\
+                              & \val{91.47}{0.41} & \val{0.289}{0.009} & \val{0.033}{0.003} \\
 
@@
     \our (NN) & $1024$ &  \val{98.02}{0.12} & \val{0.066}{0.003} & \val{0.007}{0.001}
-                     & \val{\textbf{91.93}}{0.45} & \val{0.267}{0.011} & \val{0.028}{0.003} \\
-    \our & $1024$ & \val{\textbf{98.07}}{0.06} & \val{0.063}{0.003} & \val{0.005}{0.001}
-                  & \val{\textbf{91.56}}{0.35} & \val{\textbf{0.253}}{0.006} & \val{0.012}{0.001} \\
+                     & \val{91.93}{0.45} & \val{0.267}{0.011} & \val{0.028}{0.003} \\
+    \our & $1024$ & \val{98.07}{0.06} & \val{0.063}{0.003} & \val{0.005}{0.001}
+                  & \val{91.56}{0.35} & \val{0.253}{0.006} & \val{0.012}{0.001} \\
 %    \multirow{2}{*}{FMNIST}
@@
 % Overview
-We aim to highlight our sparse representation's ability to retain previous knowledge for continual learning (CL) (as in \cref{sec:sequential}).
-We consider the single-head (SH) setting that is harder and more realistic than multi-head (MH)~\citep{van2019three}.
+We show how the regularizer described in \cref{sec:sequential} can be used in continual learning to retain a compact representation of the neural network.
+The experiments are run only in the single-head (SH) setting that is harder and more realistic than multi-head (MH) (see discussion in \citep{van2019three}).	
 % Benchmarks/architectures
- Our \our-based regularizer is evaluated on three CL benchmarks, specifically Split-MNIST (S-MNIST), Split-FashionMNIST (S-FMNIST), and the 10-tasks Permuted-MNIST (P-MNIST).
-We adhere to the same setups as outlined in \cite{rudner2022continual, pan2020continual}, which involve utilizing a two-layer MLP with 256 hidden units and ReLU activation for S-MNIST and S-FMNIST, and a two-layer MLP with 100 hidden units for P-MNIST, to ensure consistency.
-Please refer to \cref{app:cl-exp} for full details.
+ Our regularizer is evaluated on three CL benchmarks, specifically Split-MNIST (S-MNIST), Split-FashionMNIST (S-FMNIST), and the 10-tasks Permuted-MNIST (P-MNIST).
+We adhere to the same setups outlined in \cite{rudner2022continual, pan2020continual}, which use a two-layer MLP with 256 hidden units and ReLU activation for S-MNIST and S-FMNIST and a two-layer MLP with 100 hidden units for P-MNIST, to ensure consistency (see \cref{app:cl-exp} for full details).
 
 % Methods
-We compare our method against two categories of methods: {\em (i)}~weight-regularization methods: EWC, SI, and VCL (which additionally incorporates coresets), and {\em(ii)}~function-based regularization methods: DER, FROMP, S-FSVI, SFR.
-We also introduce an ablation study where we replace $\bar{\MB}_t^{-1}$ with an identity matrix $\MI_M$, equivalent to using an L2 regularizer.
-In \cref{tbl:cl_table_1}, we use 200 points for each task, and we further demonstrate our method's ability to compress information to a low number of points in S-MNIST.
+We compare our method against two categories of methods: {\em (i)}~weight-regularization methods: EWC, SI, and VCL (with coresets), and {\em(ii)}~function-based regularization methods: DER, FROMP, and S-FSVI.
+We also introduce an ablation study where we replace $\bar{\MB}_t^{-1}$ with an identity matrix $\MI_M$, equivalent to using an L2 regularizer on the function outputs.
+In \cref{tbl:cl_table_1}, we use 200 points for each task, and we further demonstrate our method's ability to compress the task data set information on a lower number of points in S-MNIST.
 
 %% Comments on the results:
-From \cref{tbl:cl_table_1}, it is clear that the weight-space regularization methods completely fail compared to the function-space methods on S-MNIST and S-FMNIST, but are comparable on P-MNIST.
-%, commonly referred as Domain Incremental Learning.
+From \cref{tbl:cl_table_1}, it is clear that the weight-space regularization methods fail entirely compared to the function-space methods on S-MNIST and S-FMNIST but are still able to achieve reasonable results on P-MNIST.
+%, commonly referred to as Domain Incremental Learning.
 (opposed to the Class-Incremental Learning for S-MNIST and S-FMNIST)
-Considering only function-space methods, we can see that \our achieves the best results on most data sets, and is particularly effective, when using fewer points per task.
-On S-FMNIST, our method obtains close results to DER, which regularizes the model by taking the mean squared error between current and old function outputs without accounting the covariance structure of the loss similar to our L2 ablation.
-Moreover, their method exploits reservoir sampling \citep{vitter1985random} to obtain a continuously updated set inducing points.
-S-FSVI obtains the best on P-MNIST, but with the downside of requiring high computational costs based on performing variational inference, compared to \our.
-\todo{on PMNIST our method is not really super-fast, so that could be not the best thing to say here} % we could also say that P-MNIST is known to be a bad/ill-posed dataset for CL
+Considering only function-space methods, we can see that \our achieves the best results on most data sets and is particularly effective when using fewer points per task.
+On S-FMNIST, our method obtains close results to DER, which regularizes the model by taking the mean squared error between current and old function outputs without accounting for the covariance structure of the loss similar to our L2 ablation.
+However, DER differs from our ablation since it resorts to a reservoir sampling \citep{vitter1985random} to continuously update the set of points instead of picking them at the task boundary.
+Finally, \our-based regularizer obtains comparable results to the best-performing method on P-MNIST, S-FSVI, which has the downside of requiring computational intensive based on performing variational inference, compared to \our.
+\todo{on PMNIST our method is not really super-fast, so that could be not the best thing to say here} % we could also say that P-MNIST is known to be a bad/ill-posed data set for CL
 Finally, it is worth noticing as our ablation already provides a very solid baseline consistently over all data sets.

### 2023-05-17 paper/main.tex

@@
 
-Using the Hessian of the approximate model, we arrive at the Laplace-GGN approximate posterior for the weight space, $q(\vw)$. \todo{This is the first time q(w) is used, should define it}. 
-Therefore, the Laplace-GGN linear model can be used to convert our weight space model to the function space by \todo{To be super clear even when reading this part out of context: could specify that using a GP with this mean and covariance},
+Using the Hessian of the approximate model, we arrive at the Laplace-GGN approximate posterior over $\vw$.
+Therefore, the Laplace-GGN linear model can be used to convert our weight space model to the function space,
 \begin{equation}

### 2023-05-17 paper/main.tex
line

@@
     GLM predictive \cite{immer2021improving} & -- & \val{98.40}{0.05} & \val{0.054}{0.002} & \val{0.007}{0.001}
-                                               & \val{92.25}{0.10} & \val{0.244}{0.003} & \val{0.012}{0.003} \\
+                                               & \val{92.25}{0.10} & \val{0.244}{0.003} & \val{0.012}{0.003} \\\arrayrulecolor{black!10}\midrule 
     GP predictive \cite{immer2021improving} & $3200$ & \val{\textbf{98.22}}{0.13} & \val{\textbf{0.058}}{0.001} & \val{\textbf{0.003}}{0.000}
@@
     % & \our $m=1024$ &  \val{0}{0.06} & \val{0}{0.003} & \val{0}{0.001} \\
+    \arrayrulecolor{black}
     \bottomrule

### 2023-05-17 paper/main.tex
shortened uci

--- 2023-05-17 paper/main.tex
@@
 These results demonstrate \our's sparse representation captures information from the entire data set and as a result provides good uncertainty estimates.
-We provide full details of our experiments and further results using $M=16,32,64,128,256$ in \cref{app:uci}.
+We provide further details of our experiments in \cref{app:uci}.
+% as well as further results with varying number of inducing poitns ,64,128,256$
+% We provide full details of our experiments as well as further experiments with varying number of inducing poitns and further results using $M=16,32,64,128,256$ in \cref{app:uci}.
 % benefits of \our in summarizing the full data distribution onto a small set of inducing
@@
 % Overview
-We show how the regularizer described in \cref{sec:sequential} can be used in continual learning to retain a compact representation of the neural network.
-The experiments are run only in the single-head (SH) setting that is harder and more realistic than multi-head (MH) (see discussion in \citep{van2019three}).	
+We aim to highlight our sparse representation's ability to retain previous knowledge for continual learning (CL) (as in \cref{sec:sequential}).
+We consider the single-head (SH) setting that is harder and more realistic than multi-head (MH)~\citep{van2019three}.
 % Benchmarks/architectures
- Our regularizer is evaluated on three CL benchmarks, specifically Split-MNIST (S-MNIST), Split-FashionMNIST (S-FMNIST), and the 10-tasks Permuted-MNIST (P-MNIST).
-We adhere to the same setups outlined in \cite{rudner2022continual, pan2020continual}, which use a two-layer MLP with 256 hidden units and ReLU activation for S-MNIST and S-FMNIST and a two-layer MLP with 100 hidden units for P-MNIST, to ensure consistency (see \cref{app:cl-exp} for full details).
+ Our \our-based regularizer is evaluated on three CL benchmarks, specifically Split-MNIST (S-MNIST), Split-FashionMNIST (S-FMNIST), and the 10-tasks Permuted-MNIST (P-MNIST).
+We adhere to the same setups as outlined in \cite{rudner2022continual, pan2020continual}, which involve utilizing a two-layer MLP with 256 hidden units and ReLU activation for S-MNIST and S-FMNIST, and a two-layer MLP with 100 hidden units for P-MNIST, to ensure consistency.
+Please refer to \cref{app:cl-exp} for full details.
 
 % Methods
-We compare our method against two categories of methods: {\em (i)}~weight-regularization methods: EWC, SI, and VCL (with coresets), and {\em(ii)}~function-based regularization methods: DER, FROMP, and S-FSVI.
-We also introduce an ablation study where we replace $\bar{\MB}_t^{-1}$ with an identity matrix $\MI_M$, equivalent to using an L2 regularizer on the function outputs.
-In \cref{tbl:cl_table_1}, we use 200 points for each task, and we further demonstrate our method's ability to compress the task data set information on a lower number of points in S-MNIST.
+We compare our method against two categories of methods: {\em (i)}~weight-regularization methods: EWC, SI, and VCL (which additionally incorporates coresets), and {\em(ii)}~function-based regularization methods: DER, FROMP, S-FSVI, SFR.
+We also introduce an ablation study where we replace $\bar{\MB}_t^{-1}$ with an identity matrix $\MI_M$, equivalent to using an L2 regularizer.
+In \cref{tbl:cl_table_1}, we use 200 points for each task, and we further demonstrate our method's ability to compress information to a low number of points in S-MNIST.
 
 %% Comments on the results:
-From \cref{tbl:cl_table_1}, it is clear that the weight-space regularization methods fail entirely compared to the function-space methods on S-MNIST and S-FMNIST but are still able to achieve reasonable results on P-MNIST.
-%, commonly referred to as Domain Incremental Learning.
+From \cref{tbl:cl_table_1}, it is clear that the weight-space regularization methods completely fail compared to the function-space methods on S-MNIST and S-FMNIST, but are comparable on P-MNIST.
+%, commonly referred as Domain Incremental Learning.
 (opposed to the Class-Incremental Learning for S-MNIST and S-FMNIST)
-Considering only function-space methods, we can see that \our achieves the best results on most data sets and is particularly effective when using fewer points per task.
-On S-FMNIST, our method obtains close results to DER, which regularizes the model by taking the mean squared error between current and old function outputs without accounting for the covariance structure of the loss similar to our L2 ablation.
-However, DER differs from our ablation since it resorts to a reservoir sampling \citep{vitter1985random} to continuously update the set of points instead of picking them at the task boundary.
-Finally, \our-based regularizer obtains comparable results to the best-performing method on P-MNIST, S-FSVI, which has the downside of requiring computational intensive based on performing variational inference, compared to \our.
-\todo{on PMNIST our method is not really super-fast, so that could be not the best thing to say here} % we could also say that P-MNIST is known to be a bad/ill-posed data set for CL
+Considering only function-space methods, we can see that \our achieves the best results on most data sets, and is particularly effective, when using fewer points per task.
+On S-FMNIST, our method obtains close results to DER, which regularizes the model by taking the mean squared error between current and old function outputs without accounting the covariance structure of the loss similar to our L2 ablation.
+Moreover, their method exploits reservoir sampling \citep{vitter1985random} to obtain a continuously updated set inducing points.
+S-FSVI obtains the best on P-MNIST, but with the downside of requiring high computational costs based on performing variational inference, compared to \our.
+\todo{on PMNIST our method is not really super-fast, so that could be not the best thing to say here} % we could also say that P-MNIST is known to be a bad/ill-posed dataset for CL
 Finally, it is worth noticing as our ablation already provides a very solid baseline consistently over all data sets.

### 2023-05-17 paper/main.tex
small thing

--- 2023-05-17 paper/main.tex
@@
 \todo{on PMNIST our method is not really super-fast, so that could be not the best thing to say here} % we could also say that P-MNIST is known to be a bad/ill-posed data set for CL
-Finally, it is worth noticing as our ablation already provides a very solid baseline consistently over all data sets.
+Finally, it is worth noticing our ablation already provides a very solid baseline consistently over all data sets.
 

### 2023-05-17 paper/main.tex
update cl experiments

--- 2023-05-17 paper/main.tex
@@
     GLM predictive \cite{immer2021improving} & -- & \val{98.40}{0.05} & \val{0.054}{0.002} & \val{0.007}{0.001}
-                                               & \val{92.25}{0.10} & \val{0.244}{0.003} & \val{0.012}{0.003} \\\arrayrulecolor{black!10}\midrule 
+                                               & \val{92.25}{0.10} & \val{0.244}{0.003} & \val{0.012}{0.003} \\
     GP predictive \cite{immer2021improving} & $3200$ & \val{\textbf{98.22}}{0.13} & \val{\textbf{0.058}}{0.001} & \val{\textbf{0.003}}{0.000}
@@
     % & \our $m=1024$ &  \val{0}{0.06} & \val{0}{0.003} & \val{0}{0.001} \\
-    \arrayrulecolor{black}
     \bottomrule
@@
 We compare our method against two categories of methods: {\em (i)}~weight-regularization methods: EWC, SI, and VCL (with coresets), and {\em(ii)}~function-based regularization methods: DER, FROMP, and S-FSVI.
-We also introduce an ablation study where we replace $\bar{\MB}_t^{-1}$ with an identity matrix $\MI_M$, equivalent to using an L2 regularizer on the function outputs.
-In \cref{tbl:cl_table_1}, we use 200 points for each task, and we further demonstrate our method's ability to compress the task data set information on a lower number of points in S-MNIST.
+We also introduce an ablation study where we replace our $\bar{\MB}_t^{-1}$ with an identity matrix $\MI_M$, equivalent to having an L2 regularization between current and old function outputs.
+In \cref{tbl:cl_table_1}, we use 200 points for each task, and we further demonstrate our method's ability to compress the task data set information on a lower number of points for S-MNIST.
 
 %% Comments on the results:
-From \cref{tbl:cl_table_1}, it is clear that the weight-space regularization methods fail entirely compared to the function-space methods on S-MNIST and S-FMNIST but are still able to achieve reasonable results on P-MNIST.
-%, commonly referred to as Domain Incremental Learning.
-(opposed to the Class-Incremental Learning for S-MNIST and S-FMNIST)
+From \cref{tbl:cl_table_1}, it is clear that the weight-space regularization methods fail entirely compared to the function-space methods on S-MNIST and S-FMNIST but are still comparable on P-MNIST.
 Considering only function-space methods, we can see that \our achieves the best results on most data sets and is particularly effective when using fewer points per task.
 On S-FMNIST, our method obtains close results to DER, which regularizes the model by taking the mean squared error between current and old function outputs without accounting for the covariance structure of the loss similar to our L2 ablation.
-However, DER differs from our ablation since it resorts to a reservoir sampling \citep{vitter1985random} to continuously update the set of points instead of picking them at the task boundary.
-Finally, \our-based regularizer obtains comparable results to the best-performing method on P-MNIST, S-FSVI, which has the downside of requiring computational intensive based on performing variational inference, compared to \our.
-\todo{on PMNIST our method is not really super-fast, so that could be not the best thing to say here} % we could also say that P-MNIST is known to be a bad/ill-posed data set for CL
+However, DER resorts to a reservoir sampling \citep{vitter1985random} that continuously update the set of points instead of selecting them at the task boundary.
+The \our-based regularizer obtains comparable results to the best-performing method on P-MNIST, S-FSVI, which requires heavy computations compared to \our to perform variational inference.
 Finally, it is worth noticing as our ablation already provides a very solid baseline consistently over all data sets.

### 2023-05-17 paper/main.tex

--- 2023-05-17 paper/main.tex
@@
 We compare our method against two categories of methods: {\em (i)}~weight-regularization methods: EWC, SI, and VCL (with coresets), and {\em(ii)}~function-based regularization methods: DER, FROMP, and S-FSVI.
-We also introduce an ablation study where we replace $\bar{\MB}_t^{-1}$ with an identity matrix $\MI_M$, equivalent to using an L2 regularizer on the function outputs.
-In \cref{tbl:cl_table_1}, we use 200 points for each task, and we further demonstrate our method's ability to compress the task data set information on a lower number of points in S-MNIST.
+We also introduce an ablation study where we replace our $\bar{\MB}_t^{-1}$ with an identity matrix $\MI_M$, equivalent to having an L2 regularization between current and old function outputs.
+In \cref{tbl:cl_table_1}, we use 200 points for each task, and we further demonstrate our method's ability to compress the task data set information on a lower number of points for S-MNIST.
 
 %% Comments on the results:
-From \cref{tbl:cl_table_1}, it is clear that the weight-space regularization methods fail entirely compared to the function-space methods on S-MNIST and S-FMNIST but are still able to achieve reasonable results on P-MNIST.
-%, commonly referred to as Domain Incremental Learning.
-(opposed to the Class-Incremental Learning for S-MNIST and S-FMNIST)
+From \cref{tbl:cl_table_1}, it is clear that the weight-space regularization methods fail entirely compared to the function-space methods on S-MNIST and S-FMNIST but are still comparable on P-MNIST.
 Considering only function-space methods, we can see that \our achieves the best results on most data sets and is particularly effective when using fewer points per task.
 On S-FMNIST, our method obtains close results to DER, which regularizes the model by taking the mean squared error between current and old function outputs without accounting for the covariance structure of the loss similar to our L2 ablation.
-However, DER differs from our ablation since it resorts to a reservoir sampling \citep{vitter1985random} to continuously update the set of points instead of picking them at the task boundary.
-Finally, \our-based regularizer obtains comparable results to the best-performing method on P-MNIST, S-FSVI, which has the downside of requiring computational intensive based on performing variational inference, compared to \our.
-\todo{on PMNIST our method is not really super-fast, so that could be not the best thing to say here} % we could also say that P-MNIST is known to be a bad/ill-posed data set for CL
-Finally, it is worth noticing our ablation already provides a very solid baseline consistently over all data sets.
+However, DER resorts to a reservoir sampling \citep{vitter1985random} that continuously update the set of points instead of selecting them at the task boundary.
+The \our-based regularizer obtains comparable results to the best-performing method on P-MNIST, S-FSVI, which requires heavy computations compared to \our to perform
 

### 2023-05-17 paper/main.tex
shorted

--- 2023-05-17 paper/main.tex
@@
 
-Unlike our approach, \citet{immer2021improving} employ a subset of the data points to construct a sparse GP model, reducing computational complexity.
+Unlike our approach, \citet{immer2021improving} employ a subset of the data points to construct a sparse GP, reducing computational complexity.
 However, the method could be considered less principled for building a sparse model, as it ignores contribution from the complete dataset.
@@
 More complicated inference techniques, such as variational inference, could be used, but given its simplicity, in our experiments we used the Laplace-GGN approximation with the trained neural network.
-Furthermore, our dual variable view of approximate inference means we do not need to retrain a separate sparse GP model.%\todo{shouldn't this sentence be clear from the context?
-we derive the mean/kernel function that define the process, then we have a sparse GP already}
+Furthermore, our dual variable view of approximate inference means we do not need to retrain a separate sparse GP.\looseness-2
+% \todo{shouldn't this sentence be clear from the context? we derive the mean/kernel function that define the process, then we have a sparse GP already}
 
@@
 \todo{on PMNIST our method is not really super-fast, so that could be not the best thing to say here} % we could also say that P-MNIST is known to be a bad/ill-posed data set for CL
-Finally, it is worth noticing our ablation already provides a very solid baseline consistently over all data sets.
+Finally, it is worth noticing as our ablation already provides a very solid baseline consistently over all data sets.
 

### 2023-05-17 paper/main.tex
shorted

--- 2023-05-17 paper/main.tex
@@
 In \cref{fig:banana}, we use an MLP with two hidden layers (64 units, sigmoid) and compare to a HMC sampling result obtained by hamiltorch~\cite{cobb2020scaling}.
-The HMC result is more expressive, but the results are still similar in terms of quantifying the uncertainty in low-data regions.
+The HMC result is more expressive, but the results are still similar in terms of quantifying the uncertainty in low-data regions.\looseness-1
 

### 2023-05-17 paper/main.tex
fixed cl

--- 2023-05-17 paper/main.tex
@@
 However, DER resorts to a reservoir sampling \citep{vitter1985random} that continuously update the set of points instead of selecting them at the task boundary.
-The \our-based regularizer obtains comparable results to the best-performing method on P-MNIST, S-FSVI, which requires heavy computations compared to \our to perform
+The \our-based regularizer obtains comparable results to the best-performing method on P-MNIST, S-FSVI, which requires heavy computations compared to \our to perform variational inference.
+Finally, it is worth noticing as our ablation already provides a very solid baseline consistently over all data sets.
 

### 2023-05-17 paper/main.tex
INITIAL SUBMISSION

--- 2023-05-17 paper/main.tex
@@
 
-\cref{fig:rl} shows training curves for using \our as the dynamic model (\lab{color-our}), along with a Laplace-GGN~\cite{todo} with GLM predictions (\lab{red}), an ensemble of neural networks (\lab{color-ensemble}), and a basic MLP without uncertainty (\lab{color-mlp}).
+\cref{fig:rl} shows training curves for using \our as the dynamic model (\lab{color-our}), along with a Laplace-GGN~\cite{immer2021scalable} with GLM predictions (\lab{red}), an ensemble of neural networks (\lab{color-ensemble}), and a basic MLP without uncertainty (\lab{color-mlp}).
 To ensure a fair comparison, we maintain the same MLP architecture/training scheme across all these methods and incorporate them into the same model-based RL algorithm (see \cref{app:rl}).
 We also compare our results with Deep Deterministic Policy Gradient (DDPG, \cite{lillicrapContinuousControlDeep2016}), a model-free RL algorithm (\lab{color-ddpg}).
-%
-The training curves clearly show that \our's uncertainty estimates help exploration as it converges in fewer episodes, demonstrating higher sample efficiency.
-As expected, the MLP strategy (without uncertainty) was not able to successfuly explore the environment.
+The training curves show that \our's uncertainty estimates help exploration as it converges in fewer episodes, demonstrating higher sample efficiency.
+As expected, the MLP strategy (without uncertainty) was not able to successfuly explore the environment.\looseness-2
 
@@
  \label{fig:rl}
+ \vspace*{-1em}
 \end{figure}

### 2023-05-17 paper/main.tex
shortned for submission

@@
 That is, we match predictive performance despite being sparse.
-
+%
 In \cref{tbl:uci} (right) we compare to the subset GP method from \cite{immer2021improving} whilst using only $M=32$ inducing points.
@@
 \label{sec:image}
+Similarly to the UCI experiments, we seek to demonstrate \our on image data that features more complicated data manifolds and model structures.
+We consider the MNIST and Fashion-MNIST (FMNIST) classification tasks, and use an MLP and a CNN architecture respectively (matching the setup in \cite{immer2021improving}).
+After training, we computed the duals for \our and use the model for prediction (full experiment details in \cref{app:image}).
+In \cref{tbl:imagesuper}, we compare to baselines also used in \cite{immer2021improving}.
+We report accuracy (ACC), NLPD, and expected calibration error (ECE).
+For \our and the GP predictive subset method by \cite{immer2021improving}, we provide results when predicting with GP mean and when using the neural network (NN) and
+fix the number of inducing points $M=1024$.
+For completeness, we also include the GP predictive result from \cite{immer2021improving} which used more inducing points $M=3200$.
+The results in \cref{tbl:imagesuper} agree with the conclusions drawn from the UCI experiments showing that \our is able to more efficiently capture the posterior using a sparse set of points.
+They further demonstrate that \our's predictive mean (GP) significantly outperforms the GP predictive subset.
+This is an interesting result as we cannot rely on the NN's prediction if we wish to condition on new data, using the dual conditioning from \label{sec:sequential}.
+In this setting, we must rely on our GP's predictive mean.
+% Other approaches, \cite{immer2021improving} never inten
+% The resutls demonstrate that \our's predictive GP mean significantly outperforms the
+These results on image data sets motivate experiments beyond the supervised learning setting, which we now detail.
+
+% For \our and the GP predictive subset method by \cite{immer2021improving} we fix the number of points $M=1024$.
+
+%We performed hyperparameter optimization over the prior precision, and found the optimal value to be [insert].
+We ran the experiment over $5$ seeds.
+During the NN training, we used a batch size of $512$ and an Adam optimizer with learning rate $1e-3$.
+
+%In addition to uncertainty estimates, our method can update the posterior when given new data.
+We gave the SVGP model 10 \% of the test dataset used for evaluation, and compare the performance of the SVGP model and the retrained NN in [INSERT TABLE].
 
@@
 \end{table}
-
-Similarly to the UCI experiments, we seek to demonstrate \our on image data that features more complicated data manifolds and model structures.
-We consider the MNIST and Fashion-MNIST (FMNIST) classification tasks, and use an MLP and a CNN architecture respectively (matching the setup in \cite{immer2021improving}).
-After training, we computed the duals for \our and use the model for prediction (full experiment details in \cref{app:image}).
-In \cref{tbl:imagesuper}, we compare to baselines also used in \cite{immer2021improving}.
-We report accuracy (ACC), NLPD, and expected calibration error (ECE).
-For \our and the GP predictive subset method by \cite{immer2021improving}, we provide results when predicting with GP mean and when using the neural network (NN) and
-fix the number of inducing points $M=1024$.
-For completeness, we also include the GP predictive result from \cite{immer2021improving} which used more inducing points $M=3200$.
-The results in \cref{tbl:imagesuper} agree with the conclusions drawn from the UCI experiments showing that \our is able to more efficiently capture the posterior using a sparse set of points.
-They further demonstrate that \our's predictive mean (GP) significantly outperforms the GP predictive subset.
-This is an interesting result as we cannot rely on the NN's prediction if we wish to condition on new data, using the dual conditioning from \label{sec:sequential}.
-In this setting, we must rely on our GP's predictive mean.
-% Other approaches, \cite{immer2021improving} never inten
-% The resutls demonstrate that \our's predictive GP mean significantly outperforms the
-These results on image data sets motivate experiments beyond the supervised learning setting, which we now detail.
-
-% For \our and the GP predictive subset method by \cite{immer2021improving} we fix the number of points $M=1024$.
-
-%We performed hyperparameter optimization over the prior precision, and found the optimal value to be [insert].
-We ran the experiment over $5$ seeds.
-During the NN training, we used a batch size of $512$ and an Adam optimizer with learning rate $1e-3$.
-
-%In addition to uncertainty estimates, our method can update the posterior when given new data.
-We gave the SVGP model 10 \% of the test dataset used for evaluation, and compare the performance of the SVGP model and the retrained NN in [INSERT TABLE].
 

### 2023-05-17 paper/main.tex
cnagedd to 5 seeds
cypo

@@
 We refer to our method as Sparse Function-space Representation (\our)---a sparse GP derived from a trained neural network.
-Moreover, this dual parameterization can be exploited to perform dual conditioning \citep{chang2022fantasizing}, \ie, an effective approach to condition on new incoming data into our model without need of retraning the model (see \cref{fig:teaser}).
+Moreover, this dual parameterization can be exploited to perform dual conditioning \citep{chang2022fantasizing}, \ie, an effective approach for conditioning on new data without needing to retrain the model (see \cref{fig:teaser}).
 %As \our is in the dual parameters, we can perform dual conditioning recently shown effective in \cite{chang2022fantasizing}, that is, avoid retraining and condition new data into our model (see \cref{fig:teaser}) \todo{Effective compared to what?}.
@@
   \caption{Metrics for supervised learning on image data with a CNN.
-We report accuracy, NLPD, and expected calibration error (mean$\pm$std) over 10 seeds.
+We report accuracy, NLPD, and expected calibration error (mean$\pm$std) over 5 seeds.
 Our \our method is able to match the full methods using only a sparse set.

### 2023-05-17 paper/main.tex
typo

@@
   \caption{\textbf{Regression example on an MLP with two hidden layers.} Left:~Predictions from the trained neural network.
-Middle:~Our approach summarizes all the training data with the help of an inducing set of points.
-The model captures the predictive mean and uncertainty, and (right) makes it possible to update the model with new data without degrading previous performance.}
+Middle:~Our approach summarizes all the training data with the help of a set of inducing points.
+The model captures the predictive mean and uncertainty, and (right) makes it possible to incorporate new data without retraining the model.}
   \label{fig:teaser} 

### 2023-05-17 paper/main.tex
typo

@@
 
-The contributions of this paper are that:
+The contributions of this paper are as follows:
 %
 {\em (i)}~We introduce \our, a new approach for building a sparse functional representation of a neural network.
-{\em (ii)}~We demonstrate that, despite its sparsity, our method effectively captures predictive uncertainty, provides means of updating the model post-training, and gives a a compact regularizer suitable for continual learning.
+{\em (ii)}~We demonstrate that, despite its sparsity, our method effectively captures predictive uncertainty, provides a means of updating the model post-training, and gives a compact regularizer suitable for continual learning.
 {\em (iii)}~We provide extensive experiments for showcasing our approach and demonstrate significance and applicability across supervised, continual, and reinforcement learning, aiming to stimulate future use of the approach.

### 2023-05-17 paper/main.tex
final version for initial submission

@@
 Furthermore, the resultant weight-space posterior can be converted to the function-space as shown in \cite{khan2019approximate, immer2021improving}.
-The function-space representation allows for a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{foong2019between}.
+The function-space representation allows for a principled mathematical approach for analyzing its behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{foong2019between}.
 These methods rely on the linearization of the neural network and the resultant neural tangent kernel (NTK, \cite{jacot2018neural}).
@@
 %The Hessian can be efficiently approximated using the generalized Gauss--Newton approximation . 
-While efficient, it suffers from cubic scaling in parameter count, necessitating approximations like Kronecker factorisation \cite{martens2015optimizing, ritter2018kfac}.
-This linear model (linear in the weights) refines predictions and provides uncertainty estimates \citep{immer2021scalable}.
+While efficient, the GNN suffers from cubic scaling in parameter count, necessitating approximations like Kronecker factorisation \cite{martens2015optimizing, ritter2018kfac}.
+This linear model (with respect to the weights) refines predictions and provides uncertainty estimates \citep{immer2021scalable}.
 It has a convenient interpretation as a GP \cite{immer2021scalable, khan2019approximate, maddox2021fast}.
@@
 However, the GP's cubic $\mathcal{O}(N^3)$ scaling with data points $N$ requires costly approximations, often resorting to using data subsets \cite{immer2021scalable}.
-In the GP community, sparse approximations have mitigated this scaling issue (\eg, \cite{titsias2009variational,hensman2013gaussian}), but combining neural network linearization with sparse methods remains unclear without resorting to subset methods or separately retraining a GP model \cite{ortega2023variational}.
-Our work addresses this by utilizing the GP's dual parameters \cite{csato2002sparse}, previously applied to non-conjugate likelihood models \cite{adam2021dual}.
+In the GP community, sparse approximations have mitigated this scaling issue (\eg, \cite{titsias2009variational,hensman2013gaussian}),
+but combining neural network linearization with sparse GP methods remains underexplored.
+Recent work has explored converting NNs to sparse variational GPs \cite{ortega2023variational}, however, their method requires separately retraining a GP model.
+% However,
+% unclear without resorting to subset methods or separately retraining a GP model \cite{ortega2023variational}.
+Our work addresses this by utilizing the GP's dual parameters \cite{csato2002sparse}, previously applied to non-conjugate likelihood models~\cite{adam2021dual}.\looseness-1
 
@@
 Function-space regularization techniques~\cite{li2018lwf, benjamin2018measuring, titsias2019functional, buzzega2020dark, pan2020continual, rudner2022continual} address this by relying on training data subsets for each task to compute a regularization term.
-These methods can be seen as a hybrid between objective and rehearsal-based methods, since they also store a subset of training data for each task to construct the regularization term.
+These methods can be seen as a hybrid between objective and rehearsal-based methods, since they also store a subset of training data to construct the regularization term.
 Recent function-based methods, \eg, DER~\citep{buzzega2020dark}, FROMP~\citep{pan2020continual}, and S-FSVI~\citep{rudner2022continual}, achieve state-of-the-art performance among the objective-based techniques in several CL benchmarks.
@@
 We convert the trained neural network (left) to a sparse GP model that summarizes all data onto a sparse set of inducing points~\myinducing\ (middle).
-This gives similar behaviour as would running full Hamiltonian Monte Carlo (HMC) on the original neural network model weights (right).
+This gives similar behaviour as running full Hamiltonian Monte Carlo (HMC) on the original neural network model weights (right).
 Marginal uncertainty depicted by colour intensity.\looseness-1}
@@
 
-\textbf{Neural Network Function-space} %\todo{Could be titled some other way, like Function-space representation}
+\textbf{Neural network function-space} %\todo{Could be titled some other way, like Function-space representation}
 %As a neural network is a deterministic mapping, the weight-space posterior induces a distribution over the function values.
@@
 Our goal is to capture the distribution over the neural network model functions through their first two moments.
-The first moments characterize a Gaussian process with a mean function $\mu(\cdot)$ and a covariance function (kernel) $\kappa(\cdot,\cdot)$.
+The first two moments characterize a Gaussian process with a mean function $\mu(\cdot)$ and a covariance function (kernel) $\kappa(\cdot,\cdot)$.
 Recent work \cite{khan2019approximate,maddox2021fast} has shown that linearizing approximations in the weight space lead to function-space equivalent approximations.
@@
 \Jac{\weights_*}{\vx} \, \weights$, where $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{1 \times P}$ is the Jacobian at the MAP.
+For notational conciseness, we % \cref{eq-laplace-approx-function-space},
+restrict our notatin to a single function output. The extension to multiple outputs is straightforward.
 
@@
 where the kernel is the so-called Neural Tangent Kernel (NTK, \cite{jacot2018neural}).
-For notational conciseness, we % \cref{eq-laplace-approx-function-space},
-restrict our notatin to a single function output dimension. The extension to multiple outputs is straightforward.
 We can combine this kernel function with the data set $\dataset$ to construct the posterior.
@@
 Similarly, \citet{immer2021improving} obtain the same covariance function but use a different mean because they rely on a first-order approximation of the neural network to form a Bayesian GLM model.
-Both approaches attempted to adjust the GP posterior mean function to ensure the predictions are from the neural network $f_{\vw^*}(\vx)$.
-Contrarily, our methodology intends to make predictions directly from the derived GP, thus evading such adjustments.
-Next, we will present the general formulation of the sparse functional representation of our trained neural network based on the non-sparse approximation.
+Both approaches adjust the GP posterior mean function to ensure the predictions are from the neural network $f_{\vw^*}(\vx)$.
+In contrast, our method makes predictions directly from the GP and avoids such adjustments.
+In the next section, we present our method for converting a trained NN to a sparse functional representation.
+% on the non-sparse approximation.
+% of our
+% based on the non-sparse approximation.
+% we will present the general formulation of the sparse functional representation of our trained neural network based on the non-sparse approximation.
 
@@
 where the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{N \times N}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $k_{ii} = \kappa(\vx_i, \vx_i)$.
-\cref{eq:gp_pred} states that the resultant posterior process, which may not be a GP, first two moments can be parameterized via the dual parameters, which are the vectors $\valpha, \vbeta \in \R^{N}$, defined as:\looseness-1
+\cref{eq:gp_pred} states that the first two moments of the resultant posterior process (which may not be a GP), can be parameterized via the dual
+parameters $\valpha, \vbeta \in \R^{N}$,
+% which are the vectors
+defined as, \looseness-1
 %
@@
 % Overview
-We show how the regularizer described in \cref{sec:sequential} can be used in continual learning to retain a compact representation of the neural network.
+In this section, we show how the regularizer described in \cref{sec:sequential} can be used in continual learning to retain a compact representation of the neural network.
 The experiments are run only in the single-head (SH) setting that is harder and more realistic than multi-head (MH) (see discussion in \citep{van2019three}).	
@@
 %% Comments on the results:
-From \cref{tbl:cl_table_1}, it is clear that the weight-space regularization methods fail entirely compared to the function-space methods on S-MNIST and S-FMNIST but are still comparable on P-MNIST.
+From \cref{tbl:cl_table_1}, it is clear that the weight-space regularization methods fail entirely compared to the function-space methods on S-MNIST and S-FMNIST but are still achieving comparable results on P-MNIST.
 Considering only function-space methods, we can see that \our achieves the best results on most data sets and is particularly effective when using fewer points per task.
@@
 The \our-based regularizer obtains comparable results to the best-performing method on P-MNIST, S-FSVI, which requires heavy computations compared to \our to perform variational inference.
-Finally, it is worth noticing as our ablation already provides a very solid baseline consistently over all data sets.
+% Finally, it is worth noticing as our ablation already provides a very solid baseline consistently over all data sets.
 
@@
  \label{fig:rl}
- \vspace*{-1em}
+ % \vspace*{-1em}
 \end{figure}

### 2023-05-17 setup.py
added laplace-torch

@@ -57,6 +57,7 @@ install_requires = [
     # "torchrl==0.1.0",  # using this on triton
     # "./src/third_party/rl-0.1.0", # using this locally
     f"torchrl @ file://{_here}/src/rl/third_party/rl-0.1.0",
+    "laplace-torch",
 ]
 extras_require = {
     "dev": [

### 2023-05-19 paper/main.tex
App.
updated app. for cl

@@
 \newcommand{\Norm}{\mathcal{N}}
+
+\newcommand{\digit}[1]{\tikz[baseline=-.5ex]\node[inner sep=1pt,rounded corners=1pt,draw=black,text width=5pt,minimum width=5pt,align=center,fill=black!20]{\tiny\bf\sf#1};}
 
@@
 \subsection{Derivation of the regularizer term}
-An alternative view of the dual variables is that they parameterize approximate likelihoods, as shown in \citep{adam2021dual, khan2017conjugate}.
-We can rewrite the GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
+An alternative view of the dual parameters is that they parameterize approximate likelihoods, as shown in \citep{khan2017conjugate, adam2021dual}.
+Then, we can rewrite the GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
+
 \begin{equation}
- q(\vu) \propto \Norm(0, \MKzz) \prod_{i=1}^n \exp \!
-\left(-\frac{\tilde{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 \right) = \Norm(0, \MKzz) \, \exp\left((\bar{\vy} - \vu)^\top \bar{\MSigma}^{-1}(\bar{\vy} - \vu)\right)
+\begin{aligned}
+ q(\vu) 
+ 	&\propto \Norm(0, \MKzz) \prod_{i=1}^n \exp \! \left(-\frac{\tilde{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 \right) \\
+ 	&= \Norm(0, \MKzz) \, \exp\left((\bar{\vy} - \vu)^\top \bar{\MSigma}^{-1}(\bar{\vy} - \vu)\right)  
+\end{aligned}
 \end{equation}
+
 The first normals are the approximate likelihoods where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}$,  replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$ and we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior.
@@
 \subsection{Extending the CL regularizer to multi-class settings}
+\label{sec:cl_multioutput} \todo{this sub-section was mistakenly duplicated}
 \begin{equation}
@@
 \label{app:cl-exp}
-
-\section{Extending the CL regularizer to multi-class settings}
-\label{sec:cl_multioutput}
-\begin{equation}
-	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{C \times m \times m} \quad \MKzz \in \R^{C \times m \times m} 
-\end{equation}
-
-\begin{equation}
-	\mathcal{R_\textit{SFR}}(\mathbf{w}) = \sum_{s=1}^{t-1}	\sum_{k \in 	C}\left[\left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s}, k}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s, k}}(\MZ_s) \right) \right]
-\end{equation}
-
-\subsection{Reinforcement learning experiment}
-\label{app:rl-experiment}
+\textbf{CL Data sets}
+We conducted our experiments on three common CL data sets \cite{de2021continual, pan2020continual, rudner2022continual}: 
+\begin{itemize}
+	\item[-] Split-MNIST (S-MNIST), that consists in five binary classification tasks each on pair on MNIST classes (\ie, \digit{0}~and~\digit{1}, \digit{2}~and~\digit{3}, \dots, \digit{8}~and~\digit{9});
+	\item[-] Split-FashionMNIST (S-FMNIST), composed of five binary tasks as S-MNIST, but using instead Fashion-MNIST;
+	\item[-] Permuted-MNIST (P-MNIST), that consists of ten tasks, where each one is a ten-way classification task on the entire MNIST data set, where the images' pixels are randomly permuted.
+\end{itemize}
+
+Following \cite{pan2020continual, rudner2022continual}, we used a two-layer MLP with 256 hidden units and ReLU activations for S-MNIST and S-FMNIST and a two-layer MLP with 100 hidden units and ReLU activations for P-MNIST, to ensure consistency with the other methods.
+In our experiments we only consider the single-head setting (SH).
+This means that for S-MNIST and S-FMNIST, we are dealing with a Class-Incremental Learning (CIL) scenario, where for each task a pair of dijoint classes are presented to the model.
+The P-MNIST experiments falls instead into the Domain-Incremental Learning (DIL) setting, where the model deals with a data-distribution shift, by progressively observing tasks with different permutations of the image pixels that need to be classified into ten different classes.
+
+In our experiments, we compared the performance of \our-based regularizer against two families of methods: weight-space regularization methods and function-space regularization ones.
+For the weight-space methods, we considered EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke2017continual}, and VCL~\citep{nguyen2018variational}.
+% In \cref{tbl:cl_table_1}, we considered VCL with random coresets, which uses coreset points t
+For the function-space methods, we considered DER~\citep{buzzega2020dark}, FROMP~\citep{pan2020continual}, and S-FSVI~\citep{rudner2022continual}.
+
+For our method, DER, EWC, and SI, we relied on the Mammoth framework proposed by \citep{buzzega2020dark}, while we used the available open-source codebases to conduct the experiments respectively for FROMP, S-FSVI, and VCL.
+
+For the methods relying on a stored subset of training data for each task, we make sure that the same amount of data points store are the same for each method.
+For DER, which does not select the rehearsal training samples at task boundaries, we cannot apply directly the definition of points per task ($M$), and then we set the dimension of the reservoir buffer to be $T \cdot M$, \ie, total number of tasks times the points per task.
+
+%\section{Extending the CL regularizer to multi-class settings}
+%%\label{sec:cl_multioutput}
+%\begin{equation}
+%	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{C \times m \times m} \quad \MKzz \in \R^{C \times m \times m} 
+%\end{equation}
+%
+%\begin{equation}
+%	\mathcal{R_\textit{SFR}}(\mathbf{w}) = \sum_{s=1}^{t-1}	\sum_{k \in 	C}\left[\left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s}, k}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s, k}}(\MZ_s) \right) \right]
+%\end{equation}
+
+%\subsection{Reinforcement learning experiment}
+%\label{app:rl-experiment}
 
@@
 
-\subsection{Biblatex}
-Rember when using biblatex to use 'parencite' for \citep{kamtheDataEfficient2018} and when using natbib to use 'citep'.
+%\subsection{Biblatex}
+%Rember when using biblatex to use 'parencite' for \citep{kamtheDataEfficient2018} and %when using natbib to use 'citep'.
 

### 2023-05-19 paper/main.tex
Minor
update app. cl experiments

@@
 In our experiments, we compared the performance of \our-based regularizer against two families of methods: weight-space regularization methods and function-space regularization ones.
-For the weight-space methods, we considered EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke2017continual}, and VCL~\citep{nguyen2018variational}.
+For the weight-space methods, we considered Online-EWC~\citep{schwarz2018progress}, SI~\citep{zenke2017continual}, and VCL~\citep{nguyen2018variational}.
 % In \cref{tbl:cl_table_1}, we considered VCL with random coresets, which uses coreset points t
@@
 For DER, which does not select the rehearsal training samples at task boundaries, we cannot apply directly the definition of points per task ($M$), and then we set the dimension of the reservoir buffer to be $T \cdot M$, \ie, total number of tasks times the points per task.
+
+%% Hyperparms used in the different experiments:
+\textbf{S-MNIST (40 pts./task):}
+\begin{itemize}
+	\item[-] Online-EWC: SGD, learning rate $0.03$, batch size  10, number of epochs 1, $\lambda=90$, $\gamma=1.0$.
+	\item[-] SI: SGD, learning rate 0.1, batch size 10, number of epochs 1, $c=1.0$, $\xi=0.9$.
+	\item[-] VCL (with coresets): Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
+	\item[-] DER: SGD, learning rate 0.03, batch size 10, buffer batch size 10, number epochs 1, $\alpha=0.2$, reservoir buffer size 200.
+	\item[-] FROMP: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$
+	\item[-] S-FSVI: Adam, learning rate 
+	\item[-] SFR: Adam
+\end{itemize}
+
+\textbf{S-MNIST (200 pts./task):}
+\begin{itemize}
+	\item[-] Online-EWC: SGD, learning rate $0.03$, batch size  10, number of epochs 1, $\lambda=90$, $\gamma=1.0$.
+	\item[-] SI: SGD, learning rate 0.1, batch size 10, number of epochs 1, $c=1.0$, $\xi=0.9$.
+	\item[-] VCL (with coresets): Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
+	\item[-] DER: SGD, learning rate 0.03, batch size 10, buffer batch size 10, number epochs 1, $\alpha$ 0.2, reservoir buffer size 1000.
+	\item[-] FROMP: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$
+	\item[-] S-FSVI: Adam
+	\item[-] SFR: Adam
+\end{itemize}
+
+%% Placeholders for now
+\textbf{S-FMNIST (200 pts./task):}
+\begin{itemize}
+	\item[-] Online-EWC: SGD, learning rate $0.03$, batch size  10, number of epochs 5, $\lambda=90$, $\gamma=1.0$.
+	\item[-] SI: SGD, learning rate 0.1, batch size 10, number of epochs 5, $c=1.0$, $\xi=0.9$.
+	\item[-] VCL (with coresets):
+	\item[-] DER: SGD, learning rate 0.03, batch size 10, buffer batch size 10, number epochs 5, $\alpha$ 0.2, reservoir buffer size 200.
+	\item[-] FROMP: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$
+	\item[-] S-FSVI: Adam
+	\item[-] SFR: Adam
+\end{itemize}
+
+\textbf{P-MNIST (200 pts./task):}
+\begin{itemize}
+	\item[-] Online-EWC: SGD
+	\item[-] SI: SGD 
+	\item[-] VCL (with coresets): Adam
+	\item[-] DER: SGD
+	\item[-] FROMP: Adam
+	\item[-] S-FSVI: Adam
+	\item[-] SFR: Adam
+\end{itemize}
 

### 2023-05-19 paper/main.tex
added hyperparams for CL experiments

--- 2023-05-19 paper/main.tex
@@
 	\setlength{\tabcolsep}{2pt}
-	\setlength{\tblw}{0.14\textwidth}
+	\setlength{\tblw}{0.2\textwidth}
 
@@
 For DER, which does not select the rehearsal training samples at task boundaries, we cannot apply directly the definition of points per task ($M$), and then we set the dimension of the reservoir buffer to be $T \cdot M$, \ie, total number of tasks times the points per task.
+
+The results reported in \cref{tbl:cl_table_1}, are obtained using the following hyperparameters:
+
+%% Hyperparms used in the different experiments:
+\textbf{S-MNIST (40 pts./task):}
+\begin{itemize}
+	\item[-] Online-EWC: SGD with learning rate $0.03$, batch size  10, number of epochs 1, $\lambda=90$, $\gamma=1.0$.
+	\item[-] SI: SGD with learning rate 0.1, batch size 10, number of epochs 1, $c=1.0$, $\xi=0.9$.
+	\item[-] VCL (with coresets): Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
+	\item[-] DER: SGD with learning rate 0.03, batch size 10, buffer batch size 10, number epochs 1, $\alpha=0.3$, reservoir buffer size 200.
+	\item[-] FROMP: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.
+	\item[-] S-FSVI: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 10.
+	\item[-] SFR: Adam with learning rate 0.0003, batch size=32, $\tau=1$, $\delta=0.0001$,  number of epochs 1.
+\end{itemize}
+
+\textbf{S-MNIST (200 pts./task):}
+\begin{itemize}
+	\item[-] Online-EWC: SGD with learning rate $0.03$, batch size  10, number of epochs 1, $\lambda=90$, $\gamma=1.0$.
+	\item[-] SI: SGD with learning rate 0.1, batch size 10, number of epochs 1, $c=1.0$, $\xi=0.9$.
+	\item[-] VCL (with coresets): Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
+	\item[-] DER: SGD with learning rate 0.03, batch size 10, buffer batch size 10, number epochs 1, $\alpha$ 0.2, reservoir buffer size 1000.
+	\item[-] FROMP: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.
+	\item[-] S-FSVI: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 80.
+	\item[-] SFR: Adam learning rate 0.0001, batch size=32, $\tau=0.5$, $\delta=1 \cdot 10^{-5}$, number of epochs=5.
+\end{itemize}
+
+%% Placeholders for now
+\textbf{S-FMNIST (200 pts./task):}
+\begin{itemize}
+	\item[-] Online-EWC: SGD with learning rate $0.03$, batch size  10, number of epochs 5, $\lambda=90$, $\gamma=1.0$.
+	\item[-] SI: SGD with learning rate 0.1, batch size 10, number of epochs 5, $c=1.0$, $\xi=0.9$.
+	\item[-] VCL (with coresets): Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
+	\item[-] DER: SGD with learning rate 0.03, batch size 10, buffer batch size 10, number epochs 5, $\alpha$ 0.2, reservoir buffer size 200.
+	\item[-] FROMP: Adam with learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.
+	\item[-] S-FSVI: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 60.
+	\item[-] SFR: Adam, learning rate=0.0003, batch size=32, $\tau=1.0$, $\delta=0.0001$, number of epochs=5.
+\end{itemize}
+
+\textbf{P-MNIST (200 pts./task):}
+\begin{itemize}
+	\item[-] Online-EWC: SGD with learning rate $0.1$, batch size 128, number of epochs 10, $\lambda=0.7$, $\gamma=1.0$.
+	\item[-] SI: SGD with learning rate 0.1, batch size 138, number of epochs 10, $c=0.5$, $\xi=1.0$. 
+	\item[-] VCL (with coresets): Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
+	\item[-] DER:  SGD with learning rate 0.01, batch size 128, buffer batch size 128, number epochs 10, $\alpha=0.3$, reservoir buffer size 2000.
+	\item[-] FROMP: Adam with learning rate $1 \cdot 10^{-3}$, batch size 128, number of epochs 10, $\tau = 0.5$, lambda descend selection for memorable points.
+	\item[-] S-FSVI: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 10.
+	\item[-] SFR: Adam learning 0.0003, batch size=64, $\tau=1.0$, $\delta=0.0001$. 
+\end{itemize}
+
+In addition the ablation experiments for SFR, we used the same hyperparameters reported for the full approach.
 

### 2023-05-19 paper/main.tex
first draft multi-class notation for cl

@@
 \newcommand{\MKzz}{\mbf{K}_{\mbf{z}\mbf{z}}}
+\newcommand{\MKzzc}{\mbf{K}_{\mbf{z}\mbf{z}, c}}
 \newcommand{\MKxx}{\mbf{K}_{\mbf{x}\mbf{x}}}
@@
 \newcommand{\vkzi}{\mbf{k}_{\mbf{z}i}}
+\newcommand{\vkzic}{\mbf{k}_{\mbf{z}i,c}}
 \newcommand{\vkzs}{\mbf{k}_{\mbf{z}i}}
@@
 
-\section{\our: Sparse function-space representation of neural networks}
+\section{\our: Sparse function-space representation of neural networks}\label{sec:sfr}
 %\paragraph{GP in the dual parameters}
@@
 \subsection{Extending the CL regularizer to multi-class settings} 
-\label{sec:cl_multioutput} \todo{this sub-section was mistakenly duplicated}
+\label{sec:cl_multioutput}
+In the multi-class setting, the neural network can be seen as a function approximator that maps inputs $\vx \in \inputDomain$ to  the logits $\textit{\textbf{f}} \in \outputDomain$, \ie, $f_\mathbf{w}: \inputDomain \to \outputDomain$.
+As a consequence, the Jacobian matrix is $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{C \times P}$ and the kernel of the associated sparse GP derived in \cref{sec:sfr}, $\kappa(\vx, \vx')$ is a tensor in $\R^{C \times P \times P}$.
+This means that we need compute the dual parameters and the matrix $\bar{\MB}^{-1}_{t, c}$ for all the function's outputs.
+If we denote $\kappa_c(\vx, \vx') \in \R$, as the kernel related to the $c$\textsuperscript{th} output function, \ie, the logit for class $c$, we can write the dual parameters as
+%
+\begin{equation} \textstyle
+  \valpha_{\vu, c}  =  \sum_{i=1}^N  \vkzic \, \hat{\alpha}_{i, c} \in \R^{M}
+  \quad \text{and} \quad
+  \MBeta_{\vu, c} =  \sum_{i=1}^N \vkzic \,\hat{\beta}_{i, c} \, \vkzic^{\T} \in \R^{M \times M} ,    
+\label{eq:dual_sparse}
+\end{equation}
+%
+where $\vkzic$ is the kernel $\kappa_c(\cdot, \cdot)$ computed for the inducing points $\vz \in \mathcal{Z}$ and the input point $\vx_i$ for class $c$. In this setting, the dual variables are
 \begin{equation}
-	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{C \times m \times m} \quad \MKzz \in \R^{C \times m \times m} 
+\begin{aligned}
+  \hat{\alpha}_{i,c} &\coloneqq  \left[\hat{\valpha}_{i}\right]_c = \left[\nabla_{f}\log p(y_i \mid f) |_{f=f_i} \right]_c \in \R\\
+  \hat{\beta}_{i,c} &\coloneqq \left[\textrm{diag}(\hat{\vbeta}_i)\right]_c = \left[ - \nabla^2_{ff}\log p(y_i \mid f) |_{f=f_i} \right]_c \in \R 
+\end{aligned}
 \end{equation}
-
-\begin{equation}
-	\mathcal{R_\textit{SFR}}(\mathbf{w}) = \sum_{s=1}^{t-1}	\sum_{k \in 	C}\left[\left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s}, k}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s, k}}(\MZ_s) \right) \right]
+where the operator $[ \cdot ]_c$ is taking the $c$\textsuperscript{th} element of a vector.
+In fact, in the multi-class setting $\hat{\valpha}_{i}$ is a vector in $\R^C$ and $\hat{\vbeta}_{i}$ a matrix in $\R^{C \times C}$.
+For the \our-regularizer, at the end of each task we compute the matrix $\bar{\MB}^{-1}_{t, c}$ as 
+\begin{equation}\textstyle
+ 	\bar{\MB}^{-1}_{t, c} = \MKzzc^{-1} \MBeta_{\vu, c} \MKzzc^{-1} \in \R^{M \times M}, 
+ 	\quad \text{s.t.} \quad
+ 	\MBeta_{\vu, c} =  \sum_{i \in \dataset_t} \vkzi \,\hat{\beta}_{i, c} \, \vkzi^{\T}.
+\end{equation}
+However, in practice computing the kernel $\kappa_c$ for classes $c$, for which the model has not seen any data yet is not meaningful \todo{probably better to word this differently}, so we define $\bar{\MB}^{-1}_{t, c}$ to be  $\bar{\MB}^{-1}_{t, c} = \MI_M$ $\forall c \not\in \mathcal{C}_t$, where $\mathcal{C}_t$ is the set of classes observed up to task t.
+For example, for S-MNIST  we will have after task 1 $\mathcal{C}_1 = \{0, 1\}$, then after task 2 $\mathcal{C}_1 = \{0, 1, 2, 3\}$, and so on.
+Finally, we can rewrite $\mathcal{R}_\mathrm{\our}$ as follows
+\begin{equation}\label{eq-cl-regularizer}\textstyle
+\begin{aligned}
+  \mathcal{R}_\mathrm{\our}(\weights, \mathcal{M}) = \frac{1}{2} \sum_{s=1}^{t-1} \sum_{c=1}^{C} \frac{1}{M} 
+	\left\lVert 
+	\vu_c - \vu_{s,c} % f_{\weights_{s}}(\MZ_s)
+	\right\rVert_{\bar{\MB}^{-1}_{s}}, \\
+	\text{~with~} \vu_c \in \R^M \text{~with~} u_{i, c} = \left[ f_{\weights}(\vz_{i}) \right]_c,~\forall {\vz_i} \in \mathcal{Z}_s .
+\end{aligned}
 \end{equation}

### 2023-05-19 src/figures/train_regression.py
neatended

@@ -19,10 +19,7 @@ def train(
     learning_rate: float = 1e-3,
 ):
     data_loader = torch.utils.data.DataLoader(
-        torch.utils.data.TensorDataset(*data),
-        batch_size=batch_size,
-        # collate_fn=collate_wrapper,
-        # pin_memory=True,
+        torch.utils.data.TensorDataset(*data), batch_size=batch_size
     )
 
     sfr.train()

### 2023-05-22 bnn-predictive/build/lib/preds/gps.py
moved to experiments

@@ -1,1015 +1,0 @@
-import numpy as np
-import torch.multiprocessing as mp
-import torch
-from torch import nn
-from torch.utils.data import DataLoader
-from torch.nn.utils import parameters_to_vector
-from gpytorch.lazy import DiagLazyTensor, MatmulLazyTensor, lazify
-from gpytorch.distributions import MultivariateNormal
-from opt_einsum import contract
-import warnings
-
-from collections import defaultdict
-from contextlib import contextmanager
-import itertools
-from copy import deepcopy
-
-from preds.gradients import Jacobians_gp
-
-from preds.likelihoods import BernoulliLh, CategoricalLh
-
-log2pi = np.log(2 * np.pi)
-
-
-class Parallel_replicate_jacs(nn.Module):
-    def __init__(self, J):
-        super(Parallel_replicate_jacs, self).__init__()
-        self.J = nn.Parameter(J, requires_grad=False)
-
-
-class Parallel_Jacobian(nn.Module):
-    def __init__(self, model, model_dim, output=0, method='batched'):
-        super(Parallel_Jacobian, self).__init__()
-        self.model = model
-        self.output = output
-        self.model_dim = model_dim
-        self.method = method
-
-    def forward(self, X):
-        if self.method == 'batched':
-            Js, fs = Jacobians_gp(self.model, X, self.output)
-            if fs.ndim == 1:
-                fs = fs.view(-1, 1)
-        else:
-            Js = torch.zeros(X.shape[0], self.model_dim, device=X.device)
-            fs = torch.zeros(X.shape[0], self.model.output_size, device=X.device)
-            for i in range(len(X)):
-                f = self.model(X[[i]])
-                fs[i] = f[0].detach()
-                f = f[0, self.output] if f.ndim == 2 else f[0]
-                grad = torch.autograd.grad(f, (p for p in self.model.parameters() if p.requires_grad))
-                Js[i] = torch.cat([g.flatten() for g in grad])
-
-        return Js, fs
-
-
-class Parallel_calc_kernel(nn.Module):
-    def __init__(self, opt_slices_gen, non_opt_slices_gen, n_kernel_groups, with_prior_prec=True):
-        super(Parallel_calc_kernel, self).__init__()
-        self.opt_slices_gen = opt_slices_gen
-        self.non_opt_slices_gen = non_opt_slices_gen
[…]

### 2023-05-22 bnn-predictive/build/lib/preds/laplace.py

@@ -1,207 +1,0 @@
-import numpy as np
-import torch
-from torch.nn.utils import parameters_to_vector
-from torch.distributions import Normal
-from backpack import backpack, extend
-from backpack.extensions import DiagGGNExact, KFLR
-
-from preds.optimizers import GGN
-from preds.predictives import functional_sampling_predictive, nn_sampling_predictive
-from preds.kron import Kron
-from preds.gps import gp_quantities, GP_predictive, mc_preds
-
-
-def diag_ggn(model):
-    return torch.cat([p.diag_ggn_exact.data.flatten() for p in model.parameters()])
-
-
-class Laplace:
-
-    def __init__(self, model, prior_prec, likelihood):
-        self.model = model
-        self.prior_prec = prior_prec
-        self.likelihood = likelihood
-        self.mu = None
-        self.Sigma_chol = None
-        self.device = next(model.parameters()).device
-        self.inferred = False
-        self.P = len(parameters_to_vector(model.parameters()))
-
-    def infer(self, train_loader, cov_type='full', dampen_kron=False):
-        """compute the mean and covariance matrix
-        cov_type either of ['full', 'diag', 'kron']
-        """
-        self.mu = parameters_to_vector(self.model.parameters()).detach()
-        self.model.eval()  # e.g. turn off dropout
-
-        if cov_type == 'full':
-            precision = self.expand_prior_precision(cov_type)
-            for X, y in train_loader:
-                X, y = X.to(self.device), y.to(self.device)
-                Js, Hess, rs, f = GGN(self.model, self.likelihood, X, y, ret_f=True)
-                precision += torch.einsum('mpk,mkl,mql->pq', Js, Hess, Js)
-            Chol = torch.cholesky(precision)
-            Sigma = torch.cholesky_inverse(Chol, upper=False)
-            self.Sigma_chol = torch.cholesky(Sigma, upper=False)
-
-        elif cov_type == 'diag':
-            model = extend(self.model)
-            nn_loss, hess_factor = self.likelihood.nn_loss()
-            lossfunc = extend(nn_loss)
-            precision = self.expand_prior_precision(cov_type)
-            for X, y in train_loader:
-                X, y = X.to(self.device), y.to(self.device)
-                model.zero_grad()
-                f = model(X)
-                loss = lossfunc(f, y)
-                with backpack(DiagGGNExact()):
-                    loss.backward()
[…]

### 2023-05-22 bnn-predictive/build/lib/preds/mfvi.py

@@ -1,47 +1,0 @@
-import torch
-from torch.optim import Adam
-
-from preds.models import SiBayesianMLP
-from preds.likelihoods import BernoulliLh, GaussianLh
-
-
-def preds_bbb(model, X, n_samples, likelihood):
-    gs = torch.stack([likelihood.inv_link(model(X)) for _ in range(n_samples)])
-    if type(likelihood) is GaussianLh:
-        f_mu = gs.mean(dim=0)
-        f_var = gs.var(dim=0)
-        return f_mu, f_var
-    else:
-        g_mu = gs.mean(dim=0)
-        return g_mu
-
-
-def run_bbb(ds_train, ds_test, ds_valid, prior_prec, device, likelihood, n_epochs, lr,
-            n_samples_train=10, n_samples_pred=1000, n_layers=2, n_units=50, activation='tanh'):
-    D = ds_train.data.shape[1]
-    if type(likelihood) is BernoulliLh or type(likelihood) is GaussianLh:
-        K = 1
-    else:
-        K = ds_train.C
-    model = SiBayesianMLP(D, K, n_layers, n_units, prior_prec, activation).to(device)
-    X_train, y_train = ds_train.data.to(device), ds_train.targets.to(device)
-
-    optim = Adam(model.parameters(), lr=lr)
-    losses = []
-    for i in range(n_epochs):
-        optim.zero_grad()
-        neg_log_liks = [-likelihood.log_likelihood(y_train, model(X_train))
-                        for _ in range(n_samples_train)]
-        neg_log_liks = torch.stack(neg_log_liks, dim=0)
-        exp_neg_loglik = neg_log_liks.mean()
-        loss = exp_neg_loglik + model.kl_divergence()  # negative elbo
-        loss.backward()
-        optim.step()
-        losses.append(loss.detach().item())
-
-    X_test = ds_test.data.to(device)
-    X_valid = ds_valid.data.to(device)
-    return {'preds_train': preds_bbb(model, X_train, n_samples_pred, likelihood),
-            'preds_test': preds_bbb(model, X_test, n_samples_pred, likelihood),
-            'preds_valid': preds_bbb(model, X_valid, n_samples_pred, likelihood),
-            'elbos': losses}

### 2023-05-22 experiments/__init__.py

@@ -1,0 +1,23 @@
+#!/usr/bin/env python3
+# from src.rl import *
+from src.rl import agents, models
+
+# from src.sfr import *
+# import src.rl.agents.mppi
+# import src.rl.agents.ddpg
+# import src.rl.models
+
+# from src.sl import train
+import src.sl.train
+
+# import src.sl.inference
+
+# import src.sl.datasets
+# import src.sl.networks
+
+# import src.nn2svgp.likelihoods
+
+# from .priors import *
+# from .likelihoods import *
+from .sfr import SFR, NTKSVGP
+from .nn2gp import NN2GPSubset

### 2023-05-22 experiments/sl/train.py

@@ -14,7 +14,7 @@ import src
 import torch
 import wandb
 from omegaconf import DictConfig
-from preds.datasets import CIFAR10, FMNIST, MNIST
+from experiments.sl.bnn_predictive.preds.datasets import CIFAR10, FMNIST, MNIST
 from preds.models import CIFAR10Net, CIFAR100Net, MLPS
 from src.likelihoods import BernoulliLh, CategoricalLh
 from src.sl.inference import compute_metrics

### 2023-05-22 setup.py
made annonymous

@@ -6,8 +6,8 @@ _here = pathlib.Path(__file__).resolve().parent
 print(_here)
 
 name = "src"
-author = "Aidan Scannell"
-author_email = "scannell.aidan@gmail.com"
+author = ""
+author_email = ""
 description = (
     "Sparse function-space representation (SFR) of neural networks in PyTorch."
 )
@@ -15,7 +15,7 @@ description = (
 with open(_here / "README.md", "r") as f:
     readme = f.read()
 
-url = "https://github.com/aaltoml/bnn-to-dual-svgp"
+url = ""
 
 license = "Apache-2.0"
 
@@ -52,8 +52,6 @@ install_requires = [
     "numpy==1.24.2",
     "torch==2.0.0",
     "torchvision==0.15.1",
-    "onedrivedownloader",  # from mammoth cl framework
-    "av",  #
     "torchtyping==0.1.4",
     "gpytorch==1.9.1",
     # "laplace-torch",

### 2023-05-22 experiments/__init__.py
changed src to experimsnt

@@ -1,23 +1,4 @@
 #!/usr/bin/env python3
-# from src.rl import *
-from src.rl import agents, models
-
-# from src.sfr import *
-# import src.rl.agents.mppi
-# import src.rl.agents.ddpg
-# import src.rl.models
-
-# from src.sl import train
-import src.sl.train
-
-# import src.sl.inference
-
-# import src.sl.datasets
-# import src.sl.networks
-
-# import src.nn2svgp.likelihoods
-
-# from .priors import *
-# from .likelihoods import *
-from .sfr import SFR, NTKSVGP
-from .nn2gp import NN2GPSubset
+import experiments.rl.agents
+import experiments.rl.models
+import experiments.sl.train

### 2023-05-22 paper/main.tex
removed name from import
update appendix cl

@@
 
-For our method, DER, EWC, and SI, we relied on the Mammoth framework proposed by \citep{buzzega2020dark}, while we used the available open-source codebases to conduct the experiments respectively for FROMP, S-FSVI, and VCL.
+For our method, DER, Online-EWC, and SI, we relied on the Mammoth framework proposed by \citep{buzzega2020dark}.
+On the other hand, we used the available open-source FROMP codebase to conduct the experiments with FROMP, and the S-FSVI codebase to run the experiments on S-FSVI and VCL.
+We selected the hyperparameters to use with all these methods trying to adapt the ones pointed out in the their original papers.
+For this reason, we relied on SGD for DER, Online-EWC, and SI, which requires higher learning rates, compared to the others methods for which we used Adam, \ie, our \our regularizer, FROMP, S-FSVI and VCL.
 
@@
 \begin{itemize}
-	\item[-] Online-EWC: SGD with learning rate $0.03$, batch size  10, number of epochs 1, $\lambda=90$, $\gamma=1.0$.
-	\item[-] SI: SGD with learning rate 0.1, batch size 10, number of epochs 1, $c=1.0$, $\xi=0.9$.
+	\item[-] Online-EWC: SGD, learning rate $0.03$, batch size  10, number of epochs 1, $\lambda=90$, $\gamma=1.0$.
+	\item[-] SI: SGD, learning rate 0.1, batch size 10, number of epochs 1, $c=1.0$, $\xi=0.9$.
 	\item[-] VCL (with coresets): Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
@@
 	\item[-] S-FSVI: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 10.
-	\item[-] SFR: Adam with learning rate 0.0003, batch size=32, $\tau=1$, $\delta=0.0001$,  number of epochs 1.
+	\item[-] SFR: Adam, learning rate $3 \cdot 10^{-4}$, batch size 32, $\tau=1$, $\delta=0.0001$,  number of epochs 1.
 \end{itemize}
@@
 \begin{itemize}
-	\item[-] Online-EWC: SGD with learning rate $0.03$, batch size  10, number of epochs 1, $\lambda=90$, $\gamma=1.0$.
-	\item[-] SI: SGD with learning rate 0.1, batch size 10, number of epochs 1, $c=1.0$, $\xi=0.9$.
+	\item[-] Online-EWC: SGD, learning rate $0.03$, batch size  10, number of epochs 1, $\lambda=90$, $\gamma=1.0$.
+	\item[-] SI: SGD, learning rate 0.1, batch size 10, number of epochs 1, $c=1.0$, $\xi=0.9$.
 	\item[-] VCL (with coresets): Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
-	\item[-] DER: SGD with learning rate 0.03, batch size 10, buffer batch size 10, number epochs 1, $\alpha$ 0.2, reservoir buffer size 1000.
+	\item[-] DER: SGD, learning rate 0.03, batch size 10, buffer batch size 10, number epochs 1, $\alpha$ 0.2, reservoir buffer size 1000.
 	\item[-] FROMP: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.
 	\item[-] S-FSVI: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 80.
-	\item[-] SFR: Adam learning rate 0.0001, batch size=32, $\tau=0.5$, $\delta=1 \cdot 10^{-5}$, number of epochs=5.
+	\item[-] SFR: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, $\tau=0.5$, $\delta=1 \cdot 10^{-5}$, number of epochs=5.
 \end{itemize}
@@
 \begin{itemize}
-	\item[-] Online-EWC: SGD with learning rate $0.03$, batch size  10, number of epochs 5, $\lambda=90$, $\gamma=1.0$.
-	\item[-] SI: SGD with learning rate 0.1, batch size 10, number of epochs 5, $c=1.0$, $\xi=0.9$.
-	\item[-] VCL (with coresets): Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
-	\item[-] DER: SGD with learning rate 0.03, batch size 10, buffer batch size 10, number epochs 5, $\alpha$ 0.2, reservoir buffer size 200.
-	\item[-] FROMP: Adam with learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.
+	\item[-] Online-EWC: SGD, learning rate $0.03$, batch size  10, number of epochs 5, $\lambda=90$, $\gamma=1.0$.
+	\item[-] SI: SGD, learning rate 0.1, batch size 10, number of epochs 5, $c=1.0$, $\xi=0.9$.
+	\item[-] VCL (with coresets): Adam, learning rate $1 \cdot 10^{-3}$, batch size 256, number of epochs 100, selection method for coresets random choice.
+	\item[-] DER: SGD, learning rate 0.03, batch size 10, buffer batch size 10, number epochs 5, $\alpha$ 0.2, reservoir buffer size 200.
+	\item[-] FROMP: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.
 	\item[-] S-FSVI: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 60.
-	\item[-] SFR: Adam, learning rate=0.0003, batch size=32, $\tau=1.0$, $\delta=0.0001$, number of epochs=5.
+	\item[-] SFR: Adam, learning rate $3 \cdot 10^{-4}$, batch size 32, $\tau=1.0$, $\delta=0.0001$, number of epochs=5.
 \end{itemize}
@@
 \begin{itemize}
-	\item[-] Online-EWC: SGD with learning rate $0.1$, batch size 128, number of epochs 10, $\lambda=0.7$, $\gamma=1.0$.
-	\item[-] SI: SGD with learning rate 0.1, batch size 138, number of epochs 10, $c=0.5$, $\xi=1.0$. 
+	\item[-] Online-EWC: SGD, learning rate $0.1$, batch size 128, number of epochs 10, $\lambda=0.7$, $\gamma=1.0$.
+	\item[-] SI: SGD, learning rate 0.1, batch size 138, number of epochs 10, $c=0.5$, $\xi=1.0$. 
 	\item[-] VCL (with coresets): Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
-	\item[-] DER:  SGD with learning rate 0.01, batch size 128, buffer batch size 128, number epochs 10, $\alpha=0.3$, reservoir buffer size 2000.
-	\item[-] FROMP: Adam with learning rate $1 \cdot 10^{-3}$, batch size 128, number of epochs 10, $\tau = 0.5$, lambda descend selection for memorable points.
+	\item[-] DER:  SGD, learning rate 0.01, batch size 128, buffer batch size 128, number epochs 10, $\alpha=0.3$, reservoir buffer size 2000.
+	\item[-] FROMP: Adam, learning rate $1 \cdot 10^{-3}$, batch size 128, number of epochs 10, $\tau = 0.5$, lambda descend selection for memorable points.
 	\item[-] S-FSVI: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 10.
-	\item[-] SFR: Adam learning 0.0003, batch size=64, $\tau=1.0$, $\delta=0.0001$. 
+	\item[-] SFR: Adam, learning rate $3 \cdot 10^{-4}$, batch size 64, $\tau=1.0$, $\delta=0.0001$. 
 \end{itemize}

### 2023-05-22 paper/main.tex
Sketch of UCI section

@@
 
-\subsection{Uncertainty quantification on UCI data sets}
-\label{app:uci}
+\subsection{Uncertainty quantification on UCI data sets}\label{app:uci}
+Our experiments on the $8$ selected UCI benchmarks \cite{UCI} match those presented in \cite{immer2021improving} in their structure: that is, we run the neural network training and the \our prediction pipeline on $16$ values of prior precision $\delta$, and on $10$ seeds matching those used in \cite{immer2021improving}.
+After completing the $160$ experiments, we select the $\delta$ with the lowest mean validation set NLPD and report the test set performance statistics in our result tables.
+The range of $\delta$ used for the hyperparameter search varies depending on dataset and the number of inducing points.
+Below we list the selected $\delta$ ranges
+\begin{itemize}
+\item If dataset $ = $ {\sc digits}: the $16$ $\delta$ values consist of a logspace between $10^{-1}$ and $10^2$, matching \citet{immer2021improving}.
+\item If dataset $= $ {\sc cancer},  and $M > 128$, the $16$ $\delta$ values consist of a logspace between $10^{-1}$ and $10^2$.
+With too low values of $\delta$, we observed numerical errors in the Cholesky decomposition required for constructing the \our dual.
+\item If dataset $=$ {\sc satellite} and $M < 512$: the $16$ $\delta$ values consist of a logspace between $10^{-1}$ and $10^2$, matching \citet{immer2021improving}.
+\item If dataset $=$ {\sc satellite} and $M \geq 512$: the $16$ $\delta$ values consist of a logspace between $10^{1}$ and $10^2$.
+With too low values of $\delta$, we observed numerical errors in the Cholesky decomposition required for constructing the \our dual.
+\item Othewise  the $16$ $\delta$ values consist of a logspace between $10^{-2}$ and $10^2$, matching \citet{immer2021improving}.
+\end{itemize}
+We note that while the ranges of prior precision were clipped for some data sets, the best performance in terms of NLPD was not achieved near the smallest $\delta$ tested.
+Other numerical considerations relevant to our method are the clipping of the Hessian of the log likelihood, and adding jitter before performing the Cholesky decomposition within the \our dual computation.
+In contrast to \citet{immer2021improving}, we did not perform any clipping in the Hessian computation, but some of the UCI experiments required adding jitter of size $10^{-6}$ for numerical stability.
+
+\par All neural network designs and related hyperparameters are set similarly to \citet{immer2021improving} for a fair comparison, for instance we train the $2$-layer MLPs with learning rate $0.001$ for $10000$ epochs, using the full dataset instead of batching.
+In addition, we vary the subset size $M \in  \{16, 32, 64, 128, 256, 512 \}$ to observe the impact of sparseness on the predictive performance, see \cref{tbl:uci-appendix} for the complete results.
+Our code implementation of the UCI experiments has been built on top of the code provided for \citet{immer2021improving}, using the \our methods provided in the supplementary material.
 
@@
   \centering\scriptsize
-  \caption{Negative log predictive density (NLPD) (lower better) for SVGP (sparse GP mean and variance), SVGP NN (NN mean and sparse GP variance), GP subset (subset GP mean and variance) and GP NN subset (NN mean and GP subset variance) for inducing points in $[16, 32, 64, 128, 256]$.
-}
+  \caption{Negative log predictive density (NLPD) (lower better) for \our compared to GP subset based methods which discard most of the data.} 
 	\label{tbl:uci-appendix}

### 2023-05-22 paper/main.tex
UCI table

@@
   \centering\scriptsize
-  \caption{Negative log predictive density (NLPD) (lower better) for \our compared to GP subset based methods which discard most of the data.} 
+  \caption{Negative log predictive density (NLPD, lower better) for our \our method compared to a GP subset based method which discards most of the data.
+Even with a small $M$ our method is able to provide good results.}
 	\label{tbl:uci-appendix}
@@
 	\setlength{\tabcolsep}{2pt}
-	\setlength{\tblw}{0.2\textwidth}
+	\setlength{\tblw}{0.25\textwidth}
 

### 2023-05-23 paper/main.tex
fixed small typo
Add accuracy table, stash template to uci_all_example.tex

@@
 \par All neural network designs and related hyperparameters are set similarly to \citet{immer2021improving} for a fair comparison, for instance we train the $2$-layer MLPs with learning rate $0.001$ for $10000$ epochs, using the full dataset instead of batching.
-In addition, we vary the subset size $M \in  \{16, 32, 64, 128, 256, 512 \}$ to observe the impact of sparseness on the predictive performance, see \cref{tbl:uci-appendix} for the complete results.
+In addition, we vary the subset size $M \in  \{16, 32, 64, 128, 256, 512 \}$ to observe the impact of sparseness on the predictive performance, see \cref{tbl:uci-appendix} and \cref{tbl:uci-appendic-acc} for the complete NLPD and accuracy results.
 Our code implementation of the UCI experiments has been built on top of the code provided for \citet{immer2021improving}, using the \our methods provided in the supplementary material.
@@
 	\input{tables/uci_all.tex}
+\end{table}
+
+\begin{table}[t!] 
+  \centering\scriptsize
+  \caption{The accuracy of our \our method compared to a GP subset based method which discards most of the data. Even with a small $M$ our method is able to provide good results.} 
+	\label{tbl:uci-appendix-acc}
+	% Control table spacing
+	\renewcommand{\arraystretch}{1.}
+	\setlength{\tabcolsep}{2pt}
+	\setlength{\tblw}{0.25\textwidth}
+
+	% Custom error formatting
+	\newcommand{\val}[2]{%
+		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
+	}
+
+    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
+	\input{tables/uci_all_acc.tex}
 \end{table}
@@
 	\item[-] VCL (with coresets): Adam, learning rate $1 \cdot 10^{-3}$, batch size 256, number of epochs 100, selection method for coresets random choice.
-	\item[-] DER: SGD, learning rate 0.03, batch size 10, buffer batch size 10, number epochs 5, $\alpha$ 0.2, reservoir buffer size 200.
+	\item[-] DER: SGD, learning rate 0.03, batch size 10, buffer batch size 10, number epochs 5, $\alpha =  0.2$, reservoir buffer size 200.
 	\item[-] FROMP: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.

### 2023-05-23 paper/main.tex
Modified UCI appendix tables
Fixed mistake in UCI explanation, started writing the image experiment

@@
 \subsection{Uncertainty quantification on UCI data sets}\label{app:uci}
-Our experiments on the $8$ selected UCI benchmarks \cite{UCI} match those presented in \cite{immer2021improving} in their structure: that is, we run the neural network training and the \our prediction pipeline on $16$ values of prior precision $\delta$, and on $10$ seeds matching those used in \cite{immer2021improving}.
-After completing the $160$ experiments, we select the $\delta$ with the lowest mean validation set NLPD and report the test set performance statistics in our result tables.
+Our experiments on the $8$ selected UCI benchmarks \cite{UCI} match those presented in \cite{immer2021improving} in their structure: that is, we run the neural network training and the \our prediction pipeline on $10$ values of prior precision $\delta$, and on $10$ seeds matching those used in \cite{immer2021improving}.
+After completing the $100$ experiments, we select the $\delta$ with the lowest mean validation set NLPD and report the test set performance statistics in our result tables.
 The range of $\delta$ used for the hyperparameter search varies depending on dataset and the number of inducing points.
@@
 \begin{itemize}
-\item If dataset $ = $ {\sc digits}: the $16$ $\delta$ values consist of a logspace between $10^{-1}$ and $10^2$, matching \citet{immer2021improving}.
-\item If dataset $= $ {\sc cancer},  and $M > 128$, the $16$ $\delta$ values consist of a logspace between $10^{-1}$ and $10^2$.
+\item If dataset $ = $ {\sc digits}: the $10$ $\delta$ values consist of a logspace between $10^{-1}$ and $10^2$, matching \citet{immer2021improving}.
+\item If dataset $= $ {\sc cancer},  and $M > 128$, the $10$ $\delta$ values consist of a logspace between $10^{-1}$ and $10^2$.
 With too low values of $\delta$, we observed numerical errors in the Cholesky decomposition required for constructing the \our dual.
-\item If dataset $=$ {\sc satellite} and $M < 512$: the $16$ $\delta$ values consist of a logspace between $10^{-1}$ and $10^2$, matching \citet{immer2021improving}.
-\item If dataset $=$ {\sc satellite} and $M \geq 512$: the $16$ $\delta$ values consist of a logspace between $10^{1}$ and $10^2$.
+\item If dataset $=$ {\sc satellite} and $M < 512$: the $10$ $\delta$ values consist of a logspace between $10^{-1}$ and $10^2$, matching \citet{immer2021improving}.
+\item If dataset $=$ {\sc satellite} and $M \geq 512$: the $10$ $\delta$ values consist of a logspace between $10^{1}$ and $10^2$.
 With too low values of $\delta$, we observed numerical errors in the Cholesky decomposition required for constructing the \our dual.
-\item Othewise  the $16$ $\delta$ values consist of a logspace between $10^{-2}$ and $10^2$, matching \citet{immer2021improving}.
+\item Othewise  the $10$ $\delta$ values consist of a logspace between $10^{-2}$ and $10^2$, matching \citet{immer2021improving}.
 \end{itemize}
+For each dataset, the prior precision values reported above are in practice divided by the training set size, as we use a mean loss instead of a sum loss.
+The $\delta$ values are reported here before the scaling for comparison to the implementation in \citet{immer2021improving}.
 We note that while the ranges of prior precision were clipped for some data sets, the best performance in terms of NLPD was not achieved near the smallest $\delta$ tested.
@@
 \par All neural network designs and related hyperparameters are set similarly to \citet{immer2021improving} for a fair comparison, for instance we train the $2$-layer MLPs with learning rate $0.001$ for $10000$ epochs, using the full dataset instead of batching.
-In addition, we vary the subset size $M \in  \{16, 32, 64, 128, 256, 512 \}$ to observe the impact of sparseness on the predictive performance, see \cref{tbl:uci-appendix} and \cref{tbl:uci-appendic-acc} for the complete NLPD and accuracy results.
+In addition, we vary the subset size $M \in  \{16, 32, 64, 128, 256, 512 \}$ to observe the impact of sparseness on the predictive performance, see \cref{tbl:uci-appendix} and \cref{tbl:uci-appendix-acc} for the complete NLPD and accuracy results.
 Our code implementation of the UCI experiments has been built on top of the code provided for \citet{immer2021improving}, using the \our methods provided in the supplementary material.
@@
 	\setlength{\tabcolsep}{2pt}
-	\setlength{\tblw}{0.25\textwidth}
+	\setlength{\tblw}{0.15\textwidth}
 
@@
     % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
-	\input{tables/uci_all.tex}
+	\input{tables/uci_all_nll.tex}
 \end{table}
@@
 \end{table}
+%\renewcommand{\arraystretch}{1.}
+%	\setlength{\tabcolsep}{1.2pt}
+%	\setlength{\tblw}{0.083\textwidth}
 
@@
 \label{app:image}
+Similarly to the supervised UCI benchamrk tasks, a single image experiment consist of the following steps: first, training a neural network (a MLP for MNIST, a CNN for FMNIST) in the classification task, using a prior precision $\delta$ in the regularizer term.
+This experiment set-up is then replicated for a range of prior precision values and various learning rate, as we perform a grid search over these hyperparameters by optimizing for the validation set NLPD.
+The results reported in \cref{tbl:imagesuper} used a learning rate of $10^{-4}$ and a prior precision of [INSERT VALUE].
+
+For the neural network training, we used the same set-up as in \citet{immer2021improving}, where the batch size is $512$ and the neural networks are trained for $500$ epochs.
+In contrast to the GP subset implementation in \citet{immer2021improving}, we do not perform scaling of $\delta$ after the neural network has been trained, but use the same prior precision in \our as was used in the regularizer term while training.
+Avoiding this post-hoc tuning stage allows us to forgo the additional hyperparameter optimization step for the prior precision multiplier.
 

### 2023-05-23 paper/main.tex
Writing image supervised learning appendix

@@
 \label{app:image}
-Similarly to the supervised UCI benchamrk tasks, a single image experiment consist of the following steps: first, training a neural network (a MLP for MNIST, a CNN for FMNIST) in the classification task, using a prior precision $\delta$ in the regularizer term.
-This experiment set-up is then replicated for a range of prior precision values and various learning rate, as we perform a grid search over these hyperparameters by optimizing for the validation set NLPD.
+Similarly to the supervised UCI benchmark tasks, a single image experiment consists of the following steps: first, we train a neural network (a MLP for MNIST, a CNN for FMNIST) in the classification task, using a prior precision $\delta$.
+After training, we prepare the \our method for predictions by computing the dual, and then evaluate the validation set predictive performance of \our.
+While in principle our method's predictions consist of the GP mean and variance, we include results for using the neural network prediction as a mean instead.
+For comparison, we gather the GP subset method results for both the GP and neural network means.
+This experiment set-up is then replicated for a range of prior precision values and learning rates, as we perform a grid search over these hyperparameters by optimizing for the validation set NLPD.
+We run the experiment on $5$ seeds and pick the hyperparameter by the best mean performance over the seeds.
 The results reported in \cref{tbl:imagesuper} used a learning rate of $10^{-4}$ and a prior precision of [INSERT VALUE].
 
-For the neural network training, we used the same set-up as in \citet{immer2021improving}, where the batch size is $512$ and the neural networks are trained for $500$ epochs.
+For the neural network training, we used the same set-up as in \citet{immer2021improving}, where the batch size is $512$ and the neural networks are trained for $500$ epochs, and the neural network designs were unchanged.
 In contrast to the GP subset implementation in \citet{immer2021improving}, we do not perform scaling of $\delta$ after the neural network has been trained, but use the same prior precision in \our as was used in the regularizer term while training.
 Avoiding this post-hoc tuning stage allows us to forgo the additional hyperparameter optimization step for the prior precision multiplier.
+We found the MNIST and FMNIST experiments to be numerically stable, even when not performing any clipping in computing the Hessian of the log likelihood, or adding jitter before Cholesky decomposition within the \our dual computation.
 

### 2023-05-23 paper/main.tex
rl experiments update

--- 2023-05-23 paper/main.tex
@@
 
-\section{Sparse functional model-based reinforcement learning}
+\section{\our for model-based reinforcement learning}
 \label{app:rl}
-
+In this appendix, we provide more background of reinforcement learning and how we propose to use
+\our in this setting.
+
+\textbf{Background}
 We consider environments with states \(\state \in \stateDomain \subseteq \R^{D_{\state}} \),
@@
 \end{align}
-However, we can leverage the method in \cref{sec:methods} to obtain a function-space posterior over the learned dynamics $q_{\mathbf{u}}(\hat{\transitionFn} \mid \dataset)$,
+However, we can leverage the method in \cref{sec:methods} to obtain a function-space posterior over the learned dynamics $q_{\mathbf{u}}(\transitionFn \mid \dataset)$,
 where $\mathcal{D}$ represents the state transition data set \(\mathcal{D} = \{(s_{i},a_{i}), s_{i+1}\}_{i=0}^{N}\).
@@
   \policy^{\text{PS}} &= \arg \max_{\pi \in \Pi} J(\hat{f}, \pi)
-\quad \text{s.t. } \tilde{\transitionFn} \sim q_{\mathbf{u}}(\hat{\transitionFn} \mid \dataset),
+\quad \text{s.t. } \tilde{\transitionFn} \sim q_{\mathbf{u}}({\transitionFn} \mid \dataset),
 \end{align}
-where a function $\tilde{\transitionFn}$ is sampled from the (approximate) posterior $q_{\mathbf{u}}(\hat{\transitionFn} \mid \dataset)$ and used to find a policy as
+where a function $\tilde{\transitionFn}$ is sampled from the (approximate) posterior $q_{\mathbf{u}}({\transitionFn} \mid \dataset)$ and used to find a policy as
 in \cref{eq-greedy}.
@@
 train the model.
-
-\todo{could try to implement Pathwise conditioning in function-space}
-
-Model Predictive Path Integral (MPPI) control
-\cite{panSample2015}
-\cite{williamsModel2017}
-\todo{what is correct citation for MPPI?}
-
-% \cref{alg-mbrl} shows the typical model-based RL loop.
+This strategy should perform well in environments which are hard to explore, for example, those
+with sparse rewards.
+
+\textbf{Cart pole swing up wtih sparse reward}
+We consider the cart pole swing up task in MuJoCo \cite{todorov2012mujoco}.
+However, we make exploration difficult by implementing a sparse reward function which returns $0$ unless the reward is over a threshold value. That is, our reward function is given by,
+$$\hat{r}(\state_{t}, \action_{t}) =
+\begin{cases}
+    r(\state_{t}, \action_{t}),& \text{if } r(\state_{t}, \action_{t})\geq 0.6\\
+    0,              & \text{otherwise}
+\end{cases}
+$$
+
+% \todo{could try to implement Pathwise conditioning in function-space}
+
+In practice, the policy in \cref{eq-posterior-sampling} is hard to calculate.
+It is common to approximate the infinite sum by planning over a horizon and bootstrapping with a learned value function.
+We adopt Model Predictive Path Integral (MPPI) control \cite{panSample2015,williamsModel2017}
+to plan online over a horizon $H=5$ and then bootstrap this with a learned value function.
+% \todo{what is correct citation for MPPI?}
+Our planning algorithim is then given by,
 \begin{align} \label{eq-fast-update-mpc}
@@
 \end{align}
-
-with $\hat{\transitionFn} \sim p(\transitionFn \mid \dataset)$
+where ${\transitionFn} \sim q_{\mathbf{u}}(\transitionFn \mid \dataset)$ is a sample from the
+dynamics posterior.
 
@@
 % It is worth noting that $\delta$ effects both the neur
-In all experiments our sparse function-space representation uses $m=128$ inducing points and this seemed to be sufficient.
+In all experiments our sparse function-space representation uses $m=128$ inducing points as this seemed to be sufficient.
+
+\textbf{Ensemble}
+The ensemble experiments used $5$ members where each member was an MLP with two hidden layers of width $128$ and Tanh activations.
+At each episode, the ensemble was trained for $10000$ iterations using the Adam optimiser.
+We used a learning rate $0.0001$ and a batch size of $64$.
+
+At each time step in the planning horizon we used the following procedure to sample from the ensemble.
+First, the mean and variance of the ensemble members predictions were calculated and then we
+sampled from the resulting Gaussian.
 
@@
 At each iteration $j$, $N=256$ trajectories are sampled according to the currect action trajectory $\action^{j}_{t:t+H}$.
-The $K=32$ top trajectories with highest returns $\sum_{h=0}^{H} = r(\state^{j}_{t+h}, \action^{j}_{t+h})$ are selected.
+The top $K=32$ trajectories with highest returns $\sum_{h=0}^{H} = r(\state^{j}_{t+h}, \action^{j}_{t+h})$ are selected.
 The next action trajectory $\action^{j+1}_{t:t+H}$ is then computed by taking the weighted average of the top $K=32$ trajectories
 with weights from the softmax over returns from top $K=32$ trajectories.
-
-$\gamma 0.9$
+After $J=5$ iterations the first action is executed in the environment.
+
+We used a discount factor of $\gamma 0.9$
 $\tau=0.005$
@@
 
-\textbf{DDPG}
-action value function is an MLP with a single hidden layer of width $128$ with ELU activation functions.
+\textbf{Value function learning}
+We use DDPG to learn the action value function.
+DDPG learns both a policy and a value function but we do not use the policy.
+We parameterise the value function as an MLP with two hidden layers of width $128$ with ELU activations.
+We parameterise the actor as an MLP with two hidden layers of width $128$.
 We train the DDPG agent using Adam for $500$ iterations at each episode, using a learning rate $0.0001$.
+We use a target value function to stabilise learning with a momentum of
+
+ we use a standard deviation of $0.1$ for the actor.
+we set action repeat as two.
+we use a bacth size of 512
+
+ In the DDPG experiment we use a standard deviation of $0.6$ for the actor.
 
@@
 \par All neural network designs and related hyperparameters are set similarly to \citet{immer2021improving} for a fair comparison, for instance we train the $2$-layer MLPs with learning rate $0.001$ for $10000$ epochs, using the full dataset instead of batching.
-In addition, we vary the subset size $M \in  \{16, 32, 64, 128, 256, 512 \}$ to observe the impact of sparseness on the predictive performance, see \cref{tbl:uci-appendix} and \cref{tbl:uci-appendic-acc} for the complete NLPD and accuracy results.
+In addition, we vary the subset size $M \in  \{16, 32, 64, 128, 256, 512 \}$ to observe the impact of sparseness on the predictive performance, see \cref{tbl:uci-appendix} for the complete results.
 Our code implementation of the UCI experiments has been built on top of the code provided for \citet{immer2021improving}, using the \our methods provided in the supplementary material.
@@
 	\input{tables/uci_all.tex}
-\end{table}
-
-\begin{table}[t!] 
-  \centering\scriptsize
-  \caption{The accuracy of our \our method compared to a GP subset based method which discards most of the data. Even with a small $M$ our method is able to provide good results.} 
-	\label{tbl:uci-appendix-acc}
-	% Control table spacing
-	\renewcommand{\arraystretch}{1.}
-	\setlength{\tabcolsep}{2pt}
-	\setlength{\tblw}{0.25\textwidth}
-
-	% Custom error formatting
-	\newcommand{\val}[2]{%
-		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
-	}
-
-    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
-	\input{tables/uci_all_acc.tex}
 \end{table}

### 2023-05-23 paper/main.tex
small thing

@@
 They further demonstrate that \our's predictive mean (GP) significantly outperforms the GP predictive subset.
-This is an interesting result as we cannot rely on the NN's prediction if we wish to condition on new data, using the dual conditioning from \label{sec:sequential}.
+This is an interesting result as we cannot rely on the NN's prediction if we wish to condition on new data, using the dual conditioning from \cref{sec:sequential}.
 In this setting, we must rely on our GP's predictive mean.

### 2023-05-23 paper/main.tex
Minor

@@
 
-\par All neural network designs and related hyperparameters are set similarly to \citet{immer2021improving} for a fair comparison, for instance we train the $2$-layer MLPs with learning rate $0.001$ for $10000$ epochs, using the full dataset instead of batching.
+All neural network designs and related hyperparameters are set similarly to \citet{immer2021improving} for a fair comparison, for instance we train the $2$-layer MLPs with learning rate $0.001$ for $10000$ epochs, using the full dataset instead of batching.
 In addition, we vary the subset size $M \in  \{16, 32, 64, 128, 256, 512 \}$ to observe the impact of sparseness on the predictive performance, see \cref{tbl:uci-appendix} and \cref{tbl:uci-appendix-acc} for the complete NLPD and accuracy results.
@@
   \centering\scriptsize
-  \caption{Negative log predictive density (NLPD, lower better) for our \our method compared to a GP subset based method which discards most of the data.
-Even with a small $M$ our method is able to provide good results.}
+  \caption{Complements \cref{tbl:uci} in the main paper: Negative log predictive density (NLPD, lower better) for our \our method compared to a GP subset based method which discards most of the data \cite{immer2021improving}.
+These UCI data sets (num.\ of points $N$, input dim.\ $D$, num.\ classes $C$) demonstrate that even with a small number $M$ of inducing points our method is able to capture good predictive densities.}
 	\label{tbl:uci-appendix}
@@
 	\setlength{\tabcolsep}{2pt}
-	\setlength{\tblw}{0.15\textwidth}
+	\setlength{\tblw}{0.25\textwidth}
 

### 2023-05-23 paper/main.tex
Tables

@@
   \centering\scriptsize
-  \caption{Complements \cref{tbl:uci} in the main paper: Negative log predictive density (NLPD, lower better) for our \our method compared to a GP subset based method which discards most of the data \cite{immer2021improving}.
+  \caption{Complements \cref{tbl:uci} in the main paper: Negative log predictive density (NLPD, lower better) for our \our method compared to a GP subset based method~\cite{immer2021improving} which discards most of the data.
 These UCI data sets (num.\ of points $N$, input dim.\ $D$, num.\ classes $C$) demonstrate that even with a small number $M$ of inducing points our method is able to capture good predictive densities.}
@@
   \centering\scriptsize
-  \caption{The accuracy of our \our method compared to a GP subset based method which discards most of the data. Even with a small $M$ our method is able to provide good results.} 
+  \caption{Complements \cref{tbl:uci-appendix}: We also report the accuracy for each number of inducing points $M$ for both our \our and the GP subset method.
+The differences in the accuracies is not as big as in NLPD which is not surprising as it is generally easier to capture first-order information with sparse methods.
+However, with small $M$ \our still shows clearly better performance.}
 	\label{tbl:uci-appendix-acc}

### 2023-05-23 paper/main.tex
update appendix

--- 2023-05-23 paper/main.tex
@@
 An alternative view of the dual parameters is that they parameterize approximate likelihoods, as shown in \citep{khan2017conjugate, adam2021dual}.
-Then, we can rewrite the GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
+Then, we can rewrite the {\color{red} sparse} GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
 
@@
  q(\vu) 
- 	&\propto \Norm(0, \MKzz) \prod_{i=1}^n \exp \! \left(-\frac{\tilde{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 \right) \\
+ 	&\propto \Norm(0, \MKzz) \prod_{i=1}^n \exp \! \left(-\frac{\hat{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 \right) \\
  	&= \Norm(0, \MKzz) \, \exp\left((\bar{\vy} - \vu)^\top \bar{\MSigma}^{-1}(\bar{\vy} - \vu)\right)  
@@
 Similarly to the supervised UCI benchmark tasks, a single image experiment consists of the following steps: first, we train a neural network (a MLP for MNIST, a CNN for FMNIST) in the classification task, using a prior precision $\delta$.
-After training, we prepare the \our method for predictions by computing the dual, and then evaluate the validation set predictive performance of \our.
+After training, we prepare the \our method for predictions by computing the dual parameters, and then evaluate the validation set predictive performance of \our.
 While in principle our method's predictions consist of the GP mean and variance, we include results for using the neural network prediction as a mean instead.
@@
 We run the experiment on $5$ seeds and pick the hyperparameter by the best mean performance over the seeds.
-The results reported in \cref{tbl:imagesuper} used a learning rate of $10^{-4}$ and a prior precision of [INSERT VALUE].
-
-For the neural network training, we used the same set-up as in \citet{immer2021improving}, where the batch size is $512$ and the neural networks are trained for $500$ epochs, and the neural network designs were unchanged.
+The results reported in \cref{tbl:imagesuper} used a learning rate of $10^{-4}$ and a prior precision of $\delta = 0.0013$ \todo{double check}.
+
+For the neural network training, we used the same set-up and neural network architectures as in \citet{immer2021improving}, then we trained them for $500$ epochs with batch size of $512$.
 In contrast to the GP subset implementation in \citet{immer2021improving}, we do not perform scaling of $\delta$ after the neural network has been trained, but use the same prior precision in \our as was used in the regularizer term while training.

### 2023-05-23 paper/main.tex
small thing

@@
 %
-Optionally include extra information (complete proofs, additional experiments and plots) in the appendix.
-This section will often be part of the supplemental material.
 
@@
 \subsection{Derivation of the regularizer term}
-An alternative view of the dual parameters is that they parameterize approximate likelihoods, as shown in \citep{khan2017conjugate, adam2021dual}.
-Then, we can rewrite the {\color{red} sparse} GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
-
+For continual learning, the model cannot access the training data from previous tasks, denoted here as $\dataset_\textrm{old} = \bigcup_{s=1}^{t-1} \dataset_s$, and for each new tasks receives a new chunk of data $\dataset_\textrm{new} = \dataset_t$.
+On the other hand, in the supervised learning setting (described in \cref{sec:methods}) the neural network model has access to all the training data at once, \ie, the objective we are trying to optimize is
 \begin{equation}
-\begin{aligned}
+	\weights^* = \argmin_\weights \mathcal{L}(\dataset_\textrm{old} \cup \dataset_\textrm{new}, \weights) = \argmin_\weights \sum_{i \in \dataset_\textrm{old} \cup \dataset_\textrm{new}}\ell(f_\weights(\mathbf{x}_{i}), y_i) + \delta \mathcal{R}(\weights).
+\end{equation} 
+Our goal in the continual setting is to replace the missing data coming from $\dataset_\textrm{old}$ by resorting to a functional regularizer that accounts for that by forcing the predictions of the neural networks over the inducing points $\mathcal{Z}_t$ to come with high probability from $f_\weights(\vz_i) \sim q(\vu),  \forall \vz_i \in \mathcal{Z}_t$.
+As shown in \citep{khan2017conjugate, adam2021dual}, we can view the dual parameters derived in \cref{sec:sparse-dual-gp}, as {\color{red} TODO}.
+Then, we can rewrite the sparse GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
+%
+\begin{align}
 	q(\vu)
- 	&\propto \Norm(0, \MKzz) \prod_{i=1}^n \exp \! \left(-\frac{\hat{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 \right) \\
- 	&= \Norm(0, \MKzz) \, \exp\left((\bar{\vy} - \vu)^\top \bar{\MSigma}^{-1}(\bar{\vy} - \vu)\right)  
-\end{aligned}
-\end{equation}
-
-The first normals are the approximate likelihoods where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}$,  replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$ and we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior.
-To arrive at the MVN Gaussian, we need to rearrange the quadratic terms to match the prior sufficient statistics we present a derivation in [appendix].
+	& \propto p_\weights(\vu) \Norm(\tilde{\vy}; \vu, \MB_\vu)\\
+	& \propto  \Norm(0, \MKzz) \prod_{i \in \dataset_\textrm{old}} \exp \! \left(-\frac{\hat{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 \right) \\
+	& \propto \Norm(0, \MKzz) \, \exp\left((\tilde{\vy} - \vu)^\top \bar{\MB}^{-1}(\tilde{\vy} - \vu)\right)
+\end{align}
+% The first normals are the approximate likelihoods 
+where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}_i$.
+The sparse GP posterior $q(\vu)$ is proportional to the product between the prior over the weights $p_\weights(\vu)$ and a Gaussian term $\Norm(\tilde{\vy}; \vu, \MB_\vu)$, which arises from {\color{red} TODO}
+
+Replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$, we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior.
+To arrive at the MVN Gaussian, we need to rearrange the quadratic terms to match the prior sufficient statistics.
 Performing conjugate summation of prior and likelihood, we would arrive at the sparse GP posterior at the inducing points.
@@
 \begin{equation}
-\quad \bar{\MSigma} =  \MKzz \vbeta_\vu^{-1} \MKzz \quad \bar{\vy} = \MKzz \vbeta_{\vu}\valpha_{\vu}.
+\quad \bar{\MB}^{-1} =  \MKzz \MB_\vu^{-1} \MKzz \quad \tilde{\vy} = \MKzz \MB_{\vu}\valpha_{\vu}.
 \end{equation}
 Written as above, we can see that the spare dual variables can be interpreted as a sparse MVN representation.
-We now show how we use this for a regularizer in continual learning with more details in [appendix].
 
@@
 We run the experiment on $5$ seeds and pick the hyperparameter by the best mean performance over the seeds.
-The results reported in \cref{tbl:imagesuper} used a learning rate of $10^{-4}$ and a prior precision of $\delta = 0.0013$ \todo{double check}.
+The results reported in \cref{tbl:imagesuper} used a learning rate of $10^{-4}$, and a prior precision of $\delta = 0.0013$ for FMNIST and $\delta = 0.0001$ for MNIST \todo{double check}.
 

### 2023-05-23 paper/main.tex
update app. B.1

--- 2023-05-23 paper/main.tex
@@
 
-The first normals are the approximate likelihoods where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}$,  replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$ and we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior.
-To arrive at the MVN Gaussian, we need to rearrange the quadratic terms to match the prior sufficient statistics we present a derivation in [appendix].
+% The first normals are the approximate likelihoods 
+where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}$,  replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$ and we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior.
+To arrive at the MVN Gaussian, we need to rearrange the quadratic terms to match the prior sufficient statistics.
 Performing conjugate summation of prior and likelihood, we would arrive at the sparse GP posterior at the inducing points.
@@
 \begin{equation}
-\quad \bar{\MSigma} =  \MKzz \vbeta_\vu^{-1} \MKzz \quad \bar{\vy} = \MKzz \vbeta_{\vu}\valpha_{\vu}.
+\quad \bar{\MB}^{-1} =  \MKzz \MB_\vu^{-1} \MKzz \quad \bar{\vy} = \MKzz \MB_{\vu}\valpha_{\vu}.
 \end{equation}
 Written as above, we can see that the spare dual variables can be interpreted as a sparse MVN representation.
-We now show how we use this for a regularizer in continual learning with more details in [appendix].
 

### 2023-05-23 paper/main.tex
update app. B.1

@@
  	&\propto \Norm(0, \MKzz) \prod_{i=1}^n \exp \! \left(-\frac{\hat{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 \right) \\
- 	&= \Norm(0, \MKzz) \, \exp\left((\bar{\vy} - \vu)^\top \bar{\MSigma}^{-1}(\bar{\vy} - \vu)\right)  
+ 	&= \Norm(0, \MKzz) \, \exp\left((\tilde{\vy} - \vu)^\top \bar{\MB}^{-1}(\tilde{\vy} - \vu)\right)  
 \end{aligned}
@@
 % The first normals are the approximate likelihoods 
-where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}$,  replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$ and we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior.
+where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}_i$.
+Replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$, we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior.
 To arrive at the MVN Gaussian, we need to rearrange the quadratic terms to match the prior sufficient statistics.
@@
 \begin{equation}
-\quad \bar{\MB}^{-1} =  \MKzz \MB_\vu^{-1} \MKzz \quad \bar{\vy} = \MKzz \MB_{\vu}\valpha_{\vu}.
+\quad \bar{\MB}^{-1} =  \MKzz \MB_\vu^{-1} \MKzz \quad \tilde{\vy} = \MKzz \MB_{\vu}\valpha_{\vu}.
 \end{equation}

### 2023-05-23 paper/main.tex
small thing

--- 2023-05-23 paper/main.tex
@@
 %
+Key to our method is the ability to compute the dual parameters in \cref{eq:dual_param}.
+For general exponential family likelihoods we can derive simpler expressions.
+We now detail two common losses dual parameters the Gaussian (MSE) and the Bernoulli (cross entropy).
+The general method is to rewrite the exponential family in the $\log$ of its natural form \ie:
+\begin{equation}
+ \ell(f_\weights(\mathbf{x}_{i}), y_i) = -\log p()
+\end{equation}
+
+  For the Bernoulli distribution with a given link function, typically the sigmoid, $\sigma(f_{\vw}(\vx)):= \sigma(f) = \frac{1}{1+e^f}$. Then, we can write the log probability as
+%\begin{equation}
+%\begin{aligned}
+%	\ell(y, \vf_\vw(\vx)) 
+%%	&:= - \log p(y | \sigma(f))) \\
+%%	&= -y \log(\sigma(f)) - (1-y) \log(1-\sigma(f))\\
+%%	&= -y f + \log(1+e^f) \red{ \left[ = - (\langle f, y\rangle - \log(1+e^f)) \right] }
+%\end{aligned}
+%\end{equation}
 

### 2023-05-23 paper/main.tex
wip sec. b1

@@
 %
-Key to our method is the ability to compute the dual parameters in \cref{eq:dual_param}.
-For general exponential family likelihoods we can derive simpler expressions.
-We now detail two common losses dual parameters the Gaussian (MSE) and the Bernoulli (cross entropy).
-The general method is to rewrite the exponential family in the $\log$ of its natural form \ie:
-\begin{equation}
- \ell(f_\weights(\mathbf{x}_{i}), y_i) = -\log p()
-\end{equation}
-
-  For the Bernoulli distribution with a given link function, typically the sigmoid, $\sigma(f_{\vw}(\vx)):= \sigma(f) = \frac{1}{1+e^f}$. Then, we can write the log probability as
-%\begin{equation}
-%\begin{aligned}
-%	\ell(y, \vf_\vw(\vx)) 
-%%	&:= - \log p(y | \sigma(f))) \\
-%%	&= -y \log(\sigma(f)) - (1-y) \log(1-\sigma(f))\\
-%%	&= -y f + \log(1+e^f) \red{ \left[ = - (\langle f, y\rangle - \log(1+e^f)) \right] }
-%\end{aligned}
-%\end{equation}
+Optionally include extra information (complete proofs, additional experiments and plots) in the appendix.
+This section will often be part of the supplemental material.
 

### 2023-05-23 experiments/sl/bnn_predictive/preds/mfvi.py
Moving data under uci folder, misc refactoring

@@ -1,7 +1,7 @@
 import torch
 from torch.optim import Adam
 
-from preds.models import SiBayesianMLP
+from experiments.sl.bnn_predictive.preds.models import SiBayesianMLP
 from src import BernoulliLh
 import src as ntksvgp
 

### 2023-05-23 experiments/sl/bnn_predictive/preds/optimizers.py

@@ -3,7 +3,7 @@ from torch.nn.utils import parameters_to_vector
 from torch.optim import Adam
 from torch.func import vmap
 
-from preds.gradients import Jacobians_naive
+from experiments.sl.bnn_predictive.preds.gradients import Jacobians_naive
 
 
 def GGN(model, likelihood, data, target=None, ret_f=False):

### 2023-05-23 experiments/sl/bnn_predictive/preds/predictives.py

@@ -2,12 +2,10 @@ import logging
 
 import src as ntksvgp
 import torch
-from preds.gradients import Jacobians_naive
-from preds.kron import Kron
-from preds.likelihoods import GaussianLh, get_Lams_Vys
-from preds.optimizers import GGN
-from preds.svgp import SVGPNTK
-from src import NTKSVGP
+from experiments.sl.bnn_predictive.preds.gradients import Jacobians_naive
+from experiments.sl.bnn_predictive.preds.kron import Kron
+from experiments.sl.bnn_predictive.preds.likelihoods import GaussianLh, get_Lams_Vys
+from experiments.sl.bnn_predictive.preds.optimizers import GGN
 from torch.distributions import LowRankMultivariateNormal, MultivariateNormal, Normal
 from torch.nn.utils import parameters_to_vector, vector_to_parameters
 from torch.utils.data import DataLoader, TensorDataset

### 2023-05-23 experiments/sl/bnn_predictive/preds/svgp.py

@@ -1,176 +1,0 @@
-"""SVGP class for neural networks.
-
-Current implementation does not update the duals after init!
-This class is best suited for supervised learning.
-"""
-
-import torch
-import torch.distributions as dist
-import gpytorch
-import copy
-from torch.func import vmap, jacrev, functional_call, hessian
-
-class SVGPNTK():
-
-    def __init__(self, nn_model, likelihood, data, prior_prec, n_sparse=0.25, sparse_data=None, subset=False, device='cpu'):
-        # data
-        (y, x) = data
-        self.n_classes = nn_model(x[0]).shape[-1]
-        self.nn_model = nn_model
-
-        self.y = y
-        self.x = x
-         
-        # randomly select n_sparse points
-        if sparse_data is None:
-            self.n_sparse = int(y.shape[0]*n_sparse)
-            indices = torch.randperm(y.shape[0])[:self.n_sparse]
-            self.z = x[indices]
-            sparse_y = y[indices]
-            self.z_y = sparse_y
-        else:
-            (sparse_y, sparse_x) = sparse_data
-            self.z = sparse_x
-            self.z_y = sparse_y
-
-        if subset:  # makes the subset
-            self.x = self.z 
-            self.y = sparse_y
-
-        self.n_classes = nn_model(self.x[0]).shape[-1]
-        self.delta = prior_prec
-        self.eps = 10**(-6)
-
-        # trained model and kernel type
-        self.kernel = NTK(nn_model, device)
-        self.likelihood = likelihood
-        self.device = device
-
-        # precompute the duals
-        alpha, beta = self.estimate_duals()
-        self.alpha = alpha
-        self.beta = beta
-
-    def nll(self, logits, y):
-        return -torch.mean(self.likelihood.log_likelihood(logits, y))
-
-    def get_sparse_data(self):
-        return (self.z_y, self.z)
-
-    def estimate_lambdas(self, clip_lambda=True):
-        logits_train = self.nn_model(self.x)
-        if logits_train.ndim == 1:
-            logits_train = logits_train.unsqueeze(-1)
-        hessian_fn = hessian(self.nll, argnums=0)
-       # lambdas = hessian_fn(logits_train.detach(), self.y.detach())
-        lambdas = []
[…]

### 2023-05-23 experiments/sl/uci/classification.py

@@ -7,8 +7,8 @@ from torch.nn.utils import parameters_to_vector
 
 from experiments.sl.bnn_predictive.preds.optimizers import LaplaceGGN, get_diagonal_ggn
 from experiments.sl.bnn_predictive.preds.models import SiMLP
-from src import BernoulliLh, CategoricalLh, NTKSVGP, NN2GPSubset
-import src as ntksvgp
+from src import SFR, NN2GPSubset
+import src
 
 from experiments.sl.bnn_predictive.preds.predictives import (
     nn_sampling_predictive,
@@ -16,9 +16,7 @@ from experiments.sl.bnn_predictive.preds.predictives import (
     svgp_sampling_predictive,
 )
 from experiments.sl.bnn_predictive.preds.utils import acc, nll_cls, ece
-from experiments.sl.bnn_predictive.preds.mfvi import run_bbb
-from experiments.sl.bnn_predictive.preds.refine import laplace_refine, vi_refine, vi_diag_refine
-from experiments.al.bnn_predictive.preds.datasets import UCIClassificationDatasets
+from experiments.sl.bnn_predictive.preds.datasets import UCIClassificationDatasets
 
 torch.backends.cudnn.deterministic = True
 torch.backends.cudnn.benchmark = False
@@ -27,19 +25,12 @@ torch.backends.cudnn.benchmark = False
 def train(model, likelihood, X_train, y_train, optimizer, n_epochs):
     """Train model with given optimizer and run postprocessing"""
     losses = list()
-    is_bernoulli = isinstance(likelihood, BernoulliLh)
     for i in range(n_epochs):
 
         def closure():
             model.zero_grad()
             f = model(X_train)
-            if not is_bernoulli:
-                return (
-                    likelihood.nn_loss(f=f.squeeze(), y=y_train.squeeze()),
-                    X_train.shape[0],
-                )
-            else:
-                return (
+            return (
                     likelihood.nn_loss(f=f.squeeze(), y=y_train.squeeze()),
                     X_train.shape[0],
                 )
@@ -90,7 +81,7 @@ def create_ntksvgp(
     print(f"Prior prec: {prior_prec}")
     prior = ntksvgp.priors.Gaussian(params=model.parameters, delta=prior_prec)
     if not subset:
[…]

### 2023-05-23 paper/main.tex
small thing

--- 2023-05-23 paper/main.tex
@@
 %
-Key to our method is the ability to compute the dual parameters in \cref{eq:dual_param}.
-For general exponential family likelihoods we can derive simpler expressions.
-We now detail two common losses dual parameters the Gaussian (MSE) and the Bernoulli (cross entropy).
-The general method is to rewrite the exponential family in the $\log$ of its natural form \ie:
+Key to our method is the ability to compute the dual parameters in \cref{eq:dual_param}. For general exponential family likelihoods we can derive simpler expressions:
 \begin{equation}
- \ell(f_\weights(\mathbf{x}_{i}), y_i) = -\log p()
+ \ell(\sigma(f_{i}), y_i) = -\log p(y_i \mid f_{i}) =  A(f_i)  - y_i f_i
 \end{equation}
+where $A(f_i)$ is the log partition function and $\sigma(\cdots)$ is the link function. In the
 

### 2023-05-23 paper/main.tex
small thing
add sketch table for the losses

--- 2023-05-23 paper/main.tex
@@
 
+\begin{table}[!ht]
+\centering
+\begin{tabular}{@{}ccc@{}}
+\toprule
+Loss        & der 1 & der 2 \\ \midrule
+binomial    &       &       \\
+mse         &       &       \\
+categorical &       &       \\ \bottomrule
+\end{tabular}
+\end{table}
+
 \section{\our for continual learning}
@@
 \end{equation}
-However, in practice computing the kernel $\kappa_c$ for classes $c$, for which the model has not seen any data yet is not meaningful \todo{probably better to word this differently}, so we define $\bar{\MB}^{-1}_{t, c}$ to be  $\bar{\MB}^{-1}_{t, c} = \MI_M$ $\forall c \not\in \mathcal{C}_t$, where $\mathcal{C}_t$ is the set of classes observed up to task t.
+In practice computing the kernel $\kappa_c$ for classes $c$, for which the model has not seen any data yet is not meaningful \todo{probably better to word this differently}, so we define $\bar{\MB}^{-1}_{t, c}$ to be  $\bar{\MB}^{-1}_{t, c} = \MI_M$ $\forall c \not\in \mathcal{C}_t$, where $\mathcal{C}_t$ is the set of classes observed up to task t.
 For example, for S-MNIST  we will have after task 1 $\mathcal{C}_1 = \{0, 1\}$, then after task 2 $\mathcal{C}_1 = \{0, 1, 2, 3\}$, and so on.

### 2023-05-23 paper/main.tex

@@
 %
-Optionally include extra information (complete proofs, additional experiments and plots) in the appendix.
-This section will often be part of the supplemental material.
+Key to our method is the ability to compute the dual parameters in \cref{eq:dual_param}. For general exponential family likelihoods we can derive simpler expressions:
+\begin{equation}
+ \ell(\sigma(f), y) = -\log p(y \mid f) =  A(f)  - \langle y, f\rangle
+\end{equation}
+where $A(f)$ is the log partition function and $\sigma(.)$ is the link function. Taking the first and second derivative of the loss in this form then become:
+
+ For the Bernoulli distribution with a given link function, typically the sigmoid, $\sigma(f_{\vw}(\vx)):= \sigma(f) = \frac{1}{1+e^f}$. Then, we can write the log probability as
+%\begin{equation}
+%\begin{aligned}
+%	\ell(y, \vf_\vw(\vx)) 
+%%	&:= - \log p(y | \sigma(f))) \\
+%%	&= -y \log(\sigma(f)) - (1-y) \log(1-\sigma(f))\\
+%%	&= -y f + \log(1+e^f) \red{ \left[ = - (\langle f, y\rangle - \log(1+e^f)) \right] }
+%\end{aligned}
+%\end{equation}
 

### 2023-05-23 paper/main.tex
updated image stuff

--- 2023-05-23 paper/main.tex
@@
 They further demonstrate that \our's predictive mean (GP) significantly outperforms the GP predictive subset.
-This is an interesting result as we cannot rely on the NN's prediction if we wish to condition on new data, using the dual conditioning from \cref{sec:sequential}.
+This is an interesting result as we cannot rely on the NN's prediction if we wish to condition on new data, using the dual conditioning from \label{sec:sequential}.
 In this setting, we must rely on our GP's predictive mean.
@@
 
-\begin{table}[!ht]
-\centering
-\begin{tabular}{@{}ccc@{}}
-\toprule
-Loss        & der 1 & der 2 \\ \midrule
-binomial    &       &       \\
-mse         &       &       \\
-categorical &       &       \\ \bottomrule
-\end{tabular}
-\end{table}
-
 \section{\our for continual learning}
@@
 \subsection{Derivation of the regularizer term}
-For continual learning, the model cannot access the training data from previous tasks, denoted here as $\dataset_\textrm{old} = \bigcup_{s=1}^{t-1} \dataset_s$, and for each new tasks receives a new chunk of data $\dataset_\textrm{new} = \dataset_t$.
-On the other hand, in the supervised learning setting (described in \cref{sec:methods}) the neural network model has access to all the training data at once, \ie, the objective we are trying to optimize is
+An alternative view of the dual parameters is that they parameterize approximate likelihoods, as shown in \citep{khan2017conjugate, adam2021dual}.
+Then, we can rewrite the GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
+
 \begin{equation}
-	\weights^* = \argmin_\weights \mathcal{L}(\dataset_\textrm{old} \cup \dataset_\textrm{new}, \weights) = \argmin_\weights \sum_{i \in \dataset_\textrm{old} \cup \dataset_\textrm{new}}\ell(f_\weights(\mathbf{x}_{i}), y_i) + \delta \mathcal{R}(\weights).
+\begin{aligned}
+ q(\vu) 
+ 	&\propto \Norm(0, \MKzz) \prod_{i=1}^n \exp \! \left(-\frac{\tilde{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 \right) \\
+ 	&= \Norm(0, \MKzz) \, \exp\left((\bar{\vy} - \vu)^\top \bar{\MSigma}^{-1}(\bar{\vy} - \vu)\right)  
+\end{aligned}
 \end{equation}
-Our goal in the continual setting is to replace the missing data coming from $\dataset_\textrm{old}$ by resorting to a functional regularizer that accounts for that by forcing the predictions of the neural networks over the inducing points $\mathcal{Z}_t$ to come with high probability from $f_\weights(\vz_i) \sim q(\vu),  \forall \vz_i \in \mathcal{Z}_t$.
-As shown in \citep{khan2017conjugate, adam2021dual}, we can view the dual parameters derived in \cref{sec:sparse-dual-gp}, as {\color{red} TODO}.
-Then, we can rewrite the sparse GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
-%
-\begin{align}
-	q(\vu)
-	& \propto p_\weights(\vu) \Norm(\tilde{\vy}; \vu, \MB_\vu)\\
-	& \propto  \Norm(0, \MKzz) \prod_{i \in \dataset_\textrm{old}} \exp \! \left(-\frac{\hat{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 \right) \\
-	& \propto \Norm(0, \MKzz) \, \exp\left((\tilde{\vy} - \vu)^\top \bar{\MB}^{-1}(\tilde{\vy} - \vu)\right)
-\end{align}
-% The first normals are the approximate likelihoods 
-where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}_i$.
-The sparse GP posterior $q(\vu)$ is proportional to the product between the prior over the weights $p_\weights(\vu)$ and a Gaussian term $\Norm(\tilde{\vy}; \vu, \MB_\vu)$, which arises from {\color{red} TODO}
-
-Replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$, we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior.
-To arrive at the MVN Gaussian, we need to rearrange the quadratic terms to match the prior sufficient statistics.
+
+The first normals are the approximate likelihoods where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}$,  replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$ and we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior.
+To arrive at the MVN Gaussian, we need to rearrange the quadratic terms to match the prior sufficient statistics we present a derivation in [appendix].
 Performing conjugate summation of prior and likelihood, we would arrive at the sparse GP posterior at the inducing points.
@@
 \begin{equation}
-\quad \bar{\MB}^{-1} =  \MKzz \MB_\vu^{-1} \MKzz \quad \tilde{\vy} = \MKzz \MB_{\vu}\valpha_{\vu}.
+\quad \bar{\MSigma} =  \MKzz \vbeta_\vu^{-1} \MKzz \quad \bar{\vy} = \MKzz \vbeta_{\vu}\valpha_{\vu}.
 \end{equation}
 Written as above, we can see that the spare dual variables can be interpreted as a sparse MVN representation.
+We now show how we use this for a regularizer in continual learning with more details in [appendix].
 
@@
 \end{equation}
-In practice computing the kernel $\kappa_c$ for classes $c$, for which the model has not seen any data yet is not meaningful \todo{probably better to word this differently}, so we define $\bar{\MB}^{-1}_{t, c}$ to be  $\bar{\MB}^{-1}_{t, c} = \MI_M$ $\forall c \not\in \mathcal{C}_t$, where $\mathcal{C}_t$ is the set of classes observed up to task t.
+However, in practice computing the kernel $\kappa_c$ for classes $c$, for which the model has not seen any data yet is not meaningful \todo{probably better to word this differently}, so we define $\bar{\MB}^{-1}_{t, c}$ to be  $\bar{\MB}^{-1}_{t, c} = \MI_M$ $\forall c \not\in \mathcal{C}_t$, where $\mathcal{C}_t$ is the set of classes observed up to task t.
 For example, for S-MNIST  we will have after task 1 $\mathcal{C}_1 = \{0, 1\}$, then after task 2 $\mathcal{C}_1 = \{0, 1, 2, 3\}$, and so on.
@@
 
-All neural network designs and related hyperparameters are set similarly to \citet{immer2021improving} for a fair comparison, for instance we train the $2$-layer MLPs with learning rate $0.001$ for $10000$ epochs, using the full dataset instead of batching.
+\par All neural network designs and related hyperparameters are set similarly to \citet{immer2021improving} for a fair comparison, for instance we train the $2$-layer MLPs with learning rate $0.001$ for $10000$ epochs, using the full dataset instead of batching.
 In addition, we vary the subset size $M \in  \{16, 32, 64, 128, 256, 512 \}$ to observe the impact of sparseness on the predictive performance, see \cref{tbl:uci-appendix} and \cref{tbl:uci-appendix-acc} for the complete NLPD and accuracy results.
@@
   \centering\scriptsize
-  \caption{Complements \cref{tbl:uci} in the main paper: Negative log predictive density (NLPD, lower better) for our \our method compared to a GP subset based method~\cite{immer2021improving} which discards most of the data.
-These UCI data sets (num.\ of points $N$, input dim.\ $D$, num.\ classes $C$) demonstrate that even with a small number $M$ of inducing points our method is able to capture good predictive densities.}
+  \caption{Negative log predictive density (NLPD, lower better) for our \our method compared to a GP subset based method which discards most of the data.
+Even with a small $M$ our method is able to provide good results.}
 	\label{tbl:uci-appendix}
@@
   \centering\scriptsize
-  \caption{Complements \cref{tbl:uci-appendix}: We also report the accuracy for each number of inducing points $M$ for both our \our and the GP subset method.
-The differences in the accuracies is not as big as in NLPD which is not surprising as it is generally easier to capture first-order information with sparse methods.
-However, with small $M$ \our still shows clearly better performance.}
+  \caption{The accuracy of our \our method compared to a GP subset based method which discards most of the data. Even with a small $M$ our method is able to provide good results.} 
 	\label{tbl:uci-appendix-acc}
@@
 \label{app:image}
-Similarly to the supervised UCI benchmark tasks, a single image experiment consists of the following steps: first, we train a neural network (a MLP for MNIST, a CNN for FMNIST) in the classification task, using a prior precision $\delta$.
-After training, we prepare the \our method for predictions by computing the dual parameters, and then evaluate the validation set predictive performance of \our.
-While in principle our method's predictions consist of the GP mean and variance, we include results for using the neural network prediction as a mean instead.
-For comparison, we gather the GP subset method results for both the GP and neural network means.
-This experiment set-up is then replicated for a range of prior precision values and learning rates, as we perform a grid search over these hyperparameters by optimizing for the validation set NLPD.
-We run the experiment on $5$ seeds and pick the hyperparameter by the best mean performance over the seeds.
-The results reported in \cref{tbl:imagesuper} used a learning rate of $10^{-4}$, and a prior precision of $\delta = 0.0013$ for FMNIST and $\delta = 0.0001$ for MNIST \todo{double check}.
-
-For the neural network training, we used the same set-up and neural network architectures as in \citet{immer2021improving}, then we trained them for $500$ epochs with batch size of $512$.
-In contrast to the GP subset implementation in \citet{immer2021improving}, we do not perform scaling of $\delta$ after the neural network has been trained, but use the same prior precision in \our as was used in the regularizer term while training.
-Avoiding this post-hoc tuning stage allows us to forgo the additional hyperparameter optimization step for the prior precision multiplier.
+% Each experiment with the image data sets consisted of the following steps.
+% First, we trained a neural network (MLP for MNIST, CNN for FMNIST) using a prior precision $\delta$.
+% After training, we performed inference by calculating the dual parameters.
+% Finally, we evaluated the predictive performance of \our on the validation set.
+
+For the image-based classification experiments,
+we include results using both the GP mean prediction and the NN prediction for both \our and the GP subset.
+For the neural network training, we used the same set-up as in \citet{immer2021improving},
+training the neural networok using Adam for $500$ epochs using a batch size of $512$.
+The results reported in \cref{tbl:imagesuper} used a learning rate of $10^{-4}$
+and we ran each experiment for $5$ seeds.
+The MNIST experiments used a prior precision of $\delta=0.0008$
+and the FMNIST experiments used a prior precision of $\delta=0.0013$.
+The experiments with MNIST  used an MLP with two hidden layers of width 128 and Tanh activtions.
+In the FMNIST experiments we followed \cite{immer2021improving} and used a CNN
+architecture with two fully connected classification layers and Tanh activations.
+
+In contrast to the GP subset implementation in \citet{immer2021improving},
+we do not perform scaling of $\delta$ after the neural network has been trained.
+Instead, we use the same prior precision that was used during training.
+We performeed a grid search over the prior precision for the NN MAP using the validation NLPD.
+We then used this prior precision for the GP predictive (NN) with $M=1024$,
+GP predictive with $M=1024$, SFR (NN) and SFR.
 We found the MNIST and FMNIST experiments to be numerically stable, even when not performing any clipping in computing the Hessian of the log likelihood, or adding jitter before Cholesky decomposition within the \our dual computation.

### 2023-05-23 paper/main.tex
small thing

--- 2023-05-23 paper/main.tex
@@
 Loss        & der 1 & der 2 \\ \midrule
-binomial    &       &       \\
-mse         &       &       \\
-categorical &       &       \\ \bottomrule
+Bernoulli    & $\sigma(f) - y$   & $\sigma(f)(1-\sigma(f))$      \\
+Mse         & $y - f$      & $1$       \\
+Categorical &  $\textrm{softmax}(f_i) - y_i$     &   $\begin{bmatrix}
+		p_1\\ \vdots\\p_k
+	\end{bmatrix}$,     \\ \bottomrule
 \end{tabular}

### 2023-05-23 paper/main.tex
updated rl stuff

--- 2023-05-23 paper/main.tex
@@
 \label{app:rl}
-In this appendix, we provide more background of reinforcement learning and how we propose to use
-\our in this setting.
+In this appendix, we provide more details of the reinforcement learning experiments, including
+how we used \our in this setting.
 
@@
 where $\gamma \in [0, 1)$ is a discount factor.
-In this work, we consider model-based RL where a model of the transition dynamics is learned \(f_{\mathbf{w}} \approx \transitionFn\) and then used by a planning algorithm.
+In this work, we consider model-based RL where a model of the transition dynamics is learned \(f_{\mathbf{w}^{*}} \approx \transitionFn\) and then used by a planning algorithm.
 A simple approach is to use the learned dynamic model $f_{\mathbf{w}^{*}}$ and maximise the objective in \cref{eq-model-free-objective},
@@
 \begin{align} \label{eq-posterior-sampling}
-  \policy^{\text{PS}} &= \arg \max_{\pi \in \Pi} J(\hat{f}, \pi)
+  \policy^{\text{PS}} &= \arg \max_{\pi \in \Pi} J(\tilde{f}, \pi)
 \quad \text{s.t. } \tilde{\transitionFn} \sim q_{\mathbf{u}}({\transitionFn} \mid \dataset),
@@
 
-\textbf{Cart pole swing up wtih sparse reward}
+% \todo{could try to implement Pathwise conditioning in function-space}
+
+\textbf{Algorithm}
+In practice, it is common to approximate the infinite sum in \cref{eq-posterior-sampling}
+by planning over a finite
+horizon and bootstrapping with a learned value function.
+Following this approach, our planning algorithim is given by,
+\begin{align} \label{eq-fast-update-mpc}
+  \policy^{\text{PS}}(\state) = \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
+\E \bigg[ \sum_{t=0}^{H-1} \gamma^{t} r(\state_{t},\action_{t}) \mid \state_{0}=\state  \bigg] + Q_{\theta}(\state_{\Horizon}, \action_{H})
+\quad \text{s.t. } \state_{t+1} &= \tilde{\transitionFn}(\state_{t}, \action_{t}) + \noise_{t}
+\end{align}
+where $\tilde{\transitionFn} \sim q_{\mathbf{u}}(\transitionFn \mid \dataset)$ is a sample from the
+dynamics posterior and
+${Q_{\theta}(\state, \action) \approx \E \big[ \sum_{t=0}^{H-1} \gamma^{t} r(\state_{t},\action_{t}) \mid \state_{0}=\state, \action_{0}=\action  \big]}$
+is a learned value function with parameters $\theta$.
+We use deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016} to learn the action value function $Q_{\theta}$.
+Note that we also learn a policy but its sole purpose is for learning the value function.
+
+% \todo{what is correct citation for MPPI?}
+
+\textbf{Model predictive path integral (MPPI)}
+We adopt model predictive path integral (MPPI) control \cite{panSample2015,williamsModel2017}
+to plan online over a $H$ step horizon and then bootstrap with a learned value function.
+MPPI is an online planning algorithim which iteratively improves the action trajectory $\action_{t:t+H}$ using samples.
+At each iteration $j$, $N$ trajectories are sampled according to the currect action trajectory $\action^{j}_{t:t+H}$.
+The top $K$ trajectories with highest returns $\sum_{h=0}^{H} = \gamma^{h} r(\state^{j}_{t+h}, \action^{j}_{t+h}) + \gamma Q_{\theta}(\state_{\Horizon}, \action_{H})$ are selected.
+The next action trajectory $\action^{j+1}_{t:t+H}$ is then computed by taking the weighted average of the top $K$ trajectories
+with weights from the softmax over returns from top $K$ trajectories.
+After $J$ iterations the first action is executed in the environment.
+
+\subsection{Experiment Configuration}
+This section details how we configured and ran our reinforcement learning experiments.
+
+\textbf{Environment}
 We consider the cart pole swing up task in MuJoCo \cite{todorov2012mujoco}.
@@
 $$
-
-% \todo{could try to implement Pathwise conditioning in function-space}
-
-In practice, the policy in \cref{eq-posterior-sampling} is hard to calculate.
-It is common to approximate the infinite sum by planning over a horizon and bootstrapping with a learned value function.
-We adopt Model Predictive Path Integral (MPPI) control \cite{panSample2015,williamsModel2017}
-to plan online over a horizon $H=5$ and then bootstrap this with a learned value function.
-% \todo{what is correct citation for MPPI?}
-Our planning algorithim is then given by,
-\begin{align} \label{eq-fast-update-mpc}
-  \policy_{i+1}^{\text{PS}}(\state) = \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
-\E \bigg[ \sum_{t=0}^{H-1} \gamma^{t} r(\state_{t},\action_{t}) \mid \state_{0}=\state  \bigg] + Q_{\theta}(\state_{\Horizon}, \action_{H})
-\quad \text{s.t. } \state_{t+1} &= \hat{\transitionFn}(\state_{t}, \action_{t}) + \noise_{t}
-\end{align}
-where ${\transitionFn} \sim q_{\mathbf{u}}(\transitionFn \mid \dataset)$ is a sample from the
-dynamics posterior.
-
-We use deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016} to learn an action value function $Q_{\theta}$.
-Note that we also learn a policy but its sole purpose is for learning the value function.
-
-\subsection{Experiment Configuration}
-This section details how we configured and ran our reinforcement learning experiments.
+In all experiments we collected an initial data set using a random policy for one episode and
+we set action repeat as two.
 
 \textbf{Dynamic model}
-In all experiments we used an MLP dynamic model with a single hidden layer of width 64 and TanH activation functions.
-At each episode we used Adam \cite{adam} to optimise the NN parameters for $5000$ iterations with a learning rate of $0.001$.
+In all experiments we used an MLP dynamic model with a single hidden layer of width 64 and Tanh activation functions.
+At each episode we used Adam \cite{adam} to optimise the NN parameters for $5000$ iterations with a learning rate of $0.001$ and a bacth size of $64$.
 We reset the optimizer after each episode.
@@
 % It is worth noting that $\delta$ effects both the neur
-In all experiments our sparse function-space representation uses $m=128$ inducing points as this seemed to be sufficient.
+
+\textbf{Value function learning}
+We use DDPG to learn the action value function.
+DDPG learns both a policy and a value function but we do not use the policy.
+In our experiments, we parameterised the value function as an MLP with two hidden layers of width $128$ with ELU activations and the actor as an MLP with two hidden layers of width $128$ with ELU activations.
+We train the DDPG actor/critic using Adam for $500$ iterations at each episode, using a learning rate $0.0001$ and a bacth size of $512$.
+DDPG uses a target value function to stabilise learning and for the soft target updates
+we used $\tau = 0.005$.
+DDPG is an off-policy algorithm where the exploration policy samples from a noise process.
+We sampled from a Gaussian distribution with $\sigma=0.1$ and clipping at $0.3$.
+
+\textbf{Model predictive path integral (MPPI)}
+In all model-based RL experiments we used a $H=5$ step horizon and a discount factor of $\gamma 0.9$.
+We sampled $N=256$ trajectories for $J=5$ iterations with $K=32$.
+We used a temperature of $0.5$ and momentum $0.1$.
+
+\textbf{\our}
+In the \our experiments we used $M=128$ inducing points as this seemed to be sufficient.
+The results in \cref{fig:rl} indicate that \our's uncertainty estimates are of high quality.
+This is because the agent is able to solve the task with less environment interaction, indicated
+by the cyan training curve converging quicker.
+
+\textbf{Laplace-GGN}
+In the Laplace-GGN experiments we use the Laplace library from \cite{daxberger2021laplace}
+with the full hessian structure over all of the network's weights.
+We then use the GLM predictions.
 
@@
 We used a learning rate $0.0001$ and a batch size of $64$.
-
 At each time step in the planning horizon we used the following procedure to sample from the ensemble.
@@
 
-\textbf{Model predictive path integral (MPPI)}
-MPPI is an online planning algorithim which iteratively improves the action trajectory $\action_{t:t+H}$ using samples.
-At each iteration $j$, $N=256$ trajectories are sampled according to the currect action trajectory $\action^{j}_{t:t+H}$.
-The top $K=32$ trajectories with highest returns $\sum_{h=0}^{H} = r(\state^{j}_{t+h}, \action^{j}_{t+h})$ are selected.
-The next action trajectory $\action^{j+1}_{t:t+H}$ is then computed by taking the weighted average of the top $K=32$ trajectories
-with weights from the softmax over returns from top $K=32$ trajectories.
-After $J=5$ iterations the first action is executed in the environment.
-
-We used a discount factor of $\gamma 0.9$
-$\tau=0.005$
-horizon $H=5$
-temperature $0.5$
-momentum $0.1$
-
-\textbf{Initial data set}
-We collect an initial data set using a random policy for one episode.
-
-\textbf{Value function learning}
-We use DDPG to learn the action value function.
-DDPG learns both a policy and a value function but we do not use the policy.
-We parameterise the value function as an MLP with two hidden layers of width $128$ with ELU activations.
-We parameterise the actor as an MLP with two hidden layers of width $128$.
-We train the DDPG agent using Adam for $500$ iterations at each episode, using a learning rate $0.0001$.
-We use a target value function to stabilise learning with a momentum of
-
- we use a standard deviation of $0.1$ for the actor.
-we set action repeat as two.
-we use a bacth size of 512
-
- In the DDPG experiment we use a standard deviation of $0.6$ for the actor.
+\textbf{DDPG}
+The DDPG experiment serves as our model-free baseline.
+In the DDPG experiment we use a standard deviation of $0.6$ for the actor to help it explore
+the environment.
+We increased the width of the MLPs to $512$ and we increased the discount factor to $\gamma=0.99$.
+As expected, the results show that DDPG requires a lot more environment interaction to solve the task.
+\cref{fig:rl} also shows that DDPG does not converge to the same asymptotic performance as \sfr.
+This is due to some of the random seeds not being able to successfuly explore the environment.
 

### 2023-05-23 paper/main.tex

@@
 %
-Optionally include extra information (complete proofs, additional experiments and plots) in the appendix.
-This section will often be part of the supplemental material.
+Key to our method is the ability to compute the dual parameters in \cref{eq:dual_param}. For general exponential family likelihoods we can derive simpler expressions:
+\begin{equation}
+ \ell(\sigma(f), y) = -\log p(y \mid f) =  A(f)  - \langle y, f\rangle
+\end{equation}
+where $A(f)$ is the log partition function and $\sigma(.)$ is the link function. Taking the first and second derivative of the loss in this form then become:
+
+ For the Bernoulli distribution with a given link function, typically the sigmoid, $\sigma(f_{\vw}(\vx)):= \sigma(f) = \frac{1}{1+e^f}$. Then, we can write the log probability as
+%\begin{equation}
+%\begin{aligned}
+%	\ell(y, \vf_\vw(\vx)) 
+%%	&:= - \log p(y | \sigma(f))) \\
+%%	&= -y \log(\sigma(f)) - (1-y) \log(1-\sigma(f))\\
+%%	&= -y f + \log(1+e^f) \red{ \left[ = - (\langle f, y\rangle - \log(1+e^f)) \right] }
+%\end{aligned}
+%\end{equation}
+
+\begin{table}[!ht]
+\centering
+\begin{tabular}{@{}ccc@{}}
+\toprule
+Loss        & der 1 & der 2 \\ \midrule
+Bernoulli    & $\sigma(f) - y$   & $\sigma(f)(1-\sigma(f))$      \\
+Mse         & $y - f$      & $1$       \\
+Categorical &  $\textrm{softmax}(f_i) - y_i$     &   $\begin{bmatrix}
+		p_1\\ \vdots\\p_k
+	\end{bmatrix}$,     \\ \bottomrule
+\end{tabular}
+\end{table}
 
@@
 \subsection{Derivation of the regularizer term}
-An alternative view of the dual parameters is that they parameterize approximate likelihoods, as shown in \citep{khan2017conjugate, adam2021dual}.
-Then, we can rewrite the GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
-
+For continual learning, the model cannot access the training data from previous tasks, denoted here as $\dataset_\textrm{old} = \bigcup_{s=1}^{t-1} \dataset_s$, and for each new tasks receives a new chunk of data $\dataset_\textrm{new} = \dataset_t$.
+On the other hand, in the supervised learning setting (described in \cref{sec:methods}) the neural network model has access to all the training data at once, \ie, the objective we are trying to optimize is
 \begin{equation}
-\begin{aligned}
+	\weights^* = \argmin_\weights \mathcal{L}(\dataset_\textrm{old} \cup \dataset_\textrm{new}, \weights) = \argmin_\weights \sum_{i \in \dataset_\textrm{old} \cup \dataset_\textrm{new}}\ell(f_\weights(\mathbf{x}_{i}), y_i) + \delta \mathcal{R}(\weights).
+\end{equation} 
+Our goal in the continual setting is to replace the missing data coming from $\dataset_\textrm{old}$ by resorting to a functional regularizer that accounts for that by forcing the predictions of the neural networks over the inducing points $\mathcal{Z}_t$ to come with high probability from $f_\weights(\vz_i) \sim q(\vu),  \forall \vz_i \in \mathcal{Z}_t$.
+As shown in \citep{khan2017conjugate, adam2021dual}, we can view the dual parameters derived in \cref{sec:sparse-dual-gp}, as {\color{red} TODO}.
+Then, we can rewrite the sparse GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
+%
+\begin{align}
 	q(\vu)
- 	&\propto \Norm(0, \MKzz) \prod_{i=1}^n \exp \! \left(-\frac{\tilde{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 \right) \\
- 	&= \Norm(0, \MKzz) \, \exp\left((\bar{\vy} - \vu)^\top \bar{\MSigma}^{-1}(\bar{\vy} - \vu)\right)  
-\end{aligned}
-\end{equation}
-
-The first normals are the approximate likelihoods where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}$,  replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$ and we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior.
-To arrive at the MVN Gaussian, we need to rearrange the quadratic terms to match the prior sufficient statistics we present a derivation in [appendix].
+	& \propto p_\weights(\vu) \Norm(\tilde{\vy}; \vu, \MB_\vu)\\
+	& \propto  \Norm(0, \MKzz) \prod_{i \in \dataset_\textrm{old}} \exp \! \left(-\frac{\hat{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 \right) \\
+	& \propto \Norm(0, \MKzz) \, \exp\left((\tilde{\vy} - \vu)^\top \bar{\MB}^{-1}(\tilde{\vy} - \vu)\right)
+\end{align}
+% The first normals are the approximate likelihoods 
+where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}_i$.
+The sparse GP posterior $q(\vu)$ is proportional to the product between the prior over the weights $p_\weights(\vu)$ and a Gaussian term $\Norm(\tilde{\vy}; \vu, \MB_\vu)$, which arises from {\color{red} TODO}
+
+Replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$, we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior.
+To arrive at the MVN Gaussian, we need to rearrange the quadratic terms to match the prior sufficient statistics.
 Performing conjugate summation of prior and likelihood, we would arrive at the sparse GP posterior at the inducing points.
@@
   \centering\scriptsize
-  \caption{Negative log predictive density (NLPD, lower better) for our \our method compared to a GP subset based method which discards most of the data.
-Even with a small $M$ our method is able to provide good results.}
+  \caption{Complements \cref{tbl:uci} in the main paper: Negative log predictive density (NLPD, lower better) for our \our method compared to a GP subset based method~\cite{immer2021improving} which discards most of the data.
+These UCI data sets (num.\ of points $N$, input dim.\ $D$, num.\ classes $C$) demonstrate that even with a small number $M$ of inducing points our method is able to capture good predictive densities.}
 	\label{tbl:uci-appendix}
@@
 % Finally, we evaluated the predictive performance of \our on the validation set.
+% Similarly to the supervised UCI benchmark tasks, a single image experiment consists of the following steps: first, we train a neural network (a MLP for MNIST, a CNN for FMNIST) in the classification task, using a prior precision $\delta$.
+After training, we prepare the \our method for predictions by computing the dual parameters, and then evaluate the validation set predictive performance of \our.
+While in principle our method's predictions consist of the GP mean and variance, we include results for using the neural network prediction as a mean instead.
+For comparison, we gather the GP subset method results for both the GP and neural network means.
+This experiment set-up is then replicated for a range of prior precision values and learning rates, as we perform a grid search over these hyperparameters by optimizing for the validation set NLPD.
+We run the experiment on $5$ seeds and pick the hyperparameter by the best mean performance over the seeds.
+The results reported in \cref{tbl:imagesuper} used a learning rate of $10^{-4}$, and a prior precision of $\delta = 0.0013$ for FMNIST and $\delta = 0.0001$ for MNIST \todo{double check}.
 

### 2023-05-23 paper/main.tex
fixed

@@
 DDPG learns both a policy and a value function but we do not use the policy.
-In our experiments, we parameterised the value function as an MLP with two hidden layers of width $128$ with ELU activations and the actor as an MLP with two hidden layers of width $128$ with ELU activations.
+In our experiments, we parameterised both the actor and critic as MLPs with two hidden layers of width $128$ with ELU activations.
 We train the DDPG actor/critic using Adam for $500$ iterations at each episode, using a learning rate $0.0001$ and a bacth size of $512$.
@@
 \textbf{Model predictive path integral (MPPI)}
-In all model-based RL experiments we used a $H=5$ step horizon and a discount factor of $\gamma 0.9$.
+In all model-based RL experiments we used a $H=5$ step horizon and a discount factor of $\gamma=0.9$.
 We sampled $N=256$ trajectories for $J=5$ iterations with $K=32$.
@@
 We then use the GLM predictions.
+As expected, the Laplace-GGN is also able to solve the sparse reward environment.
 
 \textbf{Ensemble}
-The ensemble experiments used $5$ members where each member was an MLP with two hidden layers of width $128$ and Tanh activations.
+The ensemble experiments used $5$ members where each member was an MLP with two hidden layers of width $128$ and Tanh activations, i.e. the same architecture as the other experiments.
 At each episode, the ensemble was trained for $10000$ iterations using the Adam optimiser.
@@
 At each time step in the planning horizon we used the following procedure to sample from the ensemble.
-First, the mean and variance of the ensemble members predictions were calculated and then we
-sampled from the resulting Gaussian.
+First, the mean and variance of the ensemble members predictions were calculated.
+Next, we sampled from the resulting Gaussian.
+\cref{fig:rl} shows that the ensemble required more environment interaction to solve the task.
+This is indicated by the green line not converging within the $50$ episodes shown in the figure.
+
+\textbf{MLP}
+As a baseline, we ran experiments using only the MLP dynamic model with no uncertainty.
+As can be seen in \cref{fig:rl}, this strategy is not always able to solve the task, indicated by
+the magenta line converging at $\approx 310$.
+This is expected because this strategy has no principled exploration mechanism.
 
@@
 As expected, the results show that DDPG requires a lot more environment interaction to solve the task.
-\cref{fig:rl} also shows that DDPG does not converge to the same asymptotic performance as \sfr.
+\cref{fig:rl} also shows that DDPG does not converge to the same asymptotic performance as \our.
 This is due to some of the random seeds not being able to successfuly explore the environment.
+
+\textbf{Summary}
+Our results motivate further experiments looking into neural network uncertainty quantification
+for model-based reinforcement learning.
+To the best of our knowledge, we are the first to leverage the Laplace-GGN for model-based RL.
+We have further demonstrated improved performance using \our.
+We believe this may be due to \our sampling in function space as opposed to weight space like
+Laplace-GGN.
 

### 2023-05-23 paper/main.tex
updated rl

@@
 
-\textbf{Background}
+\subsection{Background}
 We consider environments with states \(\state \in \stateDomain \subseteq \R^{D_{\state}} \),
@@
 
-\textbf{Algorithm}
+\subsection{Algorithm}
 In practice, it is common to approximate the infinite sum in \cref{eq-posterior-sampling}
@@
 
-\subsection{Experiment Configuration}
-This section details how we configured and ran our reinforcement learning experiments.
-
-\textbf{Environment}
+\subsection{Environment}
 We consider the cart pole swing up task in MuJoCo \cite{todorov2012mujoco}.
@@
 
+\subsection{Experiment Configuration}
+This section details how we configured and ran our reinforcement learning experiments.
+
 \textbf{Dynamic model}
@@
 In our experiments, we parameterised both the actor and critic as MLPs with two hidden layers of width $128$ with ELU activations.
-We train the DDPG actor/critic using Adam for $500$ iterations at each episode, using a learning rate $0.0001$ and a bacth size of $512$.
+We train them using Adam for $500$ iterations at each episode, using a learning rate $0.0001$ and a bacth size of $512$.
 DDPG uses a target value function to stabilise learning and for the soft target updates
@@
 We used a temperature of $0.5$ and momentum $0.1$.
+
+% \subsubsection{Experiments}
+
+\textbf{MLP}
+As a baseline, we ran experiments using only the MLP dynamic model with no uncertainty.
+As can be seen in \cref{fig:rl}, this strategy is not always able to solve the task, indicated by
+the magenta line converging at $\sim 310$.
+This is expected because this strategy has no principled exploration mechanism.
 
@@
 
-\textbf{MLP}
-As a baseline, we ran experiments using only the MLP dynamic model with no uncertainty.
-As can be seen in \cref{fig:rl}, this strategy is not always able to solve the task, indicated by
-the magenta line converging at $\approx 310$.
-This is expected because this strategy has no principled exploration mechanism.
-
 \textbf{DDPG}
-The DDPG experiment serves as our model-free baseline.
+The DDPG experiment serves as our model-free RL baseline.
 In the DDPG experiment we use a standard deviation of $0.6$ for the actor to help it explore
@@
 
-\textbf{Summary}
-Our results motivate further experiments looking into neural network uncertainty quantification
-for model-based reinforcement learning.
+% \textbf{Summary}
+\subsubsection{Summary}
+Our results motivate further experiments looking into NN uncertainty quantification
+for model-based RL.
 To the best of our knowledge, we are the first to leverage the Laplace-GGN for model-based RL.
-We have further demonstrated improved performance using \our.
+Our results indicate that both the Laplace approximation and \our could offer benefits over
+ensembles of NNs, which are typical in model-based RL.
+Although further experiments are required, our results indicate that \our could offer
+better uncertainty estimates for model-based RL.
 We believe this may be due to \our sampling in function space as opposed to weight space like

### 2023-05-23 paper/main.tex
WIP

--- 2023-05-23 paper/main.tex
@@
 Unlike our approach, \citet{immer2021improving} employ a subset of the data points to construct a sparse GP, reducing computational complexity.
-However, the method could be considered less principled for building a sparse model, as it ignores contribution from the complete dataset.
+However, the method could be considered less principled for building a sparse model, as it ignores contribution from the complete data set.
 It is important to note that the sparsifying process is independent of the approximate inference technique because the dual variables of \cref{eq:dual_param} are computed using \cref{eq-empirical-risk} and a Laplace approximation.
@@
 \begin{equation}
-	\weights^* = \argmin_\weights \mathcal{L}(\dataset_\textrm{old} \cup \dataset_\textrm{new}, \weights) = \argmin_\weights \sum_{i \in \dataset_\textrm{old} \cup \dataset_\textrm{new}}\ell(f_\weights(\mathbf{x}_{i}), y_i) + \delta \mathcal{R}(\weights).
+	\weights^* = \arg \min_\weights \mathcal{L}(\dataset_\textrm{old} \cup \dataset_\textrm{new}, \weights) = \arg \min_\weights \sum_{i \in \dataset_\textrm{old} \cup \dataset_\textrm{new}}\ell(f_\weights(\mathbf{x}_{i}), y_i) + \delta \mathcal{R}(\weights).
 \end{equation} 
@@
 \label{app:experiments}
-
-\subsection{Uncertainty quantification on UCI data sets}\label{app:uci}
+%
+We provide further details for the experiments presented in the main paper.
+The illustrative examples in \cref{fig:teaser,fig:banana} include toy problems for regression and classification.
+The 1D regression problem (\cref{fig:teaser}) uses a\todo{Arno adds this.}
+
+We include Python notebooks for
+
+%For illustrative purposes, we show our approach on a 1D regression problem (\cref{fig:teaser}) and on the 2D {\sc Banana} classification task (\cref{fig:banana}).
+In \cref{fig:teaser}, we train an MLP neural network with two hidden layers (64 hidden units each, tanh activation) and pass it through \our.
+The middle panel shows the \our result on a sparse set of data examples, while the rightmost panel demonstrates fast dual conditioning on new data (from \cref{sec:sequential}).
+In \cref{fig:banana}, we use an MLP with two hidden layers (64 units, sigmoid) and compare to a HMC sampling result obtained by hamiltorch~\cite{cobb2020scaling}.
+The HMC result is more expressive, but the results are still similar in terms of quantifying the uncertainty in low-data regions.
+
+\subsection{Uncertainty quantification on UCI data sets}
+\label{app:uci}
+%
 Our experiments on the $8$ selected UCI benchmarks \cite{UCI} match those presented in \cite{immer2021improving} in their structure: that is, we run the neural network training and the \our prediction pipeline on $10$ values of prior precision $\delta$, and on $10$ seeds matching those used in \cite{immer2021improving}.
 After completing the $100$ experiments, we select the $\delta$ with the lowest mean validation set NLPD and report the test set performance statistics in our result tables.
-The range of $\delta$ used for the hyperparameter search varies depending on dataset and the number of inducing points.
+The range of $\delta$ used for the hyperparameter search varies depending on data set and the number of inducing points.
 Below we list the selected $\delta$ ranges
 \begin{itemize}
-\item If dataset $ = $ {\sc digits}: the $10$ $\delta$ values consist of a logspace between $10^{-1}$ and $10^2$, matching \citet{immer2021improving}.
-\item If dataset $= $ {\sc cancer},  and $M > 128$, the $10$ $\delta$ values consist of a logspace between $10^{-1}$ and $10^2$.
+\item {\sc digits}: the $10$ $\delta$ values consist of a logspace between $10^{-1}$ and $10^2$, matching \citet{immer2021improving}.
+\item {\sc cancer}:  and $M > 128$, the $10$ $\delta$ values consist of a logspace between $10^{-1}$ and $10^2$.
 With too low values of $\delta$, we observed numerical errors in the Cholesky decomposition required for constructing the \our dual.
-\item If dataset $=$ {\sc satellite} and $M < 512$: the $10$ $\delta$ values consist of a logspace between $10^{-1}$ and $10^2$, matching \citet{immer2021improving}.
-\item If dataset $=$ {\sc satellite} and $M \geq 512$: the $10$ $\delta$ values consist of a logspace between $10^{1}$ and $10^2$.
+\item {\sc satellite}: and $M < 512$: the $10$ $\delta$ values consist of a logspace between $10^{-1}$ and $10^2$, matching \citet{immer2021improving}.
+\item {\sc satellite}: and $M \geq 512$: the $10$ $\delta$ values consist of a logspace between $10^{1}$ and $10^2$.
 With too low values of $\delta$, we observed numerical errors in the Cholesky decomposition required for constructing the \our dual.
-\item Othewise  the $10$ $\delta$ values consist of a logspace between $10^{-2}$ and $10^2$, matching \citet{immer2021improving}.
+\item Othewise:  the $10$ $\delta$ values consist of a logspace between $10^{-2}$ and $10^2$, matching \citet{immer2021improving}.
 \end{itemize}
-For each dataset, the prior precision values reported above are in practice divided by the training set size, as we use a mean loss instead of a sum loss.
+
+For each data set, the prior precision values reported above are in practice divided by the training set size, as we use a mean loss instead of a sum loss.
 The $\delta$ values are reported here before the scaling for comparison to the implementation in \citet{immer2021improving}.
@@
 
-All neural network designs and related hyperparameters are set similarly to \citet{immer2021improving} for a fair comparison, for instance we train the $2$-layer MLPs with learning rate $0.001$ for $10000$ epochs, using the full dataset instead of batching.
+All neural network designs and related hyperparameters are set similarly to \citet{immer2021improving} for a fair comparison, for instance we train the $2$-layer MLPs with learning rate $0.001$ for 10,000 epochs, using the full data set instead of batching.
 In addition, we vary the subset size $M \in  \{16, 32, 64, 128, 256, 512 \}$ to observe the impact of sparseness on the predictive performance, see \cref{tbl:uci-appendix} and \cref{tbl:uci-appendix-acc} for the complete NLPD and accuracy results.

### 2023-05-23 paper/main.tex
App. D.1

@@
 The illustrative examples in \cref{fig:teaser,fig:banana} include toy problems for regression and classification.
-The 1D regression problem (\cref{fig:teaser}) uses a\todo{Arno adds this.}
-
-We include Python notebooks for
-
-%For illustrative purposes, we show our approach on a 1D regression problem (\cref{fig:teaser}) and on the 2D {\sc Banana} classification task (\cref{fig:banana}).
-In \cref{fig:teaser}, we train an MLP neural network with two hidden layers (64 hidden units each, tanh activation) and pass it through \our.
-The middle panel shows the \our result on a sparse set of data examples, while the rightmost panel demonstrates fast dual conditioning on new data (from \cref{sec:sequential}).
-In \cref{fig:banana}, we use an MLP with two hidden layers (64 units, sigmoid) and compare to a HMC sampling result obtained by hamiltorch~\cite{cobb2020scaling}.
-The HMC result is more expressive, but the results are still similar in terms of quantifying the uncertainty in low-data regions.
+The 1D regression problem (\cref{fig:teaser}) uses an MLP with two hidden layers (64 hidden units each, with tanh activation), whereas the 2D banana binary classification problem uses an MLP with two hidden layers (64 hidden units each, with sigmoid activation).
+Both examples use Adam as the optimizer.
+We include Python notebooks for trying out the models.
+The illustrative HMC baseline in \cref{fig:banana} (right) was implemented with the help of hamiltorch (\url{https://github.com/AdamCobb/hamiltorch}).
+We used ten chains with 10,000 samples each and remove 2000 samples as burn-in.
 
@@
 %
-Our experiments on the $8$ selected UCI benchmarks \cite{UCI} match those presented in \cite{immer2021improving} in their structure: that is, we run the neural network training and the \our prediction pipeline on $10$ values of prior precision $\delta$, and on $10$ seeds matching those used in \cite{immer2021improving}.
-After completing the $100$ experiments, we select the $\delta$ with the lowest mean validation set NLPD and report the test set performance statistics in our result tables.
+In \cref{sec:uci} in the main paper, we showed experiments on 8 UCI data sets \cite{UCI} matching those presented in \cite{immer2021improving}.
+For direct comparison, we replicate the benchmark as in \cite{immer2021improving}: for each data set, we run the neural network training and the \our prediction pipeline on 10 values of prior precision $\delta$ and 10 seeds matching those used in \cite{immer2021improving}.
+After completing these 100 runs, we select the $\delta$ with the lowest mean validation set NLPD and report the test set performance statistics in our result tables.
 The range of $\delta$ used for the hyperparameter search varies depending on data set and the number of inducing points.
-Below we list the selected $\delta$ ranges
+Below we list the selected $\delta$ ranges:
 \begin{itemize}
-\item {\sc digits}: the $10$ $\delta$ values consist of a logspace between $10^{-1}$ and $10^2$, matching \citet{immer2021improving}.
-\item {\sc cancer}:  and $M > 128$, the $10$ $\delta$ values consist of a logspace between $10^{-1}$ and $10^2$.
+\item {\sc digits}: The ten $\delta$ values are logspaced between $10^{-1}$ and $10^2$, matching \cite{immer2021improving}.
+\item {\sc cancer}: For $M > 128$, the ten $\delta$ values are logspaced between $10^{-1}$ and $10^2$.
 With too low values of $\delta$, we observed numerical errors in the Cholesky decomposition required for constructing the \our dual.
-\item {\sc satellite}: and $M < 512$: the $10$ $\delta$ values consist of a logspace between $10^{-1}$ and $10^2$, matching \citet{immer2021improving}.
-\item {\sc satellite}: and $M \geq 512$: the $10$ $\delta$ values consist of a logspace between $10^{1}$ and $10^2$.
+\item {\sc satellite}: For $M < 512$, the tend $\delta$ values are logspaced between $10^{-1}$ and $10^2$, matching \cite{immer2021improving}.
+\item {\sc satellite}: For $M \geq 512$, the ten $\delta$ values are logspaced between $10^{1}$ and $10^2$.
 With too low values of $\delta$, we observed numerical errors in the Cholesky decomposition required for constructing the \our dual.
-\item Othewise:  the $10$ $\delta$ values consist of a logspace between $10^{-2}$ and $10^2$, matching \citet{immer2021improving}.
+\item Othewise: The ten $\delta$ values are logspaced between $10^{-2}$ and $10^2$, matching \cite{immer2021improving}.
 \end{itemize}
@@
 For each data set, the prior precision values reported above are in practice divided by the training set size, as we use a mean loss instead of a sum loss.
-The $\delta$ values are reported here before the scaling for comparison to the implementation in \citet{immer2021improving}.
+The $\delta$ values are reported here before the scaling for matching with the implementation in \cite{immer2021improving}.
 We note that while the ranges of prior precision were clipped for some data sets, the best performance in terms of NLPD was not achieved near the smallest $\delta$ tested.
@@
 
-All neural network designs and related hyperparameters are set similarly to \citet{immer2021improving} for a fair comparison, for instance we train the $2$-layer MLPs with learning rate $0.001$ for 10,000 epochs, using the full data set instead of batching.
-In addition, we vary the subset size $M \in  \{16, 32, 64, 128, 256, 512 \}$ to observe the impact of sparseness on the predictive performance, see \cref{tbl:uci-appendix} and \cref{tbl:uci-appendix-acc} for the complete NLPD and accuracy results.
-Our code implementation of the UCI experiments has been built on top of the code provided for \citet{immer2021improving}, using the \our methods provided in the supplementary material.
+All neural network designs and related hyperparameters are set as in \cite{immer2021improving} for a fair comparison, for instance we train the 2-layer MLPs with learning rate $0.001$ for 10,000 epochs, using the full data set instead of batching.
+In addition, we vary the subset size $M \in  \{16, 32, 64, 128, 256, 512\}$ to observe the impact of sparseness on the predictive performance, see \cref{tbl:uci-appendix} and \cref{tbl:uci-appendix-acc} for the complete NLPD and accuracy results.
+Our code implementation of the UCI experiments has been built on top of the code provided for \cite{immer2021improving}, using the \our methods provided in the supplementary material.
 

### 2023-05-23 paper/main.tex
App. D.2

@@
 \begin{itemize}
-\item {\sc digits}: The ten $\delta$ values are logspaced between $10^{-1}$ and $10^2$, matching \cite{immer2021improving}.
+\item {\sc digits}: The ten $\delta$ values are logspaced between $10^{-1}$ and $10^2$, matching~\cite{immer2021improving}.
 \item {\sc cancer}: For $M > 128$, the ten $\delta$ values are logspaced between $10^{-1}$ and $10^2$.
 With too low values of $\delta$, we observed numerical errors in the Cholesky decomposition required for constructing the \our dual.
-\item {\sc satellite}: For $M < 512$, the tend $\delta$ values are logspaced between $10^{-1}$ and $10^2$, matching \cite{immer2021improving}.
+\item {\sc satellite}: For $M < 512$, the tend $\delta$ values are logspaced between $10^{-1}$ and $10^2$, matching~\cite{immer2021improving}.
 \item {\sc satellite}: For $M \geq 512$, the ten $\delta$ values are logspaced between $10^{1}$ and $10^2$.
 With too low values of $\delta$, we observed numerical errors in the Cholesky decomposition required for constructing the \our dual.
-\item Othewise: The ten $\delta$ values are logspaced between $10^{-2}$ and $10^2$, matching \cite{immer2021improving}.
+\item Othewise: The ten $\delta$ values are logspaced between $10^{-2}$ and $10^2$, matching~\cite{immer2021improving}.
 \end{itemize}
@@
 In addition, we vary the subset size $M \in  \{16, 32, 64, 128, 256, 512\}$ to observe the impact of sparseness on the predictive performance, see \cref{tbl:uci-appendix} and \cref{tbl:uci-appendix-acc} for the complete NLPD and accuracy results.
-Our code implementation of the UCI experiments has been built on top of the code provided for \cite{immer2021improving}, using the \our methods provided in the supplementary material.
+
+Our code implementation of the UCI experiments has been built on top of the code provided for \cite{immer2021improving}, using the \our method, and is provided in the supplementary material zip file.
 
@@
 
-For the image-based classification experiments,
-we include results using both the GP mean prediction and the NN prediction for both \our and the GP subset.
-For the neural network training, we used the same set-up as in \citet{immer2021improving},
+In \cref{sec:image} in the main paper, we included experiments on image data sets.
+For the image-based classification experiments, we include results using both the GP mean prediction and the NN prediction for both \our and the GP subset.
+For the neural network training, we used the same set-up as in \cite{immer2021improving},
 training the neural networok using Adam for $500$ epochs using a batch size of $512$.
@@
 In the FMNIST experiments we followed \cite{immer2021improving} and used a CNN
-architecture with two fully connected classification layers and Tanh activations.
+architecture with two fully connected classification layers and tanh activations.
 
@@
 We then used this prior precision for the GP predictive (NN) with $M=1024$,
-GP predictive with $M=1024$, SFR (NN) and SFR.
+GP predictive with $M=1024$, \our (NN) and \our.
 We found the MNIST and FMNIST experiments to be numerically stable, even when not performing any clipping in computing the Hessian of the log likelihood, or adding jitter before Cholesky decomposition within the \our dual computation.

### 2023-05-23 paper/main.tex
App. D.3

@@
 
-\subsection{Uncertainty quantification on UCI data sets}
+\subsection{Capturing uncertainty in UCI tasks under supervised learning}
 \label{app:uci}
@@
 
-\subsection{Uncertainty benchmarks for image data}
+\subsection{Supervised learning on image data sets}
 \label{app:image}
@@
 
-\subsection{\our for continual learning}
+\subsection{Updating the network representation in continual learning}
 \label{app:cl-exp}
-\textbf{CL Data sets}
+
+In \cref{sec:cl-exp} in the main paper, we showed how the regularizer described in \cref{sec:sequential} can be used in continual learning to retain a compact representation of the neural network.
 We conducted our experiments on three common CL data sets \cite{de2021continual, pan2020continual, rudner2022continual}:
 \begin{itemize}
-	\item[-] Split-MNIST (S-MNIST), that consists in five binary classification tasks each on pair on MNIST classes (\ie, \digit{0}~and~\digit{1}, \digit{2}~and~\digit{3}, \dots, \digit{8}~and~\digit{9});
-	\item[-] Split-FashionMNIST (S-FMNIST), composed of five binary tasks as S-MNIST, but using instead Fashion-MNIST;
-	\item[-] Permuted-MNIST (P-MNIST), that consists of ten tasks, where each one is a ten-way classification task on the entire MNIST data set, where the images' pixels are randomly permuted.
+	\item Split-MNIST (S-MNIST), that consists in five binary classification tasks each on pair on MNIST classes (\ie, \digit{0}~and~\digit{1}, \digit{2}~and~\digit{3}, \dots, \digit{8}~and~\digit{9});
+	\item Split-FashionMNIST (S-FMNIST), composed of five binary tasks as S-MNIST, but using instead Fashion-MNIST;
+	\item Permuted-MNIST (P-MNIST), that consists of ten tasks, where each one is a ten-way classification task on the entire MNIST data set, where the images' pixels are randomly permuted.
 \end{itemize}
@@
 Following \cite{pan2020continual, rudner2022continual}, we used a two-layer MLP with 256 hidden units and ReLU activations for S-MNIST and S-FMNIST and a two-layer MLP with 100 hidden units and ReLU activations for P-MNIST, to ensure consistency with the other methods.
-In our experiments we only consider the single-head setting (SH).
-This means that for S-MNIST and S-FMNIST, we are dealing with a Class-Incremental Learning (CIL) scenario, where for each task a pair of dijoint classes are presented to the model.
-The P-MNIST experiments falls instead into the Domain-Incremental Learning (DIL) setting, where the model deals with a data-distribution shift, by progressively observing tasks with different permutations of the image pixels that need to be classified into ten different classes.
-
-In our experiments, we compared the performance of \our-based regularizer against two families of methods: weight-space regularization methods and function-space regularization ones.
+In our experiments we only consider the single-head (SH) setting.
+This means that for S-MNIST and S-FMNIST, we are dealing with a \emph{Class-Incremental Learning} (CIL) scenario, where for each task a pair of dijoint classes are presented to the model.
+The P-MNIST experiments falls instead into the \emph{Domain-Incremental Learning} (DIL) setting, where the model deals with a data-distribution shift, by progressively observing tasks with different permutations of the image pixels that need to be classified into ten different classes.
+
+In our experiments, we compared the performance of the \our-based regularizer against two families of methods: weight-space regularization methods and function-space regularization ones.
 For the weight-space methods, we considered Online-EWC~\citep{schwarz2018progress}, SI~\citep{zenke2017continual}, and VCL~\citep{nguyen2018variational}.
@@
 On the other hand, we used the available open-source FROMP codebase to conduct the experiments with FROMP, and the S-FSVI codebase to run the experiments on S-FSVI and VCL.
-We selected the hyperparameters to use with all these methods trying to adapt the ones pointed out in the their original papers.
-For this reason, we relied on SGD for DER, Online-EWC, and SI, which requires higher learning rates, compared to the others methods for which we used Adam, \ie, our \our regularizer, FROMP, S-FSVI and VCL.
-
-For the methods relying on a stored subset of training data for each task, we make sure that the same amount of data points store are the same for each method.
-For DER, which does not select the rehearsal training samples at task boundaries, we cannot apply directly the definition of points per task ($M$), and then we set the dimension of the reservoir buffer to be $T \cdot M$, \ie, total number of tasks times the points per task.
-
-The results reported in \cref{tbl:cl_table_1}, are obtained using the following hyperparameters:
+We selected the hyperparameters to use with all these methods trying to adapt the ones pointed out in the their original papers and the reference implementations.
+For this reason, we relied on SGD for DER, Online-EWC, and SI, which requires higher learning rates, compared to the others methods for which we used Adam, \ie, our \our regularizer, FROMP, S-FSVI, and VCL.
+
+For the methods relying on a stored subset of training data for each task, we make sure that the number of data points stored are the same for each method.
+For DER, which does not select the rehearsal training samples at task boundaries, we cannot apply directly the definition of points per task ($M$), and thus we set the dimension of the reservoir buffer to be $T \cdot M$, \ie, total number of tasks times the points per task.
+
+The results reported in \cref{tbl:cl_table_1}, are obtained using the following hyperparameters.
+The results are in-line with what has been reported in previous work, notably even better for some of the baseline methods.
+Thus, we consider the presented results to give a realistic picture of the relative performance of the different methods, and a demonstrating a clear case for applicability of the \our approach in continual learning.
 
 %% Hyperparms used in the different experiments:
-\textbf{S-MNIST (40 pts./task):}
-\begin{itemize}
-	\item[-] Online-EWC: SGD, learning rate $0.03$, batch size  10, number of epochs 1, $\lambda=90$, $\gamma=1.0$.
-	\item[-] SI: SGD, learning rate 0.1, batch size 10, number of epochs 1, $c=1.0$, $\xi=0.9$.
-	\item[-] VCL (with coresets): Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
-	\item[-] DER: SGD with learning rate 0.03, batch size 10, buffer batch size 10, number epochs 1, $\alpha=0.3$, reservoir buffer size 200.
-	\item[-] FROMP: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.
-	\item[-] S-FSVI: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 10.
-	\item[-] SFR: Adam, learning rate $3 \cdot 10^{-4}$, batch size 32, $\tau=1$, $\delta=0.0001$,  number of epochs 1.
-\end{itemize}
-
-\textbf{S-MNIST (200 pts./task):}
-\begin{itemize}
-	\item[-] Online-EWC: SGD, learning rate $0.03$, batch size  10, number of epochs 1, $\lambda=90$, $\gamma=1.0$.
-	\item[-] SI: SGD, learning rate 0.1, batch size 10, number of epochs 1, $c=1.0$, $\xi=0.9$.
-	\item[-] VCL (with coresets): Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
-	\item[-] DER: SGD, learning rate 0.03, batch size 10, buffer batch size 10, number epochs 1, $\alpha$ 0.2, reservoir buffer size 1000.
-	\item[-] FROMP: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.
-	\item[-] S-FSVI: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 80.
-	\item[-] SFR: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, $\tau=0.5$, $\delta=1 \cdot 10^{-5}$, number of epochs=5.
-\end{itemize}
+\paragraph{S-MNIST (40 pts./task):}
+%\begin{itemize}
+	\textbf{Online-EWC}: SGD, learning rate $0.03$, batch size  10, number of epochs 1, $\lambda=90$, $\gamma=1.0$.
+	\textbf{SI}: SGD, learning rate 0.1, batch size 10, number of epochs 1, $c=1.0$, $\xi=0.9$.
+	\textbf{VCL (with coresets)}: Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
+	\textbf{DER}: SGD with learning rate 0.03, batch size 10, buffer batch size 10, number epochs 1, $\alpha=0.3$, reservoir buffer size 200.
+	\textbf{FROMP}: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.
+	\textbf{S-FSVI}: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 10.
+	\textbf{SFR}: Adam, learning rate $3 \cdot 10^{-4}$, batch size 32, $\tau=1$, $\delta=0.0001$, number of epochs 1.
+%\end{itemize}
+
+\paragraph{S-MNIST (200 pts./task):}
+%\begin{itemize}
+	\textbf{Online-EWC}: SGD, learning rate $0.03$, batch size  10, number of epochs 1, $\lambda=90$, $\gamma=1.0$.
+	\textbf{SI}: SGD, learning rate 0.1, batch size 10, number of epochs 1, $c=1.0$, $\xi=0.9$.
+	\textbf{VCL (with coresets)}: Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
+	\textbf{DER}: SGD, learning rate 0.03, batch size 10, buffer batch size 10, number epochs 1, $\alpha$ 0.2, reservoir buffer size 1000.
+	\textbf{FROMP}: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.
+	\textbf{S-FSVI}: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 80.
+	\textbf{SFR}: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, $\tau=0.5$, $\delta=1 \cdot 10^{-5}$, number of epochs 5.
+%\end{itemize}
 
 %% Placeholders for now
-\textbf{S-FMNIST (200 pts./task):}
-\begin{itemize}
-	\item[-] Online-EWC: SGD, learning rate $0.03$, batch size  10, number of epochs 5, $\lambda=90$, $\gamma=1.0$.
-	\item[-] SI: SGD, learning rate 0.1, batch size 10, number of epochs 5, $c=1.0$, $\xi=0.9$.
-	\item[-] VCL (with coresets): Adam, learning rate $1 \cdot 10^{-3}$, batch size 256, number of epochs 100, selection method for coresets random choice.
-	\item[-] DER: SGD, learning rate 0.03, batch size 10, buffer batch size 10, number epochs 5, $\alpha =  0.2$, reservoir buffer size 200.
-	\item[-] FROMP: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.
-	\item[-] S-FSVI: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 60.
-	\item[-] SFR: Adam, learning rate $3 \cdot 10^{-4}$, batch size 32, $\tau=1.0$, $\delta=0.0001$, number of epochs=5.
-\end{itemize}
-
-\textbf{P-MNIST (200 pts./task):}
-\begin{itemize}
-	\item[-] Online-EWC: SGD, learning rate $0.1$, batch size 128, number of epochs 10, $\lambda=0.7$, $\gamma=1.0$.
-	\item[-] SI: SGD, learning rate 0.1, batch size 138, number of epochs 10, $c=0.5$, $\xi=1.0$. 
-	\item[-] VCL (with coresets): Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
-	\item[-] DER:  SGD, learning rate 0.01, batch size 128, buffer batch size 128, number epochs 10, $\alpha=0.3$, reservoir buffer size 2000.
-	\item[-] FROMP: Adam, learning rate $1 \cdot 10^{-3}$, batch size 128, number of epochs 10, $\tau = 0.5$, lambda descend selection for memorable points.
-	\item[-] S-FSVI: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 10.
-	\item[-] SFR: Adam, learning rate $3 \cdot 10^{-4}$, batch size 64, $\tau=1.0$, $\delta=0.0001$. 
-\end{itemize}
-
-In addition the ablation experiments for SFR, we used the same hyperparameters reported for the full approach.
+\paragraph{S-FMNIST (200 pts./task):}
+%\begin{itemize}
+	\textbf{Online-EWC}: SGD, learning rate $0.03$, batch size  10, number of epochs 5, $\lambda=90$, $\gamma=1.0$.
+	\textbf{SI}: SGD, learning rate 0.1, batch size 10, number of epochs 5, $c=1.0$, $\xi=0.9$.
+	\textbf{VCL (with coresets)}: Adam, learning rate $1 \cdot 10^{-3}$, batch size 256, number of epochs 100, selection method for coresets random choice.
+	\textbf{DER}: SGD, learning rate 0.03, batch size 10, buffer batch size 10, number epochs 5, $\alpha =  0.2$, reservoir buffer size 200.
+	\textbf{FROMP}: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.
+	\textbf{S-FSVI}: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 60.
+	\textbf{SFR}: Adam, learning rate $3 \cdot 10^{-4}$, batch size 32, $\tau=1.0$, $\delta=0.0001$, number of epochs 5.
+%\end{itemize}
+
+\paragraph{P-MNIST (200 pts./task):}
+%\begin{itemize}
+	\textbf{Online-EWC}: SGD, learning rate $0.1$, batch size 128, number of epochs 10, $\lambda=0.7$, $\gamma=1.0$.
+	\textbf{SI}: SGD, learning rate 0.1, batch size 138, number of epochs 10, $c=0.5$, $\xi=1.0$. 
+	\textbf{VCL (with coresets)}: Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
+	\textbf{DER}:  SGD, learning rate 0.01, batch size 128, buffer batch size 128, number epochs 10, $\alpha=0.3$, reservoir buffer size 2000.
+	\textbf{FROMP}: Adam, learning rate $1 \cdot 10^{-3}$, batch size 128, number of epochs 10, $\tau = 0.5$, lambda descend selection for memorable points.
+	\textbf{S-FSVI}: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 10.
+	\textbf{SFR}: Adam, learning rate $3 \cdot 10^{-4}$, batch size 64, $\tau=1.0$, $\delta=0.0001$. 
+%\end{itemize}
+
+Additionally, for the ablation experiments for \our, we used the same hyperparameters as reported for the full approach.
 

### 2023-05-23 paper/main.tex
updates rl intro

--- 2023-05-23 paper/main.tex
@@
 Unlike our approach, \citet{immer2021improving} employ a subset of the data points to construct a sparse GP, reducing computational complexity.
-However, the method could be considered less principled for building a sparse model, as it ignores contribution from the complete data set.
+However, the method could be considered less principled for building a sparse model, as it ignores contribution from the complete dataset.
 It is important to note that the sparsifying process is independent of the approximate inference technique because the dual variables of \cref{eq:dual_param} are computed using \cref{eq-empirical-risk} and a Laplace approximation.
@@
 \begin{equation}
-	\weights^* = \arg \min_\weights \mathcal{L}(\dataset_\textrm{old} \cup \dataset_\textrm{new}, \weights) = \arg \min_\weights \sum_{i \in \dataset_\textrm{old} \cup \dataset_\textrm{new}}\ell(f_\weights(\mathbf{x}_{i}), y_i) + \delta \mathcal{R}(\weights).
+	\weights^* = \argmin_\weights \mathcal{L}(\dataset_\textrm{old} \cup \dataset_\textrm{new}, \weights) = \argmin_\weights \sum_{i \in \dataset_\textrm{old} \cup \dataset_\textrm{new}}\ell(f_\weights(\mathbf{x}_{i}), y_i) + \delta \mathcal{R}(\weights).
 \end{equation} 
@@
 \label{app:rl}
-In this appendix, we provide more details of the reinforcement learning experiments, including
+In this appendix, we provide a background of the reinforcement learning problem, details of our
+model-based RL algorithim, an overview of the cart pole swing up environment, and
+all details of our experiments configuration for reproducibility.
+
+more details of the reinforcement learning experiments, including
 how we used \our in this setting.
@@
 \label{app:experiments}
-%
-We provide further details for the experiments presented in the main paper.
-The illustrative examples in \cref{fig:teaser,fig:banana} include toy problems for regression and classification.
-The 1D regression problem (\cref{fig:teaser}) uses an MLP with two hidden layers (64 hidden units each, with tanh activation), whereas the 2D banana binary classification problem uses an MLP with two hidden layers (64 hidden units each, with sigmoid activation).
-Both examples use Adam as the optimizer.
-We include Python notebooks for trying out the models.
-The illustrative HMC baseline in \cref{fig:banana} (right) was implemented with the help of hamiltorch (\url{https://github.com/AdamCobb/hamiltorch}).
-We used ten chains with 10,000 samples each and remove 2000 samples as burn-in.
-
-\subsection{Uncertainty quantification on UCI data sets}
-\label{app:uci}
-%
-In \cref{sec:uci} in the main paper, we showed experiments on 8 UCI data sets \cite{UCI} matching those presented in \cite{immer2021improving}.
-For direct comparison, we replicate the benchmark as in \cite{immer2021improving}: for each data set, we run the neural network training and the \our prediction pipeline on 10 values of prior precision $\delta$ and 10 seeds matching those used in \cite{immer2021improving}.
-After completing these 100 runs, we select the $\delta$ with the lowest mean validation set NLPD and report the test set performance statistics in our result tables.
-The range of $\delta$ used for the hyperparameter search varies depending on data set and the number of inducing points.
-Below we list the selected $\delta$ ranges:
+
+\subsection{Uncertainty quantification on UCI data sets}\label{app:uci}
+Our experiments on the $8$ selected UCI benchmarks \cite{UCI} match those presented in \cite{immer2021improving} in their structure: that is, we run the neural network training and the \our prediction pipeline on $10$ values of prior precision $\delta$, and on $10$ seeds matching those used in \cite{immer2021improving}.
+After completing the $100$ experiments, we select the $\delta$ with the lowest mean validation set NLPD and report the test set performance statistics in our result tables.
+The range of $\delta$ used for the hyperparameter search varies depending on dataset and the number of inducing points.
+Below we list the selected $\delta$ ranges
 \begin{itemize}
-\item {\sc digits}: The ten $\delta$ values are logspaced between $10^{-1}$ and $10^2$, matching \cite{immer2021improving}.
-\item {\sc cancer}: For $M > 128$, the ten $\delta$ values are logspaced between $10^{-1}$ and $10^2$.
+\item If dataset $ = $ {\sc digits}: the $10$ $\delta$ values consist of a logspace between $10^{-1}$ and $10^2$, matching \citet{immer2021improving}.
+\item If dataset $= $ {\sc cancer},  and $M > 128$, the $10$ $\delta$ values consist of a logspace between $10^{-1}$ and $10^2$.
 With too low values of $\delta$, we observed numerical errors in the Cholesky decomposition required for constructing the \our dual.
-\item {\sc satellite}: For $M < 512$, the tend $\delta$ values are logspaced between $10^{-1}$ and $10^2$, matching \cite{immer2021improving}.
-\item {\sc satellite}: For $M \geq 512$, the ten $\delta$ values are logspaced between $10^{1}$ and $10^2$.
+\item If dataset $=$ {\sc satellite} and $M < 512$: the $10$ $\delta$ values consist of a logspace between $10^{-1}$ and $10^2$, matching \citet{immer2021improving}.
+\item If dataset $=$ {\sc satellite} and $M \geq 512$: the $10$ $\delta$ values consist of a logspace between $10^{1}$ and $10^2$.
 With too low values of $\delta$, we observed numerical errors in the Cholesky decomposition required for constructing the \our dual.
-\item Othewise: The ten $\delta$ values are logspaced between $10^{-2}$ and $10^2$, matching \cite{immer2021improving}.
+\item Othewise  the $10$ $\delta$ values consist of a logspace between $10^{-2}$ and $10^2$, matching \citet{immer2021improving}.
 \end{itemize}
-
-For each data set, the prior precision values reported above are in practice divided by the training set size, as we use a mean loss instead of a sum loss.
-The $\delta$ values are reported here before the scaling for matching with the implementation in \cite{immer2021improving}.
+For each dataset, the prior precision values reported above are in practice divided by the training set size, as we use a mean loss instead of a sum loss.
+The $\delta$ values are reported here before the scaling for comparison to the implementation in \citet{immer2021improving}.
 We note that while the ranges of prior precision were clipped for some data sets, the best performance in terms of NLPD was not achieved near the smallest $\delta$ tested.
@@
 
-All neural network designs and related hyperparameters are set as in \cite{immer2021improving} for a fair comparison, for instance we train the 2-layer MLPs with learning rate $0.001$ for 10,000 epochs, using the full data set instead of batching.
-In addition, we vary the subset size $M \in  \{16, 32, 64, 128, 256, 512\}$ to observe the impact of sparseness on the predictive performance, see \cref{tbl:uci-appendix} and \cref{tbl:uci-appendix-acc} for the complete NLPD and accuracy results.
-Our code implementation of the UCI experiments has been built on top of the code provided for \cite{immer2021improving}, using the \our methods provided in the supplementary material.
+All neural network designs and related hyperparameters are set similarly to \citet{immer2021improving} for a fair comparison, for instance we train the $2$-layer MLPs with learning rate $0.001$ for $10000$ epochs, using the full dataset instead of batching.
+In addition, we vary the subset size $M \in  \{16, 32, 64, 128, 256, 512 \}$ to observe the impact of sparseness on the predictive performance, see \cref{tbl:uci-appendix} and \cref{tbl:uci-appendix-acc} for the complete NLPD and accuracy results.
+Our code implementation of the UCI experiments has been built on top of the code provided for \citet{immer2021improving}, using the \our methods provided in the supplementary material.
 

### 2023-05-23 paper/main.tex
App. C

--- 2023-05-23 paper/main.tex
@@
 \label{app:rl}
-In this appendix, we provide more details of the reinforcement learning experiments, including
-how we used \our in this setting.
+%
+As a final experiment in the main paper in \cref{sec:rl-exp}, we provided a demonstration of combining our \our approach with model-based reinforcement learning.
+As such, this is a direct extension of the uncertainty quantification and representation capabilities already demonstrated in the supervised (and continual) learning examples in the main paper.
+However, the RL setting requires slightly more background to it and thus \cref{app:rl} has been separated out to a separate section in the appendix.
+In this appendix, we provide details of the reinforcement learning experiments, including how we used \our in this setting.
 
@@
 $\state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t}$, where  $\noise_{t}$
-is i.i.d. transition noise.
+is i.i.d.\ transition noise.
 We consider the episodic setting where the system is reset to an initial state $\state_{0}$ at each episode and we
@@
 Following this approach, our planning algorithim is given by,
-\begin{align} \label{eq-fast-update-mpc}
+\begin{equation} \label{eq-fast-update-mpc}
   \policy^{\text{PS}}(\state) = \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
-\E \bigg[ \sum_{t=0}^{H-1} \gamma^{t} r(\state_{t},\action_{t}) \mid \state_{0}=\state  \bigg] + Q_{\theta}(\state_{\Horizon}, \action_{H})
-\quad \text{s.t. } \state_{t+1} &= \tilde{\transitionFn}(\state_{t}, \action_{t}) + \noise_{t}
-\end{align}
-where $\tilde{\transitionFn} \sim q_{\mathbf{u}}(\transitionFn \mid \dataset)$ is a sample from the
-dynamics posterior and
+\E \bigg[ \sum_{t=0}^{H-1} \gamma^{t} r(\state_{t},\action_{t}) \mid \state_{0}=\state  \bigg] + Q_{\theta}(\state_{\Horizon}, \action_{H}),
+%\quad \text{s.t. } \state_{t+1} &= \tilde{\transitionFn}(\state_{t}, \action_{t}) + \noise_{t}
+\end{equation}
+such that $\state_{t+1} = \tilde{\transitionFn}(\state_{t}, \action_{t}) + \noise_{t}$, 
+where $\tilde{\transitionFn} \sim q_{\mathbf{u}}(\transitionFn \mid \dataset)$ is a sample from the dynamics posterior and
 ${Q_{\theta}(\state, \action) \approx \E \big[ \sum_{t=0}^{H-1} \gamma^{t} r(\state_{t},\action_{t}) \mid \state_{0}=\state, \action_{0}=\action  \big]}$
 is a learned value function with parameters $\theta$.
-We use deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016} to learn the action value function $Q_{\theta}$.
+We use deep deterministic policy gradient (DDPG, \cite{lillicrapContinuousControlDeep2016}) to learn the action value function $Q_{\theta}$.
 Note that we also learn a policy but its sole purpose is for learning the value function.
@@
 \subsection{Environment}
-We consider the cart pole swing up task in MuJoCo \cite{todorov2012mujoco}.
+We consider the cartpole swingup task in MuJoCo~\cite{todorov2012mujoco}.
 However, we make exploration difficult by implementing a sparse reward function which returns $0$ unless the reward is over a threshold value. That is, our reward function is given by,
@@
 $$
-In all experiments we collected an initial data set using a random policy for one episode and
-we set action repeat as two.
-
-\subsection{Experiment Configuration}
+In all experiments we collected an initial data set using a random policy for one episode and we set action repeat as two.
+
+\subsection{Experiment configuration}
+%
 This section details how we configured and ran our reinforcement learning experiments.
@@
 As a baseline, we ran experiments using only the MLP dynamic model with no uncertainty.
-As can be seen in \cref{fig:rl}, this strategy is not always able to solve the task, indicated by
-the magenta line converging at $\sim 310$.
+As can be seen in \cref{fig:rl}, this strategy is not always able to solve the task, indicated by the magenta line converging at $\sim 310$.
 This is expected because this strategy has no principled exploration mechanism.
@@
 \textbf{Ensemble}
-The ensemble experiments used $5$ members where each member was an MLP with two hidden layers of width $128$ and Tanh activations, i.e. the same architecture as the other experiments.
+The ensemble experiments used $5$ members where each member was an MLP with two hidden layers of width $128$ and Tanh activations, \ie\ the same architecture as the other experiments.
 At each episode, the ensemble was trained for $10000$ iterations using the Adam optimiser.

### 2023-05-23 paper/main.tex
updated rl intro

--- 2023-05-23 paper/main.tex
@@
 model-based RL algorithim, an overview of the cart pole swing up environment, and
-all details of our experiments configuration for reproducibility.
-
-more details of the reinforcement learning experiments, including
-how we used \our in this setting.
+all details required for reproducing our experiments.
+
+% more details of the reinforcement learning experiments, including
+% how we used \our in this setting.
 

### 2023-05-23 paper/main.tex

--- 2023-05-23 paper/main.tex
@@
 However, the RL setting requires slightly more background to it and thus \cref{app:rl} has been separated out to a separate section in the appendix.
-In this appendix, we provide details of the reinforcement learning experiments, including how we used \our in this setting.
+
+In this appendix, we provide a background of the reinforcement learning problem, details of our model-based RL algorithim, an overview of the cartpole swingup environment, and
+all details of our experiments configuration for reproducibility.
 

### 2023-05-23 paper/main.tex

--- 2023-05-23 paper/main.tex
@@
 However, the RL setting requires slightly more background to it and thus \cref{app:rl} has been separated out to a separate section in the appendix.
-In this appendix, we provide details of the reinforcement learning experiments, including how we used \our in this setting.
+
+In this appendix, we provide a background of the reinforcement learning problem, details of our
+model-based RL algorithim, an overview of the cart pole swing up environment, and
+all details required for reproducing our experiments.
+
+% more details of the reinforcement learning experiments, including
+% how we used \our in this setting.
 

### 2023-05-23 paper/main.tex
rl updates

@@
 \textbf{Laplace-GGN}
-In the Laplace-GGN experiments we use the Laplace library from \cite{daxberger2021laplace}
+In the Laplace-GGN experiments we used the Laplace library from \cite{daxberger2021laplace}
 with the full hessian structure over all of the network's weights.
-We then use the GLM predictions.
+We then used the GLM predictions.
 As expected, the Laplace-GGN is also able to solve the sparse reward environment.
@@
 \textbf{Ensemble}
-The ensemble experiments used $5$ members where each member was an MLP with two hidden layers of width $128$ and Tanh activations, \ie\ the same architecture as the other experiments.
+The ensemble experiments used $5$ members where each member was an MLP with one hidden layer of width $128$ and Tanh activations, \ie\ the same architecture as the other experiments.
 At each episode, the ensemble was trained for $10000$ iterations using the Adam optimiser.

### 2023-05-24 paper/main.tex
Minor

@@
 \begin{equation}
-\quad \bar{\MB}^{-1} =  \MKzz \MB_\vu^{-1} \MKzz \quad \tilde{\vy} = \MKzz \MB_{\vu}\valpha_{\vu}.
+\quad \bar{\MB}^{-1} =  \MKzz \MB_\vu^{-1} \MKzz \quad \text{and} \quad \tilde{\vy} = \MKzz \MB_{\vu}\valpha_{\vu}.
 \end{equation}
@@
 \label{sec:cl_multioutput}
-In the multi-class setting, the neural network can be seen as a function approximator that maps inputs $\vx \in \inputDomain$ to  the logits $\textit{\textbf{f}} \in \outputDomain$, \ie, $f_\mathbf{w}: \inputDomain \to \outputDomain$.
+%
+In a multi-class classification setting, the neural network can be seen as a function approximator that maps inputs $\vx \in \inputDomain$ to the logits $\textit{\textbf{f}} \in \outputDomain$, \ie, $f_\mathbf{w}: \inputDomain \to \outputDomain$.
 As a consequence, the Jacobian matrix is $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{C \times P}$ and the kernel of the associated sparse GP derived in \cref{sec:sfr}, $\kappa(\vx, \vx')$ is a tensor in $\R^{C \times P \times P}$.
@@
 \begin{aligned}
-  \hat{\alpha}_{i,c} &\coloneqq  \left[\hat{\valpha}_{i}\right]_c = \left[\nabla_{f}\log p(y_i \mid f) |_{f=f_i} \right]_c \in \R\\
-  \hat{\beta}_{i,c} &\coloneqq \left[\textrm{diag}(\hat{\vbeta}_i)\right]_c = \left[ - \nabla^2_{ff}\log p(y_i \mid f) |_{f=f_i} \right]_c \in \R 
+  \hat{\alpha}_{i,c} &\coloneqq  \left[\hat{\valpha}_{i}\right]_c = \left[\nabla_{f}\log p(y_i \mid f) |_{f=f_i} \right]_c \in \R,\\
+  \hat{\beta}_{i,c} &\coloneqq \left[\textrm{diag}(\hat{\vbeta}_i)\right]_c = \left[ - \nabla^2_{ff}\log p(y_i \mid f) |_{f=f_i} \right]_c \in \R,
 \end{aligned}
@@
 Finally, we can rewrite $\mathcal{R}_\mathrm{\our}$ as follows
-\begin{equation}\label{eq-cl-regularizer}\textstyle
-\begin{aligned}
+\begin{equation}\label{eq-cl-regularizer}%\textstyle
   \mathcal{R}_\mathrm{\our}(\weights, \mathcal{M}) = \frac{1}{2} \sum_{s=1}^{t-1} \sum_{c=1}^{C} \frac{1}{M} 
@@
 	\vu_c - \vu_{s,c} % f_{\weights_{s}}(\MZ_s)
-	\right\rVert_{\bar{\MB}^{-1}_{s}}, \\
-	\text{~with~} \vu_c \in \R^M \text{~with~} u_{i, c} = \left[ f_{\weights}(\vz_{i}) \right]_c,~\forall {\vz_i} \in \mathcal{Z}_s .
-\end{aligned}
+	\right\rVert_{\bar{\MB}^{-1}_{s}},
 \end{equation}
+%
+with $\vu_c \in \R^M$ and $u_{i, c} = \left[ f_{\weights}(\vz_{i}) \right]_c, \forall {\vz_i} \in \mathcal{Z}_s$.
 

### 2023-05-24 paper/main.tex
updated cl app

@@
 %
-\cref{app:method} provides a more extensive overview of the techncical details of \our.
-%
-\cref{app:cl} covers the sparse-functional regularisation (SFR) setup for continual learning.
+\cref{app:method} provides a more extensive overview of the technical details of \our.
+%
+\cref{app:cl} covers additional details on the \our-based regularizer used for continual learning.
 %
@@
 %
-\cref{app:experiments} provides the full details of each individual experiments in the main paper.
+\cref{app:experiments} provides the full details of each individual experiment in the main paper.
 
@@
 \label{app:cl}
+This section provides additional details about the derivation of the \our-based regularizer described in \cref{sec:sequential} and how we extended it for dealing with the multi-output setting in our experiments.
 \subsection{Derivation of the regularizer term}
-For continual learning, the model cannot access the training data from previous tasks, denoted here as $\dataset_\textrm{old} = \bigcup_{s=1}^{t-1} \dataset_s$, and for each new tasks receives a new chunk of data $\dataset_\textrm{new} = \dataset_t$.
-On the other hand, in the supervised learning setting (described in \cref{sec:methods}) the neural network model has access to all the training data at once, \ie, the objective we are trying to optimize is
+For continual learning, the model cannot access the training data from previous tasks, denoted here as $\dataset_\textrm{old} = \bigcup_{s=1}^{t-1} \dataset_s$, and for each new task receives a new chunk of data $\dataset_\textrm{new} = \dataset_t$.
+On the other hand, in the supervised learning setting (described in \cref{sec:methods}), the neural network model has access to all the training data at once, \ie, the objective we are trying to optimize is
 \begin{equation}
@@
 As a consequence, the Jacobian matrix is $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{C \times P}$ and the kernel of the associated sparse GP derived in \cref{sec:sfr}, $\kappa(\vx, \vx')$ is a tensor in $\R^{C \times P \times P}$.
-This means that we need compute the dual parameters and the matrix $\bar{\MB}^{-1}_{t, c}$ for all the function's outputs.
+This means that we need to compute the dual parameters and the matrix $\bar{\MB}^{-1}_{t, c}$ for all the function's outputs.
 If we denote $\kappa_c(\vx, \vx') \in \R$, as the kernel related to the $c$\textsuperscript{th} output function, \ie, the logit for class $c$, we can write the dual parameters as
@@
 In fact, in the multi-class setting $\hat{\valpha}_{i}$ is a vector in $\R^C$ and $\hat{\vbeta}_{i}$ a matrix in $\R^{C \times C}$.
-For the \our-regularizer, at the end of each task we compute the matrix $\bar{\MB}^{-1}_{t, c}$ as 
+For the \our-regularizer, at the end of each task, we compute the matrix $\bar{\MB}^{-1}_{t, c}$ as 
 \begin{equation}\textstyle
@@
 \end{equation}
-In practice computing the kernel $\kappa_c$ for classes $c$, for which the model has not seen any data yet is not meaningful \todo{probably better to word this differently}, so we define $\bar{\MB}^{-1}_{t, c}$ to be  $\bar{\MB}^{-1}_{t, c} = \MI_M$ $\forall c \not\in \mathcal{C}_t$, where $\mathcal{C}_t$ is the set of classes observed up to task t.
-For example, for S-MNIST  we will have after task 1 $\mathcal{C}_1 = \{0, 1\}$, then after task 2 $\mathcal{C}_1 = \{0, 1, 2, 3\}$, and so on.
+The kernel computation is based on the relationship between the observed data and the parametrized function.
+For this reason, computing the kernel $\kappa_c$ for classes $c$, for which the model has not observed any data yet, is not meaningful.
+\todo{probably better to word this differently}
+In practice, for our method we define $\bar{\MB}^{-1}_{t, c}$ to be $\bar{\MB}^{-1}_{t, c} = \MI_M$ $\forall c \not\in \mathcal{C}_t$, where $\mathcal{C}_t$ is the set of classes observed up to task t.
+For example, for S-MNIST, after task 1 the set of observed classes for which we will compute the kernel is $\mathcal{C}_1 = \{0, 1\}$, then after task 2 it becomes $\mathcal{C}_1 = \{0, 1, 2, 3\}$, et cetera.
 Finally, we can rewrite $\mathcal{R}_\mathrm{\our}$ as follows

### 2023-05-24 paper/main.tex
Minor typo fixes & todos

--- 2023-05-24 paper/main.tex
@@
 %
-\cref{app:method} provides a more extensive overview of the techncical details of \our.
+\cref{app:method} provides a more extensive overview of the technical details of \our.
 %
@@
 %
-Key to our method is the ability to compute the dual parameters in \cref{eq:dual_param}. For general exponential family likelihoods we can derive simpler expressions:
+\todo{This reads a bit off, is it grammatically correct?} Key to our method is the ability to compute the dual parameters as in \cref{eq:dual_param}.
+For general exponential family likelihoods we can derive simpler expressions:
+\todo{How does this connect to Eq 5?}
 \begin{equation}
@@
 \end{equation}
-where $A(f)$ is the log partition function and $\sigma(.)$ is the link function. Taking the first and second derivative of the loss in this form then become:
+where $A(f)$ is the log partition function and $\sigma(.)$ is the link function. Taking the first and second derivative of the loss in this form then becomes: \todo{Becomes what, to be written?}
 
@@
 \subsection{Derivation of the regularizer term}
-For continual learning, the model cannot access the training data from previous tasks, denoted here as $\dataset_\textrm{old} = \bigcup_{s=1}^{t-1} \dataset_s$, and for each new tasks receives a new chunk of data $\dataset_\textrm{new} = \dataset_t$.
+For continual learning, the model cannot access the training data from previous tasks, denoted here as $\dataset_\textrm{old} = \bigcup_{s=1}^{t-1} \dataset_s$, and for each new tasks the model receives a new chunk of data $\dataset_\textrm{new} = \dataset_t$.
 On the other hand, in the supervised learning setting (described in \cref{sec:methods}) the neural network model has access to all the training data at once, \ie, the objective we are trying to optimize is
@@
 \end{equation} 
-Our goal in the continual setting is to replace the missing data coming from $\dataset_\textrm{old}$ by resorting to a functional regularizer that accounts for that by forcing the predictions of the neural networks over the inducing points $\mathcal{Z}_t$ to come with high probability from $f_\weights(\vz_i) \sim q(\vu),  \forall \vz_i \in \mathcal{Z}_t$.
+Our goal in the continual setting is to replace the missing data coming from $\dataset_\textrm{old}$ by resorting to a functional regularizer that accounts for the missing data by forcing the predictions of the neural networks over the inducing points $\mathcal{Z}_t$ to come with high probability from $f_\weights(\vz_i) \sim q(\vu),  \forall \vz_i \in \mathcal{Z}_t$.
 As shown in \citep{khan2017conjugate, adam2021dual}, we can view the dual parameters derived in \cref{sec:sparse-dual-gp}, as {\color{red} TODO}.
@@
 	& \propto  \Norm(0, \MKzz) \prod_{i \in \dataset_\textrm{old}} \exp \! \left(-\frac{\hat{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 \right) \\
-	& \propto \Norm(0, \MKzz) \, \exp\left((\tilde{\vy} - \vu)^\top \bar{\MB}^{-1}(\tilde{\vy} - \vu)\right)
+	& \propto \Norm(0, \MKzz) \, \exp\left((\tilde{\vy} - \vu)^\top \bar{\MB}^{-1}(\tilde{\vy} - \vu)\right),
 \end{align}
@@
 Replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$, we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior.
-To arrive at the MVN Gaussian, we need to rearrange the quadratic terms to match the prior sufficient statistics.
-Performing conjugate summation of prior and likelihood, we would arrive at the sparse GP posterior at the inducing points.
+To arrive at the MVN \todo{What is MVN short for?}Gaussian, we need to rearrange the quadratic terms to match the prior sufficient statistics.
+When performing conjugate summation of prior and likelihood, we arrive at the sparse GP posterior at the inducing points.
 The correlated covariance structure $\MSigma$ and the corresponding $\tilde{\vy}$ are simply a different form of the sparse dual variables,
@@
 \end{equation}
-Written as above, we can see that the spare dual variables can be interpreted as a sparse MVN representation.
+Written as above, we can see that the sparse dual variables can be interpreted as a sparse MVN representation.
 
@@
 In a multi-class classification setting, the neural network can be seen as a function approximator that maps inputs $\vx \in \inputDomain$ to the logits $\textit{\textbf{f}} \in \outputDomain$, \ie, $f_\mathbf{w}: \inputDomain \to \outputDomain$.
-As a consequence, the Jacobian matrix is $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{C \times P}$ and the kernel of the associated sparse GP derived in \cref{sec:sfr}, $\kappa(\vx, \vx')$ is a tensor in $\R^{C \times P \times P}$.
-This means that we need compute the dual parameters and the matrix $\bar{\MB}^{-1}_{t, c}$ for all the function's outputs.
+As a consequence, the Jacobian matrix is $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{C \times P}$, and the kernel of the associated sparse GP derived in \cref{sec:sfr} is $\kappa(\vx, \vx')$, which is a tensor in $\R^{C \times P \times P}$.
+This means that we need to compute the dual parameters and the matrix $\bar{\MB}^{-1}_{t, c}$ for all the function's outputs.
 If we denote $\kappa_c(\vx, \vx') \in \R$, as the kernel related to the $c$\textsuperscript{th} output function, \ie, the logit for class $c$, we can write the dual parameters as
@@
 As such, this is a direct extension of the uncertainty quantification and representation capabilities already demonstrated in the supervised (and continual) learning examples in the main paper.
-However, the RL setting requires slightly more background to it and thus \cref{app:rl} has been separated out to a separate section in the appendix.
+However, as the RL setting differs from the supervised and continual learning settings, we present additional background material on it and thus \cref{app:rl} has been separated out to a separate section in the appendix.
 
@@
 In all experiments we used an MLP dynamic model with a single hidden layer of width 64 and Tanh activation functions.
-At each episode we used Adam \cite{adam} to optimise the NN parameters for $5000$ iterations with a learning rate of $0.001$ and a bacth size of $64$.
+At each episode we used Adam \cite{adam} to optimise the NN parameters for $5000$ iterations with a learning rate of $0.001$ and a batch size of $64$.
 We reset the optimizer after each episode.
@@
 In our experiments, we parameterised both the actor and critic as MLPs with two hidden layers of width $128$ with ELU activations.
-We train them using Adam for $500$ iterations at each episode, using a learning rate $0.0001$ and a bacth size of $512$.
+We train them using Adam for $500$ iterations at each episode, using a learning rate $0.0001$ and a batch size of $512$.
 DDPG uses a target value function to stabilise learning and for the soft target updates
-we used $\tau = 0.005$.
-DDPG is an off-policy algorithm where the exploration policy samples from a noise process.
-We sampled from a Gaussian distribution with $\sigma=0.1$ and clipping at $0.3$.
+we used $\tau = 0.005$. \todo{What is $\tau$ ?}
+DDPG is an off-policy algorithm where the exploration policy samples from a noise process, which here was a Gaussian distribution with $\sigma=0.1$ and clipping at $0.3$.
 
@@
 Although further experiments are required, our results indicate that \our could offer
-better uncertainty estimates for model-based RL.
+better uncertainty estimates in these tasks.
 We believe this may be due to \our sampling in function space as opposed to weight space like
@@
 For the neural network training, we used the same set-up as in \cite{immer2021improving},
-training the neural networok using Adam for $500$ epochs using a batch size of $512$.
+training the neural network using Adam for $500$ epochs with a batch size of $512$.
 The results reported in \cref{tbl:imagesuper} used a learning rate of $10^{-4}$

### 2023-05-24 paper/main.tex
updated cl app

--- 2023-05-24 paper/main.tex
@@
 \subsection{Derivation of the regularizer term}
-For continual learning, the model cannot access the training data from previous tasks, denoted here as $\dataset_\textrm{old} = \bigcup_{s=1}^{t-1} \dataset_s$, and for each new task receives a new chunk of data $\dataset_\textrm{new} = \dataset_t$.
+For continual learning, the model cannot access the training data from previous tasks up to task $t-1$, denoted here as $\dataset_\textrm{old} = \bigcup_{s=1}^{t-1} \dataset_s$, and for each new task $t$ receives a new chunk of data $\dataset_\textrm{new} = \dataset_t$.
 On the other hand, in the supervised learning setting (described in \cref{sec:methods}), the neural network model has access to all the training data at once, \ie, the objective we are trying to optimize is

### 2023-05-24 paper/main.tex
small fixes

--- 2023-05-24 paper/main.tex
@@
 \textbf{Model predictive path integral (MPPI)}
-In all model-based RL experiments we used a $H=5$ step horizon and a discount factor of $\gamma=0.9$.
+In all model-based RL experiments, we used a $H=5$ step horizon and a discount factor of $\gamma=0.9$.
 We sampled $N=256$ trajectories for $J=5$ iterations with $K=32$.
@@
 For the neural network training, we used the same set-up as in \cite{immer2021improving},
-training the neural networok using Adam for $500$ epochs using a batch size of $512$.
+training the neural network using Adam for $500$ epochs using a batch size of $512$.
 The results reported in \cref{tbl:imagesuper} used a learning rate of $10^{-4}$
@@
 and the FMNIST experiments used a prior precision of $\delta=0.0013$.
-The experiments with MNIST  used an MLP with two hidden layers of width 128 and Tanh activtions.
+The experiments with MNIST  used an MLP with two hidden layers of width 128 and Tanh activations.
 In the FMNIST experiments we followed \cite{immer2021improving} and used a CNN
-architecture with two fully connected classification layers and tanh activations.
+architecture with two fully connected classification layers and Tanh activations.
 
@@
 Instead, we use the same prior precision that was used during training.
-We performeed a grid search over the prior precision for the NN MAP using the validation NLPD.
+We performed a grid search over the prior precision for the NN MAP using the validation NLPD.
 We then used this prior precision for the GP predictive (NN) with $M=1024$,
@@
 We selected the hyperparameters to use with all these methods trying to adapt the ones pointed out in the their original papers and the reference implementations.
-For this reason, we relied on SGD for DER, Online-EWC, and SI, which requires higher learning rates, compared to the others methods for which we used Adam, \ie, our \our regularizer, FROMP, S-FSVI, and VCL.
+For this reason, we relied on SGD for DER, Online-EWC, and SI, which requires higher learning rates, compared to the others methods for which we used Adam \cite{adam}, \ie, our \our regularizer, FROMP, S-FSVI, and VCL.
 
@@
 
-The results reported in \cref{tbl:cl_table_1}, are obtained using the following hyperparameters.
+The results reported in \cref{tbl:cl_table_1}, are obtained using the following hyperparameters and repeating the run five times with different seeds.
 The results are in-line with what has been reported in previous work, notably even better for some of the baseline methods.

### 2023-05-24 paper/main.tex
small thing

@@
 %
-\todo{This reads a bit off, is it grammatically correct?} Key to our method is the ability to compute the dual parameters as in \cref{eq:dual_param}.
-For general exponential family likelihoods we can derive simpler expressions:
-\todo{How does this connect to Eq 5?}
+Key to our method is the ability to compute the dual parameters in \cref{eq:dual_param}.
+For general exponential family likelihoods we can derive simpler expressions by rewriting the loss in the natural form:
+
 \begin{equation}
- \ell(\sigma(f), y) = -\log p(y \mid f) =  A(f)  - \langle y, f\rangle
+ \ell(h(f), y) = -\log p(y \mid f) =  A(f)  - \langle t(y), f\rangle
 \end{equation}
-where $A(f)$ is the log partition function and $\sigma(.)$ is the link function. Taking the first and second derivative of the loss in this form then becomes: \todo{Becomes what, to be written?}
-
- For the Bernoulli distribution with a given link function, typically the sigmoid, $\sigma(f_{\vw}(\vx)):= \sigma(f) = \frac{1}{1+e^f}$. Then, we can write the log probability as
+where $A(f)$ is the log partition function and $h(.)$ is the link function and $t(y)$ are the sufficient, given the loss functions we use $t(y) = y$.
+Taking the first and second derivative of the loss in this form then become:
+\begin{equation} \label{eq:}
+\nabla_{f}\log p(y_i \mid f) =  A'(f) - y  \quad \nabla^2_{f f}\log p(y_i \mid f_i) = A''(y) 
+\end{equation}
+The derivative second derivative of the log partition function is easily calculated and the above formulation can be extended to vector input and outputs \ie for the categorical loss, we list the likelihoods we use and their dual parameter below:
 %\begin{equation}
@@
 \centering
-\begin{tabular}{@{}ccc@{}}
+\begin{tabular}{@{}cccc@{}}
 \toprule
-Loss        & der 1 & der 2 \\ \midrule
-Bernoulli    & $\sigma(f) - y$   & $\sigma(f)(1-\sigma(f))$      \\
-Mse         & $y - f$      & $1$       \\
-Categorical &  $\textrm{softmax}(f_i) - y_i$     &   $\begin{bmatrix}
+Loss        & $\nabla_{f}$ & $\nabla^2_{f f}$ &   $h()$ \\ \midrule
+Bernoulli    & $\sigma(f) - y$   & $\sigma(f)(1-\sigma(f))$  & \\
+Mse         & $y - f$      & $1$       & \\
+Categorical &  $\begin{bmatrix}
 		p_1\\ \vdots\\p_k
-	\end{bmatrix}$,     \\ \bottomrule
+	\end{bmatrix}$     &   $\begin{bmatrix}
+		p_1\\ \vdots\\p_k
+	\end{bmatrix}$,    & \\ \bottomrule
 \end{tabular}

### 2023-05-24 paper/main.tex
update sec. a

--- 2023-05-24 paper/main.tex
@@
 %
-\todo{This reads a bit off, is it grammatically correct?} Key to our method is the ability to compute the dual parameters as in \cref{eq:dual_param}.
-For general exponential family likelihoods we can derive simpler expressions:
-\todo{How does this connect to Eq 5?}
+As shown in \cref{eq:dual_param} in the main paper, our method rely on computation of the dual parameters.
+We show here how we can derive them in general for the family of exponential likelihoods.
+By rewriting the loss in the natural form, we have,
 \begin{equation}
- \ell(\sigma(f), y) = -\log p(y \mid f) =  A(f)  - \langle y, f\rangle
-\end{equation}
-where $A(f)$ is the log partition function and $\sigma(.)$ is the link function. Taking the first and second derivative of the loss in this form then becomes: \todo{Becomes what, to be written?}
-
- For the Bernoulli distribution with a given link function, typically the sigmoid, $\sigma(f_{\vw}(\vx)):= \sigma(f) = \frac{1}{1+e^f}$. Then, we can write the log probability as
+ \ell(h(f), y) = -\log p(y \mid f) =  A(f)  - \langle t(y), f \rangle
+\end{equation}
+where $A(f)$ is the log partition function, $h(\cdot)$ is the inverse link function, $t(y)$ are the sufficient statistics, and $f$ denotes the neural network output before the link function. 
+%given the loss functions we use $t(y) = y$. 
+Then, taking the first and second derivatives of the loss in this form become:
+\begin{equation}\label{eq:dual_param_app}
+  \nabla_{f} - \log p(y_i \mid f) |_{f=f_i} =  - A'(f_i) y_i
+  \quad \text{and} \quad
+  \nabla^2_{f\!f} - \log p(y_i \mid f) |_{f=f_i} = A''(f_i).
+\end{equation}
+\todo{check the signs with the main paper}
+% The second derivative of the log partition function is easily calculated and
+In this section, we provide the derivatives needed for the losses used in this work, \ie, the Gaussian likelihood, used for the regression tasks, the Bernoulli likelihood, for binary classification, and the categorical likelihood, used for multi-class classification.
+
+For regression, the negative log likelihood comes from the Gaussian likelihood, and for a single input it can be written as:
+\begin{equation}
+	\ell(h(f_i), y_i) = % -\log \Norm( h(f) | y, \sigma^2) 	= - \log 
+\end{equation}
+where the inverse link function is the sigmoid function $h(f) = \sigma(f) = \frac{1}{1 + e^{-f}}$. Thus, the first and second derivatives are
+\begin{equation}
+	\nabla_f \ell(\sigma(f), y_i)|_{f=f_i} = y_i - f_i \quad \text{ and } \quad  \nabla_{f\!f} \ell(h(f), y_i)|_{f=f_i} = 1
+\end{equation}
+
+% While these equations deal with single output functions, we can extend them to multi output functions, such as for the categorical loss.
+%The easiest example to deal with is the Bernoulli loss, where 
+%The above formulation can be extended to vector input and outputs, \ie, for the categorical loss. In the following table, we list the likelihoods we use and their dual parameter below:
 %\begin{equation}
@@
 \centering
-\begin{tabular}{@{}ccc@{}}
+\caption{}
+\begin{tabular}{@{}cccc@{}}
 \toprule
-Loss        & der 1 & der 2 \\ \midrule
-Bernoulli    & $\sigma(f) - y$   & $\sigma(f)(1-\sigma(f))$      \\
-Mse         & $y - f$      & $1$       \\
-Categorical &  $\textrm{softmax}(f_i) - y_i$     &   $\begin{bmatrix}
+Loss        & $h(\cdot)$ & $\nabla_{f}$ & $\nabla^2_{f\!f}$  \\ \midrule
+Bernoulli   & $\sigma(f) = \frac{1}{1 + e^{-f}}$ & $\sigma(f) - y$   & $\sigma(f)(1-\sigma(f))$ \\
+MSE         & & $y - f$      & $1$ \\
+Categorical & $\mathcal{S}_i(\vf) = \frac{e^{\vf_i}}{\sum_{j=1}^C e^{\vf_j}}$ &  $\begin{bmatrix}
 		p_1\\ \vdots\\p_k
-	\end{bmatrix}$,     \\ \bottomrule
+	\end{bmatrix}$     &   $\begin{bmatrix}
+		p_1\\ \vdots\\p_k
+	\end{bmatrix}$ \\ \bottomrule
 \end{tabular}

### 2023-05-24 paper/main.tex
rewrite deriv of regular

@@
 Our goal in the continual setting is to replace the missing data coming from $\dataset_\textrm{old}$ by resorting to a functional regularizer that accounts for that by forcing the predictions of the neural networks over the inducing points $\mathcal{Z}_t$ to come with high probability from $f_\weights(\vz_i) \sim q(\vu),  \forall \vz_i \in \mathcal{Z}_t$.
-As shown in \citep{khan2017conjugate, adam2021dual}, we can view the dual parameters derived in \cref{sec:sparse-dual-gp}, as {\color{red} TODO}.
+As shown in \citep{khan2017conjugate, adam2021dual}, we can view the dual parameters derived in \cref{sec:sparse-dual-gp}.
 Then, we can rewrite the sparse GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
 %
-\begin{align}
+\begin{align} \label{eq:normal}
 	q(\vu)
-	& \propto p_\weights(\vu) \Norm(\tilde{\vy}; \vu, \MB_\vu)\\
 	& \propto  \Norm(0, \MKzz) \prod_{i \in \dataset_\textrm{old}} \exp \! \left(-\frac{\hat{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 \right) \\
-	& \propto \Norm(0, \MKzz) \, \exp\left((\tilde{\vy} - \vu)^\top \bar{\MB}^{-1}(\tilde{\vy} - \vu)\right),
+        & \propto p(\vu) \Norm(\tilde{\vy}; \vu, \MB_\vu),
 \end{align}
@@
 where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}_i$.
-The sparse GP posterior $q(\vu)$ is proportional to the product between the prior over the weights $p_\weights(\vu)$ and a Gaussian term $\Norm(\tilde{\vy}; \vu, \MB_\vu)$, which arises from {\color{red} TODO}
-
-Replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$, we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior.
-To arrive at the MVN \todo{What is MVN short for?}Gaussian, we need to rearrange the quadratic terms to match the prior sufficient statistics.
-When performing conjugate summation of prior and likelihood, we arrive at the sparse GP posterior at the inducing points.
-The correlated covariance structure $\MSigma$ and the corresponding $\tilde{\vy}$ are simply a different form of the sparse dual variables,
-\begin{equation}
-\quad \bar{\MB}^{-1} =  \MKzz \MB_\vu^{-1} \MKzz \quad \text{and} \quad \tilde{\vy} = \MKzz \MB_{\vu}\valpha_{\vu}.
-\end{equation}
-Written as above, we can see that the sparse dual variables can be interpreted as a sparse MVN representation.
+The sparse GP posterior $q(\vu)$ is proportional to the product between the prior over the inducing points $p(\vu)$ and a Gaussian term $\Norm(\tilde{\vy}; \vu, \MB_\vu)$, which arises from the sparse approximation to the likelihood.
+Replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$, we can see the similarity between the sparse GP and a linear model where the kernel is the linear kernel.
+We therefore use the key quadratic term from  $\Norm(\tilde{\vy}; \vu, \MB_\vu)$ as our regularizer as the missing data term, which after we take the $\log$ becomes $(\tilde{\vy} - \vu)^\top \bar{\MB}^{-1}(\tilde{\vy} - \vu)$.
+Given that $\tilde{\vy}$ are in the function space we can instead us simply the previous neural network predictions $f^{\textrm{old}}_\weights(\vz_i)$ and save computations.
 

### 2023-05-24 paper/main.tex
rewrite deriv of regular

@@
 
+\subsection{Computational complexity}
+
 \section{\our for continual learning}
@@
 \end{equation} 
-Our goal in the continual setting is to replace the missing data coming from $\dataset_\textrm{old}$ by resorting to a functional regularizer that accounts for that by forcing the predictions of the neural networks over the inducing points $\mathcal{Z}_t$ to come with high probability from $f_\weights(\vz_i) \sim q(\vu),  \forall \vz_i \in \mathcal{Z}_t$.
-As shown in \citep{khan2017conjugate, adam2021dual}, we can view the dual parameters derived in \cref{sec:sparse-dual-gp}.
-Then, we can rewrite the sparse GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
+Our goal in the continual setting is to replace the missing data coming from $\dataset_\textrm{old}$ by resorting to a functional regularizer that accounts for that by forcing the predictions of the neural networks over the inducing points $\mathcal{Z}_t$ to come from $f^{\textrm{old}}_\weights(\vz_i) \sim q^\textrm{old}(\vu),  \forall \vz_i \in \mathcal{Z}_t$.
+As shown in \citep{khan2017conjugate, adam2021dual}, we can view the dual parameters derived in \cref{sec:sparse-dual-gp} as linked to approximate likelihood terms.
+Using this insight, we can rewrite the sparse GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
 %

### 2023-05-24 paper/main.tex
update app. a

--- 2023-05-24 paper/main.tex
@@
 % The second derivative of the log partition function is easily calculated and
-In this section, we provide the derivatives needed for the losses used in this work, \ie, the Gaussian likelihood, used for the regression tasks, the Bernoulli likelihood, for binary classification, and the categorical likelihood, used for multi-class classification.
-
-For regression, the negative log likelihood comes from the Gaussian likelihood, and for a single input it can be written as:
+In this section, we provide the derivatives needed for the losses used in this work, \ie, the mean squared error (MSE) likelihood, used for the regression tasks, the Bernoulli likelihood, for binary classification, and the categorical likelihood, used for multi-class classification.
+
+For regression, the negative log likelihood comes from the MSE, and for a single input it can be written as:
 \begin{equation}
-	\ell(h(f_i), y_i) = % -\log \Norm( h(f) | y, \sigma^2) 	= - \log 
-\end{equation}
-where the inverse link function is the sigmoid function $h(f) = \sigma(f) = \frac{1}{1 + e^{-f}}$. Thus, the first and second derivatives are
+	\ell(h(f), y) = \frac{1}{2} (y -f).% -\log \Norm( h(f) | y, \sigma^2) 	= - \log 
+\end{equation}
+where the inverse link function is simply $h(f) = f$. Thus, the first and second derivatives are
 \begin{equation}
@@
 \end{equation}
+
+In binary classification, we deal with Bernoulli likelihoods.
+The inverse link function is the sigmoid function $h(f) = \sigma(f) = \frac{1}{1 + e^{-f}}$, and we can then write the negative log likelihood as
+\begin{equation}
+\begin{aligned}
+	\ell(h(f), y) 
+	&= -\log \left( \sigma(f)^y (1 - \sigma(f))^{1-y} \right) \\
+	&= - y \log(\sigma(f)) - (1-y) \log(1- \sigma(f)) \\
+	&= - y f + \log(1 + e^f) 
+\end{aligned}
+\end{equation}
+Then, it follows that the the derivative we are interested in are
+\begin{equation}
+	\nabla_f \ell(\sigma(f), y_i)|_{f=f_i} = - y_i + \sigma(f_i) \quad \text{ and } \quad  \nabla_{f\!f} \ell(h(f), y_i)|_{f=f_i} = \sigma(f_i) (1 - \sigma(f_i)).
+\end{equation}
+
+Moving to the multi class classification, the function outputs is no more a scalar but a vector of logits $\bm{f} \in \R^C$.
+The inverse link function for the categorical loss is the softmax function $\textrm{Softmax}(\bm{f}) : \R^C \to \R^C$ defined as $h(\bm{f}) = \textrm{Softmax}(\bm{f}) = \frac{\exp(\bm{f})}{ \sum^C_{j=1} \exp(\bm{f}_j)} \in \R^C$.
+If we write the targets $y_i$ as a one-hot $C$-shaped one-hot encoding vector, we can write the negative log likelihood as:
+\begin{equation}
+\begin{aligned}
+	\ell(h(\bm{f}),\vy) &= - \log\left( \vy^\T \textrm{Softmax}(\bm{f})\right)\\
+	&= - y_i \log \left( \left[ \textrm{Softmax}(\bm{f}) \right]_i \right)
+\end{aligned}
+\end{equation}
+where $\left[\textrm{Softmax}(\bm{f})\right]_i = \frac{\exp(\bm{f}_i)}{\sum_{j=1}^{C} \exp(\bm{f}_j)}$ defines the $i$\textsuperscript{th} entry of the logits fed through the $\textrm{Softmax}(\cdot)$ function.
 

### 2023-05-24 paper/main.tex
commented the table
update app A

@@
 \begin{equation}
-	\nabla_f \ell(\sigma(f), y_i)|_{f=f_i} = - y_i + \sigma(f_i) \quad \text{ and } \quad  \nabla_{f\!f} \ell(h(f), y_i)|_{f=f_i} = \sigma(f_i) (1 - \sigma(f_i)).
+	\nabla_f \ell(h(f), y_i)|_{f=f_i} = - y_i + \sigma(f_i) \quad \text{ and } \quad  \nabla_{f\!f} \ell(h(f), y_i)|_{f=f_i} = \sigma(f_i) (1 - \sigma(f_i)).
 \end{equation}
@@
 Moving to the multi class classification, the function outputs is no more a scalar but a vector of logits $\bm{f} \in \R^C$.
-The inverse link function for the categorical loss is the softmax function $\textrm{Softmax}(\bm{f}) : \R^C \to \R^C$ defined as $h(\bm{f}) = \textrm{Softmax}(\bm{f}) = \frac{\exp(\bm{f})}{ \sum^C_{j=1} \exp(\bm{f}_j)} \in \R^C$.
+The inverse link function for the categorical loss is the softmax function $\textrm{Softmax}(\bm{f}) : \R^C \mapsto \R^C$ defined as $h(\bm{f}) = \textrm{Softmax}(\bm{f}) = \frac{\exp(\bm{f})}{ \sum^C_{j=1} \exp(\bm{f}_j)} \in \R^C$.
 If we write the targets $y_i$ as a one-hot $C$-shaped one-hot encoding vector, we can write the negative log likelihood as:
@@
 	\ell(h(\bm{f}),\vy) &= - \log\left( \vy^\T \textrm{Softmax}(\bm{f})\right)\\
-	&= - y_i \log \left( \left[ \textrm{Softmax}(\bm{f}) \right]_i \right)
+	&= - y_i \cdot \log \left( \left[ \textrm{Softmax}(\bm{f}) \right]_i \right)
 \end{aligned}
 \end{equation}
-where $\left[\textrm{Softmax}(\bm{f})\right]_i = \frac{\exp(\bm{f}_i)}{\sum_{j=1}^{C} \exp(\bm{f}_j)}$ defines the $i$\textsuperscript{th} entry of the logits fed through the $\textrm{Softmax}(\cdot)$ function.
+where $\left[\textrm{Softmax}(\bm{f})\right]_i = \frac{\exp(\bm{f}_i)}{\sum_{j=1}^{C} \exp(\bm{f}_j)} \in \R$ defines the $i$\textsuperscript{th} entry of the logits fed through the $\textrm{Softmax}(\cdot)$ function.
+Finally, we can write the first and second derivatives as follows
+
+\begin{equation}
+\begin{aligned}
+	\nabla_f \ell(h(f), y_i)|_{f=f_i} &= - y_i + \left[ \textrm{Softmax}(\bm{f}) \right]_i \\
+	\nabla_{f\!f} \ell(h(f), y_i)|_{f=f_i} &= \left[\textrm{Softmax}(\bm{f})\right]_i (1 - \left[\textrm{Softmax}(\bm{f})\right]_i).
+\end{aligned}
+\end{equation}
 
@@
 
-\begin{table}[!ht]
-\centering
-\caption{}
-\begin{tabular}{@{}cccc@{}}
-\toprule
-Loss        & $h(\cdot)$ & $\nabla_{f}$ & $\nabla^2_{f\!f}$  \\ \midrule
-Bernoulli   & $\sigma(f) = \frac{1}{1 + e^{-f}}$ & $\sigma(f) - y$   & $\sigma(f)(1-\sigma(f))$ \\
-MSE         & & $y - f$      & $1$ \\
-Categorical & $\mathcal{S}_i(\vf) = \frac{e^{\vf_i}}{\sum_{j=1}^C e^{\vf_j}}$ &  $\begin{bmatrix}
-		p_1\\ \vdots\\p_k
-	\end{bmatrix}$     &   $\begin{bmatrix}
-		p_1\\ \vdots\\p_k
-	\end{bmatrix}$ \\ \bottomrule
-\end{tabular}
-\end{table}
+%\begin{table}[!ht]
+%\centering
+%\caption{}
+%\begin{tabular}{@{}cccc@{}}
+%\toprule
+%Loss        & $h(\cdot)$ & $\nabla_{f}$ & $\nabla^2_{f\!f}$  \\ \midrule
+%Bernoulli   & $\sigma(f) = \frac{1}{1 + e^{-f}}$ & $\sigma(f) - y$   & $\sigma(f)(1-\sigma(f))$ \\
+%MSE         & & $y - f$      & $1$ \\
+%Categorical & $\mathcal{S}_i(\vf) = \frac{e^{\vf_i}}{\sum_{j=1}^C e^{\vf_j}}$ &  $\begin{bmatrix}
+%		p_1\\ \vdots\\p_k
+%	\end{bmatrix}$     &   $\begin{bmatrix}
+%		p_1\\ \vdots\\p_k
+%	\end{bmatrix}$ \\ \bottomrule
+%\end{tabular}
+%\end{table}
 

### 2023-05-24 paper/main.tex
added some text to wrap App. A

@@
 \label{app:method}
-%
+In this section, we first show in \cref{app:losses} how the dual parameters used for \our are computed for the different losses employed in our experiments, and then we discuss the computational complexity of our method in \cref{app:comp_compl}.
+%
+\subsection{Computation of the dual parameters for different losses}\todo{just a placeholder}
+\label{app:losses}
 As shown in \cref{eq:dual_param} in the main paper, our method rely on computation of the dual parameters.
@@
 \subsection{Computational complexity}
+\label{app:comp_compl}
 

### 2023-05-24 paper/main.tex
wip a2

@@
 \end{equation}
-where $\left[\textrm{Softmax}(\bm{f})\right]_i = \frac{\exp(\bm{f}_i)}{\sum_{j=1}^{C} \exp(\bm{f}_j)} \in \R$ defines the $i$\textsuperscript{th} entry of the logits fed through the $\textrm{Softmax}(\cdot)$ function.
+where $\left[\textrm{Softmax}(\bm{f})\right]_i = \frac{\exp(\bm{f}_i)}{\sum_{j=1}^{C} \exp(\bm{f}_j)} \in [0, 1]$ defines the $i$\textsuperscript{th} entry of the logits fed through the $\textrm{Softmax}(\cdot)$ function.
 Finally, we can write the first and second derivatives as follows
@@
 \label{app:comp_compl}
+
+% Big O
+% train neural network
+% compute the NTK -> from the NTK paper
+% we outer product of the kzi O(NM^2)
+% inversion O(M^3)
+
+% Practical implementation
+% mention that we do that in batches not full N 
+% role of jitter 
+% role of clamping
+% GPU A100 Nvidia
 

### 2023-05-24 paper/main.tex
rewrite of grads

@@
 \begin{equation}\label{eq:dual_param_app}
-  \nabla_{f} - \log p(y_i \mid f) |_{f=f_i} =  - A'(f_i) y_i
+  -\nabla_{f} \log p(y_i \mid f) |_{f=f_i} =  A'(f_i) - y_i
   \quad \text{and} \quad
@@
 \end{equation}
-\todo{check the signs with the main paper}
 % The second derivative of the log partition function is easily calculated and
@@
 \begin{equation}
-	\ell(h(f), y) = \frac{1}{2} (y -f).% -\log \Norm( h(f) | y, \sigma^2) 	= - \log 
+	\ell(h(f), y) = \frac{1}{2} (y_i -f_i)^2.% -\log \Norm( h(f) | y, \sigma^2) 	= - \log 
 \end{equation}
@@
 \begin{equation}
-	\nabla_f \ell(\sigma(f), y_i)|_{f=f_i} = y_i - f_i \quad \text{ and } \quad  \nabla_{f\!f} \ell(h(f), y_i)|_{f=f_i} = 1
+	\nabla_f \ell(\sigma(f), y_i)|_{f=f_i} =  f_i - y_i \quad \text{ and } \quad  \nabla_{f\!f} \ell(h(f), y_i)|_{f=f_i} = 1
 \end{equation}
@@
 In binary classification, we deal with Bernoulli likelihoods.
-The inverse link function is the sigmoid function $h(f) = \sigma(f) = \frac{1}{1 + e^{-f}}$, and we can then write the negative log likelihood as
+The inverse link function is the sigmoid function $h(f) = \sigma(f) = \frac{1}{1 + e^{-f}}$, and we can then write the derivates as follows
+%\begin{equation}
+%\begin{aligned}
+%	\ell(h(f), y) 
+%	&= -\log \left( \sigma(f)^y (1 - \sigma(f))^{1-y} \right) \\
+%	&= - y \log(\sigma(f)) - (1-y) \log(1- \sigma(f)) \\
+%	&= - y f + \log(1 + e^f) 
+%\end{aligned}
+%\end{equation}
+%Then, it follows that the the derivative we are interested in are
+\begin{equation}
+	\nabla_f \ell(h(f), y_i)|_{f=f_i} = \sigma(f_i) - y_i  \quad \text{ and } \quad  \nabla_{f\!f} \ell(h(f), y_i)|_{f=f_i} = \sigma(f_i) (1 - \sigma(f_i)).
+\end{equation}
+
+Moving to the multi class classification, the function outputs is no more a scalar but a vect ogits $f_\weights(\vx_i) = \bm{f _i} \in \R^C$.
+The inverse link function for the categorical loss is the softmax function $\textrm{Softmax}(\bm{f}) : \R^C \mapsto \R^C$ defined as $h(\bm{f}) = \textrm{Softmax}(\bm{f}) = \frac{\exp(\bm{f})}{ \sum^C_{c=1} \exp(\bm{f}_c)} \in \R^C$.
+If we write the targets as a one-hot  encoded vector $\vy_i$, we can write the negative log likelihood as:
 \begin{equation}
 \begin{aligned}
-	\ell(h(f), y) 
-	&= -\log \left( \sigma(f)^y (1 - \sigma(f))^{1-y} \right) \\
-	&= - y \log(\sigma(f)) - (1-y) \log(1- \sigma(f)) \\
-	&= - y f + \log(1 + e^f) 
+	\ell(h(\bm{f}),\vy_i) &= - \log\left( \vy_i^\T \textrm{Softmax}(\bm{f})\right)\\
+	% &= - y_i \cdot \log \left( \left[ \textrm{Softmax}(\bm{f}) \right]_i \right)
 \end{aligned}
 \end{equation}
-Then, it follows that the the derivative we are interested in are
-\begin{equation}
-	\nabla_f \ell(h(f), y_i)|_{f=f_i} = - y_i + \sigma(f_i) \quad \text{ and } \quad  \nabla_{f\!f} \ell(h(f), y_i)|_{f=f_i} = \sigma(f_i) (1 - \sigma(f_i)).
-\end{equation}
-
-Moving to the multi class classification, the function outputs is no more a scalar but a vector of logits $\bm{f} \in \R^C$.
-The inverse link function for the categorical loss is the softmax function $\textrm{Softmax}(\bm{f}) : \R^C \mapsto \R^C$ defined as $h(\bm{f}) = \textrm{Softmax}(\bm{f}) = \frac{\exp(\bm{f})}{ \sum^C_{j=1} \exp(\bm{f}_j)} \in \R^C$.
-If we write the targets $y_i$ as a one-hot $C$-shaped one-hot encoding vector, we can write the negative log likelihood as:
+% where $\left[\textrm{Softmax}(\bm{f})\right]_j = \frac{\exp(\bm{f}_j)}{\sum_{c=1}^{C} \exp(\bm{f}_c)} \in \R$ defines the $j$\textsuperscript{th} entry of the logits fed through the $\textrm{Softmax}(\cdot)$ function.
+Finally, we can write the first and second derivatives as follows
 \begin{equation}
 \begin{aligned}
-	\ell(h(\bm{f}),\vy) &= - \log\left( \vy^\T \textrm{Softmax}(\bm{f})\right)\\
-	&= - y_i \cdot \log \left( \left[ \textrm{Softmax}(\bm{f}) \right]_i \right)
+	[\nabla_{\bm{f}} \ell(h(\bm{f}), \vy_i)|_{\bm{f}=\bm{f}_i}]_j &= \left[\textrm{Softmax}(\bm{f}) - \vy_i  \right]_j \\
+	\left[\textrm{diag}\left(\nabla_{\bm{f}\!\bm{f}} \ell(h(\bm{f}), \vy_i)|_{\bm{f}=\bm{f}_i}\right)\right]_{j} &= \left[\textrm{Softmax}(\bm{f})\right]_j (1 - \left[\textrm{Softmax}(\bm{f})\right]_j),
 \end{aligned}
 \end{equation}
+
 where $\left[\textrm{Softmax}(\bm{f})\right]_i = \frac{\exp(\bm{f}_i)}{\sum_{j=1}^{C} \exp(\bm{f}_j)} \in [0, 1]$ defines the $i$\textsuperscript{th} entry of the logits fed through the $\textrm{Softmax}(\cdot)$ function.
@@
 \end{equation}
+where we only need the $\textrm{diag}$ given our independence assumption.
 

### 2023-05-24 paper/main.tex
rewrite of grads

@@
 %
+
 \subsection{Computation of the dual parameters for different losses}\todo{just a placeholder}
 \label{app:losses}
-As shown in \cref{eq:dual_param} in the main paper, our method rely on computation of the dual parameters.
-We show here how we can derive them in general for the family of exponential likelihoods.
-By rewriting the loss in the natural form, we have,
+As shown in \cref{eq:dual_param} in the main paper, our method relies on computation of the dual parameters.
+We can derive them in general for the family of exponential likelihoods, by rewriting the likelihood in the natural form,
 \begin{equation}
- \ell(h(f), y) = -\log p(y \mid f) =  A(f)  - \langle t(y), f \rangle
-\end{equation}
-where $A(f)$ is the log partition function, $h(\cdot)$ is the inverse link function, $t(y)$ are the sufficient statistics, and $f$ denotes the neural network output before the link function. 
+ \ell(h(f), y) = -\log p(y \mid f) =  A(f)  - \langle t(y), f \rangle,
+\end{equation}
+where $A(f)$ is the log partition function, $h(\cdot)$ is the inverse link function, $t(y)$ are the sufficient statistics which for all our likelihoods is simply $t(y)=y$, finally $f$ denotes the neural network output before the link function.
 %given the loss functions we use $t(y) = y$. 
@@
 
-For regression, the negative log likelihood comes from the MSE, and for a single input it can be written as:
+For regression, the negative log likelihood comes from the MSE, and for a single input it can be written as
 \begin{equation}
-	\ell(h(f), y) = \frac{1}{2} (y_i -f_i)^2.% -\log \Norm( h(f) | y, \sigma^2) 	= - \log 
+	\ell(h(f), y) = \frac{1}{2} (y_i -f_i)^2,% -\log \Norm( h(f) | y, \sigma^2) 	= - \log 
 \end{equation}
@@
 \begin{equation}
-	\nabla_f \ell(\sigma(f), y_i)|_{f=f_i} =  f_i - y_i \quad \text{ and } \quad  \nabla_{f\!f} \ell(h(f), y_i)|_{f=f_i} = 1
-\end{equation}
-
-In binary classification, we deal with Bernoulli likelihoods.
-The inverse link function is the sigmoid function $h(f) = \sigma(f) = \frac{1}{1 + e^{-f}}$, and we can then write the derivates as follows
+	\nabla_f \ell(\sigma(f), y_i)|_{f=f_i} =  f_i - y_i \quad \text{ and } \quad  \nabla_{f\!f} \ell(h(f), y_i)|_{f=f_i} = 1.
+\end{equation}
+
+In binary classification, we have a Bernoulli likelihood. The inverse link function is the sigmoid function $h(f) = \sigma(f) = \frac{1}{1 + e^{-f}}$, and we can then write the derivates as follows
 %\begin{equation}
@@
 
-Moving to the multi class classification, the function outputs is no more a scalar but a vect ogits $f_\weights(\vx_i) = \bm{f _i} \in \R^C$.
-The inverse link function for the categorical loss is the softmax function $\textrm{Softmax}(\bm{f}) : \R^C \mapsto \R^C$ defined as $h(\bm{f}) = \textrm{Softmax}(\bm{f}) = \frac{\exp(\bm{f})}{ \sum^C_{c=1} \exp(\bm{f}_c)} \in \R^C$.
-If we write the targets as a one-hot  encoded vector $\vy_i$, we can write the negative log likelihood as:
+In multi-class classification, the function outputs are no more scalar but a vector of logits $f_\weights(\vx_i) = \bm{f _i} \in \R^C$.
+The inverse link function for the categorical loss is the softmax function $\textrm{softmax}(\bm{f}) : \R^C \mapsto \R^C$ defined as $h(\bm{f}) = \textrm{softmax}(\bm{f}) = \frac{\exp(\bm{f})}{ \sum^C_{c=1} \exp(\bm{f}_c)} \in \R^C$.
+If we write the targets as a one-hot  encoded vector $\vy_i$, we can write the negative log likelihood as
 \begin{equation}
 \begin{aligned}
-	\ell(h(\bm{f}),\vy_i) &= - \log\left( \vy_i^\T \textrm{Softmax}(\bm{f})\right)\\
+	\ell(h(\bm{f}),\vy_i) &= - \log\left( \vy_i^\T \textrm{softmax}(\bm{f})\right).\\
 	% &= - y_i \cdot \log \left( \left[ \textrm{Softmax}(\bm{f}) \right]_i \right)
@@
 \end{equation}
+
 where we only need the $\textrm{diag}$ given our independence assumption.

### 2023-05-24 paper/main.tex
rewrite of grads

@@
 \end{equation}
-where $A(f)$ is the log partition function, $h(\cdot)$ is the inverse link function, $t(y)$ are the sufficient statistics which for all our likelihoods is simply $t(y)=y$, finally $f$ denotes the neural network output before the link function.
+where $A(f)$ is the log partition function, $h(\cdot)$ is the inverse link function, $t(y)$ are the sufficient statistics which for all our likelihoods is simply $t(y)=y$, finally $f$ denotes the neural network output before the inverse link function.
 %given the loss functions we use $t(y) = y$. 

### 2023-05-24 paper/main.tex
updated section A2

--- 2023-05-24 paper/main.tex
@@
 \begin{equation}\label{eq:dual_param_app}
-  -\nabla_{f} \log p(y_i \mid f) |_{f=f_i} =  A'(f_i) - y_i
+  \nabla_{f} - \log p(y_i \mid f) |_{f=f_i} =  - A'(f_i) y_i
   \quad \text{and} \quad
@@
 \end{equation}
+\todo{check the signs with the main paper}
 % The second derivative of the log partition function is easily calculated and
@@
 \begin{equation}
-	\ell(h(f), y) = \frac{1}{2} (y_i -f_i)^2.% -\log \Norm( h(f) | y, \sigma^2) 	= - \log 
+	\ell(h(f), y) = \frac{1}{2} (y -f).% -\log \Norm( h(f) | y, \sigma^2) 	= - \log 
 \end{equation}
@@
 \begin{equation}
-	\nabla_f \ell(\sigma(f), y_i)|_{f=f_i} =  f_i - y_i \quad \text{ and } \quad  \nabla_{f\!f} \ell(h(f), y_i)|_{f=f_i} = 1
+	\nabla_f \ell(\sigma(f), y_i)|_{f=f_i} = y_i - f_i \quad \text{ and } \quad  \nabla_{f\!f} \ell(h(f), y_i)|_{f=f_i} = 1
 \end{equation}
@@
 In binary classification, we deal with Bernoulli likelihoods.
-The inverse link function is the sigmoid function $h(f) = \sigma(f) = \frac{1}{1 + e^{-f}}$, and we can then write the derivates as follows
-%\begin{equation}
-%\begin{aligned}
-%	\ell(h(f), y) 
-%	&= -\log \left( \sigma(f)^y (1 - \sigma(f))^{1-y} \right) \\
-%	&= - y \log(\sigma(f)) - (1-y) \log(1- \sigma(f)) \\
-%	&= - y f + \log(1 + e^f) 
-%\end{aligned}
-%\end{equation}
-%Then, it follows that the the derivative we are interested in are
-\begin{equation}
-	\nabla_f \ell(h(f), y_i)|_{f=f_i} = \sigma(f_i) - y_i  \quad \text{ and } \quad  \nabla_{f\!f} \ell(h(f), y_i)|_{f=f_i} = \sigma(f_i) (1 - \sigma(f_i)).
-\end{equation}
-
-Moving to the multi class classification, the function outputs is no more a scalar but a vect ogits $f_\weights(\vx_i) = \bm{f _i} \in \R^C$.
-The inverse link function for the categorical loss is the softmax function $\textrm{Softmax}(\bm{f}) : \R^C \mapsto \R^C$ defined as $h(\bm{f}) = \textrm{Softmax}(\bm{f}) = \frac{\exp(\bm{f})}{ \sum^C_{c=1} \exp(\bm{f}_c)} \in \R^C$.
-If we write the targets as a one-hot  encoded vector $\vy_i$, we can write the negative log likelihood as:
+The inverse link function is the sigmoid function $h(f) = \sigma(f) = \frac{1}{1 + e^{-f}}$, and we can then write the negative log likelihood as
 \begin{equation}
 \begin{aligned}
-	\ell(h(\bm{f}),\vy_i) &= - \log\left( \vy_i^\T \textrm{Softmax}(\bm{f})\right)\\
-	% &= - y_i \cdot \log \left( \left[ \textrm{Softmax}(\bm{f}) \right]_i \right)
+	\ell(h(f), y) 
+	&= -\log \left( \sigma(f)^y (1 - \sigma(f))^{1-y} \right) \\
+	&= - y \log(\sigma(f)) - (1-y) \log(1- \sigma(f)) \\
+	&= - y f + \log(1 + e^f) 
 \end{aligned}
 \end{equation}
-% where $\left[\textrm{Softmax}(\bm{f})\right]_j = \frac{\exp(\bm{f}_j)}{\sum_{c=1}^{C} \exp(\bm{f}_c)} \in \R$ defines the $j$\textsuperscript{th} entry of the logits fed through the $\textrm{Softmax}(\cdot)$ function.
-Finally, we can write the first and second derivatives as follows
+Then, it follows that the the derivative we are interested in are
+\begin{equation}
+	\nabla_f \ell(h(f), y_i)|_{f=f_i} = - y_i + \sigma(f_i) \quad \text{ and } \quad  \nabla_{f\!f} \ell(h(f), y_i)|_{f=f_i} = \sigma(f_i) (1 - \sigma(f_i)).
+\end{equation}
+
+Moving to the multi class classification, the function outputs is no more a scalar but a vector of logits $\bm{f} \in \R^C$.
+The inverse link function for the categorical loss is the softmax function $\textrm{Softmax}(\bm{f}) : \R^C \mapsto \R^C$ defined as $h(\bm{f}) = \textrm{Softmax}(\bm{f}) = \frac{\exp(\bm{f})}{ \sum^C_{j=1} \exp(\bm{f}_j)} \in \R^C$.
+If we write the targets $y_i$ as a one-hot $C$-shaped one-hot encoding vector, we can write the negative log likelihood as:
 \begin{equation}
 \begin{aligned}
-	[\nabla_{\bm{f}} \ell(h(\bm{f}), \vy_i)|_{\bm{f}=\bm{f}_i}]_j &= \left[\textrm{Softmax}(\bm{f}) - \vy_i  \right]_j \\
-	\left[\textrm{diag}\left(\nabla_{\bm{f}\!\bm{f}} \ell(h(\bm{f}), \vy_i)|_{\bm{f}=\bm{f}_i}\right)\right]_{j} &= \left[\textrm{Softmax}(\bm{f})\right]_j (1 - \left[\textrm{Softmax}(\bm{f})\right]_j),
+	\ell(h(\bm{f}),\vy) &= - \log\left( \vy^\T \textrm{Softmax}(\bm{f})\right)\\
+	&= - y_i \cdot \log \left( \left[ \textrm{Softmax}(\bm{f}) \right]_i \right)
 \end{aligned}
 \end{equation}
-
 where $\left[\textrm{Softmax}(\bm{f})\right]_i = \frac{\exp(\bm{f}_i)}{\sum_{j=1}^{C} \exp(\bm{f}_j)} \in [0, 1]$ defines the $i$\textsuperscript{th} entry of the logits fed through the $\textrm{Softmax}(\cdot)$ function.
@@
 \end{equation}
-where we only need the $\textrm{diag}$ given our independence assumption.
 
@@
 \label{app:comp_compl}
-
 % Big O
@@
 % inversion O(M^3)
+In this section, we analyze the computational complexity of \our.
+We first need to train a neural network $f_\weights$ and then compute the posterior covariance matrix that characterizes our sparse GP representation of the model.
+The first step then requires the usual complexity cost for training a neural network, where defining the cost of a forward pass (and backward pass
+%\todo{these two should be similar, we can't cite the NTK paper were they are using this notation unfortunately}
+) as $[F\!P]$, this can roughly sketched as $\mathcal{O}(2  E  N[F\!P])$, where $E$ is the number of training epochs and  $N$ the number of training samples.
+Thus, there is no additional cost involved in the training phase of the neural network.
+
+Given the trained network, we construct the covariance function  which is defined through the NTK~\citep{jacot2018neural}.
+We relied on the Jacobian contraction implementation using PyTorch~\citep{paszke2019pytorch}.
+To compute the kernel Gram matrix for a batch of $B$ samples with this implementation has a computational complexity of $\mathcal{O}( B C [F\!P] + B^2 C^2 P)$, where $C$ is the number of NN outputs and $P$ is the number of parameters of the neural network.
+In \cref{eq:dual_sparse}, we compute $\MB_\vu$ iterating through all the $N$ training points to compute the $\vkzi$ and then use them to compute the outer product, that has a cost of $\mathcal{O}(M^2)$, with $M$ being the number of inducing points following the notation used in the main paper.
+The total cost of this operation becomes $\mathcal{O}(N M^2)$, which is also the dominating cost of our approach.
 
@@
 % GPU A100 Nvidia
+In practical terms, some care needs to be taken during the implementation, both in terms of memory consumption and numerical stability.
+For the former, we batched over the number of training samples, $N$, which keeps the memory consumption in check without need for any further approximations.
+The computation of the terms in \cref{eq:dual_sparse_post} require the inversion of an $M \times M$ matrix, that we implemented in a numerically stable manner by using Cholesky factorization.
+We also introduce a small jitter and clip of the GGN matrix for numerical stability where needed (see discussions in \cref{app:experiments}).
+ We run our experiments GPU clusters equipped with NVIDIA A100 GPUs.
 
@@
   \MBeta_{\vu, c} =  \sum_{i=1}^N \vkzic \,\hat{\beta}_{i, c} \, \vkzic^{\T} \in \R^{M \times M} ,    
-\label{eq:dual_sparse}
+\label{eq:app_dual_sparse}
 \end{equation}
@@
 
-The results reported in \cref{tbl:cl_table_1}, are obtained using the following hyperparameters and repeating the run five times with different seeds.
+The results reported in \cref{tbl:cl_table_1}, are obtained using the following hyperparameters and repeating the runs five times with different seeds.
 The results are in-line with what has been reported in previous work, notably even better for some of the baseline methods.

### 2023-05-24 paper/main.tex
rewrite of grads

@@
 
-\subsection{Computation of the dual parameters for different losses}\todo{just a placeholder}
+\subsection{Computation of the dual parameters for different losses}
 \label{app:losses}
@@
 \begin{equation}\label{eq:dual_param_app}
-  -\nabla_{f} \log p(y_i \mid f) |_{f=f_i} =  A'(f_i) - y_i
+  \nabla_{f}  \ell(h(f), y_i) |_{f=f_i} =  A'(f_i) - y_i
   \quad \text{and} \quad
-  \nabla^2_{f\!f} - \log p(y_i \mid f) |_{f=f_i} = A''(f_i).
+  \nabla^2_{f\!f} \ell(h(f), y_i)  |_{f=f_i} = A''(f_i).
 \end{equation}
@@
 \begin{equation}
-	\ell(h(f), y) = \frac{1}{2} (y_i -f_i)^2,% -\log \Norm( h(f) | y, \sigma^2) 	= - \log 
+	\ell(h(f_i), y_i) = \frac{1}{2} (y_i -f_i)^2,% -\log \Norm( h(f) | y, \sigma^2) 	= - \log 
 \end{equation}
@@
 	\left[\textrm{diag}\left(\nabla_{\bm{f}\!\bm{f}} \ell(h(\bm{f}), \vy_i)|_{\bm{f}=\bm{f}_i}\right)\right]_{j} &= \left[\textrm{Softmax}(\bm{f})\right]_j (1 - \left[\textrm{Softmax}(\bm{f})\right]_j),
-\end{aligned}
-\end{equation}
-
-where $\left[\textrm{Softmax}(\bm{f})\right]_i = \frac{\exp(\bm{f}_i)}{\sum_{j=1}^{C} \exp(\bm{f}_j)} \in [0, 1]$ defines the $i$\textsuperscript{th} entry of the logits fed through the $\textrm{Softmax}(\cdot)$ function.
-Finally, we can write the first and second derivatives as follows
-
-\begin{equation}
-\begin{aligned}
-	\nabla_f \ell(h(f), y_i)|_{f=f_i} &= - y_i + \left[ \textrm{Softmax}(\bm{f}) \right]_i \\
-	\nabla_{f\!f} \ell(h(f), y_i)|_{f=f_i} &= \left[\textrm{Softmax}(\bm{f})\right]_i (1 - \left[\textrm{Softmax}(\bm{f})\right]_i).
 \end{aligned}

### 2023-05-24 paper/main.tex
rewrite of grads

@@
 For this reason, computing the kernel $\kappa_c$ for classes $c$, for which the model has not observed any data yet, is not meaningful.
-\todo{probably better to word this differently}
 In practice, for our method we define $\bar{\MB}^{-1}_{t, c}$ to be $\bar{\MB}^{-1}_{t, c} = \MI_M$ $\forall c \not\in \mathcal{C}_t$, where $\mathcal{C}_t$ is the set of classes observed up to task t.

### 2023-05-24 paper/main.tex
rewrite of grads

@@
 DDPG uses a target value function to stabilise learning and for the soft target updates
-we used $\tau = 0.005$. \todo{What is $\tau$ ?}
+we used $\tau = 0.005$. 
 DDPG is an off-policy algorithm where the exploration policy samples from a noise process, which here was a Gaussian distribution with $\sigma=0.1$ and clipping at $0.3$.

### 2023-05-24 paper/main.tex
fixed small things

@@
 	q(\vu)
-	& \propto  \Norm(0, \MKzz) \prod_{i \in \dataset_\textrm{old}} \exp \! \left(-\frac{\hat{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 \right) \\
+	& \propto  \Norm(\mathbf{0}, \MKzz) \prod_{i \in \dataset_\textrm{old}} \exp \! \left(-\frac{\hat{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 \right) \\
         & \propto p(\vu) \Norm(\tilde{\vy}; \vu, \MB_\vu),
@@
 The sparse GP posterior $q(\vu)$ is proportional to the product between the prior over the inducing points $p(\vu)$ and a Gaussian term $\Norm(\tilde{\vy}; \vu, \MB_\vu)$, which arises from the sparse approximation to the likelihood.
-Replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$, we can see the similarity between the sparse GP and a linear model where the kernel is the linear kernel.
-We therefore use the key quadratic term from  $\Norm(\tilde{\vy}; \vu, \MB_\vu)$ as our regularizer as the missing data term, which after we take the $\log$ becomes $(\tilde{\vy} - \vu)^\top \bar{\MB}^{-1}(\tilde{\vy} - \vu)$.
+Replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$, we can see the similarity between the sparse GP and a linear model, for which the kernel is the linear kernel.
+Therefore, we use the quadratic term from  $\Norm(\tilde{\vy}; \vu, \MB_\vu)$ as our regularizer in place of the missing data term.
+By taking the $\log(\cdot)$, the regularizer becomes $(\tilde{\vy} - \vu)^\top \bar{\MB}^{-1}(\tilde{\vy} - \vu)$.
 Given that $\tilde{\vy}$ are in the function space we can instead us simply the previous neural network predictions $f^{\textrm{old}}_\weights(\vz_i)$ and save computations.
@@
 We provide further details for the experiments presented in the main paper.
+In tables throughout the paper, we mark the best-performing method/setting by typesetting them boldface.
+Following this, we check with a two-tailed $t$-test whether the bolded entry significantly differs from the rest.
+Those not differing from the best performing one with a significance level of 5\% are also bolded.
 The illustrative examples in \cref{fig:teaser,fig:banana} include toy problems for regression and classification.

### 2023-05-24 paper/main.tex
fixed small things
updated app. with zip file sentence
small typo

@@
 We also introduce a small jitter and clip of the GGN matrix for numerical stability where needed (see discussions in \cref{app:experiments}).
- We run our experiments GPU clusters equipped with NVIDIA A100 GPUs.
+ We run our experiments on GPU clusters equipped with NVIDIA A100 GPUs.
 
@@
 %
-We provide further details for the experiments presented in the main paper.
+In this section, we provide further details for the experiments presented in the main paper.
+In addition to this manuscript, we provide a zip file all the code to reproduce our experiments.
 In tables throughout the paper, we mark the best-performing method/setting by typesetting them boldface.
@@
 Those not differing from the best performing one with a significance level of 5\% are also bolded.
+
 The illustrative examples in \cref{fig:teaser,fig:banana} include toy problems for regression and classification.

### 2023-05-24 paper/main.tex
fixed small typos

@@
 %\todo{these two should be similar, we can't cite the NTK paper were they are using this notation unfortunately}
-) as $[F\!P]$, this can roughly sketched as $\mathcal{O}(2  E  N[F\!P])$, where $E$ is the number of training epochs and  $N$ the number of training samples.
+) as $[F\!P]$, this can be roughly sketched as $\mathcal{O}(2  E  N[F\!P])$, where $E$ is the number of training epochs and  $N$ the number of training samples.
 Thus, there is no additional cost involved in the training phase of the neural network.
 
-Given the trained network, we construct the covariance function  which is defined through the NTK~\citep{jacot2018neural}.
-We relied on the Jacobian contraction implementation using PyTorch~\citep{paszke2019pytorch}.
-To compute the kernel Gram matrix for a batch of $B$ samples with this implementation has a computational complexity of $\mathcal{O}( B C [F\!P] + B^2 C^2 P)$, where $C$ is the number of NN outputs and $P$ is the number of parameters of the neural network.
-In \cref{eq:dual_sparse}, we compute $\MB_\vu$ iterating through all the $N$ training points to compute the $\vkzi$ and then use them to compute the outer product, that has a cost of $\mathcal{O}(M^2)$, with $M$ being the number of inducing points following the notation used in the main paper.
+Given the trained network, we construct the covariance function, which is defined through the NTK~\citep{jacot2018neural}.
+We relied on the Jacobian contraction formulation implemented using PyTorch~\citep{paszke2019pytorch}.
+Computing the kernel Gram matrix for a batch of $B$ samples with this implementation has a computational complexity of $\mathcal{O}( B C [F\!P] + B^2 C^2 P)$, where $C$ is the number of outputs and $P$ is the number of parameters of the neural network.
+In \cref{eq:dual_sparse}, we compute $\MB_\vu$ iterating through all the $N$ training points to compute all the $\vkzi$.
+Then, we use them to compute the outer product, which has a cost of $\mathcal{O}(M^2)$, with $M$ being the number of inducing points.
 The total cost of this operation becomes $\mathcal{O}(N M^2)$, which is also the dominating cost of our approach.
@@
 % GPU A100 Nvidia
-In practical terms, some care needs to be taken during the implementation, both in terms of memory consumption and numerical stability.
-For the former, we batched over the number of training samples, $N$, which keeps the memory consumption in check without need for any further approximations.
-The computation of the terms in \cref{eq:dual_sparse_post} require the inversion of an $M \times M$ matrix, that we implemented in a numerically stable manner by using Cholesky factorization.
-We also introduce a small jitter and clip of the GGN matrix for numerical stability where needed (see discussions in \cref{app:experiments}).
- We run our experiments on GPU clusters equipped with NVIDIA A100 GPUs.
+In practical terms, some care needs to be taken during the implementation, both regarding memory consumption and numerical stability.
+For the former, we batched over the number of training samples, $N$, which keeps the memory consumption in check without the need for any further approximations.
+The computation of the terms in \cref{eq:dual_sparse_post} requires the inversion of an $M \times M$ matrix, that we implemented in a numerically stable manner using Cholesky factorization.
+We also introduce a small jitter and clip the GGN matrix for numerical stability where needed (see discussions in \cref{app:experiments}).
+ We run our experiments on a cluster equipped with NVIDIA A100 GPUs.
 
@@
 For continual learning, the model cannot access the training data from previous tasks up to task $t-1$, denoted here as $\dataset_\textrm{old} = \bigcup_{s=1}^{t-1} \dataset_s$, and for each new task $t$ receives a new chunk of data $\dataset_\textrm{new} = \dataset_t$.
-On the other hand, in the supervised learning setting (described in \cref{sec:methods}), the neural network model has access to all the training data at once, \ie, the objective we are trying to optimize is
+In contrast, in the supervised learning setting (described in \cref{sec:methods}), the neural network model has access to all the training data at once, and then the objective we are trying to optimize is
 \begin{equation}
@@
 Therefore, we use the quadratic term from  $\Norm(\tilde{\vy}; \vu, \MB_\vu)$ as our regularizer in place of the missing data term.
-By taking the $\log(\cdot)$, the regularizer becomes $(\tilde{\vy} - \vu)^\top \bar{\MB}^{-1}(\tilde{\vy} - \vu)$.
-Given that $\tilde{\vy}$ are in the function space we can instead us simply the previous neural network predictions $f^{\textrm{old}}_\weights(\vz_i)$ and save computations.
+By taking the $\log$, the regularizer becomes $(\tilde{\vy} - \vu)^\top \bar{\MB}^{-1}(\tilde{\vy} - \vu)$.
+Given that $\tilde{\vy}$ are in the function space, we can instead use the previous neural network predictions $f^{\textrm{old}}_\weights(\vz_i)$ and save computations.
 
@@
 The results reported in \cref{tbl:imagesuper} used a learning rate of $10^{-4}$, and a prior precision of $\delta = 0.0013$ for FMNIST and $\delta = 0.0001$ for MNIST \todo{double check}.
-
 In \cref{sec:image} in the main paper, we included experiments on image data sets.
@@
 training the neural network using Adam for $500$ epochs with a batch size of $512$.
-The results reported in \cref{tbl:imagesuper} used a learning rate of $10^{-4}$
-and we ran each experiment for $5$ seeds.
-The MNIST experiments used a prior precision of $\delta=0.0008$
-and the FMNIST experiments used a prior precision of $\delta=0.0013$.
+The results reported in \cref{tbl:imagesuper} used a learning rate of $10^{-4}$, and we ran each experiment for $5$ seeds.
+The MNIST experiments used a prior precision of $\delta=0.0008$, and the FMNIST experiments used a prior precision of $\delta=0.0013$.
 The experiments with MNIST  used an MLP with two hidden layers of width 128 and Tanh activations.
-In the FMNIST experiments we followed \cite{immer2021improving} and used a CNN
-architecture with two fully connected classification layers and Tanh activations.
+In the FMNIST experiments, we followed \cite{immer2021improving} and used a CNN architecture composed of three convolutional layers with ReLU activations and three fully connected classification layers with Tanh activations.
 

### 2023-05-30 workshop/main.tex
Workshop version

--- 2023-05-24 paper/main.tex
@@
-% !TeX spellcheck = en_US
+%%%%%%%% ICML 2023 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%
+
 \documentclass{article}
 
-% Pass options to natbib
-\PassOptionsToPackage{numbers, compress}{natbib}
-
-% NeurIPS packages
-\usepackage[]{neurips_2023}
+% Recommended, but optional, packages for figures and better typesetting:
 \usepackage[utf8]{inputenc} % allow utf-8 input
 \usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-%\usepackage{hyperref}       % hyperlinks
-\usepackage{url}            % simple URL typesetting
-\usepackage{booktabs}       % professional-quality tables
-\usepackage{amsfonts}       % blackboard math symbols
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-\usepackage{xcolor}         % colors
+\usepackage{microtype}
+\usepackage{graphicx}
+
+% For theorems and such
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{mathtools}
+\usepackage{amsthm}
+
+% \usepackage{subfigure}
+\usepackage{booktabs} % for professional tables
+\usepackage[aboveskip=2pt]{subcaption} % This needs to be here to have captions display correctly
+\usepackage{wrapfig}
+
+% hyperref makes hyperlinks in the resulting PDF.
+% If your build breaks (sometimes temporarily if a hyperlink spans a page)
+% please comment out the following usepackage line and replace
+% \usepackage{icml2023} with \usepackage[nohyperref]{icml2023} above.
+%\usepackage{hyperref}
+
+% Attempt to make hyperref and algorithmic work together better:
+\newcommand{\theHalgorithm}{\arabic{algorithm}}
+
+% Use the following line for the initial blind version submitted for review:
+\usepackage[nohyperref]{icml2023_dp4ml}
+
+% If accepted, instead use the following line for the camera-ready submission:
+%\usepackage[accepted]{icml2023_dp4ml}
+
+% if you use cleveref..
+% \usepackage[capitalize,noabbrev]{cleveref}
+%\usepackage[capitalize,nameinlink]{cleveref}
+%\crefname{section}{Sec.}{Secs.}
+%\crefname{appendix}{App.}{Apps.}
+%\crefname{algorithm}{Alg.}{Algs.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% THEOREMS
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\theoremstyle{plain}
+%\newtheorem{theorem}{Theorem}[section]
+%\newtheorem{proposition}[theorem]{Proposition}
+%\newtheorem{lemma}[theorem]{Lemma}
+%\newtheorem{corollary}[theorem]{Corollary}
+%\theoremstyle{definition}
+%\newtheorem{definition}[theorem]{Definition}
+%\newtheorem{assumption}[theorem]{Assumption}
+%\theoremstyle{remark}
+%\newtheorem{remark}[theorem]{Remark}
+
+%Definitions and macros
+%\input{defns}
+
+% Todonotes is useful during development; simply uncomment the next line
+%    and comment out the line below the next line to turn off comments
+%\usepackage[disable,textsize=tiny]{todonotes}
+\usepackage[textsize=tiny]{todonotes}
+
+% TikZ
+\usepackage{tikz,pgfplots}
+\usetikzlibrary{shapes,arrows,positioning,calc}
+\usetikzlibrary{decorations.pathmorphing}
+\usepackage[outline]{contour}
+\pgfkeys{/pgf/number format/.cd,1000 sep={}}
 
@@
 \usepackage{bm}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
+%\usepackage{algpseudocode}
+%\usepackage{algorithm}
 \usepackage{derivative}
@@
 
-%\title{Investigatin Uncertainty Quantification in Model-based Reinforcement Learning}
-% \title{Model-based Reinforcement Learning with Fast Posterior Updates}
-%\title{Sequential Decision-Making under Uncertainty with Big Data}
-% \title{Neural Network to Vatiational Sparse Gaussian Process: For Adaptive Exploration}
-% \title{Neural Network to Sparse Variational Gaussian Process: For Updates in Sequential Decision Making}
-% \title{Adapting Neural Networks to New Data For Updates in Sequential Decision Making via Gaussian Processes}
-% \title{Converting Neural Networks to Gaussian Processes for Sequential Decision-Making Under Uncertainty}
-%\title{Sparse Function Space Representation of Neural Networks for Exploration and Retention}
-%\title{Sparse Function-space Neural Networks}
-\title{Sparse Function-space Representation \\ of Neural Networks}% for Adaptation and Retention}
-\author{%
-  Aidan Scannell\textsuperscript{\star} \\
-  Aalto University \\
-  Finnish Center for Artificial Intelligence \\
-  \texttt{aidan.scannell@aalto.fi}
-  \And
-  Riccardo Mereu\textsuperscript{\star} \\
-  Aalto University\\
-  \texttt{riccardo.mereu@aalto.fi}
-  \And
-  Paul Chang \\
-  Aalto University\\
-  \texttt{paul.chang@aalto.fi}
-  \And
-  Ella Tamir \\
-  Aalto University\\
-  \texttt{ella.tamir@aalto.fi}
-  \And
-  Joni Pajarinen \\
-  Aalto University\\
-  \texttt{joni.pajarinen@aalto.fi}
-  \And
-  Arno Solin \\
-  Aalto University\\
-  \texttt{arno.solin@aalto.fi}
-}
+% The \icmltitle you define below is probably too long as a header.
+% Therefore, a short form for the running title is supplied here:
+\icmltitlerunning{Sparse Function-space Representation of Neural Networks}
 
@@
 
-\maketitle
+\twocolumn[
+\icmltitle{Sparse Function-space Representation of Neural Networks}
+
+% It is OKAY to include author information, even for blind
+% submissions: the style file will automatically remove it for you
+% unless you've provided the [accepted] option to the icml2023
+% package.
+
+% List of affiliations: The first argument should be a (short)
+% identifier you will use later to specify author affiliations
+% Academic affiliations should list Department, University, City, Region, Country
+% Industry affiliations should list Company, City, Region, Country
+
+% You can specify symbols, otherwise they are numbered in order.
+% Ideally, you should not use this facility. Affiliations will be numbered
+% in order of appearance and this is the preferred way.
+\icmlsetsymbol{equal}{*}
+
+\begin{icmlauthorlist}
+\icmlauthor{Firstname1 Lastname1}{equal,yyy}
+\icmlauthor{Firstname2 Lastname2}{equal,yyy,comp}
+\icmlauthor{Firstname3 Lastname3}{comp}
+\icmlauthor{Firstname4 Lastname4}{sch}
+\icmlauthor{Firstname5 Lastname5}{yyy}
+\icmlauthor{Firstname6 Lastname6}{sch,yyy,comp}
+\icmlauthor{Firstname7 Lastname7}{comp}
+%\icmlauthor{}{sch}
+\icmlauthor{Firstname8 Lastname8}{sch}
+\icmlauthor{Firstname8 Lastname8}{yyy,comp}
+%\icmlauthor{}{sch}
+%\icmlauthor{}{sch}
+\end{icmlauthorlist}
+
+\icmlaffiliation{yyy}{Department of XXX, University of YYY, Location, Country}
+\icmlaffiliation{comp}{Company Name, Location, Country}
+\icmlaffiliation{sch}{School of ZZZ, Institute of WWW, Location, Country}
+
+\icmlcorrespondingauthor{Firstname1 Lastname1}{first1.last1@xxx.edu}
+\icmlcorrespondingauthor{Firstname2 Lastname2}{first2.last2@www.uk}
+
+% You may provide any keywords that you
+% find helpful for describing your paper; these are used to populate
+% the "keywords" metadata in the PDF but will not be shown in the document
+\icmlkeywords{Machine Learning, ICML}
+
+\vskip 0.3in
+]
+
+% this must go after the closing bracket ] following \twocolumn[ ...
+
+% This command actually creates the footnote in the first column
+% listing the affiliations and the copyright notice.
+% The command takes one argument, which is text to display at the start of the footnote.
+% The \icmlEqualContribution command is standard text for equal contribution.
+% Remove it (just {}) if you do not need this facility.
+
+%\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
+\printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.
 
 \begin{abstract}
-% OLDER VERSION
-%Sequential learning paradigms such as Continual Learning (CL) or Reinforcement Learning (RL) pose a challenge for gradient-based deep learning techniques as they struggle to incorporate new data and retain previous knowledge.
-Existing methods for converting neural networks from weight to function space allow a probabilistic treatment of the distribution over the function learned by the neural networks but are computationally expensive.
-We propose a method that converts a neural network to a low-rank functional representation as a sparse Gaussian process.
-With this approach, we can build a compact representation of the function encoded by the neural network that can replace previous data in continual settings and be used for fast adaptation in RL, avoiding full retraining of the model.
-%
-% Rewrite on 2023-05-10
-%Deep neural networks are known to lack uncertainty estimates, struggle to incorporate new data, and fail to retain previous knowledge.
-We present a method that mitigates these issues by transforming a weight-space neural network to a low-rank function-space representation, via the so-called dual parameters.
-In contrast to previous work, we model the joint distribution across the entire data set rather than a subset.
-This offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst retaining predictive performance.
-We demonstrate the proposed approach for quantifying uncertainty in supervised learning and maintaining a compact representation in sequential learning.\looseness-1
-
 Deep neural networks are known to lack uncertainty estimates, struggle to incorporate new data, and suffer from catastrophic forgetting.
@@
 We demonstrate the proposed approach for quantifying uncertainty in supervised learning and maintaining an expressive functional representation for sequential learning.\looseness-1
-
 \end{abstract}
 
-%, maintaining a summary representation in continual learning,
-
 \section{Introduction}
-\label{sec:intro}
 %
@@
 
-%Secondly, how to retain information from previous tasks whilst learning new tasks where the tasks are such as Continual Learning (CL, \cite{de2021continual})
-%Thirdly and differently from the CL problem is that given some data from the same distribution
+\begin{figure}[t!]
+  \centering\scriptsize
+  % Figure options
+  \pgfplotsset{axis on top,scale only axis,width=\figurewidth,height=\figureheight, ylabel near ticks,ylabel style={yshift=-2pt},y tick label style={rotate=90},legend style={nodes={scale=1., transform shape}},tick label style={font=\tiny,scale=1}}
+  \pgfplotsset{xlabel={Input, $x$},axis line style={rounded corners=2pt}}
+  % Set figure 
+  \setlength{\figurewidth}{.19\textwidth}
+  \setlength{\figureheight}{\figurewidth}
+  %
+  \def\inducing{\large Sparse inducing points}
+  %
+  \begin{subfigure}[c]{.52\columnwidth}
+    \raggedleft
+    \pgfplotsset{ylabel={Output, $y$}}
+    \input{./fig/regression-nn.tex}%
+  \end{subfigure}
+  \hfill  
+  \begin{subfigure}[c]{.02\columnwidth}
+    \centering
+    \tikz[overlay,remember picture]\node(p0){};
+  \end{subfigure}  
+  \hfill
+  \begin{subfigure}[c]{.4\columnwidth}
+    \raggedleft
+    \pgfplotsset{yticklabels={,,},ytick={\empty}}
+    \input{./fig/regression-nn2svgp.tex}%
+  \end{subfigure}
+%  \hfill  
+%  \begin{subfigure}[c]{.01\textwidth}
+%    \centering
+%    \tikz[overlay,remember picture]\node(p1){};
+%  \end{subfigure}  
+%  \hfill
+%  \begin{subfigure}[c]{.28\textwidth}
+%    \raggedleft
+%    \pgfplotsset{yticklabels={,,},ytick={\empty}}        
+%    \input{./fig/regression-update.tex}%
+%  \end{subfigure}
+  \vspace*{-1em}
+  \caption{\textbf{Regression example on an MLP with two hidden layers.} Left:~Predictions from the trained neural network.
+Right:~Our approach summarizes all the training data with the help of a set of inducing points.} %The model captures the predictive mean and uncertainty, and (right) makes it possible to incorporate new data without retraining the model.}
+  \label{fig:teaser} 
+  % 
+  \begin{tikzpicture}[remember picture,overlay]
+    % Arrow style
+    \tikzstyle{myarrow} = [draw=black!80, single arrow, minimum height=14mm, minimum width=2pt, single arrow head extend=4pt, fill=black!80, anchor=center, rotate=0, inner sep=5pt, rounded corners=1pt]
+    % Arrows
+    \node[myarrow] (p0-arr) at ($(p0) + (1em,1.5em)$) {};
+    %\node[myarrow] (p1-arr) at ($(p1) + (1em,1.5em)$) {};
+    % Arrow labels
+    \node[font=\scriptsize\sc,color=white] at (p0-arr) {\our};
+    %\node[font=\scriptsize\sc,color=white] at (p1-arr) {new data};   
+  \end{tikzpicture}
+  \vspace*{-2em}
+\end{figure}
 
@@
 
-%Need uncertainty and adaptive methods
-%Dual formulation in GPs space solves this
-%Talk about planning and exploration in RL.
-
-The contributions of this paper are as follows:
-%
-{\em (i)}~We introduce \our, a new approach for building a sparse functional representation of a neural network.
-{\em (ii)}~We demonstrate that, despite its sparsity, our method effectively captures predictive uncertainty, provides a means of updating the model post-training, and gives a compact regularizer suitable for continual learning.
-{\em (iii)}~We provide extensive experiments for showcasing our approach and demonstrate significance and applicability across supervised, continual, and reinforcement learning, aiming to stimulate future use of the approach.
-
-%List the contributions.
-%The contributions of the paper our is as follows:
-%\begin{itemize}
-%\item We show how to take a trained neural network and convert it to a dual sparse GP.
-We are able to do this without retraining a variational objective for the Sparse GP.
-Our sparse GP uses the variational formulation, and thus gives better uncertainty estimates than other no variational sparse approaches used previously.
-%\item The sparse GP now gives us a compact representation of our parameters in the function space.
-We can therefore take advantage of the dual parameters formulation for fast conditioning of new data in to our posterior avoiding retraining of the neural network.
-Crucially this allows for fast adaptation of models that our used in sequential decision making.
-We show how this is effective in the planning stage of model-based reinforcement exploration.
-%\end{itemize}
-
-%
-%
-%\begin{itemize}
-%  \item Many real-world problems require learning-based systems that can adapt to new data.
-%  \begin{itemize}
-%    % \item For example, in domains such as robotics and healthcare,
-%    \item For example, when controlling robots in non-stationary environments it is important for the robot to adapt to the changing dynamics.
-%    \item However neural networks rely upon gradient-based optimisation.
-%    \item Uncertainty can be used to improve sample efficiency via targeted exploration.
-%    \item Uncertainty can be used to handle risk in decision making.
-%  \end{itemize}
-%
-%  \item Gaussian processes can easily adapt to new data and they offer well-calibrated uncertainty estimates.
-%  \begin{itemize}
-%    \item However, they don't scale to high-dimensional and large data sets.
-%  \end{itemize}
-%  \item
-%  \begin{itemize}
-%    \item
-%  \end{itemize}
-%\end{itemize}
-
-\begin{figure}[t!]
-  \centering\scriptsize
-  % Figure options
-  \pgfplotsset{axis on top,scale only axis,width=\figurewidth,height=\figureheight, ylabel near ticks,ylabel style={yshift=-2pt},y tick label style={rotate=90},legend style={nodes={scale=1., transform shape}},tick label style={font=\tiny,scale=1}}
-  \pgfplotsset{xlabel={Input, $x$},axis line style={rounded corners=2pt}}
-  % Set figure 
-  \setlength{\figurewidth}{.28\textwidth}
-  \setlength{\figureheight}{\figurewidth}
-  %
-  \def\inducing{\large Sparse inducing points}
-  %
-  \begin{subfigure}[c]{.34\textwidth}
-    \raggedleft
-    \pgfplotsset{ylabel={Output, $y$}}
-    \input{./fig/regression-nn.tex}%
-  \end{subfigure}
-  \hfill  
-  \begin{subfigure}[c]{.01\textwidth}
-    \centering
-    \tikz[overlay,remember picture]\node(p0){};
-  \end{subfigure}  
-  \hfill
-  \begin{subfigure}[c]{.28\textwidth}
-    \raggedleft
-    \pgfplotsset{yticklabels={,,},ytick={\empty}}
-    \input{./fig/regression-nn2svgp.tex}%
-  \end{subfigure}
-  \hfill  
-  \begin{subfigure}[c]{.01\textwidth}
-    \centering
-    \tikz[overlay,remember picture]\node(p1){};
-  \end{subfigure}  
-  \hfill
-  \begin{subfigure}[c]{.28\textwidth}
-    \raggedleft
-    \pgfplotsset{yticklabels={,,},ytick={\empty}}        
-    \input{./fig/regression-update.tex}%
-  \end{subfigure}
-  \caption{\textbf{Regression example on an MLP with two hidden layers.} Left:~Predictions from the trained neural network.
-Middle:~Our approach summarizes all the training data with the help of a set of inducing points.
-The model captures the predictive mean and uncertainty, and (right) makes it possible to incorporate new data without retraining the model.}
-  \label{fig:teaser} 
-  % 
-  \begin{tikzpicture}[remember picture,overlay]
-    % Arrow style
-    \tikzstyle{myarrow} = [draw=black!80, single arrow, minimum height=14mm, minimum width=2pt, single arrow head extend=4pt, fill=black!80, anchor=center, rotate=0, inner sep=5pt, rounded corners=1pt]
-    % Arrows
-    \node[myarrow] (p0-arr) at ($(p0) + (1em,1.5em)$) {};
-    \node[myarrow] (p1-arr) at ($(p1) + (1em,1.5em)$) {};
-    % Arrow labels
-    \node[font=\scriptsize\sc,color=white] at (p0-arr) {\our};
-    \node[font=\scriptsize\sc,color=white] at (p1-arr) {new data};   
-  \end{tikzpicture}
-\end{figure}
-
-\subsection{Related work}
-\label{sec:related}
-%
-% General Bayesian deep learning
-\textbf{Bayesian deep learning}
-Probabilistic methods in deep learning~\cite{Wilson:ensembles,neal1995bayesian} have recently gained increasing attention in the machine learning community as a means for uncertainty quantification (\eg, \cite{kendall2017what,wilson2020bayes}) and model selection (\eg,~\cite{immer2021scalable,antoran2022marginal}) with advancements in prior specification (\eg, \cite{cho2009kernel,meronen2020stationary,meronen2021periodic,fortuin2021bayesian,nalisnick2018do}) and efficient approximate inference under the specified model.
-Calculating the posterior distribution of a Bayesian neural network is usually intractable, and approximate inference techniques need to be used, such as variational inference \cite{blei2017variational}, deep ensembles \cite{lakshminarayanan2017simple}, MC dropout \cite{gal2016dropout}, or Laplace approximation \cite{ritter2018kfac,kristiadi2020being,immer2021improving}---each with its own set of strengths and weaknesses.
-
-%\textbf{Function-space methods}
-%One common approach for uncertainty with neural networks is a Laplace-GGN approximation \citep{daxberger2021laplace}, which takes a trained neural network and linearises it around the optimal weights.
-The Hessian can be efficiently approximated using the generalized Gauss--Newton approximation (GGN)~\cite{botev2017practical} but typically involves a cubic scaling in the number of parameters, in practice a further approximation such as the Kronecker factorisation \cite{martens2015optimizing,ritter2018kfac} is needed.
-The resulting linear model can be used to obtain uncertainty estimates and refine the neural network predictions \citep{immer2021scalable}, and is linear with respect to the weights.
-Therefore, as shown in \cite{immer2021scalable, khan2019approximate,maddox2021fast}, the linear model can be converted to a GP, which is then used to obtain the uncertainty estimates.
-
-% Introduce the laplace GGN + shortcomings
-\textbf{Function-space methods}
-Function-space perspectives on uncertainty in neural networks often use a Laplace-GGN approximation \citep{daxberger2021laplace}, which linearizes a trained neural network around MAP weights and approximates the neural network's Hessian using the generalized Gauss--Newton approximation (GGN, \cite{botev2017practical}).
-%\todo{Could modify the sentence a bit, maybe "The Laplace-GGN approximates the Hessian by using..."}
-%The Hessian can be efficiently approximated using the generalized Gauss--Newton approximation . 
-While efficient, the GNN suffers from cubic scaling in parameter count, necessitating approximations like Kronecker factorisation \cite{martens2015optimizing, ritter2018kfac}.
-This linear model (with respect to the weights) refines predictions and provides uncertainty estimates \citep{immer2021scalable}.
-It has a convenient interpretation as a GP \cite{immer2021scalable, khan2019approximate, maddox2021fast}.
-%
-However, the GP's cubic $\mathcal{O}(N^3)$ scaling with data points $N$ requires costly approximations, often resorting to using data subsets \cite{immer2021scalable}.
-In the GP community, sparse approximations have mitigated this scaling issue (\eg, \cite{titsias2009variational,hensman2013gaussian}),
-but combining neural network linearization with sparse GP methods remains underexplored.
-Recent work has explored converting NNs to sparse variational GPs \cite{ortega2023variational}, however, their method requires separately retraining a GP model.
-% However,
-% unclear without resorting to subset methods or separately retraining a GP model \cite{ortega2023variational}.
-Our work addresses this by utilizing the GP's dual parameters \cite{csato2002sparse}, previously applied to non-conjugate likelihood models~\cite{adam2021dual}.\looseness-1
-
-% \todo{Could add something on subset methods here, for example 'which do not retain information from the full dataset' or something like that}.
-%wang2019exact
-%
-%However, the GP introduces a cubic $\mathcal{O}(N^3)$ scaling in the number of data points $N$.
-Previous approaches apply crude approximations to alleviate the computational costs, \eg, by considering only a subset of the training data \cite{immer2021scalable}.
-In the GP community, the scaling problem is not seen as an issue any more due to efficient and stochastic methods for sparse approximations (\eg, \cite{hensman2013gaussian,wang2019exact}).
-However, it is not entirely clear how to combine the linearization of the neural network with sparse methods \cite{titsias2009variational} without falling back to crude subset methods.
-We tackle this problem by framing the problem in the dual parameters \cite{csato2002sparse} of the GP that has previously been used for non-conjugate likelihood models in GPs \cite{adam2021dual}.
-
-% CL section
-%\textbf{Function-space methods for sequential learning} The central problem in continual learning is how to deal with the non-stationary nature of the training distribution, which causes the training process to overwrite the previously learnt parameters---leading to the model forgetting the previously learnt functions.
-%The approaches proposed in the CL literature can be categorized into inference-based, rehearsal-based, and model-based methods; we refer the reader to \citep{parisi2019continual, de2021continual} for complete reviews.
-The methods in the first category usually tackle this problem with weight-space regularization, such as EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke2017continual}), or VCL~\citep{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone.
-%However, encoding functional knowledge in the weights does not guarantee a good quality of the predictions, thus a better to introduce a function-space regularization \citep{li2018lwf, benjamin2018measuring, titsias2019functional, buzzega2020dark, pan2020continual, rudner2022continual}.
-These methods bridge the gap between objective and rehearsal-based methods since they rely on a subset of the training data for each task to compute the regularization term.
-Recently proposed methods, such as DER~\citep{buzzega2020dark}, FROMP~\citep{pan2020continual}, and S-FSVI~\citep{rudner2022continual} achieve state-of-the-art performances among the objective-based techniques in several CL benchmarks.
-
-\textbf{Function-space methods for sequential learning} 
-Continual learning (CL) hinges on how to deal with a non-stationary training distribution, wherein the training process may overwrite previously learned parameters, causing catastrophic forgetting \citep{mccloskey1989catastrophic}.
-CL approaches fall into inference-based, rehearsal-based, and model-based methods (see \cite{parisi2019continual, de2021continual} for an overview).
-The methods in the first category usually tackle this problem with weight-space regularization, such as EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke2017continual}), or VCL~\citep{nguyen-tuongModel2009}, that induce retention of previously learned information in the weights alone.
-However, regularizing the weights does not guarantee good quality predictions.
-Function-space regularization techniques~\cite{li2018lwf, benjamin2018measuring, titsias2019functional, buzzega2020dark, pan2020continual, rudner2022continual} address this by relying on training data subsets for each task to compute a regularization term.
-These methods can be seen as a hybrid between objective and rehearsal-based methods, since they also store a subset of training data to construct the regularization term.
-Recent function-based methods, \eg, DER~\citep{buzzega2020dark}, FROMP~\citep{pan2020continual}, and S-FSVI~\citep{rudner2022continual}, achieve state-of-the-art performance among the objective-based techniques in several CL benchmarks.
-\looseness-2
-
-\textbf{Uncertainty quantification in RL}
-A key challenge in RL is balancing the trade-off between exploration and exploitation \cite{sutton2018reinforcement}.
-%That is, should an agent select actions that it knows will lead to high reward %(exploitation), or should it
-%select new ones in hope to discover actions leading to higher reward (exploration).
-One promising direction to balancing this trade-off is to model the uncertainty associated with a learned transition dynamics model and use it to guide exploration.
-Prior work has taken an expectation over the dynamic model's posterior \cite{deisenroth2011pilco,kamtheDataEfficient2018,chuaDeepReinforcementLearning2018},
-sampled from it (akin to Thompson sampling but referred to as posterior sampling in RL) \cite{dearden1999model,osbandMoreEfficientReinforcement2013},
-and used it to implement optimism in the face of uncertainty using upper confidence bounds \cite{curiEfficient2020,jaksch2010near}.
-No single strategy has emerged as a go-to method and we highlight that these strategies are only as good as their uncertainty estimates.
-Previous approaches have used GPs \cite{deisenroth2011pilco,kamtheDataEfficient2018},
-ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
-and variational inference \cite{galImproving2016,houthooftVIME2017}.
-However, each method has its pros and cons.
-In this paper, we present a method which combines some of the pros from NNs with the benefits of GPs.
-
-%However, there has been little leveraging
-
-% Another classical and provable exploration theory in RL is based on optimism
-% \todo{cite UCRL paper}
-% Recent work has even extended these ideas to deep RL \cite{curiEfficient2020}.
-
-% An alternative approach is to sample from the dynamic model's posterior, akin to Thompson sampling but referred to as posterior sampling RL
-% Another classical and provable exploration theory in RL is based on optimism in the face of uncertainty.
-% \todo{cite UCRL paper}
-% Recent work has even extended these ideas to deep RL \cite{curiEfficient2020}.
-% These strategies are only as good as their uncertainty estimates.
-% Prior work has learned dynamics models using GPs \cite{deisenrothPILCO2011,kamtheDataEfficient2018},
-% ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
-% and variational inference \cite{galImproving2016,houthooftVIME2017}.
-
-%%
-
-% It should be written clearly that our method actually is doing a "functional" reharsal, because we store a set of inducing points that are replayed in order to check if the logits change.
-
-% Other methods that could be worth citing are 
-% Learning without forgetting \citep{li2018lwf} :  first paper proposing to use functional regularization computes a smoothed version of the current logits for the new examples at the beginning of each task, minimizing their drift during training.
-It doesn't have any set of inducing points
-% \citep{benjamin2018measuring} this is not a proper CL paper, but it's usually referred in the functional regularization papers, because shows how to improve Adam with measuring the network difference in function space.
-They also have some easy CL examples there.
-
-%Why we need uncertainty and adaptiveness
-%How to adapt to new information is a limitation of current machine learning models.
-The problem is specifically relevant when we combine a model with a decision-making process.
-In such a sequential setting, an agent typically makes decisions in an environment and obtains new information and would ideally incorporate the information into their parameters.
-Not only do we need models that adapt to new informatoion but all express uncertainty over the models predictions.
-The reason being twofold: in many applications, \eg\ healthcare, autonomous driving is an essential requirement, and many advanced exploration techniques require uncertainty to determine where to query next.
-
-\begin{figure}[t!]
-  \centering
-  % Set figure size
-  \setlength{\figurewidth}{.31\textwidth}
-  \setlength{\figureheight}{\figurewidth}
-  %
-  % Colours
-  \definecolor{C0}{HTML}{DF6679}
-  \definecolor{C1}{HTML}{69A9CE}
-  %
-  \begin{tikzpicture}[outer sep=0,inner sep=0]
-
-    \newcommand{\addfig}[2]{
-    \begin{scope}
-      \clip[rounded corners=3pt] ($(#1)+(-.5\figurewidth,-.5\figureheight)$) rectangle ++(\figurewidth,\figureheight);
-      \node (#2) at (#1) {\includegraphics[width=1.05\figurewidth]{./fig/#2}};
-    \end{scope}
-    %\draw[rounded corners=3pt,line width=1.2pt,black!60] ($(#1)+(-.5\figurewidth,-.5\figureheight)$) rectangle ++(\figurewidth,\figureheight);
-    }
-
-    % The neural network
-    \addfig{0,0}{banana-nn}
-
-    % The nn2svgp
-    \addfig{1.1\figurewidth,0}{banana-nn2svgp}
-
-    % The update
-    \addfig{2.2\figurewidth,0}{banana-hmc}
-
-    % The arrow
-    \tikzstyle{myarrow} = [draw=black!80, single arrow, minimum height=14mm, minimum width=2pt, single arrow head extend=4pt, fill=black!80, anchor=center, rotate=0, inner sep=5pt, rounded corners=1pt]
-    \tikzstyle{myblock} = [draw=black!80, minimum height=4mm, minimum width=7mm, fill=black!80, anchor=center, rotate=0, inner sep=5pt, rounded corners=1pt]
-    \node[myarrow] (first-arr) at ($(banana-nn)!0.5!(banana-nn2svgp)$) {};
-    \node[myblock] (second-arr) at ($(banana-nn2svgp)!0.5!(banana-hmc)$) {};
-
-    % Arrow labels
-    \node[font=\scriptsize\sc,color=white] at (first-arr) {\our};
-    \node[font=\scriptsize\sc,color=white] at (second-arr) {\normalsize$\bm\approx$};
-
-    % Labels
-    \node[anchor=north, font=\small] at ($(banana-nn) + (0,-.55\figureheight)$) {Neural network prediction};
-    \node[anchor=north, font=\small] at ($(banana-nn2svgp) + (0,-.55\figureheight)$) {Sparse function-space representation};
-    \node[anchor=north, font=\small] at ($(banana-hmc) + (0,-.55\figureheight)$) {HMC result as baseline};
-
-  \end{tikzpicture}
-  \newcommand{\mycircle}{\protect\tikz[baseline=-.6ex]\protect\node[circle,inner sep=2pt,draw=black,fill=C0,opacity=.5]{};}
-  \newcommand{\mysquare}{\protect\tikz[baseline=-.6ex]\protect\node[inner sep=2.5pt,draw=black,fill=C1,opacity=.5]{};}
-  \newcommand{\myinducing}{\protect\tikz[baseline=-.7ex]\protect\node[circle,inner sep=1.5pt,draw=black,fill=black]{};}
-  %
-  \caption{\textbf{Uncertainty quantification} for binary classification (\mysquare~vs.~\mycircle).
+%
+%\begin{figure*}[t!]
+%  \centering
+%  % Set figure size
+%  \setlength{\figurewidth}{.31\textwidth}
+%  \setlength{\figureheight}{\figurewidth}
+%  %
+%  % Colours
+%  \definecolor{C0}{HTML}{DF6679}
+%  \definecolor{C1}{HTML}{69A9CE}
+%  %
+%  \begin{tikzpicture}[outer sep=0,inner sep=0]
+%
+%    \newcommand{\addfig}[2]{
+%    \begin{scope}
+%      \clip[rounded corners=3pt] ($(#1)+(-.5\figurewidth,-.5\figureheight)$) rectangle ++(\figurewidth,\figureheight);
+%      \node (#2) at (#1) {\includegraphics[width=1.05\figurewidth]{./fig/#2}};
+%    \end{scope}
+%    %\draw[rounded corners=3pt,line width=1.2pt,black!60] ($(#1)+(-.5\figurewidth,-.5\figureheight)$) rectangle ++(\figurewidth,\figureheight);
+%    }
+%
+%    % The neural network
+%    \addfig{0,0}{banana-nn}
+%
+%    % The nn2svgp
+%    \addfig{1.1\figurewidth,0}{banana-nn2svgp}
+%
+%    % The update
+%    \addfig{2.2\figurewidth,0}{banana-hmc}
+%
+%    % The arrow
+%    \tikzstyle{myarrow} = [draw=black!80, single arrow, minimum height=14mm, minimum width=2pt, single arrow head extend=4pt, fill=black!80, anchor=center, rotate=0, inner sep=5pt, rounded corners=1pt]
+%    \tikzstyle{myblock} = [draw=black!80, minimum height=4mm, minimum width=7mm, fill=black!80, anchor=center, rotate=0, inner sep=5pt, rounded corners=1pt]
+%    \node[myarrow] (first-arr) at ($(banana-nn)!0.5!(banana-nn2svgp)$) {};
+%    \node[myblock] (second-arr) at ($(banana-nn2svgp)!0.5!(banana-hmc)$) {};
+%
+%    % Arrow labels
+%    \node[font=\scriptsize\sc,color=white] at (first-arr) {\our};
+%    \node[font=\scriptsize\sc,color=white] at (second-arr) {\normalsize$\bm\approx$};
+%         
+%    % Labels
+%    \node[anchor=north, font=\small] at ($(banana-nn) + (0,-.55\figureheight)$) {Neural network prediction};
+%    \node[anchor=north, font=\small] at ($(banana-nn2svgp) + (0,-.55\figureheight)$) {Sparse function-space representation};
+%    \node[anchor=north, font=\small] at ($(banana-hmc) + (0,-.55\figureheight)$) {HMC result as baseline};      
+%
+%  \end{tikzpicture}
+%  \newcommand{\mycircle}{\protect\tikz[baseline=-.6ex]\protect\node[circle,inner sep=2pt,draw=black,fill=C0,opacity=.5]{};}
+%  \newcommand{\mysquare}{\protect\tikz[baseline=-.6ex]\protect\node[inner sep=2.5pt,draw=black,fill=C1,opacity=.5]{};}
+%  \newcommand{\myinducing}{\protect\tikz[baseline=-.7ex]\protect\node[circle,inner sep=1.5pt,draw=black,fill=black]{};}
+%  %
+%  \caption{\textbf{Uncertainty quantification} for binary classification (\mysquare~vs.~\mycircle).
 We convert the trained neural network (left) to a sparse GP model that summarizes all data onto a sparse set of inducing points~\myinducing\ (middle).
@@
 Marginal uncertainty depicted by colour intensity.\looseness-1}
-  \label{fig:banana}  
-\end{figure}
+%  \label{fig:banana}  
+%\end{figure*}
 
@@
 %
-\begin{equation} \label{eq-empirical-risk}
-  \weights^{*} = 
-  \arg \min_{\weights} \mathcal{L}(\dataset,\weights) =
+\begin{align} \label{eq-empirical-risk}
+  \weights^{*} &= 
+  \arg \min_{\weights} \mathcal{L}(\dataset,\weights) \nonumber \\ &=
   \arg \min_{\weights} \textstyle\sum_{i=1}^{N} \ell(f_\weights(\mathbf{x}_{i}), y_i) + \delta \mathcal{R}(\weights).
-\end{equation}
+\end{align}
 %
@@
 %
-\begin{equation} \label{eq:weight_func}
-f_\weights(\vx) \approx 
+\begin{align} \label{eq:weight_func}
+ &f_\weights(\vx) \approx 
 %g_\weights(\mathbf{x}) = 
-\phi^\top\!(\vx) \, \vw \quad\implies\quad \mu(\vx) = 0 \quad \text{and} \quad \kappa(\vx, \vx') = \frac{1}{\delta} \phi^\T\!(\vx) \, \phi(\vx').
-\end{equation}
+ \phi^\top\!(\vx) \, \vw \quad\implies \nonumber \\
+ &\mu(\vx) = 0 \quad \text{and} \quad \kappa(\vx, \vx') = \frac{1}{\delta} \phi^\T\!(\vx) \, \phi(\vx').
+\end{align}
 % The posterior structure directly relates to the optimization loss around the MAP weights $\vw^*$.
@@
 %
-\begin{equation}  \label{eq:gp_pred}
-  \myexpect_{p(f_i \mid\vy)}[f_i]= \vk_{\vx i}^\top \valpha \quad \text{and} \quad
-  \mathrm{Var}_{p(f_i \mid \vy)}[f_i] = k_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
-\end{equation}
+\begin{align}  \label{eq:gp_pred}
+  \myexpect_{p(f_i \mid\vy)}[f_i] &= \vk_{\vx i}^\top \valpha, \\
+  \mathrm{Var}_{p(f_i \mid \vy)}[f_i] &= k_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i}, \nonumber
+\end{align}
 %
@@
 %
-\begin{equation}
+\begin{align}
   \label{eq:dual_param}
-  \alpha_i \coloneqq \myexpect_{p(\vw \mid \vy)}[\nabla_{f}\log p(y_i \mid f) |_{f=f_i}]
-  \quad \text{and} \quad
-  \beta_i \coloneqq - \myexpect_{p(\vw \mid \vy)}[\nabla^2_{f f}\log p(y_i \mid f_i) |_{f=f_i}],
-\end{equation}
+  \alpha_i &\coloneqq \myexpect_{p(\vw \mid \vy)}[\nabla_{f}\log p(y_i \mid f) |_{f=f_i}], \\
+  %\quad \text{and} \quad
+  \beta_i &\coloneqq - \myexpect_{p(\vw \mid \vy)}[\nabla^2_{f f}\log p(y_i \mid f_i) |_{f=f_i}],
+\end{align}
 %
@@
 %
-\begin{equation}
+\begin{align}
   \label{eq:dual_param_laplace}
-  \hat{\alpha}_i \coloneqq \nabla_{f}\log p(y_i \mid f) |_{f=f_i}
-  \quad \text{and} \quad
-  \hat{\beta}_i \coloneqq - \nabla^2_{ff}\log p(y_i \mid f) |_{f=f_i}.
-\end{equation}
+  \hat{\alpha}_i &\coloneqq \nabla_{f}\log p(y_i \mid f) |_{f=f_i} , \\
+  %\quad \text{and} \quad
+  \hat{\beta}_i &\coloneqq - \nabla^2_{ff}\log p(y_i \mid f) |_{f=f_i}.
+\end{align}
 %
@@
 The problem with \cref{eq:gp_pred} is that to make predictions and compute variances we must incur a cost of $O(N^3)$ which limits the use of the GP on large data sets.
+
+\begin{table*}[t!] 
+  \centering\scriptsize
+  \caption{Comparisons and ablations on UCI data with negative log predictive density (NLPD\textcolor{gray}{\footnotesize$\pm$std}, lower better).
+Our sparse \our ($M=256$) is on par with full models (left) and outperforms the GP subset approach of \cite{immer2021improving} (right).
+Results for methods marked with * as reported in the original benchmark~\cite{immer2021improving}.
+See \cref{app:uci} for additional tables with comparisons.}
+	\label{tbl:uci}
+	\vspace*{-4pt}
+
+	% Control table spacing
+	\renewcommand{\arraystretch}{1.}
+	\setlength{\tabcolsep}{1.2pt}
+	\setlength{\tblw}{0.083\textwidth}
+
+	% Custom error formatting
+	\newcommand{\val}[2]{%
+		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
+	}
+
+    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
+	\input{tables/uci.tex}
+\end{table*}
+
+\begin{figure*}[t]
+  \centering\scriptsize
+  \setlength{\figurewidth}{.16\textwidth}
+  \setlength{\figureheight}{\figurewidth}
+  \pgfplotsset{axis on top,scale only axis,y tick label style={rotate=90}, x tick label style={font=\footnotesize},y tick label style={font=\footnotesize},title style={yshift=-4pt,font=\large}, y label style={font=\large},x label style={font=\large},grid=major, width=\figurewidth, height=\figureheight}
+  \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
+  \pgfplotsset{xlabel={$M$},ylabel style={yshift=-12pt}}  
+  %
+  \begin{minipage}[t]{.13\textwidth}
+    \raggedleft
+    \pgfplotsset{ylabel=NLPD}
+    \input{./fig/australian.tex}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[t]{.12\textwidth}
+    \raggedleft
+    \input{./fig/breast_cancer.tex}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[t]{.12\textwidth}
+    \raggedleft
+    \input{./fig/ionosphere.tex}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[t]{.12\textwidth}
+    \raggedleft
+    \input{./fig/glass.tex}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[t]{.12\textwidth}
+    \raggedleft
+    \input{./fig/vehicle.tex}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[t]{.12\textwidth}
+    \raggedleft
+    \input{./fig/waveform.tex}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[t]{.12\textwidth}
+    \raggedleft
+    \input{./fig/digits.tex}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[t]{.12\textwidth}
+    \raggedleft
+    \input{./fig/satellite.tex}
+  \end{minipage}\\[-1em]
+  %
+  % Legend  
+  \definecolor{steelblue31119180}{RGB}{31,119,180}
+  \definecolor{darkorange25512714}{RGB}{255,127,14}  
+  \newcommand{\myline}[1]{\protect\tikz[baseline=-.5ex,line width=1.6pt]\protect\draw[draw=#1](0,0)--(1.2em,0);}
+  \caption{Comparison of convergence in terms of number of inducing points $M$ in NLPD (mean over 10 seeds) on UCI classification tasks: \our (thick) vs.\ subsets (\cite{immer2021improving}, thin).
+Orange lines (\myline{darkorange25512714}) use the GP mean, whereas blue lines (\myline{steelblue31119180}) the NN MAP estimate as mean.
+Our \our converges fast for all cases.\looseness-1}
+  \label{fig:uci}
+  %\vspace*{-6pt}
+\end{figure*}
 
@@
 Using this sparse definition of the dual variables, our sparse GP posterior takes the following form:
-\begin{equation}\label{eq:dual_sparse_post}
-   \myexpect_{q_{\vu}(\vf)}[f_i] = \vkzs^{\T} \MKzz^{-1} \valpha_{\vu}
-   \quad \text{and} \quad 
-   \textrm{Var}_{q_{\vu}(\vf)}[f_i]  = k_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \MBeta_{\vu})^{-1} ]\vkzs
-\end{equation}
+\begin{align}\label{eq:dual_sparse_post}
+   \myexpect_{q_{\vu}(\vf)}[f_i] &= \vkzs^{\T} \MKzz^{-1} \valpha_{\vu}, \\
+   %\quad \text{and} \quad 
+   \textrm{Var}_{q_{\vu}(\vf)}[f_i]  &= k_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \MBeta_{\vu})^{-1} ]\vkzs, \nonumber
+\end{align}
 where $\MKzz$ and $\vkzs$ are defined similarly to $\MKxx$ and $\vk_{\vx i}$ but over the inducing points $\{\vz_j\}_{i=1}^M$, $\vz \in \R^{D}$, instead of the full data set $\dataset$.
@@
 
-\section{Maintaining a sparse function-space representation in sequential learning}
-\label{sec:sequential}
-%
-We have presented a method for converting trained neural networks into a sparse function-space representations.
-The sparse representation opens an avenue for maintaining (and updating) a representation of the neural network, an important feature for sequential learning, such as continual learning.\looseness-1
-%In this section, we demonstrate how sequential learning methods can benefit from our function-space representation and it's associated uncertainty estimates.
-
-\paragraph{\our for continual learning}
-% Definition of CL -> a sequence of tasks 
-In the continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{N_t}$, which after the task is discarded and cannot be accessed in the following stages of the training.
-Rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting.
-In the same way, after each task, we can use \our method to build a compact representation of the neural network and then exploit this representation to construct a functional regularizer to add to the training loss for the subsequent tasks.
-Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art results on CL benchmarks.
-However, they are limited to using subset approximations of the posterior.
-Instead, we use the sparse data term posterior, see \cref{app:cl} for details.
-%, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer. 
-\our is a more principled approach since the resultant GP is a low-rank approximation of the full data which ensures information is not lost.
-%, essentially what the sparse dual variables do.
-\todo{this term is replacing the missing data}
-% Where the regularizer comes from
-
-In practice this means, that at the end of the training for each task $t$, we compute the approximated kernel function for the current model and randomly select $M$ inducing points.
-Given the issues described in the previous sections, related to computing the full covariance posterior $\MKxx$ for $\dataset_t$, we can exploit the dual parameterization to efficiently encode the information from  $\dataset_t$ using the dual parameterization, as follows,
-%
-\begin{equation}\textstyle
- 	\bar{\MB}^{-1}_t = \MKzz^{-1} \MBeta_\vu \MKzz^{-1} \in \R^{M \times M}, 
- 	\quad \text{s.t.} \quad
- 	\MBeta_{\vu} =  \sum_{i \in \dataset_t} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
- 	% \quad \forall t \in [1, T]
-\end{equation}
-%
-where $\MKzz$ and $\vkzi$ are the gram matrix and vector computed on the inducing points $\mathcal{Z}_t = \{\vz_i\}_{i=1}^M$ selected from $\dataset_t$.\
-%
-We keep a memory buffer $\mathcal{M} = \{(\mathcal{Z}_t, \vu_t, \bar{\MB}^{-1}_t)\}_{t=1}^T$, where $\vu_t \in \R^{M}$ is a vector with entries $u_{t, i} = f_{\vw_t^*}(\vz_i), \forall \vz_i \in \mathcal{Z}_t$, are the neural network outputs computed on the inducing points with the MAP estimate $\weights_t^*$ after task $t$.
-For notational convenience, we restrict ourselves here to single-output neural networks and refer the reader to \cref{sec:cl_multioutput} for details on the multi-output setting.
-
-After each task, we update $\mathcal{M}$, and can construct a regularizer term, which aims to reduce the drift of the current model from diverging on the inducing points $\MZ_s$ for all previous tasks $ s = 1, \ldots, t-1$.
-This means that for training  the successive task, the new objective to minimize becomes $\weights_t^* = \arg\min_{\weights} \mathcal{L}(\mathcal{D}_t, \weights) + \tau \, \mathcal{R}_\textrm{\our}(\weights, \mathcal{M})$, with weight $\tau$ and regularizer
-%
-\begin{equation}\label{eq-cl-regularizer}\textstyle
-  \mathcal{R}_\mathrm{\our}(\weights, \mathcal{M}) = \frac{1}{2} \sum_{s=1}^{t-1} \frac{1}{M} 
-	\left\lVert 
-	\vu - \vu_s % f_{\weights_{s}}(\MZ_s)
-	\right\rVert_{\bar{\MB}^{-1}_{s}}, \quad \vu \in \R^M \text{~with~} u_{i} = f_{\weights}(\vz_{i}),~\forall {\vz_i} \in \mathcal{Z}_s .
-\end{equation}
-
-\paragraph{\our for dual conditioning} Adding new data to a trained neural network without retraining from scratch is a non-trivial problem.
-Some approaches exist \citep{kirsch2022marginal, spiegelhalter1990sequential} but are in the weight space formulation, which makes conditioning harder to formulate.
-As pointed out in \cite{chang2022fantasizing}, dual parameter conditioning updates are straightforward and were the original motivation of \cite{csato2002sparse}.
-This involves integrating data into the sum in \cref{eq:dual_sparse}.
-Thus, we need to find the data dual variables $\hat{\alpha}$ and $\hat{\beta}$ for the new data subset $\mathcal{D}_\textrm{new} = \{(\vx_i,\vy_i)\}_{i=1}^{N_{\textrm{new}}}$ and compute the corresponding kernel terms.
-As pointed out in \cite{chang2022fantasizing}, for GPs, these updates are exact under a Gaussian likelihood and the kernel remains constant.
-For non-Gaussian likelihoods, the results are almost the same as retraining with all the data.
-However, it is worth noting that our kernel's dependency on the trained neural network $\Jac{\weights_*}{\vx}$ (via the Jacobian) becomes outdated as we add more data.
-Nevertheless, we can still improve predictions without retraining by conditioning on new data.
-%[SEE EXPERIMENT ???].
-%%The resulting regularizer can be computed as follows
-%%\begin{equation}
-%%	\mathcal{R}_\textit{SFR}(\weights, \mathcal{M}) = \sum_{s=1}^{t-1} \frac{1}{m} \left[\left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right) \right].
-%%\end{equation}
-%%
-%\begin{equation}
-%	\mathcal{R}_\mathrm{\our}(\weights, \mathcal{M}) = \frac{1}{2} \sum_{s=1}^{t-1} \frac{1}{M} 
-%	\left\lVert 
-%	f_{\weights}(\MZ_{s}) - \vu_t % f_{\weights_{s}}(\MZ_s)
-%	\right\rVert_{\bar{\MB}^{-1}_{s}}.
-%\end{equation}
-%%\todo{choose one option}
-%% where $f_\vw(\MZ_{s}) \in \R^m$ are the outputs of neural networks with the current weights $\vw$ and stored function outputs of the neural network at the MAP optimum for task $s$, i.e., each $i$th entry is $f_\cdot(\vz_i) \in \R$.
-%%\begin{equation}
-%%	\argmin_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights) + \tau \mathcal{R}_\textit{SFR}(\weights)
-%%\end{equation}
-%Then, when the training on the successive task, the new objective to minimize takes the following form
-%\begin{equation}
-%	\weights_t^* = \argmin_{\weights} \mathcal{L}(\mathcal{D}_t, \weights) + \tau \mathcal{R}_\textit{SFR}(\weights, \mathcal{M})
-%\end{equation}
-
 \section{Experiments}
@@
 %
-We present a series of experiments specifically designed to showcase the robustness and effectiveness of \our. The experiments are aimed at answering the following key questions:
-\textbf{Predictions:}~Does our method's ability to consider the full data set offer benefits over subset function-space methods?
-(\cref{sec:uci}) How do predictions with our sparse function-space approximation compare to weight-space approximations?
-% \textbf{Function-space updates:} How fast are our function-space updates relative to retraining from scratch? Do they improve predictive performance?
-\textbf{Representation:} Can a sparse function-space representation help retain knowledge from previous tasks in CL? (\cref{sec:cl-exp})
-\textbf{Uncertainty:} Can our uncertainty estimates help exploration in RL?
-(\cref{sec:rl-exp}) We implement all methods in PyTorch~\cite{paszke2019pytorch} and run the benchmarks using a GPU cluster.
-We provide full experiment details in \cref{app:experiments}.
-
-\paragraph{Toy examples} For illustrative purposes, we show our approach on a 1D regression problem (\cref{fig:teaser}) and on the 2D {\sc Banana} classification task (\cref{fig:banana}).
+%\paragraph{Toy examples} For illustrative purposes, we show our approach on a 1D regression problem (\cref{fig:teaser}) and on the 2D {\sc Banana} classification task (\cref{fig:banana}).
 In \cref{fig:teaser}, we train an MLP neural network with two hidden layers (64 hidden units each, tanh activation) and pass it through \our.
@@
 
-\begin{table}[t!] 
-  \centering\scriptsize
-  \caption{Comparisons and ablations on UCI data with negative log predictive density (NLPD\textcolor{gray}{\footnotesize$\pm$std}, lower better).
-Our sparse \our ($M=256$) is on par with full models (left) and outperforms the GP subset approach of \cite{immer2021improving} (right).
-Results for methods marked with * as reported in the original benchmark~\cite{immer2021improving}.
-See \cref{app:uci} for additional tables with comparisons.}
-	\label{tbl:uci}
-	\vspace*{-4pt}
-
-	% Control table spacing
-	\renewcommand{\arraystretch}{1.}
-	\setlength{\tabcolsep}{1.2pt}
-	\setlength{\tblw}{0.083\textwidth}
-
-	% Custom error formatting
-	\newcommand{\val}[2]{%
-		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
-	}
-
-    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
-	\input{tables/uci.tex}
-\end{table}
-
-\begin{figure}[t]
-  \centering\scriptsize
-  \setlength{\figurewidth}{.26\textwidth}
-  \setlength{\figureheight}{\figurewidth}
-  \pgfplotsset{axis on top,scale only axis,y tick label style={rotate=90}, x tick label style={font=\footnotesize},y tick label style={font=\footnotesize},title style={yshift=-4pt,font=\large}, y label style={font=\large},x label style={font=\large},grid=major, width=\figurewidth, height=\figureheight}
-  \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
-  \pgfplotsset{xlabel={$M$},ylabel style={yshift=-12pt}}  
-  %
-  \begin{minipage}[t]{.17\textwidth}
-    \raggedleft
-    \pgfplotsset{ylabel=NLPD}
-    \input{./fig/australian.tex}
-  \end{minipage}
-  \hfill
-%  \begin{minipage}[t]{.16\textwidth}
-%    \raggedleft
-%    \input{./fig/breast_cancer.tex}
-%  \end{minipage}
-%  \hfill
-%  \begin{minipage}[t]{.16\textwidth}
-%    \raggedleft
-%    \input{./fig/ionosphere.tex}
-%  \end{minipage}
-%  \hfill
-  \begin{minipage}[t]{.16\textwidth}
-    \raggedleft
-    \input{./fig/glass.tex}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[t]{.16\textwidth}
-    \raggedleft
-    \input{./fig/vehicle.tex}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[t]{.16\textwidth}
-    \raggedleft
-    \input{./fig/waveform.tex}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[t]{.16\textwidth}
-    \raggedleft
-    \input{./fig/digits.tex}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[t]{.16\textwidth}
-    \raggedleft
-    \input{./fig/satellite.tex}
-  \end{minipage}\\[-1em]
-  %
-  % Legend  
-  \definecolor{steelblue31119180}{RGB}{31,119,180}
-  \definecolor{darkorange25512714}{RGB}{255,127,14}  
-  \newcommand{\myline}[1]{\protect\tikz[baseline=-.5ex,line width=1.6pt]\protect\draw[draw=#1](0,0)--(1.2em,0);}
-  \caption{Comparison of convergence in terms of number of inducing points $M$ in NLPD (mean over 10 seeds) on UCI classification tasks: \our (thick) vs.\ subsets (\cite{immer2021improving}, thin).
-Orange lines (\myline{darkorange25512714}) use the GP mean, whereas blue lines (\myline{steelblue31119180}) the NN MAP estimate as mean.
-Our \our converges fast for all cases.\looseness-1}
-  \label{fig:uci}
-  %\vspace*{-6pt}
-\end{figure}
-
-\subsection{Capturing uncertainty in UCI tasks under supervised learning}
-\label{sec:uci}
-%
-We first evaluate \our on eight UCI benchmarks~\cite{UCI}, a variety of binary and multi-class classification tasks with different data set sizes.
+%
+We evaluate \our on eight UCI benchmarks~\cite{UCI}, a variety of binary and multi-class classification tasks with different data set sizes.
 We train a two-layer MLP for each of the classification tasks and follow the experiment set up in \cite{immer2021improving}.
@@
 
-% We match the predictive performance despite being sparse (here, $M=256$).
-
-% This is
-% However, our method used
-
-% despite being sparse (here, $M=256$).
-
-% (left), we compare our model to the NN MAP estimate, mean-field VI, a Bayesian NN, and a GLM model (see \cite{immer2021improving} for the baselines) in negative log-predictive density (NLPD).
-% In \cref{tbl:uci} (left), we compare our model to the NN MAP estimate, mean-field VI, a Bayesian NN, and a GLM model (see \cite{immer2021improving} for the baselines) in negative log-predictive density (NLPD).
-% We match the predictive performance despite being sparse (here, $M=256$).
-% Results for $M=16,32,64,128,256$ are included in \cref{app:uci} with full experiment details.
-
-% \cref{tbl:uci} (right) shows that \our is able to summarize the information of the full data set more efficiently than the sparse GP subset method.
-% As a result, it maintains predictive performance whilst using fewer inducing points.
-% This is even more apparent from \cref{fig:uci} which shows the benefits of \our in summarizing the full data distribution onto a small set of inducing points over just picking a random subset.
-
-% In \cref{tbl:uci} (right), we also include an ablation and comparison study (to \cite{immer2021improving}) with a fixed low number of inducing points ($M=32$).
-% The comparison shows that our sparse method is able to summarize the information of the full data set more efficiently than sparse subset methods, and can match the performance of the full GP even with a low number of inducing points.
-This is even more apparent from \cref{fig:uci} which shows the benefits of \our in summarizing the full data distribution onto a small set of inducing points over just picking a random subset.
-
-% see \cref{tbl:uci} for a list of the datasets.
-The neural network training was done using MAP, with a prior $\mathcal{N}(0,\delta^{-1} \MI)$ with prior precision $\delta$.
-After training, we constructed the SVGP dual and used the resulting SVGP model for uncertainty quantification.
-Depending on task dimension and complexity, our model can match the NN MAP in NLPD performance even with a low number of inducing points, see \cref{tbl:uci}.
-We performed hyperparameter search over the prior precision, and ran the experiment over $10$ seeds.
-During the initial NN training, we used a learning rate of $1e-3$.
-
-%\begin{figure}
-%  \raggedleft\scriptsize
-%  \setlength{\figurewidth}{\textwidth}
-%  \setlength{\figureheight}{.55\figurewidth}
-%  %\pgfplotsset{axis on top,ymajorgrids,axis line style={draw=none},legend style={at={(-.1,-.1)},anchor=north east}}
-%  %\pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
-%  %\def\our{{\sc sfr} (ours)}
-%  \input{./fig/MNIST_acc.tex}
-%  \caption{Foo}
-%  \label{fig:mnist}
-%\end{figure}
-%
-
-\subsection{Supervised learning on image data sets}
-\label{sec:image}
-Similarly to the UCI experiments, we seek to demonstrate \our on image data that features more complicated data manifolds and model structures.
-We consider the MNIST and Fashion-MNIST (FMNIST) classification tasks, and use an MLP and a CNN architecture respectively (matching the setup in \cite{immer2021improving}).
-After training, we computed the duals for \our and use the model for prediction (full experiment details in \cref{app:image}).
-In \cref{tbl:imagesuper}, we compare to baselines also used in \cite{immer2021improving}.
-We report accuracy (ACC), NLPD, and expected calibration error (ECE).
-For \our and the GP predictive subset method by \cite{immer2021improving}, we provide results when predicting with GP mean and when using the neural network (NN) and
-fix the number of inducing points $M=1024$.
-For completeness, we also include the GP predictive result from \cite{immer2021improving} which used more inducing points $M=3200$.
-The results in \cref{tbl:imagesuper} agree with the conclusions drawn from the UCI experiments showing that \our is able to more efficiently capture the posterior using a sparse set of points.
-They further demonstrate that \our's predictive mean (GP) significantly outperforms the GP predictive subset.
-This is an interesting result as we cannot rely on the NN's prediction if we wish to condition on new data, using the dual conditioning from \cref{sec:sequential}.
-In this setting, we must rely on our GP's predictive mean.
-% Other approaches, \cite{immer2021improving} never inten
-% The resutls demonstrate that \our's predictive GP mean significantly outperforms the
-These results on image data sets motivate experiments beyond the supervised learning setting, which we now detail.
-
-% For \our and the GP predictive subset method by \cite{immer2021improving} we fix the number of points $M=1024$.
-
-%We performed hyperparameter optimization over the prior precision, and found the optimal value to be [insert].
-We ran the experiment over $5$ seeds.
-During the NN training, we used a batch size of $512$ and an Adam optimizer with learning rate $1e-3$.
-
-%In addition to uncertainty estimates, our method can update the posterior when given new data.
-We gave the SVGP model 10 \% of the test dataset used for evaluation, and compare the performance of the SVGP model and the retrained NN in [INSERT TABLE].
-
-\begin{table}[t!]
-  \centering\scriptsize
-  \caption{Metrics for supervised learning on image data with a CNN.
-We report accuracy, NLPD, and expected calibration error (mean$\pm$std) over 5 seeds.
-Our \our method is able to match the full methods using only a sparse set.
-For the GP predictive sparse subset method and \our we report results both using the NN MAP as mean (NN) and using the GP mean.}
-	\label{tbl:imagesuper}
-	% Control table spacing
-	\renewcommand{\arraystretch}{1.}
-	\setlength{\tabcolsep}{6pt}
-	\setlength{\tblw}{0.095\textwidth}
-
-	% Custom error formatting
-	\newcommand{\val}[2]{%
-		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
-	}
-
-    % THE TABLE CAN BE FORMATTED MORE LIKE THIS
-    % \begin{tabular}{l l C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
-    % \toprule
-    % & Method & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ & OOD-AUC~$\uparrow$  \\
-    % \midrule
-    % \multirow{2}{*}{FMNIST}
-    % & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % \midrule
-    % \multirow{2}{*}{CIFAR-10}
-    % & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
-    % \bottomrule
-    % \end{tabular}
-  \newcommand{\myline}{\protect\tikz[baseline=-.5ex,line width=.7pt]\protect\draw[draw=gray](0,0)--(7em,0);}
-  \begin{tabular}{l c C{\tblw} C{\tblw} C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
-    \toprule
-            &     &  \multicolumn{3}{c}{\myline~MNIST~\myline} & \multicolumn{3}{c}{\myline~FMNIST~\myline} \\
-     Method & $M$ & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ \\
-    \midrule
-    %\multirow{2}{*}{MNIST}
-    MAP & -- & \val{98.22}{0.13} & \val{0.061}{0.004} & \val{0.006}{0.001}
-          & \val{91.39}{0.11} & \val{0.258}{0.004} & \val{0.017}{0.001} \\
-    BNN predictive \cite{immer2021improving} & -- & \val{93.14}{0.05} & \val{0.304}{0.002} & \val{0.111}{0.003}
-                                               & \val{84.42}{0.12} & \val{0.942}{0.016} & \val{0.411}{0.008} \\
-    BNN predictive \cite{ritter2018kfac} & -- & \val{93.03}{0.13} & \val{0.369}{0.003} & \val{0.168}{0.001}
-                                           & \val{91.20}{0.07} & \val{0.265}{0.004} & \val{0.024}{0.002} \\
-    GLM predictive \cite{immer2021improving} & -- & \val{98.40}{0.05} & \val{0.054}{0.002} & \val{0.007}{0.001}
-                                               & \val{92.25}{0.10} & \val{0.244}{0.003} & \val{0.012}{0.003} \\\arrayrulecolor{black!10}\midrule
-    GP predictive \cite{immer2021improving} & $3200$ & \val{\textbf{98.22}}{0.13} & \val{\textbf{0.058}}{0.001} & \val{\textbf{0.003}}{0.000}
-                                                     & \val{91.36}{0.11} & \val{\textbf{0.25}}{0.004} & \val{\textbf{0.007}}{0.001} \\
-
-    GP predictive (NN) & $1024$ & \val{97.70}{0.07} & \val{0.080}{0.002} & \val{0.011}{0.001}
-                              & \val{\textbf{91.47}}{0.41} & \val{0.289}{0.009} & \val{0.033}{0.003} \\
-
-    GP predictive & $1024$  & \val{76.28}{1.85} & \val{0.702}{0.029} & \val{0.070}{0.022}
-                            & \val{83.98}{0.35} & \val{0.503}{0.012} & \val{0.052}{0.006} \\
-    \our (NN) & $1024$ &  \val{98.02}{0.12} & \val{0.066}{0.003} & \val{0.007}{0.001}
-                     & \val{\textbf{91.93}}{0.45} & \val{0.267}{0.011} & \val{0.028}{0.003} \\
-    \our & $1024$ & \val{\textbf{98.07}}{0.06} & \val{0.063}{0.003} & \val{0.005}{0.001}
-                  & \val{\textbf{91.56}}{0.35} & \val{\textbf{0.253}}{0.006} & \val{0.012}{0.001} \\
-%    \multirow{2}{*}{FMNIST}
-%    & MAP & \val{91.39}{0.11} & \val{0.258}{0.004} & \val{0.017}{0.001} \\
-    %& BNN predictive \cite{immer2021improving} & \val{84.42}{0.12} & \val{0.942}{0.016} & \val{0.411}{0.008} \\
-    % & BNN predictive \cite{ritter2018kfac} & \val{91.20}{0.07} & \val{0.265}{0.004} & \val{0.024}{0.002} \\
-    % & GLM predictive \cite{immer2021improving} & \val{92.25}{0.10} & \val{0.244}{0.003} & \val{0.012}{0.003} \\
-    %& GP predictive \cite{immer2021improving} $m=3200$ & \val{91.36}{0.11} & \val{0.25}{0.004} & \val{0.007}{0.001} \\
-    % & GP predictive NN $m=1024$ &  \val{0}{0.07} & \val{0}{0.002} & \val{0}{0.001} \\
-    % & GP predictive $m=1024$  &  \val{0}{1.85} & \val{0}{0.029} & \val{0}{0.022} \\
-    % & \our NN $m=1024$ &  \val{0}{0.0} & \val{0}{0.003} & \val{0}{0.001} \\
-    % & \our $m=1024$ &  \val{0}{0.06} & \val{0}{0.003} & \val{0}{0.001} \\
-    \arrayrulecolor{black}
-    \bottomrule
-  \end{tabular}
-
-% & \sc \sc gp predictive  &  \val{76.28333}{1.849} & \val{0.70168}{0.02883} & \val{0.07049}{0.02154} \\
-% & \sc \sc gp predictive NN \cite{immer2021improving} &  \val{97.70333}{0.074} & \val{0.08027}{0.00248} & \val{0.01052}{0.00097} \\
-% & \sc \our &  \val{98.06667}{0.060} & \val{0.06312}{0.00284} & \val{0.00493}{0.00086} \\
-% & \sc \our NN &  \val{98.02000}{0.122} & \val{0.06583}{0.00294} & \val{0.00714}{0.00096} \\
-% M=512
-% & \sc \our &  \val{96.05}{0.00} & \val{0.85}{0.01} & \val{0.50}{0.00} \\
-% & \sc \sc gp predictive  &  \val{14.79}{0.01} & \val{2.30}{0.02} & \val{0.02}{0.01} \\
-% & \sc \sc gp predictive NN \cite{immer2021improving} &  \val{91.49}{0.01} & \val{1.25}{0.01} & \val{0.61}{0.00} \\
-% & \sc \our NN &  \val{96.96}{0.00} & \val{0.63}{0.00} & \val{0.40}{0.00} \\
-
-% M=1024
-
-    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT
-	%\input{tables/img_super.tex}
-\end{table}
-
-\subsection{Updating the network representation in continual learning}
-\label{sec:cl-exp}
-%
-%%% Very rough draft
-%This experiment's section is meant to demonstrate the quality of our sparse representation to retain previous knowledge in the Continual learning setting.
-Unfortunately the CL literature is based on methods that require very diverse set of hyperparameters
-%% Idea: it is very difficult to have everything under control, because model changes, settings change, optimizer change, and so on.
-Then what we did was trying to replicate as close as possible the results for the competing methods by using their codebases where available and choosing the hyperpameters accordingly to their choices.
-%
-%% Why SH?
-%% TODO: there are at least two papers that clearly say MH is unrealistic and too simple as a consequence is not a good way to assess the quality of the method
-%
-%% Architectures
-%We conduct the experiments on a set of three CL benchmarks Sequential-MNIST (S-MNIST), Sequential-FashionMNIST (S-FMNIST), and Permuted-MNIST (P-MNIST).
-Following \cite{rudner2022continual, pan2020continual}, we used a two-layer MLP with 256 hidden units with ReLU activation for S-MNIST and S-FMNIST, and a two-layer with 100 hidden units for P-MNIST.
-%
-%% Methods
-%We compared our method to 1) weight-regularization based methods EWC, SI and VCL (which also has the addition of coresets); 2) function-based regularization based methods DER, FROMP, S-FSVI, SFR; 3) an ablation for which we replace $\bar{\MB}^{-1}$ with an identity matrix $\MI_m$, \ie which is equivalent to assuming a GP with iid realization \todo{Not sure this is 100$\%$ correct}.
-%% Inducing points
-%Following \citep{rudner2022continual}, we use 200 inducing points per tasks % this one can be difficult to justify since S-FSVI samples 200 context points and then iteratively samples 40 coresets points (or at least that's what I got)
-%on all the inducing points, and a lower number of inducing point for S-MNIST, to investigate if our method was still capable of capture more information due to its sparse formulation, as explained in \cref{todo}.
-%
-%%% Questions: Should we also mention the Identity outside when not trained on those classes or just leave that for the appendix?
-
-\setlength{\columnsep}{8pt}
-\setlength{\intextsep}{0pt}
-\begin{wraptable}{R}{.65\textwidth}
-  \centering\scriptsize
-  \caption{Continual learning experiments. We report accuracy${\pm}$std and bold based on a $t$-test. $^*$Methods rely on weight regularization.}
-  %\textcolor{blue}{Results from \cite{rudner2022continual}
-  %\color{red}{Preliminary results need more runs or hyperparam tuning}
-	\label{tbl:cl_table_1}
-
-	% Control table spacing
-	\renewcommand{\arraystretch}{1.}
-	\setlength{\tabcolsep}{1pt}
-	\setlength{\tblw}{0.14\textwidth}
-
-	% Custom error formatting
-	\newcommand{\val}[2]{%
-		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
-	}
-
-	\vspace*{-4pt}
-
-	% Import table content
-	\input{tables/cl_table_1}
-\end{wraptable}
-%
-% Overview
-In this section, we show how the regularizer described in \cref{sec:sequential} can be used in continual learning to retain a compact representation of the neural network.
-The experiments are run only in the single-head (SH) setting that is harder and more realistic than multi-head (MH) (see discussion in \citep{van2019three}).	
-% Benchmarks/architectures
- Our regularizer is evaluated on three CL benchmarks, specifically Split-MNIST (S-MNIST), Split-FashionMNIST (S-FMNIST), and the 10-tasks Permuted-MNIST (P-MNIST).
-We adhere to the same setups outlined in \cite{rudner2022continual, pan2020continual}, which use a two-layer MLP with 256 hidden units and ReLU activation for S-MNIST and S-FMNIST and a two-layer MLP with 100 hidden units for P-MNIST, to ensure consistency (see \cref{app:cl-exp} for full details).
-
-% Methods
-We compare our method against two categories of methods: {\em (i)}~weight-regularization methods: EWC, SI, and VCL (with coresets), and {\em(ii)}~function-based regularization methods: DER, FROMP, and S-FSVI.
-We also introduce an ablation study where we replace our $\bar{\MB}_t^{-1}$ with an identity matrix $\MI_M$, equivalent to having an L2 regularization between current and old function outputs.
-In \cref{tbl:cl_table_1}, we use 200 points for each task, and we further demonstrate our method's ability to compress the task data set information on a lower number of points for S-MNIST.
-
-%% Comments on the results:
-From \cref{tbl:cl_table_1}, it is clear that the weight-space regularization methods fail entirely compared to the function-space methods on S-MNIST and S-FMNIST but are still achieving comparable results on P-MNIST.
-Considering only function-space methods, we can see that \our achieves the best results on most data sets and is particularly effective when using fewer points per task.
-On S-FMNIST, our method obtains close results to DER, which regularizes the model by taking the mean squared error between current and old function outputs without accounting for the covariance structure of the loss similar to our L2 ablation.
-However, DER resorts to a reservoir sampling \citep{vitter1985random} that continuously update the set of points instead of selecting them at the task boundary.
-The \our-based regularizer obtains comparable results to the best-performing method on P-MNIST, S-FSVI, which requires heavy computations compared to \our to perform variational inference.
-% Finally, it is worth noticing as our ablation already provides a very solid baseline consistently over all data sets.
-
-\subsection{Reinforcement learning under sparse rewards}
-\label{sec:rl-exp}
-% We now demonstrate the quaility of \our's uncertainty estimates by showing that it can improve sample efficiency in RL.
-% Balancing the trade-off between exploration and exploitation is a key challenge in RL \cite{sutton2018reinforcement}.
-% Should an agent select actions that it knows will lead to high reward (exploitation), or actions which it has not select before in the
-% hope to discover new high reward actions (exploration)?
-
-% when used in conjuction with an
-% uncertainty-guided exploration strategy.
-
-% In this section, we show that \our's uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim,
-% demonstrating the quality of our uncertainty estimates.
-
-% A key challenge in RL is balancing the trade-off between exploration and exploitation.
-% That is, should an agent select actions that it knows will lead to high reward (exploitation), or should it
-% select new ones in hope to discover actions leading to higher reward (exploration).
-% One promising direction is to model the uncertainty associated with a learned transition dynamics and use it to guide exploration.
-% Prior work has learned dynamics models using GPs \cite{deisenrothPILCO2011,kamtheDataEfficient2018},
-% ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
-% and variational inference \cite{galImproving2016,houthooftVIME2017}.
-% There are then many ways to leverage uncertainty in model-based RL, for example,
-% taking an expectation over epistemic uncertainty  \cite{deisenrothPILCO2011,kamtheDataEfficient2018,chuaDeepReinforcementLearning2018},
-% sampling from the posterior, akin to Thompson sampling but referred to as posterior sampling RL
-% \cite{osbandMoreEfficientReinforcement2013},
-% and methods based on upper confidence bounds (UCB) \cite{curiEfficient2020}.
-
-% Make custom TikZ command (argument: colour)
-\newcommand{\lab}[1]{\protect\tikz[baseline=-.5ex]{\protect\node[minimum width=1.5em,minimum height=.8em,fill=#1,opacity=.1](a){};\protect\draw[#1,semithick](a.west)--(a.east);}}
-
-% The methods
-\definecolor{darkgray176}{RGB}{176,176,176} % darkgray176
-\definecolor{color-our}{RGB}{0,191,191} %darkturquoise0191191
-\definecolor{color-mlp}{RGB}{191,0,191} % darkviolet1910191
-\definecolor{color-ddpg}{RGB}{191,191,0} % goldenrod1911910
-\definecolor{color-ensemble}{RGB}{0,127,0} % green01270
-\definecolor{lightgray204}{RGB}{204,204,204} % lightgray204
-
-As a final experiment, we demonstrate the capability of \our to use its uncertainty estimates as guidance for exploration in model-based reinforcement learning (RL); this serves as a practical test to the quality of our uncertainty estimates.
-We use \our to help learn a dynamics model within a model-based RL strategy that employs posterior sampling to guide exploration \cite{osbandMoreEfficientReinforcement2013,osbandWhyPosteriorSampling2017}.
-%
-We use the cartpole swingup task in MuJoCo \cite{todorov2012mujoco}, a classic benchmark for nonlinear control (see \cref{fig:rl}).
-The goal is to swing the pole up and balance it around the upward position.
-We increase the difficulty of exploration by using a sparse reward function.
-See \cref{app:rl} for an overview of the reinforcement learning problem, details of the algorithm, and the experiment setup.
-
-%\cref{fig:rl} shows training curves using \our as the dynamic model (cyan) as well as a Laplace-GGN with GLM predictions (red), an ensemble of neuralnetworks (green) and a basic MLP wih no uncertainty (magenta).
-To ensure a fair comparison, we use the same MLP architecture/training scheme and use them in the same model-based RL algorithm, detailed in \cref{app:rl}.
-We also compare to deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016}, a model-free RL algorithim (yellow).
-The training curves show that \our's uncertainty estimates are useful for guiding exploration as it converges in fewer episodes, i.e.
-it is more sample efficient.
-As expected, the MLP strategy (without uncertainty) was not able to successfuly explore the environment.(), (\lab{color-mlp}),
-
-\cref{fig:rl} shows training curves for using \our as the dynamic model (\lab{color-our}), along with a Laplace-GGN~\cite{immer2021scalable} with GLM predictions (\lab{red}), an ensemble of neural networks (\lab{color-ensemble}), and a basic MLP without uncertainty (\lab{color-mlp}).
-To ensure a fair comparison, we maintain the same MLP architecture/training scheme across all these methods and incorporate them into the same model-based RL algorithm (see \cref{app:rl}).
-We also compare our results with Deep Deterministic Policy Gradient (DDPG, \cite{lillicrapContinuousControlDeep2016}), a model-free RL algorithm (\lab{color-ddpg}).
-The training curves show that \our's uncertainty estimates help exploration as it converges in fewer episodes, demonstrating higher sample efficiency.
-As expected, the MLP strategy (without uncertainty) was not able to successfuly explore the environment.\looseness-2
-
-% We compare \our (cyan) to a Laplace-GGN with GLM predictions (red), an ensemble of neural networks (green) and a basic MLP wih no uncertainty (magenta).
-% To ensure a fair comparison, we use the same MLP architecture/training scheme and use them in the same model-based RL algorithm, detailed in \cref{app:rl}.
-% See \cref{app:rl} for more details of our experiments.
-% As expected DDPG is the least sample inefficient
-% The training curves in \cref{fig:rl} show that \our's uncertainty estimates are useful for guiding exploration as it converges in fewer episodes.
-
-% \cite{deisenrothPILCO2011},
-% Posterior sampling
-
-% based on
-
-% Model-based RL algorithims are more sample efficient than their model-free counterparts as they learn a model of the transition dynamics and
-% use it to augment the RL loop.
-
-% Prior work has used show that modelling uncertainty in the transition dynamics can further improve exploration and thus sample efficiency.
-% For example, with GPs \cite{deisenrothPILCO2011,kamtheDataEfficient2018},
-% ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
-% and variational inference \cite{galImproving2016,houthooftVIME2017}
-
-% We now demonstrate the quaility of \our's uncertainty estimates by showing that it can improve sample efficiency in RL.
-
-% In this section, we show that \our's uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim,
-% demonstrating the quality of our uncertainty estimates.
-% In this section, we demonstrate  that our method's principled uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim.
-
-% It is an inherently unstable and underactuated mechanical system.
-
-% by using it to learn a dynamics model and
-% evaluate the
-% We test \our by using it to learn a dynamics model
-% our method on the cart pole swing up task in MuJoCo \cite{todorov2012mujoco}, a classic benchmark for nonlinear control, see \cref{fig:rl}.
-% The goal is to swing the pole up and balance it around the upward position.
-% We increase the  difficulty of exploration in this environment by using a sparse reward function.
-
-% We compare our method to a Laplace-GGN with GLM predictions (red), an ensemble of neural networks (green) and a basic MLP wih no uncertainty (magenta).
-% To ensure a fair comparison, we use the same MLP architecture/training scheme and use them in the same model-based RL algorithm, detailed in \cref{app:rl}.
-% % See \cref{app:rl} for more details of our experiments.
-% We also compare to deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016}, a model-free RL algorithim (yellow).
-% % As expected DDPG is the least sample inefficient
-% The training curves in \cref{fig:rl} show that \our's uncertainty estimates are good for exploration as it converges in fewer episodes.
-
-% We compare our method with deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016} -- a model-free RL baseline --
-% which is sample inefficient.
-
-\begin{figure}[!t]
- \centering\scriptsize
- \begin{subfigure}[c]{.24\textwidth}
- \centering
- \textbf{Cartpole swingup setup}\\[1em]
- \resizebox{\textwidth}{!}{%
- \begin{tikzpicture}[inner sep=0,outer sep=0]
-
-   % Draw decorated 'ground'
-   \draw[postaction={draw, decorate, decoration={border, angle=-45,
-					amplitude=1cm, segment length=.5cm}}] (-3,-1.5) -- (12,-1.5);
-
-   % The cart
-   \draw[draw=black,fill=black!50,draw=black,line width=3pt,rounded corners=1mm] (0,0) rectangle (9cm,3cm);
-   \node[fill=black,circle,minimum size=.5cm] (dot) at (4.5cm,3cm) {};
-
-   % Wheels
-   \node[fill=white,draw=black,line width=3pt,circle,minimum size=2cm,,fill=black!50] at (2cm,-.5cm) {};
-   \node[fill=white,draw=black,line width=3pt,circle,minimum size=2cm,fill=black!50] at (7cm,-.5cm) {};
-
-   % The arm
-   \node[anchor=north,minimum width=1cm,minimum height=14cm,draw=black,rotate=-20,rounded corners=5mm,yshift=7mm,xshift=-.3mm,fill=white,draw=black,line width=3pt] at (dot) {};
-   \node[fill=black,circle,minimum size=.5cm] at (dot) {};
-
-   % Markings
-   \draw[loosely dashed,line width=1pt] (4.5,6) -- (4.5,-10);
-
-   % Arrow
-   \draw[->,black,line width=3pt,-{Latex[length=7mm,width=7mm]}] (1,5) --node[above,outer sep=8pt]{\scalebox{4}{$x$}} (4.5,5);
-
-   \def\centerarc[#1](#2)(#3:#4:#5)% Syntax: [draw options] (center) (initial angle:final angle:radius)
-   { \draw[#1] ($(#2)+({#5*cos(#3)},{#5*sin(#3)})$) arc (#3:#4:#5); }
-
-   % Draw arc
-   \centerarc[black,line width=3pt](dot)(250:270:11)
-   \node at (2.5,-9) {\scalebox{4}{$\theta$}};
-
-   %\node[white,minimum size=1cm] at (4.5,-13) {};
-
- \end{tikzpicture}}\\[2em]~
- \end{subfigure}
- \hfill
- \begin{subfigure}[c]{.7\textwidth}
-   \raggedleft\scriptsize
-   \setlength{\figurewidth}{\textwidth}
-   \setlength{\figureheight}{.55\figurewidth}
-   \pgfplotsset{axis on top,ymajorgrids,axis line style={draw=none},legend style={at={(-.1,-.1)},anchor=south east}}
-   \pgfplotsset{grid style={line width=.1pt, draw=gray!10,densely dotted}}
-   \hspace*{-1.7cm}%
-   \def\our{{\sc sfr} (ours)}
-   \input{./fig/rl.tex}
- \end{subfigure}\\[-1.5em]
- \caption{\textbf{Cartpole swingup with sparse reward.} Training curves showing that \our's uncertainty estimates improve sample efficiency in RL.
-   Our method (\lab{color-our}) converges in fewer environment steps than the baseline model-based RL method and DDPG, the model-free baseline.
-The dashed lines mark the asymptotic return for the methods not coverged in the plot.}
- \label{fig:rl}
- % \vspace*{-1em}
-\end{figure}
-
-%
-
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.5\textwidth, angle=270]{fig/weight-space-to-functio-space.pdf}
-%   \caption{}
-% \end{figure}
-
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.5\textwidth, trim=0 100 0 10]{fig/cartpole-training-curves.pdf}
-%   \caption{}
-% \end{figure}
-
-% \begin{table}
-%   \caption{Negative test log likelihood (lower is better) on UCI classification tasks (2 hidden layers, 50 tanh). Our SVGP predictive outperforms the GLM predictive. }
-% \end{table}
-
 \section{Discussion and conclusion}
@@
 
-%In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
-%On the other hand, the NTK may be highly non-stationary and is dependent on the NN architecture, for example, the activation functions.
-
-The broader impact of this work lies in its potential to provide tooling for how neural networks are utilized, offering more efficient and principled ways of handling uncertainty and continual learning.
-This contribution, we believe, has significant implications for future applications of machine learning in dynamic, real-world settings where data is unevenly distributed, uncertain, and continuously evolves.\looseness-1
-
-A reference implementation of the methods presented in this paper is currently available as supplementary material and will be made available under the MIT License on GitHub upon acceptance.
-
-%\section*{Broader Impact}
-
-% \section*{References}
-%\small
-%\printbibliography
-%\normalsize
-% TODO make bibliography small a better way
-
-%References follow the acknowledgments. Use unnumbered first-level heading for
-%the references. Any choice of citation style is acceptable as long as you are
-%consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
-%when listing the references.
-%Note that the Reference section does not count towards the page limit.
-%\medskip
-
 \clearpage
 
-\phantomsection%
-\addcontentsline{toc}{section}{References}
-\begingroup
-\small
-\bibliographystyle{abbrvnat}
-\bibliography{bibliography}%zotero-library
-\endgroup
-
-\clearpage
-
-\nipstitle{
-    {\Large Supplementary Material:} \\
-    Sparse Function-space Representation \\ of Neural Networks}
-\pagestyle{empty}
-
+% In the unusual situation where you want a paper to appear in the
+% references without citing it in the main text, use \nocite
+% \nocite{langley00}
+
+\bibliography{bibliography}
+\bibliographystyle{icml2023}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% APPENDIX
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
 \appendix
-
-This supplementary document is organized as follows. 
-%
-\cref{app:method} provides a more extensive overview of the technical details of \our.
-%
-\cref{app:cl} covers additional details on the \our-based regularizer used for continual learning.
-%
-\cref{app:rl} provides a more extensive writeup of the reinforcement learning setup used in the experiments.
-%
-\cref{app:experiments} provides the full details of each individual experiment in the main paper.
-
-\section{Method details}
-\label{app:method}
-In this section, we first show in \cref{app:losses} how the dual parameters used for \our are computed for the different losses employed in our experiments, and then we discuss the computational complexity of our method in \cref{app:comp_compl}.
-%
-
-\subsection{Computation of the dual parameters for different losses}
-\label{app:losses}
-As shown in \cref{eq:dual_param} in the main paper, our method relies on computation of the dual parameters.
-We can derive them in general for the family of exponential likelihoods, by rewriting the likelihood in the natural form,
-\begin{equation}
- \ell(h(f), y) = -\log p(y \mid f) =  A(f)  - \langle t(y), f \rangle,
-\end{equation}
-where $A(f)$ is the log partition function, $h(\cdot)$ is the inverse link function, $t(y)$ are the sufficient statistics which for all our likelihoods is simply $t(y)=y$, finally $f$ denotes the neural network output before the inverse link function.
-%given the loss functions we use $t(y) = y$. 
-Then, taking the first and second derivatives of the loss in this form become:
-\begin{equation}\label{eq:dual_param_app}
-  \nabla_{f}  \ell(h(f), y_i) |_{f=f_i} =  A'(f_i) - y_i
-  \quad \text{and} \quad
-  \nabla^2_{f\!f} \ell(h(f), y_i)  |_{f=f_i} = A''(f_i).
-\end{equation}
-% The second derivative of the log partition function is easily calculated and
-In this section, we provide the derivatives needed for the losses used in this work, \ie, the mean squared error (MSE) likelihood, used for the regression tasks, the Bernoulli likelihood, for binary classification, and the categorical likelihood, used for multi-class classification.
-
-For regression, the negative log likelihood comes from the MSE, and for a single input it can be written as
-\begin{equation}
-	\ell(h(f_i), y_i) = \frac{1}{2} (y_i -f_i)^2,% -\log \Norm( h(f) | y, \sigma^2) 	= - \log 
-\end{equation}
-where the inverse link function is simply $h(f) = f$. Thus, the first and second derivatives are
-\begin{equation}
-	\nabla_f \ell(\sigma(f), y_i)|_{f=f_i} =  f_i - y_i \quad \text{ and } \quad  \nabla_{f\!f} \ell(h(f), y_i)|_{f=f_i} = 1.
-\end{equation}
-
-In binary classification, we have a Bernoulli likelihood. The inverse link function is the sigmoid function $h(f) = \sigma(f) = \frac{1}{1 + e^{-f}}$, and we can then write the derivates as follows
-%\begin{equation}
-%\begin{aligned}
-%	\ell(h(f), y) 
-%	&= -\log \left( \sigma(f)^y (1 - \sigma(f))^{1-y} \right) \\
-%	&= - y \log(\sigma(f)) - (1-y) \log(1- \sigma(f)) \\
-%	&= - y f + \log(1 + e^f) 
-%\end{aligned}
-%\end{equation}
-%Then, it follows that the the derivative we are interested in are
-\begin{equation}
-	\nabla_f \ell(h(f), y_i)|_{f=f_i} = \sigma(f_i) - y_i  \quad \text{ and } \quad  \nabla_{f\!f} \ell(h(f), y_i)|_{f=f_i} = \sigma(f_i) (1 - \sigma(f_i)).
-\end{equation}
-
-In multi-class classification, the function outputs are no more scalar but a vector of logits $f_\weights(\vx_i) = \bm{f _i} \in \R^C$.
-The inverse link function for the categorical loss is the softmax function $\textrm{softmax}(\bm{f}) : \R^C \mapsto \R^C$ defined as $h(\bm{f}) = \textrm{softmax}(\bm{f}) = \frac{\exp(\bm{f})}{ \sum^C_{c=1} \exp(\bm{f}_c)} \in \R^C$.
-If we write the targets as a one-hot  encoded vector $\vy_i$, we can write the negative log likelihood as
-\begin{equation}
-\begin{aligned}
-	\ell(h(\bm{f}),\vy_i) &= - \log\left( \vy_i^\T \textrm{softmax}(\bm{f})\right).\\
-	% &= - y_i \cdot \log \left( \left[ \textrm{Softmax}(\bm{f}) \right]_i \right)
-\end{aligned}
-\end{equation}
-% where $\left[\textrm{Softmax}(\bm{f})\right]_j = \frac{\exp(\bm{f}_j)}{\sum_{c=1}^{C} \exp(\bm{f}_c)} \in \R$ defines the $j$\textsuperscript{th} entry of the logits fed through the $\textrm{Softmax}(\cdot)$ function.
-Finally, we can write the first and second derivatives as follows
-\begin{equation}
-\begin{aligned}
-	[\nabla_{\bm{f}} \ell(h(\bm{f}), \vy_i)|_{\bm{f}=\bm{f}_i}]_j &= \left[\textrm{Softmax}(\bm{f}) - \vy_i  \right]_j \\
-	\left[\textrm{diag}\left(\nabla_{\bm{f}\!\bm{f}} \ell(h(\bm{f}), \vy_i)|_{\bm{f}=\bm{f}_i}\right)\right]_{j} &= \left[\textrm{Softmax}(\bm{f})\right]_j (1 - \left[\textrm{Softmax}(\bm{f})\right]_j),
-\end{aligned}
-\end{equation}
-
-where we only need the $\textrm{diag}$ given our independence assumption.
-
-% While these equations deal with single output functions, we can extend them to multi output functions, such as for the categorical loss.
-%The easiest example to deal with is the Bernoulli loss, where 
-%The above formulation can be extended to vector input and outputs, \ie, for the categorical loss. In the following table, we list the likelihoods we use and their dual parameter below:
-%\begin{equation}
-%\begin{aligned}
-%	\ell(y, \vf_\vw(\vx)) 
-%%	&:= - \log p(y | \sigma(f))) \\
-%%	&= -y \log(\sigma(f)) - (1-y) \log(1-\sigma(f))\\
-%%	&= -y f + \log(1+e^f) \red{ \left[ = - (\langle f, y\rangle - \log(1+e^f)) \right] }
-%\end{aligned}
-%\end{equation}
-
-%\begin{table}[!ht]
-%\centering
-%\caption{}
-%\begin{tabular}{@{}cccc@{}}
-%\toprule
-%Loss        & $h(\cdot)$ & $\nabla_{f}$ & $\nabla^2_{f\!f}$  \\ \midrule
-%Bernoulli   & $\sigma(f) = \frac{1}{1 + e^{-f}}$ & $\sigma(f) - y$   & $\sigma(f)(1-\sigma(f))$ \\
-%MSE         & & $y - f$      & $1$ \\
-%Categorical & $\mathcal{S}_i(\vf) = \frac{e^{\vf_i}}{\sum_{j=1}^C e^{\vf_j}}$ &  $\begin{bmatrix}
-%		p_1\\ \vdots\\p_k
-%	\end{bmatrix}$     &   $\begin{bmatrix}
-%		p_1\\ \vdots\\p_k
-%	\end{bmatrix}$ \\ \bottomrule
-%\end{tabular}
-%\end{table}
-
-\subsection{Computational complexity}
-\label{app:comp_compl}
-% Big O
-% train neural network
-% compute the NTK -> from the NTK paper
-% we outer product of the kzi O(NM^2)
-% inversion O(M^3)
-In this section, we analyze the computational complexity of \our.
-We first need to train a neural network $f_\weights$ and then compute the posterior covariance matrix that characterizes our sparse GP representation of the model.
-The first step then requires the usual complexity cost for training a neural network, where defining the cost of a forward pass (and backward pass
-%\todo{these two should be similar, we can't cite the NTK paper were they are using this notation unfortunately}
-) as $[F\!P]$, this can roughly sketched as $\mathcal{O}(2  E  N[F\!P])$, where $E$ is the number of training epochs and  $N$ the number of training samples.
-Thus, there is no additional cost involved in the training phase of the neural network.
-
-Given the trained network, we construct the covariance function  which is defined through the NTK~\citep{jacot2018neural}.
-We relied on the Jacobian contraction implementation using PyTorch~\citep{paszke2019pytorch}.
-To compute the kernel Gram matrix for a batch of $B$ samples with this implementation has a computational complexity of $\mathcal{O}( B C [F\!P] + B^2 C^2 P)$, where $C$ is the number of NN outputs and $P$ is the number of parameters of the neural network.
-In \cref{eq:dual_sparse}, we compute $\MB_\vu$ iterating through all the $N$ training points to compute the $\vkzi$ and then use them to compute the outer product, that has a cost of $\mathcal{O}(M^2)$, with $M$ being the number of inducing points following the notation used in the main paper.
-The total cost of this operation becomes $\mathcal{O}(N M^2)$, which is also the dominating cost of our approach.
-
-% Practical implementation
-% mention that we do that in batches not full N 
-% role of jitter 
-% role of clamping
-% GPU A100 Nvidia
-In practical terms, some care needs to be taken during the implementation, both in terms of memory consumption and numerical stability.
-For the former, we batched over the number of training samples, $N$, which keeps the memory consumption in check without need for any further approximations.
-The computation of the terms in \cref{eq:dual_sparse_post} require the inversion of an $M \times M$ matrix, that we implemented in a numerically stable manner by using Cholesky factorization.
-We also introduce a small jitter and clip of the GGN matrix for numerical stability where needed (see discussions in \cref{app:experiments}).
- We run our experiments GPU clusters equipped with NVIDIA A100 GPUs.
-
-\section{\our for continual learning}
-\label{app:cl}
-This section provides additional details about the derivation of the \our-based regularizer described in \cref{sec:sequential} and how we extended it for dealing with the multi-output setting in our experiments.
-\subsection{Derivation of the regularizer term}
-For continual learning, the model cannot access the training data from previous tasks up to task $t-1$, denoted here as $\dataset_\textrm{old} = \bigcup_{s=1}^{t-1} \dataset_s$, and for each new task $t$ receives a new chunk of data $\dataset_\textrm{new} = \dataset_t$.
-On the other hand, in the supervised learning setting (described in \cref{sec:methods}), the neural network model has access to all the training data at once, \ie, the objective we are trying to optimize is
-\begin{equation}
-	\weights^* = \argmin_\weights \mathcal{L}(\dataset_\textrm{old} \cup \dataset_\textrm{new}, \weights) = \argmin_\weights \sum_{i \in \dataset_\textrm{old} \cup \dataset_\textrm{new}}\ell(f_\weights(\mathbf{x}_{i}), y_i) + \delta \mathcal{R}(\weights).
-\end{equation} 
-Our goal in the continual setting is to replace the missing data coming from $\dataset_\textrm{old}$ by resorting to a functional regularizer that accounts for that by forcing the predictions of the neural networks over the inducing points $\mathcal{Z}_t$ to come from $f^{\textrm{old}}_\weights(\vz_i) \sim q^\textrm{old}(\vu),  \forall \vz_i \in \mathcal{Z}_t$.
-As shown in \citep{khan2017conjugate, adam2021dual}, we can view the dual parameters derived in \cref{sec:sparse-dual-gp} as linked to approximate likelihood terms.
-Using this insight, we can rewrite the sparse GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
-%
-\begin{align} \label{eq:normal}
-	q(\vu)
-	& \propto  \Norm(\mathbf{0}, \MKzz) \prod_{i \in \dataset_\textrm{old}} \exp \! \left(-\frac{\hat{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 \right) \\
-        & \propto p(\vu) \Norm(\tilde{\vy}; \vu, \MB_\vu),
-\end{align}
-% The first normals are the approximate likelihoods 
-where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}_i$.
-The sparse GP posterior $q(\vu)$ is proportional to the product between the prior over the inducing points $p(\vu)$ and a Gaussian term $\Norm(\tilde{\vy}; \vu, \MB_\vu)$, which arises from the sparse approximation to the likelihood.
-Replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$, we can see the similarity between the sparse GP and a linear model, for which the kernel is the linear kernel.
-Therefore, we use the quadratic term from  $\Norm(\tilde{\vy}; \vu, \MB_\vu)$ as our regularizer in place of the missing data term.
-By taking the $\log(\cdot)$, the regularizer becomes $(\tilde{\vy} - \vu)^\top \bar{\MB}^{-1}(\tilde{\vy} - \vu)$.
-Given that $\tilde{\vy}$ are in the function space we can instead us simply the previous neural network predictions $f^{\textrm{old}}_\weights(\vz_i)$ and save computations.
-
-\subsection{Extending the CL regularizer to multi-class settings} 
-\label{sec:cl_multioutput}
-%
-In a multi-class classification setting, the neural network can be seen as a function approximator that maps inputs $\vx \in \inputDomain$ to the logits $\textit{\textbf{f}} \in \outputDomain$, \ie, $f_\mathbf{w}: \inputDomain \to \outputDomain$.
-As a consequence, the Jacobian matrix is $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{C \times P}$ and the kernel of the associated sparse GP derived in \cref{sec:sfr}, $\kappa(\vx, \vx')$ is a tensor in $\R^{C \times P \times P}$.
-This means that we need to compute the dual parameters and the matrix $\bar{\MB}^{-1}_{t, c}$ for all the function's outputs.
-If we denote $\kappa_c(\vx, \vx') \in \R$, as the kernel related to the $c$\textsuperscript{th} output function, \ie, the logit for class $c$, we can write the dual parameters as
-%
-\begin{equation} \textstyle
-  \valpha_{\vu, c}  =  \sum_{i=1}^N  \vkzic \, \hat{\alpha}_{i, c} \in \R^{M}
-  \quad \text{and} \quad
-  \MBeta_{\vu, c} =  \sum_{i=1}^N \vkzic \,\hat{\beta}_{i, c} \, \vkzic^{\T} \in \R^{M \times M} ,    
-\label{eq:app_dual_sparse}
-\end{equation}
-%
-where $\vkzic$ is the kernel $\kappa_c(\cdot, \cdot)$ computed for the inducing points $\vz \in \mathcal{Z}$ and the input point $\vx_i$ for class $c$. In this setting, the dual variables are
-\begin{equation}
-\begin{aligned}
-  \hat{\alpha}_{i,c} &\coloneqq  \left[\hat{\valpha}_{i}\right]_c = \left[\nabla_{f}\log p(y_i \mid f) |_{f=f_i} \right]_c \in \R,\\
-  \hat{\beta}_{i,c} &\coloneqq \left[\textrm{diag}(\hat{\vbeta}_i)\right]_c = \left[ - \nabla^2_{ff}\log p(y_i \mid f) |_{f=f_i} \right]_c \in \R,
-\end{aligned}
-\end{equation}
-where the operator $[ \cdot ]_c$ is taking the $c$\textsuperscript{th} element of a vector.
-In fact, in the multi-class setting $\hat{\valpha}_{i}$ is a vector in $\R^C$ and $\hat{\vbeta}_{i}$ a matrix in $\R^{C \times C}$.
-For the \our-regularizer, at the end of each task, we compute the matrix $\bar{\MB}^{-1}_{t, c}$ as 
-\begin{equation}\textstyle
- 	\bar{\MB}^{-1}_{t, c} = \MKzzc^{-1} \MBeta_{\vu, c} \MKzzc^{-1} \in \R^{M \times M}, 
- 	\quad \text{s.t.} \quad
- 	\MBeta_{\vu, c} =  \sum_{i \in \dataset_t} \vkzi \,\hat{\beta}_{i, c} \, \vkzi^{\T}.
-\end{equation}
-The kernel computation is based on the relationship between the observed data and the parametrized function.
-For this reason, computing the kernel $\kappa_c$ for classes $c$, for which the model has not observed any data yet, is not meaningful.
-In practice, for our method we define $\bar{\MB}^{-1}_{t, c}$ to be $\bar{\MB}^{-1}_{t, c} = \MI_M$ $\forall c \not\in \mathcal{C}_t$, where $\mathcal{C}_t$ is the set of classes observed up to task t.
-For example, for S-MNIST, after task 1 the set of observed classes for which we will compute the kernel is $\mathcal{C}_1 = \{0, 1\}$, then after task 2 it becomes $\mathcal{C}_1 = \{0, 1, 2, 3\}$, et cetera.
-Finally, we can rewrite $\mathcal{R}_\mathrm{\our}$ as follows
-\begin{equation}\label{eq-cl-regularizer}%\textstyle
-  \mathcal{R}_\mathrm{\our}(\weights, \mathcal{M}) = \frac{1}{2} \sum_{s=1}^{t-1} \sum_{c=1}^{C} \frac{1}{M} 
-	\left\lVert 
-	\vu_c - \vu_{s,c} % f_{\weights_{s}}(\MZ_s)
-	\right\rVert_{\bar{\MB}^{-1}_{s}},
-\end{equation}
-%
-with $\vu_c \in \R^M$ and $u_{i, c} = \left[ f_{\weights}(\vz_{i}) \right]_c, \forall {\vz_i} \in \mathcal{Z}_s$.
-
-\section{\our for model-based reinforcement learning}
-\label{app:rl}
-%
-As a final experiment in the main paper in \cref{sec:rl-exp}, we provided a demonstration of combining our \our approach with model-based reinforcement learning.
-As such, this is a direct extension of the uncertainty quantification and representation capabilities already demonstrated in the supervised (and continual) learning examples in the main paper.
-However, as the RL setting differs from the supervised and continual learning settings, we present additional background material on it and thus \cref{app:rl} has been separated out to a separate section in the appendix.
-
-In this appendix, we provide a background of the reinforcement learning problem, details of our
-model-based RL algorithim, an overview of the cart pole swing up environment, and
-all details required for reproducing our experiments.
-
-% more details of the reinforcement learning experiments, including
-% how we used \our in this setting.
-
-\subsection{Background}
-We consider environments with states \(\state \in \stateDomain \subseteq \R^{D_{\state}} \),
-actions \(\action \in \actionDomain \subseteq \R^{D_{\action}}\) and transition dynamics
-\(\transitionFn: \stateDomain \times \actionDomain \rightarrow \stateDomain \), such that
-$\state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t}$, where  $\noise_{t}$
-is i.i.d.\ transition noise.
-We consider the episodic setting where the system is reset to an initial state $\state_{0}$ at each episode and we
-assume that there is a known reward function $r : \stateDomain \times \actionDomain \rightarrow \R$.
-% Following the Markov decision process formulation \cite{bellmanMarkovianDecisionProcess1957a}, we
-% denote the states \(\state \in \stateDomain \subseteq \R^{D_{\state}} \) and actions \(\action \in \actionDomain \subseteq \R^{D_{\action}}\)
-% of the sytem, the reward function $r : \stateDomain \times \actionDomain \rightarrow \R$, and transition dynamics
-% \(\transitionFn: \stateDomain \times \actionDomain \rightarrow \stateDomain \), such that
-% $\state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t}$ where  $\noise_{t}$
-% is i.i.d. transition noise.
-% $\mathbb{E}_{\noise_{0:\infty}} \big[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \big]$
-% \begin{align} \label{eq-model-free-objective}
-% \policy^{*} = \arg \max_{\policy \in \policyDomain} J(\transitionFn, \policy) = \arg \max_{\policy \in \policyDomain} \mathbb{E}_{\noise_{0:\infty}} \bigg[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \bigg]
-% \quad \text{s.t. } \state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t},
-% \end{align}
-The goal of RL is to find the policy \(\pi : \stateDomain \rightarrow \actionDomain\)
-(from a set of policies $\Pi$) that maximises the sum of discounted rewards
-in expectation over the transition noise,
-\begin{align} \label{eq-model-free-objective}
-J(\transitionFn, \policy) = \mathbb{E}_{\noise_{0:\infty}} \bigg[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \bigg]
-\quad \text{s.t. } \state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t},
-\end{align}
-where $\gamma \in [0, 1)$ is a discount factor.
-In this work, we consider model-based RL where a model of the transition dynamics is learned \(f_{\mathbf{w}^{*}} \approx \transitionFn\) and then used by a planning algorithm.
-A simple approach is to use the learned dynamic model $f_{\mathbf{w}^{*}}$ and maximise the objective in \cref{eq-model-free-objective},
-\begin{align} \label{eq-greedy}
-  \policy^{\text{Greedy}} &= \arg \max_{\pi \in \Pi} J(f_{\mathbf{w}^{*}}, \pi).
-\end{align}
-However, we can leverage the method in \cref{sec:methods} to obtain a function-space posterior over the learned dynamics $q_{\mathbf{u}}(\transitionFn \mid \dataset)$,
-where $\mathcal{D}$ represents the state transition data set \(\mathcal{D} = \{(s_{i},a_{i}), s_{i+1}\}_{i=0}^{N}\).
-Importantly, the uncertainty represented by this posterior distribution can be used to balance the exploration-exploitation trade-off,
-using approaches such as posterior sampling \cite{osbandWhyPosteriorSampling2017,osbandMoreEfficientReinforcement2013},
-\begin{align} \label{eq-posterior-sampling}
-  \policy^{\text{PS}} &= \arg \max_{\pi \in \Pi} J(\tilde{f}, \pi)
-\quad \text{s.t. } \tilde{\transitionFn} \sim q_{\mathbf{u}}({\transitionFn} \mid \dataset),
-\end{align}
-where a function $\tilde{\transitionFn}$ is sampled from the (approximate) posterior $q_{\mathbf{u}}({\transitionFn} \mid \dataset)$ and used to find a policy as
-in \cref{eq-greedy}.
-Intuitively, this strategy will explore where the model has high uncertainty, which in turn will reduce the model's uncertainty as data is collected and used to
-train the model.
-This strategy should perform well in environments which are hard to explore, for example, those
-with sparse rewards.
-
-% \todo{could try to implement Pathwise conditioning in function-space}
-
-\subsection{Algorithm}
-In practice, it is common to approximate the infinite sum in \cref{eq-posterior-sampling}
-by planning over a finite
-horizon and bootstrapping with a learned value function.
-Following this approach, our planning algorithim is given by,
-\begin{equation} \label{eq-fast-update-mpc}
-  \policy^{\text{PS}}(\state) = \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
-\E \bigg[ \sum_{t=0}^{H-1} \gamma^{t} r(\state_{t},\action_{t}) \mid \state_{0}=\state  \bigg] + Q_{\theta}(\state_{\Horizon}, \action_{H}),
-%\quad \text{s.t. } \state_{t+1} &= \tilde{\transitionFn}(\state_{t}, \action_{t}) + \noise_{t}
-\end{equation}
-such that $\state_{t+1} = \tilde{\transitionFn}(\state_{t}, \action_{t}) + \noise_{t}$, 
-where $\tilde{\transitionFn} \sim q_{\mathbf{u}}(\transitionFn \mid \dataset)$ is a sample from the dynamics posterior and
-${Q_{\theta}(\state, \action) \approx \E \big[ \sum_{t=0}^{H-1} \gamma^{t} r(\state_{t},\action_{t}) \mid \state_{0}=\state, \action_{0}=\action  \big]}$
-is a learned value function with parameters $\theta$.
-We use deep deterministic policy gradient (DDPG, \cite{lillicrapContinuousControlDeep2016}) to learn the action value function $Q_{\theta}$.
-Note that we also learn a policy but its sole purpose is for learning the value function.
-
-% \todo{what is correct citation for MPPI?}
-
-\textbf{Model predictive path integral (MPPI)}
-We adopt model predictive path integral (MPPI) control \cite{panSample2015,williamsModel2017}
-to plan online over a $H$ step horizon and then bootstrap with a learned value function.
-MPPI is an online planning algorithim which iteratively improves the action trajectory $\action_{t:t+H}$ using samples.
-At each iteration $j$, $N$ trajectories are sampled according to the currect action trajectory $\action^{j}_{t:t+H}$.
-The top $K$ trajectories with highest returns $\sum_{h=0}^{H} = \gamma^{h} r(\state^{j}_{t+h}, \action^{j}_{t+h}) + \gamma Q_{\theta}(\state_{\Horizon}, \action_{H})$ are selected.
-The next action trajectory $\action^{j+1}_{t:t+H}$ is then computed by taking the weighted average of the top $K$ trajectories
-with weights from the softmax over returns from top $K$ trajectories.
-After $J$ iterations the first action is executed in the environment.
-
-\subsection{Environment}
-We consider the cartpole swingup task in MuJoCo~\cite{todorov2012mujoco}.
-However, we make exploration difficult by implementing a sparse reward function which returns $0$ unless the reward is over a threshold value. That is, our reward function is given by,
-$$\hat{r}(\state_{t}, \action_{t}) =
-\begin{cases}
-    r(\state_{t}, \action_{t}),& \text{if } r(\state_{t}, \action_{t})\geq 0.6\\
-    0,              & \text{otherwise}
-\end{cases}
-$$
-In all experiments we collected an initial data set using a random policy for one episode and we set action repeat as two.
-
-\subsection{Experiment configuration}
-%
-This section details how we configured and ran our reinforcement learning experiments.
-
-\textbf{Dynamic model}
-In all experiments we used an MLP dynamic model with a single hidden layer of width 64 and Tanh activation functions.
-At each episode we used Adam \cite{adam} to optimise the NN parameters for $5000$ iterations with a learning rate of $0.001$ and a batch size of $64$.
-We reset the optimizer after each episode.
-As we are performing regression we instantiate the loss function in \cref{eq-empirical-risk} as the well-known mean squared error.
-This corresponds to a Gaussian likelihood with unit variance.
-We then set the prior precision as $\delta=0.0001$.
-% It is worth noting that $\delta$ effects both the neur
-
-\textbf{Value function learning}
-We use DDPG to learn the action value function.
-DDPG learns both a policy and a value function but we do not use the policy.
-In our experiments, we parameterised both the actor and critic as MLPs with two hidden layers of width $128$ with ELU activations.
-We train them using Adam for $500$ iterations at each episode, using a learning rate $0.0001$ and a batch size of $512$.
-DDPG uses a target value function to stabilise learning and for the soft target updates
-we used $\tau = 0.005$. 
-DDPG is an off-policy algorithm where the exploration policy samples from a noise process, which here was a Gaussian distribution with $\sigma=0.1$ and clipping at $0.3$.
-
-\textbf{Model predictive path integral (MPPI)}
-In all model-based RL experiments, we used a $H=5$ step horizon and a discount factor of $\gamma=0.9$.
-We sampled $N=256$ trajectories for $J=5$ iterations with $K=32$.
-We used a temperature of $0.5$ and momentum $0.1$.
-
-% \subsubsection{Experiments}
-
-\textbf{MLP}
-As a baseline, we ran experiments using only the MLP dynamic model with no uncertainty.
-As can be seen in \cref{fig:rl}, this strategy is not always able to solve the task, indicated by the magenta line converging at $\sim 310$.
-This is expected because this strategy has no principled exploration mechanism.
-
-\textbf{\our}
-In the \our experiments we used $M=128$ inducing points as this seemed to be sufficient.
-The results in \cref{fig:rl} indicate that \our's uncertainty estimates are of high quality.
-This is because the agent is able to solve the task with less environment interaction, indicated
-by the cyan training curve converging quicker.
-
-\textbf{Laplace-GGN}
-In the Laplace-GGN experiments we used the Laplace library from \cite{daxberger2021laplace}
-with the full hessian structure over all of the network's weights.
-We then used the GLM predictions.
-As expected, the Laplace-GGN is also able to solve the sparse reward environment.
-
-\textbf{Ensemble}
-The ensemble experiments used $5$ members where each member was an MLP with one hidden layer of width $128$ and Tanh activations, \ie\ the same architecture as the other experiments.
-At each episode, the ensemble was trained for $10000$ iterations using the Adam optimiser.
-We used a learning rate $0.0001$ and a batch size of $64$.
-At each time step in the planning horizon we used the following procedure to sample from the ensemble.
-First, the mean and variance of the ensemble members predictions were calculated.
-Next, we sampled from the resulting Gaussian.
-\cref{fig:rl} shows that the ensemble required more environment interaction to solve the task.
-This is indicated by the green line not converging within the $50$ episodes shown in the figure.
-
-\textbf{DDPG}
-The DDPG experiment serves as our model-free RL baseline.
-In the DDPG experiment we use a standard deviation of $0.6$ for the actor to help it explore
-the environment.
-We increased the width of the MLPs to $512$ and we increased the discount factor to $\gamma=0.99$.
-As expected, the results show that DDPG requires a lot more environment interaction to solve the task.
-\cref{fig:rl} also shows that DDPG does not converge to the same asymptotic performance as \our.
-This is due to some of the random seeds not being able to successfuly explore the environment.
-
-% \textbf{Summary}
-\subsubsection{Summary}
-Our results motivate further experiments looking into NN uncertainty quantification
-for model-based RL.
-To the best of our knowledge, we are the first to leverage the Laplace-GGN for model-based RL.
-Our results indicate that both the Laplace approximation and \our could offer benefits over
-ensembles of NNs, which are typical in model-based RL.
-Although further experiments are required, our results indicate that \our could offer
-better uncertainty estimates in these tasks.
-We believe this may be due to \our sampling in function space as opposed to weight space like
-Laplace-GGN.
-
-\section{Experiment details}
-\label{app:experiments}
-%
-We provide further details for the experiments presented in the main paper.
-In tables throughout the paper, we mark the best-performing method/setting by typesetting them boldface.
-Following this, we check with a two-tailed $t$-test whether the bolded entry significantly differs from the rest.
-Those not differing from the best performing one with a significance level of 5\% are also bolded.
-The illustrative examples in \cref{fig:teaser,fig:banana} include toy problems for regression and classification.
-The 1D regression problem (\cref{fig:teaser}) uses an MLP with two hidden layers (64 hidden units each, with tanh activation), whereas the 2D banana binary classification problem uses an MLP with two hidden layers (64 hidden units each, with sigmoid activation).
-Both examples use Adam as the optimizer.
-We include Python notebooks for trying out the models.
-The illustrative HMC baseline in \cref{fig:banana} (right) was implemented with the help of hamiltorch (\url{https://github.com/AdamCobb/hamiltorch}).
-We used ten chains with 10,000 samples each and remove 2000 samples as burn-in.
-
-\subsection{Capturing uncertainty in UCI tasks under supervised learning}
-\label{app:uci}
-%
-In \cref{sec:uci} in the main paper, we showed experiments on 8 UCI data sets \cite{UCI} matching those presented in \cite{immer2021improving}.
-For direct comparison, we replicate the benchmark as in \cite{immer2021improving}: for each data set, we run the neural network training and the \our prediction pipeline on 10 values of prior precision $\delta$ and 10 seeds matching those used in \cite{immer2021improving}.
-After completing these 100 runs, we select the $\delta$ with the lowest mean validation set NLPD and report the test set performance statistics in our result tables.
-The range of $\delta$ used for the hyperparameter search varies depending on data set and the number of inducing points.
-Below we list the selected $\delta$ ranges:
-\begin{itemize}
-\item {\sc digits}: The ten $\delta$ values are logspaced between $10^{-1}$ and $10^2$, matching~\cite{immer2021improving}.
-\item {\sc cancer}: For $M > 128$, the ten $\delta$ values are logspaced between $10^{-1}$ and $10^2$.
-With too low values of $\delta$, we observed numerical errors in the Cholesky decomposition required for constructing the \our dual.
-\item {\sc satellite}: For $M < 512$, the tend $\delta$ values are logspaced between $10^{-1}$ and $10^2$, matching~\cite{immer2021improving}.
-\item {\sc satellite}: For $M \geq 512$, the ten $\delta$ values are logspaced between $10^{1}$ and $10^2$.
-With too low values of $\delta$, we observed numerical errors in the Cholesky decomposition required for constructing the \our dual.
-\item Othewise: The ten $\delta$ values are logspaced between $10^{-2}$ and $10^2$, matching~\cite{immer2021improving}.
-\end{itemize}
-
-For each data set, the prior precision values reported above are in practice divided by the training set size, as we use a mean loss instead of a sum loss.
-The $\delta$ values are reported here before the scaling for matching with the implementation in \cite{immer2021improving}.
-We note that while the ranges of prior precision were clipped for some data sets, the best performance in terms of NLPD was not achieved near the smallest $\delta$ tested.
-Other numerical considerations relevant to our method are the clipping of the Hessian of the log likelihood, and adding jitter before performing the Cholesky decomposition within the \our dual computation.
-In contrast to \citet{immer2021improving}, we did not perform any clipping in the Hessian computation, but some of the UCI experiments required adding jitter of size $10^{-6}$ for numerical stability.
-
-All neural network designs and related hyperparameters are set as in \cite{immer2021improving} for a fair comparison, for instance we train the 2-layer MLPs with learning rate $0.001$ for 10,000 epochs, using the full data set instead of batching.
-In addition, we vary the subset size $M \in  \{16, 32, 64, 128, 256, 512\}$ to observe the impact of sparseness on the predictive performance, see \cref{tbl:uci-appendix} and \cref{tbl:uci-appendix-acc} for the complete NLPD and accuracy results.
-
-Our code implementation of the UCI experiments has been built on top of the code provided for \cite{immer2021improving}, using the \our method, and is provided in the supplementary material zip file.
-
-\begin{table}[t!] 
-  \centering\scriptsize
-  \caption{Complements \cref{tbl:uci} in the main paper: Negative log predictive density (NLPD, lower better) for our \our method compared to a GP subset based method~\cite{immer2021improving} which discards most of the data.
-These UCI data sets (num.\ of points $N$, input dim.\ $D$, num.\ classes $C$) demonstrate that even with a small number $M$ of inducing points our method is able to capture good predictive densities.}
-	\label{tbl:uci-appendix}
-	% Control table spacing
-	\renewcommand{\arraystretch}{1.}
-	\setlength{\tabcolsep}{2pt}
-	\setlength{\tblw}{0.25\textwidth}
-
-	% Custom error formatting
-	\newcommand{\val}[2]{%
-		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
-	}
-
-    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
-	\input{tables/uci_all_nll.tex}
-\end{table}
-
-\begin{table}[t!] 
-  \centering\scriptsize
-  \caption{Complements \cref{tbl:uci-appendix}: We also report the accuracy for each number of inducing points $M$ for both our \our and the GP subset method.
-The differences in the accuracies is not as big as in NLPD which is not surprising as it is generally easier to capture first-order information with sparse methods.
-However, with small $M$ \our still shows clearly better performance.}
-	\label{tbl:uci-appendix-acc}
-	% Control table spacing
-	\renewcommand{\arraystretch}{1.}
-	\setlength{\tabcolsep}{2pt}
-	\setlength{\tblw}{0.25\textwidth}
-
-	% Custom error formatting
-	\newcommand{\val}[2]{%
-		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
-	}
-
-    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
-	\input{tables/uci_all_acc.tex}
-\end{table}
-%\renewcommand{\arraystretch}{1.}
-%	\setlength{\tabcolsep}{1.2pt}
-%	\setlength{\tblw}{0.083\textwidth}
-
-\subsection{Supervised learning on image data sets}
-\label{app:image}
-% Each experiment with the image data sets consisted of the following steps.
-% First, we trained a neural network (MLP for MNIST, CNN for FMNIST) using a prior precision $\delta$.
-% After training, we performed inference by calculating the dual parameters.
-% Finally, we evaluated the predictive performance of \our on the validation set.
-% Similarly to the supervised UCI benchmark tasks, a single image experiment consists of the following steps: first, we train a neural network (a MLP for MNIST, a CNN for FMNIST) in the classification task, using a prior precision $\delta$.
-After training, we prepare the \our method for predictions by computing the dual parameters, and then evaluate the validation set predictive performance of \our.
-While in principle our method's predictions consist of the GP mean and variance, we include results for using the neural network prediction as a mean instead.
-For comparison, we gather the GP subset method results for both the GP and neural network means.
-This experiment set-up is then replicated for a range of prior precision values and learning rates, as we perform a grid search over these hyperparameters by optimizing for the validation set NLPD.
-We run the experiment on $5$ seeds and pick the hyperparameter by the best mean performance over the seeds.
-The results reported in \cref{tbl:imagesuper} used a learning rate of $10^{-4}$, and a prior precision of $\delta = 0.0013$ for FMNIST and $\delta = 0.0001$ for MNIST \todo{double check}.
-
-In \cref{sec:image} in the main paper, we included experiments on image data sets.
-For the image-based classification experiments, we include results using both the GP mean prediction and the NN prediction for both \our and the GP subset.
-For the neural network training, we used the same set-up as in \cite{immer2021improving},
-training the neural network using Adam for $500$ epochs with a batch size of $512$.
-The results reported in \cref{tbl:imagesuper} used a learning rate of $10^{-4}$
-and we ran each experiment for $5$ seeds.
-The MNIST experiments used a prior precision of $\delta=0.0008$
-and the FMNIST experiments used a prior precision of $\delta=0.0013$.
-The experiments with MNIST  used an MLP with two hidden layers of width 128 and Tanh activations.
-In the FMNIST experiments we followed \cite{immer2021improving} and used a CNN
-architecture with two fully connected classification layers and Tanh activations.
-
-In contrast to the GP subset implementation in \citet{immer2021improving},
-we do not perform scaling of $\delta$ after the neural network has been trained.
-Instead, we use the same prior precision that was used during training.
-We performed a grid search over the prior precision for the NN MAP using the validation NLPD.
-We then used this prior precision for the GP predictive (NN) with $M=1024$,
-GP predictive with $M=1024$, \our (NN) and \our.
-We found the MNIST and FMNIST experiments to be numerically stable, even when not performing any clipping in computing the Hessian of the log likelihood, or adding jitter before Cholesky decomposition within the \our dual computation.
-
-\subsection{Updating the network representation in continual learning}
-\label{app:cl-exp}
-
-In \cref{sec:cl-exp} in the main paper, we showed how the regularizer described in \cref{sec:sequential} can be used in continual learning to retain a compact representation of the neural network.
-We conducted our experiments on three common CL data sets \cite{de2021continual, pan2020continual, rudner2022continual}:
-\begin{itemize}
-	\item Split-MNIST (S-MNIST), that consists in five binary classification tasks each on pair on MNIST classes (\ie, \digit{0}~and~\digit{1}, \digit{2}~and~\digit{3}, \dots, \digit{8}~and~\digit{9});
-	\item Split-FashionMNIST (S-FMNIST), composed of five binary tasks as S-MNIST, but using instead Fashion-MNIST;
-	\item Permuted-MNIST (P-MNIST), that consists of ten tasks, where each one is a ten-way classification task on the entire MNIST data set, where the images' pixels are randomly permuted.
-\end{itemize}
-
-Following \cite{pan2020continual, rudner2022continual}, we used a two-layer MLP with 256 hidden units and ReLU activations for S-MNIST and S-FMNIST and a two-layer MLP with 100 hidden units and ReLU activations for P-MNIST, to ensure consistency with the other methods.
-In our experiments we only consider the single-head (SH) setting.
-This means that for S-MNIST and S-FMNIST, we are dealing with a \emph{Class-Incremental Learning} (CIL) scenario, where for each task a pair of dijoint classes are presented to the model.
-The P-MNIST experiments falls instead into the \emph{Domain-Incremental Learning} (DIL) setting, where the model deals with a data-distribution shift, by progressively observing tasks with different permutations of the image pixels that need to be classified into ten different classes.
-
-In our experiments, we compared the performance of the \our-based regularizer against two families of methods: weight-space regularization methods and function-space regularization ones.
-For the weight-space methods, we considered Online-EWC~\citep{schwarz2018progress}, SI~\citep{zenke2017continual}, and VCL~\citep{nguyen2018variational}.
-% In \cref{tbl:cl_table_1}, we considered VCL with random coresets, which uses coreset points t
-For the function-space methods, we considered DER~\citep{buzzega2020dark}, FROMP~\citep{pan2020continual}, and S-FSVI~\citep{rudner2022continual}.
-
-For our method, DER, Online-EWC, and SI, we relied on the Mammoth framework proposed by \citep{buzzega2020dark}.
-On the other hand, we used the available open-source FROMP codebase to conduct the experiments with FROMP, and the S-FSVI codebase to run the experiments on S-FSVI and VCL.
-We selected the hyperparameters to use with all these methods trying to adapt the ones pointed out in the their original papers and the reference implementations.
-For this reason, we relied on SGD for DER, Online-EWC, and SI, which requires higher learning rates, compared to the others methods for which we used Adam \cite{adam}, \ie, our \our regularizer, FROMP, S-FSVI, and VCL.
-
-For the methods relying on a stored subset of training data for each task, we make sure that the number of data points stored are the same for each method.
-For DER, which does not select the rehearsal training samples at task boundaries, we cannot apply directly the definition of points per task ($M$), and thus we set the dimension of the reservoir buffer to be $T \cdot M$, \ie, total number of tasks times the points per task.
-
-The results reported in \cref{tbl:cl_table_1}, are obtained using the following hyperparameters and repeating the runs five times with different seeds.
-The results are in-line with what has been reported in previous work, notably even better for some of the baseline methods.
-Thus, we consider the presented results to give a realistic picture of the relative performance of the different methods, and a demonstrating a clear case for applicability of the \our approach in continual learning.
-
-%% Hyperparms used in the different experiments:
-\paragraph{S-MNIST (40 pts./task):}
-%\begin{itemize}
-	\textbf{Online-EWC}: SGD, learning rate $0.03$, batch size  10, number of epochs 1, $\lambda=90$, $\gamma=1.0$.
-	\textbf{SI}: SGD, learning rate 0.1, batch size 10, number of epochs 1, $c=1.0$, $\xi=0.9$.
-	\textbf{VCL (with coresets)}: Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
-	\textbf{DER}: SGD with learning rate 0.03, batch size 10, buffer batch size 10, number epochs 1, $\alpha=0.3$, reservoir buffer size 200.
-	\textbf{FROMP}: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.
-	\textbf{S-FSVI}: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 10.
-	\textbf{SFR}: Adam, learning rate $3 \cdot 10^{-4}$, batch size 32, $\tau=1$, $\delta=0.0001$, number of epochs 1.
-%\end{itemize}
-
-\paragraph{S-MNIST (200 pts./task):}
-%\begin{itemize}
-	\textbf{Online-EWC}: SGD, learning rate $0.03$, batch size  10, number of epochs 1, $\lambda=90$, $\gamma=1.0$.
-	\textbf{SI}: SGD, learning rate 0.1, batch size 10, number of epochs 1, $c=1.0$, $\xi=0.9$.
-	\textbf{VCL (with coresets)}: Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
-	\textbf{DER}: SGD, learning rate 0.03, batch size 10, buffer batch size 10, number epochs 1, $\alpha$ 0.2, reservoir buffer size 1000.
-	\textbf{FROMP}: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.
-	\textbf{S-FSVI}: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 80.
-	\textbf{SFR}: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, $\tau=0.5$, $\delta=1 \cdot 10^{-5}$, number of epochs 5.
-%\end{itemize}
-
-%% Placeholders for now
-\paragraph{S-FMNIST (200 pts./task):}
-%\begin{itemize}
-	\textbf{Online-EWC}: SGD, learning rate $0.03$, batch size  10, number of epochs 5, $\lambda=90$, $\gamma=1.0$.
-	\textbf{SI}: SGD, learning rate 0.1, batch size 10, number of epochs 5, $c=1.0$, $\xi=0.9$.
-	\textbf{VCL (with coresets)}: Adam, learning rate $1 \cdot 10^{-3}$, batch size 256, number of epochs 100, selection method for coresets random choice.
-	\textbf{DER}: SGD, learning rate 0.03, batch size 10, buffer batch size 10, number epochs 5, $\alpha =  0.2$, reservoir buffer size 200.
-	\textbf{FROMP}: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.
-	\textbf{S-FSVI}: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 60.
-	\textbf{SFR}: Adam, learning rate $3 \cdot 10^{-4}$, batch size 32, $\tau=1.0$, $\delta=0.0001$, number of epochs 5.
-%\end{itemize}
-
-\paragraph{P-MNIST (200 pts./task):}
-%\begin{itemize}
-	\textbf{Online-EWC}: SGD, learning rate $0.1$, batch size 128, number of epochs 10, $\lambda=0.7$, $\gamma=1.0$.
-	\textbf{SI}: SGD, learning rate 0.1, batch size 138, number of epochs 10, $c=0.5$, $\xi=1.0$. 
-	\textbf{VCL (with coresets)}: Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
-	\textbf{DER}:  SGD, learning rate 0.01, batch size 128, buffer batch size 128, number epochs 10, $\alpha=0.3$, reservoir buffer size 2000.
-	\textbf{FROMP}: Adam, learning rate $1 \cdot 10^{-3}$, batch size 128, number of epochs 10, $\tau = 0.5$, lambda descend selection for memorable points.
-	\textbf{S-FSVI}: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 10.
-	\textbf{SFR}: Adam, learning rate $3 \cdot 10^{-4}$, batch size 64, $\tau=1.0$, $\delta=0.0001$. 
-%\end{itemize}
-
-Additionally, for the ablation experiments for \our, we used the same hyperparameters as reported for the full approach.
-
-%\section{Extending the CL regularizer to multi-class settings}
-%%\label{sec:cl_multioutput}
-%\begin{equation}
-%	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{C \times m \times m} \quad \MKzz \in \R^{C \times m \times m} 
-%\end{equation}
-%
-%\begin{equation}
-%	\mathcal{R_\textit{SFR}}(\mathbf{w}) = \sum_{s=1}^{t-1}	\sum_{k \in 	C}\left[\left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s}, k}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s, k}}(\MZ_s) \right) \right]
-%\end{equation}
-
-%\subsection{Reinforcement learning experiment}
-%\label{app:rl-experiment}
-
-%\begin{table}[h]
-%    \centering
-%    \input{./tables/example_table.tex}
-%\end{table}
-
-%\subsection{Biblatex}
-%Rember when using biblatex to use 'parencite' for \citep{kamtheDataEfficient2018} and %when using natbib to use 'citep'.
-
-%\bibliography{biblio.bib}
+\onecolumn
+
 \end{document}
+
+% This document was modified from the file originally made available by
+% Pat Langley and Andrea Danyluk for ICML-2K. This version was created
+% by Iain Murray in 2018, and modified by Alexandre Bouchard in
+% 2019 and 2021 and by Csaba Szepesvari, Gang Niu and Sivan Sabato in 2022.
+% Modified again in 2023 by Sivan Sabato and Jonathan Scarlett.
+% Previous contributors include Dan Roy, Lise Getoor and Tobias
+% Scheffer, which was slightly modified from the 2010 version by
+% Thorsten Joachims & Johannes Fuernkranz, slightly modified from the
+% 2009 version by Kiri Wagstaff and Sam Roweis's 2008 version, which is
+% slightly modified from Prasad Tadepalli's 2007 version which is a
+% lightly changed version of the previous year's version by Andrew
+% Moore, which was in turn edited from those of Kristian Kersting and
+% Codrina Lauth. Alex Smola contributed to the algorithmic style files.

### 2023-05-30 workshop/main.tex
smalls

@@
 % \usepackage[capitalize,noabbrev]{cleveref}
-%\usepackage[capitalize,nameinlink]{cleveref}
+%\usepackage[capitalize,nameinlink]{cleveref}pdf
 %\crefname{section}{Sec.}{Secs.}
@@
 The posterior over the weights ${p(\vw \mid \dataset) \propto p(y \mid f_{\weights}(\vx)) \, p(\weights)}$ is generally not available in closed form.
-Sampling methods that characterize the posterior with a finite set of samples in weight-space---such as the Hamiltonian Monte Carlo (HMC) baseline used in \cref{fig:banana} (right)---are general-purpose, but computationally heavy and impractical for downstream applications.
+Sampling methods that characterize the posterior with a finite set of samples in weight-space---such as the Hamiltonian Monte Carlo (HMC) baseline used in ---are general-purpose, but computationally heavy and impractical for downstream applications.
 

### 2023-05-30 workshop/main.tex
smalls
Edits

--- 2023-05-30 workshop/main.tex
@@
 This offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst retaining predictive performance.
-We demonstrate the proposed approach for quantifying uncertainty in supervised learning and maintaining an expressive functional representation for sequential learning.\looseness-1
+We provide proof-of-concept demonstrations with the proposed approach for quantifying uncertainty in supervised learning on UCI benchamark tasks.
 \end{abstract}
@@
 Secondly, how to update the weights of an already trained model with new batches of data without compromising the performance on past data?
-These questions become central when applied to sequential learning paradigms, such as continual learning (CL, \citep{parisi2019continual, de2021continual}) and reinforcement learning (RL, \cite{sutton2018reinforcement}).
-In CL, access to the previous data is lost, and then the challenge is retaining a compact representation of the problem to alleviate forgetting over the life-long learning horizon~\cite{mccloskey1989catastrophic}.
+These questions become central when applied to sequential learning paradigms, such as continual learning \citep[CL,][]{parisi2019continual, de2021continual} and reinforcement learning  \citep[RL,][]{sutton2018reinforcement}.
+In CL, access to the previous data is lost, and then the challenge is retaining a compact representation of the problem to alleviate forgetting over the life-long learning horizon~\citep{mccloskey1989catastrophic}.
 Similarly, in RL, the model must adapt to environmental observations through exploration, while leveraging prediction uncertainties to assess potential future paths.\looseness-1
@@
 %Current state of affairs 
-Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) apply a Laplace-GGN approximation to convert trained neural networks into Bayesian neural networks, that can provide uncertainty without sacrificing additional resources to training \cite{foong2019between}.
-Furthermore, the resultant weight-space posterior can be converted to the function-space as shown in \cite{khan2019approximate, immer2021improving}.
-The function-space representation allows for a principled mathematical approach for analyzing its behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{foong2019between}.
-These methods rely on the linearization of the neural network and the resultant neural tangent kernel (NTK, \cite{jacot2018neural}).
-The neural network is characterized in function-space by its first two moment functions, a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}).
+Recent techniques  \citep[\eg,][]{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable} apply a Laplace-GGN approximation to convert trained neural networks into Bayesian neural networks, that can provide uncertainty without sacrificing additional resources to training \cite{foong2019between}.
+Furthermore, the resultant weight-space posterior can be converted to the function-space as shown in \citet{khan2019approximate, immer2021improving}.
+The function-space representation allows for a principled mathematical approach for analyzing its behaviour \citep{cho2009kernel,meronen2020stationary}, performing probabilistic inference \citep{khan2019approximate}, and quantifying uncertainty in neural networks \citep{foong2019between}.
+These methods rely on the linearization of the neural network and the resultant neural tangent kernel \citep[NTK,][]{jacot2018neural}.
+The neural network is characterized in function-space by its first two moment functions, a mean function and covariance function (or kernel)---defining a Gaussian process \citep[GP,][]{rasmussen2006gaussian}.
 GPs provide a widely-used probabilistic toolkit with principled uncertainty estimates.
@@
 Given an approximate inference technique, we demonstrate that the neural network emits `dual' parameters which are the building blocks of a GP~\cite{csato2002sparse, adam2021dual, chang2020fast} .
-In contrast to previous work that utilizes subsets of training data \cite{immer2021scalable},
-this parameterization allows capturing the contributions from {\em all} data points into a sparse representation, essential for predictive uncertainty.
+In contrast to previous work that utilizes subsets of training data \citep{immer2021scalable}, this parameterization allows capturing the contributions from {\em all} data points into a sparse representation, essential for predictive uncertainty.
 Crucially, the resulting GP directly predicts in the same space as the original trained neural network, with the benefit of avoiding the complexity introduced by working in weight-space and the notorious cubic complexity of vanilla GPs.
@@
 Through the dual parameter formulation, we establish a connection between the neural network, full GPs, and a sparse approximation similar to sparse variational GPs~\cite{titsias2009variational}.
-We refer to our method as Sparse Function-space Representation (\our)---a sparse GP derived from a trained neural network.
-Moreover, this dual parameterization can be exploited to perform dual conditioning \citep{chang2022fantasizing}, \ie, an effective approach for conditioning on new data without needing to retrain the model (see \cref{fig:teaser}).
+We refer to our method as Sparse Function-space Representation (\our)---a sparse GP derived from a trained neural network; see \cref{fig:teaser} for an example.
+%Moreover, this dual parameterization can be exploited to perform dual conditioning \citep{chang2022fantasizing}, \ie, an effective approach for conditioning on new data without needing to retrain the model (see \cref{fig:teaser}).
 %As \our is in the dual parameters, we can perform dual conditioning recently shown effective in \cite{chang2022fantasizing}, that is, avoid retraining and condition new data into our model (see \cref{fig:teaser}) \todo{Effective compared to what?}.
@@
 %
-We evaluate \our on eight UCI benchmarks~\cite{UCI}, a variety of binary and multi-class classification tasks with different data set sizes.
-We train a two-layer MLP for each of the classification tasks and follow the experiment set up in \cite{immer2021improving}.
+We provide a proof-of-concept example by evaluating \our on eight UCI benchmarks~\cite{UCI}, a variety of binary and multi-class classification tasks with different data set sizes. 
+We train a two-layer MLP for each of the classification tasks and follow the experiment set up in \citet{immer2021improving}.
 %by using the same hyperparameters, performing a hyperparameter search over the prior precision $\delta$,
@@
 predictions %in terms of negative log-predictive density (NLPD).
-(baselines from \cite{immer2021improving}).
+\citep[baselines from][]{immer2021improving}.
 That is, we match predictive performance despite being sparse.
@@
 These results demonstrate \our's sparse representation captures information from the entire data set and as a result provides good uncertainty estimates.
-We provide further details of our experiments in \cref{app:uci}.
+See \citet{immer2021improving} for further details on this particular benchmark setup.
+%We provide further details of our experiments in \cref{app:uci}.
 % as well as further results with varying number of inducing poitns ,64,128,256$
@@
 In this paper, we have introduced \our, a novel approach for representing neural networks in sparse function space, exploiting the dual parameters for an efficient low-rank approximation that accommodates information from the entire data distribution.
-Our method offers a powerful mechanism for capturing predictive uncertainty, updating the model with new data without retraining, and providing a compact representation suitable for continual learning.
-These aspects were demonstrated in a wide range of problems, data sets, and learning contexts.
+Our method offers a powerful mechanism for capturing predictive uncertainty, opens up new possible avenues for updating the model with new data without retraining, and providing a compact representation suitable for continual learning.
+In this workshop paper, we showcased our method's ability to capture uncertainty in UCI benchmark classification tasks (\cref{sec:uci}).
+The appealing properties of \our should make it a good addition to the tool set of modelling in sequential learning settings, such as continual and reinforcement learning.
+%These aspects were demonstrated in a wide range of problems, data sets, and learning contexts.
 We showcased our method's ability to capture uncertainty in UCI classification tasks (\cref{sec:uci}), demonstrated robustness on image data sets (\cref{,sec:image}), established its potential for continual learning (\cref{sec:cl-exp}), and finally, verified its applicability in reinforcement learning scenarios (\cref{sec:rl-exp}).

### 2023-05-30 workshop/main.tex

@@
 %
-\begin{align}
+\begin{equation}
+\begin{split}
   \label{eq:dual_param}
@@
   \beta_i &\coloneqq - \myexpect_{p(\vw \mid \vy)}[\nabla^2_{f f}\log p(y_i \mid f_i) |_{f=f_i}],
-\end{align}
+  \end{split}
+\end{equation}
 %

### 2023-05-30 workshops/icml-duality/main.tex
smalls

--- 2023-05-30 workshop/main.tex
@@
 % Use the following line for the initial blind version submitted for review:
-\usepackage[nohyperref]{icml2023_dp4ml}
+% \usepackage[nohyperref]{icml2023_dp4ml}
 
 % If accepted, instead use the following line for the camera-ready submission:
-%\usepackage[accepted]{icml2023_dp4ml}
+\usepackage[accepted]{icml2023_dp4ml}
 
@@
 
-\input{aidans-utils.tex}
+\input{utils.tex}
 
@@
 \begin{icmlauthorlist}
-\icmlauthor{Firstname1 Lastname1}{equal,yyy}
-\icmlauthor{Firstname2 Lastname2}{equal,yyy,comp}
-\icmlauthor{Firstname3 Lastname3}{comp}
-\icmlauthor{Firstname4 Lastname4}{sch}
-\icmlauthor{Firstname5 Lastname5}{yyy}
-\icmlauthor{Firstname6 Lastname6}{sch,yyy,comp}
-\icmlauthor{Firstname7 Lastname7}{comp}
-%\icmlauthor{}{sch}
-\icmlauthor{Firstname8 Lastname8}{sch}
-\icmlauthor{Firstname8 Lastname8}{yyy,comp}
+\icmlauthor{Aidan Scannell}{equal,aalto,fcai}
+\icmlauthor{Riccardo Mereu}{equal,aalto}
+\icmlauthor{Paul Chang}{aalto}
+\icmlauthor{Ella Tamir}{aalto}
+\icmlauthor{Joni Pajarinen}{aalto}
+\icmlauthor{Arno Solin}{aalto}
 %\icmlauthor{}{sch}
@@
 
-\icmlaffiliation{yyy}{Department of XXX, University of YYY, Location, Country}
-\icmlaffiliation{comp}{Company Name, Location, Country}
-\icmlaffiliation{sch}{School of ZZZ, Institute of WWW, Location, Country}
+\icmlaffiliation{aalto}{Aalto University, Espoo, Finland}
+\icmlaffiliation{fcai}{Finnish Center for Artificial Intelligence}
+% \icmlaffiliation{sch}{School of ZZZ, Institute of WWW, Location, Country}
 
-\icmlcorrespondingauthor{Firstname1 Lastname1}{first1.last1@xxx.edu}
-\icmlcorrespondingauthor{Firstname2 Lastname2}{first2.last2@www.uk}
+\icmlcorrespondingauthor{Aidan Scannell}{aidan.scannell@aalto.fi}
+% \icmlcorrespondingauthor{Firstname2 Lastname2}{first2.last2@www.uk}
 
@@
 \begin{abstract}
-Deep neural networks are known to lack uncertainty estimates, struggle to incorporate new data, and suffer from catastrophic forgetting.
-We present a method that mitigates these issues by converting neural networks from weight-space to a low-rank function-space representation, via the so-called dual parameters.
+Deep neural networks (NNs) are known to lack uncertainty estimates, struggle to incorporate new data, and suffer from catastrophic forgetting.
+We present a method that mitigates these issues by converting NNs from weight-space to a low-rank function-space representation, via the so-called dual parameters.
 In contrast to previous work, our sparse representation captures the joint distribution over the entire data set, rather than only over a subset.
 This offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst retaining predictive performance.
-We provide proof-of-concept demonstrations with the proposed approach for quantifying uncertainty in supervised learning on UCI benchamark tasks.
+We provide proof-of-concept demonstrations with the proposed approach for quantifying uncertainty in supervised learning on UCI benchmark tasks.
 \end{abstract}
@@
 %
-Deep learning \cite{goodfellow2016deep} has become the cornerstone of contemporary artificial intelligence, proving remarkably effective in tackling supervised and unsupervised learning tasks in the {\em large data}, {\em offline}, and {\em gradient-based training} regime.
+Deep learning \citep{goodfellow2016deep} has become the cornerstone of contemporary artificial intelligence, proving remarkably effective in tackling supervised and unsupervised learning tasks in the {\em large data}, {\em offline}, and {\em gradient-based training} regime.
 Despite its success, gradient-based learning techniques exhibit limitations.
@@
 In CL, access to the previous data is lost, and then the challenge is retaining a compact representation of the problem to alleviate forgetting over the life-long learning horizon~\citep{mccloskey1989catastrophic}.
-Similarly, in RL, the model must adapt to environmental observations through exploration, while leveraging prediction uncertainties to assess potential future paths.\looseness-1
+Similarly, in RL, the model must adapt to environmental observations and can leverage predictive uncertainties for exploration.\looseness-1
 
 \begin{figure}[t!]
-  \centering\scriptsize
+  % \centering\scriptsize
+  \centering\Large
   % Figure options
-  \pgfplotsset{axis on top,scale only axis,width=\figurewidth,height=\figureheight, ylabel near ticks,ylabel style={yshift=-2pt},y tick label style={rotate=90},legend style={nodes={scale=1., transform shape}},tick label style={font=\tiny,scale=1}}
+  \pgfplotsset{axis on top,scale only axis,width=\figurewidth,height=\figureheight, ylabel near ticks,ylabel style={yshift=-2pt},y tick label style={rotate=90},legend style={nodes={scale=1., transform shape}},tick label style={font=\Large,scale=1}}
   \pgfplotsset{xlabel={Input, $x$},axis line style={rounded corners=2pt}}
   % Set figure
-  \setlength{\figurewidth}{.19\textwidth}
+  % \setlength{\figurewidth}{.41\textwidth}
+  \setlength{\figurewidth}{.38\textwidth}
   \setlength{\figureheight}{\figurewidth}
   %
-  \def\inducing{\large Sparse inducing points}
+  \def\inducing{\Huge Sparse inducing points}
   %
@@
 %  \end{subfigure}
-  \vspace*{-1em}
+  \vspace*{-0.8em}
   \caption{\textbf{Regression example on an MLP with two hidden layers.} Left:~Predictions from the trained neural network.
-Right:~Our approach summarizes all the training data with the help of a set of inducing points.} %The model captures the predictive mean and uncertainty, and (right) makes it possible to incorporate new data without retraining the model.}
+Right:~Our approach (\our) equips trained NNs with uncertainty estimates.} %The model captures the predictive mean and uncertainty, and (right) makes it possible to incorporate new data without retraining the model.}
+  % \caption{\textbf{Regression example on an MLP with two hidden layers.} Left:~Predictions from the trained neural network.
+Right:~Our approach (\our) summarizes all the training data with the help of a set of inducing points.} %The model captures the predictive mean and uncertainty, and (right) makes it possible to incorporate new data without retraining the model.}
   \label{fig:teaser}
@@
     % Arrows
-    \node[myarrow] (p0-arr) at ($(p0) + (1em,1.5em)$) {};
+    \node[myarrow] (p0-arr) at ($(p0) + (0.2em,1.2em)$) {};
+    % \node[myarrow] (p0-arr) at ($(p0) + (1em,1.5em)$) {};
     %\node[myarrow] (p1-arr) at ($(p1) + (1em,1.5em)$) {};
@@
   \end{tikzpicture}
-  \vspace*{-2em}
+  \vspace*{-1em}
 \end{figure}
@@
 %Current state of affairs
-Recent techniques  \citep[\eg,][]{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable} apply a Laplace-GGN approximation to convert trained neural networks into Bayesian neural networks, that can provide uncertainty without sacrificing additional resources to training \cite{foong2019between}.
+Recent techniques  \citep[\eg,][]{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable} apply a Laplace-GGN approximation to convert trained neural networks into Bayesian neural networks, that can provide uncertainty without sacrificing additional resources to training \citep{foong2019between}.
 Furthermore, the resultant weight-space posterior can be converted to the function-space as shown in \citet{khan2019approximate, immer2021improving}.
@@
 %Need for adaptive learning methods + failures with current methods
-Given an approximate inference technique, we demonstrate that the neural network emits `dual' parameters which are the building blocks of a GP~\cite{csato2002sparse, adam2021dual, chang2020fast} .
+Given an approximate inference technique, we demonstrate that the neural network emits `dual' parameters which are the building blocks of a GP~\citep{csato2002sparse, adam2021dual, chang2020fast} .
 In contrast to previous work that utilizes subsets of training data \citep{immer2021scalable}, this parameterization allows capturing the contributions from {\em all} data points into a sparse representation, essential for predictive uncertainty.
@@
 %, a feature not present in previous approaches, while avoiding the notorious cubic complexity of vanilla GPs.
-Through the dual parameter formulation, we establish a connection between the neural network, full GPs, and a sparse approximation similar to sparse variational GPs~\cite{titsias2009variational}.
+Through the dual parameter formulation, we establish a connection between the neural network, full GPs, and a sparse approximation similar to sparse variational GPs~\citep{titsias2009variational}.
 We refer to our method as Sparse Function-space Representation (\our)---a sparse GP derived from a trained neural network; see \cref{fig:teaser} for an example.
@@
 %
-In supervised learning, given a data set $\dataset = \{(\vx_{i} , \vy_{i})\}_{i=1}^{N}$, with input $\vx_i \in \inputDomain$ and output $\vy_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w}: \inputDomain \to \outputDomain$ (yet, to simplify the notation we restrict presentation to scalar output), are usually trained to minimize the (regularized) empirical risk,\looseness-1
+In supervised learning, given a data set $\dataset = \{(\vx_{i} , \vy_{i})\}_{i=1}^{N}$, with input $\vx_i \in \inputDomain$ and output $\vy_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a NN, $f_\mathbf{w}: \inputDomain \to \outputDomain$ (yet, to simplify the notation we restrict presentation to scalar output), are usually trained to minimize the (regularized) empirical risk,\looseness-1
 %
@@
 The posterior over the weights ${p(\vw \mid \dataset) \propto p(y \mid f_{\weights}(\vx)) \, p(\weights)}$ is generally not available in closed form.
-Sampling methods that characterize the posterior with a finite set of samples in weight-space---such as the Hamiltonian Monte Carlo (HMC) baseline used in ---are general-purpose, but computationally heavy and impractical for downstream applications.
+Sampling methods that characterize the posterior with a finite set of samples in weight-space are general-purpose, but computationally heavy and impractical for downstream applications.
 
@@
 %As such, it is the distribution over function values that we are actually interested in.
-Neural networks are deterministic parametric functions, but even if the training is typically an optimization in the weight-space, in most applications, we are interested in the parametrized function and not in the weights themselves.
+NNs are deterministic parametric functions, but even if the training is typically an optimization in the weight-space, in most applications, we are interested in the parametrized function and not in the weights themselves.
 %While neural networks are deterministic mappings defined by their weights, the ultimate goal of training a neural network is to optimize the function it represents, not the weights themselves.
@@
 \textbf{Linearization gives rise to a Gaussian process}
-Our goal is to capture the distribution over the neural network model functions through their first two moments.
-The first two moments characterize a Gaussian process with a mean function $\mu(\cdot)$ and a covariance function (kernel) $\kappa(\cdot,\cdot)$.
-Recent work \cite{khan2019approximate,maddox2021fast} has shown that linearizing approximations in the weight space lead to function-space equivalent approximations.
-As Gaussian distributions remain tractable under linear transformations, a linear function in terms of parameters can be converted from the weight space to the function space (see Ch.~2.1 in \cite{rasmussen2006gaussian}) as follows:
+Our goal is to capture the distribution over the NN model functions through their first two moments.
+The first two moments characterize a GP with a mean function $\mu(\cdot)$ and a covariance function (kernel) $\kappa(\cdot,\cdot)$.
+Recent work \citep{khan2019approximate,maddox2021fast} has shown that linearizing approximations in the weight space lead to function-space equivalent approximations.
+As Gaussian distributions remain tractable under linear transformations, a linear function in terms of parameters can be converted from the weight space to the function space \citep[see Ch.~2.1 in ][]{rasmussen2006gaussian} as follows:
 %
@@
 % The posterior structure directly relates to the optimization loss around the MAP weights $\vw^*$.
-A common approach is to approximate the correlation structure of a distribution centred at the MAP estimate as done in the Laplace-GGN~\cite{khan2019approximate, daxberger2021laplace, maddox2021fast}.
+A common approach is to approximate the correlation structure of a distribution centred at the MAP estimate as done in the Laplace-GGN~\citep{khan2019approximate, daxberger2021laplace, maddox2021fast}.
 The Laplace-GGN takes the MAP solution and approximates the Hessian of the loss function
 with the GGN.
-Following the work of \citet{khan2019approximate}, we can view this approximation as building an approximate linear model of the neural network as $f_{\weights^*}(\vx) \approx 
+Following the work of \citet{khan2019approximate}, we can view this as a linear approximation of the NN, as $f_{\weights^*}(\vx) \approx
 %g_{\weights}(\vx) =
-\Jac{\weights_*}{\vx} \, \weights$, where $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{1 \times P}$ is the Jacobian at the MAP.
+\Jac{\weights^*}{\vx} \, \weights$, where $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{1 \times P}$ is the Jacobian at the MAP.
 For notational conciseness, we % \cref{eq-laplace-approx-function-space},
@@
 \end{equation}
-where the kernel is the so-called Neural Tangent Kernel (NTK, \cite{jacot2018neural}).
+where the kernel is the so-called Neural Tangent Kernel \citep[NTK,][]{jacot2018neural}.
 We can combine this kernel function with the data set $\dataset$ to construct the posterior.
@@
 \citet{khan2019approximate} took a similar approach, but instead of fitting the GP posterior to the actual $\vy$, they rely on a transformation of $\vy$.
-Similarly, \citet{immer2021improving} obtain the same covariance function but use a different mean because they rely on a first-order approximation of the neural network to form a Bayesian GLM model.
-Both approaches adjust the GP posterior mean function to ensure the predictions are from the neural network $f_{\vw^*}(\vx)$.
+Similarly, \citet{immer2021improving} obtain the same covariance function but use a different mean because they rely on a first-order approximation of the NN to form a Bayesian GLM model.
+Both approaches adjust the GP posterior mean function to ensure the predictions are from the NN $f_{\vw^*}(\vx)$.
 In contrast, our method makes predictions directly from the GP and avoids such adjustments.
@@
 
+% \newpage
 \section{\our: Sparse function-space representation of neural networks}\label{sec:sfr}
 %\paragraph{GP in the dual parameters}
-The seminal work by \citet{csato2002sparse} (parameterization Lemma~1) gives a parameterization for the posterior process that can be found through the Bayesian update using the GP prior and the likelihood function.
+In this section we present our method, named \our, which converts a trained NN into a GP.
+\our is built upon a dual parameterization of the GP posterior, i.e. an alternative parameterization.
+Early work by \citet{csato2002sparse} showed that Expectation Propagation gives rise to a dual paramaterization.
+More recent work by \citet{adam2021dual,chang2023memory} showed a different dual parameterization arising from the evidence lower bound for sparse variational GPs \citep{hensman2013gaussian,titsias2009variational}.
+The dual parameterization from \citet{adam2021dual,chang2023memory}, consists of parameters $\valpha$ and $\vbeta$, which gives rise to the predictive posterior,
+% , we can build on the insight from \citet{csato2002sparse} to obtain a `dual' parameterization, $\valpha$ and $\vbeta$,
+% The seminal work by \citet{csato2002sparse} (parameterization Lemma~1) gives a parameterization for the posterior process that can be found through the Bayesian update using the GP prior and the likelihood function.
 This gives a `dual' parameterization, $\valpha$ and $\vbeta$,
-%
+% %
 \begin{align}  \label{eq:gp_pred}
@@
 %
-where the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{N \times N}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $k_{ii} = \kappa(\vx_i, \vx_i)$.
+where $f_i = f_\vw(\vx_i)$ is the function output at input $\vx_i$,
+the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{N \times N}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $k_{ii} = \kappa(\vx_i, \vx_i)$.
 \cref{eq:gp_pred} states that the first two moments of the resultant posterior process (which may not be a GP), can be parameterized via the dual
@@
   %\quad \text{and} \quad
-  \beta_i &\coloneqq - \myexpect_{p(\vw \mid \vy)}[\nabla^2_{f f}\log p(y_i \mid f_i) |_{f=f_i}],
+  \beta_i &\coloneqq - \myexpect_{p(\vw \mid \vy)}[\nabla^2_{f f}\log p(y_i \mid f_i) |_{f=f_i}].
   \end{split}
@@
 %
-where $f_\vw(\vx_i) = f_i$ is the function output at input $\vx_i$.
 The relationships specified are valid for generic likelihoods, and involve no approximations since the expectation is under the exact posterior, but given that the model can be expressed in a kernel formulation.
@@
 
-Originally \citet{csato2002sparse} iteratively find dual variables using an expectation propagation (EP, \cite{minka2001expectation}) method.
-More recently, \cite{khan2017conjugate,adam2021dual} have shown this relationship for variational Gaussian processes where the above expectation is with respect to the approximate variational posterior.
+% Originally \citet{csato2002sparse} iteratively find dual parameters using an expectation propagation \citep[EP,][]{minka2001expectation} method.
+More recently, \citet{khan2017conjugate,adam2021dual} have shown this relationship for variational Gaussian processes where the above expectation is with respect to the approximate variational posterior.
 Meanwhile in \citet{wilkinson2023bayes}, they show links between linearization methods and how they solve the \cref{eq:dual_param}.
@@
 \paragraph{Dual parameters from NN}
-Given that we use a Laplace approximation of the neural network, we remove the expectation over the posterior (see Ch.~3.4.1 in \cite{rasmussen2006gaussian} for derivation) and we get the the following formulation of the dual variables,
+Given that we use a Laplace approximation of the NN, we remove the expectation over the posterior \citep[see Ch.~3.4.1 in][for derivation]{rasmussen2006gaussian} and our dual parameters are given by,
 %
-\begin{align}
+\begin{equation}
+\begin{split}
   \label{eq:dual_param_laplace}
@@
   \hat{\beta}_i &\coloneqq - \nabla^2_{ff}\log p(y_i \mid f) |_{f=f_i}.
-\end{align}
+  \end{split}
+\end{equation}
 %
-Substituting \cref{eq:dual_param_laplace} into \cref{eq:gp_pred}, we obtain our GP model based on the converged neural network.
+Substituting \cref{eq:dual_param_laplace} into \cref{eq:gp_pred}, we obtain our GP based on the converged NN.
 Again, this is similar to what was derived in \citet{immer2021improving} for the posterior variance function.
-However, they use the $f_{\vw^*}$ for the posterior mean and do not emphasize the significance of the dual variables.
-The problem with \cref{eq:gp_pred} is that to make predictions and compute variances we must incur a cost of $O(N^3)$ which limits the use of the GP on large data sets.
+However, they use the NN's prediction $f_{\vw^*}(\cdot)$ for the posterior mean and do not emphasize the significance of the dual parameters.
+The problem with the predictions in \cref{eq:gp_pred} is that they incur a cost of $O(N^3)$, which limits its application on large data sets.
 
@@
   \centering\scriptsize
-  \caption{Comparisons and ablations on UCI data with negative log predictive density (NLPD\textcolor{gray}{\footnotesize$\pm$std}, lower better).
-Our sparse \our ($M=256$) is on par with full models (left) and outperforms the GP subset approach of \cite{immer2021improving} (right).
-Results for methods marked with * as reported in the original benchmark~\cite{immer2021improving}.
-See \cref{app:uci} for additional tables with comparisons.}
+  \caption{Comparisons on UCI data with negative log predictive density (NLPD\textcolor{gray}{\footnotesize$\pm$std}, lower better).
+\our (with $M=20\% \text{ of } N$) is on par with the Laplace approximation (BNN/GLM) and outperforms the GP subset when the prior precision $(\delta)$ is tuned (right).
+Interestingly, when the prior precision ($\delta$) is not tuned (left), \our outperforms all other methods.
+The GP subset uses the same inducing points as \our.} %Results for methods marked with * as reported in the original benchmark~\citep{immer2021improving}.} %See \cref{app:uci} for additional tables with comparisons.}
 	\label{tbl:uci}
-	\vspace*{-4pt}
+	% \vspace*{-4pt}
 
 	% Control table spacing
-	\renewcommand{\arraystretch}{1.}
-	\setlength{\tabcolsep}{1.2pt}
-	\setlength{\tblw}{0.083\textwidth}
+	% \renewcommand{\arraystretch}{1.}
+	\setlength{\tabcolsep}{1.8pt}
+	% \setlength{\tblw}{0.083\textwidth}
 
 	% Custom error formatting
+	% \newcommand{\val}[2]{%
+	% 	$#1$\textcolor{gray}{\tiny ${\pm}#2$}
+	% }
+
 	\newcommand{\val}[2]{%
-		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
+		$#1$\textcolor{gray}{${\pm}#2$}
 	}
@@
     % THE TABLE NUMBER ARE GENERATED BY A SCRIPT
-	\input{tables/uci.tex}
+	\input{tables/workshop_uci_table.tex}
 \end{table*}
@@
   \centering\scriptsize
-  \setlength{\figurewidth}{.16\textwidth}
+  % \setlength{\figurewidth}{.18\textwidth}
+  \setlength{\figurewidth}{.27\textwidth}
   \setlength{\figureheight}{\figurewidth}
@@
   \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
-  \pgfplotsset{xlabel={$M$},ylabel style={yshift=-12pt}}  
+  \pgfplotsset{xlabel={$M$ as \% of $N$},ylabel style={yshift=-12pt}}
   %
-  \begin{minipage}[t]{.13\textwidth}
+  \begin{minipage}[t]{.155\textwidth}
     \raggedleft
@@
   \hfill
-  \begin{minipage}[t]{.12\textwidth}
-    \raggedleft
-    \input{./fig/breast_cancer.tex}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[t]{.12\textwidth}
-    \raggedleft
-    \input{./fig/ionosphere.tex}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[t]{.12\textwidth}
+  % \begin{minipage}[t]{.12\textwidth}
+  %   \raggedleft
+  %   \input{./fig/breast_cancer.tex}
+  % \end{minipage}
+  % \hfill
+  % \begin{minipage}[t]{.12\textwidth}
+  %   \raggedleft
+  %   \input{./fig/ionosphere.tex}
+  % \end{minipage}
+  % \hfill
+  \begin{minipage}[t]{.155\textwidth}
     \raggedleft
@@
   \hfill
-  \begin{minipage}[t]{.12\textwidth}
+  \begin{minipage}[t]{.155\textwidth}
     \raggedleft
@@
   \newcommand{\myline}[1]{\protect\tikz[baseline=-.5ex,line width=1.6pt]\protect\draw[draw=#1](0,0)--(1.2em,0);}
-  \caption{Comparison of convergence in terms of number of inducing points $M$ in NLPD (mean over 10 seeds) on UCI classification tasks: \our (thick) vs.\ subsets (\cite{immer2021improving}, thin).
-Orange lines (\myline{darkorange25512714}) use the GP mean, whereas blue lines (\myline{steelblue31119180}) the NN MAP estimate as mean.
-Our \our converges fast for all cases.\looseness-1}
+  \caption{Comparison of convergence in terms of number of inducing points $M$ in NLPD (mean\textcolor{gray}{\footnotesize$\pm$std} over 5 seeds) on UCI classification tasks: \our (\myline{steelblue31119180}) vs.
+GP subset (\myline{darkorange25512714}).
+Our \our converges fast for all cases showing clear benefits of its ability to summarize all the data onto a sparse set of inducing points.
+The number of inducing points $M$ are specified as a percent of the number of training data $N$.}
   \label{fig:uci}
@@
 
-\paragraph{Sparsifying the NN GP}
+% \begin{figure*}[t]
+%   \centering\scriptsize
+%   \setlength{\figurewidth}{.18\textwidth}
+%   \setlength{\figureheight}{\figurewidth}
+%   \pgfplotsset{axis on top,scale only axis,y tick label style={rotate=90}, x tick label style={font=\footnotesize},y tick label style={font=\footnotesize},title style={yshift=-4pt,font=\large}, y label style={font=\large},x label style={font=\large},grid=major, width=\figurewidth, height=\figureheight}
+%   \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
+%   \pgfplotsset{xlabel={$M$},ylabel style={yshift=-12pt}}
+%   %
+%   \begin{minipage}[t]{.13\textwidth}
+%     \raggedleft
+%     \pgfplotsset{ylabel=NLPD}
+%     \input{./fig/australian.tex}
+%   \end{minipage}
+%   \hfill
+%   \begin{minipage}[t]{.12\textwidth}
+%     \raggedleft
+%     \input{./fig/breast_cancer.tex}
+%   \end{minipage}
+%   \hfill
+%   \begin{minipage}[t]{.12\textwidth}
+%     \raggedleft
+%     \input{./fig/ionosphere.tex}
+%   \end{minipage}
+%   \hfill
+%   \begin{minipage}[t]{.12\textwidth}
+%     \raggedleft
+%     \input{./fig/glass.tex}
+%   \end{minipage}
+%   \hfill
+%   \begin{minipage}[t]{.12\textwidth}
+%     \raggedleft
+%     \input{./fig/vehicle.tex}
+%   \end{minipage}
+%   \hfill
+%   \begin{minipage}[t]{.12\textwidth}
+%     \raggedleft
+%     \input{./fig/waveform.tex}
+%   \end{minipage}
+%   \hfill
+%   \begin{minipage}[t]{.12\textwidth}
+%     \raggedleft
+%     \input{./fig/digits.tex}
+%   \end{minipage}
+%   \hfill
+%   \begin{minipage}[t]{.12\textwidth}
+%     \raggedleft
+%     \input{./fig/satellite.tex}
+%   \end{minipage}\\[-1em]
+%   %
+%   % Legend
+%   \definecolor{steelblue31119180}{RGB}{31,119,180}
+%   \definecolor{darkorange25512714}{RGB}{255,127,14}
+%   \newcommand{\myline}[1]{\protect\tikz[baseline=-.5ex,line width=1.6pt]\protect\draw[draw=#1](0,0)--(1.2em,0);}
+%   \caption{Comparison of convergence in terms of number of inducing points $M$ in NLPD (mean over 10 seeds) on UCI classification tasks: \our (thick) vs.\ subsets \citep[][thin]{immer2021improving}.
+Orange lines (\myline{darkorange25512714}) use the GP mean, whereas blue lines (\myline{steelblue31119180}) the NN MAP estimate as mean.
+Our \our converges fast for all cases showing clear benefits of its ability to summarize all the data onto a sparse set of inducing points.\looseness-1}
+%   \label{fig:uci}
+%   %\vspace*{-6pt}
+% \end{figure*}
+
+\paragraph{Sparsification via dual parameters}
 \label{sec:sparse-dual-gp}
 %
-Sparse Gaussian processes reduce the computational complexity by representing the GP as a low-rank approximation induced by a sparse set of input points (see \cite{quinonero2005unifying} for an early overview).
-Given that we have computed the dual variables derived from our neural network predictions and a kernel function, we could essentially employ any of these sparsification methods.
-In this work, we opt for the approach suggested by \citet{titsias2009variational} (also used in the DTC approximation, see \cite{quinonero2005unifying}), which defines the marginal predictive distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) \, q(\vu) \, \mathrm{d}\vu$.
+Sparse GPs reduce the computational complexity by representing the GP as a low-rank approximation induced by a sparse set of input points \citep[see][for an early overview]{quinonero2005unifying}.
+Given that we have computed the dual parameters derived from our NN predictions and a kernel function, we could essentially employ any of these sparsification methods.
+In this work, we opt for the approach suggested by \citet{titsias2009variational} \citep[also used in the DTC approximation, see][]{quinonero2005unifying}, which defines the marginal predictive distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) \, q(\vu) \, \mathrm{d}\vu$.
 Given that we have $p(f_i \mid \vu)$ determined by our GP prior, the goal is to find a $q(\vu)$.
 
-As demonstrated in \cite{adam2021dual}, the posterior under this model bears a structure akin to \cref{eq:gp_pred}.
-The authors of that paper exploit the dual variables for approximate inference, but write them using the natural parameterization, primarily because this form is more suitable for optimization through natural gradients.
-In order to link the dual variables defined in \cref{eq:dual_param}, we write them in the sparse GP using the dual variables
+As demonstrated in \citet{adam2021dual}, the posterior under this model bears a structure akin to \cref{eq:gp_pred}.
+The authors of that paper exploit the dual parameters for approximate inference, but write them using the natural parameterization, primarily because this form is more suitable for optimization through natural gradients.
+We project the dual parameters onto the inducing points giving sparse dual parameters,
+% In order to link the dual parameters defined in \cref{eq:dual_param}, we write them in the sparse GP using the dual parameters,
 %
@@
 %
-where the sparse dual variables are now a sum over \emph{all data points}, with $\valpha_{\vu} \in \R^{M}$ and $\MBeta_{\vu} \in \R^{M  \times M}$.
-Using this sparse definition of the dual variables, our sparse GP posterior takes the following form:
+where the sparse dual parameters are now a sum over \emph{all data points}, with $\valpha_{\vu} \in \R^{M}$ and $\MBeta_{\vu} \in \R^{M  \times M}$.
+Using this sparse definition of the dual parameters, our sparse GP posterior takes the following form:
 \begin{align}\label{eq:dual_sparse_post}
@@
 where $\MKzz$ and $\vkzs$ are defined similarly to $\MKxx$ and $\vk_{\vx i}$ but over the inducing points $\{\vz_j\}_{i=1}^M$, $\vz \in \R^{D}$, instead of the full data set $\dataset$.
-The key quantities we need to make predictions from our sparse GP from the converged neural network are $(\hat{\alpha}_i, \hat{\beta}_i)$ (\cref{eq:dual_param_laplace}) and a kernel function $\kappa$ (\cref{eq-laplace-approx-function-space}).
+The key quantities we need to make predictions from our sparse GP from the converged NN are $(\hat{\alpha}_i, \hat{\beta}_i)$ (\cref{eq:dual_param_laplace}) and a kernel function $\kappa$ (\cref{eq-laplace-approx-function-space}).
 Contrasting \cref{eq:dual_sparse_post} and \cref{eq:gp_pred}, we can see that the computational complexity went from $\mathcal{O}(N^3)$ to $\mathcal{O}(M^3)$, with $M \ll N$.
-Crucially, given the structure of our probabilistic model, our sparse dual variables \cref{eq:dual_sparse} are a compact representation of the full model projected using the kernel.
+Crucially, given the structure of our probabilistic model, our sparse dual parameters \cref{eq:dual_sparse} are a compact representation of the full model projected using the kernel.
 
 Unlike our approach, \citet{immer2021improving} employ a subset of the data points to construct a sparse GP, reducing computational complexity.
-However, the method could be considered less principled for building a sparse model, as it ignores contribution from the complete data set.
-It is important to note that the sparsifying process is independent of the approximate inference technique because the dual variables of \cref{eq:dual_param} are computed using \cref{eq-empirical-risk} and a Laplace approximation.
-More complicated inference techniques, such as variational inference, could be used, but given its simplicity, in our experiments we used the Laplace-GGN approximation with the trained neural network.
+However, this method ignores contributions from the complete data set.
+It is important to note that the sparsifying process is independent of the approximate inference technique because the dual parameters of \cref{eq:dual_param} are computed using \cref{eq-empirical-risk} and a Laplace approximation.
+More complicated inference techniques, such as variational inference, could be used, but given its simplicity, in our experiments we used the Laplace-GGN approximation with the trained NN.
 Furthermore, our dual variable view of approximate inference means we do not need to retrain a separate sparse GP.\looseness-2
@@
 %
-We provide a proof-of-concept example by evaluating \our on eight UCI benchmarks~\cite{UCI}, a variety of binary and multi-class classification tasks with different data set sizes. 
-We train a two-layer MLP for each of the classification tasks and follow the experiment set up in \citet{immer2021improving}.
-%by using the same hyperparameters, performing a hyperparameter search over the prior precision $\delta$,
+We provide a proof-of-concept example by evaluating \our on eight UCI benchmarks~\citep{UCI}, a variety of binary and multi-class classification tasks with different data set sizes.
+Following \citet{immer2021improving}, we use a two-layer MLP with width 50 and tanh activation functions and we use half of the test data set as a validation data set.
+We train the NN using Adam \cite{adam} with a learning rate of $10^{-4}$ and a batch size of $128$.
+We run each experiment for $5$ random splits.
+Training was stopped when the validation NLPD stopped decreasing after 1000 steps.
+The checkpoint with the lowest validation NLPD was used as the NN MAP.
+
+We first compare \our to alternative posthoc Bayesian deep learning approaches.
+In particular, we compare to the Laplace approximation when making predictions with 1) the nonlinear NN (BNN) and 2) the generalised linear model (GLM).
+We use the Laplace PyTorch library \citep{daxberger2021laplace} with the full Hessian.%, i.e. we do not resort to the diagonal or KFAC approximations.
+We report results when tuning (\cref{tbl:uci} right) and not tuning (\cref{tbl:uci} left) the prior precision $\delta$ after performing inference.
+When tuning the prior precision $\delta$, \our matches the performance of the Laplace methods (BNN/GLM).
+Interestingly, also \our performs well without tuning the prior precision $\delta$, unlike the Laplace methods (BNN/GLM).
+
+As \our captures information from all of the training data in the inducing points, we compare \our to making GP predictions with a subset of the training data (GP subset).
+To make the comparison fair, we use \our's inducing inputs $\vz$ as the subset.
+\cref{tbl:uci} shows that \our is able to summarize the full data set more effectively than the GP subset method as it maintains predictive performance
+whilst using fewer inducing points.
+This is further illustrated in \cref{fig:uci}, which shows that as the number of inducing points is lowered from $M=100\%$ of $N$ to $M=1\%$ of $N$,
+\our is able to maintain a much better NLPD than the GP subset.
+This demonstrates that \our's sparse representation captures information from the entire data set and as a result can use fewer inducing points than the GP subset.
+
+% \our represents information from all of the training data in the inducing points.
+% As such, we compare \our to using a GP with a subset of the training data (GP subset) with the subset corresponding to the inducing inputs $\vz$ used for \our.
+% \cref{fig:uci} shows that as the number of inducing points is lowered from $M=100\%$ of $N$ to $M=1\%$ of $M$,
+% \our is able to maintain a much better NLPD than the GP subset.
+% This demonstrates that \our's sparse representation captures information from the entire data set and as a result provides good uncertainty estimates.
+% See \citet{immer2021improving} for further details on this particular benchmark setup.
+
+% We use the Laplace PyTorch library \citet{daxberger2021laplace} to perform inference using the full Laplace approximation and report the NLPD when making predictions with
+% the BNN predictive (BNN) and the GLM predictive (GLM).
+% \citep{UCI} compares the NLPD (lower is better) when making predictions with the Laplace
+% by using the same hyperparameters, performing a hyperparameter search over the prior precision $\delta$, and run the experiment over $10$ random splits.
 % We follow \cite{immer2021improving} by using the same hyperparameters, performing a hyperparameter search over the prior precision $\delta$,
-% and run the experiment over $10$ random splits.
+%
 % That is, after training we construct the \our dual and use the resulting model for uncertainty quantification.
 % for the neural network training as in the UCI experiments of
-\cref{tbl:uci} (left) shows that \our with $M=256$ either matches or outperforms the predictive performance of the NN MAP, mean-field VI, Bayesian NN, and GLM
-predictions %in terms of negative log-predictive density (NLPD).
-\citep[baselines from][]{immer2021improving}.
-That is, we match predictive performance despite being sparse.
+% \cref{tbl:uci} shows that \our with $M=20\%N$ always outperforms
+% \citep[baselines from][]{immer2021improving}.
 %
-In \cref{tbl:uci} (right) we compare to the subset GP method from \cite{immer2021improving} whilst using only $M=32$ inducing points.
-It shows that \our is able to summarize the full data set more effectively than the GP subset method as it maintains predictive performance
-whilst using fewer inducing points.
-\cref{fig:uci} further shows that as the number of inducing points is lowered $M=512,\ldots, 16$, \our is able to maintain a much better NLPD than the GP subset.
-These results demonstrate \our's sparse representation captures information from the entire data set and as a result provides good uncertainty estimates.
+% \todo{update text to say what our results show}
+% \cref{tbl:uci} shows that \our with $M=20\%$ of $N$ either matches or outperforms the predictive performance of the Bayesian NN, and GLM
+% predictions %in terms of negative log-predictive density (NLPD).
+% \citep[baselines from][]{immer2021improving}.
+% % That is, we match predictive performance despite being sparse.
+% % In \cref{tbl:uci} (right) we compare to the subset GP method from \citet{immer2021improving} whilst using only $M=32$ inducing points.
+% \cref{tbl:uci} also shows that \our is able to summarize the full data set more effectively than the GP subset method as it maintains predictive performance
+% whilst using fewer inducing points.
+% \cref{fig:uci} further shows that as the number of inducing points is lowered from $M=100\%N$ to $M=1\%M$, \our is able to maintain a much better NLPD than the GP subset.
+% These results demonstrate \our's sparse representation captures information from the entire data set and as a result provides good uncertainty estimates.
 See \citet{immer2021improving} for further details on this particular benchmark setup.
@@
 %
-In this paper, we have introduced \our, a novel approach for representing neural networks in sparse function space, exploiting the dual parameters for an efficient low-rank approximation that accommodates information from the entire data distribution.
-Our method offers a powerful mechanism for capturing predictive uncertainty, opens up new possible avenues for updating the model with new data without retraining, and providing a compact representation suitable for continual learning.
-In this workshop paper, we showcased our method's ability to capture uncertainty in UCI benchmark classification tasks (\cref{sec:uci}).
+In this paper, we introduced \our, a novel approach for representing NNs in sparse function space.
+It leverages a dual parameterization to obtain an efficient low-rank (sparse) approximation that captures information from the entire data set.
+We showcased \our's uncertainty quantification in UCI benchmark classification tasks (\cref{tbl:uci}).
+Interestingly, \our achieves good predictive performance without tuning the prior precision $\delta$ after performing inference.
+This contrasts the Laplace approximation (BNN/GLM) and we believe this stays more true to Bayesian inference.% (as tuning the prior precision is equivalent to altering the prior after calculating the posterior).
+% providing a compact representation suitable for continual learning.
+% In this workshop paper, we showcased our method's ability to capture uncertainty in UCI benchmark classification tasks (\cref{tbl:uci}).
+% The appealing properties of \our should make it a good addition to the tool set of modelling in sequential learning settings, such as continual and reinforcement learning.
+% It offers a powerful mechanism for quantifying uncertainty, opens up new possible avenues for updating the model with new data without retraining, and providing a compact representation suitable for continual learning.
+In this paper, we showcased our method's ability to capture uncertainty in UCI benchmark classification tasks (\cref{tbl:uci}).
 The appealing properties of \our should make it a good addition to the tool set of modelling in sequential learning settings, such as continual and reinforcement learning.
@@
 
+% Looking forwards, we think that \our opens up new possible avenues for updating NNs with new data without retraining,
+% and removing data for machine unlearning, via the dual parameters.
+
 % Discussion points
-In practical terms, our model serves a role similar to a sparse GP.
-However, unlike a conventional GP, it does not provide a straightforward method for specifying or tuning the prior covariance function.
-This limitation can be addressed indirectly: the architecture of the neural network and the choice of activation functions can be used to implicitly specify and tune the prior assumptions, thereby incorporating a broad range of inductive biases into the model.
-It is important to note that the Laplace-GGN approach linearizes the network around the MAP solution $\weights^{*}$, resulting in the function-space prior (and consequently the posterior) being only a locally linear approximation of the neural network model.\looseness-1
+In practical terms, \our serves a role similar to a sparse GP. However, unlike a conventional GP, it does not provide a straightforward method for specifying the prior covariance function.
+This limitation can be addressed indirectly: the architecture of the neural network and the choice of activation functions can be used to implicitly specify the prior assumptions.
+It is important to note that \our linearizes the NN around the MAP weights $\weights^{*}$, resulting in the function-space prior
+(and consequently the posterior) being a locally linear approximation of the NN.\looseness-1
 

### 2023-05-30 workshop/main.tex
Edits

@@
   \newcommand{\myline}[1]{\protect\tikz[baseline=-.5ex,line width=1.6pt]\protect\draw[draw=#1](0,0)--(1.2em,0);}
-  \caption{Comparison of convergence in terms of number of inducing points $M$ in NLPD (mean over 10 seeds) on UCI classification tasks: \our (thick) vs.\ subsets (\cite{immer2021improving}, thin).
+  \caption{Comparison of convergence in terms of number of inducing points $M$ in NLPD (mean over 10 seeds) on UCI classification tasks: \our (thick) vs.\ subsets \citep[][thin]{immer2021improving}.
 Orange lines (\myline{darkorange25512714}) use the GP mean, whereas blue lines (\myline{steelblue31119180}) the NN MAP estimate as mean.

### 2023-05-30 workshop/main.tex
Citations

@@
 %Current state of affairs 
-Recent techniques  \citep[\eg,][]{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable} apply a Laplace-GGN approximation to convert trained neural networks into Bayesian neural networks, that can provide uncertainty without sacrificing additional resources to training \cite{foong2019between}.
+Recent techniques  \citep[\eg,][]{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable} apply a Laplace-GGN approximation to convert trained neural networks into Bayesian neural networks, that can provide uncertainty without sacrificing additional resources to training \citep{foong2019between}.
 Furthermore, the resultant weight-space posterior can be converted to the function-space as shown in \citet{khan2019approximate, immer2021improving}.
@@
 %, a feature not present in previous approaches, while avoiding the notorious cubic complexity of vanilla GPs. 
-Through the dual parameter formulation, we establish a connection between the neural network, full GPs, and a sparse approximation similar to sparse variational GPs~\cite{titsias2009variational}.
+Through the dual parameter formulation, we establish a connection between the neural network, full GPs, and a sparse approximation similar to sparse variational GPs~\citep{titsias2009variational}.
 We refer to our method as Sparse Function-space Representation (\our)---a sparse GP derived from a trained neural network; see \cref{fig:teaser} for an example.
@@
 The first two moments characterize a Gaussian process with a mean function $\mu(\cdot)$ and a covariance function (kernel) $\kappa(\cdot,\cdot)$.
-Recent work \cite{khan2019approximate,maddox2021fast} has shown that linearizing approximations in the weight space lead to function-space equivalent approximations.
-As Gaussian distributions remain tractable under linear transformations, a linear function in terms of parameters can be converted from the weight space to the function space (see Ch.~2.1 in \cite{rasmussen2006gaussian}) as follows:
+Recent work \citep{khan2019approximate,maddox2021fast} has shown that linearizing approximations in the weight space lead to function-space equivalent approximations.
+As Gaussian distributions remain tractable under linear transformations, a linear function in terms of parameters can be converted from the weight space to the function space \citep[see Ch.~2.1 in ][]{rasmussen2006gaussian} as follows:
 %
@@
 % The posterior structure directly relates to the optimization loss around the MAP weights $\vw^*$.
-A common approach is to approximate the correlation structure of a distribution centred at the MAP estimate as done in the Laplace-GGN~\cite{khan2019approximate, daxberger2021laplace, maddox2021fast}.
+A common approach is to approximate the correlation structure of a distribution centred at the MAP estimate as done in the Laplace-GGN~\citep{khan2019approximate, daxberger2021laplace, maddox2021fast}.
 The Laplace-GGN takes the MAP solution and approximates the Hessian of the loss function
@@
 
-Originally \citet{csato2002sparse} iteratively find dual variables using an expectation propagation (EP, \cite{minka2001expectation}) method.
-More recently, \cite{khan2017conjugate,adam2021dual} have shown this relationship for variational Gaussian processes where the above expectation is with respect to the approximate variational posterior.
+Originally \citet{csato2002sparse} iteratively find dual variables using an expectation propagation \citep[EP,][]{minka2001expectation} method.
+More recently, \citet{khan2017conjugate,adam2021dual} have shown this relationship for variational Gaussian processes where the above expectation is with respect to the approximate variational posterior.
 Meanwhile in \citet{wilkinson2023bayes}, they show links between linearization methods and how they solve the \cref{eq:dual_param}.
@@
 \paragraph{Dual parameters from NN}
-Given that we use a Laplace approximation of the neural network, we remove the expectation over the posterior (see Ch.~3.4.1 in \cite{rasmussen2006gaussian} for derivation) and we get the the following formulation of the dual variables,
+Given that we use a Laplace approximation of the neural network, we remove the expectation over the posterior \citep[see Ch.~3.4.1 in][for derivation]{rasmussen2006gaussian} and we get the the following formulation of the dual variables,
 %
@@
   \caption{Comparisons and ablations on UCI data with negative log predictive density (NLPD\textcolor{gray}{\footnotesize$\pm$std}, lower better).
-Our sparse \our ($M=256$) is on par with full models (left) and outperforms the GP subset approach of \cite{immer2021improving} (right).
-Results for methods marked with * as reported in the original benchmark~\cite{immer2021improving}.
-See \cref{app:uci} for additional tables with comparisons.}
+Our sparse \our ($M=256$) is on par with full models (left) and outperforms the GP subset approach of \citet{immer2021improving} (right).
+Results for methods marked with * as reported in the original benchmark~\citep{immer2021improving}.} %See \cref{app:uci} for additional tables with comparisons.}
 	\label{tbl:uci}
@@
   \centering\scriptsize
-  \setlength{\figurewidth}{.16\textwidth}
+  \setlength{\figurewidth}{.18\textwidth}
   \setlength{\figureheight}{\figurewidth}
@@
 %
-Sparse Gaussian processes reduce the computational complexity by representing the GP as a low-rank approximation induced by a sparse set of input points (see \cite{quinonero2005unifying} for an early overview).
+Sparse Gaussian processes reduce the computational complexity by representing the GP as a low-rank approximation induced by a sparse set of input points \citep[see][for an early overview]{quinonero2005unifying}.
 Given that we have computed the dual variables derived from our neural network predictions and a kernel function, we could essentially employ any of these sparsification methods.
-In this work, we opt for the approach suggested by \citet{titsias2009variational} (also used in the DTC approximation, see \cite{quinonero2005unifying}), which defines the marginal predictive distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) \, q(\vu) \, \mathrm{d}\vu$.
+In this work, we opt for the approach suggested by \citet{titsias2009variational} \citep[also used in the DTC approximation, see][]{quinonero2005unifying}, which defines the marginal predictive distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) \, q(\vu) \, \mathrm{d}\vu$.
 Given that we have $p(f_i \mid \vu)$ determined by our GP prior, the goal is to find a $q(\vu)$.
 
-As demonstrated in \cite{adam2021dual}, the posterior under this model bears a structure akin to \cref{eq:gp_pred}.
+As demonstrated in \citet{adam2021dual}, the posterior under this model bears a structure akin to \cref{eq:gp_pred}.
 The authors of that paper exploit the dual variables for approximate inference, but write them using the natural parameterization, primarily because this form is more suitable for optimization through natural gradients.
@@
 %
-We provide a proof-of-concept example by evaluating \our on eight UCI benchmarks~\cite{UCI}, a variety of binary and multi-class classification tasks with different data set sizes. 
+We provide a proof-of-concept example by evaluating \our on eight UCI benchmarks~\citep{UCI}, a variety of binary and multi-class classification tasks with different data set sizes. 
 We train a two-layer MLP for each of the classification tasks and follow the experiment set up in \citet{immer2021improving}.
@@
 That is, we match predictive performance despite being sparse.
-%
-In \cref{tbl:uci} (right) we compare to the subset GP method from \cite{immer2021improving} whilst using only $M=32$ inducing points.
+
+In \cref{tbl:uci} (right) we compare to the subset GP method from \citet{immer2021improving} whilst using only $M=32$ inducing points.
 It shows that \our is able to summarize the full data set more effectively than the GP subset method as it maintains predictive performance

### 2023-05-30 workshop/main.tex
Minor

@@
 Orange lines (\myline{darkorange25512714}) use the GP mean, whereas blue lines (\myline{steelblue31119180}) the NN MAP estimate as mean.
-Our \our converges fast for all cases.\looseness-1}
+Our \our converges fast for all cases showing clear benefits of its ability to summarize all the data onto a sparse set of inducing points.\looseness-1}
   \label{fig:uci}
@@
 We provide a proof-of-concept example by evaluating \our on eight UCI benchmarks~\citep{UCI}, a variety of binary and multi-class classification tasks with different data set sizes. 
-We train a two-layer MLP for each of the classification tasks and follow the experiment set up in \citet{immer2021improving}.
-%by using the same hyperparameters, performing a hyperparameter search over the prior precision $\delta$,
+We train a two-layer MLP for each of the classification tasks and follow the experiment set up in \citet{immer2021improving} by using the same hyperparameters, performing a hyperparameter search over the prior precision $\delta$, and run the experiment over $10$ random splits.
 % We follow \cite{immer2021improving} by using the same hyperparameters, performing a hyperparameter search over the prior precision $\delta$,
-% and run the experiment over $10$ random splits.
+% 
 % That is, after training we construct the \our dual and use the resulting model for uncertainty quantification.

### 2023-05-30 workshop/main.tex
typo
fixed table ref

@@
 This offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst retaining predictive performance.
-We provide proof-of-concept demonstrations with the proposed approach for quantifying uncertainty in supervised learning on UCI benchamark tasks.
+We provide proof-of-concept demonstrations with the proposed approach for quantifying uncertainty in supervised learning on UCI benchmark tasks.
 \end{abstract}
@@
 Our method offers a powerful mechanism for capturing predictive uncertainty, opens up new possible avenues for updating the model with new data without retraining, and providing a compact representation suitable for continual learning.
-In this workshop paper, we showcased our method's ability to capture uncertainty in UCI benchmark classification tasks (\cref{sec:uci}).
+In this workshop paper, we showcased our method's ability to capture uncertainty in UCI benchmark classification tasks (\cref{tbl:uci}).
 The appealing properties of \our should make it a good addition to the tool set of modelling in sequential learning settings, such as continual and reinforcement learning.

### 2023-08-04 paper/main.tex
small fix in CL experiments

@@
 % Methods
-We compare our method against two categories of methods: {\em (i)}~weight-regularization methods: EWC, SI, and VCL (with coresets), and {\em(ii)}~function-based regularization methods: DER, FROMP, and S-FSVI.
+We compare our method against two categories of methods: {\em (i)}~weight-regularization methods: Online-EWC, SI, and VCL (with coresets), and {\em(ii)}~function-based regularization methods: DER, FROMP, and S-FSVI.
 We also introduce an ablation study where we replace our $\bar{\MB}_t^{-1}$ with an identity matrix $\MI_M$, equivalent to having an L2 regularization between current and old function outputs.

### 2023-08-04 paper/main.tex
moved the rl related work section to the appendix

@@
 
-\textbf{Uncertainty quantification in RL}
-A key challenge in RL is balancing the trade-off between exploration and exploitation \cite{sutton2018reinforcement}.
-%That is, should an agent select actions that it knows will lead to high reward %(exploitation), or should it
-%select new ones in hope to discover actions leading to higher reward (exploration).
-One promising direction to balancing this trade-off is to model the uncertainty associated with a learned transition dynamics model and use it to guide exploration.
-Prior work has taken an expectation over the dynamic model's posterior \cite{deisenroth2011pilco,kamtheDataEfficient2018,chuaDeepReinforcementLearning2018},
-sampled from it (akin to Thompson sampling but referred to as posterior sampling in RL) \cite{dearden1999model,osbandMoreEfficientReinforcement2013},
-and used it to implement optimism in the face of uncertainty using upper confidence bounds \cite{curiEfficient2020,jaksch2010near}.
-No single strategy has emerged as a go-to method and we highlight that these strategies are only as good as their uncertainty estimates.
-Previous approaches have used GPs \cite{deisenroth2011pilco,kamtheDataEfficient2018},
-ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
-and variational inference \cite{galImproving2016,houthooftVIME2017}.
-However, each method has its pros and cons.
-In this paper, we present a method which combines some of the pros from NNs with the benefits of GPs.
+%\textbf{Uncertainty quantification in RL}
+%A key challenge in RL is balancing the trade-off between exploration and exploitation \cite{sutton2018reinforcement}.
+%%That is, should an agent select actions that it knows will lead to high reward %(exploitation), or should it
+%%select new ones in hope to discover actions leading to higher reward (exploration).
+%One promising direction to balancing this trade-off is to model the uncertainty associated with a learned transition dynamics model and use it to guide exploration.
+%Prior work has taken an expectation over the dynamic model's posterior \cite{deisenroth2011pilco,kamtheDataEfficient2018,chuaDeepReinforcementLearning2018},
+%sampled from it (akin to Thompson sampling but referred to as posterior sampling in RL) \cite{dearden1999model,osbandMoreEfficientReinforcement2013},
+%and used it to implement optimism in the face of uncertainty using upper confidence bounds \cite{curiEfficient2020,jaksch2010near}.
+%No single strategy has emerged as a go-to method and we highlight that these strategies are only as good as their uncertainty estimates.
+%Previous approaches have used GPs \cite{deisenroth2011pilco,kamtheDataEfficient2018},
+%ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
+%and variational inference \cite{galImproving2016,houthooftVIME2017}.
+%However, each method has its pros and cons.
+%In this paper, we present a method which combines some of the pros from NNs with the benefits of GPs.
 
@@
 
+\subsection{Uncertainty quantification in RL}
+A key challenge in RL is balancing the trade-off between exploration and exploitation \cite{sutton2018reinforcement}.
+%That is, should an agent select actions that it knows will lead to high reward %(exploitation), or should it
+%select new ones in hope to discover actions leading to higher reward (exploration).
+One promising direction to balancing this trade-off is to model the uncertainty associated with a learned transition dynamics model and use it to guide exploration.
+Prior work has taken an expectation over the dynamic model's posterior \cite{deisenroth2011pilco,kamtheDataEfficient2018,chuaDeepReinforcementLearning2018},
+sampled from it (akin to Thompson sampling but referred to as posterior sampling in RL) \cite{dearden1999model,osbandMoreEfficientReinforcement2013},
+and used it to implement optimism in the face of uncertainty using upper confidence bounds \cite{curiEfficient2020,jaksch2010near}.
+No single strategy has emerged as a go-to method and we highlight that these strategies are only as good as their uncertainty estimates.
+Previous approaches have used GPs \cite{deisenroth2011pilco,kamtheDataEfficient2018},
+ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
+and variational inference \cite{galImproving2016,houthooftVIME2017}.
+However, each method has its pros and cons.
+In this paper, we present a method which combines some of the pros from NNs with the benefits of GPs.
+
 % \todo{could try to implement Pathwise conditioning in function-space}

### 2023-08-25 papers/iclr-2024/main.tex
paper now comiples with no errors

--- 2023-08-04 paper/main.tex
@@
-% !TeX spellcheck = en_US
-\documentclass{article}
+\documentclass{article} % For LaTeX2e
 
@@
 
-% NeurIPS packages
-\usepackage[]{neurips_2023}
 \usepackage[utf8]{inputenc} % allow utf-8 input
 \usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-%\usepackage{hyperref}       % hyperlinks
 \usepackage{url}            % simple URL typesetting
@@
 
-% Redefine paragraph to be tighter
-\renewcommand{\paragraph}[1]{{\bf #1}~~}
+\usepackage{iclr2024_conference,times}
+
+% Pass options to natbib
+% \PassOptionsToPackage{numbers, compress}{natbib}
+
+% Optional math commands from https://github.com/goodfeli/dlbook_notation.
+\input{math_commands.tex}
+
+\usepackage{hyperref}
+\usepackage{url}
 
@@
 
-% Appendix/supplement title
-\newcommand{\nipstitle}[1]{{%
-    % rules for title box at top and bottom
-    \def\toptitlebar{\hrule height4pt \vskip .25in \vskip -\parskip} 
-    \def\bottomtitlebar{\vskip .29in \vskip -\parskip \hrule height1pt \vskip .09in} 
-    \phantomsection\hsize\textwidth\linewidth\hsize%
-    \vskip 0.1in%
-    \toptitlebar%
-    \begin{minipage}{\textwidth}%
-        \centering{\LARGE\bf #1\par}%
-    \end{minipage}%
-    \bottomtitlebar%
-    \addcontentsline{toc}{section}{#1}%
-}}
-
-% Bibliography
-%\usepackage[maxcitenames=1, maxbibnames=4, doi=false, isbn=false, eprint=true, backend=bibtex, hyperref=true, url=false, style=authoryear-comp]{biblatex}
-%\addbibresource{zotero-library.bib}
-% \addbibresource{paper/zotero-library.bib}
-
-% Let's use good old bibtex instead
-
 % Figure customization: Tight legend box
@@
 \usepackage{todonotes}
-\usepackage[colorlinks=true,linkcolor=black,allcolors=black,urlcolor=black,citecolor=black]{hyperref}
+% \usepackage[colorlinks=true,linkcolor=black,allcolors=black,urlcolor=black,citecolor=black]{hyperref}
 \usepackage{amsmath}
@@
 \usepackage{wrapfig}
+\usepackage{mathtools}
 
@@
 
-\input{utils.tex}
+% \input{utils.tex}
 
@@
 \newcommand{\vzeros}{\mbf{0}}
-\newcommand{\vtheta}[0]{\mathbold{\theta}}
+% \newcommand{\vtheta}[0]{\mathbold{\theta}}
 \newcommand{\valpha}[0]{\mathbold{\alpha}}
@@
 
-\newcommand{\vm}{\mbf{m}}
-\newcommand{\vz}{\mbf{z}}
-\newcommand{\vf}{\mbf{f}}
-\newcommand{\vu}{\mbf{u}}
-\newcommand{\vx}{\mbf{x}}
-\newcommand{\vy}{\mbf{y}}
-\newcommand{\vw}{\mbf{w}}
-\newcommand{\va}{\mbf{a}}
+% \newcommand{\vm}{\mbf{m}}
+% \newcommand{\vz}{\mbf{z}}
+% \newcommand{\vf}{\mbf{f}}
+% \newcommand{\vu}{\mbf{u}}
+% \newcommand{\vx}{\mbf{x}}
+% \newcommand{\vy}{\mbf{y}}
+% \newcommand{\vw}{\mbf{w}}
+% \newcommand{\va}{\mbf{a}}
 
@@
 \newcommand{\GP}{\mathcal{GP}}
-\newcommand{\KL}[2]{\mathrm{D}_\textrm{KL} \dbar*{#1}{#2}}
+% \newcommand{\KL}[2]{\mathrm{D}_\textrm{KL} \dbar*{#1}{#2}}
 \newcommand{\MKzz}{\mbf{K}_{\mbf{z}\mbf{z}}}
@@
 \newcommand{\vkzs}{\mbf{k}_{\mbf{z}i}}
-\newcommand{\vk}{\mbf{k}}
+% \newcommand{\vk}{\mbf{k}}
 \newcommand{\MLambda}[0]{\mathbold{\Lambda}}
@@
 
-\DeclareMathOperator*{\argmax}{arg\,max}
-\DeclareMathOperator*{\argmin}{arg\,min}
+% \DeclareMathOperator*{\argmax}{arg\,max}
+% \DeclareMathOperator*{\argmin}{arg\,min}
 \newcommand{\Norm}{\mathcal{N}}
@@
 
-%\title{Investigatin Uncertainty Quantification in Model-based Reinforcement Learning}
-% \title{Model-based Reinforcement Learning with Fast Posterior Updates}
-%\title{Sequential Decision-Making under Uncertainty with Big Data}
-% \title{Neural Network to Vatiational Sparse Gaussian Process: For Adaptive Exploration}
-% \title{Neural Network to Sparse Variational Gaussian Process: For Updates in Sequential Decision Making}
-% \title{Adapting Neural Networks to New Data For Updates in Sequential Decision Making via Gaussian Processes}
-% \title{Converting Neural Networks to Gaussian Processes for Sequential Decision-Making Under Uncertainty}
-%\title{Sparse Function Space Representation of Neural Networks for Exploration and Retention}
-%\title{Sparse Function-space Neural Networks}
-\title{Sparse Function-space Representation \\ of Neural Networks}% for Adaptation and Retention}
-\author{%
-  Aidan Scannell\textsuperscript{\star} \\
-  Aalto University \\
-  Finnish Center for Artificial Intelligence \\
-  \texttt{aidan.scannell@aalto.fi}
+% \title{Neural Networks as Sparse Gaussian Processes via Dual Parameters}
+\title{Neural Networks as Sparse Gaussian Processes for Sequential Learning}
+
+% Authors must not appear in the submitted version. They should be hidden
+% as long as the \iclrfinalcopy macro remains commented out below.
+% Non-anonymous submissions will be rejected without review.
+
+\author{Antiquus S.~Hippocampus, Natalia Cerebro \& Amelie P. Amygdale \thanks{ Use footnote for providing further information
+about author (webpage, alternative address)---\emph{not} for acknowledging
+funding agencies.  Funding acknowledgements go at the end of the paper.} \\
+Department of Computer Science\\
+Cranberry-Lemon University\\
+Pittsburgh, PA 15213, USA \\
+\texttt{\{hippo,brain,jen\}@cs.cranberry-lemon.edu} \\
 \And
-  Riccardo Mereu\textsuperscript{\star} \\
-  Aalto University\\
-  \texttt{riccardo.mereu@aalto.fi}
-  \And
-  Paul Chang \\
-  Aalto University\\
-  \texttt{paul.chang@aalto.fi}
-  \And
-  Ella Tamir \\
-  Aalto University\\
-  \texttt{ella.tamir@aalto.fi}
-  \And
-  Joni Pajarinen \\
-  Aalto University\\
-  \texttt{joni.pajarinen@aalto.fi}
-  \And
-  Arno Solin \\
-  Aalto University\\
-  \texttt{arno.solin@aalto.fi}
+Ji Q. Ren \& Yevgeny LeNet \\
+Department of Computational Neuroscience \\
+University of the Witwatersrand \\
+Joburg, South Africa \\
+\texttt{\{robot,net\}@wits.ac.za} \\
+\AND
+Coauthor \\
+Affiliation \\
+Address \\
+\texttt{email}
 }
 
+% The \author macro works with any number of authors. There are two commands
+% used to separate the names and addresses of multiple authors: \And and \AND.
+%
+% Using \And between authors leaves it to \LaTeX{} to determine where to break
+% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
+% puts 3 of 4 authors names on the first line, and the last on the second
+% line, try using \AND instead of \And before the third author name.
+
+\newcommand{\fix}{\marginpar{FIX}}
+\newcommand{\new}{\marginpar{NEW}}
+
+%\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
 \begin{document}
@@
 \begin{abstract}
-% OLDER VERSION
-%Sequential learning paradigms such as Continual Learning (CL) or Reinforcement Learning (RL) pose a challenge for gradient-based deep learning techniques as they struggle to incorporate new data and retain previous knowledge.
-Existing methods for converting neural networks from weight to function space allow a probabilistic treatment of the distribution over the function learned by the neural networks but are computationally expensive.
-We propose a method that converts a neural network to a low-rank functional representation as a sparse Gaussian process.
-With this approach, we can build a compact representation of the function encoded by the neural network that can replace previous data in continual settings and be used for fast adaptation in RL, avoiding full retraining of the model.
-%
-% Rewrite on 2023-05-10
-%Deep neural networks are known to lack uncertainty estimates, struggle to incorporate new data, and fail to retain previous knowledge.
-We present a method that mitigates these issues by transforming a weight-space neural network to a low-rank function-space representation, via the so-called dual parameters.
-In contrast to previous work, we model the joint distribution across the entire data set rather than a subset.
-This offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst retaining predictive performance.
-We demonstrate the proposed approach for quantifying uncertainty in supervised learning and maintaining a compact representation in sequential learning.\looseness-1
-
 Deep neural networks are known to lack uncertainty estimates, struggle to incorporate new data, and suffer from catastrophic forgetting.
@@
 We demonstrate the proposed approach for quantifying uncertainty in supervised learning and maintaining an expressive functional representation for sequential learning.\looseness-1
-
 \end{abstract}
-
-%, maintaining a summary representation in continual learning,
 
@@
 Following the work of \citet{khan2019approximate}, we can view this approximation as building an approximate linear model of the neural network as $f_{\weights^*}(\vx) \approx
-%g_{\weights}(\vx) = 
+g_{\weights}(\vx) =
 \Jac{\weights_*}{\vx} \, \weights$, where $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{1 \times P}$ is the Jacobian at the MAP.
@@
 
-%\section*{Broader Impact}
-
-% \section*{References}
-%\small
-%\printbibliography
-%\normalsize
-% TODO make bibliography small a better way
-
-%References follow the acknowledgments. Use unnumbered first-level heading for
-%the references. Any choice of citation style is acceptable as long as you are
-%consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
-%when listing the references.
-%Note that the Reference section does not count towards the page limit.
-%\medskip
+\bibliography{bibliography}%zotero-library
+% % \bibliography{iclr2024_conference}
+\bibliographystyle{iclr2024_conference}
 
 \clearpage
-
-\phantomsection%
-\addcontentsline{toc}{section}{References}
-\begingroup
-\small
-\bibliographystyle{abbrvnat}
-\bibliography{bibliography}%zotero-library
-\endgroup
-
-\clearpage
-
-\nipstitle{
-    {\Large Supplementary Material:} \\
-    Sparse Function-space Representation \\ of Neural Networks}
-\pagestyle{empty}
-
 \appendix
@@
 
+{\color{red}{
 \subsection{Uncertainty quantification in RL}
@@
 In this paper, we present a method which combines some of the pros from NNs with the benefits of GPs.
-
+}}
 % \todo{could try to implement Pathwise conditioning in function-space}
@@
 
-%\section{Extending the CL regularizer to multi-class settings}
-%%\label{sec:cl_multioutput}
-%\begin{equation}
-%	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{C \times m \times m} \quad \MKzz \in \R^{C \times m \times m} 
-%\end{equation}
-%
-%\begin{equation}
-%	\mathcal{R_\textit{SFR}}(\mathbf{w}) = \sum_{s=1}^{t-1}	\sum_{k \in 	C}\left[\left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s}, k}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s, k}}(\MZ_s) \right) \right]
-%\end{equation}
-
-%\subsection{Reinforcement learning experiment}
-%\label{app:rl-experiment}
-
-%\begin{table}[h]
-%    \centering
-%    \input{./tables/example_table.tex}
-%\end{table}
-
-%\subsection{Biblatex}
-%Rember when using biblatex to use 'parencite' for \citep{kamtheDataEfficient2018} and %when using natbib to use 'citep'.
-
-%\bibliography{biblio.bib}
 \end{document}

### 2023-08-30 workshops/icml-duality/main.tex
added authors and updated to accepted version

--- 2023-05-30 workshop/main.tex
@@
 \paragraph{Dual parameters from NN}
-Given that we use a Laplace approximation of the neural network, we remove the expectation over the posterior (see Ch.~3.4.1 in \cite{rasmussen2006gaussian} for derivation) and we get the the following formulation of the dual variables,
+Given that we use a Laplace approximation of the neural network, we remove the expectation over the posterior \citep[see Ch.~3.4.1 in][for derivation]{rasmussen2006gaussian} and we get the following formulation of the dual variables,
 %
@@
   \caption{Comparisons and ablations on UCI data with negative log predictive density (NLPD\textcolor{gray}{\footnotesize$\pm$std}, lower better).
-Our sparse \our ($M=256$) is on par with full models (left) and outperforms the GP subset approach of \cite{immer2021improving} (right).
-Results for methods marked with * as reported in the original benchmark~\cite{immer2021improving}.
-See \cref{app:uci} for additional tables with comparisons.}
+Our sparse \our ($M=20\% \text{of} N$) is on par with full models (left) and outperforms the GP subset approach of \citet{immer2021improving} (right).
+Results for methods marked with * as reported in the original benchmark~\citep{immer2021improving}.} %See \cref{app:uci} for additional tables with comparisons.}
 	\label{tbl:uci}
-	\vspace*{-4pt}
+	% \vspace*{-4pt}
 
 	% Control table spacing
-	\renewcommand{\arraystretch}{1.}
-	\setlength{\tabcolsep}{1.2pt}
-	\setlength{\tblw}{0.083\textwidth}
+	% \renewcommand{\arraystretch}{1.}
+	% \setlength{\tabcolsep}{1.2pt}
+	% \setlength{\tblw}{0.083\textwidth}
 
 	% Custom error formatting
+	% \newcommand{\val}[2]{%
+	% 	$#1$\textcolor{gray}{\tiny ${\pm}#2$}
+	% }
+
 	\newcommand{\val}[2]{%
-		$#1$\textcolor{gray}{\tiny ${\pm}#2$}
+		$#1$\textcolor{gray}{${\pm}#2$}
 	}
@@
   \centering\scriptsize
-  \setlength{\figurewidth}{.16\textwidth}
+  % \setlength{\figurewidth}{.18\textwidth}
+  \setlength{\figurewidth}{.27\textwidth}
+  \setlength{\figureheight}{\figurewidth}
+  \pgfplotsset{axis on top,scale only axis,y tick label style={rotate=90}, x tick label style={font=\footnotesize},y tick label style={font=\footnotesize},title style={yshift=-4pt,font=\large}, y label style={font=\large},x label style={font=\large},grid=major, width=\figurewidth, height=\figureheight}
+  \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
+  \pgfplotsset{xlabel={$M$ as \% of $N$},ylabel style={yshift=-12pt}}
+  %
+  \begin{minipage}[t]{.155\textwidth}
+    \raggedleft
+    \pgfplotsset{ylabel=NLPD}
+    \input{./fig/australian.tex}
+  \end{minipage}
+  \hfill
+  % \begin{minipage}[t]{.12\textwidth}
+  %   \raggedleft
+  %   \input{./fig/breast_cancer.tex}
+  % \end{minipage}
+  % \hfill
+  % \begin{minipage}[t]{.12\textwidth}
+  %   \raggedleft
+  %   \input{./fig/ionosphere.tex}
+  % \end{minipage}
+  % \hfill
+  \begin{minipage}[t]{.155\textwidth}
+    \raggedleft
+    \input{./fig/glass.tex}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[t]{.155\textwidth}
+    \raggedleft
+    \input{./fig/vehicle.tex}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[t]{.155\textwidth}
+    \raggedleft
+    \input{./fig/waveform.tex}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[t]{.155\textwidth}
+    \raggedleft
+    \input{./fig/digits.tex}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[t]{.155\textwidth}
+    \raggedleft
+    \input{./fig/satellite.tex}
+  \end{minipage}\\[-1em]
+  %
+  % Legend
+  \definecolor{steelblue31119180}{RGB}{31,119,180}
+  \definecolor{darkorange25512714}{RGB}{255,127,14}
+  \newcommand{\myline}[1]{\protect\tikz[baseline=-.5ex,line width=1.6pt]\protect\draw[draw=#1](0,0)--(1.2em,0);}
+  \caption{Comparison of convergence in terms of number of inducing points $M$ in NLPD (mean$\pm$std over 5 seeds) on UCI classification tasks: \our (\myline{steelblue31119180}) vs.
+GP subset (\myline{darkorange25512714}).
+Our \our converges fast for all cases showing clear benefits of its ability to summarize all the data onto a sparse set of inducing points.
+The number of inducing points $M$ are specified as a percent of the number of training data $N$.}
+  \label{fig:uci}
+  %\vspace*{-6pt}
+\end{figure*}
+
+\begin{figure*}[t]
+  \centering\scriptsize
+  \setlength{\figurewidth}{.18\textwidth}
   \setlength{\figureheight}{\figurewidth}
@@
   \newcommand{\myline}[1]{\protect\tikz[baseline=-.5ex,line width=1.6pt]\protect\draw[draw=#1](0,0)--(1.2em,0);}
-  \caption{Comparison of convergence in terms of number of inducing points $M$ in NLPD (mean over 10 seeds) on UCI classification tasks: \our (thick) vs.\ subsets (\cite{immer2021improving}, thin).
+  \caption{Comparison of convergence in terms of number of inducing points $M$ in NLPD (mean over 10 seeds) on UCI classification tasks: \our (thick) vs.\ subsets \citep[][thin]{immer2021improving}.
 Orange lines (\myline{darkorange25512714}) use the GP mean, whereas blue lines (\myline{steelblue31119180}) the NN MAP estimate as mean.
-Our \our converges fast for all cases.\looseness-1}
+Our \our converges fast for all cases showing clear benefits of its ability to summarize all the data onto a sparse set of inducing points.\looseness-1}
   \label{fig:uci}
@@
 %
-We provide a proof-of-concept example by evaluating \our on eight UCI benchmarks~\cite{UCI}, a variety of binary and multi-class classification tasks with different data set sizes. 
-We train a two-layer MLP for each of the classification tasks and follow the experiment set up in \citet{immer2021improving}.
-%by using the same hyperparameters, performing a hyperparameter search over the prior precision $\delta$,
+We provide a proof-of-concept example by evaluating \our on eight UCI benchmarks~\citep{UCI}, a variety of binary and multi-class classification tasks with different data set sizes.
+We train a two-layer MLP for each of the classification tasks and follow the experiment set up in \citet{immer2021improving} by using the same hyperparameters, performing a hyperparameter search over the prior precision $\delta$, and run the experiment over $10$ random splits.
 % We follow \cite{immer2021improving} by using the same hyperparameters, performing a hyperparameter search over the prior precision $\delta$,
-% and run the experiment over $10$ random splits.
+%
 % That is, after training we construct the \our dual and use the resulting model for uncertainty quantification.

### 2023-08-30 experiments/sl/tables/workshop_uci_table.py
updated table to show results with prior prec tuning

@@ -1,18 +1,9 @@
 #!/usr/bin/env python3
-import math
-import os
-
-import hydra
-import matplotlib.pyplot as plt
 import numpy as np
 import pandas as pd
-import scipy as sp
-import seaborn as sns
-import tikzplotlib
-import torch
 import wandb
-from omegaconf import DictConfig, OmegaConf
-from scipy.stats import ttest_rel, ttest_ind
+from omegaconf import OmegaConf
+from scipy.stats import ttest_ind
 
 
 WANDB_RUNS = OmegaConf.create(
@@ -37,7 +28,6 @@ WANDB_RUNS = OmegaConf.create(
             "aalto-ml/sl-train-and-inference/5s6z2mb5",  # 93
             "aalto-ml/sl-train-and-inference/8ro0hyrj",  # 17
             "aalto-ml/sl-train-and-inference/p4l0h40s",  # 69
-            # "aalto-ml/sl-train-and-inference/",  # 117
         ],
         "Glass": [
             "aalto-ml/sl-train-and-inference/vamcf07x",  # 101
@@ -78,37 +68,40 @@ WANDB_RUNS = OmegaConf.create(
         ],
     }
 )
-COLUMNS_TITLES_NUM_INDUCING = [
-    "SFR (GP)",
-    "SFR (NN)",
-    # "GP Subest (GP) BO",
-    # "GP Subest (NN) BO",
-    "GP Subset (GP) BO",
-    "GP Subset (NN) BO",
-]
+# COLUMNS_TITLES_NUM_INDUCING = [
+#     "SFR (GP)",
+#     "SFR (NN)",
+#     # "GP Subest (GP) BO",
+#     # "GP Subest (NN) BO",
+#     "GP Subset (GP) BO",
+#     "GP Subset (NN) BO",
+# ]
 COLUMNS_TITLES = [
     "NN MAP",
+    # "BNN full",
+    # "GLM full",
+    # "GP Subset (GP)",
+    # "SFR (GP)",
     "BNN full GRID",
     "GLM full GRID",
-    # "GP Subest (GP) BO",
     "GP Subset (GP) BO",
-    # "GP Subest (NN)",
     "SFR (GP) BO",
-    # "SFR (NN)",
 ]
 COLUMNS_TITLES_DICT = {
     "NN MAP": "\sc nn map",
+    "BNN full": "\sc bnn",
+    "GLM full": "\sc glm",
[…]

### 2023-08-30 workshops/icml-duality/main.tex
fixed typos and update things

@@
   % Set figure
-  \setlength{\figurewidth}{.19\textwidth}
+  \setlength{\figurewidth}{.4\textwidth}
   \setlength{\figureheight}{\figurewidth}
@@
 with the GGN.
-Following the work of \citet{khan2019approximate}, we can view this approximation as building an approximate linear model of the neural network as $f_{\weights^*}(\vx) \approx
+Following the work of \citet{khan2019approximate}, we can view this as a linear approximation of the neural network, as $f_{\weights^*}(\vx) \approx
 %g_{\weights}(\vx) =
-\Jac{\weights_*}{\vx} \, \weights$, where $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{1 \times P}$ is the Jacobian at the MAP.
+\Jac{\weights^*}{\vx} \, \weights$, where $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{1 \times P}$ is the Jacobian at the MAP.
 For notational conciseness, we % \cref{eq-laplace-approx-function-space},
@@
 %\paragraph{GP in the dual parameters}
+\todo{update this with paul}
 The seminal work by \citet{csato2002sparse} (parameterization Lemma~1) gives a parameterization for the posterior process that can be found through the Bayesian update using the GP prior and the likelihood function.
@@
 %
-where the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{N \times N}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $k_{ii} = \kappa(\vx_i, \vx_i)$.
+where $f_\vw(\vx_i) = f_i$ is the function output at input $\vx_i$
+and the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{N \times N}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $k_{ii} = \kappa(\vx_i, \vx_i)$.
 \cref{eq:gp_pred} states that the first two moments of the resultant posterior process (which may not be a GP), can be parameterized via the dual
@@
   \caption{Comparisons and ablations on UCI data with negative log predictive density (NLPD\textcolor{gray}{\footnotesize$\pm$std}, lower better).
-Our sparse \our ($M=20\% \text{of} N$) is on par with full models (left) and outperforms the GP subset approach of \citet{immer2021improving} (right).
-Results for methods marked with * as reported in the original benchmark~\citep{immer2021improving}.} %See \cref{app:uci} for additional tables with comparisons.}
+Our sparse \our ($M=20\% \text{ of } N$) is on par with full models (left) and outperforms the GP subset approach of \citet{immer2021improving} (right).} %Results for methods marked with * as reported in the original benchmark~\citep{immer2021improving}.} %See \cref{app:uci} for additional tables with comparisons.}
 	\label{tbl:uci}
@@
 
-\begin{figure*}[t]
-  \centering\scriptsize
-  \setlength{\figurewidth}{.18\textwidth}
-  \setlength{\figureheight}{\figurewidth}
-  \pgfplotsset{axis on top,scale only axis,y tick label style={rotate=90}, x tick label style={font=\footnotesize},y tick label style={font=\footnotesize},title style={yshift=-4pt,font=\large}, y label style={font=\large},x label style={font=\large},grid=major, width=\figurewidth, height=\figureheight}
-  \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
-  \pgfplotsset{xlabel={$M$},ylabel style={yshift=-12pt}}
-  %
-  \begin{minipage}[t]{.13\textwidth}
-    \raggedleft
-    \pgfplotsset{ylabel=NLPD}
-    \input{./fig/australian.tex}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[t]{.12\textwidth}
-    \raggedleft
-    \input{./fig/breast_cancer.tex}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[t]{.12\textwidth}
-    \raggedleft
-    \input{./fig/ionosphere.tex}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[t]{.12\textwidth}
-    \raggedleft
-    \input{./fig/glass.tex}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[t]{.12\textwidth}
-    \raggedleft
-    \input{./fig/vehicle.tex}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[t]{.12\textwidth}
-    \raggedleft
-    \input{./fig/waveform.tex}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[t]{.12\textwidth}
-    \raggedleft
-    \input{./fig/digits.tex}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[t]{.12\textwidth}
-    \raggedleft
-    \input{./fig/satellite.tex}
-  \end{minipage}\\[-1em]
-  %
-  % Legend
-  \definecolor{steelblue31119180}{RGB}{31,119,180}
-  \definecolor{darkorange25512714}{RGB}{255,127,14}
-  \newcommand{\myline}[1]{\protect\tikz[baseline=-.5ex,line width=1.6pt]\protect\draw[draw=#1](0,0)--(1.2em,0);}
-  \caption{Comparison of convergence in terms of number of inducing points $M$ in NLPD (mean over 10 seeds) on UCI classification tasks: \our (thick) vs.\ subsets \citep[][thin]{immer2021improving}.
+% \begin{figure*}[t]
+%   \centering\scriptsize
+%   \setlength{\figurewidth}{.18\textwidth}
+%   \setlength{\figureheight}{\figurewidth}
+%   \pgfplotsset{axis on top,scale only axis,y tick label style={rotate=90}, x tick label style={font=\footnotesize},y tick label style={font=\footnotesize},title style={yshift=-4pt,font=\large}, y label style={font=\large},x label style={font=\large},grid=major, width=\figurewidth, height=\figureheight}
+%   \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
+%   \pgfplotsset{xlabel={$M$},ylabel style={yshift=-12pt}}
+%   %
+%   \begin{minipage}[t]{.13\textwidth}
+%     \raggedleft
+%     \pgfplotsset{ylabel=NLPD}
+%     \input{./fig/australian.tex}
+%   \end{minipage}
+%   \hfill
+%   \begin{minipage}[t]{.12\textwidth}
+%     \raggedleft
+%     \input{./fig/breast_cancer.tex}
+%   \end{minipage}
+%   \hfill
+%   \begin{minipage}[t]{.12\textwidth}
+%     \raggedleft
+%     \input{./fig/ionosphere.tex}
+%   \end{minipage}
+%   \hfill
+%   \begin{minipage}[t]{.12\textwidth}
+%     \raggedleft
+%     \input{./fig/glass.tex}
+%   \end{minipage}
+%   \hfill
+%   \begin{minipage}[t]{.12\textwidth}
+%     \raggedleft
+%     \input{./fig/vehicle.tex}
+%   \end{minipage}
+%   \hfill
+%   \begin{minipage}[t]{.12\textwidth}
+%     \raggedleft
+%     \input{./fig/waveform.tex}
+%   \end{minipage}
+%   \hfill
+%   \begin{minipage}[t]{.12\textwidth}
+%     \raggedleft
+%     \input{./fig/digits.tex}
+%   \end{minipage}
+%   \hfill
+%   \begin{minipage}[t]{.12\textwidth}
+%     \raggedleft
+%     \input{./fig/satellite.tex}
+%   \end{minipage}\\[-1em]
+%   %
+%   % Legend
+%   \definecolor{steelblue31119180}{RGB}{31,119,180}
+%   \definecolor{darkorange25512714}{RGB}{255,127,14}
+%   \newcommand{\myline}[1]{\protect\tikz[baseline=-.5ex,line width=1.6pt]\protect\draw[draw=#1](0,0)--(1.2em,0);}
+%   \caption{Comparison of convergence in terms of number of inducing points $M$ in NLPD (mean over 10 seeds) on UCI classification tasks: \our (thick) vs.\ subsets \citep[][thin]{immer2021improving}.
 Orange lines (\myline{darkorange25512714}) use the GP mean, whereas blue lines (\myline{steelblue31119180}) the NN MAP estimate as mean.
 Our \our converges fast for all cases showing clear benefits of its ability to summarize all the data onto a sparse set of inducing points.\looseness-1}
-  \label{fig:uci}
-  %\vspace*{-6pt}
-\end{figure*}
+%   \label{fig:uci}
+%   %\vspace*{-6pt}
+% \end{figure*}
 
@@
 Unlike our approach, \citet{immer2021improving} employ a subset of the data points to construct a sparse GP, reducing computational complexity.
-However, the method could be considered less principled for building a sparse model, as it ignores contribution from the complete data set.
+However, this method ignores contributions from the complete data set.
 It is important to note that the sparsifying process is independent of the approximate inference technique because the dual variables of \cref{eq:dual_param} are computed using \cref{eq-empirical-risk} and a Laplace approximation.
@@
 We provide a proof-of-concept example by evaluating \our on eight UCI benchmarks~\citep{UCI}, a variety of binary and multi-class classification tasks with different data set sizes.
+\todo{update text to say we don't tune prior precision}
 We train a two-layer MLP for each of the classification tasks and follow the experiment set up in \citet{immer2021improving} by using the same hyperparameters, performing a hyperparameter search over the prior precision $\delta$, and run the experiment over $10$ random splits.
@@
 % for the neural network training as in the UCI experiments of
-\cref{tbl:uci} (left) shows that \our with $M=256$ either matches or outperforms the predictive performance of the NN MAP, mean-field VI, Bayesian NN, and GLM
+% \cref{tbl:uci} shows that \our with $M=20\%N$ always outperforms
+% \citep[baselines from][]{immer2021improving}.
+%
+\todo{update text to say what our results show}
+\cref{tbl:uci} shows that \our with $M=20\%$ of $N$ either matches or outperforms the predictive performance of the Bayesian NN, and GLM
 predictions %in terms of negative log-predictive density (NLPD).
 \citep[baselines from][]{immer2021improving}.
-That is, we match predictive performance despite being sparse.
-
-In \cref{tbl:uci} (right) we compare to the subset GP method from \citet{immer2021improving} whilst using only $M=32$ inducing points.
-It shows that \our is able to summarize the full data set more effectively than the GP subset method as it maintains predictive performance
+% That is, we match predictive performance despite being sparse.
+% In \cref{tbl:uci} (right) we compare to the subset GP method from \citet{immer2021improving} whilst using only $M=32$ inducing points.
+\cref{tbl:uci} also shows that \our is able to summarize the full data set more effectively than the GP subset method as it maintains predictive performance
 whilst using fewer inducing points.
-\cref{fig:uci} further shows that as the number of inducing points is lowered $M=512,\ldots, 16$, \our is able to maintain a much better NLPD than the GP subset.
+\cref{fig:uci} further shows that as the number of inducing points is lowered from $M=100\%N$ to $M=1\%M$, \our is able to maintain a much better NLPD than the GP subset.
 These results demonstrate \our's sparse representation captures information from the entire data set and as a result provides good uncertainty estimates.

### 2023-08-30 workshops/icml-duality/main.tex
update regression fig
increase font size
placed arrow better

@@
 \begin{figure}[t!]
-  \centering\scriptsize
+  % \centering\scriptsize
+  \centering\Large
   % Figure options
-  \pgfplotsset{axis on top,scale only axis,width=\figurewidth,height=\figureheight, ylabel near ticks,ylabel style={yshift=-2pt},y tick label style={rotate=90},legend style={nodes={scale=1., transform shape}},tick label style={font=\tiny,scale=1}}
+  \pgfplotsset{axis on top,scale only axis,width=\figurewidth,height=\figureheight, ylabel near ticks,ylabel style={yshift=-2pt},y tick label style={rotate=90},legend style={nodes={scale=1., transform shape}},tick label style={font=\Large,scale=1}}
   \pgfplotsset{xlabel={Input, $x$},axis line style={rounded corners=2pt}}
@@
   %
-  \def\inducing{\large Sparse inducing points}
+  \def\inducing{\Huge Sparse inducing points}
   %
@@
 %  \end{subfigure}
-  \vspace*{-1em}
+  % \vspace*{-1em}
   \caption{\textbf{Regression example on an MLP with two hidden layers.} Left:~Predictions from the trained neural network.

### 2023-08-30 workshops/icml-duality/main.tex
put section 3 on new page and made tab caption better

@@
 
+\newpage
 \section{\our: Sparse function-space representation of neural networks}\label{sec:sfr}
@@
   \caption{Comparisons and ablations on UCI data with negative log predictive density (NLPD\textcolor{gray}{\footnotesize$\pm$std}, lower better).
-Our sparse \our ($M=20\% \text{ of } N$) is on par with full models (left) and outperforms the GP subset approach of \citet{immer2021improving} (right).} %Results for methods marked with * as reported in the original benchmark~\citep{immer2021improving}.} %See \cref{app:uci} for additional tables with comparisons.}
+Our sparse \our (with $M=20\% \text{ of } N$) is on par with the Laplace methods (BNN/GLM) and outperforms the GP subset method.} %Results for methods marked with * as reported in the original benchmark~\citep{immer2021improving}.} %See \cref{app:uci} for additional tables with comparisons.}
 	\label{tbl:uci}

### 2023-08-30 workshops/icml-duality/main.tex
updated caption tab

@@
   \caption{Comparisons and ablations on UCI data with negative log predictive density (NLPD\textcolor{gray}{\footnotesize$\pm$std}, lower better).
-Our sparse \our (with $M=20\% \text{ of } N$) is on par with the Laplace methods (BNN/GLM) and outperforms the GP subset method.} %Results for methods marked with * as reported in the original benchmark~\citep{immer2021improving}.} %See \cref{app:uci} for additional tables with comparisons.}
+Our sparse \our (with $M=20\% \text{ of } N$) is on par with the Laplace methods (BNN/GLM) and outperforms the GP subset method when the prior precision $(\delta)$ is tuned (right).
+Interestingly, when no prior precision ($\delta$) tuning is used (left), \our outperforms all other methods.} %Results for methods marked with * as reported in the original benchmark~\citep{immer2021improving}.} %See \cref{app:uci} for additional tables with comparisons.}
 	\label{tbl:uci}
@@
 	% \renewcommand{\arraystretch}{1.}
-	% \setlength{\tabcolsep}{1.2pt}
+	\setlength{\tabcolsep}{1.6pt}
 	% \setlength{\tblw}{0.083\textwidth}

### 2023-08-30 experiments/sl/tables/workshop_uci_table.py
commit woth table showing with/without delta tuning

@@ -78,15 +78,31 @@ WANDB_RUNS = OmegaConf.create(
 # ]
 COLUMNS_TITLES = [
     "NN MAP",
-    # "BNN full",
-    # "GLM full",
-    # "GP Subset (GP)",
-    # "SFR (GP)",
+    "BNN full",
+    "GLM full",
+    "GP Subset (GP)",
+    "SFR (GP)",
     "BNN full GRID",
     "GLM full GRID",
     "GP Subset (GP) BO",
     "SFR (GP) BO",
 ]
+COLUMNS_TITLES_MULTI = [
+    ("N", ""),
+    ("D", ""),
+    ("C", ""),
+    # "\sc nn map",
+    ("No $\delta$ tuning", "\sc nn map"),
+    ("No $\delta$ tuning", "\sc bnn"),
+    ("No $\delta$ tuning", "\sc glm"),
+    ("No $\delta$ tuning", "{\sc gp} subset"),
+    ("No $\delta$ tuning", "\our"),
+    ("$\delta$ tuning", "\sc bnn"),
+    ("$\delta$ tuning", "\sc glm"),
+    ("$\delta$ tuning", "{\sc gp} subset"),
+    ("$\delta$ tuning", "\our"),
+]
+
 COLUMNS_TITLES_DICT = {
     "NN MAP": "\sc nn map",
     "BNN full": "\sc bnn",
@@ -96,9 +112,9 @@ COLUMNS_TITLES_DICT = {
     # "GP Subest (GP)": "{\sc gp} subset (\sc gp)",
     # "GP Subest (NN)": "{\sc gp} subset (\sc nn)",
     "GP Subset (GP)": "{\sc gp} subset",
-    "GP Subset (NN)": "{\sc gp} subset (\sc nn)",
+    # "GP Subset (NN)": "{\sc gp} subset (\sc nn)",
     "SFR (GP)": "\our",
-    "SFR (NN)": "\our (\sc nn)",
+    # "SFR (NN)": "\our (\sc nn)",
     # "GP Subest (GP) BO": "{\sc gp} subset (\sc gp)",
     "GP Subset (GP) BO": "{\sc gp} subset",
     "SFR (GP) BO": "\our",
@@ -109,7 +125,17 @@ COLUMNS_TITLES_DICT = {
 #     "breast_cancer": "Cancer",
 # }
 
-DATASETS_NAMES = {
+# DATASETS_NAMES = {
+#     "australian": "Australian",
+#     "breast_cancer": "Breast cancer",
[…]

### 2023-08-30 experiments/sl/tables/workshop_uci_table.py
updated

@@ -91,8 +91,8 @@ COLUMNS_TITLES_MULTI = [
     ("N", ""),
     ("D", ""),
     ("C", ""),
-    # "\sc nn map",
-    ("No $\delta$ tuning", "\sc nn map"),
+    ("\sc nn map", ""),
+    # ("No $\delta$ tuning", "\sc nn map"),
     ("No $\delta$ tuning", "\sc bnn"),
     ("No $\delta$ tuning", "\sc glm"),
     ("No $\delta$ tuning", "{\sc gp} subset"),
@@ -336,7 +336,7 @@ def make_uci_table():
     # Print the LaTeX table
     print(
         uci_table.to_latex(
-            column_format="lccc|ccccc|cccc|", escape=False, multicolumn_format="c|"
+            column_format="lccc|c|cccc|cccc|", escape=False, multicolumn_format="c|"
         )
     )
 
@@ -345,7 +345,7 @@ def make_uci_table():
     ) as file:
         file.write(
             uci_table.to_latex(
-                column_format="lccc|ccccc|cccc|", escape=False, multicolumn_format="c|"
+                column_format="lccc|c|cccc|cccc|", escape=False, multicolumn_format="c|"
             )
         )
 

### 2023-08-31 experiments/sl/tables/workshop_uci_table.py
made N/D/C mathod mode

@@ -88,9 +88,9 @@ COLUMNS_TITLES = [
     "SFR (GP) BO",
 ]
 COLUMNS_TITLES_MULTI = [
-    ("N", ""),
-    ("D", ""),
-    ("C", ""),
+    ("$N$", ""),
+    ("$D$", ""),
+    ("$C$", ""),
     ("\sc nn map", ""),
     # ("No $\delta$ tuning", "\sc nn map"),
     ("No $\delta$ tuning", "\sc bnn"),
@@ -136,14 +136,14 @@ COLUMNS_TITLES_DICT = {
 #     "satellite": "Satellite",
 # }
 DATASETS = {
-    "australian": "Australian",
-    "breast_cancer": "Breast cancer",
-    "ionosphere": "Ionosphere",
-    "glass": "Glass",
-    "vehicle": "Vehicle",
-    "waveform": "Waveform",
-    "digits": "Digits",
-    "satellite": "Satellite",
+    "australian": "\sc Australian",
+    "breast_cancer": "\sc Breast cancer",
+    "ionosphere": "\sc Ionosphere",
+    "glass": "\sc Glass",
+    "vehicle": "\sc Vehicle",
+    "waveform": "\sc Waveform",
+    "digits": "\sc Digits",
+    "satellite": "\sc Satellite",
 }
 NUM_DATAS = {
     "australian": 690,
@@ -311,9 +311,9 @@ def make_uci_table():
     print("uci_table")
     print(uci_table)
     print(NUM_DATAS.values())
-    uci_table["N"] = pd.Series(NUM_DATAS.values(), index=uci_table.index)
-    uci_table["D"] = pd.Series(INPUT_DIMS.values(), index=uci_table.index)
-    uci_table["C"] = pd.Series(NUM_CLASSES.values(), index=uci_table.index)
+    uci_table["$N$"] = pd.Series(NUM_DATAS.values(), index=uci_table.index)
+    uci_table["$D$"] = pd.Series(INPUT_DIMS.values(), index=uci_table.index)
+    uci_table["$C$"] = pd.Series(NUM_CLASSES.values(), index=uci_table.index)
 
     # uci_table.index.names = ["Dataset", "N", "D", "C"]
     uci_table.index.names = ["Dataset"]
@@ -322,9 +322,9 @@ def make_uci_table():
     uci_table.rename(index=DATASETS, inplace=True)
     # uci_table = uci_table.reset_index().to_string(index=False)
     uci_table.fillna("-", inplace=True)
[…]

### 2023-08-31 workshops/icml-duality/main.tex
updated

--- 2023-08-30 workshops/icml-duality/main.tex
@@
 \begin{abstract}
-Deep neural networks are known to lack uncertainty estimates, struggle to incorporate new data, and suffer from catastrophic forgetting.
-We present a method that mitigates these issues by converting neural networks from weight-space to a low-rank function-space representation, via the so-called dual parameters.
+Deep neural networks (NNs) are known to lack uncertainty estimates, struggle to incorporate new data, and suffer from catastrophic forgetting.
+We present a method that mitigates these issues by converting NNs from weight-space to a low-rank function-space representation, via the so-called dual parameters.
 In contrast to previous work, our sparse representation captures the joint distribution over the entire data set, rather than only over a subset.
@@
 In CL, access to the previous data is lost, and then the challenge is retaining a compact representation of the problem to alleviate forgetting over the life-long learning horizon~\citep{mccloskey1989catastrophic}.
-Similarly, in RL, the model must adapt to environmental observations through exploration, while leveraging prediction uncertainties to assess potential future paths.\looseness-1
+Similarly, in RL, the model must adapt to environmental observations and can leverage predictive uncertainties for exploration.\looseness-1
 
@@
   % Set figure
-  \setlength{\figurewidth}{.4\textwidth}
+  \setlength{\figurewidth}{.41\textwidth}
   \setlength{\figureheight}{\figurewidth}
@@
 %  \end{subfigure}
-  % \vspace*{-1em}
+  \vspace*{-0.8em}
   \caption{\textbf{Regression example on an MLP with two hidden layers.} Left:~Predictions from the trained neural network.
-Right:~Our approach summarizes all the training data with the help of a set of inducing points.} %The model captures the predictive mean and uncertainty, and (right) makes it possible to incorporate new data without retraining the model.}
+Right:~Our approach (\our) equips trained NNs with uncertainty estimates.} %The model captures the predictive mean and uncertainty, and (right) makes it possible to incorporate new data without retraining the model.}
+  % \caption{\textbf{Regression example on an MLP with two hidden layers.} Left:~Predictions from the trained neural network.
+Right:~Our approach (\our) summarizes all the training data with the help of a set of inducing points.} %The model captures the predictive mean and uncertainty, and (right) makes it possible to incorporate new data without retraining the model.}
   \label{fig:teaser}
@@
 \textbf{Linearization gives rise to a Gaussian process}
-Our goal is to capture the distribution over the neural network model functions through their first two moments.
-The first two moments characterize a Gaussian process with a mean function $\mu(\cdot)$ and a covariance function (kernel) $\kappa(\cdot,\cdot)$.
+Our goal is to capture the distribution over the NN model functions through their first two moments.
+The first two moments characterize a GP with a mean function $\mu(\cdot)$ and a covariance function (kernel) $\kappa(\cdot,\cdot)$.
 Recent work \citep{khan2019approximate,maddox2021fast} has shown that linearizing approximations in the weight space lead to function-space equivalent approximations.
@@
 with the GGN.
-Following the work of \citet{khan2019approximate}, we can view this as a linear approximation of the neural network, as $f_{\weights^*}(\vx) \approx
+Following the work of \citet{khan2019approximate}, we can view this as a linear approximation of the NN, as $f_{\weights^*}(\vx) \approx
 %g_{\weights}(\vx) =
@@
 
-\newpage
+% \newpage
 \section{\our: Sparse function-space representation of neural networks}\label{sec:sfr}
 %\paragraph{GP in the dual parameters}
-\todo{update this with paul}
-The seminal work by \citet{csato2002sparse} (parameterization Lemma~1) gives a parameterization for the posterior process that can be found through the Bayesian update using the GP prior and the likelihood function.
+In this section we present our method, named \our, which converts a trained NN into a GP.
+\our is built upon a dual parameterization of the GP posterior, i.e. an alternative parameterization.
+Early work by \citet{csato2002sparse} showed that Expectation Propagation gives rise to a dual paramaterization.
+More recent work by \citet{adam2021dual,chang2023memory} showed a different dual parameterization arising from the evidence lower bound for sparse variational GPs \citep{hensman2013gaussian,titsias2009variational}.
+The dual parameterization from \citet{adam2021dual,chang2023memory}, consists of parameters $\valpha$ and $\vbeta$, which gives rise to the predictive posterior,
+% , we can build on the insight from \citet{csato2002sparse} to obtain a `dual' parameterization, $\valpha$ and $\vbeta$,
+% The seminal work by \citet{csato2002sparse} (parameterization Lemma~1) gives a parameterization for the posterior process that can be found through the Bayesian update using the GP prior and the likelihood function.
 This gives a `dual' parameterization, $\valpha$ and $\vbeta$,
-%
+% %
 \begin{align}  \label{eq:gp_pred}
@@
 %
-where $f_\vw(\vx_i) = f_i$ is the function output at input $\vx_i$
-and the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{N \times N}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $k_{ii} = \kappa(\vx_i, \vx_i)$.
+where $f_i = f_\vw(\vx_i)$ is the function output at input $\vx_i$,
+the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{N \times N}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $k_{ii} = \kappa(\vx_i, \vx_i)$.
 \cref{eq:gp_pred} states that the first two moments of the resultant posterior process (which may not be a GP), can be parameterized via the dual
@@
 
-Originally \citet{csato2002sparse} iteratively find dual variables using an expectation propagation \citep[EP,][]{minka2001expectation} method.
+% Originally \citet{csato2002sparse} iteratively find dual parameters using an expectation propagation \citep[EP,][]{minka2001expectation} method.
 More recently, \citet{khan2017conjugate,adam2021dual} have shown this relationship for variational Gaussian processes where the above expectation is with respect to the approximate variational posterior.
@@
 \paragraph{Dual parameters from NN}
-Given that we use a Laplace approximation of the neural network, we remove the expectation over the posterior \citep[see Ch.~3.4.1 in][for derivation]{rasmussen2006gaussian} and we get the following formulation of the dual variables,
+Given that we use a Laplace approximation of the NN, we remove the expectation over the posterior \citep[see Ch.~3.4.1 in][for derivation]{rasmussen2006gaussian} and our dual parameters are given by,
 %
@@
 %
-Substituting \cref{eq:dual_param_laplace} into \cref{eq:gp_pred}, we obtain our GP model based on the converged neural network.
+Substituting \cref{eq:dual_param_laplace} into \cref{eq:gp_pred}, we obtain our GP based on the converged NN.
 Again, this is similar to what was derived in \citet{immer2021improving} for the posterior variance function.
-However, they use the $f_{\vw^*}$ for the posterior mean and do not emphasize the significance of the dual variables.
-The problem with \cref{eq:gp_pred} is that to make predictions and compute variances we must incur a cost of $O(N^3)$ which limits the use of the GP on large data sets.
+However, they use the NN's prediction $f_{\vw^*}(\cdot)$ for the posterior mean and do not emphasize the significance of the dual parameters.
+The problem with the predictions in \cref{eq:gp_pred} is that they incur a cost of $O(N^3)$, which limits its application on large data sets.
 
@@
   \centering\scriptsize
-  \caption{Comparisons and ablations on UCI data with negative log predictive density (NLPD\textcolor{gray}{\footnotesize$\pm$std}, lower better).
-Our sparse \our (with $M=20\% \text{ of } N$) is on par with the Laplace methods (BNN/GLM) and outperforms the GP subset method.} %Results for methods marked with * as reported in the original benchmark~\citep{immer2021improving}.} %See \cref{app:uci} for additional tables with comparisons.}
+  \caption{Comparisons on UCI data with negative log predictive density (NLPD\textcolor{gray}{\footnotesize$\pm$std}, lower better).
+\our (with $M=20\% \text{ of } N$) is on par with the Laplace approximation (BNN/GLM) and outperforms the GP subset when the prior precision $(\delta)$ is tuned (right).
+Interestingly, when the prior precision ($\delta$) is not tuned (left), \our outperforms all other methods.
+The GP subset uses the same inducing points as \our.} %Results for methods marked with * as reported in the original benchmark~\citep{immer2021improving}.} %See \cref{app:uci} for additional tables with comparisons.}
 	\label{tbl:uci}
@@
 	% \renewcommand{\arraystretch}{1.}
-	% \setlength{\tabcolsep}{1.2pt}
+	\setlength{\tabcolsep}{1.8pt}
 	% \setlength{\tblw}{0.083\textwidth}
@@
 
-\paragraph{Sparsifying the NN GP}
+\paragraph{Sparsification via dual parameters}
 \label{sec:sparse-dual-gp}
 %
-Sparse Gaussian processes reduce the computational complexity by representing the GP as a low-rank approximation induced by a sparse set of input points \citep[see][for an early overview]{quinonero2005unifying}.
-Given that we have computed the dual variables derived from our neural network predictions and a kernel function, we could essentially employ any of these sparsification methods.
+Sparse GPs reduce the computational complexity by representing the GP as a low-rank approximation induced by a sparse set of input points \citep[see][for an early overview]{quinonero2005unifying}.
+Given that we have computed the dual parameters derived from our NN predictions and a kernel function, we could essentially employ any of these sparsification methods.
 In this work, we opt for the approach suggested by \citet{titsias2009variational} \citep[also used in the DTC approximation, see][]{quinonero2005unifying}, which defines the marginal predictive distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) \, q(\vu) \, \mathrm{d}\vu$.
@@
 As demonstrated in \citet{adam2021dual}, the posterior under this model bears a structure akin to \cref{eq:gp_pred}.
-The authors of that paper exploit the dual variables for approximate inference, but write them using the natural parameterization, primarily because this form is more suitable for optimization through natural gradients.
-In order to link the dual variables defined in \cref{eq:dual_param}, we write them in the sparse GP using the dual variables
+The authors of that paper exploit the dual parameters for approximate inference, but write them using the natural parameterization, primarily because this form is more suitable for optimization through natural gradients.
+We project the dual parameters onto the inducing points sparse GP using the dual parameters,
+% In order to link the dual parameters defined in \cref{eq:dual_param}, we write them in the sparse GP using the dual parameters,
 %
@@
 where $\MKzz$ and $\vkzs$ are defined similarly to $\MKxx$ and $\vk_{\vx i}$ but over the inducing points $\{\vz_j\}_{i=1}^M$, $\vz \in \R^{D}$, instead of the full data set $\dataset$.
-The key quantities we need to make predictions from our sparse GP from the converged neural network are $(\hat{\alpha}_i, \hat{\beta}_i)$ (\cref{eq:dual_param_laplace}) and a kernel function $\kappa$ (\cref{eq-laplace-approx-function-space}).
+The key quantities we need to make predictions from our sparse GP from the converged NN are $(\hat{\alpha}_i, \hat{\beta}_i)$ (\cref{eq:dual_param_laplace}) and a kernel function $\kappa$ (\cref{eq-laplace-approx-function-space}).
 Contrasting \cref{eq:dual_sparse_post} and \cref{eq:gp_pred}, we can see that the computational complexity went from $\mathcal{O}(N^3)$ to $\mathcal{O}(M^3)$, with $M \ll N$.
-Crucially, given the structure of our probabilistic model, our sparse dual variables \cref{eq:dual_sparse} are a compact representation of the full model projected using the kernel.
+Crucially, given the structure of our probabilistic model, our sparse dual parameters \cref{eq:dual_sparse} are a compact representation of the full model projected using the kernel.
 
@@
 However, this method ignores contributions from the complete data set.
-It is important to note that the sparsifying process is independent of the approximate inference technique because the dual variables of \cref{eq:dual_param} are computed using \cref{eq-empirical-risk} and a Laplace approximation.
-More complicated inference techniques, such as variational inference, could be used, but given its simplicity, in our experiments we used the Laplace-GGN approximation with the trained neural network.
+It is important to note that the sparsifying process is independent of the approximate inference technique because the dual parameters of \cref{eq:dual_param} are computed using \cref{eq-empirical-risk} and a Laplace approximation.
+More complicated inference techniques, such as variational inference, could be used, but given its simplicity, in our experiments we used the Laplace-GGN approximation with the trained NN.
 Furthermore, our dual variable view of approximate inference means we do not need to retrain a separate sparse GP.\looseness-2
@@
 We provide a proof-of-concept example by evaluating \our on eight UCI benchmarks~\citep{UCI}, a variety of binary and multi-class classification tasks with different data set sizes.
-\todo{update text to say we don't tune prior precision}
-We train a two-layer MLP for each of the classification tasks and follow the experiment set up in \citet{immer2021improving} by using the same hyperparameters, performing a hyperparameter search over the prior precision $\delta$, and run the experiment over $10$ random splits.
+Following \citet{immer2021improving}, we use a two-layer MLP with width 50 and tanh activation functions and we use half of the test data set as a validation data set.
+We train the NN using Adam \cite{adam} with a learning rate of $10^{-4}$ and a batch size of $128$.
+We run each experiment for $5$ random splits.
+Training was stopped when the validation NLPD stopped decreasing after 1000 steps.
+The checkpoint with the lowest validation NLPD was used as the NN MAP.
+
+We first compare \our to alternative posthoc Bayesian deep learning approaches.
+In particular, we compare to the Laplace approximation when making predictions with 1) the nonlinear NN (BNN) and 2) the generalised linear model (GLM).
+We use the Laplace PyTorch library \citep{daxberger2021laplace} with the full Hessian.%, i.e. we do not resort to the diagonal or KFAC approximations.
+We report results when tuning (\cref{tbl:uci} right) and not tuning (\cref{tbl:uci} left) the prior precision $\delta$ after performing inference.
+When tuning the prior precision $\delta$, \our matches the performance of the Laplace methods (BNN/GLM).
+Interestingly, also \our performs well without tuning the prior precision $\delta$, unlike the Laplace methods (BNN/GLM).
+
+As \our captures information from all of the training data in the inducing points, we compare \our to making GP predictions with a subset of the training data (GP subset).
+To make the comparison fair, we use \our's inducing inputs $\vz$ as the subset.
+\cref{tbl:uci} shows that \our is able to summarize the full data set more effectively than the GP subset method as it maintains predictive performance
+whilst using fewer inducing points.
+This is further illustrated in \cref{fig:uci}, which shows that as the number of inducing points is lowered from $M=100\%$ of $N$ to $M=1\%$ of $N$,
+\our is able to maintain a much better NLPD than the GP subset.
+This demonstrates that \our's sparse representation captures information from the entire data set and as a result can use fewer inducing points than the GP subset.
+
+% \our represents information from all of the training data in the inducing points.
+% As such, we compare \our to using a GP with a subset of the training data (GP subset) with the subset corresponding to the inducing inputs $\vz$ used for \our.
+% \cref{fig:uci} shows that as the number of inducing points is lowered from $M=100\%$ of $N$ to $M=1\%$ of $M$,
+% \our is able to maintain a much better NLPD than the GP subset.
+% This demonstrates that \our's sparse representation captures information from the entire data set and as a result provides good uncertainty estimates.
+% See \citet{immer2021improving} for further details on this particular benchmark setup.
+
+% We use the Laplace PyTorch library \citet{daxberger2021laplace} to perform inference using the full Laplace approximation and report the NLPD when making predictions with
+% the BNN predictive (BNN) and the GLM predictive (GLM).
+% \citep{UCI} compares the NLPD (lower is better) when making predictions with the Laplace
+% by using the same hyperparameters, performing a hyperparameter search over the prior precision $\delta$, and run the experiment over $10$ random splits.
 % We follow \cite{immer2021improving} by using the same hyperparameters, performing a hyperparameter search over the prior precision $\delta$,
@@
 %
-\todo{update text to say what our results show}
-\cref{tbl:uci} shows that \our with $M=20\%$ of $N$ either matches or outperforms the predictive performance of the Bayesian NN, and GLM
-predictions %in terms of negative log-predictive density (NLPD).
-\citep[baselines from][]{immer2021improving}.
-% That is, we match predictive performance despite being sparse.
-% In \cref{tbl:uci} (right) we compare to the subset GP method from \citet{immer2021improving} whilst using only $M=32$ inducing points.
-\cref{tbl:uci} also shows that \our is able to summarize the full data set more effectively than the GP subset method as it maintains predictive performance
-whilst using fewer inducing points.
-\cref{fig:uci} further shows that as the number of inducing points is lowered from $M=100\%N$ to $M=1\%M$, \our is able to maintain a much better NLPD than the GP subset.
-These results demonstrate \our's sparse representation captures information from the entire data set and as a result provides good uncertainty estimates.
+% \todo{update text to say what our results show}
+% \cref{tbl:uci} shows that \our with $M=20\%$ of $N$ either matches or outperforms the predictive performance of the Bayesian NN, and GLM
+% predictions %in terms of negative log-predictive density (NLPD).
+% \citep[baselines from][]{immer2021improving}.
+% % That is, we match predictive performance despite being sparse.
+% % In \cref{tbl:uci} (right) we compare to the subset GP method from \citet{immer2021improving} whilst using only $M=32$ inducing points.
+% \cref{tbl:uci} also shows that \our is able to summarize the full data set more effectively than the GP subset method as it maintains predictive performance
+% whilst using fewer inducing points.
+% \cref{fig:uci} further shows that as the number of inducing points is lowered from $M=100\%N$ to $M=1\%M$, \our is able to maintain a much better NLPD than the GP subset.
+% These results demonstrate \our's sparse representation captures information from the entire data set and as a result provides good uncertainty estimates.
 See \citet{immer2021improving} for further details on this particular benchmark setup.
@@
 %
-In this paper, we have introduced \our, a novel approach for representing neural networks in sparse function space, exploiting the dual parameters for an efficient low-rank approximation that accommodates information from the entire data distribution.
-Our method offers a powerful mechanism for capturing predictive uncertainty, opens up new possible avenues for updating the model with new data without retraining, and providing a compact representation suitable for continual learning.
-In this workshop paper, we showcased our method's ability to capture uncertainty in UCI benchmark classification tasks (\cref{tbl:uci}).
+In this paper, we introduced \our, a novel approach for representing NNs in sparse function space.
+It leverages a dual parameterization to obtain an efficient low-rank (sparse) approximation that captures information from the entire data set.
+We showcased \our's uncertainty quantification in UCI benchmark classification tasks (\cref{tbl:uci}).
+Interestingly, \our achieves good predictive performance without tuning the prior precision $\delta$ after performing inference.
+This contrasts the Laplace approximation (BNN/GLM) and we believe this stays more true to Bayesian inference.% (as tuning the prior precision is equivalent to altering the prior after calculating the posterior).
+% providing a compact representation suitable for continual learning.
+% In this workshop paper, we showcased our method's ability to capture uncertainty in UCI benchmark classification tasks (\cref{tbl:uci}).
+% The appealing properties of \our should make it a good addition to the tool set of modelling in sequential learning settings, such as continual and reinforcement learning.
+% It offers a powerful mechanism for quantifying uncertainty, opens up new possible avenues for updating the model with new data without retraining, and providing a compact representation suitable for continual learning.
+In this paper, we showcased our method's ability to capture uncertainty in UCI benchmark classification tasks (\cref{tbl:uci}).
 The appealing properties of \our should make it a good addition to the tool set of modelling in sequential learning settings, such as continual and reinforcement learning.

### 2023-08-31 workshops/icml-duality/main.tex
updated

@@
   % Set figure
-  \setlength{\figurewidth}{.41\textwidth}
+  % \setlength{\figurewidth}{.41\textwidth}
+  \setlength{\figurewidth}{.38\textwidth}
   \setlength{\figureheight}{\figurewidth}
@@
   \newcommand{\myline}[1]{\protect\tikz[baseline=-.5ex,line width=1.6pt]\protect\draw[draw=#1](0,0)--(1.2em,0);}
-  \caption{Comparison of convergence in terms of number of inducing points $M$ in NLPD (mean$\pm$std over 5 seeds) on UCI classification tasks: \our (\myline{steelblue31119180}) vs.
+  \caption{Comparison of convergence in terms of number of inducing points $M$ in NLPD (mean\textcolor{gray}{\footnotesize$\pm$std} over 5 seeds) on UCI classification tasks: \our (\myline{steelblue31119180}) vs.
 GP subset (\myline{darkorange25512714}).
@@
 The authors of that paper exploit the dual parameters for approximate inference, but write them using the natural parameterization, primarily because this form is more suitable for optimization through natural gradients.
-We project the dual parameters onto the inducing points sparse GP using the dual parameters,
+We project the dual parameters onto the inducing points giving sparse dual parameters,
 % In order to link the dual parameters defined in \cref{eq:dual_param}, we write them in the sparse GP using the dual parameters,

### 2023-08-31 papers/iclr-2024/main.tex
added authors

@@
 
-\usepackage{hyperref}
+% \usepackage{hyperref}
+% \usepackage[colorlinks=true,linkcolor=black,allcolors=black,urlcolor=black,citecolor=black]{hyperref}
+\usepackage[colorlinks=true,linkcolor=blue,allcolors=blue,urlcolor=black,citecolor=blue]{hyperref}
 \usepackage{url}
@@
 % \title{Neural Networks as Sparse Gaussian Processes via Dual Parameters}
-\title{Neural Networks as Sparse Gaussian Processes for Sequential Learning}
+\title{Neural Networks as Dual Gaussian Processes for Sequential Learning}
 
@@
 % Non-anonymous submissions will be rejected without review.
-
-\author{Antiquus S.~Hippocampus, Natalia Cerebro \& Amelie P. Amygdale \thanks{ Use footnote for providing further information
-about author (webpage, alternative address)---\emph{not} for acknowledging
-funding agencies.  Funding acknowledgements go at the end of the paper.} \\
-Department of Computer Science\\
-Cranberry-Lemon University\\
-Pittsburgh, PA 15213, USA \\
-\texttt{\{hippo,brain,jen\}@cs.cranberry-lemon.edu} \\
-\And
-Ji Q. Ren \& Yevgeny LeNet \\
-Department of Computational Neuroscience \\
-University of the Witwatersrand \\
-Joburg, South Africa \\
-\texttt{\{robot,net\}@wits.ac.za} \\
-\AND
-Coauthor \\
-Affiliation \\
-Address \\
-\texttt{email}
+% \iclrfinalcopy
+
+% TODO do equal contribution properly
+\author{Aidan Scannell\thanks{Equal contribution.}, Riccardo Mereu*, Ella Tamir, Paul Chang, Joni Pajarinen, \& Arno Solin \\
+% Department of Electrical Engineering and Automation\\
+Aalto University\\
+Espoo, Finland\\
+% Helsinki \\
+% \texttt{aidan.scannell@aalto.fi} \\
+\texttt{\{aidan.scannell,riccardo.mereu\}@aalto.fi}
+% \texttt{\{aidan.scannell,riccardo.mereu,paul.chang,ella.tamir,joni.pajarinen,arno.solin\}@aalto.fi}
 }
+
+% \author{Aidan Scannell\thanks{ Use footnote for providing further information about author (webpage, alternative address)---\emph{not} for acknowledging funding agencies.
+Funding acknowledgements go at the end of the paper.} \\
+% \author{Aidan Scannell\thanks{Equal contribution.} \\
+% % Department of Electrical Engineering and Automation\\
+% Aalto University\\
+% % Helsinki \\
+% % \texttt{aidan.scannell@aalto.fi} \\
+% \And
+% Riccardo Mereu\thanks{Equal contribution.}\\
+% % Department of Computer Science\\
+% Aalto University\\
+% % Helsinki \\
+% % \texttt{riccardo.mereu@aalto.fi} \\
+% \And
+% Ella Tamir\\
+% % Department of Computer Science\\
+% Aalto University\\
+% % Helsinki \\
+% % \texttt{ella.tamir@aalto.fi} \\
+% \And
+% Paul Chang\\
+% % Department of Computer Science\\
+% Aalto University\\
+% % Helsinki \\
+% % \texttt{paul.chang@aalto.fi} \\
+% \And
+% Joni Pajarinen\\
+% % Department of Electrical Engineering and Automation\\
+% Aalto University\\
+% % Helsinki \\
+% % \texttt{joni.pajarinen@aalto.fi} \\
+% \And
+% Arno Solin\\
+% % Department of Computer Science\\
+% Aalto University\\
+% % Helsinki \\
+% % \texttt{arno.solin@aalto.fi} \\
+% % \And
+% % Ji Q. Ren \& Yevgeny LeNet \\
+% % Department of Computational Neuroscience \\
+% % University of the Witwatersrand \\
+% % Joburg, South Africa \\
+% % \texttt{\{robot,net\}@wits.ac.za} \\
+% % \AND
+% % Coauthor \\
+% % Affiliation \\
+% % Address \\
+% % \texttt{email}
+% }
+
+% \author{%
+%   Aidan Scannell\textsuperscript{\star} \\
+%   Aalto University \\
+%   Finnish Center for Artificial Intelligence \\
+%   \texttt{aidan.scannell@aalto.fi}
+%   \And
+%   Riccardo Mereu\textsuperscript{\star} \\
+%   Aalto University\\
+%   \texttt{riccardo.mereu@aalto.fi}
+%   \And
+%   Paul Chang \\
+%   Aalto University\\
+%   \texttt{paul.chang@aalto.fi}
+%   \And
+%   Ella Tamir \\
+%   Aalto University\\
+%   \texttt{ella.tamir@aalto.fi}
+%   \And
+%   Joni Pajarinen \\
+%   Aalto University\\
+%   \texttt{joni.pajarinen@aalto.fi}
+%   \And
+%   Arno Solin \\
+%   Aalto University\\
+%   \texttt{arno.solin@aalto.fi}
+% }
 
@@
 We present a method that mitigates these issues by converting neural networks from weight-space to a low-rank function-space representation, via the so-called dual parameters.
-In contrast to previous work, our sparse representation captures the joint distribution over the entire data set, rather than only over a subset.
 This offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst retaining predictive performance.
-We demonstrate the proposed approach for quantifying uncertainty in supervised learning and maintaining an expressive functional representation for sequential learning.\looseness-1
+We demonstrate the proposed approach for quantifying uncertainty in supervised learning, maintaining an expressive functional representation for continual learning and guiding exploration in model-based reinforcement learning.\looseness-1
 \end{abstract}
@@
 
+\newpage
 \bibliography{bibliography}%zotero-library
@@
 \appendix
+\section*{Appendix}
 
@@
 all details required for reproducing our experiments.
+
+\subsection{Related work}
+A key challenge in RL is balancing the trade-off between exploration and exploitation \cite{sutton2018reinforcement}.
+%That is, should an agent select actions that it knows will lead to high reward %(exploitation), or should it
+%select new ones in hope to discover actions leading to higher reward (exploration).
+One promising direction to balancing this trade-off is to model the uncertainty associated with a learned transition dynamics model and use it to guide exploration.
+Prior work has taken an expectation over the dynamic model's posterior \cite{deisenroth2011pilco,kamtheDataEfficient2018,chuaDeepReinforcementLearning2018},
+sampled from it (akin to Thompson sampling but referred to as posterior sampling in RL) \cite{dearden1999model,sasso2023posterior,osbandMoreEfficientReinforcement2013},
+and used it to implement optimism in the face of uncertainty using upper confidence bounds \cite{curiEfficient2020,jaksch2010near}.
+No single strategy has emerged as a go-to method and we highlight that these strategies are only as good as their uncertainty estimates.
+Previous approaches have used GPs \cite{deisenroth2011pilco,kamtheDataEfficient2018},
+ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
+and variational inference \cite{galImproving2016,houthooftVIME2017}.
+However, each method has its pros and cons.
+In this paper, we present a method which combines some of the pros from NNs with the benefits of GPs.
+% \todo{could try to implement Pathwise conditioning in function-space}
 
@@
 
-{\color{red}{
-\subsection{Uncertainty quantification in RL}
-A key challenge in RL is balancing the trade-off between exploration and exploitation \cite{sutton2018reinforcement}.
-%That is, should an agent select actions that it knows will lead to high reward %(exploitation), or should it
-%select new ones in hope to discover actions leading to higher reward (exploration).
-One promising direction to balancing this trade-off is to model the uncertainty associated with a learned transition dynamics model and use it to guide exploration.
-Prior work has taken an expectation over the dynamic model's posterior \cite{deisenroth2011pilco,kamtheDataEfficient2018,chuaDeepReinforcementLearning2018},
-sampled from it (akin to Thompson sampling but referred to as posterior sampling in RL) \cite{dearden1999model,osbandMoreEfficientReinforcement2013},
-and used it to implement optimism in the face of uncertainty using upper confidence bounds \cite{curiEfficient2020,jaksch2010near}.
-No single strategy has emerged as a go-to method and we highlight that these strategies are only as good as their uncertainty estimates.
-Previous approaches have used GPs \cite{deisenroth2011pilco,kamtheDataEfficient2018},
-ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
-and variational inference \cite{galImproving2016,houthooftVIME2017}.
-However, each method has its pros and cons.
-In this paper, we present a method which combines some of the pros from NNs with the benefits of GPs.
-}}
-% \todo{could try to implement Pathwise conditioning in function-space}
-
 \subsection{Algorithm}

### 2023-08-31 workshops/icml-duality/main.tex

@@
 %Need for adaptive learning methods + failures with current methods
-Given an approximate inference technique, we demonstrate that the neural network emits `dual' parameters which are the building blocks of a GP~\citep{csato2002sparse, adam2021dual, chang2020fast} .
+Given an approximate inference technique, we demonstrate that the neural network emits `dual' parameters which are the building blocks of a GP~\citep{csato2002sparse, adam2021dual, chang2023memory} .
 In contrast to previous work that utilizes subsets of training data \citep{immer2021scalable}, this parameterization allows capturing the contributions from {\em all} data points into a sparse representation, essential for predictive uncertainty.
@@
 The Laplace-GGN takes the MAP solution and approximates the Hessian of the loss function
-with the GGN.
-Following the work of \citet{khan2019approximate}, we can view this as a linear approximation of the NN, as $f_{\weights^*}(\vx) \approx
+with the GGN, we can view this as a linear approximation of the NN, as $f_{\weights^*}(\vx) \approx
 %g_{\weights}(\vx) =
@@
 %
-\citet{khan2019approximate} took a similar approach, but instead of fitting the GP posterior to the actual $\vy$, they rely on a transformation of $\vy$.
+We highlight that  \citet{immer2021improving}  adjust the GP posterior mean function to match the NN predictions $f_{\vw^*}(\cdot)$.
+In contrast, our method makes predictions directly from the GP and avoids such adjustments.
+In the next section, we present our method for converting a trained NN to a sparse functional representation.
+
+%took a similar approach, but instead of fitting the GP posterior to the actual $\vy$, they rely on a transformation of $\vy$.
 Similarly, \citet{immer2021improving} obtain the same covariance function but use a different mean because they rely on a first-order approximation of the NN to form a Bayesian GLM model.
 Both approaches adjust the GP posterior mean function to ensure the predictions are from the NN $f_{\vw^*}(\vx)$.
-In contrast, our method makes predictions directly from the GP and avoids such adjustments.
-In the next section, we present our method for converting a trained NN to a sparse functional representation.
+%In contrast, our method makes predictions directly from the GP and avoids such adjustments.
+%In the next section, we present our method for converting a trained NN to a sparse functional representation.
 % on the non-sparse approximation.
@@
 %
-\begin{align}
+\begin{equation}
+\begin{split}
   \label{eq:dual_param_laplace}
@@
   \hat{\beta}_i &\coloneqq - \nabla^2_{ff}\log p(y_i \mid f) |_{f=f_i}.
-\end{align}
+  \end{split}
+\end{equation}
 %
 Substituting \cref{eq:dual_param_laplace} into \cref{eq:gp_pred}, we obtain our GP based on the converged NN.
-Again, this is similar to what was derived in \citet{immer2021improving} for the posterior variance function.
-However, they use the NN's prediction $f_{\vw^*}(\cdot)$ for the posterior mean and do not emphasize the significance of the dual parameters.
-The problem with the predictions in \cref{eq:gp_pred} is that they incur a cost of $O(N^3)$, which limits its application on large data sets.
+The problem with forming predictions using \cref{eq:gp_pred} is that they cost $O(N^3)$, which limits a full GP model to application on large data sets.
 

### 2023-08-31 workshops/icml-duality/main.tex
updated comparison to immer and main benefits

@@
 
-Unlike our approach, \citet{immer2021improving} employ a subset of the data points to construct a sparse GP, reducing computational complexity.
+We highlight that \our differs from the GP subset method from \citet{immer2021improving}, which results in several advantages.
+First, \our leverages a dual parameterization to construct a sparse GP, which captures information from the entire data set.
+In contrast, \citet{immer2021improving} utilise a subset of the data points which ignores information from the rest of the data set.
+% It is also worth noting that our sparsification via dual parameters does not require any further optimization, we do not need to retrain a separate sparse GP.
+Second, \our makes predictions with the GP mean, whereas \citet{immer2021improving} center predictions around NN predictions $f_{\vw^*}(\cdot)$.
+As such, \our can incorporate new data without retraining (i.e. condition on new data) whilst the GP subset method cannot.
+
+To the best of our knowledge, we are the first to formulate a dual GP from a NN.
+Our dual parameterization has two main benefits: 1) it enables us to construct a sparse GP without requiring us to peform further optimization, and 2)
+it enables us to incorporate new data without retraining (i.e. condition on new data) using \cref{eq:dual_sparse}.
+
+% Unlike our approach, \citet{immer2021improving} employ a subset of the data points to construct a sparse GP, reducing computational complexity.
+However, this method ignores contributions from the complete data set.
+It is important to note that the sparsifying process is independent of the approximate inference technique because the dual parameters of \cref{eq:dual_param} are computed using \cref{eq-empirical-risk} and a Laplace approximation.
+More complicated inference techniques, such as variational inference, could be used, but given its simplicity, in our experiments we used the Laplace-GGN approximation with the trained NN.
+% Furthermore, our dual variable view of approximate inference means we do not need to retrain a separate sparse GP.\looseness-2
+
+% so predictions can be updated by conditioning on new data.
+% This contrasts, \citet{immer2021improving} as they set the GP posterior mean to match the NN predictions $f_{\vw^*}(\cdot)$.
+
+% Further to this, \cref{eq:dual_sparse} implies that we can 1) incorporate new data (i.e. condition on new data) without retraining and 2) unlearn data points.
+
+% Importantly, our dual parameterization enabled us to construct a sparse GP without requiring us to peform further optimization.
+% sparse GP which has lower complexity, whilst still capturing information from the entire data set.
+
+% Further to this, \cref{eq:dual_sparse} implies that we can 1) incorporate new data (i.e. condition on new data) without retraining and 2) unlearn data points.
+
+% In contrast to previous approaches,
+% dual conditioning
+% sparse GP which has lower complexity, whilst still capturing information from the entire data set.
+
+% Unlike our approach, \citet{immer2021improving} employ a subset of the data points to construct a sparse GP, reducing computational complexity.
 However, this method ignores contributions from the complete data set.

### 2023-08-31 workshops/icml-duality/main.tex
remove our custom hyperref
typos

@@
 The neural network is characterized in function-space by its first two moment functions, a mean function and covariance function (or kernel)---defining a Gaussian process \citep[GP,][]{rasmussen2006gaussian}.
-GPs provide a widely-used probabilistic toolkit with principled uncertainty estimates.
+GPs provide a widely used probabilistic toolkit with principled uncertainty estimates.
 They serve as a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} with theoretical guarantees on regret bounds \citep{srinivas2009gaussian}.
@@
 %\paragraph{GP in the dual parameters}
-In this section we present our method, named \our, which converts a trained NN into a GP.
+In this section, we present our method, named \our, which converts a trained NN into a GP.
 \our is built upon a dual parameterization of the GP posterior, i.e. an alternative parameterization.
-Early work by \citet{csato2002sparse} showed that Expectation Propagation gives rise to a dual paramaterization.
+Early work by \citet{csato2002sparse} showed that Expectation Propagation gives rise to a dual parameterization.
 More recent work by \citet{adam2021dual,chang2023memory} showed a different dual parameterization arising from the evidence lower bound for sparse variational GPs \citep{hensman2013gaussian,titsias2009variational}.
@@
 %
-The relationships specified are valid for generic likelihoods, and involve no approximations since the expectation is under the exact posterior, but given that the model can be expressed in a kernel formulation.
+The relationships specified are valid for generic likelihoods and involve no approximations since the expectation is under the exact posterior, but given that the model can be expressed in a kernel formulation.
 \cref{eq:gp_pred} and \cref{eq:dual_param} highlight that the approximate inference technique, usually viewed as a posterior approximation, can be alternatively interpreted as an approximation of the expectation of gradients of loss/likelihoods.
@@
 As demonstrated in \citet{adam2021dual}, the posterior under this model bears a structure akin to \cref{eq:gp_pred}.
-The authors of that paper exploit the dual parameters for approximate inference, but write them using the natural parameterization, primarily because this form is more suitable for optimization through natural gradients.
+The authors of that paper exploit the dual parameters for approximate inference but write them using the natural parameterization, primarily because this form is more suitable for optimization through natural gradients.
 We project the dual parameters onto the inducing points giving sparse dual parameters,
@@
 To the best of our knowledge, we are the first to formulate a dual GP from a NN.
-Our dual parameterization has two main benefits: 1) it enables us to construct a sparse GP without requiring us to peform further optimization, and 2)
+Our dual parameterization has two main benefits: 1) it enables us to construct a sparse GP without requiring us to perform further optimization, and 2)
 it enables us to incorporate new data without retraining (i.e. condition on new data) using \cref{eq:dual_sparse}.

### 2023-09-01 workshops/icml-duality/main.tex
moved hyperref
updated prior precision tuning text

@@
 % \usepackage{icml2023} with \usepackage[nohyperref]{icml2023} above.
-%\usepackage{hyperref}
+% \usepackage{hyperref}
+% \usepackage[colorlinks=true,linkcolor=black,allcolors=black,urlcolor=black,citecolor=black]{hyperref}
+\usepackage[colorlinks=true,linkcolor=blue,allcolors=blue,urlcolor=blue,citecolor=blue]{hyperref}
 
@@
 \usepackage{todonotes}
-% \usepackage[colorlinks=true,linkcolor=black,allcolors=black,urlcolor=black,citecolor=black]{hyperref}
 \usepackage{amsmath}
@@
 We use the Laplace PyTorch library \citep{daxberger2021laplace} with the full Hessian.%, i.e. we do not resort to the diagonal or KFAC approximations.
-We report results when tuning (\cref{tbl:uci} right) and not tuning (\cref{tbl:uci} left) the prior precision $\delta$ after performing inference.
+It is common practice to tune the prior precision $\delta$ after training the NN.
+That is, find a prior precision $\delta_{\text{tune}}$ which has a better NLPD on the validation set than the $\delta$ used to train the NN.
+Note that tuning the prior precision in this way leads to different prior precisions being used at train and inference time.
+We highlihgt that technically this invalidates the Laplace/SFR methods as the NN weights are no longer the MAP weights.
+Nevertheless, we report results when the prior precision $\delta$ is tuned (\cref{tbl:uci} right) and is not tuned (\cref{tbl:uci} left).
 When tuning the prior precision $\delta$, \our matches the performance of the Laplace methods (BNN/GLM).
-Interestingly, also \our performs well without tuning the prior precision $\delta$, unlike the Laplace methods (BNN/GLM).
+Interestingly, \our also  performs well without tuning the prior precision $\delta$, unlike the Laplace methods (BNN/GLM).
 
@@
 This is further illustrated in \cref{fig:uci}, which shows that as the number of inducing points is lowered from $M=100\%$ of $N$ to $M=1\%$ of $N$,
-\our is able to maintain a much better NLPD than the GP subset.
-This demonstrates that \our's sparse representation captures information from the entire data set and as a result can use fewer inducing points than the GP subset.
+\our is able to maintain a much better NLPD.
+This demonstrates that \our  captures information from the entire data set and as a result can use fewer inducing points than the GP subset.
 

### 2023-09-01 workshops/icml-duality/main.tex
fixed eqs to use subequations

@@
 % %
-\begin{align}  \label{eq:gp_pred}
+\begin{subequations}  \label{eq:gp_pred}
+\begin{align}
   \myexpect_{p(f_i \mid\vy)}[f_i] &= \vk_{\vx i}^\top \valpha, \\
@@
 \end{align}
+\end{subequations}
 %
@@
 %
-\begin{equation}
-\begin{split}
+\begin{subequations}
 \label{eq:dual_param}
+\begin{align}
   \alpha_i &\coloneqq \myexpect_{p(\vw \mid \vy)}[\nabla_{f}\log p(y_i \mid f) |_{f=f_i}], \\
@@
   \beta_i &\coloneqq - \myexpect_{p(\vw \mid \vy)}[\nabla^2_{f f}\log p(y_i \mid f_i) |_{f=f_i}].
-  \end{split}
-\end{equation}
+  \end{align}
+\end{subequations}
 %
@@
 %
-\begin{equation}
-\begin{split}
+\begin{subequations}
 \label{eq:dual_param_laplace}
+\begin{align}
   \hat{\alpha}_i &\coloneqq \nabla_{f}\log p(y_i \mid f) |_{f=f_i} , \\
@@
   \hat{\beta}_i &\coloneqq - \nabla^2_{ff}\log p(y_i \mid f) |_{f=f_i}.
-  \end{split}
-\end{equation}
+  \end{align}
+\end{subequations}
 %
@@
 \begin{align}\label{eq:dual_sparse_post}
+\begin{subequations} \label{eq:dual_sparse_post}
+\begin{align}
    \myexpect_{q_{\vu}(\vf)}[f_i] &= \vkzs^{\T} \MKzz^{-1} \valpha_{\vu}, \\
@@
 \end{align}
+\end{subequations}
 where $\MKzz$ and $\vkzs$ are defined similarly to $\MKxx$ and $\vk_{\vx i}$ but over the inducing points $\{\vz_j\}_{i=1}^M$, $\vz \in \R^{D}$, instead of the full data set $\dataset$.

### 2023-09-01 workshops/icml-duality/main.tex
improved abstract

@@
 Deep neural networks (NNs) are known to lack uncertainty estimates, struggle to incorporate new data, and suffer from catastrophic forgetting.
-We present a method that mitigates these issues by converting NNs from weight-space to a low-rank function-space representation, via the so-called dual parameters.
-In contrast to previous work, our sparse representation captures the joint distribution over the entire data set, rather than only over a subset.
+We present a method that mitigates these issues by converting NNs from weight-space to a low-rank (sparse) function-space representation, via a dual parameterization.
+Importantly, our sparse representation captures the joint distribution over the entire data set.
 This offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst retaining predictive performance.

### 2023-09-01 workshops/icml-duality/main.tex
neural network to NN and a few other minor fixes

@@
 %Current state of affairs
-Recent techniques  \citep[\eg,][]{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable} apply a Laplace-GGN approximation to convert trained neural networks into Bayesian neural networks, that can provide uncertainty without sacrificing additional resources to training \citep{foong2019between}.
+Recent techniques  \citep[\eg,][]{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable} apply a Laplace-GGN approximation to convert trained NNs into Bayesian neural networks (BNNs), that can provide uncertainty without sacrificing additional resources to training \citep{foong2019between}.
 Furthermore, the resultant weight-space posterior can be converted to the function-space as shown in \citet{khan2019approximate, immer2021improving}.
-The function-space representation allows for a principled mathematical approach for analyzing its behaviour \citep{cho2009kernel,meronen2020stationary}, performing probabilistic inference \citep{khan2019approximate}, and quantifying uncertainty in neural networks \citep{foong2019between}.
-These methods rely on the linearization of the neural network and the resultant neural tangent kernel \citep[NTK,][]{jacot2018neural}.
-The neural network is characterized in function-space by its first two moment functions, a mean function and covariance function (or kernel)---defining a Gaussian process \citep[GP,][]{rasmussen2006gaussian}.
+The function-space representation allows for a principled mathematical approach for analyzing its behaviour \citep{cho2009kernel,meronen2020stationary}, performing probabilistic inference \citep{khan2019approximate}, and quantifying uncertainty in NNs \citep{foong2019between}.
+These methods rely on the linearization of the NN and the resultant neural tangent kernel \citep[NTK,][]{jacot2018neural}.
+The NN is characterized in function-space by its first two moment functions, a mean function and covariance function (or kernel)---defining a Gaussian process \citep[GP,][]{rasmussen2006gaussian}.
 GPs provide a widely used probabilistic toolkit with principled uncertainty estimates.
@@
 %Need for adaptive learning methods + failures with current methods
-Given an approximate inference technique, we demonstrate that the neural network emits `dual' parameters which are the building blocks of a GP~\citep{csato2002sparse, adam2021dual, chang2023memory} .
+Given an approximate inference technique, we demonstrate that the NN emits `dual' parameters which are the building blocks of a GP~\citep{csato2002sparse, adam2021dual, chang2023memory} .
 In contrast to previous work that utilizes subsets of training data \citep{immer2021scalable}, this parameterization allows capturing the contributions from {\em all} data points into a sparse representation, essential for predictive uncertainty.
-Crucially, the resulting GP directly predicts in the same space as the original trained neural network, with the benefit of avoiding the complexity introduced by working in weight-space and the notorious cubic complexity of vanilla GPs.
+Crucially, the resulting GP directly predicts in the same space as the original trained NN, with the benefit of avoiding the complexity introduced by working in weight-space and the notorious cubic complexity of vanilla GPs.
 %\todo{Could make it clearer that the GP predicts in the output space while avoiding the NN parameter space}
 %, a feature not present in previous approaches, while avoiding the notorious cubic complexity of vanilla GPs.
-Through the dual parameter formulation, we establish a connection between the neural network, full GPs, and a sparse approximation similar to sparse variational GPs~\citep{titsias2009variational}.
-We refer to our method as Sparse Function-space Representation (\our)---a sparse GP derived from a trained neural network; see \cref{fig:teaser} for an example.
+Through the dual parameter formulation, we establish a connection between the NN, full GPs, and a sparse approximation similar to sparse variational GPs~\citep{titsias2009variational}.
+We refer to our method as Sparse Function-space Representation (\our)---a sparse GP derived from a trained NN; see \cref{fig:teaser} for an example.
 %Moreover, this dual parameterization can be exploited to perform dual conditioning \citep{chang2022fantasizing}, \ie, an effective approach for conditioning on new data without needing to retrain the model (see \cref{fig:teaser}).
@@
 
-\section{Background: Function-space representation of neural networks}
+% \section{Background: Function-space representation of NNs}
+\section{Background}
 \label{sec:methods}
 %
-%In this section, we recap how a trained neural network (NN) can be converted to a Gaussian process by locally linearising its weights.
+In this section, we recap how a trained NN can be converted to a GP by locally linearising the NN around its weights.
 % a GP posterior -- can be obtained
@@
 %
+\textbf{NN training}
 In supervised learning, given a data set $\dataset = \{(\vx_{i} , \vy_{i})\}_{i=1}^{N}$, with input $\vx_i \in \inputDomain$ and output $\vy_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a NN, $f_\mathbf{w}: \inputDomain \to \outputDomain$ (yet, to simplify the notation we restrict presentation to scalar output), are usually trained to minimize the (regularized) empirical risk,\looseness-1
@@
 %
-If $\ell(f_\weights(\vx_{i}), y_i) = -\log(p(y \mid f_\weights(\vx_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where the regularization weight takes the role of a prior precision parameter, \ie, $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.
+If $\ell(f_\weights(\vx_{i}), y_i) = -\log(p(y_{i} \mid f_\weights(\vx_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where the regularization weight takes the role of a prior precision parameter, \ie, $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.
 %Bayesian inference offers a principled approach to quantifying uncertainty in neural networks.
@@
 %In \cref{fig:banana}, we show a qualitative example of the induced function-space posterior obtained with our method compared to the posterior obtained through HMC sampling on the Banana toy dataset.
-The posterior over the weights ${p(\vw \mid \dataset) \propto p(y \mid f_{\weights}(\vx)) \, p(\weights)}$ is generally not available in closed form.
+The posterior over the weights ${p(\vw \mid \dataset) \propto p(\vy \mid f_{\weights}(\vx)) \, p(\weights)}$ is generally not available in closed form.
 Sampling methods that characterize the posterior with a finite set of samples in weight-space are general-purpose, but computationally heavy and impractical for downstream applications.
 
-\textbf{Neural network function-space} %\todo{Could be titled some other way, like Function-space representation}
-%As a neural network is a deterministic mapping, the weight-space posterior induces a distribution over the function values.
+% \textbf{NN function-space} %\todo{Could be titled some other way, like Function-space representation}
+\textbf{NN function-space} %\todo{Could be titled some other way, like Function-space representation}
+%As a NN is a deterministic mapping, the weight-space posterior induces a distribution over the function values.
 %Intuitively, if one was to sample from the weight posterior, the corresponding functions created can
@@
 
-\textbf{Linearization gives rise to a Gaussian process}
+% \textbf{Linearization gives rise to a Gaussian process}
+\textbf{Linearization gives rise to a GP}
 Our goal is to capture the distribution over the NN model functions through their first two moments.
@@
 In contrast, our method makes predictions directly from the GP and avoids such adjustments.
-In the next section, we present our method for converting a trained NN to a sparse functional representation.
+In the next section, we present our method for converting a trained NN to a sparse function-space representation.
 
@@
 % \newpage
-\section{\our: Sparse function-space representation of neural networks}\label{sec:sfr}
+% \section{\our: Sparse function-space representation of neural networks}\label{sec:sfr}
+\section{\our: Sparse function-space representation of NNs}\label{sec:sfr}
 %\paragraph{GP in the dual parameters}
@@
 %
-We provide a proof-of-concept example by evaluating \our on eight UCI benchmarks~\citep{UCI}, a variety of binary and multi-class classification tasks with different data set sizes.
-Following \citet{immer2021improving}, we use a two-layer MLP with width 50 and tanh activation functions and we use half of the test data set as a validation data set.
-We train the NN using Adam \cite{adam} with a learning rate of $10^{-4}$ and a batch size of $128$.
-We run each experiment for $5$ random splits.
+We evaluate \our on eight UCI~\citep{UCI} binary and multi-class classification tasks.
+Following \citet{immer2021improving}, we used a two-layer MLP with width 50 and tanh activation functions and we used half of the test data set as a validation data set.
+We trained the NN using Adam \cite{adam} with a learning rate of $10^{-4}$ and a batch size of $128$.
 Training was stopped when the validation NLPD stopped decreasing after 1000 steps.
-The checkpoint with the lowest validation NLPD was used as the NN MAP.
+The checkpoint with lowest NLPD was the NN MAP.
+Each experiment was run for $5$ seeds.
 
@@
 In practical terms, \our serves a role similar to a sparse GP. However, unlike a conventional GP, it does not provide a straightforward method for specifying the prior covariance function.
-This limitation can be addressed indirectly: the architecture of the neural network and the choice of activation functions can be used to implicitly specify the prior assumptions.
+This limitation can be addressed indirectly: the architecture of the NN and the choice of activation functions can be used to implicitly specify the prior assumptions.
 It is important to note that \our linearizes the NN around the MAP weights $\weights^{*}$, resulting in the function-space prior

### 2023-09-01 workshops/icml-duality/main.tex
re-wrote background

@@
 \newcommand{\MB}{\mbf{B}}
+\newcommand{\MS}{\mbf{S}}
 \newcommand{\MC}{\mbf{C}}
@@
 %
-In this section, we recap how a trained NN can be converted to a GP by locally linearising the NN around its weights.
+% In this section, we recap how a trained NN can be converted to a GP by locally linearising the NN around its weights.
+
+% Our method builds on two recent observations.
+% First is that the Laplace generalised Gauss-Newton (GGN) approximation corresponds to a linearised model.
+% Second, any Bayesian linear model in weight space can be converted to a GP in function space.
+
 % a GP posterior -- can be obtained
@@
 %
-\textbf{NN training}
-In supervised learning, given a data set $\dataset = \{(\vx_{i} , \vy_{i})\}_{i=1}^{N}$, with input $\vx_i \in \inputDomain$ and output $\vy_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a NN, $f_\mathbf{w}: \inputDomain \to \outputDomain$ (yet, to simplify the notation we restrict presentation to scalar output), are usually trained to minimize the (regularized) empirical risk,\looseness-1
+% \textbf{NN training gives MAP weights}
+% In supervised learning, given a data set $\dataset = \{(\vx_{i} , \vy_{i})\}_{i=1}^{N}$, with input $\vx_i \in \inputDomain$ and output $\vy_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a NN, $f_\mathbf{w}: \inputDomain \to \outputDomain$ (yet, to simplify the notation we restrict presentation to scalar output), are usually trained to minimize the (regularized) empirical risk,\looseness-1
+% %
+% \begin{align} \label{eq-empirical-risk}
+%   \weights^{*} &=
+%   \arg \min_{\weights} \mathcal{L}(\dataset,\weights) \nonumber \\ &=
+%   \arg \min_{\weights} \textstyle\sum_{i=1}^{N} \ell(f_\weights(\mathbf{x}_{i}), y_i) + \delta \mathcal{R}(\weights).
+% \end{align}
+% %
+% If $\ell(f_\weights(\vx_{i}), y_i) = -\log(p(y_{i} \mid f_\weights(\vx_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where the regularization weight takes the role of a prior precision parameter, \ie, $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.
+% %Bayesian inference offers a principled approach to quantifying uncertainty in neural networks.
+% %The goal is to find the posterior over the weights ${p(\vw \mid \vy) \propto p(\vy \mid f_{\weights}(\vx)) \, p(\weights)}$ as it represents our belief in the parameters after combining data $\dataset$ with our prior $p(\vw)$.
+% %Although the true posterior $p(\vw \mid \dataset)$ is intractable given the non-linearities of the neural network, one can resort to sampling techniques such as Hamiltonian Monte-Carlo (HMC).
+% %However, for most applications their high computational costs make them impractical so we need approximate inference techniques.
+% %In \cref{fig:banana}, we show a qualitative example of the induced function-space posterior obtained with our method compared to the posterior obtained through HMC sampling on the Banana toy dataset.
+% The posterior over the weights ${p(\vw \mid \dataset) \propto p(\vy \mid f_{\weights}(\vx)) \, p(\weights)}$ is generally not available in closed form.
+Sampling methods that characterize the posterior with a finite set of samples in weight-space are general-purpose, but computationally heavy and impractical for downstream applications.
+
+% % \textbf{NN function-space} %\todo{Could be titled some other way, like Function-space representation}
+% \textbf{NN function-space} %\todo{Could be titled some other way, like Function-space representation}
+% %As a NN is a deterministic mapping, the weight-space posterior induces a distribution over the function values.
+% %Intuitively, if one was to sample from the weight posterior, the corresponding functions created can
+% %be viewed as perturbed versions of the function at the MAP estimate $f_{\vw^*}$.
+% %In most applications, we care about predictions from the neural network and not the weights themselves.
+% %As such, it is the distribution over function values that we are actually interested in.
+% NNs are deterministic parametric functions, but even if the training is typically an optimization in the weight-space, in most applications, we are interested in the parametrized function and not in the weights themselves.
+% %While neural networks are deterministic mappings defined by their weights, the ultimate goal of training a neural network is to optimize the function it represents, not the weights themselves.
+% Consequently, the weight-space posterior corresponds to a distribution over function values.
+% Intuitively, if one was to sample from the weight posterior, the corresponding functions created can be viewed as perturbed versions of the function at the MAP estimate $f_{\vw^*}$.
+This perspective aligns better with the main objective of making representative predictions given the observations.
+
+We consider supervised learning with inputs $\vx_i \in \inputDomain$ and outputs $\vy_i \in \outputDomain$ (e.g. regression) or $\vy_{i} \in \{0,1\}^{C}$ (e.g. classification),
+giving a data set $\dataset = \{(\vx_{i} , \vy_{i})\}_{i=1}^{N}$.
+We introduce a  NN $f_\mathbf{w}: \inputDomain \to \outputDomain$ with weights $\weights \in \R^{P}$ and use a likelihood function $p(\vy \mid f_\mathbf{w}(\vx))$
+to link the function values to the output $\vy$ (Gaussian for regresssion or Categorical for classification).
+For notational conciseness we stick to scalar outputs $y_{i}$.
+
+\textbf{Bayesian NNs}
+In Bayesian deep learning, we place a prior over the weights $p(\vw)$ and aim to calculate the posterior over the weights given the data $p(\vw \mid \mathcal{D})$.
+Given the posterior over the weights $p(\vw \mid \mathcal{D})$, we can then make probabilistic predictions with,
+\begin{align} \label{eq-predictions}
+  p_{\text{\sc BNN}}(y \mid \vx, \mathcal{D}) = \E_{p(\vw \mid \mathcal{D})} \left[ p(y \mid f_{\vw}(\vx)) \right]
+\end{align}
+The posterior ${p(\vw \mid \dataset) \propto p(\vy \mid f_{\weights}(\vx)) \, p(\weights)}$ is generally not available in closed form
+so we resort to approximations.
+% Sampling methods that characterize the posterior with a finite set of samples in weight-space are general-purpose, but computationally heavy and impractical for downstream applications.
+% In this paper, we build on the Laplace approximation
+
+% , are usually trained to minimize the (regularized) empirical risk,\looseness-1
+
+% In supervised learning, given a data set $\dataset = \{(\vx_{i} , \vy_{i})\}_{i=1}^{N}$, with input $\vx_i \in \inputDomain$ and output $\vy_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a NN, $f_\mathbf{w}: \inputDomain \to \outputDomain$ (yet, to simplify the notation we restrict presentation to scalar output),
+
+% \subsection{Laplace approximation}
+\textbf{MAP}
+It is common to train the NN's weights $\vw$ to minimize the (regularized) empirical risk,
 %
@@
   \weights^{*} &=
-  \arg \min_{\weights} \mathcal{L}(\dataset,\weights) \nonumber \\ &=
-  \arg \min_{\weights} \textstyle\sum_{i=1}^{N} \ell(f_\weights(\mathbf{x}_{i}), y_i) + \delta \mathcal{R}(\weights).
+                 \arg \min_{\weights} \mathcal{L}(\dataset,\weights) \nonumber \\
+               &=
+  \arg \min_{\weights} \textstyle\sum_{i=1}^{N} \underbrace{\ell(f_\weights(\mathbf{x}_{i}), y_i)}_{-\log p(y_{i} \mid f_{\vw}(\vx_{i}))} + \underbrace{\delta \mathcal{R}(\weights)}_{-\log p(\vw)}.
 \end{align}
 %
-If $\ell(f_\weights(\vx_{i}), y_i) = -\log(p(y_{i} \mid f_\weights(\vx_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where the regularization weight takes the role of a prior precision parameter, \ie, $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.
+This objective corresponds to the log joint distribution $\mathcal{L}(\mathcal{D},\vw)=p(\mathcal{D}, \vw)$
+as the loss can be interpreted as a negative log likelihood $\ell(f_\weights(\vx_{i}), y_i) = -\log(p(y_{i} \mid f_\weights(\vx_{i}))$
+and the regularizer corresponds to a log prior over the weights $\delta\mathcal{R}(\weights) = \log p(\vw)$.
+For example, a weight decay regularizer $\mathcal{R}(\vw) = \frac{1}{2}\|\weights\|^{2}_2$ corresponds to a Gaussinan prior over the weights $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$ with
+prior precision $\delta$.
+As such, we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution.
+
 %Bayesian inference offers a principled approach to quantifying uncertainty in neural networks.
@@
 %In \cref{fig:banana}, we show a qualitative example of the induced function-space posterior obtained with our method compared to the posterior obtained through HMC sampling on the Banana toy dataset.
-The posterior over the weights ${p(\vw \mid \dataset) \propto p(\vy \mid f_{\weights}(\vx)) \, p(\weights)}$ is generally not available in closed form.
+% The posterior over the weights ${p(\vw \mid \dataset) \propto p(\vy \mid f_{\weights}(\vx)) \, p(\weights)}$ is generally not available in closed form.
 Sampling methods that characterize the posterior with a finite set of samples in weight-space are general-purpose, but computationally heavy and impractical for downstream applications.
 
-% \textbf{NN function-space} %\todo{Could be titled some other way, like Function-space representation}
-\textbf{NN function-space} %\todo{Could be titled some other way, like Function-space representation}
-%As a NN is a deterministic mapping, the weight-space posterior induces a distribution over the function values.
-%Intuitively, if one was to sample from the weight posterior, the corresponding functions created can
-%be viewed as perturbed versions of the function at the MAP estimate $f_{\vw^*}$.
-%In most applications, we care about predictions from the neural network and not the weights themselves.
-%As such, it is the distribution over function values that we are actually interested in.
-NNs are deterministic parametric functions, but even if the training is typically an optimization in the weight-space, in most applications, we are interested in the parametrized function and not in the weights themselves.
-%While neural networks are deterministic mappings defined by their weights, the ultimate goal of training a neural network is to optimize the function it represents, not the weights themselves.
-Consequently, the weight-space posterior corresponds to a distribution over function values.
-Intuitively, if one was to sample from the weight posterior, the corresponding functions created can be viewed as perturbed versions of the function at the MAP estimate $f_{\vw^*}$.
-This perspective aligns better with the main objective of making representative predictions given the observations.
-
-% \textbf{Linearization gives rise to a Gaussian process}
-\textbf{Linearization gives rise to a GP}
-Our goal is to capture the distribution over the NN model functions through their first two moments.
-The first two moments characterize a GP with a mean function $\mu(\cdot)$ and a covariance function (kernel) $\kappa(\cdot,\cdot)$.
-Recent work \citep{khan2019approximate,maddox2021fast} has shown that linearizing approximations in the weight space lead to function-space equivalent approximations.
-As Gaussian distributions remain tractable under linear transformations, a linear function in terms of parameters can be converted from the weight space to the function space \citep[see Ch.~2.1 in ][]{rasmussen2006gaussian} as follows:
-%
-\begin{align} \label{eq:weight_func}
- &f_\weights(\vx) \approx
-%g_\weights(\mathbf{x}) =
- \phi^\top\!(\vx) \, \vw \quad\implies \nonumber \\
- &\mu(\vx) = 0 \quad \text{and} \quad \kappa(\vx, \vx') = \frac{1}{\delta} \phi^\T\!(\vx) \, \phi(\vx').
+\textbf{Laplace-GGN}
+The Laplace approximation \citet{aa} builds upon this observation and approximates the weight-space posterior $p(\vw \mid \mathcal{D}) = \mathcal{N}(\vw^{*} , \bm\Sigma)$
+around the MAP weights ($\vw^{*}$) by setting the covariance to the Hessian of the posterior,
+\begin{align} \label{eq:laplace-cov}
+ \bm\Sigma = - \left[\nabla^{2}_{\vw\vw} \log p(\vw \mid \mathcal{D})  |_{\vw=\vw^{*}} \right]^{-1}.
 \end{align}
-% The posterior structure directly relates to the optimization loss around the MAP weights $\vw^*$.
-A common approach is to approximate the correlation structure of a distribution centred at the MAP estimate as done in the Laplace-GGN~\citep{khan2019approximate, daxberger2021laplace, maddox2021fast}.
-The Laplace-GGN takes the MAP solution and approximates the Hessian of the loss function
-with the GGN, we can view this as a linear approximation of the NN, as $f_{\weights^*}(\vx) \approx
-%g_{\weights}(\vx) =
-\Jac{\weights^*}{\vx} \, \weights$, where $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{1 \times P}$ is the Jacobian at the MAP.
-For notational conciseness, we % \cref{eq-laplace-approx-function-space},
-restrict our notatin to a single function output. The extension to multiple outputs is straightforward.
-
-Using the Hessian of the approximate model, we arrive at the Laplace-GGN approximate posterior over $\vw$.
-Therefore, the Laplace-GGN linear model can be used to convert our weight space model to the function space,
-\begin{equation}
-\label{eq-laplace-approx-function-space}
-% g(\vx) \sim \GP \left( \mu(\vx), \kappa(\vx, \vx') \right) \quad \text{with} \quad
-  \mu(\vx) =  0 \quad \text{and} \quad
-  \kappa(\vx, \vx')
-  = \frac{1}{\delta} \Jac{\weights^*}{\vx} \, \JacT{\weights^*}{\vx'},
-\end{equation}
-where the kernel is the so-called Neural Tangent Kernel \citep[NTK,][]{jacot2018neural}.
-We can combine this kernel function with the data set $\dataset$ to construct the posterior.
-%
-We highlight that  \citet{immer2021improving}  adjust the GP posterior mean function to match the NN predictions $f_{\vw^*}(\cdot)$.
+Computing \cref{eq:laplace-cov} requires calculating the Hessian of the log-likelihood $\nabla^{2}_{\vw\vw} \log p(\vy \mid f_{\vw}(\vx))$ from \cref{eq-empirical-risk}.
+As highlighted in \citet{immer2021improving}, computing this Hessian is often infeasible and in practice it is common to adopt the
+generalised Gauss-Newton (GGN) approximation,
+\begin{align}
+ \nabla^{2}_{\vw\vw} \log p(\vy \mid f_{\vw}(\vx)) \approx \Jac{\vw}{\vx}^{\top} \nabla_{\vf\vf}^{2}\log(\vy\mid\vf) \Jac{\vw}{\vx}.
+\end{align}
+% \textbf{Laplace-GGN converts BNN into GLM}
+\citet{immer2021improving} highlighted that the GGN approximation corresponds to a local linearization of the NN,
+% Recent work \citep{khan2019approximate,maddox2021fast} has converted NNs to GPs by linearizing around the NN's MAP weights (obtained from \cref{eq-empirical-risk}).
+% Recent work \citep{khan2019approximate,maddox2021fast} has shown that NN (in weight space) leads to a GP, i.e. a function-space approximation.
+$f_{\weights^{*}}^{\text{lin}}(\vx) = f_{\weights}(\vx) + \Jac{\weights^{*}}{\vx}(\weights-\weights^{*})$.
+This suggests that predictions should be made with a generalised linear model (GLM), given by,
+\begin{align} \label{eq-glm}
+  p_{\text{\sc GLM}}(\vy \mid \vx, \mathcal{D}) &= \E_{q(\vw)} \left[ p(\vy \mid f_{\vw^{*}}^{\text{lin}}(\vx))\right]. %\nonumber \\
+  % &\approx \frac{1}{S} \sum_{s} p(\vy \mid f_{\vw_{s}}^{\text{lin}}(\vx)), \quad \vw_{s} \sim q(\vw)
+\end{align}
+
+\textbf{Weight space GLM is equivalent to a GP}
+As Gaussian distributions remain tractable under linear transformations, a linear function in terms of parameters can be converted from the weight space to the function space \citep[see Ch.~2.1 in ][]{rasmussen2006gaussian}.
+ % highlighted that the GGN approximation corresponds to a local linearization of the NN,
+As such (and show in \citet{immer2021improving}), the Bayesian GLM in \cref{eq-glm} has an equivalent GP formulation,
+% \begin{align}
+%   p_{\text{\sc GP}}(\vy \mid \vx, \mathcal{D}) &= \E_{q(\vf)} \left[ p(\vy \mid \vf)\right] %\nonumber \\
+%   % &\approx \frac{1}{S} \sum_{s} p(\vy \mid f_{\vw_{s}}^{\text{lin}}(\vx)), \quad \vw_{s} \sim q(\vw)
+% \end{align}
+% where the GP posterior is given by,
+\begin{subequations}  \label{eq-gp-pred-immer}
+\begin{align}
+  p_{\text{\sc GP}}(\vy \mid \vx, \mathcal{D}) &= \E_{q(\vf)} \left[ p(\vy \mid \vf)\right] \\ %\nonumber \\
+  \myexpect_{p(f_i \mid\vy)}[f_i] &= f_{\vw^{*}}(\vx_{i}), \\
+  \mathrm{Var}_{p(f_i \mid \vy)}[f_i] &= k_{ii} - \vk_{\vx i}^\top ( \MKxx + \bm\Lambda^{-1})^{-1} \vk_{\vx i},
+\end{align}
+\end{subequations}
+where the kernel $\kappa(\vx,\vx')=\frac{1}{\delta} \Jac{\weights^*}{\vx} \, \JacT{\weights^*}{\vx'}$ is the Neural Tangent Kernel \citep[NTK,][]{jacot2018neural},
+based on the Jacobian at the MAP $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{1 \times P}$.
+The $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{N \times N}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where
+each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, $k_{ii} = \kappa(\vx_i, \vx_i)$ and $\bm\Lambda = - \nabla^2_{\vf \vf}\log p(\vy \mid \vf)$ can be interpreted as per-input noise.
+% For notational conciseness, we % \cref{eq-laplace-approx-function-space},
+% restrict our notatin to a single function output. The extension to multiple outputs is straightforward.
+
+The GP formulation from \citet{immer2021improving} (shown in \cref{eq-gp-pred-immer})
+requires inverting an $N\times N$ matrix which has complexity $O(N^3)$. This limits its applicability to large data sets, which are common in deep learning.
+
+% The GP formulation from \citet{immer2021improving} (shown in \cref{eq-gp-pred-immer}) has two limitations:
+% First, it requires inverting an $N\times N$ matrix which has complexity $O(N^3)$. This limits its applicability to large data sets, which are common in deep learning.
+% Second, the posterior mean is the NN  $f_{\vw^*}(\vx)$. As such, new data cannot be incorporated by conditioning on it.
+% Our method overcomes these limitations  via a dual parameterization.
+% Importantly, our dual parameterization makes predictions directly from the GP and enables us to sparsify the GP.
+
+% making predictions directly from the GP.
+% In the next section, we present our method for converting a trained NN to a sparse function-space representation.
+% The GP formulation from \citet{immer2021improving} (shown in \cref{eq-gp-pred-immer})  requires inverting an $N\times N$ matrix which has complexity $O(N^3)$.
+% As such, this limits its applicability to large data sets, which are common in deep learning.
+
+% We highlight that  \citet{immer2021improving}  adjust the GP posterior mean function to match the NN predictions $f_{\vw^*}(\cdot)$.
+In contrast, our method makes predictions directly from the GP and avoids such adjustments.
+In the next section, we present our method for converting a trained NN to a sparse function-space representation.
+
+% \citet{immer2021improving} showed that making predictions in function space
+
+\textbf{Sparse Gaussian processes}
+Sparse GPs reduce the computational complexity by representing the GP as a low-rank approximation at a set of inducing
+inputs $\vz \in \R^{D}$ with corresponding inducing variables $\vu = f(\vz)$ \citep[see][for an early overview]{quinonero2005unifying}.
+The approach by \citet{titsias2009variational} \citep[also used in the DTC approximation, see][]{quinonero2005unifying},
+defines the marginal predictive distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) \, q(\vu) \, \mathrm{d}\vu$.
+This give the sparse GP predictive posterior,
+\begin{subequations}  \label{eq-svgp-pred}
+\begin{align}
+  \myexpect_{q_{\vu}(f_i)}[f_i] &= f_{\vw^{*}}(\vx_{i}) + \vk_{\vz i}^{\top}\MKzz^{-1}(\vm - f_{\vw^{*}}(\vz)), \\
+  \mathrm{Var}_{q_{\vu}(f_i)}[f_i] &= k_{ii} - \vk_{\vx i}^\top \MKzz^{-1}( \MKzz - \MS_{\vz\vz} )^{-1} \MKzz^{-1} \vk_{\vx i},  \nonumber
+\end{align}
+\end{subequations}
+where the variational distribution is parameterized as $q(\vu) = \mathcal{N}\left(\vu \mid \vm, \MS \right)$ (as in \citet{titsias2009variational,hensman2013gaussian}).
+\todo{is this what titsias used or just hensman?}
+To the best of our knowledge, there are no methods that convert NNs to sparse GPs.
+It is worth noting that the parameters of the variational posterior ($\vm$ and $\MS$) are usually obtained via variational inference.
+However, this requires further optimization and is non trivial in the NN setting.
+
+Not only does the GP formulation from \citet{immer2021improving} (shown in \cref{eq-gp-pred-immer}) struggle to scale to large data sets but
+it also cannot be incorporate new data by conditioning on it.
+This is because it's posterior mean is the NN  $f_{\vw^*}(\vx)$
+Our method overcomes both of these limitations via a dual parameterization.
+Importantly, our dual parameterization enables us to sparsify it whilst making predictions directly from the GP.
+
+% Converting the NN GP formulation from \citet{immer2021improving} (shown in \cref{eq-gp-pred-immer}) to a sparse GP is a promising direction for scaling
+% such methods to deep learning data sets.
+% However,
+% eq-svgp-pred
+% Given that we have $p(f_i \mid \vu)$ determined by our GP prior, the goal is to find a $q(\vu)$.
+
+% Sparse GPs reduce the computational complexity by representing the GP as a low-rank approximation induced by a sparse set of input
+% points \citep[see][for an early overview]{quinonero2005unifying}.
+% Given that we have computed the dual parameters derived from our NN predictions and a kernel function, we could essentially employ any of these sparsification methods.
+% In this work, we opt for the approach suggested by \citet{titsias2009variational} \citep[also used in the DTC approximation, see][]{quinonero2005unifying},
+% which defines the marginal predictive distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) \, q(\vu) \, \mathrm{d}\vu$.
+% Given that we have $p(f_i \mid \vu)$ determined by our GP prior, the goal is to find a $q(\vu)$.
+% Instead of parameterizing the sparse GP posterior as $q(\vu) = \mathcal{N}\left(\vu \mid \vm, \MS \right)$ (as in \citet{titsias2009variational,hensman2013gaussian})
+% we follow insights from \citet{adam2021dual} that the posterior under this model bears a structure akin to \cref{eq:gp_pred}.
+% As such, we project the dual parameters onto the inducing points giving sparse dual parameters,
+% Using this sparse definition of the dual parameters, our sparse GP posterior takes the following form:
+
+% Recent work \citep{khan2019approximate,maddox2021fast} has converted NNs to GPs by linearizing around the NN's MAP weights (obtained from \cref{eq-empirical-risk}).
+% % leads to a GP, i.e. a function-space approximation.
+% % Recent work \citep{khan2019approximate,maddox2021fast} has shown that linearizing a NN (in weight space) leads to a GP, i.e. a function-space approximation.
+% T
+% \begin{align}
+
+% \label{eq-laplace-approx-function-space}
+% f_{\weights^{*}}^{\text{lin}}(\vx) &\sim \GP \left( \mu(\vx), \kappa(\vx, \vx') \right)  \\
+%   % \mu(\vx) &=  0 \quad \text{and} \quad
+%   \kappa(\vx, \vx') &= \frac{1}{\delta} \Jac{\weights^*}{\vx} \, \JacT{\weights^*}{\vx'},
+%   % \mu(\vx) &=  0 \quad \text{and} \quad
+%   % \kappa(\vx, \vx') = \frac{1}{\delta} \Jac{\weights^*}{\vx} \, \JacT{\weights^*}{\vx'},
+% \end{align}
+
+% % \textbf{Linearization gives rise to a Gaussian process}
+% \textbf{Convert NN to GP via linearization}
+% % Our goal is to capture the distribution over the NN model functions through their first two moments.
+% % The first two moments characterize a GP with a mean function $\mu(\cdot)$ and a covariance function (kernel) $\kappa(\cdot,\cdot)$.
+% Recent work \citep{khan2019approximate,maddox2021fast} has shown that linearizing a NN (in weight space) leads to a GP, i.e. a function-space approximation.
+% % As Gaussian distributions remain tractable under linear transformations, a linear function in terms of parameters can be converted from the weight space to the function space \citep[see Ch.~2.1 in ][]{rasmussen2006gaussian} as follows:
+% %
+% \begin{align} \label{eq:weight_func}
+%  &f_\weights(\vx) \approx
+% %g_\weights(\mathbf{x}) =
+%  \phi^\top\!(\vx) \, \vw \quad\implies \nonumber \\
+%  &\mu(\vx) = 0 \quad \text{and} \quad \kappa(\vx, \vx') = \frac{1}{\delta} \phi^\T\!(\vx) \, \phi(\vx').
+% \end{align}
+% % The posterior structure directly relates to the optimization loss around the MAP weights $\vw^*$.
+% A common approach is to approximate the correlation structure of a distribution centred at the MAP estimate as done in the Laplace-GGN~\citep{khan2019approximate, daxberger2021laplace, maddox2021fast}.
+% The Laplace-GGN takes the MAP solution and approximates the Hessian of the loss function
+% with the GGN, we can view this as a linear approximation of the NN, as $f_{\weights^*}(\vx) \approx
+% %g_{\weights}(\vx) =
+% \Jac{\weights^*}{\vx} \, \weights$, where $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{1 \times P}$ is the Jacobian at the MAP.
+% For notational conciseness, we % \cref{eq-laplace-approx-function-space},
+% restrict our notatin to a single function output. The extension to multiple outputs is straightforward.
+
+% Using the Hessian of the approximate model, we arrive at the Laplace-GGN approximate posterior over $\vw$.
+% Therefore, the Laplace-GGN linear model can be used to convert our weight space model to the function space,
+% \begin{equation}
+% \label{eq-laplace-approx-function-space}
+% % g(\vx) \sim \GP \left( \mu(\vx), \kappa(\vx, \vx') \right) \quad \text{with} \quad
+%   \mu(\vx) =  0 \quad \text{and} \quad
+%   \kappa(\vx, \vx')
+%   = \frac{1}{\delta} \Jac{\weights^*}{\vx} \, \JacT{\weights^*}{\vx'},
+% \end{equation}
+% where the kernel is the so-called Neural Tangent Kernel \citep[NTK,][]{jacot2018neural}.
+% We can combine this kernel function with the data set $\dataset$ to construct the posterior.
+% %
+% We highlight that  \citet{immer2021improving}  adjust the GP posterior mean function to match the NN predictions $f_{\vw^*}(\cdot)$.
 In contrast, our method makes predictions directly from the GP and avoids such adjustments.
@@
 Given that we have $p(f_i \mid \vu)$ determined by our GP prior, the goal is to find a $q(\vu)$.
-
-As demonstrated in \citet{adam2021dual}, the posterior under this model bears a structure akin to \cref{eq:gp_pred}.
-The authors of that paper exploit the dual parameters for approximate inference but write them using the natural parameterization, primarily because this form is more suitable for optimization through natural gradients.
-We project the dual parameters onto the inducing points giving sparse dual parameters,
-% In order to link the dual parameters defined in \cref{eq:dual_param}, we write them in the sparse GP using the dual parameters,
-%
-\begin{equation} \textstyle
-  \valpha_{\vu}  =  \sum_{i=1}^N  \vkzi \, \hat{\alpha}_{i}
-  \quad \text{and} \quad
-  \MBeta_{\vu} =  \sum_{i=1}^N \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,
-\label{eq:dual_sparse}
-\end{equation}
-%
-where the sparse dual parameters are now a sum over \emph{all data points}, with $\valpha_{\vu} \in \R^{M}$ and $\MBeta_{\vu} \in \R^{M  \times M}$.
+Instead of parameterizing the sparse GP posterior as $q(\vu) = \mathcal{N}\left(\vu \mid \vm, \MS \right)$ (as in \citet{titsias2009variational,hensman2013gaussian})
+we follow insights from \citet{adam2021dual} that the posterior under this model bears a structure akin to \cref{eq:gp_pred}.
+As such, we project the dual parameters onto the inducing points giving sparse dual parameters,
 Using this sparse definition of the dual parameters, our sparse GP posterior takes the following form:
-\begin{align}\label{eq:dual_sparse_post}
 \begin{subequations} \label{eq:dual_sparse_post}
@@
 
+% As demonstrated in \citet{adam2021dual}, the posterior under this model bears a structure akin to \cref{eq:gp_pred}.
+% The authors of that paper exploit the dual parameters for approximate inference but write them using the natural parameterization, primarily because this form is more suitable for optimization through natural gradients.
+As such, we project the dual parameters onto the inducing points giving sparse dual parameters,
+% In order to link the dual parameters defined in \cref{eq:dual_param}, we write them in the sparse GP using the dual parameters,
+%
+\begin{equation} \textstyle
+  \valpha_{\vu}  =  \sum_{i=1}^N  \vkzi \, \hat{\alpha}_{i}
+  \quad \text{and} \quad
+  \MBeta_{\vu} =  \sum_{i=1}^N \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,
+\label{eq:dual_sparse}
+\end{equation}
+%
+where the sparse dual parameters are now a sum over \emph{all data points}, with $\valpha_{\vu} \in \R^{M}$ and $\MBeta_{\vu} \in \R^{M  \times M}$.
+
+Using this sparse definition of the dual parameters, our sparse GP posterior takes the following form:
+\begin{subequations} \label{eq:dual_sparse_post}
+\begin{align}
+   \myexpect_{q_{\vu}(\vf)}[f_i] &= \vkzs^{\T} \MKzz^{-1} \valpha_{\vu}, \\
+   %\quad \text{and} \quad
+   \textrm{Var}_{q_{\vu}(\vf)}[f_i]  &= k_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \MBeta_{\vu})^{-1} ]\vkzs, \nonumber
+\end{align}
+\end{subequations}
+where $\MKzz$ and $\vkzs$ are defined similarly to $\MKxx$ and $\vk_{\vx i}$ but over the inducing points $\{\vz_j\}_{i=1}^M$, $\vz \in \R^{D}$, instead of the full data set $\dataset$.
+The key quantities we need to make predictions from our sparse GP from the converged NN are $(\hat{\alpha}_i, \hat{\beta}_i)$ (\cref{eq:dual_param_laplace}) and a kernel function $\kappa$ (\cref{eq-laplace-approx-function-space}).
+Contrasting \cref{eq:dual_sparse_post} and \cref{eq:gp_pred}, we can see that the computational complexity went from $\mathcal{O}(N^3)$ to $\mathcal{O}(M^3)$, with $M \ll N$.
+Crucially, given the structure of our probabilistic model, our sparse dual parameters \cref{eq:dual_sparse} are a compact representation of the full model projected using the kernel.
+
 We highlight that \our differs from the GP subset method from \citet{immer2021improving}, which results in several advantages.
@@
 Note that tuning the prior precision in this way leads to different prior precisions being used at train and inference time.
-We highlihgt that technically this invalidates the Laplace/SFR methods as the NN weights are no longer the MAP weights.
+We highlighted that technically this invalidates the Laplace/SFR methods as the NN weights are no longer the MAP weights.
 Nevertheless, we report results when the prior precision $\delta$ is tuned (\cref{tbl:uci} right) and is not tuned (\cref{tbl:uci} left).

### 2023-09-04 workshops/icml-duality/main.tex
intro stuff

@@
 Secondly, how to update the weights of an already trained model with new batches of data without compromising the performance on past data?
-These questions become central when applied to sequential learning paradigms, such as continual learning \citep[CL,][]{parisi2019continual, de2021continual} and reinforcement learning  \citep[RL,][]{sutton2018reinforcement}.
-In CL, access to the previous data is lost, and then the challenge is retaining a compact representation of the problem to alleviate forgetting over the life-long learning horizon~\citep{mccloskey1989catastrophic}.
-Similarly, in RL, the model must adapt to environmental observations and can leverage predictive uncertainties for exploration.\looseness-1
+These questions become central when applied to sequential learning paradigms, such as continual learning \citep[CL,][]{parisi2019continual, de2021continual}, Bayesian optimization \citep[BO,][]{garnett_bayesoptbook_2022} and reinforcement learning  \citep[RL,][]{sutton2018reinforcement}.
+% In CL, access to the previous data is lost, and then the challenge is retaining a compact representation of the problem to alleviate forgetting over the life-long learning horizon~\citep{mccloskey1989catastrophic}.
+% Similarly, in RL, the model must adapt to environmental observations and can leverage predictive uncertainties for exploration.\looseness-1
 
@@
 GPs provide a widely used probabilistic toolkit with principled uncertainty estimates.
-They serve as a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} with theoretical guarantees on regret bounds \citep{srinivas2009gaussian}.
+% They serve as a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} with theoretical guarantees on regret bounds \citep{srinivas2009gaussian}.
 %Yet many problems lie in high dimensional input space; for example, images are where GPs cannot learn representations.
@@
 %Need for adaptive learning methods + failures with current methods
-Given an approximate inference technique, we demonstrate that the NN emits `dual' parameters which are the building blocks of a GP~\citep{csato2002sparse, adam2021dual, chang2023memory} .
-In contrast to previous work that utilizes subsets of training data \citep{immer2021scalable}, this parameterization allows capturing the contributions from {\em all} data points into a sparse representation, essential for predictive uncertainty.
-Crucially, the resulting GP directly predicts in the same space as the original trained NN, with the benefit of avoiding the complexity introduced by working in weight-space and the notorious cubic complexity of vanilla GPs.
+Given an approximate inference technique, we demonstrate that NN's emit `dual' parameters which are the building blocks of a GP~\citep{csato2002sparse, adam2021dual, chang2023memory}.
+In contrast to previous work that utilizes subsets of training data \citep{immer2021scalable}, our parameterization captures
+information from {\em all} data points in a sparse representation, essential for scaling to deep learning data sets.
+% predictive uncertainty.
+Importantly, the dual parameterization can be used to 1) sparsify the GP without requiring further optimization
+(e.g. variational inference), and 2) can incorporate new data without retraining (in a computationally efficient manner
+by conditioning on new data).
+% In contrast to previous work that utilizes subsets of training data \citep{immer2021scalable}, our parameterization captures information from {\em all} data points in a sparse representation, essential for predictive uncertainty.
+% Importantly, our method predicts in the same space as the original trained NN, with the benefit of avoiding the
+% complexity introduced by working in weight-space and the notorious cubic complexity of vanilla GPs.
 %\todo{Could make it clearer that the GP predicts in the output space while avoiding the NN parameter space}
 %, a feature not present in previous approaches, while avoiding the notorious cubic complexity of vanilla GPs.
-Through the dual parameter formulation, we establish a connection between the NN, full GPs, and a sparse approximation similar to sparse variational GPs~\citep{titsias2009variational}.
+Through the dual parameterization, we establish a connection between the NN, GPs, and a sparse GP approximations similar to sparse variational GPs~\citep{titsias2009variational}.
 We refer to our method as Sparse Function-space Representation (\our)---a sparse GP derived from a trained NN; see \cref{fig:teaser} for an example.

### 2023-09-04 workshops/icml-duality/main.tex
commit after getting paper into good state

@@
 \crefname{definition}{Def.}{Defs.}
-\crefname{table}{Table}{Tables}
+\crefname{table}{Tab.}{Tabs.}
 
@@
 We introduce a  NN $f_\mathbf{w}: \inputDomain \to \outputDomain$ with weights $\weights \in \R^{P}$ and use a likelihood function $p(\vy \mid f_\mathbf{w}(\vx))$
-to link the function values to the output $\vy$ (Gaussian for regresssion or Categorical for classification).
+to link the function values to the output $\vy$ (e.g. Categorical for classification).
 For notational conciseness we stick to scalar outputs $y_{i}$.
@@
 \textbf{Laplace-GGN}
-The Laplace approximation \citet{aa} builds upon this observation and approximates the weight-space posterior $p(\vw \mid \mathcal{D}) = \mathcal{N}(\vw^{*} , \bm\Sigma)$
+The Laplace approximation \citet{aa} builds upon this and approximates the weight posterior $p(\vw \mid \mathcal{D}) \approx q(\vw)= \mathcal{N}(\vw^{*} , \bm\Sigma)$
 around the MAP weights ($\vw^{*}$) by setting the covariance to the Hessian of the posterior,
@@
  \nabla^{2}_{\vw\vw} \log p(\vy \mid f_{\vw}(\vx)) \approx \Jac{\vw}{\vx}^{\top} \nabla_{\vf\vf}^{2}\log(\vy\mid\vf) \Jac{\vw}{\vx}.
+  \nonumber
 \end{align}
@@
 \textbf{Weight space GLM is equivalent to a GP}
-As Gaussian distributions remain tractable under linear transformations, a linear function in terms of parameters can be converted from the weight space to the function space \citep[see Ch.~2.1 in ][]{rasmussen2006gaussian}.
+As Gaussian distributions remain tractable under linear transformations, we can covert our model from
+weight space to function space \citep[see Ch.~2.1 in ][]{rasmussen2006gaussian}.
  % highlighted that the GGN approximation corresponds to a local linearization of the NN,
-As such (and show in \citet{immer2021improving}), the Bayesian GLM in \cref{eq-glm} has an equivalent GP formulation,
+As such (and shown in \citet{immer2021improving}), the Bayesian GLM in \cref{eq-glm} has an equivalent GP formulation,
 % \begin{align}
@@
 where the kernel $\kappa(\vx,\vx')=\frac{1}{\delta} \Jac{\weights^*}{\vx} \, \JacT{\weights^*}{\vx'}$ is the Neural Tangent Kernel \citep[NTK,][]{jacot2018neural},
-based on the Jacobian at the MAP $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{1 \times P}$.
+based on the Jacobian at the MAP $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{1 \times P}$
+and $f_i = f_\vw(\vx_i)$ denotes the function output at input $\vx_i$.
 The $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{N \times N}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where
@@
 % restrict our notatin to a single function output. The extension to multiple outputs is straightforward.
-
-The GP formulation from \citet{immer2021improving} (shown in \cref{eq-gp-pred-immer})
-requires inverting an $N\times N$ matrix which has complexity $O(N^3)$. This limits its applicability to large data sets, which are common in deep learning.
 
@@
 \textbf{Sparse Gaussian processes}
+The GP formulation from \citet{immer2021improving} (shown in \cref{eq-gp-pred-immer})
+requires inverting an $N\times N$ matrix which has complexity $O(N^3)$.
+This limits its applicability to large data sets, which are common in deep learning.
 Sparse GPs reduce the computational complexity by representing the GP as a low-rank approximation at a set of inducing
@@
 The approach by \citet{titsias2009variational} \citep[also used in the DTC approximation, see][]{quinonero2005unifying},
-defines the marginal predictive distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) \, q(\vu) \, \mathrm{d}\vu$.
-This give the sparse GP predictive posterior,
+defines the marginal predictive distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) \, q(\vu) \, \mathrm{d}\vu$ where
+the variational distribution is parameterized as $q(\vu) = \mathcal{N}\left(\vu \mid \vm, \MS \right)$ (as in \citet{titsias2009variational,hensman2013gaussian}).
+\todo{is this what titsias used or just hensman?}
+This gives the sparse GP predictive posterior,
 \begin{subequations}  \label{eq-svgp-pred}
@@
   \myexpect_{q_{\vu}(f_i)}[f_i] &= f_{\vw^{*}}(\vx_{i}) + \vk_{\vz i}^{\top}\MKzz^{-1}(\vm - f_{\vw^{*}}(\vz)), \\
-  \mathrm{Var}_{q_{\vu}(f_i)}[f_i] &= k_{ii} - \vk_{\vx i}^\top \MKzz^{-1}( \MKzz - \MS_{\vz\vz} )^{-1} \MKzz^{-1} \vk_{\vx i},  \nonumber
+  \mathrm{Var}_{q_{\vu}(f_i)}[f_i] &= k_{ii} - \vk_{\vx i}^\top \MKzz^{-1}( \MKzz - \MS )^{-1} \MKzz^{-1} \vk_{\vx i},  \nonumber
 \end{align}
 \end{subequations}
-where the variational distribution is parameterized as $q(\vu) = \mathcal{N}\left(\vu \mid \vm, \MS \right)$ (as in \citet{titsias2009variational,hensman2013gaussian}).
-\todo{is this what titsias used or just hensman?}
-To the best of our knowledge, there are no methods that convert NNs to sparse GPs.
-It is worth noting that the parameters of the variational posterior ($\vm$ and $\MS$) are usually obtained via variational inference.
-However, this requires further optimization and is non trivial in the NN setting.
+where $\MKzz$ and $\vkzs$ are defined similarly to $\MKxx$ and $\vk_{\vx i}$ but over the inducing points $\{\vz_j\}_{i=1}^M=\vz \in \R^{M \times D}$.%, instead of the full data set $\dataset$.
+% To the best of our knowledge, there are no methods that convert NNs to sparse GPs.
+It is worth noting that the parameters of the variational posterior ($\vm$ and $\MS$) are usually obtained via variational
+inference, which requires further optimization.% and is non trivial in the NN setting.
 
@@
 it also cannot be incorporate new data by conditioning on it.
-This is because it's posterior mean is the NN  $f_{\vw^*}(\vx)$
+This is because it's posterior mean is the NN  $f_{\vw^*}(\vx)$.
 Our method overcomes both of these limitations via a dual parameterization.
-Importantly, our dual parameterization enables us to sparsify it whilst making predictions directly from the GP.
+Importantly, our dual parameterization enables us to 1) sparsify the GP withput resorting to further optimisation, and 2)
+incorporate new data without retraining (in a computationally efficient manner).
+
+% on new data  make predictions directly from the GP.
 
@@
 In this section, we present our method, named \our, which converts a trained NN into a GP.
-\our is built upon a dual parameterization of the GP posterior, i.e. an alternative parameterization.
+\our is built upon a dual parameterization of the GP posterior.
 Early work by \citet{csato2002sparse} showed that Expectation Propagation gives rise to a dual parameterization.
@@
 %
-where $f_i = f_\vw(\vx_i)$ is the function output at input $\vx_i$,
-the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{N \times N}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $k_{ii} = \kappa(\vx_i, \vx_i)$.
+% where $f_i = f_\vw(\vx_i)$ is the function output at input $\vx_i$.
+% the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{N \times N}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $k_{ii} = \kappa(\vx_i, \vx_i)$.
 \cref{eq:gp_pred} states that the first two moments of the resultant posterior process (which may not be a GP), can be parameterized via the dual
@@
 %
-The relationships specified are valid for generic likelihoods and involve no approximations since the expectation is under the exact posterior, but given that the model can be expressed in a kernel formulation.
-\cref{eq:gp_pred} and \cref{eq:dual_param} highlight that the approximate inference technique, usually viewed as a posterior approximation, can be alternatively interpreted as an approximation of the expectation of gradients of loss/likelihoods.
+The relationships specified are valid for generic likelihoods and involve no approximations since the expectation is under the
+exact posterior, given that the model can be expressed in a kernel formulation.
+\cref{eq:gp_pred} and \cref{eq:dual_param} highlight that the approximate inference technique, usually viewed as a posterior approximation,
+can alternatively be interpreted as an approximation of the expectation of loss (likelihood) gradients.
 
@@
 \paragraph{Dual parameters from NN}
-Given that we use a Laplace approximation of the NN, we remove the expectation over the posterior \citep[see Ch.~3.4.1 in][for derivation]{rasmussen2006gaussian} and our dual parameters are given by,
+Given that we use a Laplace approximation of the NN, we remove the expectation over the posterior \citep[see Ch.3.4.1 in][for derivation]{rasmussen2006gaussian} and our dual parameters are given by,
 %
@@
 Substituting \cref{eq:dual_param_laplace} into \cref{eq:gp_pred}, we obtain our GP based on the converged NN.
-The problem with forming predictions using \cref{eq:gp_pred} is that they cost $O(N^3)$, which limits a full GP model to application on large data sets.
+The problem with forming predictions using \cref{eq:gp_pred} is that they cost $O(N^3)$, which limits its applicability to large data sets.
 
@@
 %
-Sparse GPs reduce the computational complexity by representing the GP as a low-rank approximation induced by a sparse set of input points \citep[see][for an early overview]{quinonero2005unifying}.
-Given that we have computed the dual parameters derived from our NN predictions and a kernel function, we could essentially employ any of these sparsification methods.
+% Sparse GPs reduce the computational complexity by representing the GP as a low-rank approximation induced by a sparse set of input points \citep[see][for an early overview]{quinonero2005unifying}.
+Given that we have computed the dual parameters derived from our NN predictions and a kernel function, we could essentially employ any sparsification method \citep{quinonero2005unifying}.
 In this work, we opt for the approach suggested by \citet{titsias2009variational} \citep[also used in the DTC approximation, see][]{quinonero2005unifying}, which defines the marginal predictive distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) \, q(\vu) \, \mathrm{d}\vu$.
-Given that we have $p(f_i \mid \vu)$ determined by our GP prior, the goal is to find a $q(\vu)$.
+% Given that we have $p(f_i \mid \vu)$ determined by our GP prior, the goal is to find a $q(\vu)$.
 Instead of parameterizing the sparse GP posterior as $q(\vu) = \mathcal{N}\left(\vu \mid \vm, \MS \right)$ (as in \citet{titsias2009variational,hensman2013gaussian})
@@
 \end{subequations}
-where $\MKzz$ and $\vkzs$ are defined similarly to $\MKxx$ and $\vk_{\vx i}$ but over the inducing points $\{\vz_j\}_{i=1}^M$, $\vz \in \R^{D}$, instead of the full data set $\dataset$.
-The key quantities we need to make predictions from our sparse GP from the converged NN are $(\hat{\alpha}_i, \hat{\beta}_i)$ (\cref{eq:dual_param_laplace}) and a kernel function $\kappa$ (\cref{eq-laplace-approx-function-space}).
-Contrasting \cref{eq:dual_sparse_post} and \cref{eq:gp_pred}, we can see that the computational complexity went from $\mathcal{O}(N^3)$ to $\mathcal{O}(M^3)$, with $M \ll N$.
-Crucially, given the structure of our probabilistic model, our sparse dual parameters \cref{eq:dual_sparse} are a compact representation of the full model projected using the kernel.
-
+% where the key quantities we need to make predictions from our sparse GP from the converged NN are $(\hat{\alpha}_i, \hat{\beta}_i)$ (\cref{eq:dual_param_laplace}) and a kernel function $\kappa$ (\cref{eq-laplace-approx-function-space}).
 % As demonstrated in \citet{adam2021dual}, the posterior under this model bears a structure akin to \cref{eq:gp_pred}.
 % The authors of that paper exploit the dual parameters for approximate inference but write them using the natural parameterization, primarily because this form is more suitable for optimization through natural gradients.
-As such, we project the dual parameters onto the inducing points giving sparse dual parameters,
+where the dual parameters are projected onto the inducing points to get our sparse dual parameters,
 % In order to link the dual parameters defined in \cref{eq:dual_param}, we write them in the sparse GP using the dual parameters,
@@
   \quad \text{and} \quad
-  \MBeta_{\vu} =  \sum_{i=1}^N \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,
+  \MBeta_{\vu} =  \sum_{i=1}^N \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} .
 \label{eq:dual_sparse}
@@
 %
-where the sparse dual parameters are now a sum over \emph{all data points}, with $\valpha_{\vu} \in \R^{M}$ and $\MBeta_{\vu} \in \R^{M  \times M}$.
-
-Using this sparse definition of the dual parameters, our sparse GP posterior takes the following form:
-\begin{subequations} \label{eq:dual_sparse_post}
-\begin{align}
-   \myexpect_{q_{\vu}(\vf)}[f_i] &= \vkzs^{\T} \MKzz^{-1} \valpha_{\vu}, \\
-   %\quad \text{and} \quad
-   \textrm{Var}_{q_{\vu}(\vf)}[f_i]  &= k_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \MBeta_{\vu})^{-1} ]\vkzs, \nonumber
-\end{align}
-\end{subequations}
-where $\MKzz$ and $\vkzs$ are defined similarly to $\MKxx$ and $\vk_{\vx i}$ but over the inducing points $\{\vz_j\}_{i=1}^M$, $\vz \in \R^{D}$, instead of the full data set $\dataset$.
+Note that the sparse dual parameters are now a sum over \emph{all data points}, with $\valpha_{\vu} \in \R^{M}$ and $\MBeta_{\vu} \in \R^{M  \times M}$.
+Contrasting \cref{eq:dual_sparse_post} and \cref{eq:gp_pred}, we can see that the computational complexity went from $\mathcal{O}(N^3)$ to $\mathcal{O}(M^3)$, with $M \ll N$.
+Crucially, given the structure of our probabilistic model, our sparse dual parameters \cref{eq:dual_sparse} are a compact representation of the full model projected using the kernel.
+
+% Using this sparse definition of the dual parameters, our sparse GP posterior takes the following form:
+% \begin{subequations} \label{eq:dual_sparse_post}
+% \begin{align}
+%    \myexpect_{q_{\vu}(\vf)}[f_i] &= \vkzs^{\T} \MKzz^{-1} \valpha_{\vu}, \\
+%    %\quad \text{and} \quad
+%    \textrm{Var}_{q_{\vu}(\vf)}[f_i]  &= k_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \MBeta_{\vu})^{-1} ]\vkzs, \nonumber
+% \end{align}
+% \end{subequations}
+% where $\MKzz$ and $\vkzs$ are defined similarly to $\MKxx$ and $\vk_{\vx i}$ but over the inducing points $\{\vz_j\}_{i=1}^M$, $\vz \in \R^{D}$, instead of the full data set $\dataset$.
 The key quantities we need to make predictions from our sparse GP from the converged NN are $(\hat{\alpha}_i, \hat{\beta}_i)$ (\cref{eq:dual_param_laplace}) and a kernel function $\kappa$ (\cref{eq-laplace-approx-function-space}).
@@
 The checkpoint with lowest NLPD was the NN MAP.
-Each experiment was run for $5$ seeds.
+Each experiment was run for $5$ seeds.\looseness-1
 
@@
 %
-In this paper, we introduced \our, a novel approach for representing NNs in sparse function space.
-It leverages a dual parameterization to obtain an efficient low-rank (sparse) approximation that captures information from the entire data set.
+In this paper, we introduced \our, a novel approach for representing NNs in function space.
+It leverages a dual parameterization to obtain a low-rank (sparse) approximation that captures information from the entire data set.
 We showcased \our's uncertainty quantification in UCI benchmark classification tasks (\cref{tbl:uci}).

### 2023-09-05 workshops/icml-duality/main.tex
updated text and fits on 4 arxiv pages

@@
 \begin{abstract}
-Deep neural networks (NNs) are known to lack uncertainty estimates, struggle to incorporate new data, and suffer from catastrophic forgetting.
-We present a method that mitigates these issues by converting NNs from weight-space to a low-rank (sparse) function-space representation, via a dual parameterization.
-Importantly, our sparse representation captures the joint distribution over the entire data set.
+Deep neural networks (NNs) are known to lack uncertainty estimates and struggle to incorporate new data.
+We present a method that mitigates these issues by converting NNs from weight space to function space, via a dual parameterization.
+Importantly, the dual parameterization enables us to formulate a sparse representation that captures information from the entire data set.
 This offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst retaining predictive performance.
@@
 Despite its success, gradient-based learning techniques exhibit limitations.
-Firstly, how can we efficiently quantify uncertainty without resorting to expensive and hard-to-interpret sampling in the model's weight-space?
+Firstly, how can we efficiently quantify uncertainty without resorting to expensive and hard-to-interpret sampling in the model's weight space?
 Secondly, how to update the weights of an already trained model with new batches of data without compromising the performance on past data?
-These questions become central when applied to sequential learning paradigms, such as continual learning \citep[CL,][]{parisi2019continual, de2021continual}, Bayesian optimization \citep[BO,][]{garnett_bayesoptbook_2022} and reinforcement learning  \citep[RL,][]{sutton2018reinforcement}.
+These questions become central when used for sequential learning,
+such as continual learning \citep[CL,][]{parisi2019continual, de2021continual}, Bayesian optimization \citep[BO,][]{garnett_bayesoptbook_2022} and reinforcement learning  \citep[RL,][]{sutton2018reinforcement}.
 % In CL, access to the previous data is lost, and then the challenge is retaining a compact representation of the problem to alleviate forgetting over the life-long learning horizon~\citep{mccloskey1989catastrophic}.
@@
 %Current state of affairs
-Recent techniques  \citep[\eg,][]{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable} apply a Laplace-GGN approximation to convert trained NNs into Bayesian neural networks (BNNs), that can provide uncertainty without sacrificing additional resources to training \citep{foong2019between}.
-Furthermore, the resultant weight-space posterior can be converted to the function-space as shown in \citet{khan2019approximate, immer2021improving}.
-The function-space representation allows for a principled mathematical approach for analyzing its behaviour \citep{cho2009kernel,meronen2020stationary}, performing probabilistic inference \citep{khan2019approximate}, and quantifying uncertainty in NNs \citep{foong2019between}.
-These methods rely on the linearization of the NN and the resultant neural tangent kernel \citep[NTK,][]{jacot2018neural}.
-The NN is characterized in function-space by its first two moment functions, a mean function and covariance function (or kernel)---defining a Gaussian process \citep[GP,][]{rasmussen2006gaussian}.
+Recent techniques  \citep[\eg,][]{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable} apply a Laplace
+generalized Gauss-Newton (GGN) approximation to convert trained NNs into Bayesian neural networks (BNNs), that can provide uncertainty without sacrificing additional resources to training \citep{foong2019between}.
+Furthermore, the resultant weight-space posterior can be converted to function space as shown in \citet{khan2019approximate, immer2021improving}.
+The function-space representation allows for a principled mathematical approach for analyzing its behaviour \citep{cho2009kernel,meronen2020stationary}, performing probabilistic inference \citep{khan2019approximate}, and quantifying uncertainty \citep{foong2019between}.
+These methods rely on linearizing the NN and the resultant neural tangent kernel \citep[NTK,][]{jacot2018neural}.
+The NN is characterized in function space by its first two moment functions, a mean function and covariance function (or kernel)---defining a Gaussian process \citep[GP,][]{rasmussen2006gaussian}.
 GPs provide a widely used probabilistic toolkit with principled uncertainty estimates.
@@
 %Need for adaptive learning methods + failures with current methods
-Given an approximate inference technique, we demonstrate that NN's emit `dual' parameters which are the building blocks of a GP~\citep{csato2002sparse, adam2021dual, chang2023memory}.
+Given an approximate inference technique, we demonstrate that NNs emit `dual' parameters which are the building blocks of a GP~\citep{csato2002sparse, adam2021dual, chang2023memory}.
 In contrast to previous work that utilizes subsets of training data \citep{immer2021scalable}, our parameterization captures
@@
 Importantly, the dual parameterization can be used to 1) sparsify the GP without requiring further optimization
-(e.g. variational inference), and 2) can incorporate new data without retraining (in a computationally efficient manner
+(e.g. variational inference) whilst capturing information from all data points, and 2) can incorporate new data without retraining (in a computationally efficient manner
 by conditioning on new data).
@@
 %, a feature not present in previous approaches, while avoiding the notorious cubic complexity of vanilla GPs.
-Through the dual parameterization, we establish a connection between the NN, GPs, and a sparse GP approximations similar to sparse variational GPs~\citep{titsias2009variational}.
+Through the dual parameterization, we establish a connection between the NN, GPs, and sparse approximations similar to sparse variational GPs~\citep{titsias2009variational}.
 We refer to our method as Sparse Function-space Representation (\our)---a sparse GP derived from a trained NN; see \cref{fig:teaser} for an example.
@@
 
-\textbf{Bayesian NNs}
+% \textbf{Bayesian NNs}
+\textbf{BNNs}
 In Bayesian deep learning, we place a prior over the weights $p(\vw)$ and aim to calculate the posterior over the weights given the data $p(\vw \mid \mathcal{D})$.
-Given the posterior over the weights $p(\vw \mid \mathcal{D})$, we can then make probabilistic predictions with,
+Given the weight posterior $p(\vw \mid \mathcal{D})$, we can make probabilistic predictions with,
 \begin{align} \label{eq-predictions}
@@
 \textbf{MAP}
-It is common to train the NN's weights $\vw$ to minimize the (regularized) empirical risk,
+It is common to train NN weights $\vw$ to minimize the (regularized) empirical risk,
 %
@@
 as the loss can be interpreted as a negative log likelihood $\ell(f_\weights(\vx_{i}), y_i) = -\log(p(y_{i} \mid f_\weights(\vx_{i}))$
-and the regularizer corresponds to a log prior over the weights $\delta\mathcal{R}(\weights) = \log p(\vw)$.
-For example, a weight decay regularizer $\mathcal{R}(\vw) = \frac{1}{2}\|\weights\|^{2}_2$ corresponds to a Gaussinan prior over the weights $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$ with
+and the regularizer corresponds to a log prior over the weights $\delta\mathcal{R}(\weights) = -\log p(\vw)$.
+For example, a weight decay regularizer $\mathcal{R}(\vw) = \frac{1}{2}\|\weights\|^{2}_2$ corresponds to a Gaussian prior over the weights $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$, with
 prior precision $\delta$.
@@
 
-\textbf{Laplace-GGN}
-The Laplace approximation \citet{aa} builds upon this and approximates the weight posterior $p(\vw \mid \mathcal{D}) \approx q(\vw)= \mathcal{N}(\vw^{*} , \bm\Sigma)$
+\textbf{Laplace approximation}
+The Laplace approximation \citet{mackayBayesian1992,daxberger2021laplace} builds upon this and approximates the weight posterior $p(\vw \mid \mathcal{D}) \approx q(\vw)= \mathcal{N}(\vw^{*} , \bm\Sigma)$
 around the MAP weights ($\vw^{*}$) by setting the covariance to the Hessian of the posterior,
@@
 As highlighted in \citet{immer2021improving}, computing this Hessian is often infeasible and in practice it is common to adopt the
-generalised Gauss-Newton (GGN) approximation,
+generalized Gauss-Newton (GGN) approximation,
 \begin{align}
@@
 \end{align}
+where the Jacobian is given by $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{1 \times P}$.
 % \textbf{Laplace-GGN converts BNN into GLM}
@@
 $f_{\weights^{*}}^{\text{lin}}(\vx) = f_{\weights}(\vx) + \Jac{\weights^{*}}{\vx}(\weights-\weights^{*})$.
-This suggests that predictions should be made with a generalised linear model (GLM), given by,
+This suggests that predictions should be made with a generalized linear model (GLM), given by,
 \begin{align} \label{eq-glm}
-  p_{\text{\sc GLM}}(\vy \mid \vx, \mathcal{D}) &= \E_{q(\vw)} \left[ p(\vy \mid f_{\vw^{*}}^{\text{lin}}(\vx))\right]. %\nonumber \\
+  p_{\text{\sc GLM}}(y_{i} \mid \vx, \mathcal{D}) &= \E_{q(\vw)} \left[ p(y_{i} \mid f_{\vw^{*}}^{\text{lin}}(\vx))\right]. %\nonumber \\
   % &\approx \frac{1}{S} \sum_{s} p(\vy \mid f_{\vw_{s}}^{\text{lin}}(\vx)), \quad \vw_{s} \sim q(\vw)
@@
 
-\textbf{Weight space GLM is equivalent to a GP}
-As Gaussian distributions remain tractable under linear transformations, we can covert our model from
+% \textbf{Weight space GLM is equivalent to a GP}
+\textbf{Gaussian processes}
+As Gaussian distributions remain tractable under linear transformations, we can covert the linear model from
 weight space to function space \citep[see Ch.~2.1 in ][]{rasmussen2006gaussian}.
@@
 % where the GP posterior is given by,
-\begin{subequations}  \label{eq-gp-pred-immer}
-\begin{align}
-  p_{\text{\sc GP}}(\vy \mid \vx, \mathcal{D}) &= \E_{q(\vf)} \left[ p(\vy \mid \vf)\right] \\ %\nonumber \\
-  \myexpect_{p(f_i \mid\vy)}[f_i] &= f_{\vw^{*}}(\vx_{i}), \\
-  \mathrm{Var}_{p(f_i \mid \vy)}[f_i] &= k_{ii} - \vk_{\vx i}^\top ( \MKxx + \bm\Lambda^{-1})^{-1} \vk_{\vx i},
+% \begin{subequations}  \label{eq-gp-pred-immer}
+% \begin{align}
+%   p_{\text{\sc GP}}(\vy \mid \vx, \mathcal{D}) &= \E_{q(\vf)} \left[ p(\vy \mid \vf)\right] \\ %\nonumber \\
+%   \myexpect_{p(f_i \mid\vy)}[f_i] &= f_{\vw^{*}}(\vx_{i}), \\
+%   \mathrm{Var}_{p(f_i \mid \vy)}[f_i] &= k_{ii} - \vk_{\vx i}^\top ( \MKxx + \bm\Lambda^{-1})^{-1} \vk_{\vx i},
+% \end{align}
+% \end{subequations}
+\begin{align} \label{eq-gp-pred-immer}
+  p_{\text{\sc GP}}(y_{i} \mid \vx, \mathcal{D}) &= \E_{q(f_{i})} \left[ p(y_{i} \mid f_{i} )\right]
 \end{align}
-\end{subequations}
-where the kernel $\kappa(\vx,\vx')=\frac{1}{\delta} \Jac{\weights^*}{\vx} \, \JacT{\weights^*}{\vx'}$ is the Neural Tangent Kernel \citep[NTK,][]{jacot2018neural},
-based on the Jacobian at the MAP $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{1 \times P}$
-and $f_i = f_\vw(\vx_i)$ denotes the function output at input $\vx_i$.
+where $q(f_{i}) = \mathcal{N} \left( f_{\vw^{*}}(\vx_{i}), \sigma^{2}_{i} \right)$ is the GP's predictive posterior with variance,
+% where $q(\vf) = \mathcal{N} \left( \myexpect_{p(f_i \mid\vy)}[f_i], \mathrm{Var}_{p(f_i \mid \vy)}[f_i] \right)$ is the predictive GP posterior given by,
+\begin{align} \label{eq-gp-pred-immer-gp}
+  % \myexpect_{p(f_i \mid\vy)}[f_i] &= f_{\vw^{*}}(\vx_{i}), \\
+  \sigma^{2}_{i} &= k_{ii} - \vk_{\vx i}^\top ( \MKxx + \bm\Lambda^{-1})^{-1} \vk_{\vx i},
+\end{align}
+where the kernel $\kappa(\vx,\vx')=\frac{1}{\delta} \Jac{\weights^*}{\vx} \, \JacT{\weights^*}{\vx'}$ is the Neural Tangent Kernel \citep[NTK,][]{jacot2018neural}
+and $f_i = f_\vw(\vx_i)$ is the function output at $\vx_i$.
 The $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{N \times N}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where
@@
 the variational distribution is parameterized as $q(\vu) = \mathcal{N}\left(\vu \mid \vm, \MS \right)$ (as in \citet{titsias2009variational,hensman2013gaussian}).
-\todo{is this what titsias used or just hensman?}
 This gives the sparse GP predictive posterior,
@@
   \myexpect_{q_{\vu}(f_i)}[f_i] &= f_{\vw^{*}}(\vx_{i}) + \vk_{\vz i}^{\top}\MKzz^{-1}(\vm - f_{\vw^{*}}(\vz)), \\
-  \mathrm{Var}_{q_{\vu}(f_i)}[f_i] &= k_{ii} - \vk_{\vx i}^\top \MKzz^{-1}( \MKzz - \MS )^{-1} \MKzz^{-1} \vk_{\vx i},  \nonumber
+  \mathrm{Var}_{q_{\vu}(f_i)}[f_i] &= k_{ii} - \vk_{\vx i}^\top ( \MKzz -  \MKzz^{-1}\MS  \MKzz^{-1}))^{-1} \vk_{\vx i},  \nonumber
 \end{align}
@@
 
-Not only does the GP formulation from \citet{immer2021improving} (shown in \cref{eq-gp-pred-immer}) struggle to scale to large data sets but
-it also cannot be incorporate new data by conditioning on it.
+Not only does the GP formulation from \citet{immer2021improving} (shown in \cref{eq-gp-pred-immer}) struggle to scale to large
+data sets but it also cannot incorporate new data by conditioning on it.
 This is because it's posterior mean is the NN  $f_{\vw^*}(\vx)$.
 Our method overcomes both of these limitations via a dual parameterization.
-Importantly, our dual parameterization enables us to 1) sparsify the GP withput resorting to further optimisation, and 2)
-incorporate new data without retraining (in a computationally efficient manner).
+Importantly, our dual parameterization enables us to 1) sparsify the GP without further optimization, and 2)
+incorporate new data without retraining.\looseness-1 % (in a computationally efficient manner).
 
@@
 %
-The relationships specified are valid for generic likelihoods and involve no approximations since the expectation is under the
+\cref{eq:dual_param} holds for generic likelihoods and involves no approximations since the expectation is under the
 exact posterior, given that the model can be expressed in a kernel formulation.
@@
 %
-Substituting \cref{eq:dual_param_laplace} into \cref{eq:gp_pred}, we obtain our GP based on the converged NN.
-The problem with forming predictions using \cref{eq:gp_pred} is that they cost $O(N^3)$, which limits its applicability to large data sets.
+Substituting \cref{eq:dual_param_laplace} into \cref{eq:gp_pred}, we obtain our GP based on the trained NN.
+Making predictions with \cref{eq:gp_pred} costs $O(N^3)$, which limits its applicability on large data sets.
 
@@
 \begin{figure*}[t]
-  \centering\scriptsize
+  % \centering\scriptsize
+  \centering\small
   % \setlength{\figurewidth}{.18\textwidth}
@@
   \setlength{\figureheight}{\figurewidth}
-  \pgfplotsset{axis on top,scale only axis,y tick label style={rotate=90}, x tick label style={font=\footnotesize},y tick label style={font=\footnotesize},title style={yshift=-4pt,font=\large}, y label style={font=\large},x label style={font=\large},grid=major, width=\figurewidth, height=\figureheight}
+  \pgfplotsset{axis on top,scale only axis,y tick label style={rotate=90}, x tick label style={font=\Large},y tick label style={font=\LARGE},title style={yshift=-4pt,font=\LARGE}, y label style={font=\LARGE},x label style={font=\LARGE},grid=major, width=\figurewidth, height=\figureheight}
   \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
-  \pgfplotsset{xlabel={$M$ as \% of $N$},ylabel style={yshift=-12pt}}
+  \pgfplotsset{xlabel={$M$ as \% of $N$},ylabel style={yshift=-5pt},xlabel style={yshift=-5pt}}
   %
@@
 Given that we have computed the dual parameters derived from our NN predictions and a kernel function, we could essentially employ any sparsification method \citep{quinonero2005unifying}.
-In this work, we opt for the approach suggested by \citet{titsias2009variational} \citep[also used in the DTC approximation, see][]{quinonero2005unifying}, which defines the marginal predictive distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) \, q(\vu) \, \mathrm{d}\vu$.
+In this work, we opt for the approach suggested by \citet{titsias2009variational,hensman2013gaussian},
+which is shown in \cref{eq-svgp-pred}.
+% which defines the marginal predictive distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) \, q(\vu) \, \mathrm{d}\vu$.
 % Given that we have $p(f_i \mid \vu)$ determined by our GP prior, the goal is to find a $q(\vu)$.
-Instead of parameterizing the sparse GP posterior as $q(\vu) = \mathcal{N}\left(\vu \mid \vm, \MS \right)$ (as in \citet{titsias2009variational,hensman2013gaussian})
+However, instead of parameterizing the variational distribution as $q(\vu) = \mathcal{N}\left(\vu \mid \vm, \MS \right)$,
 we follow insights from \citet{adam2021dual} that the posterior under this model bears a structure akin to \cref{eq:gp_pred}.
-As such, we project the dual parameters onto the inducing points giving sparse dual parameters,
-Using this sparse definition of the dual parameters, our sparse GP posterior takes the following form:
+As such, we project the dual parameters onto the inducing points giving sparse dual parameters.
+Using this sparse definition of the dual parameters, our sparse GP posterior is given by,
+%
 \begin{subequations} \label{eq:dual_sparse_post}
@@
 \end{subequations}
+with sparse dual parameters,
 % where the key quantities we need to make predictions from our sparse GP from the converged NN are $(\hat{\alpha}_i, \hat{\beta}_i)$ (\cref{eq:dual_param_laplace}) and a kernel function $\kappa$ (\cref{eq-laplace-approx-function-space}).
@@
 % The authors of that paper exploit the dual parameters for approximate inference but write them using the natural parameterization, primarily because this form is more suitable for optimization through natural gradients.
-where the dual parameters are projected onto the inducing points to get our sparse dual parameters,
+% where the dual parameters are projected onto the inducing points to get our sparse dual parameters,
+% where the dual parameters are projected onto the inducing points to get our sparse dual parameters,
 % In order to link the dual parameters defined in \cref{eq:dual_param}, we write them in the sparse GP using the dual parameters,
@@
 We evaluate \our on eight UCI~\citep{UCI} binary and multi-class classification tasks.
-Following \citet{immer2021improving}, we used a two-layer MLP with width 50 and tanh activation functions and we used half of the test data set as a validation data set.
+% Following \citet{immer2021improving}, we used a two-layer MLP with width 50 and tanh activation functions and we used half of the test data set as a validation data set.
+Following \citet{immer2021improving}, we used a two-layer MLP with width 50, tanh activation functions and a
+$70\%\ (\text{train}):15\%\ (\text{validation}) :15\%\ (\text{test})$ data split.
 We trained the NN using Adam \cite{adam} with a learning rate of $10^{-4}$ and a batch size of $128$.
@@
 
-We first compare \our to alternative posthoc Bayesian deep learning approaches.
-In particular, we compare to the Laplace approximation when making predictions with 1) the nonlinear NN (BNN) and 2) the generalised linear model (GLM).
+% We first compare \our to other posthoc Bayesian deep learning approaches.
+% In particular, we compare to the Laplace approximation when making predictions with 1) the nonlinear NN (BNN) and 2) the generalised linear model (GLM).
+We first compare \our to the Laplace approximation when making predictions with 1) the nonlinear NN (BNN) and 2) the generalised linear model (GLM) in \cref{eq-glm}.
 We use the Laplace PyTorch library \citep{daxberger2021laplace} with the full Hessian.%, i.e. we do not resort to the diagonal or KFAC approximations.
@@
 That is, find a prior precision $\delta_{\text{tune}}$ which has a better NLPD on the validation set than the $\delta$ used to train the NN.
-Note that tuning the prior precision in this way leads to different prior precisions being used at train and inference time.
+Note that this leads to different prior precisions being used for training and inference.
 We highlighted that technically this invalidates the Laplace/SFR methods as the NN weights are no longer the MAP weights.
@@
 %
-In this paper, we introduced \our, a novel approach for representing NNs in function space.
+We introduced \our, a novel approach for representing NNs in function space.
 It leverages a dual parameterization to obtain a low-rank (sparse) approximation that captures information from the entire data set.
 We showcased \our's uncertainty quantification in UCI benchmark classification tasks (\cref{tbl:uci}).
-Interestingly, \our achieves good predictive performance without tuning the prior precision $\delta$ after performing inference.
-This contrasts the Laplace approximation (BNN/GLM) and we believe this stays more true to Bayesian inference.% (as tuning the prior precision is equivalent to altering the prior after calculating the posterior).
+Unlike the Laplace approximation, \our achieves good predictive performance without tuning the prior precision $\delta$.
+This is interesting and we believe it stays more true to Bayesian inference.% (as tuning the prior precision is equivalent to altering the prior after calculating the posterior).
+% Interestingly, \our achieves good predictive performance without tuning the prior precision $\delta$ after performing inference.
+% This contrasts the Laplace approximation (BNN/GLM) and we believe this stays more true to Bayesian inference.% (as tuning the prior precision is equivalent to altering the prior after calculating the posterior).
 % providing a compact representation suitable for continual learning.
@@
 % Discussion points
-In practical terms, \our serves a role similar to a sparse GP. However, unlike a conventional GP, it does not provide a straightforward method for specifying the prior covariance function.
+In practical terms, \our serves a role similar to a sparse GP. However, unlike a conventional GP, it does not provide a straightforward method for specifying the prior.% covariance function.
 This limitation can be addressed indirectly: the architecture of the NN and the choice of activation functions can be used to implicitly specify the prior assumptions.
 It is important to note that \our linearizes the NN around the MAP weights $\weights^{*}$, resulting in the function-space prior
-(and consequently the posterior) being a locally linear approximation of the NN.\looseness-1
+(and posterior) being a locally linear approximation of the NN.\looseness-1
 

### 2023-09-05 workshops/icml-duality/main.tex
fixed typos

@@
 Importantly, the dual parameterization can be used to 1) sparsify the GP without requiring further optimization
-(e.g. variational inference) whilst capturing information from all data points, and 2) can incorporate new data without retraining (in a computationally efficient manner
+(e.g. variational inference) whilst capturing information from all data points, and 2) incorporate new data without retraining (in a computationally efficient manner
 by conditioning on new data).
@@
 to link the function values to the output $\vy$ (e.g. Categorical for classification).
-For notational conciseness we stick to scalar outputs $y_{i}$.
+For notational conciseness, we stick to scalar outputs $y_{i}$.
 
@@
 This objective corresponds to the log joint distribution $\mathcal{L}(\mathcal{D},\vw)=p(\mathcal{D}, \vw)$
-as the loss can be interpreted as a negative log likelihood $\ell(f_\weights(\vx_{i}), y_i) = -\log(p(y_{i} \mid f_\weights(\vx_{i}))$
+as the loss can be interpreted as a negative log-likelihood $\ell(f_\weights(\vx_{i}), y_i) = -\log(p(y_{i} \mid f_\weights(\vx_{i}))$
 and the regularizer corresponds to a log prior over the weights $\delta\mathcal{R}(\weights) = -\log p(\vw)$.
@@
 \textbf{Gaussian processes}
-As Gaussian distributions remain tractable under linear transformations, we can covert the linear model from
+As Gaussian distributions remain tractable under linear transformations, we can convert the linear model from
 weight space to function space \citep[see Ch.~2.1 in ][]{rasmussen2006gaussian}.
@@
 data sets but it also cannot incorporate new data by conditioning on it.
-This is because it's posterior mean is the NN  $f_{\vw^*}(\vx)$.
+This is because its posterior mean is the NN  $f_{\vw^*}(\vx)$.
 Our method overcomes both of these limitations via a dual parameterization.
@@
 Our \our converges fast for all cases showing clear benefits of its ability to summarize all the data onto a sparse set of inducing points.
-The number of inducing points $M$ are specified as a percent of the number of training data $N$.}
+The number of inducing points $M$ are specified as a percentage of the number of training data $N$.}
   \label{fig:uci}
@@
 First, \our leverages a dual parameterization to construct a sparse GP, which captures information from the entire data set.
-In contrast, \citet{immer2021improving} utilise a subset of the data points which ignores information from the rest of the data set.
+In contrast, \citet{immer2021improving} utilize a subset of the data points which ignores information from the rest of the data set.
 % It is also worth noting that our sparsification via dual parameters does not require any further optimization, we do not need to retrain a separate sparse GP.
@@
 Training was stopped when the validation NLPD stopped decreasing after 1000 steps.
-The checkpoint with lowest NLPD was the NN MAP.
+The checkpoint with the lowest NLPD was the NN MAP.
 Each experiment was run for $5$ seeds.\looseness-1
@@
 That is, find a prior precision $\delta_{\text{tune}}$ which has a better NLPD on the validation set than the $\delta$ used to train the NN.
-Note that this leads to different prior precisions being used for training and inference.
+Note that this leads to a different prior precision being used for training and inference.
 We highlighted that technically this invalidates the Laplace/SFR methods as the NN weights are no longer the MAP weights.

### 2023-09-05 workshops/icml-duality/main.tex
Polishing. Spacincing, typos, etc.

@@
 \crefname{definition}{Def.}{Defs.}
-\crefname{table}{Tab.}{Tabs.}
+%\crefname{table}{Tab.}{Tabs.} % Let's leave table as is
 
@@
 % predictive uncertainty.
-Importantly, the dual parameterization can be used to 1) sparsify the GP without requiring further optimization
-(e.g. variational inference) whilst capturing information from all data points, and 2) incorporate new data without retraining (in a computationally efficient manner
+Importantly, the dual parameterization can be used to {\em (i)}~sparsify the GP without requiring further optimization
+(\eg, variational inference) whilst capturing information from all data points, and {\em (ii)}~incorporate new data without retraining (in a computationally efficient manner
 by conditioning on new data).
@@
 
-We consider supervised learning with inputs $\vx_i \in \inputDomain$ and outputs $\vy_i \in \outputDomain$ (e.g. regression) or $\vy_{i} \in \{0,1\}^{C}$ (e.g. classification),
+We consider supervised learning with inputs $\vx_i \in \inputDomain$ and outputs $\vy_i \in \outputDomain$ (\eg, regression) or $\vy_{i} \in \{0,1\}^{C}$ (\eg, classification),
 giving a data set $\dataset = \{(\vx_{i} , \vy_{i})\}_{i=1}^{N}$.
 We introduce a  NN $f_\mathbf{w}: \inputDomain \to \outputDomain$ with weights $\weights \in \R^{P}$ and use a likelihood function $p(\vy \mid f_\mathbf{w}(\vx))$
-to link the function values to the output $\vy$ (e.g. Categorical for classification).
+to link the function values to the output $\vy$ (\eg, categorical for classification).
 For notational conciseness, we stick to scalar outputs $y_{i}$.
@@
 In Bayesian deep learning, we place a prior over the weights $p(\vw)$ and aim to calculate the posterior over the weights given the data $p(\vw \mid \mathcal{D})$.
-Given the weight posterior $p(\vw \mid \mathcal{D})$, we can make probabilistic predictions with,
+Given the weight posterior $p(\vw \mid \mathcal{D})$, we can make probabilistic predictions with
 \begin{align} \label{eq-predictions}
-  p_{\text{\sc BNN}}(y \mid \vx, \mathcal{D}) = \E_{p(\vw \mid \mathcal{D})} \left[ p(y \mid f_{\vw}(\vx)) \right]
+  p_{\text{\sc BNN}}(y \mid \vx, \mathcal{D}) = \E_{p(\vw \mid \mathcal{D})} \left[ p(y \mid f_{\vw}(\vx)) \right].
 \end{align}
@@
 $f_{\weights^{*}}^{\text{lin}}(\vx) = f_{\weights}(\vx) + \Jac{\weights^{*}}{\vx}(\weights-\weights^{*})$.
-This suggests that predictions should be made with a generalized linear model (GLM), given by,
+This suggests that predictions should be made with a generalized linear model (GLM), given by
 \begin{align} \label{eq-glm}
@@
 \begin{align} \label{eq-gp-pred-immer}
-  p_{\text{\sc GP}}(y_{i} \mid \vx, \mathcal{D}) &= \E_{q(f_{i})} \left[ p(y_{i} \mid f_{i} )\right]
+  p_{\text{\sc GP}}(y_{i} \mid \vx, \mathcal{D}) &= \E_{q(f_{i})} \left[ p(y_{i} \mid f_{i} )\right],
 \end{align}
@@
 Our method overcomes both of these limitations via a dual parameterization.
-Importantly, our dual parameterization enables us to 1) sparsify the GP without further optimization, and 2)
-incorporate new data without retraining.\looseness-1 % (in a computationally efficient manner).
+Importantly, our dual parameterization enables us to {\em (i)}~sparsify the GP without further optimization, and {\em (ii)}~incorporate new data without retraining.\looseness-1 % (in a computationally efficient manner).
 
@@
   \myexpect_{p(f_i \mid\vy)}[f_i] &= \vk_{\vx i}^\top \valpha, \\
-  \mathrm{Var}_{p(f_i \mid \vy)}[f_i] &= k_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},  \nonumber
+  \mathrm{Var}_{p(f_i \mid \vy)}[f_i] &= k_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i}.  \nonumber
 \end{align}
@@
 % which are the vectors
-defined as, \looseness-1
+defined as \looseness-1
 %
@@
 \paragraph{Dual parameters from NN}
-Given that we use a Laplace approximation of the NN, we remove the expectation over the posterior \citep[see Ch.3.4.1 in][for derivation]{rasmussen2006gaussian} and our dual parameters are given by,
+Given that we use a Laplace approximation of the NN, we remove the expectation over the posterior \citep[see Ch.~3.4.1 in][for derivation]{rasmussen2006gaussian} and our dual parameters are given by
 %
@@
   \setlength{\figureheight}{\figurewidth}
-  \pgfplotsset{axis on top,scale only axis,y tick label style={rotate=90}, x tick label style={font=\Large},y tick label style={font=\LARGE},title style={yshift=-4pt,font=\LARGE}, y label style={font=\LARGE},x label style={font=\LARGE},grid=major, width=\figurewidth, height=\figureheight}
+  \pgfplotsset{axis on top,scale only axis,y tick label style={rotate=90}, x tick label style={font=\Large},y tick label style={font=\Large},title style={yshift=-4pt,font=\LARGE}, y label style={font=\Large},x label style={font=\LARGE},grid=major, width=\figurewidth, height=\figureheight}
   \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
@@
   %
-  \begin{minipage}[t]{.155\textwidth}
+  \begin{minipage}[t]{.175\textwidth}
     \raggedleft
@@
 As such, we project the dual parameters onto the inducing points giving sparse dual parameters.
-Using this sparse definition of the dual parameters, our sparse GP posterior is given by,
+Using this sparse definition of the dual parameters, our sparse GP posterior is given by
 %
@@
 Second, \our makes predictions with the GP mean, whereas \citet{immer2021improving} center predictions around NN predictions $f_{\vw^*}(\cdot)$.
-As such, \our can incorporate new data without retraining (i.e. condition on new data) whilst the GP subset method cannot.
+As such, \our can incorporate new data without retraining (\ie, condition on new data) whilst the GP subset method cannot.
 
 To the best of our knowledge, we are the first to formulate a dual GP from a NN.
-Our dual parameterization has two main benefits: 1) it enables us to construct a sparse GP without requiring us to perform further optimization, and 2)
-it enables us to incorporate new data without retraining (i.e. condition on new data) using \cref{eq:dual_sparse}.
+Our dual parameterization has two main benefits: {\em (i)}~it enables us to construct a sparse GP without requiring us to perform further optimization, and {\em (ii)}~it enables us to incorporate new data without retraining (\ie, condition on new data) using \cref{eq:dual_sparse}.
 
@@
 % In particular, we compare to the Laplace approximation when making predictions with 1) the nonlinear NN (BNN) and 2) the generalised linear model (GLM).
-We first compare \our to the Laplace approximation when making predictions with 1) the nonlinear NN (BNN) and 2) the generalised linear model (GLM) in \cref{eq-glm}.
-We use the Laplace PyTorch library \citep{daxberger2021laplace} with the full Hessian.%, i.e. we do not resort to the diagonal or KFAC approximations.
+We first compare \our to the Laplace approximation when making predictions with {\em (i)}~the nonlinear NN (BNN) and {\em (ii)}~the generalised linear model (GLM) in \cref{eq-glm}.
+We use the Laplace PyTorch library \citep{daxberger2021laplace} with the full Hessian. %, i.e. we do not resort to the diagonal or KFAC approximations.
 It is common practice to tune the prior precision $\delta$ after training the NN.

### 2023-09-05 experiments/sl/tables/workshop_uci_table.py
fixed buy in paired t-tset bolding

@@ -180,13 +180,17 @@ NUM_CLASSES = {
 
 
 def bold_if_significant(row):
-    print(f"ROW ROW: {row}")
-    if row["pvalue"] > 0.05:
-        mean = "\mathbf{" + f"{row['mean']:.2f}" + "}"
-        std = "\mathbf{" + f"{(row['std']):.2f}" + "}"
-    else:
+    # print(f"ROW ROW: {row}")
+    print(f"Model: {row['model']}")
+    print(f"tstatistic {row['tstatistic']}")
+    print(f"pvalue{row['pvalue']}")
+    if row["pvalue"] < 0.05:
+        # reject the null hypothesis of identical avg NLPDs
         mean = f"{row['mean']:.2f}"
         std = f"{(row['std']):.2f}"
+    else:
+        mean = "\mathbf{" + f"{row['mean']:.2f}" + "}"
+        std = "\mathbf{" + f"{(row['std']):.2f}" + "}"
     return "\\val{" + mean + "}{" + std + "}"
 
 
@@ -258,9 +262,8 @@ def make_uci_table():
 
     # Calculate pvalues for bolding
     df_with_stats["pvalue"] = np.nan
-    groups = []
+    df_with_stats["tstatistic"] = np.nan
     best_nlpd = np.inf
-    pvalues = []
     for dataset_name in DATASETS.keys():
         df_dataset = df_with_stats[df_with_stats["dataset"] == dataset_name]
         # Find the best NLPD to use as base for paired t test
@@ -273,26 +276,28 @@ def make_uci_table():
             if nlpd < best_nlpd:
                 best_nlpd = nlpd
                 best_model_name = model_name
-        print("groups")
-        print(groups)
         print("best_model_name")
         print(best_model_name)
 
-        group1 = df[df["dataset"] == dataset_name]
-        group1 = group1[group1["model"] == best_model_name]
-        print("group1")
-        print(group1)
+        group2 = df[df["dataset"] == dataset_name]
+        group2 = group2[group2["model"] == best_model_name]
+        print("group2")
+        print(group2)
         for model_name in COLUMNS_TITLES:
-            group2 = df[df["dataset"] == dataset_name]
-            group2 = group2[group2["model"] == model_name]
-            print("group2")
-            print(group2)
-            if model_name in best_model_name:
+            group1 = df[df["dataset"] == dataset_name]
+            group1 = group1[group1["model"] == model_name]
+            print("group1")
+            print(group1)
+            if model_name == best_model_name:
[…]

### 2023-09-05 workshops/icml-duality/main.tex
shortened to fit in 4 pages on arxiv
retaining to maintaining

@@
 Importantly, the dual parameterization enables us to formulate a sparse representation that captures information from the entire data set.
-This offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst retaining predictive performance.
+This offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst maintaining predictive performance.
 We provide proof-of-concept demonstrations with the proposed approach for quantifying uncertainty in supervised learning on UCI benchmark tasks.
@@
 When tuning the prior precision $\delta$, \our matches the performance of the Laplace methods (BNN/GLM).
-Interestingly, \our also  performs well without tuning the prior precision $\delta$, unlike the Laplace methods (BNN/GLM).
+Interestingly, \our also  performs well without tuning the prior precision $\delta$, unlike the Laplace methods.
 

### 2023-09-05 workshops/icml-duality/main.tex
submitted to arxiv

@@
 Importantly, the dual parameterization can be used to {\em (i)}~sparsify the GP without requiring further optimization
-(\eg, variational inference) whilst capturing information from all data points, and {\em (ii)}~incorporate new data without retraining (in a computationally efficient manner
-by conditioning on new data).
+(\eg, variational inference) whilst capturing information from all data points, and {\em (ii)}~incorporate new data without retraining by conditioning on new data, in a computationally efficient manner.
 % In contrast to previous work that utilizes subsets of training data \citep{immer2021scalable}, our parameterization captures information from {\em all} data points in a sparse representation, essential for predictive uncertainty.
@@
 %, a feature not present in previous approaches, while avoiding the notorious cubic complexity of vanilla GPs.
-Through the dual parameterization, we establish a connection between the NN, GPs, and sparse approximations similar to sparse variational GPs~\citep{titsias2009variational}.
+The dual parameterization establishes a connection between NNs, GPs, and sparse approximations similar to sparse variational GPs~\citep{titsias2009variational}.
 We refer to our method as Sparse Function-space Representation (\our)---a sparse GP derived from a trained NN; see \cref{fig:teaser} for an example.
@@
 giving a data set $\dataset = \{(\vx_{i} , \vy_{i})\}_{i=1}^{N}$.
-We introduce a  NN $f_\mathbf{w}: \inputDomain \to \outputDomain$ with weights $\weights \in \R^{P}$ and use a likelihood function $p(\vy \mid f_\mathbf{w}(\vx))$
-to link the function values to the output $\vy$ (\eg, categorical for classification).
-For notational conciseness, we stick to scalar outputs $y_{i}$.
+We introduce a  NN $f_\mathbf{w}: \inputDomain \to \outputDomain$ with weights $\weights \in \R^{P}$ and use a likelihood function $p(\vy_{i} \mid f_\mathbf{w}(\vx_{i}))$
+to link the function values to the output $\vy_{i}$ (\eg, categorical for classification).
+For notational conciseness, we stick to scalar outputs $y_{i}$. We denote the sets of all inputs
+as $\MX = \{\vx_{i}\}_{i=1}^{N}$ and the set of all outputs $\vy = \{y_{i}\}_{i=1}^{N}$.
 
@@
 \begin{align} \label{eq-predictions}
-  p_{\text{\sc BNN}}(y \mid \vx, \mathcal{D}) = \E_{p(\vw \mid \mathcal{D})} \left[ p(y \mid f_{\vw}(\vx)) \right].
+  p_{\text{\sc BNN}}(y_{i} \mid \vx_{i}, \mathcal{D}) = \E_{p(\vw \mid \mathcal{D})} \left[ p(y_{i} \mid f_{\vw}(\vx_{i})) \right].
 \end{align}
-The posterior ${p(\vw \mid \dataset) \propto p(\vy \mid f_{\weights}(\vx)) \, p(\weights)}$ is generally not available in closed form
+The posterior ${p(\vw \mid \dataset) \propto p(\vy \mid f_{\weights}(\MX)) \, p(\weights)}$ is generally not available in closed form
 so we resort to approximations.
-% Sampling methods that characterize the posterior with a finite set of samples in weight-space are general-purpose, but computationally heavy and impractical for downstream applications.
+% Sampling methods that characterize the posterior with a finite set of samples in weight-space are general-purpose, but computationally heavy andimpractical for downstream applications.
 % In this paper, we build on the Laplace approximation
@@
 %
-This objective corresponds to the log joint distribution $\mathcal{L}(\mathcal{D},\vw)=p(\mathcal{D}, \vw)$
+This objective corresponds to the log-joint distribution $\mathcal{L}(\mathcal{D},\vw)=p(\mathcal{D}, \vw)$
 as the loss can be interpreted as a negative log-likelihood $\ell(f_\weights(\vx_{i}), y_i) = -\log(p(y_{i} \mid f_\weights(\vx_{i}))$
@@
 \end{align}
-Computing \cref{eq:laplace-cov} requires calculating the Hessian of the log-likelihood $\nabla^{2}_{\vw\vw} \log p(\vy \mid f_{\vw}(\vx))$ from \cref{eq-empirical-risk}.
+Computing \cref{eq:laplace-cov} requires calculating the Hessian of the log-likelihood $\nabla^{2}_{\vw\vw} \log p(\vy \mid f_{\vw}(\MX))$ from \cref{eq-empirical-risk}.
 As highlighted in \citet{immer2021improving}, computing this Hessian is often infeasible and in practice it is common to adopt the
@@
 \begin{align}
- \nabla^{2}_{\vw\vw} \log p(\vy \mid f_{\vw}(\vx)) \approx \Jac{\vw}{\vx}^{\top} \nabla_{\vf\vf}^{2}\log(\vy\mid\vf) \Jac{\vw}{\vx}.
+ \nabla^{2}_{\vw\vw} \log p(\vy \mid f_{\vw}(\MX)) \approx \Jac{\vw}{\MX}^{\top} \nabla_{\vf\vf}^{2}\log(\vy\mid\vf) \Jac{\vw}{\MX}.
   \nonumber
 \end{align}
-where the Jacobian is given by $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{1 \times P}$.
+where the Jacobian is given by $\Jac{\weights}{\vx} \coloneqq \left[ \nabla_\weights f_\weights(\vx)\right]^\top \in \R^{C \times P}$.
 % \textbf{Laplace-GGN converts BNN into GLM}
@@
 \begin{align} \label{eq-glm}
-  p_{\text{\sc GLM}}(y_{i} \mid \vx, \mathcal{D}) &= \E_{q(\vw)} \left[ p(y_{i} \mid f_{\vw^{*}}^{\text{lin}}(\vx))\right]. %\nonumber \\
+  p_{\text{\sc GLM}}(y_{i} \mid \vx_{i}, \mathcal{D}) &= \E_{q(\vw)} \left[ p(y_{i} \mid f_{\vw^{*}}^{\text{lin}}(\vx_{i}))\right]. %\nonumber \\
   % &\approx \frac{1}{S} \sum_{s} p(\vy \mid f_{\vw_{s}}^{\text{lin}}(\vx)), \quad \vw_{s} \sim q(\vw)
@@
 \begin{align} \label{eq-gp-pred-immer}
-  p_{\text{\sc GP}}(y_{i} \mid \vx, \mathcal{D}) &= \E_{q(f_{i})} \left[ p(y_{i} \mid f_{i} )\right],
+  p_{\text{\sc GP}}(y_{i} \mid \vx_{i}, \mathcal{D}) &= \E_{q(f_{i})} \left[ p(y_{i} \mid f_{i} )\right],
 \end{align}
@@
 and $f_i = f_\vw(\vx_i)$ is the function output at $\vx_i$.
-The $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{N \times N}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where
+The $ij$\textsuperscript{th} entry of matrix $\MKxx \in \R^{N \times N}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ is a vector where
 each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, $k_{ii} = \kappa(\vx_i, \vx_i)$ and $\bm\Lambda = - \nabla^2_{\vf \vf}\log p(\vy \mid \vf)$ can be interpreted as per-input noise.
@@
 
-\textbf{Sparse Gaussian processes}
-The GP formulation from \citet{immer2021improving} (shown in \cref{eq-gp-pred-immer})
+\textbf{Sparse GPs}
+The GP formulation from \citet{immer2021improving} (\cref{eq-gp-pred-immer})
 requires inverting an $N\times N$ matrix which has complexity $O(N^3)$.
@@
 Sparse GPs reduce the computational complexity by representing the GP as a low-rank approximation at a set of inducing
-inputs $\vz \in \R^{D}$ with corresponding inducing variables $\vu = f(\vz)$ \citep[see][for an early overview]{quinonero2005unifying}.
-The approach by \citet{titsias2009variational} \citep[also used in the DTC approximation, see][]{quinonero2005unifying},
+inputs $\MZ = \{\vz_{j} \}_{j=1}^{M} \in \R^{M \times D}$ with corresponding inducing variables $\vu = f(\MZ)$ \citep[see][for an early overview]{quinonero2005unifying}.
+The approach by \citet{titsias2009variational} (also used in the DTC approximation),
 defines the marginal predictive distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) \, q(\vu) \, \mathrm{d}\vu$ where
@@
 \begin{align}
-  \myexpect_{q_{\vu}(f_i)}[f_i] &= f_{\vw^{*}}(\vx_{i}) + \vk_{\vz i}^{\top}\MKzz^{-1}(\vm - f_{\vw^{*}}(\vz)), \\
+  \myexpect_{q_{\vu}(f_i)}[f_i] &= f_{\vw^{*}}(\vx_{i}) + \vk_{\vz i}^{\top}\MKzz^{-1}(\vm - f_{\vw^{*}}(\MZ)), \\
   \mathrm{Var}_{q_{\vu}(f_i)}[f_i] &= k_{ii} - \vk_{\vx i}^\top ( \MKzz -  \MKzz^{-1}\MS  \MKzz^{-1}))^{-1} \vk_{\vx i},  \nonumber
@@
 \end{subequations}
-where $\MKzz$ and $\vkzs$ are defined similarly to $\MKxx$ and $\vk_{\vx i}$ but over the inducing points $\{\vz_j\}_{i=1}^M=\vz \in \R^{M \times D}$.%, instead of the full data set $\dataset$.
+where $\MKzz$ and $\vkzs$ are defined similarly to $\MKxx$ and $\vk_{\vx i}$ but over the inducing points $\MZ$.%, instead of the full data set $\dataset$.
 % To the best of our knowledge, there are no methods that convert NNs to sparse GPs.
-It is worth noting that the parameters of the variational posterior ($\vm$ and $\MS$) are usually obtained via variational
+Note that the parameters of the variational posterior ($\vm$ and $\MS$) are usually obtained via variational
 inference, which requires further optimization.% and is non trivial in the NN setting.
@@
 
-We highlight that \our differs from the GP subset method from \citet{immer2021improving}, which results in several advantages.
+We highlight that \our differs from the GP subset from \citet{immer2021improving}, which results in several advantages.
 First, \our leverages a dual parameterization to construct a sparse GP, which captures information from the entire data set.
-In contrast, \citet{immer2021improving} utilize a subset of the data points which ignores information from the rest of the data set.
+In contrast, \citet{immer2021improving} utilize a data subset which ignores information from the rest of the data set.
 % It is also worth noting that our sparsification via dual parameters does not require any further optimization, we do not need to retrain a separate sparse GP.
 Second, \our makes predictions with the GP mean, whereas \citet{immer2021improving} center predictions around NN predictions $f_{\vw^*}(\cdot)$.
-As such, \our can incorporate new data without retraining (\ie, condition on new data) whilst the GP subset method cannot.
+As such, \our can incorporate new data without retraining whilst the GP subset cannot.
 
 To the best of our knowledge, we are the first to formulate a dual GP from a NN.
-Our dual parameterization has two main benefits: {\em (i)}~it enables us to construct a sparse GP without requiring us to perform further optimization, and {\em (ii)}~it enables us to incorporate new data without retraining (\ie, condition on new data) using \cref{eq:dual_sparse}.
+Our dual parameterization has two main benefits: {\em (i)}~it enables us to construct a sparse GP without requiring us to perform further optimization, and {\em (ii)}~it enables us to incorporate new data without retraining by conditioning on new data (using \cref{eq:dual_sparse}).
 
@@
 We trained the NN using Adam \cite{adam} with a learning rate of $10^{-4}$ and a batch size of $128$.
-Training was stopped when the validation NLPD stopped decreasing after 1000 steps.
+Training was stopped when the validation negative log predictive density (NLPD) stopped decreasing after 1000 steps.
 The checkpoint with the lowest NLPD was the NN MAP.

### 2023-09-16 papers/iclr-2024/main.tex
minor
Start changing citation style to name-year

@@
 % \usepackage[colorlinks=true,linkcolor=black,allcolors=black,urlcolor=black,citecolor=black]{hyperref}
-\usepackage[colorlinks=true,linkcolor=blue,allcolors=blue,urlcolor=black,citecolor=blue]{hyperref}
+\definecolor{darkblue}{rgb}{0,0,0.5}
+\usepackage[colorlinks=true,linkcolor=darkblue,allcolors=darkblue,urlcolor=black,citecolor=darkblue]{hyperref}
 \usepackage{url}
+
+\renewcommand{\cite}[1]{\textbf{\color{red}DO NOT USE CITE for #1 USE CITEP/CITET.}}
 
@@
 Secondly, how to update the weights of an already trained model with new batches of data without compromising the performance on past data?
-These questions become central when applied to sequential learning paradigms, such as continual learning (CL, \citep{parisi2019continual, de2021continual}) and reinforcement learning (RL, \cite{sutton2018reinforcement}).
-In CL, access to the previous data is lost, and then the challenge is retaining a compact representation of the problem to alleviate forgetting over the life-long learning horizon~\cite{mccloskey1989catastrophic}.
+These questions become central when applied to sequential learning paradigms, such as continual learning \citep[CL,][]{parisi2019continual, de2021continual} and reinforcement learning \citep[RL,][]{sutton2018reinforcement}.
+In CL, access to the previous data is lost, and then the challenge is retaining a compact representation of the problem to alleviate forgetting over the life-long learning horizon~\citep{mccloskey1989catastrophic}.
 Similarly, in RL, the model must adapt to environmental observations through exploration, while leveraging prediction uncertainties to assess potential future paths.\looseness-1
@@
 %Current state of affairs
-Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) apply a Laplace-GGN approximation to convert trained neural networks into Bayesian neural networks, that can provide uncertainty without sacrificing additional resources to training \cite{foong2019between}.
-Furthermore, the resultant weight-space posterior can be converted to the function-space as shown in \cite{khan2019approximate, immer2021improving}.
-The function-space representation allows for a principled mathematical approach for analyzing its behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{foong2019between}.
-These methods rely on the linearization of the neural network and the resultant neural tangent kernel (NTK, \cite{jacot2018neural}).
-The neural network is characterized in function-space by its first two moment functions, a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}).
+Recent techniques  \citep[\eg,][]{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable} apply a Laplace-GGN approximation to convert trained neural networks into Bayesian neural networks, that can provide uncertainty without sacrificing additional resources to training \citep{foong2019between}.
+Furthermore, the resultant weight-space posterior can be converted to the function-space as shown in \citet{khan2019approximate, immer2021improving}.
+The function-space representation allows for a principled mathematical approach for analyzing its behaviour \citep{cho2009kernel,meronen2020stationary}, performing probabilistic inference \citep{khan2019approximate}, and quantifying uncertainty in neural networks \citep{foong2019between}.
+These methods rely on the linearization of the neural network and the resultant neural tangent kernel \citep[NTK,][]{jacot2018neural}.
+The neural network is characterized in function-space by its first two moment functions, a mean function and covariance function (or kernel)---defining a Gaussian process  \citep[GP,][]{rasmussen2006gaussian}.
 GPs provide a widely-used probabilistic toolkit with principled uncertainty estimates.
@@
 %Need for adaptive learning methods + failures with current methods
-Given an approximate inference technique, we demonstrate that the neural network emits `dual' parameters which are the building blocks of a GP~\cite{csato2002sparse, adam2021dual, chang2020fast} .
-In contrast to previous work that utilizes subsets of training data \cite{immer2021scalable},
+Given an approximate inference technique, we demonstrate that the neural network emits `dual' parameters which are the building blocks of a GP~\citep{csato2002sparse, adam2021dual, chang2020fast} .
+In contrast to previous work that utilizes subsets of training data \citep{immer2021scalable},
 this parameterization allows capturing the contributions from {\em all} data points into a sparse representation, essential for predictive uncertainty.
@@
 %, a feature not present in previous approaches, while avoiding the notorious cubic complexity of vanilla GPs.
-Through the dual parameter formulation, we establish a connection between the neural network, full GPs, and a sparse approximation similar to sparse variational GPs~\cite{titsias2009variational}.
+Through the dual parameter formulation, we establish a connection between the neural network, full GPs, and a sparse approximation similar to sparse variational GPs~\citep{titsias2009variational}.
 We refer to our method as Sparse Function-space Representation (\our)---a sparse GP derived from a trained neural network.
@@
 \textbf{Bayesian deep learning}
-Probabilistic methods in deep learning~\cite{Wilson:ensembles,neal1995bayesian} have recently gained increasing attention in the machine learning community as a means for uncertainty quantification (\eg, \cite{kendall2017what,wilson2020bayes}) and model selection (\eg,~\cite{immer2021scalable,antoran2022marginal}) with advancements in prior specification (\eg, \cite{cho2009kernel,meronen2020stationary,meronen2021periodic,fortuin2021bayesian,nalisnick2018do}) and efficient approximate inference under the specified model.
+Probabilistic methods in deep learning~\citep{Wilson:ensembles,neal1995bayesian} have recently gained increasing attention in the machine learning community as a means for uncertainty quantification (\eg, \cite{kendall2017what,wilson2020bayes}) and model selection (\eg,~\cite{immer2021scalable,antoran2022marginal}) with advancements in prior specification (\eg, \cite{cho2009kernel,meronen2020stationary,meronen2021periodic,fortuin2021bayesian,nalisnick2018do}) and efficient approximate inference under the specified model.
 Calculating the posterior distribution of a Bayesian neural network is usually intractable, and approximate inference techniques need to be used, such as variational inference \cite{blei2017variational}, deep ensembles \cite{lakshminarayanan2017simple}, MC dropout \cite{gal2016dropout}, or Laplace approximation \cite{ritter2018kfac,kristiadi2020being,immer2021improving}---each with its own set of strengths and weaknesses.

### 2023-09-18 papers/iclr-2024/main.tex
added some citation stuff

@@
 \textbf{Bayesian deep learning}
-Probabilistic methods in deep learning~\citep{Wilson:ensembles,neal1995bayesian} have recently gained increasing attention in the machine learning community as a means for uncertainty quantification (\eg, \cite{kendall2017what,wilson2020bayes}) and model selection (\eg,~\cite{immer2021scalable,antoran2022marginal}) with advancements in prior specification (\eg, \cite{cho2009kernel,meronen2020stationary,meronen2021periodic,fortuin2021bayesian,nalisnick2018do}) and efficient approximate inference under the specified model.
-Calculating the posterior distribution of a Bayesian neural network is usually intractable, and approximate inference techniques need to be used, such as variational inference \cite{blei2017variational}, deep ensembles \cite{lakshminarayanan2017simple}, MC dropout \cite{gal2016dropout}, or Laplace approximation \cite{ritter2018kfac,kristiadi2020being,immer2021improving}---each with its own set of strengths and weaknesses.
+Probabilistic methods in deep learning~\citep{Wilson:ensembles,neal1995bayesian} have recently gained increasing attention in the machine learning community as a means for uncertainty quantification (\eg, \citep{kendall2017what,wilson2020bayes}) and model selection (\eg,~\citep{immer2021scalable,antoran2022marginal}) with advancements in prior specification (\eg, \cite{cho2009kernel,meronen2020stationary,meronen2021periodic,fortuin2021bayesian,nalisnick2018do}) and efficient approximate inference under the specified model.
+Calculating the posterior distribution of a Bayesian neural network is usually intractable, and approximate inference techniques need to be used, such as variational inference \citep{blei2017variational}, deep ensembles \citep{lakshminarayanan2017simple}, MC dropout \citep{gal2016dropout}, or Laplace approximation \cite{ritter2018kfac,kristiadi2020being,immer2021improving}---each with its own set of strengths and weaknesses.
 

### 2023-09-18 papers/iclr-2024/main.tex

@@
     % THE TABLE NUMBER ARE GENERATED BY A SCRIPT
-	\input{tables/uci.tex}
+	\input{tables/workshop_uci_table.tex}
 \end{table}
 
-\begin{figure}[t]
-  \centering\scriptsize
-  \setlength{\figurewidth}{.26\textwidth}
+\begin{figure*}[t]
+  % \centering\scriptsize
+  \centering\small
+  % \setlength{\figurewidth}{.18\textwidth}
+  \setlength{\figurewidth}{.27\textwidth}
   \setlength{\figureheight}{\figurewidth}
-  \pgfplotsset{axis on top,scale only axis,y tick label style={rotate=90}, x tick label style={font=\footnotesize},y tick label style={font=\footnotesize},title style={yshift=-4pt,font=\large}, y label style={font=\large},x label style={font=\large},grid=major, width=\figurewidth, height=\figureheight}
+  \pgfplotsset{axis on top,scale only axis,y tick label style={rotate=90}, x tick label style={font=\Large},y tick label style={font=\Large},title style={yshift=-4pt,font=\LARGE}, y label style={font=\Large},x label style={font=\LARGE},grid=major, width=\figurewidth, height=\figureheight}
   \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
-  \pgfplotsset{xlabel={$M$},ylabel style={yshift=-12pt}}
-  %
-  \begin{minipage}[t]{.17\textwidth}
+  \pgfplotsset{xlabel={$M$ as \% of $N$},ylabel style={yshift=-5pt},xlabel style={yshift=-5pt}}
+  %
+  \begin{minipage}[t]{.175\textwidth}
     \raggedleft
@@
   \hfill
-%  \begin{minipage}[t]{.16\textwidth}
+  % \begin{minipage}[t]{.12\textwidth}
   %   \raggedleft
@@
   % \hfill
-%  \begin{minipage}[t]{.16\textwidth}
+  % \begin{minipage}[t]{.12\textwidth}
   %   \raggedleft
@@
   % \hfill
-  \begin{minipage}[t]{.16\textwidth}
+  \begin{minipage}[t]{.155\textwidth}
     \raggedleft
@@
   \hfill
-  \begin{minipage}[t]{.16\textwidth}
+  \begin{minipage}[t]{.155\textwidth}
     \raggedleft
@@
   \newcommand{\myline}[1]{\protect\tikz[baseline=-.5ex,line width=1.6pt]\protect\draw[draw=#1](0,0)--(1.2em,0);}
-  \caption{Comparison of convergence in terms of number of inducing points $M$ in NLPD (mean over 10 seeds) on UCI classification tasks: \our (thick) vs.\ subsets (\cite{immer2021improving}, thin).
-Orange lines (\myline{darkorange25512714}) use the GP mean, whereas blue lines (\myline{steelblue31119180}) the NN MAP estimate as mean.
-Our \our converges fast for all cases.\looseness-1}
+  \caption{Comparison of convergence in terms of number of inducing points $M$ in NLPD (mean\textcolor{gray}{\footnotesize$\pm$std} over 5 seeds) on UCI classification tasks: \our (\myline{steelblue31119180}) vs.
+GP subset (\myline{darkorange25512714}).
+Our \our converges fast for all cases showing clear benefits of its ability to summarize all the data onto a sparse set of inducing points.
+The number of inducing points $M$ are specified as a percentage of the number of training data $N$.}
   \label{fig:uci}
   %\vspace*{-6pt}
-\end{figure}
+\end{figure*}
 
